### 2022-01-28 index.Rmd
Initial commit

---
title: "Preliminary results: Accelerating ORSF pilot study"
description: |
  Partial model fitting improves computation time and prognostic accuracy for the ORSF.
author:
  - name: Byron C. Jaeger
affiliation: Wake Forest School of Medicine
date: "`r Sys.Date()`"
output:
  distill::distill_article:
  toc: true
toc_depth: 2
code_folding: true
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE)

source(here::here("packages.R"))

source("R/sim_surv.R")

rspec <- round_spec() |> 
  round_using_magnitude(digits = c(3, 2, 2, 1),
                        breaks = c(1, 10, 100, Inf))

names(rspec) <- paste('table.glue', names(rspec), sep = '.')

options(rspec)

tar_load(names = data_results)

```

# Introduction

This document shows the full preliminary results that I have included in a response to reviewers for my submission to the Wake Forest Center for Biomedical Informatics Pilot Award. In my response, I present a table that aggregates results over three datasets. In this document, all three datasets are described and the results for each dataset are tabulated.

# Datasets

## Mayo Clinic Primary Biliary Cholangitis Data, N = 276

Primary sclerosing cholangitis is an autoimmune disease leading to destruction of the small bile ducts in the liver. Progression is slow but inexhortable, eventually leading to cirrhosis and liver decompensation. The condition has been recognised since at least 1851 and was named "primary biliary cirrhosis" in 1949. Because cirrhosis is a feature only of advanced disease, a change of its name to "primary biliary cholangitis" was proposed by patient advocacy groups in 2014.

This data is from the Mayo Clinic trial in PBC conducted between 1974 and 1984. A total of 424 PBC patients, referred to Mayo Clinic during that ten-year interval, met eligibility criteria for the randomized placebo controlled trial of the drug D-penicillamine. The first 312 cases in the data set participated in the randomized trial and contain largely complete data. The additional 112 cases did not participate in the clinical trial, but consented to have basic measurements recorded and to be followed for survival. Six of those cases were lost to follow-up shortly after diagnosis, so the data here are on an additional 106 cases as well as the 312 randomized participants. The `pbc_orsf` data includes 276 participants who had no missing data for the study covariates. The first 10 rows of the data are printed here:

```{r}
as_tibble(pbc_orsf)
```

## Rotterdam Breast Cancer Data, N = 2,982

The `rotterdam` data set includes 2982 primary breast cancers patients whose records were included in the Rotterdam tumor bank. These data sets are used in a paper by Royston and Altman that is referenced below. The first 10 rows of the data are printed here:

```{r}
as_tibble(survival::rotterdam)
```

## Simulated data with interactions, N = 5,000

A simulated dataset with normally distributed predictor variables was generated. Predictor variables $z_1$, $\dots$, $z_{10}$ were negatively associated with the outcome, and $x_1$, $\dots$, $x_{10}$ were positively associated with the outcome. Predictor variables $g_1$, $\dots$, $g_5$ were unrelated to the outcome, but each of the $g_i$ variables had an interaction effect with $x_i$ (i.e., $g_1$ interacted with $x_1$, $g_2$ interacted with $x_2$, and so on, with $g_5$ interacting with $x_5$). An example of these simulated data are presented below.

```{r}

as_tibble(sim_surv(n=10))

```

# Methods

I compare four different modeling techniques:

1. `aorsf` - the software I propose to develop further.

1. `obliqueRSF` - the software I previously developed for ORSFs.

1. `randomForestSRC` - A standard package for random forests.

1. `ranger` - Another standard package for random forests.

These techniques are compared based on their discrimination (C-statistic) and scaled Brier score, which are computed using the `riskRegression` package, and specifically `riskRegression::Score()`. Computational time required for model fitting and model predictions are also presented. Results are averaged over 25 runs of Monte-Carlo Cross-validation. In each run of Monte-Carlo Cross-validation, the current data are separated into a training and testing set, all modeling techniques are applied to the training set, and model predictions are evaluated in the testing set.

# Results

Overall, `aorsf` and `obliqueRSF` had the highest prognostic accuracy, but `aorsf` is __much__ faster. In addition, while `obliqueRSF` was more accurate overall than `ranger` and `randomForestSRC`, it was not as accurate as `aorsf`!

```{r}

results_overall <- data_results |> 
  group_by(model) |>
  summarize(
    across(
      .cols = c(cstat, IPA, time_fit, time_prd),
      .fns = list(mean = mean, sd = sd)
    )
  ) |> 
  mutate(data = 'Overall')

data_tbl <- data_results |> 
  group_by(model, data) |>
  summarize(
    across(
      .cols = c(cstat, IPA, time_fit, time_prd),
      .fns = list(mean = mean, sd = sd)
    )
  ) |> 
  bind_rows(results_overall) |> 
  group_by(data) |> 
  mutate(
    across(.cols = starts_with("time"), .fns = as.numeric),
    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf'],
    time_prd_ratio = time_prd_mean / time_prd_mean[model == 'aorsf']
  ) |> 
  transmute(
    model, 
    data = recode(
      data,
      'pbc_orsf' = 'Mayo Clinic Primary Biliary Cholangitis Data, N = 276',
      'rotterdam' = 'Rotterdam Breast Cancer Data, N = 2,982',
      'sim' = 'Simulated data with interactions, N = 5,000'
    ),
    cstat = table_glue("{cstat_mean} ({cstat_sd})"),
    ipa = table_glue("{IPA_mean} ({IPA_sd})"),
    time_fit_mean = format(round(time_fit_mean, 4), nsmall = 4),
    time_fit_ratio = table_value(time_fit_ratio),
    time_prd_mean = format(round(time_prd_mean, 4), nsmall = 4),
    time_prd_ratio = table_value(time_prd_ratio)
  )

gt(data_tbl, rowname_col = 'model', groupname_col = 'data') |> 
  cols_label(cstat = 'C-Statistic (SD)',
             ipa = 'Scaled Brier Score (SD)',
             time_fit_mean = 'Mean, seconds',
             time_fit_ratio = 'Ratio',
             time_prd_mean = 'Mean, seconds',
             time_prd_ratio = 'Ratio') |> 
  cols_align(align = 'center') |> 
  tab_spanner(label = 'Model prediction accuracy',
              columns = c('cstat', 'ipa')) |> 
  tab_spanner(label = 'Model fit time',
              columns = c('time_fit_mean', 'time_fit_ratio')) |> 
  tab_spanner(label = 'Risk prediction time',
              columns = c('time_prd_mean', 'time_prd_ratio'))

```

# Conclusion

The novelty of `aorsf` is its use of partially trained models in non-terminal nodes of decision trees. While `obliqueRSF` develops fully trained models, which require iteration until a convergence criteria is met, `aorsf` just completes one iteration and moves along. Initially I thought this computational shortcut would hurt the accuracy of the model, but the reality is that using partially trained models appears to improve the accuracy of the ORSF by increasing the diversity of trees in the ensemble.

# REFERENCES

1. Source for `pbc_orsf` data: T Therneau and P Grambsch (2000), Modeling Survival Data: Extending the Cox Model, Springer-Verlag, New York. ISBN: 0-387-98784-3.

1. Source for `rotterdam` data: Patrick Royston and Douglas Altman, External validation of a Cox prognostic model: principles and methods. BMC Medical Research Methodology 2013, 13:33

### 2022-01-28 R/model_fit.R

@@ -1,0 +1,40 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param type
+#' @param train
+model_fit <- function(type, train) {
+
+
+  message("fitting ", type, " model")
+
+  start_time <- Sys.time()
+
+  switch(
+    type,
+
+    'aorsf' = {
+      res <- orsf(Surv(time, status) ~ ., data = train)
+    },
+    'obliqueRSF' = {
+      res <- ORSF(train, ntree = 500, verbose = FALSE)
+    },
+    'randomForestSRC' = {
+      res <- rfsrc(Surv(time, status) ~ ., data = train)
+    },
+    'ranger' = {
+      res <- ranger(
+        Surv(time, status) ~ ., data = train, splitrule = 'extratrees'
+      )
+    }
+
+  )
+
+  end_time <- Sys.time()
+
+
+  list(model = res, time = end_time - start_time)
+
+}

### 2022-01-28 R/model_pred.R

@@ -1,0 +1,38 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param fit
+#' @param type
+#' @param test
+model_pred <- function(fit, type, test, pred_horizon) {
+
+
+  message("predicting risk with ", type, " model")
+
+  start_time <- Sys.time()
+
+  res <- switch(
+    type,
+
+    'aorsf' = {
+      predict(fit$model, new_data = test, pred_horizon = pred_horizon)
+    },
+    'obliqueRSF' = {
+      1-predict(fit$model, newdata = test, times = pred_horizon)
+    },
+    'randomForestSRC' = {
+      predictRisk(fit$model, newdata = test, times = pred_horizon)
+    },
+    'ranger' = {
+      predictRisk(fit$model, newdata = test, times = pred_horizon)
+    }
+
+  )
+
+  end_time <- Sys.time()
+
+  list(prediction = as.numeric(res), time = end_time - start_time)
+
+}

### 2022-01-28 packages.R

@@ -1,0 +1,16 @@
+## library() calls go here
+library(conflicted)
+library(dotenv)
+library(targets)
+library(tarchetypes)
+
+library(aorsf)
+library(survival)
+library(obliqueRSF)
+library(tidyverse)
+library(riskRegression)
+library(ranger)
+library(randomForestSRC)
+library(table.glue)
+library(gt)
+library(simsurv)

### 2022-03-07 index.Rmd
swap to berd app

@@
 ---
-title: "Preliminary results: Accelerating ORSF pilot study"
+title: "Variable Importance for Oblique Learning Ensembles of Trees (VIOLET)"
 description: |
-  Partial model fitting improves computation time and prognostic accuracy for the ORSF.
+  Preliminary results for BERD pilot application
 author:
@@
 rspec <- round_spec() |> 
-  round_using_magnitude(digits = c(3, 2, 2, 1),
+  round_using_magnitude(digits = c(3, 2, 1, 1),
                         breaks = c(1, 10, 100, Inf))
@@
 
-tar_load(names = data_results)
+tar_load(names = benchmark_vi_smry)
 
@@
 
-# Introduction
+## Introduction
 
-This document shows the full preliminary results that I have included in a response to reviewers for my submission to the Wake Forest Center for Biomedical Informatics Pilot Award.
-In my response, I present a table that aggregates results over three datasets.
-In this document, all three datasets are described and the results for each dataset are tabulated.
+This document shows the full preliminary results that I have included in my application for the Biostatistics, Epidemiology, and Research Design (BERD) Program's Methods Pilot Award.
+The data simulation process is described in full detail, followed by an outline of the proposed simulation study.
+Last, results are tabulated for each simulation scenario described, and also in aggregate form.
+The final aggregate table is presented in the BERD application.
 
-# Datasets
+## Data Simulation
 
-## Mayo Clinic Primary Biliary Cholangitis Data, N = 276
+A simulated data set with five types of predictor variables was generated in each run for the current simulation study. The size of each predictor set was fixed at 25 for our analysis.
 
-Primary sclerosing cholangitis is an autoimmune disease leading to destruction of the small bile ducts in the liver.
-Progression is slow but inexhortable, eventually leading to cirrhosis and liver decompensation.
-The condition has been recognised since at least 1851 and was named "primary biliary cirrhosis" in 1949.
-Because cirrhosis is a feature only of advanced disease, a change of its name to "primary biliary cholangitis" was proposed by patient advocacy groups in 2014.
+- $z$ (irrelevant) variables $z_1$, $\dots$, $z_{25}$ had no relationship with the outcome.
 
-This data is from the Mayo Clinic trial in PBC conducted between 1974 and 1984.
-A total of 424 PBC patients, referred to Mayo Clinic during that ten-year interval, met eligibility criteria for the randomized placebo controlled trial of the drug D-penicillamine.
-The first 312 cases in the data set participated in the randomized trial and contain largely complete data.
-The additional 112 cases did not participate in the clinical trial, but consented to have basic measurements recorded and to be followed for survival.
-Six of those cases were lost to follow-up shortly after diagnosis, so the data here are on an additional 106 cases as well as the 312 randomized participants.
-The `pbc_orsf` data includes 276 participants who had no missing data for the study covariates.
-The first 10 rows of the data are printed here:
+- $x$ (linear effect) variables $x_1$, $\dots$, $x_{25}$ had a linear relationship with the outcome.
 
-```{r}
-as_tibble(pbc_orsf)
-```
+- $w$ (non-linear effect) variables $w_1$, $\dots$, $w_{25}$ had a non-linear relationship with the outcome. The non-linear relationship followed a sinusoidal curve with varying period length.
 
-## Rotterdam Breast Cancer Data, N = 2,982
+- $g$ (conditional linear) variables $g_1$, $\dots$, $g_{25}$ had a conditional linear relationship with the outcome.
+In other words, for each $i \in \{1, \ldots, 25\}$,  $g_i$ had no relationship to the outcome, but $g_i * x_i$ was linearly related to the outcome.
 
-The `rotterdam` data set includes 2982 primary breast cancers patients whose records were included in the Rotterdam tumor bank.
-These data sets are used in a paper by Royston and Altman that is referenced below.
-The first 10 rows of the data are printed here:
+- $v$ (combination linear) variables $v_1$, $\dots$, $v_{25}$ had a combination linear relationship with the outcome.
+In other words, $v_1, v_2, v_3$ each had no effect on the outcome individually, but the latent variable $v_1*c_1* + v_2*c_2 + v_3 * c_3$ was linearly related to the outcome.
+Coefficients $c_i$ were generated at random uniformly from -1 to -0.5 and 0.5 to 1.
 
-```{r}
-as_tibble(survival::rotterdam)
-```
+__Mean and standard deviation__ The multivariate normal distribution that generated values for the predictor matrix had a mean of zero and standard deviation of 1 for each variable.
 
-## Simulated data with interactions, N = 5,000
+__Correlation__: The correlation among $z$ variables was allowed to be non-zero as was the correlation among $x$ variables and the correlation between $x$ and $z$ variables.
+For all non-zero correlations, a value was selected at random uniformly between a lower and upper boundary.
+We simulated five scenarios by varying the boundaries of correlation:
 
-A simulated dataset with normally distributed predictor variables was generated.
-Predictor variables $z_1$, $\dots$, $z_{10}$ were negatively associated with the outcome, and $x_1$, $\dots$, $x_{10}$ were positively associated with the outcome.
-Predictor variables $g_1$, $\dots$, $g_5$ were unrelated to the outcome, but each of the $g_i$ variables had an interaction effect with $x_i$ (i.e., $g_1$ interacted with $x_1$, $g_2$ interacted with $x_2$, and so on, with $g_5$ interacting with $x_5$).
-An example of these simulated data are presented below.
+1. lower bound: 0; upper bound: 0
+1. lower bound: -0.1; upper bound: 0.1
+2. lower bound: -0.2; upper bound: 0.2
+1. lower bound: -0.3; upper bound: 0.3
+3. lower bound: -0.4; upper bound: 0.4
+
+The correlations were generated symmetrically and were adjusted if needed to create the nearest positive definite covariance matrix using `Matrix::nearPD()`.
+
+__Effect sizes__: A total effect of 3 was distributed evenly across each predictor group.
+For example, with 25 $x$ predictors, the increase in log-hazard associated with a 1 unit increased in each $x$ variable was $3 / 25 = 0.12$.
+
+__Outcomes__: A censored outcome variable was generated with the `simsurv::simsurv()` using a predictor matrix that included all relevant predictors.
+After the outcome was generated the interactions, non-linear transformations, and linear combinations of relevant predictors were dropped from the data.
+
+### Demo and validation of simulated data
+
+Some tests of the simulated data are presented below.
+If you have no skepticism regarding the simulated data, you can safely skip this sub-section.
+For simplicity, we set the number of predictors to 3 for each predictor group.
+
+__Data generation__: There are no tests for this step, just a glimpse of the simulated set of data.
 
@@
 
-as_tibble(sim_surv(n=10))
+set.seed(329)
+
+ss_demo <-
+  sim_surv(
+    n_obs = 5000,
+    n_z = 3,
+    n_x = 3,
+    n_g = 3,
+    n_w = 3,
+    n_v = 3
+  )
+
+glimpse(ss_demo$data)
 
@@
 
-# Methods
-
-I compare four different modeling techniques:
-
-1. `aorsf` - the software I propose to develop further.
-
-1. `obliqueRSF` - the software I previously developed for ORSFs.
-
-1. `randomForestSRC` - A standard package for random forests.
-
-1. `ranger` - Another standard package for random forests.
-
-These techniques are compared based on their discrimination (C-statistic) and scaled Brier score, which are computed using the `riskRegression` package, and specifically `riskRegression::Score()`.
-Computational time required for model fitting and model predictions are also presented.
-Results are averaged over 25 runs of Monte-Carlo Cross-validation.
-In each run of Monte-Carlo Cross-validation, the current data are separated into a training and testing set, all modeling techniques are applied to the training set, and model predictions are evaluated in the testing set.
-
-# Results
-
-Overall, `aorsf` and `obliqueRSF` had the highest prognostic accuracy, but `aorsf` is __much__ faster.
-In addition, while `obliqueRSF` was more accurate overall than `ranger` and `randomForestSRC`, it was not as accurate as `aorsf`!
+__Column means__: This test verifies that the mean of each predictor is close to zero, and that roughly 40% of outcomes were censored.
 
@@
 
-results_overall <- data_results |> 
+data_sim <- ss_demo$data
+
+data_sim$true_v <- 
+  with(
+    data_sim,
+      v1 * ss_demo$coefs_lc[[1]][1] + 
+      v2 * ss_demo$coefs_lc[[1]][2] + 
+      v3 * ss_demo$coefs_lc[[1]][3] 
+  )
+
+data_means <- apply(data_sim, 2, mean) |> 
+  round(3) |> 
+  enframe()
+
+# we can see that the mean of each predictor is close to zero, and that roughly 40% of outcomes were censored.
+data_means
+
+```
+
+__Effects detected__: This test verifies that, when the oracle model is used, an effect is only detected for variables that have a relationship to the outcome.
+
+```{r}
+
+dd <- datadist(data_sim)
+options(datadist = dd)
+
+mdl <- cph(
+  Surv(time, status) ~ 
+    # z variables; no effect should be detected
+    z1 + z2 + z3 +
+    # x variables; effect should be detected
+    # g variables; no effect should be detected
+    # interaction between x and g; effect should be detected
+    x1*g1 + x2*g2 + x3*g3 + 
+    # w variables; effect should be detected and should be nonlinear
+    rcs(w1) + rcs(w2) + rcs(w3) + 
+    # v variables; no effect should be detected for individual
+    # variables v1, v2, and v3, but the linear combination of
+    # these variables should have a detectable effect.
+    # note: v1 is not included due to co-linearity 
+    v2 + v3 + true_v,
+  data = data_sim
+)
+
+# All expectations outlined above are met!
+anova(mdl)
+
+```
+
+__Effect size estimation for linear effects__: This test verifies that, when the oracle model is used, the estimated effect sizes for variables with linear effects are consistent with the effect sizes used to simulate the data.
+
+```{r}
+
+effects_expected <- c("x1" = 1, 
+                      "x2" = 1, 
+                      "x3" = 1,
+                      "g1" = 0,
+                      "g2" = 0,
+                      "g3" = 0,
+                      "x1 * g1" = 1,       
+                      "x2 * g2" = 1,       
+                      "x3 * g3" = 1, 
+                      "v2" = 0,
+                      "v3" = 0,
+                      "true_v" = 1)
+
+effects_observed <- coef(mdl)[names(effects_expected)]
+
+# the differences between observed and expected estimates is small
+abs(effects_expected - effects_observed) |> 
+  enframe(name = 'predictor',
+          value = 'bias')
+
+```
+
+__Effect size estimation for non-linear effects__: This test verifies that, when the oracle model is used, the estimated effect sizes for variables with non-linear effects are consistent with the effect sizes used to simulate the data.
+
+```{r}
+
+data_gg <- 
+  list(w1 = as.data.frame(Predict(mdl, w1)) |> select(x=w1, yhat),
+       w2 = as.data.frame(Predict(mdl, w2)) |> select(x=w2, yhat),
+       w3 = as.data.frame(Predict(mdl, w3)) |> select(x=w3, yhat)) |> 
+  bind_rows(.id = 'xvar') |> 
+  filter(x > -2.5, x < 2.5) |> 
+  mutate(xvar = recode(xvar,
+                       w1 = "Non-linear variable: w1",
+                       w2 = "Non-linear variable: w2",
+                       w3 = "Non-linear variable: w3")) |> 
+  as_tibble()
+
+# We expect increasing wiggle from left to right.
+
+ggplot(data_gg) + 
+  aes(x = x, y = yhat) + 
+  geom_line() + 
+  facet_wrap(~ xvar) + 
+  theme_bw() + 
+  labs(x = 'W value', y = 'Estimated log-hazard')
+
+```
+
+These results verify that the simulated data set has the expected properties 
+# Simulation Study
+
+I compare four different techniques to measure variable importance (VI).
+
+1. `Negation importance`: the method I propose to develop further with this pilot application. This is computed using an oblique random survival forest model.
+
+1. `ANOVA importance`: A method introduced by Menze et al. This is computed using an oblique random survival forest model.
+
+1. `SHAP importance`: A method introduced by Lundberg et al. SHAP importance is widely regarded as a gold standard due to its excellent asymptotic properties. This is computed using a boosting model.
+
+1. `Permutation importance`: A method introduced by Leo Breiman. This is computed using a standard random survival forest model.
+
+__Evaluation of variable importance techniques__: VI techniques are compared based on their discrimination (C-statistic) between relevant and irrelevant predictor variables.
+The relevant predictor variables are those that have a relationship to the outcome ($x$, $w$, $g$, and $v$ variables), and the irrelevant variables are those with no relationship to the outcome, i.e.
+the $z$ variables.
+This is equivalent to assigning a binary outcome to each variable: 1 if it is relevant, 0 otherwise, and then computing a C-statistic for discrimination of the relevant versus irrelevant variables using variable importance as a 'prediction' for the variables.
+
+__Details on C-statistic computation:__ The C-statistic is computed using `yardstick::roc_auc`, which wraps `pROC::roc`.
+To illustrate, if a variable importance metric assigned higher importance for all of the $x$ variables compared to all the $z$ variables, it would have a C-statistic of 1 for the $x$ variables.
+
+## Results
+
+Table 1: Discrimination between relevant and irrelevant predictor variables for each VI technique in 6 different simulated scenarios.
+Cells that are highlighted with a light blue color indicate which variable importance technique had the best discrimination for a given sample size, correlation setting, and variable type.
+For example, ANOVA importance had the best discrimination for linear effects with N = 2,500 and zero correlation between the linear effects and irrelevant variables.
+However, when the correlation between linear effects and irrelevant variables was non-zero, negation importance had the best discrimination across all scenarios and for each effect type.
+Given the low likelihood of ever having a real dataset with zero correlation between the predictor variables, these data suggest that negation importance can be very beneficial in applied settings.
+
+```{r}
+
+data_gt <-  
+  benchmark_vi_smry |>
+  ungroup() |> 
+  mutate(xcorr = recode(xcorr, 
+                        '0.0' = '|Corr(linear effects, irrelevant effect)| = 0',
+                        '0.1' = '|Corr(linear effects, irrelevant effect)| \u2264 0.10',
+                        '0.2' = '|Corr(linear effects, irrelevant effect)| \u2264 0.20',
+                        '0.3' = '|Corr(linear effects, irrelevant effect)| \u2264 0.30',
+                        '0.4' = '|Corr(linear effects, irrelevant effect)| \u2264 0.40'),
+         model = recode(model,
+                        'aorsf' = 'Negation importance',
+                        'aorsf_menze' = 'ANOVA importance',
+                        'xgboost' = 'SHAP importance',
+                        'randomForestSRC' = 'Permutation importance')) |> 
+  select(n_obs, model, xcorr, overall, x, w, g, v) |> 
+  pivot_wider(names_from = n_obs, 
+              values_from = c(overall, x, w, g, v)) |> 
+  select(xcorr,
+         model,
+         overall_2500,
+         x_2500,
+         w_2500,
+         g_2500,
+         v_2500,
+         overall_5000,
+         x_5000,
+         w_5000,
+         g_5000,
+         v_5000) |> 
+  arrange(xcorr, model)
+
+cols_to_highlight <- c("overall_2500",
+                       "x_2500",
+                       "w_2500",
+                       "g_2500",
+                       "v_2500",
+                       "overall_5000",
+                       "x_5000",
+                       "w_5000",
+                       "g_5000",
+                       "v_5000")
+
+max_row_positions <- data_gt |>
+  group_by(xcorr) |> 
+  summarize(across(all_of(cols_to_highlight), which.max)) |> 
+  mutate(xcorr = c(0, 4, 8, 12, 16)) |> 
+  pivot_longer(cols = -xcorr) |> 
+  mutate(value = value + xcorr) |> 
+  select(name, value)
+
+code_styles <- map2_chr(
+  .x = max_row_positions$value,
+  .y = max_row_positions$name,
+  .f = ~ paste0(
+    "|>",
+    "tab_style(style = cell_fill(color = 'lightblue')",
+    ", locations = cells_body(columns = ", .y, ",rows = ", .x, "))"
+  )
+)
+
+results_tbl_1 <- data_gt |> 
+  mutate(across(ends_with("0"), ~table_value(100*.x))) |> 
+  gt(rowname_col = 'model', groupname_col = 'xcorr') |> 
+  tab_stubhead(label = 'Variable importance technique') |> 
+  tab_spanner(label = 'N = 2,500', 
+              columns = c("overall_2500",
+                          "x_2500",
+                          "w_2500",
+                          "g_2500",
+                          "v_2500")) |> 
+  tab_spanner(label = 'N = 5,000', 
+              columns = c("overall_5000",
+                          "x_5000",
+                          "w_5000",
+                          "g_5000",
+                          "v_5000")) |> 
+  cols_label(
+    overall_2500 = "All effects",
+    x_2500 = "Linear effects",
+    w_2500 = "Non-linear effects",
+    g_2500 = "Interaction effects",
+    v_2500 = "Combo effects",
+    overall_5000 = "All effects",
+    x_5000 = "Linear effects",
+    w_5000 = "Non-linear effects",
+    g_5000 = "Interaction effects",
+    v_5000 = "Combo effects"
+  ) |> 
+  cols_align(align = 'center')
+
+code_to_run <- paste0('results_tbl_1', 
+                      paste0(code_styles, collapse = ''))
+
+eval(rlang::parse_expr(code_to_run))
+
+```
+
+### Overall summary
+
+Due to space constraints, the pilot application presents a summary of the results in Table 1.
+This summary aggregates the results from the 6 scenarios presented above, and it is shown here here to verify.
+
+Table 2: Discrimination between relevant and irrelevant predictor variables for each VI technique.
+Negation importance obtains the highest C-statistic for each variable type except non-linear variables, where it closely trails SHAP importance.
+
+```{r}
+
+data_fig <- benchmark_vi_smry |>
+  ungroup() |> 
+  mutate(model = recode(model,
+                        'aorsf' = 'Negation importance',
+                        'aorsf_menze' = 'ANOVA importance',
+                        'xgboost' = 'SHAP importance',
+                        'randomForestSRC' = 'Permutation importance')) |> 
+  select(n_obs, model, xcorr, overall) |> 
+  group_by(n_obs, model, xcorr) |> 
+  summarize(value = mean(overall))
+
+ggplot(data_fig) + 
+  aes(x = xcorr, y = value, col = model) + 
+  geom_line() +
+  facet_wrap(~n_obs)
+
+results_tbl_2 <- benchmark_vi_smry |>
+  ungroup() |> 
+  mutate(model = recode(model,
+                        'aorsf' = 'Negation importance',
+                        'aorsf_menze' = 'ANOVA importance',
+                        'xgboost' = 'SHAP importance',
+                        'randomForestSRC' = 'Permutation importance')) |> 
+  select(n_obs, model, xcorr, overall, x, w, g, v) |> 
   group_by(model) |> 
@@
     across(
-      .cols = c(cstat, IPA, time_fit, time_prd),
-      .fns = list(mean = mean, sd = sd)
+      c(overall, x, w, g, v),
+      ~table_value(mean(.x))
     )
   ) |> 
-  mutate(data = 'Overall')
+  gt(rowname_col = 'model') |> 
+  tab_stubhead(label = 'Variable importance technique') |> 
+  cols_label(
+    overall = "Overall",
+    x = "Linear effects",
+    w = "Non-linear effects",
+    g = "Interaction effects",
+    v = "Combo effects"
+  ) |> 
+  cols_align(align = 'center')
 
-data_tbl <- data_results |> 
-  group_by(model, data) |>
-  summarize(
-    across(
-      .cols = c(cstat, IPA, time_fit, time_prd),
-      .fns = list(mean = mean, sd = sd)
-    )
-  ) |> 
-  bind_rows(results_overall) |> 
-  group_by(data) |> 
-  mutate(
-    across(.cols = starts_with("time"), .fns = as.numeric),
-    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf'],
-    time_prd_ratio = time_prd_mean / time_prd_mean[model == 'aorsf']
-  ) |> 
-  transmute(
-    model, 
-    data = recode(
-      data,
-      'pbc_orsf' = 'Mayo Clinic Primary Biliary Cholangitis Data, N = 276',
-      'rotterdam' = 'Rotterdam Breast Cancer Data, N = 2,982',
-      'sim' = 'Simulated data with interactions, N = 5,000'
-    ),
-    cstat = table_glue("{cstat_mean} ({cstat_sd})"),
-    ipa = table_glue("{IPA_mean} ({IPA_sd})"),
-    time_fit_mean = format(round(time_fit_mean, 4), nsmall = 4),
-    time_fit_ratio = table_value(time_fit_ratio),
-    time_prd_mean = format(round(time_prd_mean, 4), nsmall = 4),
-    time_prd_ratio = table_value(time_prd_ratio)
-  )
-
-gt(data_tbl, rowname_col = 'model', groupname_col = 'data') |> 
-  cols_label(cstat = 'C-Statistic (SD)',
-             ipa = 'Scaled Brier Score (SD)',
-             time_fit_mean = 'Mean, seconds',
-             time_fit_ratio = 'Ratio',
-             time_prd_mean = 'Mean, seconds',
-             time_prd_ratio = 'Ratio') |> 
-  cols_align(align = 'center') |> 
-  tab_spanner(label = 'Model prediction accuracy',
-              columns = c('cstat', 'ipa')) |> 
-  tab_spanner(label = 'Model fit time',
-              columns = c('time_fit_mean', 'time_fit_ratio')) |> 
-  tab_spanner(label = 'Risk prediction time',
-              columns = c('time_prd_mean', 'time_prd_ratio'))
+results_tbl_2
 
@@
 
-The novelty of `aorsf` is its use of partially trained models in non-terminal nodes of decision trees.
-While `obliqueRSF` develops fully trained models, which require iteration until a convergence criteria is met, `aorsf` just completes one iteration and moves along.
-Initially I thought this computational shortcut would hurt the accuracy of the model, but the reality is that using partially trained models appears to improve the accuracy of the ORSF by increasing the diversity of trees in the ensemble.
+The strengths of negation importance are:
+
+1.
+It can be computed for any type of oblique random forest, as it only leverages the linear coefficients in the nodes.
+(ANOVA importance requires a p-value be computed for each variable in each node).
+
+1. It penalizes over-fitting by evaluating performance in out-of-bag data.
+
+1. In the current simulation, it had the most reliable estimate of variable importance when irrelevant variables were correlated to relevant ones.
 

### 2022-03-07 R/bench_pred.R

@@ -1,0 +1,119 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param data_source
+#' @param run_seed
+bench_pred <- function(data_source, run_seed, test_prop = 1/2) {
+
+  switch(
+
+    data_source,
+
+    'pbc_orsf' = {
+      data_all <- aorsf::pbc_orsf |>
+        select(-id) |>
+        as_tibble()
+    },
+
+    'rotterdam' = {
+      data_all <- survival::rotterdam |>
+        mutate(time = pmin(rtime, dtime),
+               status = if_else(rtime < dtime, recur, death)) |>
+        select(age, meno, size, grade, nodes, pgr, er, hormon,
+               time, status) |>
+        as_tibble()
+    },
+
+    'actg' = {
+
+      data_all <- mlr3proba::actg |>
+        as_tibble() |>
+        select(-id, -time_d, -censor_d) |>
+        rename(status = censor)
+
+    },
+
+    'sim' = {
+
+      data_all <- sim_surv() |>
+        getElement('data')
+
+    }
+
+  )
+
+  pred_horizon <- median(data_all$time)
+
+  set.seed(run_seed)
+
+  test_index <- sample(x = seq(nrow(data_all)),
+                       size = round(nrow(data_all) * test_prop),
+                       replace = FALSE)
+
+  train <- data_all[-test_index, ]
+  test <- data_all[test_index, ]
+
+  models <- set_names(
+    c(
+      'aorsf',
+      # 'obliqueRSF',
+      'xgboost',
+      'randomForestSRC',
+      'ranger'
+    )
+  )
+
+  fits <- map(models, model_fit, train = as.data.frame(train))
+
+  prds <- map2(.x = fits,
+               .y = models,
+               .f = model_pred,
+               test = as.data.frame(test),
+               pred_horizon = pred_horizon)
+
+  times_fit <- fits |>
+    map_dfr('time') |>
+    mutate(action = 'fit')
+
+  times_prd <- prds |>
+    map_dfr('time') |>
+    mutate(action = 'prd')
+
+  times <-
+    bind_rows(times_fit, times_prd) |>
+    mutate(data = data_source, run = run_seed) |>
+    pivot_longer(cols = any_of(models),
+                 names_to = 'model',
+                 values_to = 'time') |>
+    pivot_wider(names_from = action,
[…]

### 2022-03-07 R/model_fit.R

@@ -18,12 +18,32 @@ model_fit <- function(type, train) {
     'aorsf' = {
       res <- orsf(Surv(time, status) ~ ., data = train)
     },
+
+    'xgboost' = {
+
+
+      xmat <- model.matrix(~. -1, data = train) |>
+        as_tibble() |>
+        as_sgb_data(status = status, time = time)
+
+
+      res <- sgb_fit(sgb_df = xmat,
+                     verbose = 0,
+                     params = list(max_depth=2,
+                                   eta = 0.01,
+                                   objective = 'survival:cox',
+                                   eval_metric = 'cox-nloglik'))
+
+    },
+
     'obliqueRSF' = {
       res <- ORSF(train, ntree = 500, verbose = FALSE)
     },
+
     'randomForestSRC' = {
       res <- rfsrc(Surv(time, status) ~ ., data = train)
     },
+
     'ranger' = {
       res <- ranger(
         Surv(time, status) ~ ., data = train, splitrule = 'extratrees'

### 2022-03-07 R/model_pred.R

@@ -19,12 +19,26 @@ model_pred <- function(fit, type, test, pred_horizon) {
     'aorsf' = {
       predict(fit$model, new_data = test, pred_horizon = pred_horizon)
     },
+
+    'xgboost' = {
+
+      .test <- model.matrix(~. -1L, data = test) |>
+        as_tibble() |>
+        select(-time, -status) |>
+        as.matrix()
+
+      1-predict(fit$model, new_data = .test, eval_times = pred_horizon)
+
+    },
+
     'obliqueRSF' = {
       1-predict(fit$model, newdata = test, times = pred_horizon)
     },
+
     'randomForestSRC' = {
       predictRisk(fit$model, newdata = test, times = pred_horizon)
     },
+
     'ranger' = {
       predictRisk(fit$model, newdata = test, times = pred_horizon)
     }

### 2022-03-07 R/model_varsel.R

@@ -1,0 +1,99 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param model
+#' @param train
+model_varsel <- function(model, train) {
+
+  stopifnot(ncol(train) > 2)
+
+  message("computing variable importance using ", model)
+
+  start_time <- Sys.time()
+
+  switch(
+    model,
+
+    'aorsf' = {
+
+      fit <- orsf(Surv(time, status) ~ .,
+                  data_train = train,
+                  importance = TRUE)
+
+      vi <- fit$importance
+
+
+    },
+
+    'aorsf_menze' = {
+
+      fit <- orsf(Surv(time, status) ~ ., data_train = train,
+                  control = orsf_control_cph(iter_max = 20))
+
+      vi <- orsf_vi_pvalue(fit)
+
+    },
+
+    'aorsf_pv' = {
+
+      fit <- orsf(Surv(time, status) ~ ., data_train = train,
+                  control = orsf_control_cph(iter_max = 20))
+      vi <- aorsf:::orsf_vi_pv(fit)
+
+    },
+
+    'xgboost' = {
+
+      xmat <- as.matrix(select(train, -time, -status))
+      ymat <- train$time
+      ymat[train$status == 0] <- ymat[train$status == 0] * (-1)
+
+      fit_cv <- xgb.cv(data = xmat,
+                       params = list(eta = 0.05),
+                       label = ymat, nfold=10,
+                       nrounds = 500,
+                       objective = 'survival:cox',
+                       eval_metric = 'cox-nloglik',
+                       verbose = FALSE,
+                       early_stopping_rounds = 25)
+
+      fit_final <- xgboost(data = xmat, label = ymat,
+                           params = list(eta = 0.02),
+                           nrounds = fit_cv$best_iteration,
+                           objective = 'survival:cox',
+                           eval_metric = 'cox-nloglik',
+                           verbose = FALSE)
+
+      fit_shap <-
+        predict(fit_final, newdata = xmat, predcontrib = TRUE) |>
+        apply(MARGIN = 2, function(x) mean(abs(x)))
+
+      vi <- fit_shap[-which(names(fit_shap)=='BIAS')]
+
+
+    },
+
+    'randomForestSRC' = {
+      fit <- rfsrc(Surv(time, status) ~ ., data = train, importance = TRUE)
+      vi <- fit$importance
+
[…]

### 2022-03-07 R/sim_surv.R

@@ -4,79 +4,227 @@
 #'
 #' @title
 
-sim_surv <- function(nobs = 5000, pred_horiz = 2.5) {
+sim_surv <- function(n_obs = 2500,
+                     n_z = 25,
+                     n_x = 25,
+                     n_g = 25,
+                     n_w = 25,
+                     n_v = 25,
+                     correlated_x = 0,
+                     pred_horiz = 2.5) {
 
-  covs <- data.frame(z1 = rnorm(nobs),
-                     z2 = rnorm(nobs),
-                     z3 = rnorm(nobs),
-                     z4 = rnorm(nobs),
-                     z5 = rnorm(nobs),
-                     z6 = rnorm(nobs),
-                     z7 = rnorm(nobs),
-                     z8 = rnorm(nobs),
-                     z9 = rnorm(nobs),
-                     z10 = rnorm(nobs),
-                     x1 = rnorm(nobs),
-                     x2 = rnorm(nobs),
-                     x3 = rnorm(nobs),
-                     x4 = rnorm(nobs),
-                     x5 = rnorm(nobs),
-                     x6 = rnorm(nobs),
-                     x7 = rnorm(nobs),
-                     x8 = rnorm(nobs),
-                     x9 = rnorm(nobs),
-                     x10 = rnorm(nobs),
-                     g1 = rnorm(nobs), #rbinom(nobs, 1, 1/2),
-                     g2 = rnorm(nobs), #rbinom(nobs, 1, 1/2),
-                     g3 = rnorm(nobs), #rbinom(nobs, 1, 1/2),
-                     g4 = rnorm(nobs), #rbinom(nobs, 1, 1/2),
-                     g5 = rnorm(nobs)) #rbinom(nobs, 1, 1/2))
+  stopifnot(n_x > 0)
+  stopifnot(n_z > 0)
+  stopifnot(n_v >= 3)
 
-  covs$int_1 = with(covs, x1 * g1)
-  covs$int_2 = with(covs, x2 * g2)
-  covs$int_3 = with(covs, x3 * g3)
-  covs$int_4 = with(covs, x4 * g4)
-  covs$int_5 = with(covs, x5 * g5)
+  stopifnot(n_x >= n_g)
+
+  z_names <- paste0('z', seq(n_z))
+  x_names <- paste0('x', seq(n_x))
+  g_names <- paste0('g', seq(n_g))
+  w_names <- paste0('w', seq(n_w))
[…]

### 2022-03-07 R/varsel_run.R

@@ -5,7 +5,10 @@
 #' @title
 #' @param source
 #' @param run_seed
-analysis_run <- function(source, run_seed, test_prop = 1/2) {
+varsel_run <- function(source = source,
+                       run_seed = run_seed,
+                       test_prop = 1/2,
+                       keep_prop = 1/2) {
 
   switch(
 
@@ -49,19 +52,32 @@ analysis_run <- function(source, run_seed, test_prop = 1/2) {
   models <- set_names(
     c(
       'aorsf',
-      'obliqueRSF',
       'randomForestSRC',
       'ranger'
     )
   )
 
-  fits <- map(models, model_fit, train = as.data.frame(train))
+  vis <- map(models,
+             .f = model_varsel,
+             train = as.data.frame(train))
+
+  vis$aorsf$vi
+
+  fits <- map2(
+    models,
+    vars,
+    .f = ~model_fit(.x, train = as.data.frame(train[, .y$vars]))
+  )
 
   prds <- map2(.x = fits,
                .y = models,
                .f = model_pred,
                test = as.data.frame(test),
                pred_horizon = pred_horizon)
+
+  times_sel <- vars |>
+    map_dfr('time') |>
+    mutate(action = 'var_sel')
 
   times_fit <- fits |>
     map_dfr('time') |>
@@ -72,7 +88,7 @@ analysis_run <- function(source, run_seed, test_prop = 1/2) {
     mutate(action = 'prd')
 
   times <-
-    bind_rows(times_fit, times_prd) |>
+    bind_rows(times_sel, times_fit, times_prd) |>
     mutate(data = source, run = run_seed) |>
     pivot_longer(cols = any_of(models),
                  names_to = 'model',
@@ -105,5 +121,3 @@ analysis_run <- function(source, run_seed, test_prop = 1/2) {
   score
 
 }
-
-

### 2022-03-10 index.Rmd
catg variables added; it seemed necessary

@@
 
-set.seed(329)
+set.seed(32987)
 
@@
     n_w = 3,
-    n_v = 3
+    n_v = 3,
+    # omit categorical variables; these are tested separately
+    n_c = 0 
   )
@@
 
-__Column means__: This test verifies that the mean of each predictor is close to zero, and that roughly 40% of outcomes were censored.
+__Column means__: This test verifies that the mean of each predictor is close to zero, and that roughly 45% of outcomes were censored.
 
@@
 
-data_means <- apply(data_sim, 2, mean) |> 
+data_means <- data_sim |> 
+  select(where(is.numeric)) |> 
+  apply(2, mean) |> 
   round(3) |> 
@@
   mutate(xcorr = recode(xcorr, 
-                        '0.0' = '|Corr(linear effects, irrelevant effect)| = 0',
-                        '0.1' = '|Corr(linear effects, irrelevant effect)| \u2264 0.10',
-                        '0.2' = '|Corr(linear effects, irrelevant effect)| \u2264 0.20',
-                        '0.3' = '|Corr(linear effects, irrelevant effect)| \u2264 0.30',
-                        '0.4' = '|Corr(linear effects, irrelevant effect)| \u2264 0.40'),
+                        '0.0' = '|Corr(linear effect variables, irrelevant variables)| = 0',
+                        '0.1' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.10',
+                        '0.2' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.20',
+                        '0.3' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.30',
+                        '0.4' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.40'),
          model = recode(model,
@@
                         'randomForestSRC' = 'Permutation importance')) |> 
-  select(n_obs, model, xcorr, overall, x, w, g, v) |> 
+  select(n_obs, model, xcorr, overall, x, w, g, v, c) |> 
   pivot_wider(names_from = n_obs, 
-              values_from = c(overall, x, w, g, v)) |> 
+              values_from = c(overall, x, w, g, v, c)) |> 
   select(xcorr,
@@
          v_2500,
+         c_2500,
          overall_5000,
@@
          g_5000,
-         v_5000) |> 
+         v_5000,
+         c_5000) |> 
   arrange(xcorr, model)
@@
                        "v_2500",
+                       "c_2500",
                        "overall_5000",
@@
                        "g_5000",
-                       "v_5000")
+                       "v_5000",
+                       "c_5000")
 
@@
                           "g_2500",
-                          "v_2500")) |> 
+                          "v_2500",
+                          "c_2500")) |> 
   tab_spanner(label = 'N = 5,000', 
@@
                           "g_5000",
-                          "v_5000")) |> 
+                          "v_5000",
+                          "c_5000")) |> 
   cols_label(
@@
     v_2500 = "Combo effects",
+    c_2500 = "Categorical effects",
     overall_5000 = "All effects",
@@
     g_5000 = "Interaction effects",
-    v_5000 = "Combo effects"
+    v_5000 = "Combo effects",
+    c_5000 = "Categorical effects"
   ) |> 
@@
 
+```{r}
+
+data_fig <- benchmark_vi_smry |>
+  ungroup() |> 
+  mutate(
+    n_obs = recode(n_obs,
+                   '2500' = 'Training data sample size = 2,500',
+                   '5000' = 'Training data sample size = 5,000'),
+    model = factor(model,
+                   levels = c('aorsf',
+                              'aorsf_menze',
+                              'xgboost',
+                              'randomForestSRC'),
+                   labels = c('Negation importance',
+                              'ANOVA importance',
+                              'SHAP importance',
+                              'Permutation importance'))
+  )
+
+fig <- ggplot(data_fig) + 
+  aes(x = xcorr, y = overall, col = model) + 
+  geom_line() +
+  geom_point(size = 2) +
+  scale_color_manual(values = c("purple", "orange", "grey", "limegreen")) +
+  facet_wrap(~n_obs) + 
+  labs(x = "max( |Corr(linear effect variables, irrelevant variables)| )",
+       y = "Discrimination between relevant\nand irrelevant predictor variables",
+       color = 'Variable importance\nestimated using') + 
+  theme_bw() + 
+  theme(panel.grid = element_blank())
+
+ggsave(filename = 'plot_violet.png',
+       plot = fig,
+       device = 'png',
+       width = 9,
+       height = 4,
+       dpi = 600)
+
+fig
+
+```
+
 Table 2: Discrimination between relevant and irrelevant predictor variables for each VI technique.
@@
 ```{r}
-
-data_fig <- benchmark_vi_smry |>
-  ungroup() |> 
-  mutate(model = recode(model,
-                        'aorsf' = 'Negation importance',
-                        'aorsf_menze' = 'ANOVA importance',
-                        'xgboost' = 'SHAP importance',
-                        'randomForestSRC' = 'Permutation importance')) |> 
-  select(n_obs, model, xcorr, overall) |> 
-  group_by(n_obs, model, xcorr) |> 
-  summarize(value = mean(overall))
-
-ggplot(data_fig) + 
-  aes(x = xcorr, y = value, col = model) + 
-  geom_line() +
-  facet_wrap(~n_obs)
 
@@
                         'randomForestSRC' = 'Permutation importance')) |> 
-  select(n_obs, model, xcorr, overall, x, w, g, v) |> 
+  select(n_obs, model, xcorr, overall, x, w, g, v, c) |> 
   group_by(model) |> 
@@
     across(
-      c(overall, x, w, g, v),
+      c(overall, x, w, g, v, c),
       ~table_value(mean(.x))
@@
     g = "Interaction effects",
-    v = "Combo effects"
+    v = "Combo effects",
+    c = "Categorical effects"
   ) |> 

### 2022-03-10 R/bench_vi.R

@@ -53,8 +53,6 @@ bench_vi <- function(data_source,
     mutate(vi_true = if_else(vi_id %in% vars_signal, 1, 0),
            vi_true = factor(vi_true))
 
-  library(yardstick)
-
   vars_data <- enframe(vars) |>
     unnest_wider(col = value) |>
     unnest_longer(col = vi) |>
@@ -91,6 +89,13 @@ bench_vi <- function(data_source,
               auc = .estimate,
               var_type = 'v')
 
+  roc_c <- vars_data |>
+    filter(var_type %in% c('z', 'c')) |>
+    roc_auc(vi, truth = vi_true, event_level = 'second') |>
+    transmute(model = name,
+              auc = .estimate,
+              var_type = 'c')
+
   roc_overall <- vars_data |>
     group_by(name) |>
     roc_auc(vi, truth = vi_true, event_level = 'second') |>
@@ -102,7 +107,8 @@ bench_vi <- function(data_source,
                    roc_x,
                    roc_w,
                    roc_g,
-                   roc_v) |>
+                   roc_v,
+                   roc_c) |>
     pivot_wider(names_from = var_type,
                 values_from = auc)
 

### 2022-03-10 R/model_varsel.R

@@ -13,40 +13,34 @@ model_varsel <- function(model, train) {
 
   start_time <- Sys.time()
 
+  if(model %in% c('aorsf', 'aorsf_menze')){
+    fit <- orsf(Surv(time, status) ~ ., data_train = train,
+                control = orsf_control_cph(iter_max = 10))
+  }
+
   switch(
     model,
 
     'aorsf' = {
 
-      fit <- orsf(Surv(time, status) ~ .,
-                  data_train = train,
-                  importance = TRUE)
-
-      vi <- fit$importance
-
+      vi <- orsf_vi_negate(fit)
 
     },
 
     'aorsf_menze' = {
 
-      fit <- orsf(Surv(time, status) ~ ., data_train = train,
-                  control = orsf_control_cph(iter_max = 20))
-
-      vi <- orsf_vi_pvalue(fit)
-
-    },
-
-    'aorsf_pv' = {
-
-      fit <- orsf(Surv(time, status) ~ ., data_train = train,
-                  control = orsf_control_cph(iter_max = 20))
-      vi <- aorsf:::orsf_vi_pv(fit)
+      vi <- orsf_vi_anova(fit)
 
     },
 
     'xgboost' = {
 
-      xmat <- as.matrix(select(train, -time, -status))
+      xmat <- train |>
+        as.data.table() |>
+        one_hot() |>
+        select(-time, -status) |>
+        as.matrix()
+
       ymat <- train$time
       ymat[train$status == 0] <- ymat[train$status == 0] * (-1)
 
@@ -60,7 +54,7 @@ model_varsel <- function(model, train) {
                        early_stopping_rounds = 25)
 
       fit_final <- xgboost(data = xmat, label = ymat,
-                           params = list(eta = 0.02),
+                           params = list(eta = 0.05),
                            nrounds = fit_cv$best_iteration,
                            objective = 'survival:cox',
                            eval_metric = 'cox-nloglik',
@@ -70,7 +64,14 @@ model_varsel <- function(model, train) {
         predict(fit_final, newdata = xmat, predcontrib = TRUE) |>
         apply(MARGIN = 2, function(x) mean(abs(x)))
 
-      vi <- fit_shap[-which(names(fit_shap)=='BIAS')]
+      vi <- fit_shap[-which(names(fit_shap)=='BIAS')] |>
+        enframe() |>
+        separate(name, into = c('var', 'cat'),
+                 sep = '_',
+                 fill = 'right') |>
[…]

### 2022-03-10 R/sim_surv.R

@@ -5,11 +5,12 @@
 #' @title
 
 sim_surv <- function(n_obs = 2500,
-                     n_z = 25,
-                     n_x = 25,
-                     n_g = 25,
-                     n_w = 25,
-                     n_v = 25,
+                     n_z = 20,
+                     n_x = 20,
+                     n_g = 20,
+                     n_w = 20,
+                     n_v = 20,
+                     n_c = 10,
                      correlated_x = 0,
                      pred_horiz = 2.5) {
 
@@ -24,6 +25,7 @@ sim_surv <- function(n_obs = 2500,
   g_names <- paste0('g', seq(n_g))
   w_names <- paste0('w', seq(n_w))
   v_names <- paste0('v', seq(n_v))
+  c_names <- paste0('c', seq(n_c))
 
   .names <- c(z_names, x_names)
 
@@ -33,7 +35,9 @@ sim_surv <- function(n_obs = 2500,
 
   if(n_v > 0) .names <- c(.names, v_names)
 
-  n_vars <- n_z + n_x + n_g + n_w + n_v
+  if(n_c > 0) .names <- c(.names, c_names)
+
+  n_vars <- n_z + n_x + n_g + n_w + n_v + n_c
 
   if(correlated_x > 0){
 
@@ -50,8 +54,7 @@ sim_surv <- function(n_obs = 2500,
             min = -correlated_x,
             max = correlated_x)
 
-
-
+    # symmetry
     mat_covar[upper.tri(mat_covar)] <- t(mat_covar)[upper.tri(mat_covar)]
 
     mat_covar <- Matrix::nearPD(mat_covar)$mat
@@ -73,7 +76,7 @@ sim_surv <- function(n_obs = 2500,
 
   covs <- as.data.frame(covs)
 
-  # Interaction variables
+  # Interaction variables ----
 
   vars_interaction <- c()
 
@@ -95,7 +98,7 @@ sim_surv <- function(n_obs = 2500,
 
   }
 
-  # Non-linear variables
+  # Non-linear variables ----
 
   if(n_w > 0){
 
@@ -112,7 +115,7 @@ sim_surv <- function(n_obs = 2500,
 
   }
 
-  # linear combination variables
+  # linear combination variables ----
 
   random_sign <- function(x) {
 
@@ -169,6 +172,7 @@ sim_surv <- function(n_obs = 2500,
[…]

### 2022-03-10 packages.R

@@ -17,6 +17,9 @@ library(randomForestSRC)
 library(table.glue)
 library(gt)
 library(simsurv)
+library(yardstick)
+library(data.table)
+library(mltools)
 
 conflict_prefer("filter", "dplyr")
 conflict_prefer("summarize", "dplyr")

### 2022-04-13 index.Rmd
turning into the repo for a paper
by now the BERD pilot application has been reviewed and it will soon be
time to submit aorsf to ROpenSci. Per the ROpenSci ML standard to
show the functionality of aorsf compared to similar packages, I am
setting this repo up as a project to coordinate benchmarking aorsf
versus similar software. Once the project is developed more, I will
convert it to a paper.

--- 2022-01-28 index.Rmd
@@
 ---
-title: "Preliminary results: Accelerating ORSF pilot study"
+title: "Benchmarking the accelerated oblique random survival forest"
 description: |
-  Partial model fitting improves computation time and prognostic accuracy for the ORSF.
+  Comparing prediction accuracy and identification of relevant predictor variables
 author:
@@
 
-tar_load(names = data_results)
+tar_load(names = c(bm_pred_comb, bm_vi_comb))
 
@@
 
-# Introduction
+# Benchmarking aorsf
 
-This document shows the full preliminary results that I have included in a response to reviewers for my submission to the Wake Forest Center for Biomedical Informatics Pilot Award.
-In my response, I present a table that aggregates results over three datasets.
-In this document, all three datasets are described and the results for each dataset are tabulated.
+Welcome! This benchmark experiment is under construction and will eventually be the basis of a paper that formally introduces the novel mechanisms at play in the {`aorsf`} package.
 
-# Datasets
+## Methods
 
-## Mayo Clinic Primary Biliary Cholangitis Data, N = 276
+### Machine learning algorithms
+
+The benchmark experiment uses real and simulated data to compare the following machine learning algorithms {`R package`}:
+
+1. accelerated oblique random survival forests {`aorsf`}
+1. original oblique random survival forests {`obliqueRSF`}
+1. axis-based random survival forests {`randomForestSRC` & `ranger`}
+1. axis-based conditional inference forests {`party`}
+1. gradient boosted decision trees {`xgboost`}
+
+__Note__ Presently, the original oblique random survival forest is not included in the benchmark results.
+This is because the original oblique random survival forest runs very slowly, turning a 10-minute benchmark into a 6 hour benchmark.
+I will include it once the project is more stable.
+
+__Note__ {`xgboost`} requires careful tuning to obtain ideal performance.
+While we do tune the number of boosting steps in this benchmark, we do not go beyond that and instead use default setting for hyper-parameters.
+
+### Prediction accuracy
+
+The machine learning algorithms above are compared based on their discrimination (C-statistic) and scaled Brier score, which are computed using the `riskRegression` package, and specifically `riskRegression::Score()`.
+Computational time required for model fitting and model predictions are also presented.
+Results are averaged over 15 runs of Monte-Carlo Cross-validation.
+In each run of Monte-Carlo Cross-validation, the current data are separated into a training and testing set, all modeling techniques are applied to the training set, and model predictions are evaluated in the testing set.
+
+### Variable importance
+
+I compare four different techniques to measure variable importance (VI).
+
+1. `Negation importance`: the method I propose to develop further with this pilot application. This is computed using an accelerated oblique random survival forest model.
+
+1. `ANOVA importance`: A method introduced by Menze et al. This is computed using an accelerated oblique random survival forest model.
+
+1. `SHAP importance`: A method introduced by Lundberg et al. SHAP importance is widely regarded as a gold standard due to its excellent asymptotic properties. This is computed using a boosting model.
+
+1. `Permutation importance`: A method introduced by Leo Breiman. This is computed using a standard random survival forest model.
+
+__Evaluation of variable importance techniques__: VI techniques are compared based on their discrimination (C-statistic) between relevant and irrelevant predictor variables.
+The relevant predictor variables are those that have a relationship to the outcome, and the irrelevant variables are those with no relationship to the outcome.
+This is equivalent to assigning a binary outcome to each variable: 1 if it is relevant, 0 otherwise, and then computing a C-statistic for discrimination of the relevant versus irrelevant variables using VI as a 'prediction' for the variables.
+
+__Details on C-statistic computation:__ The C-statistic for VI is not the same thing as the C-statistic for prediction accuracy.
+Since relevance of a variable is binary, the C-statistic for VI is computed using `yardstick::roc_auc`, which wraps `pROC::roc`.
+
+## Data sets
+
+### Mayo Clinic Primary Biliary Cholangitis Data, N = 276
 
@@
 
-## Rotterdam Breast Cancer Data, N = 2,982
+### Rotterdam Breast Cancer Data, N = 2,982
 
@@
 
-## Simulated data with interactions, N = 5,000
+### Simulated data
 
-A simulated dataset with normally distributed predictor variables was generated.
-Predictor variables $z_1$, $\dots$, $z_{10}$ were negatively associated with the outcome, and $x_1$, $\dots$, $x_{10}$ were positively associated with the outcome.
-Predictor variables $g_1$, $\dots$, $g_5$ were unrelated to the outcome, but each of the $g_i$ variables had an interaction effect with $x_i$ (i.e., $g_1$ interacted with $x_1$, $g_2$ interacted with $x_2$, and so on, with $g_5$ interacting with $x_5$).
-An example of these simulated data are presented below.
+The simulated data contain right-censored time-to-event outcomes with five types of predictor variables:
+
+- $z$ (irrelevant) variables $z_1$, $\dots$, $z_{k}$ had no relationship with the outcome.
+
+- $x$ (linear effect) variables $x_1$, $\dots$, $x_{k}$ had a linear relationship with the outcome.
+
+- $w$ (non-linear effect) variables $w_1$, $\dots$, $w_{k}$ had a non-linear relationship with the outcome. The non-linear relationship followed a sinusoidal curve with varying period length.
+
+- $g$ (conditional linear) variables $g_1$, $\dots$, $g_{k}$ had a conditional linear relationship with the outcome.
+In other words, for each $i \in \{1, \ldots, k\}$,  $g_i$ had no relationship to the outcome, but $g_i * x_i$ was linearly related to the outcome.
+
+- $v$ (combination linear) variables $v_1$, $\dots$, $v_{k}$ had a combination linear relationship with the outcome.
+In other words, $v_1, v_2, v_3$ each had no effect on the outcome individually, but the latent variable $v_1*c_1* + v_2*c_2 + v_3 * c_3$ was linearly related to the outcome.
+Coefficients $c_i$ were generated at random uniformly from -1 to -0.5 and 0.5 to 1.
+
+__Mean and standard deviation__ The multivariate normal distribution that generated values for the predictor matrix had a mean of zero and standard deviation of 1 for each variable.
+
+__Correlation__: The correlation among $z$ variables was allowed to be non-zero as was the correlation among $x$ variables and the correlation between $x$ and $z$ variables.
+For all non-zero correlations, a value was selected at random uniformly between a lower and upper boundary.
+We set the lower boundary as -0.1 and upper boundary as +0.1.
+The correlations were adjusted if needed to create the nearest positive definite covariance matrix using `Matrix::nearPD()`.
+
+__Effect sizes__: A total effect of 6 was distributed evenly across each predictor group.
+For example, with a total of $k$ linear effect predictors (i.e., the $x$ variables), the increase in log-hazard associated with a 1 unit increased in each $x$ variable was $6 / 25 = 0.24$, i.e., about a 27% increase in relative risk.
+
+__Outcomes__: A censored outcome variable was generated with the `simsurv::simsurv()` function using a predictor matrix that included all relevant predictors.
+After the outcome was generated the interactions, non-linear transformations, and linear combinations of relevant predictors were dropped from the data.
+
+#### Demo and validation of simulated data
+
+Some tests of the simulated data are presented here.
+If you have no skepticism regarding the simulated data, you can safely skip this sub-section.
+For simplicity, we set the number of predictors ($k$) to 3 for each predictor group.
+
+__Data generation__: There are no tests for this step, just a glimpse of the simulated set of data.
 
@@
 
-as_tibble(sim_surv(n=10))
+set.seed(32987)
+
+ss_demo <-
+  sim_surv(
+    n_obs = 10000,
+    n_z = 3,
+    n_x = 3,
+    n_g = 3,
+    n_w = 3,
+    n_v = 3,
+    # omit categorical variables; these are under construction
+    n_c = 0
+  )
+
+glimpse(ss_demo$data)
 
@@
 
-# Methods
-
-I compare four different modeling techniques:
-
-1. `aorsf` - the software I propose to develop further.
-
-1. `obliqueRSF` - the software I previously developed for ORSFs.
-
-1. `randomForestSRC` - A standard package for random forests.
-
-1. `ranger` - Another standard package for random forests.
-
-These techniques are compared based on their discrimination (C-statistic) and scaled Brier score, which are computed using the `riskRegression` package, and specifically `riskRegression::Score()`.
-Computational time required for model fitting and model predictions are also presented.
-Results are averaged over 25 runs of Monte-Carlo Cross-validation.
-In each run of Monte-Carlo Cross-validation, the current data are separated into a training and testing set, all modeling techniques are applied to the training set, and model predictions are evaluated in the testing set.
-
-# Results
-
-Overall, `aorsf` and `obliqueRSF` had the highest prognostic accuracy, but `aorsf` is __much__ faster.
-In addition, while `obliqueRSF` was more accurate overall than `ranger` and `randomForestSRC`, it was not as accurate as `aorsf`!
+__Column means__: This test verifies that the mean of each predictor is close to zero, and that roughly 45% of outcomes were censored.
 
@@
 
-results_overall <- data_results |> 
+data_sim <- ss_demo$data
+
+data_sim$true_v <-
+  with(
+    data_sim,
+      v1 * ss_demo$coefs_lc[[1]][1] +
+      v2 * ss_demo$coefs_lc[[1]][2] +
+      v3 * ss_demo$coefs_lc[[1]][3]
+  )
+
+data_means <- data_sim |>
+  select(where(is.numeric)) |>
+  apply(2, mean) |>
+  round(3) |>
+  enframe()
+
+# we can see that the mean of each predictor is close to zero, and that roughly 40% of outcomes were censored.
+data_means
+
+```
+
+__Effects detected__: This test verifies that, when the oracle model is used, an effect is only detected for variables that have a relationship to the outcome.
+
+```{r}
+
+dd <- datadist(data_sim)
+options(datadist = dd)
+
+mdl <- cph(
+  Surv(time, status) ~
+    # z variables; no effect should be detected
+    z1 + z2 + z3 +
+    # x variables; effect should be detected
+    # g variables; no effect should be detected
+    # interaction between x and g; effect should be detected
+    x1*g1 + x2*g2 + x3*g3 +
+    # w variables; effect should be detected and should be nonlinear
+    rcs(w1) + rcs(w2) + rcs(w3) +
+    # v variables; no effect should be detected for individual
+    # variables v1, v2, and v3, but the linear combination of
+    # these variables should have a detectable effect.
+    # note: v1 is not included due to co-linearity
+    v2 + v3 + true_v,
+  data = data_sim
+)
+
+# All expectations outlined above are met!
+anova(mdl)
+
+```
+
+__Effect size estimation for linear effects__: This test verifies that, when the oracle model is used, the estimated effect sizes for variables with linear effects are consistent with the effect sizes used to simulate the data.
+
+```{r}
+
+effects_expected <- c("x1" = 2,
+                      "x2" = 2,
+                      "x3" = 2,
+                      "g1" = 0,
+                      "g2" = 0,
+                      "g3" = 0,
+                      "x1 * g1" = 2,
+                      "x2 * g2" = 2,
+                      "x3 * g3" = 2,
+                      "v2" = 0,
+                      "v3" = 0,
+                      "true_v" = 2)
+
+effects_observed <- coef(mdl)[names(effects_expected)]
+
+# the differences between observed and expected estimates is small
+abs(effects_expected - effects_observed) |>
+  enframe(name = 'predictor',
+          value = 'bias')
+
+```
+
+__Effect size estimation for non-linear effects__: This test verifies that, when the oracle model is used, the estimated effect sizes for variables with non-linear effects are consistent with the effect sizes used to simulate the data.
+
+```{r}
+
+data_gg <-
+  list(w1 = as.data.frame(rms::Predict(mdl, w1)) |> select(x=w1, yhat),
+       w2 = as.data.frame(rms::Predict(mdl, w2)) |> select(x=w2, yhat),
+       w3 = as.data.frame(rms::Predict(mdl, w3)) |> select(x=w3, yhat)) |>
+  bind_rows(.id = 'xvar') |>
+  filter(x > -2.5, x < 2.5) |>
+  mutate(xvar = recode(xvar,
+                       w1 = "Non-linear variable: w1",
+                       w2 = "Non-linear variable: w2",
+                       w3 = "Non-linear variable: w3")) |>
+  as_tibble()
+
+# We expect increasing wiggle from left to right.
+
+ggplot(data_gg) +
+  aes(x = x, y = yhat) +
+  geom_line() +
+  facet_wrap(~ xvar) +
+  theme_bw() +
+  labs(x = 'W value', y = 'Estimated log-hazard')
+
+```
+
+These results verify that the simulated data set has the expected properties
+
+## Results
+
+### Prediction accuracy
+
+Overall, {`aorsf`} had the highest prognostic accuracy (__Table 1__), obtaining the highest C-statistic and scaled brier score in each of the three datasets.
+In addition, {`aorsf`} grew tree ensembles about 10 times as fast as {`ranger`} and generated predictions about 25 times as fast as {`party`}.
+Not bad!
+While {`aorsf`} was slower than {`randomForestSRC`}, its predictions were substantially more accurate.
+
+__Table 1__ Prognostic accuracy and computational efficiency of machine learning algorithms applied to real and simulated data.
+
+```{r}
+
+results_overall <- bm_pred_comb |> 
+  mutate(model = recode(model, 'cif' = 'party')) |> 
   group_by(model) |>
@@
 
-data_tbl <- data_results |> 
+data_tbl <- bm_pred_comb |> 
+  mutate(model = recode(model, 'cif' = 'party')) |> 
   group_by(model, data) |>
@@
       'rotterdam' = 'Rotterdam Breast Cancer Data, N = 2,982',
-      'sim' = 'Simulated data with interactions, N = 5,000'
+      'sim' = 'Simulated data'
     ),
@@
 
-# Conclusion
+### Variable importance
 
-The novelty of `aorsf` is its use of partially trained models in non-terminal nodes of decision trees.
-While `obliqueRSF` develops fully trained models, which require iteration until a convergence criteria is met, `aorsf` just completes one iteration and moves along.
-Initially I thought this computational shortcut would hurt the accuracy of the model, but the reality is that using partially trained models appears to improve the accuracy of the ORSF by increasing the diversity of trees in the ensemble.
+__Table 2__: Discrimination between relevant and irrelevant predictor variables for each VI technique in .
+Cells that are highlighted with a light blue color indicate which variable importance technique had the best discrimination for a given sample size, correlation setting, and variable type.
+
+```{r}
+
+data_gt <- bm_vi_comb |>
+  group_by(n_obs, xcorr, model) |> 
+  summarize(
+    across(
+      .cols = c(overall, x, w, g, v),
+      .fns = function(x) table_glue("{mean(x)} ({sd(x)})")
+    )
+  ) |> 
+  ungroup() |> 
+  mutate(
+    xcorr = recode(
+      xcorr, 
+      '0.0' = '|Corr(linear effect variables, irrelevant variables)| = 0',
+      '0.1' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.10',
+      '0.2' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.20',
+      '0.3' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.30',
+      '0.4' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.40'),
+    model = factor(
+      model,
+      levels = c('aorsf',
+                 'aorsf_menze',
+                 'xgboost',
+                 'randomForestSRC',
+                 'ranger'),
+      labels = c('Negation importance',
+                 'ANOVA importance',
+                 'SHAP importance',
+                 'Permutation importance (SRC)',
+                 'Permutation importance (ranger)')
+    )
+  ) |> 
+  select(model, overall, x, w, g, v) |> 
+  arrange(model)
+
+tbl <- data_gt |> 
+  gt(rowname_col = 'model', groupname_col = 'xcorr') |> 
+  tab_stubhead(label = 'Variable importance technique') |> 
+  cols_label(
+    overall = "All effects",
+    x = "Linear effects",
+    w = "Non-linear effects",
+    g = "Interaction effects",
+    v = "Combo effects") |> 
+  cols_align(align = 'center')
+
+tbl
+
+```
+
+## Conclusion
+
+{`aorsf`} offers novel, computationally efficient techniques to fit and interpret oblique random survival forests.
+The benchmarks above are incomplete, and I will be developing them more over time as I slowly work towards a paper.
 

### 2022-04-13 R/bench_pred.R

@@ -5,7 +5,14 @@
 #' @title
 #' @param data_source
 #' @param run_seed
-bench_pred <- function(data_source, run_seed, test_prop = 1/2) {
+bench_pred <- function(data_source,
+                       n_obs = NULL,
+                       n_z = NULL,
+                       correlated_x = NULL,
+                       run_seed,
+                       test_prop = 1/2) {
+
+  set.seed(run_seed)
 
   switch(
 
@@ -37,7 +44,9 @@ bench_pred <- function(data_source, run_seed, test_prop = 1/2) {
 
     'sim' = {
 
-      data_all <- sim_surv() |>
+      data_all <- sim_surv(n_obs = n_obs,
+                           n_z = n_z,
+                           correlated_x = correlated_x) |>
         getElement('data')
 
     }
@@ -46,18 +55,33 @@ bench_pred <- function(data_source, run_seed, test_prop = 1/2) {
 
   pred_horizon <- median(data_all$time)
 
-  set.seed(run_seed)
 
-  test_index <- sample(x = seq(nrow(data_all)),
-                       size = round(nrow(data_all) * test_prop),
-                       replace = FALSE)
+  if(data_source == 'sim'){
 
-  train <- data_all[-test_index, ]
-  test <- data_all[test_index, ]
+    train <- data_all
+
+    test <- sim_surv(n_obs = 5000,
+                     n_z = n_z,
+                     correlated_x = correlated_x) |>
+      getElement('data')
+
+  } else {
+
+    test_index <- sample(x = seq(nrow(data_all)),
+                         size = round(nrow(data_all) * test_prop),
+                         replace = FALSE)
+
+    train <- data_all[-test_index, ]
+    test <- data_all[test_index, ]
+
+
+  }
+
 
   models <- set_names(
     c(
       'aorsf',
+      'cif',
       # 'obliqueRSF',
       'xgboost',
       'randomForestSRC',
@@ -108,7 +132,10 @@ bench_pred <- function(data_source, run_seed, test_prop = 1/2) {
   score <- cstat |>
     left_join(brier, by = 'model') |>
     left_join(times, by = 'model') |>
-    as_tibble()
+    as_tibble() |>
+    mutate(n_obs = n_obs,
+           n_z = n_z,
+           correlated_x = correlated_x)
 
   print(score)
 

### 2022-04-13 R/model_fit.R

@@ -10,50 +10,69 @@ model_fit <- function(type, train) {
 
   message("fitting ", type, " model")
 
+  mtry <- round(sqrt(ncol(train)-2))
+  node_size <- 10
+
+  orsf_prefit <- orsf(Surv(time, status) ~ .,
+                      mtry = mtry,
+                      split_min_obs = node_size,
+                      data = train,
+                      no_fit = TRUE)
+
   start_time <- Sys.time()
 
   switch(
     type,
 
     'aorsf' = {
-      res <- orsf(Surv(time, status) ~ ., data = train)
+      res <- orsf_train(orsf_prefit)
+    },
+
+    'cif' = {
+      res <- cforest(Surv(time, status) ~ .,
+                     controls = cforest_unbiased(mtry = mtry),
+                     data = train)
     },
 
     'xgboost' = {
-
-
       xmat <- model.matrix(~. -1, data = train) |>
         as_tibble() |>
         as_sgb_data(status = status, time = time)
 
-
       res <- sgb_fit(sgb_df = xmat,
                      verbose = 0,
-                     params = list(max_depth=2,
-                                   eta = 0.01,
+                     params = list(eta = 0.01,
                                    objective = 'survival:cox',
                                    eval_metric = 'cox-nloglik'))
-
     },
 
     'obliqueRSF' = {
-      res <- ORSF(train, ntree = 500, verbose = FALSE)
+      res <- ORSF(train,
+                  ntree = 500,
+                  verbose = FALSE,
+                  mtry = mtry,
+                  min_obs_to_split_node = node_size)
     },
 
     'randomForestSRC' = {
-      res <- rfsrc(Surv(time, status) ~ ., data = train)
+      res <- rfsrc(Surv(time, status) ~ .,
+                   data = train,
+                   mtry = mtry,
+                   nodesize = node_size)
     },
 
     'ranger' = {
       res <- ranger(
-        Surv(time, status) ~ ., data = train, splitrule = 'extratrees'
+        Surv(time, status) ~ .,
+        data = train,
+        mtry = mtry,
+        min.node.size = node_size
       )
     }
 
   )
 
   end_time <- Sys.time()
-
 
   list(model = res, time = end_time - start_time)
 

### 2022-04-13 R/sim_surv.R

@@ -10,7 +10,7 @@ sim_surv <- function(n_obs = 2500,
                      n_g = 20,
                      n_w = 20,
                      n_v = 20,
-                     n_c = 10,
+                     n_c = 0,
                      correlated_x = 0,
                      pred_horiz = 2.5) {
 
@@ -168,11 +168,11 @@ sim_surv <- function(n_obs = 2500,
   betas <- vector(mode = 'numeric', length = ncol(covs))
   names(betas) <- names(covs)
 
-  if(n_x > 0)  x_effect   <- 3 / n_x else x_effect   <- 0
-  if(n_g > 0)  int_effect <- 3 / n_g else int_effect <- 0
-  if(n_w > 0)  nl_effect  <- 3 / n_w else nl_effect  <- 0
-  if(n_v > 0)  lc_effect  <- 3 / n_v else lc_effect  <- 0
-  if(n_c > 0)  c_effect   <- 3 / n_c else c_effect   <- 0
+  if(n_x > 0)  x_effect   <- 6 / n_x else x_effect   <- 0
+  if(n_g > 0)  int_effect <- 6 / n_g else int_effect <- 0
+  if(n_w > 0)  nl_effect  <- 6 / n_w else nl_effect  <- 0
+  if(n_v > 0)  lc_effect  <- 6 / n_v else lc_effect  <- 0
+  if(n_c > 0)  c_effect   <- 6 / n_c else c_effect   <- 0
 
   betas[str_detect(names(betas), '^x')] <- x_effect
 

### 2022-04-13 _targets.R

@@ -11,29 +11,30 @@ plan(callr)
 ## Load your R files
 lapply(list.files("./R", full.names = TRUE), base::source)
 
-analyses_pred <- expand_grid(data_source = c("pbc_orsf",
-                                             "rotterdam",
-                                             "sim"),
-                             run_seed = 1:100)
+analyses_real <- expand_grid(data_source = c("pbc_orsf",
+                                             "rotterdam"),
+                             run_seed = 1:15)
 
-analyses_vi <- expand_grid(data_source = 'sim',
-                           n_obs = c(2500, 5000),
-                           n_z = c(20),
-                           correlated_x = c(0, 0.1, 0.2, 0.3, 0.4),
-                           run_seed = 1:50)
+analyses_sim <- expand_grid(data_source = 'sim',
+                            n_obs = c(1000),
+                            n_z = c(20),
+                            correlated_x = c(0.1),
+                            run_seed = 1:15)
 
 
-## tar_plan supports drake-style targets and also tar_target()
 tar_plan(
 
-  # benchmark_pred <- tar_map(
-  #   values = analyses_pred,
-  #   tar_target(res_pred, bench_pred(data_source = data_source,
-  #                                   run_seed = run_seed))
-  # ),
+  bm_pred <- tar_map(
+    values = bind_rows(analyses_sim, analyses_real),
+    tar_target(res_pred, bench_pred(data_source = data_source,
+                                    n_obs = n_obs,
+                                    n_z = n_z,
+                                    correlated_x = correlated_x,
+                                    run_seed = run_seed))
+  ),
 
-  benchmark_vi <- tar_map(
-    values = analyses_vi,
+  bm_vi <- tar_map(
+    values = analyses_sim,
     tar_target(res_vi, bench_vi(data_source = data_source,
                                 n_obs = n_obs,
                                 n_z = n_z,
@@ -42,16 +43,16 @@ tar_plan(
 
   ),
 
-  tar_combine(
-    benchmark_vi_comb,
-    benchmark_vi[[1]],
-    command = bind_rows(!!!.x)
-  ),
 
-  tar_target(
-    benchmark_vi_smry,
-    bench_vi_summarize(benchmark_vi_comb)
-  )
+  tar_combine(bm_pred_comb, bm_pred[[1]]),
+
+  tar_combine(bm_vi_comb, bm_vi[[1]])
+
+  #
+  # tar_target(
+  #   benchmark_vi_smry,
+  #   bench_vi_summarize(benchmark_vi_comb)
+  # )
 
 )
 

### 2022-04-13 packages.R

@@ -20,6 +20,8 @@ library(simsurv)
 library(yardstick)
 library(data.table)
 library(mltools)
+library(party)
 
 conflict_prefer("filter", "dplyr")
 conflict_prefer("summarize", "dplyr")
+conflict_prefer("Predict", "modeltools")

### 2022-04-14 index.Rmd
bumping up number of runs to 50

@@
 Computational time required for model fitting and model predictions are also presented.
-Results are averaged over 15 runs of Monte-Carlo Cross-validation.
+Results are averaged over 50 runs of Monte-Carlo Cross-validation.
 In each run of Monte-Carlo Cross-validation, the current data are separated into a training and testing set, all modeling techniques are applied to the training set, and model predictions are evaluated in the testing set.
@@
       .cols = c(overall, x, w, g, v),
-      .fns = function(x) table_glue("{mean(x)} ({sd(x)})")
+      .fns = function(x) table_glue("{mean(x)}")
     )

### 2022-04-14 _targets.R

@@ -13,13 +13,13 @@ lapply(list.files("./R", full.names = TRUE), base::source)
 
 analyses_real <- expand_grid(data_source = c("pbc_orsf",
                                              "rotterdam"),
-                             run_seed = 1:15)
+                             run_seed = 1:50)
 
 analyses_sim <- expand_grid(data_source = 'sim',
                             n_obs = c(1000),
                             n_z = c(20),
                             correlated_x = c(0.1),
-                            run_seed = 1:15)
+                            run_seed = 1:50)
 
 
 tar_plan(

### 2022-05-09 index.Rmd
prepping for tar_future with 1 core

@@
   mutate(model = recode(model, 'cif' = 'party')) |> 
-  group_by(model, data) |>
+  group_by(model, data, n_z, n_obs, correlated_x) |>
   summarize(
@@
   bind_rows(results_overall) |> 
+  mutate(
+    data = if_else(
+      is.na(n_z),
+      true = data,
+      false = as.character(
+        glue::glue("Simulation, N junk = {n_z}, N obs = {n_obs}, X corr \u2264 {correlated_x}")
+      )
+    )
+  ) |> 
   group_by(data) |> 
@@
     across(.cols = starts_with("time"), .fns = as.numeric),
-    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf'],
-    time_prd_ratio = time_prd_mean / time_prd_mean[model == 'aorsf']
+    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf-1'],
+    time_prd_ratio = time_prd_mean / time_prd_mean[model == 'aorsf-1']
   ) |> 
+  arrange(data, desc(cstat_mean)) |> 
   transmute(
@@
       '0.3' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.30',
-      '0.4' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.40'),
+      '0.4' = '|Corr(linear effect variables, irrelevant variables)| \u2264 0.40'
+    ),
     model = factor(
@@
   ) |> 
-  select(model, overall, x, w, g, v) |> 
+  select(model, xcorr, overall, x, w, g, v) |> 
   arrange(model)

### 2022-05-09 R/guide_it_build.R

@@ -66,8 +66,8 @@ guide_it_build <- function(){
     .(
       TORSEND,
       TORSEDD,
-      BUMETA,
-      BUMETAND,
+      # BUMETA,
+      # BUMETAND,
       BBDOSE,
       FUROSND,
       FUROSE,
@@ -82,7 +82,7 @@ guide_it_build <- function(){
       aldpct,
       arbpct,
       bbpct,
-      ivause,
+      # ivause,
       valsart,
       diurdose,
       acearbpt,
@@ -104,13 +104,19 @@ guide_it_build <- function(){
     )
   ]
 
-  list(demog,
-       endpt,
-       clabs,
-       slabs,
-       meds) |>
+  out <- list(demog,
+              endpt,
+              clabs,
+              slabs,
+              meds) |>
     reduce(.f = merge,
            by = 'deidnum',
            all.x = TRUE)
+
+  out[ARB == 0, ARBDOSE := 0]
+  out[ALDOS == 0, ALDODOSE := 0]
+  out[TORSEND != 1 | is.na(TORSEND), TORSEDD := 0]
+
+  out[, `:=`(ARB = NULL, ALDOS = NULL, TORSEND = NULL)]
 
 }

### 2022-05-09 R/model_fit.R

@@ -12,17 +12,40 @@ model_fit <- function(type, train) {
 
   mtry <- round(sqrt(ncol(train)-2))
   node_size <- 10
+  aorsf_cph_iter <- 1
 
-  orsf_prefit <- orsf(Surv(time, status) ~ .,
-                      mtry = mtry,
-                      split_min_obs = node_size,
-                      data = train,
-                      no_fit = TRUE)
+  type_simplified <- type
+
+  control = orsf_control_net()
+
+  if(str_detect(type, '^aorsf')){
+
+    aorsf_cph_iter = as.numeric(str_extract(type, '\\d+'))
+
+    if(!is.na(aorsf_cph_iter)) {
+      control = orsf_control_cph(iter_max = aorsf_cph_iter)
+    }
+
+    type_simplified <- 'aorsf'
+
+  }
+
+
+  orsf_prefit <- orsf(
+    Surv(time, status) ~ .,
+    mtry = mtry,
+    split_min_obs = node_size,
+    control = control,
+    data = train,
+    no_fit = TRUE
+  )
 
   start_time <- Sys.time()
 
+  print(type_simplified)
+
   switch(
-    type,
+    type_simplified,
 
     'aorsf' = {
       res <- orsf_train(orsf_prefit)
@@ -32,6 +55,23 @@ model_fit <- function(type, train) {
       res <- cforest(Surv(time, status) ~ .,
                      controls = cforest_unbiased(mtry = mtry),
                      data = train)
+    },
+
+    'coxtime' = {
+
+      res <- coxtime(
+        Surv(time, status) ~ .,
+        data = train,
+        frac = 0.3,
+        activation = "relu",
+        num_nodes = c(as.integer(mtry), 8L, 4L, 2L),
+        dropout = 0.1,
+        early_stopping = TRUE,
+        epochs = 100,
+        batch_size = 32L
+      )
+
+
     },
 
     'xgboost' = {
@@ -61,8 +101,9 @@ model_fit <- function(type, train) {
     'obliqueRSF' = {
       res <- ORSF(train,
                   ntree = 500,
-                  verbose = FALSE,
                   mtry = mtry,
+                  verbose = FALSE,
+                  use.cv = nrow(train) < 500,
                   min_obs_to_split_node = node_size)
     },
 

### 2022-05-23 paper/jmlr/main.Rnw
first target journal picked

\documentclass[twoside,11pt]{article}

% Any additional packages needed should be included after jmlr2e.
% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
%
% It also sets the bibliographystyle to plainnat; for more information on
% natbib citation styles, see the natbib documentation, a copy of which
% is archived at http://www.jmlr.org/format/natbib.pdf

% Available options for package jmlr2e are:
%
%   - abbrvbib : use abbrvnat for the bibliography style
%   - nohyperref : do not load the hyperref package
%   - preprint : remove JMLR specific information from the template,
%         useful for example for posting to preprint servers.
%
% Example of using the package with custom options:
%
% \usepackage[abbrvbib, preprint]{jmlr2e}

\usepackage{jmlr2e}
% extra packages for tables
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}

\definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}

% Definitions of handy macros can go here

\newcommand{\dataset}{{\cal D}}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}

% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}

\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{meila00a}{Marina Meil\u{a} and Michael I. Jordan}

% Short headings should be running head and authors last names

\ShortHeadings{Learning with Mixtures of Trees}{Meil\u{a} and Jordan}
\firstpageno{1}

\begin{document}

\title{Accelerated oblique random survival forests}

\author{\name Marina Meil\u{a} \email mmp@stat.washington.edu \\
       \addr Department of Statistics\\
       University of Washington\\
       Seattle, WA 98195-4322, USA
       \AND
       \name Michael I.\ Jordan \email jordan@cs.berkeley.edu \\
       \addr Division of Computer Science and Department of Statistics\\
       University of California\\
       Berkeley, CA 94720-1776, USA}

\editor{Kevin Murphy and Bernhard Sch{\"o}lkopf}

\maketitle

<<echo = FALSE, include = FALSE>>=

setwd(here::here())
source("packages.R")
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      dpi = 300)

rspec <- round_spec() |>
  round_using_magnitude(digits = c(3, 2, 1, 1),
                        breaks = c(1, 10, 100, Inf))

names(rspec) <- paste('table.glue', names(rspec), sep = '.')

options(rspec)

tar_load(names = c(bm_pred_comb, bm_vi_comb))

@

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
abstract here
\end{abstract}

\begin{keywords}
  Bayesian networks, mixture models, Chow-Liu trees
\end{keywords}

\section{Introduction}

\section{Related work}

Several machine learning algorithms can engage with right-censored time-to-event outcomes. In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks.

accelerated oblique random survival forests \texttt{aorsf}

original oblique random survival forests \texttt{obliqueRSF}

axis-based random survival forests \texttt{randomForestSRC \& ranger}

axis-based conditional inference forests \texttt{party}

gradient boosted decision trees \texttt{xgboost}

\section{Results}

<<>>=

results_overall <- bm_pred_comb |>
  group_by(model) |>
  summarize(
    across(
      .cols = c(cstat, IPA, time_fit, time_prd),
      .fns = list(mean = mean, sd = sd)
    )
  ) |>
  mutate(data = 'Overall')

data_tbl <- bm_pred_comb |>
  group_by(model, data, n_z, n_obs, correlated_x) |>
  summarize(
    across(
      .cols = c(cstat, IPA, time_fit, time_prd),
      .fns = list(mean = mean, sd = sd)
    )
  ) |>
  bind_rows(results_overall) |>
  mutate(
    data = if_else(
      is.na(n_z),
      true = data,
      false = as.character(
        glue::glue("Simulation, N junk = {n_z}, N obs = {n_obs}, X corr less then or equal to {correlated_x}")
      )
    )
  ) |>
  group_by(data) |>
  mutate(
    across(.cols = starts_with("time"), .fns = as.numeric),
    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf-1'],
    time_prd_ratio = time_prd_mean / time_prd_mean[model == 'aorsf-1']
  ) |>
  arrange(data, desc(cstat_mean)) |>
  transmute(
    model = recode(
      model,
      "aorsf-15" = 'aORSF(i=15)',
      "aorsf-1" = 'aORSF(i=1)',
      "ranger" = 'Ranger',
      "xgboost" = 'Xgboost',
      "cif" = "Party",
      "randomForestSRC" = "Rfsrc",
      "coxtime" = "Coxtime"
    ),
    data = recode(
      data,
      'pbc_orsf' = 'Mayo Clinic Primary Biliary Cholangitis Data, N = 276',
      'rotterdam' = 'Rotterdam Breast Cancer Data, N = 2,982',
      'sim' = 'Simulated data'
    ),
    cstat = table_glue("{cstat_mean} ({cstat_sd})"),
    ipa = table_glue("{IPA_mean} ({IPA_sd})"),
    time_fit_mean = format(round(time_fit_mean, 3), nsmall = 3),
    time_fit_ratio = table_value(time_fit_ratio),
    time_prd_mean = format(round(time_prd_mean, 3), nsmall = 3),
    time_prd_ratio = table_value(time_prd_ratio)
  )

indents <- table(data_tbl$data)

data_tbl |>
  ungroup() |>
  select(-data) |>
  kable(booktabs=TRUE,
        longtable=TRUE,
        col.names = c(' ',
                      'C-Statistic',
                      'Scaled Brier',
                      'Mean',
                      'Ratio',
                      'Mean',
                      'Ratio'),
        align = 'lcc') |>
  pack_rows(index = indents,
            italic = TRUE,
            hline_before = TRUE,
            hline_after = TRUE) |>
  kable_styling(latex_options = c("repeat_header")) |>
  add_header_above(header = c(" " = 1,
                              "Performance metric (SD)" = 2,
                              "Fit model" = 2,
                              "Predict risk" = 2)) |>
  add_header_above(header = c(" " = 3,
                              "Computing time, seconds" = 4))

@

% Acknowledgements should go at the end, before appendices and references

\acks{We would like to acknowledge support for this project
from the National Science Foundation (NSF grant IIS-9988642)
and the Multidisciplinary Research Program of the Department
of Defense (MURI N00014-00-1-0637). }

% Manual newpage inserted to improve layout of sample file - not
% needed in general before appendices/bibliography.

\newpage

\appendix
\section*{Appendix A.}
\label{app:theorem}

% Note: in this sample, the section number is hard-coded in. Following
% proper LaTeX conventions, it should properly be coded as a reference:

%In this appendix we prove the following theorem from
%Section~\ref{sec:textree-generalization}:

In this appendix we prove the following theorem from
Section~6.2:

\noindent
{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
respective empirical mutual information values based on the sample
$\dataset$. Then
\[
	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
\]
with equality only if $u$ is identically 0.} \hfill\BlackBox

\noindent
{\bf Proof}. We use the notation:
\[
P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
\]
These values represent the (empirical) probabilities of $v$
taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\

{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}

\vskip 0.2in
\bibliography{main}

\end{document}

### 2022-05-23 paper/jmlr/main.tex
first target journal picked

\documentclass[twoside,11pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\makeatletter
\@ifundefined{AddToHook}{}{\AddToHook{package/xcolor/after}{\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}}}
\makeatother
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\makeatletter
\@ifundefined{AddToHook}{}{\AddToHook{package/xcolor/after}{
\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
}}
\makeatother
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

% Any additional packages needed should be included after jmlr2e.
% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
%
% It also sets the bibliographystyle to plainnat; for more information on
% natbib citation styles, see the natbib documentation, a copy of which
% is archived at http://www.jmlr.org/format/natbib.pdf

% Available options for package jmlr2e are:
%
%   - abbrvbib : use abbrvnat for the bibliography style
%   - nohyperref : do not load the hyperref package
%   - preprint : remove JMLR specific information from the template,
%         useful for example for posting to preprint servers.
%
% Example of using the package with custom options:
%
% \usepackage[abbrvbib, preprint]{jmlr2e}

\usepackage{jmlr2e}
% extra packages for tables
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}

\definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}

% Definitions of handy macros can go here

\newcommand{\dataset}{{\cal D}}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}

% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}

\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{meila00a}{Marina Meil\u{a} and Michael I. Jordan}

% Short headings should be running head and authors last names

\ShortHeadings{Learning with Mixtures of Trees}{Meil\u{a} and Jordan}
\firstpageno{1}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\title{Accelerated oblique random survival forests}

\author{\name Marina Meil\u{a} \email mmp@stat.washington.edu \\
       \addr Department of Statistics\\
       University of Washington\\
       Seattle, WA 98195-4322, USA
       \AND
       \name Michael I.\ Jordan \email jordan@cs.berkeley.edu \\
       \addr Division of Computer Science and Department of Statistics\\
       University of California\\
       Berkeley, CA 94720-1776, USA}

\editor{Kevin Murphy and Bernhard Sch{\"o}lkopf}

\maketitle

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
abstract here
\end{abstract}

\begin{keywords}
  Bayesian networks, mixture models, Chow-Liu trees
\end{keywords}

\section{Introduction}

\section{Related work}

Several machine learning algorithms can engage with right-censored time-to-event outcomes. In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks.

accelerated oblique random survival forests \texttt{aorsf}

original oblique random survival forests \texttt{obliqueRSF}

axis-based random survival forests \texttt{randomForestSRC \& ranger}

axis-based conditional inference forests \texttt{party}

gradient boosted decision trees \texttt{xgboost}

\section{Results}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\begin{longtable}{lcclccl}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Computing time, seconds} \\
\cmidrule(l{3pt}r{3pt}){4-7}
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Performance metric (SD)} & \multicolumn{2}{c}{Fit model} & \multicolumn{2}{c}{Predict risk} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
  & C-Statistic & Scaled Brier & Mean & Ratio & Mean & Ratio\\
\midrule
\endfirsthead
\multicolumn{7}{@{}l}{\textit{(continued)}}\\
\toprule
  & C-Statistic & Scaled Brier & Mean & Ratio & Mean & Ratio\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{actg}}}\\
\hline
\hspace{1em}Ranger & 0.740 (0.042) & 0.053 (0.034) & 0.316 & 0.334 & 0.120 & 1.95\\
\hspace{1em}Xgboost & 0.739 (0.041) & 0.044 (0.052) & 3.496 & 3.69 & 0.028 & 0.461\\
\hspace{1em}aORSF(i=1) & 0.735 (0.041) & 0.046 (0.050) & 0.947 & 1.00 & 0.062 & 1.00\\
\hspace{1em}obliqueRSF & 0.734 (0.038) & 0.049 (0.041) & 42.337 & 44.7 & 4.027 & 65.3\\
\hspace{1em}aORSF(i=15) & 0.733 (0.039) & 0.044 (0.048) & 2.199 & 2.32 & 0.056 & 0.904\\
\hspace{1em}Party & 0.733 (0.036) & 0.048 (0.044) & 1.950 & 2.06 & 2.795 & 45.3\\
\hspace{1em}aorsf-net & 0.729 (0.037) & 0.041 (0.052) & 29.028 & 30.6 & 0.060 & 0.969\\
\hspace{1em}Rfsrc & 0.719 (0.040) & 0.027 (0.067) & 0.288 & 0.304 & 0.056 & 0.908\\
\hspace{1em}Coxtime & 0.585 (0.127) & -0.004 (0.052) & 9.717 & 10.3 & 0.458 & 7.42\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{breast}}}\\
\hline
\hspace{1em}aORSF(i=1) & 0.742 (0.046) & 0.116 (0.045) & 4.732 & 1.00 & 0.300 & 1.00\\
\hspace{1em}obliqueRSF & 0.739 (0.049) & 0.112 (0.042) & 2854.152 & 603.2 & 6.075 & 20.3\\
\hspace{1em}aORSF(i=15) & 0.739 (0.048) & 0.117 (0.048) & 11.412 & 2.41 & 0.289 & 0.964\\
\hspace{1em}Party & 0.736 (0.054) & 0.102 (0.039) & 7.197 & 1.52 & 1.862 & 6.21\\
\hspace{1em}Xgboost & 0.731 (0.050) & 0.094 (0.038) & 5.372 & 1.14 & 0.274 & 0.913\\
\hspace{1em}aorsf-net & 0.730 (0.048) & 0.020 (0.086) & 611.280 & 129.2 & 0.299 & 0.996\\
\hspace{1em}Ranger & 0.728 (0.047) & 0.087 (0.035) & 0.281 & 0.059 & 0.171 & 0.570\\
\hspace{1em}Rfsrc & 0.688 (0.040) & 0.046 (0.043) & 0.436 & 0.092 & 0.152 & 0.508\\
\hspace{1em}Coxtime & 0.659 (0.080) & -0.007 (0.123) & 17.179 & 3.63 & 1.307 & 4.36\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{colon}}}\\
\hline
\hspace{1em}Rfsrc & 0.816 (0.020) & 0.283 (0.029) & 1.469 & 0.470 & 0.172 & 0.884\\
\hspace{1em}aORSF(i=15) & 0.787 (0.021) & 0.219 (0.030) & 7.471 & 2.39 & 0.190 & 0.975\\
\hspace{1em}aORSF(i=1) & 0.785 (0.018) & 0.219 (0.027) & 3.127 & 1.00 & 0.195 & 1.00\\
\hspace{1em}aorsf-net & 0.784 (0.020) & 0.215 (0.029) & 159.569 & 51.0 & 0.190 & 0.977\\
\hspace{1em}Xgboost & 0.783 (0.018) & 0.231 (0.025) & 8.686 & 2.78 & 0.049 & 0.252\\
\hspace{1em}obliqueRSF & 0.782 (0.019) & 0.219 (0.021) & 294.395 & 94.2 & 8.161 & 41.9\\
\hspace{1em}Party & 0.753 (0.019) & 0.185 (0.020) & 3.273 & 1.05 & 6.168 & 31.7\\
\hspace{1em}Ranger & 0.741 (0.021) & 0.151 (0.017) & 1.030 & 0.329 & 0.631 & 3.24\\
\hspace{1em}Coxtime & 0.531 (0.052) & -0.003 (0.005) & 14.933 & 4.78 & 2.590 & 13.3\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{flchain}}}\\
\hline
\hspace{1em}aORSF(i=1) & 0.831 (0.013) & 0.334 (0.025) & 14.475 & 1.00 & 1.238 & 1.00\\
\hspace{1em}aORSF(i=15) & 0.831 (0.013) & 0.333 (0.024) & 29.203 & 2.02 & 1.231 & 0.994\\
\hspace{1em}aorsf-net & 0.829 (0.013) & 0.330 (0.024) & 442.726 & 30.6 & 1.219 & 0.985\\
\hspace{1em}Xgboost & 0.829 (0.012) & 0.331 (0.021) & 7.123 & 0.492 & 0.267 & 0.216\\
\hspace{1em}Ranger & 0.828 (0.013) & 0.325 (0.022) & 100.469 & 6.94 & 17.866 & 14.4\\
\hspace{1em}Party & 0.827 (0.013) & 0.325 (0.024) & 33.053 & 2.28 & 81.937 & 66.2\\
\hspace{1em}obliqueRSF & 0.825 (0.013) & 0.325 (0.024) & 1800.099 & 124.4 & 59.969 & 48.4\\
\hspace{1em}Rfsrc & 0.825 (0.012) & 0.323 (0.022) & 5.793 & 0.400 & 0.453 & 0.366\\
\hspace{1em}Coxtime & 0.582 (0.109) & -0.015 (0.067) & 22.765 & 1.57 & 13.661 & 11.0\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{gbsg2}}}\\
\hline
\hspace{1em}Ranger & 0.733 (0.045) & 0.118 (0.030) & 0.373 & 0.401 & 0.124 & 1.83\\
\hspace{1em}obliqueRSF & 0.732 (0.036) & 0.151 (0.040) & 130.378 & 140.0 & 2.473 & 36.4\\
\hspace{1em}aORSF(i=15) & 0.731 (0.037) & 0.146 (0.046) & 2.116 & 2.27 & 0.061 & 0.899\\
\hspace{1em}Party & 0.731 (0.038) & 0.146 (0.044) & 0.691 & 0.742 & 1.008 & 14.8\\
\hspace{1em}aORSF(i=1) & 0.730 (0.037) & 0.144 (0.049) & 0.931 & 1.00 & 0.068 & 1.00\\
\hspace{1em}aorsf-net & 0.729 (0.036) & 0.144 (0.047) & 57.048 & 61.3 & 0.062 & 0.910\\
\hspace{1em}Xgboost & 0.728 (0.037) & 0.126 (0.037) & 2.580 & 2.77 & 0.029 & 0.428\\
\hspace{1em}Rfsrc & 0.723 (0.035) & 0.139 (0.047) & 0.618 & 0.664 & 0.086 & 1.27\\
\hspace{1em}Coxtime & 0.519 (0.058) & -0.057 (0.134) & 10.882 & 11.7 & 0.680 & 10.0\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{guide\_it}}}\\
\hline
\hspace{1em}aORSF(i=1) & 0.725 (0.032) & 0.124 (0.038) & 1.663 & 1.00 & 0.110 & 1.00\\
\hspace{1em}aORSF(i=15) & 0.724 (0.034) & 0.123 (0.039) & 4.896 & 2.94 & 0.106 & 0.963\\
\hspace{1em}aorsf-net & 0.724 (0.034) & 0.119 (0.040) & 84.799 & 51.0 & 0.110 & 0.994\\
\hspace{1em}obliqueRSF & 0.714 (0.037) & 0.111 (0.037) & 235.729 & 141.8 & 3.299 & 29.9\\
\hspace{1em}Ranger & 0.713 (0.035) & 0.104 (0.032) & 0.446 & 0.268 & 0.188 & 1.70\\
\hspace{1em}Party & 0.709 (0.036) & 0.102 (0.032) & 1.525 & 0.917 & 1.728 & 15.7\\
\hspace{1em}Coxtime & 0.699 (0.032) & 0.077 (0.053) & 12.268 & 7.38 & 0.565 & 5.13\\
\hspace{1em}Rfsrc & 0.698 (0.033) & 0.098 (0.034) & 0.846 & 0.509 & 0.101 & 0.915\\
\hspace{1em}Xgboost & 0.688 (0.032) & 0.073 (0.037) & 4.948 & 2.98 & 0.033 & 0.295\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{Mayo Clinic Primary Biliary Cholangitis Data, N = 276}}}\\
\hline
\hspace{1em}Xgboost & 0.874 (0.011) & 0.218 (0.019) & 11.715 & 0.359 & 0.365 & 0.123\\
\hspace{1em}aORSF(i=15) & 0.867 (0.011) & 0.221 (0.015) & 77.709 & 2.38 & 2.874 & 0.967\\
\hspace{1em}aORSF(i=1) & 0.867 (0.011) & 0.219 (0.016) & 32.619 & 1.00 & 2.970 & 1.00\\
\hspace{1em}aorsf-net & 0.867 (0.011) & 0.221 (0.016) & 628.839 & 19.3 & 3.054 & 1.03\\
\hspace{1em}obliqueRSF & 0.865 (0.012) & 0.217 (0.015) & 2098.616 & 64.3 & 270.503 & 91.1\\
\hspace{1em}Party & 0.861 (0.013) & 0.214 (0.014) & 111.579 & 3.42 & 460.042 & 154.9\\
\hspace{1em}Ranger & 0.859 (0.012) & 0.189 (0.013) & 171.040 & 5.24 & 89.041 & 30.0\\
\hspace{1em}Rfsrc & 0.858 (0.012) & 0.215 (0.014) & 11.646 & 0.357 & 1.420 & 0.478\\
\hspace{1em}Coxtime & 0.590 (0.105) & 0.000 (0.001) & 19.733 & 0.605 & 50.705 & 17.1\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{nafld}}}\\
\hline
\hspace{1em}aORSF(i=1) & 0.796 (0.077) & 0.210 (0.149) & 8.429 & 1.00 & 0.683 & 1.00\\
\hspace{1em}aORSF(i=15) & 0.796 (0.078) & 0.210 (0.148) & 20.977 & 2.49 & 0.668 & 0.978\\
\hspace{1em}aorsf-net & 0.793 (0.080) & 0.202 (0.160) & 270.097 & 32.0 & 0.685 & 1.00\\
\hspace{1em}obliqueRSF & 0.792 (0.075) & 0.187 (0.115) & 1025.773 & 121.7 & 37.539 & 55.0\\
\hspace{1em}Xgboost & 0.789 (0.082) & 0.187 (0.180) & 6.797 & 0.806 & 0.213 & 0.311\\
\hspace{1em}Party & 0.787 (0.077) & 0.190 (0.131) & 24.327 & 2.89 & 56.237 & 82.3\\
\hspace{1em}Rfsrc & 0.786 (0.085) & 0.198 (0.155) & 2.467 & 0.293 & 0.285 & 0.417\\
\hspace{1em}Ranger & 0.785 (0.075) & 0.170 (0.119) & 19.567 & 2.32 & 8.448 & 12.4\\
\hspace{1em}Coxtime & 0.641 (0.148) & 0.038 (0.211) & 18.944 & 2.25 & 7.395 & 10.8\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{Overall}}}\\
\hline
\hspace{1em}aORSF(i=1) & 0.926 (0.032) & 0.484 (0.078) & 0.327 & 1.00 & 0.031 & 1.00\\
\hspace{1em}aorsf-net & 0.924 (0.031) & 0.481 (0.077) & 20.545 & 62.8 & 0.027 & 0.861\\
\hspace{1em}obliqueRSF & 0.924 (0.034) & 0.442 (0.066) & 165.436 & 505.8 & 0.671 & 21.5\\
\hspace{1em}aORSF(i=15) & 0.922 (0.031) & 0.474 (0.074) & 0.711 & 2.17 & 0.025 & 0.786\\
\hspace{1em}Party & 0.920 (0.041) & 0.432 (0.073) & 0.276 & 0.844 & 0.319 & 10.2\\
\hspace{1em}Xgboost & 0.917 (0.035) & 0.458 (0.085) & 4.339 & 13.3 & 0.033 & 1.04\\
\hspace{1em}Rfsrc & 0.916 (0.033) & 0.444 (0.079) & 0.101 & 0.308 & 0.033 & 1.07\\
\hspace{1em}Ranger & 0.903 (0.034) & 0.349 (0.041) & 0.035 & 0.107 & 0.042 & 1.33\\
\hspace{1em}Coxtime & 0.562 (0.201) & -0.012 (0.018) & 12.376 & 37.8 & 0.322 & 10.3\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{peakV02}}}\\
\hline
\hspace{1em}aorsf-net & 0.721 (0.022) & 0.112 (0.034) & 174.090 & 37.6 & 0.320 & 1.04\\
\hspace{1em}obliqueRSF & 0.720 (0.022) & 0.119 (0.030) & 614.000 & 132.8 & 10.231 & 33.3\\
\hspace{1em}aORSF(i=15) & 0.720 (0.020) & 0.115 (0.031) & 10.718 & 2.32 & 0.302 & 0.983\\
\hspace{1em}aORSF(i=1) & 0.720 (0.020) & 0.113 (0.032) & 4.625 & 1.00 & 0.308 & 1.00\\
\hspace{1em}Party & 0.718 (0.023) & 0.117 (0.029) & 5.315 & 1.15 & 9.747 & 31.7\\
\hspace{1em}Ranger & 0.714 (0.022) & 0.103 (0.023) & 2.211 & 0.478 & 1.358 & 4.42\\
\hspace{1em}Rfsrc & 0.714 (0.019) & 0.111 (0.026) & 1.718 & 0.372 & 0.193 & 0.627\\
\hspace{1em}Xgboost & 0.714 (0.018) & 0.102 (0.028) & 5.134 & 1.11 & 0.047 & 0.152\\
\hspace{1em}Coxtime & 0.701 (0.028) & 0.097 (0.032) & 20.249 & 4.38 & 3.560 & 11.6\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{Rotterdam Breast Cancer Data, N = 2,982}}}\\
\hline
\hspace{1em}aorsf-net & 0.724 (0.012) & 0.151 (0.018) & 260.864 & 43.4 & 0.377 & 0.954\\
\hspace{1em}aORSF(i=1) & 0.723 (0.013) & 0.150 (0.019) & 6.007 & 1.00 & 0.395 & 1.00\\
\hspace{1em}aORSF(i=15) & 0.723 (0.013) & 0.150 (0.019) & 13.286 & 2.21 & 0.390 & 0.985\\
\hspace{1em}Xgboost & 0.722 (0.014) & 0.143 (0.017) & 3.979 & 0.662 & 0.089 & 0.225\\
\hspace{1em}Ranger & 0.721 (0.013) & 0.143 (0.014) & 1.881 & 0.313 & 1.819 & 4.60\\
\hspace{1em}obliqueRSF & 0.720 (0.013) & 0.149 (0.017) & 912.920 & 152.0 & 18.351 & 46.4\\
\hspace{1em}Party & 0.719 (0.012) & 0.147 (0.016) & 6.186 & 1.03 & 15.125 & 38.3\\
\hspace{1em}Rfsrc & 0.716 (0.013) & 0.137 (0.020) & 2.762 & 0.460 & 0.261 & 0.661\\
\hspace{1em}Coxtime & 0.502 (0.049) & -0.047 (0.154) & 18.276 & 3.04 & 5.857 & 14.8\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{sprint-acm}}}\\
\hline
\hspace{1em}Xgboost & 0.798 (0.014) & 0.205 (0.026) & 13.680 & 0.447 & 0.199 & 0.087\\
\hspace{1em}aORSF(i=15) & 0.795 (0.013) & 0.199 (0.020) & 87.852 & 2.87 & 2.271 & 0.992\\
\hspace{1em}aORSF(i=1) & 0.795 (0.013) & 0.199 (0.022) & 30.597 & 1.00 & 2.288 & 1.00\\
\hspace{1em}aorsf-net & 0.795 (0.013) & 0.192 (0.023) & 934.189 & 30.5 & 2.298 & 1.00\\
\hspace{1em}obliqueRSF & 0.794 (0.013) & 0.194 (0.019) & 4216.468 & 137.8 & 81.441 & 35.6\\
\hspace{1em}Party & 0.792 (0.012) & 0.187 (0.017) & 93.194 & 3.05 & 130.262 & 56.9\\
\hspace{1em}Rfsrc & 0.791 (0.011) & 0.192 (0.020) & 6.913 & 0.226 & 0.496 & 0.217\\
\hspace{1em}Ranger & 0.784 (0.013) & 0.175 (0.016) & 9.100 & 0.297 & 8.720 & 3.81\\
\hspace{1em}Coxtime & 0.768 (0.087) & 0.177 (0.054) & 46.094 & 1.51 & 15.082 & 6.59\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{sprint-cvd}}}\\
\hline
\hspace{1em}aorsf-net & 0.822 (0.018) & 0.136 (0.016) & 532.742 & 24.2 & 1.615 & 1.01\\
\hspace{1em}Party & 0.821 (0.015) & 0.121 (0.009) & 92.038 & 4.18 & 126.234 & 79.0\\
\hspace{1em}aORSF(i=15) & 0.821 (0.018) & 0.131 (0.011) & 59.100 & 2.68 & 1.591 & 0.995\\
\hspace{1em}aORSF(i=1) & 0.821 (0.018) & 0.131 (0.011) & 22.035 & 1.00 & 1.599 & 1.00\\
\hspace{1em}obliqueRSF & 0.821 (0.016) & 0.128 (0.009) & 1569.905 & 71.2 & 92.265 & 57.7\\
\hspace{1em}Xgboost & 0.819 (0.016) & 0.135 (0.019) & 10.625 & 0.482 & 0.099 & 0.062\\
\hspace{1em}Rfsrc & 0.817 (0.014) & 0.130 (0.013) & 3.344 & 0.152 & 0.451 & 0.282\\
\hspace{1em}Ranger & 0.812 (0.017) & 0.113 (0.008) & 5.724 & 0.260 & 6.390 & 4.00\\
\hspace{1em}Coxtime & 0.787 (0.021) & 0.098 (0.024) & 20.202 & 0.917 & 13.321 & 8.33\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{time-to-million}}}\\
\hline
\hspace{1em}Xgboost & 0.933 (0.018) & 0.553 (0.055) & 13.028 & 9.08 & 0.034 & 0.420\\
\hspace{1em}Coxtime & 0.931 (0.016) & 0.563 (0.057) & 20.527 & 14.3 & 0.751 & 9.27\\
\hspace{1em}aORSF(i=15) & 0.931 (0.017) & 0.534 (0.038) & 4.789 & 3.34 & 0.076 & 0.941\\
\hspace{1em}aorsf-net & 0.930 (0.017) & 0.535 (0.039) & 78.002 & 54.4 & 0.077 & 0.952\\
\hspace{1em}aORSF(i=1) & 0.929 (0.018) & 0.530 (0.040) & 1.435 & 1.00 & 0.081 & 1.00\\
\hspace{1em}Rfsrc & 0.925 (0.018) & 0.527 (0.041) & 0.822 & 0.573 & 0.066 & 0.812\\
\hspace{1em}Party & 0.912 (0.024) & 0.466 (0.043) & 0.617 & 0.430 & 0.905 & 11.2\\
\hspace{1em}obliqueRSF & 0.909 (0.024) & 0.337 (0.031) & 239.423 & 166.9 & 2.436 & 30.0\\
\hspace{1em}Ranger & 0.904 (0.024) & 0.436 (0.042) & 0.076 & 0.053 & 0.125 & 1.54\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{vdv}}}\\
\hline
\hspace{1em}Xgboost & 0.778 (0.096) & -0.065 (0.330) & 4.236 & 1.55 & 1.617 & 2.78\\
\hspace{1em}Rfsrc & 0.773 (0.118) & 0.047 (0.189) & 0.185 & 0.068 & 0.304 & 0.523\\
\hspace{1em}aORSF(i=15) & 0.772 (0.091) & 0.053 (0.126) & 2.841 & 1.04 & 0.552 & 0.948\\
\hspace{1em}aORSF(i=1) & 0.772 (0.082) & 0.046 (0.119) & 2.732 & 1.00 & 0.582 & 1.00\\
\hspace{1em}Ranger & 0.765 (0.075) & 0.024 (0.119) & 0.496 & 0.181 & 0.099 & 0.171\\
\hspace{1em}obliqueRSF & 0.764 (0.076) & 0.064 (0.131) & 120.857 & 44.2 & 2.945 & 5.06\\
\hspace{1em}Party & 0.761 (0.088) & 0.053 (0.119) & 7.889 & 2.89 & 5.362 & 9.21\\
\hspace{1em}aorsf-net & 0.750 (0.100) & 0.055 (0.188) & 21.757 & 7.96 & 0.552 & 0.948\\
\hspace{1em}Coxtime & 0.678 (0.134) & -0.259 (0.417) & 29.478 & 10.8 & 1.899 & 3.26\\
\addlinespace[0.3em]
\hline
\multicolumn{7}{l}{\textit{\textbf{veteran}}}\\
\hline
\hspace{1em}aORSF(i=15) & 0.846 (0.053) & 0.291 (0.072) & 0.352 & 1.90 & 0.012 & 0.656\\
\hspace{1em}aORSF(i=1) & 0.843 (0.053) & 0.289 (0.071) & 0.186 & 1.00 & 0.018 & 1.00\\
\hspace{1em}aorsf-net & 0.840 (0.055) & 0.281 (0.077) & 15.971 & 86.1 & 0.012 & 0.657\\
\hspace{1em}Ranger & 0.836 (0.072) & 0.175 (0.057) & 0.019 & 0.104 & 0.028 & 1.56\\
\hspace{1em}obliqueRSF & 0.835 (0.051) & 0.192 (0.051) & 91.890 & 495.3 & 0.235 & 13.2\\
\hspace{1em}Rfsrc & 0.816 (0.064) & 0.248 (0.079) & 0.057 & 0.310 & 0.023 & 1.27\\
\hspace{1em}Party & 0.816 (0.061) & 0.208 (0.059) & 0.117 & 0.632 & 0.067 & 3.75\\
\hspace{1em}Xgboost & 0.780 (0.069) & 0.151 (0.085) & 3.009 & 16.2 & 0.026 & 1.47\\
\hspace{1em}Coxtime & 0.523 (0.077) & -0.038 (0.055) & 9.481 & 51.1 & 0.159 & 8.97\\*
\end{longtable}

\end{knitrout}

% Acknowledgements should go at the end, before appendices and references

\acks{We would like to acknowledge support for this project
from the National Science Foundation (NSF grant IIS-9988642)
and the Multidisciplinary Research Program of the Department
of Defense (MURI N00014-00-1-0637). }

% Manual newpage inserted to improve layout of sample file - not
% needed in general before appendices/bibliography.

\newpage

\appendix
\section*{Appendix A.}
\label{app:theorem}

% Note: in this sample, the section number is hard-coded in. Following
% proper LaTeX conventions, it should properly be coded as a reference:

%In this appendix we prove the following theorem from
%Section~\ref{sec:textree-generalization}:

In this appendix we prove the following theorem from
Section~6.2:

\noindent
{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
respective empirical mutual information values based on the sample
$\dataset$. Then
\[
	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
\]
with equality only if $u$ is identically 0.} \hfill\BlackBox

\noindent
{\bf Proof}. We use the notation:
\[
P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
\]
These values represent the (empirical) probabilities of $v$
taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\

{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}

\vskip 0.2in
\bibliography{main}

\end{document}

### 2022-05-23 paper/jmlr/sample.tex
first target journal picked

--- 2022-05-23 paper/jmlr/main.Rnw
@@
 \usepackage{jmlr2e}
-% extra packages for tables
-\usepackage{longtable}
-\usepackage{colortbl}
-\usepackage{amsmath}
-\usepackage{booktabs}
-\usepackage{caption}
-
-\definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}
 
@@
 
-\title{Accelerated oblique random survival forests}
+\title{Learning with Mixtures of Trees}
 
@@
 
-<<echo = FALSE, include = FALSE>>=
-
-setwd(here::here())
-source("packages.R")
-library(knitr)
-library(kableExtra)
-
-knitr::opts_chunk$set(echo = FALSE,
-                      message = FALSE,
-                      dpi = 300)
-
-rspec <- round_spec() |>
-  round_using_magnitude(digits = c(3, 2, 1, 1),
-                        breaks = c(1, 10, 100, Inf))
-
-names(rspec) <- paste('table.glue', names(rspec), sep = '.')
-
-options(rspec)
-
-tar_load(names = c(bm_pred_comb, bm_vi_comb))
-
-@
-
 \begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
-abstract here
+This paper describes the mixtures-of-trees model, a probabilistic
+model for discrete multidimensional domains.  Mixtures-of-trees
+generalize the probabilistic trees of \citet{chow:68}
+in a different and complementary direction to that of Bayesian networks.
+We present efficient algorithms for learning mixtures-of-trees
+models in maximum likelihood and Bayesian frameworks.
+We also discuss additional efficiencies that can be
+obtained when data are ``sparse,'' and we present data
+structures and algorithms that exploit such sparseness.
+Experimental results demonstrate the performance of the
+model for both density estimation and classification.
+We also discuss the sense in which tree-based classifiers
+perform an implicit form of feature selection, and demonstrate
+a resulting insensitivity to irrelevant attributes.
 \end{abstract}
@@
 
-\section{Related work}
+Probabilistic inference has become a core technology in AI,
+largely due to developments in graph-theoretic methods for the
+representation and manipulation of complex probability
+distributions~\citep{pearl:88}.  Whether in their guise as
+directed graphs (Bayesian networks) or as undirected graphs (Markov
+random fields), \emph{probabilistic graphical models} have a number
+of virtues as representations of uncertainty and as inference engines.
+Graphical models allow a separation between qualitative, structural
+aspects of uncertain knowledge and the quantitative, parametric aspects
+of uncertainty...\\
 
-Several machine learning algorithms can engage with right-censored time-to-event outcomes.
-In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks.
-
-accelerated oblique random survival forests \texttt{aorsf}
-
-original oblique random survival forests \texttt{obliqueRSF}
-
-axis-based random survival forests \texttt{randomForestSRC \& ranger}
-
-axis-based conditional inference forests \texttt{party}
-
-gradient boosted decision trees \texttt{xgboost}
-
-\section{Results}
-
-<<>>=
-
-results_overall <- bm_pred_comb |>
-  group_by(model) |>
-  summarize(
-    across(
-      .cols = c(cstat, IPA, time_fit, time_prd),
-      .fns = list(mean = mean, sd = sd)
-    )
-  ) |>
-  mutate(data = 'Overall')
-
-data_tbl <- bm_pred_comb |>
-  group_by(model, data, n_z, n_obs, correlated_x) |>
-  summarize(
-    across(
-      .cols = c(cstat, IPA, time_fit, time_prd),
-      .fns = list(mean = mean, sd = sd)
-    )
-  ) |>
-  bind_rows(results_overall) |>
-  mutate(
-    data = if_else(
-      is.na(n_z),
-      true = data,
-      false = as.character(
-        glue::glue("Simulation, N junk = {n_z}, N obs = {n_obs}, X corr less then or equal to {correlated_x}")
-      )
-    )
-  ) |>
-  group_by(data) |>
-  mutate(
-    across(.cols = starts_with("time"), .fns = as.numeric),
-    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf-1'],
-    time_prd_ratio = time_prd_mean / time_prd_mean[model == 'aorsf-1']
-  ) |>
-  arrange(data, desc(cstat_mean)) |>
-  transmute(
-    model = recode(
-      model,
-      "aorsf-15" = 'aORSF(i=15)',
-      "aorsf-1" = 'aORSF(i=1)',
-      "ranger" = 'Ranger',
-      "xgboost" = 'Xgboost',
-      "cif" = "Party",
-      "randomForestSRC" = "Rfsrc",
-      "coxtime" = "Coxtime"
-    ),
-    data = recode(
-      data,
-      'pbc_orsf' = 'Mayo Clinic Primary Biliary Cholangitis Data, N = 276',
-      'rotterdam' = 'Rotterdam Breast Cancer Data, N = 2,982',
-      'sim' = 'Simulated data'
-    ),
-    cstat = table_glue("{cstat_mean} ({cstat_sd})"),
-    ipa = table_glue("{IPA_mean} ({IPA_sd})"),
-    time_fit_mean = format(round(time_fit_mean, 3), nsmall = 3),
-    time_fit_ratio = table_value(time_fit_ratio),
-    time_prd_mean = format(round(time_prd_mean, 3), nsmall = 3),
-    time_prd_ratio = table_value(time_prd_ratio)
-  )
-
-indents <- table(data_tbl$data)
-
-data_tbl |>
-  ungroup() |>
-  select(-data) |>
-  kable(booktabs=TRUE,
-        longtable=TRUE,
-        col.names = c(' ',
-                      'C-Statistic',
-                      'Scaled Brier',
-                      'Mean',
-                      'Ratio',
-                      'Mean',
-                      'Ratio'),
-        align = 'lcc') |>
-  pack_rows(index = indents,
-            italic = TRUE,
-            hline_before = TRUE,
-            hline_after = TRUE) |>
-  kable_styling(latex_options = c("repeat_header")) |>
-  add_header_above(header = c(" " = 1,
-                              "Performance metric (SD)" = 2,
-                              "Fit model" = 2,
-                              "Predict risk" = 2)) |>
-  add_header_above(header = c(" " = 3,
-                              "Computing time, seconds" = 4))
-
-@
+{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
 
@@
 \vskip 0.2in
-\bibliography{main}
+\bibliography{sample}
 

### 2022-05-23 R/bench_pred.R

@@ -13,84 +13,20 @@ bench_pred <- function(data_source,
                        test_prop = 1/4) {
 
   conflict_prefer("filter", "dplyr")
+  conflict_prefer("slice", "dplyr")
   conflict_prefer("summarize", "dplyr")
   conflict_prefer("Predict", "modeltools")
+
 
   # one core per worker
   options(parallelly.availableCores.custom = function() { 1L })
 
-  print(paste("Number of cores available:", availableCores()))
-
   set.seed(run_seed)
 
-  switch(
-
-    data_source,
-
-    'pbc_orsf' = {
-      data_all <- aorsf::pbc_orsf |>
-        select(-id) |>
-        as_tibble()
-    },
-
-    'rotterdam' = {
-      data_all <- survival::rotterdam |>
-        mutate(time = pmin(rtime, dtime),
-               status = if_else(rtime < dtime, recur, death)) |>
-        select(age, meno, size, grade, nodes, pgr, er, hormon,
-               time, status) |>
-        as_tibble()
-    },
-
-    'actg' = {
-
-      data_all <- mlr3proba::actg |>
-        as_tibble() |>
-        select(-id, -time_d, -censor_d) |>
-        rename(status = censor)
-
-    },
-
-    'guide_it' = {
-
-      data_all <- guide_it_build() |>
-        select(-deidnum)
-
-    },
-
-    'breast' = {
-
-      data("Breast",package='biospear')
-
-      data_all <- Breast
-
-      names(data_all)[4:ncol(data_all)] <-
-        paste('var',4:ncol(data_all),sep='_')
-
-    },
-
-    'sim' = {
-
-      data_all <- sim_surv(n_obs = n_obs,
-                           n_z = n_z,
-                           correlated_x = correlated_x) |>
-        getElement('data')
-
-    },
-
-    'sprint-cvd' = {
-
-      data_all <- load_sprint_ndi(outcome = 'cvd')
-
-    },
-
-    'sprint-acm' = {
-
-      data_all <- load_sprint_ndi(outcome = 'acm')
-
-    }
-
-  )
+  data_all <- load_data(data_source,
+                        n_obs = n_obs,
+                        n_z = n_z,
+                        correlated_x = correlated_x)
 
   pred_horizon <- median(data_all$time)
 
@@ -120,13 +56,11 @@ bench_pred <- function(data_source,
   models <- set_names(
     c(
[…]

### 2022-05-23 R/model_fit.R

@@ -10,8 +10,10 @@ model_fit <- function(type, train) {
 
   message("fitting ", type, " model")
 
+  # params shared by all tree models
   mtry <- round(sqrt(ncol(train)-2))
   node_size <- 10
+
   aorsf_cph_iter <- 1
 
   type_simplified <- type
@@ -30,25 +32,23 @@ model_fit <- function(type, train) {
 
   }
 
-
-  orsf_prefit <- orsf(
-    Surv(time, status) ~ .,
-    mtry = mtry,
-    split_min_obs = node_size,
-    control = control,
-    data = train,
-    no_fit = TRUE
-  )
-
   start_time <- Sys.time()
 
-  print(type_simplified)
-
   switch(
+
     type_simplified,
 
     'aorsf' = {
-      res <- orsf_train(orsf_prefit)
+      res <- orsf(
+        data_train = train,
+        formula = Surv(time, status) ~ .,
+        mtry = mtry,
+        n_retry = 3,
+        split_min_obs = node_size,
+        control = control,
+        oobag_pred = FALSE
+      )
+
     },
 
     'cif' = {
@@ -59,18 +59,53 @@ model_fit <- function(type, train) {
 
     'coxtime' = {
 
+
+      nn <- list(
+        c(mtry),
+        c(mtry, mtry/2),
+        c(mtry, mtry/2 , mtry/2),
+        c(mtry, mtry/2, mtry/2 , mtry/2),
+        c(mtry, mtry, mtry/2, mtry/2 , mtry/2),
+        c(mtry, mtry, mtry, mtry/2, mtry/2 , mtry/2),
+        c(mtry, mtry, mtry, mtry, mtry/2, mtry/2 , mtry/2),
+        c(mtry, mtry, mtry, mtry, mtry, mtry/2, mtry/2 , mtry/2)
+      )
+
+      tuners <- map(
+        .x = nn,
+        .f = ~ coxtime(
+          Surv(time, status) ~ .,
+          data = train,
+          frac = 0.25,
+          activation = "relu",
+          num_nodes = .x,
+          dropout = 0.1,
+          early_stopping = TRUE,
+          epochs = 500,
+          batch_size = 32L
+        )
+      )
+
+      scores <- tuners |>
+        map_dbl(~min(.x$model$val_metrics$scores$loss$score))
+
+      winner_loss_vals <-
+        tuners[[which.min(scores)]]$model$val_metrics$scores$loss$score
+
+      epochs <-
[…]

### 2022-05-23 _targets.R

@@ -13,15 +13,23 @@ lapply(list.files("./R", full.names = TRUE), base::source)
 
 analyses_real <- expand_grid(
   data_source = c(
+    "vdv",
+    "veteran",
+    "colon",
     "pbc_orsf",
+    'time-to-million',
+    'gbsg2',
+    'peakV02',
+    'flchain',
+    'nafld',
     "rotterdam",
-    "actg"
-    # "guide_it"
-    # "breast",
-    # "sprint-cvd",
-    # "sprint-acm"
+    "actg",
+    "guide_it",
+    "breast",
+    "sprint-cvd",
+    "sprint-acm"
   ),
-  run_seed = 1:10
+  run_seed = 1:19
 ) |>
   mutate(
     n_obs = NA_real_,
@@ -39,7 +47,7 @@ analyses_sim <- expand_grid(data_source = 'sim',
 tar_plan(
 
   bm_pred <- tar_map(
-    values = analyses_real, #bind_rows(analyses_sim, analyses_real),
+    values = analyses_real, #bind_rows(analyses_real, analyses_sim),
     tar_target(
       res_pred,
       bench_pred(data_source = data_source,
@@ -49,26 +57,31 @@ tar_plan(
                  run_seed = run_seed),
       resources = tar_resources(
         future = tar_resources_future(
-          resources = list(n_cores=1)
+          resources = list(n_cores=3)
         )
       )
     )
   ),
 
-  # bm_vi <- tar_map(
-  #   values = analyses_sim,
-  #   tar_target(res_vi, bench_vi(data_source = data_source,
-  #                               n_obs = n_obs,
-  #                               n_z = n_z,
-  #                               run_seed = run_seed,
-  #                               correlated_x = correlated_x))
-  #
-  # ),
+  bm_vi <- tar_map(
+    values = analyses_sim,
+    tar_target(res_vi, bench_vi(data_source = data_source,
+                                n_obs = n_obs,
+                                n_z = n_z,
+                                run_seed = run_seed,
+                                correlated_x = correlated_x))
+
+  ),
+
+  tar_target(
+    data_key,
+    summarize_data_source(x = unique(analyses_real$data_source))
+  ),
 
 
   tar_combine(bm_pred_comb, bm_pred[[1]]),
 
-  # tar_combine(bm_vi_comb, bm_vi[[1]])
+  tar_combine(bm_vi_comb, bm_vi[[1]])
 
   #
   # tar_target(

### 2022-05-24 paper/jmlr/main.Rnw
much more modular sim

@@
 \usepackage{caption}
+\usepackage{hyperref}
+\hypersetup{hidelinks}
 
@@
 
+Table \ref{table:1} is an example of a referenced \LaTeX{}.
 Several machine learning algorithms can engage with right-censored time-to-event outcomes.
@@
 
+\begin{table}[h!]
+\centering
+\begin{tabular}{p{2cm} | p{3cm} p{7cm}}
+ \hline
+ Learner & Software & Description \\ [0.5ex]
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Random Survival Forests}}\\
+ \hline\hline
+ Standard & \href{https://www.randomforestsrc.org/index.html}{\texttt{RandomForestSRC}} & Axis based survival trees following Leo Breiman's original random forest algorithm, with cut-points selected to maximize a log-rank statistic.
+\\ \hline
+ Oblique & \href{https://CRAN.R-project.org/package=obliqueRSF}{\texttt{obliqueRSF}} \newline \href{https://bcjaeger.github.io/aorsf/}{\texttt{aorsf}} & Oblique survival trees following Leo Breiman's random forest algorithm but not using random coefficients for linear combinations.
+\texttt{obliqueRSF} uses penalized models, and \texttt{aorsf} additionally uses partially trained models.
+Cut-points are selected to maximize a log-rank statistic.
+\\ \hline
+ Extremely \,Randomized & \href{https://CRAN.R-project.org/package=ranger}{\texttt{ranger}} & Axis-based survival trees grown with randomly selected features and cut-points\\ \hline
+ Conditional \,Inference & \href{http://party.r-forge.r-project.org/}{\texttt{party}} & Axis based survival trees grown using unbiased recursive partitioning.  \\
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Boosting ensembles}}\\
+ \hline\hline
+ Trees & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & The Cox likelihood function is maximized additively with decision trees.
+Nested cross validation (5 folds) is applied to tune the number of trees grown.
+\\
+ Models & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & The accelerated failure time likelihood function is maximized additively with decision trees.
+Nested cross validation (5 folds) is applied to tune the number of trees grown.
+\\
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Regression models}}\\
+ \hline\hline
+ Cox Net & \texttt{glmnet} & The Cox model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Neural networks}}\\
+ \hline\hline
+ Cox Time & 6 & 87837  \\
+ \hline
+\end{tabular}
+\caption{Table to test captions and labels.}
+\label{table:1}
+\end{table}
+
 \section{Results}
@@
     across(
-      .cols = c(cstat, IPA, time_fit, time_prd),
+      .cols = c(cstat, IPA, time_fit, time_pred),
       .fns = list(mean = mean, sd = sd)
@@
     across(.cols = starts_with("time"), .fns = as.numeric),
-    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf-1'],
-    time_prd_ratio = time_prd_mean / time_prd_mean[model == 'aorsf-1']
+    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf_1'],
+    time_pred_ratio = time_pred_mean / time_pred_mean[model == 'aorsf_1']
   ) |>
@@
       model,
-      "aorsf-15" = 'aORSF(i=15)',
-      "aorsf-1" = 'aORSF(i=1)',
+      "aorsf_15" = 'aORSF(i=15)',
+      "aorsf_1" = 'aORSF(i=1)',
       "ranger" = 'Ranger',
@@
     time_fit_ratio = table_value(time_fit_ratio),
-    time_prd_mean = format(round(time_prd_mean, 3), nsmall = 3),
-    time_prd_ratio = table_value(time_prd_ratio)
+    time_pred_mean = format(round(time_pred_mean, 3), nsmall = 3),
+    time_pred_ratio = table_value(time_pred_ratio)
   )

### 2022-05-24 paper/jmlr/main.tex
much more modular sim

@@
 gradient boosted decision trees \texttt{xgboost}
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{p{2cm} | p{3cm} p{7cm}}
+ \hline
+ Learner & Software & Description \\ [0.5ex]
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Random Survival Forests}}\\
+ \hline\hline
+ Standard & \href{https://www.randomforestsrc.org/index.html}{\texttt{RandomForestSRC}} & Axis based survival trees following Leo Breiman's original random forest algorithm, with cut-points selected to maximize a log-rank statistic.
+\\ \hline
+ Oblique & \href{https://CRAN.R-project.org/package=obliqueRSF}{\texttt{obliqueRSF}} \newline \href{https://bcjaeger.github.io/aorsf/}{\texttt{aorsf}} & Oblique survival trees following Leo Breiman's random forest algorithm but not using random coefficients for linear combinations.
+\texttt{obliqueRSF} uses penalized models, and \texttt{aorsf} additionally uses partially trained models.
+Cut-points are selected to maximize a log-rank statistic.
+\\ \hline
+ Extremely \,Randomized & \href{https://CRAN.R-project.org/package=ranger}{\texttt{ranger}} & Axis-based survival trees grown with randomly selected features and cut-points\\ \hline
+ Conditional \,Inference & \href{http://party.r-forge.r-project.org/}{\texttt{party}} & Axis based survival trees grown using unbiased recursive partitioning.  \\
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Boosting ensembles}}\\
+ \hline\hline
+ Trees & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & The Cox likelihood function is maximized additively with decision trees.
+Nested cross validation (5 folds) is applied to tune the number of trees grown.
+\\
+ Models & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & The accelerated failure time likelihood function is maximized additively with decision trees.
+Nested cross validation (5 folds) is applied to tune the number of trees grown.
+\\
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Regression models}}\\
+ \hline\hline
+ Cox Net & \texttt{glmnet} & The Cox model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Neural networks}}\\
+ \hline\hline
+ Cox Time & 6 & 87837  \\
+ \hline
+\end{tabular}
+\caption{Table to test captions and labels.}
+\label{table:1}
+\end{table}
 
@@
 \hline
-\hspace{1em}Ranger & 0.740 (0.042) & 0.053 (0.034) & 0.316 & 0.334 & 0.120 & 1.95\\
-\hspace{1em}Xgboost & 0.739 (0.041) & 0.044 (0.052) & 3.496 & 3.69 & 0.028 & 0.461\\
-\hspace{1em}aORSF(i=1) & 0.735 (0.041) & 0.046 (0.050) & 0.947 & 1.00 & 0.062 & 1.00\\
-\hspace{1em}obliqueRSF & 0.734 (0.038) & 0.049 (0.041) & 42.337 & 44.7 & 4.027 & 65.3\\
-\hspace{1em}aORSF(i=15) & 0.733 (0.039) & 0.044 (0.048) & 2.199 & 2.32 & 0.056 & 0.904\\
-\hspace{1em}Party & 0.733 (0.036) & 0.048 (0.044) & 1.950 & 2.06 & 2.795 & 45.3\\
-\hspace{1em}aorsf-net & 0.729 (0.037) & 0.041 (0.052) & 29.028 & 30.6 & 0.060 & 0.969\\
-\hspace{1em}Rfsrc & 0.719 (0.040) & 0.027 (0.067) & 0.288 & 0.304 & 0.056 & 0.908\\
-\hspace{1em}Coxtime & 0.585 (0.127) & -0.004 (0.052) & 9.717 & 10.3 & 0.458 & 7.42\\
+\hspace{1em}Party & 0.772 (0.058) & 0.076 (0.042) & 2.181 & 2.19 & 4.889 & 4.62\\
+\hspace{1em}aORSF(i=1) & 0.755 (0.059) & 0.057 (0.055) & 0.998 & 1.00 & 1.057 & 1.00\\
+\hspace{1em}Ranger & 0.754 (0.064) & 0.064 (0.027) & 0.397 & 0.398 & 0.510 & 0.483\\
+\hspace{1em}aORSF(i=15) & 0.754 (0.063) & 0.052 (0.056) & 2.498 & 2.50 & 2.559 & 2.42\\
+\hspace{1em}Rfsrc & 0.752 (0.064) & 0.061 (0.047) & 0.775 & 0.777 & 0.833 & 0.787\\
+\hspace{1em}aorsf\_net & 0.750 (0.059) & 0.055 (0.064) & 28.449 & 28.5 & 28.510 & 27.0\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aORSF(i=1) & 0.742 (0.046) & 0.116 (0.045) & 4.732 & 1.00 & 0.300 & 1.00\\
-\hspace{1em}obliqueRSF & 0.739 (0.049) & 0.112 (0.042) & 2854.152 & 603.2 & 6.075 & 20.3\\
-\hspace{1em}aORSF(i=15) & 0.739 (0.048) & 0.117 (0.048) & 11.412 & 2.41 & 0.289 & 0.964\\
-\hspace{1em}Party & 0.736 (0.054) & 0.102 (0.039) & 7.197 & 1.52 & 1.862 & 6.21\\
-\hspace{1em}Xgboost & 0.731 (0.050) & 0.094 (0.038) & 5.372 & 1.14 & 0.274 & 0.913\\
-\hspace{1em}aorsf-net & 0.730 (0.048) & 0.020 (0.086) & 611.280 & 129.2 & 0.299 & 0.996\\
-\hspace{1em}Ranger & 0.728 (0.047) & 0.087 (0.035) & 0.281 & 0.059 & 0.171 & 0.570\\
-\hspace{1em}Rfsrc & 0.688 (0.040) & 0.046 (0.043) & 0.436 & 0.092 & 0.152 & 0.508\\
-\hspace{1em}Coxtime & 0.659 (0.080) & -0.007 (0.123) & 17.179 & 3.63 & 1.307 & 4.36\\
+\hspace{1em}aORSF(i=15) & 0.764 (0.008) & 0.143 (0.016) & 11.867 & 2.56 & 12.403 & 2.43\\
+\hspace{1em}Ranger & 0.756 (0.013) & 0.102 (0.017) & 0.555 & 0.120 & 0.724 & 0.142\\
+\hspace{1em}Party & 0.753 (0.013) & 0.118 (0.016) & 8.030 & 1.73 & 10.445 & 2.05\\
+\hspace{1em}aORSF(i=1) & 0.751 (0.002) & 0.120 (0.012) & 4.636 & 1.00 & 5.106 & 1.00\\
+\hspace{1em}aorsf\_net & 0.741 (0.022) & 0.062 (0.049) & 585.625 & 126.3 & 585.887 & 114.7\\
+\hspace{1em}Rfsrc & 0.707 (0.005) & 0.049 (0.039) & 1.354 & 0.292 & 1.522 & 0.298\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Rfsrc & 0.816 (0.020) & 0.283 (0.029) & 1.469 & 0.470 & 0.172 & 0.884\\
-\hspace{1em}aORSF(i=15) & 0.787 (0.021) & 0.219 (0.030) & 7.471 & 2.39 & 0.190 & 0.975\\
-\hspace{1em}aORSF(i=1) & 0.785 (0.018) & 0.219 (0.027) & 3.127 & 1.00 & 0.195 & 1.00\\
-\hspace{1em}aorsf-net & 0.784 (0.020) & 0.215 (0.029) & 159.569 & 51.0 & 0.190 & 0.977\\
-\hspace{1em}Xgboost & 0.783 (0.018) & 0.231 (0.025) & 8.686 & 2.78 & 0.049 & 0.252\\
-\hspace{1em}obliqueRSF & 0.782 (0.019) & 0.219 (0.021) & 294.395 & 94.2 & 8.161 & 41.9\\
-\hspace{1em}Party & 0.753 (0.019) & 0.185 (0.020) & 3.273 & 1.05 & 6.168 & 31.7\\
-\hspace{1em}Ranger & 0.741 (0.021) & 0.151 (0.017) & 1.030 & 0.329 & 0.631 & 3.24\\
-\hspace{1em}Coxtime & 0.531 (0.052) & -0.003 (0.005) & 14.933 & 4.78 & 2.590 & 13.3\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{flchain}}}\\
-\hline
-\hspace{1em}aORSF(i=1) & 0.831 (0.013) & 0.334 (0.025) & 14.475 & 1.00 & 1.238 & 1.00\\
-\hspace{1em}aORSF(i=15) & 0.831 (0.013) & 0.333 (0.024) & 29.203 & 2.02 & 1.231 & 0.994\\
-\hspace{1em}aorsf-net & 0.829 (0.013) & 0.330 (0.024) & 442.726 & 30.6 & 1.219 & 0.985\\
-\hspace{1em}Xgboost & 0.829 (0.012) & 0.331 (0.021) & 7.123 & 0.492 & 0.267 & 0.216\\
-\hspace{1em}Ranger & 0.828 (0.013) & 0.325 (0.022) & 100.469 & 6.94 & 17.866 & 14.4\\
-\hspace{1em}Party & 0.827 (0.013) & 0.325 (0.024) & 33.053 & 2.28 & 81.937 & 66.2\\
-\hspace{1em}obliqueRSF & 0.825 (0.013) & 0.325 (0.024) & 1800.099 & 124.4 & 59.969 & 48.4\\
-\hspace{1em}Rfsrc & 0.825 (0.012) & 0.323 (0.022) & 5.793 & 0.400 & 0.453 & 0.366\\
-\hspace{1em}Coxtime & 0.582 (0.109) & -0.015 (0.067) & 22.765 & 1.57 & 13.661 & 11.0\\
+\hspace{1em}Rfsrc & 0.815 (0.007) & 0.279 (0.007) & 1.854 & 0.581 & 2.026 & 0.600\\
+\hspace{1em}aORSF(i=15) & 0.778 (0.007) & 0.199 (0.018) & 7.515 & 2.36 & 7.709 & 2.28\\
+\hspace{1em}aORSF(i=1) & 0.776 (0.004) & 0.201 (0.014) & 3.190 & 1.00 & 3.378 & 1.00\\
+\hspace{1em}aorsf\_net & 0.753 (0.006) & 0.156 (0.018) & 149.637 & 46.9 & 149.809 & 44.3\\
+\hspace{1em}Party & 0.753 (0.012) & 0.183 (0.008) & 3.968 & 1.24 & 10.451 & 3.09\\
+\hspace{1em}Ranger & 0.738 (0.008) & 0.147 (0.005) & 1.795 & 0.563 & 2.398 & 0.710\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Ranger & 0.733 (0.045) & 0.118 (0.030) & 0.373 & 0.401 & 0.124 & 1.83\\
-\hspace{1em}obliqueRSF & 0.732 (0.036) & 0.151 (0.040) & 130.378 & 140.0 & 2.473 & 36.4\\
-\hspace{1em}aORSF(i=15) & 0.731 (0.037) & 0.146 (0.046) & 2.116 & 2.27 & 0.061 & 0.899\\
-\hspace{1em}Party & 0.731 (0.038) & 0.146 (0.044) & 0.691 & 0.742 & 1.008 & 14.8\\
-\hspace{1em}aORSF(i=1) & 0.730 (0.037) & 0.144 (0.049) & 0.931 & 1.00 & 0.068 & 1.00\\
-\hspace{1em}aorsf-net & 0.729 (0.036) & 0.144 (0.047) & 57.048 & 61.3 & 0.062 & 0.910\\
-\hspace{1em}Xgboost & 0.728 (0.037) & 0.126 (0.037) & 2.580 & 2.77 & 0.029 & 0.428\\
-\hspace{1em}Rfsrc & 0.723 (0.035) & 0.139 (0.047) & 0.618 & 0.664 & 0.086 & 1.27\\
-\hspace{1em}Coxtime & 0.519 (0.058) & -0.057 (0.134) & 10.882 & 11.7 & 0.680 & 10.0\\
+\hspace{1em}Ranger & 0.704 (0.076) & 0.090 (0.045) & 0.328 & 0.339 & 0.450 & 0.438\\
+\hspace{1em}Party & 0.686 (0.042) & 0.092 (0.048) & 0.746 & 0.773 & 2.055 & 2.00\\
+\hspace{1em}aORSF(i=15) & 0.685 (0.048) & 0.077 (0.066) & 2.077 & 2.15 & 2.144 & 2.09\\
+\hspace{1em}Rfsrc & 0.676 (0.032) & 0.067 (0.052) & 0.931 & 0.963 & 1.014 & 0.986\\
+\hspace{1em}aORSF(i=1) & 0.674 (0.045) & 0.062 (0.062) & 0.966 & 1.00 & 1.028 & 1.00\\
+\hspace{1em}aorsf\_net & 0.670 (0.038) & 0.068 (0.056) & 57.024 & 59.0 & 57.087 & 55.5\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aORSF(i=1) & 0.725 (0.032) & 0.124 (0.038) & 1.663 & 1.00 & 0.110 & 1.00\\
-\hspace{1em}aORSF(i=15) & 0.724 (0.034) & 0.123 (0.039) & 4.896 & 2.94 & 0.106 & 0.963\\
-\hspace{1em}aorsf-net & 0.724 (0.034) & 0.119 (0.040) & 84.799 & 51.0 & 0.110 & 0.994\\
-\hspace{1em}obliqueRSF & 0.714 (0.037) & 0.111 (0.037) & 235.729 & 141.8 & 3.299 & 29.9\\
-\hspace{1em}Ranger & 0.713 (0.035) & 0.104 (0.032) & 0.446 & 0.268 & 0.188 & 1.70\\
-\hspace{1em}Party & 0.709 (0.036) & 0.102 (0.032) & 1.525 & 0.917 & 1.728 & 15.7\\
-\hspace{1em}Coxtime & 0.699 (0.032) & 0.077 (0.053) & 12.268 & 7.38 & 0.565 & 5.13\\
-\hspace{1em}Rfsrc & 0.698 (0.033) & 0.098 (0.034) & 0.846 & 0.509 & 0.101 & 0.915\\
-\hspace{1em}Xgboost & 0.688 (0.032) & 0.073 (0.037) & 4.948 & 2.98 & 0.033 & 0.295\\
+\hspace{1em}aORSF(i=15) & 0.730 (0.009) & 0.133 (0.008) & 4.705 & 2.67 & 4.811 & 2.57\\
+\hspace{1em}aORSF(i=1) & 0.728 (0.014) & 0.132 (0.012) & 1.762 & 1.00 & 1.869 & 1.00\\
+\hspace{1em}aorsf\_net & 0.728 (0.020) & 0.133 (0.015) & 86.476 & 49.1 & 86.590 & 46.3\\
+\hspace{1em}Party & 0.705 (0.021) & 0.101 (0.010) & 1.800 & 1.02 & 3.727 & 1.99\\
+\hspace{1em}Rfsrc & 0.705 (0.032) & 0.109 (0.027) & 1.000 & 0.568 & 1.104 & 0.591\\
+\hspace{1em}Ranger & 0.704 (0.016) & 0.102 (0.001) & 0.663 & 0.376 & 0.855 & 0.457\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Xgboost & 0.874 (0.011) & 0.218 (0.019) & 11.715 & 0.359 & 0.365 & 0.123\\
-\hspace{1em}aORSF(i=15) & 0.867 (0.011) & 0.221 (0.015) & 77.709 & 2.38 & 2.874 & 0.967\\
-\hspace{1em}aORSF(i=1) & 0.867 (0.011) & 0.219 (0.016) & 32.619 & 1.00 & 2.970 & 1.00\\
-\hspace{1em}aorsf-net & 0.867 (0.011) & 0.221 (0.016) & 628.839 & 19.3 & 3.054 & 1.03\\
-\hspace{1em}obliqueRSF & 0.865 (0.012) & 0.217 (0.015) & 2098.616 & 64.3 & 270.503 & 91.1\\
-\hspace{1em}Party & 0.861 (0.013) & 0.214 (0.014) & 111.579 & 3.42 & 460.042 & 154.9\\
-\hspace{1em}Ranger & 0.859 (0.012) & 0.189 (0.013) & 171.040 & 5.24 & 89.041 & 30.0\\
-\hspace{1em}Rfsrc & 0.858 (0.012) & 0.215 (0.014) & 11.646 & 0.357 & 1.420 & 0.478\\
-\hspace{1em}Coxtime & 0.590 (0.105) & 0.000 (0.001) & 19.733 & 0.605 & 50.705 & 17.1\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{nafld}}}\\
-\hline
-\hspace{1em}aORSF(i=1) & 0.796 (0.077) & 0.210 (0.149) & 8.429 & 1.00 & 0.683 & 1.00\\
-\hspace{1em}aORSF(i=15) & 0.796 (0.078) & 0.210 (0.148) & 20.977 & 2.49 & 0.668 & 0.978\\
-\hspace{1em}aorsf-net & 0.793 (0.080) & 0.202 (0.160) & 270.097 & 32.0 & 0.685 & 1.00\\
-\hspace{1em}obliqueRSF & 0.792 (0.075) & 0.187 (0.115) & 1025.773 & 121.7 & 37.539 & 55.0\\
-\hspace{1em}Xgboost & 0.789 (0.082) & 0.187 (0.180) & 6.797 & 0.806 & 0.213 & 0.311\\
-\hspace{1em}Party & 0.787 (0.077) & 0.190 (0.131) & 24.327 & 2.89 & 56.237 & 82.3\\
-\hspace{1em}Rfsrc & 0.786 (0.085) & 0.198 (0.155) & 2.467 & 0.293 & 0.285 & 0.417\\
-\hspace{1em}Ranger & 0.785 (0.075) & 0.170 (0.119) & 19.567 & 2.32 & 8.448 & 12.4\\
-\hspace{1em}Coxtime & 0.641 (0.148) & 0.038 (0.211) & 18.944 & 2.25 & 7.395 & 10.8\\
+\hspace{1em}aORSF(i=1) & 0.787 (0.094) & 0.202 (0.188) & 2.204 & 1.00 & 2.400 & 1.00\\
+\hspace{1em}aORSF(i=15) & 0.787 (0.100) & 0.203 (0.186) & 5.038 & 2.29 & 5.242 & 2.18\\
+\hspace{1em}Ranger & 0.783 (0.091) & 0.161 (0.138) & 0.709 & 0.322 & 1.053 & 0.438\\
+\hspace{1em}aorsf\_net & 0.782 (0.101) & 0.190 (0.202) & 128.300 & 58.2 & 128.469 & 53.5\\
+\hspace{1em}Party & 0.779 (0.094) & 0.185 (0.167) & 3.291 & 1.49 & 6.998 & 2.92\\
+\hspace{1em}Rfsrc & 0.778 (0.113) & 0.195 (0.187) & 0.956 & 0.434 & 1.076 & 0.448\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aORSF(i=1) & 0.926 (0.032) & 0.484 (0.078) & 0.327 & 1.00 & 0.031 & 1.00\\
-\hspace{1em}aorsf-net & 0.924 (0.031) & 0.481 (0.077) & 20.545 & 62.8 & 0.027 & 0.861\\
-\hspace{1em}obliqueRSF & 0.924 (0.034) & 0.442 (0.066) & 165.436 & 505.8 & 0.671 & 21.5\\
-\hspace{1em}aORSF(i=15) & 0.922 (0.031) & 0.474 (0.074) & 0.711 & 2.17 & 0.025 & 0.786\\
-\hspace{1em}Party & 0.920 (0.041) & 0.432 (0.073) & 0.276 & 0.844 & 0.319 & 10.2\\
-\hspace{1em}Xgboost & 0.917 (0.035) & 0.458 (0.085) & 4.339 & 13.3 & 0.033 & 1.04\\
-\hspace{1em}Rfsrc & 0.916 (0.033) & 0.444 (0.079) & 0.101 & 0.308 & 0.033 & 1.07\\
-\hspace{1em}Ranger & 0.903 (0.034) & 0.349 (0.041) & 0.035 & 0.107 & 0.042 & 1.33\\
-\hspace{1em}Coxtime & 0.562 (0.201) & -0.012 (0.018) & 12.376 & 37.8 & 0.322 & 10.3\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{peakV02}}}\\
-\hline
-\hspace{1em}aorsf-net & 0.721 (0.022) & 0.112 (0.034) & 174.090 & 37.6 & 0.320 & 1.04\\
-\hspace{1em}obliqueRSF & 0.720 (0.022) & 0.119 (0.030) & 614.000 & 132.8 & 10.231 & 33.3\\
-\hspace{1em}aORSF(i=15) & 0.720 (0.020) & 0.115 (0.031) & 10.718 & 2.32 & 0.302 & 0.983\\
-\hspace{1em}aORSF(i=1) & 0.720 (0.020) & 0.113 (0.032) & 4.625 & 1.00 & 0.308 & 1.00\\
-\hspace{1em}Party & 0.718 (0.023) & 0.117 (0.029) & 5.315 & 1.15 & 9.747 & 31.7\\
-\hspace{1em}Ranger & 0.714 (0.022) & 0.103 (0.023) & 2.211 & 0.478 & 1.358 & 4.42\\
-\hspace{1em}Rfsrc & 0.714 (0.019) & 0.111 (0.026) & 1.718 & 0.372 & 0.193 & 0.627\\
-\hspace{1em}Xgboost & 0.714 (0.018) & 0.102 (0.028) & 5.134 & 1.11 & 0.047 & 0.152\\
-\hspace{1em}Coxtime & 0.701 (0.028) & 0.097 (0.032) & 20.249 & 4.38 & 3.560 & 11.6\\
+\hspace{1em}aORSF(i=1) & 0.946 (0.018) & 0.493 (0.083) & 0.344 & 1.00 & 0.376 & 1.00\\
+\hspace{1em}aorsf\_net & 0.939 (0.018) & 0.484 (0.052) & 23.093 & 67.2 & 23.123 & 61.6\\
+\hspace{1em}Party & 0.936 (0.022) & 0.454 (0.022) & 0.288 & 0.839 & 0.518 & 1.38\\
+\hspace{1em}aORSF(i=15) & 0.936 (0.014) & 0.474 (0.080) & 0.744 & 2.17 & 0.773 & 2.06\\
+\hspace{1em}Rfsrc & 0.927 (0.012) & 0.462 (0.070) & 0.363 & 1.06 & 0.397 & 1.06\\
+\hspace{1em}Ranger & 0.926 (0.014) & 0.344 (0.055) & 0.044 & 0.127 & 0.085 & 0.226\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.724 (0.012) & 0.151 (0.018) & 260.864 & 43.4 & 0.377 & 0.954\\
-\hspace{1em}aORSF(i=1) & 0.723 (0.013) & 0.150 (0.019) & 6.007 & 1.00 & 0.395 & 1.00\\
-\hspace{1em}aORSF(i=15) & 0.723 (0.013) & 0.150 (0.019) & 13.286 & 2.21 & 0.390 & 0.985\\
-\hspace{1em}Xgboost & 0.722 (0.014) & 0.143 (0.017) & 3.979 & 0.662 & 0.089 & 0.225\\
-\hspace{1em}Ranger & 0.721 (0.013) & 0.143 (0.014) & 1.881 & 0.313 & 1.819 & 4.60\\
-\hspace{1em}obliqueRSF & 0.720 (0.013) & 0.149 (0.017) & 912.920 & 152.0 & 18.351 & 46.4\\
-\hspace{1em}Party & 0.719 (0.012) & 0.147 (0.016) & 6.186 & 1.03 & 15.125 & 38.3\\
-\hspace{1em}Rfsrc & 0.716 (0.013) & 0.137 (0.020) & 2.762 & 0.460 & 0.261 & 0.661\\
-\hspace{1em}Coxtime & 0.502 (0.049) & -0.047 (0.154) & 18.276 & 3.04 & 5.857 & 14.8\\
+\hspace{1em}Ranger & 0.719 (0.011) & 0.145 (0.011) & 2.480 & 0.410 & 4.456 & 0.692\\
+\hspace{1em}aorsf\_net & 0.714 (0.007) & 0.141 (0.007) & 237.007 & 39.2 & 237.337 & 36.9\\
+\hspace{1em}Party & 0.712 (0.008) & 0.141 (0.012) & 7.030 & 1.16 & 21.888 & 3.40\\
+\hspace{1em}aORSF(i=1) & 0.712 (0.006) & 0.139 (0.008) & 6.053 & 1.00 & 6.436 & 1.00\\
+\hspace{1em}aORSF(i=15) & 0.711 (0.005) & 0.139 (0.007) & 13.541 & 2.24 & 13.925 & 2.16\\
+\hspace{1em}Rfsrc & 0.701 (0.008) & 0.120 (0.010) & 2.222 & 0.367 & 2.458 & 0.382\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{sprint-acm}}}\\
+\multicolumn{7}{l}{\textit{\textbf{time\_to\_million}}}\\
 \hline
-\hspace{1em}Xgboost & 0.798 (0.014) & 0.205 (0.026) & 13.680 & 0.447 & 0.199 & 0.087\\
-\hspace{1em}aORSF(i=15) & 0.795 (0.013) & 0.199 (0.020) & 87.852 & 2.87 & 2.271 & 0.992\\
-\hspace{1em}aORSF(i=1) & 0.795 (0.013) & 0.199 (0.022) & 30.597 & 1.00 & 2.288 & 1.00\\
-\hspace{1em}aorsf-net & 0.795 (0.013) & 0.192 (0.023) & 934.189 & 30.5 & 2.298 & 1.00\\
-\hspace{1em}obliqueRSF & 0.794 (0.013) & 0.194 (0.019) & 4216.468 & 137.8 & 81.441 & 35.6\\
-\hspace{1em}Party & 0.792 (0.012) & 0.187 (0.017) & 93.194 & 3.05 & 130.262 & 56.9\\
-\hspace{1em}Rfsrc & 0.791 (0.011) & 0.192 (0.020) & 6.913 & 0.226 & 0.496 & 0.217\\
-\hspace{1em}Ranger & 0.784 (0.013) & 0.175 (0.016) & 9.100 & 0.297 & 8.720 & 3.81\\
-\hspace{1em}Coxtime & 0.768 (0.087) & 0.177 (0.054) & 46.094 & 1.51 & 15.082 & 6.59\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{sprint-cvd}}}\\
-\hline
-\hspace{1em}aorsf-net & 0.822 (0.018) & 0.136 (0.016) & 532.742 & 24.2 & 1.615 & 1.01\\
-\hspace{1em}Party & 0.821 (0.015) & 0.121 (0.009) & 92.038 & 4.18 & 126.234 & 79.0\\
-\hspace{1em}aORSF(i=15) & 0.821 (0.018) & 0.131 (0.011) & 59.100 & 2.68 & 1.591 & 0.995\\
-\hspace{1em}aORSF(i=1) & 0.821 (0.018) & 0.131 (0.011) & 22.035 & 1.00 & 1.599 & 1.00\\
-\hspace{1em}obliqueRSF & 0.821 (0.016) & 0.128 (0.009) & 1569.905 & 71.2 & 92.265 & 57.7\\
-\hspace{1em}Xgboost & 0.819 (0.016) & 0.135 (0.019) & 10.625 & 0.482 & 0.099 & 0.062\\
-\hspace{1em}Rfsrc & 0.817 (0.014) & 0.130 (0.013) & 3.344 & 0.152 & 0.451 & 0.282\\
-\hspace{1em}Ranger & 0.812 (0.017) & 0.113 (0.008) & 5.724 & 0.260 & 6.390 & 4.00\\
-\hspace{1em}Coxtime & 0.787 (0.021) & 0.098 (0.024) & 20.202 & 0.917 & 13.321 & 8.33\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{time-to-million}}}\\
-\hline
-\hspace{1em}Xgboost & 0.933 (0.018) & 0.553 (0.055) & 13.028 & 9.08 & 0.034 & 0.420\\
-\hspace{1em}Coxtime & 0.931 (0.016) & 0.563 (0.057) & 20.527 & 14.3 & 0.751 & 9.27\\
-\hspace{1em}aORSF(i=15) & 0.931 (0.017) & 0.534 (0.038) & 4.789 & 3.34 & 0.076 & 0.941\\
-\hspace{1em}aorsf-net & 0.930 (0.017) & 0.535 (0.039) & 78.002 & 54.4 & 0.077 & 0.952\\
-\hspace{1em}aORSF(i=1) & 0.929 (0.018) & 0.530 (0.040) & 1.435 & 1.00 & 0.081 & 1.00\\
-\hspace{1em}Rfsrc & 0.925 (0.018) & 0.527 (0.041) & 0.822 & 0.573 & 0.066 & 0.812\\
-\hspace{1em}Party & 0.912 (0.024) & 0.466 (0.043) & 0.617 & 0.430 & 0.905 & 11.2\\
-\hspace{1em}obliqueRSF & 0.909 (0.024) & 0.337 (0.031) & 239.423 & 166.9 & 2.436 & 30.0\\
-\hspace{1em}Ranger & 0.904 (0.024) & 0.436 (0.042) & 0.076 & 0.053 & 0.125 & 1.54\\
+\hspace{1em}aorsf\_net & 0.937 (0.013) & 0.560 (0.040) & 78.384 & 55.8 & 78.461 & 53.0\\
+\hspace{1em}aORSF(i=15) & 0.937 (0.018) & 0.555 (0.043) & 4.491 & 3.20 & 4.569 & 3.09\\
+\hspace{1em}aORSF(i=1) & 0.935 (0.017) & 0.552 (0.039) & 1.405 & 1.00 & 1.481 & 1.00\\
+\hspace{1em}Rfsrc & 0.932 (0.023) & 0.550 (0.045) & 0.784 & 0.558 & 0.853 & 0.576\\
+\hspace{1em}Party & 0.921 (0.014) & 0.485 (0.034) & 0.621 & 0.442 & 1.684 & 1.14\\
+\hspace{1em}Ranger & 0.916 (0.023) & 0.452 (0.039) & 0.324 & 0.231 & 0.428 & 0.289\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Xgboost & 0.778 (0.096) & -0.065 (0.330) & 4.236 & 1.55 & 1.617 & 2.78\\
-\hspace{1em}Rfsrc & 0.773 (0.118) & 0.047 (0.189) & 0.185 & 0.068 & 0.304 & 0.523\\
-\hspace{1em}aORSF(i=15) & 0.772 (0.091) & 0.053 (0.126) & 2.841 & 1.04 & 0.552 & 0.948\\
-\hspace{1em}aORSF(i=1) & 0.772 (0.082) & 0.046 (0.119) & 2.732 & 1.00 & 0.582 & 1.00\\
-\hspace{1em}Ranger & 0.765 (0.075) & 0.024 (0.119) & 0.496 & 0.181 & 0.099 & 0.171\\
-\hspace{1em}obliqueRSF & 0.764 (0.076) & 0.064 (0.131) & 120.857 & 44.2 & 2.945 & 5.06\\
-\hspace{1em}Party & 0.761 (0.088) & 0.053 (0.119) & 7.889 & 2.89 & 5.362 & 9.21\\
-\hspace{1em}aorsf-net & 0.750 (0.100) & 0.055 (0.188) & 21.757 & 7.96 & 0.552 & 0.948\\
-\hspace{1em}Coxtime & 0.678 (0.134) & -0.259 (0.417) & 29.478 & 10.8 & 1.899 & 3.26\\
+\hspace{1em}Rfsrc & 0.782 (0.231) & 0.033 (0.185) & 0.198 & 0.080 & 0.450 & 0.148\\
+\hspace{1em}aorsf\_net & 0.770 (0.161) & -0.019 (0.283) & 20.190 & 8.13 & 20.749 & 6.80\\
+\hspace{1em}aORSF(i=1) & 0.762 (0.079) & -0.012 (0.126) & 2.484 & 1.00 & 3.050 & 1.00\\
+\hspace{1em}Ranger & 0.751 (0.070) & -0.017 (0.093) & 0.484 & 0.195 & 0.576 & 0.189\\
+\hspace{1em}aORSF(i=15) & 0.735 (0.171) & -0.025 (0.135) & 2.569 & 1.03 & 3.136 & 1.03\\
+\hspace{1em}Party & 0.722 (0.102) & -0.030 (0.165) & 8.098 & 3.26 & 14.088 & 4.62\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aORSF(i=15) & 0.846 (0.053) & 0.291 (0.072) & 0.352 & 1.90 & 0.012 & 0.656\\
-\hspace{1em}aORSF(i=1) & 0.843 (0.053) & 0.289 (0.071) & 0.186 & 1.00 & 0.018 & 1.00\\
-\hspace{1em}aorsf-net & 0.840 (0.055) & 0.281 (0.077) & 15.971 & 86.1 & 0.012 & 0.657\\
-\hspace{1em}Ranger & 0.836 (0.072) & 0.175 (0.057) & 0.019 & 0.104 & 0.028 & 1.56\\
-\hspace{1em}obliqueRSF & 0.835 (0.051) & 0.192 (0.051) & 91.890 & 495.3 & 0.235 & 13.2\\
-\hspace{1em}Rfsrc & 0.816 (0.064) & 0.248 (0.079) & 0.057 & 0.310 & 0.023 & 1.27\\
-\hspace{1em}Party & 0.816 (0.061) & 0.208 (0.059) & 0.117 & 0.632 & 0.067 & 3.75\\
-\hspace{1em}Xgboost & 0.780 (0.069) & 0.151 (0.085) & 3.009 & 16.2 & 0.026 & 1.47\\
-\hspace{1em}Coxtime & 0.523 (0.077) & -0.038 (0.055) & 9.481 & 51.1 & 0.159 & 8.97\\*
+\hspace{1em}Ranger & 0.865 (0.063) & 0.183 (0.036) & 0.023 & 0.113 & 0.043 & 0.194\\
+\hspace{1em}aORSF(i=15) & 0.837 (0.048) & 0.281 (0.075) & 0.371 & 1.84 & 0.387 & 1.75\\
+\hspace{1em}aORSF(i=1) & 0.833 (0.053) & 0.278 (0.081) & 0.202 & 1.00 & 0.222 & 1.00\\
+\hspace{1em}Party & 0.833 (0.057) & 0.235 (0.056) & 0.150 & 0.744 & 0.231 & 1.04\\
+\hspace{1em}aorsf\_net & 0.820 (0.059) & 0.256 (0.083) & 17.115 & 84.7 & 17.133 & 77.3\\
+\hspace{1em}Rfsrc & 0.784 (0.111) & 0.218 (0.112) & 0.077 & 0.380 & 0.099 & 0.447\\*
 \end{longtable}

### 2022-05-24 R/bench_pred.R

@@ -6,6 +6,10 @@
 #' @param data_source
 #' @param run_seed
 bench_pred <- function(data_source,
+                       model_type,
+                       data_load_fun,
+                       model_fit_fun,
+                       model_prd_fun,
                        n_obs = NULL,
                        n_z = NULL,
                        correlated_x = NULL,
@@ -17,19 +21,11 @@ bench_pred <- function(data_source,
   conflict_prefer("summarize", "dplyr")
   conflict_prefer("Predict", "modeltools")
 
-
-  # one core per worker
-  options(parallelly.availableCores.custom = function() { 1L })
-
   set.seed(run_seed)
 
-  data_all <- load_data(data_source,
-                        n_obs = n_obs,
-                        n_z = n_z,
-                        correlated_x = correlated_x)
-
-  pred_horizon <- median(data_all$time)
-
+  data_all <- data_load_fun(n_obs = n_obs,
+                            n_z = n_z,
+                            correlated_x = correlated_x)
 
   if(data_source == 'sim'){
 
@@ -52,22 +48,6 @@ bench_pred <- function(data_source,
 
   }
 
-
-  models <- set_names(
-    c(
-      'aorsf-1',
-      'aorsf-15',
-      'aorsf-net',
-      'cif',
-      'coxtime',
-      'obliqueRSF',
-      'xgboost',
-      'randomForestSRC',
-      'ranger'
-    )
-  )
-
-
   imputer <- recipe(x = train, time + status ~ .) |>
     step_impute_mean(all_numeric_predictors()) |>
     step_impute_mode(all_nominal_predictors()) |>
@@ -75,66 +55,56 @@ bench_pred <- function(data_source,
     step_range(all_numeric_predictors()) |>
     prep()
 
-  .train <- juice(imputer)
-  .test <- bake(imputer, new_data = test)
+  .train <- as.data.frame(juice(imputer))
+  .test <- as.data.frame(bake(imputer, new_data = test))
 
+  pred_horizon <- median(.train$time)
 
-  fits <- map(models, model_fit, train = as.data.frame(.train))
+  model <- model_fit_fun(train = .train) |>
+    model_prd_fun(test = .test, pred_horizon = pred_horizon)
 
-  prds <- map2(.x = fits,
-               .y = models,
-               .f = model_pred,
-               test = as.data.frame(.test),
[…]

### 2022-05-24 R/model_fit.R

@@ -5,184 +5,268 @@
 #' @title
 #' @param type
 #' @param train
-model_fit <- function(type, train) {
 
 
-  message("fitting ", type, " model")
+# template to be used for writing specific functions
+# model_fit <- function(train, node_size = 10){
+#
+  # mtry <- round(sqrt(ncol(train)-2))
+  #
+  # start_time <- Sys.time()
+  #
+  # # code for fitting
+  #
+  # end_time <- Sys.time()
+  #
+  # list(fit = fit, time_fit = end_time - start_time)
+#
+# }
 
-  # params shared by all tree models
+aorsf_cph_1_fit <- function(train, node_size = 10){
+
   mtry <- round(sqrt(ncol(train)-2))
-  node_size <- 10
-
-  aorsf_cph_iter <- 1
-
-  type_simplified <- type
-
-  control = orsf_control_net()
-
-  if(str_detect(type, '^aorsf')){
-
-    aorsf_cph_iter = as.numeric(str_extract(type, '\\d+'))
-
-    if(!is.na(aorsf_cph_iter)) {
-      control = orsf_control_cph(iter_max = aorsf_cph_iter)
-    }
-
-    type_simplified <- 'aorsf'
-
-  }
 
   start_time <- Sys.time()
 
-  switch(
-
-    type_simplified,
-
-    'aorsf' = {
-      res <- orsf(
-        data_train = train,
-        formula = Surv(time, status) ~ .,
-        mtry = mtry,
-        n_retry = 3,
-        split_min_obs = node_size,
-        control = control,
-        oobag_pred = FALSE
-      )
-
-    },
-
-    'cif' = {
-      res <- cforest(Surv(time, status) ~ .,
-                     controls = cforest_unbiased(mtry = mtry),
-                     data = train)
-    },
-
-    'coxtime' = {
-
-
-      nn <- list(
-        c(mtry),
-        c(mtry, mtry/2),
-        c(mtry, mtry/2 , mtry/2),
-        c(mtry, mtry/2, mtry/2 , mtry/2),
-        c(mtry, mtry, mtry/2, mtry/2 , mtry/2),
-        c(mtry, mtry, mtry, mtry/2, mtry/2 , mtry/2),
-        c(mtry, mtry, mtry, mtry, mtry/2, mtry/2 , mtry/2),
-        c(mtry, mtry, mtry, mtry, mtry, mtry/2, mtry/2 , mtry/2)
-      )
-
-      tuners <- map(
-        .x = nn,
[…]

### 2022-05-24 R/model_new.R

@@ -1,0 +1,20 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param model_type
+model_new <- function(model_type) {
+
+  out <- list(model_fit = NULL,
+              model_pred = NULL,
+              time_fit = NULL,
+              time_pred = NULL)
+
+  attr(out, 'model_type') <- model_type
+
+  class(out) <- str_extract(model_type, '[a-zA-Z]+')
+
+  out
+
+}

### 2022-05-24 R/summarize_data_source.R

@@ -11,26 +11,23 @@ summarize_data_source <- function(x) {
   conflict_prefer("summarize", "dplyr")
   conflict_prefer("Predict", "modeltools")
 
-  x = c(
-    "vdv",
-    "veteran",
-    "colon",
-    "pbc_orsf",
-    'time-to-million',
-    'gbsg2',
-    'peakV02',
-    'flchain',
-    'nafld',
-    "rotterdam",
-    "actg",
-    "guide_it",
-    "breast",
-    "sprint-cvd",
-    "sprint-acm"
-  ) |>
-    set_names()
-
-  all_data <- map(.x = x, .f = load_data)
+  all_data = list(
+    "vdv" = load_vdv(),
+    "veteran" = load_veteran(),
+    "colon" = load_colon(),
+    "pbc_orsf" = load_pbc_orsf(),
+    'time_to_million' = load_time_to_million(),
+    'gbsg2' = load_gbsg2(),
+    'peakV02' = load_peakV02(),
+    'flchain' = load_flchain(),
+    'nafld' = load_nafld(),
+    "rotterdam" = load_rotterdam(),
+    "actg" = load_actg(),
+    "guide_it" = load_guide_it(),
+    "breast" = load_breast(),
+    "sprint_cvd" = load_sprint_cvd(),
+    "sprint_acm" = load_sprint_acm()
+  )
 
   data_info <- map_dfr(
     .x = all_data,

### 2022-06-06 paper/jmlr/main.Rnw
prediction benchmark and intro

--- 2022-05-23 paper/jmlr/main.Rnw
@@
 \usepackage{jmlr2e}
-% extra packages for tables
+% extra packages
 \usepackage{longtable}
@@
 \usepackage{caption}
+\usepackage{hyperref}
+\hypersetup{hidelinks}
+\usepackage{geometry}
+\usepackage{pdflscape}
+\usepackage{bm}
 
@@
 \newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
+\newcommand{\ie}{that is}
+\newcommand{\eg}{for example}
+\newcommand{\cstat}{\widehat{\text{C}}(t)}
+\newcommand{\bstat}{\widehat{\text{BS}}(t)}
+\newcommand{\bsbar}{\mathcal{\widehat{BS}}(t_1, t_2)}
+\newcommand{\bskap}{\mathcal{\widehat{BS}}_0(t_1, t_2)}
+
+\newcommand{\ntrain}{N_{\text{train}}}
+\newcommand{\ntest}{N_{\text{test}}}
 
@@
 
-\ShortHeadings{Learning with Mixtures of Trees}{Meil\u{a} and Jordan}
+\ShortHeadings{Accelerated oblique random survival forests}{Jaeger et al}
 \firstpageno{1}
@@
 
-\author{\name Marina Meil\u{a} \email mmp@stat.washington.edu \\
-       \addr Department of Statistics\\
-       University of Washington\\
-       Seattle, WA 98195-4322, USA
+\author{\name Byron C. Jaeger \email bjaeger@wakehealth.edu \\
+       \addr Department of Biostatistics and Data Science\\
+       Wake Forest University School of Medicine\\
+       Winston-Salem, NC 27157, USA
        \AND
-       \name Michael I.\ Jordan \email jordan@cs.berkeley.edu \\
-       \addr Division of Computer Science and Department of Statistics\\
-       University of California\\
-       Berkeley, CA 94720-1776, USA}
+       \name Sawyer Welden \email swelden@wakehealth.edu \\
+       \addr Department of Biostatistics and Data Science\\
+       Wake Forest University School of Medicine\\
+       Winston-Salem, NC 27157, USA
+       \AND
+       \name Kristin Lenoir \email klenoir@wakehealth.edu \\
+       \addr Department of Biostatistics and Data Science\\
+       Wake Forest University School of Medicine\\
+       Winston-Salem, NC 27157, USA
+       \AND
+       \name Jaime L Speiser \email jspeiser@wakehealth.edu \\
+       \addr Department of Biostatistics and Data Science\\
+       Wake Forest University School of Medicine\\
+       Winston-Salem, NC 27157, USA
+       \AND
+       \name Matthew Segar \email Matthew.Segar@UTSouthwestern.edu \\
+       \addr Division of Cardiology, Department of Internal Medicine, \\
+       University of Texas Southwestern Medical Center, Dallas
+       \AND
+       \name Nicholas M. Pajewski \email npajewsk@wakehealth.edu \\
+       \addr Department of Biostatistics and Data Science\\
+       Wake Forest University School of Medicine\\
+       Winston-Salem, NC 27157, USA}
 
-\editor{Kevin Murphy and Bernhard Sch{\"o}lkopf}
+\editor{TBD}
 
@@
 
-tar_load(names = c(bm_pred_comb, bm_vi_comb))
+tar_load(names = c(bm_pred_comb,
+                   bm_vi_comb,
+                   bm_pred_viz,
+                   bm_pred_model_viz,
+                   data_key,
+                   model_key))
+
+to_omit <- bm_pred_comb |>
+  filter(is.na(cstat) | is.na(ibs_scaled)) |>
+  distinct(data, run) |>
+  as.list() |>
+  map(unique)
+
+bm_pred_comb <- bm_pred_comb |>
+  filter( ! (data %in% to_omit$data & run %in% to_omit$run) )
 
@@
 
+\newpage
+
 \begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
-abstract here
+
+The oblique random survival forest (ORSF) is an ensemble method for supervised learning that extends the random survival forest (RSF).
+Trees in the ORSF are grown using linear combinations of variables to create branches in the tree, whereas in the RSF a single variable is used.
+ORSF ensembles often have higher prediction accuracy than RSF ensembles, but the additional computational overhead of fitting ORSF ensembles limits their scope of application.
+In addition, few methods have been developed for interpretation of ORSF ensembles.
+In this article, we introduce and evaluate methods to accelerate the ORSF (\ie, reduce computational overhead) and compute the importance of individual variables in the ORSF We show that our strategy to accelerate the ORSF is up to 500 times faster than existing software for ORSFs (the \texttt{obliqueRSF} R package), and that prediction accuracy of the accelerated ORSF is equivalent or superior to that of existing ORSF methods.
+We estimate importance of variables for the ORSF by negating each coefficient used for the given variable in linear combinations, and then computing the reduction in out-of-bag accuracy.
+We show with simulation that  `negation importance' can discriminate between signal and noise variables, and it outperforms several state-of-the-art variable importance techniques in this task when there is correlation among predictors.
+
 \end{abstract}
@@
 \begin{keywords}
-  Bayesian networks, mixture models, Chow-Liu trees
+  Random Forests, Survival, Efficient, Variable Importance
 \end{keywords}
@@
 
+Risk prediction can reduce the burden of disease by educating patients and providers and guiding strategies to prevent and treat disease in a wide range of medical domains \citep{moons2012riskI, moons2012riskII}.
+The random survival forest (RSF), a supervised learning algorithm that can engage with censored outcomes, is frequently used for risk prediction.
+Notable characteristics of the RSF include uniform convergence of its ensemble survival function to the true population survival function when the predictor space is discrete.
+In addition, software implementing the RSF is freely available, extremely efficient, and full of tools to interpret and explain the RSF.
+However, there remains considerable potential to improve the RSF in risk prediction tasks where training samples are not large enough to guarantee asymptotic properties or predictor spaces are non-discrete (\ie, predictors are continuous).
+
+RSFs may be axis based or oblique.
+The axis based RSF uses a single predictor whereas the oblique RSF uses a linear combination of predictors to create branches in trees.
+While axis based decision boundaries are always perpendicular to the axis of the relevant predictor, linear combinations of predictors create oblique decision boundaries that are neither parallel nor perpendicular to axes of their contributing predictors.
+Prior work has found the oblique RSF has higher prediction accuracy than the axis based RSF in general benchmarks \citep{jaeger2019oblique} and that oblique splitting is particularly effective when predictor spaces are non-discrete.
+However, existing methods to implement oblique RSFs use fully trained models in each non-leaf node to identify linear combinations of predictors, exponentially increasing the number of operations required for the oblique RSF versus its axis based counterpart.
+In addition, standard methods to estimate the importance of individual variables in the RSF are less effective in the oblique RSF.
+
+In this article, we introduce methods to increase computational efficiency and estimate variable importance (VI) for oblique RSFs.
+We evaluate computational efficiency, prediction accuracy, and the ability to discriminate between signal and noise variables using the proposed methods compared to standard and state-of-the-art methods.
+To accomplish these goals, we analyze 23 distinct risk prediction tasks from real data and conduct a simulation study.
+All methods introduced in this article for oblique RSFs are available in the \texttt{aorsf} R Package.
+
 \section{Related work}
 
-Several machine learning algorithms can engage with right-censored time-to-event outcomes.
-In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks.
+\citet{breiman2001random} introduced the axis-based random forest (RF) and the oblique RF (oRF).
+Axis based RFs recursively split data using a single predictor at each non-leaf node in decision trees, whereas oRFs use multiple predictors in linear combination.
+The splits are called `oblique' because linear combinations of predictors create decision boundaries that are neither parallel nor perpendicular to their axes have higher prediction accuracy in external data compared to their axis based counterparts.
+Several studies investigating RFs for classification and regression have noted that oblique RFs have lower generalization than their axis-based counterparts.
 
-accelerated oblique random survival forests \texttt{aorsf}
+The axis-based RF proposed in \citet{breiman2001random} was extended to survival outcomes by \citet{ishwaran2008random} and the oblique RF  la soon after RFs for classification and regression were developed by \citet{breiman2001random}, and oblique RFs for survival were Several studies have shown that oblique recursive partitioning improves the generalization error of RFs for classification and regression, b
 
-original oblique random survival forests \texttt{obliqueRSF}
+% More recently, \citet{jaeger2019oblique} showed that the generalization error of RFs for survival outcomes improves when multiple predictors are used in linear combination instead of a single predictor to split non-leaf nodes in trees, similar to RFs for classification and regression \citet{breiman2001random}.
+Splitting data with a single predictor creates a decision boundary that is perpendicular to its axis, whereas the decision boundary formed by a linear combination of predictors is neither perpendicular nor parallel to their respective axes.
 
-axis-based random survival forests \texttt{randomForestSRC \& ranger}
+% \citet{breiman2001random} introduced the axis-based random forest (RF) and oblique RF.
+Axis based RFs recursively split data using a single predictor at each non-leaf node in decision trees, whereas oRFs use multiple predictors in linear combination.
+The splits are called `oblique' because linear combinations of predictors create decision boundaries that are neither parallel nor perpendicular to their axes have higher prediction accuracy in external data compared to their axis based counterparts.
+However, many oRFs require a fully trained model to be embedded in each non-leaf node to identify linear combinations of predictors, exponentially increasing the number of operations required for fitting an oRF versus an axis based RF.
+In addition, standard methods to interpret RFs (\eg, permutation importance) are less effective when used to interpret the oRF because they are not designed to engage with oblique trees.
 
-axis-based conditional inference forests \texttt{party}
+Several supervised learning algorithms can develop prediction functions for right-censored time-to-event outcomes, henceforth referred to as survival outcomes.
+\cite{ishwaran2008random} developed the RF for survival, an extension of the RF for regression and classification developed by \citet{breiman2001random}.
+Fast algorithms to fit the RF for survival are available in the \texttt{randomForestSRC} R package \citep{randomForestSRC}.
+A similar implementation of the RF for survival can be found in the \texttt{ranger} R package \citep{ranger}, which is particularly suited for high dimensional data.
+The RF for survival can also be fit using unbiased recursive partitioning \citep{cif} via the \texttt{party} R package \citep{hothorn2010party}.
 
-gradient boosted decision trees \texttt{xgboost}
+\citet{zhu2015reinforcement}
 
-\section{Results}
+\citet{zhu2013tree}
+
+\citet{menze2011oblique} introduced an oblique RF (oRF) for classification that utilizes fully trained models at non-leaf nodes to identify linear combinations of predictors.
+\citet{tomita2020sparse} introduced sparse projections for oRFs for classification.
+\citet{katuwal2020heterogeneous} developed a heterogeneous oRF for classification that applies several linear classifiers at each non-leaf node.
+Compared to classification, fewer studies have developed oRFs for survival.
+\citet{jaeger2019oblique} introduced an oRF for survival that applies penalized regression at each non-leaf node and disseminated algorithms to fit the oRF for survival in the \texttt{obliqueRSF} R package \citep{obliqueRSF}.
+
+Variable importance (VI) for oRFs VI has been estimated for oRFs using analysis of variance (ANOVA),6 but this only applies in the rare case where p-values are calculable for coefficients in linear combinations.
+Permutation importance is used to estimate VI in RFs,14 but is not ideal for oRFs because it does not account for the coefficients used in linear combinations.
+Shapley VI, a method based in game theory,15 has excellent asymptotic properties for interpretation,16,17 but is computationally infeasible and can only be approximated efficiently for standard decision trees.18
+
+\section{Novel techniques for oblique random survival forests}
+
+\subsection{Partial training at non-leaf nodes}
+
+\subsection{Negation variable importance}
+
+We propose a new VI method, ``negation importance",  that can be used for any oRF and accounts for the coefficients in linear combinations.
+
+\section{Numeric experiments}
+
+\subsection{Benchmark of prediction accuracy}
+
+\subsubsection{Learners}
+
+In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks (Table \ref{table:learners}).
+For random forest learners, the number of observations required in terminal nodes was fixed at 10, the number of randomly selected predictors was the nearest integer to the square root of the total number of predictors, and the number of trees in the ensemble was 500.
+
+\newgeometry{margin=1cm} % modify this if you need even more space
+\begin{landscape}
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{p{2cm} | p{3cm} p{4cm} p{12cm}}
+ \hline
+ Learner Class & Software & Learners & Description \\ [0.5ex]
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Random Survival Forests}}\\
+ \hline\hline
+ Standard & \href{https://www.randomforestsrc.org/index.html}{\texttt{RandomForestSRC}} & \texttt{rfsrc-standard} & Axis based survival trees following Leo Breiman's original random forest algorithm, with cut-points selected to maximize a log-rank statistic.
+\\ \hline
+ Oblique & \href{https://CRAN.R-project.org/package=obliqueRSF}{\texttt{obliqueRSF}} \newline \href{https://bcjaeger.github.io/aorsf/}{\texttt{aorsf}} &
+ \texttt{obliqueRSF-net} \newline
+ \texttt{aorsf-net} \newline
+ \texttt{aorsf-cph($i=1$)} \newline
+ \texttt{aorsf-cph($i \leq 15$)} \newline
+ \texttt{aorsf-extratrees} &
+ Oblique survival trees following Leo Breiman's random forest algorithm.
+Linear combinations of inputs are derived using \texttt{glmnet} in \texttt{obliqueRSF-net} and \texttt{aorsf-net}, using Newton Raphson scoring for the Cox partial likelihood function in \texttt{aorsf-cph($i=1$)} and \texttt{aorsf-cph($i \leq 15$)}, and chosen randomly from a uniform distribution in \texttt{aorsf-extratrees}.
+Cut-points are selected to maximize a log-rank statistic.
+\\ \hline
+ Extremely \,Randomized & \href{https://CRAN.R-project.org/package=ranger}{\texttt{ranger}} & \texttt{ranger-extratrees} & Axis-based survival trees grown with randomly selected features and cut-points\\ \hline
+ Conditional \,Inference & \href{http://party.r-forge.r-project.org/}{\texttt{party}} & \texttt{party-cif} & Axis based survival trees grown using unbiased recursive partitioning.  \\
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Boosting ensembles}}\\
+ \hline\hline
+ Trees & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & \texttt{xgboost-cox} &  The Cox partial likelihood function is maximized additively with decision trees.
+Nested cross validation (5 folds) is applied to tune the number of trees grown.
+\\
+ Models & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & \texttt{xgboost-aft} & The accelerated failure time likelihood function is maximized additively with decision trees.
+Nested cross validation (5 folds) is applied to tune the number of trees grown.
+\\
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Regression models}}\\
+ \hline\hline
+ Cox Net & \texttt{glmnet} & \texttt{glmnet-cox} & The Cox model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
+ \hline\hline
+ \multicolumn{3}{l}{\textit{Neural networks}}\\
+ \hline\hline
+ Cox Time & \href{https://raphaels1.github.io/survivalmodels/}{\texttt{survivalmodels}} & \texttt{nn-cox} & A neural network based on the proportional hazards model with time-varying effects  \\
+ \hline
+\end{tabular}
+\caption{Learning algorithms assessed in numeric studies}
+\label{table:learners}
+\end{table}
+
+\end{landscape}
+\restoregeometry
+
+\subsubsection{Evaluation of prediction accuracy} \label{sec:prediction_accuracy}
+
+Our primary metric for evaluating the accuracy of predicted risk is the integrated and scaled Brier score \citep{graf1999assessment}.
+For observation $i$ in the testing data, let $\widehat{S}(t \mid \bm{x}_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$ and let $\bm{x}_i$ be the vector of predictor values.
+Define \begin{align*}
+\bstat = \frac{1}{\ntest} \sum_{i=1}^{\ntest} &\{ \widehat{S}(t \mid \bm{x}_i)^2 \cdot I(T_i \leq t, \delta_i = 1) \cdot \widehat{G}(T_i)^{-1} \\ &+ [1-\widehat{S}(t \mid \bm{x}_i)]^2 \cdot I(T_i > t) \cdot \widehat{G}(t)^{-1}\}
+\end{align*} where $\widehat{G}(t)$ is the Kaplan-Meier estimate of the censoring distribution.
+As $\bstat$ is time dependent, integration over time provides a summary measure of performance over a range of plausible prediction horizons.
+The integrated $\bstat$ is defined as \begin{equation}
+\bsbar = \frac{1}{t_2 - t_1}\int_{t_1}^{t_2} \widehat{\text{BS}}(t) dt.
+\end{equation} In our results, $t_1$ and $t_2$ are the 25th and 75th percentile of event times, respectively.
+$\bsbar$, a sum of squared prediction errors, can be scaled to produce a measure of explained residual variation (\ie, an $R^2$ statistic) by computing \begin{equation}
+R^2 = 1 - \frac{\bsbar}{\bskap}
+\end{equation} where $\bskap$ is the integrated Brier score when a Kaplan-Meier estimate for survival based on the training data is used as the survival prediction function $\widehat{S}(t)$.
+We refer to this $R^2$ statistic as the index of prediction accuracy and we scale its values by 100 to avoid unnecessary leading zero's.
+For example, we present 25 if $R^2$ is 0.25 and present 10.2 if the difference between two $R^2$ is 0.102.
+
+\subsubsection{Statistical analysis}
+
+\subsubsection{Results}
+
+<<fig.height=10, fig.width=9, dpi=400>>=
+bm_pred_viz$ibs_scaled
+@
+
+<<fig.height=10, fig.width=9, dpi=400>>=
+bm_pred_model_viz$ibs_scaled
+@
+
+\subsection{Benchmark of variable selection}
+
+% Acknowledgements should go at the end, before appendices and references
+
+\acks{Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine}
+
+% Manual newpage inserted to improve layout of sample file - not
+% needed in general before appendices/bibliography.
+
+\newpage
+
+\appendix
+\section*{Appendix A.}
+
+<<fig.height=10, fig.width=9, dpi=400>>=
+bm_pred_viz$cstat
+@
+
+\newpage
 
 <<>>=
+
+data_recoder <- data_key |>
+  transmute(data,
+            label = paste0(label, "; ",
+                           outcome, ", n = ", .data$nrow,
+                           ", p = ", .data$ncol)) |>
+  deframe()
+
+model_recoder <- model_key |>
+  deframe()
 
@@
     across(
-      .cols = c(cstat, IPA, time_fit, time_prd),
-      .fns = list(mean = mean, sd = sd)
+      .cols = c(cstat, ibs_scaled, time_fit, time_pred),
+      .fns = list(mean = mean,
+                  median = median,
+                  sd = sd)
     )
@@
 data_tbl <- bm_pred_comb |>
-  group_by(model, data, n_z, n_obs, correlated_x) |>
+  group_by(model, data) |>
   summarize(
     across(
-      .cols = c(cstat, IPA, time_fit, time_prd),
-      .fns = list(mean = mean, sd = sd)
+      .cols = c(cstat, ibs_scaled, time_fit, time_pred),
+      .fns = list(mean = mean,
+                  median = median,
+                  sd = sd)
     )
@@
   bind_rows(results_overall) |>
-  mutate(
-    data = if_else(
-      is.na(n_z),
-      true = data,
-      false = as.character(
-        glue::glue("Simulation, N junk = {n_z}, N obs = {n_obs}, X corr less then or equal to {correlated_x}")
-      )
-    )
-  ) |>
+  # mutate(
+  #   data = if_else(
+  #     is.na(n_z),
+  #     true = data,
+  #     false = as.character(
+  #       glue::glue("Simulation, N junk = {n_z}, N obs = {n_obs}, X corr less than or equal to {correlated_x}")
+  #     )
+  #   )
+  # ) |>
   group_by(data) |>
@@
     across(.cols = starts_with("time"), .fns = as.numeric),
-    time_fit_ratio = time_fit_mean / time_fit_mean[model == 'aorsf-1'],
-    time_prd_ratio = time_prd_mean / time_prd_mean[model == 'aorsf-1']
+    time_fit_ratio = time_fit_median /
+      time_fit_median[model == 'aorsf_cph_1'],
+    time_pred_ratio = time_pred_median /
+      time_pred_median[model == 'aorsf_cph_1']
   ) |>
-  arrange(data, desc(cstat_mean)) |>
+  ungroup() |>
+  arrange(data, desc(ibs_scaled_mean)) |>
   transmute(
-    model = recode(
-      model,
-      "aorsf-15" = 'aORSF(i=15)',
-      "aorsf-1" = 'aORSF(i=1)',
-      "ranger" = 'Ranger',
-      "xgboost" = 'Xgboost',
-      "cif" = "Party",
-      "randomForestSRC" = "Rfsrc",
-      "coxtime" = "Coxtime"
+    data = recode(data, !!!data_recoder),
+    data = fct_relevel(factor(data), 'Overall'),
+    model = recode(model, !!!model_recoder),
+    ibs_scaled = table_glue(
+      "{ibs_scaled_mean} ({ibs_scaled_sd})"
     ),
-    data = recode(
-      data,
-      'pbc_orsf' = 'Mayo Clinic Primary Biliary Cholangitis Data, N = 276',
-      'rotterdam' = 'Rotterdam Breast Cancer Data, N = 2,982',
-      'sim' = 'Simulated data'
+    cstat = table_glue(
+      "{cstat_mean} ({cstat_sd})"
     ),
-    cstat = table_glue("{cstat_mean} ({cstat_sd})"),
-    ipa = table_glue("{IPA_mean} ({IPA_sd})"),
-    time_fit_mean = format(round(time_fit_mean, 3), nsmall = 3),
+    time_fit_median = format(round(time_fit_median, 3), nsmall = 3),
     time_fit_ratio = table_value(time_fit_ratio),
-    time_prd_mean = format(round(time_prd_mean, 3), nsmall = 3),
-    time_prd_ratio = table_value(time_prd_ratio)
-  )
+    time_pred_median = format(round(time_pred_median, 3), nsmall = 3),
+    time_pred_ratio = table_value(time_pred_ratio)
+  ) |>
+  arrange(data)
 
@@
 data_tbl |>
-  ungroup() |>
   select(-data) |>
@@
         col.names = c(' ',
+                      'Scaled Brier',
                       'C-Statistic',
-                      'Scaled Brier',
-                      'Mean',
+                      'Median',
                       'Ratio',
-                      'Mean',
+                      'Median',
                       'Ratio'),
@@
 
-% Acknowledgements should go at the end, before appendices and references
-
-\acks{We would like to acknowledge support for this project
-from the National Science Foundation (NSF grant IIS-9988642)
-and the Multidisciplinary Research Program of the Department
-of Defense (MURI N00014-00-1-0637). }
-
-% Manual newpage inserted to improve layout of sample file - not
-% needed in general before appendices/bibliography.
-
-\newpage
-
-\appendix
-\section*{Appendix A.}
-\label{app:theorem}
-
-% Note: in this sample, the section number is hard-coded in. Following
-% proper LaTeX conventions, it should properly be coded as a reference:
-
-%In this appendix we prove the following theorem from
-%Section~\ref{sec:textree-generalization}:
-
-In this appendix we prove the following theorem from
-Section~6.2:
-
-\noindent
-{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
-not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
-dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
-which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
-respective empirical mutual information values based on the sample
-$\dataset$. Then
-\[
-	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
-\]
-with equality only if $u$ is identically 0.} \hfill\BlackBox
-
-\noindent
-{\bf Proof}. We use the notation:
-\[
-P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
-P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
-\]
-These values represent the (empirical) probabilities of $v$
-taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
-by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\
-
-{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
-
 \vskip 0.2in

### 2022-06-06 paper/jmlr/main.tex
prediction benchmark and intro

@@
 \hypersetup{hidelinks}
+\usepackage{geometry}
+\usepackage{pdflscape}
+\usepackage{bm}
 
@@
 
+Risk prediction can reduce the burden of disease by educating patients and providers and guiding strategies to prevent and treat disease in a wide range of medical domains \citep{moons2012riskI, moons2012riskII}.
+The random survival forest (RSF), a supervised learning algorithm that can engage with censored outcomes, is frequently used for risk prediction.
+Notable characteristics of the RSF include uniform convergence of its ensemble survival function to the true population survival function when the predictor space is discrete.
+In addition, software implementing the RSF is freely available, extremely efficient, and full of tools to interpret and explain the RSF.
+However, there remains considerable potential to improve the RSF in risk prediction tasks where training samples are not large enough to guarantee asymptotic properties or predictor spaces are non-discrete (\ie, predictors are continuous).
+
+RSFs may be axis based or oblique.
+The axis based RSF uses a single predictor whereas the oblique RSF uses a linear combination of predictors to create branches in trees.
+While axis based decision boundaries are always perpendicular to the axis of the relevant predictor, linear combinations of predictors create oblique decision boundaries that are neither parallel nor perpendicular to axes of their contributing predictors.
+Prior work has found the oblique RSF has higher prediction accuracy than the axis based RSF in general benchmarks \citep{jaeger2019oblique} and that oblique splitting is particularly effective when predictor spaces are non-discrete.
+However, existing methods to implement oblique RSFs use fully trained models in each non-leaf node to identify linear combinations of predictors, exponentially increasing the number of operations required for the oblique RSF versus its axis based counterpart.
+In addition, standard methods to estimate the importance of individual variables in the RSF are less effective in the oblique RSF.
+
+In this article, we introduce methods to increase computational efficiency and estimate variable importance (VI) for oblique RSFs.
+We evaluate computational efficiency, prediction accuracy, and the ability to discriminate between signal and noise variables using the proposed methods compared to standard and state-of-the-art methods.
+To accomplish these goals, we analyze 23 distinct risk prediction tasks from real data and conduct a simulation study.
+All methods introduced in this article for oblique RSFs are available in the \texttt{aorsf} R Package.
+
 \section{Related work}
 
-Table \ref{table:1} is an example of a referenced \LaTeX{}.
-Several machine learning algorithms can engage with right-censored time-to-event outcomes.
-In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks.
+\citet{breiman2001random} introduced the axis-based random forest (RF) and the oblique RF (oRF).
+Axis based RFs recursively split data using a single predictor at each non-leaf node in decision trees, whereas oRFs use multiple predictors in linear combination.
+The splits are called `oblique' because linear combinations of predictors create decision boundaries that are neither parallel nor perpendicular to their axes have higher prediction accuracy in external data compared to their axis based counterparts.
+Several studies investigating RFs for classification and regression have noted that oblique RFs have lower generalization than their axis-based counterparts.
 
-accelerated oblique random survival forests \texttt{aorsf}
+The axis-based RF proposed in \citet{breiman2001random} was extended to survival outcomes by \citet{ishwaran2008random} and the oblique RF  la soon after RFs for classification and regression were developed by \citet{breiman2001random}, and oblique RFs for survival were Several studies have shown that oblique recursive partitioning improves the generalization error of RFs for classification and regression, b
 
-original oblique random survival forests \texttt{obliqueRSF}
+% More recently, \citet{jaeger2019oblique} showed that the generalization error of RFs for survival outcomes improves when multiple predictors are used in linear combination instead of a single predictor to split non-leaf nodes in trees, similar to RFs for classification and regression \citet{breiman2001random}.
+Splitting data with a single predictor creates a decision boundary that is perpendicular to its axis, whereas the decision boundary formed by a linear combination of predictors is neither perpendicular nor parallel to their respective axes.
 
-axis-based random survival forests \texttt{randomForestSRC \& ranger}
+% \citet{breiman2001random} introduced the axis-based random forest (RF) and oblique RF.
+Axis based RFs recursively split data using a single predictor at each non-leaf node in decision trees, whereas oRFs use multiple predictors in linear combination.
+The splits are called `oblique' because linear combinations of predictors create decision boundaries that are neither parallel nor perpendicular to their axes have higher prediction accuracy in external data compared to their axis based counterparts.
+However, many oRFs require a fully trained model to be embedded in each non-leaf node to identify linear combinations of predictors, exponentially increasing the number of operations required for fitting an oRF versus an axis based RF.
+In addition, standard methods to interpret RFs (\eg, permutation importance) are less effective when used to interpret the oRF because they are not designed to engage with oblique trees.
 
-axis-based conditional inference forests \texttt{party}
+Several supervised learning algorithms can develop prediction functions for right-censored time-to-event outcomes, henceforth referred to as survival outcomes.
+\cite{ishwaran2008random} developed the RF for survival, an extension of the RF for regression and classification developed by \citet{breiman2001random}.
+Fast algorithms to fit the RF for survival are available in the \texttt{randomForestSRC} R package \citep{randomForestSRC}.
+A similar implementation of the RF for survival can be found in the \texttt{ranger} R package \citep{ranger}, which is particularly suited for high dimensional data.
+The RF for survival can also be fit using unbiased recursive partitioning \citep{cif} via the \texttt{party} R package \citep{hothorn2010party}.
 
-gradient boosted decision trees \texttt{xgboost}
+\citet{zhu2015reinforcement}
+
+\citet{zhu2013tree}
+
+\citet{menze2011oblique} introduced an oblique RF (oRF) for classification that utilizes fully trained models at non-leaf nodes to identify linear combinations of predictors.
+\citet{tomita2020sparse} introduced sparse projections for oRFs for classification.
+\citet{katuwal2020heterogeneous} developed a heterogeneous oRF for classification that applies several linear classifiers at each non-leaf node.
+Compared to classification, fewer studies have developed oRFs for survival.
+\citet{jaeger2019oblique} introduced an oRF for survival that applies penalized regression at each non-leaf node and disseminated algorithms to fit the oRF for survival in the \texttt{obliqueRSF} R package \citep{obliqueRSF}.
+
+Variable importance (VI) for oRFs VI has been estimated for oRFs using analysis of variance (ANOVA),6 but this only applies in the rare case where p-values are calculable for coefficients in linear combinations.
+Permutation importance is used to estimate VI in RFs,14 but is not ideal for oRFs because it does not account for the coefficients used in linear combinations.
+Shapley VI, a method based in game theory,15 has excellent asymptotic properties for interpretation,16,17 but is computationally infeasible and can only be approximated efficiently for standard decision trees.18
+
+\section{Novel techniques for oblique random survival forests}
+
+\subsection{Partial training at non-leaf nodes}
+
+\subsection{Negation variable importance}
+
+We propose a new VI method, ``negation importance",  that can be used for any oRF and accounts for the coefficients in linear combinations.
+
+\section{Numeric experiments}
+
+\subsection{Benchmark of prediction accuracy}
+
+\subsubsection{Learners}
+
+In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks (Table \ref{table:learners}).
+For random forest learners, the number of observations required in terminal nodes was fixed at 10, the number of randomly selected predictors was the nearest integer to the square root of the total number of predictors, and the number of trees in the ensemble was 500.
+
+\newgeometry{margin=1cm} % modify this if you need even more space
+\begin{landscape}
 
@@
 \centering
-\begin{tabular}{p{2cm} | p{3cm} p{7cm}}
+\begin{tabular}{p{2cm} | p{3cm} p{4cm} p{12cm}}
  \hline
- Learner & Software & Description \\ [0.5ex]
+ Learner Class & Software & Learners & Description \\ [0.5ex]
  \hline\hline
@@
  \hline\hline
- Standard & \href{https://www.randomforestsrc.org/index.html}{\texttt{RandomForestSRC}} & Axis based survival trees following Leo Breiman's original random forest algorithm, with cut-points selected to maximize a log-rank statistic.
+ Standard & \href{https://www.randomforestsrc.org/index.html}{\texttt{RandomForestSRC}} & \texttt{rfsrc-standard} & Axis based survival trees following Leo Breiman's original random forest algorithm, with cut-points selected to maximize a log-rank statistic.
 \\ \hline
- Oblique & \href{https://CRAN.R-project.org/package=obliqueRSF}{\texttt{obliqueRSF}} \newline \href{https://bcjaeger.github.io/aorsf/}{\texttt{aorsf}} & Oblique survival trees following Leo Breiman's random forest algorithm but not using random coefficients for linear combinations.
-\texttt{obliqueRSF} uses penalized models, and \texttt{aorsf} additionally uses partially trained models.
+ Oblique & \href{https://CRAN.R-project.org/package=obliqueRSF}{\texttt{obliqueRSF}} \newline \href{https://bcjaeger.github.io/aorsf/}{\texttt{aorsf}} &
+ \texttt{obliqueRSF-net} \newline
+ \texttt{aorsf-net} \newline
+ \texttt{aorsf-cph($i=1$)} \newline
+ \texttt{aorsf-cph($i \leq 15$)} \newline
+ \texttt{aorsf-extratrees} &
+ Oblique survival trees following Leo Breiman's random forest algorithm.
+Linear combinations of inputs are derived using \texttt{glmnet} in \texttt{obliqueRSF-net} and \texttt{aorsf-net}, using Newton Raphson scoring for the Cox partial likelihood function in \texttt{aorsf-cph($i=1$)} and \texttt{aorsf-cph($i \leq 15$)}, and chosen randomly from a uniform distribution in \texttt{aorsf-extratrees}.
 Cut-points are selected to maximize a log-rank statistic.
 \\ \hline
- Extremely \,Randomized & \href{https://CRAN.R-project.org/package=ranger}{\texttt{ranger}} & Axis-based survival trees grown with randomly selected features and cut-points\\ \hline
- Conditional \,Inference & \href{http://party.r-forge.r-project.org/}{\texttt{party}} & Axis based survival trees grown using unbiased recursive partitioning.  \\
+ Extremely \,Randomized & \href{https://CRAN.R-project.org/package=ranger}{\texttt{ranger}} & \texttt{ranger-extratrees} & Axis-based survival trees grown with randomly selected features and cut-points\\ \hline
+ Conditional \,Inference & \href{http://party.r-forge.r-project.org/}{\texttt{party}} & \texttt{party-cif} & Axis based survival trees grown using unbiased recursive partitioning.  \\
  \hline\hline
@@
  \hline\hline
- Trees & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & The Cox likelihood function is maximized additively with decision trees.
+ Trees & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & \texttt{xgboost-cox} &  The Cox partial likelihood function is maximized additively with decision trees.
 Nested cross validation (5 folds) is applied to tune the number of trees grown.
 \\
- Models & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & The accelerated failure time likelihood function is maximized additively with decision trees.
+ Models & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & \texttt{xgboost-aft} & The accelerated failure time likelihood function is maximized additively with decision trees.
 Nested cross validation (5 folds) is applied to tune the number of trees grown.
@@
  \hline\hline
- Cox Net & \texttt{glmnet} & The Cox model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
+ Cox Net & \texttt{glmnet} & \texttt{glmnet-cox} & The Cox model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
  \hline\hline
@@
  \hline\hline
- Cox Time & 6 & 87837  \\
+ Cox Time & \href{https://raphaels1.github.io/survivalmodels/}{\texttt{survivalmodels}} & \texttt{nn-cox} & A neural network based on the proportional hazards model with time-varying effects  \\
  \hline
 \end{tabular}
-\caption{Table to test captions and labels.}
-\label{table:1}
+\caption{Learning algorithms assessed in numeric studies}
+\label{table:learners}
 \end{table}
 
-\section{Results}
+\end{landscape}
+\restoregeometry
+
+\subsubsection{Evaluation of prediction accuracy} \label{sec:prediction_accuracy}
+
+Our primary metric for evaluating the accuracy of predicted risk is the integrated and scaled Brier score \citep{graf1999assessment}.
+For observation $i$ in the testing data, let $\widehat{S}(t \mid \bm{x}_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$ and let $\bm{x}_i$ be the vector of predictor values.
+Define \begin{align*}
+\bstat = \frac{1}{\ntest} \sum_{i=1}^{\ntest} &\{ \widehat{S}(t \mid \bm{x}_i)^2 \cdot I(T_i \leq t, \delta_i = 1) \cdot \widehat{G}(T_i)^{-1} \\ &+ [1-\widehat{S}(t \mid \bm{x}_i)]^2 \cdot I(T_i > t) \cdot \widehat{G}(t)^{-1}\}
+\end{align*} where $\widehat{G}(t)$ is the Kaplan-Meier estimate of the censoring distribution.
+As $\bstat$ is time dependent, integration over time provides a summary measure of performance over a range of plausible prediction horizons.
+The integrated $\bstat$ is defined as \begin{equation}
+\bsbar = \frac{1}{t_2 - t_1}\int_{t_1}^{t_2} \widehat{\text{BS}}(t) dt.
+\end{equation} In our results, $t_1$ and $t_2$ are the 25th and 75th percentile of event times, respectively.
+$\bsbar$, a sum of squared prediction errors, can be scaled to produce a measure of explained residual variation (\ie, an $R^2$ statistic) by computing \begin{equation}
+R^2 = 1 - \frac{\bsbar}{\bskap}
+\end{equation} where $\bskap$ is the integrated Brier score when a Kaplan-Meier estimate for survival based on the training data is used as the survival prediction function $\widehat{S}(t)$.
+We refer to this $R^2$ statistic as the index of prediction accuracy and we scale its values by 100 to avoid unnecessary leading zero's.
+For example, we present 25 if $R^2$ is 0.25 and present 10.2 if the difference between two $R^2$ is 0.102.
+
+\subsubsection{Statistical analysis}
+
+\subsubsection{Results}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-2-1} 
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-3-1} 
+\end{knitrout}
+
+\subsection{Benchmark of variable selection}
+
+% Acknowledgements should go at the end, before appendices and references
+
+\acks{Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine}
+
+% Manual newpage inserted to improve layout of sample file - not
+% needed in general before appendices/bibliography.
+
+\newpage
+
+\appendix
+\section*{Appendix A.}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-4-1} 
+\end{knitrout}
+
+\newpage
 
@@
 \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
-  & C-Statistic & Scaled Brier & Mean & Ratio & Mean & Ratio\\
+  & Scaled Brier & C-Statistic & Median & Ratio & Median & Ratio\\
 \midrule
@@
 \toprule
-  & C-Statistic & Scaled Brier & Mean & Ratio & Mean & Ratio\\
+  & Scaled Brier & C-Statistic & Median & Ratio & Median & Ratio\\
 \midrule
@@
 \hline
-\multicolumn{7}{l}{\textit{\textbf{actg}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Overall}}}\\
 \hline
-\hspace{1em}Party & 0.772 (0.058) & 0.076 (0.042) & 2.181 & 2.19 & 4.889 & 4.62\\
-\hspace{1em}aORSF(i=1) & 0.755 (0.059) & 0.057 (0.055) & 0.998 & 1.00 & 1.057 & 1.00\\
-\hspace{1em}Ranger & 0.754 (0.064) & 0.064 (0.027) & 0.397 & 0.398 & 0.510 & 0.483\\
-\hspace{1em}aORSF(i=15) & 0.754 (0.063) & 0.052 (0.056) & 2.498 & 2.50 & 2.559 & 2.42\\
-\hspace{1em}Rfsrc & 0.752 (0.064) & 0.061 (0.047) & 0.775 & 0.777 & 0.833 & 0.787\\
-\hspace{1em}aorsf\_net & 0.750 (0.059) & 0.055 (0.064) & 28.449 & 28.5 & 28.510 & 27.0\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.136 (0.123) & 0.763 (0.077) & 2.460 & 2.95 & 0.202 & 0.974\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.135 (0.124) & 0.763 (0.077) & 0.833 & 1.00 & 0.207 & 1.00\\
+\hspace{1em}aorsf-net & 0.133 (0.127) & 0.762 (0.077) & 53.399 & 64.1 & 0.200 & 0.966\\
+\hspace{1em}glmnet-cox & 0.124 (0.136) & 0.753 (0.081) & 0.209 & 0.251 & 0.004 & 0.019\\
+\hspace{1em}party-cif & 0.123 (0.111) & 0.755 (0.074) & 1.583 & 1.90 & 4.360 & 21.0\\
+\hspace{1em}rfsrc-standard & 0.120 (0.128) & 0.747 (0.080) & 1.554 & 1.86 & 0.150 & 0.725\\
+\hspace{1em}obliqueRSF-net & 0.120 (0.093) & 0.762 (0.076) & 268.416 & 322.0 & 18.002 & 86.9\\
+\hspace{1em}ranger-extratrees & 0.108 (0.097) & 0.753 (0.073) & 0.217 & 0.261 & 0.211 & 1.02\\
+\hspace{1em}aorsf-random & 0.102 (0.092) & 0.740 (0.072) & 1.857 & 2.23 & 0.191 & 0.924\\
+\hspace{1em}xgboost-cox & 0.080 (0.114) & 0.740 (0.095) & 3.645 & 4.37 & 0.005 & 0.024\\
+\hspace{1em}xgboost-aft & -3.86 (5.01) & 0.753 (0.078) & 12.587 & 15.1 & 0.008 & 0.039\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{breast}}}\\
+\multicolumn{7}{l}{\textit{\textbf{ACTG 320; AIDS diagnosis, n = 1151, p = 12}}}\\
 \hline
-\hspace{1em}aORSF(i=15) & 0.764 (0.008) & 0.143 (0.016) & 11.867 & 2.56 & 12.403 & 2.43\\
-\hspace{1em}Ranger & 0.756 (0.013) & 0.102 (0.017) & 0.555 & 0.120 & 0.724 & 0.142\\
-\hspace{1em}Party & 0.753 (0.013) & 0.118 (0.016) & 8.030 & 1.73 & 10.445 & 2.05\\
-\hspace{1em}aORSF(i=1) & 0.751 (0.002) & 0.120 (0.012) & 4.636 & 1.00 & 5.106 & 1.00\\
-\hspace{1em}aorsf\_net & 0.741 (0.022) & 0.062 (0.049) & 585.625 & 126.3 & 585.887 & 114.7\\
-\hspace{1em}Rfsrc & 0.707 (0.005) & 0.049 (0.039) & 1.354 & 0.292 & 1.522 & 0.298\\
+\hspace{1em}aorsf-random & 0.032 (0.017) & 0.749 (0.035) & 1.404 & 2.75 & 0.119 & 1.02\\
+\hspace{1em}obliqueRSF-net & 0.031 (0.018) & 0.751 (0.035) & 28.321 & 55.4 & 15.117 & 129.1\\
+\hspace{1em}ranger-extratrees & 0.030 (0.014) & 0.739 (0.035) & 0.358 & 0.701 & 0.159 & 1.36\\
+\hspace{1em}party-cif & 0.030 (0.024) & 0.749 (0.034) & 1.631 & 3.19 & 4.292 & 36.6\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.029 (0.023) & 0.755 (0.038) & 1.146 & 2.24 & 0.116 & 0.991\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.029 (0.023) & 0.750 (0.040) & 0.511 & 1.00 & 0.117 & 1.00\\
+\hspace{1em}aorsf-net & 0.024 (0.027) & 0.750 (0.036) & 19.546 & 38.2 & 0.119 & 1.01\\
+\hspace{1em}glmnet-cox & 0.023 (0.026) & 0.755 (0.038) & 0.179 & 0.349 & 0.003 & 0.026\\
+\hspace{1em}rfsrc-standard & 0.013 (0.034) & 0.736 (0.037) & 0.638 & 1.25 & 0.060 & 0.514\\
+\hspace{1em}xgboost-cox & 0.006 (0.045) & 0.762 (0.035) & 3.745 & 7.33 & 0.003 & 0.026\\
+\hspace{1em}xgboost-aft & -8.44 (1.61) & 0.744 (0.034) & 11.231 & 22.0 & 0.006 & 0.051\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{colon}}}\\
+\multicolumn{7}{l}{\textit{\textbf{ACTG 320; death, n = 1151, p = 12}}}\\
 \hline
-\hspace{1em}Rfsrc & 0.815 (0.007) & 0.279 (0.007) & 1.854 & 0.581 & 2.026 & 0.600\\
-\hspace{1em}aORSF(i=15) & 0.778 (0.007) & 0.199 (0.018) & 7.515 & 2.36 & 7.709 & 2.28\\
-\hspace{1em}aORSF(i=1) & 0.776 (0.004) & 0.201 (0.014) & 3.190 & 1.00 & 3.378 & 1.00\\
-\hspace{1em}aorsf\_net & 0.753 (0.006) & 0.156 (0.018) & 149.637 & 46.9 & 149.809 & 44.3\\
-\hspace{1em}Party & 0.753 (0.012) & 0.183 (0.008) & 3.968 & 1.24 & 10.451 & 3.09\\
-\hspace{1em}Ranger & 0.738 (0.008) & 0.147 (0.005) & 1.795 & 0.563 & 2.398 & 0.710\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.013 (0.017) & 0.831 (0.050) & 0.683 & 2.35 & 0.076 & 1.03\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.013 (0.018) & 0.835 (0.050) & 0.291 & 1.00 & 0.074 & 1.00\\
+\hspace{1em}aorsf-random & 0.011 (0.013) & 0.802 (0.060) & 1.081 & 3.72 & 0.086 & 1.16\\
+\hspace{1em}obliqueRSF-net & 0.010 (0.010) & 0.824 (0.048) & 8.654 & 29.8 & 11.022 & 148.8\\
+\hspace{1em}aorsf-net & 0.008 (0.030) & 0.821 (0.054) & 15.008 & 51.6 & 0.085 & 1.14\\
+\hspace{1em}ranger-extratrees & 0.005 (0.015) & 0.776 (0.055) & 0.040 & 0.139 & 0.136 & 1.84\\
+\hspace{1em}party-cif & 0.001 (0.024) & 0.781 (0.055) & 1.610 & 5.54 & 4.228 & 57.1\\
+\hspace{1em}xgboost-cox & -0.003 (0.003) & 0.500 (0.000) & 0.113 & 0.389 & 0.002 & 0.027\\
+\hspace{1em}rfsrc-standard & -0.014 (0.048) & 0.785 (0.058) & 0.084 & 0.287 & 0.036 & 0.480\\
+\hspace{1em}glmnet-cox & -0.036 (0.073) & 0.735 (0.109) & 0.285 & 0.981 & 0.002 & 0.027\\
+\hspace{1em}xgboost-aft & -22.6 (6.75) & 0.774 (0.058) & 10.436 & 35.9 & 0.005 & 0.068\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{gbsg2}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Colon cancer; death, n = 929, p = 12}}}\\
 \hline
-\hspace{1em}Ranger & 0.704 (0.076) & 0.090 (0.045) & 0.328 & 0.339 & 0.450 & 0.438\\
-\hspace{1em}Party & 0.686 (0.042) & 0.092 (0.048) & 0.746 & 0.773 & 2.055 & 2.00\\
-\hspace{1em}aORSF(i=15) & 0.685 (0.048) & 0.077 (0.066) & 2.077 & 2.15 & 2.144 & 2.09\\
-\hspace{1em}Rfsrc & 0.676 (0.032) & 0.067 (0.052) & 0.931 & 0.963 & 1.014 & 0.986\\
-\hspace{1em}aORSF(i=1) & 0.674 (0.045) & 0.062 (0.062) & 0.966 & 1.00 & 1.028 & 1.00\\
-\hspace{1em}aorsf\_net & 0.670 (0.038) & 0.068 (0.056) & 57.024 & 59.0 & 57.087 & 55.5\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.102 (0.016) & 0.720 (0.015) & 0.818 & 1.00 & 0.208 & 1.00\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.101 (0.016) & 0.720 (0.015) & 1.917 & 2.34 & 0.205 & 0.984\\
+\hspace{1em}party-cif & 0.100 (0.012) & 0.713 (0.013) & 1.178 & 1.44 & 4.053 & 19.5\\
+\hspace{1em}aorsf-random & 0.098 (0.012) & 0.719 (0.015) & 1.640 & 2.00 & 0.191 & 0.918\\
+\hspace{1em}aorsf-net & 0.097 (0.016) & 0.720 (0.015) & 51.648 & 63.1 & 0.195 & 0.938\\
+\hspace{1em}rfsrc-standard & 0.091 (0.018) & 0.707 (0.013) & 1.462 & 1.79 & 0.149 & 0.716\\
+\hspace{1em}obliqueRSF-net & 0.090 (0.007) & 0.720 (0.014) & 241.184 & 294.8 & 44.328 & 213.1\\
+\hspace{1em}ranger-extratrees & 0.083 (0.008) & 0.710 (0.015) & 0.571 & 0.698 & 0.251 & 1.21\\
+\hspace{1em}glmnet-cox & 0.079 (0.016) & 0.712 (0.020) & 0.110 & 0.135 & 0.004 & 0.019\\
+\hspace{1em}xgboost-cox & 0.065 (0.014) & 0.703 (0.015) & 3.225 & 3.94 & 0.004 & 0.019\\
+\hspace{1em}xgboost-aft & -1.09 (0.188) & 0.708 (0.013) & 10.975 & 13.4 & 0.006 & 0.029\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{guide\_it}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Colon cancer; recurrence, n = 929, p = 12}}}\\
 \hline
-\hspace{1em}aORSF(i=15) & 0.730 (0.009) & 0.133 (0.008) & 4.705 & 2.67 & 4.811 & 2.57\\
-\hspace{1em}aORSF(i=1) & 0.728 (0.014) & 0.132 (0.012) & 1.762 & 1.00 & 1.869 & 1.00\\
-\hspace{1em}aorsf\_net & 0.728 (0.020) & 0.133 (0.015) & 86.476 & 49.1 & 86.590 & 46.3\\
-\hspace{1em}Party & 0.705 (0.021) & 0.101 (0.010) & 1.800 & 1.02 & 3.727 & 1.99\\
-\hspace{1em}Rfsrc & 0.705 (0.032) & 0.109 (0.027) & 1.000 & 0.568 & 1.104 & 0.591\\
-\hspace{1em}Ranger & 0.704 (0.016) & 0.102 (0.001) & 0.663 & 0.376 & 0.855 & 0.457\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.103 (0.020) & 0.716 (0.019) & 0.819 & 1.00 & 0.210 & 1.00\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.102 (0.019) & 0.715 (0.018) & 1.939 & 2.37 & 0.205 & 0.975\\
+\hspace{1em}aorsf-net & 0.099 (0.020) & 0.716 (0.019) & 50.594 & 61.8 & 0.192 & 0.913\\
+\hspace{1em}party-cif & 0.096 (0.016) & 0.705 (0.017) & 1.142 & 1.39 & 3.756 & 17.9\\
+\hspace{1em}obliqueRSF-net & 0.090 (0.010) & 0.715 (0.018) & 250.487 & 305.8 & 42.658 & 203.0\\
+\hspace{1em}aorsf-random & 0.089 (0.014) & 0.705 (0.018) & 1.653 & 2.02 & 0.190 & 0.905\\
+\hspace{1em}rfsrc-standard & 0.086 (0.021) & 0.697 (0.017) & 1.473 & 1.80 & 0.151 & 0.719\\
+\hspace{1em}ranger-extratrees & 0.080 (0.011) & 0.699 (0.018) & 0.498 & 0.608 & 0.243 & 1.15\\
+\hspace{1em}glmnet-cox & 0.078 (0.017) & 0.710 (0.023) & 0.111 & 0.135 & 0.004 & 0.019\\
+\hspace{1em}xgboost-cox & 0.061 (0.013) & 0.698 (0.019) & 2.951 & 3.60 & 0.004 & 0.019\\
+\hspace{1em}xgboost-aft & -1.16 (0.240) & 0.705 (0.019) & 11.566 & 14.1 & 0.006 & 0.029\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{Mayo Clinic Primary Biliary Cholangitis Data, N = 276}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Early breast cancer; recurrence or death, n = 614, p = 1692}}}\\
 \hline
-\hspace{1em}aORSF(i=1) & 0.787 (0.094) & 0.202 (0.188) & 2.204 & 1.00 & 2.400 & 1.00\\
-\hspace{1em}aORSF(i=15) & 0.787 (0.100) & 0.203 (0.186) & 5.038 & 2.29 & 5.242 & 2.18\\
-\hspace{1em}Ranger & 0.783 (0.091) & 0.161 (0.138) & 0.709 & 0.322 & 1.053 & 0.438\\
-\hspace{1em}aorsf\_net & 0.782 (0.101) & 0.190 (0.202) & 128.300 & 58.2 & 128.469 & 53.5\\
-\hspace{1em}Party & 0.779 (0.094) & 0.185 (0.167) & 3.291 & 1.49 & 6.998 & 2.92\\
-\hspace{1em}Rfsrc & 0.778 (0.113) & 0.195 (0.187) & 0.956 & 0.434 & 1.076 & 0.448\\
+\hspace{1em}obliqueRSF-net & 0.076 (0.024) & 0.754 (0.031) & 1867.133 & 705.0 & 14.418 & 37.5\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.072 (0.027) & 0.752 (0.028) & 5.022 & 1.90 & 0.398 & 1.04\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.070 (0.028) & 0.752 (0.029) & 2.648 & 1.00 & 0.384 & 1.00\\
+\hspace{1em}party-cif & 0.069 (0.020) & 0.749 (0.034) & 8.450 & 3.19 & 4.065 & 10.6\\
+\hspace{1em}ranger-extratrees & 0.061 (0.022) & 0.742 (0.032) & 0.220 & 0.083 & 0.179 & 0.467\\
+\hspace{1em}glmnet-cox & 0.046 (0.031) & 0.724 (0.036) & 5.730 & 2.16 & 0.006 & 0.016\\
+\hspace{1em}xgboost-cox & 0.030 (0.028) & 0.745 (0.032) & 2.586 & 0.977 & 0.006 & 0.016\\
+\hspace{1em}rfsrc-standard & 0.029 (0.034) & 0.699 (0.030) & 0.606 & 0.229 & 0.617 & 1.61\\
+\hspace{1em}aorsf-random & 0.028 (0.015) & 0.692 (0.034) & 3.622 & 1.37 & 0.359 & 0.934\\
+\hspace{1em}aorsf-net & 0.025 (0.062) & 0.750 (0.027) & 451.897 & 170.6 & 0.381 & 0.991\\
+\hspace{1em}xgboost-aft & -2.92 (0.594) & 0.749 (0.028) & 10.199 & 3.85 & 0.009 & 0.024\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{Overall}}}\\
+\multicolumn{7}{l}{\textit{\textbf{FCL; death, n = 541, p = 7}}}\\
 \hline
-\hspace{1em}aORSF(i=1) & 0.946 (0.018) & 0.493 (0.083) & 0.344 & 1.00 & 0.376 & 1.00\\
-\hspace{1em}aorsf\_net & 0.939 (0.018) & 0.484 (0.052) & 23.093 & 67.2 & 23.123 & 61.6\\
-\hspace{1em}Party & 0.936 (0.022) & 0.454 (0.022) & 0.288 & 0.839 & 0.518 & 1.38\\
-\hspace{1em}aORSF(i=15) & 0.936 (0.014) & 0.474 (0.080) & 0.744 & 2.17 & 0.773 & 2.06\\
-\hspace{1em}Rfsrc & 0.927 (0.012) & 0.462 (0.070) & 0.363 & 1.06 & 0.397 & 1.06\\
-\hspace{1em}Ranger & 0.926 (0.014) & 0.344 (0.055) & 0.044 & 0.127 & 0.085 & 0.226\\
+\hspace{1em}glmnet-cox & 0.118 (0.034) & 0.790 (0.034) & 0.080 & 0.331 & 0.002 & 0.039\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.098 (0.044) & 0.771 (0.034) & 0.440 & 1.81 & 0.051 & 1.01\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.097 (0.043) & 0.770 (0.034) & 0.243 & 1.00 & 0.051 & 1.00\\
+\hspace{1em}aorsf-net & 0.095 (0.044) & 0.762 (0.034) & 13.416 & 55.3 & 0.052 & 1.01\\
+\hspace{1em}obliqueRSF-net & 0.089 (0.032) & 0.764 (0.035) & 97.197 & 400.4 & 5.365 & 105.1\\
+\hspace{1em}party-cif & 0.083 (0.042) & 0.750 (0.036) & 0.281 & 1.16 & 1.574 & 30.8\\
+\hspace{1em}aorsf-random & 0.082 (0.034) & 0.756 (0.032) & 0.459 & 1.89 & 0.052 & 1.02\\
+\hspace{1em}ranger-extratrees & 0.072 (0.019) & 0.748 (0.036) & 0.032 & 0.130 & 0.080 & 1.58\\
+\hspace{1em}rfsrc-standard & 0.065 (0.053) & 0.736 (0.035) & 0.111 & 0.458 & 0.040 & 0.784\\
+\hspace{1em}xgboost-cox & 0.028 (0.055) & 0.694 (0.117) & 0.325 & 1.34 & 0.002 & 0.039\\
+\hspace{1em}xgboost-aft & -2.63 (0.596) & 0.757 (0.034) & 7.205 & 29.7 & 0.005 & 0.098\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{Rotterdam Breast Cancer Data, N = 2,982}}}\\
+\multicolumn{7}{l}{\textit{\textbf{FCL; relapse, n = 541, p = 7}}}\\
 \hline
-\hspace{1em}Ranger & 0.719 (0.011) & 0.145 (0.011) & 2.480 & 0.410 & 4.456 & 0.692\\
-\hspace{1em}aorsf\_net & 0.714 (0.007) & 0.141 (0.007) & 237.007 & 39.2 & 237.337 & 36.9\\
-\hspace{1em}Party & 0.712 (0.008) & 0.141 (0.012) & 7.030 & 1.16 & 21.888 & 3.40\\
-\hspace{1em}aORSF(i=1) & 0.712 (0.006) & 0.139 (0.008) & 6.053 & 1.00 & 6.436 & 1.00\\
-\hspace{1em}aORSF(i=15) & 0.711 (0.005) & 0.139 (0.007) & 13.541 & 2.24 & 13.925 & 2.16\\
-\hspace{1em}Rfsrc & 0.701 (0.008) & 0.120 (0.010) & 2.222 & 0.367 & 2.458 & 0.382\\
+\hspace{1em}glmnet-cox & 0.024 (0.020) & 0.611 (0.033) & 0.086 & 0.236 & 0.002 & 0.027\\
+\hspace{1em}ranger-extratrees & 0.016 (0.016) & 0.593 (0.024) & 0.031 & 0.086 & 0.081 & 1.07\\
+\hspace{1em}obliqueRSF-net & 0.010 (0.018) & 0.589 (0.023) & 221.459 & 610.5 & 10.676 & 141.1\\
+\hspace{1em}xgboost-cox & 0.006 (0.016) & 0.591 (0.030) & 1.383 & 3.81 & 0.003 & 0.040\\
+\hspace{1em}aorsf-random & 0.006 (0.020) & 0.585 (0.026) & 0.697 & 1.92 & 0.071 & 0.937\\
+\hspace{1em}party-cif & 0.003 (0.020) & 0.589 (0.021) & 0.280 & 0.772 & 1.775 & 23.5\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.002 (0.023) & 0.590 (0.027) & 0.709 & 1.95 & 0.075 & 0.997\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.002 (0.023) & 0.589 (0.026) & 0.363 & 1.00 & 0.076 & 1.00\\
+\hspace{1em}aorsf-net & 0.001 (0.023) & 0.587 (0.027) & 20.256 & 55.8 & 0.075 & 0.996\\
+\hspace{1em}rfsrc-standard & -0.033 (0.031) & 0.572 (0.025) & 0.917 & 2.53 & 0.087 & 1.16\\
+\hspace{1em}xgboost-aft & -0.858 (0.311) & 0.578 (0.031) & 6.260 & 17.3 & 0.005 & 0.066\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{time\_to\_million}}}\\
+\multicolumn{7}{l}{\textit{\textbf{GBSG II; recurrence or death, n = 686, p = 10}}}\\
 \hline
-\hspace{1em}aorsf\_net & 0.937 (0.013) & 0.560 (0.040) & 78.384 & 55.8 & 78.461 & 53.0\\
-\hspace{1em}aORSF(i=15) & 0.937 (0.018) & 0.555 (0.043) & 4.491 & 3.20 & 4.569 & 3.09\\
-\hspace{1em}aORSF(i=1) & 0.935 (0.017) & 0.552 (0.039) & 1.405 & 1.00 & 1.481 & 1.00\\
-\hspace{1em}Rfsrc & 0.932 (0.023) & 0.550 (0.045) & 0.784 & 0.558 & 0.853 & 0.576\\
-\hspace{1em}Party & 0.921 (0.014) & 0.485 (0.034) & 0.621 & 0.442 & 1.684 & 1.14\\
-\hspace{1em}Ranger & 0.916 (0.023) & 0.452 (0.039) & 0.324 & 0.231 & 0.428 & 0.289\\
+\hspace{1em}obliqueRSF-net & 0.125 (0.015) & 0.747 (0.018) & 283.036 & 530.9 & 10.993 & 80.3\\
+\hspace{1em}party-cif & 0.125 (0.021) & 0.745 (0.020) & 0.465 & 0.873 & 2.516 & 18.4\\
+\hspace{1em}aorsf-net & 0.123 (0.024) & 0.741 (0.019) & 37.619 & 70.6 & 0.132 & 0.963\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.121 (0.026) & 0.739 (0.018) & 1.202 & 2.25 & 0.136 & 0.993\\
+\hspace{1em}rfsrc-standard & 0.120 (0.026) & 0.739 (0.019) & 1.528 & 2.87 & 0.113 & 0.825\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.117 (0.025) & 0.736 (0.018) & 0.533 & 1.00 & 0.137 & 1.00\\
+\hspace{1em}aorsf-random & 0.108 (0.022) & 0.729 (0.025) & 1.226 & 2.30 & 0.130 & 0.948\\
+\hspace{1em}ranger-extratrees & 0.094 (0.014) & 0.737 (0.023) & 0.061 & 0.113 & 0.141 & 1.03\\
+\hspace{1em}glmnet-cox & 0.088 (0.017) & 0.731 (0.021) & 0.091 & 0.170 & 0.003 & 0.022\\
+\hspace{1em}xgboost-cox & 0.086 (0.019) & 0.736 (0.021) & 2.596 & 4.87 & 0.003 & 0.022\\
+\hspace{1em}xgboost-aft & -1.10 (0.176) & 0.734 (0.021) & 10.121 & 19.0 & 0.006 & 0.044\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{vdv}}}\\
+\multicolumn{7}{l}{\textit{\textbf{GUIDE-IT; CVD death, n = 894, p = 59}}}\\
 \hline
-\hspace{1em}Rfsrc & 0.782 (0.231) & 0.033 (0.185) & 0.198 & 0.080 & 0.450 & 0.148\\
-\hspace{1em}aorsf\_net & 0.770 (0.161) & -0.019 (0.283) & 20.190 & 8.13 & 20.749 & 6.80\\
-\hspace{1em}aORSF(i=1) & 0.762 (0.079) & -0.012 (0.126) & 2.484 & 1.00 & 3.050 & 1.00\\
-\hspace{1em}Ranger & 0.751 (0.070) & -0.017 (0.093) & 0.484 & 0.195 & 0.576 & 0.189\\
-\hspace{1em}aORSF(i=15) & 0.735 (0.171) & -0.025 (0.135) & 2.569 & 1.03 & 3.136 & 1.03\\
-\hspace{1em}Party & 0.722 (0.102) & -0.030 (0.165) & 8.098 & 3.26 & 14.088 & 4.62\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.075 (0.019) & 0.739 (0.030) & 0.578 & 1.00 & 0.130 & 1.00\\
+\hspace{1em}aorsf-net & 0.074 (0.020) & 0.738 (0.030) & 27.827 & 48.2 & 0.134 & 1.03\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.072 (0.020) & 0.738 (0.029) & 1.369 & 2.37 & 0.129 & 0.993\\
+\hspace{1em}obliqueRSF-net & 0.061 (0.015) & 0.736 (0.029) & 220.667 & 382.1 & 11.349 & 87.2\\
+\hspace{1em}party-cif & 0.056 (0.015) & 0.732 (0.030) & 1.431 & 2.48 & 3.202 & 24.6\\
+\hspace{1em}glmnet-cox & 0.056 (0.041) & 0.704 (0.097) & 0.497 & 0.860 & 0.002 & 0.015\\
+\hspace{1em}ranger-extratrees & 0.052 (0.013) & 0.729 (0.032) & 0.521 & 0.902 & 0.182 & 1.40\\
+\hspace{1em}rfsrc-standard & 0.048 (0.026) & 0.704 (0.029) & 0.776 & 1.34 & 0.061 & 0.470\\
+\hspace{1em}aorsf-random & 0.034 (0.012) & 0.694 (0.033) & 1.064 & 1.84 & 0.134 & 1.03\\
+\hspace{1em}xgboost-cox & 0.021 (0.066) & 0.744 (0.024) & 3.668 & 6.35 & 0.003 & 0.023\\
+\hspace{1em}xgboost-aft & -4.95 (0.885) & 0.729 (0.027) & 11.776 & 20.4 & 0.007 & 0.054\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{veteran}}}\\
+\multicolumn{7}{l}{\textit{\textbf{GUIDE-IT; HF hospitalization, n = 894, p = 59}}}\\
 \hline
-\hspace{1em}Ranger & 0.865 (0.063) & 0.183 (0.036) & 0.023 & 0.113 & 0.043 & 0.194\\
-\hspace{1em}aORSF(i=15) & 0.837 (0.048) & 0.281 (0.075) & 0.371 & 1.84 & 0.387 & 1.75\\
-\hspace{1em}aORSF(i=1) & 0.833 (0.053) & 0.278 (0.081) & 0.202 & 1.00 & 0.222 & 1.00\\
-\hspace{1em}Party & 0.833 (0.057) & 0.235 (0.056) & 0.150 & 0.744 & 0.231 & 1.04\\
-\hspace{1em}aorsf\_net & 0.820 (0.059) & 0.256 (0.083) & 17.115 & 84.7 & 17.133 & 77.3\\
-\hspace{1em}Rfsrc & 0.784 (0.111) & 0.218 (0.112) & 0.077 & 0.380 & 0.099 & 0.447\\*
+\hspace{1em}aorsf-net & 0.081 (0.019) & 0.719 (0.023) & 54.048 & 60.8 & 0.207 & 1.03\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.081 (0.019) & 0.719 (0.023) & 2.465 & 2.77 & 0.198 & 0.986\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.080 (0.020) & 0.719 (0.024) & 0.889 & 1.00 & 0.200 & 1.00\\
+\hspace{1em}ranger-extratrees & 0.073 (0.012) & 0.717 (0.024) & 0.566 & 0.636 & 0.202 & 1.01\\
+\hspace{1em}obliqueRSF-net & 0.073 (0.012) & 0.715 (0.025) & 382.769 & 430.5 & 13.800 & 68.9\\
+\hspace{1em}party-cif & 0.070 (0.012) & 0.711 (0.024) & 1.381 & 1.55 & 3.363 & 16.8\\
+\hspace{1em}rfsrc-standard & 0.059 (0.019) & 0.691 (0.023) & 1.511 & 1.70 & 0.118 & 0.591\\
+\hspace{1em}glmnet-cox & 0.053 (0.023) & 0.692 (0.030) & 0.433 & 0.488 & 0.003 & 0.015\\
+\hspace{1em}aorsf-random & 0.051 (0.011) & 0.682 (0.025) & 2.100 & 2.36 & 0.196 & 0.980\\
+\hspace{1em}xgboost-cox & 0.039 (0.019) & 0.694 (0.027) & 2.967 & 3.34 & 0.002 & 0.010\\
+\hspace{1em}xgboost-aft & -2.12 (0.324) & 0.696 (0.025) & 12.660 & 14.2 & 0.006 & 0.030\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Heart Transplant; graft-loss or death, n = 3787, p = 52}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.051 (0.007) & 0.730 (0.013) & 126.867 & 33.3 & 1.065 & 1.03\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.050 (0.007) & 0.731 (0.014) & 3.809 & 1.00 & 1.034 & 1.00\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.050 (0.007) & 0.730 (0.013) & 10.098 & 2.65 & 1.029 & 0.995\\
+\hspace{1em}party-cif & 0.048 (0.006) & 0.731 (0.012) & 10.755 & 2.82 & 39.378 & 38.1\\
+\hspace{1em}rfsrc-standard & 0.048 (0.009) & 0.727 (0.012) & 3.702 & 0.972 & 1.115 & 1.08\\
+\hspace{1em}obliqueRSF-net & 0.048 (0.006) & 0.729 (0.013) & 365.863 & 96.1 & 161.863 & 156.6\\
+\hspace{1em}ranger-extratrees & 0.044 (0.006) & 0.727 (0.013) & 5.396 & 1.42 & 3.471 & 3.36\\
+\hspace{1em}glmnet-cox & 0.035 (0.005) & 0.710 (0.017) & 1.362 & 0.358 & 0.010 & 0.010\\
+\hspace{1em}xgboost-cox & 0.032 (0.008) & 0.717 (0.015) & 3.871 & 1.02 & 0.016 & 0.016\\
+\hspace{1em}aorsf-random & 0.028 (0.004) & 0.691 (0.014) & 6.272 & 1.65 & 1.040 & 1.01\\
+\hspace{1em}xgboost-aft & -4.26 (0.534) & 0.726 (0.012) & 12.730 & 3.34 & 0.009 & 0.009\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Monoclonal gammopathy; death, n = 1384, p = 8}}}\\
+\hline
+\hspace{1em}aorsf-cph(maxit = 15) & 0.158 (0.017) & 0.743 (0.011) & 3.015 & 2.22 & 0.332 & 1.00\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.157 (0.017) & 0.742 (0.011) & 1.360 & 1.00 & 0.332 & 1.00\\
+\hspace{1em}obliqueRSF-net & 0.155 (0.013) & 0.743 (0.011) & 240.551 & 176.9 & 16.910 & 50.9\\
+\hspace{1em}aorsf-net & 0.154 (0.017) & 0.741 (0.011) & 90.724 & 66.7 & 0.325 & 0.979\\
+\hspace{1em}party-cif & 0.152 (0.016) & 0.739 (0.012) & 1.585 & 1.17 & 6.240 & 18.8\\
+\hspace{1em}rfsrc-standard & 0.150 (0.018) & 0.737 (0.011) & 2.484 & 1.83 & 0.192 & 0.579\\
+\hspace{1em}aorsf-random & 0.147 (0.014) & 0.736 (0.012) & 2.999 & 2.21 & 0.316 & 0.951\\
+\hspace{1em}glmnet-cox & 0.139 (0.022) & 0.728 (0.014) & 0.121 & 0.089 & 0.004 & 0.012\\
+\hspace{1em}xgboost-cox & 0.122 (0.014) & 0.734 (0.012) & 3.480 & 2.56 & 0.005 & 0.015\\
+\hspace{1em}ranger-extratrees & 0.116 (0.007) & 0.745 (0.012) & 0.063 & 0.046 & 0.202 & 0.607\\
+\hspace{1em}xgboost-aft & -0.863 (0.151) & 0.732 (0.013) & 11.184 & 8.23 & 0.006 & 0.018\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Monoclonal gammopathy; malignancy, n = 1384, p = 8}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.015 (0.011) & 0.650 (0.046) & 0.101 & 0.138 & 0.002 & 0.014\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.009 (0.014) & 0.639 (0.031) & 1.456 & 2.00 & 0.141 & 0.995\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.008 (0.014) & 0.636 (0.030) & 0.728 & 1.00 & 0.142 & 1.00\\
+\hspace{1em}ranger-extratrees & 0.007 (0.007) & 0.633 (0.030) & 0.058 & 0.080 & 0.162 & 1.14\\
+\hspace{1em}aorsf-random & 0.007 (0.014) & 0.628 (0.029) & 1.149 & 1.58 & 0.140 & 0.983\\
+\hspace{1em}xgboost-cox & 0.007 (0.014) & 0.644 (0.040) & 1.932 & 2.65 & 0.002 & 0.014\\
+\hspace{1em}aorsf-net & 0.006 (0.014) & 0.634 (0.029) & 23.343 & 32.1 & 0.141 & 0.996\\
+\hspace{1em}obliqueRSF-net & 0.005 (0.012) & 0.626 (0.032) & 39.064 & 53.6 & 16.273 & 114.6\\
+\hspace{1em}party-cif & 0.004 (0.013) & 0.626 (0.031) & 1.558 & 2.14 & 5.620 & 39.6\\
+\hspace{1em}rfsrc-standard & -0.011 (0.018) & 0.611 (0.032) & 0.793 & 1.09 & 0.075 & 0.528\\
+\hspace{1em}xgboost-aft & -5.45 (1.09) & 0.630 (0.037) & 9.725 & 13.4 & 0.006 & 0.042\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Movies released in 2015-2018; gross 1M USD, n = 551, p = 46}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.619 (0.029) & 0.941 (0.009) & 0.180 & 0.226 & 0.004 & 0.019\\
+\hspace{1em}aorsf-net & 0.531 (0.024) & 0.929 (0.010) & 52.636 & 66.0 & 0.182 & 1.00\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.523 (0.022) & 0.927 (0.010) & 2.814 & 3.53 & 0.182 & 1.00\\
+\hspace{1em}rfsrc-standard & 0.521 (0.023) & 0.923 (0.011) & 1.705 & 2.14 & 0.103 & 0.567\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.517 (0.024) & 0.923 (0.011) & 0.797 & 1.00 & 0.181 & 1.00\\
+\hspace{1em}xgboost-cox & 0.508 (0.030) & 0.932 (0.010) & 12.812 & 16.1 & 0.006 & 0.033\\
+\hspace{1em}party-cif & 0.479 (0.025) & 0.904 (0.015) & 0.393 & 0.493 & 2.302 & 12.7\\
+\hspace{1em}ranger-extratrees & 0.432 (0.025) & 0.901 (0.016) & 0.058 & 0.073 & 0.108 & 0.594\\
+\hspace{1em}obliqueRSF-net & 0.323 (0.021) & 0.911 (0.015) & 163.647 & 205.2 & 27.707 & 152.7\\
+\hspace{1em}aorsf-random & 0.300 (0.025) & 0.850 (0.023) & 1.511 & 1.90 & 0.170 & 0.934\\
+\hspace{1em}xgboost-aft & -0.483 (0.078) & 0.927 (0.011) & 50.372 & 63.2 & 0.009 & 0.047\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Non-alcohol fatty liver disease; death, n = 17549, p = 24}}}\\
+\hline
+\hspace{1em}aorsf-cph(maxit = 15) & 0.217 (0.010) & 0.868 (0.006) & 50.582 & 2.70 & 43.776 & 1.15\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.217 (0.010) & 0.869 (0.006) & 18.704 & 1.00 & 37.967 & 1.00\\
+\hspace{1em}aorsf-net & 0.214 (0.010) & 0.865 (0.006) & 478.494 & 25.6 & 37.231 & 0.981\\
+\hspace{1em}obliqueRSF-net & 0.213 (0.010) & 0.868 (0.006) & 1560.671 & 83.4 & 6530.150 & 172.0\\
+\hspace{1em}rfsrc-standard & 0.212 (0.011) & 0.860 (0.007) & 12.257 & 0.655 & 1.293 & 0.034\\
+\hspace{1em}glmnet-cox & 0.211 (0.011) & 0.860 (0.006) & 1.509 & 0.081 & 0.464 & 0.012\\
+\hspace{1em}party-cif & 0.208 (0.009) & 0.863 (0.006) & 72.349 & 3.87 & 716.204 & 18.9\\
+\hspace{1em}ranger-extratrees & 0.184 (0.007) & 0.860 (0.006) & 44.210 & 2.36 & 96.730 & 2.55\\
+\hspace{1em}aorsf-random & 0.144 (0.006) & 0.838 (0.007) & 25.720 & 1.38 & 37.114 & 0.978\\
+\hspace{1em}xgboost-cox & 0.022 (0.015) & 0.876 (0.006) & 9.865 & 0.527 & 1.013 & 0.027\\
+\hspace{1em}xgboost-aft & -7.06 (0.796) & 0.874 (0.006) & 29.664 & 1.59 & 1.001 & 0.026\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Primary biliary cholangitis; death, n = 276, p = 19}}}\\
+\hline
+\hspace{1em}aorsf-cph(maxit = 1) & 0.418 (0.048) & 0.905 (0.023) & 0.191 & 1.00 & 0.045 & 1.00\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.408 (0.047) & 0.902 (0.023) & 0.443 & 2.32 & 0.047 & 1.05\\
+\hspace{1em}aorsf-net & 0.402 (0.044) & 0.901 (0.024) & 14.653 & 76.7 & 0.046 & 1.03\\
+\hspace{1em}rfsrc-standard & 0.378 (0.048) & 0.890 (0.026) & 0.101 & 0.527 & 0.038 & 0.854\\
+\hspace{1em}obliqueRSF-net & 0.363 (0.037) & 0.903 (0.024) & 109.549 & 573.2 & 1.750 & 39.1\\
+\hspace{1em}aorsf-random & 0.345 (0.038) & 0.889 (0.022) & 0.433 & 2.27 & 0.046 & 1.03\\
+\hspace{1em}party-cif & 0.344 (0.039) & 0.899 (0.027) & 0.194 & 1.02 & 0.401 & 8.95\\
+\hspace{1em}glmnet-cox & 0.337 (0.053) & 0.885 (0.027) & 0.101 & 0.526 & 0.002 & 0.045\\
+\hspace{1em}ranger-extratrees & 0.270 (0.034) & 0.890 (0.029) & 0.026 & 0.135 & 0.038 & 0.855\\
+\hspace{1em}xgboost-cox & 0.263 (0.095) & 0.879 (0.026) & 4.438 & 23.2 & 0.002 & 0.045\\
+\hspace{1em}xgboost-aft & -0.985 (0.345) & 0.881 (0.024) & 9.390 & 49.1 & 0.007 & 0.146\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Rotterdam tumor bank; death, n = 2982, p = 11}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.170 (0.014) & 0.764 (0.011) & 156.389 & 51.8 & 1.283 & 0.947\\
+\hspace{1em}obliqueRSF-net & 0.167 (0.012) & 0.764 (0.012) & 453.760 & 150.2 & 117.582 & 86.7\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.167 (0.014) & 0.762 (0.011) & 7.285 & 2.41 & 1.353 & 0.998\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.165 (0.015) & 0.760 (0.012) & 3.021 & 1.00 & 1.356 & 1.00\\
+\hspace{1em}party-cif & 0.164 (0.012) & 0.762 (0.012) & 4.837 & 1.60 & 28.933 & 21.3\\
+\hspace{1em}rfsrc-standard & 0.163 (0.014) & 0.759 (0.011) & 3.315 & 1.10 & 1.024 & 0.755\\
+\hspace{1em}aorsf-random & 0.157 (0.012) & 0.755 (0.012) & 5.742 & 1.90 & 1.275 & 0.941\\
+\hspace{1em}ranger-extratrees & 0.141 (0.007) & 0.751 (0.011) & 3.462 & 1.15 & 2.475 & 1.83\\
+\hspace{1em}xgboost-cox & 0.135 (0.014) & 0.756 (0.012) & 3.849 & 1.27 & 0.020 & 0.015\\
+\hspace{1em}glmnet-cox & 0.120 (0.010) & 0.732 (0.011) & 0.211 & 0.070 & 0.025 & 0.018\\
+\hspace{1em}xgboost-aft & -1.36 (0.159) & 0.763 (0.011) & 15.373 & 5.09 & 0.009 & 0.007\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Rotterdam tumor bank; recurrence, n = 2982, p = 11}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.151 (0.011) & 0.739 (0.010) & 533.082 & 162.9 & 134.838 & 89.5\\
+\hspace{1em}aorsf-net & 0.150 (0.013) & 0.738 (0.010) & 170.007 & 52.0 & 1.437 & 0.954\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.148 (0.013) & 0.736 (0.010) & 8.035 & 2.46 & 1.523 & 1.01\\
+\hspace{1em}party-cif & 0.147 (0.012) & 0.736 (0.010) & 5.107 & 1.56 & 31.190 & 20.7\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.147 (0.013) & 0.735 (0.010) & 3.272 & 1.00 & 1.506 & 1.00\\
+\hspace{1em}aorsf-random & 0.143 (0.010) & 0.733 (0.009) & 6.299 & 1.93 & 1.394 & 0.926\\
+\hspace{1em}rfsrc-standard & 0.142 (0.013) & 0.733 (0.010) & 3.258 & 0.996 & 0.925 & 0.614\\
+\hspace{1em}ranger-extratrees & 0.137 (0.007) & 0.736 (0.009) & 3.429 & 1.05 & 2.687 & 1.78\\
+\hspace{1em}glmnet-cox & 0.119 (0.008) & 0.729 (0.010) & 0.252 & 0.077 & 0.022 & 0.014\\
+\hspace{1em}xgboost-cox & 0.115 (0.008) & 0.732 (0.011) & 3.302 & 1.01 & 0.022 & 0.015\\
+\hspace{1em}xgboost-aft & -1.06 (0.148) & 0.737 (0.010) & 14.130 & 4.32 & 0.010 & 0.007\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Serum free light chain; death, n = 7874, p = 10}}}\\
+\hline
+\hspace{1em}aorsf-cph(maxit = 15) & 0.249 (0.013) & 0.824 (0.008) & 19.646 & 2.34 & 17.424 & 0.761\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.249 (0.014) & 0.824 (0.007) & 8.398 & 1.00 & 22.885 & 1.00\\
+\hspace{1em}aorsf-net & 0.249 (0.013) & 0.821 (0.008) & 305.832 & 36.4 & 21.792 & 0.952\\
+\hspace{1em}glmnet-cox & 0.248 (0.012) & 0.819 (0.007) & 0.615 & 0.073 & 0.234 & 0.010\\
+\hspace{1em}obliqueRSF-net & 0.247 (0.012) & 0.820 (0.008) & 1107.351 & 131.9 & 817.888 & 35.7\\
+\hspace{1em}ranger-extratrees & 0.243 (0.010) & 0.819 (0.008) & 15.165 & 1.81 & 15.048 & 0.658\\
+\hspace{1em}party-cif & 0.243 (0.012) & 0.817 (0.008) & 19.999 & 2.38 & 155.997 & 6.82\\
+\hspace{1em}rfsrc-standard & 0.242 (0.013) & 0.814 (0.008) & 6.781 & 0.807 & 0.620 & 0.027\\
+\hspace{1em}aorsf-random & 0.230 (0.012) & 0.815 (0.008) & 14.450 & 1.72 & 20.496 & 0.896\\
+\hspace{1em}xgboost-cox & 0.091 (0.035) & 0.822 (0.008) & 6.066 & 0.722 & 0.136 & 0.006\\
+\hspace{1em}xgboost-aft & -2.69 (0.251) & 0.822 (0.008) & 18.993 & 2.26 & 0.650 & 0.028\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{SPRINT; CVD death, n = 9361, p = 174}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.071 (0.011) & 0.793 (0.014) & 13.662 & 1.13 & 0.027 & 0.006\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.070 (0.007) & 0.795 (0.013) & 36.982 & 3.06 & 4.419 & 0.951\\
+\hspace{1em}aorsf-net & 0.069 (0.009) & 0.794 (0.013) & 358.365 & 29.7 & 4.222 & 0.909\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.069 (0.007) & 0.795 (0.013) & 12.084 & 1.00 & 4.645 & 1.00\\
+\hspace{1em}obliqueRSF-net & 0.067 (0.006) & 0.796 (0.014) & 1138.135 & 94.2 & 1242.623 & 267.5\\
+\hspace{1em}rfsrc-standard & 0.064 (0.008) & 0.786 (0.015) & 5.499 & 0.455 & 1.247 & 0.268\\
+\hspace{1em}party-cif & 0.061 (0.005) & 0.796 (0.013) & 49.198 & 4.07 & 194.676 & 41.9\\
+\hspace{1em}ranger-extratrees & 0.054 (0.004) & 0.789 (0.014) & 8.810 & 0.729 & 9.762 & 2.10\\
+\hspace{1em}aorsf-random & 0.027 (0.002) & 0.745 (0.016) & 16.090 & 1.33 & 4.634 & 0.998\\
+\hspace{1em}xgboost-cox & 0.007 (0.019) & 0.797 (0.013) & 7.793 & 0.645 & 0.031 & 0.007\\
+\hspace{1em}xgboost-aft & -10.7 (0.853) & 0.794 (0.013) & 23.758 & 1.97 & 0.017 & 0.004\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{SPRINT; death, n = 9361, p = 174}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.123 (0.012) & 0.770 (0.010) & 5.748 & 0.327 & 0.072 & 0.005\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.117 (0.009) & 0.770 (0.010) & 55.731 & 3.17 & 13.261 & 0.895\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.116 (0.009) & 0.769 (0.009) & 17.581 & 1.00 & 14.818 & 1.00\\
+\hspace{1em}aorsf-net & 0.114 (0.010) & 0.769 (0.010) & 614.727 & 35.0 & 11.692 & 0.789\\
+\hspace{1em}obliqueRSF-net & 0.113 (0.007) & 0.767 (0.010) & 3120.498 & 177.5 & 1215.032 & 82.0\\
+\hspace{1em}rfsrc-standard & 0.110 (0.009) & 0.762 (0.010) & 8.948 & 0.509 & 0.805 & 0.054\\
+\hspace{1em}party-cif & 0.107 (0.007) & 0.764 (0.010) & 51.458 & 2.93 & 222.920 & 15.0\\
+\hspace{1em}ranger-extratrees & 0.097 (0.005) & 0.756 (0.010) & 15.249 & 0.867 & 11.477 & 0.774\\
+\hspace{1em}aorsf-random & 0.053 (0.003) & 0.719 (0.011) & 23.393 & 1.33 & 15.908 & 1.07\\
+\hspace{1em}xgboost-cox & 0.031 (0.022) & 0.772 (0.009) & 9.917 & 0.564 & 0.082 & 0.006\\
+\hspace{1em}xgboost-aft & -4.39 (0.355) & 0.772 (0.010) & 24.150 & 1.37 & 0.027 & 0.002\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Systolic Heart Failure; death, n = 2231, p = 41}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.114 (0.012) & 0.747 (0.012) & 0.272 & 0.113 & 0.010 & 0.013\\
+\hspace{1em}obliqueRSF-net & 0.114 (0.011) & 0.747 (0.012) & 388.113 & 161.6 & 56.165 & 70.8\\
+\hspace{1em}aorsf-net & 0.112 (0.013) & 0.743 (0.012) & 119.347 & 49.7 & 0.813 & 1.02\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.111 (0.013) & 0.744 (0.012) & 6.734 & 2.80 & 0.798 & 1.01\\
+\hspace{1em}party-cif & 0.111 (0.010) & 0.745 (0.012) & 4.287 & 1.79 & 18.913 & 23.8\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.110 (0.015) & 0.744 (0.012) & 2.401 & 1.00 & 0.793 & 1.00\\
+\hspace{1em}rfsrc-standard & 0.105 (0.012) & 0.735 (0.012) & 2.526 & 1.05 & 0.273 & 0.345\\
+\hspace{1em}ranger-extratrees & 0.092 (0.008) & 0.738 (0.013) & 3.196 & 1.33 & 1.399 & 1.76\\
+\hspace{1em}xgboost-cox & 0.090 (0.012) & 0.745 (0.011) & 4.108 & 1.71 & 0.010 & 0.013\\
+\hspace{1em}aorsf-random & 0.081 (0.006) & 0.731 (0.013) & 4.722 & 1.97 & 0.779 & 0.983\\
+\hspace{1em}xgboost-aft & -1.97 (0.226) & 0.741 (0.010) & 13.112 & 5.46 & 0.008 & 0.010\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{VA lung cancer trial; death, n = 137, p = 8}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.200 (0.049) & 0.792 (0.036) & 10.492 & 91.2 & 0.024 & 1.00\\
+\hspace{1em}aorsf-cph(maxit = 1) & 0.199 (0.049) & 0.790 (0.036) & 0.115 & 1.00 & 0.024 & 1.00\\
+\hspace{1em}aorsf-cph(maxit = 15) & 0.198 (0.050) & 0.789 (0.037) & 0.225 & 1.95 & 0.024 & 1.00\\
+\hspace{1em}rfsrc-standard & 0.176 (0.046) & 0.781 (0.035) & 0.063 & 0.546 & 0.026 & 1.08\\
+\hspace{1em}glmnet-cox & 0.161 (0.044) & 0.784 (0.041) & 0.071 & 0.614 & 0.002 & 0.083\\
+\hspace{1em}aorsf-random & 0.151 (0.047) & 0.772 (0.044) & 0.295 & 2.56 & 0.023 & 0.958\\
+\hspace{1em}party-cif & 0.129 (0.039) & 0.766 (0.036) & 0.098 & 0.855 & 0.121 & 5.04\\
+\hspace{1em}obliqueRSF-net & 0.127 (0.035) & 0.791 (0.034) & 60.532 & 525.9 & 0.660 & 27.5\\
+\hspace{1em}ranger-extratrees & 0.091 (0.036) & 0.772 (0.038) & 0.020 & 0.175 & 0.026 & 1.09\\
+\hspace{1em}xgboost-cox & 0.069 (0.066) & 0.742 (0.055) & 1.400 & 12.2 & 0.002 & 0.083\\
+\hspace{1em}xgboost-aft & -0.010 (0.131) & 0.750 (0.044) & 5.934 & 51.5 & 0.005 & 0.208\\*
 \end{longtable}
@@
 \end{knitrout}
-
-% Acknowledgements should go at the end, before appendices and references
-
-\acks{We would like to acknowledge support for this project
-from the National Science Foundation (NSF grant IIS-9988642)
-and the Multidisciplinary Research Program of the Department
-of Defense (MURI N00014-00-1-0637). }
-
-% Manual newpage inserted to improve layout of sample file - not
-% needed in general before appendices/bibliography.
-
-\newpage
-
-\appendix
-\section*{Appendix A.}
-\label{app:theorem}
-
-% Note: in this sample, the section number is hard-coded in. Following
-% proper LaTeX conventions, it should properly be coded as a reference:
-
-%In this appendix we prove the following theorem from
-%Section~\ref{sec:textree-generalization}:
-
-In this appendix we prove the following theorem from
-Section~6.2:
-
-\noindent
-{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
-not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
-dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
-which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
-respective empirical mutual information values based on the sample
-$\dataset$. Then
-\[
-	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
-\]
-with equality only if $u$ is identically 0.} \hfill\BlackBox
-
-\noindent
-{\bf Proof}. We use the notation:
-\[
-P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
-P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
-\]
-These values represent the (empirical) probabilities of $v$
-taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
-by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\
-
-{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
 

### 2022-06-06 R/bench_pred.R

@@ -9,17 +9,12 @@ bench_pred <- function(data_source,
                        model_type,
                        data_load_fun,
                        model_fit_fun,
-                       model_prd_fun,
+                       model_pred_fun,
                        n_obs = NULL,
                        n_z = NULL,
                        correlated_x = NULL,
                        run_seed,
-                       test_prop = 1/4) {
-
-  conflict_prefer("filter", "dplyr")
-  conflict_prefer("slice", "dplyr")
-  conflict_prefer("summarize", "dplyr")
-  conflict_prefer("Predict", "modeltools")
+                       test_prop = 1/2) {
 
   set.seed(run_seed)
 
@@ -58,52 +53,79 @@ bench_pred <- function(data_source,
   .train <- as.data.frame(juice(imputer))
   .test <- as.data.frame(bake(imputer, new_data = test))
 
-  pred_horizon <- median(.train$time)
+  event_time_bounds <- quantile(
+    x = data_all$time[data_all$status==1],
+    probs = c(.25, .75)
+  )
 
-  model <- model_fit_fun(train = .train) |>
-    model_prd_fun(test = .test, pred_horizon = pred_horizon)
+  pred_horizon <- sort(unique(.test$time[.test$status == 1]))
+
+  pred_horizon <- pred_horizon[pred_horizon <= event_time_bounds['75%']]
+  pred_horizon <- pred_horizon[pred_horizon >= event_time_bounds['25%']]
+
+  if(is_empty(pred_horizon)) return(NULL)
+
+  # Don't pipe here - it can mess up the measurement
+  # of time during model fitting and model predictions.
+
+  model <- model_fit_fun(train = .train,
+                         pred_horizon = pred_horizon)
+
+  predictions <- model_pred_fun(object = model,
+                                test = .test,
+                                pred_horizon = pred_horizon)
 
   sc <- try(
     Score(
-      object = set_names(list(model$pred), model_type),
+      object = set_names(list(predictions$pred), model_type),
       formula = Surv(time, status) ~ 1,
       data = test,
-      summary = 'IPA',
+      summary = c('IPA', 'ibs'),
       times = pred_horizon
     ),
     silent = TRUE)
 
   score <- tibble(model = model_type,
                   cstat = NA_real_,
-                  Brier = NA_real_,
-                  IPA = NA_real_)
[…]

### 2022-06-06 R/bench_pred_model.R

@@ -1,0 +1,87 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param bm_pred_clean
+#' @param data_key
+#' @param model_key
+bench_pred_model <- function(bm_pred_clean, data_key, model_key) {
+
+  bm_pred_clean <- filter(bm_pred_clean, model != 'xgb_aft')
+
+  # fit <- stan_glmer(data = bm_pred_clean,
+  #                   formula = ibs_scaled ~ model + (1|data/run))
+
+  bm_pred_mdat <- bm_pred_clean |>
+    select(data, run, model, cstat, ibs_scaled) |>
+    pivot_wider(names_from = model,
+                values_from = c(cstat, ibs_scaled),
+                names_sep = '..') |>
+    mutate(
+      across(
+        .cols = starts_with('cstat'),
+        .fns = ~ .x - cstat..aorsf_cph_1
+      ),
+      across(
+        .cols = starts_with('ibs_scaled'),
+        .fns = ~ .x - ibs_scaled..aorsf_cph_1
+      )
+    ) |>
+    select(-ibs_scaled..aorsf_cph_1, -cstat..aorsf_cph_1) |>
+    pivot_longer(cols = matches('^cstat|^ibs_scaled')) |>
+    separate(name, into = c("metric", "model"), sep = '\\.\\.') |>
+    mutate(across(where(is.character), as.factor))
+
+  mdl <- list(
+
+    ibs_scaled = stan_glmer(
+      data = bm_pred_mdat,
+      formula = value ~ -1 + model + (1 | data/run),
+      subset = metric == 'ibs_scaled'
+    ),
+
+    cstat = stan_glmer(
+      data = bm_pred_mdat,
+      formula = value ~ -1 + model + (1 | data/run),
+      subset = metric == 'cstat'
+    )
+
+  )
+
+  newdata <- distinct(bm_pred_mdat, model)
+
+  data_infer <- map_dfr(
+    .x = mdl,
+    .id = 'metric',
+    .f = ~ posterior_epred(.x,
+                           newdata = newdata,
+                           re.form = ~0) |>
+      as_tibble() |>
+      set_names(newdata$model) |>
+      pivot_longer(everything(), names_to = 'model') |>
+      add_row(model = 'aorsf_cph_1', value = Inf) |>
+      mutate(model = factor(model),
[…]

### 2022-06-06 R/clean_bm_pred.R

@@ -1,0 +1,32 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param bm_pred_comb
+clean_bm_pred <- function(bm_pred_comb) {
+
+  to_omit <- bm_pred_comb |>
+    filter(is.na(cstat) | is.na(ibs_scaled)) |>
+    distinct(data, run) |>
+    group_by(data) |>
+    group_split() |>
+    map(as.list)
+
+  for(i in seq_along(to_omit)){
+
+    bm_pred_comb <- bm_pred_comb |>
+      filter( ! (data %in% unique(to_omit[[i]]$data) &
+                   run %in% to_omit[[i]]$run) )
+
+  }
+
+  # bm_pred_comb$IPA[bm_pred_comb$model == 'xgb_aft'] <- NA_real_
+
+  bm_pred_comb |>
+    mutate(
+      across(starts_with("time_"),
+             as.numeric)
+    )
+
+}

### 2022-06-06 R/data_load.R

@@ -1,0 +1,850 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param data_source
+
+
+vdv_load <- function(...){
+
+  data("vdv", package = 'randomForestSRC')
+
+  vdv |>
+    rename(status = Censoring,
+           time = Time)
+
+
+}
+veteran_load <- function(...){
+
+  data("veteran", package = 'randomForestSRC')
+  veteran
+
+}
+
+colon_load <- function(outcome){
+
+  data_tmp <- survival::colon |>
+    as_tibble() |>
+    filter(etype == switch(outcome,
+                           'death' = 2,
+                           'recur' = 1))
+
+  data_tmp |>
+    select(-id, -study, -node4, -etype) |>
+    mutate(sex = factor(sex,
+                        levels = c(0,1),
+                        labels = c('female', 'male')),
+           differ = factor(differ,
+                           levels = c(1, 2, 3),
+                           labels = c('well', 'moderate', 'poor')))
+
+}
+
+
+colon_recur_load <- function(...){
+  colon_load(outcome = 'recur')
+}
+
+colon_acm_load <- function(...){
+  colon_load(outcome = 'death')
+}
+
+pbc_orsf_load <- function(...){
+
+  aorsf::pbc_orsf |>
+    select(-id) |>
+    as_tibble()
+
+}
+time_to_million_load <- function(...){
+
+  data("time_to_million", package = 'censored')
+
+  time_to_million |>
+    rename(status = event) |>
+    # dropping text and dates
+    select(-title, -released, -distributor)
+
+}
+gbsg2_load <- function(...){
+
+  data("GBSG2", package = "TH.data")
+
+  GBSG2 |>
+    as_tibble() |>
+    rename(status = cens)
+
+}
+peakV02_load <- function(...){
+
+  data("peakVO2", package = 'randomForestSRC')
+
+  peakVO2 |>
+    rename(time = ttodead, status = died)
+
+
+}
+flchain_load <- function(...){
+
+  survival::flchain |>
+    rename(time = futime, status = death) |>
+    # the chapter variable indicates who died,
+    # not fair to use it as a predictor
+    select(-chapter) |>
+    # 3 died on the same day their sample was collected,
[…]

### 2022-06-06 R/guide_it_build.R

@@ -97,12 +97,25 @@ guide_it_build <- function(){
     ,
     .(
       deidnum,
-      # CV Death or HF Hospitalization
-      status = dthhfadj,
-      # Days from randomization to CV Death or HF Hospitalization
-      time = pmax(1, dhfadjdy)
+      # CV Death
+      status_cvdeath = dthcvadj,
+      time_cvdeath = pmax(1/2, dcvadjdy),
+      # HF Hospitalization
+      status_hfhosp = hoshfadj,
+      time_hfhosp = pmax(1/2, dhfadjdy)
     )
   ]
+
+  # endpt <- fread("data/guide-it/best_endpoints_ads.csv")[
+  #   ,
+  #   .(
+  #     deidnum,
+  #     # CV Death or HF Hospitalization
+  #     status = dthhfadj,
+  #     # Days from randomization to CV Death or HF Hospitalization
+  #     time = pmax(1, dhfadjdy)
+  #   )
+  # ]
 
   out <- list(demog,
               endpt,
@@ -118,5 +131,9 @@ guide_it_build <- function(){
   out[TORSEND != 1 | is.na(TORSEND), TORSEDD := 0]
 
   out[, `:=`(ARB = NULL, ALDOS = NULL, TORSEND = NULL)]
+
+  fwrite(out, file = 'data/guide-it/analysis.csv')
+
+  NULL
 
 }

### 2022-06-06 R/load_data.R

@@ -1,144 +1,0 @@
-#' .. content for \description{} (no empty lines) ..
-#'
-#' .. content for \details{} ..
-#'
-#' @title
-#' @param data_source
-
-
-load_vdv <- function(...){
-
-  data("vdv", package = 'randomForestSRC')
-
-  vdv |>
-    rename(status = Censoring,
-           time = Time)
-
-
-}
-
-load_veteran <- function(...){
-
-  data("veteran", package = 'randomForestSRC')
-  veteran
-
-}
-load_colon <- function(...){
-
-  survival::colon |>
-    select(-id, -study, -node4, -etype) |>
-    mutate(sex = factor(sex,
-                        levels = c(0,1),
-                        labels = c('female', 'male')),
-           differ = factor(differ,
-                           levels = c(1, 2, 3),
-                           labels = c('well', 'moderate', 'poor')))
-
-}
-load_pbc_orsf <- function(...){
-
-  aorsf::pbc_orsf |>
-    select(-id) |>
-    as_tibble()
-
-}
-load_time_to_million <- function(...){
-
-  data("time_to_million", package = 'censored')
-
-  time_to_million |>
-    rename(status = event) |>
-    # dropping text and dates
-    select(-title, -released, -distributor)
-
-}
-load_gbsg2 <- function(...){
-
-  data("GBSG2", package = "TH.data")
-
-  GBSG2 |>
-    as_tibble() |>
-    rename(status = cens)
-
-}
-load_peakV02 <- function(...){
-
-  data("peakVO2", package = 'randomForestSRC')
-
-  peakVO2 |>
-    rename(time = ttodead, status = died)
-
-
-}
-load_flchain <- function(...){
-
-  survival::flchain |>
-    rename(time = futime, status = death) |>
-    # the chapter variable indicates who died,
-    # not fair to use it as a predictor
-    select(-chapter) |>
-    # 3 died on the same day their sample was collected,
-    # let's call that a half day.
-    mutate(time = pmax(time, 1/2))
-
-}
-
-load_nafld <- function(...){
-
-  read_csv('data/nafld.csv')
-
-}
-
-load_rotterdam <- function(...){
-
-  survival::rotterdam |>
-    mutate(time = pmin(rtime, dtime),
-           status = if_else(rtime < dtime, recur, death)) |>
-    select(age, meno, size, grade, nodes, pgr, er, hormon,
[…]

### 2022-06-06 R/load_sprint_ndi.R

@@ -1,255 +1,0 @@
-#' .. content for \description{} (no empty lines) ..
-#'
-#' .. content for \details{} ..
-#'
-#' @title
-
-load_sprint_ndi <- function(outcome) {
-
-  stopifnot(outcome %in% c('acm', 'cvd'))
-
-  data_in <- read_csv("Z:/npajewski/NDI/Data/longterm_death.csv")
-
-  if(outcome == 'acm')
-    data_in$status <- data_in$acm_event
-
-  if(outcome == 'cvd')
-    data_in$status <- as.numeric(data_in$cvd_event_cr == 1)
-
-  data_selected <- data_in |>
-    transmute(
-      time = acm_years,
-      status,
-      intensive,
-      sub_senior,
-      altdevice,
-      hr,
-      unable,
-      stand_sbp,
-      stand_dbp,
-      stand_hr,
-      dizzy,
-      n_agents,
-      ACEINH,
-      ALDORB,
-      ALPBBL,
-      ALPHA,
-      is_bbl,
-      ANG_RB,
-      CENTRL,
-      DHPCCB,
-      DIRVAS,
-      KSPDIU,
-      LOODIU,
-      NDHCCB,
-      NI_BBL,
-      RENINI,
-      THZDIU,
-      n_classes,
-      liveWithOthers,
-      education,
-      fulltime,
-      Work_FulPrt,
-      Insured,
-      drugbene,
-      atrialFib,
-      angina,
-      heartAtt,
-      conHeartFail,
-      irrHeartBeat,
-      ulcer,
-      crohns,
-      diverticulitis,
-      hepatitis,
-      gallbladder,
-      kidinfect,
-      BPH,
-      prostatitis,
-      osteoarthritis,
-      rheArthritis,
-      gout,
-      othArthritis,
-      hipprob,
-      cancer,
-      skinCancer,
-      pvd,
-      seizure,
-      stroke,
-      tia,
-      thyroidDis,
-      anemia,
-      diabetes,
-      hypertens,
-      lowBkPain,
-      cataracts,
-      schizo,
-      depress,
-      bipolar,
-      anxiety,
-      ptsd,
-      alcohol,
-      CVDFamHst,
-      drink_4cat = factor(drink_4cat),
-      smoke_pkyrs,
-      vigactiv,
-      lessvigactiv,
-      aspirin,
-      othmed,
-      egfr,
-      screat,
-      sub_ckd,
-      eGFR_CKDEPI,
-      spanishno,
-      myocardinfarc,
[…]

### 2022-06-06 R/model_key.R

@@ -1,0 +1,40 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+
+make_model_key <- function() {
+
+  tibble(
+    term = c(
+      "aorsf_cph_1",
+      "aorsf_cph_15",
+      "aorsf_random",
+      "aorsf_net",
+      "obliqueRSF",
+      "cif",
+      "cox_net",
+      "coxtime",
+      "xgb_cox",
+      "xgb_aft",
+      "randomForestSRC",
+      "ranger"
+    ),
+    label = c(
+      "aorsf-cph(maxit = 1)",
+      "aorsf-cph(maxit = 15)",
+      "aorsf-random",
+      "aorsf-net",
+      "obliqueRSF-net",
+      "party-cif",
+      "glmnet-cox",
+      "nn-cox",
+      "xgboost-cox",
+      "xgboost-aft",
+      "rfsrc-standard",
+      "ranger-extratrees"
+    ),
+  )
+
+}

### 2022-06-06 _targets.R

@@ -1,10 +1,12 @@
 ## Load your packages, e.g. library(targets).
-source("./packages.R")
+
+suppressMessages(source("./packages.R"))
 
 library(future)
 library(future.callr)
 plan(callr)
 
+tar_config_set(reporter_make = 'verbose')
 
 # conda config --set ssl_verify no to install pycox packs
 
@@ -12,83 +14,53 @@ plan(callr)
 lapply(list.files("./R", full.names = TRUE), base::source)
 
 model_fitters <- c(
-  'aorsf_1',
-  'aorsf_15',
+  'aorsf_cph_1',
+  'aorsf_cph_15',
+  "aorsf_random",
   'aorsf_net',
   'cif',
+  'cox_net',
   # 'coxtime',
-  # 'obliqueRSF',
-  # 'xgboost',
+  'obliqueRSF',
+  'xgb_cox',
+  'xgb_aft',
   'randomForestSRC',
   'ranger'
 )
 
 analyses_real <- expand_grid(
   data_source = c(
-    "vdv",
     "veteran",
-    "colon",
+    "colon_recur",
+    "colon_acm",
     "pbc_orsf",
     'time_to_million',
     'gbsg2',
-    # 'peakV02',
-    # 'flchain',
-    # 'nafld',
-    "rotterdam",
-    "actg",
-    "guide_it",
-    "breast"
-    # "sprint_cvd",
-    # "sprint_acm"
+    'peakV02',
+    'flchain',
+    'nafld',
+    "rotterdam_recur",
+    "rotterdam_acm",
+    "actg_aids",
+    "actg_death",
+    "guide_it_cvd",
+    "guide_it_hfhosp",
+    "breast",
+    "sprint_cvd",
+    "sprint_acm",
+    "phts",
+    "follic_death",
+    "follic_relapse",
+    "mgus2_death",
+    "mgus2_pcm"
   ),
   model_type = model_fitters,
-  run_seed = 1:3
+  run_seed = 1:50
 ) |>
   mutate(
-    data_load_fun = case_when(
-      data_source == "vdv"             ~ syms("load_vdv"),
-      data_source == "veteran"         ~ syms("load_veteran"),
-      data_source == "colon"           ~ syms("load_colon"),
-      data_source == "pbc_orsf"        ~ syms("load_pbc_orsf"),
-      data_source == "time_to_million" ~ syms("load_time_to_million"),
-      data_source == "gbsg2"           ~ syms("load_gbsg2"),
[…]

### 2022-06-06 packages.R

@@ -6,10 +6,10 @@ library(tarchetypes)
 
 library(aorsf)
 library(survival)
+library(scales)
 library(survivalmodels)
 library(obliqueRSF)
 library(xgboost)
-library(xgboost.surv)
 library(tidyverse)
 library(recipes)
 library(rms)
@@ -17,15 +17,19 @@ library(riskRegression)
 library(ranger)
 library(randomForestSRC)
 library(table.glue)
-library(gt)
 library(simsurv)
+library(glmnet)
+library(glue)
 library(yardstick)
 library(data.table)
 library(mltools)
 library(party)
+library(c060)
+library(RColorBrewer)
+library(rmarkdown)
 
-conflict_prefer("filter", "dplyr")
-conflict_prefer("slice", "dplyr")
-conflict_prefer("summarize", "dplyr")
-conflict_prefer("Predict", "modeltools")
+library(tidybayes)
+library(rstan)
+library(rstanarm)
 
+source("./conflicts.R")

### 2022-06-07 paper/jmlr/main.Rnw
test sims; success without cats

@@
 Risk prediction can reduce the burden of disease by educating patients and providers and guiding strategies to prevent and treat disease in a wide range of medical domains \citep{moons2012riskI, moons2012riskII}.
-The random survival forest (RSF), a supervised learning algorithm that can engage with censored outcomes, is frequently used for risk prediction.
-Notable characteristics of the RSF include uniform convergence of its ensemble survival function to the true population survival function when the predictor space is discrete.
+The random survival forest (RSF; \citet{ishwaran2008random}), a supervised learning algorithm that can engage with censored outcomes, is frequently used for risk prediction.
+Notable characteristics of the RSF include uniform convergence of its ensemble survival function to the true population survival function when the predictor space is discrete \citep{ishwaran2010consistency}.
 In addition, software implementing the RSF is freely available, extremely efficient, and full of tools to interpret and explain the RSF.

### 2022-06-07 R/sim_surv.R

@@ -15,10 +15,6 @@ sim_surv <- function(n_obs = 2500,
                      correlated_x = 0,
                      pred_horiz = 2.5) {
 
-  stopifnot(n_x > 0)
-  # stopifnot(n_z > 0)
-  # stopifnot(n_v >= 3)
-
   stopifnot(n_x >= n_g)
 
   # z = junk variables
@@ -37,7 +33,9 @@ sim_surv <- function(n_obs = 2500,
   # categorical (not used at the moment)
   c_names <- paste0('c', seq(n_c))
 
-  .names <- c(x_names)
+  .names <- c()
+
+  if(n_x > 0) .names <- c(.names, x_names)
 
   if(n_z > 0) .names <- c(.names, z_names)
 
@@ -126,6 +124,27 @@ sim_surv <- function(n_obs = 2500,
     }
 
   }
+
+  # if(n_w > 0){
+  #
+  #   degrees <- round(seq(3, 6, length.out = n_w))
+  #
+  #   for( i in seq(n_w) ){
+  #
+  #     w_name <- paste0("w", i)
+  #     nl_names <- paste('nl', i, seq(degrees[i]), sep = '_')
+  #
+  #     poly_cols <- seq(degrees[i]) |>
+  #       map(~ covs[[w_name]]^.x) |>
+  #       reduce(.f = cbind)
+  #
+  #     colnames(poly_cols) <- nl_names
+  #
+  #     covs <- cbind(covs, poly_cols)
+  #
+  #   }
+  #
+  # }
 
   # linear combination variables ----
 
@@ -237,7 +256,12 @@ sim_surv <- function(n_obs = 2500,
     vars_junk = setdiff(names(covs)[keep], vars_signal),
     vars_interaction = vars_interaction,
     vars_lc = vars_lc,
-    coefs_lc = coefs_lc
+    coefs_lc = coefs_lc,
+    effect_x = x_effect,
+    effect_int = int_effect,
+    effect_nl = nl_effect,
+    effect_lc = lc_effect,
+    effect_c = c_effect
   )
 
 

### 2022-06-11 docs/index.Rmd
slides first draft

---
title: "Accelerated oblique random survival forests"
author: "Byron C. Jaeger"
date: Last updated `r Sys.Date()`
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class: center, middle
background-image: url("img/meme_slow_R.jpg")
background-size: contain

```{r setup, include=FALSE}

options(htmltools.dir.version = FALSE)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 600,
  fig.align='center',
  fig.height=5
)

library(tidyverse)
library(ggforce)
library(rpart)
library(rpart.plot)
library(party)
library(parttree)
library(palmerpenguins)
library(gt)
library(table.glue)
library(xaringanExtra)

# infinite moon reader doesn't like targets,
# this commented code sets up files that work for infinite moon reader
# tar_load(
#   names = c(
#     bm_pred_model_viz,
#     bm_pred_time_viz,
#     bm_pred_viz,
#     data_key
#   )
# )
# 
# write_rds(bm_pred_model_viz, "docs/index_files/bm_pred_model_viz.rds")
# write_rds(bm_pred_time_viz, "docs/index_files/bm_pred_time_viz.rds")
# write_rds(bm_pred_viz, "docs/index_files/bm_pred_viz.rds")
# write_rds(data_key, "docs/index_files/data_key.rds")

bm_pred_model_viz <- read_rds('index_files/bm_pred_model_viz.rds')
bm_pred_time_viz <- read_rds('index_files/bm_pred_time_viz.rds')
bm_pred_viz <- read_rds('index_files/bm_pred_viz.rds')
data_key <- read_rds('index_files/data_key.rds')

```

```{css texts}

.medium { font-size: 25px; }
.mediumer { font-size: 40px; }
.large { font-size: 80px; }
.larger { font-size: 160px; }
.huge { font-size: 240px; }

.rainbow-text {
  background-image: linear-gradient(to left, violet, indigo, blue, green, yellow, orange, red);   -webkit-background-clip: text;
  color: transparent;
}

```

---

## Overview

- Random forests (axis based and oblique)

    + Decision trees

    + Random survival forests (RSF)

- Accelerating the oblique RSF

    + Newton Raphson scoring

- Benchmark

    + Datasets & learners

    + Evaluation

    + Results

- Software

    + R package & website

---
class: center, middle, inverse

# .larger[Random forests] 
## (axis based and oblique)

---
background-image: url(img/penguins.png)
background-size: 45%
background-position: 85% 72.5%

## Decision trees

- Frequently used in supervised learning.

- Partitions the space of predictor variables.

- Can be used for classification, regression, and survival analysis.

##

.pull-left[
.medium[_Demo_:] <br><br> Axis-based and oblique decision trees for classification of penguin species (chinstrap, gentoo, or adelie) based on bill and flipper length.<sup>1</sup>
]

.footnote[
<sup>1</sup>Data were collected and made available by [Dr. Kristen Gorman](https://www.uaf.edu/cfos/people/faculty/detail/kristen-gorman.php) and the [Palmer Station](https://pal.lternet.edu/), a member of the [Long Term Ecological Research Network](https://lternet.edu/).
]

---

Dimensions for Adelie, Chinstrap and Gentoo Penguins at Palmer Station

```{r fig_penguins_nopart}

penguins <- drop_na(penguins)

ggplot(data = penguins) +
  aes(x = flipper_length_mm, y = bill_length_mm, label = species) +
  geom_point(aes(color = species, shape = species),
             size = 3,
             alpha = 0.8) +
  geom_mark_ellipse(aes(color = species, fill = species), alpha = 0.075) +
  theme_minimal() +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  scale_fill_manual(values = c("darkorange","purple","cyan4")) +
  labs(x = "\nFlipper length, mm",
       y = "Bill length, mm\n",
       color = "Penguin species",
       shape = "Penguin species") +
  coord_cartesian(ylim = c(30, 70),
                  xlim = c(170, 235)) +
  theme(panel.grid = element_blank(),
        legend.position = '')

```

---

Partition all the penguins into flipper length < 207 or ≥ 207 mm

```{r fig_penguins_part1}

mdl_tree <- rpart(
 formula = species ~ flipper_length_mm + bill_length_mm,
 data = penguins, 
 control = rpart.control(maxdepth = 1)
)

ggplot(data = penguins) +
  aes(x = flipper_length_mm, y = bill_length_mm, label = species) +
  geom_point(aes(color = species, shape = species),
             size = 3,
             alpha = 0.8) +
  geom_parttree(data = mdl_tree, aes(fill=species), alpha = 0.1) +
  theme_minimal() +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  scale_fill_manual(values = c("darkorange","purple","cyan4")) +
  labs(x = "\nFlipper length, mm",
       y = "Bill length, mm\n",
       color = "Penguin species",
       shape = "Penguin species") +
  coord_cartesian(ylim = c(30, 70),
                  xlim = c(170, 235)) +
  scale_x_continuous(expand = c(0,0), breaks = c(180, 200, 220)) + 
  scale_y_continuous(expand = c(0,0)) +
  theme(panel.grid = element_blank(),
        legend.position = '')

```

---

Partition penguins on the left side into into bill length < 43 or ≥ 43 mm

```{r fig_penguins_part2}

mdl_tree <- rpart(
 formula = species ~ flipper_length_mm + bill_length_mm,
 data = penguins, 
 control = rpart.control(maxdepth = 2)
)

ggplot(data = penguins) +
  aes(x = flipper_length_mm, y = bill_length_mm, label = species) +
  geom_point(aes(color = species, shape = species),
             size = 3,
             alpha = 0.8) +
  geom_parttree(data = mdl_tree, aes(fill=species), alpha = 0.1) +
  theme_minimal() +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  scale_fill_manual(values = c("darkorange","purple","cyan4")) +
  labs(x = "\nFlipper length, mm",
       y = "Bill length, mm\n",
       color = "Penguin species",
       shape = "Penguin species") +
  coord_cartesian(ylim = c(30, 70),
                  xlim = c(170, 235)) +
  scale_x_continuous(expand = c(0,0), breaks = c(180, 200, 220)) + 
  scale_y_continuous(expand = c(0,0)) +
  theme(panel.grid = element_blank(),
        legend.position = '')

# ---
# background-image: url(img/penguins_logo.png)
# background-position: 95% 5%
# background-size: 110px 120px
# layout: true

```

---

With oblique splits, partitions do not need to be rectangles

```{r fig_penguins_part2_oblique}

x_delta <- 206.5 - 170
y_delta <- 46 - 40

slope <- y_delta / x_delta
intercept <- 46 - 206.5 * slope

text_lower <-
  table_glue("bill length - {slope} * flipper length < {intercept}")
text_upper <-
  table_glue("bill length - {slope} * flipper length \u2265 {intercept}")

data_poly <- tribble(
  ~flipper_length_mm, ~bill_length_mm    , ~species,
  170               ,  30                , 'Adelie',
  206.5             ,  30                , 'Adelie',
  206.5             ,  46                , 'Adelie',
  170               ,  40                , 'Adelie',
  170               ,  40                , 'Chinstrap',
  206.5             ,  46                , 'Chinstrap',
  206.5             ,  70                , 'Chinstrap',
  170               ,  70                , 'Chinstrap',
  206.5             ,  30                , 'Gentoo',
  235               ,  30                , 'Gentoo',
  235               ,  70                , 'Gentoo',
  206.5             ,  70                , 'Gentoo',
)

ggplot(data = penguins) +
  aes(x = flipper_length_mm, y = bill_length_mm, label = species) +
  geom_polygon(data = data_poly, 
               aes(fill = species, group = species),
               alpha = 0.1,
               col = 'black') +
  geom_point(aes(color = species, shape = species),
             size = 3,
             alpha = 0.8) +
  # geom_abline(slope = slope, intercept = intercept, col = 'red')
  geom_text(
    data = tibble(flipper_length_mm = c(172, 172), 
                  bill_length_mm = c(68, 32), 
                  species = c(text_upper, text_lower)),
    hjust = 0
  ) + 
  theme_minimal() +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  scale_fill_manual(values = c("darkorange","purple","cyan4")) +
  labs(x = "\nFlipper length, mm",
       y = "Bill length, mm\n",
       color = "Penguin species",
       shape = "Penguin species") +
  coord_cartesian(ylim = c(30, 70),
                  xlim = c(170, 235)) +
  scale_x_continuous(expand = c(0,0), breaks = c(180, 200, 220)) + 
  scale_y_continuous(expand = c(0,0)) +
  theme(panel.grid = element_blank(),
        legend.position = '')

```

---

## Random survival forests (RSFs)

1. Breiman developed the random forest, a large set of decision trees injected with randomness.<sup>1, 2</sup>

.footnote[<sup>1</sup>Breiman, Leo. "Bagging predictors." Machine learning 24.2 (1996): 123-140.<br/><sup>2</sup>Breiman, Leo. "Random forests." Machine learning 45.1 (2001): 5-32.]

---

## Random survival forests (RSFs)

1. Breiman developed the random forest, a large set of decision trees injected with randomness.<sup>1, 2</sup>

1. Hothorn and, separately, Ishwaran developed extensions of the random forest for survival outcomes.<sup>3, 4</sup>

Specifically,

- Hothorn developed the conditional inference forest (CIF)

- Ishwaran developed the random survival forest (RSF)

.footnote[<sup>3</sup>Hothorn, Torsten, et al. "Unbiased recursive partitioning: A conditional inference framework." Journal of Computational and Graphical statistics 15.3 (2006): 651-674.<br/><sup>4</sup> Ishwaran, Hemant, et al. "Random survival forests." Annals of Applied Statistics 2.3 (2008): 841-860.]

---

Each leaf in the RSF contains a Kaplan-Meier estimate of survival. In the CIF, weights are applied based on sample size.

```{r}

penguins_sim <- penguins %>%
  mutate(
    time_mean = if_else(
      bill_length_mm < 40,
      true = 80,
      false = 20
    ),
    time = rnorm(n = n(), mean = time_mean, sd = 20),
    time = pmax(time, 1),
    status = rbinom(n = n(), size = 1, prob = 0.75)
  )

# png(res = 300,
#     width = 6,
#     height = 3.75,
#     units = 'in',
#     filename = 'rpart_plot_surv.png')

mdl_ctree <-
  ctree(formula = Surv(time, status) ~ bill_length_mm,
        data = penguins_sim,
        controls = ctree_control(maxdepth = 1))

plot(
  mdl_ctree,
  inner_panel = node_inner(mdl_ctree, pval = FALSE)
)

```

---

## Random survival forests (RSFs)

1. Breiman developed the random forest, a large set of decision trees injected with randomness.<sup>1, 2</sup>

1. Hothorn and, separately, Ishwaran developed extensions of the random forest to engage with survival outcomes (CIF and RSF).<sup>3, 4</sup>

1. Zhou developed a rotation survival forest and Wang developed a survival forest with an extended predictor space.<sup>5, 6</sup>

Both Zhou and Wang's extensions were based on the CIF

.footnote[<sup>5</sup>Zhou L, et al. "Rotation survival forest for right censored data." PeerJ. 2015 Jun 11;3:e1009.<br/><sup>6</sup> Wang H, et al. "Random survival forest with space extensions for censored data." Artif Intell Med. 2017 Jun;79:52-61.]

---

## Random survival forests (RSFs)

1. Breiman developed the random forest, a large set of decision trees injected with randomness.<sup>1, 2</sup>

1. Hothorn and, separately, Ishwaran developed extensions of the random forest to engage with survival outcomes (CIF and RSF).<sup>3, 4</sup>

1. Zhou developed a rotation survival forest and Wang developed a survival forest with an extended predictor based on the CIF.<sup>5, 6</sup>

1. Jaeger developed the oblique RSF, which used penalized regression to find oblique splits.<sup>7</sup>

.footnote[<sup>7</sup>Jaeger BC, et al. "Oblique random survival forests." The Annals of Applied Statistics 13.3 (2019): 1847-1883.]

---
class: center, middle, inverse

# .larger[Accelerating the oblique RSF]

---

## Accelerating the oblique RSF

Consider the usual framework for survival analysis:
$$\mathcal{D}_{\text{train}} = \left\{ (T_i, \delta_i, x_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$
- $T_i$ is the event time if $\delta_i=1$ and last point of contact if $\delta_i=0$,

- $x_i$ is a vector of predictors values.

Let $t_1 < \, \ldots \, < t_m$ denote the $m$ unique event times in $\mathcal{D}_{\text{train}}$

---

## Accelerating the oblique RSF

We identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model: $$L(\beta) = \prod_{i=1}^m \frac{e^{x_{j(i)}^T \beta}}{\sum_{j \in R_i} e^{x_j^T \beta}}$$

- $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (i.e., those still at risk at time $t_i$)

- $j(i)$ is the index of the observation for which an event occurred at time $t_i$.

---

## Newton Raphson scoring

Estimated regression coefficients $\hat{\beta}$ are updated in each step based on their first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
$$\hat{\beta}^{k+1} =  \hat{\beta}^{k} + U(\hat{\beta} = \hat{\beta}^{k})\, H^{-1}(\hat{\beta} = \hat{\beta}^{k})$$

For statistical inference, iterate until a convergence threshold is met.

For identifying linear combination of predictors in the oblique RSF, .mediumer[🤷]

- `aorsf-fast` completes one iteration.

- `aorsf-cph` iterates until convergence or 15 iterations.

---
class: center, middle, inverse

# .larger[Benchmark]

---

## Learners

__Oblique RSFs__:

- _aorsf-fast_: the fast version of aorsf

- _aorsf-cph_: the less fast but still pretty fast version of aorsf

- _aorsf-random_: randomized coefficients (Breiman's idea)

- _aorsf-net_: aorsf's copy of obliqueRSF

- _obliqueRSF-net_: oblique RSF using penalized cox regression (the original)

---

## Learners

__Oblique RSFs__:

- .rainbow-text[_aorsf-fast_]: the fast version of aorsf

- _aorsf-cph_: the less fast but still pretty fast version of aorsf

- _aorsf-random_: randomized coefficients (Breiman's idea)

- _aorsf-net_: aorsf's copy of obliqueRSF

- _obliqueRSF-net_: oblique RSF using penalized cox regression (the original)

---

## Learners

__Axis based RSFs__:

- _cif-standard_: standard CIF

- _cif-extension_: CIF with space extension

- _cif-rotate_: CIF with rotation

- _rsf-standard_: standard RSF

- _ranger-extratrees_: RSF with extremely randomized trees

---

## Learners

__Other__:

- _glmnet-cox_: Penalized Cox regression model

- _nn-cox_: Cox neural network with time-varying effects

- _xgboost-cox_: Boosted trees fitted to Cox log likelihood

- _xgboost-aft_: Boosted trees fitted to accelerated failure time.

---

## Data sets

A total of 23 risk prediction tasks in 16 data sets were analyzed.

This table is continued on the next 2 slides.

```{r}

tbls <- data_key |> 
  select(label, outcome, nrow, ncol, nevent, pcens, pmiss, pctns) |> 
  mutate(
    across(starts_with('p'),  ~.x * 100),
    across(where(is.numeric), .fns = table_value),
    outcome = Hmisc::capitalize(outcome)
  ) |> 
  arrange(label) |> 
  mutate(grp = seq(n()),
         grp = case_when(
           grp > 2 * n()/3 ~ 3, 
           grp > 1 * n()/3 ~ 2,
           TRUE ~ 1
         )) |> 
  group_by(grp) |> 
  group_map(
    ~ .x |> 
      gt(rowname_col = 'label') |> 
      cols_label(
        outcome = 'Outcome',
        nrow = 'N Obs',
        ncol = 'N Predictors',
        nevent = 'N Events',
        pcens = '% Censored',
        pmiss = '% Missing',
        pctns = "% Continuous"
      ) |> 
      cols_align(align = 'center') |> 
      cols_align(align = 'left', columns = 'outcome')
  )

tbls[[1]]

```

---
## Data sets contd.

```{r}

tbls[[2]]

```

---

## Data sets contd.

```{r}

tbls[[3]]

```

---

## Evaluation

Consider a testing data set:
$$\mathcal{D}_{\text{test}} = \left\{ (T_i, \delta_i, x_{i}) \right\}_{i=1}^{N_{\text{test}}}.$$
Let $\widehat{S}(t \mid x_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$. 
The Brier score at time $t$ is $$\widehat{\text{BS}}(t) = \frac{1}{N_{\text{test}}} \sum_{i=1}^{N_{\text{test}}} \left\{ \widehat{S}(t \mid x_i)^2 \cdot I(T_i \leq t, \delta_i = 1) \cdot \widehat{G}(T_i)^{-1} + \\ [1-\widehat{S}(t \mid x_i)]^2 \cdot I(T_i > t) \cdot \widehat{G}(t)^{-1}\right\}$$

where $\widehat{G}(\cdot)$ is the Kaplan-Meier estimate of the censoring distribution.

---

## Evaluation

As the Brier score is time dependent, integration over time provides a summary measure of performance over a range of plausible prediction horizons. The integrated Brier score is defined as

$$\mathcal{\widehat{BS}}(t_a, t_b) = \frac{1}{t_b - t_a}\int_{t_a}^{t_b} \widehat{\text{BS}}(t) dt.$$ 
In our results

- $t_a$ is the 25th percentile of event times

- $t_b$ is the 75th percentile of event times

---

## Evaluation

$\mathcal{\widehat{BS}}(t_a, t_b)$, a sum of squared prediction errors, can be scaled to produce a measure of explained residual variation (i.e., an $R^2$ statistic) by computing $$R^2 = 1 - \frac{\mathcal{\widehat{BS}}(t_a, t_b)}{\mathcal{\widehat{BS}}_0(t_a, t_b)}$$ where $\mathcal{\widehat{BS}}_0(t_a, t_b)$ is the integrated Brier score when a Kaplan-Meier estimate for survival based on the training data is used as the survival prediction function $\widehat{S}(t)$.

_Jargon_: $R^2$ = __index of prediction accuracy__ (IPA)

_Presentation_: We scale the IPA by 100 to avoid unnecessary leading zero's.

---

## Evaluation

Step 1: Collect IPA values from ten 50/50 train/test splits on each data set for each learner.

Step 2: Fit a hierarchical Bayesian model to analyze posterior expected IPA values for each learner:

$$\text{IPA} = \widehat{\gamma} \cdot \text{model} + (1\,|\, \text{data/run})$$

where `run` refers to the specific train/test split of `data`.

---

```{r bm_pred_viz_ibs, fig.height=9, fig.width=11}
bm_pred_viz$ibs_scaled
```

---

```{r bm_pred_viz_cstat, fig.height=9, fig.width=11}
bm_pred_viz$cstat
```

---

```{r bm_pred_model_viz_ibs, fig.height=6.9, fig.width=9}
bm_pred_model_viz$ibs_scaled
```

---

```{r bm_pred_model_viz_cstat, fig.height=6.9, fig.width=9}
bm_pred_model_viz$cstat
```

---

```{r bm_pred_time_viz, fig.height=6.5, fig.width=8}
bm_pred_time_viz
```

---

## Using the accelerated oblique RSF

```{r out.width='100%'}

knitr::include_url("https://bcjaeger.github.io/aorsf/")

```

---

# Thank you!

### 2022-06-11 paper/jmlr/main.Rnw
slides first draft

@@
 
-Risk prediction can reduce the burden of disease by educating patients and providers and guiding strategies to prevent and treat disease in a wide range of medical domains \citep{moons2012riskI, moons2012riskII}.
-The random survival forest (RSF; \citet{ishwaran2008random}), a supervised learning algorithm that can engage with censored outcomes, is frequently used for risk prediction.
+Risk prediction can reduce the burden of disease by educating patients and providers and guiding strategies to prevent and treat disease in a wide range of medical domains \citep{moons2012riskII, moons2012riskI}.
+The random survival forest (RSF), a supervised learning algorithm that can engage with censored outcomes, is frequently used for risk prediction.
 Notable characteristics of the RSF include uniform convergence of its ensemble survival function to the true population survival function when the predictor space is discrete \citep{ishwaran2010consistency}.
-In addition, software implementing the RSF is freely available, extremely efficient, and full of tools to interpret and explain the RSF.
+In addition, software implementing the RSF is freely available, extremely efficient, and full of tools to interpret and explain the RSF \citep{randomForestSRC, ranger, hothorn2010party}.
 However, there remains considerable potential to improve the RSF in risk prediction tasks where training samples are not large enough to guarantee asymptotic properties or predictor spaces are non-discrete (\ie, predictors are continuous).
@@
 While axis based decision boundaries are always perpendicular to the axis of the relevant predictor, linear combinations of predictors create oblique decision boundaries that are neither parallel nor perpendicular to axes of their contributing predictors.
-Prior work has found the oblique RSF has higher prediction accuracy than the axis based RSF in general benchmarks \citep{jaeger2019oblique} and that oblique splitting is particularly effective when predictor spaces are non-discrete.
-However, existing methods to implement oblique RSFs use fully trained models in each non-leaf node to identify linear combinations of predictors, exponentially increasing the number of operations required for the oblique RSF versus its axis based counterpart.
-In addition, standard methods to estimate the importance of individual variables in the RSF are less effective in the oblique RSF.
+Prior work has found the oblique RSF has higher prediction accuracy than the axis based RSF in general benchmarks \citep{jaeger2019oblique} and that oblique splitting is particularly effective when predictors are continuous \citep{menze2011oblique}.
+However, existing methods to implement oblique splitting typically use fully trained models in each non-leaf node to identify linear combinations of predictors, exponentially increasing the number of operations required for the oblique RSF versus its axis based counterpart.
+In addition, standard methods to estimate variable importance (VI) in the RSF are less effective in the oblique RSF, and few methods have been introduced to estimate VI specifically for the oblique RSF.
 
-In this article, we introduce methods to increase computational efficiency and estimate variable importance (VI) for oblique RSFs.
-We evaluate computational efficiency, prediction accuracy, and the ability to discriminate between signal and noise variables using the proposed methods compared to standard and state-of-the-art methods.
-To accomplish these goals, we analyze 23 distinct risk prediction tasks from real data and conduct a simulation study.
-All methods introduced in this article for oblique RSFs are available in the \texttt{aorsf} R Package.
+The aim of this article is to improve the computational efficiency and interpretability of the oblique RSF.
+In a general benchmark experiment including YYYY risk prediction tasks, we show that oblique RSFs with partially trained models have equivalent or superior prediction accuracy and are orders of magnitude more efficient than oblique RSFs with fully trained models in non-leaf nodes.
+We introduce a method to estimate VI for oblique RSFs and compare its ability to discriminate between signal and noise variables versus standard and state-of-the-art methods.
+All methods proposed in this article are available in the \texttt{aorsf} R Package.
 
@@
 
-\citet{breiman2001random} introduced the axis-based random forest (RF) and the oblique RF (oRF).
-Axis based RFs recursively split data using a single predictor at each non-leaf node in decision trees, whereas oRFs use multiple predictors in linear combination.
-The splits are called `oblique' because linear combinations of predictors create decision boundaries that are neither parallel nor perpendicular to their axes have higher prediction accuracy in external data compared to their axis based counterparts.
-Several studies investigating RFs for classification and regression have noted that oblique RFs have lower generalization than their axis-based counterparts.
+\subsection{Axis-based and oblique random forests}
 
-The axis-based RF proposed in \citet{breiman2001random} was extended to survival outcomes by \citet{ishwaran2008random} and the oblique RF  la soon after RFs for classification and regression were developed by \citet{breiman2001random}, and oblique RFs for survival were Several studies have shown that oblique recursive partitioning improves the generalization error of RFs for classification and regression, b
+After \citet{breiman2001random} introduced the axis-based and oblique random forest (RF), numerous methods were developed to grow oblique RFs for classification or regression tasks \citep{menze2011oblique, zhang2014oblique, rainforth2015canonical, zhu2015reinforcement, poona2016investigating, qiu2017oblique, tomita2020sparse, katuwal2020heterogeneous}.
+However, oblique splitting approaches for classification or regression may not generalize to survival tasks \citep[\eg, see][Section~4.5.1]{zhu2013tree}, and most research involving the RSF has focused on forests with axis-based trees \citep{wang2017selective}.
 
-% More recently, \citet{jaeger2019oblique} showed that the generalization error of RFs for survival outcomes improves when multiple predictors are used in linear combination instead of a single predictor to split non-leaf nodes in trees, similar to RFs for classification and regression \citet{breiman2001random}.
-Splitting data with a single predictor creates a decision boundary that is perpendicular to its axis, whereas the decision boundary formed by a linear combination of predictors is neither perpendicular nor parallel to their respective axes.
+Building on prior research for bagging survival trees \citep{hothorn2004bagging}, \citet{hothorn2006unbiased} developed an axis-based RSF in their framework for unbiased recursive partitioning, more commonly referred to as the conditional inference forest (CIF).
+\citet{zhou2016random} developed a rotation forest based on the CIF and \citet{wang2017random} developed a method for extending the predictor space of the CIF.
+\citet{ishwaran2008random} developed an axis-based RSF with strict adherence to the rules for growing trees proposed in \citet{breiman2001random}.
+\citet{jaeger2019oblique} developed the oblique RSF following the bootstrapping approach described in Breiman's original RF and incorporating early stopping rules from the CIF.
 
-% \citet{breiman2001random} introduced the axis-based random forest (RF) and oblique RF.
-Axis based RFs recursively split data using a single predictor at each non-leaf node in decision trees, whereas oRFs use multiple predictors in linear combination.
-The splits are called `oblique' because linear combinations of predictors create decision boundaries that are neither parallel nor perpendicular to their axes have higher prediction accuracy in external data compared to their axis based counterparts.
-However, many oRFs require a fully trained model to be embedded in each non-leaf node to identify linear combinations of predictors, exponentially increasing the number of operations required for fitting an oRF versus an axis based RF.
-In addition, standard methods to interpret RFs (\eg, permutation importance) are less effective when used to interpret the oRF because they are not designed to engage with oblique trees.
+\subsection{Variable importance}
 
-Several supervised learning algorithms can develop prediction functions for right-censored time-to-event outcomes, henceforth referred to as survival outcomes.
+\citet{breiman2001random} introduced permutation VI, defined for each predictor as the difference in a RF's estimated generalization error before versus after the predictor's values are randomly permuted.
+\citet{strobl2007bias} identified bias in permutation VI driven by variable selection bias and effects induced by bootstrap sampling, and proposed an unbiased permutation VI based on unbiased recursive partitioning (see \citet{hothorn2006unbiased}).
+\citet{menze2011oblique} introduced an approach to estimate VI for oblique RFs that computes an analysis of variance (ANOVA) table in non-leaf nodes to obtain p-values for each predictor contributing to the node.
+The ANOVA VI\footnote{\citet{menze2011oblique} name their method `oblique RF VI', but we use the name `ANOVA VI' in this article to avoid confusing Menze's approach with other approaches to estimate VI for oblique RFs.} is then defined for each predictor as the number of times a p-value associated with the predictor is $\leq 0.01$ while growing a forest.
+\citet{lundberg2017unified} introduced a method to estimate VI using SHapley Additive exPlanation (SHAP) values, which estimate the contribution of a predictor to a model's prediction for a given observation.
+SHAP VI is computed for each predictor by taking the mean absolute value of SHAP values for that predictor across all observations in a given set.
+
+% Several supervised learning algorithms can develop prediction functions for right-censored time-to-event outcomes, henceforth referred to as survival outcomes.
 \cite{ishwaran2008random} developed the RF for survival, an extension of the RF for regression and classification developed by \citet{breiman2001random}.
@@
 
-\citet{zhu2015reinforcement}
-
-\citet{zhu2013tree}
-
-\citet{menze2011oblique} introduced an oblique RF (oRF) for classification that utilizes fully trained models at non-leaf nodes to identify linear combinations of predictors.
-\citet{tomita2020sparse} introduced sparse projections for oRFs for classification.
-\citet{katuwal2020heterogeneous} developed a heterogeneous oRF for classification that applies several linear classifiers at each non-leaf node.
-Compared to classification, fewer studies have developed oRFs for survival.
-\citet{jaeger2019oblique} introduced an oRF for survival that applies penalized regression at each non-leaf node and disseminated algorithms to fit the oRF for survival in the \texttt{obliqueRSF} R package \citep{obliqueRSF}.
-
-Variable importance (VI) for oRFs VI has been estimated for oRFs using analysis of variance (ANOVA),6 but this only applies in the rare case where p-values are calculable for coefficients in linear combinations.
-Permutation importance is used to estimate VI in RFs,14 but is not ideal for oRFs because it does not account for the coefficients used in linear combinations.
-Shapley VI, a method based in game theory,15 has excellent asymptotic properties for interpretation,16,17 but is computationally infeasible and can only be approximated efficiently for standard decision trees.18
-
 \section{Novel techniques for oblique random survival forests}
@@
 
+Consider the usual framework for survival analysis with training data $$\dataset_{\text{train}} = \left\{ (T_i, \delta_i, \bm{x}_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$ Here, $T_i$ is the event time if $\delta_i=1$ and last point of contact if $\delta_i=0$, and $\bm{x}_i$ is a vector of predictors values.
+Assuming there are no ties, let $t_1 < \, \ldots \, < t_m$ denote the $m$ unique event times in $\dataset_{\text{train}}$.
+We propose to identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model:
+\begin{equation}\label{eqn:cox-partial-likelihood}
+L(\bm\beta) = \prod_{i=1}^m \frac{e^{\bm{x}_{j(i)}^T \bm\beta}}{\sum_{j \in R_i} e^{\bm{x}_j^T \bm\beta}},
+\end{equation}
+where $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (i.e., those still at risk at time $t_i$), and $j(i)$ is the index of the observation for which an event occurred at time $t_i$.
+The \texttt{survival} package includes documentation that outlines how to complete this estimation procedure efficiently \citep[see][exact.nw]{therneau_survival_2022}.
+Briefly, a vector of estimated regression coefficients, $\hat{\beta}$, is updated in each step of the procedure based on its first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
+$$ \hat{\beta}^{k+1} =  \hat{\beta}^{k} + U(\hat{\beta} = \hat{\beta}^{k})\, H^{-1}(\hat{\beta} = \hat{\beta}^{k}) $$
+It is vital to cycle through iterations until a convergence threshold is met for statistical inference, but it is only necessary to complete one iteration to identify coefficients for a linear combination of predictors.
+\citet{jaeger2019oblique} identified linear combinations using penalized regression models, which supply more flexible solutions for $\hat{\beta}$ at the cost of greater computational demand.
+
 \subsection{Negation variable importance}
 
-We propose a new VI method, ``negation importance",  that can be used for any oRF and accounts for the coefficients in linear combinations.
+Negation VI is similar to permutation VI in that it measures how much a model’s prediction error increases when a variable’s role in the model is de-stabilized.
+More specifically, negation VI measures the increase in an oblique RF's prediction error after flipping the sign of all coefficients linked to a variable (\ie, negating them).
+As the magnitude of a coefficient increases, so does the probability that negating it will change the oblique RF's predictions.
+Since the coefficients in each non-leaf node of an oblique RFs are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
+Although the current article focuses on oblique RSFs, negation VI can be applied to any oblique RF.
 
@@
 
-In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks (Table \ref{table:learners}).
-For random forest learners, the number of observations required in terminal nodes was fixed at 10, the number of randomly selected predictors was the nearest integer to the square root of the total number of predictors, and the number of trees in the ensemble was 500.
+In the current study, we consider four classes of learners: RFs, boosting ensembles, regression models, and neural networks (Table \ref{table:learners}).
+For RF learners, the number of observations required in terminal nodes was fixed at 10, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500.
+For boosting and regression learners, nested cross-validation was applied to identify the number of boosting steps and the magnitude of penalization, respectively.
 

### 2022-06-11 paper/jmlr/main.tex
slides first draft

--- 2022-05-24 paper/jmlr/main.tex
@@
-\documentclass[twoside,11pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass[twoside,11pt]{article}\usepackage[]{graphicx}\usepackage[]{xcolor}
 % maxwidth is the original width if it is less than linewidth
@@
 \definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\makeatletter
-\@ifundefined{AddToHook}{}{\AddToHook{package/xcolor/after}{\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}}}
-\makeatother
 \newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
@@
 \definecolor{errorcolor}{rgb}{1, 0, 0}
-\makeatletter
-\@ifundefined{AddToHook}{}{\AddToHook{package/xcolor/after}{
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-}}
-\makeatother
 \newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
@@
 
+Risk prediction can reduce the burden of disease by educating patients and providers and guiding strategies to prevent and treat disease in a wide range of medical domains \citep{moons2012riskII, moons2012riskI}.
+The random survival forest (RSF), a supervised learning algorithm that can engage with censored outcomes, is frequently used for risk prediction.
+Notable characteristics of the RSF include uniform convergence of its ensemble survival function to the true population survival function when the predictor space is discrete \citep{ishwaran2010consistency}.
+In addition, software implementing the RSF is freely available, extremely efficient, and full of tools to interpret and explain the RSF \citep{randomForestSRC, ranger, hothorn2010party}.
+However, there remains considerable potential to improve the RSF in risk prediction tasks where training samples are not large enough to guarantee asymptotic properties or predictor spaces are non-discrete (\ie, predictors are continuous).
+
+RSFs may be axis based or oblique.
+The axis based RSF uses a single predictor whereas the oblique RSF uses a linear combination of predictors to create branches in trees.
+While axis based decision boundaries are always perpendicular to the axis of the relevant predictor, linear combinations of predictors create oblique decision boundaries that are neither parallel nor perpendicular to axes of their contributing predictors.
+Prior work has found the oblique RSF has higher prediction accuracy than the axis based RSF in general benchmarks \citep{jaeger2019oblique} and that oblique splitting is particularly effective when predictors are continuous \citep{menze2011oblique}.
+However, existing methods to implement oblique splitting typically use fully trained models in each non-leaf node to identify linear combinations of predictors, exponentially increasing the number of operations required for the oblique RSF versus its axis based counterpart.
+In addition, standard methods to estimate variable importance (VI) in the RSF are less effective in the oblique RSF, and few methods have been introduced to estimate VI specifically for the oblique RSF.
+
+The aim of this article is to improve the computational efficiency and interpretability of the oblique RSF.
+In a general benchmark experiment including YYYY risk prediction tasks, we show that oblique RSFs with partially trained models have equivalent or superior prediction accuracy and are orders of magnitude more efficient than oblique RSFs with fully trained models in non-leaf nodes.
+We introduce a method to estimate VI for oblique RSFs and compare its ability to discriminate between signal and noise variables versus standard and state-of-the-art methods.
+All methods proposed in this article are available in the \texttt{aorsf} R Package.
+
 \section{Related work}
 
-Table \ref{table:1} is an example of a referenced \LaTeX{}.
-Several machine learning algorithms can engage with right-censored time-to-event outcomes.
-In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks.
+\subsection{Axis-based and oblique random forests}
 
-accelerated oblique random survival forests \texttt{aorsf}
+After \citet{breiman2001random} introduced the axis-based and oblique random forest (RF), numerous methods were developed to grow oblique RFs for classification or regression tasks \citep{menze2011oblique, zhang2014oblique, rainforth2015canonical, zhu2015reinforcement, poona2016investigating, qiu2017oblique, tomita2020sparse, katuwal2020heterogeneous}.
+However, oblique splitting approaches for classification or regression may not generalize to survival tasks \citep[\eg, see][Section~4.5.1]{zhu2013tree}, and most research involving the RSF has focused on forests with axis-based trees \citep{wang2017selective}.
 
-original oblique random survival forests \texttt{obliqueRSF}
+Building on prior research for bagging survival trees \citep{hothorn2004bagging}, \citet{hothorn2006unbiased} developed an axis-based RSF in their framework for unbiased recursive partitioning, more commonly referred to as the conditional inference forest (CIF).
+\citet{zhou2016random} developed a rotation forest based on the CIF and \citet{wang2017random} developed a method for extending the predictor space of the CIF.
+\citet{ishwaran2008random} developed an axis-based RSF with strict adherence to the rules for growing trees proposed in \citet{breiman2001random}.
+\citet{jaeger2019oblique} developed the oblique RSF following the bootstrapping approach described in Breiman's original RF and incorporating early stopping rules from the CIF.
 
-axis-based random survival forests \texttt{randomForestSRC \& ranger}
+\subsection{Variable importance}
 
-axis-based conditional inference forests \texttt{party}
+\citet{breiman2001random} introduced permutation VI, defined for each predictor as the difference in a RF's estimated generalization error before versus after the predictor's values are randomly permuted.
+\citet{strobl2007bias} identified bias in permutation VI driven by variable selection bias and effects induced by bootstrap sampling, and proposed an unbiased permutation VI based on unbiased recursive partitioning (see \citet{hothorn2006unbiased}).
+\citet{menze2011oblique} introduced an approach to estimate VI for oblique RFs that computes an analysis of variance (ANOVA) table in non-leaf nodes to obtain p-values for each predictor contributing to the node.
+The ANOVA VI\footnote{\citet{menze2011oblique} name their method `oblique RF VI', but we use the name `ANOVA VI' in this article to avoid confusing Menze's approach with other approaches to estimate VI for oblique RFs.} is then defined for each predictor as the number of times a p-value associated with the predictor is $\leq 0.01$ while growing a forest.
+\citet{lundberg2017unified} introduced a method to estimate VI using SHapley Additive exPlanation (SHAP) values, which estimate the contribution of a predictor to a model's prediction for a given observation.
+SHAP VI is computed for each predictor by taking the mean absolute value of SHAP values for that predictor across all observations in a given set.
 
-gradient boosted decision trees \texttt{xgboost}
+% Several supervised learning algorithms can develop prediction functions for right-censored time-to-event outcomes, henceforth referred to as survival outcomes.
+\cite{ishwaran2008random} developed the RF for survival, an extension of the RF for regression and classification developed by \citet{breiman2001random}.
+Fast algorithms to fit the RF for survival are available in the \texttt{randomForestSRC} R package \citep{randomForestSRC}.
+A similar implementation of the RF for survival can be found in the \texttt{ranger} R package \citep{ranger}, which is particularly suited for high dimensional data.
+The RF for survival can also be fit using unbiased recursive partitioning \citep{cif} via the \texttt{party} R package \citep{hothorn2010party}.
+
+\section{Novel techniques for oblique random survival forests}
+
+\subsection{Partial training at non-leaf nodes}
+
+Consider the usual framework for survival analysis with training data $$\dataset_{\text{train}} = \left\{ (T_i, \delta_i, \bm{x}_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$ Here, $T_i$ is the event time if $\delta_i=1$ and last point of contact if $\delta_i=0$, and $\bm{x}_i$ is a vector of predictors values.
+Assuming there are no ties, let $t_1 < \, \ldots \, < t_m$ denote the $m$ unique event times in $\dataset_{\text{train}}$.
+We propose to identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model:
+\begin{equation}\label{eqn:cox-partial-likelihood}
+L(\bm\beta) = \prod_{i=1}^m \frac{e^{\bm{x}_{j(i)}^T \bm\beta}}{\sum_{j \in R_i} e^{\bm{x}_j^T \bm\beta}},
+\end{equation}
+where $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (i.e., those still at risk at time $t_i$), and $j(i)$ is the index of the observation for which an event occurred at time $t_i$.
+The \texttt{survival} package includes documentation that outlines how to complete this estimation procedure efficiently \citep[see][exact.nw]{therneau_survival_2022}.
+Briefly, a vector of estimated regression coefficients, $\hat{\beta}$, is updated in each step of the procedure based on its first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
+$$ \hat{\beta}^{k+1} =  \hat{\beta}^{k} + U(\hat{\beta} = \hat{\beta}^{k})\, H^{-1}(\hat{\beta} = \hat{\beta}^{k}) $$
+It is vital to cycle through iterations until a convergence threshold is met for statistical inference, but it is only necessary to complete one iteration to identify coefficients for a linear combination of predictors.
+\citet{jaeger2019oblique} identified linear combinations using penalized regression models, which supply more flexible solutions for $\hat{\beta}$ at the cost of greater computational demand.
+
+\subsection{Negation variable importance}
+
+Negation VI is similar to permutation VI in that it measures how much a model’s prediction error increases when a variable’s role in the model is de-stabilized.
+More specifically, negation VI measures the increase in an oblique RF's prediction error after flipping the sign of all coefficients linked to a variable (\ie, negating them).
+As the magnitude of a coefficient increases, so does the probability that negating it will change the oblique RF's predictions.
+Since the coefficients in each non-leaf node of an oblique RFs are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
+Although the current article focuses on oblique RSFs, negation VI can be applied to any oblique RF.
+
+\section{Numeric experiments}
+
+\subsection{Benchmark of prediction accuracy}
+
+\subsubsection{Learners}
+
+In the current study, we consider four classes of learners: RFs, boosting ensembles, regression models, and neural networks (Table \ref{table:learners}).
+For RF learners, the number of observations required in terminal nodes was fixed at 10, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500.
+For boosting and regression learners, nested cross-validation was applied to identify the number of boosting steps and the magnitude of penalization, respectively.
+
+\newgeometry{margin=1cm} % modify this if you need even more space
+\begin{landscape}
 
@@
 \hline
-\multicolumn{7}{l}{\textit{\textbf{actg}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Overall}}}\\
 \hline
-\hspace{1em}Party & 0.772 (0.058) & 0.076 (0.042) & 2.181 & 2.19 & 4.889 & 4.62\\
-\hspace{1em}aORSF(i=1) & 0.755 (0.059) & 0.057 (0.055) & 0.998 & 1.00 & 1.057 & 1.00\\
-\hspace{1em}Ranger & 0.754 (0.064) & 0.064 (0.027) & 0.397 & 0.398 & 0.510 & 0.483\\
-\hspace{1em}aORSF(i=15) & 0.754 (0.063) & 0.052 (0.056) & 2.498 & 2.50 & 2.559 & 2.42\\
-\hspace{1em}Rfsrc & 0.752 (0.064) & 0.061 (0.047) & 0.775 & 0.777 & 0.833 & 0.787\\
-\hspace{1em}aorsf\_net & 0.750 (0.059) & 0.055 (0.064) & 28.449 & 28.5 & 28.510 & 27.0\\
+\hspace{1em}aorsf-cph & 0.132 (0.123) & 0.758 (0.077) & 0.852 & 2.86 & 0.070 & 0.922\\
+\hspace{1em}aorsf-fast & 0.132 (0.123) & 0.758 (0.077) & 0.297 & 1.00 & 0.076 & 1.00\\
+\hspace{1em}aorsf-net & 0.130 (0.126) & 0.756 (0.077) & 68.335 & 229.9 & 0.071 & 0.930\\
+\hspace{1em}cif-rotate & 0.125 (0.144) & 0.741 (0.090) & 30.981 & 104.2 & 7.536 & 98.6\\
+\hspace{1em}cif-standard & 0.120 (0.110) & 0.749 (0.076) & 2.213 & 7.44 & 5.283 & 69.2\\
+\hspace{1em}glmnet-cox & 0.119 (0.136) & 0.749 (0.079) & 0.522 & 1.76 & 0.005 & 0.066\\
+\hspace{1em}rsf-standard & 0.117 (0.127) & 0.741 (0.081) & 1.713 & 5.76 & 0.149 & 1.95\\
+\hspace{1em}obliqueRSF-net & 0.116 (0.092) & 0.755 (0.078) & 334.542 & 1,125.4 & 26.565 & 347.7\\
+\hspace{1em}cif-extension & 0.107 (0.107) & 0.746 (0.080) & 13.591 & 45.7 & 7.281 & 95.3\\
+\hspace{1em}ranger-extratrees & 0.104 (0.096) & 0.748 (0.074) & 0.745 & 2.51 & 0.510 & 6.68\\
+\hspace{1em}aorsf-random & 0.100 (0.091) & 0.735 (0.072) & 2.063 & 6.94 & 0.068 & 0.888\\
+\hspace{1em}xgboost-cox & 0.077 (0.111) & 0.737 (0.091) & 3.846 & 12.9 & 0.005 & 0.066\\
+\hspace{1em}nn-cox & 0.031 (0.116) & 0.615 (0.126) & 15.466 & 52.0 & 1.652 & 21.6\\
+\hspace{1em}xgboost-aft & -3.72 (4.96) & 0.746 (0.079) & 13.542 & 45.6 & 0.008 & 0.106\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{breast}}}\\
+\multicolumn{7}{l}{\textit{\textbf{ACTG 320; AIDS diagnosis, n = 1151, p = 12}}}\\
 \hline
-\hspace{1em}aORSF(i=15) & 0.764 (0.008) & 0.143 (0.016) & 11.867 & 2.56 & 12.403 & 2.43\\
-\hspace{1em}Ranger & 0.756 (0.013) & 0.102 (0.017) & 0.555 & 0.120 & 0.724 & 0.142\\
-\hspace{1em}Party & 0.753 (0.013) & 0.118 (0.016) & 8.030 & 1.73 & 10.445 & 2.05\\
-\hspace{1em}aORSF(i=1) & 0.751 (0.002) & 0.120 (0.012) & 4.636 & 1.00 & 5.106 & 1.00\\
-\hspace{1em}aorsf\_net & 0.741 (0.022) & 0.062 (0.049) & 585.625 & 126.3 & 585.887 & 114.7\\
-\hspace{1em}Rfsrc & 0.707 (0.005) & 0.049 (0.039) & 1.354 & 0.292 & 1.522 & 0.298\\
+\hspace{1em}aorsf-random & 0.032 (0.014) & 0.741 (0.030) & 0.637 & 4.08 & 0.041 & 1.09\\
+\hspace{1em}ranger-extratrees & 0.030 (0.013) & 0.737 (0.029) & 0.067 & 0.429 & 0.184 & 4.83\\
+\hspace{1em}cif-standard & 0.029 (0.024) & 0.743 (0.038) & 1.608 & 10.3 & 4.825 & 126.9\\
+\hspace{1em}obliqueRSF-net & 0.029 (0.019) & 0.739 (0.036) & 30.556 & 195.7 & 16.658 & 438.0\\
+\hspace{1em}aorsf-fast & 0.027 (0.020) & 0.738 (0.036) & 0.156 & 1.00 & 0.038 & 1.00\\
+\hspace{1em}aorsf-cph & 0.027 (0.022) & 0.744 (0.036) & 0.460 & 2.94 & 0.035 & 0.921\\
+\hspace{1em}cif-extension & 0.024 (0.013) & 0.716 (0.037) & 11.131 & 71.3 & 5.866 & 154.2\\
+\hspace{1em}aorsf-net & 0.022 (0.027) & 0.738 (0.036) & 20.456 & 131.0 & 0.038 & 1.00\\
+\hspace{1em}glmnet-cox & 0.016 (0.025) & 0.738 (0.030) & 0.189 & 1.21 & 0.003 & 0.079\\
+\hspace{1em}rsf-standard & 0.013 (0.028) & 0.728 (0.042) & 0.212 & 1.36 & 0.083 & 2.17\\
+\hspace{1em}cif-rotate & 0.010 (0.033) & 0.734 (0.034) & 15.072 & 96.5 & 4.201 & 110.4\\
+\hspace{1em}xgboost-cox & 0.008 (0.029) & 0.745 (0.033) & 3.452 & 22.1 & 0.003 & 0.079\\
+\hspace{1em}nn-cox & 0.002 (0.012) & 0.613 (0.089) & 12.733 & 81.5 & 0.615 & 16.2\\
+\hspace{1em}xgboost-aft & -7.79 (1.41) & 0.733 (0.030) & 11.574 & 74.1 & 0.007 & 0.184\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{colon}}}\\
+\multicolumn{7}{l}{\textit{\textbf{ACTG 320; death, n = 1151, p = 12}}}\\
 \hline
-\hspace{1em}Rfsrc & 0.815 (0.007) & 0.279 (0.007) & 1.854 & 0.581 & 2.026 & 0.600\\
-\hspace{1em}aORSF(i=15) & 0.778 (0.007) & 0.199 (0.018) & 7.515 & 2.36 & 7.709 & 2.28\\
-\hspace{1em}aORSF(i=1) & 0.776 (0.004) & 0.201 (0.014) & 3.190 & 1.00 & 3.378 & 1.00\\
-\hspace{1em}aorsf\_net & 0.753 (0.006) & 0.156 (0.018) & 149.637 & 46.9 & 149.809 & 44.3\\
-\hspace{1em}Party & 0.753 (0.012) & 0.183 (0.008) & 3.968 & 1.24 & 10.451 & 3.09\\
-\hspace{1em}Ranger & 0.738 (0.008) & 0.147 (0.005) & 1.795 & 0.563 & 2.398 & 0.710\\
+\hspace{1em}aorsf-fast & 0.012 (0.021) & 0.836 (0.045) & 0.091 & 1.00 & 0.021 & 1.00\\
+\hspace{1em}aorsf-cph & 0.011 (0.020) & 0.827 (0.052) & 0.367 & 4.02 & 0.021 & 1.02\\
+\hspace{1em}aorsf-random & 0.009 (0.015) & 0.804 (0.054) & 0.318 & 3.48 & 0.028 & 1.34\\
+\hspace{1em}obliqueRSF-net & 0.008 (0.013) & 0.829 (0.044) & 9.819 & 107.6 & 10.716 & 520.0\\
+\hspace{1em}aorsf-net & 0.005 (0.034) & 0.815 (0.052) & 14.708 & 161.2 & 0.025 & 1.19\\
+\hspace{1em}cif-extension & 0.001 (0.025) & 0.764 (0.053) & 9.440 & 103.4 & 4.147 & 201.2\\
+\hspace{1em}ranger-extratrees & 0.001 (0.023) & 0.782 (0.061) & 0.052 & 0.565 & 0.148 & 7.17\\
+\hspace{1em}cif-standard & -0.004 (0.030) & 0.777 (0.051) & 1.818 & 19.9 & 4.470 & 216.9\\
+\hspace{1em}xgboost-cox & -0.004 (0.003) & 0.500 (0.000) & 0.121 & 1.33 & 0.002 & 0.097\\
+\hspace{1em}nn-cox & -0.005 (0.003) & 0.541 (0.100) & 12.682 & 139.0 & 0.665 & 32.3\\
+\hspace{1em}rsf-standard & -0.019 (0.056) & 0.781 (0.053) & 0.091 & 0.992 & 0.043 & 2.06\\
+\hspace{1em}cif-rotate & -0.038 (0.056) & 0.701 (0.101) & 14.054 & 154.0 & 3.602 & 174.8\\
+\hspace{1em}glmnet-cox & -0.053 (0.100) & 0.743 (0.092) & 0.314 & 3.45 & 0.002 & 0.098\\
+\hspace{1em}xgboost-aft & -24.5 (8.08) & 0.757 (0.070) & 11.563 & 126.7 & 0.009 & 0.419\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{gbsg2}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Colon cancer; death, n = 929, p = 12}}}\\
 \hline
-\hspace{1em}Ranger & 0.704 (0.076) & 0.090 (0.045) & 0.328 & 0.339 & 0.450 & 0.438\\
-\hspace{1em}Party & 0.686 (0.042) & 0.092 (0.048) & 0.746 & 0.773 & 2.055 & 2.00\\
-\hspace{1em}aORSF(i=15) & 0.685 (0.048) & 0.077 (0.066) & 2.077 & 2.15 & 2.144 & 2.09\\
-\hspace{1em}Rfsrc & 0.676 (0.032) & 0.067 (0.052) & 0.931 & 0.963 & 1.014 & 0.986\\
-\hspace{1em}aORSF(i=1) & 0.674 (0.045) & 0.062 (0.062) & 0.966 & 1.00 & 1.028 & 1.00\\
-\hspace{1em}aorsf\_net & 0.670 (0.038) & 0.068 (0.056) & 57.024 & 59.0 & 57.087 & 55.5\\
+\hspace{1em}aorsf-fast & 0.100 (0.015) & 0.718 (0.013) & 0.289 & 1.00 & 0.078 & 1.00\\
+\hspace{1em}aorsf-cph & 0.099 (0.015) & 0.716 (0.012) & 0.685 & 2.37 & 0.070 & 0.909\\
+\hspace{1em}cif-standard & 0.099 (0.014) & 0.712 (0.012) & 1.571 & 5.44 & 5.267 & 67.9\\
+\hspace{1em}aorsf-net & 0.097 (0.014) & 0.716 (0.012) & 55.870 & 193.4 & 0.065 & 0.839\\
+\hspace{1em}aorsf-random & 0.095 (0.009) & 0.715 (0.012) & 2.500 & 8.65 & 0.066 & 0.852\\
+\hspace{1em}cif-rotate & 0.092 (0.018) & 0.707 (0.014) & 15.603 & 54.0 & 6.537 & 84.3\\
+\hspace{1em}obliqueRSF-net & 0.089 (0.007) & 0.717 (0.012) & 269.561 & 932.9 & 43.786 & 564.9\\
+\hspace{1em}rsf-standard & 0.088 (0.021) & 0.703 (0.012) & 1.646 & 5.70 & 0.143 & 1.85\\
+\hspace{1em}ranger-extratrees & 0.082 (0.007) & 0.711 (0.012) & 0.822 & 2.84 & 0.274 & 3.53\\
+\hspace{1em}cif-extension & 0.081 (0.006) & 0.710 (0.012) & 8.656 & 30.0 & 6.253 & 80.7\\
+\hspace{1em}glmnet-cox & 0.074 (0.013) & 0.710 (0.017) & 0.125 & 0.433 & 0.004 & 0.052\\
+\hspace{1em}xgboost-cox & 0.064 (0.011) & 0.702 (0.012) & 3.446 & 11.9 & 0.005 & 0.065\\
+\hspace{1em}nn-cox & -0.006 (0.012) & 0.504 (0.048) & 15.123 & 52.3 & 2.166 & 27.9\\
+\hspace{1em}xgboost-aft & -1.07 (0.231) & 0.708 (0.013) & 14.169 & 49.0 & 0.008 & 0.103\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{guide\_it}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Colon cancer; recurrence, n = 929, p = 12}}}\\
 \hline
-\hspace{1em}aORSF(i=15) & 0.730 (0.009) & 0.133 (0.008) & 4.705 & 2.67 & 4.811 & 2.57\\
-\hspace{1em}aORSF(i=1) & 0.728 (0.014) & 0.132 (0.012) & 1.762 & 1.00 & 1.869 & 1.00\\
-\hspace{1em}aorsf\_net & 0.728 (0.020) & 0.133 (0.015) & 86.476 & 49.1 & 86.590 & 46.3\\
-\hspace{1em}Party & 0.705 (0.021) & 0.101 (0.010) & 1.800 & 1.02 & 3.727 & 1.99\\
-\hspace{1em}Rfsrc & 0.705 (0.032) & 0.109 (0.027) & 1.000 & 0.568 & 1.104 & 0.591\\
-\hspace{1em}Ranger & 0.704 (0.016) & 0.102 (0.001) & 0.663 & 0.376 & 0.855 & 0.457\\
+\hspace{1em}aorsf-fast & 0.096 (0.015) & 0.711 (0.014) & 0.276 & 1.00 & 0.070 & 1.00\\
+\hspace{1em}aorsf-cph & 0.095 (0.015) & 0.710 (0.014) & 0.704 & 2.55 & 0.070 & 0.994\\
+\hspace{1em}aorsf-net & 0.093 (0.017) & 0.711 (0.016) & 52.298 & 189.5 & 0.069 & 0.980\\
+\hspace{1em}cif-standard & 0.092 (0.015) & 0.701 (0.015) & 1.183 & 4.28 & 4.119 & 58.4\\
+\hspace{1em}cif-rotate & 0.088 (0.019) & 0.698 (0.016) & 14.170 & 51.3 & 5.936 & 84.2\\
+\hspace{1em}obliqueRSF-net & 0.087 (0.008) & 0.711 (0.013) & 328.771 & 1,191.0 & 45.669 & 648.0\\
+\hspace{1em}aorsf-random & 0.083 (0.012) & 0.700 (0.014) & 1.998 & 7.24 & 0.075 & 1.07\\
+\hspace{1em}cif-extension & 0.081 (0.009) & 0.706 (0.013) & 9.934 & 36.0 & 6.899 & 97.9\\
+\hspace{1em}rsf-standard & 0.080 (0.020) & 0.693 (0.014) & 1.308 & 4.74 & 0.135 & 1.92\\
+\hspace{1em}ranger-extratrees & 0.076 (0.012) & 0.696 (0.012) & 0.555 & 2.01 & 0.235 & 3.34\\
+\hspace{1em}glmnet-cox & 0.071 (0.014) & 0.705 (0.020) & 0.171 & 0.621 & 0.006 & 0.085\\
+\hspace{1em}xgboost-cox & 0.059 (0.011) & 0.696 (0.014) & 3.291 & 11.9 & 0.005 & 0.071\\
+\hspace{1em}nn-cox & -0.006 (0.006) & 0.511 (0.045) & 14.010 & 50.8 & 1.651 & 23.4\\
+\hspace{1em}xgboost-aft & -1.16 (0.238) & 0.702 (0.015) & 12.004 & 43.5 & 0.007 & 0.099\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{Mayo Clinic Primary Biliary Cholangitis Data, N = 276}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Early breast cancer; recurrence or death, n = 614, p = 1692}}}\\
 \hline
-\hspace{1em}aORSF(i=1) & 0.787 (0.094) & 0.202 (0.188) & 2.204 & 1.00 & 2.400 & 1.00\\
-\hspace{1em}aORSF(i=15) & 0.787 (0.100) & 0.203 (0.186) & 5.038 & 2.29 & 5.242 & 2.18\\
-\hspace{1em}Ranger & 0.783 (0.091) & 0.161 (0.138) & 0.709 & 0.322 & 1.053 & 0.438\\
-\hspace{1em}aorsf\_net & 0.782 (0.101) & 0.190 (0.202) & 128.300 & 58.2 & 128.469 & 53.5\\
-\hspace{1em}Party & 0.779 (0.094) & 0.185 (0.167) & 3.291 & 1.49 & 6.998 & 2.92\\
-\hspace{1em}Rfsrc & 0.778 (0.113) & 0.195 (0.187) & 0.956 & 0.434 & 1.076 & 0.448\\
+\hspace{1em}obliqueRSF-net & 0.070 (0.029) & 0.748 (0.029) & 1972.453 & 2,151.1 & 15.992 & 88.3\\
+\hspace{1em}cif-rotate & 0.070 (0.020) & 0.746 (0.028) & 6858.572 & 7,479.6 & 386.651 & 2,135.1\\
+\hspace{1em}cif-standard & 0.067 (0.022) & 0.744 (0.030) & 9.810 & 10.7 & 4.401 & 24.3\\
+\hspace{1em}cif-extension & 0.066 (0.017) & 0.746 (0.027) & 46.010 & 50.2 & 7.191 & 39.7\\
+\hspace{1em}aorsf-cph & 0.063 (0.038) & 0.746 (0.028) & 1.352 & 1.47 & 0.182 & 1.00\\
+\hspace{1em}aorsf-fast & 0.061 (0.037) & 0.744 (0.027) & 0.917 & 1.00 & 0.181 & 1.00\\
+\hspace{1em}ranger-extratrees & 0.059 (0.029) & 0.741 (0.028) & 0.245 & 0.267 & 0.180 & 0.994\\
+\hspace{1em}xgboost-cox & 0.040 (0.013) & 0.745 (0.032) & 2.231 & 2.43 & 0.007 & 0.036\\
+\hspace{1em}glmnet-cox & 0.035 (0.038) & 0.721 (0.037) & 5.766 & 6.29 & 0.006 & 0.031\\
+\hspace{1em}aorsf-random & 0.027 (0.018) & 0.692 (0.038) & 2.369 & 2.58 & 0.214 & 1.18\\
+\hspace{1em}rsf-standard & 0.020 (0.050) & 0.699 (0.037) & 0.404 & 0.440 & 0.662 & 3.65\\
+\hspace{1em}aorsf-net & 0.005 (0.080) & 0.743 (0.025) & 464.340 & 506.4 & 0.181 & 0.998\\
+\hspace{1em}nn-cox & -0.017 (0.076) & 0.679 (0.050) & 18.858 & 20.6 & 1.907 & 10.5\\
+\hspace{1em}xgboost-aft & -3.09 (0.743) & 0.741 (0.021) & 12.057 & 13.1 & 0.013 & 0.072\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{Overall}}}\\
+\multicolumn{7}{l}{\textit{\textbf{FCL; death, n = 541, p = 7}}}\\
 \hline
-\hspace{1em}aORSF(i=1) & 0.946 (0.018) & 0.493 (0.083) & 0.344 & 1.00 & 0.376 & 1.00\\
-\hspace{1em}aorsf\_net & 0.939 (0.018) & 0.484 (0.052) & 23.093 & 67.2 & 23.123 & 61.6\\
-\hspace{1em}Party & 0.936 (0.022) & 0.454 (0.022) & 0.288 & 0.839 & 0.518 & 1.38\\
-\hspace{1em}aORSF(i=15) & 0.936 (0.014) & 0.474 (0.080) & 0.744 & 2.17 & 0.773 & 2.06\\
-\hspace{1em}Rfsrc & 0.927 (0.012) & 0.462 (0.070) & 0.363 & 1.06 & 0.397 & 1.06\\
-\hspace{1em}Ranger & 0.926 (0.014) & 0.344 (0.055) & 0.044 & 0.127 & 0.085 & 0.226\\
+\hspace{1em}glmnet-cox & 0.119 (0.031) & 0.791 (0.040) & 0.133 & 1.48 & 0.003 & 0.150\\
+\hspace{1em}aorsf-cph & 0.102 (0.039) & 0.769 (0.034) & 0.175 & 1.94 & 0.020 & 1.00\\
+\hspace{1em}aorsf-fast & 0.101 (0.039) & 0.769 (0.032) & 0.090 & 1.00 & 0.020 & 1.00\\
+\hspace{1em}aorsf-net & 0.097 (0.041) & 0.760 (0.037) & 18.501 & 205.4 & 0.021 & 1.05\\
+\hspace{1em}obliqueRSF-net & 0.093 (0.027) & 0.766 (0.038) & 115.794 & 1,285.4 & 5.807 & 290.1\\
+\hspace{1em}aorsf-random & 0.090 (0.030) & 0.763 (0.033) & 0.319 & 3.54 & 0.020 & 1.00\\
+\hspace{1em}cif-standard & 0.087 (0.043) & 0.752 (0.038) & 1.227 & 13.6 & 1.275 & 63.7\\
+\hspace{1em}cif-extension & 0.086 (0.041) & 0.731 (0.042) & 6.649 & 73.8 & 2.610 & 130.4\\
+\hspace{1em}cif-rotate & 0.085 (0.051) & 0.756 (0.028) & 7.713 & 85.6 & 2.159 & 107.9\\
+\hspace{1em}ranger-extratrees & 0.075 (0.013) & 0.744 (0.034) & 0.038 & 0.425 & 0.087 & 4.33\\
+\hspace{1em}rsf-standard & 0.071 (0.056) & 0.734 (0.039) & 0.620 & 6.88 & 0.040 & 2.00\\
+\hspace{1em}xgboost-cox & 0.049 (0.055) & 0.724 (0.097) & 2.219 & 24.6 & 0.002 & 0.100\\
+\hspace{1em}nn-cox & -0.001 (0.014) & 0.548 (0.082) & 12.668 & 140.6 & 0.510 & 25.5\\
+\hspace{1em}xgboost-aft & -2.68 (0.479) & 0.754 (0.044) & 7.761 & 86.2 & 0.006 & 0.300\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{Rotterdam Breast Cancer Data, N = 2,982}}}\\
+\multicolumn{7}{l}{\textit{\textbf{FCL; relapse, n = 541, p = 7}}}\\
 \hline
-\hspace{1em}Ranger & 0.719 (0.011) & 0.145 (0.011) & 2.480 & 0.410 & 4.456 & 0.692\\
-\hspace{1em}aorsf\_net & 0.714 (0.007) & 0.141 (0.007) & 237.007 & 39.2 & 237.337 & 36.9\\
-\hspace{1em}Party & 0.712 (0.008) & 0.141 (0.012) & 7.030 & 1.16 & 21.888 & 3.40\\
-\hspace{1em}aORSF(i=1) & 0.712 (0.006) & 0.139 (0.008) & 6.053 & 1.00 & 6.436 & 1.00\\
-\hspace{1em}aORSF(i=15) & 0.711 (0.005) & 0.139 (0.007) & 13.541 & 2.24 & 13.925 & 2.16\\
-\hspace{1em}Rfsrc & 0.701 (0.008) & 0.120 (0.010) & 2.222 & 0.367 & 2.458 & 0.382\\
+\hspace{1em}glmnet-cox & 0.033 (0.015) & 0.624 (0.019) & 0.101 & 0.791 & 0.002 & 0.074\\
+\hspace{1em}ranger-extratrees & 0.017 (0.018) & 0.594 (0.029) & 0.034 & 0.269 & 0.090 & 3.32\\
+\hspace{1em}obliqueRSF-net & 0.015 (0.015) & 0.595 (0.023) & 263.391 & 2,072.0 & 11.192 & 412.4\\
+\hspace{1em}xgboost-cox & 0.014 (0.014) & 0.605 (0.029) & 1.352 & 10.6 & 0.003 & 0.111\\
+\hspace{1em}aorsf-random & 0.013 (0.021) & 0.599 (0.027) & 0.530 & 4.17 & 0.025 & 0.922\\
+\hspace{1em}aorsf-cph & 0.009 (0.023) & 0.600 (0.028) & 0.272 & 2.14 & 0.028 & 1.04\\
+\hspace{1em}cif-standard & 0.008 (0.021) & 0.595 (0.024) & 1.143 & 8.99 & 1.784 & 65.7\\
+\hspace{1em}aorsf-fast & 0.008 (0.023) & 0.598 (0.028) & 0.127 & 1.00 & 0.027 & 1.00\\
+\hspace{1em}aorsf-net & 0.007 (0.024) & 0.596 (0.029) & 20.392 & 160.4 & 0.026 & 0.959\\
+\hspace{1em}nn-cox & -0.003 (0.018) & 0.535 (0.056) & 13.504 & 106.2 & 0.781 & 28.8\\
+\hspace{1em}cif-extension & -0.005 (0.026) & 0.581 (0.030) & 6.550 & 51.5 & 3.511 & 129.4\\
+\hspace{1em}cif-rotate & -0.011 (0.026) & 0.586 (0.031) & 8.441 & 66.4 & 3.303 & 121.7\\
+\hspace{1em}rsf-standard & -0.026 (0.034) & 0.580 (0.027) & 1.337 & 10.5 & 0.087 & 3.21\\
+\hspace{1em}xgboost-aft & -0.826 (0.317) & 0.586 (0.039) & 7.490 & 58.9 & 0.007 & 0.258\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{time\_to\_million}}}\\
+\multicolumn{7}{l}{\textit{\textbf{GBSG II; recurrence or death, n = 686, p = 10}}}\\
 \hline
-\hspace{1em}aorsf\_net & 0.937 (0.013) & 0.560 (0.040) & 78.384 & 55.8 & 78.461 & 53.0\\
-\hspace{1em}aORSF(i=15) & 0.937 (0.018) & 0.555 (0.043) & 4.491 & 3.20 & 4.569 & 3.09\\
-\hspace{1em}aORSF(i=1) & 0.935 (0.017) & 0.552 (0.039) & 1.405 & 1.00 & 1.481 & 1.00\\
-\hspace{1em}Rfsrc & 0.932 (0.023) & 0.550 (0.045) & 0.784 & 0.558 & 0.853 & 0.576\\
-\hspace{1em}Party & 0.921 (0.014) & 0.485 (0.034) & 0.621 & 0.442 & 1.684 & 1.14\\
-\hspace{1em}Ranger & 0.916 (0.023) & 0.452 (0.039) & 0.324 & 0.231 & 0.428 & 0.289\\
+\hspace{1em}obliqueRSF-net & 0.120 (0.016) & 0.741 (0.019) & 334.738 & 1,750.9 & 12.512 & 271.2\\
+\hspace{1em}cif-standard & 0.120 (0.022) & 0.739 (0.021) & 1.134 & 5.93 & 2.323 & 50.4\\
+\hspace{1em}aorsf-net & 0.118 (0.027) & 0.735 (0.022) & 38.945 & 203.7 & 0.046 & 1.00\\
+\hspace{1em}rsf-standard & 0.117 (0.025) & 0.734 (0.021) & 1.872 & 9.79 & 0.112 & 2.42\\
+\hspace{1em}aorsf-cph & 0.113 (0.029) & 0.729 (0.019) & 0.441 & 2.30 & 0.047 & 1.02\\
+\hspace{1em}cif-extension & 0.112 (0.020) & 0.740 (0.022) & 8.962 & 46.9 & 4.709 & 102.1\\
+\hspace{1em}aorsf-fast & 0.111 (0.028) & 0.729 (0.018) & 0.191 & 1.00 & 0.046 & 1.00\\
+\hspace{1em}cif-rotate & 0.108 (0.025) & 0.728 (0.018) & 13.378 & 70.0 & 5.546 & 120.2\\
+\hspace{1em}aorsf-random & 0.100 (0.028) & 0.718 (0.029) & 1.373 & 7.18 & 0.047 & 1.02\\
+\hspace{1em}ranger-extratrees & 0.091 (0.020) & 0.734 (0.028) & 0.489 & 2.56 & 0.137 & 2.98\\
+\hspace{1em}glmnet-cox & 0.084 (0.018) & 0.721 (0.021) & 0.143 & 0.750 & 0.003 & 0.065\\
+\hspace{1em}xgboost-cox & 0.081 (0.017) & 0.725 (0.019) & 2.309 & 12.1 & 0.003 & 0.065\\
+\hspace{1em}nn-cox & -0.004 (0.004) & 0.505 (0.033) & 12.705 & 66.5 & 1.348 & 29.2\\
+\hspace{1em}xgboost-aft & -1.11 (0.152) & 0.724 (0.022) & 11.618 & 60.8 & 0.007 & 0.152\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{vdv}}}\\
+\multicolumn{7}{l}{\textit{\textbf{GUIDE-IT; CVD death, n = 894, p = 59}}}\\
 \hline
-\hspace{1em}Rfsrc & 0.782 (0.231) & 0.033 (0.185) & 0.198 & 0.080 & 0.450 & 0.148\\
-\hspace{1em}aorsf\_net & 0.770 (0.161) & -0.019 (0.283) & 20.190 & 8.13 & 20.749 & 6.80\\
-\hspace{1em}aORSF(i=1) & 0.762 (0.079) & -0.012 (0.126) & 2.484 & 1.00 & 3.050 & 1.00\\
-\hspace{1em}Ranger & 0.751 (0.070) & -0.017 (0.093) & 0.484 & 0.195 & 0.576 & 0.189\\
-\hspace{1em}aORSF(i=15) & 0.735 (0.171) & -0.025 (0.135) & 2.569 & 1.03 & 3.136 & 1.03\\
-\hspace{1em}Party & 0.722 (0.102) & -0.030 (0.165) & 8.098 & 3.26 & 14.088 & 4.62\\
+\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.749 (0.029) & 0.181 & 1.00 & 0.037 & 1.00\\
+\hspace{1em}aorsf-net & 0.073 (0.017) & 0.745 (0.029) & 28.715 & 158.4 & 0.040 & 1.08\\
+\hspace{1em}aorsf-cph & 0.070 (0.019) & 0.744 (0.029) & 0.423 & 2.33 & 0.040 & 1.08\\
+\hspace{1em}glmnet-cox & 0.069 (0.037) & 0.737 (0.071) & 1.067 & 5.89 & 0.003 & 0.081\\
+\hspace{1em}obliqueRSF-net & 0.062 (0.014) & 0.742 (0.025) & 245.122 & 1,352.1 & 11.754 & 317.4\\
+\hspace{1em}cif-rotate & 0.060 (0.014) & 0.718 (0.027) & 37.291 & 205.7 & 4.865 & 131.4\\
+\hspace{1em}cif-standard & 0.057 (0.014) & 0.738 (0.025) & 2.289 & 12.6 & 3.756 & 101.4\\
+\hspace{1em}ranger-extratrees & 0.052 (0.014) & 0.739 (0.031) & 0.766 & 4.22 & 0.218 & 5.89\\
+\hspace{1em}cif-extension & 0.050 (0.013) & 0.727 (0.024) & 13.957 & 77.0 & 5.947 & 160.6\\
+\hspace{1em}rsf-standard & 0.044 (0.022) & 0.705 (0.029) & 1.611 & 8.89 & 0.075 & 2.03\\
+\hspace{1em}xgboost-cox & 0.037 (0.046) & 0.743 (0.020) & 4.400 & 24.3 & 0.003 & 0.081\\
+\hspace{1em}aorsf-random & 0.030 (0.013) & 0.696 (0.030) & 1.521 & 8.39 & 0.042 & 1.12\\
+\hspace{1em}nn-cox & 0.020 (0.040) & 0.677 (0.093) & 13.762 & 75.9 & 0.675 & 18.2\\
+\hspace{1em}xgboost-aft & -5.15 (1.19) & 0.733 (0.021) & 15.383 & 84.9 & 0.007 & 0.189\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{veteran}}}\\
+\multicolumn{7}{l}{\textit{\textbf{GUIDE-IT; HF hospitalization, n = 894, p = 59}}}\\
 \hline
-\hspace{1em}Ranger & 0.865 (0.063) & 0.183 (0.036) & 0.023 & 0.113 & 0.043 & 0.194\\
-\hspace{1em}aORSF(i=15) & 0.837 (0.048) & 0.281 (0.075) & 0.371 & 1.84 & 0.387 & 1.75\\
-\hspace{1em}aORSF(i=1) & 0.833 (0.053) & 0.278 (0.081) & 0.202 & 1.00 & 0.222 & 1.00\\
-\hspace{1em}Party & 0.833 (0.057) & 0.235 (0.056) & 0.150 & 0.744 & 0.231 & 1.04\\
-\hspace{1em}aorsf\_net & 0.820 (0.059) & 0.256 (0.083) & 17.115 & 84.7 & 17.133 & 77.3\\
-\hspace{1em}Rfsrc & 0.784 (0.111) & 0.218 (0.112) & 0.077 & 0.380 & 0.099 & 0.447\\*
+\hspace{1em}aorsf-net & 0.086 (0.017) & 0.727 (0.025) & 68.304 & 241.1 & 0.070 & 1.12\\
+\hspace{1em}aorsf-fast & 0.085 (0.018) & 0.728 (0.027) & 0.283 & 1.00 & 0.063 & 1.00\\
+\hspace{1em}aorsf-cph & 0.085 (0.020) & 0.727 (0.025) & 0.713 & 2.52 & 0.063 & 1.00\\
+\hspace{1em}obliqueRSF-net & 0.076 (0.011) & 0.725 (0.024) & 472.412 & 1,667.8 & 14.859 & 235.6\\
+\hspace{1em}ranger-extratrees & 0.073 (0.011) & 0.722 (0.023) & 0.801 & 2.83 & 0.514 & 8.15\\
+\hspace{1em}cif-standard & 0.072 (0.011) & 0.719 (0.023) & 2.043 & 7.21 & 3.784 & 60.0\\
+\hspace{1em}cif-rotate & 0.070 (0.020) & 0.711 (0.031) & 47.306 & 167.0 & 8.016 & 127.1\\
+\hspace{1em}cif-extension & 0.066 (0.009) & 0.719 (0.021) & 18.091 & 63.9 & 8.846 & 140.3\\
+\hspace{1em}glmnet-cox & 0.064 (0.019) & 0.705 (0.024) & 1.076 & 3.80 & 0.003 & 0.048\\
+\hspace{1em}rsf-standard & 0.059 (0.023) & 0.698 (0.027) & 1.775 & 6.27 & 0.109 & 1.73\\
+\hspace{1em}aorsf-random & 0.051 (0.011) & 0.687 (0.025) & 1.882 & 6.64 & 0.062 & 0.984\\
+\hspace{1em}xgboost-cox & 0.042 (0.014) & 0.703 (0.027) & 2.982 & 10.5 & 0.003 & 0.048\\
+\hspace{1em}nn-cox & 0.039 (0.032) & 0.680 (0.077) & 14.131 & 49.9 & 0.644 & 10.2\\
+\hspace{1em}xgboost-aft & -2.22 (0.313) & 0.698 (0.028) & 12.951 & 45.7 & 0.007 & 0.111\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Heart Transplant; graft-loss or death, n = 3787, p = 52}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.054 (0.011) & 0.730 (0.019) & 161.908 & 164.7 & 34.066 & 110.1\\
+\hspace{1em}aorsf-net & 0.051 (0.007) & 0.731 (0.015) & 132.397 & 134.7 & 0.313 & 1.01\\
+\hspace{1em}aorsf-fast & 0.051 (0.007) & 0.734 (0.016) & 0.983 & 1.00 & 0.309 & 1.00\\
+\hspace{1em}aorsf-cph & 0.051 (0.007) & 0.732 (0.015) & 3.094 & 3.15 & 0.311 & 1.01\\
+\hspace{1em}cif-standard & 0.049 (0.007) & 0.732 (0.016) & 12.017 & 12.2 & 46.520 & 150.3\\
+\hspace{1em}obliqueRSF-net & 0.048 (0.007) & 0.729 (0.017) & 362.862 & 369.2 & 168.051 & 543.1\\
+\hspace{1em}rsf-standard & 0.048 (0.010) & 0.726 (0.013) & 3.527 & 3.59 & 1.138 & 3.68\\
+\hspace{1em}ranger-extratrees & 0.046 (0.007) & 0.729 (0.016) & 4.963 & 5.05 & 3.527 & 11.4\\
+\hspace{1em}glmnet-cox & 0.035 (0.006) & 0.709 (0.017) & 1.023 & 1.04 & 0.013 & 0.042\\
+\hspace{1em}cif-extension & 0.035 (0.004) & 0.726 (0.019) & 50.426 & 51.3 & 24.989 & 80.8\\
+\hspace{1em}xgboost-cox & 0.030 (0.008) & 0.716 (0.021) & 3.520 & 3.58 & 0.011 & 0.036\\
+\hspace{1em}aorsf-random & 0.028 (0.003) & 0.688 (0.014) & 3.025 & 3.08 & 0.296 & 0.956\\
+\hspace{1em}nn-cox & 0.023 (0.011) & 0.679 (0.023) & 16.704 & 17.0 & 11.675 & 37.7\\
+\hspace{1em}xgboost-aft & -4.38 (0.466) & 0.721 (0.013) & 13.594 & 13.8 & 0.008 & 0.026\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Monoclonal gammopathy; death, n = 1384, p = 8}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.158 (0.020) & 0.742 (0.015) & 17.616 & 38.2 & 8.081 & 71.1\\
+\hspace{1em}aorsf-cph & 0.157 (0.015) & 0.741 (0.010) & 1.254 & 2.72 & 0.112 & 0.983\\
+\hspace{1em}aorsf-fast & 0.156 (0.015) & 0.740 (0.010) & 0.461 & 1.00 & 0.114 & 1.00\\
+\hspace{1em}obliqueRSF-net & 0.154 (0.012) & 0.742 (0.011) & 244.591 & 530.3 & 17.341 & 152.5\\
+\hspace{1em}aorsf-net & 0.154 (0.014) & 0.739 (0.010) & 97.606 & 211.6 & 0.108 & 0.946\\
+\hspace{1em}cif-standard & 0.150 (0.014) & 0.737 (0.011) & 2.419 & 5.24 & 8.105 & 71.3\\
+\hspace{1em}rsf-standard & 0.150 (0.015) & 0.735 (0.010) & 1.834 & 3.98 & 0.182 & 1.60\\
+\hspace{1em}aorsf-random & 0.145 (0.013) & 0.733 (0.011) & 2.662 & 5.77 & 0.105 & 0.924\\
+\hspace{1em}cif-extension & 0.142 (0.009) & 0.745 (0.012) & 11.262 & 24.4 & 6.808 & 59.9\\
+\hspace{1em}glmnet-cox & 0.134 (0.019) & 0.724 (0.013) & 0.140 & 0.304 & 0.005 & 0.044\\
+\hspace{1em}xgboost-cox & 0.122 (0.012) & 0.731 (0.012) & 3.765 & 8.16 & 0.005 & 0.044\\
+\hspace{1em}ranger-extratrees & 0.115 (0.005) & 0.741 (0.011) & 0.098 & 0.212 & 0.645 & 5.68\\
+\hspace{1em}nn-cox & 0.030 (0.053) & 0.610 (0.092) & 15.851 & 34.4 & 1.194 & 10.5\\
+\hspace{1em}xgboost-aft & -0.854 (0.157) & 0.732 (0.013) & 12.951 & 28.1 & 0.009 & 0.083\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Monoclonal gammopathy; malignancy, n = 1384, p = 8}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.016 (0.011) & 0.660 (0.055) & 0.119 & 0.558 & 0.003 & 0.069\\
+\hspace{1em}aorsf-cph & 0.011 (0.009) & 0.648 (0.034) & 0.626 & 2.94 & 0.044 & 1.02\\
+\hspace{1em}aorsf-fast & 0.011 (0.010) & 0.646 (0.035) & 0.213 & 1.00 & 0.044 & 1.00\\
+\hspace{1em}cif-extension & 0.008 (0.007) & 0.631 (0.024) & 11.659 & 54.8 & 5.776 & 132.5\\
+\hspace{1em}aorsf-net & 0.008 (0.011) & 0.646 (0.034) & 26.190 & 123.1 & 0.044 & 1.01\\
+\hspace{1em}xgboost-cox & 0.008 (0.013) & 0.645 (0.039) & 1.886 & 8.86 & 0.003 & 0.069\\
+\hspace{1em}ranger-extratrees & 0.008 (0.007) & 0.646 (0.033) & 0.071 & 0.334 & 0.888 & 20.4\\
+\hspace{1em}obliqueRSF-net & 0.007 (0.008) & 0.634 (0.031) & 49.465 & 232.5 & 17.992 & 412.8\\
+\hspace{1em}aorsf-random & 0.007 (0.012) & 0.638 (0.033) & 1.737 & 8.16 & 0.046 & 1.06\\
+\hspace{1em}cif-standard & 0.007 (0.008) & 0.632 (0.031) & 1.981 & 9.31 & 6.793 & 155.9\\
+\hspace{1em}nn-cox & -0.005 (0.006) & 0.501 (0.044) & 12.103 & 56.9 & 1.392 & 31.9\\
+\hspace{1em}rsf-standard & -0.009 (0.015) & 0.623 (0.029) & 0.906 & 4.26 & 0.074 & 1.70\\
+\hspace{1em}cif-rotate & -0.026 (0.022) & 0.551 (0.031) & 13.529 & 63.6 & 4.724 & 108.4\\
+\hspace{1em}xgboost-aft & -5.70 (1.21) & 0.634 (0.041) & 11.718 & 55.1 & 0.007 & 0.161\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Movies released in 2015-2018; gross 1M USD, n = 551, p = 46}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.641 (0.024) & 0.943 (0.007) & 23.806 & 89.0 & 6.131 & 105.6\\
+\hspace{1em}glmnet-cox & 0.621 (0.034) & 0.939 (0.010) & 0.200 & 0.747 & 0.004 & 0.069\\
+\hspace{1em}nn-cox & 0.542 (0.072) & 0.905 (0.030) & 22.066 & 82.5 & 1.527 & 26.3\\
+\hspace{1em}aorsf-net & 0.531 (0.027) & 0.928 (0.010) & 68.367 & 255.5 & 0.061 & 1.05\\
+\hspace{1em}aorsf-cph & 0.523 (0.025) & 0.925 (0.011) & 0.812 & 3.04 & 0.060 & 1.04\\
+\hspace{1em}rsf-standard & 0.520 (0.023) & 0.922 (0.011) & 1.205 & 4.50 & 0.105 & 1.81\\
+\hspace{1em}aorsf-fast & 0.515 (0.027) & 0.921 (0.013) & 0.268 & 1.00 & 0.058 & 1.00\\
+\hspace{1em}xgboost-cox & 0.509 (0.025) & 0.931 (0.010) & 13.948 & 52.1 & 0.005 & 0.086\\
+\hspace{1em}cif-standard & 0.475 (0.027) & 0.900 (0.018) & 0.971 & 3.63 & 1.894 & 32.6\\
+\hspace{1em}cif-extension & 0.454 (0.027) & 0.919 (0.013) & 10.381 & 38.8 & 6.372 & 109.8\\
+\hspace{1em}ranger-extratrees & 0.429 (0.022) & 0.897 (0.018) & 0.079 & 0.295 & 0.975 & 16.8\\
+\hspace{1em}obliqueRSF-net & 0.320 (0.026) & 0.907 (0.018) & 157.741 & 589.5 & 27.372 & 471.5\\
+\hspace{1em}aorsf-random & 0.296 (0.034) & 0.844 (0.029) & 1.520 & 5.68 & 0.054 & 0.936\\
+\hspace{1em}xgboost-aft & -0.449 (0.081) & 0.927 (0.011) & 54.157 & 202.4 & 0.009 & 0.155\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Non-alcohol fatty liver disease; death, n = 17549, p = 24}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.217 (0.009) & 0.870 (0.005) & 20.788 & 3.65 & 18.417 & 1.35\\
+\hspace{1em}aorsf-fast & 0.217 (0.009) & 0.870 (0.005) & 5.700 & 1.00 & 13.667 & 1.00\\
+\hspace{1em}aorsf-net & 0.214 (0.008) & 0.866 (0.006) & 502.140 & 88.1 & 10.280 & 0.752\\
+\hspace{1em}obliqueRSF-net & 0.213 (0.008) & 0.870 (0.006) & 1549.268 & 271.8 & 6853.986 & 501.5\\
+\hspace{1em}glmnet-cox & 0.212 (0.009) & 0.862 (0.005) & 2.153 & 0.378 & 1.017 & 0.074\\
+\hspace{1em}rsf-standard & 0.211 (0.009) & 0.861 (0.005) & 13.233 & 2.32 & 1.564 & 0.114\\
+\hspace{1em}cif-standard & 0.209 (0.007) & 0.865 (0.006) & 72.946 & 12.8 & 760.360 & 55.6\\
+\hspace{1em}cif-rotate & 0.194 (0.007) & 0.866 (0.005) & 292.104 & 51.2 & 235.407 & 17.2\\
+\hspace{1em}ranger-extratrees & 0.184 (0.007) & 0.861 (0.005) & 50.579 & 8.87 & 142.725 & 10.4\\
+\hspace{1em}cif-extension & 0.169 (0.002) & 0.867 (0.006) & 128.534 & 22.5 & 214.030 & 15.7\\
+\hspace{1em}aorsf-random & 0.143 (0.007) & 0.840 (0.007) & 17.955 & 3.15 & 21.539 & 1.58\\
+\hspace{1em}xgboost-cox & 0.020 (0.014) & 0.877 (0.005) & 9.073 & 1.59 & 1.098 & 0.080\\
+\hspace{1em}nn-cox & -0.002 (0.012) & 0.570 (0.109) & 59.880 & 10.5 & 334.754 & 24.5\\
+\hspace{1em}xgboost-aft & -7.40 (0.776) & 0.875 (0.006) & 28.666 & 5.03 & 0.807 & 0.059\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Primary biliary cholangitis; death, n = 276, p = 19}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.423 (0.031) & 0.902 (0.022) & 0.080 & 1.00 & 0.020 & 1.00\\
+\hspace{1em}aorsf-cph & 0.411 (0.032) & 0.901 (0.022) & 0.161 & 2.01 & 0.020 & 1.00\\
+\hspace{1em}aorsf-net & 0.405 (0.033) & 0.900 (0.022) & 16.130 & 201.4 & 0.020 & 1.01\\
+\hspace{1em}cif-rotate & 0.395 (0.042) & 0.893 (0.023) & 10.099 & 126.1 & 2.363 & 118.0\\
+\hspace{1em}rsf-standard & 0.383 (0.033) & 0.888 (0.024) & 0.111 & 1.38 & 0.040 & 2.01\\
+\hspace{1em}obliqueRSF-net & 0.360 (0.032) & 0.900 (0.023) & 122.137 & 1,525.3 & 2.067 & 103.3\\
+\hspace{1em}aorsf-random & 0.349 (0.026) & 0.889 (0.021) & 0.373 & 4.65 & 0.020 & 1.00\\
+\hspace{1em}cif-standard & 0.338 (0.033) & 0.895 (0.026) & 0.260 & 3.25 & 1.471 & 73.5\\
+\hspace{1em}cif-extension & 0.336 (0.031) & 0.893 (0.024) & 11.191 & 139.8 & 4.839 & 241.7\\
+\hspace{1em}glmnet-cox & 0.336 (0.050) & 0.882 (0.029) & 0.121 & 1.51 & 0.002 & 0.100\\
+\hspace{1em}ranger-extratrees & 0.264 (0.026) & 0.886 (0.029) & 0.030 & 0.377 & 0.041 & 2.05\\
+\hspace{1em}xgboost-cox & 0.242 (0.110) & 0.875 (0.024) & 4.640 & 58.0 & 0.002 & 0.100\\
+\hspace{1em}nn-cox & -0.024 (0.019) & 0.613 (0.174) & 11.186 & 139.7 & 0.252 & 12.6\\
+\hspace{1em}xgboost-aft & -0.969 (0.333) & 0.877 (0.022) & 9.772 & 122.0 & 0.006 & 0.300\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Rotterdam tumor bank; death, n = 2982, p = 11}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.164 (0.012) & 0.760 (0.009) & 154.345 & 134.0 & 0.397 & 0.395\\
+\hspace{1em}obliqueRSF-net & 0.162 (0.010) & 0.759 (0.009) & 554.274 & 481.3 & 124.158 & 123.4\\
+\hspace{1em}aorsf-cph & 0.160 (0.012) & 0.757 (0.010) & 2.673 & 2.32 & 0.909 & 0.904\\
+\hspace{1em}aorsf-fast & 0.158 (0.013) & 0.755 (0.010) & 1.152 & 1.00 & 1.006 & 1.00\\
+\hspace{1em}cif-standard & 0.158 (0.010) & 0.757 (0.009) & 8.251 & 7.16 & 47.391 & 47.1\\
+\hspace{1em}rsf-standard & 0.156 (0.014) & 0.754 (0.009) & 3.058 & 2.66 & 0.277 & 0.276\\
+\hspace{1em}aorsf-random & 0.151 (0.010) & 0.750 (0.010) & 5.985 & 5.20 & 0.414 & 0.411\\
+\hspace{1em}cif-rotate & 0.150 (0.012) & 0.752 (0.012) & 34.744 & 30.2 & 29.541 & 29.4\\
+\hspace{1em}ranger-extratrees & 0.139 (0.005) & 0.747 (0.009) & 3.357 & 2.91 & 2.866 & 2.85\\
+\hspace{1em}xgboost-cox & 0.131 (0.014) & 0.753 (0.009) & 5.214 & 4.53 & 0.019 & 0.019\\
+\hspace{1em}cif-extension & 0.131 (0.005) & 0.750 (0.009) & 26.506 & 23.0 & 30.945 & 30.7\\
+\hspace{1em}glmnet-cox & 0.118 (0.009) & 0.731 (0.010) & 0.770 & 0.668 & 0.018 & 0.018\\
+\hspace{1em}nn-cox & -0.003 (0.009) & 0.521 (0.036) & 17.492 & 15.2 & 8.753 & 8.70\\
+\hspace{1em}xgboost-aft & -1.33 (0.121) & 0.760 (0.007) & 14.435 & 12.5 & 0.010 & 0.010\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Rotterdam tumor bank; recurrence, n = 2982, p = 11}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.147 (0.013) & 0.736 (0.011) & 547.423 & 368.6 & 134.826 & 288.4\\
+\hspace{1em}aorsf-net & 0.146 (0.014) & 0.735 (0.011) & 170.103 & 114.5 & 0.431 & 0.923\\
+\hspace{1em}cif-standard & 0.144 (0.013) & 0.734 (0.011) & 5.107 & 3.44 & 32.549 & 69.6\\
+\hspace{1em}aorsf-cph & 0.143 (0.014) & 0.734 (0.011) & 3.336 & 2.25 & 0.462 & 0.988\\
+\hspace{1em}aorsf-fast & 0.142 (0.014) & 0.732 (0.011) & 1.485 & 1.00 & 0.467 & 1.00\\
+\hspace{1em}aorsf-random & 0.139 (0.013) & 0.730 (0.011) & 4.762 & 3.21 & 0.428 & 0.916\\
+\hspace{1em}rsf-standard & 0.138 (0.014) & 0.731 (0.011) & 3.256 & 2.19 & 0.285 & 0.609\\
+\hspace{1em}ranger-extratrees & 0.135 (0.009) & 0.734 (0.011) & 4.162 & 2.80 & 3.054 & 6.53\\
+\hspace{1em}cif-rotate & 0.130 (0.012) & 0.727 (0.011) & 37.933 & 25.5 & 38.363 & 82.1\\
+\hspace{1em}cif-extension & 0.119 (0.007) & 0.731 (0.011) & 23.917 & 16.1 & 28.877 & 61.8\\
+\hspace{1em}glmnet-cox & 0.117 (0.009) & 0.727 (0.010) & 0.788 & 0.531 & 0.027 & 0.058\\
+\hspace{1em}xgboost-cox & 0.112 (0.008) & 0.730 (0.011) & 3.856 & 2.60 & 0.021 & 0.045\\
+\hspace{1em}nn-cox & -0.002 (0.002) & 0.536 (0.072) & 23.903 & 16.1 & 11.126 & 23.8\\
+\hspace{1em}xgboost-aft & -1.01 (0.126) & 0.734 (0.011) & 17.639 & 11.9 & 0.010 & 0.022\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Serum free light chain; death, n = 7874, p = 10}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.253 (0.017) & 0.825 (0.009) & 2.773 & 1.00 & 3.620 & 1.00\\
+\hspace{1em}aorsf-cph & 0.253 (0.016) & 0.825 (0.010) & 7.965 & 2.87 & 5.799 & 1.60\\
+\hspace{1em}aorsf-net & 0.252 (0.014) & 0.823 (0.009) & 341.019 & 123.0 & 5.805 & 1.60\\
+\hspace{1em}glmnet-cox & 0.250 (0.014) & 0.820 (0.008) & 1.330 & 0.480 & 0.093 & 0.026\\
+\hspace{1em}obliqueRSF-net & 0.249 (0.013) & 0.821 (0.009) & 1185.401 & 427.5 & 803.301 & 221.9\\
+\hspace{1em}ranger-extratrees & 0.246 (0.011) & 0.821 (0.008) & 17.067 & 6.15 & 13.889 & 3.84\\
+\hspace{1em}rsf-standard & 0.245 (0.015) & 0.816 (0.009) & 4.618 & 1.67 & 0.575 & 0.159\\
+\hspace{1em}cif-standard & 0.245 (0.013) & 0.818 (0.009) & 20.846 & 7.52 & 162.079 & 44.8\\
+\hspace{1em}aorsf-random & 0.235 (0.013) & 0.818 (0.010) & 9.661 & 3.48 & 5.046 & 1.39\\
+\hspace{1em}cif-rotate & 0.228 (0.009) & 0.819 (0.008) & 71.056 & 25.6 & 137.166 & 37.9\\
+\hspace{1em}cif-extension & 0.203 (0.005) & 0.821 (0.008) & 46.895 & 16.9 & 184.798 & 51.0\\
+\hspace{1em}xgboost-cox & 0.095 (0.042) & 0.824 (0.009) & 6.667 & 2.40 & 0.098 & 0.027\\
+\hspace{1em}nn-cox & 0.004 (0.007) & 0.664 (0.116) & 30.033 & 10.8 & 32.325 & 8.93\\
+\hspace{1em}xgboost-aft & -2.73 (0.324) & 0.823 (0.009) & 23.886 & 8.61 & 0.035 & 0.010\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{sim}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.044 (0.015) & 0.649 (0.027) & 227.140 & 172.6 & 89.309 & 1.82\\
+\hspace{1em}aorsf-cph & 0.043 (0.015) & 0.653 (0.025) & 3.021 & 2.30 & 51.086 & 1.04\\
+\hspace{1em}aorsf-fast & 0.039 (0.016) & 0.654 (0.025) & 1.316 & 1.00 & 48.973 & 1.00\\
+\hspace{1em}aorsf-random & 0.034 (0.011) & 0.631 (0.027) & 7.939 & 6.03 & 87.358 & 1.78\\
+\hspace{1em}obliqueRSF-net & 0.034 (0.012) & 0.632 (0.030) & 930.202 & 707.0 & 388.323 & 7.93\\
+\hspace{1em}cif-standard & 0.029 (0.011) & 0.622 (0.029) & 7.953 & 6.04 & 282.681 & 5.77\\
+\hspace{1em}cif-rotate & 0.029 (0.016) & 0.614 (0.038) & 342.777 & 260.5 & 714.891 & 14.6\\
+\hspace{1em}rsf-standard & 0.024 (0.010) & 0.623 (0.021) & 5.085 & 3.86 & 2.070 & 0.042\\
+\hspace{1em}ranger-extratrees & 0.021 (0.006) & 0.637 (0.025) & 4.566 & 3.47 & 6.406 & 0.131\\
+\hspace{1em}cif-extension & 0.018 (0.006) & 0.617 (0.027) & 107.534 & 81.7 & 1067.369 & 21.8\\
+\hspace{1em}glmnet-cox & -0.003 (0.038) & 0.637 (0.027) & 0.552 & 0.420 & 1.597 & 0.033\\
+\hspace{1em}xgboost-cox & -0.005 (0.036) & 0.633 (0.029) & 16.874 & 12.8 & 1.507 & 0.031\\
+\hspace{1em}nn-cox & -0.032 (0.051) & 0.639 (0.024) & 37.356 & 28.4 & 20.600 & 0.421\\
+\hspace{1em}xgboost-aft & -1.65 (0.119) & 0.642 (0.025) & 50.341 & 38.3 & 1.301 & 0.027\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{SPRINT; CVD death, n = 9361, p = 174}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.070 (0.007) & 0.794 (0.012) & 340.154 & 104.7 & 0.934 & 0.970\\
+\hspace{1em}aorsf-cph & 0.070 (0.006) & 0.796 (0.011) & 10.101 & 3.11 & 0.971 & 1.01\\
+\hspace{1em}glmnet-cox & 0.069 (0.012) & 0.793 (0.010) & 14.356 & 4.42 & 0.035 & 0.036\\
+\hspace{1em}aorsf-fast & 0.069 (0.006) & 0.795 (0.010) & 3.248 & 1.00 & 0.963 & 1.00\\
+\hspace{1em}obliqueRSF-net & 0.068 (0.005) & 0.795 (0.012) & 1222.666 & 376.4 & 1319.126 & 1,369.4\\
+\hspace{1em}rsf-standard & 0.064 (0.007) & 0.785 (0.015) & 5.389 & 1.66 & 0.654 & 0.679\\
+\hspace{1em}cif-standard & 0.061 (0.004) & 0.795 (0.011) & 50.214 & 15.5 & 199.723 & 207.3\\
+\hspace{1em}cif-rotate & 0.060 (0.005) & 0.787 (0.010) & 1115.642 & 343.5 & 139.444 & 144.8\\
+\hspace{1em}ranger-extratrees & 0.054 (0.004) & 0.790 (0.013) & 7.376 & 2.27 & 9.679 & 10.0\\
+\hspace{1em}nn-cox & 0.043 (0.010) & 0.765 (0.016) & 24.813 & 7.64 & 35.150 & 36.5\\
+\hspace{1em}cif-extension & 0.034 (0.002) & 0.786 (0.011) & 125.227 & 38.6 & 53.842 & 55.9\\
+\hspace{1em}aorsf-random & 0.026 (0.003) & 0.743 (0.018) & 6.889 & 2.12 & 1.101 & 1.14\\
+\hspace{1em}xgboost-cox & 0.010 (0.016) & 0.796 (0.010) & 7.945 & 2.45 & 0.033 & 0.034\\
+\hspace{1em}xgboost-aft & -10.7 (0.988) & 0.792 (0.011) & 28.849 & 8.88 & 0.017 & 0.018\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{SPRINT; death, n = 9361, p = 174}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.125 (0.010) & 0.771 (0.010) & 4.785 & 0.846 & 0.079 & 0.013\\
+\hspace{1em}aorsf-cph & 0.119 (0.007) & 0.770 (0.009) & 14.349 & 2.54 & 3.891 & 0.624\\
+\hspace{1em}aorsf-fast & 0.119 (0.007) & 0.771 (0.008) & 5.654 & 1.00 & 6.238 & 1.00\\
+\hspace{1em}aorsf-net & 0.115 (0.007) & 0.769 (0.009) & 663.058 & 117.3 & 4.744 & 0.760\\
+\hspace{1em}obliqueRSF-net & 0.114 (0.006) & 0.768 (0.008) & 3192.241 & 564.6 & 1289.532 & 206.7\\
+\hspace{1em}rsf-standard & 0.112 (0.006) & 0.763 (0.008) & 6.376 & 1.13 & 0.728 & 0.117\\
+\hspace{1em}cif-standard & 0.108 (0.006) & 0.765 (0.009) & 46.063 & 8.15 & 211.693 & 33.9\\
+\hspace{1em}nn-cox & 0.103 (0.011) & 0.758 (0.009) & 95.278 & 16.9 & 85.933 & 13.8\\
+\hspace{1em}ranger-extratrees & 0.098 (0.004) & 0.758 (0.009) & 9.978 & 1.76 & 11.653 & 1.87\\
+\hspace{1em}cif-rotate & 0.093 (0.005) & 0.746 (0.009) & 1057.791 & 187.1 & 188.939 & 30.3\\
+\hspace{1em}cif-extension & 0.056 (0.002) & 0.748 (0.009) & 138.879 & 24.6 & 110.890 & 17.8\\
+\hspace{1em}aorsf-random & 0.053 (0.003) & 0.720 (0.010) & 14.509 & 2.57 & 5.249 & 0.841\\
+\hspace{1em}xgboost-cox & 0.033 (0.022) & 0.772 (0.008) & 11.262 & 1.99 & 0.090 & 0.014\\
+\hspace{1em}xgboost-aft & -4.40 (0.306) & 0.772 (0.008) & 32.854 & 5.81 & 0.719 & 0.115\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Systolic Heart Failure; death, n = 2231, p = 41}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.113 (0.015) & 0.745 (0.012) & 0.833 & 0.568 & 0.019 & 0.080\\
+\hspace{1em}obliqueRSF-net & 0.113 (0.014) & 0.746 (0.012) & 419.889 & 286.1 & 60.875 & 254.5\\
+\hspace{1em}cif-rotate & 0.113 (0.016) & 0.741 (0.011) & 72.369 & 49.3 & 22.019 & 92.1\\
+\hspace{1em}aorsf-net & 0.111 (0.015) & 0.743 (0.012) & 123.021 & 83.8 & 0.242 & 1.01\\
+\hspace{1em}cif-standard & 0.109 (0.013) & 0.743 (0.012) & 5.397 & 3.68 & 23.166 & 96.9\\
+\hspace{1em}aorsf-fast & 0.108 (0.018) & 0.743 (0.011) & 1.468 & 1.00 & 0.239 & 1.00\\
+\hspace{1em}aorsf-cph & 0.107 (0.016) & 0.742 (0.011) & 3.011 & 2.05 & 0.239 & 1.00\\
+\hspace{1em}rsf-standard & 0.105 (0.013) & 0.736 (0.010) & 3.688 & 2.51 & 0.734 & 3.07\\
+\hspace{1em}cif-extension & 0.095 (0.006) & 0.744 (0.012) & 31.103 & 21.2 & 18.063 & 75.5\\
+\hspace{1em}xgboost-cox & 0.092 (0.009) & 0.745 (0.010) & 4.791 & 3.26 & 0.010 & 0.042\\
+\hspace{1em}ranger-extratrees & 0.090 (0.009) & 0.735 (0.012) & 4.377 & 2.98 & 1.483 & 6.20\\
+\hspace{1em}aorsf-random & 0.081 (0.005) & 0.729 (0.010) & 3.206 & 2.18 & 0.231 & 0.964\\
+\hspace{1em}nn-cox & 0.079 (0.026) & 0.712 (0.021) & 24.930 & 17.0 & 5.889 & 24.6\\
+\hspace{1em}xgboost-aft & -2.03 (0.186) & 0.741 (0.008) & 14.681 & 10.0 & 0.500 & 2.09\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{VA lung cancer trial; death, n = 137, p = 8}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.198 (0.045) & 0.789 (0.036) & 0.058 & 1.00 & 0.013 & 1.00\\
+\hspace{1em}aorsf-cph & 0.197 (0.049) & 0.789 (0.039) & 0.104 & 1.78 & 0.013 & 0.994\\
+\hspace{1em}aorsf-net & 0.197 (0.044) & 0.789 (0.037) & 10.595 & 181.7 & 0.013 & 0.994\\
+\hspace{1em}cif-rotate & 0.196 (0.061) & 0.782 (0.039) & 5.268 & 90.3 & 1.148 & 87.7\\
+\hspace{1em}rsf-standard & 0.174 (0.048) & 0.780 (0.042) & 0.086 & 1.47 & 0.032 & 2.41\\
+\hspace{1em}cif-extension & 0.171 (0.047) & 0.788 (0.036) & 5.560 & 95.3 & 1.611 & 123.1\\
+\hspace{1em}glmnet-cox & 0.155 (0.031) & 0.781 (0.038) & 0.093 & 1.59 & 0.002 & 0.153\\
+\hspace{1em}aorsf-random & 0.154 (0.046) & 0.773 (0.042) & 0.225 & 3.86 & 0.012 & 0.918\\
+\hspace{1em}cif-standard & 0.128 (0.037) & 0.764 (0.037) & 0.097 & 1.67 & 0.122 & 9.33\\
+\hspace{1em}obliqueRSF-net & 0.125 (0.035) & 0.791 (0.029) & 66.665 & 1,143.0 & 0.709 & 54.2\\
+\hspace{1em}ranger-extratrees & 0.091 (0.037) & 0.779 (0.041) & 0.025 & 0.433 & 0.031 & 2.37\\
+\hspace{1em}xgboost-cox & 0.041 (0.070) & 0.736 (0.053) & 0.809 & 13.9 & 0.002 & 0.153\\
+\hspace{1em}nn-cox & -0.040 (0.041) & 0.481 (0.058) & 11.874 & 203.6 & 0.148 & 11.3\\
+\hspace{1em}xgboost-aft & -0.042 (0.142) & 0.748 (0.049) & 7.545 & 129.4 & 0.006 & 0.459\\*
 \end{longtable}

### 2022-06-11 paper/paper-old.Rmd
slides first draft

--- 2022-05-09 index.Rmd
@@
 1.  accelerated oblique random survival forests {`aorsf`}
-1. original oblique random survival forests {`obliqueRSF`}
-1. axis-based random survival forests {`randomForestSRC` & `ranger`}
-1. axis-based conditional inference forests {`party`}
-1. gradient boosted decision trees {`xgboost`}
+2.  original oblique random survival forests {`obliqueRSF`}
+3.  axis-based random survival forests {`randomForestSRC` & `ranger`}
+4.  axis-based conditional inference forests {`party`}
+5.  gradient boosted decision trees {`xgboost`}
 
-__Note__ Presently, the original oblique random survival forest is not included in the benchmark results.
+**Note** Presently, the original oblique random survival forest is not included in the benchmark results.
 This is because the original oblique random survival forest runs very slowly, turning a 10-minute benchmark into a 6 hour benchmark.
@@
 
-__Note__ {`xgboost`} requires careful tuning to obtain ideal performance.
+**Note** {`xgboost`} requires careful tuning to obtain ideal performance.
 While we do tune the number of boosting steps in this benchmark, we do not go beyond that and instead use default setting for hyper-parameters.
@@
 
-1. `ANOVA importance`: A method introduced by Menze et al. This is computed using an accelerated oblique random survival forest model.
+2.  `ANOVA importance`: A method introduced by Menze et al. This is computed using an accelerated oblique random survival forest model.
 
-1. `SHAP importance`: A method introduced by Lundberg et al. SHAP importance is widely regarded as a gold standard due to its excellent asymptotic properties. This is computed using a boosting model.
+3.  `SHAP importance`: A method introduced by Lundberg et al. SHAP importance is widely regarded as a gold standard due to its excellent asymptotic properties. This is computed using a boosting model.
 
-1. `Permutation importance`: A method introduced by Leo Breiman. This is computed using a standard random survival forest model.
+4.  `Permutation importance`: A method introduced by Leo Breiman. This is computed using a standard random survival forest model.
 
-__Evaluation of variable importance techniques__: VI techniques are compared based on their discrimination (C-statistic) between relevant and irrelevant predictor variables.
+**Evaluation of variable importance techniques**: VI techniques are compared based on their discrimination (C-statistic) between relevant and irrelevant predictor variables.
 The relevant predictor variables are those that have a relationship to the outcome, and the irrelevant variables are those with no relationship to the outcome.
@@
 
-__Details on C-statistic computation:__ The C-statistic for VI is not the same thing as the C-statistic for prediction accuracy.
+**Details on C-statistic computation:** The C-statistic for VI is not the same thing as the C-statistic for prediction accuracy.
 Since relevance of a variable is binary, the C-statistic for VI is computed using `yardstick::roc_auc`, which wraps `pROC::roc`.
@@
 
-__Mean and standard deviation__ The multivariate normal distribution that generated values for the predictor matrix had a mean of zero and standard deviation of 1 for each variable.
+**Mean and standard deviation** The multivariate normal distribution that generated values for the predictor matrix had a mean of zero and standard deviation of 1 for each variable.
 
-__Correlation__: The correlation among $z$ variables was allowed to be non-zero as was the correlation among $x$ variables and the correlation between $x$ and $z$ variables.
+**Correlation**: The correlation among $z$ variables was allowed to be non-zero as was the correlation among $x$ variables and the correlation between $x$ and $z$ variables.
 For all non-zero correlations, a value was selected at random uniformly between a lower and upper boundary.
@@
 
-__Effect sizes__: A total effect of 6 was distributed evenly across each predictor group.
+**Effect sizes**: A total effect of 6 was distributed evenly across each predictor group.
 For example, with a total of $k$ linear effect predictors (i.e., the $x$ variables), the increase in log-hazard associated with a 1 unit increased in each $x$ variable was $6 / 25 = 0.24$, i.e., about a 27% increase in relative risk.
 
-__Outcomes__: A censored outcome variable was generated with the `simsurv::simsurv()` function using a predictor matrix that included all relevant predictors.
+**Outcomes**: A censored outcome variable was generated with the `simsurv::simsurv()` function using a predictor matrix that included all relevant predictors.
 After the outcome was generated the interactions, non-linear transformations, and linear combinations of relevant predictors were dropped from the data.
@@
 
-__Data generation__: There are no tests for this step, just a glimpse of the simulated set of data.
+**Data generation**: There are no tests for this step, just a glimpse of the simulated set of data.
 
@@
 
-__Column means__: This test verifies that the mean of each predictor is close to zero, and that roughly 45% of outcomes were censored.
+**Column means**: This test verifies that the mean of each predictor is close to zero, and that roughly 45% of outcomes were censored.
 
@@
 
-__Effects detected__: This test verifies that, when the oracle model is used, an effect is only detected for variables that have a relationship to the outcome.
+**Effects detected**: This test verifies that, when the oracle model is used, an effect is only detected for variables that have a relationship to the outcome.
 
@@
 
-__Effect size estimation for linear effects__: This test verifies that, when the oracle model is used, the estimated effect sizes for variables with linear effects are consistent with the effect sizes used to simulate the data.
+**Effect size estimation for linear effects**: This test verifies that, when the oracle model is used, the estimated effect sizes for variables with linear effects are consistent with the effect sizes used to simulate the data.
 
@@
 
-__Effect size estimation for non-linear effects__: This test verifies that, when the oracle model is used, the estimated effect sizes for variables with non-linear effects are consistent with the effect sizes used to simulate the data.
+**Effect size estimation for non-linear effects**: This test verifies that, when the oracle model is used, the estimated effect sizes for variables with non-linear effects are consistent with the effect sizes used to simulate the data.
 
@@
 
-Overall, {`aorsf`} had the highest prognostic accuracy (__Table 1__), obtaining the highest C-statistic and scaled brier score in each of the three datasets.
+Overall, {`aorsf`} had the highest prognostic accuracy (**Table 1**), obtaining the highest C-statistic and scaled brier score in each of the three datasets.
 In addition, {`aorsf`} grew tree ensembles about 10 times as fast as {`ranger`} and generated predictions about 25 times as fast as {`party`}.
@@
 
-__Table 1__ Prognostic accuracy and computational efficiency of machine learning algorithms applied to real and simulated data.
+**Table 1** Prognostic accuracy and computational efficiency of machine learning algorithms applied to real and simulated data.
 
@@
 
-__Table 2__: Discrimination between relevant and irrelevant predictor variables for each VI technique in .
+**Table 2**: Discrimination between relevant and irrelevant predictor variables for each VI technique in .
 Cells that are highlighted with a light blue color indicate which variable importance technique had the best discrimination for a given sample size, correlation setting, and variable type.
@@
 
-1. Source for `rotterdam` data: Patrick Royston and Douglas Altman, External validation of a Cox prognostic model: principles and methods. BMC Medical Research Methodology 2013, 13:33
+2.  Source for `rotterdam` data: Patrick Royston and Douglas Altman, External validation of a Cox prognostic model: principles and methods. BMC Medical Research Methodology 2013, 13:33

### 2022-06-11 R/bench_vi_summarize.R

@@ -5,23 +5,7 @@
 #' @title
 #' @param bm_vi_comb
 #' @param bm_pred_comb
-bench_vi_summarize <- function(bm_pred_comb, bm_vi_comb) {
-
-
-  bm_pred_comb |>
-    mutate(
-      data = if_else(
-        data == 'sim',
-        paste(data, n_obs, n_z, correlated_x, sep = '_'),
-        data
-      )
-    ) |>
-    group_by(model, data) |>
-    summarize(across(.cols = c(cstat, IPA, time_fit, time_prd),
-                     .fns = median)) |>
-    arrange(data, desc(cstat))
-
-  group_by(model, data, )
+bench_vi_summarize <- function(bm_vi_comb) {
 
   bm_vi_comb |>
     group_by(model, xcorr, n_obs, n_z) |>
@@ -29,8 +13,7 @@ bench_vi_summarize <- function(bm_pred_comb, bm_vi_comb) {
     arrange(xcorr, n_obs, n_z, desc(overall)) |>
     group_by(xcorr, n_obs, n_z) |>
     mutate(
-      overall_disc = (overall - .5) * 2,
-      overall_prop = overall_disc / overall_disc[1],
+      overall_prop = overall[1] / overall,
       .after = 'overall'
     )
 

### 2022-06-11 R/model_fit.R

@@ -22,6 +22,107 @@
 #
 # }
 
+rotsf_fit <- function(train, node_size = 10, ...){
+
+  mtry <- round(sqrt(ncol(train)-2))
+
+  train_onehot <- model.matrix(~. -1L, data = train) |>
+    as.data.frame()
+
+  start_time <- Sys.time()
+
+  fit <- rotsfpca(
+    formula = Surv(time, status) ~ .,
+    data = train_onehot
+  )
+
+  end_time <- Sys.time()
+
+  list(fit = fit, time_fit = end_time - start_time)
+
+}
+
+rsfse_fit <- function(train, node_size = 10, ...){
+
+  mtry <- round(sqrt(ncol(train)-2))
+
+  train_onehot <- model.matrix(~. -1L, data = train) |>
+    as.data.frame()
+
+  start_time <- Sys.time()
+
+  xnames <- setdiff(names(train_onehot), c('time', 'status'))
+
+  fit <- rsfes(
+    x = train_onehot[, xnames],
+    y = Surv(time = train_onehot$time,
+             event = train_onehot$status)
+  )
+
+  end_time <- Sys.time()
+
+  list(fit = fit, time_fit = end_time - start_time)
+
+}
+
+aorsf_cph_1_filter_fit <- function(train, node_size = 10, ...){
+
+  mtry <- round(sqrt(ncol(train)-2))
+
+  split_min_events <- min( round(sum(train$status) / 5), 5)
+
+  start_time <- Sys.time()
+
+  # fit_filter <- orsf(
+  #   data_train = train,
+  #   formula = Surv(time, status) ~ .,
+  #   n_tree = 100,
+  #   mtry = mtry,
+  #   n_retry = 3,
+  #   split_min_obs = node_size,
+  #   split_min_events = split_min_events,
+  #   control = orsf_control_cph(iter_max = 1,
+  #                              do_scale = FALSE),
+  #   oobag_pred = FALSE
+  # )
+  #
+  # vi <- orsf_vi_anova(fit_filter)
+  #
+  # n_keep <- round( length(vi) * 0.75 )
+  #
+  # keep <- c('time', 'status', names(vi)[seq(n_keep)])
+  #
+  # fit <- orsf(
+  #   data_train = train[, keep],
+  #   formula = Surv(time, status) ~ .,
+  #   mtry = mtry,
+  #   n_retry = 3,
+  #   split_min_obs = node_size,
+  #   split_min_events = split_min_events,
+  #   control = orsf_control_cph(iter_max = 1,
[…]

### 2022-06-11 R/model_key.R

@@ -10,9 +10,12 @@ make_model_key <- function() {
     term = c(
       "aorsf_cph_1",
       "aorsf_cph_15",
+      "aorsf_cph_1_filter",
       "aorsf_random",
       "aorsf_net",
       "obliqueRSF",
+      "rsfse",
+      "rotsf",
       "cif",
       "cox_net",
       "coxtime",
@@ -22,17 +25,20 @@ make_model_key <- function() {
       "ranger"
     ),
     label = c(
-      "aorsf-cph(maxit = 1)",
-      "aorsf-cph(maxit = 15)",
+      "aorsf-fast",
+      "aorsf-cph",
+      "aorsf-filter",
       "aorsf-random",
       "aorsf-net",
       "obliqueRSF-net",
-      "party-cif",
+      "cif-extension",
+      "cif-rotate",
+      "cif-standard",
       "glmnet-cox",
       "nn-cox",
       "xgboost-cox",
       "xgboost-aft",
-      "rfsrc-standard",
+      "rsf-standard",
       "ranger-extratrees"
     ),
   )

### 2022-06-11 R/sim_surv.R

@@ -59,7 +59,7 @@ sim_surv <- function(n_obs = 2500,
 
     # Make the Z variables correlate with the others
 
-    mat_covar[x_names, z_names] <-
+    mat_covar[z_names, x_names] <-
       runif(n = n_z * n_x,
             min = -correlated_x,
             max = correlated_x)
@@ -201,11 +201,11 @@ sim_surv <- function(n_obs = 2500,
   betas <- vector(mode = 'numeric', length = ncol(covs))
   names(betas) <- names(covs)
 
-  if(n_x > 0)  x_effect   <- effect_size_by_group / n_x else x_effect   <- 0
-  if(n_g > 0)  int_effect <- effect_size_by_group / n_g else int_effect <- 0
-  if(n_w > 0)  nl_effect  <- effect_size_by_group / n_w else nl_effect  <- 0
-  if(n_v > 0)  lc_effect  <- effect_size_by_group / n_v else lc_effect  <- 0
-  if(n_c > 0)  c_effect   <- effect_size_by_group / n_c else c_effect   <- 0
+  if(n_x>0) x_effect   <- effect_size_by_group*1 / n_x else x_effect   <- 0
+  if(n_g>0) int_effect <- effect_size_by_group*2 / n_g else int_effect <- 0
+  if(n_w>0) nl_effect  <- effect_size_by_group*2 / n_w else nl_effect  <- 0
+  if(n_v>0) lc_effect  <- effect_size_by_group*2 / n_v else lc_effect  <- 0
+  if(n_c>0) c_effect   <- effect_size_by_group*1 / n_c else c_effect   <- 0
 
   betas[str_detect(names(betas), '^x')] <- x_effect
 

### 2022-06-11 R/simplify_levels.R

@@ -1,0 +1,11 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param fctr
+simplify_levels <- function(fctr){
+  levels_current <- levels(fctr)
+  levels_simple <- letters[seq_along(levels_current)]
+  factor(fctr, levels = levels_current, labels = levels_simple)
+}

### 2022-06-11 R/summarize_data_source.R

@@ -4,43 +4,18 @@
 #'
 #' @title
 #' @param x
-summarize_data_source <- function() {
+summarize_data_source <- function(analyses_real) {
 
 
-  funs <- list(
-    accord_acm      = accord_acm_load,
-    accord_cvd      = accord_cvd_load,
-    actg_aids       = actg_aids_load,
-    actg_death      = actg_death_load,
-    breast          = breast_load,
-    colon_acm       = colon_acm_load,
-    colon_recur     = colon_recur_load,
-    flchain         = flchain_load,
-    follic_death    = follic_death_load,
-    follic_relapse  = follic_relapse_load,
-    gbsg2           = gbsg2_load,
-    guide_it_hfhosp = guide_it_hfhosp_load,
-    guide_it_cvd    = guide_it_cvd_load,
-    mgus2_death     = mgus2_death_load,
-    mgus2_pcm       = mgus2_pcm_load,
-    nafld           = nafld_load,
-    pbc_orsf        = pbc_orsf_load,
-    peakV02         = peakV02_load,
-    phts            = phts_load,
-    rotterdam_acm   = rotterdam_acm_load,
-    rotterdam_recur = rotterdam_recur_load,
-    sprint_acm      = sprint_acm_load,
-    sprint_cvd      = sprint_cvd_load,
-    time_to_million = time_to_million_load,
-    vdv             = vdv_load,
-    veteran         = veteran_load
-  )
+  funs <- analyses_real |>
+    distinct(data_source, data_load_fun) |>
+    deframe()
 
   data_info <- map_dfr(
     .x = funs,
     .f = function(f){
 
-      .x <- f()
+      .x <- do.call(what = as.character(f), args = list())
 
       list(
         nrow = nrow(.x),
@@ -53,9 +28,6 @@ summarize_data_source <- function() {
     },
     .id = 'data'
   )
-
-
-
 
   data_info |>
     mutate(
@@ -179,30 +151,6 @@ summarize_data_source <- function() {
       .before = 2
     )
 
-  # data_info |>
-  #   mutate(
-  #     label = recode(
-  #       data,
-  #       vdv = "Van't Veer LJ (2002); breast cancer",
-  #       veteran = "Kalbfleisch JD (1980); lung cancer",
-  #       colon = "Laurie JA (1989); colon cancer",
[…]

### 2022-06-12 docs/index.Rmd
up to 25 slides

@@
 ---
-class: center, middle
-background-image: url("img/meme_slow_R.jpg")
-background-size: contain
 
@@
 library(table.glue)
-library(xaringanExtra)
 
-# infinite moon reader doesn't like targets,
-# this commented code sets up files that work for infinite moon reader
-# tar_load(
-#   names = c(
-#     bm_pred_model_viz,
-#     bm_pred_time_viz,
-#     bm_pred_viz,
-#     data_key
-#   )
-# )
-# 
-# write_rds(bm_pred_model_viz, "docs/index_files/bm_pred_model_viz.rds")
-# write_rds(bm_pred_time_viz, "docs/index_files/bm_pred_time_viz.rds")
-# write_rds(bm_pred_viz, "docs/index_files/bm_pred_viz.rds")
-# write_rds(data_key, "docs/index_files/data_key.rds")
-
-bm_pred_model_viz <- read_rds('index_files/bm_pred_model_viz.rds')
-bm_pred_time_viz <- read_rds('index_files/bm_pred_time_viz.rds')
-bm_pred_viz <- read_rds('index_files/bm_pred_viz.rds')
-data_key <- read_rds('index_files/data_key.rds')
+tar_load(
+  names = c(
+    bm_pred_model_viz,
+    bm_pred_time_viz,
+    bm_pred_viz,
+    data_key
+  )
+)
 
@@
 ```
-
----
 
@@
 - Can be used for classification, regression, and survival analysis.
-
-##
 
@@
 
+Jaeger showed in general benchmarks that the oblique RSF had higher prediction accuracy than axis-based RSFs.
+However, the obliqueRSF R package is hundreds of times slower than standard R packages for axis based RSFs.
+
 .footnote[<sup>7</sup>Jaeger BC, et al. "Oblique random survival forests." The Annals of Applied Statistics 13.3 (2019): 1847-1883.]
+
+---
+class: center, middle
+background-image: url("img/meme_slow_R.jpg")
+background-size: contain
 
@@
 ---
-## Data sets contd.
+## Data sets continued
 
@@
 
-## Data sets contd.
+## Data sets continued
 
@@
 
-```{r bm_pred_time_viz, fig.height=6.5, fig.width=8}
+```{r bm_pred_time_ridges, fig.height=6.5, fig.width=8}
 bm_pred_time_viz

### 2022-06-14 docs/index.Rmd
moving slides to bonus

@@
 
-Consider the usual framework for survival analysis:
-$$\mathcal{D}_{\text{train}} = \left\{ (T_i, \delta_i, x_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$
-- $T_i$ is the event time if $\delta_i=1$ and last point of contact if $\delta_i=0$,
+We identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model: $$L(\beta) = \prod_{i=1}^m \frac{e^{x_{j(i)}^{'} \beta}}{\sum_{j \in R_i} e^{x_j^{'} \beta}}$$
 
@@
 
-Let $t_1 < \, \ldots \, < t_m$ denote the $m$ unique event times in $\mathcal{D}_{\text{train}}$
+- $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (i.e., those still at risk at time $t_i$)
 
----
-
-## Accelerating the oblique RSF
-
-We identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model: $$L(\beta) = \prod_{i=1}^m \frac{e^{x_{j(i)}^T \beta}}{\sum_{j \in R_i} e^{x_j^T \beta}}$$
-
-- $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (i.e., those still at risk at time $t_i$)
+- $t_1 < \, \ldots \, < t_m$ are the $m$ unique event times in the training data.
 
@@
 
-- .rainbow-text[_aorsf-fast_]: the fast version of aorsf
+- .rainbow-text[_aorsf-fast_]: this is the only oblique RSF we show in the racing model plots.
 
@@
 ## Data sets
+
+A total of 23 risk prediction tasks in 16 data sets were analyzed.
+
+- number of observations ranged from `r min(data_key$nrow)` to `r max(data_key$nrow)` (median = `r median(data_key$nrow)`)
+
+- number of predictors ranged from `r min(data_key$ncol)` to `r max(data_key$ncol)` (median = `r median(data_key$ncol)`)
+
+- % censored ranged from `r round(100*min(data_key$pcens))` to `r round(100*max(data_key$pcens))` (median = `r round(100*median(data_key$pcens))`)
+
+(Full table is shown in the bonus slides)
+
+---
+
+## Evaluation
+
+We measured performance of each learner with:
+
+- index of prediction accuracy (IPA); __higher__ is 👍
+
+- time-dependent concordance (C)-statistic; __higher__ is 👍
+
+- total time to fit a model and compute predictions; __lower__ is 👍
+
+---
+
+## Evaluation
+
+How do we estimate overall performance based on all 23 risk prediction tasks?
+
+Step 1: Collect IPA and C-statistic values:
+
+- For each of the 23 risk prediction problems,
+
+    + split the corresponding data into a 50/50 train/test split
+    + fit each learner to the training set
+    + evaluate each learner's predictions in the testing set
+
+--
+
+Step 2: Fit a hierarchical Bayesian model to analyze posterior expected performance for each learner:
+
+$$\text{metric} = \widehat{\gamma} \cdot \text{model} + (1\,|\, \text{data/run})$$
+
+- `run` refers to the specific train/test split of `data`
+
+- `metric` is either the IPA or the time-dependent C-statistic.
+
+---
+
+```{r bm_pred_viz_ibs, fig.height=9, fig.width=11}
+bm_pred_viz$ibs_scaled
+```
+
+---
+
+```{r bm_pred_viz_cstat, fig.height=9, fig.width=11}
+bm_pred_viz$cstat
+```
+
+---
+
+```{r bm_pred_model_viz_ibs, fig.height=6.9, fig.width=9}
+bm_pred_model_viz$ibs_scaled
+```
+
+---
+
+```{r bm_pred_model_viz_cstat, fig.height=6.9, fig.width=9}
+bm_pred_model_viz$cstat
+```
+
+---
+
+```{r bm_pred_time_ridges, fig.height=6.5, fig.width=8}
+bm_pred_time_viz
+```
+
+---
+
+## Using the accelerated oblique RSF
+
+```{r out.width='100%'}
+
+knitr::include_url("https://bcjaeger.github.io/aorsf/")
+
+```
+
+---
+
+# Thank you!
+
+---
+class: center, middle
+
+# .huge[.rainbow-text[BONUS ROUND]]
+
+---
+
+# Data sets
 
@@
 
-## Evaluation
+## Evaluation (bonus round)
 
@@
 _Jargon_: $R^2$ = __index of prediction accuracy__ (IPA)
-
-_Presentation_: We scale the IPA by 100 to avoid unnecessary leading zero's.
-
----
-
-## Evaluation
-
-Step 1: Collect IPA values from ten 50/50 train/test splits on each data set for each learner.
-
-Step 2: Fit a hierarchical Bayesian model to analyze posterior expected IPA values for each learner:
-
-$$\text{IPA} = \widehat{\gamma} \cdot \text{model} + (1\,|\, \text{data/run})$$
-
-where `run` refers to the specific train/test split of `data`.
-
----
-
-```{r bm_pred_viz_ibs, fig.height=9, fig.width=11}
-bm_pred_viz$ibs_scaled
-```
-
----
-
-```{r bm_pred_viz_cstat, fig.height=9, fig.width=11}
-bm_pred_viz$cstat
-```
-
----
-
-```{r bm_pred_model_viz_ibs, fig.height=6.9, fig.width=9}
-bm_pred_model_viz$ibs_scaled
-```
-
----
-
-```{r bm_pred_model_viz_cstat, fig.height=6.9, fig.width=9}
-bm_pred_model_viz$cstat
-```
-
----
-
-```{r bm_pred_time_ridges, fig.height=6.5, fig.width=8}
-bm_pred_time_viz
-```
-
----
-
-## Using the accelerated oblique RSF
-
-```{r out.width='100%'}
-
-knitr::include_url("https://bcjaeger.github.io/aorsf/")
-
-```
-
----
-
-# Thank you!

### 2022-06-15 paper/jmlr/main.Rnw

@@
 
-\acks{Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine}
+\acks{Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine.
+The project described was supported by the National Center for Advancing Translational Sciences (NCATS), National Institutes of Health, through Grant Award Number UL1TR001420.
+The content is solely the responsibility of the authors and does not necessarily represent the official views of the NIH.}
 

### 2022-06-15 docs/index.Rmd
paper edits
grouping all the RFs into axis based or oblique should make the paper's
main hypotheses easier to test.

@@
 
-- $t_1 < \, \ldots \, < t_m$ are the $m$ unique event times in the training data.
+    + $T_i$ is the event time if an event occurred and last point of contact otherwise.
+
+    + $t_1 < \, \ldots \, < t_m$ are the $m$ unique event times in the training data.
 
@@
 
-How do we estimate overall performance based on all 23 risk prediction tasks?
+To estimate overall performance differences:
 
@@
     + evaluate each learner's predictions in the testing set
+    + repeat 25 times
 
@@
 
-Step 2: Fit a hierarchical Bayesian model to analyze posterior expected performance for each learner:
+Step 2: Fit a hierarchical Bayesian model to analyze posterior expected differences in performance:
 

### 2022-06-15 paper/jmlr/main.Rnw
paper edits
grouping all the RFs into axis based or oblique should make the paper's
main hypotheses easier to test.

@@
 
+Consider the usual framework for survival analysis with training data $$\dataset_{\text{train}} = \left\{ (T_i, \delta_i, \bm{x}_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$ Here, $T_i$ is the event time if $\delta_i=1$ and last point of contact if $\delta_i=0$, and $\bm{x}_i$ is a vector of predictors values.
+Assuming there are no ties, let $t_1 < \, \ldots \, < t_m$ denote the $m$ unique event times in $\dataset_{\text{train}}$.
+
 \subsection{Partial training at non-leaf nodes}
 
-Consider the usual framework for survival analysis with training data $$\dataset_{\text{train}} = \left\{ (T_i, \delta_i, \bm{x}_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$ Here, $T_i$ is the event time if $\delta_i=1$ and last point of contact if $\delta_i=0$, and $\bm{x}_i$ is a vector of predictors values.
-Assuming there are no ties, let $t_1 < \, \ldots \, < t_m$ denote the $m$ unique event times in $\dataset_{\text{train}}$.
 We propose to identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model:
@@
 
-In the current study, we consider four classes of learners: RFs, boosting ensembles, regression models, and neural networks (Table \ref{table:learners}).
+We consider four classes of learners: RFs, boosting ensembles, regression models, and neural networks (Table \ref{table:learners}).
 For RF learners, the number of observations required in terminal nodes was fixed at 10, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500.
-For boosting and regression learners, nested cross-validation was applied to identify the number of boosting steps and the magnitude of penalization, respectively.
+For boosting, regression, and neural network learners, nested cross-validation was applied to tune each model, \ie, assess multiple possible values for relevant model parameters and use the values that optimize the model's estimated prediction accuracy.
+Specifically, tuning for boosting models included identifying the number of steps to complete.
+For regression models, tuning was used to identify the magnitude of penalization.
+For neural networks, the number and density of layers was tuned.
 
@@
  \hline\hline
- Standard & \href{https://www.randomforestsrc.org/index.html}{\texttt{RandomForestSRC}} & \texttt{rfsrc-standard} & Axis based survival trees following Leo Breiman's original random forest algorithm, with cut-points selected to maximize a log-rank statistic.
+
+ Axis based &
+
+ \href{https://www.randomforestsrc.org/index.html}{\texttt{RandomForestSRC}} \newline
+ \href{https://CRAN.R-project.org/package=ranger}{\texttt{ranger}} \newline
+ \href{http://party.r-forge.r-project.org/}{\texttt{party}} \newline
+ \href{https://github.com/whcsu/rotsf}{\texttt{rotsf}} \newline
+ \href{https://github.com/whcsu/rsfse}{\texttt{rsfse}} &
+
+ \texttt{rsf-standard} \newline
+ \texttt{rsf-extratrees} \newline
+ \texttt{cif-standard} \newline
+ \texttt{cif-rotate} \newline
+ \texttt{cif-spacextend} &
+
+ \texttt{rsf-standard} grows survival trees following Leo Breiman's original random forest algorithm with variables and cut-points selected to maximize a log-rank statistic.
+\texttt{rsf-extratrees} grows survival trees with randomly selected features and cut-points.
+\texttt{cif-standard} uses the framework of conditional inference to grow survival trees.
+\texttt{cif-rotate} extends \texttt{cif-standard} by applying principal component analysis to random subsets of data prior to growing each survival tree.
+\texttt{cif-spacextend} derives new predictors for each tree in the ensemble, separately.
 \\ \hline
- Oblique & \href{https://CRAN.R-project.org/package=obliqueRSF}{\texttt{obliqueRSF}} \newline \href{https://bcjaeger.github.io/aorsf/}{\texttt{aorsf}} &
+
+ Oblique &
+
+ \href{https://CRAN.R-project.org/package=obliqueRSF}{\texttt{obliqueRSF}} \newline
+ \href{https://bcjaeger.github.io/aorsf/}{\texttt{aorsf}} &
+
  \texttt{obliqueRSF-net} \newline
  \texttt{aorsf-net} \newline
- \texttt{aorsf-cph($i=1$)} \newline
- \texttt{aorsf-cph($i \leq 15$)} \newline
+ \texttt{aorsf-fast} \newline
+ \texttt{aorsf-cph} \newline
  \texttt{aorsf-extratrees} &
+
  Oblique survival trees following Leo Breiman's random forest algorithm.
-Linear combinations of inputs are derived using \texttt{glmnet} in \texttt{obliqueRSF-net} and \texttt{aorsf-net}, using Newton Raphson scoring for the Cox partial likelihood function in \texttt{aorsf-cph($i=1$)} and \texttt{aorsf-cph($i \leq 15$)}, and chosen randomly from a uniform distribution in \texttt{aorsf-extratrees}.
+Linear combinations of inputs are derived using \texttt{glmnet} in \texttt{obliqueRSF-net} and \texttt{aorsf-net}, using Newton Raphson scoring for the Cox partial likelihood function in \texttt{aorsf-fast} and \texttt{aorsf-cph}, and chosen randomly from a uniform distribution in \texttt{aorsf-extratrees}.
 Cut-points are selected to maximize a log-rank statistic.
-\\ \hline
- Extremely \,Randomized & \href{https://CRAN.R-project.org/package=ranger}{\texttt{ranger}} & \texttt{ranger-extratrees} & Axis-based survival trees grown with randomly selected features and cut-points\\ \hline
- Conditional \,Inference & \href{http://party.r-forge.r-project.org/}{\texttt{party}} & \texttt{party-cif} & Axis based survival trees grown using unbiased recursive partitioning.  \\
+\\
+
  \hline\hline
@@
  \hline\hline
- Trees & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & \texttt{xgboost-cox} &  The Cox partial likelihood function is maximized additively with decision trees.
-Nested cross validation (5 folds) is applied to tune the number of trees grown.
-\\
- Models & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & \texttt{xgboost-aft} & The accelerated failure time likelihood function is maximized additively with decision trees.
-Nested cross validation (5 folds) is applied to tune the number of trees grown.
+
+ Trees &
+
+ \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} &
+
+ \texttt{xgboost-cox} \newline
+ \texttt{xgboost-aft} &
+
+ \texttt{xgboost-cox} maximizes the Cox partial likelihood function, whereas \texttt{xgboost-aft} maximizes the accelerated failure time likelihood function.
+Nested cross validation (5 folds) is applied to tune the number of trees grown, the minimum number of observations in a leaf node was 10, the maximum depth of trees was 6, and $\sqrt{p}$ variables were considered randomly for each tree split, where $p$ is the total number of predictors.
 \\
@@
  \hline\hline
- Cox Net & \texttt{glmnet} & \texttt{glmnet-cox} & The Cox model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
+ Cox Net & \texttt{glmnet} & \texttt{glmnet-cox} & The Cox proportional hazards model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
  \hline\hline
@@
  \hline\hline
- Cox Time & \href{https://raphaels1.github.io/survivalmodels/}{\texttt{survivalmodels}} & \texttt{nn-cox} & A neural network based on the proportional hazards model with time-varying effects  \\
+ Cox Time & \href{https://raphaels1.github.io/survivalmodels/}{\texttt{survivalmodels}} & \texttt{nn-cox} & A neural network based on the proportional hazards model with time-varying effects.
+Nested cross-validation was applied to select the number of layers (from 1 to 8), the number of nodes in each layer (from $\sqrt{p}$/2 to $\sqrt{p}$), and the number of epochs to complete (up to 500).
+A drop-out rate of 10\% was applied during training.
+\\
  \hline

### 2022-06-15 paper/jmlr/main.tex
paper edits
grouping all the RFs into axis based or oblique should make the paper's
main hypotheses easier to test.

--- 2022-05-24 paper/jmlr/main.tex
@@
 
+Risk prediction can reduce the burden of disease by educating patients and providers and guiding strategies to prevent and treat disease in a wide range of medical domains \citep{moons2012riskII, moons2012riskI}.
+The random survival forest (RSF), a supervised learning algorithm that can engage with censored outcomes, is frequently used for risk prediction.
+Notable characteristics of the RSF include uniform convergence of its ensemble survival function to the true population survival function when the predictor space is discrete \citep{ishwaran2010consistency}.
+In addition, software implementing the RSF is freely available, extremely efficient, and full of tools to interpret and explain the RSF \citep{randomForestSRC, ranger, hothorn2010party}.
+However, there remains considerable potential to improve the RSF in risk prediction tasks where training samples are not large enough to guarantee asymptotic properties or predictor spaces are non-discrete (\ie, predictors are continuous).
+
+RSFs may be axis based or oblique.
+The axis based RSF uses a single predictor whereas the oblique RSF uses a linear combination of predictors to create branches in trees.
+While axis based decision boundaries are always perpendicular to the axis of the relevant predictor, linear combinations of predictors create oblique decision boundaries that are neither parallel nor perpendicular to axes of their contributing predictors.
+Prior work has found the oblique RSF has higher prediction accuracy than the axis based RSF in general benchmarks \citep{jaeger2019oblique} and that oblique splitting is particularly effective when predictors are continuous \citep{menze2011oblique}.
+However, existing methods to implement oblique splitting typically use fully trained models in each non-leaf node to identify linear combinations of predictors, exponentially increasing the number of operations required for the oblique RSF versus its axis based counterpart.
+In addition, standard methods to estimate variable importance (VI) in the RSF are less effective in the oblique RSF, and few methods have been introduced to estimate VI specifically for the oblique RSF.
+
+The aim of this article is to improve the computational efficiency and interpretability of the oblique RSF.
+In a general benchmark experiment including YYYY risk prediction tasks, we show that oblique RSFs with partially trained models have equivalent or superior prediction accuracy and are orders of magnitude more efficient than oblique RSFs with fully trained models in non-leaf nodes.
+We introduce a method to estimate VI for oblique RSFs and compare its ability to discriminate between signal and noise variables versus standard and state-of-the-art methods.
+All methods proposed in this article are available in the \texttt{aorsf} R Package.
+
 \section{Related work}
 
-Table \ref{table:1} is an example of a referenced \LaTeX{}.
-Several machine learning algorithms can engage with right-censored time-to-event outcomes.
-In the current study, we consider four classes of learners: random forests, boosting ensembles, regression models, and neural networks.
+\subsection{Axis-based and oblique random forests}
 
-accelerated oblique random survival forests \texttt{aorsf}
+After \citet{breiman2001random} introduced the axis-based and oblique random forest (RF), numerous methods were developed to grow oblique RFs for classification or regression tasks \citep{menze2011oblique, zhang2014oblique, rainforth2015canonical, zhu2015reinforcement, poona2016investigating, qiu2017oblique, tomita2020sparse, katuwal2020heterogeneous}.
+However, oblique splitting approaches for classification or regression may not generalize to survival tasks \citep[\eg, see][Section~4.5.1]{zhu2013tree}, and most research involving the RSF has focused on forests with axis-based trees \citep{wang2017selective}.
 
-original oblique random survival forests \texttt{obliqueRSF}
+Building on prior research for bagging survival trees \citep{hothorn2004bagging}, \citet{hothorn2006unbiased} developed an axis-based RSF in their framework for unbiased recursive partitioning, more commonly referred to as the conditional inference forest (CIF).
+\citet{zhou2016random} developed a rotation forest based on the CIF and \citet{wang2017random} developed a method for extending the predictor space of the CIF.
+\citet{ishwaran2008random} developed an axis-based RSF with strict adherence to the rules for growing trees proposed in \citet{breiman2001random}.
+\citet{jaeger2019oblique} developed the oblique RSF following the bootstrapping approach described in Breiman's original RF and incorporating early stopping rules from the CIF.
 
-axis-based random survival forests \texttt{randomForestSRC \& ranger}
+\subsection{Variable importance}
 
-axis-based conditional inference forests \texttt{party}
+\citet{breiman2001random} introduced permutation VI, defined for each predictor as the difference in a RF's estimated generalization error before versus after the predictor's values are randomly permuted.
+\citet{strobl2007bias} identified bias in permutation VI driven by variable selection bias and effects induced by bootstrap sampling, and proposed an unbiased permutation VI based on unbiased recursive partitioning (see \citet{hothorn2006unbiased}).
+\citet{menze2011oblique} introduced an approach to estimate VI for oblique RFs that computes an analysis of variance (ANOVA) table in non-leaf nodes to obtain p-values for each predictor contributing to the node.
+The ANOVA VI\footnote{\citet{menze2011oblique} name their method `oblique RF VI', but we use the name `ANOVA VI' in this article to avoid confusing Menze's approach with other approaches to estimate VI for oblique RFs.} is then defined for each predictor as the number of times a p-value associated with the predictor is $\leq 0.01$ while growing a forest.
+\citet{lundberg2017unified} introduced a method to estimate VI using SHapley Additive exPlanation (SHAP) values, which estimate the contribution of a predictor to a model's prediction for a given observation.
+SHAP VI is computed for each predictor by taking the mean absolute value of SHAP values for that predictor across all observations in a given set.
 
-gradient boosted decision trees \texttt{xgboost}
+% Several supervised learning algorithms can develop prediction functions for right-censored time-to-event outcomes, henceforth referred to as survival outcomes.
+\cite{ishwaran2008random} developed the RF for survival, an extension of the RF for regression and classification developed by \citet{breiman2001random}.
+Fast algorithms to fit the RF for survival are available in the \texttt{randomForestSRC} R package \citep{randomForestSRC}.
+A similar implementation of the RF for survival can be found in the \texttt{ranger} R package \citep{ranger}, which is particularly suited for high dimensional data.
+The RF for survival can also be fit using unbiased recursive partitioning \citep{cif} via the \texttt{party} R package \citep{hothorn2010party}.
+
+\section{Novel techniques for oblique random survival forests}
+
+Consider the usual framework for survival analysis with training data $$\dataset_{\text{train}} = \left\{ (T_i, \delta_i, \bm{x}_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$ Here, $T_i$ is the event time if $\delta_i=1$ and last point of contact if $\delta_i=0$, and $\bm{x}_i$ is a vector of predictors values.
+Assuming there are no ties, let $t_1 < \, \ldots \, < t_m$ denote the $m$ unique event times in $\dataset_{\text{train}}$.
+
+\subsection{Partial training at non-leaf nodes}
+
+We propose to identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model:
+\begin{equation}\label{eqn:cox-partial-likelihood}
+L(\bm\beta) = \prod_{i=1}^m \frac{e^{\bm{x}_{j(i)}^T \bm\beta}}{\sum_{j \in R_i} e^{\bm{x}_j^T \bm\beta}},
+\end{equation}
+where $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (i.e., those still at risk at time $t_i$), and $j(i)$ is the index of the observation for which an event occurred at time $t_i$.
+The \texttt{survival} package includes documentation that outlines how to complete this estimation procedure efficiently \citep[see][exact.nw]{therneau_survival_2022}.
+Briefly, a vector of estimated regression coefficients, $\hat{\beta}$, is updated in each step of the procedure based on its first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
+$$ \hat{\beta}^{k+1} =  \hat{\beta}^{k} + U(\hat{\beta} = \hat{\beta}^{k})\, H^{-1}(\hat{\beta} = \hat{\beta}^{k}) $$
+It is vital to cycle through iterations until a convergence threshold is met for statistical inference, but it is only necessary to complete one iteration to identify coefficients for a linear combination of predictors.
+\citet{jaeger2019oblique} identified linear combinations using penalized regression models, which supply more flexible solutions for $\hat{\beta}$ at the cost of greater computational demand.
+
+\subsection{Negation variable importance}
+
+Negation VI is similar to permutation VI in that it measures how much a model’s prediction error increases when a variable’s role in the model is de-stabilized.
+More specifically, negation VI measures the increase in an oblique RF's prediction error after flipping the sign of all coefficients linked to a variable (\ie, negating them).
+As the magnitude of a coefficient increases, so does the probability that negating it will change the oblique RF's predictions.
+Since the coefficients in each non-leaf node of an oblique RFs are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
+Although the current article focuses on oblique RSFs, negation VI can be applied to any oblique RF.
+
+\section{Numeric experiments}
+
+\subsection{Benchmark of prediction accuracy}
+
+\subsubsection{Learners}
+
+We consider four classes of learners: RFs, boosting ensembles, regression models, and neural networks (Table \ref{table:learners}).
+For RF learners, the number of observations required in terminal nodes was fixed at 10, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500.
+For boosting, regression, and neural network learners, nested cross-validation was applied to tune each model, \ie, assess multiple possible values for relevant model parameters and use the values that optimize the model's estimated prediction accuracy.
+Specifically, tuning for boosting models included identifying the number of steps to complete.
+For regression models, tuning was used to identify the magnitude of penalization.
+For neural networks, the number and density of layers was tuned.
+
+\newgeometry{margin=1cm} % modify this if you need even more space
+\begin{landscape}
 
@@
  \hline\hline
- Standard & \href{https://www.randomforestsrc.org/index.html}{\texttt{RandomForestSRC}} & Axis based survival trees following Leo Breiman's original random forest algorithm, with cut-points selected to maximize a log-rank statistic.
+
+ Axis based &
+
+ \href{https://www.randomforestsrc.org/index.html}{\texttt{RandomForestSRC}} \newline
+ \href{https://CRAN.R-project.org/package=ranger}{\texttt{ranger}} \newline
+ \href{http://party.r-forge.r-project.org/}{\texttt{party}} \newline
+ \href{https://github.com/whcsu/rotsf}{\texttt{rotsf}} \newline
+ \href{https://github.com/whcsu/rsfse}{\texttt{rsfse}} &
+
+ \texttt{rsf-standard} \newline
+ \texttt{rsf-extratrees} \newline
+ \texttt{cif-standard} \newline
+ \texttt{cif-rotate} \newline
+ \texttt{cif-spacextend} &
+
+ \texttt{rsf-standard} grows survival trees following Leo Breiman's original random forest algorithm with variables and cut-points selected to maximize a log-rank statistic.
+\texttt{rsf-extratrees} grows survival trees with randomly selected features and cut-points.
+\texttt{cif-standard} uses the framework of conditional inference to grow survival trees.
+\texttt{cif-rotate} extends \texttt{cif-standard} by applying principal component analysis to random subsets of data prior to growing each survival tree.
+\texttt{cif-spacextend} derives new predictors for each tree in the ensemble, separately.
 \\ \hline
- Oblique & \href{https://CRAN.R-project.org/package=obliqueRSF}{\texttt{obliqueRSF}} \newline \href{https://bcjaeger.github.io/aorsf/}{\texttt{aorsf}} & Oblique survival trees following Leo Breiman's random forest algorithm but not using random coefficients for linear combinations.
-\texttt{obliqueRSF} uses penalized models, and \texttt{aorsf} additionally uses partially trained models.
+
+ Oblique &
+
+ \href{https://CRAN.R-project.org/package=obliqueRSF}{\texttt{obliqueRSF}} \newline
+ \href{https://bcjaeger.github.io/aorsf/}{\texttt{aorsf}} &
+
+ \texttt{obliqueRSF-net} \newline
+ \texttt{aorsf-net} \newline
+ \texttt{aorsf-fast} \newline
+ \texttt{aorsf-cph} \newline
+ \texttt{aorsf-extratrees} &
+
+ Oblique survival trees following Leo Breiman's random forest algorithm.
+Linear combinations of inputs are derived using \texttt{glmnet} in \texttt{obliqueRSF-net} and \texttt{aorsf-net}, using Newton Raphson scoring for the Cox partial likelihood function in \texttt{aorsf-fast} and \texttt{aorsf-cph}, and chosen randomly from a uniform distribution in \texttt{aorsf-extratrees}.
 Cut-points are selected to maximize a log-rank statistic.
-\\ \hline
- Extremely \,Randomized & \href{https://CRAN.R-project.org/package=ranger}{\texttt{ranger}} & Axis-based survival trees grown with randomly selected features and cut-points\\ \hline
- Conditional \,Inference & \href{http://party.r-forge.r-project.org/}{\texttt{party}} & Axis based survival trees grown using unbiased recursive partitioning.  \\
+\\
+
  \hline\hline
@@
  \hline\hline
- Trees & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & The Cox likelihood function is maximized additively with decision trees.
-Nested cross validation (5 folds) is applied to tune the number of trees grown.
-\\
- Models & \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} & The accelerated failure time likelihood function is maximized additively with decision trees.
-Nested cross validation (5 folds) is applied to tune the number of trees grown.
+
+ Trees &
+
+ \href{https://xgboost.readthedocs.io/en/stable/#}{\texttt{xgboost}} &
+
+ \texttt{xgboost-cox} \newline
+ \texttt{xgboost-aft} &
+
+ \texttt{xgboost-cox} maximizes the Cox partial likelihood function, whereas \texttt{xgboost-aft} maximizes the accelerated failure time likelihood function.
+Nested cross validation (5 folds) is applied to tune the number of trees grown, the minimum number of observations in a leaf node was 10, the maximum depth of trees was 6, and $\sqrt{p}$ variables were considered randomly for each tree split, where $p$ is the total number of predictors.
 \\
@@
  \hline\hline
- Cox Net & \texttt{glmnet} & The Cox model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
+ Cox Net & \texttt{glmnet} & \texttt{glmnet-cox} & The Cox proportional hazards model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
  \hline\hline
@@
  \hline\hline
- Cox Time & 6 & 87837  \\
+ Cox Time & \href{https://raphaels1.github.io/survivalmodels/}{\texttt{survivalmodels}} & \texttt{nn-cox} & A neural network based on the proportional hazards model with time-varying effects.
+Nested cross-validation was applied to select the number of layers (from 1 to 8), the number of nodes in each layer (from $\sqrt{p}$/2 to $\sqrt{p}$), and the number of epochs to complete (up to 500).
+A drop-out rate of 10\% was applied during training.
+\\
  \hline
 \end{tabular}
-\caption{Table to test captions and labels.}
-\label{table:1}
+\caption{Learning algorithms assessed in numeric studies}
+\label{table:learners}
 \end{table}
 
-\section{Results}
+\end{landscape}
+\restoregeometry
+
+\subsubsection{Evaluation of prediction accuracy} \label{sec:prediction_accuracy}
+
+Our primary metric for evaluating the accuracy of predicted risk is the integrated and scaled Brier score \citep{graf1999assessment}.
+For observation $i$ in the testing data, let $\widehat{S}(t \mid \bm{x}_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$ and let $\bm{x}_i$ be the vector of predictor values.
+Define \begin{align*}
+\bstat = \frac{1}{\ntest} \sum_{i=1}^{\ntest} &\{ \widehat{S}(t \mid \bm{x}_i)^2 \cdot I(T_i \leq t, \delta_i = 1) \cdot \widehat{G}(T_i)^{-1} \\ &+ [1-\widehat{S}(t \mid \bm{x}_i)]^2 \cdot I(T_i > t) \cdot \widehat{G}(t)^{-1}\}
+\end{align*} where $\widehat{G}(t)$ is the Kaplan-Meier estimate of the censoring distribution.
+As $\bstat$ is time dependent, integration over time provides a summary measure of performance over a range of plausible prediction horizons.
+The integrated $\bstat$ is defined as \begin{equation}
+\bsbar = \frac{1}{t_2 - t_1}\int_{t_1}^{t_2} \widehat{\text{BS}}(t) dt.
+\end{equation} In our results, $t_1$ and $t_2$ are the 25th and 75th percentile of event times, respectively.
+$\bsbar$, a sum of squared prediction errors, can be scaled to produce a measure of explained residual variation (\ie, an $R^2$ statistic) by computing \begin{equation}
+R^2 = 1 - \frac{\bsbar}{\bskap}
+\end{equation} where $\bskap$ is the integrated Brier score when a Kaplan-Meier estimate for survival based on the training data is used as the survival prediction function $\widehat{S}(t)$.
+We refer to this $R^2$ statistic as the index of prediction accuracy and we scale its values by 100 to avoid unnecessary leading zero's.
+For example, we present 25 if $R^2$ is 0.25 and present 10.2 if the difference between two $R^2$ is 0.102.
+
+\subsubsection{Statistical analysis}
+
+\subsubsection{Results}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-2-1} 
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-3-1} 
+\end{knitrout}
+
+\subsection{Benchmark of variable selection}
+
+% Acknowledgements should go at the end, before appendices and references
+
+\acks{Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine}
+
+% Manual newpage inserted to improve layout of sample file - not
+% needed in general before appendices/bibliography.
+
+\newpage
+
+\appendix
+\section*{Appendix A.}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-4-1} 
+\end{knitrout}
+
+\newpage
 
@@
 \hline
-\multicolumn{7}{l}{\textit{\textbf{actg}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Overall}}}\\
 \hline
-\hspace{1em}Party & 0.772 (0.058) & 0.076 (0.042) & 2.181 & 2.19 & 4.889 & 4.62\\
-\hspace{1em}aORSF(i=1) & 0.755 (0.059) & 0.057 (0.055) & 0.998 & 1.00 & 1.057 & 1.00\\
-\hspace{1em}Ranger & 0.754 (0.064) & 0.064 (0.027) & 0.397 & 0.398 & 0.510 & 0.483\\
-\hspace{1em}aORSF(i=15) & 0.754 (0.063) & 0.052 (0.056) & 2.498 & 2.50 & 2.559 & 2.42\\
-\hspace{1em}Rfsrc & 0.752 (0.064) & 0.061 (0.047) & 0.775 & 0.777 & 0.833 & 0.787\\
-\hspace{1em}aorsf\_net & 0.750 (0.059) & 0.055 (0.064) & 28.449 & 28.5 & 28.510 & 27.0\\
+\hspace{1em}aorsf-cph & 0.133 (0.124) & 0.757 (0.079) & 0.830 & 2.74 & 0.070 & 0.980\\
+\hspace{1em}aorsf-fast & 0.133 (0.124) & 0.757 (0.080) & 0.302 & 1.00 & 0.072 & 1.00\\
+\hspace{1em}aorsf-net & 0.130 (0.127) & 0.755 (0.080) & 61.237 & 202.6 & 0.069 & 0.964\\
+\hspace{1em}cif-rotate & 0.125 (0.145) & 0.741 (0.092) & 30.623 & 101.3 & 7.208 & 100.3\\
+\hspace{1em}cif-standard & 0.120 (0.111) & 0.748 (0.079) & 2.035 & 6.73 & 5.128 & 71.3\\
+\hspace{1em}glmnet-cox & 0.119 (0.139) & 0.748 (0.083) & 0.253 & 0.837 & 0.005 & 0.070\\
+\hspace{1em}rsf-standard & 0.118 (0.128) & 0.741 (0.084) & 1.694 & 5.60 & 0.152 & 2.11\\
+\hspace{1em}obliqueRSF-net & 0.117 (0.094) & 0.754 (0.080) & 328.883 & 1,087.9 & 26.636 & 370.5\\
+\hspace{1em}cif-extension & 0.108 (0.108) & 0.746 (0.083) & 13.510 & 44.7 & 6.840 & 95.2\\
+\hspace{1em}ranger-extratrees & 0.106 (0.097) & 0.748 (0.076) & 0.692 & 2.29 & 0.264 & 3.68\\
+\hspace{1em}aorsf-random & 0.101 (0.092) & 0.735 (0.074) & 1.879 & 6.22 & 0.066 & 0.919\\
+\hspace{1em}xgboost-cox & 0.077 (0.114) & 0.736 (0.095) & 3.833 & 12.7 & 0.005 & 0.070\\
+\hspace{1em}nn-cox & 0.030 (0.118) & 0.610 (0.128) & 15.427 & 51.0 & 1.513 & 21.0\\
+\hspace{1em}xgboost-aft & -3.68 (4.86) & 0.747 (0.082) & 13.182 & 43.6 & 0.008 & 0.117\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{breast}}}\\
+\multicolumn{7}{l}{\textit{\textbf{ACTG 320; AIDS diagnosis, n = 1151, p = 12}}}\\
 \hline
-\hspace{1em}aORSF(i=15) & 0.764 (0.008) & 0.143 (0.016) & 11.867 & 2.56 & 12.403 & 2.43\\
-\hspace{1em}Ranger & 0.756 (0.013) & 0.102 (0.017) & 0.555 & 0.120 & 0.724 & 0.142\\
-\hspace{1em}Party & 0.753 (0.013) & 0.118 (0.016) & 8.030 & 1.73 & 10.445 & 2.05\\
-\hspace{1em}aORSF(i=1) & 0.751 (0.002) & 0.120 (0.012) & 4.636 & 1.00 & 5.106 & 1.00\\
-\hspace{1em}aorsf\_net & 0.741 (0.022) & 0.062 (0.049) & 585.625 & 126.3 & 585.887 & 114.7\\
-\hspace{1em}Rfsrc & 0.707 (0.005) & 0.049 (0.039) & 1.354 & 0.292 & 1.522 & 0.298\\
+\hspace{1em}aorsf-random & 0.028 (0.022) & 0.748 (0.038) & 0.637 & 4.19 & 0.040 & 1.06\\
+\hspace{1em}ranger-extratrees & 0.028 (0.017) & 0.740 (0.036) & 0.061 & 0.404 & 0.184 & 4.81\\
+\hspace{1em}obliqueRSF-net & 0.027 (0.022) & 0.746 (0.038) & 27.286 & 179.6 & 15.729 & 411.6\\
+\hspace{1em}aorsf-cph & 0.025 (0.029) & 0.751 (0.042) & 0.450 & 2.97 & 0.034 & 0.891\\
+\hspace{1em}cif-standard & 0.024 (0.031) & 0.744 (0.040) & 1.608 & 10.6 & 4.825 & 126.3\\
+\hspace{1em}aorsf-fast & 0.024 (0.028) & 0.745 (0.044) & 0.152 & 1.00 & 0.038 & 1.00\\
+\hspace{1em}cif-extension & 0.023 (0.015) & 0.722 (0.038) & 9.788 & 64.4 & 4.595 & 120.2\\
+\hspace{1em}aorsf-net & 0.019 (0.034) & 0.745 (0.042) & 20.231 & 133.2 & 0.038 & 0.995\\
+\hspace{1em}glmnet-cox & 0.016 (0.030) & 0.746 (0.037) & 0.183 & 1.21 & 0.002 & 0.053\\
+\hspace{1em}rsf-standard & 0.005 (0.041) & 0.730 (0.042) & 0.235 & 1.55 & 0.071 & 1.85\\
+\hspace{1em}cif-rotate & 0.004 (0.040) & 0.731 (0.038) & 15.089 & 99.3 & 4.246 & 111.1\\
+\hspace{1em}xgboost-cox & 0.000 (0.044) & 0.751 (0.033) & 3.655 & 24.1 & 0.003 & 0.079\\
+\hspace{1em}nn-cox & 0.000 (0.013) & 0.574 (0.117) & 12.345 & 81.3 & 0.639 & 16.7\\
+\hspace{1em}xgboost-aft & -8.40 (1.81) & 0.737 (0.035) & 11.029 & 72.6 & 0.007 & 0.183\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{colon}}}\\
+\multicolumn{7}{l}{\textit{\textbf{ACTG 320; death, n = 1151, p = 12}}}\\
 \hline
-\hspace{1em}Rfsrc & 0.815 (0.007) & 0.279 (0.007) & 1.854 & 0.581 & 2.026 & 0.600\\
-\hspace{1em}aORSF(i=15) & 0.778 (0.007) & 0.199 (0.018) & 7.515 & 2.36 & 7.709 & 2.28\\
-\hspace{1em}aORSF(i=1) & 0.776 (0.004) & 0.201 (0.014) & 3.190 & 1.00 & 3.378 & 1.00\\
-\hspace{1em}aorsf\_net & 0.753 (0.006) & 0.156 (0.018) & 149.637 & 46.9 & 149.809 & 44.3\\
-\hspace{1em}Party & 0.753 (0.012) & 0.183 (0.008) & 3.968 & 1.24 & 10.451 & 3.09\\
-\hspace{1em}Ranger & 0.738 (0.008) & 0.147 (0.005) & 1.795 & 0.563 & 2.398 & 0.710\\
+\hspace{1em}obliqueRSF-net & 0.007 (0.012) & 0.819 (0.051) & 9.302 & 102.7 & 10.943 & 545.1\\
+\hspace{1em}aorsf-cph & 0.007 (0.019) & 0.815 (0.058) & 0.363 & 4.00 & 0.020 & 1.00\\
+\hspace{1em}aorsf-fast & 0.006 (0.019) & 0.820 (0.054) & 0.091 & 1.00 & 0.020 & 1.00\\
+\hspace{1em}aorsf-random & 0.004 (0.015) & 0.780 (0.070) & 0.326 & 3.60 & 0.026 & 1.30\\
+\hspace{1em}ranger-extratrees & 0.001 (0.020) & 0.773 (0.071) & 0.045 & 0.497 & 0.143 & 7.13\\
+\hspace{1em}cif-extension & 0.001 (0.021) & 0.759 (0.061) & 8.354 & 92.2 & 3.905 & 194.5\\
+\hspace{1em}xgboost-cox & -0.004 (0.004) & 0.500 (0.000) & 0.120 & 1.32 & 0.002 & 0.100\\
+\hspace{1em}nn-cox & -0.004 (0.004) & 0.535 (0.110) & 11.322 & 125.0 & 0.689 & 34.3\\
+\hspace{1em}cif-standard & -0.006 (0.026) & 0.773 (0.056) & 1.758 & 19.4 & 4.361 & 217.2\\
+\hspace{1em}aorsf-net & -0.006 (0.033) & 0.799 (0.065) & 15.227 & 168.1 & 0.025 & 1.25\\
+\hspace{1em}rsf-standard & -0.031 (0.053) & 0.769 (0.069) & 0.090 & 0.994 & 0.038 & 1.90\\
+\hspace{1em}cif-rotate & -0.037 (0.052) & 0.704 (0.094) & 13.476 & 148.8 & 3.663 & 182.5\\
+\hspace{1em}glmnet-cox & -0.062 (0.092) & 0.736 (0.098) & 0.301 & 3.33 & 0.001 & 0.051\\
+\hspace{1em}xgboost-aft & -24.3 (7.36) & 0.767 (0.066) & 10.846 & 119.7 & 0.008 & 0.399\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{gbsg2}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Colon cancer; death, n = 929, p = 12}}}\\
 \hline
-\hspace{1em}Ranger & 0.704 (0.076) & 0.090 (0.045) & 0.328 & 0.339 & 0.450 & 0.438\\
-\hspace{1em}Party & 0.686 (0.042) & 0.092 (0.048) & 0.746 & 0.773 & 2.055 & 2.00\\
-\hspace{1em}aORSF(i=15) & 0.685 (0.048) & 0.077 (0.066) & 2.077 & 2.15 & 2.144 & 2.09\\
-\hspace{1em}Rfsrc & 0.676 (0.032) & 0.067 (0.052) & 0.931 & 0.963 & 1.014 & 0.986\\
-\hspace{1em}aORSF(i=1) & 0.674 (0.045) & 0.062 (0.062) & 0.966 & 1.00 & 1.028 & 1.00\\
-\hspace{1em}aorsf\_net & 0.670 (0.038) & 0.068 (0.056) & 57.024 & 59.0 & 57.087 & 55.5\\
+\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.718 (0.011) & 0.289 & 1.00 & 0.075 & 1.00\\
+\hspace{1em}aorsf-cph & 0.100 (0.014) & 0.717 (0.011) & 0.691 & 2.39 & 0.070 & 0.945\\
+\hspace{1em}cif-standard & 0.097 (0.013) & 0.710 (0.012) & 1.529 & 5.29 & 5.019 & 67.4\\
+\hspace{1em}aorsf-net & 0.097 (0.014) & 0.717 (0.012) & 55.870 & 193.4 & 0.064 & 0.853\\
+\hspace{1em}aorsf-random & 0.096 (0.010) & 0.716 (0.011) & 1.612 & 5.58 & 0.066 & 0.879\\
+\hspace{1em}obliqueRSF-net & 0.089 (0.006) & 0.717 (0.012) & 269.561 & 932.9 & 44.243 & 593.8\\
+\hspace{1em}cif-rotate & 0.087 (0.017) & 0.705 (0.014) & 15.603 & 54.0 & 6.291 & 84.4\\
+\hspace{1em}rsf-standard & 0.087 (0.019) & 0.704 (0.011) & 1.646 & 5.70 & 0.143 & 1.92\\
+\hspace{1em}ranger-extratrees & 0.083 (0.007) & 0.710 (0.011) & 0.735 & 2.54 & 0.263 & 3.53\\
+\hspace{1em}cif-extension & 0.081 (0.006) & 0.709 (0.011) & 8.523 & 29.5 & 5.850 & 78.5\\
+\hspace{1em}glmnet-cox & 0.076 (0.016) & 0.711 (0.019) & 0.132 & 0.457 & 0.004 & 0.054\\
+\hspace{1em}xgboost-cox & 0.063 (0.013) & 0.701 (0.013) & 3.266 & 11.3 & 0.004 & 0.054\\
+\hspace{1em}nn-cox & -0.013 (0.040) & 0.506 (0.042) & 14.970 & 51.8 & 1.780 & 23.9\\
+\hspace{1em}xgboost-aft & -1.11 (0.200) & 0.706 (0.013) & 12.660 & 43.8 & 0.007 & 0.094\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{guide\_it}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Colon cancer; recurrence, n = 929, p = 12}}}\\
 \hline
-\hspace{1em}aORSF(i=15) & 0.730 (0.009) & 0.133 (0.008) & 4.705 & 2.67 & 4.811 & 2.57\\
-\hspace{1em}aORSF(i=1) & 0.728 (0.014) & 0.132 (0.012) & 1.762 & 1.00 & 1.869 & 1.00\\
-\hspace{1em}aorsf\_net & 0.728 (0.020) & 0.133 (0.015) & 86.476 & 49.1 & 86.590 & 46.3\\
-\hspace{1em}Party & 0.705 (0.021) & 0.101 (0.010) & 1.800 & 1.02 & 3.727 & 1.99\\
-\hspace{1em}Rfsrc & 0.705 (0.032) & 0.109 (0.027) & 1.000 & 0.568 & 1.104 & 0.591\\
-\hspace{1em}Ranger & 0.704 (0.016) & 0.102 (0.001) & 0.663 & 0.376 & 0.855 & 0.457\\
+\hspace{1em}aorsf-fast & 0.100 (0.017) & 0.713 (0.016) & 0.282 & 1.00 & 0.069 & 1.00\\
+\hspace{1em}aorsf-cph & 0.099 (0.017) & 0.712 (0.016) & 0.708 & 2.52 & 0.070 & 1.01\\
+\hspace{1em}aorsf-net & 0.096 (0.018) & 0.713 (0.017) & 51.056 & 181.3 & 0.065 & 0.937\\
+\hspace{1em}cif-standard & 0.091 (0.015) & 0.701 (0.017) & 1.183 & 4.20 & 4.109 & 59.2\\
+\hspace{1em}obliqueRSF-net & 0.088 (0.008) & 0.711 (0.015) & 298.417 & 1,059.9 & 44.698 & 643.9\\
+\hspace{1em}aorsf-random & 0.087 (0.012) & 0.703 (0.015) & 1.629 & 5.78 & 0.064 & 0.923\\
+\hspace{1em}cif-rotate & 0.084 (0.020) & 0.695 (0.017) & 14.130 & 50.2 & 6.064 & 87.4\\
+\hspace{1em}cif-extension & 0.082 (0.009) & 0.707 (0.017) & 8.587 & 30.5 & 6.571 & 94.7\\
+\hspace{1em}rsf-standard & 0.081 (0.020) & 0.694 (0.015) & 1.408 & 5.00 & 0.139 & 2.00\\
+\hspace{1em}ranger-extratrees & 0.079 (0.011) & 0.700 (0.016) & 0.555 & 1.97 & 0.235 & 3.39\\
+\hspace{1em}glmnet-cox & 0.073 (0.018) & 0.706 (0.024) & 0.161 & 0.572 & 0.005 & 0.072\\
+\hspace{1em}xgboost-cox & 0.060 (0.011) & 0.695 (0.018) & 3.088 & 11.0 & 0.004 & 0.058\\
+\hspace{1em}nn-cox & -0.005 (0.005) & 0.506 (0.039) & 13.814 & 49.1 & 1.499 & 21.6\\
+\hspace{1em}xgboost-aft & -1.20 (0.239) & 0.701 (0.019) & 11.979 & 42.5 & 0.007 & 0.101\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{Mayo Clinic Primary Biliary Cholangitis Data, N = 276}}}\\
+\multicolumn{7}{l}{\textit{\textbf{Early breast cancer; recurrence or death, n = 614, p = 1692}}}\\
 \hline
-\hspace{1em}aORSF(i=1) & 0.787 (0.094) & 0.202 (0.188) & 2.204 & 1.00 & 2.400 & 1.00\\
-\hspace{1em}aORSF(i=15) & 0.787 (0.100) & 0.203 (0.186) & 5.038 & 2.29 & 5.242 & 2.18\\
-\hspace{1em}Ranger & 0.783 (0.091) & 0.161 (0.138) & 0.709 & 0.322 & 1.053 & 0.438\\
-\hspace{1em}aorsf\_net & 0.782 (0.101) & 0.190 (0.202) & 128.300 & 58.2 & 128.469 & 53.5\\
-\hspace{1em}Party & 0.779 (0.094) & 0.185 (0.167) & 3.291 & 1.49 & 6.998 & 2.92\\
-\hspace{1em}Rfsrc & 0.778 (0.113) & 0.195 (0.187) & 0.956 & 0.434 & 1.076 & 0.448\\
+\hspace{1em}obliqueRSF-net & 0.073 (0.024) & 0.749 (0.027) & 1951.148 & 2,519.7 & 15.143 & 83.8\\
+\hspace{1em}cif-rotate & 0.072 (0.017) & 0.748 (0.027) & 6765.191 & 8,736.4 & 351.642 & 1,947.0\\
+\hspace{1em}cif-standard & 0.068 (0.018) & 0.745 (0.029) & 8.817 & 11.4 & 4.397 & 24.3\\
+\hspace{1em}cif-extension & 0.066 (0.014) & 0.746 (0.025) & 45.390 & 58.6 & 6.577 & 36.4\\
+\hspace{1em}aorsf-cph & 0.065 (0.031) & 0.745 (0.024) & 1.280 & 1.65 & 0.179 & 0.992\\
+\hspace{1em}aorsf-fast & 0.063 (0.031) & 0.744 (0.024) & 0.774 & 1.00 & 0.181 & 1.00\\
+\hspace{1em}ranger-extratrees & 0.061 (0.024) & 0.740 (0.028) & 0.224 & 0.290 & 0.180 & 0.997\\
+\hspace{1em}glmnet-cox & 0.043 (0.034) & 0.723 (0.037) & 5.608 & 7.24 & 0.005 & 0.028\\
+\hspace{1em}xgboost-cox & 0.040 (0.014) & 0.743 (0.026) & 2.236 & 2.89 & 0.007 & 0.039\\
+\hspace{1em}aorsf-random & 0.030 (0.015) & 0.699 (0.036) & 1.847 & 2.38 & 0.190 & 1.05\\
+\hspace{1em}rsf-standard & 0.020 (0.041) & 0.693 (0.033) & 0.382 & 0.493 & 0.666 & 3.69\\
+\hspace{1em}aorsf-net & 0.003 (0.067) & 0.740 (0.022) & 464.082 & 599.3 & 0.179 & 0.992\\
+\hspace{1em}nn-cox & -0.008 (0.065) & 0.689 (0.045) & 18.607 & 24.0 & 1.926 & 10.7\\
+\hspace{1em}xgboost-aft & -3.09 (0.664) & 0.742 (0.022) & 11.258 & 14.5 & 0.010 & 0.056\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{Overall}}}\\
+\multicolumn{7}{l}{\textit{\textbf{FCL; death, n = 541, p = 7}}}\\
 \hline
-\hspace{1em}aORSF(i=1) & 0.946 (0.018) & 0.493 (0.083) & 0.344 & 1.00 & 0.376 & 1.00\\
-\hspace{1em}aorsf\_net & 0.939 (0.018) & 0.484 (0.052) & 23.093 & 67.2 & 23.123 & 61.6\\
-\hspace{1em}Party & 0.936 (0.022) & 0.454 (0.022) & 0.288 & 0.839 & 0.518 & 1.38\\
-\hspace{1em}aORSF(i=15) & 0.936 (0.014) & 0.474 (0.080) & 0.744 & 2.17 & 0.773 & 2.06\\
-\hspace{1em}Rfsrc & 0.927 (0.012) & 0.462 (0.070) & 0.363 & 1.06 & 0.397 & 1.06\\
-\hspace{1em}Ranger & 0.926 (0.014) & 0.344 (0.055) & 0.044 & 0.127 & 0.085 & 0.226\\
+\hspace{1em}glmnet-cox & 0.117 (0.028) & 0.787 (0.037) & 0.110 & 1.24 & 0.003 & 0.158\\
+\hspace{1em}aorsf-cph & 0.101 (0.039) & 0.769 (0.034) & 0.171 & 1.93 & 0.020 & 1.05\\
+\hspace{1em}aorsf-fast & 0.100 (0.038) & 0.768 (0.033) & 0.088 & 1.00 & 0.019 & 1.00\\
+\hspace{1em}aorsf-net & 0.097 (0.040) & 0.760 (0.034) & 13.429 & 151.8 & 0.020 & 1.06\\
+\hspace{1em}obliqueRSF-net & 0.089 (0.027) & 0.758 (0.036) & 108.537 & 1,226.6 & 5.743 & 302.0\\
+\hspace{1em}cif-rotate & 0.087 (0.048) & 0.755 (0.027) & 6.229 & 70.4 & 2.161 & 113.6\\
+\hspace{1em}cif-extension & 0.087 (0.036) & 0.730 (0.034) & 6.111 & 69.1 & 2.473 & 130.0\\
+\hspace{1em}aorsf-random & 0.087 (0.029) & 0.757 (0.032) & 0.304 & 3.44 & 0.020 & 1.05\\
+\hspace{1em}cif-standard & 0.084 (0.038) & 0.743 (0.036) & 0.793 & 8.97 & 1.275 & 67.1\\
+\hspace{1em}ranger-extratrees & 0.073 (0.016) & 0.741 (0.037) & 0.036 & 0.409 & 0.087 & 4.56\\
+\hspace{1em}rsf-standard & 0.072 (0.048) & 0.732 (0.034) & 0.526 & 5.94 & 0.039 & 2.07\\
+\hspace{1em}xgboost-cox & 0.029 (0.050) & 0.679 (0.121) & 0.342 & 3.87 & 0.002 & 0.105\\
+\hspace{1em}nn-cox & -0.006 (0.015) & 0.536 (0.097) & 12.668 & 143.2 & 0.444 & 23.3\\
+\hspace{1em}xgboost-aft & -2.52 (0.477) & 0.754 (0.038) & 7.286 & 82.3 & 0.006 & 0.316\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{Rotterdam Breast Cancer Data, N = 2,982}}}\\
+\multicolumn{7}{l}{\textit{\textbf{FCL; relapse, n = 541, p = 7}}}\\
 \hline
-\hspace{1em}Ranger & 0.719 (0.011) & 0.145 (0.011) & 2.480 & 0.410 & 4.456 & 0.692\\
-\hspace{1em}aorsf\_net & 0.714 (0.007) & 0.141 (0.007) & 237.007 & 39.2 & 237.337 & 36.9\\
-\hspace{1em}Party & 0.712 (0.008) & 0.141 (0.012) & 7.030 & 1.16 & 21.888 & 3.40\\
-\hspace{1em}aORSF(i=1) & 0.712 (0.006) & 0.139 (0.008) & 6.053 & 1.00 & 6.436 & 1.00\\
-\hspace{1em}aORSF(i=15) & 0.711 (0.005) & 0.139 (0.007) & 13.541 & 2.24 & 13.925 & 2.16\\
-\hspace{1em}Rfsrc & 0.701 (0.008) & 0.120 (0.010) & 2.222 & 0.367 & 2.458 & 0.382\\
+\hspace{1em}glmnet-cox & 0.029 (0.017) & 0.620 (0.024) & 0.101 & 0.798 & 0.002 & 0.075\\
+\hspace{1em}ranger-extratrees & 0.017 (0.016) & 0.596 (0.025) & 0.034 & 0.270 & 0.091 & 3.36\\
+\hspace{1em}obliqueRSF-net & 0.013 (0.016) & 0.592 (0.024) & 245.138 & 1,943.8 & 11.109 & 411.1\\
+\hspace{1em}aorsf-random & 0.012 (0.018) & 0.595 (0.024) & 0.473 & 3.75 & 0.024 & 0.892\\
+\hspace{1em}xgboost-cox & 0.010 (0.016) & 0.598 (0.032) & 1.315 & 10.4 & 0.003 & 0.111\\
+\hspace{1em}cif-standard & 0.007 (0.021) & 0.594 (0.023) & 0.950 & 7.54 & 1.722 & 63.7\\
+\hspace{1em}aorsf-fast & 0.007 (0.019) & 0.594 (0.025) & 0.126 & 1.00 & 0.027 & 1.00\\
+\hspace{1em}aorsf-cph & 0.007 (0.020) & 0.594 (0.026) & 0.272 & 2.16 & 0.028 & 1.04\\
+\hspace{1em}aorsf-net & 0.006 (0.020) & 0.592 (0.026) & 20.063 & 159.1 & 0.027 & 1.00\\
+\hspace{1em}nn-cox & 0.000 (0.019) & 0.546 (0.054) & 13.040 & 103.4 & 0.585 & 21.6\\
+\hspace{1em}cif-extension & -0.005 (0.023) & 0.580 (0.028) & 6.550 & 51.9 & 3.603 & 133.3\\
+\hspace{1em}cif-rotate & -0.012 (0.025) & 0.583 (0.030) & 7.129 & 56.5 & 3.081 & 114.0\\
+\hspace{1em}rsf-standard & -0.027 (0.032) & 0.577 (0.024) & 1.048 & 8.31 & 0.087 & 3.22\\
+\hspace{1em}xgboost-aft & -0.829 (0.337) & 0.582 (0.034) & 7.164 & 56.8 & 0.006 & 0.222\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{time\_to\_million}}}\\
+\multicolumn{7}{l}{\textit{\textbf{GBSG II; recurrence or death, n = 686, p = 10}}}\\
 \hline
-\hspace{1em}aorsf\_net & 0.937 (0.013) & 0.560 (0.040) & 78.384 & 55.8 & 78.461 & 53.0\\
-\hspace{1em}aORSF(i=15) & 0.937 (0.018) & 0.555 (0.043) & 4.491 & 3.20 & 4.569 & 3.09\\
-\hspace{1em}aORSF(i=1) & 0.935 (0.017) & 0.552 (0.039) & 1.405 & 1.00 & 1.481 & 1.00\\
-\hspace{1em}Rfsrc & 0.932 (0.023) & 0.550 (0.045) & 0.784 & 0.558 & 0.853 & 0.576\\
-\hspace{1em}Party & 0.921 (0.014) & 0.485 (0.034) & 0.621 & 0.442 & 1.684 & 1.14\\
-\hspace{1em}Ranger & 0.916 (0.023) & 0.452 (0.039) & 0.324 & 0.231 & 0.428 & 0.289\\
+\hspace{1em}obliqueRSF-net & 0.124 (0.016) & 0.745 (0.017) & 334.738 & 1,786.5 & 12.512 & 271.8\\
+\hspace{1em}cif-standard & 0.123 (0.020) & 0.742 (0.019) & 0.994 & 5.31 & 2.355 & 51.2\\
+\hspace{1em}rsf-standard & 0.120 (0.023) & 0.737 (0.019) & 1.669 & 8.91 & 0.113 & 2.46\\
+\hspace{1em}aorsf-net & 0.120 (0.024) & 0.737 (0.020) & 39.301 & 209.8 & 0.046 & 1.00\\
+\hspace{1em}aorsf-cph & 0.119 (0.025) & 0.735 (0.019) & 0.431 & 2.30 & 0.047 & 1.01\\
+\hspace{1em}aorsf-fast & 0.116 (0.024) & 0.732 (0.017) & 0.187 & 1.00 & 0.046 & 1.00\\
+\hspace{1em}cif-extension & 0.114 (0.017) & 0.742 (0.019) & 8.843 & 47.2 & 4.667 & 101.4\\
+\hspace{1em}cif-rotate & 0.107 (0.022) & 0.729 (0.017) & 12.995 & 69.4 & 5.199 & 112.9\\
+\hspace{1em}aorsf-random & 0.104 (0.024) & 0.723 (0.025) & 1.334 & 7.12 & 0.044 & 0.964\\
+\hspace{1em}ranger-extratrees & 0.094 (0.018) & 0.736 (0.025) & 0.099 & 0.526 & 0.132 & 2.87\\
+\hspace{1em}glmnet-cox & 0.091 (0.019) & 0.727 (0.021) & 0.141 & 0.752 & 0.003 & 0.065\\
+\hspace{1em}xgboost-cox & 0.083 (0.017) & 0.729 (0.020) & 2.577 & 13.8 & 0.003 & 0.065\\
+\hspace{1em}nn-cox & -0.004 (0.004) & 0.524 (0.065) & 12.618 & 67.3 & 1.165 & 25.3\\
+\hspace{1em}xgboost-aft & -1.10 (0.162) & 0.729 (0.021) & 11.930 & 63.7 & 0.007 & 0.152\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{vdv}}}\\
+\multicolumn{7}{l}{\textit{\textbf{GUIDE-IT; CVD death, n = 894, p = 59}}}\\
 \hline
-\hspace{1em}Rfsrc & 0.782 (0.231) & 0.033 (0.185) & 0.198 & 0.080 & 0.450 & 0.148\\
-\hspace{1em}aorsf\_net & 0.770 (0.161) & -0.019 (0.283) & 20.190 & 8.13 & 20.749 & 6.80\\
-\hspace{1em}aORSF(i=1) & 0.762 (0.079) & -0.012 (0.126) & 2.484 & 1.00 & 3.050 & 1.00\\
-\hspace{1em}Ranger & 0.751 (0.070) & -0.017 (0.093) & 0.484 & 0.195 & 0.576 & 0.189\\
-\hspace{1em}aORSF(i=15) & 0.735 (0.171) & -0.025 (0.135) & 2.569 & 1.03 & 3.136 & 1.03\\
-\hspace{1em}Party & 0.722 (0.102) & -0.030 (0.165) & 8.098 & 3.26 & 14.088 & 4.62\\
+\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.746 (0.027) & 0.174 & 1.00 & 0.037 & 1.00\\
+\hspace{1em}aorsf-net & 0.074 (0.019) & 0.743 (0.027) & 28.658 & 164.8 & 0.040 & 1.09\\
+\hspace{1em}aorsf-cph & 0.072 (0.018) & 0.743 (0.026) & 0.405 & 2.33 & 0.040 & 1.08\\
+\hspace{1em}glmnet-cox & 0.063 (0.041) & 0.715 (0.091) & 0.921 & 5.30 & 0.003 & 0.081\\
+\hspace{1em}obliqueRSF-net & 0.063 (0.013) & 0.741 (0.023) & 251.024 & 1,443.1 & 11.754 & 317.4\\
+\hspace{1em}cif-rotate & 0.059 (0.016) & 0.721 (0.025) & 37.291 & 214.4 & 4.884 & 131.9\\
+\hspace{1em}cif-standard & 0.058 (0.014) & 0.737 (0.022) & 2.228 & 12.8 & 3.646 & 98.5\\
+\hspace{1em}ranger-extratrees & 0.054 (0.013) & 0.737 (0.029) & 0.715 & 4.11 & 0.206 & 5.57\\
+\hspace{1em}cif-extension & 0.052 (0.011) & 0.730 (0.022) & 13.957 & 80.2 & 5.770 & 155.8\\
+\hspace{1em}rsf-standard & 0.046 (0.023) & 0.705 (0.025) & 1.219 & 7.01 & 0.075 & 2.03\\
+\hspace{1em}xgboost-cox & 0.039 (0.051) & 0.747 (0.020) & 4.233 & 24.3 & 0.003 & 0.081\\
+\hspace{1em}aorsf-random & 0.033 (0.012) & 0.695 (0.030) & 1.324 & 7.61 & 0.041 & 1.11\\
+\hspace{1em}nn-cox & 0.024 (0.036) & 0.686 (0.082) & 12.885 & 74.1 & 0.602 & 16.3\\
+\hspace{1em}xgboost-aft & -5.15 (0.987) & 0.734 (0.020) & 13.101 & 75.3 & 0.007 & 0.189\\
 \addlinespace[0.3em]
 \hline
-\multicolumn{7}{l}{\textit{\textbf{veteran}}}\\
+\multicolumn{7}{l}{\textit{\textbf{GUIDE-IT; HF hospitalization, n = 894, p = 59}}}\\
 \hline
-\hspace{1em}Ranger & 0.865 (0.063) & 0.183 (0.036) & 0.023 & 0.113 & 0.043 & 0.194\\
-\hspace{1em}aORSF(i=15) & 0.837 (0.048) & 0.281 (0.075) & 0.371 & 1.84 & 0.387 & 1.75\\
-\hspace{1em}aORSF(i=1) & 0.833 (0.053) & 0.278 (0.081) & 0.202 & 1.00 & 0.222 & 1.00\\
-\hspace{1em}Party & 0.833 (0.057) & 0.235 (0.056) & 0.150 & 0.744 & 0.231 & 1.04\\
-\hspace{1em}aorsf\_net & 0.820 (0.059) & 0.256 (0.083) & 17.115 & 84.7 & 17.133 & 77.3\\
-\hspace{1em}Rfsrc & 0.784 (0.111) & 0.218 (0.112) & 0.077 & 0.380 & 0.099 & 0.447\\*
+\hspace{1em}aorsf-net & 0.082 (0.017) & 0.722 (0.023) & 59.048 & 213.7 & 0.069 & 1.13\\
+\hspace{1em}aorsf-cph & 0.082 (0.018) & 0.722 (0.023) & 0.711 & 2.57 & 0.063 & 1.02\\
+\hspace{1em}aorsf-fast & 0.082 (0.019) & 0.722 (0.025) & 0.276 & 1.00 & 0.062 & 1.00\\
+\hspace{1em}ranger-extratrees & 0.074 (0.010) & 0.723 (0.022) & 0.703 & 2.54 & 0.215 & 3.49\\
+\hspace{1em}obliqueRSF-net & 0.074 (0.010) & 0.721 (0.023) & 468.654 & 1,695.9 & 14.749 & 239.1\\
+\hspace{1em}cif-standard & 0.071 (0.010) & 0.716 (0.023) & 1.958 & 7.09 & 3.737 & 60.6\\
+\hspace{1em}cif-rotate & 0.068 (0.018) & 0.708 (0.029) & 45.430 & 164.4 & 6.497 & 105.3\\
+\hspace{1em}cif-extension & 0.064 (0.009) & 0.714 (0.022) & 17.887 & 64.7 & 8.557 & 138.7\\
+\hspace{1em}rsf-standard & 0.059 (0.022) & 0.694 (0.026) & 1.390 & 5.03 & 0.112 & 1.81\\
+\hspace{1em}glmnet-cox & 0.058 (0.019) & 0.699 (0.024) & 0.980 & 3.54 & 0.003 & 0.049\\
+\hspace{1em}aorsf-random & 0.050 (0.010) & 0.682 (0.023) & 1.716 & 6.21 & 0.062 & 1.01\\
+\hspace{1em}xgboost-cox & 0.039 (0.017) & 0.698 (0.027) & 3.225 & 11.7 & 0.003 & 0.049\\
+\hspace{1em}nn-cox & 0.038 (0.028) & 0.683 (0.068) & 13.970 & 50.6 & 0.640 & 10.4\\
+\hspace{1em}xgboost-aft & -2.16 (0.322) & 0.696 (0.026) & 12.919 & 46.8 & 0.006 & 0.097\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Heart Transplant; graft-loss or death, n = 3787, p = 52}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.056 (0.010) & 0.731 (0.017) & 161.908 & 167.2 & 34.174 & 110.4\\
+\hspace{1em}aorsf-net & 0.053 (0.006) & 0.733 (0.013) & 132.397 & 136.8 & 0.313 & 1.01\\
+\hspace{1em}aorsf-fast & 0.052 (0.006) & 0.735 (0.014) & 0.968 & 1.00 & 0.309 & 1.00\\
+\hspace{1em}aorsf-cph & 0.051 (0.006) & 0.733 (0.013) & 3.094 & 3.20 & 0.312 & 1.01\\
+\hspace{1em}cif-standard & 0.050 (0.006) & 0.733 (0.013) & 11.540 & 11.9 & 43.325 & 140.0\\
+\hspace{1em}obliqueRSF-net & 0.049 (0.006) & 0.730 (0.014) & 363.594 & 375.6 & 168.051 & 543.1\\
+\hspace{1em}rsf-standard & 0.048 (0.009) & 0.727 (0.013) & 3.516 & 3.63 & 1.110 & 3.59\\
+\hspace{1em}ranger-extratrees & 0.046 (0.006) & 0.730 (0.013) & 5.812 & 6.00 & 3.555 & 11.5\\
+\hspace{1em}glmnet-cox & 0.036 (0.006) & 0.711 (0.016) & 1.023 & 1.06 & 0.012 & 0.039\\
+\hspace{1em}cif-extension & 0.036 (0.004) & 0.726 (0.016) & 51.192 & 52.9 & 25.128 & 81.2\\
+\hspace{1em}xgboost-cox & 0.031 (0.007) & 0.716 (0.018) & 3.516 & 3.63 & 0.011 & 0.036\\
+\hspace{1em}aorsf-random & 0.029 (0.003) & 0.693 (0.014) & 3.220 & 3.33 & 0.292 & 0.944\\
+\hspace{1em}nn-cox & 0.023 (0.012) & 0.677 (0.036) & 17.152 & 17.7 & 11.675 & 37.7\\
+\hspace{1em}xgboost-aft & -4.30 (0.486) & 0.724 (0.013) & 13.829 & 14.3 & 0.009 & 0.029\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Monoclonal gammopathy; death, n = 1384, p = 8}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.160 (0.019) & 0.744 (0.014) & 16.541 & 35.9 & 7.904 & 71.1\\
+\hspace{1em}aorsf-cph & 0.159 (0.016) & 0.742 (0.011) & 1.239 & 2.69 & 0.111 & 0.995\\
+\hspace{1em}aorsf-fast & 0.158 (0.016) & 0.742 (0.011) & 0.461 & 1.00 & 0.111 & 1.00\\
+\hspace{1em}aorsf-net & 0.156 (0.016) & 0.741 (0.011) & 99.187 & 215.0 & 0.109 & 0.977\\
+\hspace{1em}obliqueRSF-net & 0.156 (0.013) & 0.743 (0.011) & 239.204 & 518.6 & 17.341 & 155.9\\
+\hspace{1em}cif-standard & 0.151 (0.015) & 0.738 (0.012) & 2.162 & 4.69 & 8.068 & 72.6\\
+\hspace{1em}rsf-standard & 0.151 (0.017) & 0.737 (0.011) & 2.044 & 4.43 & 0.191 & 1.72\\
+\hspace{1em}aorsf-random & 0.146 (0.014) & 0.735 (0.012) & 2.586 & 5.61 & 0.104 & 0.940\\
+\hspace{1em}cif-extension & 0.144 (0.010) & 0.747 (0.013) & 11.336 & 24.6 & 6.951 & 62.5\\
+\hspace{1em}glmnet-cox & 0.138 (0.021) & 0.727 (0.014) & 0.140 & 0.304 & 0.004 & 0.036\\
+\hspace{1em}xgboost-cox & 0.123 (0.012) & 0.733 (0.012) & 3.706 & 8.03 & 0.005 & 0.045\\
+\hspace{1em}ranger-extratrees & 0.116 (0.005) & 0.744 (0.012) & 0.083 & 0.179 & 0.193 & 1.74\\
+\hspace{1em}nn-cox & 0.032 (0.057) & 0.614 (0.096) & 15.851 & 34.4 & 1.119 & 10.1\\
+\hspace{1em}xgboost-aft & -0.840 (0.148) & 0.733 (0.013) & 13.195 & 28.6 & 0.010 & 0.087\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Monoclonal gammopathy; malignancy, n = 1384, p = 8}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.015 (0.011) & 0.651 (0.055) & 0.119 & 0.587 & 0.002 & 0.048\\
+\hspace{1em}aorsf-cph & 0.010 (0.013) & 0.643 (0.036) & 0.608 & 3.01 & 0.043 & 1.02\\
+\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.641 (0.036) & 0.202 & 1.00 & 0.042 & 1.00\\
+\hspace{1em}ranger-extratrees & 0.008 (0.006) & 0.642 (0.030) & 0.072 & 0.356 & 0.785 & 18.6\\
+\hspace{1em}cif-extension & 0.008 (0.010) & 0.625 (0.028) & 9.606 & 47.5 & 5.217 & 123.3\\
+\hspace{1em}obliqueRSF-net & 0.007 (0.010) & 0.628 (0.033) & 44.947 & 222.2 & 16.670 & 393.9\\
+\hspace{1em}aorsf-net & 0.007 (0.014) & 0.641 (0.034) & 25.311 & 125.1 & 0.043 & 1.02\\
+\hspace{1em}aorsf-random & 0.007 (0.013) & 0.633 (0.033) & 1.367 & 6.76 & 0.042 & 0.993\\
+\hspace{1em}xgboost-cox & 0.007 (0.017) & 0.639 (0.039) & 1.886 & 9.32 & 0.003 & 0.071\\
+\hspace{1em}cif-standard & 0.006 (0.011) & 0.628 (0.033) & 1.730 & 8.55 & 5.759 & 136.1\\
+\hspace{1em}nn-cox & -0.003 (0.005) & 0.505 (0.041) & 12.035 & 59.5 & 1.253 & 29.6\\
+\hspace{1em}rsf-standard & -0.009 (0.018) & 0.616 (0.036) & 0.906 & 4.48 & 0.075 & 1.77\\
+\hspace{1em}cif-rotate & -0.024 (0.023) & 0.553 (0.035) & 13.627 & 67.4 & 4.933 & 116.6\\
+\hspace{1em}xgboost-aft & -5.59 (0.998) & 0.629 (0.039) & 10.872 & 53.7 & 0.007 & 0.166\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Movies released in 2015-2018; gross 1M USD, n = 551, p = 46}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.639 (0.023) & 0.943 (0.007) & 21.710 & 79.3 & 6.039 & 105.1\\
+\hspace{1em}glmnet-cox & 0.620 (0.033) & 0.940 (0.009) & 0.200 & 0.730 & 0.003 & 0.052\\
+\hspace{1em}nn-cox & 0.542 (0.082) & 0.906 (0.032) & 19.966 & 72.9 & 0.768 & 13.4\\
+\hspace{1em}aorsf-net & 0.531 (0.027) & 0.928 (0.010) & 55.942 & 204.3 & 0.060 & 1.05\\
+\hspace{1em}aorsf-cph & 0.523 (0.024) & 0.925 (0.011) & 0.810 & 2.96 & 0.059 & 1.03\\
+\hspace{1em}rsf-standard & 0.520 (0.021) & 0.922 (0.010) & 1.472 & 5.37 & 0.103 & 1.79\\
+\hspace{1em}aorsf-fast & 0.517 (0.026) & 0.922 (0.012) & 0.274 & 1.00 & 0.057 & 1.00\\
+\hspace{1em}xgboost-cox & 0.511 (0.028) & 0.932 (0.009) & 13.948 & 50.9 & 0.006 & 0.104\\
+\hspace{1em}cif-standard & 0.475 (0.028) & 0.902 (0.018) & 0.817 & 2.98 & 2.096 & 36.5\\
+\hspace{1em}cif-extension & 0.455 (0.024) & 0.920 (0.013) & 9.786 & 35.7 & 6.061 & 105.4\\
+\hspace{1em}ranger-extratrees & 0.431 (0.025) & 0.900 (0.019) & 0.079 & 0.289 & 0.114 & 1.98\\
+\hspace{1em}obliqueRSF-net & 0.320 (0.022) & 0.909 (0.017) & 155.578 & 568.2 & 27.372 & 476.1\\
+\hspace{1em}aorsf-random & 0.300 (0.031) & 0.849 (0.027) & 1.481 & 5.41 & 0.053 & 0.923\\
+\hspace{1em}xgboost-aft & -0.477 (0.082) & 0.927 (0.010) & 48.721 & 177.9 & 0.009 & 0.156\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Non-alcohol fatty liver disease; death, n = 17549, p = 24}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.215 (0.008) & 0.868 (0.005) & 19.970 & 3.60 & 15.802 & 1.40\\
+\hspace{1em}aorsf-fast & 0.215 (0.009) & 0.869 (0.005) & 5.540 & 1.00 & 11.287 & 1.00\\
+\hspace{1em}aorsf-net & 0.213 (0.008) & 0.864 (0.006) & 502.140 & 90.6 & 10.259 & 0.909\\
+\hspace{1em}obliqueRSF-net & 0.212 (0.008) & 0.868 (0.006) & 1536.877 & 277.4 & 6754.575 & 598.4\\
+\hspace{1em}rsf-standard & 0.210 (0.009) & 0.860 (0.005) & 12.179 & 2.20 & 1.378 & 0.122\\
+\hspace{1em}glmnet-cox & 0.209 (0.011) & 0.861 (0.005) & 1.900 & 0.343 & 0.876 & 0.078\\
+\hspace{1em}cif-standard & 0.208 (0.007) & 0.863 (0.006) & 72.584 & 13.1 & 753.937 & 66.8\\
+\hspace{1em}cif-rotate & 0.193 (0.008) & 0.866 (0.005) & 288.250 & 52.0 & 224.923 & 19.9\\
+\hspace{1em}ranger-extratrees & 0.183 (0.007) & 0.860 (0.005) & 46.126 & 8.33 & 146.397 & 13.0\\
+\hspace{1em}cif-extension & 0.168 (0.003) & 0.866 (0.006) & 129.626 & 23.4 & 211.122 & 18.7\\
+\hspace{1em}aorsf-random & 0.142 (0.007) & 0.838 (0.007) & 15.152 & 2.73 & 14.820 & 1.31\\
+\hspace{1em}xgboost-cox & 0.023 (0.015) & 0.876 (0.005) & 8.989 & 1.62 & 1.026 & 0.091\\
+\hspace{1em}nn-cox & -0.001 (0.009) & 0.577 (0.108) & 31.442 & 5.68 & 192.811 & 17.1\\
+\hspace{1em}xgboost-aft & -7.27 (0.765) & 0.875 (0.005) & 28.699 & 5.18 & 0.807 & 0.072\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Primary biliary cholangitis; death, n = 276, p = 19}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.430 (0.033) & 0.908 (0.021) & 0.081 & 1.00 & 0.020 & 1.00\\
+\hspace{1em}aorsf-cph & 0.418 (0.034) & 0.906 (0.021) & 0.161 & 2.00 & 0.020 & 0.996\\
+\hspace{1em}aorsf-net & 0.412 (0.035) & 0.905 (0.022) & 16.130 & 200.3 & 0.020 & 1.00\\
+\hspace{1em}cif-rotate & 0.405 (0.041) & 0.899 (0.022) & 9.930 & 123.3 & 2.165 & 107.7\\
+\hspace{1em}rsf-standard & 0.391 (0.034) & 0.895 (0.023) & 0.111 & 1.37 & 0.040 & 2.01\\
+\hspace{1em}obliqueRSF-net & 0.369 (0.032) & 0.906 (0.022) & 114.388 & 1,420.7 & 1.934 & 96.2\\
+\hspace{1em}aorsf-random & 0.354 (0.031) & 0.893 (0.020) & 0.373 & 4.63 & 0.020 & 1.00\\
+\hspace{1em}cif-standard & 0.351 (0.034) & 0.904 (0.025) & 0.241 & 2.99 & 1.152 & 57.3\\
+\hspace{1em}cif-extension & 0.348 (0.033) & 0.901 (0.023) & 9.607 & 119.3 & 3.745 & 186.4\\
+\hspace{1em}glmnet-cox & 0.342 (0.045) & 0.886 (0.028) & 0.115 & 1.43 & 0.002 & 0.101\\
+\hspace{1em}ranger-extratrees & 0.276 (0.028) & 0.894 (0.027) & 0.028 & 0.348 & 0.040 & 2.00\\
+\hspace{1em}xgboost-cox & 0.256 (0.104) & 0.881 (0.027) & 4.597 & 57.1 & 0.003 & 0.149\\
+\hspace{1em}nn-cox & -0.035 (0.064) & 0.577 (0.166) & 11.413 & 141.7 & 0.242 & 12.0\\
+\hspace{1em}xgboost-aft & -0.953 (0.305) & 0.883 (0.024) & 8.994 & 111.7 & 0.006 & 0.299\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Rotterdam tumor bank; death, n = 2982, p = 11}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.167 (0.012) & 0.762 (0.009) & 158.184 & 167.0 & 0.393 & 0.928\\
+\hspace{1em}obliqueRSF-net & 0.164 (0.010) & 0.761 (0.009) & 522.346 & 551.5 & 122.804 & 289.7\\
+\hspace{1em}aorsf-cph & 0.164 (0.012) & 0.758 (0.009) & 2.691 & 2.84 & 0.421 & 0.994\\
+\hspace{1em}aorsf-fast & 0.162 (0.012) & 0.757 (0.009) & 0.947 & 1.00 & 0.424 & 1.00\\
+\hspace{1em}cif-standard & 0.160 (0.010) & 0.759 (0.009) & 7.041 & 7.43 & 43.238 & 102.0\\
+\hspace{1em}rsf-standard & 0.160 (0.014) & 0.756 (0.009) & 2.859 & 3.02 & 0.865 & 2.04\\
+\hspace{1em}aorsf-random & 0.154 (0.010) & 0.752 (0.010) & 4.162 & 4.39 & 0.392 & 0.925\\
+\hspace{1em}cif-rotate & 0.148 (0.011) & 0.750 (0.011) & 34.744 & 36.7 & 29.541 & 69.7\\
+\hspace{1em}ranger-extratrees & 0.140 (0.006) & 0.748 (0.009) & 3.506 & 3.70 & 2.848 & 6.72\\
+\hspace{1em}xgboost-cox & 0.131 (0.014) & 0.753 (0.010) & 4.796 & 5.06 & 0.020 & 0.047\\
+\hspace{1em}cif-extension & 0.131 (0.004) & 0.751 (0.008) & 23.585 & 24.9 & 30.945 & 73.0\\
+\hspace{1em}glmnet-cox & 0.119 (0.008) & 0.731 (0.009) & 0.671 & 0.708 & 0.018 & 0.043\\
+\hspace{1em}nn-cox & -0.005 (0.011) & 0.506 (0.043) & 17.750 & 18.7 & 9.921 & 23.4\\
+\hspace{1em}xgboost-aft & -1.34 (0.161) & 0.761 (0.009) & 14.771 & 15.6 & 0.010 & 0.024\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Rotterdam tumor bank; recurrence, n = 2982, p = 11}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.148 (0.010) & 0.737 (0.009) & 547.423 & 508.8 & 133.525 & 289.3\\
+\hspace{1em}aorsf-net & 0.147 (0.011) & 0.735 (0.009) & 168.357 & 156.5 & 0.425 & 0.922\\
+\hspace{1em}aorsf-cph & 0.145 (0.011) & 0.734 (0.009) & 2.986 & 2.78 & 0.453 & 0.981\\
+\hspace{1em}cif-standard & 0.145 (0.011) & 0.734 (0.009) & 5.054 & 4.70 & 30.784 & 66.7\\
+\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 1.076 & 1.00 & 0.462 & 1.00\\
+\hspace{1em}aorsf-random & 0.140 (0.010) & 0.730 (0.008) & 4.277 & 3.97 & 0.423 & 0.917\\
+\hspace{1em}rsf-standard & 0.139 (0.012) & 0.731 (0.008) & 3.016 & 2.80 & 0.372 & 0.806\\
+\hspace{1em}ranger-extratrees & 0.135 (0.007) & 0.733 (0.009) & 3.616 & 3.36 & 2.835 & 6.14\\
+\hspace{1em}cif-rotate & 0.130 (0.010) & 0.725 (0.009) & 37.506 & 34.9 & 35.411 & 76.7\\
+\hspace{1em}cif-extension & 0.119 (0.006) & 0.731 (0.008) & 24.957 & 23.2 & 29.569 & 64.1\\
+\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.727 (0.008) & 0.706 & 0.656 & 0.028 & 0.061\\
+\hspace{1em}xgboost-cox & 0.114 (0.008) & 0.729 (0.009) & 3.816 & 3.55 & 0.020 & 0.044\\
+\hspace{1em}nn-cox & -0.002 (0.002) & 0.534 (0.068) & 21.275 & 19.8 & 9.967 & 21.6\\
+\hspace{1em}xgboost-aft & -1.01 (0.129) & 0.735 (0.009) & 15.443 & 14.4 & 0.010 & 0.022\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Serum free light chain; death, n = 7874, p = 10}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.252 (0.014) & 0.825 (0.007) & 2.664 & 1.00 & 4.471 & 1.00\\
+\hspace{1em}aorsf-cph & 0.252 (0.013) & 0.825 (0.008) & 7.125 & 2.67 & 5.990 & 1.34\\
+\hspace{1em}aorsf-net & 0.252 (0.012) & 0.823 (0.008) & 320.194 & 120.2 & 5.152 & 1.15\\
+\hspace{1em}glmnet-cox & 0.249 (0.012) & 0.820 (0.007) & 1.217 & 0.457 & 0.099 & 0.022\\
+\hspace{1em}obliqueRSF-net & 0.249 (0.011) & 0.821 (0.008) & 1170.382 & 439.3 & 814.990 & 182.3\\
+\hspace{1em}ranger-extratrees & 0.245 (0.009) & 0.820 (0.007) & 15.036 & 5.64 & 13.481 & 3.02\\
+\hspace{1em}cif-standard & 0.245 (0.011) & 0.818 (0.008) & 20.391 & 7.65 & 155.387 & 34.8\\
+\hspace{1em}rsf-standard & 0.245 (0.013) & 0.815 (0.008) & 5.872 & 2.20 & 0.575 & 0.129\\
+\hspace{1em}aorsf-random & 0.233 (0.012) & 0.816 (0.008) & 9.238 & 3.47 & 4.902 & 1.10\\
+\hspace{1em}cif-rotate & 0.230 (0.009) & 0.819 (0.007) & 67.494 & 25.3 & 137.166 & 30.7\\
+\hspace{1em}cif-extension & 0.203 (0.005) & 0.820 (0.008) & 44.122 & 16.6 & 162.158 & 36.3\\
+\hspace{1em}xgboost-cox & 0.097 (0.038) & 0.824 (0.007) & 6.133 & 2.30 & 0.101 & 0.023\\
+\hspace{1em}nn-cox & 0.003 (0.006) & 0.612 (0.135) & 25.297 & 9.49 & 27.315 & 6.11\\
+\hspace{1em}xgboost-aft & -2.71 (0.293) & 0.823 (0.008) & 22.227 & 8.34 & 0.035 & 0.008\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{sim}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.034 (0.022) & 0.632 (0.038) & 224.558 & 187.4 & 72.991 & 1.36\\
+\hspace{1em}aorsf-cph & 0.033 (0.023) & 0.635 (0.038) & 3.021 & 2.52 & 61.620 & 1.15\\
+\hspace{1em}aorsf-fast & 0.029 (0.023) & 0.636 (0.038) & 1.198 & 1.00 & 53.771 & 1.00\\
+\hspace{1em}aorsf-random & 0.029 (0.013) & 0.616 (0.033) & 7.759 & 6.47 & 68.892 & 1.28\\
+\hspace{1em}obliqueRSF-net & 0.027 (0.016) & 0.613 (0.043) & 910.443 & 759.7 & 380.178 & 7.07\\
+\hspace{1em}cif-standard & 0.023 (0.015) & 0.603 (0.043) & 6.188 & 5.16 & 231.294 & 4.30\\
+\hspace{1em}cif-rotate & 0.020 (0.021) & 0.592 (0.051) & 316.904 & 264.4 & 801.648 & 14.9\\
+\hspace{1em}rsf-standard & 0.019 (0.014) & 0.610 (0.032) & 5.788 & 4.83 & 2.322 & 0.043\\
+\hspace{1em}ranger-extratrees & 0.018 (0.008) & 0.620 (0.037) & 4.820 & 4.02 & 6.453 & 0.120\\
+\hspace{1em}cif-extension & 0.015 (0.008) & 0.599 (0.040) & 107.025 & 89.3 & 1030.394 & 19.2\\
+\hspace{1em}xgboost-cox & -0.023 (0.043) & 0.616 (0.039) & 17.126 & 14.3 & 1.747 & 0.032\\
+\hspace{1em}glmnet-cox & -0.036 (0.064) & 0.616 (0.040) & 0.545 & 0.455 & 1.462 & 0.027\\
+\hspace{1em}nn-cox & -0.059 (0.071) & 0.616 (0.043) & 29.897 & 24.9 & 18.594 & 0.346\\
+\hspace{1em}xgboost-aft & -1.66 (0.126) & 0.624 (0.038) & 52.084 & 43.5 & 1.380 & 0.026\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{SPRINT; CVD death, n = 9361, p = 174}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.072 (0.011) & 0.796 (0.011) & 14.356 & 4.42 & 0.033 & 0.036\\
+\hspace{1em}aorsf-net & 0.071 (0.007) & 0.796 (0.011) & 343.232 & 105.7 & 0.949 & 1.05\\
+\hspace{1em}aorsf-cph & 0.070 (0.006) & 0.798 (0.011) & 9.991 & 3.08 & 0.971 & 1.07\\
+\hspace{1em}aorsf-fast & 0.070 (0.006) & 0.798 (0.011) & 3.248 & 1.00 & 0.908 & 1.00\\
+\hspace{1em}obliqueRSF-net & 0.068 (0.004) & 0.798 (0.012) & 1161.784 & 357.7 & 1311.066 & 1,444.0\\
+\hspace{1em}rsf-standard & 0.065 (0.007) & 0.789 (0.014) & 5.167 & 1.59 & 0.685 & 0.755\\
+\hspace{1em}cif-standard & 0.062 (0.003) & 0.798 (0.011) & 51.058 & 15.7 & 199.723 & 220.0\\
+\hspace{1em}cif-rotate & 0.061 (0.005) & 0.791 (0.012) & 1033.390 & 318.1 & 136.883 & 150.8\\
+\hspace{1em}ranger-extratrees & 0.055 (0.003) & 0.792 (0.012) & 8.015 & 2.47 & 9.226 & 10.2\\
+\hspace{1em}nn-cox & 0.040 (0.013) & 0.765 (0.017) & 24.177 & 7.44 & 33.019 & 36.4\\
+\hspace{1em}cif-extension & 0.034 (0.002) & 0.790 (0.011) & 123.690 & 38.1 & 53.842 & 59.3\\
+\hspace{1em}aorsf-random & 0.027 (0.002) & 0.747 (0.016) & 6.889 & 2.12 & 1.101 & 1.21\\
+\hspace{1em}xgboost-cox & 0.006 (0.017) & 0.800 (0.011) & 7.910 & 2.44 & 0.033 & 0.036\\
+\hspace{1em}xgboost-aft & -10.8 (1.01) & 0.796 (0.012) & 24.603 & 7.57 & 0.016 & 0.018\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{SPRINT; death, n = 9361, p = 174}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.124 (0.012) & 0.771 (0.009) & 5.349 & 1.10 & 0.080 & 0.016\\
+\hspace{1em}aorsf-cph & 0.118 (0.008) & 0.770 (0.008) & 14.219 & 2.92 & 3.629 & 0.751\\
+\hspace{1em}aorsf-fast & 0.117 (0.008) & 0.770 (0.008) & 4.874 & 1.00 & 4.833 & 1.00\\
+\hspace{1em}aorsf-net & 0.114 (0.009) & 0.769 (0.009) & 657.473 & 134.9 & 4.336 & 0.897\\
+\hspace{1em}obliqueRSF-net & 0.113 (0.007) & 0.767 (0.008) & 3057.859 & 627.3 & 1289.532 & 266.8\\
+\hspace{1em}rsf-standard & 0.111 (0.008) & 0.763 (0.009) & 6.755 & 1.39 & 0.729 & 0.151\\
+\hspace{1em}cif-standard & 0.107 (0.006) & 0.764 (0.008) & 46.959 & 9.63 & 212.057 & 43.9\\
+\hspace{1em}nn-cox & 0.099 (0.014) & 0.757 (0.011) & 68.533 & 14.1 & 64.373 & 13.3\\
+\hspace{1em}ranger-extratrees & 0.097 (0.005) & 0.756 (0.009) & 11.099 & 2.28 & 11.653 & 2.41\\
+\hspace{1em}cif-rotate & 0.092 (0.007) & 0.745 (0.009) & 1108.036 & 227.3 & 188.939 & 39.1\\
+\hspace{1em}cif-extension & 0.056 (0.002) & 0.747 (0.009) & 139.289 & 28.6 & 103.221 & 21.4\\
+\hspace{1em}aorsf-random & 0.053 (0.003) & 0.720 (0.010) & 13.605 & 2.79 & 4.437 & 0.918\\
+\hspace{1em}xgboost-cox & 0.031 (0.023) & 0.772 (0.008) & 9.951 & 2.04 & 0.084 & 0.017\\
+\hspace{1em}xgboost-aft & -4.41 (0.302) & 0.772 (0.008) & 28.705 & 5.89 & 0.653 & 0.135\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{Systolic Heart Failure; death, n = 2231, p = 41}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.114 (0.012) & 0.747 (0.012) & 407.606 & 340.6 & 60.875 & 257.1\\
+\hspace{1em}glmnet-cox & 0.114 (0.013) & 0.746 (0.012) & 0.791 & 0.661 & 0.019 & 0.080\\
+\hspace{1em}cif-rotate & 0.113 (0.013) & 0.741 (0.011) & 72.623 & 60.7 & 22.449 & 94.8\\
+\hspace{1em}aorsf-net & 0.112 (0.013) & 0.743 (0.012) & 125.118 & 104.6 & 0.243 & 1.03\\
+\hspace{1em}aorsf-cph & 0.111 (0.014) & 0.744 (0.012) & 2.822 & 2.36 & 0.237 & 1.00\\
+\hspace{1em}aorsf-fast & 0.110 (0.015) & 0.744 (0.011) & 1.197 & 1.00 & 0.237 & 1.00\\
+\hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 5.168 & 4.32 & 22.720 & 96.0\\
+\hspace{1em}rsf-standard & 0.105 (0.011) & 0.735 (0.011) & 2.800 & 2.34 & 0.304 & 1.29\\
+\hspace{1em}cif-extension & 0.094 (0.006) & 0.744 (0.012) & 30.964 & 25.9 & 19.184 & 81.0\\
+\hspace{1em}ranger-extratrees & 0.092 (0.008) & 0.738 (0.012) & 4.404 & 3.68 & 1.442 & 6.09\\
+\hspace{1em}xgboost-cox & 0.090 (0.009) & 0.744 (0.010) & 4.784 & 4.00 & 0.010 & 0.042\\
+\hspace{1em}aorsf-random & 0.080 (0.006) & 0.731 (0.013) & 3.206 & 2.68 & 0.230 & 0.974\\
+\hspace{1em}nn-cox & 0.077 (0.024) & 0.711 (0.023) & 23.045 & 19.3 & 5.516 & 23.3\\
+\hspace{1em}xgboost-aft & -1.98 (0.218) & 0.742 (0.009) & 14.099 & 11.8 & 0.010 & 0.042\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{VA lung cancer trial; death, n = 137, p = 8}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.201 (0.051) & 0.797 (0.035) & 10.595 & 189.0 & 0.013 & 1.07\\
+\hspace{1em}aorsf-fast & 0.200 (0.050) & 0.795 (0.034) & 0.056 & 1.00 & 0.012 & 1.00\\
+\hspace{1em}cif-rotate & 0.198 (0.066) & 0.788 (0.036) & 4.899 & 87.4 & 1.095 & 90.3\\
+\hspace{1em}aorsf-cph & 0.198 (0.052) & 0.794 (0.035) & 0.104 & 1.85 & 0.012 & 0.998\\
+\hspace{1em}rsf-standard & 0.175 (0.048) & 0.787 (0.037) & 0.083 & 1.48 & 0.030 & 2.46\\
+\hspace{1em}cif-extension & 0.173 (0.048) & 0.795 (0.034) & 5.230 & 93.3 & 1.640 & 135.3\\
+\hspace{1em}glmnet-cox & 0.160 (0.036) & 0.787 (0.038) & 0.091 & 1.62 & 0.002 & 0.165\\
+\hspace{1em}aorsf-random & 0.154 (0.045) & 0.780 (0.037) & 0.226 & 4.04 & 0.012 & 0.991\\
+\hspace{1em}cif-standard & 0.128 (0.040) & 0.770 (0.037) & 0.096 & 1.71 & 0.122 & 10.1\\
+\hspace{1em}obliqueRSF-net & 0.126 (0.034) & 0.796 (0.029) & 65.750 & 1,173.0 & 0.688 & 56.8\\
+\hspace{1em}ranger-extratrees & 0.091 (0.033) & 0.778 (0.038) & 0.021 & 0.377 & 0.029 & 2.42\\
+\hspace{1em}xgboost-cox & 0.068 (0.078) & 0.750 (0.046) & 1.291 & 23.0 & 0.002 & 0.165\\
+\hspace{1em}xgboost-aft & -0.009 (0.136) & 0.753 (0.047) & 6.788 & 121.1 & 0.006 & 0.495\\
+\hspace{1em}nn-cox & -0.039 (0.036) & 0.505 (0.078) & 11.297 & 201.6 & 0.165 & 13.6\\*
 \end{longtable}

### 2022-06-15 paper/jmlr/main.Rnw
prep for simsurv update

@@
 
-\subsection{Benchmark of prediction accuracy}
+\subsection{Benchmark of prediction accuracy and computational efficiency}
 
@@
 \\
+
  \hline\hline
@@
  \hline\hline
- Cox Net & \texttt{glmnet} & \texttt{glmnet-cox} & The Cox proportional hazards model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
+
+ Cox Net &
+
+ \texttt{glmnet} &
+
+ \texttt{glmnet-cox} &
+
+ The Cox proportional hazards model is fit using an elastic net penalty. Nested cross validation (5 folds) is applied to tune penalty terms.\\
+
  \hline\hline
@@
  \hline\hline
- Cox Time & \href{https://raphaels1.github.io/survivalmodels/}{\texttt{survivalmodels}} & \texttt{nn-cox} & A neural network based on the proportional hazards model with time-varying effects.
+
+ Cox Time &
+
+ \href{https://raphaels1.github.io/survivalmodels/}{\texttt{survivalmodels}} &
+
+ \texttt{nn-cox} &
+
+ A neural network based on the proportional hazards model with time-varying effects.
 Nested cross-validation was applied to select the number of layers (from 1 to 8), the number of nodes in each layer (from $\sqrt{p}$/2 to $\sqrt{p}$), and the number of epochs to complete (up to 500).
@@
  \hline
+
 \end{tabular}
@@
 
+\subsubsection{Data sets}
+
 \subsubsection{Evaluation of prediction accuracy} \label{sec:prediction_accuracy}
 
-Our primary metric for evaluating the accuracy of predicted risk is the integrated and scaled Brier score \citep{graf1999assessment}.
-For observation $i$ in the testing data, let $\widehat{S}(t \mid \bm{x}_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$ and let $\bm{x}_i$ be the vector of predictor values.
-Define \begin{align*}
+Our primary metric for evaluating the accuracy of predicted risk is the integrated and scaled Brier score \citep{graf1999assessment}. Consider a testing data set:
+$$\dataset_{\text{test}} = \left\{ (T_i, \delta_i, x_{i}) \right\}_{i=1}^{N_{\text{test}}}.$$
+Let $\widehat{S}(t \mid x_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$.
+ For observation $i$ in $\dataset_{\text{test}}$, let $\widehat{S}(t \mid \bm{x}_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$. Define \begin{align*}
 \bstat = \frac{1}{\ntest} \sum_{i=1}^{\ntest} &\{ \widehat{S}(t \mid \bm{x}_i)^2 \cdot I(T_i \leq t, \delta_i = 1) \cdot \widehat{G}(T_i)^{-1} \\ &+ [1-\widehat{S}(t \mid \bm{x}_i)]^2 \cdot I(T_i > t) \cdot \widehat{G}(t)^{-1}\}

### 2022-06-15 paper/jmlr/main.tex
prep for simsurv update

@@
 
-Our primary metric for evaluating the accuracy of predicted risk is the integrated and scaled Brier score \citep{graf1999assessment}.
-For observation $i$ in the testing data, let $\widehat{S}(t \mid \bm{x}_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$ and let $\bm{x}_i$ be the vector of predictor values.
-Define \begin{align*}
+Our primary metric for evaluating the accuracy of predicted risk is the integrated and scaled Brier score \citep{graf1999assessment}. Consider a testing data set:
+$$\dataset_{\text{test}} = \left\{ (T_i, \delta_i, x_{i}) \right\}_{i=1}^{N_{\text{test}}}.$$
+Let $\widehat{S}(t \mid x_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$.
+ For observation $i$ in $\dataset_{\text{test}}$, let $\widehat{S}(t \mid \bm{x}_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$. Define \begin{align*}
 \bstat = \frac{1}{\ntest} \sum_{i=1}^{\ntest} &\{ \widehat{S}(t \mid \bm{x}_i)^2 \cdot I(T_i \leq t, \delta_i = 1) \cdot \widehat{G}(T_i)^{-1} \\ &+ [1-\widehat{S}(t \mid \bm{x}_i)]^2 \cdot I(T_i > t) \cdot \widehat{G}(t)^{-1}\}

### 2022-06-20 docs/index.Rmd
adding VI to slides

@@
   warning = FALSE,
-  dpi = 600,
+  dpi = 100,
   fig.align='center',
@@
 
+library(targets)
 library(tidyverse)
@@
     bm_pred_viz,
+    bm_vi_smry,
     data_key
@@
 
-    + Decision trees
-
-    + Random survival forests (RSF)
-
 - Accelerating the oblique RSF
 
-    + Newton Raphson scoring
+- Benchmark of prediction accuracy
 
-- Benchmark
+- Benchmark of variable importance
 
-    + Datasets & learners
-
-    + Evaluation
-
-    + Results
-
-- Software
-
-    + R package & website
+- R package & website
 
@@
 ---
+
+## Negation variable importance (VI)
+
+Negation VI is similar to permutation VI in that it measures how much a model’s prediction error increases when a variable’s role in the model is de-stabilized.
+
+- Negation VI measures the increase in an oblique RF's prediction error after flipping the sign of all coefficients linked to a variable.
+
+- As the magnitude of a coefficient increases, so does the probability that negating it will change the oblique RF's predictions.
+
+- Since the coefficients in each non-leaf node of an oblique RFs are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
+
+---
 class: center, middle, inverse
 
-# .larger[Benchmark]
+# .larger[Prediction Benchmark]
 
@@
 ---
+class: center, middle, inverse
+
+# .larger[Variable Importance Benchmark]
+
+---
+
+## Variable importance techniques
+
+- `randomForestSRC-permutation` - the classic approach proposed by Leo Breiman
+
+- `aorsf-negation` - the new approach I am proposing
+
+- `aorsf-anova` - The only (?) other variable importance technique for oblique random forests
+
+- `aorsf-shap` - SHAP values from an accelerated oblique RSF model
+
+- `xgboost-shap` - SHAP values from an xgboost model (gold standard)
+
+- `xgboost-gain` - Gain importance from an xgboost model (classic)
+
+---
+
+## Simulated data
+
+We simulated five classes of predictor variables:
+
+- __junk__: no relationship with the outcome.
+
+- __main__: linearly related to the outcome
+
+- __non-linear__: sinusoidal relationship to the outcome
+
+- __combination__: latent variables formed from combinations of the combination variables have a linear relationship to the outcome.
+
+- __interactions__: related to the outcome by multiplicative interaction with one other variable.
+
+---
+
+## Simulated data
+
+Start with a multivariate normal draw
+
+- All columns have a mean of zero and standard deviation of 1.
+
+- Pairwise correlations are selected at random uniformly between a lower and upper boundary.
+
+- A predictor matrix including interactions, non-linear mappings, and linear combinations is used to generate a time-to-event outcome using the `simsurv` R package
+
+- Transforms are dropped from the matrix after generating the outcome values.
+
+---
+
+## Evaluation
+
+VI techniques are compared based on their discrimination (C-statistic) between relevant and irrelevant variables.
+
+Normally a C-statistic assesses if a predicted score discriminates between positive and negative cases of a binary outcome.
+
+We use the C-statistic differently by treating each variable like a binary outcome (e.g., the outcome is 1 if the variable is relevant, 0 otherwise).
+
+In other words, we assess VI as if it were a ‘prediction’ for the status of the variable. (can only do this for simulated data).
+
+The resulting C-statistic measures the probability that a VI technique will rank a relevant variable higher than an irrelevant variable.
+
+---
+
+```{r out.width='100%', fig.align='center'}
+
+library(plotly)
+
+fig_data <- bm_vi_smry %>%
+  ungroup() %>%
+  filter(n_obs == 1000) %>%
+  mutate(
+    model = recode(
+      model, 'randomForestSRC-permutation' = 'rfsrc-permutation'
+    ),
+    model = fct_reorder(model, .x = overall),
+    pred_corr_max = factor(pred_corr_max),
+    text = table_glue(
+      "{model}<br>\\
+          Mean computation time: {as.numeric(time)} seconds<br>\\
+          C-statistic by variable class:<br>\\
+          Main effect: {main}<br>\\
+          Non-linear effect: {nlin}<br>\\
+          Combination effect: {cmbn}<br>\\
+          Interactions:<br>\\
+             w/main effect: {intr_main}<br>\\
+             w/non-linear effect: {intr_hidden_nlin}<br>\\
+             w/combination effect: {intr_hidden_cmbn}"
+    ))
+
+fig <- plot_ly(width = 800, height = 650) %>%
+  add_trace(
+    type = 'bar',
+    x = fig_data$pred_corr_max,
+    y = fig_data$overall,
+    color = fig_data$model,
+    text = table_value(fig_data$overall),
+    textposition = 'outside',
+    hoverinfo = 'text',
+    hovertext = fig_data$text
+  ) %>%
+  plotly::layout(
+    title = list(text = 'Results when N = 1000', x = 0.1),
+    xaxis = list(title = 'Max correlation among predictors'),
+    yaxis = list(title = 'C-statistic'),
+    legend = list(title = list(text = '<b>VI technique</b>'))
+  )
+
+fig
+
+```
+
+---
+
+```{r out.width='100%', fig.align='center'}
+
+library(plotly)
+
+fig_data <- bm_vi_smry %>%
+  ungroup() %>%
+  filter(n_obs == 5000) %>%
+  mutate(
+    model = recode(
+      model, 'randomForestSRC-permutation' = 'rfsrc-permutation'
+    ),
+    model = fct_reorder(model, .x = overall),
+    pred_corr_max = factor(pred_corr_max),
+    text = table_glue(
+      "{model}<br>\\
+          Mean computation time: {as.numeric(time)} seconds<br>\\
+          C-statistic by variable class:<br>\\
+          Main effect: {main}<br>\\
+          Non-linear effect: {nlin}<br>\\
+          Combination effect: {cmbn}<br>\\
+          Interactions:<br>\\
+             w/main effect: {intr_main}<br>\\
+             w/non-linear effect: {intr_hidden_nlin}<br>\\
+             w/combination effect: {intr_hidden_cmbn}"
+    ))
+
+fig <- plot_ly(width = 800, height = 650) %>%
+  add_trace(
+    type = 'bar',
+    x = fig_data$pred_corr_max,
+    y = fig_data$overall,
+    color = fig_data$model,
+    text = table_value(fig_data$overall),
+    textposition = 'outside',
+    hoverinfo = 'text',
+    hovertext = fig_data$text
+  ) %>%
+  plotly::layout(
+    title = list(text = 'Results when N = 5000', x = 0.1),
+    xaxis = list(title = 'Max correlation among predictors'),
+    yaxis = list(title = 'C-statistic'),
+    legend = list(title = list(text = '<b>VI technique</b>'))
+  )
+
+fig
+
+```
+
+---
 
 ## Using the accelerated oblique RSF
+
+(https://bcjaeger.github.io/aorsf/)
 

### 2022-06-20 paper/jmlr/main.Rnw
adding VI to slides

@@
 \newcommand{\ntest}{N_{\text{test}}}
+
+\newcommand{\secref}[1]{Section \ref{#1}}
 
@@
                       message = FALSE,
-                      dpi = 300)
+                      dpi = 600)
 
@@
 
-tar_load(names = c(bm_pred_comb,
+tar_load(names = c(bm_pred_clean,
                    bm_vi_comb,
@@
 
-to_omit <- bm_pred_comb |>
-  filter(is.na(cstat) | is.na(ibs_scaled)) |>
-  distinct(data, run) |>
-  as.list() |>
-  map(unique)
-
-bm_pred_comb <- bm_pred_comb |>
-  filter( ! (data %in% to_omit$data & run %in% to_omit$run) )
+bm_pred_comb <- bm_pred_clean
 
@@
 
-\section{Novel techniques for oblique random survival forests}
+\section{The acceleracted oblique random survival forest}
 
@@
 Since the coefficients in each non-leaf node of an oblique RFs are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
-Although the current article focuses on oblique RSFs, negation VI can be applied to any oblique RF.
+
+For consistency with prior VI techniques for the RSF and for its computational efficiency, we use Harrell's concordance (C)-statistic \citep{harrell1982evaluating} to measure change in prediction error when computing negation VI.
+We also note that while the current article focuses on oblique RSFs, negation VI can be applied to any oblique RF and can be applied with any applicable error function.
 
@@
 
-\subsubsection{Learners}
+The aim of this numeric experiment is to evaluate and compare the accelerated oblique RSF with its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and with other machine learning algorithms for risk prediction.
+Inferences drawn from this experiment include equivalence and inferiority tests based on Bayesian hierarchical models.
+
+\subsubsection{Learners} \label{sec:learners}
 
@@
 
-\subsubsection{Data sets}
-
 \subsubsection{Evaluation of prediction accuracy} \label{sec:prediction_accuracy}
@@
 \end{equation} where $\bskap$ is the integrated Brier score when a Kaplan-Meier estimate for survival based on the training data is used as the survival prediction function $\widehat{S}(t)$.
-We refer to this $R^2$ statistic as the index of prediction accuracy and we scale its values by 100 to avoid unnecessary leading zero's.
+We refer to this $R^2$ statistic as the index of prediction accuracy \citep{kattan2018index} and we scale its values by 100 to avoid unnecessary leading zero's.
 For example, we present 25 if $R^2$ is 0.25 and present 10.2 if the difference between two $R^2$ is 0.102.
+
+Our secondary metric for evaluating predicted risk is the time-dependent concordance (C)-statistic.
+Briefly, we compute the time-dependent C-statistic proposed by \citet{blanche2013estimating}, which is interpreted as the probability that a risk prediction model will assign higher risk to a case (\ie, an observation with $T \leq t$ and $\delta = 1$) versus a non-case (\ie, an observation with $T > t$).
+Similar to the index of prediction accuracy, observations with $T \leq t$ and $\delta = 0$ only contribute to inverse proportion of censoring weights.
+
+\subsubsection{Data sets}
+
+We use a collection of publicly available data sets to benchmark the prediction accuracy and computational efficiency of the accelerated ORSF and each of the other learners described in \secref{sec:learners}
 
@@
 
-<<fig.height=10, fig.width=9, dpi=400>>=
+<<fig.height=10, fig.width=9>>=
 bm_pred_viz$ibs_scaled
@@
 
-<<fig.height=10, fig.width=9, dpi=400>>=
+<<fig.height=10, fig.width=9>>=
 bm_pred_model_viz$ibs_scaled
@@
 
-\subsection{Benchmark of variable selection}
+\subsection{Benchmark of variable importance}
+
+The aim of this numeric experiment is to compare negation VI to existing methods for VI.
+We consider methods that are intrinsic to the oblique RF (\eg ANOVA VI), those that are intrinsic to the RF (\eg permutation VI), and those that are model-agnostic (\eg SHAP VI).
+All methods are evaluated based on their ability to discriminate between variables that are related to a censored outcome versus those that are not related to it.
+
+\subsubsection{Variable importance techniques}
+
+We compute permutation VI using the \texttt{randomForestSRC} package.
+Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
+Therefore, it is not incorporated in the current study's numeric experiments.
+We compute ANOVA VI using the \texttt{aorsf} package, applying a p-value threshold of 0.01 as recommended by \citet{menze2011oblique}.
+We compute SHAP VI for boosted tree models using the \texttt{xgboost} package and also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
+
+\subsubsection{Variable types}
+
+We considered five classes of predictor variable, with each class characterized by its variables' relationship to a right-censored outcome. Specifically, \begin{itemize}
+\item \textit{junk} variables had no relationship with the outcome.
+\item \textit{main effect} variables were linearly related to the outcome
+\item \textit{non-linear effect} variables had a sinusoidal relationship to the outcome
+\item \textit{combination effect} Latent variables formed by linear combinations of three observed variables.
+The observed variables have no relationship to the outcome while the latent variable is linearly related to it.
+\item \textit{interaction effect} variables related to the outcome by multiplicative interaction with one other variable.
+\end{itemize}
+
+\subsubsection{Simulated data}
+
+We generated each set of simulated data with the following steps.
+First, a $n \times p$ multivariate normal matrix was generated at random, with each of $p$ columns representing one predictor variable and each of $n$ rows one observation.
+Each predictor variable had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
+Second, a time-to-event outcome with roughly 45\% of observations censored is generated using the \texttt{simsurv} package.
+The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) is used to generate the outcome.
+Third, interactions, non-linear mappings, and combinations are dropped from the predictor matrix that learning algorithms will use to estimate VI.
+
+\subsubsection{Parameter specifications}
+
+Parameters that varied in the current simulation study included the number of observations (1000, 3000, and 5000) and the minimum and maximum correlation between predictors (-0.1 to 0.1, -0.3 to 0.3, and -0.5 to 0.5).
+Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor, with an increase of one standard deviation associated with a 64\% increase in relative risk.
+
+\subsubsection{Evaluation of variable importance}
+
+We compared VI techniques based on their discrimination (C-statistic) between relevant and irrelevant variables.
+Normally a C-statistic assesses if a predicted score discriminates between positive and negative cases of a binary outcome.
+We use the C-statistic in the current simulation study by treating each variable like a binary outcome (e.g., the outcome is 1 if the variable is relevant, 0 otherwise).
+In other words, we assess VI as if it were a ‘prediction’ for the status of the variable.
+The resulting C-statistic measures the probability that a VI technique will rank a relevant variable higher than an irrelevant variable.
+
+\subsubsection{Results}
+
+\section{Discussion}
+
+\subsection{Implications of our results}
+
+\subsection{Limitations and next steps}
 
@@
 
-<<fig.height=10, fig.width=9, dpi=400>>=
+<<fig.height=10, fig.width=9>>=
 bm_pred_viz$cstat

### 2022-06-20 paper/jmlr/main.tex
adding VI to slides

@@
 
-\subsection{Benchmark of prediction accuracy}
+\subsection{Benchmark of prediction accuracy and computational efficiency}
 
-\subsubsection{Learners}
+The aim of this numeric experiment is to evaluate and compare the accelerated oblique RSF with its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and with other machine learning algorithms for risk prediction.
+Inferences drawn from this experiment include equivalence and inferiority tests based on Bayesian hierarchical models.
+
+\subsubsection{Learners} \label{sec:learners}
 
@@
 
-\subsection{Benchmark of variable selection}
+\subsection{Benchmark of variable importance}
+
+The aim of this numeric experiment is to compare negation VI to existing methods for VI.
+We consider methods that are intrinsic to the oblique RF (\eg ANOVA VI), those that are intrinsic to the RF (\eg permutation VI), and those that are model-agnostic (\eg SHAP VI).
+All methods are evaluated based on their ability to discriminate between variables that are related to a censored outcome versus those that are not related to it.
+
+\subsubsection{Variable importance techniques}
+
+We compute permutation VI using the \texttt{randomForestSRC} package.
+Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
+Therefore, it is not incorporated in the current study's numeric experiments.
+We compute ANOVA VI using the \texttt{aorsf} package, applying a p-value threshold of 0.01 as recommended by \citet{menze2011oblique}.
+We compute SHAP VI for boosted tree models using the \texttt{xgboost} package and also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
+
+\subsubsection{Variable types}
+
+We considered five classes of predictor variable, with each class characterized by its variables' relationship to a right-censored outcome. Specifically, \begin{itemize}
+\item \textit{junk} variables had no relationship with the outcome.
+\item \textit{main effect} variables were linearly related to the outcome
+\item \textit{non-linear effect} variables had a sinusoidal relationship to the outcome
+\item \textit{combination effect} variables had no direct relationship to the outcome.
+However, latent variables formed by combining the observed combination effects have a linear relationship to the outcome.
+\item \textit{interaction effect} variables related to the outcome by multiplicative interaction with one other variable.
+\end{itemize}
+
+the variables have (1) no effect, (2) linear effect, (3) non-linear effect, (4) conditional linear effect, (5) combination linear effect, or (6) categorical effect on the outcome.
+Each conditional linear variable has an effect on the outcome that is modified by the value of one linear effect variable.
+Combination linear effect variables contribute to latent variables that are linearly related to the outcome.
+Categorical effect variables have 3 unique values, each with a different expected risk for the event of interest.
+
+\subsubsection{Simulated data}
+
+\subsubsection{Evaluation of variable importance}
+
+\subsubsection{Results}
 
@@
 \hline
-\hspace{1em}aorsf-cph & 0.133 (0.124) & 0.757 (0.079) & 0.830 & 2.74 & 0.070 & 0.980\\
-\hspace{1em}aorsf-fast & 0.133 (0.124) & 0.757 (0.080) & 0.302 & 1.00 & 0.072 & 1.00\\
-\hspace{1em}aorsf-net & 0.130 (0.127) & 0.755 (0.080) & 61.237 & 202.6 & 0.069 & 0.964\\
-\hspace{1em}cif-rotate & 0.125 (0.145) & 0.741 (0.092) & 30.623 & 101.3 & 7.208 & 100.3\\
-\hspace{1em}cif-standard & 0.120 (0.111) & 0.748 (0.079) & 2.035 & 6.73 & 5.128 & 71.3\\
-\hspace{1em}glmnet-cox & 0.119 (0.139) & 0.748 (0.083) & 0.253 & 0.837 & 0.005 & 0.070\\
-\hspace{1em}rsf-standard & 0.118 (0.128) & 0.741 (0.084) & 1.694 & 5.60 & 0.152 & 2.11\\
-\hspace{1em}obliqueRSF-net & 0.117 (0.094) & 0.754 (0.080) & 328.883 & 1,087.9 & 26.636 & 370.5\\
-\hspace{1em}cif-extension & 0.108 (0.108) & 0.746 (0.083) & 13.510 & 44.7 & 6.840 & 95.2\\
-\hspace{1em}ranger-extratrees & 0.106 (0.097) & 0.748 (0.076) & 0.692 & 2.29 & 0.264 & 3.68\\
-\hspace{1em}aorsf-random & 0.101 (0.092) & 0.735 (0.074) & 1.879 & 6.22 & 0.066 & 0.919\\
-\hspace{1em}xgboost-cox & 0.077 (0.114) & 0.736 (0.095) & 3.833 & 12.7 & 0.005 & 0.070\\
-\hspace{1em}nn-cox & 0.030 (0.118) & 0.610 (0.128) & 15.427 & 51.0 & 1.513 & 21.0\\
-\hspace{1em}xgboost-aft & -3.68 (4.86) & 0.747 (0.082) & 13.182 & 43.6 & 0.008 & 0.117\\
+\hspace{1em}aorsf-fast & 0.132 (0.114) & 0.773 (0.071) & 0.776 & 1.00 & 0.282 & 1.00\\
+\hspace{1em}rsf-standard & 0.120 (0.117) & 0.759 (0.075) & 2.016 & 2.60 & 0.444 & 1.57\\
+\hspace{1em}cif-standard & 0.119 (0.101) & 0.766 (0.069) & 4.663 & 6.01 & 18.044 & 63.9\\
+\hspace{1em}cif-rotate & 0.119 (0.130) & 0.757 (0.080) & 40.258 & 51.9 & 27.552 & 97.6\\
+\hspace{1em}glmnet-cox & 0.114 (0.124) & 0.759 (0.076) & 0.737 & 0.949 & 0.008 & 0.028\\
+\hspace{1em}xgboost-cox & 0.072 (0.103) & 0.754 (0.089) & 4.296 & 5.54 & 0.009 & 0.032\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-random & 0.028 (0.022) & 0.748 (0.038) & 0.637 & 4.19 & 0.040 & 1.06\\
-\hspace{1em}ranger-extratrees & 0.028 (0.017) & 0.740 (0.036) & 0.061 & 0.404 & 0.184 & 4.81\\
-\hspace{1em}obliqueRSF-net & 0.027 (0.022) & 0.746 (0.038) & 27.286 & 179.6 & 15.729 & 411.6\\
-\hspace{1em}aorsf-cph & 0.025 (0.029) & 0.751 (0.042) & 0.450 & 2.97 & 0.034 & 0.891\\
-\hspace{1em}cif-standard & 0.024 (0.031) & 0.744 (0.040) & 1.608 & 10.6 & 4.825 & 126.3\\
-\hspace{1em}aorsf-fast & 0.024 (0.028) & 0.745 (0.044) & 0.152 & 1.00 & 0.038 & 1.00\\
-\hspace{1em}cif-extension & 0.023 (0.015) & 0.722 (0.038) & 9.788 & 64.4 & 4.595 & 120.2\\
-\hspace{1em}aorsf-net & 0.019 (0.034) & 0.745 (0.042) & 20.231 & 133.2 & 0.038 & 0.995\\
-\hspace{1em}glmnet-cox & 0.016 (0.030) & 0.746 (0.037) & 0.183 & 1.21 & 0.002 & 0.053\\
-\hspace{1em}rsf-standard & 0.005 (0.041) & 0.730 (0.042) & 0.235 & 1.55 & 0.071 & 1.85\\
-\hspace{1em}cif-rotate & 0.004 (0.040) & 0.731 (0.038) & 15.089 & 99.3 & 4.246 & 111.1\\
-\hspace{1em}xgboost-cox & 0.000 (0.044) & 0.751 (0.033) & 3.655 & 24.1 & 0.003 & 0.079\\
-\hspace{1em}nn-cox & 0.000 (0.013) & 0.574 (0.117) & 12.345 & 81.3 & 0.639 & 16.7\\
-\hspace{1em}xgboost-aft & -8.40 (1.81) & 0.737 (0.035) & 11.029 & 72.6 & 0.007 & 0.183\\
+\hspace{1em}cif-standard & 0.024 (0.031) & 0.744 (0.040) & 1.580 & 10.7 & 3.948 & 116.0\\
+\hspace{1em}aorsf-fast & 0.024 (0.028) & 0.745 (0.044) & 0.147 & 1.00 & 0.034 & 1.00\\
+\hspace{1em}glmnet-cox & 0.016 (0.030) & 0.746 (0.037) & 0.161 & 1.10 & 0.002 & 0.059\\
+\hspace{1em}rsf-standard & 0.005 (0.041) & 0.730 (0.042) & 0.142 & 0.963 & 0.063 & 1.84\\
+\hspace{1em}cif-rotate & 0.004 (0.040) & 0.731 (0.038) & 15.182 & 103.2 & 4.149 & 121.9\\
+\hspace{1em}xgboost-cox & 0.000 (0.044) & 0.751 (0.033) & 3.630 & 24.7 & 0.003 & 0.088\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.007 (0.012) & 0.819 (0.051) & 9.302 & 102.7 & 10.943 & 545.1\\
-\hspace{1em}aorsf-cph & 0.007 (0.019) & 0.815 (0.058) & 0.363 & 4.00 & 0.020 & 1.00\\
-\hspace{1em}aorsf-fast & 0.006 (0.019) & 0.820 (0.054) & 0.091 & 1.00 & 0.020 & 1.00\\
-\hspace{1em}aorsf-random & 0.004 (0.015) & 0.780 (0.070) & 0.326 & 3.60 & 0.026 & 1.30\\
-\hspace{1em}ranger-extratrees & 0.001 (0.020) & 0.773 (0.071) & 0.045 & 0.497 & 0.143 & 7.13\\
-\hspace{1em}cif-extension & 0.001 (0.021) & 0.759 (0.061) & 8.354 & 92.2 & 3.905 & 194.5\\
-\hspace{1em}xgboost-cox & -0.004 (0.004) & 0.500 (0.000) & 0.120 & 1.32 & 0.002 & 0.100\\
-\hspace{1em}nn-cox & -0.004 (0.004) & 0.535 (0.110) & 11.322 & 125.0 & 0.689 & 34.3\\
-\hspace{1em}cif-standard & -0.006 (0.026) & 0.773 (0.056) & 1.758 & 19.4 & 4.361 & 217.2\\
-\hspace{1em}aorsf-net & -0.006 (0.033) & 0.799 (0.065) & 15.227 & 168.1 & 0.025 & 1.25\\
-\hspace{1em}rsf-standard & -0.031 (0.053) & 0.769 (0.069) & 0.090 & 0.994 & 0.038 & 1.90\\
-\hspace{1em}cif-rotate & -0.037 (0.052) & 0.704 (0.094) & 13.476 & 148.8 & 3.663 & 182.5\\
-\hspace{1em}glmnet-cox & -0.062 (0.092) & 0.736 (0.098) & 0.301 & 3.33 & 0.001 & 0.051\\
-\hspace{1em}xgboost-aft & -24.3 (7.36) & 0.767 (0.066) & 10.846 & 119.7 & 0.008 & 0.399\\
+\hspace{1em}aorsf-fast & 0.010 (0.020) & 0.834 (0.057) & 0.088 & 1.00 & 0.020 & 1.00\\
+\hspace{1em}cif-standard & -0.001 (0.025) & 0.788 (0.061) & 1.589 & 18.1 & 3.861 & 192.9\\
+\hspace{1em}xgboost-cox & -0.003 (0.004) & 0.500 (0.000) & 0.112 & 1.28 & 0.002 & 0.100\\
+\hspace{1em}rsf-standard & -0.022 (0.053) & 0.787 (0.071) & 0.084 & 0.960 & 0.035 & 1.75\\
+\hspace{1em}cif-rotate & -0.031 (0.048) & 0.714 (0.084) & 13.331 & 152.2 & 3.293 & 164.5\\
+\hspace{1em}glmnet-cox & -0.053 (0.092) & 0.736 (0.110) & 0.262 & 2.99 & 0.002 & 0.100\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{ARIC; coronary heart disease, n = 13626, p = 31}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.160 (0.008) & 0.810 (0.007) & 4.995 & 1.00 & 16.402 & 1.00\\
+\hspace{1em}rsf-standard & 0.156 (0.008) & 0.803 (0.007) & 11.043 & 2.21 & 1.245 & 0.076\\
+\hspace{1em}cif-standard & 0.134 (0.006) & 0.806 (0.007) & 68.008 & 13.6 & 441.507 & 26.9\\
+\hspace{1em}glmnet-cox & 0.124 (0.016) & 0.793 (0.009) & 1.354 & 0.271 & 0.822 & 0.050\\
+\hspace{1em}cif-rotate & 0.105 (0.003) & 0.783 (0.008) & 412.625 & 82.6 & 251.226 & 15.3\\
+\hspace{1em}xgboost-cox & 0.058 (0.016) & 0.811 (0.007) & 10.324 & 2.07 & 1.073 & 0.065\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{ARIC; death, n = 13626, p = 31}}}\\
+\hline
+\hspace{1em}rsf-standard & 0.214 (0.007) & 0.785 (0.004) & 16.361 & 1.72 & 1.636 & 0.018\\
+\hspace{1em}aorsf-fast & 0.211 (0.008) & 0.786 (0.005) & 9.521 & 1.00 & 92.722 & 1.00\\
+\hspace{1em}cif-standard & 0.201 (0.005) & 0.784 (0.005) & 66.585 & 6.99 & 585.928 & 6.32\\
+\hspace{1em}glmnet-cox & 0.181 (0.019) & 0.770 (0.008) & 2.555 & 0.268 & 1.142 & 0.012\\
+\hspace{1em}cif-rotate & 0.150 (0.008) & 0.753 (0.007) & 427.333 & 44.9 & 524.889 & 5.66\\
+\hspace{1em}xgboost-cox & 0.123 (0.006) & 0.789 (0.004) & 10.891 & 1.14 & 1.028 & 0.011\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{ARIC; heart failure, n = 13626, p = 31}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.236 (0.008) & 0.839 (0.006) & 5.758 & 1.00 & 21.727 & 1.00\\
+\hspace{1em}rsf-standard & 0.232 (0.009) & 0.833 (0.006) & 11.647 & 2.02 & 1.259 & 0.058\\
+\hspace{1em}cif-standard & 0.202 (0.006) & 0.834 (0.006) & 71.819 & 12.5 & 476.484 & 21.9\\
+\hspace{1em}cif-rotate & 0.171 (0.005) & 0.805 (0.008) & 431.960 & 75.0 & 319.739 & 14.7\\
+\hspace{1em}glmnet-cox & 0.163 (0.041) & 0.814 (0.016) & 2.435 & 0.423 & 1.106 & 0.051\\
+\hspace{1em}xgboost-cox & 0.117 (0.019) & 0.840 (0.005) & 11.828 & 2.05 & 1.131 & 0.052\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{ARIC; stroke, n = 13626, p = 31}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.091 (0.006) & 0.791 (0.010) & 5.070 & 1.00 & 12.402 & 1.00\\
+\hspace{1em}rsf-standard & 0.090 (0.007) & 0.782 (0.011) & 10.586 & 2.09 & 1.225 & 0.099\\
+\hspace{1em}glmnet-cox & 0.076 (0.006) & 0.783 (0.010) & 1.135 & 0.224 & 0.905 & 0.073\\
+\hspace{1em}cif-standard & 0.073 (0.005) & 0.784 (0.011) & 69.781 & 13.8 & 389.705 & 31.4\\
+\hspace{1em}cif-rotate & 0.052 (0.003) & 0.766 (0.010) & 407.352 & 80.4 & 170.815 & 13.8\\
+\hspace{1em}xgboost-cox & 0.048 (0.023) & 0.789 (0.010) & 7.716 & 1.52 & 0.915 & 0.074\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.718 (0.011) & 0.289 & 1.00 & 0.075 & 1.00\\
-\hspace{1em}aorsf-cph & 0.100 (0.014) & 0.717 (0.011) & 0.691 & 2.39 & 0.070 & 0.945\\
-\hspace{1em}cif-standard & 0.097 (0.013) & 0.710 (0.012) & 1.529 & 5.29 & 5.019 & 67.4\\
-\hspace{1em}aorsf-net & 0.097 (0.014) & 0.717 (0.012) & 55.870 & 193.4 & 0.064 & 0.853\\
-\hspace{1em}aorsf-random & 0.096 (0.010) & 0.716 (0.011) & 1.612 & 5.58 & 0.066 & 0.879\\
-\hspace{1em}obliqueRSF-net & 0.089 (0.006) & 0.717 (0.012) & 269.561 & 932.9 & 44.243 & 593.8\\
-\hspace{1em}cif-rotate & 0.087 (0.017) & 0.705 (0.014) & 15.603 & 54.0 & 6.291 & 84.4\\
-\hspace{1em}rsf-standard & 0.087 (0.019) & 0.704 (0.011) & 1.646 & 5.70 & 0.143 & 1.92\\
-\hspace{1em}ranger-extratrees & 0.083 (0.007) & 0.710 (0.011) & 0.735 & 2.54 & 0.263 & 3.53\\
-\hspace{1em}cif-extension & 0.081 (0.006) & 0.709 (0.011) & 8.523 & 29.5 & 5.850 & 78.5\\
-\hspace{1em}glmnet-cox & 0.076 (0.016) & 0.711 (0.019) & 0.132 & 0.457 & 0.004 & 0.054\\
-\hspace{1em}xgboost-cox & 0.063 (0.013) & 0.701 (0.013) & 3.266 & 11.3 & 0.004 & 0.054\\
-\hspace{1em}nn-cox & -0.013 (0.040) & 0.506 (0.042) & 14.970 & 51.8 & 1.780 & 23.9\\
-\hspace{1em}xgboost-aft & -1.11 (0.200) & 0.706 (0.013) & 12.660 & 43.8 & 0.007 & 0.094\\
+\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.718 (0.011) & 0.259 & 1.00 & 0.075 & 1.00\\
+\hspace{1em}cif-standard & 0.097 (0.013) & 0.710 (0.012) & 1.193 & 4.60 & 3.848 & 51.3\\
+\hspace{1em}cif-rotate & 0.087 (0.017) & 0.705 (0.014) & 13.358 & 51.5 & 5.116 & 68.1\\
+\hspace{1em}rsf-standard & 0.087 (0.019) & 0.704 (0.011) & 1.226 & 4.73 & 0.150 & 2.00\\
+\hspace{1em}glmnet-cox & 0.076 (0.016) & 0.711 (0.019) & 0.116 & 0.448 & 0.004 & 0.053\\
+\hspace{1em}xgboost-cox & 0.063 (0.013) & 0.701 (0.013) & 3.165 & 12.2 & 0.004 & 0.053\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.100 (0.017) & 0.713 (0.016) & 0.282 & 1.00 & 0.069 & 1.00\\
-\hspace{1em}aorsf-cph & 0.099 (0.017) & 0.712 (0.016) & 0.708 & 2.52 & 0.070 & 1.01\\
-\hspace{1em}aorsf-net & 0.096 (0.018) & 0.713 (0.017) & 51.056 & 181.3 & 0.065 & 0.937\\
-\hspace{1em}cif-standard & 0.091 (0.015) & 0.701 (0.017) & 1.183 & 4.20 & 4.109 & 59.2\\
-\hspace{1em}obliqueRSF-net & 0.088 (0.008) & 0.711 (0.015) & 298.417 & 1,059.9 & 44.698 & 643.9\\
-\hspace{1em}aorsf-random & 0.087 (0.012) & 0.703 (0.015) & 1.629 & 5.78 & 0.064 & 0.923\\
-\hspace{1em}cif-rotate & 0.084 (0.020) & 0.695 (0.017) & 14.130 & 50.2 & 6.064 & 87.4\\
-\hspace{1em}cif-extension & 0.082 (0.009) & 0.707 (0.017) & 8.587 & 30.5 & 6.571 & 94.7\\
-\hspace{1em}rsf-standard & 0.081 (0.020) & 0.694 (0.015) & 1.408 & 5.00 & 0.139 & 2.00\\
-\hspace{1em}ranger-extratrees & 0.079 (0.011) & 0.700 (0.016) & 0.555 & 1.97 & 0.235 & 3.39\\
-\hspace{1em}glmnet-cox & 0.073 (0.018) & 0.706 (0.024) & 0.161 & 0.572 & 0.005 & 0.072\\
-\hspace{1em}xgboost-cox & 0.060 (0.011) & 0.695 (0.018) & 3.088 & 11.0 & 0.004 & 0.058\\
-\hspace{1em}nn-cox & -0.005 (0.005) & 0.506 (0.039) & 13.814 & 49.1 & 1.499 & 21.6\\
-\hspace{1em}xgboost-aft & -1.20 (0.239) & 0.701 (0.019) & 11.979 & 42.5 & 0.007 & 0.101\\
+\hspace{1em}aorsf-fast & 0.100 (0.017) & 0.713 (0.016) & 0.259 & 1.00 & 0.076 & 1.00\\
+\hspace{1em}cif-standard & 0.091 (0.015) & 0.701 (0.017) & 1.182 & 4.56 & 3.929 & 51.7\\
+\hspace{1em}cif-rotate & 0.084 (0.020) & 0.695 (0.017) & 13.338 & 51.5 & 5.118 & 67.3\\
+\hspace{1em}rsf-standard & 0.081 (0.020) & 0.694 (0.015) & 1.223 & 4.72 & 0.151 & 1.99\\
+\hspace{1em}glmnet-cox & 0.073 (0.018) & 0.706 (0.024) & 0.115 & 0.444 & 0.004 & 0.053\\
+\hspace{1em}xgboost-cox & 0.060 (0.011) & 0.695 (0.018) & 2.895 & 11.2 & 0.004 & 0.053\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.073 (0.024) & 0.749 (0.027) & 1951.148 & 2,519.7 & 15.143 & 83.8\\
-\hspace{1em}cif-rotate & 0.072 (0.017) & 0.748 (0.027) & 6765.191 & 8,736.4 & 351.642 & 1,947.0\\
-\hspace{1em}cif-standard & 0.068 (0.018) & 0.745 (0.029) & 8.817 & 11.4 & 4.397 & 24.3\\
-\hspace{1em}cif-extension & 0.066 (0.014) & 0.746 (0.025) & 45.390 & 58.6 & 6.577 & 36.4\\
-\hspace{1em}aorsf-cph & 0.065 (0.031) & 0.745 (0.024) & 1.280 & 1.65 & 0.179 & 0.992\\
-\hspace{1em}aorsf-fast & 0.063 (0.031) & 0.744 (0.024) & 0.774 & 1.00 & 0.181 & 1.00\\
-\hspace{1em}ranger-extratrees & 0.061 (0.024) & 0.740 (0.028) & 0.224 & 0.290 & 0.180 & 0.997\\
-\hspace{1em}glmnet-cox & 0.043 (0.034) & 0.723 (0.037) & 5.608 & 7.24 & 0.005 & 0.028\\
-\hspace{1em}xgboost-cox & 0.040 (0.014) & 0.743 (0.026) & 2.236 & 2.89 & 0.007 & 0.039\\
-\hspace{1em}aorsf-random & 0.030 (0.015) & 0.699 (0.036) & 1.847 & 2.38 & 0.190 & 1.05\\
-\hspace{1em}rsf-standard & 0.020 (0.041) & 0.693 (0.033) & 0.382 & 0.493 & 0.666 & 3.69\\
-\hspace{1em}aorsf-net & 0.003 (0.067) & 0.740 (0.022) & 464.082 & 599.3 & 0.179 & 0.992\\
-\hspace{1em}nn-cox & -0.008 (0.065) & 0.689 (0.045) & 18.607 & 24.0 & 1.926 & 10.7\\
-\hspace{1em}xgboost-aft & -3.09 (0.664) & 0.742 (0.022) & 11.258 & 14.5 & 0.010 & 0.056\\
+\hspace{1em}cif-rotate & 0.070 (0.018) & 0.747 (0.027) & 6304.881 & 8,318.3 & 374.594 & 2,134.8\\
+\hspace{1em}cif-standard & 0.067 (0.019) & 0.747 (0.030) & 8.059 & 10.6 & 4.493 & 25.6\\
+\hspace{1em}aorsf-fast & 0.065 (0.028) & 0.746 (0.026) & 0.758 & 1.00 & 0.175 & 1.00\\
+\hspace{1em}glmnet-cox & 0.041 (0.032) & 0.724 (0.036) & 5.686 & 7.50 & 0.005 & 0.029\\
+\hspace{1em}xgboost-cox & 0.027 (0.034) & 0.741 (0.030) & 2.154 & 2.84 & 0.006 & 0.034\\
+\hspace{1em}rsf-standard & 0.024 (0.037) & 0.695 (0.033) & 0.323 & 0.427 & 0.666 & 3.80\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.117 (0.028) & 0.787 (0.037) & 0.110 & 1.24 & 0.003 & 0.158\\
-\hspace{1em}aorsf-cph & 0.101 (0.039) & 0.769 (0.034) & 0.171 & 1.93 & 0.020 & 1.05\\
-\hspace{1em}aorsf-fast & 0.100 (0.038) & 0.768 (0.033) & 0.088 & 1.00 & 0.019 & 1.00\\
-\hspace{1em}aorsf-net & 0.097 (0.040) & 0.760 (0.034) & 13.429 & 151.8 & 0.020 & 1.06\\
-\hspace{1em}obliqueRSF-net & 0.089 (0.027) & 0.758 (0.036) & 108.537 & 1,226.6 & 5.743 & 302.0\\
-\hspace{1em}cif-rotate & 0.087 (0.048) & 0.755 (0.027) & 6.229 & 70.4 & 2.161 & 113.6\\
-\hspace{1em}cif-extension & 0.087 (0.036) & 0.730 (0.034) & 6.111 & 69.1 & 2.473 & 130.0\\
-\hspace{1em}aorsf-random & 0.087 (0.029) & 0.757 (0.032) & 0.304 & 3.44 & 0.020 & 1.05\\
-\hspace{1em}cif-standard & 0.084 (0.038) & 0.743 (0.036) & 0.793 & 8.97 & 1.275 & 67.1\\
-\hspace{1em}ranger-extratrees & 0.073 (0.016) & 0.741 (0.037) & 0.036 & 0.409 & 0.087 & 4.56\\
-\hspace{1em}rsf-standard & 0.072 (0.048) & 0.732 (0.034) & 0.526 & 5.94 & 0.039 & 2.07\\
-\hspace{1em}xgboost-cox & 0.029 (0.050) & 0.679 (0.121) & 0.342 & 3.87 & 0.002 & 0.105\\
-\hspace{1em}nn-cox & -0.006 (0.015) & 0.536 (0.097) & 12.668 & 143.2 & 0.444 & 23.3\\
-\hspace{1em}xgboost-aft & -2.52 (0.477) & 0.754 (0.038) & 7.286 & 82.3 & 0.006 & 0.316\\
+\hspace{1em}glmnet-cox & 0.117 (0.028) & 0.787 (0.037) & 0.082 & 0.988 & 0.002 & 0.111\\
+\hspace{1em}aorsf-fast & 0.100 (0.038) & 0.768 (0.033) & 0.083 & 1.00 & 0.018 & 1.00\\
+\hspace{1em}cif-rotate & 0.087 (0.048) & 0.755 (0.027) & 6.369 & 76.7 & 1.766 & 98.0\\
+\hspace{1em}cif-standard & 0.084 (0.038) & 0.743 (0.036) & 0.751 & 9.04 & 1.020 & 56.6\\
+\hspace{1em}rsf-standard & 0.072 (0.048) & 0.732 (0.034) & 0.589 & 7.08 & 0.040 & 2.22\\
+\hspace{1em}xgboost-cox & 0.029 (0.050) & 0.679 (0.121) & 0.320 & 3.86 & 0.002 & 0.111\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.029 (0.017) & 0.620 (0.024) & 0.101 & 0.798 & 0.002 & 0.075\\
-\hspace{1em}ranger-extratrees & 0.017 (0.016) & 0.596 (0.025) & 0.034 & 0.270 & 0.091 & 3.36\\
-\hspace{1em}obliqueRSF-net & 0.013 (0.016) & 0.592 (0.024) & 245.138 & 1,943.8 & 11.109 & 411.1\\
-\hspace{1em}aorsf-random & 0.012 (0.018) & 0.595 (0.024) & 0.473 & 3.75 & 0.024 & 0.892\\
-\hspace{1em}xgboost-cox & 0.010 (0.016) & 0.598 (0.032) & 1.315 & 10.4 & 0.003 & 0.111\\
-\hspace{1em}cif-standard & 0.007 (0.021) & 0.594 (0.023) & 0.950 & 7.54 & 1.722 & 63.7\\
-\hspace{1em}aorsf-fast & 0.007 (0.019) & 0.594 (0.025) & 0.126 & 1.00 & 0.027 & 1.00\\
-\hspace{1em}aorsf-cph & 0.007 (0.020) & 0.594 (0.026) & 0.272 & 2.16 & 0.028 & 1.04\\
-\hspace{1em}aorsf-net & 0.006 (0.020) & 0.592 (0.026) & 20.063 & 159.1 & 0.027 & 1.00\\
-\hspace{1em}nn-cox & 0.000 (0.019) & 0.546 (0.054) & 13.040 & 103.4 & 0.585 & 21.6\\
-\hspace{1em}cif-extension & -0.005 (0.023) & 0.580 (0.028) & 6.550 & 51.9 & 3.603 & 133.3\\
-\hspace{1em}cif-rotate & -0.012 (0.025) & 0.583 (0.030) & 7.129 & 56.5 & 3.081 & 114.0\\
-\hspace{1em}rsf-standard & -0.027 (0.032) & 0.577 (0.024) & 1.048 & 8.31 & 0.087 & 3.22\\
-\hspace{1em}xgboost-aft & -0.829 (0.337) & 0.582 (0.034) & 7.164 & 56.8 & 0.006 & 0.222\\
+\hspace{1em}glmnet-cox & 0.029 (0.017) & 0.620 (0.024) & 0.086 & 0.717 & 0.003 & 0.120\\
+\hspace{1em}xgboost-cox & 0.010 (0.016) & 0.598 (0.032) & 1.272 & 10.6 & 0.003 & 0.120\\
+\hspace{1em}cif-standard & 0.007 (0.021) & 0.594 (0.023) & 0.753 & 6.27 & 1.153 & 46.1\\
+\hspace{1em}aorsf-fast & 0.007 (0.019) & 0.594 (0.025) & 0.120 & 1.00 & 0.025 & 1.00\\
+\hspace{1em}cif-rotate & -0.012 (0.025) & 0.583 (0.030) & 7.360 & 61.3 & 2.955 & 118.1\\
+\hspace{1em}rsf-standard & -0.027 (0.032) & 0.577 (0.024) & 0.742 & 6.18 & 0.092 & 3.68\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.124 (0.016) & 0.745 (0.017) & 334.738 & 1,786.5 & 12.512 & 271.8\\
-\hspace{1em}cif-standard & 0.123 (0.020) & 0.742 (0.019) & 0.994 & 5.31 & 2.355 & 51.2\\
-\hspace{1em}rsf-standard & 0.120 (0.023) & 0.737 (0.019) & 1.669 & 8.91 & 0.113 & 2.46\\
-\hspace{1em}aorsf-net & 0.120 (0.024) & 0.737 (0.020) & 39.301 & 209.8 & 0.046 & 1.00\\
-\hspace{1em}aorsf-cph & 0.119 (0.025) & 0.735 (0.019) & 0.431 & 2.30 & 0.047 & 1.01\\
-\hspace{1em}aorsf-fast & 0.116 (0.024) & 0.732 (0.017) & 0.187 & 1.00 & 0.046 & 1.00\\
-\hspace{1em}cif-extension & 0.114 (0.017) & 0.742 (0.019) & 8.843 & 47.2 & 4.667 & 101.4\\
-\hspace{1em}cif-rotate & 0.107 (0.022) & 0.729 (0.017) & 12.995 & 69.4 & 5.199 & 112.9\\
-\hspace{1em}aorsf-random & 0.104 (0.024) & 0.723 (0.025) & 1.334 & 7.12 & 0.044 & 0.964\\
-\hspace{1em}ranger-extratrees & 0.094 (0.018) & 0.736 (0.025) & 0.099 & 0.526 & 0.132 & 2.87\\
-\hspace{1em}glmnet-cox & 0.091 (0.019) & 0.727 (0.021) & 0.141 & 0.752 & 0.003 & 0.065\\
-\hspace{1em}xgboost-cox & 0.083 (0.017) & 0.729 (0.020) & 2.577 & 13.8 & 0.003 & 0.065\\
-\hspace{1em}nn-cox & -0.004 (0.004) & 0.524 (0.065) & 12.618 & 67.3 & 1.165 & 25.3\\
-\hspace{1em}xgboost-aft & -1.10 (0.162) & 0.729 (0.021) & 11.930 & 63.7 & 0.007 & 0.152\\
+\hspace{1em}cif-standard & 0.123 (0.020) & 0.742 (0.019) & 0.919 & 5.21 & 2.297 & 52.1\\
+\hspace{1em}rsf-standard & 0.120 (0.023) & 0.737 (0.019) & 1.198 & 6.79 & 0.115 & 2.61\\
+\hspace{1em}aorsf-fast & 0.116 (0.024) & 0.732 (0.017) & 0.176 & 1.00 & 0.044 & 1.00\\
+\hspace{1em}cif-rotate & 0.107 (0.022) & 0.729 (0.017) & 11.084 & 62.8 & 3.797 & 86.2\\
+\hspace{1em}glmnet-cox & 0.091 (0.019) & 0.727 (0.021) & 0.094 & 0.533 & 0.003 & 0.068\\
+\hspace{1em}xgboost-cox & 0.083 (0.017) & 0.729 (0.020) & 2.257 & 12.8 & 0.003 & 0.068\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.746 (0.027) & 0.174 & 1.00 & 0.037 & 1.00\\
-\hspace{1em}aorsf-net & 0.074 (0.019) & 0.743 (0.027) & 28.658 & 164.8 & 0.040 & 1.09\\
-\hspace{1em}aorsf-cph & 0.072 (0.018) & 0.743 (0.026) & 0.405 & 2.33 & 0.040 & 1.08\\
-\hspace{1em}glmnet-cox & 0.063 (0.041) & 0.715 (0.091) & 0.921 & 5.30 & 0.003 & 0.081\\
-\hspace{1em}obliqueRSF-net & 0.063 (0.013) & 0.741 (0.023) & 251.024 & 1,443.1 & 11.754 & 317.4\\
-\hspace{1em}cif-rotate & 0.059 (0.016) & 0.721 (0.025) & 37.291 & 214.4 & 4.884 & 131.9\\
-\hspace{1em}cif-standard & 0.058 (0.014) & 0.737 (0.022) & 2.228 & 12.8 & 3.646 & 98.5\\
-\hspace{1em}ranger-extratrees & 0.054 (0.013) & 0.737 (0.029) & 0.715 & 4.11 & 0.206 & 5.57\\
-\hspace{1em}cif-extension & 0.052 (0.011) & 0.730 (0.022) & 13.957 & 80.2 & 5.770 & 155.8\\
-\hspace{1em}rsf-standard & 0.046 (0.023) & 0.705 (0.025) & 1.219 & 7.01 & 0.075 & 2.03\\
-\hspace{1em}xgboost-cox & 0.039 (0.051) & 0.747 (0.020) & 4.233 & 24.3 & 0.003 & 0.081\\
-\hspace{1em}aorsf-random & 0.033 (0.012) & 0.695 (0.030) & 1.324 & 7.61 & 0.041 & 1.11\\
-\hspace{1em}nn-cox & 0.024 (0.036) & 0.686 (0.082) & 12.885 & 74.1 & 0.602 & 16.3\\
-\hspace{1em}xgboost-aft & -5.15 (0.987) & 0.734 (0.020) & 13.101 & 75.3 & 0.007 & 0.189\\
+\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.746 (0.027) & 0.166 & 1.00 & 0.036 & 1.00\\
+\hspace{1em}glmnet-cox & 0.063 (0.041) & 0.715 (0.091) & 0.995 & 5.99 & 0.002 & 0.056\\
+\hspace{1em}cif-rotate & 0.059 (0.016) & 0.721 (0.025) & 35.119 & 211.4 & 4.542 & 126.1\\
+\hspace{1em}cif-standard & 0.058 (0.014) & 0.737 (0.022) & 1.771 & 10.7 & 3.109 & 86.3\\
+\hspace{1em}rsf-standard & 0.046 (0.023) & 0.705 (0.025) & 0.638 & 3.84 & 0.063 & 1.75\\
+\hspace{1em}xgboost-cox & 0.039 (0.051) & 0.747 (0.020) & 4.202 & 25.3 & 0.003 & 0.083\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.082 (0.017) & 0.722 (0.023) & 59.048 & 213.7 & 0.069 & 1.13\\
-\hspace{1em}aorsf-cph & 0.082 (0.018) & 0.722 (0.023) & 0.711 & 2.57 & 0.063 & 1.02\\
-\hspace{1em}aorsf-fast & 0.082 (0.019) & 0.722 (0.025) & 0.276 & 1.00 & 0.062 & 1.00\\
-\hspace{1em}ranger-extratrees & 0.074 (0.010) & 0.723 (0.022) & 0.703 & 2.54 & 0.215 & 3.49\\
-\hspace{1em}obliqueRSF-net & 0.074 (0.010) & 0.721 (0.023) & 468.654 & 1,695.9 & 14.749 & 239.1\\
-\hspace{1em}cif-standard & 0.071 (0.010) & 0.716 (0.023) & 1.958 & 7.09 & 3.737 & 60.6\\
-\hspace{1em}cif-rotate & 0.068 (0.018) & 0.708 (0.029) & 45.430 & 164.4 & 6.497 & 105.3\\
-\hspace{1em}cif-extension & 0.064 (0.009) & 0.714 (0.022) & 17.887 & 64.7 & 8.557 & 138.7\\
-\hspace{1em}rsf-standard & 0.059 (0.022) & 0.694 (0.026) & 1.390 & 5.03 & 0.112 & 1.81\\
-\hspace{1em}glmnet-cox & 0.058 (0.019) & 0.699 (0.024) & 0.980 & 3.54 & 0.003 & 0.049\\
-\hspace{1em}aorsf-random & 0.050 (0.010) & 0.682 (0.023) & 1.716 & 6.21 & 0.062 & 1.01\\
-\hspace{1em}xgboost-cox & 0.039 (0.017) & 0.698 (0.027) & 3.225 & 11.7 & 0.003 & 0.049\\
-\hspace{1em}nn-cox & 0.038 (0.028) & 0.683 (0.068) & 13.970 & 50.6 & 0.640 & 10.4\\
-\hspace{1em}xgboost-aft & -2.16 (0.322) & 0.696 (0.026) & 12.919 & 46.8 & 0.006 & 0.097\\
+\hspace{1em}aorsf-fast & 0.082 (0.019) & 0.722 (0.025) & 0.262 & 1.00 & 0.551 & 1.00\\
+\hspace{1em}cif-standard & 0.071 (0.010) & 0.716 (0.023) & 1.796 & 6.85 & 3.342 & 6.07\\
+\hspace{1em}cif-rotate & 0.068 (0.018) & 0.708 (0.029) & 41.195 & 157.1 & 5.392 & 9.79\\
+\hspace{1em}rsf-standard & 0.059 (0.022) & 0.694 (0.026) & 1.230 & 4.69 & 0.123 & 0.224\\
+\hspace{1em}glmnet-cox & 0.058 (0.019) & 0.699 (0.024) & 0.914 & 3.49 & 0.003 & 0.005\\
+\hspace{1em}xgboost-cox & 0.039 (0.017) & 0.698 (0.027) & 2.792 & 10.6 & 0.003 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.056 (0.010) & 0.731 (0.017) & 161.908 & 167.2 & 34.174 & 110.4\\
-\hspace{1em}aorsf-net & 0.053 (0.006) & 0.733 (0.013) & 132.397 & 136.8 & 0.313 & 1.01\\
-\hspace{1em}aorsf-fast & 0.052 (0.006) & 0.735 (0.014) & 0.968 & 1.00 & 0.309 & 1.00\\
-\hspace{1em}aorsf-cph & 0.051 (0.006) & 0.733 (0.013) & 3.094 & 3.20 & 0.312 & 1.01\\
-\hspace{1em}cif-standard & 0.050 (0.006) & 0.733 (0.013) & 11.540 & 11.9 & 43.325 & 140.0\\
-\hspace{1em}obliqueRSF-net & 0.049 (0.006) & 0.730 (0.014) & 363.594 & 375.6 & 168.051 & 543.1\\
-\hspace{1em}rsf-standard & 0.048 (0.009) & 0.727 (0.013) & 3.516 & 3.63 & 1.110 & 3.59\\
-\hspace{1em}ranger-extratrees & 0.046 (0.006) & 0.730 (0.013) & 5.812 & 6.00 & 3.555 & 11.5\\
-\hspace{1em}glmnet-cox & 0.036 (0.006) & 0.711 (0.016) & 1.023 & 1.06 & 0.012 & 0.039\\
-\hspace{1em}cif-extension & 0.036 (0.004) & 0.726 (0.016) & 51.192 & 52.9 & 25.128 & 81.2\\
-\hspace{1em}xgboost-cox & 0.031 (0.007) & 0.716 (0.018) & 3.516 & 3.63 & 0.011 & 0.036\\
-\hspace{1em}aorsf-random & 0.029 (0.003) & 0.693 (0.014) & 3.220 & 3.33 & 0.292 & 0.944\\
-\hspace{1em}nn-cox & 0.023 (0.012) & 0.677 (0.036) & 17.152 & 17.7 & 11.675 & 37.7\\
-\hspace{1em}xgboost-aft & -4.30 (0.486) & 0.724 (0.013) & 13.829 & 14.3 & 0.009 & 0.029\\
+\hspace{1em}cif-rotate & 0.056 (0.010) & 0.731 (0.017) & 152.873 & 160.7 & 31.205 & 107.1\\
+\hspace{1em}aorsf-fast & 0.052 (0.006) & 0.735 (0.014) & 0.951 & 1.00 & 0.291 & 1.00\\
+\hspace{1em}cif-standard & 0.050 (0.006) & 0.733 (0.013) & 10.380 & 10.9 & 38.621 & 132.6\\
+\hspace{1em}rsf-standard & 0.048 (0.009) & 0.727 (0.013) & 2.246 & 2.36 & 0.893 & 3.07\\
+\hspace{1em}glmnet-cox & 0.036 (0.006) & 0.711 (0.016) & 0.920 & 0.967 & 0.018 & 0.062\\
+\hspace{1em}xgboost-cox & 0.031 (0.007) & 0.716 (0.018) & 3.383 & 3.56 & 0.011 & 0.038\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{MESA; coronary heart disease, n = 6785, p = 28}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.055 (0.009) & 0.771 (0.014) & 1.720 & 1.00 & 0.520 & 1.00\\
+\hspace{1em}rsf-standard & 0.051 (0.011) & 0.756 (0.016) & 3.294 & 1.92 & 0.430 & 0.828\\
+\hspace{1em}cif-standard & 0.049 (0.006) & 0.763 (0.014) & 20.168 & 11.7 & 102.381 & 197.0\\
+\hspace{1em}cif-rotate & 0.047 (0.006) & 0.767 (0.017) & 162.455 & 94.4 & 39.029 & 75.1\\
+\hspace{1em}glmnet-cox & 0.031 (0.017) & 0.751 (0.025) & 0.751 & 0.436 & 0.014 & 0.027\\
+\hspace{1em}xgboost-cox & 0.025 (0.027) & 0.766 (0.016) & 5.609 & 3.26 & 0.018 & 0.035\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{MESA; death, n = 6793, p = 28}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.144 (0.009) & 0.786 (0.010) & 1.797 & 1.00 & 1.069 & 1.00\\
+\hspace{1em}rsf-standard & 0.141 (0.009) & 0.780 (0.010) & 3.613 & 2.01 & 0.487 & 0.456\\
+\hspace{1em}cif-standard & 0.136 (0.007) & 0.785 (0.010) & 20.306 & 11.3 & 114.250 & 106.9\\
+\hspace{1em}cif-rotate & 0.126 (0.007) & 0.782 (0.010) & 171.028 & 95.2 & 74.574 & 69.8\\
+\hspace{1em}glmnet-cox & 0.123 (0.025) & 0.783 (0.013) & 0.702 & 0.391 & 0.046 & 0.043\\
+\hspace{1em}xgboost-cox & 0.054 (0.027) & 0.790 (0.010) & 10.187 & 5.67 & 0.052 & 0.049\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{MESA; heart failure, n = 6785, p = 28}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.108 (0.010) & 0.866 (0.014) & 1.619 & 1.00 & 0.427 & 1.00\\
+\hspace{1em}rsf-standard & 0.108 (0.013) & 0.857 (0.015) & 3.844 & 2.37 & 0.479 & 1.12\\
+\hspace{1em}cif-standard & 0.099 (0.008) & 0.860 (0.016) & 20.168 & 12.5 & 100.439 & 235.4\\
+\hspace{1em}cif-rotate & 0.098 (0.009) & 0.863 (0.014) & 148.543 & 91.7 & 36.415 & 85.4\\
+\hspace{1em}glmnet-cox & 0.036 (0.037) & 0.764 (0.137) & 0.893 & 0.551 & 0.019 & 0.045\\
+\hspace{1em}xgboost-cox & -0.002 (0.025) & 0.866 (0.012) & 8.241 & 5.09 & 0.016 & 0.038\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{7}{l}{\textit{\textbf{MESA; stroke, n = 6783, p = 28}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.766 (0.015) & 1.689 & 1.00 & 0.393 & 1.00\\
+\hspace{1em}cif-rotate & 0.025 (0.005) & 0.764 (0.016) & 151.593 & 89.7 & 32.758 & 83.4\\
+\hspace{1em}cif-standard & 0.025 (0.004) & 0.762 (0.015) & 19.936 & 11.8 & 98.802 & 251.4\\
+\hspace{1em}rsf-standard & 0.022 (0.008) & 0.750 (0.013) & 2.453 & 1.45 & 0.737 & 1.87\\
+\hspace{1em}glmnet-cox & 0.022 (0.008) & 0.763 (0.016) & 0.775 & 0.459 & 0.012 & 0.031\\
+\hspace{1em}xgboost-cox & 0.008 (0.026) & 0.764 (0.015) & 4.517 & 2.67 & 0.015 & 0.038\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.160 (0.019) & 0.744 (0.014) & 16.541 & 35.9 & 7.904 & 71.1\\
-\hspace{1em}aorsf-cph & 0.159 (0.016) & 0.742 (0.011) & 1.239 & 2.69 & 0.111 & 0.995\\
-\hspace{1em}aorsf-fast & 0.158 (0.016) & 0.742 (0.011) & 0.461 & 1.00 & 0.111 & 1.00\\
-\hspace{1em}aorsf-net & 0.156 (0.016) & 0.741 (0.011) & 99.187 & 215.0 & 0.109 & 0.977\\
-\hspace{1em}obliqueRSF-net & 0.156 (0.013) & 0.743 (0.011) & 239.204 & 518.6 & 17.341 & 155.9\\
-\hspace{1em}cif-standard & 0.151 (0.015) & 0.738 (0.012) & 2.162 & 4.69 & 8.068 & 72.6\\
-\hspace{1em}rsf-standard & 0.151 (0.017) & 0.737 (0.011) & 2.044 & 4.43 & 0.191 & 1.72\\
-\hspace{1em}aorsf-random & 0.146 (0.014) & 0.735 (0.012) & 2.586 & 5.61 & 0.104 & 0.940\\
-\hspace{1em}cif-extension & 0.144 (0.010) & 0.747 (0.013) & 11.336 & 24.6 & 6.951 & 62.5\\
-\hspace{1em}glmnet-cox & 0.138 (0.021) & 0.727 (0.014) & 0.140 & 0.304 & 0.004 & 0.036\\
-\hspace{1em}xgboost-cox & 0.123 (0.012) & 0.733 (0.012) & 3.706 & 8.03 & 0.005 & 0.045\\
-\hspace{1em}ranger-extratrees & 0.116 (0.005) & 0.744 (0.012) & 0.083 & 0.179 & 0.193 & 1.74\\
-\hspace{1em}nn-cox & 0.032 (0.057) & 0.614 (0.096) & 15.851 & 34.4 & 1.119 & 10.1\\
-\hspace{1em}xgboost-aft & -0.840 (0.148) & 0.733 (0.013) & 13.195 & 28.6 & 0.010 & 0.087\\
+\hspace{1em}cif-rotate & 0.160 (0.019) & 0.744 (0.014) & 15.319 & 34.5 & 6.540 & 62.8\\
+\hspace{1em}aorsf-fast & 0.158 (0.016) & 0.742 (0.011) & 0.444 & 1.00 & 0.104 & 1.00\\
+\hspace{1em}cif-standard & 0.151 (0.015) & 0.738 (0.012) & 1.432 & 3.23 & 6.299 & 60.5\\
+\hspace{1em}rsf-standard & 0.151 (0.017) & 0.737 (0.011) & 1.906 & 4.29 & 0.207 & 1.99\\
+\hspace{1em}glmnet-cox & 0.138 (0.021) & 0.727 (0.014) & 0.131 & 0.295 & 0.004 & 0.038\\
+\hspace{1em}xgboost-cox & 0.123 (0.012) & 0.733 (0.012) & 3.450 & 7.77 & 0.004 & 0.038\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.015 (0.011) & 0.651 (0.055) & 0.119 & 0.587 & 0.002 & 0.048\\
-\hspace{1em}aorsf-cph & 0.010 (0.013) & 0.643 (0.036) & 0.608 & 3.01 & 0.043 & 1.02\\
-\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.641 (0.036) & 0.202 & 1.00 & 0.042 & 1.00\\
-\hspace{1em}ranger-extratrees & 0.008 (0.006) & 0.642 (0.030) & 0.072 & 0.356 & 0.785 & 18.6\\
-\hspace{1em}cif-extension & 0.008 (0.010) & 0.625 (0.028) & 9.606 & 47.5 & 5.217 & 123.3\\
-\hspace{1em}obliqueRSF-net & 0.007 (0.010) & 0.628 (0.033) & 44.947 & 222.2 & 16.670 & 393.9\\
-\hspace{1em}aorsf-net & 0.007 (0.014) & 0.641 (0.034) & 25.311 & 125.1 & 0.043 & 1.02\\
-\hspace{1em}aorsf-random & 0.007 (0.013) & 0.633 (0.033) & 1.367 & 6.76 & 0.042 & 0.993\\
-\hspace{1em}xgboost-cox & 0.007 (0.017) & 0.639 (0.039) & 1.886 & 9.32 & 0.003 & 0.071\\
-\hspace{1em}cif-standard & 0.006 (0.011) & 0.628 (0.033) & 1.730 & 8.55 & 5.759 & 136.1\\
-\hspace{1em}nn-cox & -0.003 (0.005) & 0.505 (0.041) & 12.035 & 59.5 & 1.253 & 29.6\\
-\hspace{1em}rsf-standard & -0.009 (0.018) & 0.616 (0.036) & 0.906 & 4.48 & 0.075 & 1.77\\
-\hspace{1em}cif-rotate & -0.024 (0.023) & 0.553 (0.035) & 13.627 & 67.4 & 4.933 & 116.6\\
-\hspace{1em}xgboost-aft & -5.59 (0.998) & 0.629 (0.039) & 10.872 & 53.7 & 0.007 & 0.166\\
+\hspace{1em}glmnet-cox & 0.015 (0.011) & 0.651 (0.055) & 0.118 & 0.599 & 0.002 & 0.050\\
+\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.641 (0.036) & 0.197 & 1.00 & 0.040 & 1.00\\
+\hspace{1em}xgboost-cox & 0.007 (0.017) & 0.639 (0.039) & 1.734 & 8.79 & 0.003 & 0.075\\
+\hspace{1em}cif-standard & 0.006 (0.011) & 0.628 (0.033) & 1.443 & 7.32 & 5.801 & 144.9\\
+\hspace{1em}rsf-standard & -0.009 (0.018) & 0.616 (0.036) & 0.684 & 3.47 & 0.077 & 1.92\\
+\hspace{1em}cif-rotate & -0.024 (0.023) & 0.553 (0.035) & 12.997 & 65.9 & 4.817 & 120.3\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.639 (0.023) & 0.943 (0.007) & 21.710 & 79.3 & 6.039 & 105.1\\
-\hspace{1em}glmnet-cox & 0.620 (0.033) & 0.940 (0.009) & 0.200 & 0.730 & 0.003 & 0.052\\
-\hspace{1em}nn-cox & 0.542 (0.082) & 0.906 (0.032) & 19.966 & 72.9 & 0.768 & 13.4\\
-\hspace{1em}aorsf-net & 0.531 (0.027) & 0.928 (0.010) & 55.942 & 204.3 & 0.060 & 1.05\\
-\hspace{1em}aorsf-cph & 0.523 (0.024) & 0.925 (0.011) & 0.810 & 2.96 & 0.059 & 1.03\\
-\hspace{1em}rsf-standard & 0.520 (0.021) & 0.922 (0.010) & 1.472 & 5.37 & 0.103 & 1.79\\
-\hspace{1em}aorsf-fast & 0.517 (0.026) & 0.922 (0.012) & 0.274 & 1.00 & 0.057 & 1.00\\
-\hspace{1em}xgboost-cox & 0.511 (0.028) & 0.932 (0.009) & 13.948 & 50.9 & 0.006 & 0.104\\
-\hspace{1em}cif-standard & 0.475 (0.028) & 0.902 (0.018) & 0.817 & 2.98 & 2.096 & 36.5\\
-\hspace{1em}cif-extension & 0.455 (0.024) & 0.920 (0.013) & 9.786 & 35.7 & 6.061 & 105.4\\
-\hspace{1em}ranger-extratrees & 0.431 (0.025) & 0.900 (0.019) & 0.079 & 0.289 & 0.114 & 1.98\\
-\hspace{1em}obliqueRSF-net & 0.320 (0.022) & 0.909 (0.017) & 155.578 & 568.2 & 27.372 & 476.1\\
-\hspace{1em}aorsf-random & 0.300 (0.031) & 0.849 (0.027) & 1.481 & 5.41 & 0.053 & 0.923\\
-\hspace{1em}xgboost-aft & -0.477 (0.082) & 0.927 (0.010) & 48.721 & 177.9 & 0.009 & 0.156\\
+\hspace{1em}cif-rotate & 0.639 (0.023) & 0.943 (0.007) & 20.129 & 26.2 & 5.703 & 105.5\\
+\hspace{1em}glmnet-cox & 0.620 (0.033) & 0.940 (0.009) & 0.671 & 0.872 & 0.003 & 0.056\\
+\hspace{1em}rsf-standard & 0.520 (0.021) & 0.922 (0.010) & 1.666 & 2.17 & 0.103 & 1.91\\
+\hspace{1em}aorsf-fast & 0.517 (0.026) & 0.922 (0.012) & 0.769 & 1.00 & 0.054 & 1.00\\
+\hspace{1em}xgboost-cox & 0.511 (0.028) & 0.932 (0.009) & 16.829 & 21.9 & 0.005 & 0.093\\
+\hspace{1em}cif-standard & 0.475 (0.028) & 0.902 (0.018) & 0.867 & 1.13 & 2.080 & 38.5\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.215 (0.008) & 0.868 (0.005) & 19.970 & 3.60 & 15.802 & 1.40\\
-\hspace{1em}aorsf-fast & 0.215 (0.009) & 0.869 (0.005) & 5.540 & 1.00 & 11.287 & 1.00\\
-\hspace{1em}aorsf-net & 0.213 (0.008) & 0.864 (0.006) & 502.140 & 90.6 & 10.259 & 0.909\\
-\hspace{1em}obliqueRSF-net & 0.212 (0.008) & 0.868 (0.006) & 1536.877 & 277.4 & 6754.575 & 598.4\\
-\hspace{1em}rsf-standard & 0.210 (0.009) & 0.860 (0.005) & 12.179 & 2.20 & 1.378 & 0.122\\
-\hspace{1em}glmnet-cox & 0.209 (0.011) & 0.861 (0.005) & 1.900 & 0.343 & 0.876 & 0.078\\
-\hspace{1em}cif-standard & 0.208 (0.007) & 0.863 (0.006) & 72.584 & 13.1 & 753.937 & 66.8\\
-\hspace{1em}cif-rotate & 0.193 (0.008) & 0.866 (0.005) & 288.250 & 52.0 & 224.923 & 19.9\\
-\hspace{1em}ranger-extratrees & 0.183 (0.007) & 0.860 (0.005) & 46.126 & 8.33 & 146.397 & 13.0\\
-\hspace{1em}cif-extension & 0.168 (0.003) & 0.866 (0.006) & 129.626 & 23.4 & 211.122 & 18.7\\
-\hspace{1em}aorsf-random & 0.142 (0.007) & 0.838 (0.007) & 15.152 & 2.73 & 14.820 & 1.31\\
-\hspace{1em}xgboost-cox & 0.023 (0.015) & 0.876 (0.005) & 8.989 & 1.62 & 1.026 & 0.091\\
-\hspace{1em}nn-cox & -0.001 (0.009) & 0.577 (0.108) & 31.442 & 5.68 & 192.811 & 17.1\\
-\hspace{1em}xgboost-aft & -7.27 (0.765) & 0.875 (0.005) & 28.699 & 5.18 & 0.807 & 0.072\\
+\hspace{1em}aorsf-fast & 0.215 (0.009) & 0.869 (0.005) & 5.813 & 1.00 & 11.773 & 1.00\\
+\hspace{1em}rsf-standard & 0.210 (0.009) & 0.860 (0.005) & 10.989 & 1.89 & 1.393 & 0.118\\
+\hspace{1em}glmnet-cox & 0.209 (0.011) & 0.861 (0.005) & 2.110 & 0.363 & 0.124 & 0.011\\
+\hspace{1em}cif-standard & 0.208 (0.007) & 0.863 (0.006) & 64.081 & 11.0 & 674.392 & 57.3\\
+\hspace{1em}cif-rotate & 0.193 (0.008) & 0.866 (0.005) & 254.040 & 43.7 & 194.487 & 16.5\\
+\hspace{1em}xgboost-cox & 0.023 (0.015) & 0.876 (0.005) & 8.628 & 1.48 & 1.012 & 0.086\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.430 (0.033) & 0.908 (0.021) & 0.081 & 1.00 & 0.020 & 1.00\\
-\hspace{1em}aorsf-cph & 0.418 (0.034) & 0.906 (0.021) & 0.161 & 2.00 & 0.020 & 0.996\\
-\hspace{1em}aorsf-net & 0.412 (0.035) & 0.905 (0.022) & 16.130 & 200.3 & 0.020 & 1.00\\
-\hspace{1em}cif-rotate & 0.405 (0.041) & 0.899 (0.022) & 9.930 & 123.3 & 2.165 & 107.7\\
-\hspace{1em}rsf-standard & 0.391 (0.034) & 0.895 (0.023) & 0.111 & 1.37 & 0.040 & 2.01\\
-\hspace{1em}obliqueRSF-net & 0.369 (0.032) & 0.906 (0.022) & 114.388 & 1,420.7 & 1.934 & 96.2\\
-\hspace{1em}aorsf-random & 0.354 (0.031) & 0.893 (0.020) & 0.373 & 4.63 & 0.020 & 1.00\\
-\hspace{1em}cif-standard & 0.351 (0.034) & 0.904 (0.025) & 0.241 & 2.99 & 1.152 & 57.3\\
-\hspace{1em}cif-extension & 0.348 (0.033) & 0.901 (0.023) & 9.607 & 119.3 & 3.745 & 186.4\\
-\hspace{1em}glmnet-cox & 0.342 (0.045) & 0.886 (0.028) & 0.115 & 1.43 & 0.002 & 0.101\\
-\hspace{1em}ranger-extratrees & 0.276 (0.028) & 0.894 (0.027) & 0.028 & 0.348 & 0.040 & 2.00\\
-\hspace{1em}xgboost-cox & 0.256 (0.104) & 0.881 (0.027) & 4.597 & 57.1 & 0.003 & 0.149\\
-\hspace{1em}nn-cox & -0.035 (0.064) & 0.577 (0.166) & 11.413 & 141.7 & 0.242 & 12.0\\
-\hspace{1em}xgboost-aft & -0.953 (0.305) & 0.883 (0.024) & 8.994 & 111.7 & 0.006 & 0.299\\
+\hspace{1em}aorsf-fast & 0.430 (0.033) & 0.908 (0.021) & 0.075 & 1.00 & 0.018 & 1.00\\
+\hspace{1em}cif-rotate & 0.405 (0.041) & 0.899 (0.022) & 9.498 & 126.5 & 2.287 & 126.9\\
+\hspace{1em}rsf-standard & 0.391 (0.034) & 0.895 (0.023) & 0.102 & 1.36 & 0.039 & 2.17\\
+\hspace{1em}cif-standard & 0.351 (0.034) & 0.904 (0.025) & 0.194 & 2.59 & 0.850 & 47.1\\
+\hspace{1em}glmnet-cox & 0.342 (0.045) & 0.886 (0.028) & 0.104 & 1.39 & 0.002 & 0.111\\
+\hspace{1em}xgboost-cox & 0.256 (0.104) & 0.881 (0.027) & 4.587 & 61.1 & 0.003 & 0.167\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.167 (0.012) & 0.762 (0.009) & 158.184 & 167.0 & 0.393 & 0.928\\
-\hspace{1em}obliqueRSF-net & 0.164 (0.010) & 0.761 (0.009) & 522.346 & 551.5 & 122.804 & 289.7\\
-\hspace{1em}aorsf-cph & 0.164 (0.012) & 0.758 (0.009) & 2.691 & 2.84 & 0.421 & 0.994\\
-\hspace{1em}aorsf-fast & 0.162 (0.012) & 0.757 (0.009) & 0.947 & 1.00 & 0.424 & 1.00\\
-\hspace{1em}cif-standard & 0.160 (0.010) & 0.759 (0.009) & 7.041 & 7.43 & 43.238 & 102.0\\
-\hspace{1em}rsf-standard & 0.160 (0.014) & 0.756 (0.009) & 2.859 & 3.02 & 0.865 & 2.04\\
-\hspace{1em}aorsf-random & 0.154 (0.010) & 0.752 (0.010) & 4.162 & 4.39 & 0.392 & 0.925\\
-\hspace{1em}cif-rotate & 0.148 (0.011) & 0.750 (0.011) & 34.744 & 36.7 & 29.541 & 69.7\\
-\hspace{1em}ranger-extratrees & 0.140 (0.006) & 0.748 (0.009) & 3.506 & 3.70 & 2.848 & 6.72\\
-\hspace{1em}xgboost-cox & 0.131 (0.014) & 0.753 (0.010) & 4.796 & 5.06 & 0.020 & 0.047\\
-\hspace{1em}cif-extension & 0.131 (0.004) & 0.751 (0.008) & 23.585 & 24.9 & 30.945 & 73.0\\
-\hspace{1em}glmnet-cox & 0.119 (0.008) & 0.731 (0.009) & 0.671 & 0.708 & 0.018 & 0.043\\
-\hspace{1em}nn-cox & -0.005 (0.011) & 0.506 (0.043) & 17.750 & 18.7 & 9.921 & 23.4\\
-\hspace{1em}xgboost-aft & -1.34 (0.161) & 0.761 (0.009) & 14.771 & 15.6 & 0.010 & 0.024\\
+\hspace{1em}aorsf-fast & 0.162 (0.012) & 0.757 (0.009) & 1.488 & 1.00 & 0.397 & 1.00\\
+\hspace{1em}cif-standard & 0.160 (0.010) & 0.759 (0.009) & 4.838 & 3.25 & 29.075 & 73.2\\
+\hspace{1em}rsf-standard & 0.160 (0.014) & 0.756 (0.009) & 2.974 & 2.00 & 0.846 & 2.13\\
+\hspace{1em}cif-rotate & 0.148 (0.011) & 0.750 (0.011) & 34.842 & 23.4 & 32.884 & 82.8\\
+\hspace{1em}xgboost-cox & 0.131 (0.014) & 0.753 (0.010) & 4.263 & 2.87 & 0.017 & 0.043\\
+\hspace{1em}glmnet-cox & 0.119 (0.008) & 0.731 (0.009) & 0.779 & 0.523 & 0.019 & 0.048\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.148 (0.010) & 0.737 (0.009) & 547.423 & 508.8 & 133.525 & 289.3\\
-\hspace{1em}aorsf-net & 0.147 (0.011) & 0.735 (0.009) & 168.357 & 156.5 & 0.425 & 0.922\\
-\hspace{1em}aorsf-cph & 0.145 (0.011) & 0.734 (0.009) & 2.986 & 2.78 & 0.453 & 0.981\\
-\hspace{1em}cif-standard & 0.145 (0.011) & 0.734 (0.009) & 5.054 & 4.70 & 30.784 & 66.7\\
-\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 1.076 & 1.00 & 0.462 & 1.00\\
-\hspace{1em}aorsf-random & 0.140 (0.010) & 0.730 (0.008) & 4.277 & 3.97 & 0.423 & 0.917\\
-\hspace{1em}rsf-standard & 0.139 (0.012) & 0.731 (0.008) & 3.016 & 2.80 & 0.372 & 0.806\\
-\hspace{1em}ranger-extratrees & 0.135 (0.007) & 0.733 (0.009) & 3.616 & 3.36 & 2.835 & 6.14\\
-\hspace{1em}cif-rotate & 0.130 (0.010) & 0.725 (0.009) & 37.506 & 34.9 & 35.411 & 76.7\\
-\hspace{1em}cif-extension & 0.119 (0.006) & 0.731 (0.008) & 24.957 & 23.2 & 29.569 & 64.1\\
-\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.727 (0.008) & 0.706 & 0.656 & 0.028 & 0.061\\
-\hspace{1em}xgboost-cox & 0.114 (0.008) & 0.729 (0.009) & 3.816 & 3.55 & 0.020 & 0.044\\
-\hspace{1em}nn-cox & -0.002 (0.002) & 0.534 (0.068) & 21.275 & 19.8 & 9.967 & 21.6\\
-\hspace{1em}xgboost-aft & -1.01 (0.129) & 0.735 (0.009) & 15.443 & 14.4 & 0.010 & 0.022\\
+\hspace{1em}cif-standard & 0.145 (0.011) & 0.734 (0.009) & 4.883 & 2.98 & 29.781 & 67.9\\
+\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 1.636 & 1.00 & 0.438 & 1.00\\
+\hspace{1em}rsf-standard & 0.139 (0.012) & 0.731 (0.008) & 3.160 & 1.93 & 0.836 & 1.91\\
+\hspace{1em}cif-rotate & 0.130 (0.010) & 0.725 (0.009) & 36.274 & 22.2 & 36.461 & 83.2\\
+\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.727 (0.008) & 0.815 & 0.498 & 0.029 & 0.066\\
+\hspace{1em}xgboost-cox & 0.114 (0.008) & 0.729 (0.009) & 3.774 & 2.31 & 0.020 & 0.046\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.252 (0.014) & 0.825 (0.007) & 2.664 & 1.00 & 4.471 & 1.00\\
-\hspace{1em}aorsf-cph & 0.252 (0.013) & 0.825 (0.008) & 7.125 & 2.67 & 5.990 & 1.34\\
-\hspace{1em}aorsf-net & 0.252 (0.012) & 0.823 (0.008) & 320.194 & 120.2 & 5.152 & 1.15\\
-\hspace{1em}glmnet-cox & 0.249 (0.012) & 0.820 (0.007) & 1.217 & 0.457 & 0.099 & 0.022\\
-\hspace{1em}obliqueRSF-net & 0.249 (0.011) & 0.821 (0.008) & 1170.382 & 439.3 & 814.990 & 182.3\\
-\hspace{1em}ranger-extratrees & 0.245 (0.009) & 0.820 (0.007) & 15.036 & 5.64 & 13.481 & 3.02\\
-\hspace{1em}cif-standard & 0.245 (0.011) & 0.818 (0.008) & 20.391 & 7.65 & 155.387 & 34.8\\
-\hspace{1em}rsf-standard & 0.245 (0.013) & 0.815 (0.008) & 5.872 & 2.20 & 0.575 & 0.129\\
-\hspace{1em}aorsf-random & 0.233 (0.012) & 0.816 (0.008) & 9.238 & 3.47 & 4.902 & 1.10\\
-\hspace{1em}cif-rotate & 0.230 (0.009) & 0.819 (0.007) & 67.494 & 25.3 & 137.166 & 30.7\\
-\hspace{1em}cif-extension & 0.203 (0.005) & 0.820 (0.008) & 44.122 & 16.6 & 162.158 & 36.3\\
-\hspace{1em}xgboost-cox & 0.097 (0.038) & 0.824 (0.007) & 6.133 & 2.30 & 0.101 & 0.023\\
-\hspace{1em}nn-cox & 0.003 (0.006) & 0.612 (0.135) & 25.297 & 9.49 & 27.315 & 6.11\\
-\hspace{1em}xgboost-aft & -2.71 (0.293) & 0.823 (0.008) & 22.227 & 8.34 & 0.035 & 0.008\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{sim}}}\\
-\hline
-\hspace{1em}aorsf-net & 0.034 (0.022) & 0.632 (0.038) & 224.558 & 187.4 & 72.991 & 1.36\\
-\hspace{1em}aorsf-cph & 0.033 (0.023) & 0.635 (0.038) & 3.021 & 2.52 & 61.620 & 1.15\\
-\hspace{1em}aorsf-fast & 0.029 (0.023) & 0.636 (0.038) & 1.198 & 1.00 & 53.771 & 1.00\\
-\hspace{1em}aorsf-random & 0.029 (0.013) & 0.616 (0.033) & 7.759 & 6.47 & 68.892 & 1.28\\
-\hspace{1em}obliqueRSF-net & 0.027 (0.016) & 0.613 (0.043) & 910.443 & 759.7 & 380.178 & 7.07\\
-\hspace{1em}cif-standard & 0.023 (0.015) & 0.603 (0.043) & 6.188 & 5.16 & 231.294 & 4.30\\
-\hspace{1em}cif-rotate & 0.020 (0.021) & 0.592 (0.051) & 316.904 & 264.4 & 801.648 & 14.9\\
-\hspace{1em}rsf-standard & 0.019 (0.014) & 0.610 (0.032) & 5.788 & 4.83 & 2.322 & 0.043\\
-\hspace{1em}ranger-extratrees & 0.018 (0.008) & 0.620 (0.037) & 4.820 & 4.02 & 6.453 & 0.120\\
-\hspace{1em}cif-extension & 0.015 (0.008) & 0.599 (0.040) & 107.025 & 89.3 & 1030.394 & 19.2\\
-\hspace{1em}xgboost-cox & -0.023 (0.043) & 0.616 (0.039) & 17.126 & 14.3 & 1.747 & 0.032\\
-\hspace{1em}glmnet-cox & -0.036 (0.064) & 0.616 (0.040) & 0.545 & 0.455 & 1.462 & 0.027\\
-\hspace{1em}nn-cox & -0.059 (0.071) & 0.616 (0.043) & 29.897 & 24.9 & 18.594 & 0.346\\
-\hspace{1em}xgboost-aft & -1.66 (0.126) & 0.624 (0.038) & 52.084 & 43.5 & 1.380 & 0.026\\
+\hspace{1em}aorsf-fast & 0.252 (0.014) & 0.825 (0.007) & 3.093 & 1.00 & 4.842 & 1.00\\
+\hspace{1em}glmnet-cox & 0.249 (0.012) & 0.820 (0.007) & 1.261 & 0.408 & 0.081 & 0.017\\
+\hspace{1em}cif-standard & 0.245 (0.011) & 0.818 (0.008) & 19.554 & 6.32 & 146.176 & 30.2\\
+\hspace{1em}rsf-standard & 0.245 (0.013) & 0.815 (0.008) & 6.058 & 1.96 & 0.611 & 0.126\\
+\hspace{1em}cif-rotate & 0.230 (0.009) & 0.819 (0.007) & 67.331 & 21.8 & 132.391 & 27.3\\
+\hspace{1em}xgboost-cox & 0.097 (0.038) & 0.824 (0.007) & 6.139 & 1.98 & 0.084 & 0.017\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.072 (0.011) & 0.796 (0.011) & 14.356 & 4.42 & 0.033 & 0.036\\
-\hspace{1em}aorsf-net & 0.071 (0.007) & 0.796 (0.011) & 343.232 & 105.7 & 0.949 & 1.05\\
-\hspace{1em}aorsf-cph & 0.070 (0.006) & 0.798 (0.011) & 9.991 & 3.08 & 0.971 & 1.07\\
-\hspace{1em}aorsf-fast & 0.070 (0.006) & 0.798 (0.011) & 3.248 & 1.00 & 0.908 & 1.00\\
-\hspace{1em}obliqueRSF-net & 0.068 (0.004) & 0.798 (0.012) & 1161.784 & 357.7 & 1311.066 & 1,444.0\\
-\hspace{1em}rsf-standard & 0.065 (0.007) & 0.789 (0.014) & 5.167 & 1.59 & 0.685 & 0.755\\
-\hspace{1em}cif-standard & 0.062 (0.003) & 0.798 (0.011) & 51.058 & 15.7 & 199.723 & 220.0\\
-\hspace{1em}cif-rotate & 0.061 (0.005) & 0.791 (0.012) & 1033.390 & 318.1 & 136.883 & 150.8\\
-\hspace{1em}ranger-extratrees & 0.055 (0.003) & 0.792 (0.012) & 8.015 & 2.47 & 9.226 & 10.2\\
-\hspace{1em}nn-cox & 0.040 (0.013) & 0.765 (0.017) & 24.177 & 7.44 & 33.019 & 36.4\\
-\hspace{1em}cif-extension & 0.034 (0.002) & 0.790 (0.011) & 123.690 & 38.1 & 53.842 & 59.3\\
-\hspace{1em}aorsf-random & 0.027 (0.002) & 0.747 (0.016) & 6.889 & 2.12 & 1.101 & 1.21\\
-\hspace{1em}xgboost-cox & 0.006 (0.017) & 0.800 (0.011) & 7.910 & 2.44 & 0.033 & 0.036\\
-\hspace{1em}xgboost-aft & -10.8 (1.01) & 0.796 (0.012) & 24.603 & 7.57 & 0.016 & 0.018\\
+\hspace{1em}glmnet-cox & 0.072 (0.011) & 0.796 (0.011) & 12.974 & 4.88 & 0.026 & 0.025\\
+\hspace{1em}aorsf-fast & 0.070 (0.006) & 0.798 (0.011) & 2.657 & 1.00 & 1.054 & 1.00\\
+\hspace{1em}rsf-standard & 0.065 (0.007) & 0.789 (0.014) & 3.854 & 1.45 & 0.701 & 0.665\\
+\hspace{1em}cif-standard & 0.062 (0.003) & 0.798 (0.011) & 48.137 & 18.1 & 185.155 & 175.7\\
+\hspace{1em}cif-rotate & 0.061 (0.005) & 0.791 (0.012) & 907.261 & 341.4 & 135.081 & 128.2\\
+\hspace{1em}xgboost-cox & 0.006 (0.017) & 0.800 (0.011) & 6.905 & 2.60 & 0.029 & 0.028\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.124 (0.012) & 0.771 (0.009) & 5.349 & 1.10 & 0.080 & 0.016\\
-\hspace{1em}aorsf-cph & 0.118 (0.008) & 0.770 (0.008) & 14.219 & 2.92 & 3.629 & 0.751\\
-\hspace{1em}aorsf-fast & 0.117 (0.008) & 0.770 (0.008) & 4.874 & 1.00 & 4.833 & 1.00\\
-\hspace{1em}aorsf-net & 0.114 (0.009) & 0.769 (0.009) & 657.473 & 134.9 & 4.336 & 0.897\\
-\hspace{1em}obliqueRSF-net & 0.113 (0.007) & 0.767 (0.008) & 3057.859 & 627.3 & 1289.532 & 266.8\\
-\hspace{1em}rsf-standard & 0.111 (0.008) & 0.763 (0.009) & 6.755 & 1.39 & 0.729 & 0.151\\
-\hspace{1em}cif-standard & 0.107 (0.006) & 0.764 (0.008) & 46.959 & 9.63 & 212.057 & 43.9\\
-\hspace{1em}nn-cox & 0.099 (0.014) & 0.757 (0.011) & 68.533 & 14.1 & 64.373 & 13.3\\
-\hspace{1em}ranger-extratrees & 0.097 (0.005) & 0.756 (0.009) & 11.099 & 2.28 & 11.653 & 2.41\\
-\hspace{1em}cif-rotate & 0.092 (0.007) & 0.745 (0.009) & 1108.036 & 227.3 & 188.939 & 39.1\\
-\hspace{1em}cif-extension & 0.056 (0.002) & 0.747 (0.009) & 139.289 & 28.6 & 103.221 & 21.4\\
-\hspace{1em}aorsf-random & 0.053 (0.003) & 0.720 (0.010) & 13.605 & 2.79 & 4.437 & 0.918\\
-\hspace{1em}xgboost-cox & 0.031 (0.023) & 0.772 (0.008) & 9.951 & 2.04 & 0.084 & 0.017\\
-\hspace{1em}xgboost-aft & -4.41 (0.302) & 0.772 (0.008) & 28.705 & 5.89 & 0.653 & 0.135\\
+\hspace{1em}glmnet-cox & 0.124 (0.012) & 0.771 (0.009) & 4.886 & 1.02 & 0.065 & 0.017\\
+\hspace{1em}aorsf-fast & 0.117 (0.008) & 0.770 (0.008) & 4.807 & 1.00 & 3.794 & 1.00\\
+\hspace{1em}rsf-standard & 0.111 (0.008) & 0.763 (0.009) & 6.757 & 1.41 & 0.752 & 0.198\\
+\hspace{1em}cif-standard & 0.107 (0.006) & 0.764 (0.008) & 48.766 & 10.1 & 208.039 & 54.8\\
+\hspace{1em}cif-rotate & 0.092 (0.007) & 0.745 (0.009) & 1024.991 & 213.2 & 194.183 & 51.2\\
+\hspace{1em}xgboost-cox & 0.031 (0.023) & 0.772 (0.008) & 9.163 & 1.91 & 0.077 & 0.020\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.114 (0.012) & 0.747 (0.012) & 407.606 & 340.6 & 60.875 & 257.1\\
-\hspace{1em}glmnet-cox & 0.114 (0.013) & 0.746 (0.012) & 0.791 & 0.661 & 0.019 & 0.080\\
-\hspace{1em}cif-rotate & 0.113 (0.013) & 0.741 (0.011) & 72.623 & 60.7 & 22.449 & 94.8\\
-\hspace{1em}aorsf-net & 0.112 (0.013) & 0.743 (0.012) & 125.118 & 104.6 & 0.243 & 1.03\\
-\hspace{1em}aorsf-cph & 0.111 (0.014) & 0.744 (0.012) & 2.822 & 2.36 & 0.237 & 1.00\\
-\hspace{1em}aorsf-fast & 0.110 (0.015) & 0.744 (0.011) & 1.197 & 1.00 & 0.237 & 1.00\\
-\hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 5.168 & 4.32 & 22.720 & 96.0\\
-\hspace{1em}rsf-standard & 0.105 (0.011) & 0.735 (0.011) & 2.800 & 2.34 & 0.304 & 1.29\\
-\hspace{1em}cif-extension & 0.094 (0.006) & 0.744 (0.012) & 30.964 & 25.9 & 19.184 & 81.0\\
-\hspace{1em}ranger-extratrees & 0.092 (0.008) & 0.738 (0.012) & 4.404 & 3.68 & 1.442 & 6.09\\
-\hspace{1em}xgboost-cox & 0.090 (0.009) & 0.744 (0.010) & 4.784 & 4.00 & 0.010 & 0.042\\
-\hspace{1em}aorsf-random & 0.080 (0.006) & 0.731 (0.013) & 3.206 & 2.68 & 0.230 & 0.974\\
-\hspace{1em}nn-cox & 0.077 (0.024) & 0.711 (0.023) & 23.045 & 19.3 & 5.516 & 23.3\\
-\hspace{1em}xgboost-aft & -1.98 (0.218) & 0.742 (0.009) & 14.099 & 11.8 & 0.010 & 0.042\\
+\hspace{1em}glmnet-cox & 0.114 (0.013) & 0.746 (0.012) & 0.257 & 0.387 & 0.009 & 0.040\\
+\hspace{1em}cif-rotate & 0.113 (0.013) & 0.741 (0.011) & 69.125 & 104.0 & 18.805 & 84.2\\
+\hspace{1em}aorsf-fast & 0.110 (0.015) & 0.744 (0.011) & 0.665 & 1.00 & 0.223 & 1.00\\
+\hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 3.672 & 5.53 & 18.416 & 82.5\\
+\hspace{1em}rsf-standard & 0.105 (0.011) & 0.735 (0.011) & 2.072 & 3.12 & 0.298 & 1.34\\
+\hspace{1em}xgboost-cox & 0.090 (0.009) & 0.744 (0.010) & 4.047 & 6.09 & 0.009 & 0.040\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.201 (0.051) & 0.797 (0.035) & 10.595 & 189.0 & 0.013 & 1.07\\
-\hspace{1em}aorsf-fast & 0.200 (0.050) & 0.795 (0.034) & 0.056 & 1.00 & 0.012 & 1.00\\
-\hspace{1em}cif-rotate & 0.198 (0.066) & 0.788 (0.036) & 4.899 & 87.4 & 1.095 & 90.3\\
-\hspace{1em}aorsf-cph & 0.198 (0.052) & 0.794 (0.035) & 0.104 & 1.85 & 0.012 & 0.998\\
-\hspace{1em}rsf-standard & 0.175 (0.048) & 0.787 (0.037) & 0.083 & 1.48 & 0.030 & 2.46\\
-\hspace{1em}cif-extension & 0.173 (0.048) & 0.795 (0.034) & 5.230 & 93.3 & 1.640 & 135.3\\
-\hspace{1em}glmnet-cox & 0.160 (0.036) & 0.787 (0.038) & 0.091 & 1.62 & 0.002 & 0.165\\
-\hspace{1em}aorsf-random & 0.154 (0.045) & 0.780 (0.037) & 0.226 & 4.04 & 0.012 & 0.991\\
-\hspace{1em}cif-standard & 0.128 (0.040) & 0.770 (0.037) & 0.096 & 1.71 & 0.122 & 10.1\\
-\hspace{1em}obliqueRSF-net & 0.126 (0.034) & 0.796 (0.029) & 65.750 & 1,173.0 & 0.688 & 56.8\\
-\hspace{1em}ranger-extratrees & 0.091 (0.033) & 0.778 (0.038) & 0.021 & 0.377 & 0.029 & 2.42\\
-\hspace{1em}xgboost-cox & 0.068 (0.078) & 0.750 (0.046) & 1.291 & 23.0 & 0.002 & 0.165\\
-\hspace{1em}xgboost-aft & -0.009 (0.136) & 0.753 (0.047) & 6.788 & 121.1 & 0.006 & 0.495\\
-\hspace{1em}nn-cox & -0.039 (0.036) & 0.505 (0.078) & 11.297 & 201.6 & 0.165 & 13.6\\*
+\hspace{1em}aorsf-fast & 0.200 (0.050) & 0.795 (0.034) & 0.052 & 1.00 & 0.011 & 1.00\\
+\hspace{1em}cif-rotate & 0.198 (0.066) & 0.788 (0.036) & 4.620 & 88.8 & 1.017 & 92.3\\
+\hspace{1em}rsf-standard & 0.175 (0.048) & 0.787 (0.037) & 0.063 & 1.21 & 0.035 & 3.18\\
+\hspace{1em}glmnet-cox & 0.160 (0.036) & 0.787 (0.038) & 0.075 & 1.44 & 0.002 & 0.182\\
+\hspace{1em}cif-standard & 0.128 (0.040) & 0.770 (0.037) & 0.093 & 1.79 & 0.133 & 12.1\\
+\hspace{1em}xgboost-cox & 0.068 (0.078) & 0.750 (0.046) & 1.144 & 22.0 & 0.002 & 0.182\\*
 \end{longtable}

### 2022-06-20 R/bench_pred.R

@@ -11,16 +11,14 @@ bench_pred <- function(data_source,
                        model_fit_fun,
                        model_pred_fun,
                        n_obs = NULL,
-                       n_z = NULL,
-                       correlated_x = NULL,
+                       pred_corr_max = NULL,
                        run_seed,
                        test_prop = 1/2) {
 
   set.seed(run_seed)
 
   data_all <- data_load_fun(n_obs = n_obs,
-                            n_z = n_z,
-                            correlated_x = correlated_x)
+                            pred_corr_max = pred_corr_max)
 
 
   if(data_source == 'sim'){
@@ -30,8 +28,7 @@ bench_pred <- function(data_source,
     train <- data_all
 
     test <- sim_surv(n_obs = 5000,
-                     n_z = n_z,
-                     correlated_x = correlated_x) |>
+                     pred_corr_max = pred_corr_max) |>
       getElement('data')
 
   } else {
@@ -143,8 +140,7 @@ bench_pred <- function(data_source,
 
   if(data_source == 'sim'){
     out$n_obs <- n_obs
-    out$n_z <- n_z
-    out$correlated_x <- correlated_x
+    out$pred_corr_max <- pred_corr_max
   }
 
   print(out)

### 2022-06-20 R/bench_vi.R

@@ -5,29 +5,34 @@
 #' @title
 #' @param data_source
 #' @param run_seed
-bench_vi <- function(data_source,
-                     run_seed,
-                     correlated_x,
-                     n_obs,
-                     n_z) {
+bench_vi <- function(n_obs = 1000,
+                     pred_corr_max = 0.3,
+                     run_seed) {
 
   set.seed(run_seed)
 
-  sim <- sim_surv(n_obs = n_obs, n_z = n_z, correlated_x = correlated_x)
+  sim <- sim_surv(n_obs = n_obs, pred_corr_max = pred_corr_max)
 
   train <- sim$data
-  vars_signal <- sim$vars_signal
-  vars_junk <- sim$vars_junk
+
+  vars_signal <- train %>%
+    select(-time, -status, -starts_with('junk')) %>%
+    names()
+
+  vars_junk <- train %>%
+    select(starts_with('junk')) %>%
+    names()
 
   pred_horizon <- median(train$time)
 
   models <- set_names(
     c(
-      'aorsf',
-      'aorsf_menze',
-      'xgboost',
-      'randomForestSRC'
-      # 'ranger'
+      'aorsf-negation',
+      'aorsf-anova',
+      'aorsf-shap',
+      'xgboost-shap',
+      'xgboost-gain',
+      'randomForestSRC-permutation'
     )
   )
 
@@ -45,43 +50,23 @@ bench_vi <- function(data_source,
     unnest_longer(col = vi) |>
     select(name, vi, vi_id) |>
     left_join(vars_truth) |>
-    mutate(var_type = str_sub(vi_id, start = 0, end = 1)) |>
+    mutate(var_type = str_remove(vi_id, "_[0-9]+$")) |>
     group_by(name)
 
-  roc_x <- vars_data |>
-    filter(var_type %in% c('z', 'x')) |>
-    roc_auc(vi, truth = vi_true, event_level = 'second') |>
-    transmute(model = name,
-              auc = .estimate,
-              var_type = 'x')
-
-  roc_g <- vars_data |>
-    filter(var_type %in% c('z', 'g')) |>
-    roc_auc(vi, truth = vi_true, event_level = 'second') |>
-    transmute(model = name,
-              auc = .estimate,
-              var_type = 'g')
-
-  roc_w <- vars_data |>
-    filter(var_type %in% c('z', 'w')) |>
-    roc_auc(vi, truth = vi_true, event_level = 'second') |>
-    transmute(model = name,
[…]

### 2022-06-20 R/bench_vi_summarize.R

@@ -8,13 +8,34 @@
 bench_vi_summarize <- function(bm_vi_comb) {
 
   bm_vi_comb |>
-    group_by(model, xcorr, n_obs, n_z) |>
-    summarize(across(everything(), ~mean(.x))) |>
-    arrange(xcorr, n_obs, n_z, desc(overall)) |>
-    group_by(xcorr, n_obs, n_z) |>
+    group_by(model, pred_corr_max, n_obs) |>
+    summarize(across(everything(), ~mean(.x)), .groups = 'drop') |>
+    arrange(pred_corr_max, n_obs, desc(overall)) |>
+    group_by(pred_corr_max, n_obs) |>
     mutate(
       overall_prop = overall[1] / overall,
       .after = 'overall'
     )
 
 }
+
+# bm_vi_smry <- bm_vi_comb |>
+#   group_by(model) |>
+#   summarize(across(everything(), ~mean(.x)), .groups = 'drop') |>
+#   arrange(pred_corr_max, n_obs, desc(overall)) |>
+#   group_by(pred_corr_max, n_obs) |>
+#   mutate(
+#     overall_prop = overall[1] / overall,
+#     .after = 'overall'
+#   )
+#
+# gg_data <- select(bm_vi_smry, -overall_prop, -time) %>%
+#   mutate(overall = 2 * (overall - .50))
+#
+# ggplot(gg_data) +
+#   aes(x = reorder(model, overall), fill = reorder(model, overall), y = overall) +
+#   geom_bar(stat = 'identity', position = 'dodge') +
+#   coord_flip() +
+#   theme(legend.position = '') +
+#   labs(y = '2 * (C-statistic - 1/2)',
+#        x = '')

### 2022-06-20 R/data_load.R

@@ -848,3 +848,123 @@ sprint_ndi_load <- function(outcome) {
 
 }
 
+
+mesa_load <- function(outcome){
+
+  fctrs <- c("Sex", "Race", "Alcohol", "Smoking")
+
+  outcomes_keep <- switch(
+    outcome,
+    'hf' = paste(c("time", "censor"), 'hf', sep = '_'),
+    'chd' = paste(c("time", "censor"), 'chd', sep = '_'),
+    'stroke' = paste(c("time", "censor"), 'stroke', sep = '_'),
+    'death' = paste(c("time", "censor"), 'death', sep = '_')
+  )
+
+  to_drop <- c('ID',
+               'database',
+               'VisitDate',
+               'LAnova',
+               'CV',
+               "QTc",
+               "CV",
+               "LVHcv",
+               "LVHsl",
+               "hxMI",
+               "hxCABG",
+               "CVD",
+               "CHF",
+               "time_hf",
+               "censor_hf",
+               "time_death",
+               "censor_death",
+               "time_chd",
+               "censor_chd",
+               "time_stroke",
+               "censor_stroke") %>%
+    setdiff(outcomes_keep)
+
+  fread("data/mesa_and_aric.csv") %>%
+    .[database == 'mesa'] %>%
+    .[, (fctrs) := lapply(.SD, as.factor), .SDcols = fctrs] %>%
+    .[, (to_drop) := NULL] %>%
+    setnames(old = outcomes_keep, new = c("time", "status")) %>%
+    as.data.frame() %>%
+    drop_na(time, status)
+
+}
+
+
+mesa_hf_load <- function(...){
+  mesa_load(outcome = "hf")
+}
+
+mesa_chd_load <- function(...){
+  mesa_load(outcome = "chd")
+}
+
+mesa_stroke_load <- function(...){
+  mesa_load(outcome = "stroke")
+}
+
+mesa_death_load <- function(...){
+  mesa_load(outcome = "death")
+}
+
+
+aric_load <- function(outcome){
+
+  fctrs <- c("Sex", "Race", "Alcohol", "Smoking")
+
+  outcomes_keep <- switch(
+    outcome,
+    'hf' = paste(c("time", "censor"), 'hf', sep = '_'),
+    'chd' = paste(c("time", "censor"), 'chd', sep = '_'),
+    'stroke' = paste(c("time", "censor"), 'stroke', sep = '_'),
+    'death' = paste(c("time", "censor"), 'death', sep = '_')
+  )
+
+  to_drop <- c('ID',
[…]

### 2022-06-20 R/pred_wrapper_aorsf.R

@@ -1,0 +1,9 @@
+
+
+# Prediction wrapper
+pred_wrapper_aorsf <- function(object, newdata) {
+  predict(object,
+          new_data = newdata,
+          pred_horizon = 2.5) |>
+    as.numeric()
+}

### 2022-06-20 R/summarize_data_source.R

@@ -58,7 +58,15 @@ summarize_data_source <- function(analyses_real) {
         "sprint_cvd" = "SPRINT",
         "time_to_million" = "Movies released in 2015-2018",
         "vdv" = "Gene expression",
-        "veteran" = "VA lung cancer trial"
+        "veteran" = "VA lung cancer trial",
+        "mesa_hf" = "MESA",
+        "mesa_chd" = "MESA",
+        "mesa_stroke" = "MESA",
+        "mesa_death" = "MESA",
+        "aric_hf" = "ARIC",
+        "aric_chd" = "ARIC",
+        "aric_stroke" = "ARIC",
+        "aric_death" = "ARIC"
       ),
       rpack = recode(
         data,
@@ -146,7 +154,15 @@ summarize_data_source <- function(analyses_real) {
         "sprint_cvd" = "CVD death",
         "time_to_million" = "gross 1M USD",
         "vdv" = "breast cancer",
-        "veteran" = "death"
+        "veteran" = "death",
+        "mesa_hf" = "heart failure",
+        "mesa_chd" = "coronary heart disease",
+        "mesa_stroke" = "stroke",
+        "mesa_death" = "death",
+        "aric_hf" = "heart failure",
+        "aric_chd" = "coronary heart disease",
+        "aric_stroke" = "stroke",
+        "aric_death" = "death"
       ),
       .before = 2
     )

### 2022-06-20 _targets.R

@@ -18,20 +18,19 @@ lapply(list.files("./R", full.names = TRUE), base::source)
 
 model_fitters <- c(
   'aorsf_cph_1',
-  # 'aorsf_cph_1_filter',
   'aorsf_cph_15',
   'aorsf_random',
-  'aorsf_net',
+  # 'aorsf_net',
   'rotsf',
   'rsfse',
   'cif',
   'cox_net',
-  'coxtime',
-  'obliqueRSF',
+  # 'coxtime',
+  # 'obliqueRSF',
   'xgb_cox',
   'xgb_aft',
-  'randomForestSRC',
-  'ranger'
+  'randomForestSRC'
+  # 'ranger'
 )
 
 analyses_real <- expand_grid(
@@ -58,10 +57,18 @@ analyses_real <- expand_grid(
     "follic_death",
     "follic_relapse",
     "mgus2_death",
-    "mgus2_pcm"
+    "mgus2_pcm",
+    "mesa_hf",
+    "mesa_chd",
+    "mesa_stroke",
+    "mesa_death",
+    "aric_hf",
+    "aric_chd",
+    "aric_stroke",
+    "aric_death"
   ),
   model_type = model_fitters,
-  run_seed = 1:25
+  run_seed = 1:15
 ) |>
   mutate(
     data_load_fun = syms(glue("{data_source}_load")),
@@ -69,17 +76,20 @@ analyses_real <- expand_grid(
     model_pred_fun = syms(glue("{model_type}_pred"))
   )
 
-analyses_sim <- expand_grid(data_source = 'sim',
-                            n_obs = c(1000),
-                            n_z = c(20),
-                            correlated_x = c(0.3),
-                            run_seed = 1:25,
-                            model_type = model_fitters) |>
+analyses_sim_pred <- expand_grid(data_source = 'sim',
+                                 n_obs = c(1000, 2500, 5000),
+                                 pred_corr_max = c(0.10, 0.25, .50),
+                                 run_seed = 1:25,
+                                 model_type = model_fitters) |>
   mutate(
     data_load_fun = syms("sim_surv"),
     model_fit_fun = syms(glue("{model_type}_fit")),
     model_pred_fun = syms(glue("{model_type}_pred"))
   )
+
+analyses_sim_vi <- analyses_sim_pred %>%
+  select(-starts_with('model'), -starts_with('data')) %>%
+  distinct()
 
 
 tar_plan(
[…]

### 2022-06-20 packages.R

@@ -34,5 +34,7 @@ library(ggridges)
 library(tidybayes)
 library(rstan)
 library(rstanarm)
+library(fastshap)
+
 
 source("./conflicts.R")

### 2022-06-20 tests/testthat/test-sim_surv.R

@@ -1,51 +1,50 @@
 
 test_that("minimal effect bias", {
 
-  n_obs <- 500000
+  n_obs <- 10000
 
   ss_demo <-
     sim_surv(
       n_obs = n_obs,
-      n_z = 3,
-      n_x = 3,
-      n_g = 3,
-      n_w = 3,
-      n_v = 3,
-      n_c = 0,
-      effect_size_by_group = 1.5
+      n_pred_junk = 2,
+      n_pred_main = 2,
+      n_intr_main = 2,
+      n_pred_nlin = 2,
+      n_intr_nlin = 2,
+      n_pred_cmbn = 2,
+      n_intr_cmbn = 1
     )
 
-  data_sim <- ss_demo$data
 
-  data_sim$true_v <-
-    with(
-      data_sim,
-      v1 * ss_demo$coefs_lc[[1]][1] +
-        v2 * ss_demo$coefs_lc[[1]][2] +
-        v3 * ss_demo$coefs_lc[[1]][3]
+  data_sim <- ss_demo$data %>%
+    mutate(
+      hidden_cmbn_1 =
+        cmbn_1 * ss_demo$cmbn_key$hidden_cmbn_1$var_coefs[1] +
+        cmbn_2 * ss_demo$cmbn_key$hidden_cmbn_1$var_coefs[2]
     )
 
   mdl <- coxph(
     Surv(time, status) ~
-      z1 + z2 + z3 +
-      x1*g1 + x2*g2 + x3*g3 +
-      pspline(w1) + pspline(w2) + pspline(w3) +
-      v2 + v3 + true_v,
+      junk_1 + junk_2 + cmbn_1 +
+      main_1 * intr_main_1 +
+      main_2 * intr_main_2 +
+      pspline(nlin_1) * intr_hidden_nlin_1 +
+      pspline(nlin_2) * intr_hidden_nlin_2 +
+      hidden_cmbn_1 * intr_hidden_cmbn_1,
     data = data_sim
   )
 
-  effects_expected <- c("x1" = ss_demo$effect_x,
-                        "x2" = ss_demo$effect_x,
-                        "x3" = ss_demo$effect_x,
-                        "g1" = 0,
-                        "g2" = 0,
-                        "g3" = 0,
-                        "x1:g1" = ss_demo$effect_int,
-                        "x2:g2" = ss_demo$effect_int,
-                        "x3:g3" = ss_demo$effect_int,
-                        "v2" = 0,
[…]

### 2022-06-20 docs/index.Rmd
tidying up plotly results

@@
   warning = FALSE,
-  dpi = 100,
+  dpi = 600,
   fig.align='center',
@@
 
-A total of 23 risk prediction tasks in 16 data sets were analyzed.
+A total of 31 risk prediction tasks in 18 data sets were analyzed.
 
@@
 
-- For each of the 23 risk prediction problems,
+- For each of the 31 risk prediction problems,
 
@@
 
-Step 2: Fit a hierarchical Bayesian model to analyze posterior expected differences in performance:
+Step 2: Fit a Bayesian linear mixed model to analyze posterior expected differences in performance:
 
-$$\text{metric} = \widehat{\gamma} \cdot \text{model} + (1\,|\, \text{data/run})$$
+$$\text{metric} = \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run})$$
 
@@
     color = fig_data$model,
+    colors = "PuRd",
     text = table_value(fig_data$overall),
@@
     xaxis = list(title = 'Max correlation among predictors'),
-    yaxis = list(title = 'C-statistic'),
+    yaxis = list(title = 'C-statistic', range = c(0,1)),
     legend = list(title = list(text = '<b>VI technique</b>'))
@@
 
-A total of 23 risk prediction tasks in 16 data sets were analyzed.
+A total of 31 risk prediction tasks in 18 data sets were analyzed.
 
-This table is continued on the next 2 slides.
+This table is continued on the next 3 slides.
 
@@
          grp = case_when(
-           grp > 2 * n()/3 ~ 3, 
-           grp > 1 * n()/3 ~ 2,
+           grp > 3 * n()/4 ~ 4,
+           grp > 2 * n()/4 ~ 3, 
+           grp > 1 * n()/4 ~ 2,
            TRUE ~ 1
@@
 
+## Data sets continued
+
+```{r}
+
+tbls[[4]]
+
+```
+
+---
+
 ## Evaluation (bonus round)

### 2022-06-21 docs/index.Rmd
including coxtime

@@
 title: "Accelerated oblique random survival forests"
-author: "Byron C. Jaeger"
+author: "Byron C. Jaeger & Nicholas Pajewski"
 date: Last updated `r Sys.Date()`
@@
 
-## Simulated data
-
-Start with a multivariate normal draw
-
-- All columns have a mean of zero and standard deviation of 1.
-
-- Pairwise correlations are selected at random uniformly between a lower and upper boundary.
-
-- A predictor matrix including interactions, non-linear mappings, and linear combinations is used to generate a time-to-event outcome using the `simsurv` R package
-
-- Transforms are dropped from the matrix after generating the outcome values.
-
----
-
 ## Evaluation
 
-VI techniques are compared based on their discrimination (C-statistic) between relevant and irrelevant variables.
+We compute a C-statistic for each VI technique based on its discrimination between relevant and irrelevant variables.
 
-Normally a C-statistic assesses if a predicted score discriminates between positive and negative cases of a binary outcome.
+- Treat each variable like a binary outcome
 
-We use the C-statistic differently by treating each variable like a binary outcome (e.g., the outcome is 1 if the variable is relevant, 0 otherwise).
+    + The outcome is 1 if the variable is relevant
+    + The outcome is 0 if the variable is not relevant
 
-In other words, we assess VI as if it were a ‘prediction’ for the status of the variable. (can only do this for simulated data).
-
-The resulting C-statistic measures the probability that a VI technique will rank a relevant variable higher than an irrelevant variable.
+- Treat VI as if it were a ‘prediction’ for the status of the variable.
 

### 2022-06-29 paper/jmlr/main.Rnw
results for VI; viz in prog

--- 2022-06-15 paper/jmlr/main.Rnw
@@
 \usepackage{caption}
+\usepackage{multirow}
 \usepackage{hyperref}
@@
 \usepackage{bm}
+
+\DeclareCaptionLabelFormat{AppendixTables}{A.#2}
 
@@
 \newcommand{\ntest}{N_{\text{test}}}
+
+\newcommand{\secref}[1]{Section \ref{#1}}
+
+\newcommand{\tabref}[1]{Table \ref{#1}}
+\newcommand{\tabrefAppendix}[1]{Table A.\ref{#1}}
 
@@
                    bm_pred_model_viz,
+                   bm_pred_time_viz,
                    data_key,
@@
 
-to_omit <- bm_pred_comb |>
-  filter(is.na(cstat) | is.na(ibs_scaled)) |>
-  distinct(data, run) |>
-  as.list() |>
-  map(unique)
+bm_pred_n_runs <- max(bm_pred_clean$run)
 
-bm_pred_comb <- bm_pred_comb |>
-  filter( ! (data %in% to_omit$data & run %in% to_omit$run) )
+bm_pred_total_time <-
+  sum(with(bm_pred_clean, time_fit + time_pred)) / (60^2)
+
+n_learners <- nrow(model_key)
+
+n_data_sets <- length(unique(data_key$label))
+n_risk_tasks <- nrow(data_key)
+
+n_obs_model <- table_value(
+  as.integer(n_risk_tasks*bm_pred_n_runs*n_learners)
+)
+
+nrow_median <- table_value(median(data_key$nrow))
+nrow_max <- table_value(max(data_key$nrow))
+nrow_min <- table_value(min(data_key$nrow))
+
+ncol_median <- table_value(median(data_key$ncol))
+ncol_max <- table_value(max(data_key$ncol))
+ncol_min <- table_value(min(data_key$ncol))
+
+pcens_median <- table_value(100*median(data_key$pcens))
+pcens_max    <- table_value(100*max(data_key$pcens))
+pcens_min    <- table_value(100*min(data_key$pcens))
 
@@
 The aim of this article is to improve the computational efficiency and interpretability of the oblique RSF.
-In a general benchmark experiment including YYYY risk prediction tasks, we show that oblique RSFs with partially trained models have equivalent or superior prediction accuracy and are orders of magnitude more efficient than oblique RSFs with fully trained models in non-leaf nodes.
+In a general benchmark experiment including \Sexpr{n_risk_tasks} risk prediction tasks, we show that oblique RSFs with partially trained models have equivalent or superior prediction accuracy and are orders of magnitude more efficient than oblique RSFs with fully trained models in non-leaf nodes.
 We introduce a method to estimate VI for oblique RSFs and compare its ability to discriminate between signal and noise variables versus standard and state-of-the-art methods.
@@
 
-\subsection{Partial training at non-leaf nodes}
-
-We propose to identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model:
+To accelerate the oblique RSF, we propose to identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model:
 \begin{equation}\label{eqn:cox-partial-likelihood}
@@
 where $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (i.e., those still at risk at time $t_i$), and $j(i)$ is the index of the observation for which an event occurred at time $t_i$.
-The \texttt{survival} package includes documentation that outlines how to complete this estimation procedure efficiently \citep[see][exact.nw]{therneau_survival_2022}.
+Newton Raphson scoring is an extremely fast estimation procedure, and the \texttt{survival} package includes documentation that outlines how to efficiently program it \citep{therneau_survival_2022}.
 Briefly, a vector of estimated regression coefficients, $\hat{\beta}$, is updated in each step of the procedure based on its first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
 $$ \hat{\beta}^{k+1} =  \hat{\beta}^{k} + U(\hat{\beta} = \hat{\beta}^{k})\, H^{-1}(\hat{\beta} = \hat{\beta}^{k}) $$
-It is vital to cycle through iterations until a convergence threshold is met for statistical inference, but it is only necessary to complete one iteration to identify coefficients for a linear combination of predictors.
-\citet{jaeger2019oblique} identified linear combinations using penalized regression models, which supply more flexible solutions for $\hat{\beta}$ at the cost of greater computational demand.
+For statistical inference, it is recommended to complete iterations of Newton Raphson scoring until a convergence threshold is met.
+However, to identify a valid linear combination of predictors, only one iteration of Newton Raphson scoring is needed.
+It was not clear to us whether completing only one iteration of Newton Raphson scoring would provide coefficients that were stable enough to partition data effectively when we developed this technique, so we analyzed three learners in numerical experiments that assessed prediction accuracy (see \secref{sec:bm_pred}): \begin{itemize}
+\item \texttt{aorsf-extratrees}: Randomly select coefficients for linear combinations of predictors from a uniform distribution.
+\item \texttt{aorsf-fast}: Identify coefficients for linear combinations of predictor variables using one iteration of Newton Raphson scoring.
+\item \texttt{aorsf-cph}: Identify linear combinations of predictor variables using the coefficients derived from a Cox proportional hazards model.
+That is, use the coefficient estimates derived from completing iterations of Newton Raphson scoring until a convergence threshold is met or the number of iterations completed is 15, whichever occurs first.
+\end{itemize}
 
@@
 
-\subsection{Benchmark of prediction accuracy and computational efficiency}
+\subsection{Benchmark of prediction accuracy and computational efficiency} \label{sec:bm_pred}
 
-\subsubsection{Learners}
+The aim of this numeric experiment is to evaluate and compare the accelerated oblique RSF with its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and with other machine learning algorithms for risk prediction.
+Inferences drawn from this experiment include equivalence and inferiority tests based on Bayesian linear mixed models.
 
-We consider four classes of learners: RFs, boosting ensembles, regression models, and neural networks (Table \ref{table:learners}).
-For RF learners, the number of observations required in terminal nodes was fixed at 10, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500.
-For boosting, regression, and neural network learners, nested cross-validation was applied to tune each model, \ie, assess multiple possible values for relevant model parameters and use the values that optimize the model's estimated prediction accuracy.
+\subsubsection{Learners} \label{sec:learners}
+
+We consider five classes of learners: axis based RSFs, oblique RSFs, boosting ensembles, regression models, and neural networks (\tabref{tab:learners}).
+For each class, we synchronized shared tuning parameters.
+For example, for RSF learners, we set the minimum node size (a parameter shared by all RSF learners) as 10.
+Additionally, for RSF learners, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500.
+For learners that required tuning (\ie, boosting, regression, and neural networks), nested 10-fold cross-validation was applied to tune relevant model parameters.
 Specifically, tuning for boosting models included identifying the number of steps to complete.
@@
 \caption{Learning algorithms assessed in numeric studies}
-\label{table:learners}
+\label{tab:learners}
 \end{table}
@@
 \restoregeometry
-
-\subsubsection{Data sets}
 
@@
 \end{equation} where $\bskap$ is the integrated Brier score when a Kaplan-Meier estimate for survival based on the training data is used as the survival prediction function $\widehat{S}(t)$.
-We refer to this $R^2$ statistic as the index of prediction accuracy and we scale its values by 100 to avoid unnecessary leading zero's.
-For example, we present 25 if $R^2$ is 0.25 and present 10.2 if the difference between two $R^2$ is 0.102.
+We refer to this $R^2$ statistic as the index of prediction accuracy (IPA) \citep{kattan2018index}.
+
+Our secondary metric for evaluating predicted risk is the time-dependent concordance (C)-statistic.
+We compute the first time-dependent C-statistic proposed by \citet[][Equation~3]{blanche2013estimating}, which is interpreted as the probability that a risk prediction model will assign higher risk to a case (\ie, an observation with $T \leq t$ and $\delta = 1$) versus a non-case (\ie, an observation with $T > t$).
+Similar to the IPA, observations with $T \leq t$ and $\delta = 0$ only contribute to inverse proportion of censoring weights for the time-dependent C-statistic.
+
+Both the IPA and time-dependent C-statistic generally take values between 0 and 1.
+To avoid presenting an excessive amount of leading zeroes in our tables, figures, and text, we scale both the IPA and time-dependent C-statistic by 100.
+For example, we present a value of 25 if the IPA is 0.25, 87 if the time-dependent C-statistic is 0.87, and present 10.2 if the difference between two IPA values is 0.102
+
+\subsubsection{Data sets}
+
+We use a collection of \Sexpr{n_data_sets} publicly available data sets to benchmark the prediction accuracy and computational efficiency of the accelerated ORSF and each of the other learners described in \secref{sec:learners}.
+The number of right-censored outcomes per data set ranged from one to four, and the total number of risk prediction tasks we analyzed was \Sexpr{n_risk_tasks} (\tabrefAppendix{tab:datasets}).
+Across all prediction tasks, the number of observations ranged from \Sexpr{nrow_min} to \Sexpr{nrow_max} (median: \Sexpr{nrow_median}), the number of predictors ranged from \Sexpr{ncol_min} to \Sexpr{ncol_max} (median: \Sexpr{ncol_median}), and the percentage of censored observations ranged from \Sexpr{pcens_min} to \Sexpr{pcens_max} (median: \Sexpr{pcens_median}).
+
+\subsubsection{Monte-Carlo cross validation}
+
+For each risk prediction task, we completed \Sexpr{bm_pred_n_runs} runs of Monte-Carlo cross validation.
+In each run, we used a random sample containing 50\% of the available data for training and the remaining 50\% for testing each of the learners described in \secref{sec:learners}.
+Then, for each learner, we computed the IPA, time-dependent C-statistic, and computational time required to fit a prediction model and compute risk predictions.
+If any learner failed to obtain predictions on any particular split of data\footnote{For example, when the prediction task was to predict risk of death in the ACTG 320 clinical trial (26 events total), some splits did not leave enough events in the training data to fit complex learners such as the neural network}, the results for that split were omitted from downstream analyses.
 
@@
 
+After collecting data from \Sexpr{bm_pred_n_runs} replications of Monte-Carlo cross validation for all \Sexpr{n_learners} learners in all \Sexpr{n_risk_tasks} risk prediction tasks, we analyzed the resulting \Sexpr{n_obs_model} observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
+Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using resampling and Bayesian methods.
+Specifically, we fit two models: $$\text{IPA} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}) $$ and $$\text{C-stat} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}).$$ Random intercepts for specific splits of data (\ie, \texttt{run} in the model formula) were nested within datasets.
+The intercept, $\widehat{\gamma}_0$, was the expected value using \texttt{aorsf-fast} so that the coefficients in $\widehat{gamma}$ could be interpreted as expected differences between \texttt{aorsf-fast} and other learners.
+Default priors from \texttt{rstanarm} were applied for model fitting \citep{rstanarm}.
+
+\paragraph{Hypothesis testing} For both the IPA and time-dependent C-statistic, we conducted equivalence and inferiority tests based on a 1 point region of practical equivalence.
+More specifically, we concluded that two learners had practically equivalent IPA or time-dependent C-statistic if there was a 95\% or higher posterior probability that the absolute difference in the relevant metric was less than 1.
+We concluded that one learner was weakly superior when there was $\geq$ 0.95 posterior probability that the difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 0.95 posterior probability that the difference in the relevant metric was 1 or more.
+
+<<>>=
+
+n_wins_aorsf <- bm_pred_viz %>%
+  getElement('ibs_scaled') %>%
+  getElement('rankings') %>%
+  filter(model == 'aorsf_cph_1') %>%
+  pull(n_wins)
+
+ibs_scaled_mean_aorsf <- bm_pred_viz %>%
+  getElement('ibs_scaled') %>%
+  getElement('smry') %>%
+  filter(model == 'aorsf_cph_1',
+         data == 'Overall') %>%
+  mutate(eval = table_value(eval * 100)) %>%
+  pull(eval)
+
+ibs_scaled_aorsf_won_by <- bm_pred_viz %>%
+  getElement('ibs_scaled') %>%
+  getElement('diffs') %>%
+  filter(data == 'Overall') %>%
+  transmute(percent = table_value(pdiff),
+            absolute = table_value(100*adiff)) %>%
+  as.list()
+
+ibs_scaled_aorsf_equiv <- bm_pred_model_viz %>%
+  getElement('data') %>%
+  filter(metric == 'ibs_scaled',
+         model == 'aorsf-cph') %>%
+  pull(prob_equiv)
+
+ibs_scaled_aorsf_sup_min <- bm_pred_model_viz %>%
+  getElement('data') %>%
+  ungroup() %>%
+  filter(metric == 'ibs_scaled',
+         !str_detect(model, '^aorsf')) %>%
+  arrange(desc(median)) %>%
+  slice(1) %>%
+  select(model, prob_super_duper) %>%
+  mutate(model = as.character(model)) %>%
+  as.list()
+
+@
+
 \subsubsection{Results}
 
-<<fig.height=10, fig.width=9, dpi=400>>=
-bm_pred_viz$ibs_scaled
+\paragraph{Index of prediction accuracy}
+
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in \Sexpr{n_wins_aorsf} out of \Sexpr{n_risk_tasks} risk prediction tasks, with an overall mean IPA of \Sexpr{ibs_scaled_mean_aorsf} (Figure \ref{fig:bm_pred_viz_ibs}).
+Compared to the learner with the second highest mean IPA (\texttt{\Sexpr{ibs_scaled_aorsf_sup_min$model}}), \texttt{aorsf-fast}'s mean was \Sexpr{ibs_scaled_aorsf_won_by$absolute} points higher, a relative increase of \Sexpr{ibs_scaled_aorsf_won_by$percent}\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was \Sexpr{ibs_scaled_aorsf_equiv}, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from \Sexpr{ibs_scaled_aorsf_sup_min$prob_super_duper} (versus \texttt{\Sexpr{ibs_scaled_aorsf_sup_min$model}}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+
+<<bm_pred_viz_ibs, fig.height=10, fig.width=9, fig.cap="Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.">>=
+bm_pred_viz$ibs_scaled$fig
 @
 
-<<fig.height=10, fig.width=9, dpi=400>>=
-bm_pred_model_viz$ibs_scaled
+<<bm_pred_model_viz_ibs, fig.height=10, fig.width=9, fig.cap="Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
+A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.">>=
+bm_pred_model_viz$fig$ibs_scaled
 @
 
-\subsection{Benchmark of variable selection}
+\paragraph{Time-dependent concordance statistic}
+
+<<>>=
+
+n_wins_aorsf <- bm_pred_viz %>%
+  getElement('cstat') %>%
+  getElement('rankings') %>%
+  filter(model == 'aorsf_cph_1') %>%
+  pull(n_wins)
+
+cstat_mean_aorsf <- bm_pred_viz %>%
+  getElement('cstat') %>%
+  getElement('smry') %>%
+  filter(model == 'aorsf_cph_1',
+         data == 'Overall') %>%
+  mutate(eval = table_value(eval * 100)) %>%
+  pull(eval)
+
+cstat_aorsf_won_by <- bm_pred_viz %>%
+  getElement('cstat') %>%
+  getElement('diffs') %>%
+  filter(data == 'Overall') %>%
+  transmute(percent = table_value(pdiff),
+            absolute = table_value(100*adiff)) %>%
+  as.list()
+
+cstat_aorsf_equiv <- bm_pred_model_viz %>%
+  getElement('data') %>%
+  filter(metric == 'cstat',
+         model == 'aorsf-cph') %>%
+  pull(prob_equiv)
+
+cstat_aorsf_sup_min <- bm_pred_model_viz %>%
+  getElement('data') %>%
+  ungroup() %>%
+  filter(metric == 'cstat',
+         !str_detect(model, '^aorsf')) %>%
+  arrange(desc(median)) %>%
+  slice(1) %>%
+  select(model, prob_super_duper) %>%
+  mutate(model = as.character(model)) %>%
+  as.list()
+
+@
+
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in \Sexpr{n_wins_aorsf} out of \Sexpr{n_risk_tasks} risk prediction tasks, with an overall mean of \Sexpr{cstat_mean_aorsf} (Figure \ref{fig:bm_pred_viz_cstat}).
+Compared to the learner with the second highest mean C-statistic (\texttt{\Sexpr{cstat_aorsf_sup_min$model}}), \texttt{aorsf-fast}'s mean was \Sexpr{cstat_aorsf_won_by$absolute} points higher, a relative increase of \Sexpr{cstat_aorsf_won_by$percent}\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was \Sexpr{cstat_aorsf_equiv}, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from \Sexpr{cstat_aorsf_sup_min$prob_super_duper} (versus \texttt{\Sexpr{cstat_aorsf_sup_min$model}}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+
+<<bm_pred_viz_cstat, fig.height=10, fig.width=9, fig.cap="Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.">>=
+bm_pred_viz$cstat$fig
+@
+
+<<bm_pred_model_viz_cstat, fig.height=10, fig.width=9, fig.cap="Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms.
+A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.">>=
+bm_pred_model_viz$fig$cstat
+@
+
+\paragraph{Computational efficiency}
+
+Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 1/2 second longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+Compared to its predecessor, \texttt{obliqueRSF-net}, \texttt{aorsf-fast} was XYZ times faster.
+
+<<bm_pred_time, fig.height=10, fig.width=9, fig.cap="Distribution of time taken to fit a prediction model and compute predicted risk.
+The median time, in seconds, is printed and annotated for each learner by a vertical line.">>=
+bm_pred_time_viz$fig
+@
+
+\subsection{Benchmark of variable importance}
+
+The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between variables that do or do not have a relationship with a simulated outcome.
+We consider methods that are intrinsic to the oblique RF (\eg ANOVA VI), those that are intrinsic to the RF (\eg permutation VI), and those that are model-agnostic (\eg SHAP VI).
+
+\subsubsection{Variable importance techniques}
+
+We compute permutation VI for axis based RSFs using the \texttt{randomForestSRC} package.
+Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
+Therefore, it is not incorporated in the current simulation study.
+We compute ANOVA VI, negation VI, and permutation VI for oblique RSFs using the \texttt{aorsf} package.
+For ANOVA VI, we applied a p-value threshold of 0.01, following the threshold recommended by \citet{menze2011oblique}.
+We compute SHAP VI for boosted tree models using the \texttt{xgboost} package, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
+We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
+
+\subsubsection{Variable types}
+
+We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome. Specifically, \begin{itemize}
+\item \textit{irrelevant} variables had no relationship with the outcome.
+\item \textit{main effect} variables had a linear relationship to the outcome.
+\item \textit{non-linear effect} variables had a non-linear relationship to the outcome.
+\item \textit{combination effect} variables were formed by linear combinations of three other variables.
+While their combination was linearly related to the outcome, each of the three variables contributing to the combination had no relation to the outcome.
+\item \textit{interaction effect} variables were related to the outcome by multiplicative interaction with one other variable, which could have been a main effect, non-linear effect, or combination effect variable.
+\end{itemize}
+
+\subsubsection{Simulated data}
+
+We initiated each set of simulated data with a random draw of size $n$ from a $p$-dimensional multivariate normal distribution, yielding $n$ observations of $p$ predictors.
+Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
+A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package.
+The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
+Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be valuated based on their ability to detect these effects.
+
+\subsubsection{Parameter specifications}
+
+Parameters that varied in the current simulation study included the number of observations (1000, 3000, and 5000) and the minimum and maximum correlation between predictors (-0.1 to 0.1, -0.3 to 0.3, and -0.5 to 0.5).
+Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor, with an increase of one standard deviation associated with a 64\% increase in relative risk.
+
+\subsubsection{Evaluation of variable importance}
+
+We compared VI techniques based on their discrimination (\ie C-statistic) between relevant and irrelevant variables.
+Specifically, we generated a binary outcome for each predictor variable based on its relevance (\ie, the binary outcome is 1 if the variable is relevant, 0 otherwise).
+Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic is interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
+
+\subsubsection{Results}
+
+\section{Discussion}
+
+In this paper, we have developed two contributions to the oblique RSF: (1) the accelerated oblique RSF (\ie, \texttt{aorsf-fast}) and (2) negation VI.
+Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
+In numeric experiments, we found that that \texttt{aorsf-fast} is orders of magnitude more efficient and just as accurate in risk prediction tasks compared to its predecessor, \texttt{obliqueRSF-net}.
+We also found several cases where negation VI allows oblique RSF models to discriminate between relevant and irrelevant variables more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
+Our results favored negation VI in scenarios where oblique RSFs were the underlying model used to compute VI and also in scenarios where other modeling techniques (\eg, boosted tree ensembles) were used.
+
+\subsection{Implications of our results}
+
+Accurate risk prediction models have the potential to improve healthcare by directing timely interventions to patients who are most likely to benefit.
+However, prediction models that cannot be interpreted and explained have no place in clinical practice.
+The current study advances the oblique RSF, an accurate risk prediction model, several steps towards being an accurate \textit{and} interpretable risk prediction model.
+The improved computational efficiency of the accelerated oblique RSF increases the feasibility of applying model-agnostic methods (\eg, SHAP values) for interpretation.
+Faster model evaluation and re-fitting also improve diagnosis and resolution of model-based issues (\eg, model calibration deteriorates over time).
+The introduction of negation VI also advances interpretability.
+VI is intrinsically linked to model fairness, as it can be used to identify when protected characteristics such as race, religion, and sexuality are inadvertently used (either directly or through correlates of these characteristics) by a prediction model.
+Since negation VI  engages with the coefficients used in linear combinations of variables, a major component of oblique RSFs, it may be more capable of diagnosing unfairness in oblique RSFs compared to permutation importance and model-agnostic VI techniques.\footnote{In our numeric experiments, negation VI's out-performance of other methods was most pronounced in smaller samples, giving some evidence supporting this hypothesis.} Three additional consequences of engaging with coefficients in linear combinations of predictors is that negation VI \begin{enumerate}
+\item is non-random and hence reproducible without setting a random seed (a limitation of permutation importance)
+\item does not incur bias from permutation of variables into unlikely or impossible combinations (a limitation of permutation importance).
+\item can be applied to any type of oblique RF (a limitation of ANOVA importance, which can only be applied when p-values are calculable within nodes).
+\end{enumerate} These characteristics suggest negation VI can be developed into a general tool for interpretation of oblique RFs.
+
+\subsection{Limitations and next steps}
+
+The current study has several limitations.
+The accelerated oblique RSF does not account for competing risks, and so our benchmark of prediction accuracy divided tasks where competing risks were present into event-specific tasks.
+Biased estimation of incidence may occur when competing risks are ignored, and allowing the oblique RSF to account for competing risks is a high priority for future studies.
+In addition, missing data are not addressed in the accelerated oblique RSF, and users are expected to impute missing values before passing training or testing data into exported functions from the \texttt{aorsf} R package.
+However, missing data are common and it is standard for ensemble tree methods to handle missing data during the tree growing procedure.
+Thus, a second item of high priority for future studies is to develop and evaluate strategies to handle missing data while growing an oblique RSF.
 
@@
 \appendix
-\section*{Appendix A.}
 
-<<fig.height=10, fig.width=9, dpi=400>>=
-bm_pred_viz$cstat
+\section*{Appendix}
+\captionsetup{labelformat=AppendixTables}
+\setcounter{table}{0}
+
+<<>>=
+
+data_key_tbl <- data_key %>%
+  group_by(label) %>%
+  mutate(nrow = min(nrow),
+         ncol = min(ncol)) %>%
+  ungroup()
+
+data_key_tbl %>%
+  select(label, nrow, ncol, outcome, nevent, pcens) %>%
+  mutate(across(starts_with('p'), ~ .x * 100),
+         across(starts_with("n"), as.integer),
+         across(where(is.numeric), table_value),
+         across(where(is.character), str_replace, '0.000', '0'),
+         outcome = recode(
+           outcome,
+           'HF' = 'heart failure',
+           'CVD death' = 'cardiovascular death'),
+         outcome = str_to_title(outcome),
+         outcome = recode(outcome,
+                          'Gross 1m Usd' = 'Gross 1M USD',
+                          "Aids Diagnosis" ='AIDS Diagnosis')) %>%
+  kable(
+    col.names = c(
+      'Label',
+      'N observations',
+      'N predictors',
+      'Outcome',
+      "N Events",
+      '% Censored'
+    ),
+    align = 'lcclcc',
+    booktabs=TRUE,
+    longtable=TRUE,
+    format = 'latex',
+    caption = "Data sets used for numeric experiments \\label{tab:datasets}"
+  ) %>%
+  collapse_rows(columns=1:3) %>%
+  # pack_rows(index = indents,
+  #           italic = TRUE,
+  #           hline_before = TRUE,
+  #           hline_after = TRUE) %>%
+  kable_styling() %>%
+  landscape()
+
 @
@@
 
-results_overall <- bm_pred_comb |>
+results_overall <- bm_pred_clean |>
   group_by(model) |>
@@
 
-data_tbl <- bm_pred_comb |>
+data_tbl <- bm_pred_clean |>
   group_by(model, data) |>
@@
   # ) |>
-  group_by(data) |>
-  mutate(
-    across(.cols = starts_with("time"), .fns = as.numeric),
-    time_fit_ratio = time_fit_median /
-      time_fit_median[model == 'aorsf_cph_1'],
-    time_pred_ratio = time_pred_median /
-      time_pred_median[model == 'aorsf_cph_1']
-  ) |>
-  ungroup() |>
   arrange(data, desc(ibs_scaled_mean)) |>
@@
     time_fit_median = format(round(time_fit_median, 3), nsmall = 3),
-    time_fit_ratio = table_value(time_fit_ratio),
-    time_pred_median = format(round(time_pred_median, 3), nsmall = 3),
-    time_pred_ratio = table_value(time_pred_ratio)
+    time_pred_median = format(round(time_pred_median, 3), nsmall = 3)
   ) |>
@@
                       'C-Statistic',
-                      'Median',
-                      'Ratio',
-                      'Median',
-                      'Ratio'),
-        align = 'lcc') |>
+                      'Model fitting',
+                      'Risk prediction'),
+        align = 'lcc',
+        caption = "Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.") |>
   pack_rows(index = indents,
@@
                               "Performance metric (SD)" = 2,
-                              "Fit model" = 2,
-                              "Predict risk" = 2)) |>
-  add_header_above(header = c(" " = 3,
-                              "Computing time, seconds" = 4))
+                              "Computation time, seconds" = 2))
 

### 2022-06-29 paper/jmlr/main.tex
results for VI; viz in prog

@@
 \newcommand{\secref}[1]{Section \ref{#1}}
+
+\newcommand{\tabref}[1]{Table \ref{#1}}
+\newcommand{\tabrefAppendix}[1]{Table A.\ref{#1}}
 
@@
 The aim of this article is to improve the computational efficiency and interpretability of the oblique RSF.
-In a general benchmark experiment including YYYY risk prediction tasks, we show that oblique RSFs with partially trained models have equivalent or superior prediction accuracy and are orders of magnitude more efficient than oblique RSFs with fully trained models in non-leaf nodes.
+In a general benchmark experiment including 31 risk prediction tasks, we show that oblique RSFs with partially trained models have equivalent or superior prediction accuracy and are orders of magnitude more efficient than oblique RSFs with fully trained models in non-leaf nodes.
 We introduce a method to estimate VI for oblique RSFs and compare its ability to discriminate between signal and noise variables versus standard and state-of-the-art methods.
@@
 
-\subsection{Benchmark of prediction accuracy and computational efficiency}
+\subsection{Benchmark of prediction accuracy and computational efficiency} \label{sec:bm_pred}
 
 The aim of this numeric experiment is to evaluate and compare the accelerated oblique RSF with its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and with other machine learning algorithms for risk prediction.
-Inferences drawn from this experiment include equivalence and inferiority tests based on Bayesian hierarchical models.
+Inferences drawn from this experiment include equivalence and inferiority tests based on Bayesian linear mixed models.
 
@@
 
-We consider four classes of learners: RFs, boosting ensembles, regression models, and neural networks (Table \ref{table:learners}).
-For RF learners, the number of observations required in terminal nodes was fixed at 10, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500.
-For boosting, regression, and neural network learners, nested cross-validation was applied to tune each model, \ie, assess multiple possible values for relevant model parameters and use the values that optimize the model's estimated prediction accuracy.
+We consider five classes of learners: axis based RSFs, oblique RSFs, boosting ensembles, regression models, and neural networks (\tabref{tab:learners}).
+For each class, we synchronized shared tuning parameters.
+For example, for RSF learners, we set the minimum node size (a parameter shared by all RSF learners) as 10.
+Additionally, for RSF learners, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500.
+For learners that required tuning (\ie, boosting, regression, and neural networks), nested 10-fold cross-validation was applied to tune relevant model parameters.
 Specifically, tuning for boosting models included identifying the number of steps to complete.
@@
 \end{equation} where $\bskap$ is the integrated Brier score when a Kaplan-Meier estimate for survival based on the training data is used as the survival prediction function $\widehat{S}(t)$.
-We refer to this $R^2$ statistic as the index of prediction accuracy \citep{kattan2018index} and we scale its values by 100 to avoid unnecessary leading zero's.
-For example, we present 25 if $R^2$ is 0.25 and present 10.2 if the difference between two $R^2$ is 0.102.
+We refer to this $R^2$ statistic as the index of prediction accuracy (IPA) \citep{kattan2018index}.
 
 Our secondary metric for evaluating predicted risk is the time-dependent concordance (C)-statistic.
-Briefly, we compute the time-dependent C-statistic proposed by \citet{blanche2013estimating}, which is interpreted as the probability that a risk prediction model will assign higher risk to a case (\ie, an observation with $T \leq t$ and $\delta = 1$) versus a non-case (\ie, an observation with $T > t$).
-Similar to the index of prediction accuracy, observations with $T \leq t$ and $\delta = 0$ only contribute to inverse proportion of censoring weights.
+We compute the first time-dependent C-statistic proposed by \citet[][Equation~3]{blanche2013estimating}, which is interpreted as the probability that a risk prediction model will assign higher risk to a case (\ie, an observation with $T \leq t$ and $\delta = 1$) versus a non-case (\ie, an observation with $T > t$).
+Similar to the IPA, observations with $T \leq t$ and $\delta = 0$ only contribute to inverse proportion of censoring weights for the time-dependent C-statistic.
+
+Both the IPA and time-dependent C-statistic generally take values between 0 and 1.
+To avoid presenting an excessive amount of leading zeroes in our tables, figures, and text, we scale both the IPA and time-dependent C-statistic by 100.
+For example, we present a value of 25 if the IPA is 0.25, 87 if the time-dependent C-statistic is 0.87, and present 10.2 if the difference between two IPA values is 0.102
 
@@
 
-We use a collection of publicly available data sets to benchmark the prediction accuracy and computational efficiency of the accelerated ORSF and each of the other learners described in \secref{sec:learners}
+We use a collection of 18 publicly available data sets to benchmark the prediction accuracy and computational efficiency of the accelerated ORSF and each of the other learners described in \secref{sec:learners}.
+The number of right-censored outcomes per data set ranged from one to four, and the total number of risk prediction tasks we analyzed was 31 (\tabrefAppendix{tab:datasets}).
+Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 2,231), the number of predictors ranged from 7 to 1,692 (median: 41), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 78.2).
+
+\subsubsection{Monte-Carlo cross validation}
+
+For each risk prediction task, we completed 10 runs of Monte-Carlo cross validation.
+In each run, we used a random sample containing 50\% of the available data for training and the remaining 50\% for testing each of the learners described in \secref{sec:learners}.
+Then, for each learner, we computed the IPA, time-dependent C-statistic, and computational time required to fit a prediction model and compute risk predictions.
+If any learner failed to obtain predictions on any particular split of data\footnote{For example, when the prediction task was to predict risk of death in the ACTG 320 clinical trial (26 events total), some splits did not leave enough events in the training data to fit complex learners such as the neural network}, the results for that split were omitted from downstream analyses.
 
@@
 
+After collecting data from 10 replications of Monte-Carlo cross validation for all 14 learners in all 31 risk prediction tasks, we analyzed the resulting 4,340 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
+Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using resampling and Bayesian methods.
+Specifically, we fit two models: $$\text{IPA} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}) $$ and $$\text{C-stat} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}).$$ Random intercepts for specific splits of data (\ie, \texttt{run} in the model formula) were nested within datasets.
+The intercept, $\widehat{\gamma}_0$, was the expected value using \texttt{aorsf-fast} so that the coefficients in $\widehat{gamma}$ could be interpreted as expected differences between \texttt{aorsf-fast} and other learners.
+Default priors from \texttt{rstanarm} were applied for model fitting \citep{rstanarm}.
+
+\paragraph{Hypothesis testing} For both the IPA and time-dependent C-statistic, we conducted equivalence and inferiority tests based on a 1 point region of practical equivalence.
+More specifically, we concluded that two learners had practically equivalent IPA or time-dependent C-statistic if there was a 95\% or higher posterior probability that the absolute difference in the relevant metric was less than 1.
+We concluded that one learner was weakly superior when there was $\geq$ 0.95 posterior probability that the difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 0.95 posterior probability that the difference in the relevant metric was 1 or more.
+
 \subsubsection{Results}
 
+\paragraph{Index of prediction accuracy}
+
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in  out of 31 risk prediction tasks, with an overall mean IPA of  (Figure \ref{fig:bm_pred_viz_ibs}).
+Compared to the learner with the second highest mean IPA (\texttt{rsf-standard}), \texttt{aorsf-fast}'s mean was 1.21 points higher, a relative increase of 9.98\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.97, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.65 (versus \texttt{rsf-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-2-1} 
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_viz_ibs-1} \caption[Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks]{Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.}\label{fig:bm_pred_viz_ibs}
+\end{figure}
+
 \end{knitrout}
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-3-1} 
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_model_viz_ibs-1} \caption[Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms]{Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
+A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.}\label{fig:bm_pred_model_viz_ibs}
+\end{figure}
+
 \end{knitrout}
 
+\paragraph{Time-dependent concordance statistic}
+
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in  out of 31 risk prediction tasks, with an overall mean of  (Figure \ref{fig:bm_pred_viz_cstat}).
+Compared to the learner with the second highest mean C-statistic (\texttt{obliqueRSF-net}), \texttt{aorsf-fast}'s mean was 0.681 points higher, a relative increase of 0.887\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.01 (versus \texttt{obliqueRSF-net}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_viz_cstat-1} \caption[Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks]{Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.}\label{fig:bm_pred_viz_cstat}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_model_viz_cstat-1} \caption[Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms]{Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms.
+A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.}\label{fig:bm_pred_model_viz_cstat}
+\end{figure}
+
+\end{knitrout}
+
+\paragraph{Computational efficiency}
+
+Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 1/2 second longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+Compared to its predecessor, \texttt{obliqueRSF-net}, \texttt{aorsf-fast} was XYZ times faster.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_time-1} \caption[Distribution of time taken to fit a prediction model and compute predicted risk]{Distribution of time taken to fit a prediction model and compute predicted risk.
+The median time, in seconds, is printed and annotated for each learner by a vertical line.}\label{fig:bm_pred_time}
+\end{figure}
+
+\end{knitrout}
+
 \subsection{Benchmark of variable importance}
 
-The aim of this numeric experiment is to compare negation VI to existing methods for VI.
+The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between variables that do or do not have a relationship with a simulated outcome.
 We consider methods that are intrinsic to the oblique RF (\eg ANOVA VI), those that are intrinsic to the RF (\eg permutation VI), and those that are model-agnostic (\eg SHAP VI).
-All methods are evaluated based on their ability to discriminate between variables that are related to a censored outcome versus those that are not related to it.
 
@@
 
-We compute permutation VI using the \texttt{randomForestSRC} package.
+We compute permutation VI for axis based RSFs using the \texttt{randomForestSRC} package.
 Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
-Therefore, it is not incorporated in the current study's numeric experiments.
-We compute ANOVA VI using the \texttt{aorsf} package, applying a p-value threshold of 0.01 as recommended by \citet{menze2011oblique}.
-We compute SHAP VI for boosted tree models using the \texttt{xgboost} package and also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
+Therefore, it is not incorporated in the current simulation study.
+We compute ANOVA VI, negation VI, and permutation VI for oblique RSFs using the \texttt{aorsf} package.
+For ANOVA VI, we applied a p-value threshold of 0.01, following the threshold recommended by \citet{menze2011oblique}.
+We compute SHAP VI for boosted tree models using the \texttt{xgboost} package, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
+We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
 
@@
 
-We considered five classes of predictor variable, with each class characterized by its variables' relationship to a right-censored outcome. Specifically, \begin{itemize}
-\item \textit{junk} variables had no relationship with the outcome.
-\item \textit{main effect} variables were linearly related to the outcome
-\item \textit{non-linear effect} variables had a sinusoidal relationship to the outcome
-\item \textit{combination effect} variables had no direct relationship to the outcome.
-However, latent variables formed by combining the observed combination effects have a linear relationship to the outcome.
-\item \textit{interaction effect} variables related to the outcome by multiplicative interaction with one other variable.
+We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome. Specifically, \begin{itemize}
+\item \textit{irrelevant} variables had no relationship with the outcome.
+\item \textit{main effect} variables had a linear relationship to the outcome.
+\item \textit{non-linear effect} variables had a non-linear relationship to the outcome.
+\item \textit{combination effect} variables were formed by linear combinations of three other variables.
+While their combination was linearly related to the outcome, each of the three variables contributing to the combination had no relation to the outcome.
+\item \textit{interaction effect} variables were related to the outcome by multiplicative interaction with one other variable, which could have been a main effect, non-linear effect, or combination effect variable.
 \end{itemize}
 
-the variables have (1) no effect, (2) linear effect, (3) non-linear effect, (4) conditional linear effect, (5) combination linear effect, or (6) categorical effect on the outcome.
-Each conditional linear variable has an effect on the outcome that is modified by the value of one linear effect variable.
-Combination linear effect variables contribute to latent variables that are linearly related to the outcome.
-Categorical effect variables have 3 unique values, each with a different expected risk for the event of interest.
-
 \subsubsection{Simulated data}
 
+We initiated each set of simulated data with a random draw of size $n$ from a $p$-dimensional multivariate normal distribution, yielding $n$ observations of $p$ predictors.
+Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
+A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package.
+The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
+Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be valuated based on their ability to detect these effects.
+
+\subsubsection{Parameter specifications}
+
+Parameters that varied in the current simulation study included the number of observations (1000, 3000, and 5000) and the minimum and maximum correlation between predictors (-0.1 to 0.1, -0.3 to 0.3, and -0.5 to 0.5).
+Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor, with an increase of one standard deviation associated with a 64\% increase in relative risk.
+
 \subsubsection{Evaluation of variable importance}
 
+We compared VI techniques based on their discrimination (\ie C-statistic) between relevant and irrelevant variables.
+Specifically, we generated a binary outcome for each predictor variable based on its relevance (\ie, the binary outcome is 1 if the variable is relevant, 0 otherwise).
+Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic is interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
+
 \subsubsection{Results}
+
+\section{Discussion}
+
+In this paper, we have developed two contributions to the oblique RSF: (1) the accelerated oblique RSF (\ie, \texttt{aorsf-fast}) and (2) negation VI.
+Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
+In numeric experiments, we found that that \texttt{aorsf-fast} is orders of magnitude more efficient and just as accurate in risk prediction tasks compared to its predecessor, \texttt{obliqueRSF-net}.
+We also found several cases where negation VI allows oblique RSF models to discriminate between relevant and irrelevant variables more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
+Our results favored negation VI in scenarios where oblique RSFs were the underlying model used to compute VI and also in scenarios where other modeling techniques (\eg, boosted tree ensembles) were used.
+
+\subsection{Implications of our results}
+
+Accurate risk prediction models have the potential to improve healthcare by directing timely interventions to patients who are most likely to benefit.
+However, prediction models that cannot be interpreted and explained have no place in clinical practice.
+The current study advances the oblique RSF, an accurate risk prediction model, several steps towards being an accurate \textit{and} interpretable risk prediction model.
+The improved computational efficiency of the accelerated oblique RSF increases the feasibility of applying model-agnostic methods (\eg, SHAP values) for interpretation.
+Faster model evaluation and re-fitting also improve diagnosis and resolution of model-based issues (\eg, model calibration deteriorates over time).
+The introduction of negation VI also advances interpretability.
+VI is intrinsically linked to model fairness, as it can be used to identify when protected characteristics such as race, religion, and sexuality are inadvertently used (either directly or through correlates of these characteristics) by a prediction model.
+Since negation VI  engages with the coefficients used in linear combinations of variables, a major component of oblique RSFs, it may be more capable of diagnosing unfairness in oblique RSFs compared to permutation importance and model-agnostic VI techniques.\footnote{In our numeric experiments, negation VI's out-performance of other methods was most pronounced in smaller samples, giving some evidence supporting this hypothesis.} Three additional consequences of engaging with coefficients in linear combinations of predictors is that negation VI \begin{enumerate}
+\item is non-random and hence reproducible without setting a random seed (a limitation of permutation importance)
+\item does not incur bias from permutation of variables into unlikely or impossible combinations (a limitation of permutation importance).
+\item can be applied to any type of oblique RF (a limitation of ANOVA importance, which can only be applied when p-values are calculable within nodes).
+\end{enumerate} These characteristics suggest negation VI can be developed into a general tool for interpretation of oblique RFs.
+
+\subsection{Limitations and next steps}
+
+The current study has several limitations.
+The accelerated oblique RSF does not account for competing risks, and so our benchmark of prediction accuracy divided tasks where competing risks were present into event-specific tasks.
+Biased estimation of incidence may occur when competing risks are ignored, and allowing the oblique RSF to account for competing risks is a high priority for future studies.
+In addition, missing data are not addressed in the accelerated oblique RSF, and users are expected to impute missing values before passing training or testing data into exported functions from the \texttt{aorsf} R package.
+However, missing data are common and it is standard for ensemble tree methods to handle missing data during the tree growing procedure.
+Thus, a second item of high priority for future studies is to develop and evaluate strategies to handle missing data while growing an oblique RSF.
 
@@
 \appendix
-\section*{Appendix A.}
+
+\section*{Appendix}
+\captionsetup{labelformat=AppendixTables}
+\setcounter{table}{0}
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-4-1} 
+\begin{landscape}
+\begin{longtable}[t]{lcclcc}
+\caption{\label{tab:unnamed-chunk-4}Data sets used for numeric experiments \label{tab:datasets}}\\
+\toprule
+Label & N observations & N predictors & Outcome & N Events & \% Censored\\
+\midrule
+VA lung cancer trial & 137 & 8 & Death & 128 & 6.57\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Recurrence & 468 & 49.6\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash Colon cancer} & \multirow{-2}{*}{\centering\arraybackslash 929} & \multirow{-2}{*}{\centering\arraybackslash 12} & Death & 452 & 51.3\\
+\cmidrule{1-6}\pagebreak[0]
+Primary biliary cholangitis & 276 & 19 & Death & 111 & 59.8\\
+\cmidrule{1-6}\pagebreak[0]
+Movies released in 2015-2018 & 551 & 46 & Gross 1M USD & 522 & 5.26\\
+\cmidrule{1-6}\pagebreak[0]
+GBSG II & 686 & 10 & Recurrence Or Death & 299 & 56.4\\
+\cmidrule{1-6}\pagebreak[0]
+Systolic Heart Failure & 2,231 & 41 & Death & 726 & 67.5\\
+\cmidrule{1-6}\pagebreak[0]
+Serum free light chain & 7,874 & 10 & Death & 2,169 & 72.5\\
+\cmidrule{1-6}\pagebreak[0]
+Non-alcohol fatty liver disease & 17,549 & 24 & Death & 1,364 & 92.2\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Recurrence & 1,518 & 49.1\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash Rotterdam tumor bank} & \multirow{-2}{*}{\centering\arraybackslash 2,982} & \multirow{-2}{*}{\centering\arraybackslash 11} & Death & 1,272 & 57.3\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & AIDS Diagnosis & 96 & 91.7\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash ACTG 320} & \multirow{-2}{*}{\centering\arraybackslash 1,151} & \multirow{-2}{*}{\centering\arraybackslash 12} & Death & 26 & 97.7\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Cardiovascular Death & 110 & 87.7\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash GUIDE-IT} & \multirow{-2}{*}{\centering\arraybackslash 894} & \multirow{-2}{*}{\centering\arraybackslash 59} & Hf Hospitalization & 288 & 67.8\\
+\cmidrule{1-6}\pagebreak[0]
+Early breast cancer & 614 & 1,692 & Recurrence Or Death & 134 & 78.2\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Cardiovascular Death & 521 & 94.4\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash SPRINT} & \multirow{-2}{*}{\centering\arraybackslash 9,361} & \multirow{-2}{*}{\centering\arraybackslash 174} & Death & 1,644 & 82.4\\
+\cmidrule{1-6}\pagebreak[0]
+Heart Transplant & 3,787 & 52 & Graft-Loss Or Death & 500 & 86.8\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Death & 76 & 86.0\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash FCL} & \multirow{-2}{*}{\centering\arraybackslash 541} & \multirow{-2}{*}{\centering\arraybackslash 7} & Relapse & 272 & 49.7\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Death & 963 & 30.4\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash Monoclonal gammopathy} & \multirow{-2}{*}{\centering\arraybackslash 1,384} & \multirow{-2}{*}{\centering\arraybackslash 8} & Malignancy & 115 & 91.7\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Heart Failure & 339 & 95.0\\
+\cmidrule{4-6}\nopagebreak
+ &  &  & Coronary Heart Disease & 439 & 93.5\\
+\cmidrule{4-6}\nopagebreak
+ &  &  & Stroke & 292 & 95.7\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-4}{*}{\raggedright\arraybackslash MESA} & \multirow{-4}{*}{\centering\arraybackslash 6,783} & \multirow{-4}{*}{\centering\arraybackslash 48} & Death & 1,297 & 80.9\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Heart Failure & 2,981 & 78.1\\
+\cmidrule{4-6}\nopagebreak
+ &  &  & Coronary Heart Disease & 2,282 & 83.2\\
+\cmidrule{4-6}\nopagebreak
+ &  &  & Stroke & 1,323 & 90.3\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-4}{*}{\raggedright\arraybackslash ARIC} & \multirow{-4}{*}{\centering\arraybackslash 13,623} & \multirow{-4}{*}{\centering\arraybackslash 41} & Death & 6,662 & 51.1\\
+\bottomrule
+\end{longtable}
+\end{landscape}
+
 \end{knitrout}
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\begin{longtable}{lcclccl}
+\begin{longtable}[t]{lcclc}
+\caption{\label{tab:unnamed-chunk-5}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.}\\
 \toprule
-\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Computing time, seconds} \\
-\cmidrule(l{3pt}r{3pt}){4-7}
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Performance metric (SD)} & \multicolumn{2}{c}{Fit model} & \multicolumn{2}{c}{Predict risk} \\
-\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
-  & Scaled Brier & C-Statistic & Median & Ratio & Median & Ratio\\
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Performance metric (SD)} & \multicolumn{2}{c}{Computation time, seconds} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
+  & Scaled Brier & C-Statistic & Model fitting & Risk prediction\\
 \midrule
 \endfirsthead
-\multicolumn{7}{@{}l}{\textit{(continued)}}\\
+\caption[]{Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.
+\textit{(continued)}}\\
 \toprule
-  & Scaled Brier & C-Statistic & Median & Ratio & Median & Ratio\\
+  & Scaled Brier & C-Statistic & Model fitting & Risk prediction\\
 \midrule
@@
 \hline
-\multicolumn{7}{l}{\textit{\textbf{Overall}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.132 (0.114) & 0.773 (0.071) & 0.776 & 1.00 & 0.282 & 1.00\\
-\hspace{1em}rsf-standard & 0.120 (0.117) & 0.759 (0.075) & 2.016 & 2.60 & 0.444 & 1.57\\
-\hspace{1em}cif-standard & 0.119 (0.101) & 0.766 (0.069) & 4.663 & 6.01 & 18.044 & 63.9\\
-\hspace{1em}cif-rotate & 0.119 (0.130) & 0.757 (0.080) & 40.258 & 51.9 & 27.552 & 97.6\\
-\hspace{1em}glmnet-cox & 0.114 (0.124) & 0.759 (0.076) & 0.737 & 0.949 & 0.008 & 0.028\\
-\hspace{1em}xgboost-cox & 0.072 (0.103) & 0.754 (0.089) & 4.296 & 5.54 & 0.009 & 0.032\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{ACTG 320; AIDS diagnosis, n = 1151, p = 12}}}\\
-\hline
-\hspace{1em}cif-standard & 0.024 (0.031) & 0.744 (0.040) & 1.580 & 10.7 & 3.948 & 116.0\\
-\hspace{1em}aorsf-fast & 0.024 (0.028) & 0.745 (0.044) & 0.147 & 1.00 & 0.034 & 1.00\\
-\hspace{1em}glmnet-cox & 0.016 (0.030) & 0.746 (0.037) & 0.161 & 1.10 & 0.002 & 0.059\\
-\hspace{1em}rsf-standard & 0.005 (0.041) & 0.730 (0.042) & 0.142 & 0.963 & 0.063 & 1.84\\
-\hspace{1em}cif-rotate & 0.004 (0.040) & 0.731 (0.038) & 15.182 & 103.2 & 4.149 & 121.9\\
-\hspace{1em}xgboost-cox & 0.000 (0.044) & 0.751 (0.033) & 3.630 & 24.7 & 0.003 & 0.088\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{ACTG 320; death, n = 1151, p = 12}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.010 (0.020) & 0.834 (0.057) & 0.088 & 1.00 & 0.020 & 1.00\\
-\hspace{1em}cif-standard & -0.001 (0.025) & 0.788 (0.061) & 1.589 & 18.1 & 3.861 & 192.9\\
-\hspace{1em}xgboost-cox & -0.003 (0.004) & 0.500 (0.000) & 0.112 & 1.28 & 0.002 & 0.100\\
-\hspace{1em}rsf-standard & -0.022 (0.053) & 0.787 (0.071) & 0.084 & 0.960 & 0.035 & 1.75\\
-\hspace{1em}cif-rotate & -0.031 (0.048) & 0.714 (0.084) & 13.331 & 152.2 & 3.293 & 164.5\\
-\hspace{1em}glmnet-cox & -0.053 (0.092) & 0.736 (0.110) & 0.262 & 2.99 & 0.002 & 0.100\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{ARIC; coronary heart disease, n = 13626, p = 31}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.160 (0.008) & 0.810 (0.007) & 4.995 & 1.00 & 16.402 & 1.00\\
-\hspace{1em}rsf-standard & 0.156 (0.008) & 0.803 (0.007) & 11.043 & 2.21 & 1.245 & 0.076\\
-\hspace{1em}cif-standard & 0.134 (0.006) & 0.806 (0.007) & 68.008 & 13.6 & 441.507 & 26.9\\
-\hspace{1em}glmnet-cox & 0.124 (0.016) & 0.793 (0.009) & 1.354 & 0.271 & 0.822 & 0.050\\
-\hspace{1em}cif-rotate & 0.105 (0.003) & 0.783 (0.008) & 412.625 & 82.6 & 251.226 & 15.3\\
-\hspace{1em}xgboost-cox & 0.058 (0.016) & 0.811 (0.007) & 10.324 & 2.07 & 1.073 & 0.065\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{ARIC; death, n = 13626, p = 31}}}\\
-\hline
-\hspace{1em}rsf-standard & 0.214 (0.007) & 0.785 (0.004) & 16.361 & 1.72 & 1.636 & 0.018\\
-\hspace{1em}aorsf-fast & 0.211 (0.008) & 0.786 (0.005) & 9.521 & 1.00 & 92.722 & 1.00\\
-\hspace{1em}cif-standard & 0.201 (0.005) & 0.784 (0.005) & 66.585 & 6.99 & 585.928 & 6.32\\
-\hspace{1em}glmnet-cox & 0.181 (0.019) & 0.770 (0.008) & 2.555 & 0.268 & 1.142 & 0.012\\
-\hspace{1em}cif-rotate & 0.150 (0.008) & 0.753 (0.007) & 427.333 & 44.9 & 524.889 & 5.66\\
-\hspace{1em}xgboost-cox & 0.123 (0.006) & 0.789 (0.004) & 10.891 & 1.14 & 1.028 & 0.011\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{ARIC; heart failure, n = 13626, p = 31}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.236 (0.008) & 0.839 (0.006) & 5.758 & 1.00 & 21.727 & 1.00\\
-\hspace{1em}rsf-standard & 0.232 (0.009) & 0.833 (0.006) & 11.647 & 2.02 & 1.259 & 0.058\\
-\hspace{1em}cif-standard & 0.202 (0.006) & 0.834 (0.006) & 71.819 & 12.5 & 476.484 & 21.9\\
-\hspace{1em}cif-rotate & 0.171 (0.005) & 0.805 (0.008) & 431.960 & 75.0 & 319.739 & 14.7\\
-\hspace{1em}glmnet-cox & 0.163 (0.041) & 0.814 (0.016) & 2.435 & 0.423 & 1.106 & 0.051\\
-\hspace{1em}xgboost-cox & 0.117 (0.019) & 0.840 (0.005) & 11.828 & 2.05 & 1.131 & 0.052\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{ARIC; stroke, n = 13626, p = 31}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.091 (0.006) & 0.791 (0.010) & 5.070 & 1.00 & 12.402 & 1.00\\
-\hspace{1em}rsf-standard & 0.090 (0.007) & 0.782 (0.011) & 10.586 & 2.09 & 1.225 & 0.099\\
-\hspace{1em}glmnet-cox & 0.076 (0.006) & 0.783 (0.010) & 1.135 & 0.224 & 0.905 & 0.073\\
-\hspace{1em}cif-standard & 0.073 (0.005) & 0.784 (0.011) & 69.781 & 13.8 & 389.705 & 31.4\\
-\hspace{1em}cif-rotate & 0.052 (0.003) & 0.766 (0.010) & 407.352 & 80.4 & 170.815 & 13.8\\
-\hspace{1em}xgboost-cox & 0.048 (0.023) & 0.789 (0.010) & 7.716 & 1.52 & 0.915 & 0.074\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Colon cancer; death, n = 929, p = 12}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.718 (0.011) & 0.259 & 1.00 & 0.075 & 1.00\\
-\hspace{1em}cif-standard & 0.097 (0.013) & 0.710 (0.012) & 1.193 & 4.60 & 3.848 & 51.3\\
-\hspace{1em}cif-rotate & 0.087 (0.017) & 0.705 (0.014) & 13.358 & 51.5 & 5.116 & 68.1\\
-\hspace{1em}rsf-standard & 0.087 (0.019) & 0.704 (0.011) & 1.226 & 4.73 & 0.150 & 2.00\\
-\hspace{1em}glmnet-cox & 0.076 (0.016) & 0.711 (0.019) & 0.116 & 0.448 & 0.004 & 0.053\\
-\hspace{1em}xgboost-cox & 0.063 (0.013) & 0.701 (0.013) & 3.165 & 12.2 & 0.004 & 0.053\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Colon cancer; recurrence, n = 929, p = 12}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.100 (0.017) & 0.713 (0.016) & 0.259 & 1.00 & 0.076 & 1.00\\
-\hspace{1em}cif-standard & 0.091 (0.015) & 0.701 (0.017) & 1.182 & 4.56 & 3.929 & 51.7\\
-\hspace{1em}cif-rotate & 0.084 (0.020) & 0.695 (0.017) & 13.338 & 51.5 & 5.118 & 67.3\\
-\hspace{1em}rsf-standard & 0.081 (0.020) & 0.694 (0.015) & 1.223 & 4.72 & 0.151 & 1.99\\
-\hspace{1em}glmnet-cox & 0.073 (0.018) & 0.706 (0.024) & 0.115 & 0.444 & 0.004 & 0.053\\
-\hspace{1em}xgboost-cox & 0.060 (0.011) & 0.695 (0.018) & 2.895 & 11.2 & 0.004 & 0.053\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Early breast cancer; recurrence or death, n = 614, p = 1692}}}\\
-\hline
-\hspace{1em}cif-rotate & 0.070 (0.018) & 0.747 (0.027) & 6304.881 & 8,318.3 & 374.594 & 2,134.8\\
-\hspace{1em}cif-standard & 0.067 (0.019) & 0.747 (0.030) & 8.059 & 10.6 & 4.493 & 25.6\\
-\hspace{1em}aorsf-fast & 0.065 (0.028) & 0.746 (0.026) & 0.758 & 1.00 & 0.175 & 1.00\\
-\hspace{1em}glmnet-cox & 0.041 (0.032) & 0.724 (0.036) & 5.686 & 7.50 & 0.005 & 0.029\\
-\hspace{1em}xgboost-cox & 0.027 (0.034) & 0.741 (0.030) & 2.154 & 2.84 & 0.006 & 0.034\\
-\hspace{1em}rsf-standard & 0.024 (0.037) & 0.695 (0.033) & 0.323 & 0.427 & 0.666 & 3.80\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{FCL; death, n = 541, p = 7}}}\\
-\hline
-\hspace{1em}glmnet-cox & 0.117 (0.028) & 0.787 (0.037) & 0.082 & 0.988 & 0.002 & 0.111\\
-\hspace{1em}aorsf-fast & 0.100 (0.038) & 0.768 (0.033) & 0.083 & 1.00 & 0.018 & 1.00\\
-\hspace{1em}cif-rotate & 0.087 (0.048) & 0.755 (0.027) & 6.369 & 76.7 & 1.766 & 98.0\\
-\hspace{1em}cif-standard & 0.084 (0.038) & 0.743 (0.036) & 0.751 & 9.04 & 1.020 & 56.6\\
-\hspace{1em}rsf-standard & 0.072 (0.048) & 0.732 (0.034) & 0.589 & 7.08 & 0.040 & 2.22\\
-\hspace{1em}xgboost-cox & 0.029 (0.050) & 0.679 (0.121) & 0.320 & 3.86 & 0.002 & 0.111\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{FCL; relapse, n = 541, p = 7}}}\\
-\hline
-\hspace{1em}glmnet-cox & 0.029 (0.017) & 0.620 (0.024) & 0.086 & 0.717 & 0.003 & 0.120\\
-\hspace{1em}xgboost-cox & 0.010 (0.016) & 0.598 (0.032) & 1.272 & 10.6 & 0.003 & 0.120\\
-\hspace{1em}cif-standard & 0.007 (0.021) & 0.594 (0.023) & 0.753 & 6.27 & 1.153 & 46.1\\
-\hspace{1em}aorsf-fast & 0.007 (0.019) & 0.594 (0.025) & 0.120 & 1.00 & 0.025 & 1.00\\
-\hspace{1em}cif-rotate & -0.012 (0.025) & 0.583 (0.030) & 7.360 & 61.3 & 2.955 & 118.1\\
-\hspace{1em}rsf-standard & -0.027 (0.032) & 0.577 (0.024) & 0.742 & 6.18 & 0.092 & 3.68\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{GBSG II; recurrence or death, n = 686, p = 10}}}\\
-\hline
-\hspace{1em}cif-standard & 0.123 (0.020) & 0.742 (0.019) & 0.919 & 5.21 & 2.297 & 52.1\\
-\hspace{1em}rsf-standard & 0.120 (0.023) & 0.737 (0.019) & 1.198 & 6.79 & 0.115 & 2.61\\
-\hspace{1em}aorsf-fast & 0.116 (0.024) & 0.732 (0.017) & 0.176 & 1.00 & 0.044 & 1.00\\
-\hspace{1em}cif-rotate & 0.107 (0.022) & 0.729 (0.017) & 11.084 & 62.8 & 3.797 & 86.2\\
-\hspace{1em}glmnet-cox & 0.091 (0.019) & 0.727 (0.021) & 0.094 & 0.533 & 0.003 & 0.068\\
-\hspace{1em}xgboost-cox & 0.083 (0.017) & 0.729 (0.020) & 2.257 & 12.8 & 0.003 & 0.068\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{GUIDE-IT; CVD death, n = 894, p = 59}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.746 (0.027) & 0.166 & 1.00 & 0.036 & 1.00\\
-\hspace{1em}glmnet-cox & 0.063 (0.041) & 0.715 (0.091) & 0.995 & 5.99 & 0.002 & 0.056\\
-\hspace{1em}cif-rotate & 0.059 (0.016) & 0.721 (0.025) & 35.119 & 211.4 & 4.542 & 126.1\\
-\hspace{1em}cif-standard & 0.058 (0.014) & 0.737 (0.022) & 1.771 & 10.7 & 3.109 & 86.3\\
-\hspace{1em}rsf-standard & 0.046 (0.023) & 0.705 (0.025) & 0.638 & 3.84 & 0.063 & 1.75\\
-\hspace{1em}xgboost-cox & 0.039 (0.051) & 0.747 (0.020) & 4.202 & 25.3 & 0.003 & 0.083\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{GUIDE-IT; HF hospitalization, n = 894, p = 59}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.082 (0.019) & 0.722 (0.025) & 0.262 & 1.00 & 0.551 & 1.00\\
-\hspace{1em}cif-standard & 0.071 (0.010) & 0.716 (0.023) & 1.796 & 6.85 & 3.342 & 6.07\\
-\hspace{1em}cif-rotate & 0.068 (0.018) & 0.708 (0.029) & 41.195 & 157.1 & 5.392 & 9.79\\
-\hspace{1em}rsf-standard & 0.059 (0.022) & 0.694 (0.026) & 1.230 & 4.69 & 0.123 & 0.224\\
-\hspace{1em}glmnet-cox & 0.058 (0.019) & 0.699 (0.024) & 0.914 & 3.49 & 0.003 & 0.005\\
-\hspace{1em}xgboost-cox & 0.039 (0.017) & 0.698 (0.027) & 2.792 & 10.6 & 0.003 & 0.005\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Heart Transplant; graft-loss or death, n = 3787, p = 52}}}\\
-\hline
-\hspace{1em}cif-rotate & 0.056 (0.010) & 0.731 (0.017) & 152.873 & 160.7 & 31.205 & 107.1\\
-\hspace{1em}aorsf-fast & 0.052 (0.006) & 0.735 (0.014) & 0.951 & 1.00 & 0.291 & 1.00\\
-\hspace{1em}cif-standard & 0.050 (0.006) & 0.733 (0.013) & 10.380 & 10.9 & 38.621 & 132.6\\
-\hspace{1em}rsf-standard & 0.048 (0.009) & 0.727 (0.013) & 2.246 & 2.36 & 0.893 & 3.07\\
-\hspace{1em}glmnet-cox & 0.036 (0.006) & 0.711 (0.016) & 0.920 & 0.967 & 0.018 & 0.062\\
-\hspace{1em}xgboost-cox & 0.031 (0.007) & 0.716 (0.018) & 3.383 & 3.56 & 0.011 & 0.038\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{MESA; coronary heart disease, n = 6785, p = 28}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.055 (0.009) & 0.771 (0.014) & 1.720 & 1.00 & 0.520 & 1.00\\
-\hspace{1em}rsf-standard & 0.051 (0.011) & 0.756 (0.016) & 3.294 & 1.92 & 0.430 & 0.828\\
-\hspace{1em}cif-standard & 0.049 (0.006) & 0.763 (0.014) & 20.168 & 11.7 & 102.381 & 197.0\\
-\hspace{1em}cif-rotate & 0.047 (0.006) & 0.767 (0.017) & 162.455 & 94.4 & 39.029 & 75.1\\
-\hspace{1em}glmnet-cox & 0.031 (0.017) & 0.751 (0.025) & 0.751 & 0.436 & 0.014 & 0.027\\
-\hspace{1em}xgboost-cox & 0.025 (0.027) & 0.766 (0.016) & 5.609 & 3.26 & 0.018 & 0.035\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{MESA; death, n = 6793, p = 28}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.144 (0.009) & 0.786 (0.010) & 1.797 & 1.00 & 1.069 & 1.00\\
-\hspace{1em}rsf-standard & 0.141 (0.009) & 0.780 (0.010) & 3.613 & 2.01 & 0.487 & 0.456\\
-\hspace{1em}cif-standard & 0.136 (0.007) & 0.785 (0.010) & 20.306 & 11.3 & 114.250 & 106.9\\
-\hspace{1em}cif-rotate & 0.126 (0.007) & 0.782 (0.010) & 171.028 & 95.2 & 74.574 & 69.8\\
-\hspace{1em}glmnet-cox & 0.123 (0.025) & 0.783 (0.013) & 0.702 & 0.391 & 0.046 & 0.043\\
-\hspace{1em}xgboost-cox & 0.054 (0.027) & 0.790 (0.010) & 10.187 & 5.67 & 0.052 & 0.049\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{MESA; heart failure, n = 6785, p = 28}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.108 (0.010) & 0.866 (0.014) & 1.619 & 1.00 & 0.427 & 1.00\\
-\hspace{1em}rsf-standard & 0.108 (0.013) & 0.857 (0.015) & 3.844 & 2.37 & 0.479 & 1.12\\
-\hspace{1em}cif-standard & 0.099 (0.008) & 0.860 (0.016) & 20.168 & 12.5 & 100.439 & 235.4\\
-\hspace{1em}cif-rotate & 0.098 (0.009) & 0.863 (0.014) & 148.543 & 91.7 & 36.415 & 85.4\\
-\hspace{1em}glmnet-cox & 0.036 (0.037) & 0.764 (0.137) & 0.893 & 0.551 & 0.019 & 0.045\\
-\hspace{1em}xgboost-cox & -0.002 (0.025) & 0.866 (0.012) & 8.241 & 5.09 & 0.016 & 0.038\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{MESA; stroke, n = 6783, p = 28}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.766 (0.015) & 1.689 & 1.00 & 0.393 & 1.00\\
-\hspace{1em}cif-rotate & 0.025 (0.005) & 0.764 (0.016) & 151.593 & 89.7 & 32.758 & 83.4\\
-\hspace{1em}cif-standard & 0.025 (0.004) & 0.762 (0.015) & 19.936 & 11.8 & 98.802 & 251.4\\
-\hspace{1em}rsf-standard & 0.022 (0.008) & 0.750 (0.013) & 2.453 & 1.45 & 0.737 & 1.87\\
-\hspace{1em}glmnet-cox & 0.022 (0.008) & 0.763 (0.016) & 0.775 & 0.459 & 0.012 & 0.031\\
-\hspace{1em}xgboost-cox & 0.008 (0.026) & 0.764 (0.015) & 4.517 & 2.67 & 0.015 & 0.038\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Monoclonal gammopathy; death, n = 1384, p = 8}}}\\
-\hline
-\hspace{1em}cif-rotate & 0.160 (0.019) & 0.744 (0.014) & 15.319 & 34.5 & 6.540 & 62.8\\
-\hspace{1em}aorsf-fast & 0.158 (0.016) & 0.742 (0.011) & 0.444 & 1.00 & 0.104 & 1.00\\
-\hspace{1em}cif-standard & 0.151 (0.015) & 0.738 (0.012) & 1.432 & 3.23 & 6.299 & 60.5\\
-\hspace{1em}rsf-standard & 0.151 (0.017) & 0.737 (0.011) & 1.906 & 4.29 & 0.207 & 1.99\\
-\hspace{1em}glmnet-cox & 0.138 (0.021) & 0.727 (0.014) & 0.131 & 0.295 & 0.004 & 0.038\\
-\hspace{1em}xgboost-cox & 0.123 (0.012) & 0.733 (0.012) & 3.450 & 7.77 & 0.004 & 0.038\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Monoclonal gammopathy; malignancy, n = 1384, p = 8}}}\\
-\hline
-\hspace{1em}glmnet-cox & 0.015 (0.011) & 0.651 (0.055) & 0.118 & 0.599 & 0.002 & 0.050\\
-\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.641 (0.036) & 0.197 & 1.00 & 0.040 & 1.00\\
-\hspace{1em}xgboost-cox & 0.007 (0.017) & 0.639 (0.039) & 1.734 & 8.79 & 0.003 & 0.075\\
-\hspace{1em}cif-standard & 0.006 (0.011) & 0.628 (0.033) & 1.443 & 7.32 & 5.801 & 144.9\\
-\hspace{1em}rsf-standard & -0.009 (0.018) & 0.616 (0.036) & 0.684 & 3.47 & 0.077 & 1.92\\
-\hspace{1em}cif-rotate & -0.024 (0.023) & 0.553 (0.035) & 12.997 & 65.9 & 4.817 & 120.3\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Movies released in 2015-2018; gross 1M USD, n = 551, p = 46}}}\\
-\hline
-\hspace{1em}cif-rotate & 0.639 (0.023) & 0.943 (0.007) & 20.129 & 26.2 & 5.703 & 105.5\\
-\hspace{1em}glmnet-cox & 0.620 (0.033) & 0.940 (0.009) & 0.671 & 0.872 & 0.003 & 0.056\\
-\hspace{1em}rsf-standard & 0.520 (0.021) & 0.922 (0.010) & 1.666 & 2.17 & 0.103 & 1.91\\
-\hspace{1em}aorsf-fast & 0.517 (0.026) & 0.922 (0.012) & 0.769 & 1.00 & 0.054 & 1.00\\
-\hspace{1em}xgboost-cox & 0.511 (0.028) & 0.932 (0.009) & 16.829 & 21.9 & 0.005 & 0.093\\
-\hspace{1em}cif-standard & 0.475 (0.028) & 0.902 (0.018) & 0.867 & 1.13 & 2.080 & 38.5\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Non-alcohol fatty liver disease; death, n = 17549, p = 24}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.215 (0.009) & 0.869 (0.005) & 5.813 & 1.00 & 11.773 & 1.00\\
-\hspace{1em}rsf-standard & 0.210 (0.009) & 0.860 (0.005) & 10.989 & 1.89 & 1.393 & 0.118\\
-\hspace{1em}glmnet-cox & 0.209 (0.011) & 0.861 (0.005) & 2.110 & 0.363 & 0.124 & 0.011\\
-\hspace{1em}cif-standard & 0.208 (0.007) & 0.863 (0.006) & 64.081 & 11.0 & 674.392 & 57.3\\
-\hspace{1em}cif-rotate & 0.193 (0.008) & 0.866 (0.005) & 254.040 & 43.7 & 194.487 & 16.5\\
-\hspace{1em}xgboost-cox & 0.023 (0.015) & 0.876 (0.005) & 8.628 & 1.48 & 1.012 & 0.086\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Primary biliary cholangitis; death, n = 276, p = 19}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.430 (0.033) & 0.908 (0.021) & 0.075 & 1.00 & 0.018 & 1.00\\
-\hspace{1em}cif-rotate & 0.405 (0.041) & 0.899 (0.022) & 9.498 & 126.5 & 2.287 & 126.9\\
-\hspace{1em}rsf-standard & 0.391 (0.034) & 0.895 (0.023) & 0.102 & 1.36 & 0.039 & 2.17\\
-\hspace{1em}cif-standard & 0.351 (0.034) & 0.904 (0.025) & 0.194 & 2.59 & 0.850 & 47.1\\
-\hspace{1em}glmnet-cox & 0.342 (0.045) & 0.886 (0.028) & 0.104 & 1.39 & 0.002 & 0.111\\
-\hspace{1em}xgboost-cox & 0.256 (0.104) & 0.881 (0.027) & 4.587 & 61.1 & 0.003 & 0.167\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Rotterdam tumor bank; death, n = 2982, p = 11}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.162 (0.012) & 0.757 (0.009) & 1.488 & 1.00 & 0.397 & 1.00\\
-\hspace{1em}cif-standard & 0.160 (0.010) & 0.759 (0.009) & 4.838 & 3.25 & 29.075 & 73.2\\
-\hspace{1em}rsf-standard & 0.160 (0.014) & 0.756 (0.009) & 2.974 & 2.00 & 0.846 & 2.13\\
-\hspace{1em}cif-rotate & 0.148 (0.011) & 0.750 (0.011) & 34.842 & 23.4 & 32.884 & 82.8\\
-\hspace{1em}xgboost-cox & 0.131 (0.014) & 0.753 (0.010) & 4.263 & 2.87 & 0.017 & 0.043\\
-\hspace{1em}glmnet-cox & 0.119 (0.008) & 0.731 (0.009) & 0.779 & 0.523 & 0.019 & 0.048\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Rotterdam tumor bank; recurrence, n = 2982, p = 11}}}\\
-\hline
-\hspace{1em}cif-standard & 0.145 (0.011) & 0.734 (0.009) & 4.883 & 2.98 & 29.781 & 67.9\\
-\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 1.636 & 1.00 & 0.438 & 1.00\\
-\hspace{1em}rsf-standard & 0.139 (0.012) & 0.731 (0.008) & 3.160 & 1.93 & 0.836 & 1.91\\
-\hspace{1em}cif-rotate & 0.130 (0.010) & 0.725 (0.009) & 36.274 & 22.2 & 36.461 & 83.2\\
-\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.727 (0.008) & 0.815 & 0.498 & 0.029 & 0.066\\
-\hspace{1em}xgboost-cox & 0.114 (0.008) & 0.729 (0.009) & 3.774 & 2.31 & 0.020 & 0.046\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Serum free light chain; death, n = 7874, p = 10}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.252 (0.014) & 0.825 (0.007) & 3.093 & 1.00 & 4.842 & 1.00\\
-\hspace{1em}glmnet-cox & 0.249 (0.012) & 0.820 (0.007) & 1.261 & 0.408 & 0.081 & 0.017\\
-\hspace{1em}cif-standard & 0.245 (0.011) & 0.818 (0.008) & 19.554 & 6.32 & 146.176 & 30.2\\
-\hspace{1em}rsf-standard & 0.245 (0.013) & 0.815 (0.008) & 6.058 & 1.96 & 0.611 & 0.126\\
-\hspace{1em}cif-rotate & 0.230 (0.009) & 0.819 (0.007) & 67.331 & 21.8 & 132.391 & 27.3\\
-\hspace{1em}xgboost-cox & 0.097 (0.038) & 0.824 (0.007) & 6.139 & 1.98 & 0.084 & 0.017\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{SPRINT; CVD death, n = 9361, p = 174}}}\\
-\hline
-\hspace{1em}glmnet-cox & 0.072 (0.011) & 0.796 (0.011) & 12.974 & 4.88 & 0.026 & 0.025\\
-\hspace{1em}aorsf-fast & 0.070 (0.006) & 0.798 (0.011) & 2.657 & 1.00 & 1.054 & 1.00\\
-\hspace{1em}rsf-standard & 0.065 (0.007) & 0.789 (0.014) & 3.854 & 1.45 & 0.701 & 0.665\\
-\hspace{1em}cif-standard & 0.062 (0.003) & 0.798 (0.011) & 48.137 & 18.1 & 185.155 & 175.7\\
-\hspace{1em}cif-rotate & 0.061 (0.005) & 0.791 (0.012) & 907.261 & 341.4 & 135.081 & 128.2\\
-\hspace{1em}xgboost-cox & 0.006 (0.017) & 0.800 (0.011) & 6.905 & 2.60 & 0.029 & 0.028\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{SPRINT; death, n = 9361, p = 174}}}\\
-\hline
-\hspace{1em}glmnet-cox & 0.124 (0.012) & 0.771 (0.009) & 4.886 & 1.02 & 0.065 & 0.017\\
-\hspace{1em}aorsf-fast & 0.117 (0.008) & 0.770 (0.008) & 4.807 & 1.00 & 3.794 & 1.00\\
-\hspace{1em}rsf-standard & 0.111 (0.008) & 0.763 (0.009) & 6.757 & 1.41 & 0.752 & 0.198\\
-\hspace{1em}cif-standard & 0.107 (0.006) & 0.764 (0.008) & 48.766 & 10.1 & 208.039 & 54.8\\
-\hspace{1em}cif-rotate & 0.092 (0.007) & 0.745 (0.009) & 1024.991 & 213.2 & 194.183 & 51.2\\
-\hspace{1em}xgboost-cox & 0.031 (0.023) & 0.772 (0.008) & 9.163 & 1.91 & 0.077 & 0.020\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{Systolic Heart Failure; death, n = 2231, p = 41}}}\\
-\hline
-\hspace{1em}glmnet-cox & 0.114 (0.013) & 0.746 (0.012) & 0.257 & 0.387 & 0.009 & 0.040\\
-\hspace{1em}cif-rotate & 0.113 (0.013) & 0.741 (0.011) & 69.125 & 104.0 & 18.805 & 84.2\\
-\hspace{1em}aorsf-fast & 0.110 (0.015) & 0.744 (0.011) & 0.665 & 1.00 & 0.223 & 1.00\\
-\hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 3.672 & 5.53 & 18.416 & 82.5\\
-\hspace{1em}rsf-standard & 0.105 (0.011) & 0.735 (0.011) & 2.072 & 3.12 & 0.298 & 1.34\\
-\hspace{1em}xgboost-cox & 0.090 (0.009) & 0.744 (0.010) & 4.047 & 6.09 & 0.009 & 0.040\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{7}{l}{\textit{\textbf{VA lung cancer trial; death, n = 137, p = 8}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.200 (0.050) & 0.795 (0.034) & 0.052 & 1.00 & 0.011 & 1.00\\
-\hspace{1em}cif-rotate & 0.198 (0.066) & 0.788 (0.036) & 4.620 & 88.8 & 1.017 & 92.3\\
-\hspace{1em}rsf-standard & 0.175 (0.048) & 0.787 (0.037) & 0.063 & 1.21 & 0.035 & 3.18\\
-\hspace{1em}glmnet-cox & 0.160 (0.036) & 0.787 (0.038) & 0.075 & 1.44 & 0.002 & 0.182\\
-\hspace{1em}cif-standard & 0.128 (0.040) & 0.770 (0.037) & 0.093 & 1.79 & 0.133 & 12.1\\
-\hspace{1em}xgboost-cox & 0.068 (0.078) & 0.750 (0.046) & 1.144 & 22.0 & 0.002 & 0.182\\*
+\multicolumn{5}{l}{\textit{\textbf{Overall}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.133 (0.114) & 0.775 (0.072) & 0.801 & 0.170\\
+\hspace{1em}aorsf-cph & 0.132 (0.114) & 0.774 (0.071) & 1.965 & 0.173\\
+\hspace{1em}aorsf-net & 0.131 (0.116) & 0.774 (0.071) & 122.683 & 0.166\\
+\hspace{1em}rsf-standard & 0.121 (0.117) & 0.761 (0.075) & 2.089 & 0.252\\
+\hspace{1em}cif-rotate & 0.120 (0.130) & 0.758 (0.081) & 39.689 & 8.754\\
+\hspace{1em}cif-standard & 0.119 (0.100) & 0.768 (0.070) & 4.254 & 15.360\\
+\hspace{1em}obliqueRSF-net & 0.118 (0.086) & 0.774 (0.071) & 376.210 & 24.600\\
+\hspace{1em}glmnet-cox & 0.116 (0.123) & 0.763 (0.074) & 0.532 & 0.004\\
+\hspace{1em}ranger-extratrees & 0.103 (0.088) & 0.764 (0.068) & 2.519 & 2.159\\
+\hspace{1em}cif-extension & 0.099 (0.095) & 0.763 (0.072) & 23.746 & 8.318\\
+\hspace{1em}aorsf-random & 0.094 (0.084) & 0.743 (0.064) & 2.088 & 0.178\\
+\hspace{1em}xgboost-cox & 0.073 (0.102) & 0.757 (0.088) & 5.270 & 0.005\\
+\hspace{1em}nn-cox & 0.046 (0.106) & 0.655 (0.132) & 16.511 & 5.207\\
+\hspace{1em}xgboost-aft & -4.78 (4.97) & 0.767 (0.076) & 15.673 & 0.007\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{ACTG 320; AIDS diagnosis, n = 1151, p = 12}}}\\
+\hline
+\hspace{1em}aorsf-random & 0.031 (0.015) & 0.739 (0.031) & 0.396 & 0.036\\
+\hspace{1em}ranger-extratrees & 0.030 (0.014) & 0.734 (0.033) & 0.448 & 0.146\\
+\hspace{1em}cif-standard & 0.029 (0.028) & 0.740 (0.043) & 0.988 & 4.459\\
+\hspace{1em}obliqueRSF-net & 0.027 (0.022) & 0.735 (0.039) & 26.729 & 15.372\\
+\hspace{1em}aorsf-cph & 0.026 (0.024) & 0.742 (0.040) & 0.496 & 0.036\\
+\hspace{1em}aorsf-fast & 0.026 (0.022) & 0.738 (0.040) & 0.161 & 0.036\\
+\hspace{1em}cif-extension & 0.023 (0.015) & 0.711 (0.041) & 9.394 & 4.051\\
+\hspace{1em}glmnet-cox & 0.022 (0.020) & 0.741 (0.024) & 0.182 & 0.003\\
+\hspace{1em}aorsf-net & 0.021 (0.030) & 0.735 (0.038) & 18.601 & 0.037\\
+\hspace{1em}rsf-standard & 0.011 (0.030) & 0.722 (0.044) & 0.149 & 0.065\\
+\hspace{1em}xgboost-cox & 0.008 (0.033) & 0.743 (0.035) & 4.586 & 0.003\\
+\hspace{1em}cif-rotate & 0.006 (0.036) & 0.726 (0.035) & 15.373 & 3.791\\
+\hspace{1em}nn-cox & -0.008 (0.016) & 0.558 (0.129) & 13.641 & 0.549\\
+\hspace{1em}xgboost-aft & -7.76 (1.18) & 0.733 (0.029) & 13.603 & 0.007\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{ACTG 320; death, n = 1151, p = 12}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.013 (0.022) & 0.847 (0.054) & 0.104 & 0.022\\
+\hspace{1em}aorsf-cph & 0.012 (0.021) & 0.833 (0.061) & 0.335 & 0.021\\
+\hspace{1em}aorsf-net & 0.010 (0.032) & 0.829 (0.062) & 13.672 & 0.024\\
+\hspace{1em}obliqueRSF-net & 0.009 (0.013) & 0.839 (0.052) & 8.926 & 10.688\\
+\hspace{1em}aorsf-random & 0.008 (0.016) & 0.810 (0.069) & 0.218 & 0.023\\
+\hspace{1em}cif-extension & 0.007 (0.014) & 0.786 (0.050) & 8.178 & 3.578\\
+\hspace{1em}cif-standard & 0.007 (0.019) & 0.801 (0.057) & 1.008 & 4.449\\
+\hspace{1em}ranger-extratrees & 0.004 (0.018) & 0.795 (0.062) & 0.423 & 0.266\\
+\hspace{1em}xgboost-cox & -0.004 (0.003) & 0.500 (0.000) & 0.145 & 0.002\\
+\hspace{1em}nn-cox & -0.004 (0.004) & 0.574 (0.111) & 14.113 & 0.560\\
+\hspace{1em}rsf-standard & -0.007 (0.048) & 0.801 (0.059) & 0.090 & 0.036\\
+\hspace{1em}cif-rotate & -0.026 (0.034) & 0.715 (0.093) & 13.721 & 3.326\\
+\hspace{1em}glmnet-cox & -0.027 (0.072) & 0.753 (0.101) & 0.257 & 0.002\\
+\hspace{1em}xgboost-aft & -22.8 (5.25) & 0.777 (0.078) & 11.919 & 0.006\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{ARIC; coronary heart disease, n = 13623, p = 41}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.155 (0.007) & 0.807 (0.005) & 4.481 & 1.501\\
+\hspace{1em}aorsf-net & 0.152 (0.006) & 0.807 (0.004) & 498.111 & 1.449\\
+\hspace{1em}aorsf-cph & 0.151 (0.006) & 0.806 (0.004) & 15.754 & 1.558\\
+\hspace{1em}rsf-standard & 0.150 (0.007) & 0.799 (0.004) & 11.130 & 1.219\\
+\hspace{1em}obliqueRSF-net & 0.143 (0.004) & 0.809 (0.004) & 2875.869 & 334.594\\
+\hspace{1em}cif-standard & 0.132 (0.003) & 0.807 (0.004) & 70.329 & 357.765\\
+\hspace{1em}glmnet-cox & 0.128 (0.014) & 0.792 (0.007) & 1.606 & 0.019\\
+\hspace{1em}ranger-extratrees & 0.112 (0.003) & 0.793 (0.005) & 398.270 & 131.923\\
+\hspace{1em}cif-rotate & 0.104 (0.004) & 0.782 (0.007) & 550.670 & 69.312\\
+\hspace{1em}nn-cox & 0.103 (0.039) & 0.763 (0.093) & 40.780 & 85.754\\
+\hspace{1em}aorsf-random & 0.097 (0.005) & 0.769 (0.006) & 11.207 & 1.357\\
+\hspace{1em}cif-extension & 0.069 (0.002) & 0.784 (0.005) & 173.969 & 56.767\\
+\hspace{1em}xgboost-cox & 0.068 (0.017) & 0.812 (0.003) & 9.465 & 0.016\\
+\hspace{1em}xgboost-aft & -4.83 (0.210) & 0.813 (0.003) & 33.629 & 0.014\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{ARIC; death, n = 13623, p = 41}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.217 (0.007) & 0.792 (0.004) & 940.117 & 2.346\\
+\hspace{1em}rsf-standard & 0.216 (0.006) & 0.789 (0.004) & 13.902 & 1.221\\
+\hspace{1em}aorsf-fast & 0.215 (0.008) & 0.792 (0.004) & 6.921 & 2.306\\
+\hspace{1em}aorsf-cph & 0.215 (0.007) & 0.791 (0.004) & 23.219 & 2.393\\
+\hspace{1em}obliqueRSF-net & 0.206 (0.005) & 0.790 (0.004) & 7672.274 & 317.021\\
+\hspace{1em}cif-standard & 0.200 (0.005) & 0.788 (0.004) & 69.166 & 373.964\\
+\hspace{1em}nn-cox & 0.192 (0.007) & 0.778 (0.004) & 302.175 & 153.845\\
+\hspace{1em}ranger-extratrees & 0.180 (0.006) & 0.780 (0.005) & 678.904 & 94.798\\
+\hspace{1em}glmnet-cox & 0.176 (0.019) & 0.771 (0.009) & 2.425 & 0.018\\
+\hspace{1em}cif-rotate & 0.151 (0.008) & 0.755 (0.007) & 613.021 & 69.650\\
+\hspace{1em}xgboost-cox & 0.139 (0.015) & 0.794 (0.005) & 17.317 & 0.018\\
+\hspace{1em}aorsf-random & 0.130 (0.005) & 0.735 (0.005) & 21.763 & 2.126\\
+\hspace{1em}cif-extension & 0.113 (0.002) & 0.775 (0.005) & 177.598 & 52.953\\
+\hspace{1em}xgboost-aft & -1.56 (0.099) & 0.794 (0.005) & 25.317 & 0.013\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{ARIC; heart failure, n = 13623, p = 41}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.235 (0.007) & 0.842 (0.006) & 5.652 & 1.828\\
+\hspace{1em}rsf-standard & 0.230 (0.007) & 0.835 (0.005) & 9.050 & 1.075\\
+\hspace{1em}aorsf-cph & 0.230 (0.007) & 0.841 (0.006) & 17.921 & 2.008\\
+\hspace{1em}aorsf-net & 0.229 (0.007) & 0.841 (0.006) & 613.168 & 1.685\\
+\hspace{1em}obliqueRSF-net & 0.213 (0.006) & 0.841 (0.006) & 3954.453 & 334.564\\
+\hspace{1em}cif-standard & 0.199 (0.005) & 0.839 (0.006) & 70.715 & 362.530\\
+\hspace{1em}nn-cox & 0.175 (0.025) & 0.826 (0.006) & 138.006 & 231.741\\
+\hspace{1em}cif-rotate & 0.171 (0.004) & 0.806 (0.005) & 562.939 & 67.797\\
+\hspace{1em}ranger-extratrees & 0.171 (0.004) & 0.824 (0.006) & 1532.153 & 144.888\\
+\hspace{1em}glmnet-cox & 0.165 (0.046) & 0.816 (0.018) & 2.192 & 0.012\\
+\hspace{1em}aorsf-random & 0.140 (0.005) & 0.790 (0.008) & 15.028 & 1.599\\
+\hspace{1em}xgboost-cox & 0.118 (0.016) & 0.845 (0.005) & 14.769 & 0.019\\
+\hspace{1em}cif-extension & 0.108 (0.003) & 0.809 (0.007) & 195.201 & 60.594\\
+\hspace{1em}xgboost-aft & -3.80 (0.291) & 0.844 (0.005) & 38.814 & 0.015\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{ARIC; stroke, n = 13623, p = 41}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.093 (0.003) & 0.794 (0.004) & 4.096 & 1.257\\
+\hspace{1em}rsf-standard & 0.091 (0.004) & 0.785 (0.004) & 7.684 & 0.943\\
+\hspace{1em}aorsf-net & 0.090 (0.003) & 0.792 (0.004) & 384.631 & 1.222\\
+\hspace{1em}aorsf-cph & 0.089 (0.002) & 0.791 (0.005) & 14.364 & 1.263\\
+\hspace{1em}obliqueRSF-net & 0.081 (0.002) & 0.790 (0.005) & 1858.149 & 373.179\\
+\hspace{1em}glmnet-cox & 0.077 (0.004) & 0.785 (0.006) & 1.828 & 0.017\\
+\hspace{1em}nn-cox & 0.073 (0.008) & 0.779 (0.008) & 31.694 & 72.618\\
+\hspace{1em}cif-standard & 0.073 (0.002) & 0.787 (0.005) & 70.222 & 351.070\\
+\hspace{1em}ranger-extratrees & 0.067 (0.003) & 0.779 (0.008) & 217.755 & 74.836\\
+\hspace{1em}aorsf-random & 0.059 (0.003) & 0.751 (0.007) & 9.041 & 1.119\\
+\hspace{1em}cif-rotate & 0.052 (0.002) & 0.766 (0.008) & 571.269 & 67.464\\
+\hspace{1em}xgboost-cox & 0.046 (0.010) & 0.792 (0.003) & 8.153 & 0.015\\
+\hspace{1em}cif-extension & 0.036 (0.001) & 0.770 (0.007) & 169.947 & 53.605\\
+\hspace{1em}xgboost-aft & -6.55 (0.323) & 0.791 (0.003) & 31.120 & 0.013\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Colon cancer; death, n = 929, p = 12}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.100 (0.013) & 0.719 (0.011) & 0.236 & 0.051\\
+\hspace{1em}cif-standard & 0.100 (0.011) & 0.713 (0.009) & 0.663 & 3.547\\
+\hspace{1em}aorsf-cph & 0.098 (0.012) & 0.717 (0.010) & 0.640 & 0.056\\
+\hspace{1em}aorsf-net & 0.097 (0.010) & 0.718 (0.009) & 51.061 & 0.046\\
+\hspace{1em}aorsf-random & 0.095 (0.007) & 0.717 (0.012) & 1.038 & 0.046\\
+\hspace{1em}cif-rotate & 0.093 (0.015) & 0.710 (0.012) & 12.320 & 3.417\\
+\hspace{1em}obliqueRSF-net & 0.089 (0.005) & 0.718 (0.010) & 236.037 & 17.920\\
+\hspace{1em}rsf-standard & 0.088 (0.018) & 0.703 (0.008) & 1.281 & 0.150\\
+\hspace{1em}cif-extension & 0.082 (0.006) & 0.711 (0.011) & 7.857 & 3.918\\
+\hspace{1em}ranger-extratrees & 0.081 (0.008) & 0.710 (0.012) & 0.986 & 0.352\\
+\hspace{1em}glmnet-cox & 0.076 (0.013) & 0.708 (0.018) & 0.127 & 0.003\\
+\hspace{1em}xgboost-cox & 0.066 (0.008) & 0.703 (0.011) & 3.626 & 0.004\\
+\hspace{1em}nn-cox & -0.004 (0.003) & 0.481 (0.031) & 15.080 & 1.153\\
+\hspace{1em}xgboost-aft & -1.12 (0.267) & 0.707 (0.013) & 11.971 & 0.006\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Colon cancer; recurrence, n = 929, p = 12}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.097 (0.011) & 0.714 (0.010) & 0.232 & 0.051\\
+\hspace{1em}aorsf-cph & 0.097 (0.010) & 0.713 (0.009) & 0.651 & 0.051\\
+\hspace{1em}cif-standard & 0.094 (0.014) & 0.704 (0.014) & 0.662 & 3.381\\
+\hspace{1em}aorsf-net & 0.094 (0.015) & 0.714 (0.012) & 51.223 & 0.047\\
+\hspace{1em}cif-rotate & 0.092 (0.017) & 0.700 (0.014) & 11.852 & 3.577\\
+\hspace{1em}obliqueRSF-net & 0.087 (0.008) & 0.711 (0.009) & 247.097 & 15.943\\
+\hspace{1em}rsf-standard & 0.085 (0.016) & 0.696 (0.011) & 1.200 & 0.150\\
+\hspace{1em}aorsf-random & 0.083 (0.011) & 0.702 (0.010) & 0.958 & 0.046\\
+\hspace{1em}cif-extension & 0.081 (0.010) & 0.708 (0.011) & 8.680 & 4.310\\
+\hspace{1em}ranger-extratrees & 0.076 (0.014) & 0.697 (0.012) & 0.666 & 0.770\\
+\hspace{1em}glmnet-cox & 0.070 (0.013) & 0.699 (0.016) & 0.119 & 0.003\\
+\hspace{1em}xgboost-cox & 0.059 (0.012) & 0.697 (0.013) & 3.432 & 0.003\\
+\hspace{1em}nn-cox & -0.008 (0.007) & 0.524 (0.053) & 13.774 & 0.938\\
+\hspace{1em}xgboost-aft & -1.18 (0.255) & 0.703 (0.014) & 9.791 & 0.006\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Early breast cancer; recurrence or death, n = 614, p = 1692}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.064 (0.030) & 0.739 (0.027) & 1844.847 & 13.621\\
+\hspace{1em}cif-rotate & 0.061 (0.016) & 0.735 (0.021) & 7099.601 & 384.127\\
+\hspace{1em}aorsf-cph & 0.060 (0.043) & 0.740 (0.020) & 1.567 & 0.176\\
+\hspace{1em}cif-standard & 0.060 (0.020) & 0.735 (0.024) & 7.310 & 3.860\\
+\hspace{1em}cif-extension & 0.059 (0.016) & 0.736 (0.025) & 51.533 & 7.534\\
+\hspace{1em}aorsf-fast & 0.058 (0.041) & 0.737 (0.023) & 1.118 & 0.173\\
+\hspace{1em}ranger-extratrees & 0.053 (0.031) & 0.730 (0.022) & 0.387 & 1.014\\
+\hspace{1em}xgboost-cox & 0.034 (0.009) & 0.736 (0.030) & 2.480 & 0.007\\
+\hspace{1em}glmnet-cox & 0.026 (0.039) & 0.711 (0.032) & 5.909 & 0.006\\
+\hspace{1em}aorsf-random & 0.021 (0.016) & 0.686 (0.029) & 1.763 & 0.185\\
+\hspace{1em}rsf-standard & 0.021 (0.056) & 0.695 (0.037) & 0.356 & 0.625\\
+\hspace{1em}aorsf-net & 0.019 (0.095) & 0.745 (0.022) & 431.378 & 0.168\\
+\hspace{1em}nn-cox & -0.024 (0.059) & 0.656 (0.069) & 17.924 & 1.897\\
+\hspace{1em}xgboost-aft & -2.95 (0.868) & 0.737 (0.022) & 8.909 & 0.009\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{FCL; death, n = 541, p = 7}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.122 (0.024) & 0.801 (0.041) & 0.259 & 0.002\\
+\hspace{1em}aorsf-cph & 0.104 (0.040) & 0.775 (0.038) & 0.165 & 0.021\\
+\hspace{1em}aorsf-fast & 0.101 (0.040) & 0.774 (0.038) & 0.083 & 0.021\\
+\hspace{1em}aorsf-net & 0.101 (0.040) & 0.767 (0.039) & 12.969 & 0.019\\
+\hspace{1em}obliqueRSF-net & 0.096 (0.028) & 0.774 (0.038) & 93.139 & 5.120\\
+\hspace{1em}cif-standard & 0.095 (0.039) & 0.757 (0.039) & 0.283 & 1.046\\
+\hspace{1em}aorsf-random & 0.093 (0.026) & 0.766 (0.038) & 0.293 & 0.020\\
+\hspace{1em}cif-extension & 0.090 (0.037) & 0.737 (0.042) & 4.384 & 2.202\\
+\hspace{1em}cif-rotate & 0.090 (0.050) & 0.759 (0.031) & 5.744 & 2.351\\
+\hspace{1em}rsf-standard & 0.081 (0.045) & 0.737 (0.042) & 0.109 & 0.042\\
+\hspace{1em}ranger-extratrees & 0.075 (0.012) & 0.746 (0.038) & 0.038 & 0.129\\
+\hspace{1em}xgboost-cox & 0.060 (0.060) & 0.723 (0.118) & 2.339 & 0.002\\
+\hspace{1em}nn-cox & -0.005 (0.008) & 0.530 (0.074) & 12.863 & 0.443\\
+\hspace{1em}xgboost-aft & -2.66 (0.438) & 0.763 (0.047) & 8.300 & 0.006\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{FCL; relapse, n = 541, p = 7}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.031 (0.017) & 0.625 (0.020) & 0.270 & 0.003\\
+\hspace{1em}xgboost-cox & 0.014 (0.017) & 0.610 (0.027) & 1.867 & 0.003\\
+\hspace{1em}ranger-extratrees & 0.014 (0.019) & 0.593 (0.031) & 0.032 & 0.079\\
+\hspace{1em}obliqueRSF-net & 0.014 (0.015) & 0.597 (0.027) & 218.615 & 6.376\\
+\hspace{1em}aorsf-random & 0.011 (0.021) & 0.601 (0.029) & 0.428 & 0.021\\
+\hspace{1em}aorsf-cph & 0.009 (0.024) & 0.600 (0.031) & 0.276 & 0.026\\
+\hspace{1em}aorsf-fast & 0.007 (0.024) & 0.599 (0.031) & 0.116 & 0.024\\
+\hspace{1em}aorsf-net & 0.007 (0.026) & 0.597 (0.033) & 18.700 & 0.022\\
+\hspace{1em}cif-standard & 0.005 (0.020) & 0.598 (0.026) & 0.282 & 1.105\\
+\hspace{1em}nn-cox & -0.002 (0.021) & 0.556 (0.057) & 11.608 & 0.458\\
+\hspace{1em}cif-extension & -0.008 (0.026) & 0.583 (0.034) & 5.355 & 2.231\\
+\hspace{1em}cif-rotate & -0.012 (0.025) & 0.590 (0.033) & 6.589 & 2.863\\
+\hspace{1em}rsf-standard & -0.031 (0.035) & 0.580 (0.032) & 0.744 & 0.085\\
+\hspace{1em}xgboost-aft & -0.915 (0.359) & 0.584 (0.047) & 6.551 & 0.006\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{GBSG II; recurrence or death, n = 686, p = 10}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.123 (0.015) & 0.744 (0.017) & 284.837 & 7.018\\
+\hspace{1em}cif-standard & 0.123 (0.020) & 0.743 (0.019) & 0.425 & 1.696\\
+\hspace{1em}rsf-standard & 0.123 (0.022) & 0.738 (0.018) & 0.994 & 0.114\\
+\hspace{1em}aorsf-net & 0.121 (0.022) & 0.738 (0.018) & 38.168 & 0.038\\
+\hspace{1em}aorsf-cph & 0.118 (0.026) & 0.733 (0.018) & 0.405 & 0.041\\
+\hspace{1em}aorsf-fast & 0.115 (0.025) & 0.731 (0.018) & 0.165 & 0.041\\
+\hspace{1em}cif-extension & 0.115 (0.020) & 0.744 (0.022) & 8.087 & 3.238\\
+\hspace{1em}cif-rotate & 0.111 (0.022) & 0.731 (0.015) & 10.921 & 2.838\\
+\hspace{1em}aorsf-random & 0.103 (0.028) & 0.721 (0.029) & 0.755 & 0.037\\
+\hspace{1em}ranger-extratrees & 0.092 (0.024) & 0.738 (0.032) & 0.062 & 0.177\\
+\hspace{1em}xgboost-cox & 0.084 (0.014) & 0.728 (0.018) & 3.312 & 0.004\\
+\hspace{1em}glmnet-cox & 0.081 (0.019) & 0.722 (0.022) & 0.118 & 0.003\\
+\hspace{1em}nn-cox & -0.004 (0.005) & 0.509 (0.040) & 14.255 & 1.400\\
+\hspace{1em}xgboost-aft & -1.09 (0.122) & 0.728 (0.019) & 9.463 & 0.006\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{GUIDE-IT; CVD death, n = 894, p = 59}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.077 (0.020) & 0.746 (0.033) & 0.176 & 0.039\\
+\hspace{1em}aorsf-net & 0.074 (0.019) & 0.743 (0.033) & 28.167 & 0.039\\
+\hspace{1em}glmnet-cox & 0.074 (0.041) & 0.729 (0.085) & 0.514 & 0.003\\
+\hspace{1em}aorsf-cph & 0.072 (0.021) & 0.740 (0.038) & 0.416 & 0.039\\
+\hspace{1em}obliqueRSF-net & 0.064 (0.013) & 0.738 (0.028) & 239.059 & 11.676\\
+\hspace{1em}cif-rotate & 0.062 (0.017) & 0.715 (0.029) & 34.699 & 4.860\\
+\hspace{1em}cif-standard & 0.059 (0.014) & 0.732 (0.027) & 0.790 & 3.278\\
+\hspace{1em}cif-extension & 0.053 (0.011) & 0.724 (0.029) & 14.497 & 6.192\\
+\hspace{1em}ranger-extratrees & 0.052 (0.014) & 0.731 (0.031) & 0.779 & 0.461\\
+\hspace{1em}rsf-standard & 0.047 (0.026) & 0.709 (0.032) & 0.177 & 0.059\\
+\hspace{1em}aorsf-random & 0.033 (0.010) & 0.692 (0.035) & 0.489 & 0.040\\
+\hspace{1em}xgboost-cox & 0.031 (0.052) & 0.743 (0.024) & 5.143 & 0.003\\
+\hspace{1em}nn-cox & 0.028 (0.038) & 0.684 (0.085) & 13.230 & 0.544\\
+\hspace{1em}xgboost-aft & -5.44 (1.23) & 0.729 (0.023) & 13.003 & 0.006\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{GUIDE-IT; HF hospitalization, n = 894, p = 59}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.083 (0.021) & 0.724 (0.027) & 0.707 & 0.057\\
+\hspace{1em}aorsf-net & 0.083 (0.020) & 0.722 (0.024) & 53.989 & 0.059\\
+\hspace{1em}aorsf-fast & 0.083 (0.022) & 0.724 (0.026) & 0.258 & 0.056\\
+\hspace{1em}obliqueRSF-net & 0.074 (0.013) & 0.721 (0.024) & 370.352 & 8.931\\
+\hspace{1em}ranger-extratrees & 0.073 (0.014) & 0.720 (0.027) & 0.501 & 0.191\\
+\hspace{1em}cif-standard & 0.069 (0.012) & 0.714 (0.024) & 0.795 & 3.266\\
+\hspace{1em}cif-rotate & 0.067 (0.023) & 0.706 (0.031) & 40.710 & 5.037\\
+\hspace{1em}glmnet-cox & 0.066 (0.022) & 0.705 (0.026) & 0.415 & 0.003\\
+\hspace{1em}cif-extension & 0.063 (0.010) & 0.714 (0.019) & 16.510 & 6.373\\
+\hspace{1em}rsf-standard & 0.055 (0.028) & 0.693 (0.028) & 1.136 & 0.117\\
+\hspace{1em}aorsf-random & 0.051 (0.013) & 0.688 (0.028) & 0.880 & 0.054\\
+\hspace{1em}nn-cox & 0.047 (0.032) & 0.686 (0.061) & 14.014 & 0.620\\
+\hspace{1em}xgboost-cox & 0.041 (0.013) & 0.699 (0.028) & 3.763 & 0.003\\
+\hspace{1em}xgboost-aft & -2.23 (0.339) & 0.695 (0.029) & 16.064 & 0.007\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Heart Transplant; graft-loss or death, n = 3787, p = 52}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.056 (0.012) & 0.729 (0.022) & 159.153 & 20.730\\
+\hspace{1em}aorsf-fast & 0.052 (0.008) & 0.733 (0.020) & 0.893 & 0.234\\
+\hspace{1em}aorsf-cph & 0.052 (0.008) & 0.731 (0.018) & 3.216 & 0.237\\
+\hspace{1em}aorsf-net & 0.052 (0.008) & 0.730 (0.018) & 123.347 & 0.229\\
+\hspace{1em}rsf-standard & 0.051 (0.009) & 0.728 (0.014) & 2.186 & 0.832\\
+\hspace{1em}cif-standard & 0.049 (0.008) & 0.730 (0.018) & 10.333 & 36.554\\
+\hspace{1em}obliqueRSF-net & 0.049 (0.007) & 0.728 (0.020) & 387.022 & 78.390\\
+\hspace{1em}ranger-extratrees & 0.045 (0.008) & 0.727 (0.017) & 5.104 & 6.168\\
+\hspace{1em}glmnet-cox & 0.035 (0.007) & 0.707 (0.020) & 1.413 & 0.006\\
+\hspace{1em}cif-extension & 0.035 (0.004) & 0.725 (0.022) & 50.118 & 18.785\\
+\hspace{1em}xgboost-cox & 0.029 (0.008) & 0.715 (0.025) & 4.244 & 0.007\\
+\hspace{1em}nn-cox & 0.029 (0.014) & 0.693 (0.024) & 14.198 & 8.076\\
+\hspace{1em}aorsf-random & 0.028 (0.003) & 0.685 (0.013) & 2.307 & 0.217\\
+\hspace{1em}xgboost-aft & -4.31 (0.500) & 0.720 (0.012) & 13.609 & 0.007\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{MESA; coronary heart disease, n = 6785, p = 48}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.064 (0.011) & 0.807 (0.007) & 1.306 & 0.374\\
+\hspace{1em}aorsf-net & 0.063 (0.012) & 0.803 (0.008) & 174.087 & 0.379\\
+\hspace{1em}obliqueRSF-net & 0.061 (0.008) & 0.806 (0.007) & 486.618 & 269.151\\
+\hspace{1em}aorsf-cph & 0.061 (0.011) & 0.801 (0.010) & 5.635 & 0.385\\
+\hspace{1em}cif-rotate & 0.058 (0.008) & 0.801 (0.010) & 311.704 & 46.721\\
+\hspace{1em}cif-standard & 0.058 (0.007) & 0.801 (0.009) & 24.315 & 98.498\\
+\hspace{1em}rsf-standard & 0.056 (0.014) & 0.794 (0.011) & 4.745 & 0.433\\
+\hspace{1em}ranger-extratrees & 0.047 (0.005) & 0.795 (0.007) & 6.566 & 11.394\\
+\hspace{1em}cif-extension & 0.047 (0.004) & 0.803 (0.008) & 103.940 & 34.786\\
+\hspace{1em}glmnet-cox & 0.040 (0.021) & 0.774 (0.009) & 5.519 & 0.006\\
+\hspace{1em}nn-cox & 0.032 (0.025) & 0.760 (0.030) & 22.091 & 19.964\\
+\hspace{1em}aorsf-random & 0.032 (0.006) & 0.740 (0.015) & 4.558 & 0.516\\
+\hspace{1em}xgboost-cox & 0.013 (0.019) & 0.804 (0.007) & 5.369 & 0.010\\
+\hspace{1em}xgboost-aft & -9.73 (1.00) & 0.802 (0.008) & 26.660 & 0.011\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{MESA; death, n = 6793, p = 48}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.144 (0.009) & 0.791 (0.010) & 316.581 & 0.547\\
+\hspace{1em}aorsf-fast & 0.143 (0.009) & 0.791 (0.011) & 1.936 & 0.562\\
+\hspace{1em}aorsf-cph & 0.143 (0.008) & 0.790 (0.010) & 7.232 & 0.533\\
+\hspace{1em}rsf-standard & 0.140 (0.009) & 0.783 (0.011) & 3.983 & 0.470\\
+\hspace{1em}obliqueRSF-net & 0.138 (0.008) & 0.789 (0.011) & 1248.639 & 166.262\\
+\hspace{1em}cif-standard & 0.133 (0.007) & 0.786 (0.011) & 23.230 & 98.540\\
+\hspace{1em}cif-rotate & 0.124 (0.007) & 0.779 (0.011) & 322.280 & 37.520\\
+\hspace{1em}glmnet-cox & 0.114 (0.022) & 0.782 (0.012) & 1.774 & 0.007\\
+\hspace{1em}ranger-extratrees & 0.113 (0.005) & 0.783 (0.010) & 7.801 & 17.881\\
+\hspace{1em}nn-cox & 0.113 (0.041) & 0.756 (0.091) & 54.045 & 35.720\\
+\hspace{1em}cif-extension & 0.092 (0.003) & 0.778 (0.010) & 108.878 & 32.320\\
+\hspace{1em}aorsf-random & 0.070 (0.004) & 0.727 (0.008) & 7.162 & 0.550\\
+\hspace{1em}xgboost-cox & 0.057 (0.032) & 0.791 (0.010) & 10.747 & 0.010\\
+\hspace{1em}xgboost-aft & -4.50 (0.243) & 0.789 (0.009) & 18.378 & 0.010\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{MESA; heart failure, n = 6785, p = 48}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.114 (0.011) & 0.866 (0.014) & 1.172 & 0.324\\
+\hspace{1em}aorsf-net & 0.114 (0.011) & 0.864 (0.016) & 147.986 & 0.338\\
+\hspace{1em}aorsf-cph & 0.109 (0.010) & 0.858 (0.017) & 5.602 & 0.339\\
+\hspace{1em}rsf-standard & 0.108 (0.012) & 0.857 (0.013) & 2.784 & 0.895\\
+\hspace{1em}obliqueRSF-net & 0.107 (0.009) & 0.868 (0.014) & 391.939 & 332.468\\
+\hspace{1em}cif-rotate & 0.106 (0.011) & 0.873 (0.014) & 259.218 & 35.800\\
+\hspace{1em}cif-standard & 0.101 (0.010) & 0.863 (0.015) & 23.601 & 96.846\\
+\hspace{1em}nn-cox & 0.083 (0.015) & 0.828 (0.024) & 18.796 & 15.505\\
+\hspace{1em}cif-extension & 0.077 (0.005) & 0.864 (0.012) & 91.823 & 30.050\\
+\hspace{1em}ranger-extratrees & 0.075 (0.006) & 0.847 (0.018) & 7.714 & 11.655\\
+\hspace{1em}aorsf-random & 0.063 (0.006) & 0.795 (0.019) & 3.483 & 0.375\\
+\hspace{1em}glmnet-cox & 0.056 (0.047) & 0.779 (0.148) & 3.484 & 0.011\\
+\hspace{1em}xgboost-cox & -0.008 (0.011) & 0.873 (0.012) & 8.137 & 0.010\\
+\hspace{1em}xgboost-aft & -10.9 (1.08) & 0.873 (0.015) & 18.818 & 0.010\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{MESA; stroke, n = 6783, p = 48}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.025 (0.004) & 0.766 (0.018) & 269.642 & 35.908\\
+\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.766 (0.015) & 1.144 & 0.325\\
+\hspace{1em}glmnet-cox & 0.025 (0.006) & 0.769 (0.017) & 3.082 & 0.006\\
+\hspace{1em}obliqueRSF-net & 0.024 (0.004) & 0.767 (0.016) & 357.106 & 281.765\\
+\hspace{1em}cif-standard & 0.024 (0.004) & 0.763 (0.018) & 24.960 & 98.465\\
+\hspace{1em}aorsf-net & 0.024 (0.006) & 0.759 (0.016) & 138.120 & 0.340\\
+\hspace{1em}aorsf-cph & 0.024 (0.005) & 0.759 (0.016) & 4.983 & 0.325\\
+\hspace{1em}ranger-extratrees & 0.021 (0.003) & 0.758 (0.018) & 7.114 & 11.973\\
+\hspace{1em}cif-extension & 0.021 (0.002) & 0.772 (0.019) & 95.005 & 32.157\\
+\hspace{1em}rsf-standard & 0.019 (0.010) & 0.745 (0.020) & 2.679 & 0.865\\
+\hspace{1em}nn-cox & 0.017 (0.005) & 0.732 (0.037) & 18.484 & 20.376\\
+\hspace{1em}aorsf-random & 0.013 (0.003) & 0.713 (0.026) & 3.517 & 0.343\\
+\hspace{1em}xgboost-cox & 0.003 (0.021) & 0.765 (0.023) & 5.210 & 0.009\\
+\hspace{1em}xgboost-aft & -13.9 (1.53) & 0.769 (0.018) & 17.608 & 0.009\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Monoclonal gammopathy; death, n = 1384, p = 8}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.157 (0.017) & 0.741 (0.012) & 1.325 & 0.103\\
+\hspace{1em}cif-rotate & 0.156 (0.023) & 0.742 (0.018) & 15.136 & 4.979\\
+\hspace{1em}aorsf-fast & 0.155 (0.017) & 0.741 (0.012) & 0.434 & 0.097\\
+\hspace{1em}obliqueRSF-net & 0.153 (0.015) & 0.742 (0.014) & 231.507 & 12.455\\
+\hspace{1em}aorsf-net & 0.152 (0.017) & 0.739 (0.012) & 90.204 & 0.085\\
+\hspace{1em}cif-standard & 0.148 (0.017) & 0.736 (0.013) & 0.928 & 5.907\\
+\hspace{1em}rsf-standard & 0.148 (0.018) & 0.735 (0.012) & 1.988 & 0.193\\
+\hspace{1em}aorsf-random & 0.145 (0.014) & 0.734 (0.013) & 1.821 & 0.085\\
+\hspace{1em}cif-extension & 0.141 (0.010) & 0.744 (0.015) & 9.939 & 4.749\\
+\hspace{1em}glmnet-cox & 0.129 (0.019) & 0.722 (0.014) & 0.308 & 0.003\\
+\hspace{1em}xgboost-cox & 0.123 (0.012) & 0.731 (0.014) & 5.767 & 0.005\\
+\hspace{1em}ranger-extratrees & 0.115 (0.005) & 0.742 (0.014) & 0.062 & 0.364\\
+\hspace{1em}nn-cox & 0.062 (0.071) & 0.632 (0.118) & 17.238 & 0.720\\
+\hspace{1em}xgboost-aft & -0.870 (0.112) & 0.732 (0.016) & 15.477 & 0.007\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Monoclonal gammopathy; malignancy, n = 1384, p = 8}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.018 (0.010) & 0.674 (0.032) & 0.324 & 0.002\\
+\hspace{1em}aorsf-cph & 0.011 (0.009) & 0.646 (0.037) & 0.650 & 0.044\\
+\hspace{1em}xgboost-cox & 0.010 (0.007) & 0.647 (0.042) & 1.962 & 0.003\\
+\hspace{1em}aorsf-fast & 0.010 (0.009) & 0.642 (0.038) & 0.194 & 0.044\\
+\hspace{1em}obliqueRSF-net & 0.008 (0.006) & 0.635 (0.032) & 39.065 & 15.966\\
+\hspace{1em}ranger-extratrees & 0.007 (0.007) & 0.644 (0.035) & 0.061 & 0.197\\
+\hspace{1em}cif-extension & 0.007 (0.008) & 0.629 (0.028) & 8.637 & 4.451\\
+\hspace{1em}cif-standard & 0.007 (0.007) & 0.630 (0.032) & 0.956 & 6.010\\
+\hspace{1em}aorsf-net & 0.006 (0.010) & 0.645 (0.036) & 23.264 & 0.042\\
+\hspace{1em}aorsf-random & 0.006 (0.014) & 0.639 (0.037) & 0.519 & 0.042\\
+\hspace{1em}nn-cox & -0.005 (0.006) & 0.528 (0.083) & 10.752 & 0.593\\
+\hspace{1em}rsf-standard & -0.009 (0.015) & 0.626 (0.032) & 0.634 & 0.069\\
+\hspace{1em}cif-rotate & -0.034 (0.022) & 0.545 (0.032) & 12.464 & 4.154\\
+\hspace{1em}xgboost-aft & -5.78 (1.22) & 0.627 (0.045) & 9.325 & 0.006\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Movies released in 2015-2018; gross 1M USD, n = 551, p = 46}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.645 (0.026) & 0.945 (0.008) & 20.183 & 3.526\\
+\hspace{1em}glmnet-cox & 0.629 (0.037) & 0.940 (0.011) & 0.198 & 0.003\\
+\hspace{1em}aorsf-net & 0.535 (0.033) & 0.929 (0.012) & 50.651 & 0.044\\
+\hspace{1em}aorsf-cph & 0.527 (0.024) & 0.926 (0.013) & 0.792 & 0.045\\
+\hspace{1em}rsf-standard & 0.525 (0.023) & 0.923 (0.013) & 0.746 & 0.105\\
+\hspace{1em}aorsf-fast & 0.521 (0.029) & 0.923 (0.015) & 0.218 & 0.044\\
+\hspace{1em}xgboost-cox & 0.515 (0.029) & 0.933 (0.011) & 14.297 & 0.005\\
+\hspace{1em}nn-cox & 0.497 (0.143) & 0.889 (0.056) & 16.418 & 0.705\\
+\hspace{1em}cif-standard & 0.472 (0.030) & 0.900 (0.021) & 0.379 & 1.292\\
+\hspace{1em}cif-extension & 0.449 (0.026) & 0.919 (0.015) & 8.850 & 3.931\\
+\hspace{1em}ranger-extratrees & 0.432 (0.019) & 0.896 (0.020) & 0.070 & 0.127\\
+\hspace{1em}obliqueRSF-net & 0.318 (0.025) & 0.908 (0.021) & 152.602 & 9.347\\
+\hspace{1em}aorsf-random & 0.293 (0.041) & 0.841 (0.034) & 0.999 & 0.041\\
+\hspace{1em}xgboost-aft & -0.435 (0.057) & 0.930 (0.011) & 28.847 & 0.007\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Non-alcohol fatty liver disease; death, n = 17549, p = 24}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.214 (0.009) & 0.871 (0.005) & 20.799 & 1.406\\
+\hspace{1em}aorsf-fast & 0.214 (0.010) & 0.871 (0.006) & 4.828 & 1.422\\
+\hspace{1em}aorsf-net & 0.212 (0.009) & 0.867 (0.006) & 446.975 & 1.285\\
+\hspace{1em}obliqueRSF-net & 0.210 (0.008) & 0.870 (0.006) & 1520.102 & 1097.379\\
+\hspace{1em}glmnet-cox & 0.209 (0.010) & 0.861 (0.005) & 2.153 & 0.014\\
+\hspace{1em}rsf-standard & 0.207 (0.009) & 0.860 (0.006) & 11.043 & 1.209\\
+\hspace{1em}cif-standard & 0.206 (0.007) & 0.864 (0.007) & 65.607 & 616.634\\
+\hspace{1em}cif-rotate & 0.191 (0.006) & 0.866 (0.005) & 256.009 & 62.262\\
+\hspace{1em}ranger-extratrees & 0.182 (0.007) & 0.862 (0.005) & 40.654 & 303.362\\
+\hspace{1em}cif-extension & 0.167 (0.003) & 0.868 (0.006) & 122.213 & 55.889\\
+\hspace{1em}aorsf-random & 0.142 (0.007) & 0.843 (0.006) & 11.433 & 1.500\\
+\hspace{1em}xgboost-cox & 0.020 (0.015) & 0.876 (0.005) & 11.932 & 0.021\\
+\hspace{1em}nn-cox & -0.001 (0.003) & 0.580 (0.090) & 21.950 & 95.510\\
+\hspace{1em}xgboost-aft & -7.74 (0.684) & 0.875 (0.006) & 33.565 & 0.015\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Primary biliary cholangitis; death, n = 276, p = 19}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.436 (0.026) & 0.909 (0.020) & 0.071 & 0.021\\
+\hspace{1em}aorsf-cph & 0.423 (0.027) & 0.908 (0.019) & 0.152 & 0.020\\
+\hspace{1em}aorsf-net & 0.415 (0.031) & 0.907 (0.020) & 13.638 & 0.018\\
+\hspace{1em}cif-rotate & 0.404 (0.043) & 0.901 (0.022) & 9.187 & 2.214\\
+\hspace{1em}rsf-standard & 0.397 (0.023) & 0.895 (0.020) & 0.087 & 0.036\\
+\hspace{1em}obliqueRSF-net & 0.366 (0.034) & 0.908 (0.020) & 106.606 & 1.721\\
+\hspace{1em}aorsf-random & 0.353 (0.028) & 0.895 (0.020) & 0.288 & 0.019\\
+\hspace{1em}cif-standard & 0.344 (0.034) & 0.904 (0.023) & 0.185 & 0.362\\
+\hspace{1em}glmnet-cox & 0.343 (0.059) & 0.894 (0.024) & 0.120 & 0.003\\
+\hspace{1em}cif-extension & 0.341 (0.032) & 0.904 (0.019) & 5.195 & 2.236\\
+\hspace{1em}ranger-extratrees & 0.267 (0.029) & 0.897 (0.023) & 0.027 & 0.037\\
+\hspace{1em}xgboost-cox & 0.250 (0.108) & 0.881 (0.027) & 6.107 & 0.003\\
+\hspace{1em}nn-cox & -0.028 (0.019) & 0.652 (0.123) & 9.552 & 0.240\\
+\hspace{1em}xgboost-aft & -0.905 (0.366) & 0.885 (0.021) & 8.233 & 0.005\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Rotterdam tumor bank; death, n = 2982, p = 11}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.165 (0.010) & 0.760 (0.008) & 148.475 & 0.186\\
+\hspace{1em}obliqueRSF-net & 0.162 (0.009) & 0.760 (0.009) & 439.574 & 36.953\\
+\hspace{1em}aorsf-cph & 0.161 (0.010) & 0.758 (0.009) & 2.601 & 0.205\\
+\hspace{1em}aorsf-fast & 0.159 (0.011) & 0.756 (0.009) & 0.809 & 0.206\\
+\hspace{1em}cif-standard & 0.159 (0.008) & 0.759 (0.008) & 4.308 & 23.147\\
+\hspace{1em}rsf-standard & 0.157 (0.011) & 0.755 (0.008) & 2.754 & 0.522\\
+\hspace{1em}aorsf-random & 0.153 (0.007) & 0.752 (0.009) & 2.869 & 0.184\\
+\hspace{1em}cif-rotate & 0.151 (0.012) & 0.754 (0.013) & 33.457 & 8.469\\
+\hspace{1em}ranger-extratrees & 0.139 (0.005) & 0.749 (0.009) & 2.721 & 3.105\\
+\hspace{1em}xgboost-cox & 0.134 (0.011) & 0.754 (0.010) & 4.785 & 0.005\\
+\hspace{1em}cif-extension & 0.130 (0.005) & 0.751 (0.009) & 24.345 & 9.889\\
+\hspace{1em}glmnet-cox & 0.120 (0.007) & 0.733 (0.010) & 0.499 & 0.004\\
+\hspace{1em}nn-cox & -0.028 (0.087) & 0.535 (0.057) & 16.443 & 7.747\\
+\hspace{1em}xgboost-aft & -1.37 (0.126) & 0.759 (0.008) & 14.195 & 0.007\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Rotterdam tumor bank; recurrence, n = 2982, p = 11}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.148 (0.011) & 0.738 (0.011) & 513.045 & 37.957\\
+\hspace{1em}aorsf-net & 0.147 (0.012) & 0.736 (0.011) & 169.714 & 0.197\\
+\hspace{1em}aorsf-cph & 0.145 (0.012) & 0.735 (0.010) & 2.867 & 0.216\\
+\hspace{1em}cif-standard & 0.144 (0.012) & 0.735 (0.011) & 4.369 & 23.006\\
+\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.734 (0.010) & 0.896 & 0.218\\
+\hspace{1em}aorsf-random & 0.140 (0.010) & 0.731 (0.010) & 3.326 & 0.191\\
+\hspace{1em}rsf-standard & 0.138 (0.011) & 0.732 (0.009) & 2.809 & 0.281\\
+\hspace{1em}ranger-extratrees & 0.135 (0.008) & 0.735 (0.011) & 2.807 & 2.778\\
+\hspace{1em}cif-rotate & 0.133 (0.009) & 0.728 (0.010) & 35.059 & 8.648\\
+\hspace{1em}cif-extension & 0.119 (0.007) & 0.733 (0.010) & 22.197 & 8.887\\
+\hspace{1em}glmnet-cox & 0.118 (0.007) & 0.728 (0.011) & 0.498 & 0.004\\
+\hspace{1em}xgboost-cox & 0.114 (0.007) & 0.730 (0.012) & 4.233 & 0.005\\
+\hspace{1em}nn-cox & -0.002 (0.002) & 0.491 (0.028) & 24.631 & 11.769\\
+\hspace{1em}xgboost-aft & -1.06 (0.147) & 0.735 (0.011) & 13.403 & 0.007\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Serum free light chain; death, n = 7874, p = 10}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.256 (0.016) & 0.826 (0.010) & 2.468 & 0.600\\
+\hspace{1em}aorsf-cph & 0.255 (0.016) & 0.826 (0.011) & 7.124 & 0.601\\
+\hspace{1em}aorsf-net & 0.254 (0.014) & 0.824 (0.011) & 274.793 & 0.556\\
+\hspace{1em}obliqueRSF-net & 0.251 (0.014) & 0.822 (0.011) & 1071.189 & 145.107\\
+\hspace{1em}glmnet-cox & 0.251 (0.015) & 0.821 (0.010) & 0.546 & 0.011\\
+\hspace{1em}rsf-standard & 0.247 (0.016) & 0.817 (0.011) & 5.052 & 0.549\\
+\hspace{1em}cif-standard & 0.247 (0.014) & 0.819 (0.011) & 18.346 & 116.811\\
+\hspace{1em}ranger-extratrees & 0.247 (0.012) & 0.822 (0.010) & 7.234 & 16.737\\
+\hspace{1em}aorsf-random & 0.236 (0.014) & 0.819 (0.011) & 6.056 & 0.566\\
+\hspace{1em}cif-rotate & 0.228 (0.010) & 0.819 (0.009) & 62.380 & 20.093\\
+\hspace{1em}cif-extension & 0.202 (0.005) & 0.821 (0.010) & 43.862 & 21.183\\
+\hspace{1em}xgboost-cox & 0.104 (0.034) & 0.824 (0.011) & 6.743 & 0.009\\
+\hspace{1em}nn-cox & 0.001 (0.003) & 0.610 (0.135) & 23.112 & 21.723\\
+\hspace{1em}xgboost-aft & -2.75 (0.305) & 0.824 (0.011) & 30.052 & 0.009\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{SPRINT; CVD death, n = 9361, p = 174}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.070 (0.007) & 0.792 (0.008) & 12.779 & 0.016\\
+\hspace{1em}aorsf-cph & 0.067 (0.005) & 0.791 (0.010) & 10.753 & 0.649\\
+\hspace{1em}aorsf-net & 0.067 (0.005) & 0.788 (0.010) & 339.857 & 0.652\\
+\hspace{1em}aorsf-fast & 0.067 (0.004) & 0.791 (0.010) & 2.950 & 0.653\\
+\hspace{1em}obliqueRSF-net & 0.066 (0.004) & 0.790 (0.011) & 1071.167 & 425.299\\
+\hspace{1em}rsf-standard & 0.062 (0.006) & 0.780 (0.015) & 4.271 & 0.599\\
+\hspace{1em}cif-standard & 0.060 (0.003) & 0.791 (0.010) & 47.426 & 180.930\\
+\hspace{1em}cif-rotate & 0.059 (0.005) & 0.783 (0.008) & 941.817 & 112.906\\
+\hspace{1em}ranger-extratrees & 0.053 (0.003) & 0.786 (0.013) & 5.733 & 9.972\\
+\hspace{1em}nn-cox & 0.042 (0.013) & 0.765 (0.016) & 22.162 & 29.154\\
+\hspace{1em}cif-extension & 0.033 (0.002) & 0.782 (0.008) & 121.313 & 32.071\\
+\hspace{1em}aorsf-random & 0.025 (0.002) & 0.736 (0.013) & 5.621 & 0.772\\
+\hspace{1em}xgboost-cox & 0.011 (0.017) & 0.793 (0.009) & 8.908 & 0.014\\
+\hspace{1em}xgboost-aft & -10.7 (0.681) & 0.789 (0.011) & 24.248 & 0.015\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{SPRINT; death, n = 9361, p = 174}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.123 (0.008) & 0.770 (0.010) & 4.957 & 0.011\\
+\hspace{1em}aorsf-cph & 0.116 (0.006) & 0.769 (0.008) & 14.405 & 1.433\\
+\hspace{1em}aorsf-fast & 0.115 (0.007) & 0.768 (0.007) & 4.124 & 1.494\\
+\hspace{1em}aorsf-net & 0.112 (0.007) & 0.766 (0.008) & 591.726 & 0.942\\
+\hspace{1em}obliqueRSF-net & 0.111 (0.006) & 0.766 (0.008) & 2920.730 & 233.477\\
+\hspace{1em}rsf-standard & 0.109 (0.006) & 0.760 (0.007) & 6.036 & 0.711\\
+\hspace{1em}cif-standard & 0.105 (0.006) & 0.763 (0.009) & 48.060 & 191.307\\
+\hspace{1em}nn-cox & 0.098 (0.010) & 0.752 (0.013) & 29.086 & 28.125\\
+\hspace{1em}ranger-extratrees & 0.096 (0.005) & 0.755 (0.008) & 10.665 & 22.541\\
+\hspace{1em}cif-rotate & 0.091 (0.005) & 0.744 (0.008) & 1083.768 & 118.583\\
+\hspace{1em}cif-extension & 0.055 (0.002) & 0.745 (0.008) & 135.963 & 32.414\\
+\hspace{1em}aorsf-random & 0.051 (0.004) & 0.717 (0.010) & 9.053 & 1.029\\
+\hspace{1em}xgboost-cox & 0.034 (0.025) & 0.771 (0.008) & 12.900 & 0.015\\
+\hspace{1em}xgboost-aft & -4.49 (0.313) & 0.771 (0.007) & 23.081 & 0.013\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{Systolic Heart Failure; death, n = 2231, p = 41}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.117 (0.011) & 0.747 (0.013) & 0.304 & 0.004\\
+\hspace{1em}obliqueRSF-net & 0.115 (0.010) & 0.747 (0.010) & 376.210 & 26.092\\
+\hspace{1em}cif-rotate & 0.114 (0.011) & 0.741 (0.011) & 70.159 & 10.535\\
+\hspace{1em}aorsf-net & 0.113 (0.012) & 0.744 (0.012) & 121.294 & 0.159\\
+\hspace{1em}aorsf-cph & 0.113 (0.012) & 0.745 (0.011) & 1.987 & 0.150\\
+\hspace{1em}aorsf-fast & 0.111 (0.015) & 0.744 (0.011) & 0.616 & 0.151\\
+\hspace{1em}cif-standard & 0.110 (0.009) & 0.744 (0.010) & 3.623 & 15.504\\
+\hspace{1em}rsf-standard & 0.107 (0.011) & 0.737 (0.010) & 2.132 & 0.244\\
+\hspace{1em}cif-extension & 0.095 (0.004) & 0.744 (0.011) & 28.859 & 9.866\\
+\hspace{1em}xgboost-cox & 0.092 (0.007) & 0.746 (0.010) & 5.858 & 0.006\\
+\hspace{1em}ranger-extratrees & 0.090 (0.008) & 0.734 (0.012) & 2.841 & 1.923\\
+\hspace{1em}aorsf-random & 0.080 (0.004) & 0.727 (0.009) & 2.143 & 0.147\\
+\hspace{1em}nn-cox & 0.072 (0.029) & 0.705 (0.034) & 33.965 & 7.798\\
+\hspace{1em}xgboost-aft & -2.02 (0.169) & 0.741 (0.010) & 15.753 & 0.007\\
+\addlinespace[0.3em]
+\hline
+\multicolumn{5}{l}{\textit{\textbf{VA lung cancer trial; death, n = 137, p = 8}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.197 (0.066) & 0.791 (0.036) & 5.405 & 1.442\\
+\hspace{1em}aorsf-fast & 0.191 (0.049) & 0.792 (0.039) & 0.052 & 0.013\\
+\hspace{1em}aorsf-cph & 0.190 (0.055) & 0.793 (0.043) & 0.100 & 0.014\\
+\hspace{1em}aorsf-net & 0.189 (0.050) & 0.793 (0.041) & 9.623 & 0.012\\
+\hspace{1em}rsf-standard & 0.162 (0.048) & 0.777 (0.046) & 0.069 & 0.026\\
+\hspace{1em}cif-extension & 0.160 (0.052) & 0.787 (0.039) & 3.746 & 1.229\\
+\hspace{1em}glmnet-cox & 0.145 (0.031) & 0.790 (0.033) & 0.286 & 0.002\\
+\hspace{1em}aorsf-random & 0.143 (0.052) & 0.774 (0.046) & 0.244 & 0.012\\
+\hspace{1em}cif-standard & 0.121 (0.041) & 0.769 (0.039) & 0.096 & 0.122\\
+\hspace{1em}obliqueRSF-net & 0.117 (0.038) & 0.796 (0.028) & 60.816 & 0.674\\
+\hspace{1em}ranger-extratrees & 0.079 (0.039) & 0.775 (0.044) & 0.022 & 0.028\\
+\hspace{1em}xgboost-cox & 0.027 (0.068) & 0.725 (0.046) & 1.223 & 0.003\\
+\hspace{1em}xgboost-aft & -0.011 (0.112) & 0.757 (0.053) & 5.323 & 0.006\\
+\hspace{1em}nn-cox & -0.037 (0.043) & 0.555 (0.067) & 10.089 & 0.118\\*
 \end{longtable}

### 2022-06-29 R/bench_pred.R

@@ -71,6 +71,11 @@ bench_pred <- function(data_source,
 
   if(is_empty(pred_horizon)) return(NULL)
 
+  if(length(pred_horizon) > 30){
+    pred_horizon <-
+      pred_horizon[floor(seq(1, length(pred_horizon), length.out=30))]
+  }
+
   # Don't pipe here - it can mess up the measurement
   # of time during model fitting and model predictions.
 
@@ -96,7 +101,6 @@ bench_pred <- function(data_source,
     ),
     silent = TRUE
   )
-
 
   score <- tibble(model = model_type,
                   cstat = NA_real_,

### 2022-06-29 R/bench_pred_model_visualize.R

@@ -38,6 +38,10 @@ bench_pred_model_visualize <- function(bm_pred_model,
       ),
       across(
         starts_with("prob"),
+        ~ str_replace(.x, '1.00', '>.999')
+      ),
+      across(
+        starts_with("prob"),
         ~ if_else(model == 'aorsf-fast', '---', .x)
       ),
       metric = factor(metric,
@@ -156,6 +160,16 @@ bench_pred_model_visualize <- function(bm_pred_model,
     )
 
 
-  plts
+  list(fig = plts,
+       data = gg_data %>%
+         mutate(
+           metric = recode(
+             metric,
+             "Scaled integrated Brier score" = 'ibs_scaled',
+             "Time-dependent C-statistic" = 'cstat'
+           )
+         )
+  )
+
 
 }

### 2022-06-29 R/bench_pred_time_visualize.R

@@ -11,28 +11,39 @@ bench_pred_time_visualize <- function(bm_pred_clean, model_key) {
     select(model, time_fit, time_pred, data) |>
     drop_na() |>
     mutate(time = as.numeric(time_fit) + as.numeric(time_pred),
-           log_time = log(time),
            model = recode(model, !!!deframe(model_key)),
            model = fct_reorder(model, .x = time, .fun = median))
 
-  # medians <- gg_data |>
-  #   group_by(model) |>
-  #   summarize(median_time = median(time)) |>
-  #   mutate(median_time_ratio = median_time / median_time[model == 'aorsf_cph_1'])
+  medians <- gg_data |>
+    group_by(model) |>
+    summarize(time = median(time)) %>%
+    mutate(
+      color = c(
+        rep("white", floor(n()/2)),
+        rep("black", n() - floor(n()/2))
+      )
+    )
 
 
-  ggplot(gg_data) +
+  fig <- ggplot(gg_data) +
     aes(x = time, y = reorder(model, time, FUN=median),
         fill = model) +
     stat_density_ridges(
       quantile_lines = TRUE,
       quantiles = 0.5,
-      bandwidth = 0.3
+      bandwidth = 0.2
     ) +
     scale_x_log10(
       breaks = c(0.01, 0.1, 1, 10, 100, 1000, 10000),
       labels = c("0.01", "0.1", "1", "10", "100", "1,000", "10,000"),
       expand = c(0,0)
+    ) +
+    geom_text(
+      data = medians,
+      hjust = -1/10,
+      vjust = -2.5,
+      color = medians$color,
+      aes(label = table_glue("median: {time}s"))
     ) +
     scale_fill_viridis_d() +
     theme_minimal() +
@@ -43,6 +54,9 @@ bench_pred_time_visualize <- function(bm_pred_clean, model_key) {
           legend.position = '') +
     labs(x = 'Time to fit a model and compute predictions, seconds',
          y = '')
+
+  list(medians = medians,
+       fig = fig)
 
 
 }

### 2022-06-29 R/bench_pred_visualize.R

@@ -62,7 +62,7 @@ bench_pred_visualize_ <- function(
       droplevels()
   }
 
-  data_fig_overall <- bm_pred_inner |>
+  data_smry_overall <- bm_pred_inner |>
     mutate(data = fct_reorder(factor(data), .x = eval)) |>
     group_by(model) |>
     summarize(eval = f_smry(eval)) |>
@@ -78,10 +78,10 @@ bench_pred_visualize_ <- function(
     )
   )
 
-  data_fig <- bm_pred_inner |>
+  data_smry <- bm_pred_inner |>
     group_by(model, data) |>
     summarize(eval = f_smry(eval)) |>
-    bind_rows(data_fig_overall) |>
+    bind_rows(data_smry_overall) |>
     mutate(data = factor(data, levels = data_levels)) |>
     arrange(data, desc(eval)) |>
     mutate(x = as.numeric(fct_rev(data)),
@@ -90,31 +90,40 @@ bench_pred_visualize_ <- function(
     group_by(data) |>
     mutate(x = x + seq(-1/3, 1/3, length.out = n()))
 
-  gg_text_data <- data_fig |>
+  gg_text_data <- data_smry |>
     group_by(data) |>
     summarize(x = median(x)) |>
     mutate(eval = y_col_1)
 
-  data_aorsf <- data_fig |>
-    filter(model == 'aorsf_cph_1')
+  data_aorsf <- data_smry |>
+    filter(model == 'aorsf_fast')
 
-  aorsf_wins <- data_fig |>
-    filter(model != 'aorsf_cph_15',
-           model != 'aorsf_cph_1_filter',
+  aorsf_wins <- data_smry |>
+    filter(model != 'aorsf_cph',
+           model != 'aorsf_fast_filter',
            model != 'aorsf_net',
            model != 'obliqueRSF') |>
     arrange(data, desc(eval)) |>
     mutate(rank = seq(n())) |>
-    filter(rank == 1 & model == 'aorsf_cph_1') |>
+    filter(rank == 1 & model == 'aorsf_fast') |>
     pull(data)
 
-  gg_text_diffs <- data_fig |>
-    filter(model != 'aorsf_cph_15',
-           model != 'aorsf_cph_1_filter',
+  rankings <- data_smry |>
+    filter(model != 'aorsf_cph',
+           model != 'aorsf_fast_filter',
            model != 'aorsf_net',
[…]

### 2022-06-29 R/bm_vi_visualize.R

@@ -1,0 +1,256 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param bm_vi_comb
+bm_vi_visualize <- function(bm_vi_comb) {
+
+  bm_vi_smry <- bm_vi_comb %>%
+    filter(pred_corr_max != .45) %>%
+    arrange(n_obs, pred_corr_max) %>%
+    mutate(
+      intr = (intr_main+intr_hidden_cmbn+intr_hidden_nlin)/3,
+    ) %>%
+    pivot_longer(cols = c(cmbn,
+                          main,
+                          nlin,
+                          intr),
+                 names_to = 'variable') %>%
+    group_by(variable, n_obs, pred_corr_max, model) %>%
+    summarize(value = mean(value, na.rm = TRUE))
+
+  bm_vi_overall <- bm_vi_comb %>%
+    group_by(model) %>%
+    summarize(value = mean(overall)) %>%
+    mutate(variable = 'Overall')
+
+  slide_in <- bm_vi_smry$variable %>%
+    unique() %>%
+    enframe(value = 'variable', name = NULL) %>%
+    split(.$variable)
+
+  data_smry_split <-
+    bind_rows(bm_vi_overall, bm_vi_smry) %>%
+    mutate(variable = factor(variable, levels = c('Overall',
+                                                  'main',
+                                                  'cmbn',
+                                                  'nlin',
+                                                  'intr'))) %>%
+    arrange(variable, n_obs, pred_corr_max, desc(value)) %>%
+    split(.$variable)
+
+  slide_in
+
+  for(i in names(data_smry_split)){
+
+    if(i %in% names(slide_in)){
+
+      data_smry_split[[i]] <- bind_rows(
+        slide_in[[i]],
+        data_smry_split[[i]]
+      )
+
+    }
+
+  }
+
+  .order <-
+    c(
+      "Overall",
+      data_smry_split %>%
+        bind_rows(.id = 'variable') %>%
+        group_by(variable) %>%
+        summarize(m = median(value, na.rm = TRUE)) %>%
+        arrange(m) %>%
+        filter(variable != 'Overall') %>%
+        pull(variable)
+    )
+
+  data_smry_pre <- data_smry_split[.order] %>%
+    bind_rows() %>%
+    mutate(x = paste(variable, n_obs, pred_corr_max, sep = '_'),
[…]

### 2022-06-29 R/model_pred.R

@@ -72,15 +72,15 @@ aorsf_random_pred <- function(object, test, pred_horizon){
   aorsf_pred(object, test, pred_horizon)
 }
 
-aorsf_cph_1_filter_pred <- function(object, test, pred_horizon){
+aorsf_fast_filter_pred <- function(object, test, pred_horizon){
   aorsf_pred(object, test, pred_horizon)
 }
 
-aorsf_cph_15_pred <- function(object, test, pred_horizon){
+aorsf_cph_pred <- function(object, test, pred_horizon){
   aorsf_pred(object, test, pred_horizon)
 }
 
-aorsf_cph_1_pred <- function(object, test, pred_horizon){
+aorsf_fast_pred <- function(object, test, pred_horizon){
   aorsf_pred(object, test, pred_horizon)
 }
 

### 2022-06-29 R/model_varsel.R

@@ -17,8 +17,14 @@ model_varsel <- function(model, train) {
 
   if(model_fitter == 'aorsf'){
 
-    fit <- orsf(Surv(time, status) ~ ., data_train = train,
-                control = orsf_control_cph(iter_max = 10))
+    method <- str_remove(model, '^.*-')
+
+    fit <- orsf(
+      Surv(time, status) ~ .,
+      data_train = train,
+      control = orsf_control_cph(iter_max = 1),
+      importance = if(method == 'shap') 'none' else method
+    )
 
   }
 
@@ -54,7 +60,7 @@ model_varsel <- function(model, train) {
   switch(
     model,
 
-    'aorsf-negation' = {
+    'aorsf-negate' = {
 
       vi <- orsf_vi_negate(fit)
 
@@ -78,6 +84,12 @@ model_varsel <- function(model, train) {
                                 nsim = 10)
 
       vi <- apply(shap, 2, function(x) mean(abs(x)))
+
+    },
+
+    'aorsf-permute' = {
+
+      vi <- orsf_vi_permute(fit)
 
     },
 

### 2022-06-29 _targets.R

@@ -17,16 +17,16 @@ tar_option_set(memory = "transient",
 lapply(list.files("./R", full.names = TRUE), base::source)
 
 model_fitters <- c(
-  'aorsf_cph_1',
-  'aorsf_cph_15',
+  'aorsf_fast',
+  'aorsf_cph',
   'aorsf_random',
-  # 'aorsf_net',
+  'aorsf_net',
   'rotsf',
   'rsfse',
   'cif',
   'cox_net',
   'coxtime',
-  # 'obliqueRSF',
+  'obliqueRSF',
   'xgb_cox',
   'xgb_aft',
   'randomForestSRC',
@@ -68,7 +68,7 @@ analyses_real <- expand_grid(
     "aric_death"
   ),
   model_type = model_fitters,
-  run_seed = 1:15
+  run_seed = 1:12
 ) |>
   mutate(
     data_load_fun = syms(glue("{data_source}_load")),
@@ -77,8 +77,8 @@ analyses_real <- expand_grid(
   )
 
 analyses_sim_pred <- expand_grid(data_source = 'sim',
-                                 n_obs = c(1000, 2500, 5000),
-                                 pred_corr_max = c(0.10, 0.25, .50),
+                                 n_obs = c(500, 1000, 2500),
+                                 pred_corr_max = c(0, 0.15, .30, 0.45),
                                  run_seed = 1:25,
                                  model_type = model_fitters) |>
   mutate(
@@ -109,7 +109,7 @@ tar_plan(
                  run_seed = run_seed),
       resources = tar_resources(
         future = tar_resources_future(
-          resources = list(n_cores=2)
+          resources = list(n_cores=4)
         )
       ),
       memory = "transient",
@@ -191,7 +191,7 @@ tar_plan(
     bench_vi_summarize(bm_vi_comb)
   ),
 
-  # tar_target(bm_vi_viz, bm_vi_visualize(bm_vi_comb)),
+  tar_target(bm_vi_viz, bm_vi_visualize(bm_vi_comb)),
 
 
 ) |>

### 2022-07-09 paper/jmlr/main.Rnw
A.3 shows values from VI

@@
 \usepackage{bm}
+\usepackage{algorithm, algcompatible, algpseudocode}
+\usepackage{eqparbox}
+
+\DeclareMathOperator*{\argmin}{argmin}
+\DeclareMathOperator*{\argmax}{argmax}
+
+\newdimen{\algindent}
+\setlength\algindent{1.5em}          % algorithmic indent=1.5em
+\algnewcommand\LeftComment[2]{%
+\hspace{#1\algindent}$\triangleright$ \eqparbox{COMMENT}{#2} \hfill %
+}
+
+\algnewcommand{\algorithmicgoto}{\textbf{go to}}%
+\algnewcommand{\Goto}[1]{\algorithmicgoto~\ref{#1}}%
 
@@
                       message = FALSE,
-                      dpi = 600)
+                      dpi = 600,
+                      cache = FALSE)
 
-rspec <- round_spec() |>
+rspec <- round_spec() %>%
   round_using_magnitude(digits = c(3, 2, 1, 1),
@@
 tar_load(names = c(bm_pred_clean,
-                   bm_vi_comb,
+                   bm_vi_viz,
                    bm_pred_viz,
@@
 
-The oblique random survival forest (ORSF) is an ensemble method for supervised learning that extends the random survival forest (RSF).
-Trees in the ORSF are grown using linear combinations of variables to create branches in the tree, whereas in the RSF a single variable is used.
-ORSF ensembles often have higher prediction accuracy than RSF ensembles, but the additional computational overhead of fitting ORSF ensembles limits their scope of application.
-In addition, few methods have been developed for interpretation of ORSF ensembles.
-In this article, we introduce and evaluate methods to accelerate the ORSF (\ie, reduce computational overhead) and compute the importance of individual variables in the ORSF We show that our strategy to accelerate the ORSF is up to 500 times faster than existing software for ORSFs (the \texttt{obliqueRSF} R package), and that prediction accuracy of the accelerated ORSF is equivalent or superior to that of existing ORSF methods.
-We estimate importance of variables for the ORSF by negating each coefficient used for the given variable in linear combinations, and then computing the reduction in out-of-bag accuracy.
-We show with simulation that  `negation importance' can discriminate between signal and noise variables, and it outperforms several state-of-the-art variable importance techniques in this task when there is correlation among predictors.
+The oblique random survival forest (RSF) is an ensemble supervised learning method for right-censored outcomes.
+Trees in the oblique RSF are grown using linear combinations of predictors to create branches, whereas in the standard RSF a single predictor is used.
+Oblique RSF ensembles often have higher prediction accuracy than standard RSF ensembles, but the additional computational overhead of finding an optimal combination of predictors is a severe limitation.
+In addition, few methods have been developed for interpretation of oblique RSF ensembles.
+We introduce and evaluate a method to increase computational efficiency of the oblique RSF and a method to estimate importance of individual predictor variables with the oblique RSF.
+Our strategy to reduce computational overhead makes use of Newton-Raphson scoring, a classical optimization technique that we apply to the Cox partial likelihood function.
+We estimate importance of predictors for the oblique RSF by negating each coefficient used for the given predictor in linear combinations, and then computing the reduction in out-of-bag accuracy.
+In numeric experiments, we find that our implementation of the oblique RSF is roughly 500 times faster with equivalent or superior prediction accuracy compared to existing software to fit oblique RSFs.
+We find in simulation studies that `negation importance' discriminates between signal and noise predictors more reliably than permutation importance, Shapley additive explanations, and a previously introduced technique to measure variable importance with oblique RSFs based on analysis of variance.
+All methods pertaining to oblique RSFs in the current study are available in the \texttt{aorsf} R package.
 
@@
 
-Risk prediction can reduce the burden of disease by educating patients and providers and guiding strategies to prevent and treat disease in a wide range of medical domains \citep{moons2012riskII, moons2012riskI}.
-The random survival forest (RSF), a supervised learning algorithm that can engage with censored outcomes, is frequently used for risk prediction.
-Notable characteristics of the RSF include uniform convergence of its ensemble survival function to the true population survival function when the predictor space is discrete \citep{ishwaran2010consistency}.
-In addition, software implementing the RSF is freely available, extremely efficient, and full of tools to interpret and explain the RSF \citep{randomForestSRC, ranger, hothorn2010party}.
-However, there remains considerable potential to improve the RSF in risk prediction tasks where training samples are not large enough to guarantee asymptotic properties or predictor spaces are non-discrete (\ie, predictors are continuous).
+The random survival forest (RSF; \citet{ishwaran2008random, hothorn2006unbiased}) is a supervised learning algorithm that can be used for risk prediction \citep{wang2017selective}, which may reduce the burden of disease by guiding strategies for prevention and treatment in a wide range of medical domains \citep{moons2012riskII, moons2012riskI}.
+Similar to random forests (RFs) for classification and regression \citep{breiman2001random}, The RSF is a large set of de-correlated and randomized decision trees, with each tree contributing to the ensemble's prediction function.
+Notable characteristics of the RSF include uniform convergence of its ensemble survival prediction function to the true survival function, first shown by \citet{ishwaran2010consistency} and later by \citet{cui2017consistency} under more general conditions.
+However, \citet{cui2017consistency} noted that the RSF is at a disadvantage when predictors are correlated and some are not relevant to the censored outcome, which is a strong possibility when large medical databases are leveraged for risk prediction.
 
-RSFs may be axis based or oblique.
-The axis based RSF uses a single predictor whereas the oblique RSF uses a linear combination of predictors to create branches in trees.
-While axis based decision boundaries are always perpendicular to the axis of the relevant predictor, linear combinations of predictors create oblique decision boundaries that are neither parallel nor perpendicular to axes of their contributing predictors.
-Prior work has found the oblique RSF has higher prediction accuracy than the axis based RSF in general benchmarks \citep{jaeger2019oblique} and that oblique splitting is particularly effective when predictors are continuous \citep{menze2011oblique}.
-However, existing methods to implement oblique splitting typically use fully trained models in each non-leaf node to identify linear combinations of predictors, exponentially increasing the number of operations required for the oblique RSF versus its axis based counterpart.
-In addition, standard methods to estimate variable importance (VI) in the RSF are less effective in the oblique RSF, and few methods have been introduced to estimate VI specifically for the oblique RSF.
+A potential approach to improve the RSF when predictors are correlated and some are not relevant to the censored outcome is to use oblique decision trees instead of axis based trees.
+Axis based trees split data using a single predictor, creating decision boundaries that are perpendicular or parallel to axes of the predictor space \citep[see][Chapter~2]{breiman2017classification}.
+Oblique trees split data using a linear combination of predictors, creating decision boundaries that are neither parallel nor perpendicular to axes of their contributing predictors \citep[see][Chapter~5]{breiman2017classification}.
+\citet{menze2011oblique} examined prediction accuracy of RFs in the presence of correlated predictors and found that oblique RFs had substantially higher prediction accuracy compared to axis-based RFs.
+Similarly, \citet{jaeger2019oblique} found that growing RSFs with oblique rather than axis-based survival trees reduced the RSF's concordance error, with improvements ranging from 2.5\% to 24.9\% depending on the data analyzed.
 
-The aim of this article is to improve the computational efficiency and interpretability of the oblique RSF.
-In a general benchmark experiment including \Sexpr{n_risk_tasks} risk prediction tasks, we show that oblique RSFs with partially trained models have equivalent or superior prediction accuracy and are orders of magnitude more efficient than oblique RSFs with fully trained models in non-leaf nodes.
-We introduce a method to estimate VI for oblique RSFs and compare its ability to discriminate between signal and noise variables versus standard and state-of-the-art methods.
-All methods proposed in this article are available in the \texttt{aorsf} R Package.
+Oblique trees have at least two notable drawbacks compared to axis-based trees.
+First, finding a locally optimal oblique decision rule may require exponentially more computation than an axis-based rule.
+If $p$ predictors are potentially used to split $n$ observations, up to $\mathcal{O}(n^p)$ oblique splits can be assessed versus $\mathcal{O}(n \cdot p)$ axis-based splits \citep{heath1993induction, murthy1994system}.
+Second, estimating variable importance (VI) using permutation (a standard method for RFs) may be less effective in ensembles of oblique trees, as permuting the values of one predictor may not destabilize decisions that are based on many predictors.
+Although VI is one of the most widely used strategies to interpret random forests \citep{ishwaran2019standard}, few studies have investigated VI for oblique random forests \citep[see][Section~5]{menze2011oblique}, and fewer have investigated VI specifically for the oblique RSF.
+
+This study makes two contributions to oblique RSFs.
+First, we reduce their computational cost (\ie, accelerate them) with a scalable algorithm to identify linear combinations of coefficients.
+In a general benchmark experiment including \Sexpr{n_risk_tasks} risk prediction tasks, we show that accelerated oblique RSFs are roughly 500 times faster with equivalent or superior prediction accuracy compared to existing routines to fit oblique RSFs.
+Second, we improve their interpretability with `negation VI', a method to estimate VI that engages with coefficients in linear combinations of predictors instead of permuting predictor values.
+In simulation studies where VI is estimate using permutation, analysis of variance (ANOVA; see \citet{menze2011oblique}), and approximations of Shapley values, we find that negation VI improves the oblique RSF's ability to discriminate between correlated signal and noise variables.
+The accelerated oblique RSF and multiple methods to compute VI for oblique RSFs (permutation, ANOVA, and negation) are available in the \texttt{aorsf} R Package.
+
+% However, there remains considerable potential to improve the RSF in settings where training samples are not large enough to guarantee asymptotic properties or do not align with the conditions required for consistency of the RSF.
+
+% Random forests (RFs) are large sets of de-correlated, randomized decision trees \citep{breiman2001random}, which can be axis based or oblique.Although using oblique rather than axis-based trees to grow a RSF may improve its prediction accuracy,
 
@@
 
-After \citet{breiman2001random} introduced the axis-based and oblique random forest (RF), numerous methods were developed to grow oblique RFs for classification or regression tasks \citep{menze2011oblique, zhang2014oblique, rainforth2015canonical, zhu2015reinforcement, poona2016investigating, qiu2017oblique, tomita2020sparse, katuwal2020heterogeneous}.
-However, oblique splitting approaches for classification or regression may not generalize to survival tasks \citep[\eg, see][Section~4.5.1]{zhu2013tree}, and most research involving the RSF has focused on forests with axis-based trees \citep{wang2017selective}.
+After \citet{breiman2001random} introduced the axis-based and oblique RF, numerous methods were developed to grow oblique RFs for classification or regression tasks \citep{menze2011oblique, zhang2014oblique, rainforth2015canonical, zhu2015reinforcement, poona2016investigating, qiu2017oblique, tomita2020sparse, katuwal2020heterogeneous}.
+However, oblique splitting approaches for classification or regression may not generalize to survival \citep[\eg, see][Section~4.5.1]{zhu2013tree}, and most research involving the RSF has focused on forests with axis-based trees \citep{wang2017selective}.
 
@@
 $$ \hat{\beta}^{k+1} =  \hat{\beta}^{k} + U(\hat{\beta} = \hat{\beta}^{k})\, H^{-1}(\hat{\beta} = \hat{\beta}^{k}) $$
+
 For statistical inference, it is recommended to complete iterations of Newton Raphson scoring until a convergence threshold is met.
 However, to identify a valid linear combination of predictors, only one iteration of Newton Raphson scoring is needed.
-It was not clear to us whether completing only one iteration of Newton Raphson scoring would provide coefficients that were stable enough to partition data effectively when we developed this technique, so we analyzed three learners in numerical experiments that assessed prediction accuracy (see \secref{sec:bm_pred}): \begin{itemize}
-\item \texttt{aorsf-extratrees}: Randomly select coefficients for linear combinations of predictors from a uniform distribution.
-\item \texttt{aorsf-fast}: Identify coefficients for linear combinations of predictor variables using one iteration of Newton Raphson scoring.
-\item \texttt{aorsf-cph}: Identify linear combinations of predictor variables using the coefficients derived from a Cox proportional hazards model.
-That is, use the coefficient estimates derived from completing iterations of Newton Raphson scoring until a convergence threshold is met or the number of iterations completed is 15, whichever occurs first.
-\end{itemize}
+In \secref{sec:results_pred}, we formally test whether growing oblique survival trees using one iteration of Newton Raphson scoring is sufficient (\ie, provides equivalent prediction accuracy) compared to iterating until a convergence threshold is met.
+
+Algorithm \ref{alg:aorsf} presents our approach to fitting an oblique survival tree in the accelerated oblique RSF using default values from the \texttt{aorsf} R package.
+Several steps are taken to reduce computational overhead.
+First, memory is conserved by conducting bootstrap resampling via randomly generated bootstrap weights.
+Weights are integer valued, with a weight of $v$ indicating an observation was sampled $v$ times.
+Second, early stopping is applied to the tree growing procedure if a statistical criterion is not met.
+In our case, the criterion is based on the magnitude of a log-rank test statistic corresponding to splitting the data at a current node.
+Third, instead of greedy recursive partitioning, we use a `good enough' approach.
+More specifically, instead of computing a log-rank test statistic for several different linear combinations of variables and proceeding with the highest scoring option, we identify an optimal cut-point for one linear combination of variables and assess whether using this combination will create a split that passes the criterion for splitting a node.
+If it does not pass the criterion, then another linear combination will be tested, with the maximum number of attempts set by the parameter \texttt{n\_retry}.
+Often a `good-enough` split can be found in just one attempt when the training set is large, which gives the accelerated oblique RSF a computational advantage in larger training sets compared to greedy partitioning.
+
+\begin{algorithm}
+    \caption{Accelerated oblique random survival tree using default parameters.} \label{alg:aorsf}
+  \begin{algorithmic}[1]
+    \Require Training data $\dataset_{\text{train}} = \left\{ (T_i, \delta_i, \bm{x}_{i}) \right\}_{i=1}^{N_{\text{train}}}$, $\text{mtry} = \sqrt{\text{ncol}(\bm{x}_{\text{train}})}$, $\text{n\_split} = 5$, $\text{n\_retry} = 3$, and $\text{split\_min\_stat} = 3.841459$
+    \State $\mathcal{T} \gets \emptyset$
+    \State $w \gets \text{sample}(\text{from} = \left\{0, \ldots, 10\right\},\,\text{size} = \text{nrow}(\bm{x}_{\text{train}}),\, \text{replace} = \text{T})$
+    \State $\dataset_{\text{in-bag}} \gets \text{subset}(\dataset_{\text{train}},\,\text{rows} = \text{which}(w > 0))$
+    \State $w \gets \text{subset}(w,\, \text{which}(w > 0))$
+    \State $\text{node\_assignments} \gets \text{rep}(1,\,\text{times} = \text{nrow}(\bm{x}_{\text{in-bag}}))$
+    \State $\text{nodes\_to\_split} \gets \{1\}$
+     \Repeat
+     \For{$\text{node} \in \text{nodes\_to\_split}$}
+       \State $\text{n\_try} \gets 1$
+       \State $\text{node\_rows} \gets \text{which}(\text{node\_assignments} \equiv \text{node})$
+       \State $\text{node\_cols} \gets \text{sample}(\text{from} = \left\{1, \ldots, \text{ncol}(\bm{x})\right\},\, \text{size} = \text{mtry},\,\text{replace} = \text{F})$ \label{marker}
+       \State $\dataset_{\text{node}} \gets \text{subset}(\dataset_{\text{in-bag}},\,\text{rows} = \text{node\_rows},\,\text{columns} = \text{node\_cols})$
+       \State $\beta \gets \text{newt\_raph}(\dataset_{\text{node}},\, \text{weights} = \text{subset}(w, \text{node\_rows}),\, \text{max\_iter} = 1)$
+       \State $\eta \gets \bm{x}_{\text{node}} \times \beta$
+       \State $\mathcal{C} \gets \text{sample}(\text{from} = \text{unique}(\eta),\, \text{size} = \text{n\_split},\,\text{replace} = \text{F})$
+       \State $c \gets \argmax_{c^* \in \mathcal{C}} \left\{ \text{log\_rank\_stat}(\eta, c^*) \right\}$
+       \If{$\text{log\_rank\_stat}(\eta, c) \geq \text{split\_min\_stat}$}
+         \State $\mathcal{T} \gets \text{add\_node}(\mathcal{T},\, \text{name} = \text{node},\, \text{beta} = \beta,\, \text{cutpoint} = c)$
+         \State \LeftComment{0}{Right node logic omitted for brevity (identical to left node logic)}
+         \State $\text{node\_left\_name} \gets \text{max}(\text{node\_assignments}) + 1$
+         \State $\text{node\_left\_rows} \gets \text{subset}(\text{node\_rows},\,\text{which}(\eta \leq c))$
+         \State $\text{subset}(\text{node\_assignments}, \text{node\_left\_rows}) \gets \text{node\_left\_name}$
+         \If{$\text{is\_splittable}(\text{subset}(\text{node\_assignments}, \text{node\_left\_rows}))$}
+           \State $\text{nodes\_to\_split} \gets \text{nodes\_to\_split} \cup \text{node\_left\_name}$
+         \Else
+           \State $\mathcal{T} \gets \text{add\_leaf}(\mathcal{T},\, \text{data} = \text{subset}(\dataset_{\text{node}},\,\text{rows} = \text{node\_left\_rows}))$
+         \EndIf
+       \ElsIf{$\text{n\_try} \leq \text{n\_retry}$}
+         \State $\text{n\_try} \gets \text{n\_try} + 1$
+         \State \Goto{marker}
+       \Else
+         \State $\mathcal{T} \gets \text{add\_leaf}(\mathcal{T},\, \text{data} =\dataset_{\text{node}})$
+       \EndIf
+       \State $\text{nodes\_to\_split} \gets \text{nodes\_to\_split} \setminus \text{node}$
+     \EndFor
+  \Until{$\text{nodes\_to\_split} = \emptyset$}
+  \State \Return $\mathcal{T}$
+  \end{algorithmic}
+\end{algorithm}
 
@@
 As the magnitude of a coefficient increases, so does the probability that negating it will change the oblique RF's predictions.
-Since the coefficients in each non-leaf node of an oblique RFs are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
+For the current study, we use Harrell's concordance (C)-statistic \citep{harrell1982evaluating} to measure change in prediction error when computing negation VI.
 
-For consistency with prior VI techniques for the RSF and for its computational efficiency, we use Harrell's concordance (C)-statistic \citep{harrell1982evaluating} to measure change in prediction error when computing negation VI.
-We also note that while the current article focuses on oblique RSFs, negation VI can be applied to any oblique RF and can be applied with any applicable error function.
+Negation VI has several characteristics that may be helpful.
+First, although the current article focuses on oblique RSFs and uses Harrell's C-statistic, negation VI can be applied to any oblique RF using any valid error function.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic (see \texttt{?aorsf::orsf\_vi\_negate})}.
+Second, since the coefficients in each non-leaf node of an oblique tree are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
+This conjecture is formally assessed in \secref{sec:results_vi}.
+Third, unlike permutation importance, negation VI is non-random and hence reproducible without setting a random seed.
+Along these lines, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% as a result of randomly permuting the values of Hemoglobin A1c.
 
@@
 
-We consider five classes of learners: axis based RSFs, oblique RSFs, boosting ensembles, regression models, and neural networks (\tabref{tab:learners}).
+We consider four classes of learners: RSFs (both axis based and oblique), boosting ensembles, regression models, and neural networks (\tabref{tab:learners}).
 For each class, we synchronized shared tuning parameters.
@@
 Additionally, for RSF learners, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500.
-For learners that required tuning (\ie, boosting, regression, and neural networks), nested 10-fold cross-validation was applied to tune relevant model parameters.
+For boosting, regression, and neural network learners, nested 10-fold cross-validation was applied to tune relevant model parameters.
 Specifically, tuning for boosting models included identifying the number of steps to complete.
@@
  Oblique survival trees following Leo Breiman's random forest algorithm.
-Linear combinations of inputs are derived using \texttt{glmnet} in \texttt{obliqueRSF-net} and \texttt{aorsf-net}, using Newton Raphson scoring for the Cox partial likelihood function in \texttt{aorsf-fast} and \texttt{aorsf-cph}, and chosen randomly from a uniform distribution in \texttt{aorsf-extratrees}.
-Cut-points are selected to maximize a log-rank statistic.
+Linear combinations of inputs are derived using \texttt{glmnet} in \texttt{obliqueRSF-net} and \texttt{aorsf-net}, using Newton Raphson scoring for the Cox partial likelihood function in \texttt{aorsf-fast} (1 iteration of scoring) and \texttt{aorsf-cph} (up to 20 iterations), and chosen randomly from a uniform distribution in \texttt{aorsf-extratrees}.
+Cut-points are selected from 5 randomly selected candidates to maximize a log-rank statistic.
 \\
@@
 
-After collecting data from \Sexpr{bm_pred_n_runs} replications of Monte-Carlo cross validation for all \Sexpr{n_learners} learners in all \Sexpr{n_risk_tasks} risk prediction tasks, we analyzed the resulting \Sexpr{n_obs_model} observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
-Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using resampling and Bayesian methods.
+After collecting data from \Sexpr{bm_pred_n_runs} replications of Monte-Carlo cross validation for the \Sexpr{n_learners} learners in all \Sexpr{n_risk_tasks} risk prediction tasks, we analyzed the resulting \Sexpr{n_obs_model} observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
+Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using Bayesian models.
 Specifically, we fit two models: $$\text{IPA} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}) $$ and $$\text{C-stat} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}).$$ Random intercepts for specific splits of data (\ie, \texttt{run} in the model formula) were nested within datasets.
-The intercept, $\widehat{\gamma}_0$, was the expected value using \texttt{aorsf-fast} so that the coefficients in $\widehat{gamma}$ could be interpreted as expected differences between \texttt{aorsf-fast} and other learners.
+The intercept, $\widehat{\gamma}_0$, was the expected value of the outcome using \texttt{aorsf-fast}, making the coefficients in $\widehat{\gamma}$ the expected differences between \texttt{aorsf-fast} and other learners.
 Default priors from \texttt{rstanarm} were applied for model fitting \citep{rstanarm}.
@@
 More specifically, we concluded that two learners had practically equivalent IPA or time-dependent C-statistic if there was a 95\% or higher posterior probability that the absolute difference in the relevant metric was less than 1.
-We concluded that one learner was weakly superior when there was $\geq$ 0.95 posterior probability that the difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 0.95 posterior probability that the difference in the relevant metric was 1 or more.
+We concluded that one learner was weakly superior when there was $\geq$ 0.95\% posterior probability that the difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 0.95\% posterior probability that the difference in the relevant metric was 1 or more.
 
@@
 
-\subsubsection{Results}
+\subsubsection{Results} \label{sec:results_pred}
 
@@
 
-\subsubsection{Results}
+\subsubsection{Results} \label{sec:results_vi}
+
+<<>>=
+
+n_wins_aorsf <- bm_vi_viz %>%
+  getElement('rankings') %>%
+  filter(model == 'aorsf-negate') %>%
+  pull(n_wins)
+
+n_vi_tasks <- sum(bm_vi_viz$rankings$n_wins)
+
+cstat_mean_aorsf <- bm_vi_viz %>%
+  getElement('smry') %>%
+  filter(model == 'aorsf-negate',
+         data == 'Overall_NA_NA') %>%
+  mutate(value = table_value(value * 100)) %>%
+  pull(value)
+
+cstat_aorsf_won_by <- bm_vi_viz %>%
+  getElement('diffs') %>%
+  filter(data == 'Overall_NA_NA') %>%
+  transmute(percent = table_value(pdiff),
+            absolute = table_value(100*adiff)) %>%
+  as.list()
+
+cstat_vi_second_place <- bm_vi_viz %>%
+  getElement('smry') %>%
+  ungroup() %>%
+  filter(data == 'Overall_NA_NA') %>%
+  arrange(desc(value)) %>%
+  slice(2) %>%
+  transmute(model, value = table_value(100*value)) %>%
+  as.list()
+
+@
+
+Overall, \texttt{aorsf-negate} had the highest C-statistic in \Sexpr{n_wins_aorsf} out of \Sexpr{n_vi_tasks} VI tasks, with an overall mean of \Sexpr{cstat_mean_aorsf} (Figure \ref{fig:bm_vi_viz}).
+Compared to the VI technique with the second highest overall C-statistic (\texttt{\Sexpr{cstat_vi_second_place$model}}), \texttt{aorsf-negate}'s mean was \Sexpr{cstat_aorsf_won_by$absolute} points higher, a relative increase of \Sexpr{cstat_aorsf_won_by$percent}\%.
+Among each of the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables and the smallest advantage for interaction variables.
+
+<<bm_vi_viz, fig.height=11, fig.width=9, fig.cap="Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
+Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.">>=
+bm_vi_viz$fig
+@
 
@@
 VI is intrinsically linked to model fairness, as it can be used to identify when protected characteristics such as race, religion, and sexuality are inadvertently used (either directly or through correlates of these characteristics) by a prediction model.
-Since negation VI  engages with the coefficients used in linear combinations of variables, a major component of oblique RSFs, it may be more capable of diagnosing unfairness in oblique RSFs compared to permutation importance and model-agnostic VI techniques.\footnote{In our numeric experiments, negation VI's out-performance of other methods was most pronounced in smaller samples, giving some evidence supporting this hypothesis.} Three additional consequences of engaging with coefficients in linear combinations of predictors is that negation VI \begin{enumerate}
-\item is non-random and hence reproducible without setting a random seed (a limitation of permutation importance)
-\item does not incur bias from permutation of variables into unlikely or impossible combinations (a limitation of permutation importance).
-\item can be applied to any type of oblique RF (a limitation of ANOVA importance, which can only be applied when p-values are calculable within nodes).
-\end{enumerate} These characteristics suggest negation VI can be developed into a general tool for interpretation of oblique RFs.
+Since negation VI  engages with the coefficients used in linear combinations of variables, a major component of oblique RSFs, it may be more capable of diagnosing unfairness in oblique RSFs compared to permutation importance and model-agnostic VI techniques.
 
@@
 
-data_recoder <- data_key |>
+data_recoder <- data_key %>%
   transmute(data,
@@
                            outcome, ", n = ", .data$nrow,
-                           ", p = ", .data$ncol)) |>
+                           ", p = ", .data$ncol)) %>%
   deframe()
 
-model_recoder <- model_key |>
+model_recoder <- model_key %>%
   deframe()
 
-results_overall <- bm_pred_clean |>
-  group_by(model) |>
+results_overall <- bm_pred_clean %>%
+  group_by(model) %>%
   summarize(
@@
     )
-  ) |>
+  ) %>%
   mutate(data = 'Overall')
 
-data_tbl <- bm_pred_clean |>
-  group_by(model, data) |>
+data_tbl <- bm_pred_clean %>%
+  group_by(model, data) %>%
   summarize(
@@
     )
-  ) |>
-  bind_rows(results_overall) |>
+  ) %>%
+  bind_rows(results_overall) %>%
   # mutate(
@@
   #   )
-  # ) |>
-  arrange(data, desc(ibs_scaled_mean)) |>
+  # ) %>%
+  arrange(data, desc(ibs_scaled_mean)) %>%
   transmute(
@@
     time_pred_median = format(round(time_pred_median, 3), nsmall = 3)
-  ) |>
+  ) %>%
   arrange(data)
@@
 
-data_tbl |>
-  select(-data) |>
+data_tbl %>%
+  select(-data) %>%
   kable(booktabs=TRUE,
@@
         align = 'lcc',
-        caption = "Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.") |>
+        caption = "Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.") %>%
   pack_rows(index = indents,
@@
             hline_before = TRUE,
-            hline_after = TRUE) |>
-  kable_styling(latex_options = c("repeat_header")) |>
+            hline_after = TRUE) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
   add_header_above(header = c(" " = 1,
@@
                               "Computation time, seconds" = 2))
+
+@
+
+<<>>=
+
+bm_vi_smry <- bm_vi_viz$smry %>%
+  select(-x, -data) %>%
+  mutate(value = table_value(value*100)) %>%
+  pivot_wider(values_from = value, names_from = model) %>%
+  mutate(
+    variable = factor(
+      variable,
+      levels = c("Overall",
+                 "intr",
+                 "nlin",
+                 "cmbn",
+                 "main"),
+      labels = c("Overall",
+                 "Interaction effects",
+                 "Non-linear effects",
+                 "Combination effects",
+                 "Main effects")),
+    pred_corr_max = if_else(
+      is.na(pred_corr_max) | pred_corr_max == 1,
+      "Overall",
+      paste(as.integer(pred_corr_max * 100))
+    ),
+    n_obs = if_else(
+      is.na(n_obs) | n_obs == 0,
+      "Overall",
+      table_value(as.integer(n_obs))
+    )
+  ) %>%
+  select(
+    "variable",
+    "pred_corr_max",
+    "n_obs",
+    "aorsf-negate",
+    "aorsf-anova",
+    "aorsf-permute",
+    "xgboost-shap",
+    "xgboost-gain",
+    "randomForestSRC-permutation"
+  )
+
+indents <- table(bm_vi_smry$variable)
+
+bm_vi_smry %>%
+  ungroup() %>%
+  select(-variable) %>%
+  kable(booktabs=TRUE,
+        longtable=TRUE,
+        align = paste("llcccccc"),
+        col.names = c("Max correlation",
+                      "No. observations",
+                      "Negation",
+                      "ANOVA",
+                      "Permutation",
+                      "SHAP",
+                      "Gain",
+                      "Permutation"),
+        caption = "Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance") %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  add_header_above(
+    header = c(" " = 2,
+               "accelerated oblique RSF" = 3,
+               "xgboost" = 2,
+               "RSF" = 1)
+  ) %>%
+  # collapse_rows(columns = 1) %>%
+  pack_rows(group_label = 'Interactions',
+            start_row = 2,
+            end_row = 11,
+            italic = TRUE,
+            hline_before = FALSE,
+            hline_after = TRUE) %>%
+  pack_rows(group_label = 'Non-linear effects',
+            start_row = 12,
+            end_row = 21,
+            italic = TRUE,
+            hline_before = FALSE,
+            hline_after = TRUE) %>%
+pack_rows(group_label = 'Combination effects',
+            start_row = 22,
+            end_row = 31,
+            italic = TRUE,
+            hline_before = FALSE,
+            hline_after = TRUE) %>%
+  pack_rows(group_label = 'Main effects',
+            start_row = 32,
+            end_row = 41,
+            italic = TRUE,
+            hline_before = FALSE,
+            hline_after = TRUE) %>%
+  landscape()
 

### 2022-07-09 paper/jmlr/main.tex
A.3 shows values from VI

@@
 
-Risk prediction can reduce the burden of disease by educating patients and providers and guiding strategies to prevent and treat disease in a wide range of medical domains \citep{moons2012riskII, moons2012riskI}.
-The random survival forest (RSF), a supervised learning algorithm that can engage with censored outcomes, is frequently used for risk prediction.
-Notable characteristics of the RSF include uniform convergence of its ensemble survival function to the true population survival function when the predictor space is discrete \citep{ishwaran2010consistency}.
-In addition, software implementing the RSF is freely available, extremely efficient, and full of tools to interpret and explain the RSF \citep{randomForestSRC, ranger, hothorn2010party}.
-However, there remains considerable potential to improve the RSF in risk prediction tasks where training samples are not large enough to guarantee asymptotic properties or predictor spaces are non-discrete (\ie, predictors are continuous).
-
-RSFs may be axis based or oblique.
-The axis based RSF uses a single predictor whereas the oblique RSF uses a linear combination of predictors to create branches in trees.
-While axis based decision boundaries are always perpendicular to the axis of the relevant predictor, linear combinations of predictors create oblique decision boundaries that are neither parallel nor perpendicular to axes of their contributing predictors.
-Prior work has found the oblique RSF has higher prediction accuracy than the axis based RSF in general benchmarks \citep{jaeger2019oblique} and that oblique splitting is particularly effective when predictors are continuous \citep{menze2011oblique}.
-However, existing methods to implement oblique splitting typically use fully trained models in each non-leaf node to identify linear combinations of predictors, exponentially increasing the number of operations required for the oblique RSF versus its axis based counterpart.
-In addition, standard methods to estimate variable importance (VI) in the RSF are less effective in the oblique RSF, and few methods have been introduced to estimate VI specifically for the oblique RSF.
-
-The aim of this article is to improve the computational efficiency and interpretability of the oblique RSF.
-In a general benchmark experiment including 31 risk prediction tasks, we show that oblique RSFs with partially trained models have equivalent or superior prediction accuracy and are orders of magnitude more efficient than oblique RSFs with fully trained models in non-leaf nodes.
-We introduce a method to estimate VI for oblique RSFs and compare its ability to discriminate between signal and noise variables versus standard and state-of-the-art methods.
-All methods proposed in this article are available in the \texttt{aorsf} R Package.
+The random survival forest (RSF; \citet{ishwaran2008random, hothorn2006unbiased}) is a supervised learning algorithm that can be used for risk prediction \citep{wang2017selective}, which may reduce the burden of disease by guiding strategies for prevention and treatment in a wide range of medical domains \citep{moons2012riskII, moons2012riskI}.
+Similar to random forests (RFs) for classification and regression \citep{breiman2001random}, The RSF is a large set of de-correlated and randomized decision trees, with each tree contributing to the ensemble's prediction function.
+Notable characteristics of the RSF include uniform convergence of its ensemble survival prediction function to the true survival function, first shown by \citet{ishwaran2010consistency} and later by \citet{cui2017consistency} under more general conditions.
+However, \citet{cui2017consistency} noted that the RSF is at a disadvantage when predictors are correlated and some are not relevant to the censored outcome, which is a strong possibility when large medical databases are leveraged for risk prediction.
+
+A potential approach to improve the RSF when predictors are correlated and some are not relevant to the censored outcome is to use oblique decision trees instead of axis based trees.
+Axis based trees split data using a single predictor, creating decision boundaries that are perpendicular or parallel to axes of the predictor space \citep[see][Chapter~2]{breiman2017classification}.
+Oblique trees split data using a linear combination of predictors, creating decision boundaries that are neither parallel nor perpendicular to axes of their contributing predictors \citep[see][Chapter~5]{breiman2017classification}.
+\citet{menze2011oblique} examined prediction accuracy of RFs in the presence of correlated predictors and found that oblique RFs had substantially higher prediction accuracy compared to axis-based RFs.
+Similarly, \citet{jaeger2019oblique} found that growing RSFs with oblique rather than axis-based survival trees reduced the RSF's concordance error, with improvements ranging from 2.5\% to 24.9\% depending on the data analyzed.
+
+Oblique trees have at least two notable drawbacks compared to axis-based trees.
+First, finding a locally optimal oblique decision rule may require exponentially more computation than an axis-based rule.
+If $p$ predictors are potentially used to split $n$ observations, up to $\mathcal{O}(n^p)$ oblique splits can be assessed versus $\mathcal{O}(n \cdot p)$ axis-based splits \citep{heath1993induction, murthy1994system}.
+Second, estimating variable importance (VI) using permutation (a standard method for RFs) may be less effective in ensembles of oblique trees, as permuting the values of one predictor may not destabilize decisions that are based on many predictors.
+Although VI is one of the most widely used strategies to interpret random forests \citep{ishwaran2019standard}, few studies have investigated VI for oblique random forests \citep[see][Section~5]{menze2011oblique}, and fewer have investigated VI specifically for the oblique RSF.
+
+This study makes two contributions to oblique RSFs.
+First, we reduce their computational cost (\ie, accelerate them) with a scalable algorithm to identify linear combinations of coefficients.
+In a general benchmark experiment including 31 risk prediction tasks, we show that accelerated oblique RSFs are roughly 500 times faster with equivalent or superior prediction accuracy compared to existing routines to fit oblique RSFs.
+Second, we improve their interpretability with `negation VI', a method to estimate VI that engages with coefficients in linear combinations of predictors instead of permuting predictor values.
+In simulation studies where VI is estimate using permutation, analysis of variance (ANOVA; see \citet{menze2011oblique}), and approximations of Shapley values, we find that negation VI improves the oblique RSF's ability to discriminate between correlated signal and noise variables.
+The accelerated oblique RSF and multiple methods to compute VI for oblique RSFs (permutation, ANOVA, and negation) are available in the \texttt{aorsf} R Package.
+
+% However, there remains considerable potential to improve the RSF in settings where training samples are not large enough to guarantee asymptotic properties or do not align with the conditions required for consistency of the RSF.
+
+% Random forests (RFs) are large sets of de-correlated, randomized decision trees \citep{breiman2001random}, which can be axis based or oblique.Although using oblique rather than axis-based trees to grow a RSF may improve its prediction accuracy,
 
@@
 As the magnitude of a coefficient increases, so does the probability that negating it will change the oblique RF's predictions.
-Since the coefficients in each non-leaf node of an oblique RFs are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
-
-For consistency with prior VI techniques for the RSF and for its computational efficiency, we use Harrell's concordance (C)-statistic \citep{harrell1982evaluating} to measure change in prediction error when computing negation VI.
-We also note that while the current article focuses on oblique RSFs, negation VI can be applied to any oblique RF and can be applied with any applicable error function.
+For the current study, we use Harrell's concordance (C)-statistic \citep{harrell1982evaluating} to measure change in prediction error when computing negation VI.
+
+Negation VI has several characteristics that may be helpful.
+First, although the current article focuses on oblique RSFs and uses Harrell's C-statistic, negation VI can be applied to any oblique RF using any valid error function.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic (see \texttt{?aorsf::orsf\_vi\_negate})}.
+Second, since the coefficients in each non-leaf node of an oblique tree are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
+This conjecture is formally assessed in \secref{sec:results_vi}.
+Third, unlike permutation importance, negation VI is non-random and hence reproducible without setting a random seed.
+Along these lines, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% as a result of randomly permuting the values of Hemoglobin A1c.
 
@@
 
-For each risk prediction task, we completed 10 runs of Monte-Carlo cross validation.
+For each risk prediction task, we completed 5 runs of Monte-Carlo cross validation.
 In each run, we used a random sample containing 50\% of the available data for training and the remaining 50\% for testing each of the learners described in \secref{sec:learners}.
@@
 
-After collecting data from 10 replications of Monte-Carlo cross validation for all 14 learners in all 31 risk prediction tasks, we analyzed the resulting 4,340 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
-Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using resampling and Bayesian methods.
+After collecting data from 5 replications of Monte-Carlo cross validation for the 14 learners in all 31 risk prediction tasks, we analyzed the resulting 2,170 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
+Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using Bayesian models.
 Specifically, we fit two models: $$\text{IPA} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}) $$ and $$\text{C-stat} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}).$$ Random intercepts for specific splits of data (\ie, \texttt{run} in the model formula) were nested within datasets.
-The intercept, $\widehat{\gamma}_0$, was the expected value using \texttt{aorsf-fast} so that the coefficients in $\widehat{gamma}$ could be interpreted as expected differences between \texttt{aorsf-fast} and other learners.
+The intercept, $\widehat{\gamma}_0$, was the expected value of the outcome using \texttt{aorsf-fast}, making the coefficients in $\widehat{\gamma}$ the expected differences between \texttt{aorsf-fast} and other learners.
 Default priors from \texttt{rstanarm} were applied for model fitting \citep{rstanarm}.
@@
 More specifically, we concluded that two learners had practically equivalent IPA or time-dependent C-statistic if there was a 95\% or higher posterior probability that the absolute difference in the relevant metric was less than 1.
-We concluded that one learner was weakly superior when there was $\geq$ 0.95 posterior probability that the difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 0.95 posterior probability that the difference in the relevant metric was 1 or more.
-
-\subsubsection{Results}
+We concluded that one learner was weakly superior when there was $\geq$ 0.95\% posterior probability that the difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 0.95\% posterior probability that the difference in the relevant metric was 1 or more.
+
+\subsubsection{Results} \label{sec:results_pred}
 
@@
 Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in  out of 31 risk prediction tasks, with an overall mean IPA of  (Figure \ref{fig:bm_pred_viz_ibs}).
-Compared to the learner with the second highest mean IPA (\texttt{rsf-standard}), \texttt{aorsf-fast}'s mean was 1.21 points higher, a relative increase of 9.98\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.97, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.65 (versus \texttt{rsf-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+Compared to the learner with the second highest mean IPA (\texttt{rsf-standard}), \texttt{aorsf-fast}'s mean was 1.12 points higher, a relative increase of 9.30\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.95, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.63 (versus \texttt{rsf-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
 
@@
 Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in  out of 31 risk prediction tasks, with an overall mean of  (Figure \ref{fig:bm_pred_viz_cstat}).
-Compared to the learner with the second highest mean C-statistic (\texttt{obliqueRSF-net}), \texttt{aorsf-fast}'s mean was 0.681 points higher, a relative increase of 0.887\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.01 (versus \texttt{obliqueRSF-net}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+Compared to the learner with the second highest mean C-statistic (\texttt{obliqueRSF-net}), \texttt{aorsf-fast}'s mean was 0.612 points higher, a relative increase of 0.797\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.96, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.02 (versus \texttt{obliqueRSF-net}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
 
@@
 
-\subsubsection{Results}
+\subsubsection{Results} \label{sec:results_vi}
+
+Overall, \texttt{aorsf-negate} had the highest C-statistic in 21 out of 36 VI tasks, with an overall mean of 75.3 (Figure \ref{fig:bm_vi_viz}).
+Compared to the VI technique with the second highest overall C-statistic (\texttt{aorsf-anova}), \texttt{aorsf-negate}'s mean was 2.34 points higher, a relative increase of 3.21\%.
+Among each of the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables and the smallest advantage for interaction variables.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_vi_viz-1} \caption[Concordance statistic for assigning higher importance to relevant versus irrelevant variables]{Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
+Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.}\label{fig:bm_vi_viz}
+\end{figure}
+
+\end{knitrout}
 
@@
 \begin{longtable}[t]{lcclcc}
-\caption{\label{tab:unnamed-chunk-4}Data sets used for numeric experiments \label{tab:datasets}}\\
+\caption{\label{tab:unnamed-chunk-5}Data sets used for numeric experiments \label{tab:datasets}}\\
 \toprule
@@
 \begin{longtable}[t]{lcclc}
-\caption{\label{tab:unnamed-chunk-5}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.}\\
+\caption{\label{tab:unnamed-chunk-6}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.}\\
 \toprule
@@
 \hline
-\hspace{1em}aorsf-fast & 0.133 (0.114) & 0.775 (0.072) & 0.801 & 0.170\\
-\hspace{1em}aorsf-cph & 0.132 (0.114) & 0.774 (0.071) & 1.965 & 0.173\\
-\hspace{1em}aorsf-net & 0.131 (0.116) & 0.774 (0.071) & 122.683 & 0.166\\
-\hspace{1em}rsf-standard & 0.121 (0.117) & 0.761 (0.075) & 2.089 & 0.252\\
-\hspace{1em}cif-rotate & 0.120 (0.130) & 0.758 (0.081) & 39.689 & 8.754\\
-\hspace{1em}cif-standard & 0.119 (0.100) & 0.768 (0.070) & 4.254 & 15.360\\
-\hspace{1em}obliqueRSF-net & 0.118 (0.086) & 0.774 (0.071) & 376.210 & 24.600\\
-\hspace{1em}glmnet-cox & 0.116 (0.123) & 0.763 (0.074) & 0.532 & 0.004\\
-\hspace{1em}ranger-extratrees & 0.103 (0.088) & 0.764 (0.068) & 2.519 & 2.159\\
-\hspace{1em}cif-extension & 0.099 (0.095) & 0.763 (0.072) & 23.746 & 8.318\\
-\hspace{1em}aorsf-random & 0.094 (0.084) & 0.743 (0.064) & 2.088 & 0.178\\
-\hspace{1em}xgboost-cox & 0.073 (0.102) & 0.757 (0.088) & 5.270 & 0.005\\
-\hspace{1em}nn-cox & 0.046 (0.106) & 0.655 (0.132) & 16.511 & 5.207\\
-\hspace{1em}xgboost-aft & -4.78 (4.97) & 0.767 (0.076) & 15.673 & 0.007\\
+\hspace{1em}aorsf-fast & 0.132 (0.114) & 0.774 (0.072) & 0.833 & 0.173\\
+\hspace{1em}aorsf-cph & 0.131 (0.115) & 0.772 (0.072) & 2.477 & 0.174\\
+\hspace{1em}aorsf-net & 0.130 (0.118) & 0.772 (0.072) & 131.969 & 0.176\\
+\hspace{1em}rsf-standard & 0.121 (0.118) & 0.761 (0.075) & 2.070 & 0.291\\
+\hspace{1em}cif-standard & 0.120 (0.101) & 0.768 (0.071) & 4.499 & 15.774\\
+\hspace{1em}cif-rotate & 0.119 (0.129) & 0.758 (0.080) & 43.469 & 9.418\\
+\hspace{1em}obliqueRSF-net & 0.119 (0.088) & 0.773 (0.071) & 388.086 & 24.864\\
+\hspace{1em}glmnet-cox & 0.115 (0.123) & 0.761 (0.074) & 0.693 & 0.004\\
+\hspace{1em}ranger-extratrees & 0.104 (0.090) & 0.763 (0.068) & 2.147 & 1.592\\
+\hspace{1em}cif-extension & 0.099 (0.095) & 0.764 (0.072) & 23.953 & 8.487\\
+\hspace{1em}aorsf-random & 0.095 (0.085) & 0.742 (0.065) & 2.288 & 0.174\\
+\hspace{1em}xgboost-cox & 0.076 (0.105) & 0.757 (0.088) & 4.399 & 0.005\\
+\hspace{1em}nn-cox & 0.045 (0.101) & 0.648 (0.137) & 16.081 & 5.931\\
+\hspace{1em}xgboost-aft & -4.80 (5.11) & 0.767 (0.077) & 14.692 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-random & 0.031 (0.015) & 0.739 (0.031) & 0.396 & 0.036\\
-\hspace{1em}ranger-extratrees & 0.030 (0.014) & 0.734 (0.033) & 0.448 & 0.146\\
-\hspace{1em}cif-standard & 0.029 (0.028) & 0.740 (0.043) & 0.988 & 4.459\\
-\hspace{1em}obliqueRSF-net & 0.027 (0.022) & 0.735 (0.039) & 26.729 & 15.372\\
-\hspace{1em}aorsf-cph & 0.026 (0.024) & 0.742 (0.040) & 0.496 & 0.036\\
-\hspace{1em}aorsf-fast & 0.026 (0.022) & 0.738 (0.040) & 0.161 & 0.036\\
-\hspace{1em}cif-extension & 0.023 (0.015) & 0.711 (0.041) & 9.394 & 4.051\\
-\hspace{1em}glmnet-cox & 0.022 (0.020) & 0.741 (0.024) & 0.182 & 0.003\\
-\hspace{1em}aorsf-net & 0.021 (0.030) & 0.735 (0.038) & 18.601 & 0.037\\
-\hspace{1em}rsf-standard & 0.011 (0.030) & 0.722 (0.044) & 0.149 & 0.065\\
-\hspace{1em}xgboost-cox & 0.008 (0.033) & 0.743 (0.035) & 4.586 & 0.003\\
-\hspace{1em}cif-rotate & 0.006 (0.036) & 0.726 (0.035) & 15.373 & 3.791\\
-\hspace{1em}nn-cox & -0.008 (0.016) & 0.558 (0.129) & 13.641 & 0.549\\
-\hspace{1em}xgboost-aft & -7.76 (1.18) & 0.733 (0.029) & 13.603 & 0.007\\
+\hspace{1em}ranger-extratrees & 0.028 (0.018) & 0.737 (0.042) & 0.053 & 0.155\\
+\hspace{1em}aorsf-random & 0.024 (0.019) & 0.732 (0.042) & 0.452 & 0.036\\
+\hspace{1em}cif-standard & 0.024 (0.039) & 0.741 (0.060) & 1.460 & 4.523\\
+\hspace{1em}cif-extension & 0.022 (0.021) & 0.716 (0.055) & 9.093 & 4.176\\
+\hspace{1em}obliqueRSF-net & 0.020 (0.030) & 0.733 (0.056) & 26.723 & 16.653\\
+\hspace{1em}aorsf-cph & 0.017 (0.032) & 0.736 (0.056) & 0.452 & 0.037\\
+\hspace{1em}aorsf-fast & 0.016 (0.027) & 0.733 (0.054) & 0.153 & 0.034\\
+\hspace{1em}glmnet-cox & 0.011 (0.023) & 0.735 (0.034) & 0.180 & 0.002\\
+\hspace{1em}aorsf-net & 0.010 (0.041) & 0.731 (0.055) & 19.025 & 0.036\\
+\hspace{1em}xgboost-cox & 0.006 (0.046) & 0.747 (0.052) & 3.312 & 0.003\\
+\hspace{1em}rsf-standard & 0.004 (0.042) & 0.721 (0.058) & 0.466 & 0.061\\
+\hspace{1em}nn-cox & 0.001 (0.007) & 0.589 (0.138) & 10.976 & 0.666\\
+\hspace{1em}cif-rotate & -0.002 (0.050) & 0.728 (0.051) & 14.852 & 4.031\\
+\hspace{1em}xgboost-aft & -7.31 (0.690) & 0.739 (0.040) & 9.771 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.013 (0.022) & 0.847 (0.054) & 0.104 & 0.022\\
-\hspace{1em}aorsf-cph & 0.012 (0.021) & 0.833 (0.061) & 0.335 & 0.021\\
-\hspace{1em}aorsf-net & 0.010 (0.032) & 0.829 (0.062) & 13.672 & 0.024\\
-\hspace{1em}obliqueRSF-net & 0.009 (0.013) & 0.839 (0.052) & 8.926 & 10.688\\
-\hspace{1em}aorsf-random & 0.008 (0.016) & 0.810 (0.069) & 0.218 & 0.023\\
-\hspace{1em}cif-extension & 0.007 (0.014) & 0.786 (0.050) & 8.178 & 3.578\\
-\hspace{1em}cif-standard & 0.007 (0.019) & 0.801 (0.057) & 1.008 & 4.449\\
-\hspace{1em}ranger-extratrees & 0.004 (0.018) & 0.795 (0.062) & 0.423 & 0.266\\
-\hspace{1em}xgboost-cox & -0.004 (0.003) & 0.500 (0.000) & 0.145 & 0.002\\
-\hspace{1em}nn-cox & -0.004 (0.004) & 0.574 (0.111) & 14.113 & 0.560\\
-\hspace{1em}rsf-standard & -0.007 (0.048) & 0.801 (0.059) & 0.090 & 0.036\\
-\hspace{1em}cif-rotate & -0.026 (0.034) & 0.715 (0.093) & 13.721 & 3.326\\
-\hspace{1em}glmnet-cox & -0.027 (0.072) & 0.753 (0.101) & 0.257 & 0.002\\
-\hspace{1em}xgboost-aft & -22.8 (5.25) & 0.777 (0.078) & 11.919 & 0.006\\
+\hspace{1em}cif-extension & 0.004 (0.012) & 0.794 (0.066) & 12.087 & 5.085\\
+\hspace{1em}obliqueRSF-net & 0.003 (0.012) & 0.822 (0.064) & 8.856 & 11.019\\
+\hspace{1em}aorsf-fast & 0.001 (0.019) & 0.830 (0.062) & 0.094 & 0.020\\
+\hspace{1em}cif-standard & 0.000 (0.022) & 0.797 (0.079) & 1.505 & 4.550\\
+\hspace{1em}aorsf-random & 0.000 (0.016) & 0.793 (0.090) & 0.247 & 0.023\\
+\hspace{1em}aorsf-cph & -0.001 (0.018) & 0.811 (0.073) & 0.361 & 0.022\\
+\hspace{1em}xgboost-cox & -0.005 (0.003) & 0.500 (0.000) & 0.116 & 0.002\\
+\hspace{1em}nn-cox & -0.006 (0.003) & 0.514 (0.102) & 10.371 & 0.517\\
+\hspace{1em}aorsf-net & -0.006 (0.034) & 0.813 (0.070) & 13.008 & 0.023\\
+\hspace{1em}ranger-extratrees & -0.006 (0.022) & 0.768 (0.078) & 0.041 & 0.127\\
+\hspace{1em}rsf-standard & -0.027 (0.060) & 0.796 (0.074) & 0.097 & 0.037\\
+\hspace{1em}cif-rotate & -0.030 (0.037) & 0.727 (0.092) & 12.924 & 3.575\\
+\hspace{1em}glmnet-cox & -0.057 (0.096) & 0.777 (0.062) & 0.282 & 0.003\\
+\hspace{1em}xgboost-aft & -23.5 (7.27) & 0.772 (0.100) & 8.740 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.155 (0.007) & 0.807 (0.005) & 4.481 & 1.501\\
-\hspace{1em}aorsf-net & 0.152 (0.006) & 0.807 (0.004) & 498.111 & 1.449\\
-\hspace{1em}aorsf-cph & 0.151 (0.006) & 0.806 (0.004) & 15.754 & 1.558\\
-\hspace{1em}rsf-standard & 0.150 (0.007) & 0.799 (0.004) & 11.130 & 1.219\\
-\hspace{1em}obliqueRSF-net & 0.143 (0.004) & 0.809 (0.004) & 2875.869 & 334.594\\
-\hspace{1em}cif-standard & 0.132 (0.003) & 0.807 (0.004) & 70.329 & 357.765\\
-\hspace{1em}glmnet-cox & 0.128 (0.014) & 0.792 (0.007) & 1.606 & 0.019\\
-\hspace{1em}ranger-extratrees & 0.112 (0.003) & 0.793 (0.005) & 398.270 & 131.923\\
-\hspace{1em}cif-rotate & 0.104 (0.004) & 0.782 (0.007) & 550.670 & 69.312\\
-\hspace{1em}nn-cox & 0.103 (0.039) & 0.763 (0.093) & 40.780 & 85.754\\
-\hspace{1em}aorsf-random & 0.097 (0.005) & 0.769 (0.006) & 11.207 & 1.357\\
-\hspace{1em}cif-extension & 0.069 (0.002) & 0.784 (0.005) & 173.969 & 56.767\\
-\hspace{1em}xgboost-cox & 0.068 (0.017) & 0.812 (0.003) & 9.465 & 0.016\\
-\hspace{1em}xgboost-aft & -4.83 (0.210) & 0.813 (0.003) & 33.629 & 0.014\\
+\hspace{1em}aorsf-fast & 0.156 (0.005) & 0.806 (0.004) & 4.321 & 1.354\\
+\hspace{1em}aorsf-net & 0.153 (0.004) & 0.806 (0.003) & 515.337 & 1.480\\
+\hspace{1em}aorsf-cph & 0.152 (0.005) & 0.806 (0.004) & 14.632 & 1.349\\
+\hspace{1em}rsf-standard & 0.149 (0.006) & 0.797 (0.003) & 7.394 & 1.041\\
+\hspace{1em}obliqueRSF-net & 0.145 (0.002) & 0.808 (0.002) & 3100.286 & 413.186\\
+\hspace{1em}cif-standard & 0.133 (0.002) & 0.806 (0.002) & 69.980 & 358.577\\
+\hspace{1em}glmnet-cox & 0.132 (0.008) & 0.795 (0.003) & 1.467 & 0.025\\
+\hspace{1em}nn-cox & 0.123 (0.008) & 0.793 (0.004) & 82.973 & 106.367\\
+\hspace{1em}ranger-extratrees & 0.112 (0.001) & 0.792 (0.003) & 271.533 & 63.785\\
+\hspace{1em}cif-rotate & 0.106 (0.001) & 0.782 (0.006) & 578.571 & 68.467\\
+\hspace{1em}aorsf-random & 0.098 (0.004) & 0.771 (0.004) & 11.278 & 1.387\\
+\hspace{1em}cif-extension & 0.070 (0.001) & 0.784 (0.004) & 163.371 & 49.091\\
+\hspace{1em}xgboost-cox & 0.062 (0.016) & 0.811 (0.004) & 8.980 & 0.014\\
+\hspace{1em}xgboost-aft & -4.81 (0.208) & 0.812 (0.004) & 21.435 & 0.021\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.217 (0.007) & 0.792 (0.004) & 940.117 & 2.346\\
-\hspace{1em}rsf-standard & 0.216 (0.006) & 0.789 (0.004) & 13.902 & 1.221\\
-\hspace{1em}aorsf-fast & 0.215 (0.008) & 0.792 (0.004) & 6.921 & 2.306\\
-\hspace{1em}aorsf-cph & 0.215 (0.007) & 0.791 (0.004) & 23.219 & 2.393\\
-\hspace{1em}obliqueRSF-net & 0.206 (0.005) & 0.790 (0.004) & 7672.274 & 317.021\\
-\hspace{1em}cif-standard & 0.200 (0.005) & 0.788 (0.004) & 69.166 & 373.964\\
-\hspace{1em}nn-cox & 0.192 (0.007) & 0.778 (0.004) & 302.175 & 153.845\\
-\hspace{1em}ranger-extratrees & 0.180 (0.006) & 0.780 (0.005) & 678.904 & 94.798\\
-\hspace{1em}glmnet-cox & 0.176 (0.019) & 0.771 (0.009) & 2.425 & 0.018\\
-\hspace{1em}cif-rotate & 0.151 (0.008) & 0.755 (0.007) & 613.021 & 69.650\\
-\hspace{1em}xgboost-cox & 0.139 (0.015) & 0.794 (0.005) & 17.317 & 0.018\\
-\hspace{1em}aorsf-random & 0.130 (0.005) & 0.735 (0.005) & 21.763 & 2.126\\
-\hspace{1em}cif-extension & 0.113 (0.002) & 0.775 (0.005) & 177.598 & 52.953\\
-\hspace{1em}xgboost-aft & -1.56 (0.099) & 0.794 (0.005) & 25.317 & 0.013\\
+\hspace{1em}rsf-standard & 0.218 (0.004) & 0.790 (0.001) & 11.948 & 1.186\\
+\hspace{1em}aorsf-net & 0.218 (0.006) & 0.792 (0.003) & 958.228 & 2.380\\
+\hspace{1em}aorsf-cph & 0.215 (0.007) & 0.791 (0.003) & 22.614 & 2.249\\
+\hspace{1em}aorsf-fast & 0.215 (0.007) & 0.792 (0.003) & 7.190 & 2.258\\
+\hspace{1em}obliqueRSF-net & 0.208 (0.004) & 0.792 (0.003) & 7161.062 & 322.057\\
+\hspace{1em}cif-standard & 0.202 (0.004) & 0.789 (0.004) & 64.173 & 379.745\\
+\hspace{1em}glmnet-cox & 0.191 (0.017) & 0.777 (0.006) & 1.852 & 0.018\\
+\hspace{1em}nn-cox & 0.183 (0.016) & 0.781 (0.003) & 95.577 & 77.835\\
+\hspace{1em}ranger-extratrees & 0.181 (0.006) & 0.779 (0.005) & 350.659 & 58.944\\
+\hspace{1em}cif-rotate & 0.152 (0.005) & 0.755 (0.006) & 577.948 & 65.954\\
+\hspace{1em}xgboost-cox & 0.134 (0.015) & 0.795 (0.001) & 11.789 & 0.015\\
+\hspace{1em}aorsf-random & 0.130 (0.004) & 0.733 (0.003) & 18.944 & 1.995\\
+\hspace{1em}cif-extension & 0.114 (0.001) & 0.775 (0.005) & 180.959 & 50.040\\
+\hspace{1em}xgboost-aft & -1.63 (0.238) & 0.795 (0.002) & 25.690 & 0.014\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.235 (0.007) & 0.842 (0.006) & 5.652 & 1.828\\
-\hspace{1em}rsf-standard & 0.230 (0.007) & 0.835 (0.005) & 9.050 & 1.075\\
-\hspace{1em}aorsf-cph & 0.230 (0.007) & 0.841 (0.006) & 17.921 & 2.008\\
-\hspace{1em}aorsf-net & 0.229 (0.007) & 0.841 (0.006) & 613.168 & 1.685\\
-\hspace{1em}obliqueRSF-net & 0.213 (0.006) & 0.841 (0.006) & 3954.453 & 334.564\\
-\hspace{1em}cif-standard & 0.199 (0.005) & 0.839 (0.006) & 70.715 & 362.530\\
-\hspace{1em}nn-cox & 0.175 (0.025) & 0.826 (0.006) & 138.006 & 231.741\\
-\hspace{1em}cif-rotate & 0.171 (0.004) & 0.806 (0.005) & 562.939 & 67.797\\
-\hspace{1em}ranger-extratrees & 0.171 (0.004) & 0.824 (0.006) & 1532.153 & 144.888\\
-\hspace{1em}glmnet-cox & 0.165 (0.046) & 0.816 (0.018) & 2.192 & 0.012\\
-\hspace{1em}aorsf-random & 0.140 (0.005) & 0.790 (0.008) & 15.028 & 1.599\\
-\hspace{1em}xgboost-cox & 0.118 (0.016) & 0.845 (0.005) & 14.769 & 0.019\\
-\hspace{1em}cif-extension & 0.108 (0.003) & 0.809 (0.007) & 195.201 & 60.594\\
-\hspace{1em}xgboost-aft & -3.80 (0.291) & 0.844 (0.005) & 38.814 & 0.015\\
+\hspace{1em}aorsf-fast & 0.236 (0.005) & 0.842 (0.006) & 5.253 & 1.671\\
+\hspace{1em}rsf-standard & 0.231 (0.005) & 0.835 (0.004) & 10.275 & 1.254\\
+\hspace{1em}aorsf-net & 0.231 (0.004) & 0.842 (0.005) & 628.786 & 1.736\\
+\hspace{1em}aorsf-cph & 0.231 (0.006) & 0.842 (0.006) & 16.545 & 1.568\\
+\hspace{1em}obliqueRSF-net & 0.215 (0.003) & 0.841 (0.005) & 3701.023 & 306.739\\
+\hspace{1em}cif-standard & 0.200 (0.002) & 0.839 (0.005) & 67.705 & 364.696\\
+\hspace{1em}nn-cox & 0.181 (0.029) & 0.823 (0.008) & 79.949 & 112.151\\
+\hspace{1em}glmnet-cox & 0.179 (0.036) & 0.821 (0.010) & 1.899 & 0.012\\
+\hspace{1em}ranger-extratrees & 0.173 (0.003) & 0.825 (0.006) & 260.123 & 63.679\\
+\hspace{1em}cif-rotate & 0.171 (0.003) & 0.806 (0.005) & 581.803 & 66.846\\
+\hspace{1em}aorsf-random & 0.141 (0.004) & 0.792 (0.004) & 13.281 & 1.509\\
+\hspace{1em}xgboost-cox & 0.119 (0.009) & 0.844 (0.005) & 13.603 & 0.015\\
+\hspace{1em}cif-extension & 0.110 (0.003) & 0.809 (0.006) & 167.897 & 48.511\\
+\hspace{1em}xgboost-aft & -3.93 (0.269) & 0.843 (0.005) & 22.308 & 0.022\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.093 (0.003) & 0.794 (0.004) & 4.096 & 1.257\\
-\hspace{1em}rsf-standard & 0.091 (0.004) & 0.785 (0.004) & 7.684 & 0.943\\
-\hspace{1em}aorsf-net & 0.090 (0.003) & 0.792 (0.004) & 384.631 & 1.222\\
-\hspace{1em}aorsf-cph & 0.089 (0.002) & 0.791 (0.005) & 14.364 & 1.263\\
-\hspace{1em}obliqueRSF-net & 0.081 (0.002) & 0.790 (0.005) & 1858.149 & 373.179\\
-\hspace{1em}glmnet-cox & 0.077 (0.004) & 0.785 (0.006) & 1.828 & 0.017\\
-\hspace{1em}nn-cox & 0.073 (0.008) & 0.779 (0.008) & 31.694 & 72.618\\
-\hspace{1em}cif-standard & 0.073 (0.002) & 0.787 (0.005) & 70.222 & 351.070\\
-\hspace{1em}ranger-extratrees & 0.067 (0.003) & 0.779 (0.008) & 217.755 & 74.836\\
-\hspace{1em}aorsf-random & 0.059 (0.003) & 0.751 (0.007) & 9.041 & 1.119\\
-\hspace{1em}cif-rotate & 0.052 (0.002) & 0.766 (0.008) & 571.269 & 67.464\\
-\hspace{1em}xgboost-cox & 0.046 (0.010) & 0.792 (0.003) & 8.153 & 0.015\\
-\hspace{1em}cif-extension & 0.036 (0.001) & 0.770 (0.007) & 169.947 & 53.605\\
-\hspace{1em}xgboost-aft & -6.55 (0.323) & 0.791 (0.003) & 31.120 & 0.013\\
+\hspace{1em}aorsf-fast & 0.094 (0.003) & 0.794 (0.003) & 3.786 & 1.160\\
+\hspace{1em}rsf-standard & 0.092 (0.003) & 0.786 (0.005) & 5.225 & 0.875\\
+\hspace{1em}aorsf-net & 0.091 (0.003) & 0.793 (0.004) & 411.476 & 1.233\\
+\hspace{1em}aorsf-cph & 0.090 (0.003) & 0.792 (0.004) & 13.452 & 1.127\\
+\hspace{1em}obliqueRSF-net & 0.082 (0.002) & 0.791 (0.004) & 1751.465 & 410.345\\
+\hspace{1em}glmnet-cox & 0.079 (0.005) & 0.785 (0.004) & 1.493 & 0.011\\
+\hspace{1em}cif-standard & 0.074 (0.002) & 0.788 (0.004) & 78.679 & 394.309\\
+\hspace{1em}nn-cox & 0.072 (0.016) & 0.782 (0.008) & 28.811 & 84.991\\
+\hspace{1em}ranger-extratrees & 0.068 (0.003) & 0.780 (0.006) & 310.500 & 70.135\\
+\hspace{1em}aorsf-random & 0.059 (0.004) & 0.752 (0.007) & 9.207 & 1.136\\
+\hspace{1em}cif-rotate & 0.052 (0.002) & 0.768 (0.009) & 614.088 & 69.548\\
+\hspace{1em}xgboost-cox & 0.047 (0.012) & 0.792 (0.001) & 6.854 & 0.014\\
+\hspace{1em}cif-extension & 0.036 (0.001) & 0.772 (0.007) & 163.803 & 49.613\\
+\hspace{1em}xgboost-aft & -6.78 (0.231) & 0.791 (0.002) & 21.692 & 0.023\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.100 (0.013) & 0.719 (0.011) & 0.236 & 0.051\\
-\hspace{1em}cif-standard & 0.100 (0.011) & 0.713 (0.009) & 0.663 & 3.547\\
-\hspace{1em}aorsf-cph & 0.098 (0.012) & 0.717 (0.010) & 0.640 & 0.056\\
-\hspace{1em}aorsf-net & 0.097 (0.010) & 0.718 (0.009) & 51.061 & 0.046\\
-\hspace{1em}aorsf-random & 0.095 (0.007) & 0.717 (0.012) & 1.038 & 0.046\\
-\hspace{1em}cif-rotate & 0.093 (0.015) & 0.710 (0.012) & 12.320 & 3.417\\
-\hspace{1em}obliqueRSF-net & 0.089 (0.005) & 0.718 (0.010) & 236.037 & 17.920\\
-\hspace{1em}rsf-standard & 0.088 (0.018) & 0.703 (0.008) & 1.281 & 0.150\\
-\hspace{1em}cif-extension & 0.082 (0.006) & 0.711 (0.011) & 7.857 & 3.918\\
-\hspace{1em}ranger-extratrees & 0.081 (0.008) & 0.710 (0.012) & 0.986 & 0.352\\
-\hspace{1em}glmnet-cox & 0.076 (0.013) & 0.708 (0.018) & 0.127 & 0.003\\
-\hspace{1em}xgboost-cox & 0.066 (0.008) & 0.703 (0.011) & 3.626 & 0.004\\
-\hspace{1em}nn-cox & -0.004 (0.003) & 0.481 (0.031) & 15.080 & 1.153\\
-\hspace{1em}xgboost-aft & -1.12 (0.267) & 0.707 (0.013) & 11.971 & 0.006\\
+\hspace{1em}aorsf-fast & 0.099 (0.018) & 0.718 (0.013) & 0.228 & 0.047\\
+\hspace{1em}cif-standard & 0.099 (0.016) & 0.712 (0.013) & 1.158 & 3.454\\
+\hspace{1em}aorsf-cph & 0.097 (0.018) & 0.716 (0.012) & 0.646 & 0.051\\
+\hspace{1em}aorsf-net & 0.095 (0.014) & 0.716 (0.010) & 48.543 & 0.049\\
+\hspace{1em}aorsf-random & 0.095 (0.009) & 0.717 (0.012) & 1.361 & 0.045\\
+\hspace{1em}cif-rotate & 0.095 (0.020) & 0.712 (0.011) & 12.821 & 3.474\\
+\hspace{1em}obliqueRSF-net & 0.089 (0.005) & 0.716 (0.010) & 250.693 & 16.565\\
+\hspace{1em}rsf-standard & 0.084 (0.026) & 0.705 (0.008) & 1.193 & 0.135\\
+\hspace{1em}cif-extension & 0.080 (0.007) & 0.708 (0.013) & 10.097 & 4.783\\
+\hspace{1em}ranger-extratrees & 0.078 (0.010) & 0.709 (0.017) & 0.494 & 0.239\\
+\hspace{1em}glmnet-cox & 0.076 (0.018) & 0.703 (0.024) & 0.112 & 0.002\\
+\hspace{1em}xgboost-cox & 0.060 (0.006) & 0.699 (0.010) & 2.915 & 0.003\\
+\hspace{1em}nn-cox & -0.005 (0.003) & 0.521 (0.030) & 12.067 & 1.890\\
+\hspace{1em}xgboost-aft & -1.06 (0.351) & 0.707 (0.013) & 13.225 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.097 (0.011) & 0.714 (0.010) & 0.232 & 0.051\\
-\hspace{1em}aorsf-cph & 0.097 (0.010) & 0.713 (0.009) & 0.651 & 0.051\\
-\hspace{1em}cif-standard & 0.094 (0.014) & 0.704 (0.014) & 0.662 & 3.381\\
-\hspace{1em}aorsf-net & 0.094 (0.015) & 0.714 (0.012) & 51.223 & 0.047\\
-\hspace{1em}cif-rotate & 0.092 (0.017) & 0.700 (0.014) & 11.852 & 3.577\\
-\hspace{1em}obliqueRSF-net & 0.087 (0.008) & 0.711 (0.009) & 247.097 & 15.943\\
-\hspace{1em}rsf-standard & 0.085 (0.016) & 0.696 (0.011) & 1.200 & 0.150\\
-\hspace{1em}aorsf-random & 0.083 (0.011) & 0.702 (0.010) & 0.958 & 0.046\\
-\hspace{1em}cif-extension & 0.081 (0.010) & 0.708 (0.011) & 8.680 & 4.310\\
-\hspace{1em}ranger-extratrees & 0.076 (0.014) & 0.697 (0.012) & 0.666 & 0.770\\
-\hspace{1em}glmnet-cox & 0.070 (0.013) & 0.699 (0.016) & 0.119 & 0.003\\
-\hspace{1em}xgboost-cox & 0.059 (0.012) & 0.697 (0.013) & 3.432 & 0.003\\
-\hspace{1em}nn-cox & -0.008 (0.007) & 0.524 (0.053) & 13.774 & 0.938\\
-\hspace{1em}xgboost-aft & -1.18 (0.255) & 0.703 (0.014) & 9.791 & 0.006\\
+\hspace{1em}aorsf-fast & 0.097 (0.012) & 0.710 (0.009) & 0.227 & 0.055\\
+\hspace{1em}aorsf-cph & 0.096 (0.011) & 0.709 (0.008) & 0.639 & 0.052\\
+\hspace{1em}aorsf-net & 0.096 (0.016) & 0.710 (0.012) & 51.707 & 0.045\\
+\hspace{1em}cif-standard & 0.093 (0.016) & 0.700 (0.016) & 1.060 & 3.235\\
+\hspace{1em}cif-rotate & 0.092 (0.017) & 0.698 (0.016) & 12.951 & 3.530\\
+\hspace{1em}obliqueRSF-net & 0.089 (0.007) & 0.708 (0.011) & 263.760 & 15.788\\
+\hspace{1em}aorsf-random & 0.086 (0.005) & 0.702 (0.004) & 1.285 & 0.051\\
+\hspace{1em}cif-extension & 0.082 (0.005) & 0.703 (0.010) & 8.427 & 3.628\\
+\hspace{1em}rsf-standard & 0.081 (0.019) & 0.695 (0.012) & 1.290 & 0.145\\
+\hspace{1em}ranger-extratrees & 0.075 (0.008) & 0.694 (0.010) & 0.562 & 0.225\\
+\hspace{1em}glmnet-cox & 0.069 (0.012) & 0.692 (0.018) & 0.117 & 0.003\\
+\hspace{1em}xgboost-cox & 0.056 (0.011) & 0.691 (0.012) & 3.446 & 0.003\\
+\hspace{1em}nn-cox & -0.037 (0.064) & 0.519 (0.030) & 22.950 & 1.477\\
+\hspace{1em}xgboost-aft & -1.20 (0.298) & 0.698 (0.015) & 11.457 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.064 (0.030) & 0.739 (0.027) & 1844.847 & 13.621\\
-\hspace{1em}cif-rotate & 0.061 (0.016) & 0.735 (0.021) & 7099.601 & 384.127\\
-\hspace{1em}aorsf-cph & 0.060 (0.043) & 0.740 (0.020) & 1.567 & 0.176\\
-\hspace{1em}cif-standard & 0.060 (0.020) & 0.735 (0.024) & 7.310 & 3.860\\
-\hspace{1em}cif-extension & 0.059 (0.016) & 0.736 (0.025) & 51.533 & 7.534\\
-\hspace{1em}aorsf-fast & 0.058 (0.041) & 0.737 (0.023) & 1.118 & 0.173\\
-\hspace{1em}ranger-extratrees & 0.053 (0.031) & 0.730 (0.022) & 0.387 & 1.014\\
-\hspace{1em}xgboost-cox & 0.034 (0.009) & 0.736 (0.030) & 2.480 & 0.007\\
-\hspace{1em}glmnet-cox & 0.026 (0.039) & 0.711 (0.032) & 5.909 & 0.006\\
-\hspace{1em}aorsf-random & 0.021 (0.016) & 0.686 (0.029) & 1.763 & 0.185\\
-\hspace{1em}rsf-standard & 0.021 (0.056) & 0.695 (0.037) & 0.356 & 0.625\\
-\hspace{1em}aorsf-net & 0.019 (0.095) & 0.745 (0.022) & 431.378 & 0.168\\
-\hspace{1em}nn-cox & -0.024 (0.059) & 0.656 (0.069) & 17.924 & 1.897\\
-\hspace{1em}xgboost-aft & -2.95 (0.868) & 0.737 (0.022) & 8.909 & 0.009\\
+\hspace{1em}obliqueRSF-net & 0.069 (0.036) & 0.755 (0.030) & 1875.318 & 12.911\\
+\hspace{1em}cif-standard & 0.064 (0.027) & 0.752 (0.026) & 7.791 & 3.966\\
+\hspace{1em}cif-rotate & 0.062 (0.021) & 0.741 (0.017) & 6623.673 & 366.471\\
+\hspace{1em}cif-extension & 0.060 (0.021) & 0.748 (0.024) & 42.790 & 6.410\\
+\hspace{1em}aorsf-cph & 0.057 (0.054) & 0.747 (0.019) & 1.313 & 0.169\\
+\hspace{1em}aorsf-fast & 0.056 (0.054) & 0.749 (0.023) & 0.735 & 0.170\\
+\hspace{1em}ranger-extratrees & 0.054 (0.043) & 0.746 (0.022) & 0.221 & 0.165\\
+\hspace{1em}glmnet-cox & 0.026 (0.023) & 0.722 (0.019) & 5.768 & 0.007\\
+\hspace{1em}xgboost-cox & 0.025 (0.027) & 0.741 (0.017) & 2.311 & 0.007\\
+\hspace{1em}aorsf-random & 0.023 (0.023) & 0.706 (0.035) & 1.402 & 0.174\\
+\hspace{1em}aorsf-net & 0.014 (0.110) & 0.754 (0.014) & 461.060 & 0.176\\
+\hspace{1em}rsf-standard & 0.013 (0.073) & 0.698 (0.053) & 0.327 & 0.451\\
+\hspace{1em}nn-cox & -0.039 (0.088) & 0.650 (0.075) & 16.127 & 1.654\\
+\hspace{1em}xgboost-aft & -3.09 (1.10) & 0.749 (0.020) & 9.377 & 0.010\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.122 (0.024) & 0.801 (0.041) & 0.259 & 0.002\\
-\hspace{1em}aorsf-cph & 0.104 (0.040) & 0.775 (0.038) & 0.165 & 0.021\\
-\hspace{1em}aorsf-fast & 0.101 (0.040) & 0.774 (0.038) & 0.083 & 0.021\\
-\hspace{1em}aorsf-net & 0.101 (0.040) & 0.767 (0.039) & 12.969 & 0.019\\
-\hspace{1em}obliqueRSF-net & 0.096 (0.028) & 0.774 (0.038) & 93.139 & 5.120\\
-\hspace{1em}cif-standard & 0.095 (0.039) & 0.757 (0.039) & 0.283 & 1.046\\
-\hspace{1em}aorsf-random & 0.093 (0.026) & 0.766 (0.038) & 0.293 & 0.020\\
-\hspace{1em}cif-extension & 0.090 (0.037) & 0.737 (0.042) & 4.384 & 2.202\\
-\hspace{1em}cif-rotate & 0.090 (0.050) & 0.759 (0.031) & 5.744 & 2.351\\
-\hspace{1em}rsf-standard & 0.081 (0.045) & 0.737 (0.042) & 0.109 & 0.042\\
-\hspace{1em}ranger-extratrees & 0.075 (0.012) & 0.746 (0.038) & 0.038 & 0.129\\
-\hspace{1em}xgboost-cox & 0.060 (0.060) & 0.723 (0.118) & 2.339 & 0.002\\
-\hspace{1em}nn-cox & -0.005 (0.008) & 0.530 (0.074) & 12.863 & 0.443\\
-\hspace{1em}xgboost-aft & -2.66 (0.438) & 0.763 (0.047) & 8.300 & 0.006\\
+\hspace{1em}glmnet-cox & 0.117 (0.032) & 0.784 (0.045) & 0.096 & 0.002\\
+\hspace{1em}aorsf-cph & 0.097 (0.055) & 0.774 (0.044) & 0.164 & 0.019\\
+\hspace{1em}cif-extension & 0.097 (0.042) & 0.749 (0.045) & 5.240 & 2.305\\
+\hspace{1em}aorsf-net & 0.095 (0.052) & 0.770 (0.040) & 12.784 & 0.018\\
+\hspace{1em}aorsf-fast & 0.094 (0.053) & 0.774 (0.044) & 0.086 & 0.021\\
+\hspace{1em}obliqueRSF-net & 0.090 (0.035) & 0.771 (0.047) & 101.477 & 5.378\\
+\hspace{1em}rsf-standard & 0.090 (0.062) & 0.758 (0.042) & 0.562 & 0.038\\
+\hspace{1em}aorsf-random & 0.086 (0.036) & 0.763 (0.049) & 0.296 & 0.019\\
+\hspace{1em}cif-rotate & 0.085 (0.067) & 0.763 (0.036) & 6.328 & 2.376\\
+\hspace{1em}cif-standard & 0.085 (0.049) & 0.755 (0.049) & 0.730 & 1.121\\
+\hspace{1em}ranger-extratrees & 0.078 (0.017) & 0.752 (0.052) & 0.046 & 0.080\\
+\hspace{1em}xgboost-cox & 0.047 (0.074) & 0.717 (0.119) & 2.504 & 0.002\\
+\hspace{1em}nn-cox & 0.013 (0.041) & 0.493 (0.145) & 11.346 & 0.563\\
+\hspace{1em}xgboost-aft & -2.48 (0.436) & 0.754 (0.057) & 6.730 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.031 (0.017) & 0.625 (0.020) & 0.270 & 0.003\\
-\hspace{1em}xgboost-cox & 0.014 (0.017) & 0.610 (0.027) & 1.867 & 0.003\\
-\hspace{1em}ranger-extratrees & 0.014 (0.019) & 0.593 (0.031) & 0.032 & 0.079\\
-\hspace{1em}obliqueRSF-net & 0.014 (0.015) & 0.597 (0.027) & 218.615 & 6.376\\
-\hspace{1em}aorsf-random & 0.011 (0.021) & 0.601 (0.029) & 0.428 & 0.021\\
-\hspace{1em}aorsf-cph & 0.009 (0.024) & 0.600 (0.031) & 0.276 & 0.026\\
-\hspace{1em}aorsf-fast & 0.007 (0.024) & 0.599 (0.031) & 0.116 & 0.024\\
-\hspace{1em}aorsf-net & 0.007 (0.026) & 0.597 (0.033) & 18.700 & 0.022\\
-\hspace{1em}cif-standard & 0.005 (0.020) & 0.598 (0.026) & 0.282 & 1.105\\
-\hspace{1em}nn-cox & -0.002 (0.021) & 0.556 (0.057) & 11.608 & 0.458\\
-\hspace{1em}cif-extension & -0.008 (0.026) & 0.583 (0.034) & 5.355 & 2.231\\
-\hspace{1em}cif-rotate & -0.012 (0.025) & 0.590 (0.033) & 6.589 & 2.863\\
-\hspace{1em}rsf-standard & -0.031 (0.035) & 0.580 (0.032) & 0.744 & 0.085\\
-\hspace{1em}xgboost-aft & -0.915 (0.359) & 0.584 (0.047) & 6.551 & 0.006\\
+\hspace{1em}glmnet-cox & 0.036 (0.023) & 0.625 (0.028) & 0.109 & 0.002\\
+\hspace{1em}xgboost-cox & 0.023 (0.012) & 0.608 (0.029) & 1.694 & 0.002\\
+\hspace{1em}obliqueRSF-net & 0.019 (0.018) & 0.593 (0.036) & 225.137 & 6.199\\
+\hspace{1em}ranger-extratrees & 0.018 (0.023) & 0.586 (0.042) & 0.045 & 0.078\\
+\hspace{1em}aorsf-random & 0.017 (0.027) & 0.594 (0.038) & 0.427 & 0.021\\
+\hspace{1em}aorsf-cph & 0.011 (0.034) & 0.591 (0.040) & 0.318 & 0.026\\
+\hspace{1em}aorsf-fast & 0.011 (0.033) & 0.589 (0.039) & 0.128 & 0.023\\
+\hspace{1em}aorsf-net & 0.008 (0.036) & 0.587 (0.043) & 20.070 & 0.022\\
+\hspace{1em}cif-standard & 0.006 (0.028) & 0.591 (0.034) & 0.721 & 1.132\\
+\hspace{1em}nn-cox & -0.003 (0.030) & 0.534 (0.074) & 11.088 & 0.436\\
+\hspace{1em}cif-extension & -0.004 (0.037) & 0.578 (0.045) & 6.192 & 2.357\\
+\hspace{1em}cif-rotate & -0.008 (0.034) & 0.581 (0.036) & 7.111 & 2.207\\
+\hspace{1em}rsf-standard & -0.025 (0.041) & 0.578 (0.038) & 1.326 & 0.086\\
+\hspace{1em}xgboost-aft & -0.974 (0.221) & 0.574 (0.060) & 6.179 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.123 (0.015) & 0.744 (0.017) & 284.837 & 7.018\\
-\hspace{1em}cif-standard & 0.123 (0.020) & 0.743 (0.019) & 0.425 & 1.696\\
-\hspace{1em}rsf-standard & 0.123 (0.022) & 0.738 (0.018) & 0.994 & 0.114\\
-\hspace{1em}aorsf-net & 0.121 (0.022) & 0.738 (0.018) & 38.168 & 0.038\\
-\hspace{1em}aorsf-cph & 0.118 (0.026) & 0.733 (0.018) & 0.405 & 0.041\\
-\hspace{1em}aorsf-fast & 0.115 (0.025) & 0.731 (0.018) & 0.165 & 0.041\\
-\hspace{1em}cif-extension & 0.115 (0.020) & 0.744 (0.022) & 8.087 & 3.238\\
-\hspace{1em}cif-rotate & 0.111 (0.022) & 0.731 (0.015) & 10.921 & 2.838\\
-\hspace{1em}aorsf-random & 0.103 (0.028) & 0.721 (0.029) & 0.755 & 0.037\\
-\hspace{1em}ranger-extratrees & 0.092 (0.024) & 0.738 (0.032) & 0.062 & 0.177\\
-\hspace{1em}xgboost-cox & 0.084 (0.014) & 0.728 (0.018) & 3.312 & 0.004\\
-\hspace{1em}glmnet-cox & 0.081 (0.019) & 0.722 (0.022) & 0.118 & 0.003\\
-\hspace{1em}nn-cox & -0.004 (0.005) & 0.509 (0.040) & 14.255 & 1.400\\
-\hspace{1em}xgboost-aft & -1.09 (0.122) & 0.728 (0.019) & 9.463 & 0.006\\
+\hspace{1em}cif-standard & 0.127 (0.013) & 0.748 (0.013) & 0.874 & 2.321\\
+\hspace{1em}aorsf-net & 0.127 (0.018) & 0.745 (0.013) & 40.051 & 0.039\\
+\hspace{1em}obliqueRSF-net & 0.125 (0.012) & 0.746 (0.013) & 329.638 & 6.966\\
+\hspace{1em}rsf-standard & 0.124 (0.024) & 0.745 (0.018) & 1.269 & 0.116\\
+\hspace{1em}aorsf-cph & 0.121 (0.024) & 0.738 (0.016) & 0.440 & 0.038\\
+\hspace{1em}aorsf-fast & 0.120 (0.023) & 0.737 (0.017) & 0.180 & 0.038\\
+\hspace{1em}cif-extension & 0.120 (0.013) & 0.751 (0.015) & 8.690 & 3.473\\
+\hspace{1em}aorsf-random & 0.112 (0.020) & 0.732 (0.020) & 1.244 & 0.036\\
+\hspace{1em}cif-rotate & 0.107 (0.020) & 0.731 (0.012) & 11.358 & 2.827\\
+\hspace{1em}ranger-extratrees & 0.102 (0.011) & 0.750 (0.021) & 0.472 & 0.131\\
+\hspace{1em}xgboost-cox & 0.084 (0.012) & 0.733 (0.016) & 2.844 & 0.004\\
+\hspace{1em}glmnet-cox & 0.080 (0.020) & 0.724 (0.021) & 0.116 & 0.002\\
+\hspace{1em}nn-cox & -0.003 (0.003) & 0.499 (0.018) & 11.168 & 1.086\\
+\hspace{1em}xgboost-aft & -1.13 (0.163) & 0.734 (0.017) & 11.815 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.077 (0.020) & 0.746 (0.033) & 0.176 & 0.039\\
-\hspace{1em}aorsf-net & 0.074 (0.019) & 0.743 (0.033) & 28.167 & 0.039\\
-\hspace{1em}glmnet-cox & 0.074 (0.041) & 0.729 (0.085) & 0.514 & 0.003\\
-\hspace{1em}aorsf-cph & 0.072 (0.021) & 0.740 (0.038) & 0.416 & 0.039\\
-\hspace{1em}obliqueRSF-net & 0.064 (0.013) & 0.738 (0.028) & 239.059 & 11.676\\
-\hspace{1em}cif-rotate & 0.062 (0.017) & 0.715 (0.029) & 34.699 & 4.860\\
-\hspace{1em}cif-standard & 0.059 (0.014) & 0.732 (0.027) & 0.790 & 3.278\\
-\hspace{1em}cif-extension & 0.053 (0.011) & 0.724 (0.029) & 14.497 & 6.192\\
-\hspace{1em}ranger-extratrees & 0.052 (0.014) & 0.731 (0.031) & 0.779 & 0.461\\
-\hspace{1em}rsf-standard & 0.047 (0.026) & 0.709 (0.032) & 0.177 & 0.059\\
-\hspace{1em}aorsf-random & 0.033 (0.010) & 0.692 (0.035) & 0.489 & 0.040\\
-\hspace{1em}xgboost-cox & 0.031 (0.052) & 0.743 (0.024) & 5.143 & 0.003\\
-\hspace{1em}nn-cox & 0.028 (0.038) & 0.684 (0.085) & 13.230 & 0.544\\
-\hspace{1em}xgboost-aft & -5.44 (1.23) & 0.729 (0.023) & 13.003 & 0.006\\
+\hspace{1em}aorsf-fast & 0.073 (0.016) & 0.745 (0.034) & 0.167 & 0.038\\
+\hspace{1em}aorsf-net & 0.068 (0.016) & 0.739 (0.036) & 28.026 & 0.041\\
+\hspace{1em}aorsf-cph & 0.068 (0.016) & 0.738 (0.037) & 0.399 & 0.037\\
+\hspace{1em}obliqueRSF-net & 0.064 (0.013) & 0.738 (0.029) & 225.137 & 10.657\\
+\hspace{1em}xgboost-cox & 0.059 (0.018) & 0.741 (0.029) & 3.546 & 0.003\\
+\hspace{1em}cif-standard & 0.056 (0.012) & 0.727 (0.028) & 1.879 & 3.647\\
+\hspace{1em}glmnet-cox & 0.055 (0.047) & 0.700 (0.116) & 0.939 & 0.003\\
+\hspace{1em}cif-rotate & 0.055 (0.019) & 0.709 (0.037) & 35.679 & 5.129\\
+\hspace{1em}cif-extension & 0.052 (0.011) & 0.725 (0.037) & 13.726 & 5.891\\
+\hspace{1em}ranger-extratrees & 0.051 (0.011) & 0.732 (0.029) & 0.495 & 0.188\\
+\hspace{1em}rsf-standard & 0.038 (0.026) & 0.702 (0.037) & 0.592 & 0.059\\
+\hspace{1em}aorsf-random & 0.028 (0.006) & 0.676 (0.023) & 0.933 & 0.040\\
+\hspace{1em}nn-cox & 0.007 (0.017) & 0.609 (0.085) & 10.911 & 0.533\\
+\hspace{1em}xgboost-aft & -6.16 (1.21) & 0.727 (0.031) & 12.980 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.083 (0.021) & 0.724 (0.027) & 0.707 & 0.057\\
-\hspace{1em}aorsf-net & 0.083 (0.020) & 0.722 (0.024) & 53.989 & 0.059\\
-\hspace{1em}aorsf-fast & 0.083 (0.022) & 0.724 (0.026) & 0.258 & 0.056\\
-\hspace{1em}obliqueRSF-net & 0.074 (0.013) & 0.721 (0.024) & 370.352 & 8.931\\
-\hspace{1em}ranger-extratrees & 0.073 (0.014) & 0.720 (0.027) & 0.501 & 0.191\\
-\hspace{1em}cif-standard & 0.069 (0.012) & 0.714 (0.024) & 0.795 & 3.266\\
-\hspace{1em}cif-rotate & 0.067 (0.023) & 0.706 (0.031) & 40.710 & 5.037\\
-\hspace{1em}glmnet-cox & 0.066 (0.022) & 0.705 (0.026) & 0.415 & 0.003\\
-\hspace{1em}cif-extension & 0.063 (0.010) & 0.714 (0.019) & 16.510 & 6.373\\
-\hspace{1em}rsf-standard & 0.055 (0.028) & 0.693 (0.028) & 1.136 & 0.117\\
-\hspace{1em}aorsf-random & 0.051 (0.013) & 0.688 (0.028) & 0.880 & 0.054\\
-\hspace{1em}nn-cox & 0.047 (0.032) & 0.686 (0.061) & 14.014 & 0.620\\
-\hspace{1em}xgboost-cox & 0.041 (0.013) & 0.699 (0.028) & 3.763 & 0.003\\
-\hspace{1em}xgboost-aft & -2.23 (0.339) & 0.695 (0.029) & 16.064 & 0.007\\
+\hspace{1em}aorsf-cph & 0.085 (0.023) & 0.734 (0.033) & 0.707 & 0.056\\
+\hspace{1em}aorsf-fast & 0.083 (0.022) & 0.734 (0.032) & 0.254 & 0.056\\
+\hspace{1em}aorsf-net & 0.082 (0.024) & 0.729 (0.032) & 60.358 & 0.059\\
+\hspace{1em}obliqueRSF-net & 0.075 (0.018) & 0.726 (0.033) & 388.086 & 9.114\\
+\hspace{1em}ranger-extratrees & 0.073 (0.017) & 0.725 (0.032) & 0.464 & 0.188\\
+\hspace{1em}cif-standard & 0.071 (0.016) & 0.718 (0.032) & 1.643 & 3.240\\
+\hspace{1em}cif-rotate & 0.069 (0.033) & 0.710 (0.044) & 43.469 & 5.424\\
+\hspace{1em}glmnet-cox & 0.069 (0.021) & 0.710 (0.032) & 0.693 & 0.003\\
+\hspace{1em}cif-extension & 0.064 (0.014) & 0.719 (0.027) & 15.673 & 5.961\\
+\hspace{1em}rsf-standard & 0.057 (0.028) & 0.699 (0.038) & 2.421 & 0.130\\
+\hspace{1em}aorsf-random & 0.053 (0.015) & 0.693 (0.034) & 1.234 & 0.053\\
+\hspace{1em}nn-cox & 0.049 (0.029) & 0.710 (0.022) & 13.646 & 0.669\\
+\hspace{1em}xgboost-cox & 0.043 (0.018) & 0.705 (0.039) & 2.793 & 0.003\\
+\hspace{1em}xgboost-aft & -2.37 (0.383) & 0.702 (0.041) & 14.879 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.056 (0.012) & 0.729 (0.022) & 159.153 & 20.730\\
-\hspace{1em}aorsf-fast & 0.052 (0.008) & 0.733 (0.020) & 0.893 & 0.234\\
-\hspace{1em}aorsf-cph & 0.052 (0.008) & 0.731 (0.018) & 3.216 & 0.237\\
-\hspace{1em}aorsf-net & 0.052 (0.008) & 0.730 (0.018) & 123.347 & 0.229\\
-\hspace{1em}rsf-standard & 0.051 (0.009) & 0.728 (0.014) & 2.186 & 0.832\\
-\hspace{1em}cif-standard & 0.049 (0.008) & 0.730 (0.018) & 10.333 & 36.554\\
-\hspace{1em}obliqueRSF-net & 0.049 (0.007) & 0.728 (0.020) & 387.022 & 78.390\\
-\hspace{1em}ranger-extratrees & 0.045 (0.008) & 0.727 (0.017) & 5.104 & 6.168\\
-\hspace{1em}glmnet-cox & 0.035 (0.007) & 0.707 (0.020) & 1.413 & 0.006\\
-\hspace{1em}cif-extension & 0.035 (0.004) & 0.725 (0.022) & 50.118 & 18.785\\
-\hspace{1em}xgboost-cox & 0.029 (0.008) & 0.715 (0.025) & 4.244 & 0.007\\
-\hspace{1em}nn-cox & 0.029 (0.014) & 0.693 (0.024) & 14.198 & 8.076\\
-\hspace{1em}aorsf-random & 0.028 (0.003) & 0.685 (0.013) & 2.307 & 0.217\\
-\hspace{1em}xgboost-aft & -4.31 (0.500) & 0.720 (0.012) & 13.609 & 0.007\\
+\hspace{1em}cif-rotate & 0.055 (0.008) & 0.724 (0.018) & 158.338 & 21.084\\
+\hspace{1em}aorsf-cph & 0.054 (0.005) & 0.729 (0.018) & 3.324 & 0.231\\
+\hspace{1em}aorsf-fast & 0.053 (0.006) & 0.729 (0.020) & 1.271 & 0.225\\
+\hspace{1em}aorsf-net & 0.052 (0.005) & 0.725 (0.018) & 131.969 & 0.232\\
+\hspace{1em}rsf-standard & 0.052 (0.006) & 0.727 (0.014) & 2.874 & 0.985\\
+\hspace{1em}cif-standard & 0.049 (0.005) & 0.729 (0.014) & 10.011 & 35.980\\
+\hspace{1em}obliqueRSF-net & 0.049 (0.006) & 0.724 (0.018) & 372.165 & 72.309\\
+\hspace{1em}ranger-extratrees & 0.045 (0.006) & 0.725 (0.013) & 5.621 & 3.271\\
+\hspace{1em}glmnet-cox & 0.037 (0.003) & 0.703 (0.017) & 1.141 & 0.004\\
+\hspace{1em}cif-extension & 0.035 (0.004) & 0.725 (0.016) & 50.375 & 18.419\\
+\hspace{1em}xgboost-cox & 0.030 (0.008) & 0.708 (0.023) & 3.993 & 0.006\\
+\hspace{1em}aorsf-random & 0.027 (0.003) & 0.680 (0.014) & 2.518 & 0.218\\
+\hspace{1em}nn-cox & 0.019 (0.018) & 0.637 (0.063) & 16.991 & 10.575\\
+\hspace{1em}xgboost-aft & -4.47 (0.512) & 0.722 (0.009) & 14.335 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.064 (0.011) & 0.807 (0.007) & 1.306 & 0.374\\
-\hspace{1em}aorsf-net & 0.063 (0.012) & 0.803 (0.008) & 174.087 & 0.379\\
-\hspace{1em}obliqueRSF-net & 0.061 (0.008) & 0.806 (0.007) & 486.618 & 269.151\\
-\hspace{1em}aorsf-cph & 0.061 (0.011) & 0.801 (0.010) & 5.635 & 0.385\\
-\hspace{1em}cif-rotate & 0.058 (0.008) & 0.801 (0.010) & 311.704 & 46.721\\
-\hspace{1em}cif-standard & 0.058 (0.007) & 0.801 (0.009) & 24.315 & 98.498\\
-\hspace{1em}rsf-standard & 0.056 (0.014) & 0.794 (0.011) & 4.745 & 0.433\\
-\hspace{1em}ranger-extratrees & 0.047 (0.005) & 0.795 (0.007) & 6.566 & 11.394\\
-\hspace{1em}cif-extension & 0.047 (0.004) & 0.803 (0.008) & 103.940 & 34.786\\
-\hspace{1em}glmnet-cox & 0.040 (0.021) & 0.774 (0.009) & 5.519 & 0.006\\
-\hspace{1em}nn-cox & 0.032 (0.025) & 0.760 (0.030) & 22.091 & 19.964\\
-\hspace{1em}aorsf-random & 0.032 (0.006) & 0.740 (0.015) & 4.558 & 0.516\\
-\hspace{1em}xgboost-cox & 0.013 (0.019) & 0.804 (0.007) & 5.369 & 0.010\\
-\hspace{1em}xgboost-aft & -9.73 (1.00) & 0.802 (0.008) & 26.660 & 0.011\\
+\hspace{1em}aorsf-fast & 0.064 (0.010) & 0.811 (0.007) & 1.254 & 0.358\\
+\hspace{1em}aorsf-net & 0.063 (0.010) & 0.807 (0.009) & 181.663 & 0.387\\
+\hspace{1em}obliqueRSF-net & 0.063 (0.007) & 0.809 (0.005) & 511.374 & 266.957\\
+\hspace{1em}aorsf-cph & 0.061 (0.011) & 0.804 (0.009) & 5.063 & 0.365\\
+\hspace{1em}cif-rotate & 0.059 (0.006) & 0.803 (0.009) & 305.481 & 38.499\\
+\hspace{1em}cif-standard & 0.059 (0.006) & 0.804 (0.008) & 22.778 & 96.623\\
+\hspace{1em}rsf-standard & 0.057 (0.012) & 0.794 (0.012) & 2.696 & 0.440\\
+\hspace{1em}ranger-extratrees & 0.048 (0.004) & 0.798 (0.009) & 5.753 & 6.995\\
+\hspace{1em}cif-extension & 0.047 (0.004) & 0.804 (0.010) & 96.367 & 26.939\\
+\hspace{1em}glmnet-cox & 0.039 (0.018) & 0.773 (0.009) & 5.042 & 0.007\\
+\hspace{1em}aorsf-random & 0.032 (0.005) & 0.747 (0.014) & 3.235 & 0.419\\
+\hspace{1em}nn-cox & 0.032 (0.017) & 0.767 (0.025) & 14.750 & 18.081\\
+\hspace{1em}xgboost-cox & 0.012 (0.024) & 0.803 (0.008) & 4.399 & 0.008\\
+\hspace{1em}xgboost-aft & -9.98 (1.26) & 0.804 (0.009) & 16.414 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.144 (0.009) & 0.791 (0.010) & 316.581 & 0.547\\
-\hspace{1em}aorsf-fast & 0.143 (0.009) & 0.791 (0.011) & 1.936 & 0.562\\
-\hspace{1em}aorsf-cph & 0.143 (0.008) & 0.790 (0.010) & 7.232 & 0.533\\
-\hspace{1em}rsf-standard & 0.140 (0.009) & 0.783 (0.011) & 3.983 & 0.470\\
-\hspace{1em}obliqueRSF-net & 0.138 (0.008) & 0.789 (0.011) & 1248.639 & 166.262\\
-\hspace{1em}cif-standard & 0.133 (0.007) & 0.786 (0.011) & 23.230 & 98.540\\
-\hspace{1em}cif-rotate & 0.124 (0.007) & 0.779 (0.011) & 322.280 & 37.520\\
-\hspace{1em}glmnet-cox & 0.114 (0.022) & 0.782 (0.012) & 1.774 & 0.007\\
-\hspace{1em}ranger-extratrees & 0.113 (0.005) & 0.783 (0.010) & 7.801 & 17.881\\
-\hspace{1em}nn-cox & 0.113 (0.041) & 0.756 (0.091) & 54.045 & 35.720\\
-\hspace{1em}cif-extension & 0.092 (0.003) & 0.778 (0.010) & 108.878 & 32.320\\
-\hspace{1em}aorsf-random & 0.070 (0.004) & 0.727 (0.008) & 7.162 & 0.550\\
-\hspace{1em}xgboost-cox & 0.057 (0.032) & 0.791 (0.010) & 10.747 & 0.010\\
-\hspace{1em}xgboost-aft & -4.50 (0.243) & 0.789 (0.009) & 18.378 & 0.010\\
+\hspace{1em}aorsf-net & 0.146 (0.004) & 0.790 (0.008) & 326.502 & 0.545\\
+\hspace{1em}aorsf-fast & 0.146 (0.004) & 0.791 (0.009) & 1.945 & 0.601\\
+\hspace{1em}aorsf-cph & 0.144 (0.004) & 0.790 (0.008) & 6.964 & 0.509\\
+\hspace{1em}rsf-standard & 0.143 (0.003) & 0.784 (0.008) & 4.756 & 0.479\\
+\hspace{1em}obliqueRSF-net & 0.140 (0.006) & 0.790 (0.010) & 1155.640 & 154.298\\
+\hspace{1em}nn-cox & 0.137 (0.007) & 0.785 (0.007) & 26.956 & 20.710\\
+\hspace{1em}cif-standard & 0.134 (0.006) & 0.786 (0.010) & 21.844 & 107.533\\
+\hspace{1em}cif-rotate & 0.122 (0.006) & 0.777 (0.011) & 323.806 & 37.456\\
+\hspace{1em}ranger-extratrees & 0.114 (0.005) & 0.782 (0.011) & 6.711 & 6.068\\
+\hspace{1em}glmnet-cox & 0.110 (0.023) & 0.778 (0.011) & 1.500 & 0.007\\
+\hspace{1em}cif-extension & 0.092 (0.004) & 0.779 (0.011) & 109.021 & 30.388\\
+\hspace{1em}aorsf-random & 0.071 (0.003) & 0.728 (0.010) & 5.543 & 0.549\\
+\hspace{1em}xgboost-cox & 0.061 (0.013) & 0.790 (0.008) & 8.622 & 0.010\\
+\hspace{1em}xgboost-aft & -4.55 (0.242) & 0.789 (0.008) & 20.108 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.114 (0.011) & 0.866 (0.014) & 1.172 & 0.324\\
-\hspace{1em}aorsf-net & 0.114 (0.011) & 0.864 (0.016) & 147.986 & 0.338\\
-\hspace{1em}aorsf-cph & 0.109 (0.010) & 0.858 (0.017) & 5.602 & 0.339\\
-\hspace{1em}rsf-standard & 0.108 (0.012) & 0.857 (0.013) & 2.784 & 0.895\\
-\hspace{1em}obliqueRSF-net & 0.107 (0.009) & 0.868 (0.014) & 391.939 & 332.468\\
-\hspace{1em}cif-rotate & 0.106 (0.011) & 0.873 (0.014) & 259.218 & 35.800\\
-\hspace{1em}cif-standard & 0.101 (0.010) & 0.863 (0.015) & 23.601 & 96.846\\
-\hspace{1em}nn-cox & 0.083 (0.015) & 0.828 (0.024) & 18.796 & 15.505\\
-\hspace{1em}cif-extension & 0.077 (0.005) & 0.864 (0.012) & 91.823 & 30.050\\
-\hspace{1em}ranger-extratrees & 0.075 (0.006) & 0.847 (0.018) & 7.714 & 11.655\\
-\hspace{1em}aorsf-random & 0.063 (0.006) & 0.795 (0.019) & 3.483 & 0.375\\
-\hspace{1em}glmnet-cox & 0.056 (0.047) & 0.779 (0.148) & 3.484 & 0.011\\
-\hspace{1em}xgboost-cox & -0.008 (0.011) & 0.873 (0.012) & 8.137 & 0.010\\
-\hspace{1em}xgboost-aft & -10.9 (1.08) & 0.873 (0.015) & 18.818 & 0.010\\
+\hspace{1em}aorsf-fast & 0.112 (0.015) & 0.864 (0.019) & 1.187 & 0.323\\
+\hspace{1em}aorsf-net & 0.111 (0.015) & 0.860 (0.020) & 163.971 & 0.348\\
+\hspace{1em}aorsf-cph & 0.106 (0.014) & 0.855 (0.022) & 5.011 & 0.331\\
+\hspace{1em}rsf-standard & 0.104 (0.016) & 0.855 (0.017) & 2.703 & 1.010\\
+\hspace{1em}cif-rotate & 0.104 (0.015) & 0.869 (0.020) & 260.204 & 36.664\\
+\hspace{1em}obliqueRSF-net & 0.103 (0.010) & 0.864 (0.019) & 415.985 & 339.753\\
+\hspace{1em}cif-standard & 0.097 (0.012) & 0.858 (0.019) & 31.107 & 118.751\\
+\hspace{1em}cif-extension & 0.075 (0.005) & 0.861 (0.017) & 94.308 & 30.399\\
+\hspace{1em}ranger-extratrees & 0.074 (0.008) & 0.842 (0.025) & 4.955 & 6.617\\
+\hspace{1em}nn-cox & 0.067 (0.027) & 0.824 (0.032) & 13.821 & 14.093\\
+\hspace{1em}aorsf-random & 0.062 (0.009) & 0.792 (0.023) & 2.605 & 0.376\\
+\hspace{1em}glmnet-cox & 0.055 (0.050) & 0.779 (0.157) & 3.773 & 0.007\\
+\hspace{1em}xgboost-cox & -0.010 (0.011) & 0.868 (0.015) & 6.597 & 0.022\\
+\hspace{1em}xgboost-aft & -11.1 (1.17) & 0.868 (0.018) & 19.343 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.025 (0.004) & 0.766 (0.018) & 269.642 & 35.908\\
-\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.766 (0.015) & 1.144 & 0.325\\
-\hspace{1em}glmnet-cox & 0.025 (0.006) & 0.769 (0.017) & 3.082 & 0.006\\
-\hspace{1em}obliqueRSF-net & 0.024 (0.004) & 0.767 (0.016) & 357.106 & 281.765\\
-\hspace{1em}cif-standard & 0.024 (0.004) & 0.763 (0.018) & 24.960 & 98.465\\
-\hspace{1em}aorsf-net & 0.024 (0.006) & 0.759 (0.016) & 138.120 & 0.340\\
-\hspace{1em}aorsf-cph & 0.024 (0.005) & 0.759 (0.016) & 4.983 & 0.325\\
-\hspace{1em}ranger-extratrees & 0.021 (0.003) & 0.758 (0.018) & 7.114 & 11.973\\
-\hspace{1em}cif-extension & 0.021 (0.002) & 0.772 (0.019) & 95.005 & 32.157\\
-\hspace{1em}rsf-standard & 0.019 (0.010) & 0.745 (0.020) & 2.679 & 0.865\\
-\hspace{1em}nn-cox & 0.017 (0.005) & 0.732 (0.037) & 18.484 & 20.376\\
-\hspace{1em}aorsf-random & 0.013 (0.003) & 0.713 (0.026) & 3.517 & 0.343\\
-\hspace{1em}xgboost-cox & 0.003 (0.021) & 0.765 (0.023) & 5.210 & 0.009\\
-\hspace{1em}xgboost-aft & -13.9 (1.53) & 0.769 (0.018) & 17.608 & 0.009\\
+\hspace{1em}cif-rotate & 0.027 (0.003) & 0.769 (0.014) & 278.786 & 36.095\\
+\hspace{1em}aorsf-fast & 0.027 (0.002) & 0.769 (0.015) & 1.101 & 0.318\\
+\hspace{1em}obliqueRSF-net & 0.027 (0.002) & 0.768 (0.014) & 370.155 & 296.119\\
+\hspace{1em}glmnet-cox & 0.026 (0.006) & 0.762 (0.014) & 2.280 & 0.006\\
+\hspace{1em}cif-standard & 0.025 (0.002) & 0.761 (0.016) & 23.502 & 100.401\\
+\hspace{1em}aorsf-cph & 0.025 (0.003) & 0.760 (0.015) & 4.632 & 0.326\\
+\hspace{1em}aorsf-net & 0.024 (0.001) & 0.759 (0.013) & 140.310 & 0.334\\
+\hspace{1em}cif-extension & 0.022 (0.001) & 0.773 (0.016) & 93.321 & 29.177\\
+\hspace{1em}ranger-extratrees & 0.022 (0.000) & 0.757 (0.015) & 6.228 & 6.670\\
+\hspace{1em}rsf-standard & 0.021 (0.005) & 0.753 (0.018) & 2.551 & 1.012\\
+\hspace{1em}xgboost-cox & 0.020 (0.005) & 0.769 (0.011) & 3.475 & 0.008\\
+\hspace{1em}nn-cox & 0.019 (0.010) & 0.740 (0.053) & 17.371 & 20.141\\
+\hspace{1em}aorsf-random & 0.014 (0.002) & 0.717 (0.020) & 2.494 & 0.346\\
+\hspace{1em}xgboost-aft & -14.1 (1.04) & 0.773 (0.017) & 17.138 & 0.010\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.157 (0.017) & 0.741 (0.012) & 1.325 & 0.103\\
-\hspace{1em}cif-rotate & 0.156 (0.023) & 0.742 (0.018) & 15.136 & 4.979\\
-\hspace{1em}aorsf-fast & 0.155 (0.017) & 0.741 (0.012) & 0.434 & 0.097\\
-\hspace{1em}obliqueRSF-net & 0.153 (0.015) & 0.742 (0.014) & 231.507 & 12.455\\
-\hspace{1em}aorsf-net & 0.152 (0.017) & 0.739 (0.012) & 90.204 & 0.085\\
-\hspace{1em}cif-standard & 0.148 (0.017) & 0.736 (0.013) & 0.928 & 5.907\\
-\hspace{1em}rsf-standard & 0.148 (0.018) & 0.735 (0.012) & 1.988 & 0.193\\
-\hspace{1em}aorsf-random & 0.145 (0.014) & 0.734 (0.013) & 1.821 & 0.085\\
-\hspace{1em}cif-extension & 0.141 (0.010) & 0.744 (0.015) & 9.939 & 4.749\\
-\hspace{1em}glmnet-cox & 0.129 (0.019) & 0.722 (0.014) & 0.308 & 0.003\\
-\hspace{1em}xgboost-cox & 0.123 (0.012) & 0.731 (0.014) & 5.767 & 0.005\\
-\hspace{1em}ranger-extratrees & 0.115 (0.005) & 0.742 (0.014) & 0.062 & 0.364\\
-\hspace{1em}nn-cox & 0.062 (0.071) & 0.632 (0.118) & 17.238 & 0.720\\
-\hspace{1em}xgboost-aft & -0.870 (0.112) & 0.732 (0.016) & 15.477 & 0.007\\
+\hspace{1em}cif-rotate & 0.159 (0.027) & 0.745 (0.020) & 15.390 & 4.940\\
+\hspace{1em}aorsf-cph & 0.158 (0.018) & 0.743 (0.012) & 1.221 & 0.089\\
+\hspace{1em}aorsf-fast & 0.157 (0.020) & 0.743 (0.013) & 0.431 & 0.091\\
+\hspace{1em}obliqueRSF-net & 0.155 (0.018) & 0.743 (0.016) & 283.644 & 15.600\\
+\hspace{1em}aorsf-net & 0.154 (0.020) & 0.741 (0.013) & 130.364 & 0.091\\
+\hspace{1em}rsf-standard & 0.152 (0.022) & 0.739 (0.013) & 1.808 & 0.130\\
+\hspace{1em}cif-standard & 0.151 (0.021) & 0.739 (0.015) & 2.033 & 6.003\\
+\hspace{1em}aorsf-random & 0.147 (0.017) & 0.736 (0.015) & 2.273 & 0.084\\
+\hspace{1em}cif-extension & 0.143 (0.012) & 0.747 (0.017) & 10.521 & 4.415\\
+\hspace{1em}glmnet-cox & 0.131 (0.024) & 0.725 (0.015) & 0.116 & 0.003\\
+\hspace{1em}xgboost-cox & 0.125 (0.016) & 0.735 (0.015) & 5.066 & 0.004\\
+\hspace{1em}ranger-extratrees & 0.116 (0.006) & 0.744 (0.014) & 0.068 & 0.556\\
+\hspace{1em}nn-cox & 0.050 (0.044) & 0.641 (0.097) & 17.607 & 1.128\\
+\hspace{1em}xgboost-aft & -0.820 (0.130) & 0.737 (0.015) & 12.403 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.018 (0.010) & 0.674 (0.032) & 0.324 & 0.002\\
-\hspace{1em}aorsf-cph & 0.011 (0.009) & 0.646 (0.037) & 0.650 & 0.044\\
-\hspace{1em}xgboost-cox & 0.010 (0.007) & 0.647 (0.042) & 1.962 & 0.003\\
-\hspace{1em}aorsf-fast & 0.010 (0.009) & 0.642 (0.038) & 0.194 & 0.044\\
-\hspace{1em}obliqueRSF-net & 0.008 (0.006) & 0.635 (0.032) & 39.065 & 15.966\\
-\hspace{1em}ranger-extratrees & 0.007 (0.007) & 0.644 (0.035) & 0.061 & 0.197\\
-\hspace{1em}cif-extension & 0.007 (0.008) & 0.629 (0.028) & 8.637 & 4.451\\
-\hspace{1em}cif-standard & 0.007 (0.007) & 0.630 (0.032) & 0.956 & 6.010\\
-\hspace{1em}aorsf-net & 0.006 (0.010) & 0.645 (0.036) & 23.264 & 0.042\\
-\hspace{1em}aorsf-random & 0.006 (0.014) & 0.639 (0.037) & 0.519 & 0.042\\
-\hspace{1em}nn-cox & -0.005 (0.006) & 0.528 (0.083) & 10.752 & 0.593\\
-\hspace{1em}rsf-standard & -0.009 (0.015) & 0.626 (0.032) & 0.634 & 0.069\\
-\hspace{1em}cif-rotate & -0.034 (0.022) & 0.545 (0.032) & 12.464 & 4.154\\
-\hspace{1em}xgboost-aft & -5.78 (1.22) & 0.627 (0.045) & 9.325 & 0.006\\
+\hspace{1em}glmnet-cox & 0.014 (0.010) & 0.668 (0.033) & 0.107 & 0.002\\
+\hspace{1em}xgboost-cox & 0.011 (0.006) & 0.638 (0.042) & 2.752 & 0.004\\
+\hspace{1em}cif-extension & 0.011 (0.008) & 0.633 (0.040) & 8.797 & 4.210\\
+\hspace{1em}aorsf-cph & 0.010 (0.011) & 0.635 (0.045) & 0.610 & 0.043\\
+\hspace{1em}aorsf-fast & 0.010 (0.010) & 0.635 (0.048) & 0.211 & 0.042\\
+\hspace{1em}obliqueRSF-net & 0.010 (0.008) & 0.629 (0.041) & 45.749 & 17.208\\
+\hspace{1em}aorsf-net & 0.008 (0.010) & 0.642 (0.048) & 23.207 & 0.044\\
+\hspace{1em}aorsf-random & 0.008 (0.011) & 0.627 (0.039) & 0.944 & 0.042\\
+\hspace{1em}cif-standard & 0.007 (0.007) & 0.625 (0.044) & 1.989 & 6.200\\
+\hspace{1em}ranger-extratrees & 0.007 (0.009) & 0.646 (0.049) & 0.073 & 0.617\\
+\hspace{1em}rsf-standard & -0.002 (0.009) & 0.621 (0.045) & 0.632 & 0.066\\
+\hspace{1em}nn-cox & -0.005 (0.009) & 0.506 (0.025) & 10.675 & 1.079\\
+\hspace{1em}cif-rotate & -0.024 (0.011) & 0.548 (0.035) & 13.366 & 4.579\\
+\hspace{1em}xgboost-aft & -5.68 (1.27) & 0.622 (0.043) & 11.083 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.645 (0.026) & 0.945 (0.008) & 20.183 & 3.526\\
-\hspace{1em}glmnet-cox & 0.629 (0.037) & 0.940 (0.011) & 0.198 & 0.003\\
-\hspace{1em}aorsf-net & 0.535 (0.033) & 0.929 (0.012) & 50.651 & 0.044\\
-\hspace{1em}aorsf-cph & 0.527 (0.024) & 0.926 (0.013) & 0.792 & 0.045\\
-\hspace{1em}rsf-standard & 0.525 (0.023) & 0.923 (0.013) & 0.746 & 0.105\\
-\hspace{1em}aorsf-fast & 0.521 (0.029) & 0.923 (0.015) & 0.218 & 0.044\\
-\hspace{1em}xgboost-cox & 0.515 (0.029) & 0.933 (0.011) & 14.297 & 0.005\\
-\hspace{1em}nn-cox & 0.497 (0.143) & 0.889 (0.056) & 16.418 & 0.705\\
-\hspace{1em}cif-standard & 0.472 (0.030) & 0.900 (0.021) & 0.379 & 1.292\\
-\hspace{1em}cif-extension & 0.449 (0.026) & 0.919 (0.015) & 8.850 & 3.931\\
-\hspace{1em}ranger-extratrees & 0.432 (0.019) & 0.896 (0.020) & 0.070 & 0.127\\
-\hspace{1em}obliqueRSF-net & 0.318 (0.025) & 0.908 (0.021) & 152.602 & 9.347\\
-\hspace{1em}aorsf-random & 0.293 (0.041) & 0.841 (0.034) & 0.999 & 0.041\\
-\hspace{1em}xgboost-aft & -0.435 (0.057) & 0.930 (0.011) & 28.847 & 0.007\\
+\hspace{1em}cif-rotate & 0.641 (0.024) & 0.944 (0.008) & 19.336 & 3.407\\
+\hspace{1em}glmnet-cox & 0.617 (0.022) & 0.941 (0.009) & 0.199 & 0.004\\
+\hspace{1em}aorsf-net & 0.541 (0.033) & 0.930 (0.010) & 51.438 & 0.044\\
+\hspace{1em}aorsf-cph & 0.531 (0.024) & 0.928 (0.010) & 0.773 & 0.044\\
+\hspace{1em}xgboost-cox & 0.529 (0.023) & 0.932 (0.011) & 12.809 & 0.004\\
+\hspace{1em}rsf-standard & 0.529 (0.027) & 0.926 (0.010) & 1.049 & 0.102\\
+\hspace{1em}aorsf-fast & 0.522 (0.028) & 0.924 (0.012) & 0.215 & 0.042\\
+\hspace{1em}cif-standard & 0.478 (0.029) & 0.904 (0.016) & 0.717 & 1.313\\
+\hspace{1em}cif-extension & 0.451 (0.035) & 0.920 (0.013) & 8.990 & 4.395\\
+\hspace{1em}nn-cox & 0.450 (0.057) & 0.877 (0.031) & 16.406 & 1.226\\
+\hspace{1em}ranger-extratrees & 0.433 (0.025) & 0.900 (0.021) & 0.053 & 0.530\\
+\hspace{1em}obliqueRSF-net & 0.327 (0.024) & 0.911 (0.014) & 152.746 & 8.671\\
+\hspace{1em}aorsf-random & 0.304 (0.030) & 0.849 (0.019) & 1.260 & 0.040\\
+\hspace{1em}xgboost-aft & -0.418 (0.036) & 0.930 (0.008) & 28.162 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.214 (0.009) & 0.871 (0.005) & 20.799 & 1.406\\
-\hspace{1em}aorsf-fast & 0.214 (0.010) & 0.871 (0.006) & 4.828 & 1.422\\
-\hspace{1em}aorsf-net & 0.212 (0.009) & 0.867 (0.006) & 446.975 & 1.285\\
-\hspace{1em}obliqueRSF-net & 0.210 (0.008) & 0.870 (0.006) & 1520.102 & 1097.379\\
-\hspace{1em}glmnet-cox & 0.209 (0.010) & 0.861 (0.005) & 2.153 & 0.014\\
-\hspace{1em}rsf-standard & 0.207 (0.009) & 0.860 (0.006) & 11.043 & 1.209\\
-\hspace{1em}cif-standard & 0.206 (0.007) & 0.864 (0.007) & 65.607 & 616.634\\
-\hspace{1em}cif-rotate & 0.191 (0.006) & 0.866 (0.005) & 256.009 & 62.262\\
-\hspace{1em}ranger-extratrees & 0.182 (0.007) & 0.862 (0.005) & 40.654 & 303.362\\
-\hspace{1em}cif-extension & 0.167 (0.003) & 0.868 (0.006) & 122.213 & 55.889\\
-\hspace{1em}aorsf-random & 0.142 (0.007) & 0.843 (0.006) & 11.433 & 1.500\\
-\hspace{1em}xgboost-cox & 0.020 (0.015) & 0.876 (0.005) & 11.932 & 0.021\\
-\hspace{1em}nn-cox & -0.001 (0.003) & 0.580 (0.090) & 21.950 & 95.510\\
-\hspace{1em}xgboost-aft & -7.74 (0.684) & 0.875 (0.006) & 33.565 & 0.015\\
+\hspace{1em}aorsf-cph & 0.213 (0.008) & 0.870 (0.007) & 18.523 & 1.243\\
+\hspace{1em}aorsf-fast & 0.212 (0.009) & 0.870 (0.007) & 4.598 & 1.256\\
+\hspace{1em}aorsf-net & 0.210 (0.008) & 0.866 (0.007) & 455.013 & 1.352\\
+\hspace{1em}obliqueRSF-net & 0.206 (0.007) & 0.867 (0.006) & 1494.475 & 1092.517\\
+\hspace{1em}glmnet-cox & 0.205 (0.008) & 0.860 (0.006) & 1.744 & 0.020\\
+\hspace{1em}rsf-standard & 0.204 (0.007) & 0.859 (0.006) & 8.631 & 1.192\\
+\hspace{1em}cif-standard & 0.204 (0.005) & 0.861 (0.008) & 68.539 & 692.347\\
+\hspace{1em}cif-rotate & 0.189 (0.005) & 0.865 (0.004) & 259.835 & 60.332\\
+\hspace{1em}ranger-extratrees & 0.180 (0.004) & 0.861 (0.007) & 34.871 & 53.895\\
+\hspace{1em}cif-extension & 0.166 (0.002) & 0.866 (0.007) & 123.805 & 52.483\\
+\hspace{1em}aorsf-random & 0.142 (0.006) & 0.844 (0.007) & 10.215 & 1.365\\
+\hspace{1em}xgboost-cox & 0.018 (0.014) & 0.875 (0.006) & 9.416 & 0.018\\
+\hspace{1em}nn-cox & 0.000 (0.000) & 0.534 (0.076) & 17.526 & 110.282\\
+\hspace{1em}xgboost-aft & -7.57 (0.911) & 0.874 (0.006) & 26.533 & 0.014\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.436 (0.026) & 0.909 (0.020) & 0.071 & 0.021\\
-\hspace{1em}aorsf-cph & 0.423 (0.027) & 0.908 (0.019) & 0.152 & 0.020\\
-\hspace{1em}aorsf-net & 0.415 (0.031) & 0.907 (0.020) & 13.638 & 0.018\\
-\hspace{1em}cif-rotate & 0.404 (0.043) & 0.901 (0.022) & 9.187 & 2.214\\
-\hspace{1em}rsf-standard & 0.397 (0.023) & 0.895 (0.020) & 0.087 & 0.036\\
-\hspace{1em}obliqueRSF-net & 0.366 (0.034) & 0.908 (0.020) & 106.606 & 1.721\\
-\hspace{1em}aorsf-random & 0.353 (0.028) & 0.895 (0.020) & 0.288 & 0.019\\
-\hspace{1em}cif-standard & 0.344 (0.034) & 0.904 (0.023) & 0.185 & 0.362\\
-\hspace{1em}glmnet-cox & 0.343 (0.059) & 0.894 (0.024) & 0.120 & 0.003\\
-\hspace{1em}cif-extension & 0.341 (0.032) & 0.904 (0.019) & 5.195 & 2.236\\
-\hspace{1em}ranger-extratrees & 0.267 (0.029) & 0.897 (0.023) & 0.027 & 0.037\\
-\hspace{1em}xgboost-cox & 0.250 (0.108) & 0.881 (0.027) & 6.107 & 0.003\\
-\hspace{1em}nn-cox & -0.028 (0.019) & 0.652 (0.123) & 9.552 & 0.240\\
-\hspace{1em}xgboost-aft & -0.905 (0.366) & 0.885 (0.021) & 8.233 & 0.005\\
+\hspace{1em}aorsf-fast & 0.429 (0.021) & 0.907 (0.026) & 0.084 & 0.019\\
+\hspace{1em}aorsf-cph & 0.419 (0.022) & 0.905 (0.025) & 0.179 & 0.019\\
+\hspace{1em}aorsf-net & 0.412 (0.026) & 0.903 (0.027) & 14.909 & 0.020\\
+\hspace{1em}cif-rotate & 0.403 (0.047) & 0.896 (0.028) & 10.236 & 2.197\\
+\hspace{1em}rsf-standard & 0.388 (0.017) & 0.889 (0.025) & 0.166 & 0.054\\
+\hspace{1em}obliqueRSF-net & 0.372 (0.033) & 0.905 (0.027) & 108.343 & 1.921\\
+\hspace{1em}aorsf-random & 0.357 (0.022) & 0.895 (0.026) & 0.293 & 0.019\\
+\hspace{1em}glmnet-cox & 0.350 (0.066) & 0.893 (0.030) & 0.119 & 0.002\\
+\hspace{1em}cif-standard & 0.350 (0.034) & 0.901 (0.031) & 0.203 & 0.723\\
+\hspace{1em}cif-extension & 0.348 (0.033) & 0.901 (0.026) & 6.420 & 2.375\\
+\hspace{1em}ranger-extratrees & 0.280 (0.019) & 0.898 (0.028) & 0.040 & 0.040\\
+\hspace{1em}xgboost-cox & 0.263 (0.154) & 0.881 (0.040) & 4.705 & 0.003\\
+\hspace{1em}nn-cox & -0.016 (0.010) & 0.618 (0.167) & 11.658 & 0.213\\
+\hspace{1em}xgboost-aft & -0.926 (0.298) & 0.886 (0.030) & 9.824 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.165 (0.010) & 0.760 (0.008) & 148.475 & 0.186\\
-\hspace{1em}obliqueRSF-net & 0.162 (0.009) & 0.760 (0.009) & 439.574 & 36.953\\
-\hspace{1em}aorsf-cph & 0.161 (0.010) & 0.758 (0.009) & 2.601 & 0.205\\
-\hspace{1em}aorsf-fast & 0.159 (0.011) & 0.756 (0.009) & 0.809 & 0.206\\
-\hspace{1em}cif-standard & 0.159 (0.008) & 0.759 (0.008) & 4.308 & 23.147\\
-\hspace{1em}rsf-standard & 0.157 (0.011) & 0.755 (0.008) & 2.754 & 0.522\\
-\hspace{1em}aorsf-random & 0.153 (0.007) & 0.752 (0.009) & 2.869 & 0.184\\
-\hspace{1em}cif-rotate & 0.151 (0.012) & 0.754 (0.013) & 33.457 & 8.469\\
-\hspace{1em}ranger-extratrees & 0.139 (0.005) & 0.749 (0.009) & 2.721 & 3.105\\
-\hspace{1em}xgboost-cox & 0.134 (0.011) & 0.754 (0.010) & 4.785 & 0.005\\
-\hspace{1em}cif-extension & 0.130 (0.005) & 0.751 (0.009) & 24.345 & 9.889\\
-\hspace{1em}glmnet-cox & 0.120 (0.007) & 0.733 (0.010) & 0.499 & 0.004\\
-\hspace{1em}nn-cox & -0.028 (0.087) & 0.535 (0.057) & 16.443 & 7.747\\
-\hspace{1em}xgboost-aft & -1.37 (0.126) & 0.759 (0.008) & 14.195 & 0.007\\
+\hspace{1em}aorsf-net & 0.162 (0.008) & 0.758 (0.006) & 156.804 & 0.188\\
+\hspace{1em}obliqueRSF-net & 0.159 (0.008) & 0.757 (0.007) & 456.884 & 39.371\\
+\hspace{1em}aorsf-cph & 0.158 (0.008) & 0.755 (0.006) & 2.566 & 0.204\\
+\hspace{1em}aorsf-fast & 0.157 (0.009) & 0.755 (0.007) & 0.833 & 0.209\\
+\hspace{1em}cif-standard & 0.156 (0.008) & 0.755 (0.008) & 5.193 & 22.555\\
+\hspace{1em}rsf-standard & 0.154 (0.008) & 0.752 (0.005) & 2.888 & 0.287\\
+\hspace{1em}aorsf-random & 0.150 (0.006) & 0.750 (0.009) & 3.355 & 0.184\\
+\hspace{1em}cif-rotate & 0.149 (0.012) & 0.752 (0.012) & 34.118 & 8.552\\
+\hspace{1em}ranger-extratrees & 0.137 (0.002) & 0.745 (0.007) & 2.515 & 2.445\\
+\hspace{1em}xgboost-cox & 0.130 (0.003) & 0.749 (0.007) & 3.697 & 0.005\\
+\hspace{1em}cif-extension & 0.129 (0.005) & 0.748 (0.009) & 21.984 & 8.630\\
+\hspace{1em}glmnet-cox & 0.118 (0.009) & 0.731 (0.010) & 0.579 & 0.004\\
+\hspace{1em}nn-cox & -0.055 (0.122) & 0.478 (0.047) & 15.711 & 7.097\\
+\hspace{1em}xgboost-aft & -1.32 (0.146) & 0.756 (0.007) & 13.994 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.148 (0.011) & 0.738 (0.011) & 513.045 & 37.957\\
-\hspace{1em}aorsf-net & 0.147 (0.012) & 0.736 (0.011) & 169.714 & 0.197\\
-\hspace{1em}aorsf-cph & 0.145 (0.012) & 0.735 (0.010) & 2.867 & 0.216\\
-\hspace{1em}cif-standard & 0.144 (0.012) & 0.735 (0.011) & 4.369 & 23.006\\
-\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.734 (0.010) & 0.896 & 0.218\\
-\hspace{1em}aorsf-random & 0.140 (0.010) & 0.731 (0.010) & 3.326 & 0.191\\
-\hspace{1em}rsf-standard & 0.138 (0.011) & 0.732 (0.009) & 2.809 & 0.281\\
-\hspace{1em}ranger-extratrees & 0.135 (0.008) & 0.735 (0.011) & 2.807 & 2.778\\
-\hspace{1em}cif-rotate & 0.133 (0.009) & 0.728 (0.010) & 35.059 & 8.648\\
-\hspace{1em}cif-extension & 0.119 (0.007) & 0.733 (0.010) & 22.197 & 8.887\\
-\hspace{1em}glmnet-cox & 0.118 (0.007) & 0.728 (0.011) & 0.498 & 0.004\\
-\hspace{1em}xgboost-cox & 0.114 (0.007) & 0.730 (0.012) & 4.233 & 0.005\\
-\hspace{1em}nn-cox & -0.002 (0.002) & 0.491 (0.028) & 24.631 & 11.769\\
-\hspace{1em}xgboost-aft & -1.06 (0.147) & 0.735 (0.011) & 13.403 & 0.007\\
+\hspace{1em}obliqueRSF-net & 0.145 (0.012) & 0.734 (0.013) & 533.837 & 36.957\\
+\hspace{1em}aorsf-net & 0.142 (0.011) & 0.733 (0.012) & 177.250 & 0.198\\
+\hspace{1em}aorsf-cph & 0.140 (0.010) & 0.731 (0.011) & 2.818 & 0.217\\
+\hspace{1em}aorsf-fast & 0.139 (0.007) & 0.730 (0.010) & 0.860 & 0.212\\
+\hspace{1em}cif-standard & 0.139 (0.012) & 0.731 (0.012) & 4.713 & 22.975\\
+\hspace{1em}aorsf-random & 0.136 (0.010) & 0.728 (0.010) & 3.723 & 0.193\\
+\hspace{1em}rsf-standard & 0.134 (0.007) & 0.729 (0.009) & 4.065 & 0.284\\
+\hspace{1em}ranger-extratrees & 0.132 (0.009) & 0.731 (0.013) & 2.354 & 3.657\\
+\hspace{1em}cif-rotate & 0.131 (0.010) & 0.724 (0.011) & 38.071 & 9.418\\
+\hspace{1em}cif-extension & 0.117 (0.008) & 0.729 (0.012) & 22.799 & 8.526\\
+\hspace{1em}glmnet-cox & 0.117 (0.006) & 0.724 (0.013) & 0.622 & 0.004\\
+\hspace{1em}xgboost-cox & 0.111 (0.005) & 0.726 (0.014) & 4.572 & 0.005\\
+\hspace{1em}nn-cox & -0.001 (0.001) & 0.500 (0.000) & 20.913 & 11.146\\
+\hspace{1em}xgboost-aft & -1.00 (0.143) & 0.729 (0.012) & 14.752 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.256 (0.016) & 0.826 (0.010) & 2.468 & 0.600\\
-\hspace{1em}aorsf-cph & 0.255 (0.016) & 0.826 (0.011) & 7.124 & 0.601\\
-\hspace{1em}aorsf-net & 0.254 (0.014) & 0.824 (0.011) & 274.793 & 0.556\\
-\hspace{1em}obliqueRSF-net & 0.251 (0.014) & 0.822 (0.011) & 1071.189 & 145.107\\
-\hspace{1em}glmnet-cox & 0.251 (0.015) & 0.821 (0.010) & 0.546 & 0.011\\
-\hspace{1em}rsf-standard & 0.247 (0.016) & 0.817 (0.011) & 5.052 & 0.549\\
-\hspace{1em}cif-standard & 0.247 (0.014) & 0.819 (0.011) & 18.346 & 116.811\\
-\hspace{1em}ranger-extratrees & 0.247 (0.012) & 0.822 (0.010) & 7.234 & 16.737\\
-\hspace{1em}aorsf-random & 0.236 (0.014) & 0.819 (0.011) & 6.056 & 0.566\\
-\hspace{1em}cif-rotate & 0.228 (0.010) & 0.819 (0.009) & 62.380 & 20.093\\
-\hspace{1em}cif-extension & 0.202 (0.005) & 0.821 (0.010) & 43.862 & 21.183\\
-\hspace{1em}xgboost-cox & 0.104 (0.034) & 0.824 (0.011) & 6.743 & 0.009\\
-\hspace{1em}nn-cox & 0.001 (0.003) & 0.610 (0.135) & 23.112 & 21.723\\
-\hspace{1em}xgboost-aft & -2.75 (0.305) & 0.824 (0.011) & 30.052 & 0.009\\
+\hspace{1em}aorsf-fast & 0.255 (0.013) & 0.825 (0.010) & 2.479 & 0.599\\
+\hspace{1em}aorsf-cph & 0.254 (0.013) & 0.824 (0.010) & 7.005 & 0.584\\
+\hspace{1em}aorsf-net & 0.253 (0.012) & 0.822 (0.010) & 292.897 & 0.577\\
+\hspace{1em}obliqueRSF-net & 0.251 (0.011) & 0.821 (0.010) & 1112.649 & 148.434\\
+\hspace{1em}glmnet-cox & 0.250 (0.010) & 0.819 (0.009) & 0.916 & 0.006\\
+\hspace{1em}rsf-standard & 0.247 (0.014) & 0.814 (0.010) & 4.148 & 0.538\\
+\hspace{1em}ranger-extratrees & 0.247 (0.011) & 0.821 (0.009) & 7.297 & 10.711\\
+\hspace{1em}cif-standard & 0.247 (0.012) & 0.818 (0.011) & 19.302 & 120.749\\
+\hspace{1em}aorsf-random & 0.235 (0.014) & 0.817 (0.011) & 7.467 & 0.575\\
+\hspace{1em}cif-rotate & 0.229 (0.006) & 0.818 (0.008) & 63.034 & 21.236\\
+\hspace{1em}cif-extension & 0.201 (0.005) & 0.821 (0.009) & 38.570 & 21.016\\
+\hspace{1em}xgboost-cox & 0.085 (0.033) & 0.823 (0.010) & 6.025 & 0.008\\
+\hspace{1em}nn-cox & -0.002 (0.008) & 0.606 (0.114) & 21.104 & 23.211\\
+\hspace{1em}xgboost-aft & -2.84 (0.305) & 0.823 (0.010) & 17.680 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.070 (0.007) & 0.792 (0.008) & 12.779 & 0.016\\
-\hspace{1em}aorsf-cph & 0.067 (0.005) & 0.791 (0.010) & 10.753 & 0.649\\
-\hspace{1em}aorsf-net & 0.067 (0.005) & 0.788 (0.010) & 339.857 & 0.652\\
-\hspace{1em}aorsf-fast & 0.067 (0.004) & 0.791 (0.010) & 2.950 & 0.653\\
-\hspace{1em}obliqueRSF-net & 0.066 (0.004) & 0.790 (0.011) & 1071.167 & 425.299\\
-\hspace{1em}rsf-standard & 0.062 (0.006) & 0.780 (0.015) & 4.271 & 0.599\\
-\hspace{1em}cif-standard & 0.060 (0.003) & 0.791 (0.010) & 47.426 & 180.930\\
-\hspace{1em}cif-rotate & 0.059 (0.005) & 0.783 (0.008) & 941.817 & 112.906\\
-\hspace{1em}ranger-extratrees & 0.053 (0.003) & 0.786 (0.013) & 5.733 & 9.972\\
-\hspace{1em}nn-cox & 0.042 (0.013) & 0.765 (0.016) & 22.162 & 29.154\\
-\hspace{1em}cif-extension & 0.033 (0.002) & 0.782 (0.008) & 121.313 & 32.071\\
-\hspace{1em}aorsf-random & 0.025 (0.002) & 0.736 (0.013) & 5.621 & 0.772\\
-\hspace{1em}xgboost-cox & 0.011 (0.017) & 0.793 (0.009) & 8.908 & 0.014\\
-\hspace{1em}xgboost-aft & -10.7 (0.681) & 0.789 (0.011) & 24.248 & 0.015\\
+\hspace{1em}glmnet-cox & 0.071 (0.009) & 0.792 (0.008) & 14.747 & 0.014\\
+\hspace{1em}aorsf-cph & 0.067 (0.006) & 0.787 (0.009) & 9.115 & 0.938\\
+\hspace{1em}aorsf-net & 0.066 (0.006) & 0.785 (0.008) & 346.912 & 0.675\\
+\hspace{1em}aorsf-fast & 0.066 (0.005) & 0.787 (0.008) & 2.389 & 0.955\\
+\hspace{1em}obliqueRSF-net & 0.066 (0.005) & 0.786 (0.011) & 950.174 & 438.781\\
+\hspace{1em}rsf-standard & 0.061 (0.008) & 0.778 (0.015) & 3.731 & 0.592\\
+\hspace{1em}cif-standard & 0.060 (0.004) & 0.788 (0.008) & 48.930 & 187.855\\
+\hspace{1em}cif-rotate & 0.060 (0.005) & 0.783 (0.010) & 908.658 & 111.648\\
+\hspace{1em}ranger-extratrees & 0.052 (0.003) & 0.779 (0.011) & 6.309 & 18.320\\
+\hspace{1em}nn-cox & 0.039 (0.006) & 0.772 (0.015) & 18.124 & 25.781\\
+\hspace{1em}cif-extension & 0.034 (0.002) & 0.781 (0.010) & 134.710 & 41.048\\
+\hspace{1em}aorsf-random & 0.025 (0.002) & 0.731 (0.007) & 5.496 & 0.725\\
+\hspace{1em}xgboost-cox & 0.016 (0.023) & 0.792 (0.008) & 6.202 & 0.013\\
+\hspace{1em}xgboost-aft & -10.9 (0.496) & 0.787 (0.010) & 20.409 & 0.013\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.123 (0.008) & 0.770 (0.010) & 4.957 & 0.011\\
-\hspace{1em}aorsf-cph & 0.116 (0.006) & 0.769 (0.008) & 14.405 & 1.433\\
-\hspace{1em}aorsf-fast & 0.115 (0.007) & 0.768 (0.007) & 4.124 & 1.494\\
-\hspace{1em}aorsf-net & 0.112 (0.007) & 0.766 (0.008) & 591.726 & 0.942\\
-\hspace{1em}obliqueRSF-net & 0.111 (0.006) & 0.766 (0.008) & 2920.730 & 233.477\\
-\hspace{1em}rsf-standard & 0.109 (0.006) & 0.760 (0.007) & 6.036 & 0.711\\
-\hspace{1em}cif-standard & 0.105 (0.006) & 0.763 (0.009) & 48.060 & 191.307\\
-\hspace{1em}nn-cox & 0.098 (0.010) & 0.752 (0.013) & 29.086 & 28.125\\
-\hspace{1em}ranger-extratrees & 0.096 (0.005) & 0.755 (0.008) & 10.665 & 22.541\\
-\hspace{1em}cif-rotate & 0.091 (0.005) & 0.744 (0.008) & 1083.768 & 118.583\\
-\hspace{1em}cif-extension & 0.055 (0.002) & 0.745 (0.008) & 135.963 & 32.414\\
-\hspace{1em}aorsf-random & 0.051 (0.004) & 0.717 (0.010) & 9.053 & 1.029\\
-\hspace{1em}xgboost-cox & 0.034 (0.025) & 0.771 (0.008) & 12.900 & 0.015\\
-\hspace{1em}xgboost-aft & -4.49 (0.313) & 0.771 (0.007) & 23.081 & 0.013\\
+\hspace{1em}glmnet-cox & 0.124 (0.009) & 0.772 (0.009) & 4.881 & 0.011\\
+\hspace{1em}aorsf-cph & 0.117 (0.007) & 0.770 (0.008) & 13.552 & 0.894\\
+\hspace{1em}aorsf-fast & 0.116 (0.007) & 0.770 (0.006) & 3.848 & 0.893\\
+\hspace{1em}obliqueRSF-net & 0.113 (0.007) & 0.768 (0.008) & 3079.665 & 272.453\\
+\hspace{1em}aorsf-net & 0.112 (0.008) & 0.768 (0.009) & 609.650 & 0.962\\
+\hspace{1em}rsf-standard & 0.109 (0.007) & 0.761 (0.007) & 5.748 & 0.707\\
+\hspace{1em}cif-standard & 0.107 (0.007) & 0.764 (0.010) & 47.859 & 194.271\\
+\hspace{1em}nn-cox & 0.100 (0.011) & 0.760 (0.012) & 32.476 & 36.267\\
+\hspace{1em}ranger-extratrees & 0.098 (0.005) & 0.757 (0.008) & 8.455 & 9.183\\
+\hspace{1em}cif-rotate & 0.092 (0.005) & 0.746 (0.007) & 1042.564 & 114.108\\
+\hspace{1em}cif-extension & 0.056 (0.002) & 0.745 (0.009) & 134.731 & 32.668\\
+\hspace{1em}aorsf-random & 0.053 (0.004) & 0.722 (0.010) & 9.084 & 0.982\\
+\hspace{1em}xgboost-cox & 0.043 (0.032) & 0.771 (0.008) & 9.075 & 0.013\\
+\hspace{1em}xgboost-aft & -4.74 (0.262) & 0.771 (0.007) & 27.585 & 0.013\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.117 (0.011) & 0.747 (0.013) & 0.304 & 0.004\\
-\hspace{1em}obliqueRSF-net & 0.115 (0.010) & 0.747 (0.010) & 376.210 & 26.092\\
-\hspace{1em}cif-rotate & 0.114 (0.011) & 0.741 (0.011) & 70.159 & 10.535\\
-\hspace{1em}aorsf-net & 0.113 (0.012) & 0.744 (0.012) & 121.294 & 0.159\\
-\hspace{1em}aorsf-cph & 0.113 (0.012) & 0.745 (0.011) & 1.987 & 0.150\\
-\hspace{1em}aorsf-fast & 0.111 (0.015) & 0.744 (0.011) & 0.616 & 0.151\\
-\hspace{1em}cif-standard & 0.110 (0.009) & 0.744 (0.010) & 3.623 & 15.504\\
-\hspace{1em}rsf-standard & 0.107 (0.011) & 0.737 (0.010) & 2.132 & 0.244\\
-\hspace{1em}cif-extension & 0.095 (0.004) & 0.744 (0.011) & 28.859 & 9.866\\
-\hspace{1em}xgboost-cox & 0.092 (0.007) & 0.746 (0.010) & 5.858 & 0.006\\
-\hspace{1em}ranger-extratrees & 0.090 (0.008) & 0.734 (0.012) & 2.841 & 1.923\\
-\hspace{1em}aorsf-random & 0.080 (0.004) & 0.727 (0.009) & 2.143 & 0.147\\
-\hspace{1em}nn-cox & 0.072 (0.029) & 0.705 (0.034) & 33.965 & 7.798\\
-\hspace{1em}xgboost-aft & -2.02 (0.169) & 0.741 (0.010) & 15.753 & 0.007\\
+\hspace{1em}cif-rotate & 0.111 (0.014) & 0.737 (0.012) & 70.041 & 9.795\\
+\hspace{1em}obliqueRSF-net & 0.110 (0.012) & 0.742 (0.009) & 380.199 & 24.864\\
+\hspace{1em}glmnet-cox & 0.109 (0.009) & 0.740 (0.012) & 0.781 & 0.003\\
+\hspace{1em}aorsf-net & 0.107 (0.012) & 0.738 (0.009) & 119.093 & 0.160\\
+\hspace{1em}aorsf-cph & 0.107 (0.012) & 0.740 (0.009) & 2.608 & 0.154\\
+\hspace{1em}cif-standard & 0.107 (0.010) & 0.739 (0.009) & 4.088 & 15.774\\
+\hspace{1em}aorsf-fast & 0.104 (0.015) & 0.739 (0.009) & 1.078 & 0.152\\
+\hspace{1em}rsf-standard & 0.104 (0.012) & 0.734 (0.010) & 1.876 & 0.607\\
+\hspace{1em}xgboost-cox & 0.094 (0.006) & 0.741 (0.008) & 4.207 & 0.005\\
+\hspace{1em}cif-extension & 0.093 (0.005) & 0.741 (0.012) & 28.632 & 9.275\\
+\hspace{1em}ranger-extratrees & 0.085 (0.007) & 0.727 (0.008) & 3.426 & 1.592\\
+\hspace{1em}aorsf-random & 0.080 (0.004) & 0.724 (0.010) & 3.144 & 0.150\\
+\hspace{1em}nn-cox & 0.067 (0.018) & 0.694 (0.024) & 22.516 & 5.931\\
+\hspace{1em}xgboost-aft & -2.03 (0.087) & 0.739 (0.011) & 13.566 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.197 (0.066) & 0.791 (0.036) & 5.405 & 1.442\\
-\hspace{1em}aorsf-fast & 0.191 (0.049) & 0.792 (0.039) & 0.052 & 0.013\\
-\hspace{1em}aorsf-cph & 0.190 (0.055) & 0.793 (0.043) & 0.100 & 0.014\\
-\hspace{1em}aorsf-net & 0.189 (0.050) & 0.793 (0.041) & 9.623 & 0.012\\
-\hspace{1em}rsf-standard & 0.162 (0.048) & 0.777 (0.046) & 0.069 & 0.026\\
-\hspace{1em}cif-extension & 0.160 (0.052) & 0.787 (0.039) & 3.746 & 1.229\\
-\hspace{1em}glmnet-cox & 0.145 (0.031) & 0.790 (0.033) & 0.286 & 0.002\\
-\hspace{1em}aorsf-random & 0.143 (0.052) & 0.774 (0.046) & 0.244 & 0.012\\
-\hspace{1em}cif-standard & 0.121 (0.041) & 0.769 (0.039) & 0.096 & 0.122\\
-\hspace{1em}obliqueRSF-net & 0.117 (0.038) & 0.796 (0.028) & 60.816 & 0.674\\
-\hspace{1em}ranger-extratrees & 0.079 (0.039) & 0.775 (0.044) & 0.022 & 0.028\\
-\hspace{1em}xgboost-cox & 0.027 (0.068) & 0.725 (0.046) & 1.223 & 0.003\\
-\hspace{1em}xgboost-aft & -0.011 (0.112) & 0.757 (0.053) & 5.323 & 0.006\\
-\hspace{1em}nn-cox & -0.037 (0.043) & 0.555 (0.067) & 10.089 & 0.118\\*
+\hspace{1em}cif-rotate & 0.186 (0.086) & 0.789 (0.047) & 4.626 & 1.031\\
+\hspace{1em}aorsf-net & 0.180 (0.064) & 0.792 (0.036) & 10.271 & 0.012\\
+\hspace{1em}aorsf-fast & 0.177 (0.064) & 0.788 (0.042) & 0.058 & 0.011\\
+\hspace{1em}aorsf-cph & 0.175 (0.071) & 0.789 (0.044) & 0.107 & 0.013\\
+\hspace{1em}rsf-standard & 0.159 (0.068) & 0.785 (0.047) & 0.077 & 0.025\\
+\hspace{1em}cif-extension & 0.141 (0.071) & 0.777 (0.047) & 3.936 & 1.193\\
+\hspace{1em}aorsf-random & 0.134 (0.068) & 0.773 (0.042) & 0.214 & 0.012\\
+\hspace{1em}glmnet-cox & 0.133 (0.038) & 0.793 (0.022) & 0.115 & 0.002\\
+\hspace{1em}cif-standard & 0.115 (0.056) & 0.770 (0.041) & 0.117 & 0.117\\
+\hspace{1em}obliqueRSF-net & 0.110 (0.050) & 0.794 (0.025) & 59.844 & 0.634\\
+\hspace{1em}ranger-extratrees & 0.071 (0.049) & 0.762 (0.050) & 0.023 & 0.047\\
+\hspace{1em}xgboost-cox & 0.053 (0.078) & 0.728 (0.055) & 2.310 & 0.002\\
+\hspace{1em}xgboost-aft & -0.007 (0.079) & 0.759 (0.057) & 5.251 & 0.005\\
+\hspace{1em}nn-cox & -0.048 (0.046) & 0.522 (0.084) & 12.037 & 0.142\\*
 \end{longtable}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\begin{landscape}
+\begin{longtable}[t]{llcccccc}
+\caption{\label{tab:unnamed-chunk-7}Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance}\\
+\toprule
+\multicolumn{2}{c}{ } & \multicolumn{3}{c}{accelerated oblique RSF} & \multicolumn{2}{c}{xgboost} & \multicolumn{1}{c}{RSF} \\
+\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-8}
+Max correlation & No. observations & Negation & ANOVA & Permutation & SHAP & Gain & Permutation\\
+\midrule
+\endfirsthead
+\caption[]{Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance \textit{(continued)}}\\
+\toprule
+Max correlation & No. observations & Negation & ANOVA & Permutation & SHAP & Gain & Permutation\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\endlastfoot
+Overall & Overall & 75.3 & 73.0 & 72.9 & 69.0 & 64.4 & 67.1\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textit{\textbf{Interactions}}}\\
+\hline
+\hspace{1em}Overall & Overall & 58.4 & 56.6 & 59.8 & 53.1 & 48.6 & 57.9\\
+\hspace{1em}45 & 500 & 64.3 & 66.4 & 53.6 & 59.6 & 53.5 & 59.4\\
+\hspace{1em}45 & 1,000 & 48.0 & 46.7 & 58.4 & 43.1 & 42.2 & 52.7\\
+\hspace{1em}45 & 2,500 & 67.3 & 54.0 & 67.3 & 59.1 & 57.2 & 59.0\\
+\hspace{1em}15 & 500 & 48.9 & 58.8 & 55.6 & 51.6 & 45.5 & 59.5\\
+\hspace{1em}15 & 1,000 & 54.9 & 49.1 & 56.4 & 45.7 & 39.9 & 53.0\\
+\hspace{1em}15 & 2,500 & 56.4 & 55.5 & 63.9 & 54.3 & 53.4 & 53.4\\
+\hspace{1em}0 & 500 & 61.1 & 53.8 & 65.6 & 44.2 & 42.6 & 56.4\\
+\hspace{1em}0 & 1,000 & 55.1 & 60.5 & 49.5 & 54.9 & 49.3 & 60.4\\
+\hspace{1em}0 & 2,500 & 69.2 & 64.4 & 67.8 & 65.0 & 53.5 & 67.5\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textit{\textbf{Non-linear effects}}}\\
+\hline
+\hspace{1em}Overall & Overall & 71.0 & 66.6 & 67.3 & 65.5 & 60.1 & 59.2\\
+\hspace{1em}45 & 500 & 64.9 & 61.7 & 53.6 & 58.8 & 52.4 & 55.0\\
+\hspace{1em}45 & 1,000 & 59.2 & 54.0 & 60.3 & 57.7 & 53.0 & 53.5\\
+\hspace{1em}45 & 2,500 & 60.4 & 52.2 & 56.9 & 56.1 & 53.7 & 51.7\\
+\hspace{1em}15 & 500 & 60.6 & 64.5 & 62.4 & 60.3 & 56.7 & 60.1\\
+\hspace{1em}15 & 1,000 & 71.7 & 64.8 & 71.0 & 62.0 & 56.9 & 58.3\\
+\hspace{1em}15 & 2,500 & 65.0 & 61.1 & 63.1 & 57.9 & 54.1 & 55.0\\
+\hspace{1em}0 & 500 & 72.6 & 64.0 & 73.5 & 61.4 & 58.0 & 56.5\\
+\hspace{1em}0 & 1,000 & 86.8 & 85.4 & 76.5 & 80.8 & 70.2 & 67.9\\
+\hspace{1em}0 & 2,500 & 98.0 & 91.9 & 88.8 & 94.8 & 86.0 & 74.2\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textit{\textbf{Combination effects}}}\\
+\hline
+\hspace{1em}Overall & Overall & 77.9 & 76.0 & 74.5 & 70.7 & 65.7 & 68.7\\
+\hspace{1em}45 & 500 & 66.5 & 67.8 & 56.5 & 58.1 & 54.0 & 59.0\\
+\hspace{1em}45 & 1,000 & 66.1 & 62.7 & 63.5 & 58.3 & 55.2 & 64.1\\
+\hspace{1em}45 & 2,500 & 67.4 & 60.5 & 64.8 & 60.8 & 57.8 & 60.6\\
+\hspace{1em}15 & 500 & 68.9 & 73.7 & 68.6 & 65.9 & 57.7 & 65.5\\
+\hspace{1em}15 & 1,000 & 79.2 & 73.5 & 76.1 & 67.7 & 63.3 & 70.0\\
+\hspace{1em}15 & 2,500 & 73.9 & 71.7 & 73.9 & 69.2 & 64.6 & 66.0\\
+\hspace{1em}0 & 500 & 84.0 & 81.4 & 80.0 & 67.5 & 60.1 & 66.7\\
+\hspace{1em}0 & 1,000 & 95.1 & 92.8 & 89.2 & 89.1 & 80.4 & 77.5\\
+\hspace{1em}0 & 2,500 & 99.9 & 99.8 & 98.3 & 99.5 & 97.8 & 88.7\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textit{\textbf{Main effects}}}\\
+\hline
+\hspace{1em}Overall & Overall & 88.9 & 86.8 & 86.6 & 83.1 & 80.5 & 79.5\\
+\hspace{1em}45 & 500 & 77.1 & 75.6 & 71.6 & 76.4 & 73.0 & 67.3\\
+\hspace{1em}45 & 1,000 & 78.4 & 74.0 & 74.1 & 64.7 & 62.9 & 69.6\\
+\hspace{1em}45 & 2,500 & 82.0 & 73.7 & 77.1 & 74.4 & 71.0 & 69.1\\
+\hspace{1em}15 & 500 & 80.6 & 82.7 & 82.6 & 79.6 & 76.3 & 77.2\\
+\hspace{1em}15 & 1,000 & 93.3 & 90.0 & 89.0 & 83.7 & 78.8 & 77.3\\
+\hspace{1em}15 & 2,500 & 93.8 & 90.0 & 92.8 & 87.9 & 85.5 & 81.3\\
+\hspace{1em}0 & 500 & 95.3 & 96.2 & 93.5 & 82.5 & 80.6 & 81.1\\
+\hspace{1em}0 & 1,000 & 100.0 & 99.4 & 98.6 & 98.8 & 96.2 & 93.5\\
+\hspace{1em}0 & 2,500 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 99.5\\*
+\end{longtable}
+\end{landscape}
 

### 2022-07-09 R/bench_pred_real.R

@@ -1,0 +1,135 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param data_source
+#' @param run_seed
+bench_pred_real <- function(data_source,
+                            model_type,
+                            data_load_fun,
+                            model_fit_fun,
+                            model_pred_fun,
+                            run_seed,
+                            test_prop = 1/2) {
+
+  set.seed(run_seed)
+
+  data_all <- data_load_fun()
+
+  # Some R packages (not aorsf) have trouble
+  # with factors that have special characters
+  data_all <-  data_all |>
+    mutate(across(where(is.character), as.factor),
+           across(where(is.factor), simplify_levels))
+
+  test_index <- sample(x = seq(nrow(data_all)),
+                       size = round(nrow(data_all) * test_prop),
+                       replace = FALSE)
+
+  train <- data_all[-test_index, ]
+  test <- data_all[test_index, ]
+
+  imputer <- recipe(x = train, time + status ~ .) |>
+    step_impute_mean(all_numeric_predictors()) |>
+    step_impute_mode(all_nominal_predictors()) |>
+    step_nzv(all_predictors()) |>
+    step_range(all_numeric_predictors()) |>
+    prep()
+
+  .train <- as.data.frame(juice(imputer))
+  .test <- as.data.frame(bake(imputer, new_data = test))
+
+  event_time_bounds <- quantile(
+    x = data_all$time[data_all$status==1],
+    probs = c(.25, .75)
+  )
+
+  pred_horizon <- sort(unique(.test$time[.test$status == 1]))
+
+  pred_horizon <- pred_horizon[pred_horizon <= event_time_bounds['75%']]
+  pred_horizon <- pred_horizon[pred_horizon >= event_time_bounds['25%']]
+
+  if(is_empty(pred_horizon)) return(NULL)
+
+  if(length(pred_horizon) > 30){
+    pred_horizon <-
+      pred_horizon[floor(seq(1, length(pred_horizon), length.out=30))]
+  }
+
+  # Don't pipe here - it can mess up the measurement
+  # of time during model fitting and model predictions.
+
+  model <- try(
+    model_fit_fun(train = .train, pred_horizon = pred_horizon),
+    silent = TRUE
+  )
+
+  predictions <- try(
+    model_pred_fun(object = model,
[…]

### 2022-07-09 R/bench_pred_sim.R

@@ -1,53 +1,33 @@
-#' .. content for \description{} (no empty lines) ..
-#'
-#' .. content for \details{} ..
-#'
-#' @title
-#' @param data_source
-#' @param run_seed
-bench_pred <- function(data_source,
-                       model_type,
-                       data_load_fun,
-                       model_fit_fun,
-                       model_pred_fun,
-                       n_obs = NULL,
-                       pred_corr_max = NULL,
-                       run_seed,
-                       test_prop = 1/2) {
+
+
+bench_pred_sim <- function(data_source,
+                           model_type,
+                           data_load_fun,
+                           model_fit_fun,
+                           model_pred_fun,
+                           n_obs = NULL,
+                           pred_corr_max = NULL,
+                           run_seed) {
 
   set.seed(run_seed)
 
   data_all <- data_load_fun(n_obs = n_obs,
-                            pred_corr_max = pred_corr_max)
+                            pred_corr_max = pred_corr_max,
+                            n_pred_junk = 0,
+                            eff_size_pred_main = 1/3,
+                            eff_size_intr_main = 1/3,
+                            eff_size_pred_nlin = 1/3,
+                            eff_size_intr_nlin = 1/3,
+                            eff_size_pred_cmbn = 1/3,
+                            eff_size_intr_cmbn = 1/3)
 
+  data_all <- data_all$data
 
-  if(data_source == 'sim'){
+  train <- data_all
 
-    data_all <- data_all$data
-
-    train <- data_all
-
-    test <- sim_surv(n_obs = 5000,
-                     pred_corr_max = pred_corr_max) |>
-      getElement('data')
-
-  } else {
-
-    # Some R packages (not aorsf) have trouble
-    # with factors that have special characters
-    data_all <-  data_all |>
-      mutate(across(where(is.character), as.factor),
-             across(where(is.factor), simplify_levels))
-
-    test_index <- sample(x = seq(nrow(data_all)),
-                         size = round(nrow(data_all) * test_prop),
-                         replace = FALSE)
-
-    train <- data_all[-test_index, ]
-    test <- data_all[test_index, ]
-
-
-  }
+  test <- sim_surv(n_obs = 5000,
+                   pred_corr_max = pred_corr_max) |>
+    getElement('data')
 
   imputer <- recipe(x = train, time + status ~ .) |>
[…]

### 2022-07-09 R/bench_vi_visualize.R

@@ -4,11 +4,9 @@
 #'
 #' @title
 #' @param bm_vi_comb
-bm_vi_visualize <- function(bm_vi_comb) {
+bench_vi_visualize <- function(bm_vi_comb) {
 
   bm_vi_smry <- bm_vi_comb %>%
-    filter(pred_corr_max != .45) %>%
-    arrange(n_obs, pred_corr_max) %>%
     mutate(
       intr = (intr_main+intr_hidden_cmbn+intr_hidden_nlin)/3,
     ) %>%
@@ -25,19 +23,24 @@ bm_vi_visualize <- function(bm_vi_comb) {
     summarize(value = mean(overall)) %>%
     mutate(variable = 'Overall')
 
+  bm_vi_by_variable <- bm_vi_smry %>%
+    group_by(model, variable) %>%
+    summarize(value = mean(value)) %>%
+    mutate(n_obs = 0, pred_corr_max = 1)
+
   slide_in <- bm_vi_smry$variable %>%
     unique() %>%
     enframe(value = 'variable', name = NULL) %>%
     split(.$variable)
 
   data_smry_split <-
-    bind_rows(bm_vi_overall, bm_vi_smry) %>%
+    bind_rows(bm_vi_overall, bm_vi_smry, bm_vi_by_variable) %>%
     mutate(variable = factor(variable, levels = c('Overall',
                                                   'main',
                                                   'cmbn',
                                                   'nlin',
                                                   'intr'))) %>%
-    arrange(variable, n_obs, pred_corr_max, desc(value)) %>%
+    arrange(variable, desc(pred_corr_max), n_obs, desc(value)) %>%
     split(.$variable)
 
   slide_in
@@ -81,8 +84,9 @@ bm_vi_visualize <- function(bm_vi_comb) {
 
   y_col_1 = 0.15
   y_col_2 = 0.30
+  y_col_3 = 0.75
 
-  xmax <- max(ceiling(data_smry$x))
+  xmax <- max(ceiling(data_smry_pre$x))
 
   # gg_text_header <- tibble(
   #   x = c(xmax + 3/4, xmax + 3/4),
@@ -93,7 +97,7 @@ bm_vi_visualize <- function(bm_vi_comb) {
 
   gg_text_data <- data_smry_pre %>%
     mutate(x = round(x)) %>%
-    group_by(variable, n_obs, pred_corr_max, data, x) %>%
[…]

### 2022-07-09 R/clean_bm_pred.R

@@ -4,7 +4,19 @@
 #'
 #' @title
 #' @param bm_pred_comb
-clean_bm_pred <- function(bm_pred_comb) {
+clean_bm_pred <- function(bm_pred_real_comb,
+                          bm_pred_sim_comb = NULL) {
+
+  bm_pred_comb <- bm_pred_real_comb
+
+  if(!is.null(bm_pred_sim_comb)){
+
+    bm_pred_sim_comb <- bm_pred_sim_comb %>%
+      mutate(data = paste(data, n_obs, pred_corr_max*100, sep = '_'))
+
+    bm_pred_comb <- bind_rows(bm_pred_comb, bm_pred_sim_comb)
+
+  }
 
   to_omit <- bm_pred_comb |>
     filter(is.na(cstat) | is.na(ibs_scaled)) |>

### 2022-07-09 R/sim_surv.R

@@ -12,12 +12,12 @@ sim_surv <- function(n_obs = 500,
                      n_intr_nlin = 5,
                      n_pred_cmbn = 45,
                      n_intr_cmbn = 5,
-                     eff_size_pred_main = 1/2,
-                     eff_size_intr_main = 1/2,
-                     eff_size_pred_nlin = 1/2,
-                     eff_size_intr_nlin = 1/2,
-                     eff_size_pred_cmbn = 1/2,
-                     eff_size_intr_cmbn = 1/2,
+                     eff_size_pred_main = 3/4,
+                     eff_size_intr_main = 3/4,
+                     eff_size_pred_nlin = 3/4,
+                     eff_size_intr_nlin = 3/4,
+                     eff_size_pred_cmbn = 3/4,
+                     eff_size_intr_cmbn = 3/4,
                      pred_corr_min = 0.00,
                      pred_corr_max = 0.10,
                      pred_horiz = 2.5) {

### 2022-07-09 packages.R

@@ -31,6 +31,7 @@ library(rotsf)
 library(rsfse)
 library(pec)
 library(ggridges)
+library(ggpubr)
 library(tidybayes)
 library(rstan)
 library(rstanarm)

### 2022-07-14 docs/index.Rmd
results for VI; viz in prog
paper update, slide fix

@@
     bm_vi_smry,
+    bm_vi_viz,
     data_key
@@
 ```{r bm_pred_viz_ibs, fig.height=9, fig.width=11}
-bm_pred_viz$ibs_scaled
+bm_pred_viz$ibs_scaled$fig
 ```
@@
 ```{r bm_pred_viz_cstat, fig.height=9, fig.width=11}
-bm_pred_viz$cstat
+bm_pred_viz$cstat$fig
 ```
@@
 ```{r bm_pred_model_viz_ibs, fig.height=6.9, fig.width=9}
-bm_pred_model_viz$ibs_scaled
+bm_pred_model_viz$fig$ibs_scaled
 ```
@@
 ```{r bm_pred_model_viz_cstat, fig.height=6.9, fig.width=9}
-bm_pred_model_viz$cstat
+bm_pred_model_viz$fig$cstat
 ```
@@
 ```{r bm_pred_time_ridges, fig.height=6.5, fig.width=8}
-bm_pred_time_viz
+bm_pred_time_viz$fig
 ```
@@
   ungroup() %>%
-  filter(n_obs == 5000) %>%
+  filter(n_obs == 2500) %>%
   mutate(
@@
   plotly::layout(
-    title = list(text = 'Results when N = 5000', x = 0.1),
+    title = list(text = 'Results when N = 2500', x = 0.1),
     xaxis = list(title = 'Max correlation among predictors'),

### 2022-07-14 paper/jmlr/main.Rnw
paper update, slide fix

@@
 Compared to the VI technique with the second highest overall C-statistic (\texttt{\Sexpr{cstat_vi_second_place$model}}), \texttt{aorsf-negate}'s mean was \Sexpr{cstat_aorsf_won_by$absolute} points higher, a relative increase of \Sexpr{cstat_aorsf_won_by$percent}\%.
-Among each of the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables and the smallest advantage for interaction variables.
+Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
+
+The three techniques that used `aorsf` to estimate VI were ranked first (negation), second (ANOVA), and third (permutation) in overall mean C-statistic across all of the simulation scenarios.
+Computationally, ANOVA VI was the fastest technique with a median average
 
@@
 However, prediction models that cannot be interpreted and explained have no place in clinical practice.
-The current study advances the oblique RSF, an accurate risk prediction model, several steps towards being an accurate \textit{and} interpretable risk prediction model.
-The improved computational efficiency of the accelerated oblique RSF increases the feasibility of applying model-agnostic methods (\eg, SHAP values) for interpretation.
+The current study advances the oblique RSF, an accurate risk prediction model, towards being accurate, scalable, and interpretable.
+The improved computational efficiency of the accelerated oblique RSF increases the feasibility of applying oblique RSFs in a wide range of prediction tasks.
 Faster model evaluation and re-fitting also improve diagnosis and resolution of model-based issues (\eg, model calibration deteriorates over time).
@@
 Thus, a second item of high priority for future studies is to develop and evaluate strategies to handle missing data while growing an oblique RSF.
+Last, \citet{cui2017consistency} found that estimating an inverse-probability weighted hazard function at each non-leaf node of a survival tree allows the RSF to converge asymptotically to the true survival function when some variables contribute both to the risk of the event and the risk of censoring, a scenario that is very likely in the analysis of electronic medical records.
+The accelerated oblique RSF could incorporate this splitting technique by using Newton Raphson scoring to fit a model for the censoring distribution and then a weighted model could be fit to the failure distribution.
 

### 2022-07-14 paper/jmlr/main.tex
paper update, slide fix

@@
 
-For each risk prediction task, we completed 5 runs of Monte-Carlo cross validation.
+For each risk prediction task, we completed 20 runs of Monte-Carlo cross validation.
 In each run, we used a random sample containing 50\% of the available data for training and the remaining 50\% for testing each of the learners described in \secref{sec:learners}.
@@
 
-After collecting data from 5 replications of Monte-Carlo cross validation for the 14 learners in all 31 risk prediction tasks, we analyzed the resulting 2,170 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
+After collecting data from 20 replications of Monte-Carlo cross validation for the 14 learners in all 31 risk prediction tasks, we analyzed the resulting 8,680 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
 Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using Bayesian models.
@@
 Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in  out of 31 risk prediction tasks, with an overall mean IPA of  (Figure \ref{fig:bm_pred_viz_ibs}).
-Compared to the learner with the second highest mean IPA (\texttt{rsf-standard}), \texttt{aorsf-fast}'s mean was 1.12 points higher, a relative increase of 9.30\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.95, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.63 (versus \texttt{rsf-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+Compared to the learner with the second highest mean IPA (\texttt{rsf-standard}), \texttt{aorsf-fast}'s mean was 1.27 points higher, a relative increase of 10.5\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.98, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.76 (versus \texttt{rsf-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
 
@@
 Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in  out of 31 risk prediction tasks, with an overall mean of  (Figure \ref{fig:bm_pred_viz_cstat}).
-Compared to the learner with the second highest mean C-statistic (\texttt{obliqueRSF-net}), \texttt{aorsf-fast}'s mean was 0.612 points higher, a relative increase of 0.797\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.96, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.02 (versus \texttt{obliqueRSF-net}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+Compared to the learner with the second highest mean C-statistic (\texttt{obliqueRSF-net}), \texttt{aorsf-fast}'s mean was 0.643 points higher, a relative increase of 0.837\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.01 (versus \texttt{obliqueRSF-net}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
 
@@
 
-Overall, \texttt{aorsf-negate} had the highest C-statistic in 21 out of 36 VI tasks, with an overall mean of 75.3 (Figure \ref{fig:bm_vi_viz}).
-Compared to the VI technique with the second highest overall C-statistic (\texttt{aorsf-anova}), \texttt{aorsf-negate}'s mean was 2.34 points higher, a relative increase of 3.21\%.
-Among each of the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables and the smallest advantage for interaction variables.
+Overall, \texttt{aorsf-negate} had the highest C-statistic in 27 out of 36 VI tasks, with an overall mean of 76.1 (Figure \ref{fig:bm_vi_viz}).
+Compared to the VI technique with the second highest overall C-statistic (\texttt{aorsf-anova}), \texttt{aorsf-negate}'s mean was 2.22 points higher, a relative increase of 3.00\%.
+Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
+
+The three techniques that used `aorsf` to estimate VI were ranked first (negation), second (ANOVA), and third (permutation) in overall mean C-statistic across all of the simulation scenarios.
+Computationally, ANOVA VI was the fastest technique with a median average
 
@@
 \hline
-\hspace{1em}aorsf-fast & 0.132 (0.114) & 0.774 (0.072) & 0.833 & 0.173\\
-\hspace{1em}aorsf-cph & 0.131 (0.115) & 0.772 (0.072) & 2.477 & 0.174\\
-\hspace{1em}aorsf-net & 0.130 (0.118) & 0.772 (0.072) & 131.969 & 0.176\\
-\hspace{1em}rsf-standard & 0.121 (0.118) & 0.761 (0.075) & 2.070 & 0.291\\
-\hspace{1em}cif-standard & 0.120 (0.101) & 0.768 (0.071) & 4.499 & 15.774\\
-\hspace{1em}cif-rotate & 0.119 (0.129) & 0.758 (0.080) & 43.469 & 9.418\\
-\hspace{1em}obliqueRSF-net & 0.119 (0.088) & 0.773 (0.071) & 388.086 & 24.864\\
-\hspace{1em}glmnet-cox & 0.115 (0.123) & 0.761 (0.074) & 0.693 & 0.004\\
-\hspace{1em}ranger-extratrees & 0.104 (0.090) & 0.763 (0.068) & 2.147 & 1.592\\
-\hspace{1em}cif-extension & 0.099 (0.095) & 0.764 (0.072) & 23.953 & 8.487\\
-\hspace{1em}aorsf-random & 0.095 (0.085) & 0.742 (0.065) & 2.288 & 0.174\\
-\hspace{1em}xgboost-cox & 0.076 (0.105) & 0.757 (0.088) & 4.399 & 0.005\\
-\hspace{1em}nn-cox & 0.045 (0.101) & 0.648 (0.137) & 16.081 & 5.931\\
-\hspace{1em}xgboost-aft & -4.80 (5.11) & 0.767 (0.077) & 14.692 & 0.007\\
+\hspace{1em}aorsf-fast & 0.134 (0.112) & 0.774 (0.071) & 0.772 & 0.188\\
+\hspace{1em}aorsf-cph & 0.133 (0.112) & 0.773 (0.070) & 1.993 & 0.184\\
+\hspace{1em}aorsf-net & 0.126 (0.127) & 0.770 (0.074) & 128.379 & 0.177\\
+\hspace{1em}rsf-standard & 0.121 (0.116) & 0.760 (0.075) & 2.168 & 0.291\\
+\hspace{1em}cif-standard & 0.120 (0.100) & 0.768 (0.070) & 4.511 & 15.781\\
+\hspace{1em}cif-rotate & 0.120 (0.128) & 0.758 (0.080) & 42.206 & 9.111\\
+\hspace{1em}obliqueRSF-net & 0.120 (0.086) & 0.773 (0.071) & 376.676 & 24.742\\
+\hspace{1em}glmnet-cox & 0.117 (0.122) & 0.761 (0.075) & 0.460 & 0.004\\
+\hspace{1em}ranger-extratrees & 0.105 (0.088) & 0.764 (0.067) & 2.416 & 1.775\\
+\hspace{1em}cif-extension & 0.100 (0.095) & 0.763 (0.072) & 23.171 & 8.367\\
+\hspace{1em}aorsf-random & 0.095 (0.083) & 0.743 (0.064) & 2.272 & 0.180\\
+\hspace{1em}xgboost-cox & 0.072 (0.102) & 0.757 (0.088) & 4.368 & 0.004\\
+\hspace{1em}nn-cox & 0.049 (0.109) & 0.653 (0.136) & 16.163 & 4.563\\
+\hspace{1em}xgboost-aft & -4.74 (5.18) & 0.767 (0.074) & 14.635 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}ranger-extratrees & 0.028 (0.018) & 0.737 (0.042) & 0.053 & 0.155\\
-\hspace{1em}aorsf-random & 0.024 (0.019) & 0.732 (0.042) & 0.452 & 0.036\\
-\hspace{1em}cif-standard & 0.024 (0.039) & 0.741 (0.060) & 1.460 & 4.523\\
-\hspace{1em}cif-extension & 0.022 (0.021) & 0.716 (0.055) & 9.093 & 4.176\\
-\hspace{1em}obliqueRSF-net & 0.020 (0.030) & 0.733 (0.056) & 26.723 & 16.653\\
-\hspace{1em}aorsf-cph & 0.017 (0.032) & 0.736 (0.056) & 0.452 & 0.037\\
-\hspace{1em}aorsf-fast & 0.016 (0.027) & 0.733 (0.054) & 0.153 & 0.034\\
-\hspace{1em}glmnet-cox & 0.011 (0.023) & 0.735 (0.034) & 0.180 & 0.002\\
-\hspace{1em}aorsf-net & 0.010 (0.041) & 0.731 (0.055) & 19.025 & 0.036\\
-\hspace{1em}xgboost-cox & 0.006 (0.046) & 0.747 (0.052) & 3.312 & 0.003\\
-\hspace{1em}rsf-standard & 0.004 (0.042) & 0.721 (0.058) & 0.466 & 0.061\\
-\hspace{1em}nn-cox & 0.001 (0.007) & 0.589 (0.138) & 10.976 & 0.666\\
-\hspace{1em}cif-rotate & -0.002 (0.050) & 0.728 (0.051) & 14.852 & 4.031\\
-\hspace{1em}xgboost-aft & -7.31 (0.690) & 0.739 (0.040) & 9.771 & 0.006\\
+\hspace{1em}aorsf-random & 0.031 (0.020) & 0.744 (0.035) & 0.408 & 0.036\\
+\hspace{1em}ranger-extratrees & 0.029 (0.017) & 0.739 (0.037) & 0.052 & 0.145\\
+\hspace{1em}cif-standard & 0.028 (0.027) & 0.746 (0.039) & 1.052 & 4.532\\
+\hspace{1em}obliqueRSF-net & 0.028 (0.022) & 0.743 (0.039) & 26.784 & 15.942\\
+\hspace{1em}aorsf-fast & 0.026 (0.027) & 0.741 (0.041) & 0.143 & 0.034\\
+\hspace{1em}aorsf-cph & 0.026 (0.029) & 0.747 (0.040) & 0.433 & 0.035\\
+\hspace{1em}cif-extension & 0.024 (0.015) & 0.722 (0.040) & 9.266 & 4.180\\
+\hspace{1em}aorsf-net & 0.020 (0.034) & 0.742 (0.040) & 18.859 & 0.036\\
+\hspace{1em}glmnet-cox & 0.018 (0.027) & 0.744 (0.035) & 0.172 & 0.002\\
+\hspace{1em}rsf-standard & 0.011 (0.034) & 0.732 (0.042) & 0.145 & 0.059\\
+\hspace{1em}cif-rotate & 0.008 (0.037) & 0.736 (0.035) & 15.338 & 3.967\\
+\hspace{1em}nn-cox & -0.001 (0.017) & 0.638 (0.114) & 10.944 & 0.541\\
+\hspace{1em}xgboost-cox & -0.002 (0.048) & 0.748 (0.033) & 3.788 & 0.003\\
+\hspace{1em}xgboost-aft & -8.09 (1.44) & 0.736 (0.035) & 9.657 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-extension & 0.004 (0.012) & 0.794 (0.066) & 12.087 & 5.085\\
-\hspace{1em}obliqueRSF-net & 0.003 (0.012) & 0.822 (0.064) & 8.856 & 11.019\\
-\hspace{1em}aorsf-fast & 0.001 (0.019) & 0.830 (0.062) & 0.094 & 0.020\\
-\hspace{1em}cif-standard & 0.000 (0.022) & 0.797 (0.079) & 1.505 & 4.550\\
-\hspace{1em}aorsf-random & 0.000 (0.016) & 0.793 (0.090) & 0.247 & 0.023\\
-\hspace{1em}aorsf-cph & -0.001 (0.018) & 0.811 (0.073) & 0.361 & 0.022\\
-\hspace{1em}xgboost-cox & -0.005 (0.003) & 0.500 (0.000) & 0.116 & 0.002\\
-\hspace{1em}nn-cox & -0.006 (0.003) & 0.514 (0.102) & 10.371 & 0.517\\
-\hspace{1em}aorsf-net & -0.006 (0.034) & 0.813 (0.070) & 13.008 & 0.023\\
-\hspace{1em}ranger-extratrees & -0.006 (0.022) & 0.768 (0.078) & 0.041 & 0.127\\
-\hspace{1em}rsf-standard & -0.027 (0.060) & 0.796 (0.074) & 0.097 & 0.037\\
-\hspace{1em}cif-rotate & -0.030 (0.037) & 0.727 (0.092) & 12.924 & 3.575\\
-\hspace{1em}glmnet-cox & -0.057 (0.096) & 0.777 (0.062) & 0.282 & 0.003\\
-\hspace{1em}xgboost-aft & -23.5 (7.27) & 0.772 (0.100) & 8.740 & 0.006\\
+\hspace{1em}aorsf-fast & 0.008 (0.019) & 0.835 (0.056) & 0.087 & 0.020\\
+\hspace{1em}obliqueRSF-net & 0.008 (0.011) & 0.829 (0.053) & 8.678 & 10.534\\
+\hspace{1em}aorsf-cph & 0.008 (0.018) & 0.827 (0.063) & 0.351 & 0.020\\
+\hspace{1em}aorsf-random & 0.006 (0.014) & 0.802 (0.071) & 0.224 & 0.023\\
+\hspace{1em}cif-extension & 0.001 (0.021) & 0.770 (0.069) & 8.850 & 3.780\\
+\hspace{1em}ranger-extratrees & 0.000 (0.019) & 0.778 (0.073) & 0.041 & 0.126\\
+\hspace{1em}aorsf-net & -0.002 (0.032) & 0.814 (0.069) & 14.142 & 0.023\\
+\hspace{1em}cif-standard & -0.004 (0.025) & 0.784 (0.065) & 1.106 & 4.570\\
+\hspace{1em}xgboost-cox & -0.004 (0.004) & 0.500 (0.000) & 0.111 & 0.002\\
+\hspace{1em}nn-cox & -0.005 (0.004) & 0.522 (0.099) & 9.961 & 0.534\\
+\hspace{1em}rsf-standard & -0.028 (0.050) & 0.780 (0.078) & 0.093 & 0.037\\
+\hspace{1em}cif-rotate & -0.036 (0.048) & 0.709 (0.091) & 13.345 & 3.439\\
+\hspace{1em}glmnet-cox & -0.060 (0.102) & 0.749 (0.106) & 0.275 & 0.002\\
+\hspace{1em}xgboost-aft & -25.1 (7.60) & 0.778 (0.074) & 9.772 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.156 (0.005) & 0.806 (0.004) & 4.321 & 1.354\\
-\hspace{1em}aorsf-net & 0.153 (0.004) & 0.806 (0.003) & 515.337 & 1.480\\
-\hspace{1em}aorsf-cph & 0.152 (0.005) & 0.806 (0.004) & 14.632 & 1.349\\
-\hspace{1em}rsf-standard & 0.149 (0.006) & 0.797 (0.003) & 7.394 & 1.041\\
-\hspace{1em}obliqueRSF-net & 0.145 (0.002) & 0.808 (0.002) & 3100.286 & 413.186\\
-\hspace{1em}cif-standard & 0.133 (0.002) & 0.806 (0.002) & 69.980 & 358.577\\
-\hspace{1em}glmnet-cox & 0.132 (0.008) & 0.795 (0.003) & 1.467 & 0.025\\
-\hspace{1em}nn-cox & 0.123 (0.008) & 0.793 (0.004) & 82.973 & 106.367\\
-\hspace{1em}ranger-extratrees & 0.112 (0.001) & 0.792 (0.003) & 271.533 & 63.785\\
-\hspace{1em}cif-rotate & 0.106 (0.001) & 0.782 (0.006) & 578.571 & 68.467\\
-\hspace{1em}aorsf-random & 0.098 (0.004) & 0.771 (0.004) & 11.278 & 1.387\\
-\hspace{1em}cif-extension & 0.070 (0.001) & 0.784 (0.004) & 163.371 & 49.091\\
-\hspace{1em}xgboost-cox & 0.062 (0.016) & 0.811 (0.004) & 8.980 & 0.014\\
-\hspace{1em}xgboost-aft & -4.81 (0.208) & 0.812 (0.004) & 21.435 & 0.021\\
+\hspace{1em}aorsf-fast & 0.157 (0.007) & 0.811 (0.007) & 4.591 & 1.355\\
+\hspace{1em}aorsf-cph & 0.153 (0.007) & 0.810 (0.007) & 14.698 & 1.385\\
+\hspace{1em}aorsf-net & 0.153 (0.007) & 0.811 (0.007) & 507.224 & 1.477\\
+\hspace{1em}rsf-standard & 0.151 (0.007) & 0.802 (0.007) & 9.099 & 1.101\\
+\hspace{1em}obliqueRSF-net & 0.144 (0.005) & 0.813 (0.007) & 2836.384 & 351.006\\
+\hspace{1em}cif-standard & 0.133 (0.005) & 0.810 (0.007) & 70.288 & 358.500\\
+\hspace{1em}glmnet-cox & 0.129 (0.012) & 0.796 (0.008) & 1.721 & 0.011\\
+\hspace{1em}nn-cox & 0.124 (0.014) & 0.796 (0.007) & 55.992 & 105.741\\
+\hspace{1em}ranger-extratrees & 0.112 (0.005) & 0.796 (0.008) & 320.882 & 71.239\\
+\hspace{1em}cif-rotate & 0.104 (0.004) & 0.784 (0.008) & 569.756 & 70.690\\
+\hspace{1em}aorsf-random & 0.098 (0.005) & 0.773 (0.008) & 11.738 & 1.361\\
+\hspace{1em}cif-extension & 0.069 (0.002) & 0.787 (0.009) & 164.896 & 51.659\\
+\hspace{1em}xgboost-cox & 0.066 (0.018) & 0.815 (0.006) & 8.635 & 0.015\\
+\hspace{1em}xgboost-aft & -4.92 (0.295) & 0.815 (0.005) & 22.322 & 0.013\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}rsf-standard & 0.218 (0.004) & 0.790 (0.001) & 11.948 & 1.186\\
-\hspace{1em}aorsf-net & 0.218 (0.006) & 0.792 (0.003) & 958.228 & 2.380\\
-\hspace{1em}aorsf-cph & 0.215 (0.007) & 0.791 (0.003) & 22.614 & 2.249\\
-\hspace{1em}aorsf-fast & 0.215 (0.007) & 0.792 (0.003) & 7.190 & 2.258\\
-\hspace{1em}obliqueRSF-net & 0.208 (0.004) & 0.792 (0.003) & 7161.062 & 322.057\\
-\hspace{1em}cif-standard & 0.202 (0.004) & 0.789 (0.004) & 64.173 & 379.745\\
-\hspace{1em}glmnet-cox & 0.191 (0.017) & 0.777 (0.006) & 1.852 & 0.018\\
-\hspace{1em}nn-cox & 0.183 (0.016) & 0.781 (0.003) & 95.577 & 77.835\\
-\hspace{1em}ranger-extratrees & 0.181 (0.006) & 0.779 (0.005) & 350.659 & 58.944\\
-\hspace{1em}cif-rotate & 0.152 (0.005) & 0.755 (0.006) & 577.948 & 65.954\\
-\hspace{1em}xgboost-cox & 0.134 (0.015) & 0.795 (0.001) & 11.789 & 0.015\\
-\hspace{1em}aorsf-random & 0.130 (0.004) & 0.733 (0.003) & 18.944 & 1.995\\
-\hspace{1em}cif-extension & 0.114 (0.001) & 0.775 (0.005) & 180.959 & 50.040\\
-\hspace{1em}xgboost-aft & -1.63 (0.238) & 0.795 (0.002) & 25.690 & 0.014\\
+\hspace{1em}aorsf-net & 0.217 (0.006) & 0.792 (0.004) & 952.688 & 2.390\\
+\hspace{1em}rsf-standard & 0.216 (0.007) & 0.789 (0.004) & 13.694 & 1.330\\
+\hspace{1em}aorsf-fast & 0.215 (0.007) & 0.792 (0.004) & 7.760 & 2.287\\
+\hspace{1em}aorsf-cph & 0.215 (0.007) & 0.791 (0.004) & 23.194 & 2.305\\
+\hspace{1em}obliqueRSF-net & 0.207 (0.005) & 0.791 (0.004) & 7578.159 & 316.772\\
+\hspace{1em}cif-standard & 0.201 (0.005) & 0.790 (0.004) & 72.192 & 385.603\\
+\hspace{1em}nn-cox & 0.192 (0.013) & 0.780 (0.005) & 102.206 & 101.400\\
+\hspace{1em}glmnet-cox & 0.189 (0.015) & 0.776 (0.007) & 2.123 & 0.012\\
+\hspace{1em}ranger-extratrees & 0.181 (0.005) & 0.781 (0.005) & 421.367 & 67.011\\
+\hspace{1em}cif-rotate & 0.152 (0.007) & 0.757 (0.006) & 582.264 & 65.718\\
+\hspace{1em}xgboost-cox & 0.132 (0.011) & 0.794 (0.004) & 12.326 & 0.016\\
+\hspace{1em}aorsf-random & 0.130 (0.005) & 0.733 (0.006) & 22.918 & 2.061\\
+\hspace{1em}cif-extension & 0.112 (0.002) & 0.776 (0.005) & 182.973 & 54.549\\
+\hspace{1em}xgboost-aft & -1.59 (0.150) & 0.794 (0.004) & 28.205 & 0.015\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.236 (0.005) & 0.842 (0.006) & 5.253 & 1.671\\
-\hspace{1em}rsf-standard & 0.231 (0.005) & 0.835 (0.004) & 10.275 & 1.254\\
-\hspace{1em}aorsf-net & 0.231 (0.004) & 0.842 (0.005) & 628.786 & 1.736\\
-\hspace{1em}aorsf-cph & 0.231 (0.006) & 0.842 (0.006) & 16.545 & 1.568\\
-\hspace{1em}obliqueRSF-net & 0.215 (0.003) & 0.841 (0.005) & 3701.023 & 306.739\\
-\hspace{1em}cif-standard & 0.200 (0.002) & 0.839 (0.005) & 67.705 & 364.696\\
-\hspace{1em}nn-cox & 0.181 (0.029) & 0.823 (0.008) & 79.949 & 112.151\\
-\hspace{1em}glmnet-cox & 0.179 (0.036) & 0.821 (0.010) & 1.899 & 0.012\\
-\hspace{1em}ranger-extratrees & 0.173 (0.003) & 0.825 (0.006) & 260.123 & 63.679\\
-\hspace{1em}cif-rotate & 0.171 (0.003) & 0.806 (0.005) & 581.803 & 66.846\\
-\hspace{1em}aorsf-random & 0.141 (0.004) & 0.792 (0.004) & 13.281 & 1.509\\
-\hspace{1em}xgboost-cox & 0.119 (0.009) & 0.844 (0.005) & 13.603 & 0.015\\
-\hspace{1em}cif-extension & 0.110 (0.003) & 0.809 (0.006) & 167.897 & 48.511\\
-\hspace{1em}xgboost-aft & -3.93 (0.269) & 0.843 (0.005) & 22.308 & 0.022\\
+\hspace{1em}aorsf-fast & 0.234 (0.007) & 0.842 (0.005) & 5.447 & 1.627\\
+\hspace{1em}rsf-standard & 0.230 (0.007) & 0.836 (0.005) & 10.044 & 1.063\\
+\hspace{1em}aorsf-cph & 0.230 (0.006) & 0.841 (0.005) & 16.965 & 1.635\\
+\hspace{1em}aorsf-net & 0.216 (0.059) & 0.832 (0.045) & 632.139 & 1.707\\
+\hspace{1em}obliqueRSF-net & 0.213 (0.005) & 0.842 (0.005) & 3706.701 & 311.291\\
+\hspace{1em}cif-standard & 0.200 (0.004) & 0.839 (0.005) & 74.710 & 369.280\\
+\hspace{1em}nn-cox & 0.188 (0.020) & 0.827 (0.009) & 66.425 & 104.654\\
+\hspace{1em}cif-rotate & 0.172 (0.006) & 0.807 (0.007) & 577.084 & 67.496\\
+\hspace{1em}ranger-extratrees & 0.171 (0.004) & 0.825 (0.005) & 326.124 & 84.602\\
+\hspace{1em}glmnet-cox & 0.168 (0.042) & 0.818 (0.016) & 2.513 & 0.012\\
+\hspace{1em}aorsf-random & 0.139 (0.005) & 0.789 (0.006) & 15.868 & 1.587\\
+\hspace{1em}xgboost-cox & 0.122 (0.017) & 0.846 (0.005) & 11.223 & 0.015\\
+\hspace{1em}cif-extension & 0.108 (0.003) & 0.809 (0.007) & 169.585 & 49.274\\
+\hspace{1em}xgboost-aft & -3.80 (0.250) & 0.845 (0.005) & 26.160 & 0.014\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.094 (0.003) & 0.794 (0.003) & 3.786 & 1.160\\
-\hspace{1em}rsf-standard & 0.092 (0.003) & 0.786 (0.005) & 5.225 & 0.875\\
-\hspace{1em}aorsf-net & 0.091 (0.003) & 0.793 (0.004) & 411.476 & 1.233\\
-\hspace{1em}aorsf-cph & 0.090 (0.003) & 0.792 (0.004) & 13.452 & 1.127\\
-\hspace{1em}obliqueRSF-net & 0.082 (0.002) & 0.791 (0.004) & 1751.465 & 410.345\\
-\hspace{1em}glmnet-cox & 0.079 (0.005) & 0.785 (0.004) & 1.493 & 0.011\\
-\hspace{1em}cif-standard & 0.074 (0.002) & 0.788 (0.004) & 78.679 & 394.309\\
-\hspace{1em}nn-cox & 0.072 (0.016) & 0.782 (0.008) & 28.811 & 84.991\\
-\hspace{1em}ranger-extratrees & 0.068 (0.003) & 0.780 (0.006) & 310.500 & 70.135\\
-\hspace{1em}aorsf-random & 0.059 (0.004) & 0.752 (0.007) & 9.207 & 1.136\\
-\hspace{1em}cif-rotate & 0.052 (0.002) & 0.768 (0.009) & 614.088 & 69.548\\
-\hspace{1em}xgboost-cox & 0.047 (0.012) & 0.792 (0.001) & 6.854 & 0.014\\
-\hspace{1em}cif-extension & 0.036 (0.001) & 0.772 (0.007) & 163.803 & 49.613\\
-\hspace{1em}xgboost-aft & -6.78 (0.231) & 0.791 (0.002) & 21.692 & 0.023\\
+\hspace{1em}aorsf-fast & 0.094 (0.004) & 0.795 (0.007) & 4.109 & 1.124\\
+\hspace{1em}rsf-standard & 0.091 (0.005) & 0.785 (0.007) & 7.142 & 0.915\\
+\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.793 (0.008) & 13.304 & 1.124\\
+\hspace{1em}aorsf-net & 0.087 (0.018) & 0.786 (0.032) & 391.565 & 1.201\\
+\hspace{1em}obliqueRSF-net & 0.082 (0.003) & 0.792 (0.007) & 1773.436 & 379.126\\
+\hspace{1em}glmnet-cox & 0.078 (0.005) & 0.788 (0.007) & 1.789 & 0.010\\
+\hspace{1em}cif-standard & 0.074 (0.003) & 0.789 (0.007) & 72.507 & 366.228\\
+\hspace{1em}nn-cox & 0.072 (0.013) & 0.781 (0.010) & 32.716 & 93.157\\
+\hspace{1em}ranger-extratrees & 0.068 (0.003) & 0.780 (0.009) & 256.826 & 67.732\\
+\hspace{1em}aorsf-random & 0.059 (0.004) & 0.751 (0.009) & 9.314 & 1.118\\
+\hspace{1em}cif-rotate & 0.052 (0.003) & 0.769 (0.009) & 588.245 & 70.061\\
+\hspace{1em}xgboost-cox & 0.046 (0.014) & 0.794 (0.006) & 6.688 & 0.014\\
+\hspace{1em}cif-extension & 0.036 (0.002) & 0.772 (0.008) & 169.525 & 51.117\\
+\hspace{1em}xgboost-aft & -6.54 (0.420) & 0.793 (0.007) & 21.053 & 0.013\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.099 (0.018) & 0.718 (0.013) & 0.228 & 0.047\\
-\hspace{1em}cif-standard & 0.099 (0.016) & 0.712 (0.013) & 1.158 & 3.454\\
-\hspace{1em}aorsf-cph & 0.097 (0.018) & 0.716 (0.012) & 0.646 & 0.051\\
-\hspace{1em}aorsf-net & 0.095 (0.014) & 0.716 (0.010) & 48.543 & 0.049\\
-\hspace{1em}aorsf-random & 0.095 (0.009) & 0.717 (0.012) & 1.361 & 0.045\\
-\hspace{1em}cif-rotate & 0.095 (0.020) & 0.712 (0.011) & 12.821 & 3.474\\
-\hspace{1em}obliqueRSF-net & 0.089 (0.005) & 0.716 (0.010) & 250.693 & 16.565\\
-\hspace{1em}rsf-standard & 0.084 (0.026) & 0.705 (0.008) & 1.193 & 0.135\\
-\hspace{1em}cif-extension & 0.080 (0.007) & 0.708 (0.013) & 10.097 & 4.783\\
-\hspace{1em}ranger-extratrees & 0.078 (0.010) & 0.709 (0.017) & 0.494 & 0.239\\
-\hspace{1em}glmnet-cox & 0.076 (0.018) & 0.703 (0.024) & 0.112 & 0.002\\
-\hspace{1em}xgboost-cox & 0.060 (0.006) & 0.699 (0.010) & 2.915 & 0.003\\
-\hspace{1em}nn-cox & -0.005 (0.003) & 0.521 (0.030) & 12.067 & 1.890\\
-\hspace{1em}xgboost-aft & -1.06 (0.351) & 0.707 (0.013) & 13.225 & 0.006\\
+\hspace{1em}aorsf-fast & 0.098 (0.014) & 0.716 (0.012) & 0.228 & 0.050\\
+\hspace{1em}aorsf-cph & 0.098 (0.014) & 0.715 (0.011) & 0.632 & 0.051\\
+\hspace{1em}cif-standard & 0.096 (0.014) & 0.709 (0.012) & 0.666 & 3.606\\
+\hspace{1em}aorsf-random & 0.094 (0.009) & 0.714 (0.011) & 1.002 & 0.045\\
+\hspace{1em}aorsf-net & 0.090 (0.025) & 0.708 (0.037) & 49.445 & 0.046\\
+\hspace{1em}obliqueRSF-net & 0.088 (0.006) & 0.716 (0.012) & 250.492 & 16.952\\
+\hspace{1em}cif-rotate & 0.085 (0.018) & 0.704 (0.014) & 12.226 & 3.491\\
+\hspace{1em}rsf-standard & 0.084 (0.019) & 0.702 (0.010) & 1.526 & 0.149\\
+\hspace{1em}ranger-extratrees & 0.082 (0.007) & 0.710 (0.011) & 0.090 & 0.245\\
+\hspace{1em}cif-extension & 0.080 (0.006) & 0.708 (0.012) & 8.368 & 4.020\\
+\hspace{1em}glmnet-cox & 0.073 (0.014) & 0.709 (0.017) & 0.104 & 0.003\\
+\hspace{1em}xgboost-cox & 0.061 (0.013) & 0.699 (0.012) & 3.172 & 0.003\\
+\hspace{1em}nn-cox & -0.003 (0.003) & 0.511 (0.022) & 11.966 & 1.368\\
+\hspace{1em}xgboost-aft & -1.12 (0.214) & 0.705 (0.014) & 11.661 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.097 (0.012) & 0.710 (0.009) & 0.227 & 0.055\\
-\hspace{1em}aorsf-cph & 0.096 (0.011) & 0.709 (0.008) & 0.639 & 0.052\\
-\hspace{1em}aorsf-net & 0.096 (0.016) & 0.710 (0.012) & 51.707 & 0.045\\
-\hspace{1em}cif-standard & 0.093 (0.016) & 0.700 (0.016) & 1.060 & 3.235\\
-\hspace{1em}cif-rotate & 0.092 (0.017) & 0.698 (0.016) & 12.951 & 3.530\\
-\hspace{1em}obliqueRSF-net & 0.089 (0.007) & 0.708 (0.011) & 263.760 & 15.788\\
-\hspace{1em}aorsf-random & 0.086 (0.005) & 0.702 (0.004) & 1.285 & 0.051\\
-\hspace{1em}cif-extension & 0.082 (0.005) & 0.703 (0.010) & 8.427 & 3.628\\
-\hspace{1em}rsf-standard & 0.081 (0.019) & 0.695 (0.012) & 1.290 & 0.145\\
-\hspace{1em}ranger-extratrees & 0.075 (0.008) & 0.694 (0.010) & 0.562 & 0.225\\
-\hspace{1em}glmnet-cox & 0.069 (0.012) & 0.692 (0.018) & 0.117 & 0.003\\
-\hspace{1em}xgboost-cox & 0.056 (0.011) & 0.691 (0.012) & 3.446 & 0.003\\
-\hspace{1em}nn-cox & -0.037 (0.064) & 0.519 (0.030) & 22.950 & 1.477\\
-\hspace{1em}xgboost-aft & -1.20 (0.298) & 0.698 (0.015) & 11.457 & 0.006\\
+\hspace{1em}aorsf-fast & 0.097 (0.016) & 0.711 (0.015) & 0.228 & 0.050\\
+\hspace{1em}aorsf-cph & 0.096 (0.017) & 0.710 (0.014) & 0.641 & 0.050\\
+\hspace{1em}cif-standard & 0.089 (0.016) & 0.698 (0.015) & 0.661 & 3.398\\
+\hspace{1em}obliqueRSF-net & 0.086 (0.009) & 0.708 (0.014) & 258.163 & 16.636\\
+\hspace{1em}aorsf-net & 0.085 (0.044) & 0.705 (0.025) & 50.808 & 0.048\\
+\hspace{1em}aorsf-random & 0.085 (0.013) & 0.700 (0.015) & 0.998 & 0.047\\
+\hspace{1em}cif-rotate & 0.083 (0.020) & 0.694 (0.016) & 12.335 & 3.554\\
+\hspace{1em}cif-extension & 0.081 (0.008) & 0.704 (0.015) & 8.129 & 3.884\\
+\hspace{1em}rsf-standard & 0.078 (0.021) & 0.692 (0.014) & 1.621 & 0.147\\
+\hspace{1em}ranger-extratrees & 0.077 (0.011) & 0.697 (0.014) & 0.090 & 0.238\\
+\hspace{1em}glmnet-cox & 0.071 (0.018) & 0.702 (0.024) & 0.115 & 0.003\\
+\hspace{1em}xgboost-cox & 0.058 (0.010) & 0.691 (0.016) & 3.002 & 0.003\\
+\hspace{1em}nn-cox & -0.014 (0.033) & 0.502 (0.035) & 13.490 & 1.248\\
+\hspace{1em}xgboost-aft & -1.22 (0.257) & 0.698 (0.017) & 12.295 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.069 (0.036) & 0.755 (0.030) & 1875.318 & 12.911\\
-\hspace{1em}cif-standard & 0.064 (0.027) & 0.752 (0.026) & 7.791 & 3.966\\
-\hspace{1em}cif-rotate & 0.062 (0.021) & 0.741 (0.017) & 6623.673 & 366.471\\
-\hspace{1em}cif-extension & 0.060 (0.021) & 0.748 (0.024) & 42.790 & 6.410\\
-\hspace{1em}aorsf-cph & 0.057 (0.054) & 0.747 (0.019) & 1.313 & 0.169\\
-\hspace{1em}aorsf-fast & 0.056 (0.054) & 0.749 (0.023) & 0.735 & 0.170\\
-\hspace{1em}ranger-extratrees & 0.054 (0.043) & 0.746 (0.022) & 0.221 & 0.165\\
-\hspace{1em}glmnet-cox & 0.026 (0.023) & 0.722 (0.019) & 5.768 & 0.007\\
-\hspace{1em}xgboost-cox & 0.025 (0.027) & 0.741 (0.017) & 2.311 & 0.007\\
-\hspace{1em}aorsf-random & 0.023 (0.023) & 0.706 (0.035) & 1.402 & 0.174\\
-\hspace{1em}aorsf-net & 0.014 (0.110) & 0.754 (0.014) & 461.060 & 0.176\\
-\hspace{1em}rsf-standard & 0.013 (0.073) & 0.698 (0.053) & 0.327 & 0.451\\
-\hspace{1em}nn-cox & -0.039 (0.088) & 0.650 (0.075) & 16.127 & 1.654\\
-\hspace{1em}xgboost-aft & -3.09 (1.10) & 0.749 (0.020) & 9.377 & 0.010\\
+\hspace{1em}obliqueRSF-net & 0.072 (0.024) & 0.750 (0.028) & 1858.856 & 13.453\\
+\hspace{1em}cif-rotate & 0.070 (0.018) & 0.747 (0.028) & 6486.756 & 347.401\\
+\hspace{1em}cif-standard & 0.068 (0.018) & 0.747 (0.028) & 8.224 & 4.008\\
+\hspace{1em}aorsf-cph & 0.065 (0.031) & 0.744 (0.023) & 1.313 & 0.182\\
+\hspace{1em}cif-extension & 0.065 (0.015) & 0.746 (0.026) & 43.993 & 6.218\\
+\hspace{1em}aorsf-fast & 0.064 (0.030) & 0.746 (0.024) & 0.746 & 0.180\\
+\hspace{1em}ranger-extratrees & 0.061 (0.023) & 0.743 (0.028) & 0.218 & 0.658\\
+\hspace{1em}glmnet-cox & 0.041 (0.032) & 0.725 (0.035) & 5.758 & 0.006\\
+\hspace{1em}aorsf-random & 0.027 (0.015) & 0.693 (0.039) & 1.671 & 0.174\\
+\hspace{1em}xgboost-cox & 0.026 (0.035) & 0.741 (0.028) & 2.272 & 0.007\\
+\hspace{1em}rsf-standard & 0.021 (0.041) & 0.695 (0.032) & 0.777 & 0.314\\
+\hspace{1em}nn-cox & -0.020 (0.076) & 0.680 (0.050) & 16.928 & 1.662\\
+\hspace{1em}aorsf-net & -0.048 (0.260) & 0.730 (0.055) & 455.331 & 0.176\\
+\hspace{1em}xgboost-aft & -3.08 (0.662) & 0.742 (0.024) & 9.532 & 0.010\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.117 (0.032) & 0.784 (0.045) & 0.096 & 0.002\\
-\hspace{1em}aorsf-cph & 0.097 (0.055) & 0.774 (0.044) & 0.164 & 0.019\\
-\hspace{1em}cif-extension & 0.097 (0.042) & 0.749 (0.045) & 5.240 & 2.305\\
-\hspace{1em}aorsf-net & 0.095 (0.052) & 0.770 (0.040) & 12.784 & 0.018\\
-\hspace{1em}aorsf-fast & 0.094 (0.053) & 0.774 (0.044) & 0.086 & 0.021\\
-\hspace{1em}obliqueRSF-net & 0.090 (0.035) & 0.771 (0.047) & 101.477 & 5.378\\
-\hspace{1em}rsf-standard & 0.090 (0.062) & 0.758 (0.042) & 0.562 & 0.038\\
-\hspace{1em}aorsf-random & 0.086 (0.036) & 0.763 (0.049) & 0.296 & 0.019\\
-\hspace{1em}cif-rotate & 0.085 (0.067) & 0.763 (0.036) & 6.328 & 2.376\\
-\hspace{1em}cif-standard & 0.085 (0.049) & 0.755 (0.049) & 0.730 & 1.121\\
-\hspace{1em}ranger-extratrees & 0.078 (0.017) & 0.752 (0.052) & 0.046 & 0.080\\
-\hspace{1em}xgboost-cox & 0.047 (0.074) & 0.717 (0.119) & 2.504 & 0.002\\
-\hspace{1em}nn-cox & 0.013 (0.041) & 0.493 (0.145) & 11.346 & 0.563\\
-\hspace{1em}xgboost-aft & -2.48 (0.436) & 0.754 (0.057) & 6.730 & 0.005\\
+\hspace{1em}glmnet-cox & 0.115 (0.031) & 0.783 (0.037) & 0.091 & 0.002\\
+\hspace{1em}aorsf-fast & 0.098 (0.040) & 0.767 (0.032) & 0.079 & 0.019\\
+\hspace{1em}aorsf-cph & 0.097 (0.041) & 0.768 (0.033) & 0.166 & 0.019\\
+\hspace{1em}aorsf-net & 0.092 (0.043) & 0.750 (0.051) & 13.196 & 0.019\\
+\hspace{1em}obliqueRSF-net & 0.090 (0.029) & 0.760 (0.038) & 96.051 & 5.285\\
+\hspace{1em}cif-extension & 0.087 (0.039) & 0.731 (0.038) & 5.172 & 2.488\\
+\hspace{1em}aorsf-random & 0.086 (0.030) & 0.757 (0.034) & 0.267 & 0.019\\
+\hspace{1em}cif-rotate & 0.086 (0.053) & 0.757 (0.030) & 6.010 & 2.042\\
+\hspace{1em}cif-standard & 0.085 (0.040) & 0.747 (0.036) & 0.290 & 1.114\\
+\hspace{1em}ranger-extratrees & 0.075 (0.016) & 0.741 (0.033) & 0.044 & 0.083\\
+\hspace{1em}rsf-standard & 0.070 (0.052) & 0.733 (0.037) & 0.109 & 0.038\\
+\hspace{1em}xgboost-cox & 0.036 (0.054) & 0.689 (0.112) & 0.348 & 0.002\\
+\hspace{1em}nn-cox & -0.003 (0.023) & 0.527 (0.112) & 11.211 & 0.423\\
+\hspace{1em}xgboost-aft & -2.56 (0.515) & 0.753 (0.039) & 7.831 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.036 (0.023) & 0.625 (0.028) & 0.109 & 0.002\\
-\hspace{1em}xgboost-cox & 0.023 (0.012) & 0.608 (0.029) & 1.694 & 0.002\\
-\hspace{1em}obliqueRSF-net & 0.019 (0.018) & 0.593 (0.036) & 225.137 & 6.199\\
-\hspace{1em}ranger-extratrees & 0.018 (0.023) & 0.586 (0.042) & 0.045 & 0.078\\
-\hspace{1em}aorsf-random & 0.017 (0.027) & 0.594 (0.038) & 0.427 & 0.021\\
-\hspace{1em}aorsf-cph & 0.011 (0.034) & 0.591 (0.040) & 0.318 & 0.026\\
-\hspace{1em}aorsf-fast & 0.011 (0.033) & 0.589 (0.039) & 0.128 & 0.023\\
-\hspace{1em}aorsf-net & 0.008 (0.036) & 0.587 (0.043) & 20.070 & 0.022\\
-\hspace{1em}cif-standard & 0.006 (0.028) & 0.591 (0.034) & 0.721 & 1.132\\
-\hspace{1em}nn-cox & -0.003 (0.030) & 0.534 (0.074) & 11.088 & 0.436\\
-\hspace{1em}cif-extension & -0.004 (0.037) & 0.578 (0.045) & 6.192 & 2.357\\
-\hspace{1em}cif-rotate & -0.008 (0.034) & 0.581 (0.036) & 7.111 & 2.207\\
-\hspace{1em}rsf-standard & -0.025 (0.041) & 0.578 (0.038) & 1.326 & 0.086\\
-\hspace{1em}xgboost-aft & -0.974 (0.221) & 0.574 (0.060) & 6.179 & 0.006\\
+\hspace{1em}glmnet-cox & 0.028 (0.018) & 0.617 (0.024) & 0.089 & 0.002\\
+\hspace{1em}ranger-extratrees & 0.017 (0.016) & 0.593 (0.026) & 0.033 & 0.081\\
+\hspace{1em}obliqueRSF-net & 0.013 (0.016) & 0.590 (0.025) & 217.653 & 6.187\\
+\hspace{1em}aorsf-random & 0.012 (0.018) & 0.595 (0.026) & 0.395 & 0.021\\
+\hspace{1em}xgboost-cox & 0.012 (0.015) & 0.597 (0.032) & 1.357 & 0.002\\
+\hspace{1em}aorsf-cph & 0.007 (0.022) & 0.595 (0.027) & 0.262 & 0.023\\
+\hspace{1em}aorsf-fast & 0.007 (0.021) & 0.594 (0.026) & 0.111 & 0.022\\
+\hspace{1em}cif-standard & 0.006 (0.020) & 0.592 (0.023) & 0.293 & 1.114\\
+\hspace{1em}aorsf-net & 0.006 (0.022) & 0.591 (0.028) & 19.287 & 0.022\\
+\hspace{1em}nn-cox & -0.001 (0.023) & 0.551 (0.062) & 11.433 & 0.439\\
+\hspace{1em}cif-extension & -0.007 (0.024) & 0.576 (0.029) & 5.918 & 2.338\\
+\hspace{1em}cif-rotate & -0.016 (0.026) & 0.579 (0.031) & 7.022 & 1.987\\
+\hspace{1em}rsf-standard & -0.028 (0.033) & 0.576 (0.026) & 0.833 & 0.086\\
+\hspace{1em}xgboost-aft & -0.897 (0.328) & 0.581 (0.037) & 6.337 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-standard & 0.127 (0.013) & 0.748 (0.013) & 0.874 & 2.321\\
-\hspace{1em}aorsf-net & 0.127 (0.018) & 0.745 (0.013) & 40.051 & 0.039\\
-\hspace{1em}obliqueRSF-net & 0.125 (0.012) & 0.746 (0.013) & 329.638 & 6.966\\
-\hspace{1em}rsf-standard & 0.124 (0.024) & 0.745 (0.018) & 1.269 & 0.116\\
-\hspace{1em}aorsf-cph & 0.121 (0.024) & 0.738 (0.016) & 0.440 & 0.038\\
-\hspace{1em}aorsf-fast & 0.120 (0.023) & 0.737 (0.017) & 0.180 & 0.038\\
-\hspace{1em}cif-extension & 0.120 (0.013) & 0.751 (0.015) & 8.690 & 3.473\\
-\hspace{1em}aorsf-random & 0.112 (0.020) & 0.732 (0.020) & 1.244 & 0.036\\
-\hspace{1em}cif-rotate & 0.107 (0.020) & 0.731 (0.012) & 11.358 & 2.827\\
-\hspace{1em}ranger-extratrees & 0.102 (0.011) & 0.750 (0.021) & 0.472 & 0.131\\
-\hspace{1em}xgboost-cox & 0.084 (0.012) & 0.733 (0.016) & 2.844 & 0.004\\
-\hspace{1em}glmnet-cox & 0.080 (0.020) & 0.724 (0.021) & 0.116 & 0.002\\
-\hspace{1em}nn-cox & -0.003 (0.003) & 0.499 (0.018) & 11.168 & 1.086\\
-\hspace{1em}xgboost-aft & -1.13 (0.163) & 0.734 (0.017) & 11.815 & 0.006\\
+\hspace{1em}obliqueRSF-net & 0.122 (0.015) & 0.744 (0.017) & 313.230 & 6.842\\
+\hspace{1em}cif-standard & 0.121 (0.020) & 0.741 (0.020) & 0.426 & 1.769\\
+\hspace{1em}rsf-standard & 0.118 (0.024) & 0.735 (0.020) & 1.394 & 0.116\\
+\hspace{1em}aorsf-cph & 0.117 (0.026) & 0.734 (0.018) & 0.407 & 0.038\\
+\hspace{1em}aorsf-fast & 0.114 (0.025) & 0.731 (0.017) & 0.171 & 0.039\\
+\hspace{1em}cif-extension & 0.113 (0.018) & 0.741 (0.020) & 8.106 & 3.385\\
+\hspace{1em}aorsf-net & 0.109 (0.058) & 0.732 (0.036) & 37.488 & 0.038\\
+\hspace{1em}cif-rotate & 0.107 (0.025) & 0.729 (0.018) & 10.819 & 2.645\\
+\hspace{1em}aorsf-random & 0.103 (0.025) & 0.722 (0.026) & 0.786 & 0.036\\
+\hspace{1em}ranger-extratrees & 0.094 (0.019) & 0.736 (0.025) & 0.051 & 0.136\\
+\hspace{1em}glmnet-cox & 0.089 (0.018) & 0.726 (0.021) & 0.098 & 0.002\\
+\hspace{1em}xgboost-cox & 0.080 (0.017) & 0.729 (0.018) & 2.465 & 0.003\\
+\hspace{1em}nn-cox & -0.003 (0.005) & 0.524 (0.052) & 11.570 & 0.838\\
+\hspace{1em}xgboost-aft & -1.10 (0.165) & 0.728 (0.022) & 10.557 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.073 (0.016) & 0.745 (0.034) & 0.167 & 0.038\\
-\hspace{1em}aorsf-net & 0.068 (0.016) & 0.739 (0.036) & 28.026 & 0.041\\
-\hspace{1em}aorsf-cph & 0.068 (0.016) & 0.738 (0.037) & 0.399 & 0.037\\
-\hspace{1em}obliqueRSF-net & 0.064 (0.013) & 0.738 (0.029) & 225.137 & 10.657\\
-\hspace{1em}xgboost-cox & 0.059 (0.018) & 0.741 (0.029) & 3.546 & 0.003\\
-\hspace{1em}cif-standard & 0.056 (0.012) & 0.727 (0.028) & 1.879 & 3.647\\
-\hspace{1em}glmnet-cox & 0.055 (0.047) & 0.700 (0.116) & 0.939 & 0.003\\
-\hspace{1em}cif-rotate & 0.055 (0.019) & 0.709 (0.037) & 35.679 & 5.129\\
-\hspace{1em}cif-extension & 0.052 (0.011) & 0.725 (0.037) & 13.726 & 5.891\\
-\hspace{1em}ranger-extratrees & 0.051 (0.011) & 0.732 (0.029) & 0.495 & 0.188\\
-\hspace{1em}rsf-standard & 0.038 (0.026) & 0.702 (0.037) & 0.592 & 0.059\\
-\hspace{1em}aorsf-random & 0.028 (0.006) & 0.676 (0.023) & 0.933 & 0.040\\
-\hspace{1em}nn-cox & 0.007 (0.017) & 0.609 (0.085) & 10.911 & 0.533\\
-\hspace{1em}xgboost-aft & -6.16 (1.21) & 0.727 (0.031) & 12.980 & 0.007\\
+\hspace{1em}aorsf-fast & 0.078 (0.017) & 0.751 (0.026) & 0.160 & 0.037\\
+\hspace{1em}aorsf-net & 0.076 (0.017) & 0.748 (0.027) & 27.393 & 0.039\\
+\hspace{1em}aorsf-cph & 0.073 (0.019) & 0.746 (0.029) & 0.379 & 0.037\\
+\hspace{1em}glmnet-cox & 0.067 (0.042) & 0.719 (0.087) & 0.498 & 0.003\\
+\hspace{1em}obliqueRSF-net & 0.064 (0.013) & 0.744 (0.023) & 221.509 & 11.260\\
+\hspace{1em}cif-rotate & 0.060 (0.014) & 0.720 (0.025) & 34.884 & 5.270\\
+\hspace{1em}cif-standard & 0.059 (0.014) & 0.741 (0.023) & 0.880 & 3.606\\
+\hspace{1em}ranger-extratrees & 0.054 (0.013) & 0.741 (0.030) & 0.091 & 0.178\\
+\hspace{1em}cif-extension & 0.052 (0.012) & 0.730 (0.024) & 13.387 & 5.416\\
+\hspace{1em}rsf-standard & 0.049 (0.022) & 0.708 (0.027) & 0.169 & 0.058\\
+\hspace{1em}xgboost-cox & 0.041 (0.045) & 0.745 (0.018) & 3.691 & 0.003\\
+\hspace{1em}aorsf-random & 0.033 (0.013) & 0.700 (0.029) & 0.499 & 0.039\\
+\hspace{1em}nn-cox & 0.006 (0.017) & 0.622 (0.088) & 10.440 & 0.558\\
+\hspace{1em}xgboost-aft & -5.08 (1.03) & 0.734 (0.021) & 10.919 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.085 (0.023) & 0.734 (0.033) & 0.707 & 0.056\\
-\hspace{1em}aorsf-fast & 0.083 (0.022) & 0.734 (0.032) & 0.254 & 0.056\\
-\hspace{1em}aorsf-net & 0.082 (0.024) & 0.729 (0.032) & 60.358 & 0.059\\
-\hspace{1em}obliqueRSF-net & 0.075 (0.018) & 0.726 (0.033) & 388.086 & 9.114\\
-\hspace{1em}ranger-extratrees & 0.073 (0.017) & 0.725 (0.032) & 0.464 & 0.188\\
-\hspace{1em}cif-standard & 0.071 (0.016) & 0.718 (0.032) & 1.643 & 3.240\\
-\hspace{1em}cif-rotate & 0.069 (0.033) & 0.710 (0.044) & 43.469 & 5.424\\
-\hspace{1em}glmnet-cox & 0.069 (0.021) & 0.710 (0.032) & 0.693 & 0.003\\
-\hspace{1em}cif-extension & 0.064 (0.014) & 0.719 (0.027) & 15.673 & 5.961\\
-\hspace{1em}rsf-standard & 0.057 (0.028) & 0.699 (0.038) & 2.421 & 0.130\\
-\hspace{1em}aorsf-random & 0.053 (0.015) & 0.693 (0.034) & 1.234 & 0.053\\
-\hspace{1em}nn-cox & 0.049 (0.029) & 0.710 (0.022) & 13.646 & 0.669\\
-\hspace{1em}xgboost-cox & 0.043 (0.018) & 0.705 (0.039) & 2.793 & 0.003\\
-\hspace{1em}xgboost-aft & -2.37 (0.383) & 0.702 (0.041) & 14.879 & 0.007\\
+\hspace{1em}aorsf-fast & 0.080 (0.020) & 0.722 (0.027) & 0.241 & 0.053\\
+\hspace{1em}aorsf-cph & 0.080 (0.019) & 0.721 (0.025) & 0.691 & 0.054\\
+\hspace{1em}obliqueRSF-net & 0.073 (0.011) & 0.720 (0.025) & 382.054 & 9.235\\
+\hspace{1em}ranger-extratrees & 0.072 (0.010) & 0.721 (0.023) & 0.107 & 0.191\\
+\hspace{1em}aorsf-net & 0.072 (0.043) & 0.716 (0.037) & 53.293 & 0.057\\
+\hspace{1em}cif-standard & 0.069 (0.011) & 0.715 (0.025) & 0.802 & 3.237\\
+\hspace{1em}cif-rotate & 0.066 (0.020) & 0.706 (0.031) & 41.812 & 5.179\\
+\hspace{1em}cif-extension & 0.064 (0.009) & 0.715 (0.023) & 14.460 & 5.513\\
+\hspace{1em}glmnet-cox & 0.059 (0.021) & 0.700 (0.026) & 0.453 & 0.003\\
+\hspace{1em}rsf-standard & 0.056 (0.023) & 0.693 (0.027) & 1.503 & 0.119\\
+\hspace{1em}aorsf-random & 0.049 (0.010) & 0.683 (0.024) & 0.914 & 0.053\\
+\hspace{1em}nn-cox & 0.044 (0.027) & 0.694 (0.041) & 12.746 & 0.589\\
+\hspace{1em}xgboost-cox & 0.038 (0.018) & 0.698 (0.028) & 2.920 & 0.003\\
+\hspace{1em}xgboost-aft & -2.24 (0.328) & 0.696 (0.027) & 13.125 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.055 (0.008) & 0.724 (0.018) & 158.338 & 21.084\\
-\hspace{1em}aorsf-cph & 0.054 (0.005) & 0.729 (0.018) & 3.324 & 0.231\\
-\hspace{1em}aorsf-fast & 0.053 (0.006) & 0.729 (0.020) & 1.271 & 0.225\\
-\hspace{1em}aorsf-net & 0.052 (0.005) & 0.725 (0.018) & 131.969 & 0.232\\
-\hspace{1em}rsf-standard & 0.052 (0.006) & 0.727 (0.014) & 2.874 & 0.985\\
-\hspace{1em}cif-standard & 0.049 (0.005) & 0.729 (0.014) & 10.011 & 35.980\\
-\hspace{1em}obliqueRSF-net & 0.049 (0.006) & 0.724 (0.018) & 372.165 & 72.309\\
-\hspace{1em}ranger-extratrees & 0.045 (0.006) & 0.725 (0.013) & 5.621 & 3.271\\
-\hspace{1em}glmnet-cox & 0.037 (0.003) & 0.703 (0.017) & 1.141 & 0.004\\
-\hspace{1em}cif-extension & 0.035 (0.004) & 0.725 (0.016) & 50.375 & 18.419\\
-\hspace{1em}xgboost-cox & 0.030 (0.008) & 0.708 (0.023) & 3.993 & 0.006\\
-\hspace{1em}aorsf-random & 0.027 (0.003) & 0.680 (0.014) & 2.518 & 0.218\\
-\hspace{1em}nn-cox & 0.019 (0.018) & 0.637 (0.063) & 16.991 & 10.575\\
-\hspace{1em}xgboost-aft & -4.47 (0.512) & 0.722 (0.009) & 14.335 & 0.007\\
+\hspace{1em}cif-rotate & 0.055 (0.010) & 0.729 (0.017) & 158.010 & 21.041\\
+\hspace{1em}aorsf-net & 0.052 (0.006) & 0.730 (0.013) & 126.426 & 0.231\\
+\hspace{1em}aorsf-fast & 0.051 (0.007) & 0.733 (0.015) & 0.875 & 0.222\\
+\hspace{1em}aorsf-cph & 0.051 (0.006) & 0.732 (0.014) & 3.009 & 0.226\\
+\hspace{1em}cif-standard & 0.049 (0.007) & 0.731 (0.014) & 10.227 & 36.786\\
+\hspace{1em}obliqueRSF-net & 0.048 (0.006) & 0.728 (0.015) & 365.007 & 70.588\\
+\hspace{1em}rsf-standard & 0.047 (0.010) & 0.725 (0.013) & 2.462 & 0.933\\
+\hspace{1em}ranger-extratrees & 0.046 (0.007) & 0.729 (0.014) & 5.510 & 3.387\\
+\hspace{1em}glmnet-cox & 0.036 (0.006) & 0.709 (0.016) & 0.969 & 0.005\\
+\hspace{1em}cif-extension & 0.035 (0.004) & 0.725 (0.018) & 49.685 & 18.172\\
+\hspace{1em}xgboost-cox & 0.030 (0.007) & 0.715 (0.019) & 3.479 & 0.005\\
+\hspace{1em}aorsf-random & 0.028 (0.003) & 0.689 (0.013) & 2.461 & 0.218\\
+\hspace{1em}nn-cox & 0.021 (0.013) & 0.669 (0.043) & 15.828 & 9.990\\
+\hspace{1em}xgboost-aft & -4.46 (0.518) & 0.723 (0.013) & 14.471 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.064 (0.010) & 0.811 (0.007) & 1.254 & 0.358\\
-\hspace{1em}aorsf-net & 0.063 (0.010) & 0.807 (0.009) & 181.663 & 0.387\\
-\hspace{1em}obliqueRSF-net & 0.063 (0.007) & 0.809 (0.005) & 511.374 & 266.957\\
-\hspace{1em}aorsf-cph & 0.061 (0.011) & 0.804 (0.009) & 5.063 & 0.365\\
-\hspace{1em}cif-rotate & 0.059 (0.006) & 0.803 (0.009) & 305.481 & 38.499\\
-\hspace{1em}cif-standard & 0.059 (0.006) & 0.804 (0.008) & 22.778 & 96.623\\
-\hspace{1em}rsf-standard & 0.057 (0.012) & 0.794 (0.012) & 2.696 & 0.440\\
-\hspace{1em}ranger-extratrees & 0.048 (0.004) & 0.798 (0.009) & 5.753 & 6.995\\
-\hspace{1em}cif-extension & 0.047 (0.004) & 0.804 (0.010) & 96.367 & 26.939\\
-\hspace{1em}glmnet-cox & 0.039 (0.018) & 0.773 (0.009) & 5.042 & 0.007\\
-\hspace{1em}aorsf-random & 0.032 (0.005) & 0.747 (0.014) & 3.235 & 0.419\\
-\hspace{1em}nn-cox & 0.032 (0.017) & 0.767 (0.025) & 14.750 & 18.081\\
-\hspace{1em}xgboost-cox & 0.012 (0.024) & 0.803 (0.008) & 4.399 & 0.008\\
-\hspace{1em}xgboost-aft & -9.98 (1.26) & 0.804 (0.009) & 16.414 & 0.009\\
+\hspace{1em}aorsf-fast & 0.064 (0.010) & 0.807 (0.010) & 1.254 & 0.359\\
+\hspace{1em}aorsf-net & 0.063 (0.010) & 0.804 (0.010) & 174.770 & 0.380\\
+\hspace{1em}obliqueRSF-net & 0.062 (0.008) & 0.809 (0.009) & 489.721 & 264.595\\
+\hspace{1em}aorsf-cph & 0.061 (0.010) & 0.801 (0.012) & 5.084 & 0.365\\
+\hspace{1em}cif-standard & 0.059 (0.006) & 0.803 (0.011) & 23.030 & 98.735\\
+\hspace{1em}cif-rotate & 0.058 (0.007) & 0.803 (0.010) & 290.894 & 38.516\\
+\hspace{1em}rsf-standard & 0.057 (0.012) & 0.795 (0.012) & 3.507 & 1.082\\
+\hspace{1em}ranger-extratrees & 0.047 (0.004) & 0.794 (0.010) & 7.733 & 6.984\\
+\hspace{1em}cif-extension & 0.046 (0.003) & 0.805 (0.010) & 99.785 & 30.035\\
+\hspace{1em}glmnet-cox & 0.039 (0.017) & 0.775 (0.016) & 4.983 & 0.007\\
+\hspace{1em}nn-cox & 0.034 (0.014) & 0.771 (0.018) & 16.832 & 16.923\\
+\hspace{1em}aorsf-random & 0.031 (0.005) & 0.735 (0.015) & 3.622 & 0.410\\
+\hspace{1em}xgboost-cox & 0.013 (0.020) & 0.803 (0.010) & 4.416 & 0.008\\
+\hspace{1em}xgboost-aft & -9.73 (1.00) & 0.803 (0.010) & 19.012 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.146 (0.004) & 0.790 (0.008) & 326.502 & 0.545\\
-\hspace{1em}aorsf-fast & 0.146 (0.004) & 0.791 (0.009) & 1.945 & 0.601\\
-\hspace{1em}aorsf-cph & 0.144 (0.004) & 0.790 (0.008) & 6.964 & 0.509\\
-\hspace{1em}rsf-standard & 0.143 (0.003) & 0.784 (0.008) & 4.756 & 0.479\\
-\hspace{1em}obliqueRSF-net & 0.140 (0.006) & 0.790 (0.010) & 1155.640 & 154.298\\
-\hspace{1em}nn-cox & 0.137 (0.007) & 0.785 (0.007) & 26.956 & 20.710\\
-\hspace{1em}cif-standard & 0.134 (0.006) & 0.786 (0.010) & 21.844 & 107.533\\
-\hspace{1em}cif-rotate & 0.122 (0.006) & 0.777 (0.011) & 323.806 & 37.456\\
-\hspace{1em}ranger-extratrees & 0.114 (0.005) & 0.782 (0.011) & 6.711 & 6.068\\
-\hspace{1em}glmnet-cox & 0.110 (0.023) & 0.778 (0.011) & 1.500 & 0.007\\
-\hspace{1em}cif-extension & 0.092 (0.004) & 0.779 (0.011) & 109.021 & 30.388\\
-\hspace{1em}aorsf-random & 0.071 (0.003) & 0.728 (0.010) & 5.543 & 0.549\\
-\hspace{1em}xgboost-cox & 0.061 (0.013) & 0.790 (0.008) & 8.622 & 0.010\\
-\hspace{1em}xgboost-aft & -4.55 (0.242) & 0.789 (0.008) & 20.108 & 0.009\\
+\hspace{1em}aorsf-net & 0.144 (0.008) & 0.791 (0.009) & 302.684 & 0.545\\
+\hspace{1em}aorsf-fast & 0.144 (0.008) & 0.792 (0.010) & 1.785 & 0.630\\
+\hspace{1em}aorsf-cph & 0.143 (0.007) & 0.791 (0.009) & 6.757 & 0.532\\
+\hspace{1em}rsf-standard & 0.140 (0.008) & 0.783 (0.009) & 4.567 & 0.475\\
+\hspace{1em}obliqueRSF-net & 0.139 (0.007) & 0.791 (0.010) & 1155.438 & 154.187\\
+\hspace{1em}nn-cox & 0.134 (0.012) & 0.789 (0.010) & 32.143 & 19.831\\
+\hspace{1em}cif-standard & 0.133 (0.006) & 0.788 (0.009) & 23.210 & 99.971\\
+\hspace{1em}glmnet-cox & 0.126 (0.026) & 0.788 (0.012) & 1.504 & 0.006\\
+\hspace{1em}cif-rotate & 0.126 (0.007) & 0.783 (0.010) & 318.556 & 36.862\\
+\hspace{1em}ranger-extratrees & 0.113 (0.004) & 0.784 (0.009) & 7.675 & 6.070\\
+\hspace{1em}cif-extension & 0.092 (0.003) & 0.781 (0.009) & 110.511 & 30.598\\
+\hspace{1em}aorsf-random & 0.069 (0.005) & 0.725 (0.008) & 5.706 & 0.551\\
+\hspace{1em}xgboost-cox & 0.056 (0.030) & 0.794 (0.010) & 8.559 & 0.010\\
+\hspace{1em}xgboost-aft & -4.42 (0.238) & 0.792 (0.009) & 22.063 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.112 (0.015) & 0.864 (0.019) & 1.187 & 0.323\\
-\hspace{1em}aorsf-net & 0.111 (0.015) & 0.860 (0.020) & 163.971 & 0.348\\
-\hspace{1em}aorsf-cph & 0.106 (0.014) & 0.855 (0.022) & 5.011 & 0.331\\
-\hspace{1em}rsf-standard & 0.104 (0.016) & 0.855 (0.017) & 2.703 & 1.010\\
-\hspace{1em}cif-rotate & 0.104 (0.015) & 0.869 (0.020) & 260.204 & 36.664\\
-\hspace{1em}obliqueRSF-net & 0.103 (0.010) & 0.864 (0.019) & 415.985 & 339.753\\
-\hspace{1em}cif-standard & 0.097 (0.012) & 0.858 (0.019) & 31.107 & 118.751\\
-\hspace{1em}cif-extension & 0.075 (0.005) & 0.861 (0.017) & 94.308 & 30.399\\
-\hspace{1em}ranger-extratrees & 0.074 (0.008) & 0.842 (0.025) & 4.955 & 6.617\\
-\hspace{1em}nn-cox & 0.067 (0.027) & 0.824 (0.032) & 13.821 & 14.093\\
-\hspace{1em}aorsf-random & 0.062 (0.009) & 0.792 (0.023) & 2.605 & 0.376\\
-\hspace{1em}glmnet-cox & 0.055 (0.050) & 0.779 (0.157) & 3.773 & 0.007\\
-\hspace{1em}xgboost-cox & -0.010 (0.011) & 0.868 (0.015) & 6.597 & 0.022\\
-\hspace{1em}xgboost-aft & -11.1 (1.17) & 0.868 (0.018) & 19.343 & 0.009\\
+\hspace{1em}aorsf-fast & 0.114 (0.011) & 0.867 (0.012) & 1.145 & 0.317\\
+\hspace{1em}aorsf-cph & 0.109 (0.012) & 0.859 (0.014) & 4.847 & 0.330\\
+\hspace{1em}rsf-standard & 0.109 (0.012) & 0.857 (0.011) & 3.064 & 1.083\\
+\hspace{1em}obliqueRSF-net & 0.106 (0.008) & 0.869 (0.012) & 402.559 & 332.725\\
+\hspace{1em}cif-rotate & 0.105 (0.010) & 0.870 (0.012) & 262.282 & 37.634\\
+\hspace{1em}cif-standard & 0.101 (0.009) & 0.864 (0.013) & 24.266 & 98.478\\
+\hspace{1em}aorsf-net & 0.098 (0.071) & 0.849 (0.068) & 152.112 & 0.342\\
+\hspace{1em}cif-extension & 0.076 (0.005) & 0.865 (0.011) & 94.286 & 30.425\\
+\hspace{1em}ranger-extratrees & 0.075 (0.005) & 0.848 (0.015) & 7.014 & 6.801\\
+\hspace{1em}nn-cox & 0.072 (0.027) & 0.828 (0.023) & 15.582 & 14.415\\
+\hspace{1em}aorsf-random & 0.063 (0.006) & 0.796 (0.015) & 2.686 & 0.368\\
+\hspace{1em}glmnet-cox & 0.047 (0.044) & 0.757 (0.153) & 3.628 & 0.007\\
+\hspace{1em}xgboost-cox & -0.011 (0.020) & 0.871 (0.010) & 6.431 & 0.009\\
+\hspace{1em}xgboost-aft & -11.1 (1.34) & 0.871 (0.012) & 20.098 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.027 (0.003) & 0.769 (0.014) & 278.786 & 36.095\\
-\hspace{1em}aorsf-fast & 0.027 (0.002) & 0.769 (0.015) & 1.101 & 0.318\\
-\hspace{1em}obliqueRSF-net & 0.027 (0.002) & 0.768 (0.014) & 370.155 & 296.119\\
-\hspace{1em}glmnet-cox & 0.026 (0.006) & 0.762 (0.014) & 2.280 & 0.006\\
-\hspace{1em}cif-standard & 0.025 (0.002) & 0.761 (0.016) & 23.502 & 100.401\\
-\hspace{1em}aorsf-cph & 0.025 (0.003) & 0.760 (0.015) & 4.632 & 0.326\\
-\hspace{1em}aorsf-net & 0.024 (0.001) & 0.759 (0.013) & 140.310 & 0.334\\
-\hspace{1em}cif-extension & 0.022 (0.001) & 0.773 (0.016) & 93.321 & 29.177\\
-\hspace{1em}ranger-extratrees & 0.022 (0.000) & 0.757 (0.015) & 6.228 & 6.670\\
-\hspace{1em}rsf-standard & 0.021 (0.005) & 0.753 (0.018) & 2.551 & 1.012\\
-\hspace{1em}xgboost-cox & 0.020 (0.005) & 0.769 (0.011) & 3.475 & 0.008\\
-\hspace{1em}nn-cox & 0.019 (0.010) & 0.740 (0.053) & 17.371 & 20.141\\
-\hspace{1em}aorsf-random & 0.014 (0.002) & 0.717 (0.020) & 2.494 & 0.346\\
-\hspace{1em}xgboost-aft & -14.1 (1.04) & 0.773 (0.017) & 17.138 & 0.010\\
+\hspace{1em}cif-rotate & 0.024 (0.004) & 0.760 (0.017) & 273.629 & 37.321\\
+\hspace{1em}obliqueRSF-net & 0.024 (0.004) & 0.763 (0.015) & 355.997 & 289.216\\
+\hspace{1em}cif-standard & 0.024 (0.004) & 0.758 (0.016) & 23.726 & 98.376\\
+\hspace{1em}aorsf-fast & 0.024 (0.006) & 0.761 (0.015) & 1.099 & 0.313\\
+\hspace{1em}aorsf-cph & 0.023 (0.005) & 0.755 (0.016) & 4.501 & 0.322\\
+\hspace{1em}ranger-extratrees & 0.021 (0.003) & 0.756 (0.015) & 7.037 & 6.789\\
+\hspace{1em}cif-extension & 0.021 (0.002) & 0.766 (0.017) & 95.086 & 29.190\\
+\hspace{1em}glmnet-cox & 0.021 (0.010) & 0.763 (0.017) & 3.726 & 0.007\\
+\hspace{1em}rsf-standard & 0.018 (0.009) & 0.742 (0.018) & 3.127 & 1.058\\
+\hspace{1em}aorsf-net & 0.017 (0.027) & 0.746 (0.045) & 138.918 & 0.330\\
+\hspace{1em}nn-cox & 0.013 (0.009) & 0.721 (0.050) & 17.998 & 20.421\\
+\hspace{1em}aorsf-random & 0.013 (0.003) & 0.710 (0.023) & 2.582 & 0.338\\
+\hspace{1em}xgboost-cox & 0.000 (0.024) & 0.760 (0.019) & 4.044 & 0.008\\
+\hspace{1em}xgboost-aft & -13.7 (1.50) & 0.762 (0.016) & 18.133 & 0.010\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.159 (0.027) & 0.745 (0.020) & 15.390 & 4.940\\
-\hspace{1em}aorsf-cph & 0.158 (0.018) & 0.743 (0.012) & 1.221 & 0.089\\
-\hspace{1em}aorsf-fast & 0.157 (0.020) & 0.743 (0.013) & 0.431 & 0.091\\
-\hspace{1em}obliqueRSF-net & 0.155 (0.018) & 0.743 (0.016) & 283.644 & 15.600\\
-\hspace{1em}aorsf-net & 0.154 (0.020) & 0.741 (0.013) & 130.364 & 0.091\\
-\hspace{1em}rsf-standard & 0.152 (0.022) & 0.739 (0.013) & 1.808 & 0.130\\
-\hspace{1em}cif-standard & 0.151 (0.021) & 0.739 (0.015) & 2.033 & 6.003\\
-\hspace{1em}aorsf-random & 0.147 (0.017) & 0.736 (0.015) & 2.273 & 0.084\\
-\hspace{1em}cif-extension & 0.143 (0.012) & 0.747 (0.017) & 10.521 & 4.415\\
-\hspace{1em}glmnet-cox & 0.131 (0.024) & 0.725 (0.015) & 0.116 & 0.003\\
-\hspace{1em}xgboost-cox & 0.125 (0.016) & 0.735 (0.015) & 5.066 & 0.004\\
-\hspace{1em}ranger-extratrees & 0.116 (0.006) & 0.744 (0.014) & 0.068 & 0.556\\
-\hspace{1em}nn-cox & 0.050 (0.044) & 0.641 (0.097) & 17.607 & 1.128\\
-\hspace{1em}xgboost-aft & -0.820 (0.130) & 0.737 (0.015) & 12.403 & 0.006\\
+\hspace{1em}cif-rotate & 0.157 (0.018) & 0.743 (0.014) & 15.346 & 4.755\\
+\hspace{1em}aorsf-cph & 0.155 (0.015) & 0.741 (0.010) & 1.157 & 0.087\\
+\hspace{1em}aorsf-fast & 0.154 (0.015) & 0.741 (0.009) & 0.393 & 0.087\\
+\hspace{1em}obliqueRSF-net & 0.153 (0.012) & 0.742 (0.010) & 229.434 & 12.810\\
+\hspace{1em}aorsf-net & 0.153 (0.014) & 0.739 (0.009) & 88.786 & 0.087\\
+\hspace{1em}cif-standard & 0.149 (0.013) & 0.737 (0.010) & 0.998 & 5.743\\
+\hspace{1em}rsf-standard & 0.147 (0.016) & 0.735 (0.010) & 2.002 & 0.201\\
+\hspace{1em}aorsf-random & 0.144 (0.013) & 0.733 (0.011) & 1.762 & 0.082\\
+\hspace{1em}cif-extension & 0.142 (0.009) & 0.745 (0.012) & 10.648 & 4.681\\
+\hspace{1em}glmnet-cox & 0.136 (0.020) & 0.726 (0.014) & 0.117 & 0.003\\
+\hspace{1em}xgboost-cox & 0.121 (0.011) & 0.732 (0.011) & 3.801 & 0.003\\
+\hspace{1em}ranger-extratrees & 0.115 (0.004) & 0.742 (0.011) & 0.058 & 0.198\\
+\hspace{1em}nn-cox & 0.031 (0.044) & 0.612 (0.102) & 15.825 & 0.684\\
+\hspace{1em}xgboost-aft & -0.868 (0.152) & 0.732 (0.012) & 12.704 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.014 (0.010) & 0.668 (0.033) & 0.107 & 0.002\\
-\hspace{1em}xgboost-cox & 0.011 (0.006) & 0.638 (0.042) & 2.752 & 0.004\\
-\hspace{1em}cif-extension & 0.011 (0.008) & 0.633 (0.040) & 8.797 & 4.210\\
-\hspace{1em}aorsf-cph & 0.010 (0.011) & 0.635 (0.045) & 0.610 & 0.043\\
-\hspace{1em}aorsf-fast & 0.010 (0.010) & 0.635 (0.048) & 0.211 & 0.042\\
-\hspace{1em}obliqueRSF-net & 0.010 (0.008) & 0.629 (0.041) & 45.749 & 17.208\\
-\hspace{1em}aorsf-net & 0.008 (0.010) & 0.642 (0.048) & 23.207 & 0.044\\
-\hspace{1em}aorsf-random & 0.008 (0.011) & 0.627 (0.039) & 0.944 & 0.042\\
-\hspace{1em}cif-standard & 0.007 (0.007) & 0.625 (0.044) & 1.989 & 6.200\\
-\hspace{1em}ranger-extratrees & 0.007 (0.009) & 0.646 (0.049) & 0.073 & 0.617\\
-\hspace{1em}rsf-standard & -0.002 (0.009) & 0.621 (0.045) & 0.632 & 0.066\\
-\hspace{1em}nn-cox & -0.005 (0.009) & 0.506 (0.025) & 10.675 & 1.079\\
-\hspace{1em}cif-rotate & -0.024 (0.011) & 0.548 (0.035) & 13.366 & 4.579\\
-\hspace{1em}xgboost-aft & -5.68 (1.27) & 0.622 (0.043) & 11.083 & 0.006\\
+\hspace{1em}glmnet-cox & 0.016 (0.012) & 0.654 (0.050) & 0.104 & 0.002\\
+\hspace{1em}aorsf-cph & 0.011 (0.012) & 0.644 (0.034) & 0.592 & 0.041\\
+\hspace{1em}aorsf-fast & 0.010 (0.013) & 0.641 (0.034) & 0.193 & 0.042\\
+\hspace{1em}ranger-extratrees & 0.008 (0.007) & 0.641 (0.033) & 0.050 & 0.177\\
+\hspace{1em}cif-extension & 0.008 (0.009) & 0.626 (0.026) & 8.936 & 4.415\\
+\hspace{1em}aorsf-random & 0.007 (0.013) & 0.633 (0.034) & 0.519 & 0.041\\
+\hspace{1em}aorsf-net & 0.007 (0.013) & 0.641 (0.032) & 22.912 & 0.042\\
+\hspace{1em}cif-standard & 0.006 (0.009) & 0.627 (0.029) & 1.072 & 6.223\\
+\hspace{1em}xgboost-cox & 0.005 (0.017) & 0.641 (0.036) & 1.798 & 0.003\\
+\hspace{1em}obliqueRSF-net & 0.002 (0.023) & 0.623 (0.040) & 42.157 & 16.489\\
+\hspace{1em}nn-cox & -0.004 (0.006) & 0.502 (0.052) & 10.457 & 0.704\\
+\hspace{1em}rsf-standard & -0.010 (0.016) & 0.615 (0.030) & 0.733 & 0.075\\
+\hspace{1em}cif-rotate & -0.025 (0.023) & 0.550 (0.032) & 12.854 & 4.638\\
+\hspace{1em}xgboost-aft & -5.63 (1.08) & 0.628 (0.039) & 11.106 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.641 (0.024) & 0.944 (0.008) & 19.336 & 3.407\\
-\hspace{1em}glmnet-cox & 0.617 (0.022) & 0.941 (0.009) & 0.199 & 0.004\\
-\hspace{1em}aorsf-net & 0.541 (0.033) & 0.930 (0.010) & 51.438 & 0.044\\
-\hspace{1em}aorsf-cph & 0.531 (0.024) & 0.928 (0.010) & 0.773 & 0.044\\
-\hspace{1em}xgboost-cox & 0.529 (0.023) & 0.932 (0.011) & 12.809 & 0.004\\
-\hspace{1em}rsf-standard & 0.529 (0.027) & 0.926 (0.010) & 1.049 & 0.102\\
-\hspace{1em}aorsf-fast & 0.522 (0.028) & 0.924 (0.012) & 0.215 & 0.042\\
-\hspace{1em}cif-standard & 0.478 (0.029) & 0.904 (0.016) & 0.717 & 1.313\\
-\hspace{1em}cif-extension & 0.451 (0.035) & 0.920 (0.013) & 8.990 & 4.395\\
-\hspace{1em}nn-cox & 0.450 (0.057) & 0.877 (0.031) & 16.406 & 1.226\\
-\hspace{1em}ranger-extratrees & 0.433 (0.025) & 0.900 (0.021) & 0.053 & 0.530\\
-\hspace{1em}obliqueRSF-net & 0.327 (0.024) & 0.911 (0.014) & 152.746 & 8.671\\
-\hspace{1em}aorsf-random & 0.304 (0.030) & 0.849 (0.019) & 1.260 & 0.040\\
-\hspace{1em}xgboost-aft & -0.418 (0.036) & 0.930 (0.008) & 28.162 & 0.007\\
+\hspace{1em}cif-rotate & 0.637 (0.023) & 0.943 (0.007) & 19.478 & 3.481\\
+\hspace{1em}glmnet-cox & 0.619 (0.032) & 0.940 (0.009) & 0.177 & 0.002\\
+\hspace{1em}aorsf-net & 0.531 (0.030) & 0.929 (0.011) & 52.072 & 0.044\\
+\hspace{1em}aorsf-cph & 0.523 (0.024) & 0.926 (0.011) & 0.785 & 0.042\\
+\hspace{1em}rsf-standard & 0.520 (0.022) & 0.923 (0.011) & 1.168 & 0.103\\
+\hspace{1em}nn-cox & 0.518 (0.065) & 0.901 (0.027) & 17.218 & 0.694\\
+\hspace{1em}aorsf-fast & 0.517 (0.028) & 0.923 (0.013) & 0.216 & 0.043\\
+\hspace{1em}xgboost-cox & 0.515 (0.028) & 0.932 (0.009) & 13.556 & 0.004\\
+\hspace{1em}cif-standard & 0.473 (0.026) & 0.902 (0.018) & 0.376 & 1.207\\
+\hspace{1em}cif-extension & 0.455 (0.025) & 0.920 (0.013) & 8.982 & 3.967\\
+\hspace{1em}ranger-extratrees & 0.432 (0.023) & 0.900 (0.019) & 0.047 & 0.108\\
+\hspace{1em}obliqueRSF-net & 0.319 (0.023) & 0.909 (0.019) & 154.491 & 9.054\\
+\hspace{1em}aorsf-random & 0.300 (0.035) & 0.850 (0.030) & 0.889 & 0.039\\
+\hspace{1em}xgboost-aft & -0.474 (0.073) & 0.928 (0.010) & 34.905 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.213 (0.008) & 0.870 (0.007) & 18.523 & 1.243\\
-\hspace{1em}aorsf-fast & 0.212 (0.009) & 0.870 (0.007) & 4.598 & 1.256\\
-\hspace{1em}aorsf-net & 0.210 (0.008) & 0.866 (0.007) & 455.013 & 1.352\\
-\hspace{1em}obliqueRSF-net & 0.206 (0.007) & 0.867 (0.006) & 1494.475 & 1092.517\\
-\hspace{1em}glmnet-cox & 0.205 (0.008) & 0.860 (0.006) & 1.744 & 0.020\\
-\hspace{1em}rsf-standard & 0.204 (0.007) & 0.859 (0.006) & 8.631 & 1.192\\
-\hspace{1em}cif-standard & 0.204 (0.005) & 0.861 (0.008) & 68.539 & 692.347\\
-\hspace{1em}cif-rotate & 0.189 (0.005) & 0.865 (0.004) & 259.835 & 60.332\\
-\hspace{1em}ranger-extratrees & 0.180 (0.004) & 0.861 (0.007) & 34.871 & 53.895\\
-\hspace{1em}cif-extension & 0.166 (0.002) & 0.866 (0.007) & 123.805 & 52.483\\
-\hspace{1em}aorsf-random & 0.142 (0.006) & 0.844 (0.007) & 10.215 & 1.365\\
-\hspace{1em}xgboost-cox & 0.018 (0.014) & 0.875 (0.006) & 9.416 & 0.018\\
-\hspace{1em}nn-cox & 0.000 (0.000) & 0.534 (0.076) & 17.526 & 110.282\\
-\hspace{1em}xgboost-aft & -7.57 (0.911) & 0.874 (0.006) & 26.533 & 0.014\\
+\hspace{1em}aorsf-cph & 0.213 (0.008) & 0.869 (0.005) & 17.980 & 1.260\\
+\hspace{1em}aorsf-fast & 0.213 (0.009) & 0.870 (0.005) & 4.871 & 1.369\\
+\hspace{1em}aorsf-net & 0.211 (0.008) & 0.865 (0.006) & 452.725 & 1.292\\
+\hspace{1em}obliqueRSF-net & 0.210 (0.008) & 0.869 (0.006) & 1432.168 & 1054.002\\
+\hspace{1em}rsf-standard & 0.207 (0.009) & 0.860 (0.005) & 9.926 & 1.180\\
+\hspace{1em}glmnet-cox & 0.207 (0.010) & 0.861 (0.005) & 1.748 & 0.012\\
+\hspace{1em}cif-standard & 0.206 (0.007) & 0.864 (0.006) & 67.734 & 629.975\\
+\hspace{1em}cif-rotate & 0.191 (0.007) & 0.865 (0.005) & 263.866 & 61.085\\
+\hspace{1em}ranger-extratrees & 0.181 (0.007) & 0.861 (0.005) & 37.518 & 97.910\\
+\hspace{1em}cif-extension & 0.167 (0.003) & 0.867 (0.006) & 125.152 & 53.729\\
+\hspace{1em}aorsf-random & 0.141 (0.007) & 0.839 (0.007) & 9.722 & 1.365\\
+\hspace{1em}xgboost-cox & 0.020 (0.015) & 0.877 (0.005) & 9.143 & 0.018\\
+\hspace{1em}nn-cox & 0.000 (0.000) & 0.558 (0.096) & 22.004 & 120.407\\
+\hspace{1em}xgboost-aft & -7.55 (0.727) & 0.875 (0.005) & 29.714 & 0.014\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.429 (0.021) & 0.907 (0.026) & 0.084 & 0.019\\
-\hspace{1em}aorsf-cph & 0.419 (0.022) & 0.905 (0.025) & 0.179 & 0.019\\
-\hspace{1em}aorsf-net & 0.412 (0.026) & 0.903 (0.027) & 14.909 & 0.020\\
-\hspace{1em}cif-rotate & 0.403 (0.047) & 0.896 (0.028) & 10.236 & 2.197\\
-\hspace{1em}rsf-standard & 0.388 (0.017) & 0.889 (0.025) & 0.166 & 0.054\\
-\hspace{1em}obliqueRSF-net & 0.372 (0.033) & 0.905 (0.027) & 108.343 & 1.921\\
-\hspace{1em}aorsf-random & 0.357 (0.022) & 0.895 (0.026) & 0.293 & 0.019\\
-\hspace{1em}glmnet-cox & 0.350 (0.066) & 0.893 (0.030) & 0.119 & 0.002\\
-\hspace{1em}cif-standard & 0.350 (0.034) & 0.901 (0.031) & 0.203 & 0.723\\
-\hspace{1em}cif-extension & 0.348 (0.033) & 0.901 (0.026) & 6.420 & 2.375\\
-\hspace{1em}ranger-extratrees & 0.280 (0.019) & 0.898 (0.028) & 0.040 & 0.040\\
-\hspace{1em}xgboost-cox & 0.263 (0.154) & 0.881 (0.040) & 4.705 & 0.003\\
-\hspace{1em}nn-cox & -0.016 (0.010) & 0.618 (0.167) & 11.658 & 0.213\\
-\hspace{1em}xgboost-aft & -0.926 (0.298) & 0.886 (0.030) & 9.824 & 0.006\\
+\hspace{1em}aorsf-fast & 0.425 (0.029) & 0.905 (0.021) & 0.069 & 0.018\\
+\hspace{1em}aorsf-cph & 0.414 (0.031) & 0.902 (0.021) & 0.150 & 0.018\\
+\hspace{1em}cif-rotate & 0.398 (0.037) & 0.895 (0.021) & 9.844 & 2.240\\
+\hspace{1em}rsf-standard & 0.388 (0.032) & 0.891 (0.022) & 0.093 & 0.038\\
+\hspace{1em}aorsf-net & 0.388 (0.077) & 0.895 (0.030) & 14.684 & 0.019\\
+\hspace{1em}obliqueRSF-net & 0.363 (0.029) & 0.902 (0.022) & 110.615 & 1.817\\
+\hspace{1em}aorsf-random & 0.350 (0.024) & 0.891 (0.019) & 0.283 & 0.019\\
+\hspace{1em}cif-standard & 0.345 (0.031) & 0.899 (0.024) & 0.186 & 0.363\\
+\hspace{1em}cif-extension & 0.342 (0.031) & 0.897 (0.023) & 5.197 & 2.313\\
+\hspace{1em}glmnet-cox & 0.335 (0.045) & 0.881 (0.028) & 0.115 & 0.002\\
+\hspace{1em}ranger-extratrees & 0.271 (0.025) & 0.889 (0.026) & 0.028 & 0.038\\
+\hspace{1em}xgboost-cox & 0.238 (0.105) & 0.874 (0.024) & 4.873 & 0.003\\
+\hspace{1em}nn-cox & -0.019 (0.018) & 0.548 (0.131) & 10.566 & 0.240\\
+\hspace{1em}xgboost-aft & -0.946 (0.320) & 0.879 (0.021) & 9.855 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.162 (0.008) & 0.758 (0.006) & 156.804 & 0.188\\
-\hspace{1em}obliqueRSF-net & 0.159 (0.008) & 0.757 (0.007) & 456.884 & 39.371\\
-\hspace{1em}aorsf-cph & 0.158 (0.008) & 0.755 (0.006) & 2.566 & 0.204\\
-\hspace{1em}aorsf-fast & 0.157 (0.009) & 0.755 (0.007) & 0.833 & 0.209\\
-\hspace{1em}cif-standard & 0.156 (0.008) & 0.755 (0.008) & 5.193 & 22.555\\
-\hspace{1em}rsf-standard & 0.154 (0.008) & 0.752 (0.005) & 2.888 & 0.287\\
-\hspace{1em}aorsf-random & 0.150 (0.006) & 0.750 (0.009) & 3.355 & 0.184\\
-\hspace{1em}cif-rotate & 0.149 (0.012) & 0.752 (0.012) & 34.118 & 8.552\\
-\hspace{1em}ranger-extratrees & 0.137 (0.002) & 0.745 (0.007) & 2.515 & 2.445\\
-\hspace{1em}xgboost-cox & 0.130 (0.003) & 0.749 (0.007) & 3.697 & 0.005\\
-\hspace{1em}cif-extension & 0.129 (0.005) & 0.748 (0.009) & 21.984 & 8.630\\
-\hspace{1em}glmnet-cox & 0.118 (0.009) & 0.731 (0.010) & 0.579 & 0.004\\
-\hspace{1em}nn-cox & -0.055 (0.122) & 0.478 (0.047) & 15.711 & 7.097\\
-\hspace{1em}xgboost-aft & -1.32 (0.146) & 0.756 (0.007) & 13.994 & 0.007\\
+\hspace{1em}aorsf-net & 0.165 (0.012) & 0.761 (0.009) & 156.800 & 0.190\\
+\hspace{1em}obliqueRSF-net & 0.163 (0.010) & 0.760 (0.009) & 452.125 & 37.754\\
+\hspace{1em}aorsf-cph & 0.162 (0.012) & 0.758 (0.010) & 2.537 & 0.198\\
+\hspace{1em}aorsf-fast & 0.160 (0.013) & 0.756 (0.009) & 0.796 & 0.198\\
+\hspace{1em}cif-standard & 0.159 (0.011) & 0.759 (0.009) & 4.692 & 22.441\\
+\hspace{1em}rsf-standard & 0.158 (0.013) & 0.755 (0.008) & 2.703 & 0.781\\
+\hspace{1em}aorsf-random & 0.153 (0.010) & 0.752 (0.010) & 2.959 & 0.184\\
+\hspace{1em}cif-rotate & 0.148 (0.012) & 0.752 (0.012) & 34.158 & 8.476\\
+\hspace{1em}ranger-extratrees & 0.139 (0.005) & 0.749 (0.009) & 2.888 & 2.552\\
+\hspace{1em}xgboost-cox & 0.132 (0.013) & 0.754 (0.009) & 3.742 & 0.004\\
+\hspace{1em}cif-extension & 0.130 (0.005) & 0.751 (0.009) & 22.061 & 8.711\\
+\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.731 (0.010) & 0.219 & 0.004\\
+\hspace{1em}nn-cox & -0.036 (0.096) & 0.515 (0.044) & 15.998 & 8.140\\
+\hspace{1em}xgboost-aft & -1.37 (0.131) & 0.761 (0.008) & 14.219 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.145 (0.012) & 0.734 (0.013) & 533.837 & 36.957\\
-\hspace{1em}aorsf-net & 0.142 (0.011) & 0.733 (0.012) & 177.250 & 0.198\\
-\hspace{1em}aorsf-cph & 0.140 (0.010) & 0.731 (0.011) & 2.818 & 0.217\\
-\hspace{1em}aorsf-fast & 0.139 (0.007) & 0.730 (0.010) & 0.860 & 0.212\\
-\hspace{1em}cif-standard & 0.139 (0.012) & 0.731 (0.012) & 4.713 & 22.975\\
-\hspace{1em}aorsf-random & 0.136 (0.010) & 0.728 (0.010) & 3.723 & 0.193\\
-\hspace{1em}rsf-standard & 0.134 (0.007) & 0.729 (0.009) & 4.065 & 0.284\\
-\hspace{1em}ranger-extratrees & 0.132 (0.009) & 0.731 (0.013) & 2.354 & 3.657\\
-\hspace{1em}cif-rotate & 0.131 (0.010) & 0.724 (0.011) & 38.071 & 9.418\\
-\hspace{1em}cif-extension & 0.117 (0.008) & 0.729 (0.012) & 22.799 & 8.526\\
-\hspace{1em}glmnet-cox & 0.117 (0.006) & 0.724 (0.013) & 0.622 & 0.004\\
-\hspace{1em}xgboost-cox & 0.111 (0.005) & 0.726 (0.014) & 4.572 & 0.005\\
-\hspace{1em}nn-cox & -0.001 (0.001) & 0.500 (0.000) & 20.913 & 11.146\\
-\hspace{1em}xgboost-aft & -1.00 (0.143) & 0.729 (0.012) & 14.752 & 0.006\\
+\hspace{1em}obliqueRSF-net & 0.148 (0.011) & 0.736 (0.010) & 534.578 & 39.093\\
+\hspace{1em}aorsf-net & 0.146 (0.013) & 0.735 (0.010) & 162.899 & 0.193\\
+\hspace{1em}cif-standard & 0.144 (0.012) & 0.734 (0.010) & 4.570 & 22.729\\
+\hspace{1em}aorsf-cph & 0.144 (0.013) & 0.734 (0.009) & 2.769 & 0.211\\
+\hspace{1em}aorsf-fast & 0.142 (0.013) & 0.733 (0.010) & 0.869 & 0.210\\
+\hspace{1em}aorsf-random & 0.139 (0.011) & 0.730 (0.009) & 3.217 & 0.190\\
+\hspace{1em}rsf-standard & 0.138 (0.013) & 0.730 (0.009) & 2.838 & 0.633\\
+\hspace{1em}ranger-extratrees & 0.135 (0.008) & 0.734 (0.010) & 2.746 & 2.677\\
+\hspace{1em}cif-rotate & 0.130 (0.011) & 0.726 (0.010) & 36.702 & 8.773\\
+\hspace{1em}cif-extension & 0.119 (0.007) & 0.731 (0.009) & 22.630 & 8.891\\
+\hspace{1em}glmnet-cox & 0.117 (0.009) & 0.727 (0.009) & 0.224 & 0.004\\
+\hspace{1em}xgboost-cox & 0.114 (0.008) & 0.730 (0.010) & 3.367 & 0.004\\
+\hspace{1em}nn-cox & -0.012 (0.031) & 0.498 (0.056) & 18.236 & 9.861\\
+\hspace{1em}xgboost-aft & -1.05 (0.145) & 0.734 (0.010) & 14.853 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.255 (0.013) & 0.825 (0.010) & 2.479 & 0.599\\
-\hspace{1em}aorsf-cph & 0.254 (0.013) & 0.824 (0.010) & 7.005 & 0.584\\
-\hspace{1em}aorsf-net & 0.253 (0.012) & 0.822 (0.010) & 292.897 & 0.577\\
-\hspace{1em}obliqueRSF-net & 0.251 (0.011) & 0.821 (0.010) & 1112.649 & 148.434\\
-\hspace{1em}glmnet-cox & 0.250 (0.010) & 0.819 (0.009) & 0.916 & 0.006\\
-\hspace{1em}rsf-standard & 0.247 (0.014) & 0.814 (0.010) & 4.148 & 0.538\\
-\hspace{1em}ranger-extratrees & 0.247 (0.011) & 0.821 (0.009) & 7.297 & 10.711\\
-\hspace{1em}cif-standard & 0.247 (0.012) & 0.818 (0.011) & 19.302 & 120.749\\
-\hspace{1em}aorsf-random & 0.235 (0.014) & 0.817 (0.011) & 7.467 & 0.575\\
-\hspace{1em}cif-rotate & 0.229 (0.006) & 0.818 (0.008) & 63.034 & 21.236\\
-\hspace{1em}cif-extension & 0.201 (0.005) & 0.821 (0.009) & 38.570 & 21.016\\
-\hspace{1em}xgboost-cox & 0.085 (0.033) & 0.823 (0.010) & 6.025 & 0.008\\
-\hspace{1em}nn-cox & -0.002 (0.008) & 0.606 (0.114) & 21.104 & 23.211\\
-\hspace{1em}xgboost-aft & -2.84 (0.305) & 0.823 (0.010) & 17.680 & 0.009\\
+\hspace{1em}aorsf-fast & 0.250 (0.015) & 0.826 (0.008) & 2.023 & 0.596\\
+\hspace{1em}aorsf-cph & 0.250 (0.014) & 0.825 (0.008) & 6.558 & 0.594\\
+\hspace{1em}glmnet-cox & 0.247 (0.012) & 0.820 (0.007) & 0.492 & 0.006\\
+\hspace{1em}obliqueRSF-net & 0.247 (0.012) & 0.821 (0.008) & 1099.217 & 148.193\\
+\hspace{1em}aorsf-net & 0.245 (0.025) & 0.821 (0.014) & 294.157 & 0.564\\
+\hspace{1em}ranger-extratrees & 0.243 (0.010) & 0.821 (0.008) & 9.813 & 11.248\\
+\hspace{1em}cif-standard & 0.243 (0.012) & 0.818 (0.009) & 19.411 & 119.735\\
+\hspace{1em}rsf-standard & 0.242 (0.014) & 0.816 (0.009) & 4.514 & 0.563\\
+\hspace{1em}aorsf-random & 0.232 (0.012) & 0.817 (0.009) & 6.739 & 0.572\\
+\hspace{1em}cif-rotate & 0.227 (0.009) & 0.819 (0.007) & 65.161 & 21.299\\
+\hspace{1em}cif-extension & 0.202 (0.005) & 0.821 (0.008) & 39.535 & 20.315\\
+\hspace{1em}xgboost-cox & 0.091 (0.041) & 0.824 (0.008) & 5.971 & 0.008\\
+\hspace{1em}nn-cox & 0.001 (0.007) & 0.603 (0.111) & 23.138 & 25.985\\
+\hspace{1em}xgboost-aft & -2.81 (0.306) & 0.823 (0.008) & 18.228 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.071 (0.009) & 0.792 (0.008) & 14.747 & 0.014\\
-\hspace{1em}aorsf-cph & 0.067 (0.006) & 0.787 (0.009) & 9.115 & 0.938\\
-\hspace{1em}aorsf-net & 0.066 (0.006) & 0.785 (0.008) & 346.912 & 0.675\\
-\hspace{1em}aorsf-fast & 0.066 (0.005) & 0.787 (0.008) & 2.389 & 0.955\\
-\hspace{1em}obliqueRSF-net & 0.066 (0.005) & 0.786 (0.011) & 950.174 & 438.781\\
-\hspace{1em}rsf-standard & 0.061 (0.008) & 0.778 (0.015) & 3.731 & 0.592\\
-\hspace{1em}cif-standard & 0.060 (0.004) & 0.788 (0.008) & 48.930 & 187.855\\
-\hspace{1em}cif-rotate & 0.060 (0.005) & 0.783 (0.010) & 908.658 & 111.648\\
-\hspace{1em}ranger-extratrees & 0.052 (0.003) & 0.779 (0.011) & 6.309 & 18.320\\
-\hspace{1em}nn-cox & 0.039 (0.006) & 0.772 (0.015) & 18.124 & 25.781\\
-\hspace{1em}cif-extension & 0.034 (0.002) & 0.781 (0.010) & 134.710 & 41.048\\
-\hspace{1em}aorsf-random & 0.025 (0.002) & 0.731 (0.007) & 5.496 & 0.725\\
-\hspace{1em}xgboost-cox & 0.016 (0.023) & 0.792 (0.008) & 6.202 & 0.013\\
-\hspace{1em}xgboost-aft & -10.9 (0.496) & 0.787 (0.010) & 20.409 & 0.013\\
+\hspace{1em}aorsf-net & 0.070 (0.008) & 0.795 (0.012) & 349.169 & 0.675\\
+\hspace{1em}glmnet-cox & 0.070 (0.012) & 0.794 (0.010) & 13.482 & 0.011\\
+\hspace{1em}aorsf-fast & 0.069 (0.006) & 0.796 (0.010) & 2.411 & 0.605\\
+\hspace{1em}aorsf-cph & 0.069 (0.006) & 0.795 (0.011) & 9.085 & 0.617\\
+\hspace{1em}obliqueRSF-net & 0.067 (0.005) & 0.797 (0.012) & 1012.843 & 426.872\\
+\hspace{1em}rsf-standard & 0.064 (0.007) & 0.786 (0.015) & 4.506 & 0.894\\
+\hspace{1em}cif-standard & 0.061 (0.004) & 0.796 (0.011) & 51.748 & 183.859\\
+\hspace{1em}cif-rotate & 0.060 (0.005) & 0.788 (0.011) & 964.703 & 114.180\\
+\hspace{1em}ranger-extratrees & 0.054 (0.003) & 0.791 (0.013) & 7.401 & 8.262\\
+\hspace{1em}nn-cox & 0.036 (0.021) & 0.765 (0.018) & 21.029 & 28.604\\
+\hspace{1em}cif-extension & 0.034 (0.002) & 0.788 (0.011) & 123.576 & 32.717\\
+\hspace{1em}aorsf-random & 0.026 (0.003) & 0.746 (0.017) & 5.646 & 0.745\\
+\hspace{1em}xgboost-cox & 0.007 (0.017) & 0.797 (0.011) & 7.242 & 0.014\\
+\hspace{1em}xgboost-aft & -11.0 (0.929) & 0.794 (0.012) & 20.941 & 0.013\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.124 (0.009) & 0.772 (0.009) & 4.881 & 0.011\\
-\hspace{1em}aorsf-cph & 0.117 (0.007) & 0.770 (0.008) & 13.552 & 0.894\\
-\hspace{1em}aorsf-fast & 0.116 (0.007) & 0.770 (0.006) & 3.848 & 0.893\\
-\hspace{1em}obliqueRSF-net & 0.113 (0.007) & 0.768 (0.008) & 3079.665 & 272.453\\
-\hspace{1em}aorsf-net & 0.112 (0.008) & 0.768 (0.009) & 609.650 & 0.962\\
-\hspace{1em}rsf-standard & 0.109 (0.007) & 0.761 (0.007) & 5.748 & 0.707\\
-\hspace{1em}cif-standard & 0.107 (0.007) & 0.764 (0.010) & 47.859 & 194.271\\
-\hspace{1em}nn-cox & 0.100 (0.011) & 0.760 (0.012) & 32.476 & 36.267\\
-\hspace{1em}ranger-extratrees & 0.098 (0.005) & 0.757 (0.008) & 8.455 & 9.183\\
-\hspace{1em}cif-rotate & 0.092 (0.005) & 0.746 (0.007) & 1042.564 & 114.108\\
-\hspace{1em}cif-extension & 0.056 (0.002) & 0.745 (0.009) & 134.731 & 32.668\\
-\hspace{1em}aorsf-random & 0.053 (0.004) & 0.722 (0.010) & 9.084 & 0.982\\
-\hspace{1em}xgboost-cox & 0.043 (0.032) & 0.771 (0.008) & 9.075 & 0.013\\
-\hspace{1em}xgboost-aft & -4.74 (0.262) & 0.771 (0.007) & 27.585 & 0.013\\
+\hspace{1em}glmnet-cox & 0.122 (0.012) & 0.770 (0.010) & 5.077 & 0.011\\
+\hspace{1em}aorsf-cph & 0.117 (0.008) & 0.770 (0.009) & 13.329 & 1.489\\
+\hspace{1em}aorsf-fast & 0.116 (0.009) & 0.770 (0.008) & 3.671 & 1.525\\
+\hspace{1em}aorsf-net & 0.113 (0.009) & 0.768 (0.009) & 608.998 & 0.987\\
+\hspace{1em}obliqueRSF-net & 0.112 (0.007) & 0.767 (0.009) & 2613.893 & 241.525\\
+\hspace{1em}rsf-standard & 0.110 (0.007) & 0.763 (0.009) & 6.285 & 0.695\\
+\hspace{1em}cif-standard & 0.106 (0.007) & 0.764 (0.009) & 49.138 & 191.018\\
+\hspace{1em}nn-cox & 0.098 (0.010) & 0.757 (0.010) & 38.077 & 31.856\\
+\hspace{1em}ranger-extratrees & 0.096 (0.005) & 0.756 (0.009) & 9.668 & 9.128\\
+\hspace{1em}cif-rotate & 0.091 (0.006) & 0.745 (0.009) & 1091.007 & 115.077\\
+\hspace{1em}cif-extension & 0.055 (0.002) & 0.747 (0.010) & 136.050 & 33.685\\
+\hspace{1em}aorsf-random & 0.052 (0.003) & 0.719 (0.010) & 9.318 & 1.016\\
+\hspace{1em}xgboost-cox & 0.028 (0.024) & 0.772 (0.008) & 9.389 & 0.013\\
+\hspace{1em}xgboost-aft & -4.51 (0.336) & 0.771 (0.008) & 26.478 & 0.014\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.111 (0.014) & 0.737 (0.012) & 70.041 & 9.795\\
-\hspace{1em}obliqueRSF-net & 0.110 (0.012) & 0.742 (0.009) & 380.199 & 24.864\\
-\hspace{1em}glmnet-cox & 0.109 (0.009) & 0.740 (0.012) & 0.781 & 0.003\\
-\hspace{1em}aorsf-net & 0.107 (0.012) & 0.738 (0.009) & 119.093 & 0.160\\
-\hspace{1em}aorsf-cph & 0.107 (0.012) & 0.740 (0.009) & 2.608 & 0.154\\
-\hspace{1em}cif-standard & 0.107 (0.010) & 0.739 (0.009) & 4.088 & 15.774\\
-\hspace{1em}aorsf-fast & 0.104 (0.015) & 0.739 (0.009) & 1.078 & 0.152\\
-\hspace{1em}rsf-standard & 0.104 (0.012) & 0.734 (0.010) & 1.876 & 0.607\\
-\hspace{1em}xgboost-cox & 0.094 (0.006) & 0.741 (0.008) & 4.207 & 0.005\\
-\hspace{1em}cif-extension & 0.093 (0.005) & 0.741 (0.012) & 28.632 & 9.275\\
-\hspace{1em}ranger-extratrees & 0.085 (0.007) & 0.727 (0.008) & 3.426 & 1.592\\
-\hspace{1em}aorsf-random & 0.080 (0.004) & 0.724 (0.010) & 3.144 & 0.150\\
-\hspace{1em}nn-cox & 0.067 (0.018) & 0.694 (0.024) & 22.516 & 5.931\\
-\hspace{1em}xgboost-aft & -2.03 (0.087) & 0.739 (0.011) & 13.566 & 0.007\\
+\hspace{1em}obliqueRSF-net & 0.114 (0.012) & 0.747 (0.011) & 376.279 & 24.724\\
+\hspace{1em}cif-rotate & 0.113 (0.013) & 0.741 (0.010) & 70.063 & 10.454\\
+\hspace{1em}glmnet-cox & 0.113 (0.013) & 0.746 (0.011) & 0.260 & 0.003\\
+\hspace{1em}aorsf-net & 0.112 (0.014) & 0.744 (0.011) & 119.643 & 0.160\\
+\hspace{1em}aorsf-cph & 0.111 (0.014) & 0.745 (0.010) & 1.972 & 0.153\\
+\hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 3.959 & 15.682\\
+\hspace{1em}aorsf-fast & 0.110 (0.016) & 0.745 (0.010) & 0.625 & 0.153\\
+\hspace{1em}rsf-standard & 0.105 (0.012) & 0.736 (0.009) & 2.032 & 0.276\\
+\hspace{1em}cif-extension & 0.094 (0.006) & 0.745 (0.011) & 28.859 & 9.510\\
+\hspace{1em}ranger-extratrees & 0.092 (0.008) & 0.738 (0.012) & 2.893 & 1.729\\
+\hspace{1em}xgboost-cox & 0.091 (0.009) & 0.745 (0.009) & 4.478 & 0.004\\
+\hspace{1em}aorsf-random & 0.081 (0.005) & 0.732 (0.012) & 2.335 & 0.150\\
+\hspace{1em}nn-cox & 0.080 (0.024) & 0.710 (0.032) & 19.019 & 4.359\\
+\hspace{1em}xgboost-aft & -2.04 (0.178) & 0.742 (0.008) & 13.559 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.186 (0.086) & 0.789 (0.047) & 4.626 & 1.031\\
-\hspace{1em}aorsf-net & 0.180 (0.064) & 0.792 (0.036) & 10.271 & 0.012\\
-\hspace{1em}aorsf-fast & 0.177 (0.064) & 0.788 (0.042) & 0.058 & 0.011\\
-\hspace{1em}aorsf-cph & 0.175 (0.071) & 0.789 (0.044) & 0.107 & 0.013\\
-\hspace{1em}rsf-standard & 0.159 (0.068) & 0.785 (0.047) & 0.077 & 0.025\\
-\hspace{1em}cif-extension & 0.141 (0.071) & 0.777 (0.047) & 3.936 & 1.193\\
-\hspace{1em}aorsf-random & 0.134 (0.068) & 0.773 (0.042) & 0.214 & 0.012\\
-\hspace{1em}glmnet-cox & 0.133 (0.038) & 0.793 (0.022) & 0.115 & 0.002\\
-\hspace{1em}cif-standard & 0.115 (0.056) & 0.770 (0.041) & 0.117 & 0.117\\
-\hspace{1em}obliqueRSF-net & 0.110 (0.050) & 0.794 (0.025) & 59.844 & 0.634\\
-\hspace{1em}ranger-extratrees & 0.071 (0.049) & 0.762 (0.050) & 0.023 & 0.047\\
-\hspace{1em}xgboost-cox & 0.053 (0.078) & 0.728 (0.055) & 2.310 & 0.002\\
-\hspace{1em}xgboost-aft & -0.007 (0.079) & 0.759 (0.057) & 5.251 & 0.005\\
-\hspace{1em}nn-cox & -0.048 (0.046) & 0.522 (0.084) & 12.037 & 0.142\\*
+\hspace{1em}aorsf-net & 0.204 (0.044) & 0.796 (0.036) & 9.921 & 0.012\\
+\hspace{1em}aorsf-fast & 0.204 (0.044) & 0.794 (0.034) & 0.047 & 0.011\\
+\hspace{1em}aorsf-cph & 0.202 (0.046) & 0.793 (0.036) & 0.097 & 0.013\\
+\hspace{1em}cif-rotate & 0.202 (0.059) & 0.787 (0.038) & 4.285 & 1.059\\
+\hspace{1em}rsf-standard & 0.179 (0.044) & 0.787 (0.040) & 0.067 & 0.025\\
+\hspace{1em}cif-extension & 0.176 (0.044) & 0.794 (0.034) & 3.541 & 1.194\\
+\hspace{1em}glmnet-cox & 0.160 (0.030) & 0.787 (0.039) & 0.078 & 0.002\\
+\hspace{1em}aorsf-random & 0.156 (0.043) & 0.779 (0.039) & 0.209 & 0.011\\
+\hspace{1em}cif-standard & 0.131 (0.035) & 0.770 (0.036) & 0.099 & 0.119\\
+\hspace{1em}obliqueRSF-net & 0.128 (0.031) & 0.795 (0.029) & 59.944 & 0.660\\
+\hspace{1em}ranger-extratrees & 0.092 (0.033) & 0.778 (0.037) & 0.021 & 0.027\\
+\hspace{1em}xgboost-cox & 0.062 (0.077) & 0.747 (0.050) & 1.139 & 0.002\\
+\hspace{1em}xgboost-aft & -0.012 (0.141) & 0.753 (0.046) & 5.540 & 0.005\\
+\hspace{1em}nn-cox & -0.028 (0.036) & 0.525 (0.084) & 11.338 & 0.123\\*
 \end{longtable}
@@
 \endlastfoot
-Overall & Overall & 75.3 & 73.0 & 72.9 & 69.0 & 64.4 & 67.1\\
+Overall & Overall & 76.1 & 73.9 & 73.3 & 69.5 & 64.5 & 67.8\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 58.4 & 56.6 & 59.8 & 53.1 & 48.6 & 57.9\\
-\hspace{1em}45 & 500 & 64.3 & 66.4 & 53.6 & 59.6 & 53.5 & 59.4\\
-\hspace{1em}45 & 1,000 & 48.0 & 46.7 & 58.4 & 43.1 & 42.2 & 52.7\\
-\hspace{1em}45 & 2,500 & 67.3 & 54.0 & 67.3 & 59.1 & 57.2 & 59.0\\
-\hspace{1em}15 & 500 & 48.9 & 58.8 & 55.6 & 51.6 & 45.5 & 59.5\\
-\hspace{1em}15 & 1,000 & 54.9 & 49.1 & 56.4 & 45.7 & 39.9 & 53.0\\
-\hspace{1em}15 & 2,500 & 56.4 & 55.5 & 63.9 & 54.3 & 53.4 & 53.4\\
-\hspace{1em}0 & 500 & 61.1 & 53.8 & 65.6 & 44.2 & 42.6 & 56.4\\
-\hspace{1em}0 & 1,000 & 55.1 & 60.5 & 49.5 & 54.9 & 49.3 & 60.4\\
-\hspace{1em}0 & 2,500 & 69.2 & 64.4 & 67.8 & 65.0 & 53.5 & 67.5\\
+\hspace{1em}Overall & Overall & 58.0 & 57.4 & 58.0 & 54.3 & 48.8 & 57.1\\
+\hspace{1em}30 & 500 & 55.4 & 54.7 & 56.0 & 48.0 & 42.3 & 55.3\\
+\hspace{1em}30 & 1,000 & 56.6 & 56.0 & 57.9 & 53.2 & 48.5 & 55.4\\
+\hspace{1em}30 & 2,500 & 61.4 & 59.0 & 63.6 & 61.8 & 60.7 & 60.2\\
+\hspace{1em}15 & 500 & 53.3 & 53.5 & 53.0 & 45.1 & 39.1 & 55.0\\
+\hspace{1em}15 & 1,000 & 57.5 & 55.2 & 56.9 & 51.2 & 44.6 & 54.5\\
+\hspace{1em}15 & 2,500 & 62.2 & 58.9 & 62.5 & 61.3 & 59.6 & 61.7\\
+\hspace{1em}0 & 500 & 50.6 & 52.7 & 52.5 & 43.2 & 40.3 & 53.6\\
+\hspace{1em}0 & 1,000 & 57.8 & 58.5 & 55.1 & 53.9 & 43.0 & 55.2\\
+\hspace{1em}0 & 2,500 & 67.2 & 68.4 & 64.5 & 70.6 & 61.5 & 62.5\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 71.0 & 66.6 & 67.3 & 65.5 & 60.1 & 59.2\\
-\hspace{1em}45 & 500 & 64.9 & 61.7 & 53.6 & 58.8 & 52.4 & 55.0\\
-\hspace{1em}45 & 1,000 & 59.2 & 54.0 & 60.3 & 57.7 & 53.0 & 53.5\\
-\hspace{1em}45 & 2,500 & 60.4 & 52.2 & 56.9 & 56.1 & 53.7 & 51.7\\
-\hspace{1em}15 & 500 & 60.6 & 64.5 & 62.4 & 60.3 & 56.7 & 60.1\\
-\hspace{1em}15 & 1,000 & 71.7 & 64.8 & 71.0 & 62.0 & 56.9 & 58.3\\
-\hspace{1em}15 & 2,500 & 65.0 & 61.1 & 63.1 & 57.9 & 54.1 & 55.0\\
-\hspace{1em}0 & 500 & 72.6 & 64.0 & 73.5 & 61.4 & 58.0 & 56.5\\
-\hspace{1em}0 & 1,000 & 86.8 & 85.4 & 76.5 & 80.8 & 70.2 & 67.9\\
-\hspace{1em}0 & 2,500 & 98.0 & 91.9 & 88.8 & 94.8 & 86.0 & 74.2\\
+\hspace{1em}Overall & Overall & 72.1 & 69.6 & 67.9 & 66.0 & 60.0 & 62.1\\
+\hspace{1em}30 & 500 & 59.4 & 58.8 & 57.8 & 52.8 & 48.1 & 55.0\\
+\hspace{1em}30 & 1,000 & 62.4 & 61.3 & 60.1 & 58.0 & 52.5 & 56.0\\
+\hspace{1em}30 & 2,500 & 61.6 & 59.6 & 61.0 & 60.1 & 56.2 & 57.7\\
+\hspace{1em}15 & 500 & 63.9 & 61.9 & 61.1 & 53.2 & 47.3 & 58.6\\
+\hspace{1em}15 & 1,000 & 69.7 & 65.8 & 66.0 & 63.5 & 55.9 & 59.4\\
+\hspace{1em}15 & 2,500 & 70.9 & 67.0 & 67.8 & 67.1 & 62.7 & 63.7\\
+\hspace{1em}0 & 500 & 74.1 & 71.4 & 68.0 & 58.7 & 56.6 & 61.8\\
+\hspace{1em}0 & 1,000 & 88.8 & 84.5 & 78.5 & 82.9 & 69.7 & 67.5\\
+\hspace{1em}0 & 2,500 & 98.4 & 96.5 & 91.3 & 97.7 & 91.3 & 78.9\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 77.9 & 76.0 & 74.5 & 70.7 & 65.7 & 68.7\\
-\hspace{1em}45 & 500 & 66.5 & 67.8 & 56.5 & 58.1 & 54.0 & 59.0\\
-\hspace{1em}45 & 1,000 & 66.1 & 62.7 & 63.5 & 58.3 & 55.2 & 64.1\\
-\hspace{1em}45 & 2,500 & 67.4 & 60.5 & 64.8 & 60.8 & 57.8 & 60.6\\
-\hspace{1em}15 & 500 & 68.9 & 73.7 & 68.6 & 65.9 & 57.7 & 65.5\\
-\hspace{1em}15 & 1,000 & 79.2 & 73.5 & 76.1 & 67.7 & 63.3 & 70.0\\
-\hspace{1em}15 & 2,500 & 73.9 & 71.7 & 73.9 & 69.2 & 64.6 & 66.0\\
-\hspace{1em}0 & 500 & 84.0 & 81.4 & 80.0 & 67.5 & 60.1 & 66.7\\
-\hspace{1em}0 & 1,000 & 95.1 & 92.8 & 89.2 & 89.1 & 80.4 & 77.5\\
-\hspace{1em}0 & 2,500 & 99.9 & 99.8 & 98.3 & 99.5 & 97.8 & 88.7\\
+\hspace{1em}Overall & Overall & 78.5 & 75.8 & 75.0 & 70.6 & 65.1 & 68.2\\
+\hspace{1em}30 & 500 & 65.3 & 63.3 & 63.7 & 55.7 & 50.1 & 59.5\\
+\hspace{1em}30 & 1,000 & 67.8 & 65.7 & 65.4 & 61.7 & 55.8 & 60.8\\
+\hspace{1em}30 & 2,500 & 69.4 & 66.8 & 68.3 & 65.4 & 62.0 & 64.3\\
+\hspace{1em}15 & 500 & 71.1 & 68.3 & 66.8 & 58.3 & 51.8 & 62.3\\
+\hspace{1em}15 & 1,000 & 75.6 & 71.3 & 71.9 & 66.6 & 59.6 & 64.4\\
+\hspace{1em}15 & 2,500 & 79.1 & 74.7 & 76.8 & 73.3 & 69.2 & 70.1\\
+\hspace{1em}0 & 500 & 83.2 & 80.7 & 76.1 & 65.1 & 61.5 & 67.2\\
+\hspace{1em}0 & 1,000 & 95.8 & 92.5 & 88.5 & 89.8 & 78.6 & 76.3\\
+\hspace{1em}0 & 2,500 & 99.8 & 99.4 & 97.8 & 99.7 & 97.8 & 88.9\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 88.9 & 86.8 & 86.6 & 83.1 & 80.5 & 79.5\\
-\hspace{1em}45 & 500 & 77.1 & 75.6 & 71.6 & 76.4 & 73.0 & 67.3\\
-\hspace{1em}45 & 1,000 & 78.4 & 74.0 & 74.1 & 64.7 & 62.9 & 69.6\\
-\hspace{1em}45 & 2,500 & 82.0 & 73.7 & 77.1 & 74.4 & 71.0 & 69.1\\
-\hspace{1em}15 & 500 & 80.6 & 82.7 & 82.6 & 79.6 & 76.3 & 77.2\\
-\hspace{1em}15 & 1,000 & 93.3 & 90.0 & 89.0 & 83.7 & 78.8 & 77.3\\
-\hspace{1em}15 & 2,500 & 93.8 & 90.0 & 92.8 & 87.9 & 85.5 & 81.3\\
-\hspace{1em}0 & 500 & 95.3 & 96.2 & 93.5 & 82.5 & 80.6 & 81.1\\
-\hspace{1em}0 & 1,000 & 100.0 & 99.4 & 98.6 & 98.8 & 96.2 & 93.5\\
-\hspace{1em}0 & 2,500 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 99.5\\*
+\hspace{1em}Overall & Overall & 90.9 & 88.8 & 88.5 & 84.7 & 82.4 & 82.9\\
+\hspace{1em}30 & 500 & 79.3 & 77.1 & 75.1 & 70.1 & 66.2 & 71.0\\
+\hspace{1em}30 & 1,000 & 83.9 & 80.7 & 80.0 & 76.9 & 73.7 & 74.4\\
+\hspace{1em}30 & 2,500 & 87.0 & 83.7 & 85.2 & 82.2 & 80.8 & 79.1\\
+\hspace{1em}15 & 500 & 85.9 & 83.0 & 82.1 & 74.2 & 70.2 & 74.8\\
+\hspace{1em}15 & 1,000 & 91.0 & 87.6 & 88.2 & 84.5 & 80.5 & 80.2\\
+\hspace{1em}15 & 2,500 & 94.3 & 91.6 & 93.5 & 89.8 & 88.5 & 86.7\\
+\hspace{1em}0 & 500 & 97.2 & 95.5 & 93.2 & 85.5 & 84.3 & 85.1\\
+\hspace{1em}0 & 1,000 & 99.9 & 99.8 & 99.4 & 99.4 & 97.5 & 94.6\\
+\hspace{1em}0 & 2,500 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 99.8\\*
 \end{longtable}

### 2022-07-14 R/bench_vi.R

@@ -54,6 +54,16 @@ bench_vi <- function(n_obs = 1000,
     mutate(var_type = str_remove(vi_id, "_[0-9]+$")) |>
     group_by(name)
 
+  vars_means <- vars_data %>%
+    group_by(name) %>%
+    mutate(vi = rescale(vi, to = c(0,1))) %>%
+    group_by(name, var_type) %>%
+    summarize(vi = mean(vi)) %>%
+    pivot_wider(names_from = var_type, values_from = vi) %>%
+    rename(model = name) %>%
+    mutate(pred_corr_max = pred_corr_max,
+           n_obs = n_obs)
+
   roc_grps <- map_dfr(
     .x = c("cmbn",
            "main",
@@ -96,8 +106,7 @@ bench_vi <- function(n_obs = 1000,
     mutate(pred_corr_max = pred_corr_max,
            n_obs = n_obs)
 
-  print(score)
+  enframe(list(score = score, means = vars_means))
 
-  score
 
 }

### 2022-07-14 R/bench_vi_summarize.R

@@ -7,9 +7,15 @@
 #' @param bm_pred_comb
 bench_vi_summarize <- function(bm_vi_comb) {
 
-  bm_vi_comb |>
+  bm_vi_comb %>%
+    as.data.table() %>%
+    .[name == 'score'] %>%
+    dt_unnest(col = value) %>%
     group_by(model, pred_corr_max, n_obs) |>
-    summarize(across(everything(), ~mean(.x)), .groups = 'drop') |>
+    summarize(
+      across(c(overall, cmbn, main, nlin, starts_with("intr"), time),
+             .fns = ~mean(.x, na.rm = TRUE)),
+      .groups = 'drop') |>
     arrange(pred_corr_max, n_obs, desc(overall)) |>
     group_by(pred_corr_max, n_obs) |>
     mutate(

### 2022-07-14 R/bench_vi_visualize.R

@@ -7,6 +7,9 @@
 bench_vi_visualize <- function(bm_vi_comb) {
 
   bm_vi_smry <- bm_vi_comb %>%
+    filter(name == 'score') %>%
+    unnest(value) %>%
+    select(-name) %>%
     mutate(
       intr = (intr_main+intr_hidden_cmbn+intr_hidden_nlin)/3,
     ) %>%
@@ -18,7 +21,17 @@ bench_vi_visualize <- function(bm_vi_comb) {
     group_by(variable, n_obs, pred_corr_max, model) %>%
     summarize(value = mean(value, na.rm = TRUE))
 
+  bm_vi_time <- bm_vi_comb %>%
+    filter(name == 'score') %>%
+    unnest(value) %>%
+    select(-name) %>%
+    group_by(model) %>%
+    summarize(time = median(time))
+
   bm_vi_overall <- bm_vi_comb %>%
+    filter(name == 'score') %>%
+    unnest(value) %>%
+    select(-name) %>%
     group_by(model) %>%
     summarize(value = mean(overall)) %>%
     mutate(variable = 'Overall')
@@ -284,6 +297,7 @@ bench_vi_visualize <- function(bm_vi_comb) {
   list(smry = bind_rows(data_aorsf, data_smry),
        diffs = gg_text_diffs,
        rankings = avg_ranking,
+       times = bm_vi_time,
        fig = fig)
 
 

### 2022-07-16 paper/jmlr/main.Rnw
paper v1

@@
 Trees in the oblique RSF are grown using linear combinations of predictors to create branches, whereas in the standard RSF a single predictor is used.
-Oblique RSF ensembles often have higher prediction accuracy than standard RSF ensembles, but the additional computational overhead of finding an optimal combination of predictors is a severe limitation.
-In addition, few methods have been developed for interpretation of oblique RSF ensembles.
-We introduce and evaluate a method to increase computational efficiency of the oblique RSF and a method to estimate importance of individual predictor variables with the oblique RSF.
-Our strategy to reduce computational overhead makes use of Newton-Raphson scoring, a classical optimization technique that we apply to the Cox partial likelihood function.
+Oblique RSF ensembles often have higher prediction accuracy than standard RSF ensembles, but the additional computational overhead of assessing all possible linear combination of predictors is a severe limitation.
+In addition, few methods have been developed for interpretation of oblique RSF ensembles, and they remain something of a black box compared to their axis-based counterparts.
+In this article, we introduce and evaluate a method to increase computational efficiency of the oblique RSF and a method to estimate importance of individual predictor variables with the oblique RSF.
+Our strategy to reduce computational overhead makes use of Newton-Raphson scoring, a classical optimization technique that we apply to the Cox partial likelihood function within each non-leaf node of decision trees.
 We estimate importance of predictors for the oblique RSF by negating each coefficient used for the given predictor in linear combinations, and then computing the reduction in out-of-bag accuracy.
-In numeric experiments, we find that our implementation of the oblique RSF is roughly 500 times faster with equivalent or superior prediction accuracy compared to existing software to fit oblique RSFs.
+In numeric experiments, we find that our implementation of the oblique RSF is over 500 times faster with equivalent discrimination and superior Brier score compared to existing software for oblique RSFs.
 We find in simulation studies that `negation importance' discriminates between signal and noise predictors more reliably than permutation importance, Shapley additive explanations, and a previously introduced technique to measure variable importance with oblique RSFs based on analysis of variance.
@@
 
-The random survival forest (RSF; \citet{ishwaran2008random, hothorn2006unbiased}) is a supervised learning algorithm that can be used for risk prediction \citep{wang2017selective}, which may reduce the burden of disease by guiding strategies for prevention and treatment in a wide range of medical domains \citep{moons2012riskII, moons2012riskI}.
+Risk prediction may reduce the burden of disease by guiding strategies for prevention and treatment in a wide range of domains \citep{moons2012riskII, moons2012riskI}.
+The random survival forest (RSF; \citet{ishwaran2008random, hothorn2006unbiased}) is a supervised learning algorithm that has been used frequently for risk prediction \citep{wang2017selective}.
 Similar to random forests (RFs) for classification and regression \citep{breiman2001random}, The RSF is a large set of de-correlated and randomized decision trees, with each tree contributing to the ensemble's prediction function.
@@
 
-A potential approach to improve the RSF when predictors are correlated and some are not relevant to the censored outcome is to use oblique decision trees instead of axis based trees.
+A potential approach to improve the RSF when predictors are correlated and some are not relevant to the censored outcome is to use oblique trees instead of axis based trees.
 Axis based trees split data using a single predictor, creating decision boundaries that are perpendicular or parallel to axes of the predictor space \citep[see][Chapter~2]{breiman2017classification}.
@@
 In a general benchmark experiment including \Sexpr{n_risk_tasks} risk prediction tasks, we show that accelerated oblique RSFs are roughly 500 times faster with equivalent or superior prediction accuracy compared to existing routines to fit oblique RSFs.
-Second, we improve their interpretability with `negation VI', a method to estimate VI that engages with coefficients in linear combinations of predictors instead of permuting predictor values.
-In simulation studies where VI is estimate using permutation, analysis of variance (ANOVA; see \citet{menze2011oblique}), and approximations of Shapley values, we find that negation VI improves the oblique RSF's ability to discriminate between correlated signal and noise variables.
+Second, we improve the interpretability of oblique RSFs with `negation VI', a method to estimate VI that flips the sign of coefficients in linear combinations of predictors instead of permuting predictor values.
+In simulation studies where VI is estimated using permutation, analysis of variance (ANOVA; see \citet{menze2011oblique}), and approximations of Shapley values, we find that negation VI improves the oblique RSF's ability to discriminate between correlated signal and noise variables.
 The accelerated oblique RSF and multiple methods to compute VI for oblique RSFs (permutation, ANOVA, and negation) are available in the \texttt{aorsf} R Package.
@@
 
-\subsection{Axis-based and oblique random forests}
+Sections \ref{sec:rw_forests} and \ref{sec:rw_vi} briefly summarize prior studies that have developed methods related to the oblique RSF and VI, respectively.
+
+\subsection{Axis-based and oblique random forests} \label{sec:rw_forests}
 
@@
 \citet{ishwaran2008random} developed an axis-based RSF with strict adherence to the rules for growing trees proposed in \citet{breiman2001random}.
+A similar implementation of the RSF was implemented in the \texttt{ranger} \citep{ranger}, an R package designed for high dimensional data that allows users to fit extremely randomized survival forests \citep{geurts2006extremely}.
 \citet{jaeger2019oblique} developed the oblique RSF following the bootstrapping approach described in Breiman's original RF and incorporating early stopping rules from the CIF.
 
-\subsection{Variable importance}
+\subsection{Variable importance} \label{sec:rw_vi}
 
@@
 Negation VI is similar to permutation VI in that it measures how much a model’s prediction error increases when a variable’s role in the model is de-stabilized.
-More specifically, negation VI measures the increase in an oblique RF's prediction error after flipping the sign of all coefficients linked to a variable (\ie, negating them).
+Specifically, negation VI measures the increase in an oblique RF's prediction error after flipping the sign of all coefficients linked to a variable (\ie, negating them).
 As the magnitude of a coefficient increases, so does the probability that negating it will change the oblique RF's predictions.
@@
 
-Negation VI has several characteristics that may be helpful.
-First, although the current article focuses on oblique RSFs and uses Harrell's C-statistic, negation VI can be applied to any oblique RF using any valid error function.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic (see \texttt{?aorsf::orsf\_vi\_negate})}.
-Second, since the coefficients in each non-leaf node of an oblique tree are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
-This conjecture is formally assessed in \secref{sec:results_vi}.
-Third, unlike permutation importance, negation VI is non-random and hence reproducible without setting a random seed.
-Along these lines, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% as a result of randomly permuting the values of Hemoglobin A1c.
+Negation VI has several helpful characteristics.
+First, negation VI can be applied to any oblique RF using any valid error function.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic (see \texttt{?aorsf::orsf\_vi\_negate})} Second, since the coefficients in each non-leaf node of an oblique tree are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
+Third, unlike permutation, negation is non-random and hence reproducible without setting a random seed.
+Additionally, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% as a result of randomly permuting the values of Hemoglobin A1c.
 
 \section{Numeric experiments}
+
+<<>>=
+r_version <- paste(version$major, version$minor, sep = '.')
+@
+
+Sections \ref{sec:bm_pred} and \ref{sec:bm_vi} present numerical experiments examining the accelerated oblique RSF and negation VI, respectively.
+The code used to run these experiments is available online at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}.
+All analyses were conducted using R version \Sexpr{r_version} with assistance from multiple R packages.
+To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
 
@@
  \texttt{aorsf-net} \newline
- \texttt{aorsf-fast} \newline
+ \textcolor{purple}{\texttt{aorsf-fast}} \newline
  \texttt{aorsf-cph} \newline
@@
 \end{tabular}
-\caption{Learning algorithms assessed in numeric studies}
+\caption{Learning algorithms assessed in numeric studies.
+\textcolor{purple}{\texttt{aorsf-fast}} is the accelerated oblique random survival forest (see Algorithm \ref{alg:aorsf}), and each of the additional learners are compared to \textcolor{purple}{\texttt{aorsf-fast}} in numeric studies.}
 \label{tab:learners}
@@
 
-We use a collection of \Sexpr{n_data_sets} publicly available data sets to benchmark the prediction accuracy and computational efficiency of the accelerated ORSF and each of the other learners described in \secref{sec:learners}.
+We use a collection of \Sexpr{n_data_sets} data sets to benchmark the prediction accuracy and computational efficiency of the accelerated ORSF and each of the other learners described in \secref{sec:learners}.
 The number of right-censored outcomes per data set ranged from one to four, and the total number of risk prediction tasks we analyzed was \Sexpr{n_risk_tasks} (\tabrefAppendix{tab:datasets}).
@@
 More specifically, we concluded that two learners had practically equivalent IPA or time-dependent C-statistic if there was a 95\% or higher posterior probability that the absolute difference in the relevant metric was less than 1.
-We concluded that one learner was weakly superior when there was $\geq$ 0.95\% posterior probability that the difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 0.95\% posterior probability that the difference in the relevant metric was 1 or more.
+We concluded that one learner was weakly superior when there was $\geq$ 95\% posterior probability that the difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 95\% posterior probability that the difference in the relevant metric was 1 or more.
 
@@
   getElement('rankings') %>%
-  filter(model == 'aorsf_cph_1') %>%
+  filter(model == 'aorsf_fast') %>%
   pull(n_wins)
@@
   getElement('smry') %>%
-  filter(model == 'aorsf_cph_1',
+  filter(model == 'aorsf_fast',
          data == 'Overall') %>%
@@
 
+A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all}.
+
 \paragraph{Index of prediction accuracy}
@@
 <<bm_pred_viz_ibs, fig.height=10, fig.width=9, fig.cap="Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
-Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.">>=
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.
+As predicted survival probabilities are not a standard output from \\texttt{xgboost-aft}, it is not included in this figure.">>=
 bm_pred_viz$ibs_scaled$fig
@@
          model == 'aorsf-cph') %>%
-  pull(prob_equiv)
+  pull(prob_equiv) %>%
+  str_replace('\\>\\.', "$>$ 0.")
 
@@
   filter(metric == 'cstat',
-         !str_detect(model, '^aorsf')) %>%
+         !str_detect(model, '^aorsf'),
+         model != 'obliqueRSF-net') %>%
   arrange(desc(median)) %>%
@@
 
+<<>>=
+
+times <- bm_pred_time_viz %>%
+  getElement("medians") %>%
+  transmute(
+    model,
+    time,
+    ratio = table_value(
+      time / time[model == 'aorsf-fast']
+    )
+  ) %>%
+  as_inline('model', c('time', 'ratio')) %>%
+  set_names(str_replace(names(.), '-', '_'))
+
+@
+
 \paragraph{Computational efficiency}
@@
 Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 1/2 second longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
-Compared to its predecessor, \texttt{obliqueRSF-net}, \texttt{aorsf-fast} was XYZ times faster.
+Comparing median computing times, \texttt{aorsf-fast} was \Sexpr{times$obliqueRSF_net$ratio} times faster than its predecessor, \texttt{obliqueRSF-net}.
+In addition, \texttt{aorsf-fast} was \Sexpr{times$cif_standard$ratio}, \Sexpr{times$ranger_extratrees$ratio}, and \Sexpr{times$rsf_standard$ratio} faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
 
@@
 
-\subsection{Benchmark of variable importance}
+\subsection{Benchmark of variable importance} \label{sec:bm_vi}
 
 The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between variables that do or do not have a relationship with a simulated outcome.
-We consider methods that are intrinsic to the oblique RF (\eg ANOVA VI), those that are intrinsic to the RF (\eg permutation VI), and those that are model-agnostic (\eg SHAP VI).
+We consider methods that are intrinsic to the oblique RF (\eg, ANOVA VI), those that are intrinsic to the RF (\eg, permutation VI), and those that are model-agnostic (\eg, SHAP VI).
+VI methods with unavailable or still developing software were not included.\footnote{Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
+Therefore, it is not incorporated in the current simulation study.}
 
@@
 We compute permutation VI for axis based RSFs using the \texttt{randomForestSRC} package.
-Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
-Therefore, it is not incorporated in the current simulation study.
 We compute ANOVA VI, negation VI, and permutation VI for oblique RSFs using the \texttt{aorsf} package.
@@
 We compute SHAP VI for boosted tree models using the \texttt{xgboost} package, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
-We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
+
+% We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
 
@@
 The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
-Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be valuated based on their ability to detect these effects.
+Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be evaluated based on their ability to detect these effects.
 
@@
 
-Parameters that varied in the current simulation study included the number of observations (1000, 3000, and 5000) and the minimum and maximum correlation between predictors (-0.1 to 0.1, -0.3 to 0.3, and -0.5 to 0.5).
-Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor, with an increase of one standard deviation associated with a 64\% increase in relative risk.
+<<>>=
+
+n_obs <- bm_vi_viz$smry %>%
+  ungroup() %>%
+  distinct(n_obs) %>%
+  drop_na() %>%
+  filter(n_obs > 0) %>%
+  pull(n_obs) %>%
+  glue_collapse(sep = ', ', last = ', and ')
+
+pred_corr <- bm_vi_viz$smry %>%
+  ungroup() %>%
+  distinct(pred_corr_max) %>%
+  drop_na() %>%
+  filter(pred_corr_max < 1) %>%
+  pull(pred_corr_max) %>%
+  glue_collapse(sep = ', ', last = ', and ')
+
+@
+
+Parameters that varied in the current simulation study included the number of observations (\Sexpr{n_obs}) and the absolute value of the maximum correlation between predictors (\Sexpr{pred_corr}).
+Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
 
@@
 
-We compared VI techniques based on their discrimination (\ie C-statistic) between relevant and irrelevant variables.
+We compared VI techniques based on their discrimination (\ie, C-statistic) between relevant and irrelevant variables.
 Specifically, we generated a binary outcome for each predictor variable based on its relevance (\ie, the binary outcome is 1 if the variable is relevant, 0 otherwise).
-Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic is interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
+Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic which may be interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
 
@@
   filter(model == 'aorsf-negate',
+         data == 'Overall_NA_NA') %>%
+  mutate(value = table_value(value * 100)) %>%
+  pull(value)
+
+cstat_mean_anova <- bm_vi_viz %>%
+  getElement('smry') %>%
+  filter(model == 'aorsf-anova',
+         data == 'Overall_NA_NA') %>%
+  mutate(value = table_value(value * 100)) %>%
+  pull(value)
+
+cstat_mean_permute <- bm_vi_viz %>%
+  getElement('smry') %>%
+  filter(model == 'aorsf-permute',
          data == 'Overall_NA_NA') %>%
@@
 
-@
-
-Overall, \texttt{aorsf-negate} had the highest C-statistic in \Sexpr{n_wins_aorsf} out of \Sexpr{n_vi_tasks} VI tasks, with an overall mean of \Sexpr{cstat_mean_aorsf} (Figure \ref{fig:bm_vi_viz}).
-Compared to the VI technique with the second highest overall C-statistic (\texttt{\Sexpr{cstat_vi_second_place$model}}), \texttt{aorsf-negate}'s mean was \Sexpr{cstat_aorsf_won_by$absolute} points higher, a relative increase of \Sexpr{cstat_aorsf_won_by$percent}\%.
+vi_times <- bm_vi_viz$times %>%
+  as_inline('model', 'time') %>%
+  map(as.numeric, unit = 'secs') %>%
+  map(table_value) %>%
+  set_names(str_replace(names(.), '-', '_'))
+
+@
+
+The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = \Sexpr{cstat_mean_aorsf}$), second (\texttt{aorsf-anova}; $C = \Sexpr{cstat_mean_anova}$), and third (\texttt{aorsf-permute}; $C = \Sexpr{cstat_mean_permute}$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in \Sexpr{n_wins_aorsf} out of \Sexpr{n_vi_tasks} VI tasks (Figure \ref{fig:bm_vi_viz}).
 Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
-
-The three techniques that used `aorsf` to estimate VI were ranked first (negation), second (ANOVA), and third (permutation) in overall mean C-statistic across all of the simulation scenarios.
-Computationally, ANOVA VI was the fastest technique with a median average
+Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
+Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of \Sexpr{vi_times$aorsf_anova} seconds versus \Sexpr{vi_times$aorsf_negate} and \Sexpr{vi_times$aorsf_permute} seconds, respectively.
 
@@
 Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
-In numeric experiments, we found that that \texttt{aorsf-fast} is orders of magnitude more efficient and just as accurate in risk prediction tasks compared to its predecessor, \texttt{obliqueRSF-net}.
-We also found several cases where negation VI allows oblique RSF models to discriminate between relevant and irrelevant variables more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
-Our results favored negation VI in scenarios where oblique RSFs were the underlying model used to compute VI and also in scenarios where other modeling techniques (\eg, boosted tree ensembles) were used.
+In numeric experiments, we found that that \texttt{aorsf-fast} is over 500 times faster and just as accurate in risk prediction tasks compared to its predecessor, \texttt{obliqueRSF-net}.
+We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
+Overall, we found that estimating VI using negation instead of ANOVA increased the C-statistic for ranking a relevant variable higher than an irrelevant variable by \Sexpr{cstat_aorsf_won_by$absolute}, a relative increase of \Sexpr{cstat_aorsf_won_by$percent}\%.
 
@@
 Accurate risk prediction models have the potential to improve healthcare by directing timely interventions to patients who are most likely to benefit.
-However, prediction models that cannot be interpreted and explained have no place in clinical practice.
+However, prediction models that cannot scale adequately to large databases or cannot be interpreted and explained have no place in clinical practice.
 The current study advances the oblique RSF, an accurate risk prediction model, towards being accurate, scalable, and interpretable.
@@
 
-The current study has several limitations.
-The accelerated oblique RSF does not account for competing risks, and so our benchmark of prediction accuracy divided tasks where competing risks were present into event-specific tasks.
-Biased estimation of incidence may occur when competing risks are ignored, and allowing the oblique RSF to account for competing risks is a high priority for future studies.
-In addition, missing data are not addressed in the accelerated oblique RSF, and users are expected to impute missing values before passing training or testing data into exported functions from the \texttt{aorsf} R package.
-However, missing data are common and it is standard for ensemble tree methods to handle missing data during the tree growing procedure.
+While the current study advances the oblique RSF towards being scalable and interpretable, there remain several limitations that can be targeted in future studies.
+The accelerated oblique RSF does not account for competing risks, and biased estimation of incidence may occur when competing risks are ignored.
+Thus, allowing the oblique RSF to account for competing risks is a high priority for future studies.
+In addition, missing data are not addressed in the accelerated oblique RSF, and users of the \texttt{aorsf} R package are expected to impute missing values prior to model training and testing.
+However, missing data are common and there are numerous techniques for ensemble tree methods to handle missing data during the tree growing procedure.
 Thus, a second item of high priority for future studies is to develop and evaluate strategies to handle missing data while growing an oblique RSF.
@@
 The accelerated oblique RSF could incorporate this splitting technique by using Newton Raphson scoring to fit a model for the censoring distribution and then a weighted model could be fit to the failure distribution.
+This final item has the highest priority, as \citet{cui2017consistency} showed it is a requisite condition for consistency of axis based survival trees in fairly general settings.
 
@@
 data_tbl %>%
+  mutate(
+    ibs_scaled = if_else(
+      model == 'xgboost-aft',
+      '---',
+      ibs_scaled
+    )
+  ) %>%
   select(-data) %>%
@@
                       'Risk prediction'),
-        align = 'lcc',
-        caption = "Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.") %>%
+        align = 'lcccc',
+        caption = "Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.\\label{tab:bm_pred_all}") %>%
   pack_rows(index = indents,
             italic = TRUE,
-            hline_before = TRUE,
+            hline_before = FALSE,
             hline_after = TRUE) %>%
@@
                       "Permutation"),
-        caption = "Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance") %>%
+        caption = "Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance. \\label{tab:bm_vi}") %>%
   kable_styling(latex_options = c("repeat_header")) %>%

### 2022-07-16 paper/jmlr/main.tex
paper v1

@@
 First, we reduce their computational cost (\ie, accelerate them) with a scalable algorithm to identify linear combinations of coefficients.
-In a general benchmark experiment including 31 risk prediction tasks, we show that accelerated oblique RSFs are roughly 500 times faster with equivalent or superior prediction accuracy compared to existing routines to fit oblique RSFs.
-Second, we improve their interpretability with `negation VI', a method to estimate VI that engages with coefficients in linear combinations of predictors instead of permuting predictor values.
-In simulation studies where VI is estimate using permutation, analysis of variance (ANOVA; see \citet{menze2011oblique}), and approximations of Shapley values, we find that negation VI improves the oblique RSF's ability to discriminate between correlated signal and noise variables.
+In a general benchmark experiment including 30 risk prediction tasks, we show that accelerated oblique RSFs are roughly 500 times faster with equivalent or superior prediction accuracy compared to existing routines to fit oblique RSFs.
+Second, we improve the interpretability of oblique RSFs with `negation VI', a method to estimate VI that flips the sign of coefficients in linear combinations of predictors instead of permuting predictor values.
+In simulation studies where VI is estimated using permutation, analysis of variance (ANOVA; see \citet{menze2011oblique}), and approximations of Shapley values, we find that negation VI improves the oblique RSF's ability to discriminate between correlated signal and noise variables.
 The accelerated oblique RSF and multiple methods to compute VI for oblique RSFs (permutation, ANOVA, and negation) are available in the \texttt{aorsf} R Package.
@@
 
-Negation VI has several characteristics that may be helpful.
-First, although the current article focuses on oblique RSFs and uses Harrell's C-statistic, negation VI can be applied to any oblique RF using any valid error function.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic (see \texttt{?aorsf::orsf\_vi\_negate})}.
-Second, since the coefficients in each non-leaf node of an oblique tree are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
-This conjecture is formally assessed in \secref{sec:results_vi}.
-Third, unlike permutation importance, negation VI is non-random and hence reproducible without setting a random seed.
-Along these lines, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% as a result of randomly permuting the values of Hemoglobin A1c.
+Negation VI has several helpful characteristics.
+First, negation VI can be applied to any oblique RF using any valid error function.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic (see \texttt{?aorsf::orsf\_vi\_negate})} Second, since the coefficients in each non-leaf node of an oblique tree are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
+Third, unlike permutation, negation is non-random and hence reproducible without setting a random seed.
+Additionally, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% as a result of randomly permuting the values of Hemoglobin A1c.
 
 \section{Numeric experiments}
+
+Sections \ref{sec:bm_pred} and \ref{sec:bm_vi} present numerical experiments examining the accelerated oblique RSF and negation VI, respectively.
+The code used to run these experiments is available online at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}.
+All analyses were conducted using R version 4.1.3 with assistance from multiple R packages.
+To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
 
@@
 
-We use a collection of 18 publicly available data sets to benchmark the prediction accuracy and computational efficiency of the accelerated ORSF and each of the other learners described in \secref{sec:learners}.
-The number of right-censored outcomes per data set ranged from one to four, and the total number of risk prediction tasks we analyzed was 31 (\tabrefAppendix{tab:datasets}).
-Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 2,231), the number of predictors ranged from 7 to 1,692 (median: 41), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 78.2).
+We use a collection of 17 data sets to benchmark the prediction accuracy and computational efficiency of the accelerated ORSF and each of the other learners described in \secref{sec:learners}.
+The number of right-censored outcomes per data set ranged from one to four, and the total number of risk prediction tasks we analyzed was 30 (\tabrefAppendix{tab:datasets}).
+Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 1,807.5), the number of predictors ranged from 7 to 1,692 (median: 32.5), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 78.1).
 
@@
 
-For each risk prediction task, we completed 20 runs of Monte-Carlo cross validation.
+For each risk prediction task, we completed 22 runs of Monte-Carlo cross validation.
 In each run, we used a random sample containing 50\% of the available data for training and the remaining 50\% for testing each of the learners described in \secref{sec:learners}.
@@
 
-After collecting data from 20 replications of Monte-Carlo cross validation for the 14 learners in all 31 risk prediction tasks, we analyzed the resulting 8,680 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
+After collecting data from 22 replications of Monte-Carlo cross validation for the 14 learners in all 30 risk prediction tasks, we analyzed the resulting 9,240 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
 Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using Bayesian models.
@@
 
+A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all}.
+
 \paragraph{Index of prediction accuracy}
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in  out of 31 risk prediction tasks, with an overall mean IPA of  (Figure \ref{fig:bm_pred_viz_ibs}).
-Compared to the learner with the second highest mean IPA (\texttt{rsf-standard}), \texttt{aorsf-fast}'s mean was 1.27 points higher, a relative increase of 10.5\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.98, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.76 (versus \texttt{rsf-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 16 out of 30 risk prediction tasks, with an overall mean IPA of 13.6 (Figure \ref{fig:bm_pred_viz_ibs}).
+Compared to the learner with the second highest mean IPA (\texttt{rsf-standard}), \texttt{aorsf-fast}'s mean was 1.32 points higher, a relative increase of 10.7\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.97, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.79 (versus \texttt{rsf-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
 
@@
 \includegraphics[width=\maxwidth]{figure/bm_pred_viz_ibs-1} \caption[Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks]{Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
-Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.}\label{fig:bm_pred_viz_ibs}
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.
+As predicted survival probabilities are not a standard output from \texttt{xgboost-aft}, it is not included in this figure.}\label{fig:bm_pred_viz_ibs}
 \end{figure}
@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in  out of 31 risk prediction tasks, with an overall mean of  (Figure \ref{fig:bm_pred_viz_cstat}).
-Compared to the learner with the second highest mean C-statistic (\texttt{obliqueRSF-net}), \texttt{aorsf-fast}'s mean was 0.643 points higher, a relative increase of 0.837\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.01 (versus \texttt{obliqueRSF-net}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 10 out of 30 risk prediction tasks, with an overall mean of 77.6 (Figure \ref{fig:bm_pred_viz_cstat}).
+Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.664 points higher, a relative increase of 0.864\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was $>$ 0.999, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.19 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
 
@@
 Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 1/2 second longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
-Compared to its predecessor, \texttt{obliqueRSF-net}, \texttt{aorsf-fast} was XYZ times faster.
+Comparing median computing times, \texttt{aorsf-fast} was 525.2 times faster than its predecessor, \texttt{obliqueRSF-net}.
+In addition, \texttt{aorsf-fast} was 20.5, 4.27, and 2.79 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
 
@@
 
-Parameters that varied in the current simulation study included the number of observations (1000, 3000, and 5000) and the minimum and maximum correlation between predictors (-0.1 to 0.1, -0.3 to 0.3, and -0.5 to 0.5).
-Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor, with an increase of one standard deviation associated with a 64\% increase in relative risk.
+Parameters that varied in the current simulation study included the number of observations (500, 1000, and 2500) and the absolute value of the maximum correlation between predictors (0.3, 0.15, and 0).
+Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
 
@@
 
-Overall, \texttt{aorsf-negate} had the highest C-statistic in 27 out of 36 VI tasks, with an overall mean of 76.1 (Figure \ref{fig:bm_vi_viz}).
-Compared to the VI technique with the second highest overall C-statistic (\texttt{aorsf-anova}), \texttt{aorsf-negate}'s mean was 2.22 points higher, a relative increase of 3.00\%.
+The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = 76.0$), second (\texttt{aorsf-anova}; $C = 74.0$), and third (\texttt{aorsf-permute}; $C = 73.3$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in 27 out of 36 VI tasks (Figure \ref{fig:bm_vi_viz}).
 Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
-
-The three techniques that used `aorsf` to estimate VI were ranked first (negation), second (ANOVA), and third (permutation) in overall mean C-statistic across all of the simulation scenarios.
-Computationally, ANOVA VI was the fastest technique with a median average
+Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
+Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of 1.34 seconds versus 12.3 and 14.1 seconds, respectively.
 
@@
 Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
-In numeric experiments, we found that that \texttt{aorsf-fast} is orders of magnitude more efficient and just as accurate in risk prediction tasks compared to its predecessor, \texttt{obliqueRSF-net}.
-We also found several cases where negation VI allows oblique RSF models to discriminate between relevant and irrelevant variables more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
-Our results favored negation VI in scenarios where oblique RSFs were the underlying model used to compute VI and also in scenarios where other modeling techniques (\eg, boosted tree ensembles) were used.
+In numeric experiments, we found that that \texttt{aorsf-fast} is over 500 times faster and just as accurate in risk prediction tasks compared to its predecessor, \texttt{obliqueRSF-net}.
+We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
+Overall, we found that estimating VI using negation instead of ANOVA increased the C-statistic for ranking a relevant variable higher than an irrelevant variable by 2.00, a relative increase of 2.70\%.
 
@@
 \begin{longtable}[t]{lcclcc}
-\caption{\label{tab:unnamed-chunk-5}Data sets used for numeric experiments \label{tab:datasets}}\\
+\caption{\label{tab:unnamed-chunk-8}Data sets used for numeric experiments \label{tab:datasets}}\\
 \toprule
@@
 \multirow{-2}{*}{\raggedright\arraybackslash SPRINT} & \multirow{-2}{*}{\centering\arraybackslash 9,361} & \multirow{-2}{*}{\centering\arraybackslash 174} & Death & 1,644 & 82.4\\
-\cmidrule{1-6}\pagebreak[0]
-Heart Transplant & 3,787 & 52 & Graft-Loss Or Death & 500 & 86.8\\
 \cmidrule{1-6}\pagebreak[0]
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\begin{longtable}[t]{lcclc}
-\caption{\label{tab:unnamed-chunk-6}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.}\\
+\begin{longtable}[t]{lcccc}
+\caption{\label{tab:unnamed-chunk-9}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.\label{tab:bm_pred_all}}\\
 \toprule
@@
 \endfirsthead
-\caption[]{Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.
-\textit{(continued)}}\\
+\caption[]{Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.\label{tab:bm_pred_all} \textit{(continued)}}\\
 \toprule
@@
 \addlinespace[0.3em]
-\hline
 \multicolumn{5}{l}{\textit{\textbf{Overall}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.134 (0.112) & 0.774 (0.071) & 0.772 & 0.188\\
-\hspace{1em}aorsf-cph & 0.133 (0.112) & 0.773 (0.070) & 1.993 & 0.184\\
-\hspace{1em}aorsf-net & 0.126 (0.127) & 0.770 (0.074) & 128.379 & 0.177\\
-\hspace{1em}rsf-standard & 0.121 (0.116) & 0.760 (0.075) & 2.168 & 0.291\\
-\hspace{1em}cif-standard & 0.120 (0.100) & 0.768 (0.070) & 4.511 & 15.781\\
-\hspace{1em}cif-rotate & 0.120 (0.128) & 0.758 (0.080) & 42.206 & 9.111\\
-\hspace{1em}obliqueRSF-net & 0.120 (0.086) & 0.773 (0.071) & 376.676 & 24.742\\
-\hspace{1em}glmnet-cox & 0.117 (0.122) & 0.761 (0.075) & 0.460 & 0.004\\
-\hspace{1em}ranger-extratrees & 0.105 (0.088) & 0.764 (0.067) & 2.416 & 1.775\\
-\hspace{1em}cif-extension & 0.100 (0.095) & 0.763 (0.072) & 23.171 & 8.367\\
-\hspace{1em}aorsf-random & 0.095 (0.083) & 0.743 (0.064) & 2.272 & 0.180\\
-\hspace{1em}xgboost-cox & 0.072 (0.102) & 0.757 (0.088) & 4.368 & 0.004\\
-\hspace{1em}nn-cox & 0.049 (0.109) & 0.653 (0.136) & 16.163 & 4.563\\
-\hspace{1em}xgboost-aft & -4.74 (5.18) & 0.767 (0.074) & 14.635 & 0.007\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-fast & 0.136 (0.113) & 0.776 (0.072) & 0.721 & 0.174\\
+\hspace{1em}aorsf-cph & 0.136 (0.113) & 0.775 (0.071) & 1.867 & 0.169\\
+\hspace{1em}aorsf-net & 0.129 (0.128) & 0.771 (0.075) & 131.131 & 0.167\\
+\hspace{1em}rsf-standard & 0.123 (0.118) & 0.761 (0.076) & 2.116 & 0.278\\
+\hspace{1em}cif-standard & 0.123 (0.101) & 0.769 (0.071) & 4.312 & 14.590\\
+\hspace{1em}obliqueRSF-net & 0.122 (0.087) & 0.775 (0.072) & 379.917 & 23.183\\
+\hspace{1em}cif-rotate & 0.121 (0.130) & 0.759 (0.082) & 39.895 & 8.598\\
+\hspace{1em}glmnet-cox & 0.119 (0.124) & 0.763 (0.075) & 0.433 & 0.004\\
+\hspace{1em}ranger-extratrees & 0.107 (0.088) & 0.765 (0.067) & 1.986 & 1.289\\
+\hspace{1em}cif-extension & 0.102 (0.096) & 0.764 (0.072) & 22.524 & 7.926\\
+\hspace{1em}aorsf-random & 0.097 (0.084) & 0.744 (0.064) & 2.201 & 0.169\\
+\hspace{1em}xgboost-cox & 0.074 (0.104) & 0.759 (0.089) & 4.384 & 0.004\\
+\hspace{1em}nn-cox & 0.050 (0.109) & 0.652 (0.138) & 16.298 & 3.578\\
+\hspace{1em}xgboost-aft & --- & 0.768 (0.075) & 14.513 & 0.007\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{ACTG 320; AIDS diagnosis, n = 1151, p = 12}}}\\
 \hline
-\hspace{1em}aorsf-random & 0.031 (0.020) & 0.744 (0.035) & 0.408 & 0.036\\
-\hspace{1em}ranger-extratrees & 0.029 (0.017) & 0.739 (0.037) & 0.052 & 0.145\\
-\hspace{1em}cif-standard & 0.028 (0.027) & 0.746 (0.039) & 1.052 & 4.532\\
-\hspace{1em}obliqueRSF-net & 0.028 (0.022) & 0.743 (0.039) & 26.784 & 15.942\\
-\hspace{1em}aorsf-fast & 0.026 (0.027) & 0.741 (0.041) & 0.143 & 0.034\\
-\hspace{1em}aorsf-cph & 0.026 (0.029) & 0.747 (0.040) & 0.433 & 0.035\\
-\hspace{1em}cif-extension & 0.024 (0.015) & 0.722 (0.040) & 9.266 & 4.180\\
-\hspace{1em}aorsf-net & 0.020 (0.034) & 0.742 (0.040) & 18.859 & 0.036\\
-\hspace{1em}glmnet-cox & 0.018 (0.027) & 0.744 (0.035) & 0.172 & 0.002\\
-\hspace{1em}rsf-standard & 0.011 (0.034) & 0.732 (0.042) & 0.145 & 0.059\\
-\hspace{1em}cif-rotate & 0.008 (0.037) & 0.736 (0.035) & 15.338 & 3.967\\
-\hspace{1em}nn-cox & -0.001 (0.017) & 0.638 (0.114) & 10.944 & 0.541\\
-\hspace{1em}xgboost-cox & -0.002 (0.048) & 0.748 (0.033) & 3.788 & 0.003\\
-\hspace{1em}xgboost-aft & -8.09 (1.44) & 0.736 (0.035) & 9.657 & 0.006\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}ranger-extratrees & 0.027 (0.017) & 0.736 (0.036) & 0.052 & 0.145\\
+\hspace{1em}aorsf-random & 0.027 (0.022) & 0.741 (0.035) & 0.408 & 0.035\\
+\hspace{1em}obliqueRSF-net & 0.026 (0.023) & 0.741 (0.038) & 26.825 & 15.427\\
+\hspace{1em}cif-standard & 0.023 (0.032) & 0.740 (0.041) & 1.062 & 4.542\\
+\hspace{1em}aorsf-cph & 0.023 (0.030) & 0.744 (0.039) & 0.436 & 0.035\\
+\hspace{1em}cif-extension & 0.023 (0.016) & 0.719 (0.040) & 9.253 & 4.180\\
+\hspace{1em}aorsf-fast & 0.022 (0.029) & 0.737 (0.041) & 0.142 & 0.034\\
+\hspace{1em}aorsf-net & 0.016 (0.035) & 0.738 (0.040) & 18.751 & 0.036\\
+\hspace{1em}glmnet-cox & 0.015 (0.029) & 0.742 (0.035) & 0.174 & 0.002\\
+\hspace{1em}rsf-standard & 0.005 (0.041) & 0.727 (0.044) & 0.149 & 0.059\\
+\hspace{1em}cif-rotate & 0.002 (0.042) & 0.729 (0.040) & 15.116 & 3.882\\
+\hspace{1em}nn-cox & -0.001 (0.017) & 0.636 (0.114) & 10.863 & 0.537\\
+\hspace{1em}xgboost-cox & -0.003 (0.046) & 0.747 (0.031) & 3.788 & 0.003\\
+\hspace{1em}xgboost-aft & --- & 0.734 (0.034) & 9.657 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{ACTG 320; death, n = 1151, p = 12}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.008 (0.019) & 0.835 (0.056) & 0.087 & 0.020\\
-\hspace{1em}obliqueRSF-net & 0.008 (0.011) & 0.829 (0.053) & 8.678 & 10.534\\
-\hspace{1em}aorsf-cph & 0.008 (0.018) & 0.827 (0.063) & 0.351 & 0.020\\
-\hspace{1em}aorsf-random & 0.006 (0.014) & 0.802 (0.071) & 0.224 & 0.023\\
-\hspace{1em}cif-extension & 0.001 (0.021) & 0.770 (0.069) & 8.850 & 3.780\\
-\hspace{1em}ranger-extratrees & 0.000 (0.019) & 0.778 (0.073) & 0.041 & 0.126\\
-\hspace{1em}aorsf-net & -0.002 (0.032) & 0.814 (0.069) & 14.142 & 0.023\\
-\hspace{1em}cif-standard & -0.004 (0.025) & 0.784 (0.065) & 1.106 & 4.570\\
+\hspace{1em}obliqueRSF-net & 0.007 (0.012) & 0.824 (0.053) & 8.814 & 10.613\\
+\hspace{1em}aorsf-cph & 0.006 (0.018) & 0.823 (0.061) & 0.351 & 0.020\\
+\hspace{1em}aorsf-fast & 0.006 (0.019) & 0.829 (0.057) & 0.086 & 0.020\\
+\hspace{1em}aorsf-random & 0.004 (0.015) & 0.791 (0.075) & 0.225 & 0.023\\
+\hspace{1em}cif-extension & 0.000 (0.020) & 0.764 (0.067) & 8.850 & 3.772\\
+\hspace{1em}ranger-extratrees & 0.000 (0.019) & 0.776 (0.070) & 0.041 & 0.124\\
 \hspace{1em}xgboost-cox & -0.004 (0.004) & 0.500 (0.000) & 0.111 & 0.002\\
-\hspace{1em}nn-cox & -0.005 (0.004) & 0.522 (0.099) & 9.961 & 0.534\\
-\hspace{1em}rsf-standard & -0.028 (0.050) & 0.780 (0.078) & 0.093 & 0.037\\
-\hspace{1em}cif-rotate & -0.036 (0.048) & 0.709 (0.091) & 13.345 & 3.439\\
-\hspace{1em}glmnet-cox & -0.060 (0.102) & 0.749 (0.106) & 0.275 & 0.002\\
-\hspace{1em}xgboost-aft & -25.1 (7.60) & 0.778 (0.074) & 9.772 & 0.006\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}nn-cox & -0.005 (0.004) & 0.521 (0.095) & 10.159 & 0.520\\
+\hspace{1em}cif-standard & -0.006 (0.025) & 0.780 (0.063) & 1.117 & 4.526\\
+\hspace{1em}aorsf-net & -0.006 (0.033) & 0.808 (0.068) & 14.237 & 0.023\\
+\hspace{1em}rsf-standard & -0.033 (0.052) & 0.776 (0.075) & 0.094 & 0.036\\
+\hspace{1em}cif-rotate & -0.040 (0.048) & 0.702 (0.090) & 13.345 & 3.292\\
+\hspace{1em}glmnet-cox & -0.065 (0.098) & 0.747 (0.100) & 0.276 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.773 (0.072) & 9.772 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{ARIC; coronary heart disease, n = 13623, p = 41}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.157 (0.007) & 0.811 (0.007) & 4.591 & 1.355\\
-\hspace{1em}aorsf-cph & 0.153 (0.007) & 0.810 (0.007) & 14.698 & 1.385\\
-\hspace{1em}aorsf-net & 0.153 (0.007) & 0.811 (0.007) & 507.224 & 1.477\\
-\hspace{1em}rsf-standard & 0.151 (0.007) & 0.802 (0.007) & 9.099 & 1.101\\
-\hspace{1em}obliqueRSF-net & 0.144 (0.005) & 0.813 (0.007) & 2836.384 & 351.006\\
-\hspace{1em}cif-standard & 0.133 (0.005) & 0.810 (0.007) & 70.288 & 358.500\\
-\hspace{1em}glmnet-cox & 0.129 (0.012) & 0.796 (0.008) & 1.721 & 0.011\\
-\hspace{1em}nn-cox & 0.124 (0.014) & 0.796 (0.007) & 55.992 & 105.741\\
-\hspace{1em}ranger-extratrees & 0.112 (0.005) & 0.796 (0.008) & 320.882 & 71.239\\
-\hspace{1em}cif-rotate & 0.104 (0.004) & 0.784 (0.008) & 569.756 & 70.690\\
-\hspace{1em}aorsf-random & 0.098 (0.005) & 0.773 (0.008) & 11.738 & 1.361\\
-\hspace{1em}cif-extension & 0.069 (0.002) & 0.787 (0.009) & 164.896 & 51.659\\
-\hspace{1em}xgboost-cox & 0.066 (0.018) & 0.815 (0.006) & 8.635 & 0.015\\
-\hspace{1em}xgboost-aft & -4.92 (0.295) & 0.815 (0.005) & 22.322 & 0.013\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-fast & 0.157 (0.007) & 0.810 (0.007) & 4.561 & 1.355\\
+\hspace{1em}aorsf-cph & 0.153 (0.007) & 0.809 (0.007) & 14.677 & 1.379\\
+\hspace{1em}aorsf-net & 0.153 (0.007) & 0.810 (0.007) & 511.536 & 1.484\\
+\hspace{1em}rsf-standard & 0.151 (0.007) & 0.801 (0.007) & 9.099 & 1.077\\
+\hspace{1em}obliqueRSF-net & 0.144 (0.005) & 0.812 (0.007) & 2814.937 & 353.143\\
+\hspace{1em}cif-standard & 0.132 (0.005) & 0.810 (0.007) & 70.476 & 358.500\\
+\hspace{1em}glmnet-cox & 0.129 (0.012) & 0.796 (0.008) & 1.547 & 0.011\\
+\hspace{1em}nn-cox & 0.122 (0.014) & 0.795 (0.007) & 52.898 & 105.741\\
+\hspace{1em}ranger-extratrees & 0.112 (0.005) & 0.796 (0.009) & 305.330 & 66.584\\
+\hspace{1em}cif-rotate & 0.104 (0.004) & 0.784 (0.007) & 571.763 & 70.690\\
+\hspace{1em}aorsf-random & 0.098 (0.005) & 0.772 (0.008) & 11.675 & 1.360\\
+\hspace{1em}cif-extension & 0.069 (0.002) & 0.787 (0.009) & 165.124 & 51.252\\
+\hspace{1em}xgboost-cox & 0.065 (0.017) & 0.814 (0.005) & 8.516 & 0.015\\
+\hspace{1em}xgboost-aft & --- & 0.815 (0.006) & 22.582 & 0.013\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{ARIC; death, n = 13623, p = 41}}}\\
 \hline
-\hspace{1em}aorsf-net & 0.217 (0.006) & 0.792 (0.004) & 952.688 & 2.390\\
-\hspace{1em}rsf-standard & 0.216 (0.007) & 0.789 (0.004) & 13.694 & 1.330\\
-\hspace{1em}aorsf-fast & 0.215 (0.007) & 0.792 (0.004) & 7.760 & 2.287\\
-\hspace{1em}aorsf-cph & 0.215 (0.007) & 0.791 (0.004) & 23.194 & 2.305\\
-\hspace{1em}obliqueRSF-net & 0.207 (0.005) & 0.791 (0.004) & 7578.159 & 316.772\\
-\hspace{1em}cif-standard & 0.201 (0.005) & 0.790 (0.004) & 72.192 & 385.603\\
-\hspace{1em}nn-cox & 0.192 (0.013) & 0.780 (0.005) & 102.206 & 101.400\\
-\hspace{1em}glmnet-cox & 0.189 (0.015) & 0.776 (0.007) & 2.123 & 0.012\\
-\hspace{1em}ranger-extratrees & 0.181 (0.005) & 0.781 (0.005) & 421.367 & 67.011\\
-\hspace{1em}cif-rotate & 0.152 (0.007) & 0.757 (0.006) & 582.264 & 65.718\\
-\hspace{1em}xgboost-cox & 0.132 (0.011) & 0.794 (0.004) & 12.326 & 0.016\\
-\hspace{1em}aorsf-random & 0.130 (0.005) & 0.733 (0.006) & 22.918 & 2.061\\
-\hspace{1em}cif-extension & 0.112 (0.002) & 0.776 (0.005) & 182.973 & 54.549\\
-\hspace{1em}xgboost-aft & -1.59 (0.150) & 0.794 (0.004) & 28.205 & 0.015\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-net & 0.217 (0.006) & 0.792 (0.004) & 955.499 & 2.412\\
+\hspace{1em}rsf-standard & 0.216 (0.007) & 0.789 (0.004) & 13.881 & 1.320\\
+\hspace{1em}aorsf-cph & 0.215 (0.007) & 0.792 (0.004) & 23.030 & 2.291\\
+\hspace{1em}aorsf-fast & 0.215 (0.007) & 0.792 (0.004) & 7.760 & 2.281\\
+\hspace{1em}obliqueRSF-net & 0.207 (0.005) & 0.792 (0.004) & 7413.571 & 319.191\\
+\hspace{1em}cif-standard & 0.202 (0.004) & 0.790 (0.004) & 71.453 & 386.302\\
+\hspace{1em}nn-cox & 0.192 (0.012) & 0.780 (0.005) & 97.331 & 99.624\\
+\hspace{1em}glmnet-cox & 0.190 (0.015) & 0.777 (0.008) & 2.123 & 0.012\\
+\hspace{1em}ranger-extratrees & 0.181 (0.004) & 0.781 (0.005) & 406.320 & 66.433\\
+\hspace{1em}cif-rotate & 0.152 (0.007) & 0.757 (0.006) & 581.210 & 65.820\\
+\hspace{1em}xgboost-cox & 0.132 (0.011) & 0.795 (0.004) & 12.310 & 0.016\\
+\hspace{1em}aorsf-random & 0.130 (0.005) & 0.733 (0.005) & 21.733 & 2.051\\
+\hspace{1em}cif-extension & 0.113 (0.002) & 0.776 (0.005) & 183.959 & 53.651\\
+\hspace{1em}xgboost-aft & --- & 0.794 (0.004) & 27.733 & 0.014\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{ARIC; heart failure, n = 13623, p = 41}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.234 (0.007) & 0.842 (0.005) & 5.447 & 1.627\\
-\hspace{1em}rsf-standard & 0.230 (0.007) & 0.836 (0.005) & 10.044 & 1.063\\
-\hspace{1em}aorsf-cph & 0.230 (0.006) & 0.841 (0.005) & 16.965 & 1.635\\
-\hspace{1em}aorsf-net & 0.216 (0.059) & 0.832 (0.045) & 632.139 & 1.707\\
-\hspace{1em}obliqueRSF-net & 0.213 (0.005) & 0.842 (0.005) & 3706.701 & 311.291\\
-\hspace{1em}cif-standard & 0.200 (0.004) & 0.839 (0.005) & 74.710 & 369.280\\
-\hspace{1em}nn-cox & 0.188 (0.020) & 0.827 (0.009) & 66.425 & 104.654\\
-\hspace{1em}cif-rotate & 0.172 (0.006) & 0.807 (0.007) & 577.084 & 67.496\\
-\hspace{1em}ranger-extratrees & 0.171 (0.004) & 0.825 (0.005) & 326.124 & 84.602\\
-\hspace{1em}glmnet-cox & 0.168 (0.042) & 0.818 (0.016) & 2.513 & 0.012\\
-\hspace{1em}aorsf-random & 0.139 (0.005) & 0.789 (0.006) & 15.868 & 1.587\\
-\hspace{1em}xgboost-cox & 0.122 (0.017) & 0.846 (0.005) & 11.223 & 0.015\\
-\hspace{1em}cif-extension & 0.108 (0.003) & 0.809 (0.007) & 169.585 & 49.274\\
-\hspace{1em}xgboost-aft & -3.80 (0.250) & 0.845 (0.005) & 26.160 & 0.014\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-fast & 0.234 (0.007) & 0.842 (0.005) & 5.445 & 1.619\\
+\hspace{1em}rsf-standard & 0.230 (0.007) & 0.835 (0.005) & 10.089 & 1.049\\
+\hspace{1em}aorsf-cph & 0.229 (0.007) & 0.841 (0.005) & 16.936 & 1.624\\
+\hspace{1em}aorsf-net & 0.217 (0.057) & 0.832 (0.043) & 631.093 & 1.707\\
+\hspace{1em}obliqueRSF-net & 0.213 (0.005) & 0.841 (0.005) & 3701.663 & 311.291\\
+\hspace{1em}cif-standard & 0.199 (0.005) & 0.839 (0.005) & 74.710 & 369.446\\
+\hspace{1em}nn-cox & 0.187 (0.020) & 0.826 (0.009) & 59.242 & 95.742\\
+\hspace{1em}cif-rotate & 0.172 (0.006) & 0.806 (0.007) & 581.038 & 67.850\\
+\hspace{1em}ranger-extratrees & 0.171 (0.004) & 0.824 (0.005) & 326.124 & 86.921\\
+\hspace{1em}glmnet-cox & 0.164 (0.046) & 0.816 (0.019) & 2.424 & 0.012\\
+\hspace{1em}aorsf-random & 0.139 (0.005) & 0.789 (0.006) & 15.571 & 1.574\\
+\hspace{1em}xgboost-cox & 0.121 (0.018) & 0.845 (0.005) & 11.223 & 0.015\\
+\hspace{1em}cif-extension & 0.109 (0.003) & 0.809 (0.006) & 170.011 & 49.372\\
+\hspace{1em}xgboost-aft & --- & 0.844 (0.005) & 26.160 & 0.014\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{ARIC; stroke, n = 13623, p = 41}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.094 (0.004) & 0.795 (0.007) & 4.109 & 1.124\\
-\hspace{1em}rsf-standard & 0.091 (0.005) & 0.785 (0.007) & 7.142 & 0.915\\
-\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.793 (0.008) & 13.304 & 1.124\\
-\hspace{1em}aorsf-net & 0.087 (0.018) & 0.786 (0.032) & 391.565 & 1.201\\
-\hspace{1em}obliqueRSF-net & 0.082 (0.003) & 0.792 (0.007) & 1773.436 & 379.126\\
-\hspace{1em}glmnet-cox & 0.078 (0.005) & 0.788 (0.007) & 1.789 & 0.010\\
-\hspace{1em}cif-standard & 0.074 (0.003) & 0.789 (0.007) & 72.507 & 366.228\\
-\hspace{1em}nn-cox & 0.072 (0.013) & 0.781 (0.010) & 32.716 & 93.157\\
-\hspace{1em}ranger-extratrees & 0.068 (0.003) & 0.780 (0.009) & 256.826 & 67.732\\
-\hspace{1em}aorsf-random & 0.059 (0.004) & 0.751 (0.009) & 9.314 & 1.118\\
-\hspace{1em}cif-rotate & 0.052 (0.003) & 0.769 (0.009) & 588.245 & 70.061\\
-\hspace{1em}xgboost-cox & 0.046 (0.014) & 0.794 (0.006) & 6.688 & 0.014\\
-\hspace{1em}cif-extension & 0.036 (0.002) & 0.772 (0.008) & 169.525 & 51.117\\
-\hspace{1em}xgboost-aft & -6.54 (0.420) & 0.793 (0.007) & 21.053 & 0.013\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-fast & 0.093 (0.004) & 0.794 (0.007) & 4.101 & 1.127\\
+\hspace{1em}rsf-standard & 0.090 (0.006) & 0.785 (0.007) & 7.258 & 0.919\\
+\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.793 (0.007) & 13.277 & 1.119\\
+\hspace{1em}aorsf-net & 0.087 (0.017) & 0.786 (0.031) & 388.977 & 1.200\\
+\hspace{1em}obliqueRSF-net & 0.082 (0.003) & 0.792 (0.007) & 1768.748 & 384.697\\
+\hspace{1em}glmnet-cox & 0.078 (0.005) & 0.788 (0.007) & 1.662 & 0.010\\
+\hspace{1em}cif-standard & 0.073 (0.003) & 0.788 (0.007) & 72.160 & 363.855\\
+\hspace{1em}nn-cox & 0.071 (0.013) & 0.781 (0.009) & 31.997 & 88.257\\
+\hspace{1em}ranger-extratrees & 0.067 (0.003) & 0.780 (0.008) & 249.618 & 67.732\\
+\hspace{1em}aorsf-random & 0.059 (0.004) & 0.751 (0.009) & 9.374 & 1.121\\
+\hspace{1em}cif-rotate & 0.052 (0.003) & 0.769 (0.009) & 592.458 & 70.175\\
+\hspace{1em}xgboost-cox & 0.047 (0.013) & 0.794 (0.006) & 6.688 & 0.014\\
+\hspace{1em}cif-extension & 0.036 (0.002) & 0.771 (0.008) & 170.852 & 51.402\\
+\hspace{1em}xgboost-aft & --- & 0.793 (0.007) & 21.053 & 0.013\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Colon cancer; death, n = 929, p = 12}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.098 (0.014) & 0.716 (0.012) & 0.228 & 0.050\\
-\hspace{1em}aorsf-cph & 0.098 (0.014) & 0.715 (0.011) & 0.632 & 0.051\\
-\hspace{1em}cif-standard & 0.096 (0.014) & 0.709 (0.012) & 0.666 & 3.606\\
-\hspace{1em}aorsf-random & 0.094 (0.009) & 0.714 (0.011) & 1.002 & 0.045\\
-\hspace{1em}aorsf-net & 0.090 (0.025) & 0.708 (0.037) & 49.445 & 0.046\\
-\hspace{1em}obliqueRSF-net & 0.088 (0.006) & 0.716 (0.012) & 250.492 & 16.952\\
-\hspace{1em}cif-rotate & 0.085 (0.018) & 0.704 (0.014) & 12.226 & 3.491\\
-\hspace{1em}rsf-standard & 0.084 (0.019) & 0.702 (0.010) & 1.526 & 0.149\\
-\hspace{1em}ranger-extratrees & 0.082 (0.007) & 0.710 (0.011) & 0.090 & 0.245\\
-\hspace{1em}cif-extension & 0.080 (0.006) & 0.708 (0.012) & 8.368 & 4.020\\
-\hspace{1em}glmnet-cox & 0.073 (0.014) & 0.709 (0.017) & 0.104 & 0.003\\
-\hspace{1em}xgboost-cox & 0.061 (0.013) & 0.699 (0.012) & 3.172 & 0.003\\
-\hspace{1em}nn-cox & -0.003 (0.003) & 0.511 (0.022) & 11.966 & 1.368\\
-\hspace{1em}xgboost-aft & -1.12 (0.214) & 0.705 (0.014) & 11.661 & 0.006\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-fast & 0.098 (0.013) & 0.718 (0.012) & 0.228 & 0.050\\
+\hspace{1em}aorsf-cph & 0.097 (0.013) & 0.717 (0.012) & 0.630 & 0.051\\
+\hspace{1em}cif-standard & 0.096 (0.013) & 0.710 (0.012) & 0.670 & 3.620\\
+\hspace{1em}aorsf-random & 0.094 (0.009) & 0.715 (0.012) & 0.992 & 0.045\\
+\hspace{1em}aorsf-net & 0.090 (0.024) & 0.710 (0.036) & 49.564 & 0.046\\
+\hspace{1em}obliqueRSF-net & 0.088 (0.006) & 0.717 (0.012) & 250.492 & 16.952\\
+\hspace{1em}cif-rotate & 0.086 (0.018) & 0.705 (0.015) & 12.341 & 3.533\\
+\hspace{1em}rsf-standard & 0.085 (0.019) & 0.703 (0.011) & 1.557 & 0.151\\
+\hspace{1em}ranger-extratrees & 0.082 (0.007) & 0.710 (0.012) & 0.089 & 0.241\\
+\hspace{1em}cif-extension & 0.080 (0.006) & 0.709 (0.012) & 8.368 & 3.934\\
+\hspace{1em}glmnet-cox & 0.072 (0.013) & 0.709 (0.018) & 0.104 & 0.003\\
+\hspace{1em}xgboost-cox & 0.061 (0.012) & 0.700 (0.013) & 3.143 & 0.003\\
+\hspace{1em}nn-cox & -0.003 (0.003) & 0.515 (0.030) & 11.966 & 1.368\\
+\hspace{1em}xgboost-aft & --- & 0.706 (0.014) & 11.263 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Colon cancer; recurrence, n = 929, p = 12}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.097 (0.016) & 0.711 (0.015) & 0.228 & 0.050\\
-\hspace{1em}aorsf-cph & 0.096 (0.017) & 0.710 (0.014) & 0.641 & 0.050\\
-\hspace{1em}cif-standard & 0.089 (0.016) & 0.698 (0.015) & 0.661 & 3.398\\
-\hspace{1em}obliqueRSF-net & 0.086 (0.009) & 0.708 (0.014) & 258.163 & 16.636\\
-\hspace{1em}aorsf-net & 0.085 (0.044) & 0.705 (0.025) & 50.808 & 0.048\\
-\hspace{1em}aorsf-random & 0.085 (0.013) & 0.700 (0.015) & 0.998 & 0.047\\
-\hspace{1em}cif-rotate & 0.083 (0.020) & 0.694 (0.016) & 12.335 & 3.554\\
-\hspace{1em}cif-extension & 0.081 (0.008) & 0.704 (0.015) & 8.129 & 3.884\\
-\hspace{1em}rsf-standard & 0.078 (0.021) & 0.692 (0.014) & 1.621 & 0.147\\
-\hspace{1em}ranger-extratrees & 0.077 (0.011) & 0.697 (0.014) & 0.090 & 0.238\\
-\hspace{1em}glmnet-cox & 0.071 (0.018) & 0.702 (0.024) & 0.115 & 0.003\\
-\hspace{1em}xgboost-cox & 0.058 (0.010) & 0.691 (0.016) & 3.002 & 0.003\\
-\hspace{1em}nn-cox & -0.014 (0.033) & 0.502 (0.035) & 13.490 & 1.248\\
-\hspace{1em}xgboost-aft & -1.22 (0.257) & 0.698 (0.017) & 12.295 & 0.006\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-fast & 0.099 (0.017) & 0.713 (0.016) & 0.229 & 0.050\\
+\hspace{1em}aorsf-cph & 0.098 (0.016) & 0.712 (0.015) & 0.639 & 0.051\\
+\hspace{1em}cif-standard & 0.090 (0.016) & 0.701 (0.017) & 0.665 & 3.411\\
+\hspace{1em}aorsf-net & 0.087 (0.042) & 0.708 (0.026) & 50.808 & 0.048\\
+\hspace{1em}obliqueRSF-net & 0.087 (0.009) & 0.710 (0.016) & 258.163 & 16.507\\
+\hspace{1em}aorsf-random & 0.086 (0.013) & 0.702 (0.016) & 1.023 & 0.047\\
+\hspace{1em}cif-rotate & 0.084 (0.021) & 0.695 (0.018) & 12.248 & 3.554\\
+\hspace{1em}cif-extension & 0.081 (0.009) & 0.706 (0.017) & 8.129 & 3.936\\
+\hspace{1em}rsf-standard & 0.080 (0.021) & 0.694 (0.015) & 1.654 & 0.147\\
+\hspace{1em}ranger-extratrees & 0.079 (0.011) & 0.699 (0.016) & 0.090 & 0.242\\
+\hspace{1em}glmnet-cox & 0.071 (0.018) & 0.704 (0.024) & 0.116 & 0.003\\
+\hspace{1em}xgboost-cox & 0.059 (0.011) & 0.694 (0.018) & 3.002 & 0.003\\
+\hspace{1em}nn-cox & -0.014 (0.032) & 0.503 (0.034) & 13.121 & 1.248\\
+\hspace{1em}xgboost-aft & --- & 0.701 (0.019) & 12.035 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Early breast cancer; recurrence or death, n = 614, p = 1692}}}\\
 \hline
-\hspace{1em}obliqueRSF-net & 0.072 (0.024) & 0.750 (0.028) & 1858.856 & 13.453\\
-\hspace{1em}cif-rotate & 0.070 (0.018) & 0.747 (0.028) & 6486.756 & 347.401\\
-\hspace{1em}cif-standard & 0.068 (0.018) & 0.747 (0.028) & 8.224 & 4.008\\
-\hspace{1em}aorsf-cph & 0.065 (0.031) & 0.744 (0.023) & 1.313 & 0.182\\
-\hspace{1em}cif-extension & 0.065 (0.015) & 0.746 (0.026) & 43.993 & 6.218\\
-\hspace{1em}aorsf-fast & 0.064 (0.030) & 0.746 (0.024) & 0.746 & 0.180\\
-\hspace{1em}ranger-extratrees & 0.061 (0.023) & 0.743 (0.028) & 0.218 & 0.658\\
-\hspace{1em}glmnet-cox & 0.041 (0.032) & 0.725 (0.035) & 5.758 & 0.006\\
-\hspace{1em}aorsf-random & 0.027 (0.015) & 0.693 (0.039) & 1.671 & 0.174\\
-\hspace{1em}xgboost-cox & 0.026 (0.035) & 0.741 (0.028) & 2.272 & 0.007\\
-\hspace{1em}rsf-standard & 0.021 (0.041) & 0.695 (0.032) & 0.777 & 0.314\\
-\hspace{1em}nn-cox & -0.020 (0.076) & 0.680 (0.050) & 16.928 & 1.662\\
-\hspace{1em}aorsf-net & -0.048 (0.260) & 0.730 (0.055) & 455.331 & 0.176\\
-\hspace{1em}xgboost-aft & -3.08 (0.662) & 0.742 (0.024) & 9.532 & 0.010\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}obliqueRSF-net & 0.073 (0.023) & 0.750 (0.027) & 1867.035 & 13.505\\
+\hspace{1em}cif-rotate & 0.071 (0.017) & 0.746 (0.027) & 6498.327 & 347.595\\
+\hspace{1em}cif-standard & 0.068 (0.017) & 0.746 (0.028) & 8.392 & 4.008\\
+\hspace{1em}aorsf-cph & 0.066 (0.030) & 0.744 (0.022) & 1.313 & 0.182\\
+\hspace{1em}aorsf-fast & 0.065 (0.029) & 0.745 (0.023) & 0.740 & 0.180\\
+\hspace{1em}cif-extension & 0.065 (0.014) & 0.745 (0.025) & 43.993 & 6.218\\
+\hspace{1em}ranger-extratrees & 0.061 (0.022) & 0.741 (0.028) & 0.218 & 0.676\\
+\hspace{1em}glmnet-cox & 0.044 (0.032) & 0.724 (0.034) & 5.824 & 0.006\\
+\hspace{1em}aorsf-random & 0.027 (0.014) & 0.694 (0.038) & 1.692 & 0.172\\
+\hspace{1em}xgboost-cox & 0.027 (0.034) & 0.740 (0.027) & 2.297 & 0.007\\
+\hspace{1em}rsf-standard & 0.021 (0.039) & 0.692 (0.032) & 0.777 & 0.314\\
+\hspace{1em}nn-cox & -0.017 (0.073) & 0.681 (0.048) & 16.971 & 1.662\\
+\hspace{1em}aorsf-net & -0.039 (0.249) & 0.731 (0.052) & 455.331 & 0.176\\
+\hspace{1em}xgboost-aft & --- & 0.741 (0.023) & 9.590 & 0.010\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{FCL; death, n = 541, p = 7}}}\\
 \hline
-\hspace{1em}glmnet-cox & 0.115 (0.031) & 0.783 (0.037) & 0.091 & 0.002\\
-\hspace{1em}aorsf-fast & 0.098 (0.040) & 0.767 (0.032) & 0.079 & 0.019\\
-\hspace{1em}aorsf-cph & 0.097 (0.041) & 0.768 (0.033) & 0.166 & 0.019\\
-\hspace{1em}aorsf-net & 0.092 (0.043) & 0.750 (0.051) & 13.196 & 0.019\\
-\hspace{1em}obliqueRSF-net & 0.090 (0.029) & 0.760 (0.038) & 96.051 & 5.285\\
-\hspace{1em}cif-extension & 0.087 (0.039) & 0.731 (0.038) & 5.172 & 2.488\\
-\hspace{1em}aorsf-random & 0.086 (0.030) & 0.757 (0.034) & 0.267 & 0.019\\
-\hspace{1em}cif-rotate & 0.086 (0.053) & 0.757 (0.030) & 6.010 & 2.042\\
-\hspace{1em}cif-standard & 0.085 (0.040) & 0.747 (0.036) & 0.290 & 1.114\\
-\hspace{1em}ranger-extratrees & 0.075 (0.016) & 0.741 (0.033) & 0.044 & 0.083\\
-\hspace{1em}rsf-standard & 0.070 (0.052) & 0.733 (0.037) & 0.109 & 0.038\\
-\hspace{1em}xgboost-cox & 0.036 (0.054) & 0.689 (0.112) & 0.348 & 0.002\\
-\hspace{1em}nn-cox & -0.003 (0.023) & 0.527 (0.112) & 11.211 & 0.423\\
-\hspace{1em}xgboost-aft & -2.56 (0.515) & 0.753 (0.039) & 7.831 & 0.006\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}glmnet-cox & 0.116 (0.029) & 0.787 (0.037) & 0.091 & 0.002\\
+\hspace{1em}aorsf-fast & 0.100 (0.040) & 0.768 (0.033) & 0.079 & 0.019\\
+\hspace{1em}aorsf-cph & 0.100 (0.041) & 0.769 (0.033) & 0.165 & 0.019\\
+\hspace{1em}aorsf-net & 0.093 (0.043) & 0.752 (0.049) & 13.137 & 0.019\\
+\hspace{1em}obliqueRSF-net & 0.090 (0.028) & 0.761 (0.037) & 96.051 & 5.285\\
+\hspace{1em}cif-extension & 0.086 (0.038) & 0.731 (0.036) & 5.213 & 2.395\\
+\hspace{1em}aorsf-random & 0.086 (0.031) & 0.757 (0.033) & 0.259 & 0.019\\
+\hspace{1em}cif-rotate & 0.085 (0.050) & 0.756 (0.028) & 6.045 & 2.042\\
+\hspace{1em}cif-standard & 0.085 (0.040) & 0.747 (0.035) & 0.289 & 1.106\\
+\hspace{1em}ranger-extratrees & 0.073 (0.017) & 0.742 (0.032) & 0.043 & 0.083\\
+\hspace{1em}rsf-standard & 0.071 (0.051) & 0.733 (0.036) & 0.111 & 0.038\\
+\hspace{1em}xgboost-cox & 0.033 (0.052) & 0.697 (0.109) & 0.374 & 0.002\\
+\hspace{1em}nn-cox & -0.003 (0.022) & 0.534 (0.114) & 11.145 & 0.437\\
+\hspace{1em}xgboost-aft & --- & 0.756 (0.039) & 7.831 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{FCL; relapse, n = 541, p = 7}}}\\
 \hline
-\hspace{1em}glmnet-cox & 0.028 (0.018) & 0.617 (0.024) & 0.089 & 0.002\\
-\hspace{1em}ranger-extratrees & 0.017 (0.016) & 0.593 (0.026) & 0.033 & 0.081\\
-\hspace{1em}obliqueRSF-net & 0.013 (0.016) & 0.590 (0.025) & 217.653 & 6.187\\
-\hspace{1em}aorsf-random & 0.012 (0.018) & 0.595 (0.026) & 0.395 & 0.021\\
-\hspace{1em}xgboost-cox & 0.012 (0.015) & 0.597 (0.032) & 1.357 & 0.002\\
-\hspace{1em}aorsf-cph & 0.007 (0.022) & 0.595 (0.027) & 0.262 & 0.023\\
-\hspace{1em}aorsf-fast & 0.007 (0.021) & 0.594 (0.026) & 0.111 & 0.022\\
-\hspace{1em}cif-standard & 0.006 (0.020) & 0.592 (0.023) & 0.293 & 1.114\\
-\hspace{1em}aorsf-net & 0.006 (0.022) & 0.591 (0.028) & 19.287 & 0.022\\
-\hspace{1em}nn-cox & -0.001 (0.023) & 0.551 (0.062) & 11.433 & 0.439\\
-\hspace{1em}cif-extension & -0.007 (0.024) & 0.576 (0.029) & 5.918 & 2.338\\
-\hspace{1em}cif-rotate & -0.016 (0.026) & 0.579 (0.031) & 7.022 & 1.987\\
-\hspace{1em}rsf-standard & -0.028 (0.033) & 0.576 (0.026) & 0.833 & 0.086\\
-\hspace{1em}xgboost-aft & -0.897 (0.328) & 0.581 (0.037) & 6.337 & 0.006\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}glmnet-cox & 0.027 (0.018) & 0.619 (0.025) & 0.089 & 0.002\\
+\hspace{1em}ranger-extratrees & 0.016 (0.015) & 0.594 (0.025) & 0.032 & 0.080\\
+\hspace{1em}obliqueRSF-net & 0.011 (0.016) & 0.589 (0.023) & 217.918 & 6.187\\
+\hspace{1em}aorsf-random & 0.011 (0.018) & 0.594 (0.025) & 0.395 & 0.021\\
+\hspace{1em}xgboost-cox & 0.010 (0.016) & 0.596 (0.031) & 1.291 & 0.002\\
+\hspace{1em}aorsf-fast & 0.005 (0.020) & 0.592 (0.026) & 0.111 & 0.022\\
+\hspace{1em}aorsf-cph & 0.005 (0.021) & 0.593 (0.027) & 0.262 & 0.022\\
+\hspace{1em}cif-standard & 0.005 (0.020) & 0.591 (0.022) & 0.290 & 1.120\\
+\hspace{1em}aorsf-net & 0.005 (0.021) & 0.590 (0.027) & 19.255 & 0.022\\
+\hspace{1em}nn-cox & -0.003 (0.023) & 0.544 (0.064) & 11.514 & 0.442\\
+\hspace{1em}cif-extension & -0.007 (0.023) & 0.576 (0.028) & 6.044 & 2.303\\
+\hspace{1em}cif-rotate & -0.015 (0.025) & 0.580 (0.030) & 6.986 & 1.965\\
+\hspace{1em}rsf-standard & -0.030 (0.032) & 0.575 (0.025) & 0.843 & 0.086\\
+\hspace{1em}xgboost-aft & --- & 0.580 (0.035) & 6.226 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{GBSG II; recurrence or death, n = 686, p = 10}}}\\
 \hline
-\hspace{1em}obliqueRSF-net & 0.122 (0.015) & 0.744 (0.017) & 313.230 & 6.842\\
-\hspace{1em}cif-standard & 0.121 (0.020) & 0.741 (0.020) & 0.426 & 1.769\\
-\hspace{1em}rsf-standard & 0.118 (0.024) & 0.735 (0.020) & 1.394 & 0.116\\
-\hspace{1em}aorsf-cph & 0.117 (0.026) & 0.734 (0.018) & 0.407 & 0.038\\
-\hspace{1em}aorsf-fast & 0.114 (0.025) & 0.731 (0.017) & 0.171 & 0.039\\
-\hspace{1em}cif-extension & 0.113 (0.018) & 0.741 (0.020) & 8.106 & 3.385\\
-\hspace{1em}aorsf-net & 0.109 (0.058) & 0.732 (0.036) & 37.488 & 0.038\\
-\hspace{1em}cif-rotate & 0.107 (0.025) & 0.729 (0.018) & 10.819 & 2.645\\
-\hspace{1em}aorsf-random & 0.103 (0.025) & 0.722 (0.026) & 0.786 & 0.036\\
-\hspace{1em}ranger-extratrees & 0.094 (0.019) & 0.736 (0.025) & 0.051 & 0.136\\
-\hspace{1em}glmnet-cox & 0.089 (0.018) & 0.726 (0.021) & 0.098 & 0.002\\
-\hspace{1em}xgboost-cox & 0.080 (0.017) & 0.729 (0.018) & 2.465 & 0.003\\
-\hspace{1em}nn-cox & -0.003 (0.005) & 0.524 (0.052) & 11.570 & 0.838\\
-\hspace{1em}xgboost-aft & -1.10 (0.165) & 0.728 (0.022) & 10.557 & 0.006\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}obliqueRSF-net & 0.124 (0.016) & 0.746 (0.018) & 307.849 & 6.881\\
+\hspace{1em}cif-standard & 0.123 (0.020) & 0.743 (0.020) & 0.430 & 1.769\\
+\hspace{1em}rsf-standard & 0.120 (0.024) & 0.737 (0.020) & 1.508 & 0.116\\
+\hspace{1em}aorsf-cph & 0.120 (0.026) & 0.736 (0.018) & 0.406 & 0.038\\
+\hspace{1em}aorsf-fast & 0.117 (0.025) & 0.733 (0.017) & 0.168 & 0.039\\
+\hspace{1em}cif-extension & 0.115 (0.018) & 0.743 (0.020) & 7.990 & 3.331\\
+\hspace{1em}aorsf-net & 0.112 (0.056) & 0.734 (0.036) & 37.488 & 0.038\\
+\hspace{1em}cif-rotate & 0.107 (0.024) & 0.729 (0.018) & 10.801 & 2.745\\
+\hspace{1em}aorsf-random & 0.105 (0.025) & 0.724 (0.026) & 0.785 & 0.036\\
+\hspace{1em}ranger-extratrees & 0.095 (0.018) & 0.738 (0.025) & 0.052 & 0.136\\
+\hspace{1em}glmnet-cox & 0.090 (0.018) & 0.728 (0.021) & 0.098 & 0.002\\
+\hspace{1em}xgboost-cox & 0.082 (0.017) & 0.730 (0.019) & 2.465 & 0.003\\
+\hspace{1em}nn-cox & -0.003 (0.005) & 0.521 (0.051) & 11.570 & 0.838\\
+\hspace{1em}xgboost-aft & --- & 0.730 (0.022) & 10.495 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{GUIDE-IT; CVD death, n = 894, p = 59}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.078 (0.017) & 0.751 (0.026) & 0.160 & 0.037\\
-\hspace{1em}aorsf-net & 0.076 (0.017) & 0.748 (0.027) & 27.393 & 0.039\\
-\hspace{1em}aorsf-cph & 0.073 (0.019) & 0.746 (0.029) & 0.379 & 0.037\\
-\hspace{1em}glmnet-cox & 0.067 (0.042) & 0.719 (0.087) & 0.498 & 0.003\\
-\hspace{1em}obliqueRSF-net & 0.064 (0.013) & 0.744 (0.023) & 221.509 & 11.260\\
-\hspace{1em}cif-rotate & 0.060 (0.014) & 0.720 (0.025) & 34.884 & 5.270\\
-\hspace{1em}cif-standard & 0.059 (0.014) & 0.741 (0.023) & 0.880 & 3.606\\
-\hspace{1em}ranger-extratrees & 0.054 (0.013) & 0.741 (0.030) & 0.091 & 0.178\\
-\hspace{1em}cif-extension & 0.052 (0.012) & 0.730 (0.024) & 13.387 & 5.416\\
-\hspace{1em}rsf-standard & 0.049 (0.022) & 0.708 (0.027) & 0.169 & 0.058\\
-\hspace{1em}xgboost-cox & 0.041 (0.045) & 0.745 (0.018) & 3.691 & 0.003\\
-\hspace{1em}aorsf-random & 0.033 (0.013) & 0.700 (0.029) & 0.499 & 0.039\\
-\hspace{1em}nn-cox & 0.006 (0.017) & 0.622 (0.088) & 10.440 & 0.558\\
-\hspace{1em}xgboost-aft & -5.08 (1.03) & 0.734 (0.021) & 10.919 & 0.006\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-fast & 0.076 (0.017) & 0.748 (0.028) & 0.160 & 0.037\\
+\hspace{1em}aorsf-net & 0.075 (0.017) & 0.746 (0.028) & 27.437 & 0.039\\
+\hspace{1em}aorsf-cph & 0.072 (0.018) & 0.744 (0.029) & 0.379 & 0.037\\
+\hspace{1em}glmnet-cox & 0.068 (0.040) & 0.721 (0.084) & 0.510 & 0.003\\
+\hspace{1em}obliqueRSF-net & 0.063 (0.013) & 0.742 (0.024) & 222.174 & 11.114\\
+\hspace{1em}cif-rotate & 0.060 (0.013) & 0.721 (0.027) & 35.135 & 5.270\\
+\hspace{1em}cif-standard & 0.059 (0.013) & 0.739 (0.023) & 1.108 & 3.576\\
+\hspace{1em}ranger-extratrees & 0.054 (0.012) & 0.740 (0.029) & 0.091 & 0.183\\
+\hspace{1em}cif-extension & 0.052 (0.011) & 0.730 (0.023) & 13.427 & 5.518\\
+\hspace{1em}rsf-standard & 0.048 (0.021) & 0.707 (0.026) & 0.169 & 0.060\\
+\hspace{1em}xgboost-cox & 0.045 (0.045) & 0.746 (0.019) & 3.514 & 0.003\\
+\hspace{1em}aorsf-random & 0.033 (0.013) & 0.700 (0.029) & 0.511 & 0.039\\
+\hspace{1em}nn-cox & 0.009 (0.020) & 0.628 (0.086) & 10.335 & 0.565\\
+\hspace{1em}xgboost-aft & --- & 0.733 (0.021) & 10.963 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{GUIDE-IT; HF hospitalization, n = 894, p = 59}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.080 (0.020) & 0.722 (0.027) & 0.241 & 0.053\\
-\hspace{1em}aorsf-cph & 0.080 (0.019) & 0.721 (0.025) & 0.691 & 0.054\\
-\hspace{1em}obliqueRSF-net & 0.073 (0.011) & 0.720 (0.025) & 382.054 & 9.235\\
-\hspace{1em}ranger-extratrees & 0.072 (0.010) & 0.721 (0.023) & 0.107 & 0.191\\
-\hspace{1em}aorsf-net & 0.072 (0.043) & 0.716 (0.037) & 53.293 & 0.057\\
-\hspace{1em}cif-standard & 0.069 (0.011) & 0.715 (0.025) & 0.802 & 3.237\\
-\hspace{1em}cif-rotate & 0.066 (0.020) & 0.706 (0.031) & 41.812 & 5.179\\
-\hspace{1em}cif-extension & 0.064 (0.009) & 0.715 (0.023) & 14.460 & 5.513\\
-\hspace{1em}glmnet-cox & 0.059 (0.021) & 0.700 (0.026) & 0.453 & 0.003\\
-\hspace{1em}rsf-standard & 0.056 (0.023) & 0.693 (0.027) & 1.503 & 0.119\\
-\hspace{1em}aorsf-random & 0.049 (0.010) & 0.683 (0.024) & 0.914 & 0.053\\
-\hspace{1em}nn-cox & 0.044 (0.027) & 0.694 (0.041) & 12.746 & 0.589\\
-\hspace{1em}xgboost-cox & 0.038 (0.018) & 0.698 (0.028) & 2.920 & 0.003\\
-\hspace{1em}xgboost-aft & -2.24 (0.328) & 0.696 (0.027) & 13.125 & 0.006\\
-\addlinespace[0.3em]
-\hline
-\multicolumn{5}{l}{\textit{\textbf{Heart Transplant; graft-loss or death, n = 3787, p = 52}}}\\
-\hline
-\hspace{1em}cif-rotate & 0.055 (0.010) & 0.729 (0.017) & 158.010 & 21.041\\
-\hspace{1em}aorsf-net & 0.052 (0.006) & 0.730 (0.013) & 126.426 & 0.231\\
-\hspace{1em}aorsf-fast & 0.051 (0.007) & 0.733 (0.015) & 0.875 & 0.222\\
-\hspace{1em}aorsf-cph & 0.051 (0.006) & 0.732 (0.014) & 3.009 & 0.226\\
-\hspace{1em}cif-standard & 0.049 (0.007) & 0.731 (0.014) & 10.227 & 36.786\\
-\hspace{1em}obliqueRSF-net & 0.048 (0.006) & 0.728 (0.015) & 365.007 & 70.588\\
-\hspace{1em}rsf-standard & 0.047 (0.010) & 0.725 (0.013) & 2.462 & 0.933\\
-\hspace{1em}ranger-extratrees & 0.046 (0.007) & 0.729 (0.014) & 5.510 & 3.387\\
-\hspace{1em}glmnet-cox & 0.036 (0.006) & 0.709 (0.016) & 0.969 & 0.005\\
-\hspace{1em}cif-extension & 0.035 (0.004) & 0.725 (0.018) & 49.685 & 18.172\\
-\hspace{1em}xgboost-cox & 0.030 (0.007) & 0.715 (0.019) & 3.479 & 0.005\\
-\hspace{1em}aorsf-random & 0.028 (0.003) & 0.689 (0.013) & 2.461 & 0.218\\
-\hspace{1em}nn-cox & 0.021 (0.013) & 0.669 (0.043) & 15.828 & 9.990\\
-\hspace{1em}xgboost-aft & -4.46 (0.518) & 0.723 (0.013) & 14.471 & 0.007\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-cph & 0.080 (0.018) & 0.721 (0.024) & 0.683 & 0.054\\
+\hspace{1em}aorsf-fast & 0.079 (0.019) & 0.721 (0.026) & 0.241 & 0.053\\
+\hspace{1em}obliqueRSF-net & 0.072 (0.011) & 0.720 (0.024) & 385.158 & 9.315\\
+\hspace{1em}ranger-extratrees & 0.072 (0.010) & 0.721 (0.023) & 0.236 & 0.189\\
+\hspace{1em}aorsf-net & 0.072 (0.041) & 0.715 (0.036) & 53.536 & 0.057\\
+\hspace{1em}cif-standard & 0.069 (0.010) & 0.715 (0.024) & 0.931 & 3.280\\
+\hspace{1em}cif-rotate & 0.066 (0.019) & 0.706 (0.030) & 41.946 & 5.179\\
+\hspace{1em}cif-extension & 0.063 (0.009) & 0.713 (0.023) & 14.574 & 5.603\\
+\hspace{1em}glmnet-cox & 0.058 (0.020) & 0.699 (0.025) & 0.462 & 0.003\\
+\hspace{1em}rsf-standard & 0.055 (0.022) & 0.692 (0.026) & 1.528 & 0.119\\
+\hspace{1em}aorsf-random & 0.048 (0.010) & 0.682 (0.023) & 0.920 & 0.053\\
+\hspace{1em}nn-cox & 0.046 (0.027) & 0.695 (0.040) & 12.586 & 0.590\\
+\hspace{1em}xgboost-cox & 0.038 (0.017) & 0.697 (0.027) & 2.920 & 0.003\\
+\hspace{1em}xgboost-aft & --- & 0.695 (0.026) & 13.042 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{MESA; coronary heart disease, n = 6785, p = 48}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.064 (0.010) & 0.807 (0.010) & 1.254 & 0.359\\
-\hspace{1em}aorsf-net & 0.063 (0.010) & 0.804 (0.010) & 174.770 & 0.380\\
-\hspace{1em}obliqueRSF-net & 0.062 (0.008) & 0.809 (0.009) & 489.721 & 264.595\\
-\hspace{1em}aorsf-cph & 0.061 (0.010) & 0.801 (0.012) & 5.084 & 0.365\\
-\hspace{1em}cif-standard & 0.059 (0.006) & 0.803 (0.011) & 23.030 & 98.735\\
-\hspace{1em}cif-rotate & 0.058 (0.007) & 0.803 (0.010) & 290.894 & 38.516\\
-\hspace{1em}rsf-standard & 0.057 (0.012) & 0.795 (0.012) & 3.507 & 1.082\\
-\hspace{1em}ranger-extratrees & 0.047 (0.004) & 0.794 (0.010) & 7.733 & 6.984\\
-\hspace{1em}cif-extension & 0.046 (0.003) & 0.805 (0.010) & 99.785 & 30.035\\
-\hspace{1em}glmnet-cox & 0.039 (0.017) & 0.775 (0.016) & 4.983 & 0.007\\
-\hspace{1em}nn-cox & 0.034 (0.014) & 0.771 (0.018) & 16.832 & 16.923\\
-\hspace{1em}aorsf-random & 0.031 (0.005) & 0.735 (0.015) & 3.622 & 0.410\\
-\hspace{1em}xgboost-cox & 0.013 (0.020) & 0.803 (0.010) & 4.416 & 0.008\\
-\hspace{1em}xgboost-aft & -9.73 (1.00) & 0.803 (0.010) & 19.012 & 0.009\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-fast & 0.064 (0.009) & 0.807 (0.010) & 1.254 & 0.359\\
+\hspace{1em}aorsf-net & 0.063 (0.010) & 0.804 (0.010) & 175.507 & 0.380\\
+\hspace{1em}obliqueRSF-net & 0.063 (0.007) & 0.808 (0.009) & 495.036 & 263.736\\
+\hspace{1em}aorsf-cph & 0.061 (0.009) & 0.801 (0.011) & 5.065 & 0.365\\
+\hspace{1em}cif-standard & 0.059 (0.006) & 0.803 (0.010) & 23.165 & 98.928\\
+\hspace{1em}cif-rotate & 0.059 (0.007) & 0.802 (0.010) & 291.147 & 38.590\\
+\hspace{1em}rsf-standard & 0.058 (0.011) & 0.794 (0.011) & 3.497 & 1.115\\
+\hspace{1em}ranger-extratrees & 0.047 (0.004) & 0.794 (0.010) & 8.046 & 7.095\\
+\hspace{1em}cif-extension & 0.047 (0.003) & 0.805 (0.010) & 100.181 & 30.035\\
+\hspace{1em}glmnet-cox & 0.039 (0.016) & 0.775 (0.015) & 4.983 & 0.007\\
+\hspace{1em}nn-cox & 0.034 (0.014) & 0.771 (0.018) & 17.346 & 16.923\\
+\hspace{1em}aorsf-random & 0.031 (0.005) & 0.734 (0.015) & 3.611 & 0.409\\
+\hspace{1em}xgboost-cox & 0.016 (0.022) & 0.804 (0.010) & 4.416 & 0.008\\
+\hspace{1em}xgboost-aft & --- & 0.803 (0.010) & 18.681 & 0.009\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{MESA; death, n = 6793, p = 48}}}\\
 \hline
-\hspace{1em}aorsf-net & 0.144 (0.008) & 0.791 (0.009) & 302.684 & 0.545\\
-\hspace{1em}aorsf-fast & 0.144 (0.008) & 0.792 (0.010) & 1.785 & 0.630\\
-\hspace{1em}aorsf-cph & 0.143 (0.007) & 0.791 (0.009) & 6.757 & 0.532\\
-\hspace{1em}rsf-standard & 0.140 (0.008) & 0.783 (0.009) & 4.567 & 0.475\\
-\hspace{1em}obliqueRSF-net & 0.139 (0.007) & 0.791 (0.010) & 1155.438 & 154.187\\
-\hspace{1em}nn-cox & 0.134 (0.012) & 0.789 (0.010) & 32.143 & 19.831\\
-\hspace{1em}cif-standard & 0.133 (0.006) & 0.788 (0.009) & 23.210 & 99.971\\
-\hspace{1em}glmnet-cox & 0.126 (0.026) & 0.788 (0.012) & 1.504 & 0.006\\
-\hspace{1em}cif-rotate & 0.126 (0.007) & 0.783 (0.010) & 318.556 & 36.862\\
-\hspace{1em}ranger-extratrees & 0.113 (0.004) & 0.784 (0.009) & 7.675 & 6.070\\
-\hspace{1em}cif-extension & 0.092 (0.003) & 0.781 (0.009) & 110.511 & 30.598\\
-\hspace{1em}aorsf-random & 0.069 (0.005) & 0.725 (0.008) & 5.706 & 0.551\\
-\hspace{1em}xgboost-cox & 0.056 (0.030) & 0.794 (0.010) & 8.559 & 0.010\\
-\hspace{1em}xgboost-aft & -4.42 (0.238) & 0.792 (0.009) & 22.063 & 0.009\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-net & 0.145 (0.008) & 0.792 (0.009) & 304.543 & 0.545\\
+\hspace{1em}aorsf-fast & 0.145 (0.009) & 0.792 (0.009) & 1.769 & 0.625\\
+\hspace{1em}aorsf-cph & 0.143 (0.008) & 0.791 (0.009) & 6.747 & 0.522\\
+\hspace{1em}rsf-standard & 0.141 (0.008) & 0.784 (0.009) & 4.694 & 0.475\\
+\hspace{1em}obliqueRSF-net & 0.140 (0.007) & 0.791 (0.009) & 1154.938 & 154.248\\
+\hspace{1em}nn-cox & 0.134 (0.012) & 0.790 (0.010) & 31.798 & 18.891\\
+\hspace{1em}cif-standard & 0.134 (0.007) & 0.788 (0.009) & 23.348 & 100.276\\
+\hspace{1em}glmnet-cox & 0.129 (0.027) & 0.789 (0.012) & 1.504 & 0.007\\
+\hspace{1em}cif-rotate & 0.126 (0.007) & 0.784 (0.010) & 319.140 & 36.836\\
+\hspace{1em}ranger-extratrees & 0.114 (0.004) & 0.784 (0.008) & 7.843 & 6.084\\
+\hspace{1em}cif-extension & 0.092 (0.003) & 0.781 (0.009) & 110.957 & 30.312\\
+\hspace{1em}aorsf-random & 0.069 (0.004) & 0.725 (0.008) & 5.765 & 0.551\\
+\hspace{1em}xgboost-cox & 0.056 (0.029) & 0.794 (0.009) & 8.347 & 0.009\\
+\hspace{1em}xgboost-aft & --- & 0.793 (0.009) & 21.600 & 0.009\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{MESA; heart failure, n = 6785, p = 48}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.114 (0.011) & 0.867 (0.012) & 1.145 & 0.317\\
-\hspace{1em}aorsf-cph & 0.109 (0.012) & 0.859 (0.014) & 4.847 & 0.330\\
-\hspace{1em}rsf-standard & 0.109 (0.012) & 0.857 (0.011) & 3.064 & 1.083\\
-\hspace{1em}obliqueRSF-net & 0.106 (0.008) & 0.869 (0.012) & 402.559 & 332.725\\
-\hspace{1em}cif-rotate & 0.105 (0.010) & 0.870 (0.012) & 262.282 & 37.634\\
-\hspace{1em}cif-standard & 0.101 (0.009) & 0.864 (0.013) & 24.266 & 98.478\\
-\hspace{1em}aorsf-net & 0.098 (0.071) & 0.849 (0.068) & 152.112 & 0.342\\
+\hspace{1em}aorsf-fast & 0.114 (0.010) & 0.867 (0.012) & 1.145 & 0.317\\
+\hspace{1em}aorsf-cph & 0.109 (0.011) & 0.860 (0.014) & 4.847 & 0.330\\
+\hspace{1em}rsf-standard & 0.108 (0.011) & 0.857 (0.010) & 3.069 & 1.095\\
+\hspace{1em}obliqueRSF-net & 0.106 (0.008) & 0.870 (0.012) & 403.026 & 336.427\\
+\hspace{1em}cif-rotate & 0.104 (0.010) & 0.870 (0.012) & 262.282 & 37.519\\
+\hspace{1em}cif-standard & 0.102 (0.009) & 0.865 (0.012) & 24.266 & 98.770\\
+\hspace{1em}aorsf-net & 0.099 (0.067) & 0.851 (0.065) & 152.494 & 0.342\\
 \hspace{1em}cif-extension & 0.076 (0.005) & 0.865 (0.011) & 94.286 & 30.425\\
-\hspace{1em}ranger-extratrees & 0.075 (0.005) & 0.848 (0.015) & 7.014 & 6.801\\
-\hspace{1em}nn-cox & 0.072 (0.027) & 0.828 (0.023) & 15.582 & 14.415\\
-\hspace{1em}aorsf-random & 0.063 (0.006) & 0.796 (0.015) & 2.686 & 0.368\\
-\hspace{1em}glmnet-cox & 0.047 (0.044) & 0.757 (0.153) & 3.628 & 0.007\\
-\hspace{1em}xgboost-cox & -0.011 (0.020) & 0.871 (0.010) & 6.431 & 0.009\\
-\hspace{1em}xgboost-aft & -11.1 (1.34) & 0.871 (0.012) & 20.098 & 0.009\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}ranger-extratrees & 0.075 (0.005) & 0.849 (0.015) & 7.052 & 6.710\\
+\hspace{1em}nn-cox & 0.071 (0.026) & 0.828 (0.022) & 15.582 & 14.999\\
+\hspace{1em}aorsf-random & 0.063 (0.006) & 0.795 (0.015) & 2.638 & 0.368\\
+\hspace{1em}glmnet-cox & 0.044 (0.044) & 0.761 (0.146) & 3.775 & 0.007\\
+\hspace{1em}xgboost-cox & -0.010 (0.020) & 0.871 (0.009) & 6.431 & 0.009\\
+\hspace{1em}xgboost-aft & --- & 0.872 (0.012) & 20.098 & 0.009\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{MESA; stroke, n = 6783, p = 48}}}\\
 \hline
-\hspace{1em}cif-rotate & 0.024 (0.004) & 0.760 (0.017) & 273.629 & 37.321\\
-\hspace{1em}obliqueRSF-net & 0.024 (0.004) & 0.763 (0.015) & 355.997 & 289.216\\
-\hspace{1em}cif-standard & 0.024 (0.004) & 0.758 (0.016) & 23.726 & 98.376\\
-\hspace{1em}aorsf-fast & 0.024 (0.006) & 0.761 (0.015) & 1.099 & 0.313\\
-\hspace{1em}aorsf-cph & 0.023 (0.005) & 0.755 (0.016) & 4.501 & 0.322\\
-\hspace{1em}ranger-extratrees & 0.021 (0.003) & 0.756 (0.015) & 7.037 & 6.789\\
-\hspace{1em}cif-extension & 0.021 (0.002) & 0.766 (0.017) & 95.086 & 29.190\\
-\hspace{1em}glmnet-cox & 0.021 (0.010) & 0.763 (0.017) & 3.726 & 0.007\\
-\hspace{1em}rsf-standard & 0.018 (0.009) & 0.742 (0.018) & 3.127 & 1.058\\
-\hspace{1em}aorsf-net & 0.017 (0.027) & 0.746 (0.045) & 138.918 & 0.330\\
-\hspace{1em}nn-cox & 0.013 (0.009) & 0.721 (0.050) & 17.998 & 20.421\\
-\hspace{1em}aorsf-random & 0.013 (0.003) & 0.710 (0.023) & 2.582 & 0.338\\
-\hspace{1em}xgboost-cox & 0.000 (0.024) & 0.760 (0.019) & 4.044 & 0.008\\
-\hspace{1em}xgboost-aft & -13.7 (1.50) & 0.762 (0.016) & 18.133 & 0.010\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}cif-rotate & 0.025 (0.005) & 0.762 (0.017) & 271.158 & 37.410\\
+\hspace{1em}obliqueRSF-net & 0.025 (0.004) & 0.764 (0.016) & 354.662 & 286.074\\
+\hspace{1em}cif-standard & 0.025 (0.004) & 0.760 (0.017) & 23.751 & 98.574\\
+\hspace{1em}aorsf-fast & 0.024 (0.006) & 0.762 (0.015) & 1.095 & 0.311\\
+\hspace{1em}aorsf-cph & 0.023 (0.005) & 0.756 (0.016) & 4.436 & 0.320\\
+\hspace{1em}ranger-extratrees & 0.022 (0.003) & 0.757 (0.015) & 6.801 & 6.789\\
+\hspace{1em}glmnet-cox & 0.021 (0.010) & 0.764 (0.018) & 3.726 & 0.007\\
+\hspace{1em}cif-extension & 0.021 (0.002) & 0.767 (0.018) & 95.584 & 29.197\\
+\hspace{1em}rsf-standard & 0.019 (0.009) & 0.744 (0.018) & 3.147 & 1.066\\
+\hspace{1em}aorsf-net & 0.018 (0.026) & 0.749 (0.043) & 138.878 & 0.330\\
+\hspace{1em}nn-cox & 0.014 (0.010) & 0.725 (0.051) & 17.348 & 20.132\\
+\hspace{1em}aorsf-random & 0.013 (0.003) & 0.711 (0.023) & 2.519 & 0.338\\
+\hspace{1em}xgboost-cox & -0.001 (0.025) & 0.761 (0.018) & 4.044 & 0.008\\
+\hspace{1em}xgboost-aft & --- & 0.763 (0.016) & 17.880 & 0.010\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Monoclonal gammopathy; death, n = 1384, p = 8}}}\\
 \hline
-\hspace{1em}cif-rotate & 0.157 (0.018) & 0.743 (0.014) & 15.346 & 4.755\\
-\hspace{1em}aorsf-cph & 0.155 (0.015) & 0.741 (0.010) & 1.157 & 0.087\\
-\hspace{1em}aorsf-fast & 0.154 (0.015) & 0.741 (0.009) & 0.393 & 0.087\\
-\hspace{1em}obliqueRSF-net & 0.153 (0.012) & 0.742 (0.010) & 229.434 & 12.810\\
-\hspace{1em}aorsf-net & 0.153 (0.014) & 0.739 (0.009) & 88.786 & 0.087\\
-\hspace{1em}cif-standard & 0.149 (0.013) & 0.737 (0.010) & 0.998 & 5.743\\
-\hspace{1em}rsf-standard & 0.147 (0.016) & 0.735 (0.010) & 2.002 & 0.201\\
-\hspace{1em}aorsf-random & 0.144 (0.013) & 0.733 (0.011) & 1.762 & 0.082\\
-\hspace{1em}cif-extension & 0.142 (0.009) & 0.745 (0.012) & 10.648 & 4.681\\
-\hspace{1em}glmnet-cox & 0.136 (0.020) & 0.726 (0.014) & 0.117 & 0.003\\
-\hspace{1em}xgboost-cox & 0.121 (0.011) & 0.732 (0.011) & 3.801 & 0.003\\
-\hspace{1em}ranger-extratrees & 0.115 (0.004) & 0.742 (0.011) & 0.058 & 0.198\\
-\hspace{1em}nn-cox & 0.031 (0.044) & 0.612 (0.102) & 15.825 & 0.684\\
-\hspace{1em}xgboost-aft & -0.868 (0.152) & 0.732 (0.012) & 12.704 & 0.006\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}cif-rotate & 0.159 (0.019) & 0.744 (0.015) & 15.254 & 4.543\\
+\hspace{1em}aorsf-cph & 0.157 (0.016) & 0.742 (0.011) & 1.155 & 0.087\\
+\hspace{1em}aorsf-fast & 0.156 (0.016) & 0.742 (0.011) & 0.393 & 0.088\\
+\hspace{1em}obliqueRSF-net & 0.155 (0.013) & 0.743 (0.011) & 229.681 & 12.810\\
+\hspace{1em}aorsf-net & 0.154 (0.015) & 0.741 (0.011) & 88.452 & 0.086\\
+\hspace{1em}cif-standard & 0.150 (0.015) & 0.738 (0.012) & 0.989 & 5.746\\
+\hspace{1em}rsf-standard & 0.150 (0.017) & 0.736 (0.011) & 2.022 & 0.201\\
+\hspace{1em}aorsf-random & 0.145 (0.014) & 0.734 (0.012) & 1.762 & 0.082\\
+\hspace{1em}cif-extension & 0.143 (0.010) & 0.747 (0.013) & 10.829 & 4.681\\
+\hspace{1em}glmnet-cox & 0.139 (0.021) & 0.728 (0.014) & 0.118 & 0.003\\
+\hspace{1em}xgboost-cox & 0.123 (0.012) & 0.733 (0.012) & 3.847 & 0.003\\
+\hspace{1em}ranger-extratrees & 0.115 (0.005) & 0.744 (0.012) & 0.060 & 0.184\\
+\hspace{1em}nn-cox & 0.028 (0.043) & 0.606 (0.100) & 15.492 & 0.691\\
+\hspace{1em}xgboost-aft & --- & 0.733 (0.013) & 12.513 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Monoclonal gammopathy; malignancy, n = 1384, p = 8}}}\\
 \hline
-\hspace{1em}glmnet-cox & 0.016 (0.012) & 0.654 (0.050) & 0.104 & 0.002\\
-\hspace{1em}aorsf-cph & 0.011 (0.012) & 0.644 (0.034) & 0.592 & 0.041\\
-\hspace{1em}aorsf-fast & 0.010 (0.013) & 0.641 (0.034) & 0.193 & 0.042\\
-\hspace{1em}ranger-extratrees & 0.008 (0.007) & 0.641 (0.033) & 0.050 & 0.177\\
-\hspace{1em}cif-extension & 0.008 (0.009) & 0.626 (0.026) & 8.936 & 4.415\\
-\hspace{1em}aorsf-random & 0.007 (0.013) & 0.633 (0.034) & 0.519 & 0.041\\
-\hspace{1em}aorsf-net & 0.007 (0.013) & 0.641 (0.032) & 22.912 & 0.042\\
-\hspace{1em}cif-standard & 0.006 (0.009) & 0.627 (0.029) & 1.072 & 6.223\\
-\hspace{1em}xgboost-cox & 0.005 (0.017) & 0.641 (0.036) & 1.798 & 0.003\\
-\hspace{1em}obliqueRSF-net & 0.002 (0.023) & 0.623 (0.040) & 42.157 & 16.489\\
-\hspace{1em}nn-cox & -0.004 (0.006) & 0.502 (0.052) & 10.457 & 0.704\\
-\hspace{1em}rsf-standard & -0.010 (0.016) & 0.615 (0.030) & 0.733 & 0.075\\
-\hspace{1em}cif-rotate & -0.025 (0.023) & 0.550 (0.032) & 12.854 & 4.638\\
-\hspace{1em}xgboost-aft & -5.63 (1.08) & 0.628 (0.039) & 11.106 & 0.006\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}glmnet-cox & 0.015 (0.012) & 0.648 (0.058) & 0.104 & 0.002\\
+\hspace{1em}aorsf-cph & 0.010 (0.011) & 0.644 (0.033) & 0.592 & 0.041\\
+\hspace{1em}aorsf-fast & 0.010 (0.012) & 0.640 (0.033) & 0.192 & 0.042\\
+\hspace{1em}ranger-extratrees & 0.008 (0.006) & 0.642 (0.031) & 0.050 & 0.175\\
+\hspace{1em}cif-extension & 0.008 (0.008) & 0.625 (0.025) & 8.953 & 4.503\\
+\hspace{1em}aorsf-net & 0.007 (0.012) & 0.641 (0.031) & 22.912 & 0.042\\
+\hspace{1em}aorsf-random & 0.007 (0.013) & 0.634 (0.032) & 0.510 & 0.041\\
+\hspace{1em}cif-standard & 0.006 (0.009) & 0.625 (0.028) & 1.137 & 6.173\\
+\hspace{1em}xgboost-cox & 0.005 (0.017) & 0.638 (0.038) & 1.774 & 0.003\\
+\hspace{1em}obliqueRSF-net & 0.003 (0.022) & 0.624 (0.038) & 41.561 & 16.686\\
+\hspace{1em}nn-cox & -0.003 (0.006) & 0.507 (0.055) & 10.592 & 0.704\\
+\hspace{1em}rsf-standard & -0.010 (0.015) & 0.614 (0.029) & 0.744 & 0.074\\
+\hspace{1em}cif-rotate & -0.024 (0.022) & 0.550 (0.032) & 12.665 & 4.579\\
+\hspace{1em}xgboost-aft & --- & 0.627 (0.039) & 11.031 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Movies released in 2015-2018; gross 1M USD, n = 551, p = 46}}}\\
 \hline
-\hspace{1em}cif-rotate & 0.637 (0.023) & 0.943 (0.007) & 19.478 & 3.481\\
-\hspace{1em}glmnet-cox & 0.619 (0.032) & 0.940 (0.009) & 0.177 & 0.002\\
-\hspace{1em}aorsf-net & 0.531 (0.030) & 0.929 (0.011) & 52.072 & 0.044\\
-\hspace{1em}aorsf-cph & 0.523 (0.024) & 0.926 (0.011) & 0.785 & 0.042\\
-\hspace{1em}rsf-standard & 0.520 (0.022) & 0.923 (0.011) & 1.168 & 0.103\\
-\hspace{1em}nn-cox & 0.518 (0.065) & 0.901 (0.027) & 17.218 & 0.694\\
-\hspace{1em}aorsf-fast & 0.517 (0.028) & 0.923 (0.013) & 0.216 & 0.043\\
-\hspace{1em}xgboost-cox & 0.515 (0.028) & 0.932 (0.009) & 13.556 & 0.004\\
-\hspace{1em}cif-standard & 0.473 (0.026) & 0.902 (0.018) & 0.376 & 1.207\\
-\hspace{1em}cif-extension & 0.455 (0.025) & 0.920 (0.013) & 8.982 & 3.967\\
-\hspace{1em}ranger-extratrees & 0.432 (0.023) & 0.900 (0.019) & 0.047 & 0.108\\
-\hspace{1em}obliqueRSF-net & 0.319 (0.023) & 0.909 (0.019) & 154.491 & 9.054\\
-\hspace{1em}aorsf-random & 0.300 (0.035) & 0.850 (0.030) & 0.889 & 0.039\\
-\hspace{1em}xgboost-aft & -0.474 (0.073) & 0.928 (0.010) & 34.905 & 0.007\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}cif-rotate & 0.635 (0.025) & 0.943 (0.007) & 19.464 & 3.497\\
+\hspace{1em}glmnet-cox & 0.616 (0.036) & 0.940 (0.009) & 0.179 & 0.002\\
+\hspace{1em}aorsf-net & 0.529 (0.029) & 0.928 (0.011) & 51.788 & 0.044\\
+\hspace{1em}aorsf-cph & 0.520 (0.024) & 0.925 (0.011) & 0.783 & 0.042\\
+\hspace{1em}rsf-standard & 0.518 (0.022) & 0.922 (0.011) & 1.324 & 0.103\\
+\hspace{1em}aorsf-fast & 0.514 (0.028) & 0.922 (0.013) & 0.216 & 0.043\\
+\hspace{1em}xgboost-cox & 0.514 (0.029) & 0.932 (0.009) & 13.877 & 0.004\\
+\hspace{1em}nn-cox & 0.512 (0.068) & 0.901 (0.027) & 17.133 & 0.681\\
+\hspace{1em}cif-standard & 0.469 (0.028) & 0.901 (0.018) & 0.375 & 1.238\\
+\hspace{1em}cif-extension & 0.452 (0.026) & 0.919 (0.013) & 9.070 & 3.976\\
+\hspace{1em}ranger-extratrees & 0.428 (0.026) & 0.898 (0.019) & 0.047 & 0.108\\
+\hspace{1em}obliqueRSF-net & 0.318 (0.023) & 0.908 (0.018) & 156.326 & 9.034\\
+\hspace{1em}aorsf-random & 0.299 (0.033) & 0.849 (0.029) & 0.901 & 0.039\\
+\hspace{1em}xgboost-aft & --- & 0.927 (0.010) & 35.252 & 0.007\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Non-alcohol fatty liver disease; death, n = 17549, p = 24}}}\\
 \hline
-\hspace{1em}aorsf-cph & 0.213 (0.008) & 0.869 (0.005) & 17.980 & 1.260\\
-\hspace{1em}aorsf-fast & 0.213 (0.009) & 0.870 (0.005) & 4.871 & 1.369\\
-\hspace{1em}aorsf-net & 0.211 (0.008) & 0.865 (0.006) & 452.725 & 1.292\\
-\hspace{1em}obliqueRSF-net & 0.210 (0.008) & 0.869 (0.006) & 1432.168 & 1054.002\\
-\hspace{1em}rsf-standard & 0.207 (0.009) & 0.860 (0.005) & 9.926 & 1.180\\
-\hspace{1em}glmnet-cox & 0.207 (0.010) & 0.861 (0.005) & 1.748 & 0.012\\
-\hspace{1em}cif-standard & 0.206 (0.007) & 0.864 (0.006) & 67.734 & 629.975\\
-\hspace{1em}cif-rotate & 0.191 (0.007) & 0.865 (0.005) & 263.866 & 61.085\\
-\hspace{1em}ranger-extratrees & 0.181 (0.007) & 0.861 (0.005) & 37.518 & 97.910\\
-\hspace{1em}cif-extension & 0.167 (0.003) & 0.867 (0.006) & 125.152 & 53.729\\
-\hspace{1em}aorsf-random & 0.141 (0.007) & 0.839 (0.007) & 9.722 & 1.365\\
-\hspace{1em}xgboost-cox & 0.020 (0.015) & 0.877 (0.005) & 9.143 & 0.018\\
-\hspace{1em}nn-cox & 0.000 (0.000) & 0.558 (0.096) & 22.004 & 120.407\\
-\hspace{1em}xgboost-aft & -7.55 (0.727) & 0.875 (0.005) & 29.714 & 0.014\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-cph & 0.214 (0.008) & 0.869 (0.005) & 17.839 & 1.266\\
+\hspace{1em}aorsf-fast & 0.213 (0.008) & 0.870 (0.005) & 4.838 & 1.314\\
+\hspace{1em}aorsf-net & 0.211 (0.007) & 0.865 (0.006) & 453.851 & 1.297\\
+\hspace{1em}obliqueRSF-net & 0.210 (0.008) & 0.869 (0.005) & 1414.334 & 1054.087\\
+\hspace{1em}rsf-standard & 0.208 (0.009) & 0.860 (0.005) & 9.897 & 1.177\\
+\hspace{1em}glmnet-cox & 0.207 (0.010) & 0.861 (0.005) & 1.745 & 0.012\\
+\hspace{1em}cif-standard & 0.206 (0.007) & 0.864 (0.006) & 67.606 & 629.975\\
+\hspace{1em}cif-rotate & 0.191 (0.007) & 0.866 (0.005) & 262.207 & 61.085\\
+\hspace{1em}ranger-extratrees & 0.181 (0.007) & 0.861 (0.005) & 37.518 & 96.239\\
+\hspace{1em}cif-extension & 0.167 (0.003) & 0.867 (0.006) & 125.152 & 53.538\\
+\hspace{1em}aorsf-random & 0.141 (0.007) & 0.840 (0.006) & 9.678 & 1.364\\
+\hspace{1em}xgboost-cox & 0.021 (0.015) & 0.877 (0.005) & 9.002 & 0.018\\
+\hspace{1em}nn-cox & 0.000 (0.000) & 0.555 (0.092) & 21.841 & 115.006\\
+\hspace{1em}xgboost-aft & --- & 0.875 (0.005) & 29.487 & 0.014\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Primary biliary cholangitis; death, n = 276, p = 19}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.425 (0.029) & 0.905 (0.021) & 0.069 & 0.018\\
-\hspace{1em}aorsf-cph & 0.414 (0.031) & 0.902 (0.021) & 0.150 & 0.018\\
-\hspace{1em}cif-rotate & 0.398 (0.037) & 0.895 (0.021) & 9.844 & 2.240\\
-\hspace{1em}rsf-standard & 0.388 (0.032) & 0.891 (0.022) & 0.093 & 0.038\\
-\hspace{1em}aorsf-net & 0.388 (0.077) & 0.895 (0.030) & 14.684 & 0.019\\
-\hspace{1em}obliqueRSF-net & 0.363 (0.029) & 0.902 (0.022) & 110.615 & 1.817\\
-\hspace{1em}aorsf-random & 0.350 (0.024) & 0.891 (0.019) & 0.283 & 0.019\\
-\hspace{1em}cif-standard & 0.345 (0.031) & 0.899 (0.024) & 0.186 & 0.363\\
-\hspace{1em}cif-extension & 0.342 (0.031) & 0.897 (0.023) & 5.197 & 2.313\\
-\hspace{1em}glmnet-cox & 0.335 (0.045) & 0.881 (0.028) & 0.115 & 0.002\\
-\hspace{1em}ranger-extratrees & 0.271 (0.025) & 0.889 (0.026) & 0.028 & 0.038\\
-\hspace{1em}xgboost-cox & 0.238 (0.105) & 0.874 (0.024) & 4.873 & 0.003\\
-\hspace{1em}nn-cox & -0.019 (0.018) & 0.548 (0.131) & 10.566 & 0.240\\
-\hspace{1em}xgboost-aft & -0.946 (0.320) & 0.879 (0.021) & 9.855 & 0.006\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-fast & 0.431 (0.033) & 0.907 (0.022) & 0.069 & 0.018\\
+\hspace{1em}aorsf-cph & 0.419 (0.034) & 0.905 (0.022) & 0.152 & 0.018\\
+\hspace{1em}cif-rotate & 0.403 (0.042) & 0.897 (0.022) & 9.844 & 2.217\\
+\hspace{1em}aorsf-net & 0.396 (0.078) & 0.899 (0.031) & 14.684 & 0.019\\
+\hspace{1em}rsf-standard & 0.393 (0.036) & 0.894 (0.024) & 0.094 & 0.038\\
+\hspace{1em}obliqueRSF-net & 0.369 (0.034) & 0.905 (0.023) & 110.615 & 1.764\\
+\hspace{1em}aorsf-random & 0.356 (0.029) & 0.894 (0.021) & 0.286 & 0.019\\
+\hspace{1em}cif-standard & 0.351 (0.035) & 0.902 (0.026) & 0.186 & 0.363\\
+\hspace{1em}cif-extension & 0.348 (0.035) & 0.899 (0.024) & 5.248 & 2.252\\
+\hspace{1em}glmnet-cox & 0.340 (0.047) & 0.885 (0.029) & 0.115 & 0.002\\
+\hspace{1em}ranger-extratrees & 0.275 (0.028) & 0.893 (0.027) & 0.028 & 0.037\\
+\hspace{1em}xgboost-cox & 0.249 (0.106) & 0.878 (0.026) & 4.873 & 0.003\\
+\hspace{1em}nn-cox & -0.017 (0.017) & 0.551 (0.130) & 10.566 & 0.240\\
+\hspace{1em}xgboost-aft & --- & 0.882 (0.024) & 10.124 & 0.006\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Rotterdam tumor bank; death, n = 2982, p = 11}}}\\
 \hline
-\hspace{1em}aorsf-net & 0.165 (0.012) & 0.761 (0.009) & 156.800 & 0.190\\
-\hspace{1em}obliqueRSF-net & 0.163 (0.010) & 0.760 (0.009) & 452.125 & 37.754\\
-\hspace{1em}aorsf-cph & 0.162 (0.012) & 0.758 (0.010) & 2.537 & 0.198\\
-\hspace{1em}aorsf-fast & 0.160 (0.013) & 0.756 (0.009) & 0.796 & 0.198\\
-\hspace{1em}cif-standard & 0.159 (0.011) & 0.759 (0.009) & 4.692 & 22.441\\
-\hspace{1em}rsf-standard & 0.158 (0.013) & 0.755 (0.008) & 2.703 & 0.781\\
-\hspace{1em}aorsf-random & 0.153 (0.010) & 0.752 (0.010) & 2.959 & 0.184\\
-\hspace{1em}cif-rotate & 0.148 (0.012) & 0.752 (0.012) & 34.158 & 8.476\\
-\hspace{1em}ranger-extratrees & 0.139 (0.005) & 0.749 (0.009) & 2.888 & 2.552\\
-\hspace{1em}xgboost-cox & 0.132 (0.013) & 0.754 (0.009) & 3.742 & 0.004\\
-\hspace{1em}cif-extension & 0.130 (0.005) & 0.751 (0.009) & 22.061 & 8.711\\
-\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.731 (0.010) & 0.219 & 0.004\\
-\hspace{1em}nn-cox & -0.036 (0.096) & 0.515 (0.044) & 15.998 & 8.140\\
-\hspace{1em}xgboost-aft & -1.37 (0.131) & 0.761 (0.008) & 14.219 & 0.007\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-net & 0.165 (0.012) & 0.761 (0.009) & 156.780 & 0.189\\
+\hspace{1em}obliqueRSF-net & 0.162 (0.010) & 0.760 (0.009) & 449.043 & 37.754\\
+\hspace{1em}aorsf-cph & 0.162 (0.012) & 0.758 (0.009) & 2.515 & 0.198\\
+\hspace{1em}aorsf-fast & 0.159 (0.013) & 0.756 (0.009) & 0.796 & 0.198\\
+\hspace{1em}cif-standard & 0.159 (0.011) & 0.758 (0.009) & 4.650 & 22.504\\
+\hspace{1em}rsf-standard & 0.157 (0.014) & 0.755 (0.009) & 2.710 & 0.802\\
+\hspace{1em}aorsf-random & 0.153 (0.011) & 0.751 (0.010) & 2.990 & 0.184\\
+\hspace{1em}cif-rotate & 0.148 (0.012) & 0.751 (0.012) & 34.249 & 8.476\\
+\hspace{1em}ranger-extratrees & 0.138 (0.006) & 0.748 (0.009) & 2.921 & 2.599\\
+\hspace{1em}xgboost-cox & 0.131 (0.013) & 0.753 (0.010) & 3.742 & 0.004\\
+\hspace{1em}cif-extension & 0.130 (0.004) & 0.751 (0.009) & 22.114 & 8.625\\
+\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.732 (0.009) & 0.212 & 0.004\\
+\hspace{1em}nn-cox & -0.032 (0.092) & 0.513 (0.042) & 16.455 & 8.672\\
+\hspace{1em}xgboost-aft & --- & 0.760 (0.009) & 14.327 & 0.007\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Rotterdam tumor bank; recurrence, n = 2982, p = 11}}}\\
 \hline
-\hspace{1em}obliqueRSF-net & 0.148 (0.011) & 0.736 (0.010) & 534.578 & 39.093\\
-\hspace{1em}aorsf-net & 0.146 (0.013) & 0.735 (0.010) & 162.899 & 0.193\\
-\hspace{1em}cif-standard & 0.144 (0.012) & 0.734 (0.010) & 4.570 & 22.729\\
-\hspace{1em}aorsf-cph & 0.144 (0.013) & 0.734 (0.009) & 2.769 & 0.211\\
-\hspace{1em}aorsf-fast & 0.142 (0.013) & 0.733 (0.010) & 0.869 & 0.210\\
-\hspace{1em}aorsf-random & 0.139 (0.011) & 0.730 (0.009) & 3.217 & 0.190\\
-\hspace{1em}rsf-standard & 0.138 (0.013) & 0.730 (0.009) & 2.838 & 0.633\\
-\hspace{1em}ranger-extratrees & 0.135 (0.008) & 0.734 (0.010) & 2.746 & 2.677\\
-\hspace{1em}cif-rotate & 0.130 (0.011) & 0.726 (0.010) & 36.702 & 8.773\\
-\hspace{1em}cif-extension & 0.119 (0.007) & 0.731 (0.009) & 22.630 & 8.891\\
-\hspace{1em}glmnet-cox & 0.117 (0.009) & 0.727 (0.009) & 0.224 & 0.004\\
-\hspace{1em}xgboost-cox & 0.114 (0.008) & 0.730 (0.010) & 3.367 & 0.004\\
-\hspace{1em}nn-cox & -0.012 (0.031) & 0.498 (0.056) & 18.236 & 9.861\\
-\hspace{1em}xgboost-aft & -1.05 (0.145) & 0.734 (0.010) & 14.853 & 0.007\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}obliqueRSF-net & 0.148 (0.011) & 0.737 (0.010) & 529.355 & 39.185\\
+\hspace{1em}aorsf-net & 0.146 (0.012) & 0.735 (0.009) & 166.455 & 0.193\\
+\hspace{1em}cif-standard & 0.144 (0.011) & 0.734 (0.009) & 4.545 & 22.929\\
+\hspace{1em}aorsf-cph & 0.144 (0.012) & 0.734 (0.009) & 2.760 & 0.211\\
+\hspace{1em}aorsf-fast & 0.143 (0.012) & 0.733 (0.009) & 0.872 & 0.210\\
+\hspace{1em}aorsf-random & 0.140 (0.011) & 0.730 (0.009) & 3.281 & 0.190\\
+\hspace{1em}rsf-standard & 0.138 (0.012) & 0.731 (0.009) & 2.861 & 0.846\\
+\hspace{1em}ranger-extratrees & 0.135 (0.007) & 0.734 (0.009) & 2.765 & 2.677\\
+\hspace{1em}cif-rotate & 0.129 (0.010) & 0.725 (0.009) & 36.702 & 8.632\\
+\hspace{1em}cif-extension & 0.119 (0.006) & 0.731 (0.009) & 22.734 & 8.788\\
+\hspace{1em}glmnet-cox & 0.117 (0.008) & 0.727 (0.009) & 0.227 & 0.004\\
+\hspace{1em}xgboost-cox & 0.114 (0.008) & 0.729 (0.009) & 3.255 & 0.004\\
+\hspace{1em}nn-cox & -0.011 (0.030) & 0.500 (0.055) & 17.957 & 9.371\\
+\hspace{1em}xgboost-aft & --- & 0.735 (0.009) & 14.774 & 0.007\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Serum free light chain; death, n = 7874, p = 10}}}\\
 \hline
-\hspace{1em}aorsf-fast & 0.250 (0.015) & 0.826 (0.008) & 2.023 & 0.596\\
-\hspace{1em}aorsf-cph & 0.250 (0.014) & 0.825 (0.008) & 6.558 & 0.594\\
-\hspace{1em}glmnet-cox & 0.247 (0.012) & 0.820 (0.007) & 0.492 & 0.006\\
-\hspace{1em}obliqueRSF-net & 0.247 (0.012) & 0.821 (0.008) & 1099.217 & 148.193\\
-\hspace{1em}aorsf-net & 0.245 (0.025) & 0.821 (0.014) & 294.157 & 0.564\\
-\hspace{1em}ranger-extratrees & 0.243 (0.010) & 0.821 (0.008) & 9.813 & 11.248\\
-\hspace{1em}cif-standard & 0.243 (0.012) & 0.818 (0.009) & 19.411 & 119.735\\
-\hspace{1em}rsf-standard & 0.242 (0.014) & 0.816 (0.009) & 4.514 & 0.563\\
-\hspace{1em}aorsf-random & 0.232 (0.012) & 0.817 (0.009) & 6.739 & 0.572\\
-\hspace{1em}cif-rotate & 0.227 (0.009) & 0.819 (0.007) & 65.161 & 21.299\\
-\hspace{1em}cif-extension & 0.202 (0.005) & 0.821 (0.008) & 39.535 & 20.315\\
-\hspace{1em}xgboost-cox & 0.091 (0.041) & 0.824 (0.008) & 5.971 & 0.008\\
-\hspace{1em}nn-cox & 0.001 (0.007) & 0.603 (0.111) & 23.138 & 25.985\\
-\hspace{1em}xgboost-aft & -2.81 (0.306) & 0.823 (0.008) & 18.228 & 0.009\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}aorsf-fast & 0.250 (0.014) & 0.826 (0.008) & 2.028 & 0.592\\
+\hspace{1em}aorsf-cph & 0.250 (0.014) & 0.825 (0.008) & 6.526 & 0.593\\
+\hspace{1em}glmnet-cox & 0.247 (0.012) & 0.820 (0.007) & 0.486 & 0.006\\
+\hspace{1em}obliqueRSF-net & 0.247 (0.012) & 0.821 (0.008) & 1094.380 & 148.463\\
+\hspace{1em}aorsf-net & 0.246 (0.024) & 0.821 (0.014) & 293.468 & 0.566\\
+\hspace{1em}ranger-extratrees & 0.243 (0.009) & 0.820 (0.007) & 9.981 & 11.444\\
+\hspace{1em}rsf-standard & 0.243 (0.014) & 0.815 (0.008) & 4.619 & 0.561\\
+\hspace{1em}cif-standard & 0.243 (0.011) & 0.818 (0.008) & 19.411 & 119.478\\
+\hspace{1em}aorsf-random & 0.232 (0.012) & 0.817 (0.008) & 6.725 & 0.570\\
+\hspace{1em}cif-rotate & 0.227 (0.008) & 0.819 (0.007) & 65.281 & 21.263\\
+\hspace{1em}cif-extension & 0.201 (0.005) & 0.820 (0.008) & 39.592 & 20.428\\
+\hspace{1em}xgboost-cox & 0.094 (0.040) & 0.823 (0.008) & 5.798 & 0.008\\
+\hspace{1em}nn-cox & 0.001 (0.006) & 0.591 (0.114) & 23.551 & 26.323\\
+\hspace{1em}xgboost-aft & --- & 0.823 (0.008) & 18.228 & 0.009\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{SPRINT; CVD death, n = 9361, p = 174}}}\\
 \hline
-\hspace{1em}aorsf-net & 0.070 (0.008) & 0.795 (0.012) & 349.169 & 0.675\\
-\hspace{1em}glmnet-cox & 0.070 (0.012) & 0.794 (0.010) & 13.482 & 0.011\\
-\hspace{1em}aorsf-fast & 0.069 (0.006) & 0.796 (0.010) & 2.411 & 0.605\\
-\hspace{1em}aorsf-cph & 0.069 (0.006) & 0.795 (0.011) & 9.085 & 0.617\\
-\hspace{1em}obliqueRSF-net & 0.067 (0.005) & 0.797 (0.012) & 1012.843 & 426.872\\
-\hspace{1em}rsf-standard & 0.064 (0.007) & 0.786 (0.015) & 4.506 & 0.894\\
-\hspace{1em}cif-standard & 0.061 (0.004) & 0.796 (0.011) & 51.748 & 183.859\\
-\hspace{1em}cif-rotate & 0.060 (0.005) & 0.788 (0.011) & 964.703 & 114.180\\
-\hspace{1em}ranger-extratrees & 0.054 (0.003) & 0.791 (0.013) & 7.401 & 8.262\\
-\hspace{1em}nn-cox & 0.036 (0.021) & 0.765 (0.018) & 21.029 & 28.604\\
-\hspace{1em}cif-extension & 0.034 (0.002) & 0.788 (0.011) & 123.576 & 32.717\\
-\hspace{1em}aorsf-random & 0.026 (0.003) & 0.746 (0.017) & 5.646 & 0.745\\
-\hspace{1em}xgboost-cox & 0.007 (0.017) & 0.797 (0.011) & 7.242 & 0.014\\
-\hspace{1em}xgboost-aft & -11.0 (0.929) & 0.794 (0.012) & 20.941 & 0.013\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}glmnet-cox & 0.070 (0.011) & 0.794 (0.010) & 13.586 & 0.010\\
+\hspace{1em}aorsf-net & 0.070 (0.007) & 0.796 (0.011) & 348.986 & 0.675\\
+\hspace{1em}aorsf-fast & 0.069 (0.006) & 0.796 (0.011) & 2.415 & 0.604\\
+\hspace{1em}aorsf-cph & 0.069 (0.006) & 0.796 (0.011) & 9.014 & 0.612\\
+\hspace{1em}obliqueRSF-net & 0.067 (0.005) & 0.797 (0.012) & 1014.547 & 425.668\\
+\hspace{1em}rsf-standard & 0.064 (0.007) & 0.787 (0.014) & 4.574 & 1.245\\
+\hspace{1em}cif-standard & 0.061 (0.004) & 0.797 (0.011) & 51.137 & 182.954\\
+\hspace{1em}cif-rotate & 0.061 (0.005) & 0.789 (0.012) & 971.559 & 115.147\\
+\hspace{1em}ranger-extratrees & 0.054 (0.003) & 0.791 (0.012) & 7.589 & 8.207\\
+\hspace{1em}nn-cox & 0.036 (0.020) & 0.767 (0.019) & 21.632 & 28.604\\
+\hspace{1em}cif-extension & 0.034 (0.002) & 0.788 (0.011) & 124.094 & 32.778\\
+\hspace{1em}aorsf-random & 0.026 (0.003) & 0.746 (0.017) & 5.745 & 0.743\\
+\hspace{1em}xgboost-cox & 0.007 (0.018) & 0.798 (0.011) & 6.861 & 0.014\\
+\hspace{1em}xgboost-aft & --- & 0.794 (0.012) & 21.141 & 0.013\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{SPRINT; death, n = 9361, p = 174}}}\\
 \hline
-\hspace{1em}glmnet-cox & 0.122 (0.012) & 0.770 (0.010) & 5.077 & 0.011\\
-\hspace{1em}aorsf-cph & 0.117 (0.008) & 0.770 (0.009) & 13.329 & 1.489\\
-\hspace{1em}aorsf-fast & 0.116 (0.009) & 0.770 (0.008) & 3.671 & 1.525\\
-\hspace{1em}aorsf-net & 0.113 (0.009) & 0.768 (0.009) & 608.998 & 0.987\\
-\hspace{1em}obliqueRSF-net & 0.112 (0.007) & 0.767 (0.009) & 2613.893 & 241.525\\
-\hspace{1em}rsf-standard & 0.110 (0.007) & 0.763 (0.009) & 6.285 & 0.695\\
-\hspace{1em}cif-standard & 0.106 (0.007) & 0.764 (0.009) & 49.138 & 191.018\\
-\hspace{1em}nn-cox & 0.098 (0.010) & 0.757 (0.010) & 38.077 & 31.856\\
-\hspace{1em}ranger-extratrees & 0.096 (0.005) & 0.756 (0.009) & 9.668 & 9.128\\
-\hspace{1em}cif-rotate & 0.091 (0.006) & 0.745 (0.009) & 1091.007 & 115.077\\
-\hspace{1em}cif-extension & 0.055 (0.002) & 0.747 (0.010) & 136.050 & 33.685\\
-\hspace{1em}aorsf-random & 0.052 (0.003) & 0.719 (0.010) & 9.318 & 1.016\\
-\hspace{1em}xgboost-cox & 0.028 (0.024) & 0.772 (0.008) & 9.389 & 0.013\\
-\hspace{1em}xgboost-aft & -4.51 (0.336) & 0.771 (0.008) & 26.478 & 0.014\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}glmnet-cox & 0.122 (0.011) & 0.770 (0.010) & 5.120 & 0.011\\
+\hspace{1em}aorsf-cph & 0.116 (0.008) & 0.770 (0.009) & 13.398 & 1.453\\
+\hspace{1em}aorsf-fast & 0.116 (0.008) & 0.770 (0.008) & 3.686 & 1.431\\
+\hspace{1em}aorsf-net & 0.113 (0.009) & 0.768 (0.009) & 609.415 & 0.984\\
+\hspace{1em}obliqueRSF-net & 0.112 (0.007) & 0.767 (0.008) & 2609.859 & 237.782\\
+\hspace{1em}rsf-standard & 0.110 (0.007) & 0.762 (0.009) & 6.441 & 0.687\\
+\hspace{1em}cif-standard & 0.106 (0.006) & 0.764 (0.008) & 49.213 & 190.044\\
+\hspace{1em}nn-cox & 0.098 (0.010) & 0.757 (0.010) & 36.524 & 31.856\\
+\hspace{1em}ranger-extratrees & 0.096 (0.005) & 0.756 (0.009) & 10.926 & 9.128\\
+\hspace{1em}cif-rotate & 0.090 (0.006) & 0.745 (0.009) & 1072.994 & 115.077\\
+\hspace{1em}cif-extension & 0.055 (0.002) & 0.746 (0.009) & 136.086 & 33.237\\
+\hspace{1em}aorsf-random & 0.052 (0.003) & 0.719 (0.009) & 9.318 & 1.018\\
+\hspace{1em}xgboost-cox & 0.030 (0.024) & 0.772 (0.008) & 9.349 & 0.013\\
+\hspace{1em}xgboost-aft & --- & 0.771 (0.008) & 26.417 & 0.014\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Systolic Heart Failure; death, n = 2231, p = 41}}}\\
 \hline
-\hspace{1em}obliqueRSF-net & 0.114 (0.012) & 0.747 (0.011) & 376.279 & 24.724\\
-\hspace{1em}cif-rotate & 0.113 (0.013) & 0.741 (0.010) & 70.063 & 10.454\\
-\hspace{1em}glmnet-cox & 0.113 (0.013) & 0.746 (0.011) & 0.260 & 0.003\\
-\hspace{1em}aorsf-net & 0.112 (0.014) & 0.744 (0.011) & 119.643 & 0.160\\
-\hspace{1em}aorsf-cph & 0.111 (0.014) & 0.745 (0.010) & 1.972 & 0.153\\
-\hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 3.959 & 15.682\\
-\hspace{1em}aorsf-fast & 0.110 (0.016) & 0.745 (0.010) & 0.625 & 0.153\\
-\hspace{1em}rsf-standard & 0.105 (0.012) & 0.736 (0.009) & 2.032 & 0.276\\
-\hspace{1em}cif-extension & 0.094 (0.006) & 0.745 (0.011) & 28.859 & 9.510\\
-\hspace{1em}ranger-extratrees & 0.092 (0.008) & 0.738 (0.012) & 2.893 & 1.729\\
-\hspace{1em}xgboost-cox & 0.091 (0.009) & 0.745 (0.009) & 4.478 & 0.004\\
-\hspace{1em}aorsf-random & 0.081 (0.005) & 0.732 (0.012) & 2.335 & 0.150\\
-\hspace{1em}nn-cox & 0.080 (0.024) & 0.710 (0.032) & 19.019 & 4.359\\
-\hspace{1em}xgboost-aft & -2.04 (0.178) & 0.742 (0.008) & 13.559 & 0.007\\
-\addlinespace[0.3em]
-\hline
+\hspace{1em}obliqueRSF-net & 0.114 (0.012) & 0.748 (0.012) & 379.908 & 24.724\\
+\hspace{1em}glmnet-cox & 0.114 (0.013) & 0.747 (0.012) & 0.260 & 0.003\\
+\hspace{1em}cif-rotate & 0.114 (0.013) & 0.742 (0.011) & 70.063 & 10.518\\
+\hspace{1em}aorsf-net & 0.113 (0.013) & 0.745 (0.012) & 120.016 & 0.160\\
+\hspace{1em}aorsf-cph & 0.112 (0.014) & 0.746 (0.012) & 1.972 & 0.152\\
+\hspace{1em}cif-standard & 0.110 (0.011) & 0.745 (0.012) & 3.971 & 15.781\\
+\hspace{1em}aorsf-fast & 0.110 (0.016) & 0.745 (0.011) & 0.617 & 0.153\\
+\hspace{1em}rsf-standard & 0.106 (0.011) & 0.737 (0.010) & 2.067 & 0.278\\
+\hspace{1em}cif-extension & 0.095 (0.005) & 0.745 (0.012) & 28.919 & 9.534\\
+\hspace{1em}ranger-extratrees & 0.092 (0.008) & 0.739 (0.013) & 2.936 & 1.775\\
+\hspace{1em}xgboost-cox & 0.091 (0.009) & 0.746 (0.010) & 4.368 & 0.004\\
+\hspace{1em}aorsf-random & 0.082 (0.005) & 0.733 (0.012) & 2.553 & 0.149\\
+\hspace{1em}nn-cox & 0.078 (0.024) & 0.710 (0.031) & 18.849 & 4.563\\
+\hspace{1em}xgboost-aft & --- & 0.743 (0.009) & 13.559 & 0.007\\
+\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{VA lung cancer trial; death, n = 137, p = 8}}}\\
 \hline
-\hspace{1em}aorsf-net & 0.204 (0.044) & 0.796 (0.036) & 9.921 & 0.012\\
-\hspace{1em}aorsf-fast & 0.204 (0.044) & 0.794 (0.034) & 0.047 & 0.011\\
-\hspace{1em}aorsf-cph & 0.202 (0.046) & 0.793 (0.036) & 0.097 & 0.013\\
-\hspace{1em}cif-rotate & 0.202 (0.059) & 0.787 (0.038) & 4.285 & 1.059\\
-\hspace{1em}rsf-standard & 0.179 (0.044) & 0.787 (0.040) & 0.067 & 0.025\\
-\hspace{1em}cif-extension & 0.176 (0.044) & 0.794 (0.034) & 3.541 & 1.194\\
-\hspace{1em}glmnet-cox & 0.160 (0.030) & 0.787 (0.039) & 0.078 & 0.002\\
-\hspace{1em}aorsf-random & 0.156 (0.043) & 0.779 (0.039) & 0.209 & 0.011\\
-\hspace{1em}cif-standard & 0.131 (0.035) & 0.770 (0.036) & 0.099 & 0.119\\
-\hspace{1em}obliqueRSF-net & 0.128 (0.031) & 0.795 (0.029) & 59.944 & 0.660\\
-\hspace{1em}ranger-extratrees & 0.092 (0.033) & 0.778 (0.037) & 0.021 & 0.027\\
-\hspace{1em}xgboost-cox & 0.062 (0.077) & 0.747 (0.050) & 1.139 & 0.002\\
-\hspace{1em}xgboost-aft & -0.012 (0.141) & 0.753 (0.046) & 5.540 & 0.005\\
-\hspace{1em}nn-cox & -0.028 (0.036) & 0.525 (0.084) & 11.338 & 0.123\\*
+\hspace{1em}aorsf-fast & 0.197 (0.050) & 0.794 (0.033) & 0.047 & 0.011\\
+\hspace{1em}aorsf-net & 0.197 (0.050) & 0.796 (0.034) & 9.985 & 0.012\\
+\hspace{1em}aorsf-cph & 0.194 (0.053) & 0.793 (0.035) & 0.097 & 0.012\\
+\hspace{1em}cif-rotate & 0.192 (0.066) & 0.786 (0.037) & 4.248 & 1.059\\
+\hspace{1em}rsf-standard & 0.172 (0.049) & 0.786 (0.038) & 0.067 & 0.025\\
+\hspace{1em}cif-extension & 0.169 (0.048) & 0.793 (0.032) & 3.508 & 1.194\\
+\hspace{1em}glmnet-cox & 0.157 (0.032) & 0.786 (0.038) & 0.078 & 0.002\\
+\hspace{1em}aorsf-random & 0.151 (0.046) & 0.779 (0.037) & 0.205 & 0.011\\
+\hspace{1em}cif-standard & 0.124 (0.040) & 0.767 (0.035) & 0.098 & 0.119\\
+\hspace{1em}obliqueRSF-net & 0.123 (0.034) & 0.794 (0.028) & 59.944 & 0.669\\
+\hspace{1em}ranger-extratrees & 0.089 (0.033) & 0.777 (0.036) & 0.021 & 0.026\\
+\hspace{1em}xgboost-cox & 0.057 (0.076) & 0.748 (0.048) & 1.099 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.755 (0.045) & 5.540 & 0.005\\
+\hspace{1em}nn-cox & -0.031 (0.036) & 0.523 (0.080) & 11.159 & 0.126\\*
 \end{longtable}
@@
 \begin{longtable}[t]{llcccccc}
-\caption{\label{tab:unnamed-chunk-7}Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance}\\
+\caption{\label{tab:unnamed-chunk-10}Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance. \label{tab:bm_vi}}\\
 \toprule
@@
 \endfirsthead
-\caption[]{Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance \textit{(continued)}}\\
+\caption[]{Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance. \label{tab:bm_vi} \textit{(continued)}}\\
 \toprule
@@
 \endlastfoot
-Overall & Overall & 76.1 & 73.9 & 73.3 & 69.5 & 64.5 & 67.8\\
+Overall & Overall & 76.0 & 74.0 & 73.3 & 69.7 & 64.7 & 67.7\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 58.0 & 57.4 & 58.0 & 54.3 & 48.8 & 57.1\\
-\hspace{1em}30 & 500 & 55.4 & 54.7 & 56.0 & 48.0 & 42.3 & 55.3\\
-\hspace{1em}30 & 1,000 & 56.6 & 56.0 & 57.9 & 53.2 & 48.5 & 55.4\\
-\hspace{1em}30 & 2,500 & 61.4 & 59.0 & 63.6 & 61.8 & 60.7 & 60.2\\
-\hspace{1em}15 & 500 & 53.3 & 53.5 & 53.0 & 45.1 & 39.1 & 55.0\\
-\hspace{1em}15 & 1,000 & 57.5 & 55.2 & 56.9 & 51.2 & 44.6 & 54.5\\
-\hspace{1em}15 & 2,500 & 62.2 & 58.9 & 62.5 & 61.3 & 59.6 & 61.7\\
-\hspace{1em}0 & 500 & 50.6 & 52.7 & 52.5 & 43.2 & 40.3 & 53.6\\
-\hspace{1em}0 & 1,000 & 57.8 & 58.5 & 55.1 & 53.9 & 43.0 & 55.2\\
-\hspace{1em}0 & 2,500 & 67.2 & 68.4 & 64.5 & 70.6 & 61.5 & 62.5\\
+\hspace{1em}Overall & Overall & 58.0 & 57.7 & 58.1 & 54.6 & 49.1 & 56.8\\
+\hspace{1em}30 & 500 & 55.0 & 54.5 & 55.7 & 48.1 & 42.4 & 54.4\\
+\hspace{1em}30 & 1,000 & 57.2 & 56.4 & 58.3 & 53.5 & 48.6 & 55.7\\
+\hspace{1em}30 & 2,500 & 62.2 & 59.6 & 64.3 & 62.2 & 61.4 & 60.8\\
+\hspace{1em}15 & 500 & 53.3 & 53.6 & 53.6 & 46.2 & 40.0 & 53.9\\
+\hspace{1em}15 & 1,000 & 56.5 & 55.2 & 56.5 & 51.6 & 45.2 & 54.5\\
+\hspace{1em}15 & 2,500 & 61.5 & 59.1 & 62.3 & 61.5 & 59.2 & 61.3\\
+\hspace{1em}0 & 500 & 51.7 & 53.6 & 53.5 & 44.6 & 40.3 & 53.5\\
+\hspace{1em}0 & 1,000 & 57.0 & 59.1 & 55.3 & 53.1 & 43.1 & 55.3\\
+\hspace{1em}0 & 2,500 & 67.6 & 68.4 & 63.7 & 70.8 & 61.5 & 61.8\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 72.1 & 69.6 & 67.9 & 66.0 & 60.0 & 62.1\\
-\hspace{1em}30 & 500 & 59.4 & 58.8 & 57.8 & 52.8 & 48.1 & 55.0\\
-\hspace{1em}30 & 1,000 & 62.4 & 61.3 & 60.1 & 58.0 & 52.5 & 56.0\\
-\hspace{1em}30 & 2,500 & 61.6 & 59.6 & 61.0 & 60.1 & 56.2 & 57.7\\
-\hspace{1em}15 & 500 & 63.9 & 61.9 & 61.1 & 53.2 & 47.3 & 58.6\\
-\hspace{1em}15 & 1,000 & 69.7 & 65.8 & 66.0 & 63.5 & 55.9 & 59.4\\
-\hspace{1em}15 & 2,500 & 70.9 & 67.0 & 67.8 & 67.1 & 62.7 & 63.7\\
-\hspace{1em}0 & 500 & 74.1 & 71.4 & 68.0 & 58.7 & 56.6 & 61.8\\
-\hspace{1em}0 & 1,000 & 88.8 & 84.5 & 78.5 & 82.9 & 69.7 & 67.5\\
-\hspace{1em}0 & 2,500 & 98.4 & 96.5 & 91.3 & 97.7 & 91.3 & 78.9\\
+\hspace{1em}Overall & Overall & 71.9 & 69.5 & 68.0 & 66.0 & 60.1 & 61.7\\
+\hspace{1em}30 & 500 & 59.0 & 58.7 & 57.7 & 53.0 & 48.4 & 55.2\\
+\hspace{1em}30 & 1,000 & 61.4 & 60.3 & 59.5 & 57.7 & 52.4 & 56.0\\
+\hspace{1em}30 & 2,500 & 62.0 & 60.2 & 60.9 & 60.0 & 56.5 & 58.0\\
+\hspace{1em}15 & 500 & 63.8 & 61.8 & 61.3 & 54.5 & 48.9 & 58.3\\
+\hspace{1em}15 & 1,000 & 68.0 & 65.1 & 65.2 & 63.1 & 56.4 & 59.2\\
+\hspace{1em}15 & 2,500 & 70.7 & 66.8 & 68.4 & 66.7 & 62.0 & 62.7\\
+\hspace{1em}0 & 500 & 75.1 & 71.8 & 68.9 & 59.5 & 56.1 & 61.2\\
+\hspace{1em}0 & 1,000 & 89.0 & 84.8 & 78.8 & 82.2 & 69.2 & 67.0\\
+\hspace{1em}0 & 2,500 & 98.4 & 96.2 & 91.7 & 97.6 & 91.3 & 78.0\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 78.5 & 75.8 & 75.0 & 70.6 & 65.1 & 68.2\\
-\hspace{1em}30 & 500 & 65.3 & 63.3 & 63.7 & 55.7 & 50.1 & 59.5\\
-\hspace{1em}30 & 1,000 & 67.8 & 65.7 & 65.4 & 61.7 & 55.8 & 60.8\\
-\hspace{1em}30 & 2,500 & 69.4 & 66.8 & 68.3 & 65.4 & 62.0 & 64.3\\
-\hspace{1em}15 & 500 & 71.1 & 68.3 & 66.8 & 58.3 & 51.8 & 62.3\\
-\hspace{1em}15 & 1,000 & 75.6 & 71.3 & 71.9 & 66.6 & 59.6 & 64.4\\
-\hspace{1em}15 & 2,500 & 79.1 & 74.7 & 76.8 & 73.3 & 69.2 & 70.1\\
-\hspace{1em}0 & 500 & 83.2 & 80.7 & 76.1 & 65.1 & 61.5 & 67.2\\
-\hspace{1em}0 & 1,000 & 95.8 & 92.5 & 88.5 & 89.8 & 78.6 & 76.3\\
-\hspace{1em}0 & 2,500 & 99.8 & 99.4 & 97.8 & 99.7 & 97.8 & 88.9\\
+\hspace{1em}Overall & Overall & 78.4 & 76.0 & 75.0 & 70.8 & 65.4 & 68.3\\
+\hspace{1em}30 & 500 & 65.1 & 64.0 & 63.4 & 55.6 & 50.0 & 59.5\\
+\hspace{1em}30 & 1,000 & 67.5 & 65.6 & 65.3 & 61.7 & 55.8 & 61.0\\
+\hspace{1em}30 & 2,500 & 70.1 & 67.5 & 68.6 & 66.0 & 62.7 & 64.7\\
+\hspace{1em}15 & 500 & 70.3 & 68.1 & 66.7 & 58.7 & 52.4 & 62.2\\
+\hspace{1em}15 & 1,000 & 74.8 & 71.1 & 71.5 & 66.5 & 59.8 & 64.4\\
+\hspace{1em}15 & 2,500 & 78.8 & 74.9 & 77.0 & 73.0 & 68.9 & 70.2\\
+\hspace{1em}0 & 500 & 83.8 & 81.1 & 76.5 & 66.8 & 62.1 & 67.5\\
+\hspace{1em}0 & 1,000 & 95.6 & 92.6 & 87.9 & 89.6 & 78.9 & 76.3\\
+\hspace{1em}0 & 2,500 & 99.8 & 99.3 & 97.8 & 99.6 & 97.8 & 88.9\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 90.9 & 88.8 & 88.5 & 84.7 & 82.4 & 82.9\\
-\hspace{1em}30 & 500 & 79.3 & 77.1 & 75.1 & 70.1 & 66.2 & 71.0\\
-\hspace{1em}30 & 1,000 & 83.9 & 80.7 & 80.0 & 76.9 & 73.7 & 74.4\\
-\hspace{1em}30 & 2,500 & 87.0 & 83.7 & 85.2 & 82.2 & 80.8 & 79.1\\
-\hspace{1em}15 & 500 & 85.9 & 83.0 & 82.1 & 74.2 & 70.2 & 74.8\\
-\hspace{1em}15 & 1,000 & 91.0 & 87.6 & 88.2 & 84.5 & 80.5 & 80.2\\
-\hspace{1em}15 & 2,500 & 94.3 & 91.6 & 93.5 & 89.8 & 88.5 & 86.7\\
-\hspace{1em}0 & 500 & 97.2 & 95.5 & 93.2 & 85.5 & 84.3 & 85.1\\
-\hspace{1em}0 & 1,000 & 99.9 & 99.8 & 99.4 & 99.4 & 97.5 & 94.6\\
+\hspace{1em}Overall & Overall & 91.0 & 88.9 & 88.7 & 85.0 & 82.7 & 83.0\\
+\hspace{1em}30 & 500 & 79.4 & 77.0 & 75.5 & 70.1 & 66.3 & 70.7\\
+\hspace{1em}30 & 1,000 & 83.6 & 80.6 & 80.6 & 77.0 & 73.9 & 74.6\\
+\hspace{1em}30 & 2,500 & 86.9 & 83.8 & 85.4 & 82.2 & 80.9 & 79.1\\
+\hspace{1em}15 & 500 & 86.3 & 83.3 & 81.7 & 74.6 & 70.4 & 74.4\\
+\hspace{1em}15 & 1,000 & 91.0 & 87.9 & 88.2 & 84.7 & 81.4 & 80.5\\
+\hspace{1em}15 & 2,500 & 94.6 & 91.7 & 93.7 & 90.2 & 88.7 & 86.7\\
+\hspace{1em}0 & 500 & 97.7 & 96.2 & 94.0 & 86.6 & 84.5 & 85.9\\
+\hspace{1em}0 & 1,000 & 99.9 & 99.8 & 99.3 & 99.5 & 97.9 & 95.0\\
 \hspace{1em}0 & 2,500 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 99.8\\*

### 2022-07-16 R/bench_pred_model.R

@@ -8,8 +8,6 @@
 #' @param model_key
 bench_pred_model <- function(bm_pred_clean, data_key, model_key) {
 
-  bm_pred_clean <- filter(bm_pred_clean, model != 'xgb_aft')
-
   # fit <- stan_glmer(data = bm_pred_clean,
   #                   formula = ibs_scaled ~ model + (1|data/run))
 
@@ -36,7 +34,7 @@ bench_pred_model <- function(bm_pred_clean, data_key, model_key) {
   mdl <- list(
 
     ibs_scaled = stan_glmer(
-      data = bm_pred_mdat,
+      data = filter(bm_pred_mdat, model != 'xgb_aft'),
       formula = value ~ -1 + model + (1 | data/run),
       subset = metric == 'ibs_scaled'
     ),
@@ -49,16 +47,20 @@ bench_pred_model <- function(bm_pred_clean, data_key, model_key) {
 
   )
 
-  newdata <- distinct(bm_pred_mdat, model)
+  newdata_cstat <- distinct(bm_pred_mdat, model)
 
-  data_infer <- map_dfr(
+  newdata_ibs_scaled <- newdata_cstat %>%
+    filter(model != 'xgb_aft') %>%
+    droplevels()
+
+  data_infer <- map2_dfr(
     .x = mdl,
+    .y = list(newdata_ibs_scaled,
+              newdata_cstat),
     .id = 'metric',
-    .f = ~ posterior_epred(.x,
-                           newdata = newdata,
-                           re.form = ~0) |>
+    .f = ~ posterior_epred(.x, newdata = .y,  re.form = ~0) |>
       as_tibble() |>
-      set_names(newdata$model) |>
+      set_names(.y$model) |>
       pivot_longer(everything(), names_to = 'model') |>
       add_row(model = 'aorsf_fast', value = Inf) |>
       mutate(model = factor(model),

### 2022-07-16 R/bench_pred_model_visualize.R

@@ -50,115 +50,12 @@ bench_pred_model_visualize <- function(bm_pred_model,
                                  "Time-dependent C-statistic"))
     )
 
-
-  xmax <- max(gg_data$x)
-  y_col_0 = -equiv_bound * 10
-  y_col_1 = equiv_bound * 4
-  y_col_2 = equiv_bound * 7
-  y_col_3 = equiv_bound * 10
-
-
-  y_breaks <- seq(-5, 1) * 1/100
-
-  gg_header <- map(
-    .x = levels(gg_data$metric),
-    .f = ~ {
-      tibble(
-        x = c(xmax + 1,
-              xmax + 1,
-              xmax + 2,
-              xmax + 1,
-              xmax + 1,
-              xmax + 1),
-        median = c(y_col_0,
-                   (min(y_breaks) + max(y_breaks)) / 2,
-                   (y_col_1 + y_col_3) / 2,
-                   y_col_1,
-                   y_col_2,
-                   y_col_3),
-        label = c("Learner",
-                  .x,
-                  "Posterior probability",
-                  "Equivalence",
-                  "Difference < 0",
-                  "Difference < -1"),
-        hjust = c(0, 1/2, 1/2, 1/2, 1/2, 1/2)
-      )
-    }
-  )
-
-  gg_rect <- tibble(
-    xmin = seq(xmax+1) - 1/2,
-    xmax = seq(xmax+1) + 1/2,
-    ymin = -Inf,
-    ymax = Inf
-  ) |>
-    filter(seq(n()) %% 2 == 0)
-
   plts <- gg_data |>
     group_by(metric) |>
     group_split() |>
-    set_names(c("ibs_scaled", "cstat")) |>
-    map2(
-      .y = gg_header,
-      ~ggplot(.x) +
-        aes(x = x, y = median, label = model) +
-        geom_segment(x = 0, y = -.01, xend = xmax+1/2, yend = -.01,
-                     color = 'purple', linetype = 2) +
-        geom_segment(x = 0, y = .01, xend = xmax+1/2, yend = .01,
-                     color = 'purple', linetype = 2) +
-        geom_segment(x = 0, y = 0, xend = xmax+1/2, yend = 0,
-                     color = 'darkorange', linetype = 2) +
-        geom_vline(xintercept = c(xmax + 1/2, xmax + 3/2)) +
-        geom_segment(
-          mapping = aes(x = x,
-                        y = ci_lwr,
-                        xend = x,
[…]

### 2022-07-27 paper/arxiv/main.Rnw
pure time benchmark plus arxiv

--- 2022-07-16 paper/jmlr/main.Rnw
@@
-\documentclass[twoside,11pt]{article}
-
-% Any additional packages needed should be included after jmlr2e.
-% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
-% and defines many common macros, such as 'proof' and 'example'.
-%
-% It also sets the bibliographystyle to plainnat; for more information on
-% natbib citation styles, see the natbib documentation, a copy of which
-% is archived at http://www.jmlr.org/format/natbib.pdf
-
-% Available options for package jmlr2e are:
-%
-%   - abbrvbib : use abbrvnat for the bibliography style
-%   - nohyperref : do not load the hyperref package
-%   - preprint : remove JMLR specific information from the template,
-%         useful for example for posting to preprint servers.
-%
-% Example of using the package with custom options:
-%
-% \usepackage[abbrvbib, preprint]{jmlr2e}
-
-\usepackage{jmlr2e}
+\documentclass{article}
+
+\usepackage{arxiv}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+\usepackage{graphicx}
+\usepackage{natbib}
+\usepackage{doi}
+
+\usepackage{lipsum}
+
 % extra packages
@@
 \usepackage{amsmath}
-\usepackage{booktabs}
 \usepackage{caption}
 \usepackage{multirow}
-\usepackage{hyperref}
 \hypersetup{hidelinks}
@@
 
-% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}
-
-\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{meila00a}{Marina Meil\u{a} and Michael I. Jordan}
-
-% Short headings should be running head and authors last names
-
-\ShortHeadings{Accelerated oblique random survival forests}{Jaeger et al}
-\firstpageno{1}
+\newcommand{\nope}[1]{}
+
+\title{Accelerated and interpretable oblique random survival forests}
+
+\date{\today}	% Here you can change the date presented in the paper title
+
+\author{ \href{https://orcid.org/0000-0001-7399-2299}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Byron C. Jaeger} \\
+	Department of Biostatistics and Data Science\\
+	Wake Forest University School of Medicine\\
+	Winston-Salem, NC 27157, USA \\
+	\texttt{bjaeger@wakehealth.edu}
+	\AND
+   Sawyer Welden \\
+   Department of Biostatistics and Data Science\\
+   Wake Forest University School of Medicine\\
+   Winston-Salem, NC 27157, USA \\
+   \texttt{swelden@wakehealth.edu}
+   \And
+   Kristin Lenoir \\
+   Department of Biostatistics and Data Science\\
+   Wake Forest University School of Medicine\\
+   Winston-Salem, NC 27157, USA \\
+   \texttt{klenoir@wakehealth.edu}
+	 \And
+	 Jaime L.~Speiser \\
+	 Department of Biostatistics and Data Science\\
+	 Wake Forest University School of Medicine\\
+	 Winston-Salem, NC 27157, USA \\
+	 \texttt{jspeiser@wakehealth.edu}
+	 \And
+	 Matthew Segar \\
+   Department of Cardiology \\
+   Texas Heart Institute \\
+   Houston, TX 77030, USA \\
+	 \texttt{Matthew.Segar@BCM.edu}
+   \And
+	 Ambarish Pandey \\
+   Division of Cardiology, Department of Internal Medicine \\
+   University of Texas Southwestern Medical Center \\
+   Dallas, TX 75235, USA \\
+	 \texttt{Ambarish.Pandey@UTSouthwestern.edu}
+	 \And
+	 Nicholas M.~Pajewski \\
+	 Department of Biostatistics and Data Science\\
+	 Wake Forest University School of Medicine\\
+	 Winston-Salem, NC 27157, USA \\
+	 \texttt{npajewsk@wakehealth.edu}
+	%% \AND
+	%% Coauthor \\
+	%% Affiliation \\
+	%% Address \\
+	%% \texttt{email} \\
+	%% \And
+	%% Coauthor \\
+	%% Affiliation \\
+	%% Address \\
+	%% \texttt{email} \\
+	%% \And
+	%% Coauthor \\
+	%% Affiliation \\
+	%% Address \\
+	%% \texttt{email} \\
+}
+
+% Uncomment to remove the date
+%\date{}
+
+% Uncomment to override  the `A preprint' in the header
+%\renewcommand{\headeright}{Technical Report}
+%\renewcommand{\undertitle}{Technical Report}
+\renewcommand{\shorttitle}{\textit{arXiv} Accelerated \& interpretable oblique RSFs}
+
+%%% Add PDF metadata to help others organize their library
+%%% Once the PDF is generated, you can check the metadata with
+%%% $ pdfinfo template.pdf
+\hypersetup{
+pdftitle={Accelerated and interpretable oblique random survival forests},
+pdfsubject={q-bio.NC, q-bio.QM},
+pdfauthor={Byron C.~Jaeger},
+pdfkeywords={Random Forest, Survival, Efficiency, Variable Importance},
+}
 
 \begin{document}
-
-\title{Accelerated oblique random survival forests}
-
-\author{\name Byron C. Jaeger \email bjaeger@wakehealth.edu \\
-       \addr Department of Biostatistics and Data Science\\
-       Wake Forest University School of Medicine\\
-       Winston-Salem, NC 27157, USA
-       \AND
-       \name Sawyer Welden \email swelden@wakehealth.edu \\
-       \addr Department of Biostatistics and Data Science\\
-       Wake Forest University School of Medicine\\
-       Winston-Salem, NC 27157, USA
-       \AND
-       \name Kristin Lenoir \email klenoir@wakehealth.edu \\
-       \addr Department of Biostatistics and Data Science\\
-       Wake Forest University School of Medicine\\
-       Winston-Salem, NC 27157, USA
-       \AND
-       \name Jaime L Speiser \email jspeiser@wakehealth.edu \\
-       \addr Department of Biostatistics and Data Science\\
-       Wake Forest University School of Medicine\\
-       Winston-Salem, NC 27157, USA
-       \AND
-       \name Matthew Segar \email Matthew.Segar@UTSouthwestern.edu \\
-       \addr Division of Cardiology, Department of Internal Medicine, \\
-       University of Texas Southwestern Medical Center, Dallas
-       \AND
-       \name Nicholas M. Pajewski \email npajewsk@wakehealth.edu \\
-       \addr Department of Biostatistics and Data Science\\
-       Wake Forest University School of Medicine\\
-       Winston-Salem, NC 27157, USA}
-
-\editor{TBD}
 
@@
 
-bm_pred_n_runs <- max(bm_pred_clean$run)
+bm_pred_n_runs <- max(bm_pred_clean$data$run)
 
 bm_pred_total_time <-
-  sum(with(bm_pred_clean, time_fit + time_pred)) / (60^2)
+  sum(with(bm_pred_clean$data, time_fit + time_pred)) / (60^2)
 
@@
 
-\newpage
-
-\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
+\begin{abstract}
 
 	The oblique random survival forest (RSF) is an ensemble supervised learning method for right-censored outcomes.
-Trees in the oblique RSF are grown using linear combinations of predictors to create branches, whereas in the standard RSF a single predictor is used.
-Oblique RSF ensembles often have higher prediction accuracy than standard RSF ensembles, but the additional computational overhead of assessing all possible linear combination of predictors is a severe limitation.
-In addition, few methods have been developed for interpretation of oblique RSF ensembles, and they remain something of a black box compared to their axis-based counterparts.
+Trees in the oblique RSF are grown using linear combinations of predictors to create branches, whereas in the standard RSF, a single predictor is used.
+Oblique RSF ensembles often have higher prediction accuracy than standard RSF ensembles.
+However, assessing all possible linear combinations of predictors induces significant computational overhead that limits applications to large-scale data sets.
+In addition, few methods have been developed for interpretation of oblique RSF ensembles, and they remain more difficult to interpret compared to their axis-based counterparts.
 In this article, we introduce and evaluate a method to increase computational efficiency of the oblique RSF and a method to estimate importance of individual predictor variables with the oblique RSF.
 Our strategy to reduce computational overhead makes use of Newton-Raphson scoring, a classical optimization technique that we apply to the Cox partial likelihood function within each non-leaf node of decision trees.
-We estimate importance of predictors for the oblique RSF by negating each coefficient used for the given predictor in linear combinations, and then computing the reduction in out-of-bag accuracy.
-In numeric experiments, we find that our implementation of the oblique RSF is over 500 times faster with equivalent discrimination and superior Brier score compared to existing software for oblique RSFs.
+We estimate the importance of individual predictors for the oblique RSF by negating each coefficient used for the given predictor in linear combinations, and then computing the reduction in out-of-bag accuracy.
+In general benchmarking experiments, we find that our implementation of the oblique RSF is over 500 times faster with equivalent discrimination and superior Brier score compared to existing software for oblique RSFs.
 We find in simulation studies that `negation importance' discriminates between signal and noise predictors more reliably than permutation importance, Shapley additive explanations, and a previously introduced technique to measure variable importance with oblique RSFs based on analysis of variance.
@@
 
-\begin{keywords}
-  Random Forests, Survival, Efficient, Variable Importance
-\end{keywords}
+% keywords can be removed
+\keywords{Random Forests \and Survival \and Efficiency \and Variable Importance}
 
@@
 If $p$ predictors are potentially used to split $n$ observations, up to $\mathcal{O}(n^p)$ oblique splits can be assessed versus $\mathcal{O}(n \cdot p)$ axis-based splits \citep{heath1993induction, murthy1994system}.
-Second, estimating variable importance (VI) using permutation (a standard method for RFs) may be less effective in ensembles of oblique trees, as permuting the values of one predictor may not destabilize decisions that are based on many predictors.
+Second, estimating variable importance (VI) using permutation (a standard method for RFs) may be less effective in ensembles of oblique trees, as permuting the values of one predictor may not destabilize decisions that are based on linear combinations of predictors.
 Although VI is one of the most widely used strategies to interpret random forests \citep{ishwaran2019standard}, few studies have investigated VI for oblique random forests \citep[see][Section~5]{menze2011oblique}, and fewer have investigated VI specifically for the oblique RSF.
 
-This study makes two contributions to oblique RSFs.
-First, we reduce their computational cost (\ie, accelerate them) with a scalable algorithm to identify linear combinations of coefficients.
-In a general benchmark experiment including \Sexpr{n_risk_tasks} risk prediction tasks, we show that accelerated oblique RSFs are roughly 500 times faster with equivalent or superior prediction accuracy compared to existing routines to fit oblique RSFs.
-Second, we improve the interpretability of oblique RSFs with `negation VI', a method to estimate VI that flips the sign of coefficients in linear combinations of predictors instead of permuting predictor values.
-In simulation studies where VI is estimated using permutation, analysis of variance (ANOVA; see \citet{menze2011oblique}), and approximations of Shapley values, we find that negation VI improves the oblique RSF's ability to discriminate between correlated signal and noise variables.
-The accelerated oblique RSF and multiple methods to compute VI for oblique RSFs (permutation, ANOVA, and negation) are available in the \texttt{aorsf} R Package.
+The rest of this article is organized as follows.
+\secref{sec:background} reviews prior studies that have developed methods related to those introduced in the current study.
+In \secref{sec:aorsf}, we reduce the computational cost of oblique RSFs (\ie, accelerate them) with a scalable algorithm to identify linear combinations of coefficients.
+In \secref{sec:negation_vi}, we improve the interpretability of oblique RSFs with `negation VI', a method to estimate VI that flips the sign of coefficients in linear combinations of predictors instead of permuting predictor values.
+We evaluate these methods with general benchmarking experiments and simulation studies in \secref{sec:numeric}.
+In \secref{sec:discussion}, we summarize results from the current study and present ideas connecting the current work to existing frameworks and methods for RSFs that future studies may engage with.
+The accelerated oblique RSF and multiple methods to compute VI for oblique RSFs are available in the \texttt{aorsf} R Package.
 
@@
 
-\section{Related work}
+\section{Related work} \label{sec:background}
 
@@
 After \citet{breiman2001random} introduced the axis-based and oblique RF, numerous methods were developed to grow oblique RFs for classification or regression tasks \citep{menze2011oblique, zhang2014oblique, rainforth2015canonical, zhu2015reinforcement, poona2016investigating, qiu2017oblique, tomita2020sparse, katuwal2020heterogeneous}.
-However, oblique splitting approaches for classification or regression may not generalize to survival \citep[\eg, see][Section~4.5.1]{zhu2013tree}, and most research involving the RSF has focused on forests with axis-based trees \citep{wang2017selective}.
+However, oblique splitting approaches for classification or regression may not generalize to censored outcomes \citep[\eg, see][Section~4.5.1]{zhu2013tree}, and most research involving the RSF has focused on forests with axis-based trees \citep{wang2017selective}.
 
@@
 \citet{ishwaran2008random} developed an axis-based RSF with strict adherence to the rules for growing trees proposed in \citet{breiman2001random}.
-A similar implementation of the RSF was implemented in the \texttt{ranger} \citep{ranger}, an R package designed for high dimensional data that allows users to fit extremely randomized survival forests \citep{geurts2006extremely}.
 \citet{jaeger2019oblique} developed the oblique RSF following the bootstrapping approach described in Breiman's original RF and incorporating early stopping rules from the CIF.
 
+Fast algorithms to fit axis-based RSFs are available in the \texttt{randomForestSRC} R package \citep{randomForestSRC} and the \texttt{ranger} \citep{ranger} R package.
+\texttt{randomForestSRC} provides a unified interface to grow RFs in a wide range of analyses, and \texttt{ranger} is designed to grow RFs efficiently using high dimensional data.
+Fast algorithms to fit the CIF are provided by the \texttt{party} R package \citep{hothorn2010party}, which provides a computational toolbox for recursive partitioning using conditional inference trees.
+\citet{jaeger2019oblique} developed the \texttt{obliqueRSF} package and found it was approximately 30 times slower than \texttt{party} and nearly 200 times slower than \texttt{randomForestSRC}.
+Few studies have developed software with fast algorithms for oblique RSFs that have comparable speed compared to algorithms for axis-based RSFs.
+
 \subsection{Variable importance} \label{sec:rw_vi}
 
-\citet{breiman2001random} introduced permutation VI, defined for each predictor as the difference in a RF's estimated generalization error before versus after the predictor's values are randomly permuted.
-\citet{strobl2007bias} identified bias in permutation VI driven by variable selection bias and effects induced by bootstrap sampling, and proposed an unbiased permutation VI based on unbiased recursive partitioning (see \citet{hothorn2006unbiased}).
+Several techniques to estimate VI have been developed since \citet{breiman2001random} introduced permutation VI, which is defined for each predictor as the difference in a RF's estimated prediction error before versus after the predictor's values are randomly permuted.
+\citet{strobl2007bias} identified bias in permutation VI driven by variable selection bias and effects induced by bootstrap sampling, and proposed an unbiased permutation VI measure based on unbiased recursive partitioning \citep{hothorn2006unbiased}.
 \citet{menze2011oblique} introduced an approach to estimate VI for oblique RFs that computes an analysis of variance (ANOVA) table in non-leaf nodes to obtain p-values for each predictor contributing to the node.
@@
 SHAP VI is computed for each predictor by taking the mean absolute value of SHAP values for that predictor across all observations in a given set.
+With the exception of \citet{menze2011oblique}, few studies have evaluated estimation of VI using oblique RFs, and fewer have examined VI specifically for the oblique RSF.
 
@@
 \cite{ishwaran2008random} developed the RF for survival, an extension of the RF for regression and classification developed by \citet{breiman2001random}.
-Fast algorithms to fit the RF for survival are available in the \texttt{randomForestSRC} R package \citep{randomForestSRC}.
-A similar implementation of the RF for survival can be found in the \texttt{ranger} R package \citep{ranger}, which is particularly suited for high dimensional data.
-The RF for survival can also be fit using unbiased recursive partitioning \citep{cif} via the \texttt{party} R package \citep{hothorn2010party}.
-
-\section{The acceleracted oblique random survival forest}
-
-Consider the usual framework for survival analysis with training data $$\dataset_{\text{train}} = \left\{ (T_i, \delta_i, \bm{x}_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$ Here, $T_i$ is the event time if $\delta_i=1$ and last point of contact if $\delta_i=0$, and $\bm{x}_i$ is a vector of predictors values.
+
+\section{The accelerated oblique random survival forest} \label{sec:aorsf}
+
+This section describes our approach to reduce computational overhead of the oblique RSF.
+Consider the usual framework for right-censored time-to-event outcomes with training data $$\dataset_{\text{train}} = \left\{ (T_i, \delta_i, \bm{x}_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$ Here, $T_i$ is the event time if $\delta_i=1$ or the censoring time if $\delta_i=0$, and $\bm{x}_i$ is a vector of predictors values.
 Assuming there are no ties, let $t_1 < \, \ldots \, < t_m$ denote the $m$ unique event times in $\dataset_{\text{train}}$.
@@
 where $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (i.e., those still at risk at time $t_i$), and $j(i)$ is the index of the observation for which an event occurred at time $t_i$.
-Newton Raphson scoring is an extremely fast estimation procedure, and the \texttt{survival} package includes documentation that outlines how to efficiently program it \citep{therneau_survival_2022}.
+Newton Raphson scoring is an exceptionally fast estimation procedure, and the \texttt{survival} package includes documentation that outlines how to efficiently program it \citep{therneau_survival_2022}.
 Briefly, a vector of estimated regression coefficients, $\hat{\beta}$, is updated in each step of the procedure based on its first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
@@
 
-For statistical inference, it is recommended to complete iterations of Newton Raphson scoring until a convergence threshold is met.
-However, to identify a valid linear combination of predictors, only one iteration of Newton Raphson scoring is needed.
-In \secref{sec:results_pred}, we formally test whether growing oblique survival trees using one iteration of Newton Raphson scoring is sufficient (\ie, provides equivalent prediction accuracy) compared to iterating until a convergence threshold is met.
+For statistical inference, it is recommended to continue updating $\hat{\beta}$ by completing additional iterations of Newton Raphson scoring until a convergence threshold is met.
+However, since an estimate of $\hat{\beta}$ is created by the first iteration of Newton Raphson scoring, only one iteration of Newton Raphson scoring is needed to identify a valid linear combination of predictors.
+Moreover, computing $U$ and $H$ requires computation and exponentiation of the vector $\bm{x}\hat{\beta}$, but these steps can be skipped on the first iteration of Newton Raphson scoring if an initial value of $\hat{\beta} = 0$ is chosen, allowing for a reduction in computing operations and removing the need to scale predictor values prior to initiating the Newton Raphson algorithm.\footnote{Predictors are scaled prior to initiating the Newton Raphson algorithm to avoid exponentiation of large numbers.
+However, if only one iteration is completed with an initial value of 0 for $\hat{\beta}$, then $\exp(\bm{x}\hat{\beta}) = 1$.} In \secref{sec:results_pred}, we formally test whether growing oblique survival trees using one iteration of Newton Raphson scoring provides equivalent prediction accuracy compared to trees where iterations are completed until a convergence threshold is met.
 
@@
 Several steps are taken to reduce computational overhead.
-First, memory is conserved by conducting bootstrap resampling via randomly generated bootstrap weights.
+First, memory is conserved by conducting bootstrap resampling via randomly generated bootstrap weights rather than making a traditional bootstrap sample.
 Weights are integer valued, with a weight of $v$ indicating an observation was sampled $v$ times.
-Second, early stopping is applied to the tree growing procedure if a statistical criterion is not met.
+Second, early stopping is applied to the tree-growing procedure if a statistical criterion is not met.
 In our case, the criterion is based on the magnitude of a log-rank test statistic corresponding to splitting the data at a current node.
-Third, instead of greedy recursive partitioning, we use a `good enough' approach.
+Third, instead of greedy recursive partitioning, we use `good enough' partitioning.
 More specifically, instead of computing a log-rank test statistic for several different linear combinations of variables and proceeding with the highest scoring option, we identify an optimal cut-point for one linear combination of variables and assess whether using this combination will create a split that passes the criterion for splitting a node.
@@
     \State $\text{nodes\_to\_split} \gets \{1\}$
-     \Repeat
+     \While {$\text{nodes\_to\_split} \neq \emptyset$}
      \For{$\text{node} \in \text{nodes\_to\_split}$}
@@
        \EndIf
-       \State $\text{nodes\_to\_split} \gets \text{nodes\_to\_split} \setminus \text{node}$
+       \State $\text{nodes\_to\_split} \gets \text{nodes\_to\_split} \setminus \{\text{node}\}$
      \EndFor
-  \Until{$\text{nodes\_to\_split} = \emptyset$}
+  \EndWhile
   \State \Return $\mathcal{T}$
@@
 
-\subsection{Negation variable importance}
-
-Negation VI is similar to permutation VI in that it measures how much a model’s prediction error increases when a variable’s role in the model is de-stabilized.
+\section{Negation variable importance} \label{sec:negation_vi}
+
+This Section introduces negation VI, which is similar to permutation VI in that it measures how much a model’s prediction error increases when a variable’s role in the model is de-stabilized.
 Specifically, negation VI measures the increase in an oblique RF's prediction error after flipping the sign of all coefficients linked to a variable (\ie, negating them).
@@
 Negation VI has several helpful characteristics.
-First, negation VI can be applied to any oblique RF using any valid error function.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic (see \texttt{?aorsf::orsf\_vi\_negate})} Second, since the coefficients in each non-leaf node of an oblique tree are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
+First, negation VI generalizes to any oblique RF (\ie, not just RSFs) using any valid error function, making it both general and flexible.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic (see \texttt{?aorsf::orsf\_vi\_negate})} Second, since the coefficients in each non-leaf node of an oblique tree are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
 Third, unlike permutation, negation is non-random and hence reproducible without setting a random seed.
-Additionally, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% as a result of randomly permuting the values of Hemoglobin A1c.
-
-\section{Numeric experiments}
+Additionally, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% (a value indicative of type 2 diabetes) as a result of randomly permuting the values of Hemoglobin A1c.
+
+\section{Numeric experiments} \label{sec:numeric}
 
@@
 The code used to run these experiments is available online at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}.
-All analyses were conducted using R version \Sexpr{r_version} with assistance from multiple R packages.
+All analyses were conducted using R version \Sexpr{r_version} and coordinated by the \texttt{targets} R package \citep{targets}.
 To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
@@
 
-We consider four classes of learners: RSFs (both axis based and oblique), boosting ensembles, regression models, and neural networks (\tabref{tab:learners}).
-For each class, we synchronized shared tuning parameters.
+We consider four classes of learners: RSFs (both axis-based and oblique), boosting ensembles, regression models, and neural networks.
+Specific learners from each class are summarized in \tabref{tab:learners}.
+To facilitate fair comparisons, tuning parameters were harmonized within each class.
 For example, for RSF learners, we set the minimum node size (a parameter shared by all RSF learners) as 10.
@@
 
-Our primary metric for evaluating the accuracy of predicted risk is the integrated and scaled Brier score \citep{graf1999assessment}. Consider a testing data set:
+Our primary metric for evaluating the accuracy of predicted risk is the integrated and scaled Brier score \citep{graf1999assessment}, a proper scoring rule that combines discrimination and calibration in one value and improves interpretability by adjusting for a benchmark model \citep{kattan2018index}.
+Consider a testing data set:
 $$\dataset_{\text{test}} = \left\{ (T_i, \delta_i, x_{i}) \right\}_{i=1}^{N_{\text{test}}}.$$
-Let $\widehat{S}(t \mid x_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$.
- For observation $i$ in $\dataset_{\text{test}}$, let $\widehat{S}(t \mid \bm{x}_i)$ be the predicted probability of survival up to a given prediction horizon of $t > 0$. Define \begin{align*}
+Let $\widehat{S}(t \mid x_i)$ be the predicted probability of survival up to a given prediction time of $t > 0$.
+ For observation $i$ in $\dataset_{\text{test}}$, let $\widehat{S}(t \mid \bm{x}_i)$ be the predicted probability of survival up to a given prediction time of $t > 0$. Define \begin{align*}
 \bstat = \frac{1}{\ntest} \sum_{i=1}^{\ntest} &\{ \widehat{S}(t \mid \bm{x}_i)^2 \cdot I(T_i \leq t, \delta_i = 1) \cdot \widehat{G}(T_i)^{-1} \\ &+ [1-\widehat{S}(t \mid \bm{x}_i)]^2 \cdot I(T_i > t) \cdot \widehat{G}(t)^{-1}\}
 \end{align*} where $\widehat{G}(t)$ is the Kaplan-Meier estimate of the censoring distribution.
-As $\bstat$ is time dependent, integration over time provides a summary measure of performance over a range of plausible prediction horizons.
+As $\bstat$ is time dependent, integration over time provides a summary measure of performance over a range of plausible prediction times.
 The integrated $\bstat$ is defined as \begin{equation}
@@
 We compute the first time-dependent C-statistic proposed by \citet[][Equation~3]{blanche2013estimating}, which is interpreted as the probability that a risk prediction model will assign higher risk to a case (\ie, an observation with $T \leq t$ and $\delta = 1$) versus a non-case (\ie, an observation with $T > t$).
-Similar to the IPA, observations with $T \leq t$ and $\delta = 0$ only contribute to inverse proportion of censoring weights for the time-dependent C-statistic.
+Similar to the IPA, observations with $T \leq t$ and $\delta = 0$ only contribute to inverse probability of censoring weights for the time-dependent C-statistic.
 
@@
 
-We use a collection of \Sexpr{n_data_sets} data sets to benchmark the prediction accuracy and computational efficiency of the accelerated ORSF and each of the other learners described in \secref{sec:learners}.
-The number of right-censored outcomes per data set ranged from one to four, and the total number of risk prediction tasks we analyzed was \Sexpr{n_risk_tasks} (\tabrefAppendix{tab:datasets}).
-Across all prediction tasks, the number of observations ranged from \Sexpr{nrow_min} to \Sexpr{nrow_max} (median: \Sexpr{nrow_median}), the number of predictors ranged from \Sexpr{ncol_min} to \Sexpr{ncol_max} (median: \Sexpr{ncol_median}), and the percentage of censored observations ranged from \Sexpr{pcens_min} to \Sexpr{pcens_max} (median: \Sexpr{pcens_median}).
+We used a collection of \Sexpr{n_data_sets} data sets containing a total of \Sexpr{n_risk_tasks} risk prediction tasks (tasks per data set ranged from one to four) to benchmark the accelerated oblique RSF versus other learners.
+Participant-level data from the GUIDE-IT and SPRINT clinical trials and the ARIC and MESA community cohort studies was obtained from the National Institute of Health Biologic Specimen and Data Repository Coordinating Center (BioLINCC).
+Designs and protocols for these studies have been made available \citep{aric1989atherosclerosis, bild2002multi, felker2017effect, sprint2015randomized}.
+All other datasets were publicly available and obtained through R packages (see Appendix A.1).
+Across all prediction tasks, the number of observations ranged from \Sexpr{nrow_min} to \Sexpr{nrow_max} (median: \Sexpr{nrow_median}), the number of predictors ranged from \Sexpr{ncol_min} to \Sexpr{ncol_max} (median: \Sexpr{ncol_median}), and the percentage of censored observations ranged from \Sexpr{pcens_min} to \Sexpr{pcens_max} (median: \Sexpr{pcens_median}) (\tabrefAppendix{tab:datasets}).
 
@@
 <<>>=
+
+n_tasks_complete <- bm_pred_clean %>%
+  getElement("data") %>%
+  distinct(data, run) %>%
+  nrow()
+
+n_tasks_expected <- max(bm_pred_clean$data$run) *
+  length(unique(bm_pred_clean$data$data))
+
+bm_pred_failed_description <-
+  bm_pred_clean$omit %>%
+  mutate(
+    model = recode(model, !!!deframe(model_key)),
+    data = recode(data, !!!deframe(data_key[,c('data', 'label')]))
+  ) %>%
+  split(f = list(.$model, .$data)) %>%
+  map(
+    ~ glue(
+    "On run {glue_collapse(.x$run, sep = ', ', last = ' and ')} \\
+     for the {.x$data[1]} data, the \\texttt{{{.x$model[1]}}} \\
+     learner encountered an error during its fitting procedure"
+    )
+  ) %>%
+  reduce(paste, sep = '. ')
 
@@
   filter(metric == 'ibs_scaled',
-         !str_detect(model, '^aorsf')) %>%
+         !str_detect(model, '^aorsf|^oblique')) %>%
   arrange(desc(median)) %>%
@@
 A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all}.
+In total, \Sexpr{n_tasks_complete} out of \Sexpr{n_tasks_expected} Monte-Carlo cross validation runs were completed.
+\Sexpr{bm_pred_failed_description}.
 
@@
 
+ms_diff <- round(abs(times$glmnet_cox$time - times$aorsf_fast$time)*1000)
+
 @
@@
 
-Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 1/2 second longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about \Sexpr{ms_diff} milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
 Comparing median computing times, \texttt{aorsf-fast} was \Sexpr{times$obliqueRSF_net$ratio} times faster than its predecessor, \texttt{obliqueRSF-net}.
@@
 Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
+Using this design for simulated data, the proportion of relative risk explained by our covariates ranged from FILL IN to FILL IN, according to Heller's explained relative risk measure \citep{heller2012measure}.
 
@@
 
-\section{Discussion}
+\section{Discussion} \label{sec:discussion}
 
@@
 
-\acks{Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine.
+\subsection*{Acknowledgements}
+
+Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine.
 The project described was supported by the National Center for Advancing Translational Sciences (NCATS), National Institutes of Health, through Grant Award Number UL1TR001420.
-The content is solely the responsibility of the authors and does not necessarily represent the official views of the NIH.}
+The content is solely the responsibility of the authors and does not necessarily represent the official views of the NIH.
 
@@
 
+\subsection*{Data sources}
+
 <<>>=
-
 data_key_tbl <- data_key %>%
@@
   ungroup()
+@
+
+\begin{enumerate}
+
+<<results='asis'>>=
+
+data_key_tbl %>%
+  mutate(
+    source = if_else(
+      is.na(rpack),
+      'BioLINCC',
+      paste0('the \\texttt{', rpack, '} R package \\citep{', rpack, '}'))
+  ) %>%
+  glue_data(" \\item[] The ``{label}'' data \\citep{{{cite}}} were obtained from {source}") %>%
+  unique() %>%
+  paste(collapse = '. \n') %>%
+  # removes just the first occurrence, which is not needed.
+  str_remove(pattern = stringr::fixed('\\citep{censored}')) %>%
+  paste0(".") %>%
+  cat()
+
+@
+
+\end{enumerate}
+
+<<>>=
 
@@
 results_overall <- bm_pred_clean %>%
+  getElement('data') %>%
   group_by(model) %>%
@@
 data_tbl <- bm_pred_clean %>%
+  getElement('data') %>%
   group_by(model, data) %>%
@@
 \vskip 0.2in
+\bibliographystyle{unsrtnat}
 \bibliography{main}

### 2022-07-27 paper/arxiv/main.tex
pure time benchmark plus arxiv

--- 2022-07-27 paper/arxiv/main.Rnw
@@
-\documentclass{article}
+\documentclass{article}\usepackage[]{graphicx}\usepackage[]{xcolor}
+% maxwidth is the original width if it is less than linewidth
+% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 }
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 \maketitle
-
-<<echo = FALSE, include = FALSE>>=
-
-setwd(here::here())
-source("packages.R")
-library(knitr)
-library(kableExtra)
-
-knitr::opts_chunk$set(echo = FALSE,
-                      message = FALSE,
-                      dpi = 600,
-                      cache = FALSE)
-
-rspec <- round_spec() %>%
-  round_using_magnitude(digits = c(3, 2, 1, 1),
-                        breaks = c(1, 10, 100, Inf))
-
-names(rspec) <- paste('table.glue', names(rspec), sep = '.')
-
-options(rspec)
-
-tar_load(names = c(bm_pred_clean,
-                   bm_vi_viz,
-                   bm_pred_viz,
-                   bm_pred_model_viz,
-                   bm_pred_time_viz,
-                   data_key,
-                   model_key))
-
-bm_pred_n_runs <- max(bm_pred_clean$data$run)
-
-bm_pred_total_time <-
-  sum(with(bm_pred_clean$data, time_fit + time_pred)) / (60^2)
-
-n_learners <- nrow(model_key)
-
-n_data_sets <- length(unique(data_key$label))
-n_risk_tasks <- nrow(data_key)
-
-n_obs_model <- table_value(
-  as.integer(n_risk_tasks*bm_pred_n_runs*n_learners)
-)
-
-nrow_median <- table_value(median(data_key$nrow))
-nrow_max <- table_value(max(data_key$nrow))
-nrow_min <- table_value(min(data_key$nrow))
-
-ncol_median <- table_value(median(data_key$ncol))
-ncol_max <- table_value(max(data_key$ncol))
-ncol_min <- table_value(min(data_key$ncol))
-
-pcens_median <- table_value(100*median(data_key$pcens))
-pcens_max    <- table_value(100*max(data_key$pcens))
-pcens_min    <- table_value(100*min(data_key$pcens))
-
-@
 
@@
 
-<<>>=
-r_version <- paste(version$major, version$minor, sep = '.')
-@
-
 Sections \ref{sec:bm_pred} and \ref{sec:bm_vi} present numerical experiments examining the accelerated oblique RSF and negation VI, respectively.
 The code used to run these experiments is available online at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}.
-All analyses were conducted using R version \Sexpr{r_version} and coordinated by the \texttt{targets} R package \citep{targets}.
+All analyses were conducted using R version 4.1.3 and coordinated by the \texttt{targets} R package \citep{targets}.
 To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
@@
 
-We used a collection of \Sexpr{n_data_sets} data sets containing a total of \Sexpr{n_risk_tasks} risk prediction tasks (tasks per data set ranged from one to four) to benchmark the accelerated oblique RSF versus other learners.
+We used a collection of 20 data sets containing a total of 33 risk prediction tasks (tasks per data set ranged from one to four) to benchmark the accelerated oblique RSF versus other learners.
 Participant-level data from the GUIDE-IT and SPRINT clinical trials and the ARIC and MESA community cohort studies was obtained from the National Institute of Health Biologic Specimen and Data Repository Coordinating Center (BioLINCC).
@@
 All other datasets were publicly available and obtained through R packages (see Appendix A.1).
-Across all prediction tasks, the number of observations ranged from \Sexpr{nrow_min} to \Sexpr{nrow_max} (median: \Sexpr{nrow_median}), the number of predictors ranged from \Sexpr{ncol_min} to \Sexpr{ncol_max} (median: \Sexpr{ncol_median}), and the percentage of censored observations ranged from \Sexpr{pcens_min} to \Sexpr{pcens_max} (median: \Sexpr{pcens_median}) (\tabrefAppendix{tab:datasets}).
+Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 1,384), the number of predictors ranged from 7 to 1,692 (median: 24), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 72.5) (\tabrefAppendix{tab:datasets}).
 
@@
 
-For each risk prediction task, we completed \Sexpr{bm_pred_n_runs} runs of Monte-Carlo cross validation.
+For each risk prediction task, we completed 25 runs of Monte-Carlo cross validation.
 In each run, we used a random sample containing 50\% of the available data for training and the remaining 50\% for testing each of the learners described in \secref{sec:learners}.
@@
 
-After collecting data from \Sexpr{bm_pred_n_runs} replications of Monte-Carlo cross validation for the \Sexpr{n_learners} learners in all \Sexpr{n_risk_tasks} risk prediction tasks, we analyzed the resulting \Sexpr{n_obs_model} observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
+After collecting data from 25 replications of Monte-Carlo cross validation for the 14 learners in all 33 risk prediction tasks, we analyzed the resulting 11,550 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
 Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using Bayesian models.
@@
 
-<<>>=
-
-n_tasks_complete <- bm_pred_clean %>%
-  getElement("data") %>%
-  distinct(data, run) %>%
-  nrow()
-
-n_tasks_expected <- max(bm_pred_clean$data$run) *
-  length(unique(bm_pred_clean$data$data))
-
-bm_pred_failed_description <-
-  bm_pred_clean$omit %>%
-  mutate(
-    model = recode(model, !!!deframe(model_key)),
-    data = recode(data, !!!deframe(data_key[,c('data', 'label')]))
-  ) %>%
-  split(f = list(.$model, .$data)) %>%
-  map(
-    ~ glue(
-    "On run {glue_collapse(.x$run, sep = ', ', last = ' and ')} \\
-     for the {.x$data[1]} data, the \\texttt{{{.x$model[1]}}} \\
-     learner encountered an error during its fitting procedure"
-    )
-  ) %>%
-  reduce(paste, sep = '. ')
-
-n_wins_aorsf <- bm_pred_viz %>%
-  getElement('ibs_scaled') %>%
-  getElement('rankings') %>%
-  filter(model == 'aorsf_fast') %>%
-  pull(n_wins)
-
-ibs_scaled_mean_aorsf <- bm_pred_viz %>%
-  getElement('ibs_scaled') %>%
-  getElement('smry') %>%
-  filter(model == 'aorsf_fast',
-         data == 'Overall') %>%
-  mutate(eval = table_value(eval * 100)) %>%
-  pull(eval)
-
-ibs_scaled_aorsf_won_by <- bm_pred_viz %>%
-  getElement('ibs_scaled') %>%
-  getElement('diffs') %>%
-  filter(data == 'Overall') %>%
-  transmute(percent = table_value(pdiff),
-            absolute = table_value(100*adiff)) %>%
-  as.list()
-
-ibs_scaled_aorsf_equiv <- bm_pred_model_viz %>%
-  getElement('data') %>%
-  filter(metric == 'ibs_scaled',
-         model == 'aorsf-cph') %>%
-  pull(prob_equiv)
-
-ibs_scaled_aorsf_sup_min <- bm_pred_model_viz %>%
-  getElement('data') %>%
-  ungroup() %>%
-  filter(metric == 'ibs_scaled',
-         !str_detect(model, '^aorsf|^oblique')) %>%
-  arrange(desc(median)) %>%
-  slice(1) %>%
-  select(model, prob_super_duper) %>%
-  mutate(model = as.character(model)) %>%
-  as.list()
-
-@
-
 \subsubsection{Results} \label{sec:results_pred}
@@
 A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all}.
-In total, \Sexpr{n_tasks_complete} out of \Sexpr{n_tasks_expected} Monte-Carlo cross validation runs were completed.
-\Sexpr{bm_pred_failed_description}.
+In total, 821 out of 825 Monte-Carlo cross validation runs were completed.
+On run 13, 18, 24 and 25 for the ACTG 320 data, the \texttt{nn-cox} learner encountered an error during its fitting procedure.
 
@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in \Sexpr{n_wins_aorsf} out of \Sexpr{n_risk_tasks} risk prediction tasks, with an overall mean IPA of \Sexpr{ibs_scaled_mean_aorsf} (Figure \ref{fig:bm_pred_viz_ibs}).
-Compared to the learner with the second highest mean IPA (\texttt{\Sexpr{ibs_scaled_aorsf_sup_min$model}}), \texttt{aorsf-fast}'s mean was \Sexpr{ibs_scaled_aorsf_won_by$absolute} points higher, a relative increase of \Sexpr{ibs_scaled_aorsf_won_by$percent}\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was \Sexpr{ibs_scaled_aorsf_equiv}, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from \Sexpr{ibs_scaled_aorsf_sup_min$prob_super_duper} (versus \texttt{\Sexpr{ibs_scaled_aorsf_sup_min$model}}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
-
-<<bm_pred_viz_ibs, fig.height=10, fig.width=9, fig.cap="Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 18 out of 33 risk prediction tasks, with an overall mean IPA of 13.2 (Figure \ref{fig:bm_pred_viz_ibs}).
+Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.41 points higher, a relative increase of 12.0\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.87 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_viz_ibs-1} \caption[Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks]{Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
 Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.
-As predicted survival probabilities are not a standard output from \\texttt{xgboost-aft}, it is not included in this figure.">>=
-bm_pred_viz$ibs_scaled$fig
-@
-
-<<bm_pred_model_viz_ibs, fig.height=10, fig.width=9, fig.cap="Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
-A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.">>=
-bm_pred_model_viz$fig$ibs_scaled
-@
+As predicted survival probabilities are not a standard output from \texttt{xgboost-aft}, it is not included in this figure.}\label{fig:bm_pred_viz_ibs}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_model_viz_ibs-1} \caption[Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms]{Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
+A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.}\label{fig:bm_pred_model_viz_ibs}
+\end{figure}
+
+\end{knitrout}
 
@@
 
-<<>>=
-
-n_wins_aorsf <- bm_pred_viz %>%
-  getElement('cstat') %>%
-  getElement('rankings') %>%
-  filter(model == 'aorsf_fast') %>%
-  pull(n_wins)
-
-cstat_mean_aorsf <- bm_pred_viz %>%
-  getElement('cstat') %>%
-  getElement('smry') %>%
-  filter(model == 'aorsf_fast',
-         data == 'Overall') %>%
-  mutate(eval = table_value(eval * 100)) %>%
-  pull(eval)
-
-cstat_aorsf_won_by <- bm_pred_viz %>%
-  getElement('cstat') %>%
-  getElement('diffs') %>%
-  filter(data == 'Overall') %>%
-  transmute(percent = table_value(pdiff),
-            absolute = table_value(100*adiff)) %>%
-  as.list()
-
-cstat_aorsf_equiv <- bm_pred_model_viz %>%
-  getElement('data') %>%
-  filter(metric == 'cstat',
-         model == 'aorsf-cph') %>%
-  pull(prob_equiv) %>%
-  str_replace('\\>\\.', "$>$ 0.")
-
-cstat_aorsf_sup_min <- bm_pred_model_viz %>%
-  getElement('data') %>%
-  ungroup() %>%
-  filter(metric == 'cstat',
-         !str_detect(model, '^aorsf'),
-         model != 'obliqueRSF-net') %>%
-  arrange(desc(median)) %>%
-  slice(1) %>%
-  select(model, prob_super_duper) %>%
-  mutate(model = as.character(model)) %>%
-  as.list()
-
-@
-
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in \Sexpr{n_wins_aorsf} out of \Sexpr{n_risk_tasks} risk prediction tasks, with an overall mean of \Sexpr{cstat_mean_aorsf} (Figure \ref{fig:bm_pred_viz_cstat}).
-Compared to the learner with the second highest mean C-statistic (\texttt{\Sexpr{cstat_aorsf_sup_min$model}}), \texttt{aorsf-fast}'s mean was \Sexpr{cstat_aorsf_won_by$absolute} points higher, a relative increase of \Sexpr{cstat_aorsf_won_by$percent}\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was \Sexpr{cstat_aorsf_equiv}, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from \Sexpr{cstat_aorsf_sup_min$prob_super_duper} (versus \texttt{\Sexpr{cstat_aorsf_sup_min$model}}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
-
-<<bm_pred_viz_cstat, fig.height=10, fig.width=9, fig.cap="Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
-Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.">>=
-bm_pred_viz$cstat$fig
-@
-
-<<bm_pred_model_viz_cstat, fig.height=10, fig.width=9, fig.cap="Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms.
-A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.">>=
-bm_pred_model_viz$fig$cstat
-@
-
-<<>>=
-
-times <- bm_pred_time_viz %>%
-  getElement("medians") %>%
-  transmute(
-    model,
-    time,
-    ratio = table_value(
-      time / time[model == 'aorsf-fast']
-    )
-  ) %>%
-  as_inline('model', c('time', 'ratio')) %>%
-  set_names(str_replace(names(.), '-', '_'))
-
-ms_diff <- round(abs(times$glmnet_cox$time - times$aorsf_fast$time)*1000)
-
-@
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 8 out of 33 risk prediction tasks, with an overall mean of 77.1 (Figure \ref{fig:bm_pred_viz_cstat}).
+Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.762 points higher, a relative increase of 0.998\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.24 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_viz_cstat-1} \caption[Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks]{Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.}\label{fig:bm_pred_viz_cstat}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_model_viz_cstat-1} \caption[Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms]{Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms.
+A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.}\label{fig:bm_pred_model_viz_cstat}
+\end{figure}
+
+\end{knitrout}
 
@@
 
-Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about \Sexpr{ms_diff} milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
-Comparing median computing times, \texttt{aorsf-fast} was \Sexpr{times$obliqueRSF_net$ratio} times faster than its predecessor, \texttt{obliqueRSF-net}.
-In addition, \texttt{aorsf-fast} was \Sexpr{times$cif_standard$ratio}, \Sexpr{times$ranger_extratrees$ratio}, and \Sexpr{times$rsf_standard$ratio} faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
-
-<<bm_pred_time, fig.height=10, fig.width=9, fig.cap="Distribution of time taken to fit a prediction model and compute predicted risk.
-The median time, in seconds, is printed and annotated for each learner by a vertical line.">>=
-bm_pred_time_viz$fig
-@
+Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 158 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+Comparing median computing times, \texttt{aorsf-fast} was 700.1 times faster than its predecessor, \texttt{obliqueRSF-net}.
+In addition, \texttt{aorsf-fast} was 13.6, 1.92, and 4.20 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_time-1} \caption[Distribution of time taken to fit a prediction model and compute predicted risk]{Distribution of time taken to fit a prediction model and compute predicted risk.
+The median time, in seconds, is printed and annotated for each learner by a vertical line.}\label{fig:bm_pred_time}
+\end{figure}
+
+\end{knitrout}
 
@@
 
-<<>>=
-
-n_obs <- bm_vi_viz$smry %>%
-  ungroup() %>%
-  distinct(n_obs) %>%
-  drop_na() %>%
-  filter(n_obs > 0) %>%
-  pull(n_obs) %>%
-  glue_collapse(sep = ', ', last = ', and ')
-
-pred_corr <- bm_vi_viz$smry %>%
-  ungroup() %>%
-  distinct(pred_corr_max) %>%
-  drop_na() %>%
-  filter(pred_corr_max < 1) %>%
-  pull(pred_corr_max) %>%
-  glue_collapse(sep = ', ', last = ', and ')
-
-@
-
-Parameters that varied in the current simulation study included the number of observations (\Sexpr{n_obs}) and the absolute value of the maximum correlation between predictors (\Sexpr{pred_corr}).
+Parameters that varied in the current simulation study included the number of observations (500, 1000, and 2500) and the absolute value of the maximum correlation between predictors (0.3, 0.15, and 0).
 Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
@@
 
-<<>>=
-
-n_wins_aorsf <- bm_vi_viz %>%
-  getElement('rankings') %>%
-  filter(model == 'aorsf-negate') %>%
-  pull(n_wins)
-
-n_vi_tasks <- sum(bm_vi_viz$rankings$n_wins)
-
-cstat_mean_aorsf <- bm_vi_viz %>%
-  getElement('smry') %>%
-  filter(model == 'aorsf-negate',
-         data == 'Overall_NA_NA') %>%
-  mutate(value = table_value(value * 100)) %>%
-  pull(value)
-
-cstat_mean_anova <- bm_vi_viz %>%
-  getElement('smry') %>%
-  filter(model == 'aorsf-anova',
-         data == 'Overall_NA_NA') %>%
-  mutate(value = table_value(value * 100)) %>%
-  pull(value)
-
-cstat_mean_permute <- bm_vi_viz %>%
-  getElement('smry') %>%
-  filter(model == 'aorsf-permute',
-         data == 'Overall_NA_NA') %>%
-  mutate(value = table_value(value * 100)) %>%
-  pull(value)
-
-cstat_aorsf_won_by <- bm_vi_viz %>%
-  getElement('diffs') %>%
-  filter(data == 'Overall_NA_NA') %>%
-  transmute(percent = table_value(pdiff),
-            absolute = table_value(100*adiff)) %>%
-  as.list()
-
-cstat_vi_second_place <- bm_vi_viz %>%
-  getElement('smry') %>%
-  ungroup() %>%
-  filter(data == 'Overall_NA_NA') %>%
-  arrange(desc(value)) %>%
-  slice(2) %>%
-  transmute(model, value = table_value(100*value)) %>%
-  as.list()
-
-vi_times <- bm_vi_viz$times %>%
-  as_inline('model', 'time') %>%
-  map(as.numeric, unit = 'secs') %>%
-  map(table_value) %>%
-  set_names(str_replace(names(.), '-', '_'))
-
-@
-
-The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = \Sexpr{cstat_mean_aorsf}$), second (\texttt{aorsf-anova}; $C = \Sexpr{cstat_mean_anova}$), and third (\texttt{aorsf-permute}; $C = \Sexpr{cstat_mean_permute}$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in \Sexpr{n_wins_aorsf} out of \Sexpr{n_vi_tasks} VI tasks (Figure \ref{fig:bm_vi_viz}).
+The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = 76.0$), second (\texttt{aorsf-anova}; $C = 74.0$), and third (\texttt{aorsf-permute}; $C = 73.2$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in 26 out of 36 VI tasks (Figure \ref{fig:bm_vi_viz}).
 Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
 Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
-Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of \Sexpr{vi_times$aorsf_anova} seconds versus \Sexpr{vi_times$aorsf_negate} and \Sexpr{vi_times$aorsf_permute} seconds, respectively.
-
-<<bm_vi_viz, fig.height=11, fig.width=9, fig.cap="Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
-Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.">>=
-bm_vi_viz$fig
-@
+Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of 1.27 seconds versus 11.9 and 13.0 seconds, respectively.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_vi_viz-1} \caption[Concordance statistic for assigning higher importance to relevant versus irrelevant variables]{Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
+Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.}\label{fig:bm_vi_viz}
+\end{figure}
+
+\end{knitrout}
 
@@
 We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
-Overall, we found that estimating VI using negation instead of ANOVA increased the C-statistic for ranking a relevant variable higher than an irrelevant variable by \Sexpr{cstat_aorsf_won_by$absolute}, a relative increase of \Sexpr{cstat_aorsf_won_by$percent}\%.
+Overall, we found that estimating VI using negation instead of ANOVA increased the C-statistic for ranking a relevant variable higher than an irrelevant variable by 1.97, a relative increase of 2.66\%.
 
@@
 
-<<>>=
-data_key_tbl <- data_key %>%
-  group_by(label) %>%
-  mutate(nrow = min(nrow),
-         ncol = min(ncol)) %>%
-  ungroup()
-@
-
 \begin{enumerate}
 
-<<results='asis'>>=
-
-data_key_tbl %>%
-  mutate(
-    source = if_else(
-      is.na(rpack),
-      'BioLINCC',
-      paste0('the \\texttt{', rpack, '} R package \\citep{', rpack, '}'))
-  ) %>%
-  glue_data(" \\item[] The ``{label}'' data \\citep{{{cite}}} were obtained from {source}") %>%
-  unique() %>%
-  paste(collapse = '. \n') %>%
-  # removes just the first occurrence, which is not needed.
-  str_remove(pattern = stringr::fixed('\\citep{censored}')) %>%
-  paste0(".") %>%
-  cat()
-
-@
+ \item[] The ``VA lung cancer trial'' data \citep{kalbfleisch2011statistical} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
+ \item[] The ``Colon cancer'' data \citep{moertel1995fluorouracil} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item[] The ``Primary biliary cholangitis'' data \citep{therneau2000cox} were obtained from the \texttt{aorsf} R package \citep{aorsf}. 
+ \item[] The ``Movies released in 2015-2018'' data  were obtained from the \texttt{censored} R package \citep{censored}. 
+ \item[] The ``GBSG II'' data \citep{schumacher1994rauschecker} were obtained from the \texttt{TH.data} R package \citep{TH.data}. 
+ \item[] The ``Systolic Heart Failure'' data \citep{hsich2011identifying} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
+ \item[] The ``Serum free light chain'' data \citep{dispenzieri2012use, kyle2006prevalence} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item[] The ``Non-alcohol fatty liver disease'' data \citep{allen2018nonalcoholic} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item[] The ``Rotterdam tumor bank'' data \citep{royston2013external} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item[] The ``ACTG 320'' data \citep{hosmer2002applied} were obtained from the \texttt{mlr3proba} R package \citep{mlr3proba}. 
+ \item[] The ``GUIDE-IT'' data \citep{felker2017effect} were obtained from BioLINCC. 
+ \item[] The ``Early breast cancer'' data \citep{desmedt2011multifactorial, hatzis2011genomic, ternes2017identification} were obtained from the \texttt{biospear} R package \citep{biospear}. 
+ \item[] The ``SPRINT'' data \citep{sprint2015randomized} were obtained from BioLINCC. 
+ \item[] The ``NKI 70 gene signature'' data \citep{van2002gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}. 
+ \item[] The ``Lung cancer'' data \citep{director2008gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}. 
+ \item[] The ``NCCTG Lung Cancer'' data \citep{loprinzi1994prospective} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item[] The ``FCL'' data \citep{pintilie2006competing} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
+ \item[] The ``Monoclonal gammopathy'' data \citep{kyle2002long} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item[] The ``MESA'' data \citep{bild2002multi} were obtained from BioLINCC. 
+ \item[] The ``ARIC'' data \citep{aric1989atherosclerosis} were obtained from BioLINCC.
 
@@
 
-<<>>=
-
-data_key_tbl %>%
-  select(label, nrow, ncol, outcome, nevent, pcens) %>%
-  mutate(across(starts_with('p'), ~ .x * 100),
-         across(starts_with("n"), as.integer),
-         across(where(is.numeric), table_value),
-         across(where(is.character), str_replace, '0.000', '0'),
-         outcome = recode(
-           outcome,
-           'HF' = 'heart failure',
-           'CVD death' = 'cardiovascular death'),
-         outcome = str_to_title(outcome),
-         outcome = recode(outcome,
-                          'Gross 1m Usd' = 'Gross 1M USD',
-                          "Aids Diagnosis" ='AIDS Diagnosis')) %>%
-  kable(
-    col.names = c(
-      'Label',
-      'N observations',
-      'N predictors',
-      'Outcome',
-      "N Events",
-      '% Censored'
-    ),
-    align = 'lcclcc',
-    booktabs=TRUE,
-    longtable=TRUE,
-    format = 'latex',
-    caption = "Data sets used for numeric experiments \\label{tab:datasets}"
-  ) %>%
-  collapse_rows(columns=1:3) %>%
-  # pack_rows(index = indents,
-  #           italic = TRUE,
-  #           hline_before = TRUE,
-  #           hline_after = TRUE) %>%
-  kable_styling() %>%
-  landscape()
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\begin{landscape}
+\begin{longtable}[t]{lcclcc}
+\caption{\label{tab:unnamed-chunk-10}Data sets used for numeric experiments \label{tab:datasets}}\\
+\toprule
+Label & N observations & N predictors & Outcome & N Events & \% Censored\\
+\midrule
+VA lung cancer trial & 137 & 8 & Death & 128 & 6.57\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Recurrence & 468 & 49.6\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash Colon cancer} & \multirow{-2}{*}{\centering\arraybackslash 929} & \multirow{-2}{*}{\centering\arraybackslash 12} & Death & 452 & 51.3\\
+\cmidrule{1-6}\pagebreak[0]
+Primary biliary cholangitis & 276 & 19 & Death & 111 & 59.8\\
+\cmidrule{1-6}\pagebreak[0]
+Movies released in 2015-2018 & 551 & 46 & Gross 1M USD & 522 & 5.26\\
+\cmidrule{1-6}\pagebreak[0]
+GBSG II & 686 & 10 & Recurrence Or Death & 299 & 56.4\\
+\cmidrule{1-6}\pagebreak[0]
+Systolic Heart Failure & 2,231 & 41 & Death & 726 & 67.5\\
+\cmidrule{1-6}\pagebreak[0]
+Serum free light chain & 7,874 & 10 & Death & 2,169 & 72.5\\
+\cmidrule{1-6}\pagebreak[0]
+Non-alcohol fatty liver disease & 17,549 & 24 & Death & 1,364 & 92.2\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Recurrence & 1,518 & 49.1\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash Rotterdam tumor bank} & \multirow{-2}{*}{\centering\arraybackslash 2,982} & \multirow{-2}{*}{\centering\arraybackslash 11} & Death & 1,272 & 57.3\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & AIDS Diagnosis & 96 & 91.7\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash ACTG 320} & \multirow{-2}{*}{\centering\arraybackslash 1,151} & \multirow{-2}{*}{\centering\arraybackslash 12} & Death & 26 & 97.7\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Cardiovascular Death & 110 & 87.7\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash GUIDE-IT} & \multirow{-2}{*}{\centering\arraybackslash 894} & \multirow{-2}{*}{\centering\arraybackslash 59} & Hf Hospitalization & 288 & 67.8\\
+\cmidrule{1-6}\pagebreak[0]
+Early breast cancer & 614 & 1,692 & Recurrence Or Death & 134 & 78.2\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Cardiovascular Death & 521 & 94.4\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash SPRINT} & \multirow{-2}{*}{\centering\arraybackslash 9,361} & \multirow{-2}{*}{\centering\arraybackslash 174} & Death & 1,644 & 82.4\\
+\cmidrule{1-6}\pagebreak[0]
+NKI 70 gene signature & 144 & 77 & Death Or Metastasis & 48 & 66.7\\
+\cmidrule{1-6}\pagebreak[0]
+Lung cancer & 442 & 24 & Death & 236 & 46.6\\
+\cmidrule{1-6}\pagebreak[0]
+NCCTG Lung Cancer & 228 & 9 & Death & 165 & 27.6\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Death & 76 & 86.0\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash FCL} & \multirow{-2}{*}{\centering\arraybackslash 541} & \multirow{-2}{*}{\centering\arraybackslash 7} & Relapse & 272 & 49.7\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Death & 963 & 30.4\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash Monoclonal gammopathy} & \multirow{-2}{*}{\centering\arraybackslash 1,384} & \multirow{-2}{*}{\centering\arraybackslash 8} & Malignancy & 115 & 91.7\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Heart Failure & 339 & 95.0\\
+\cmidrule{4-6}\nopagebreak
+ &  &  & Coronary Heart Disease & 439 & 93.5\\
+\cmidrule{4-6}\nopagebreak
+ &  &  & Stroke & 292 & 95.7\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-4}{*}{\raggedright\arraybackslash MESA} & \multirow{-4}{*}{\centering\arraybackslash 6,783} & \multirow{-4}{*}{\centering\arraybackslash 48} & Death & 1,297 & 80.9\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Heart Failure & 2,981 & 78.1\\
+\cmidrule{4-6}\nopagebreak
+ &  &  & Coronary Heart Disease & 2,282 & 83.2\\
+\cmidrule{4-6}\nopagebreak
+ &  &  & Stroke & 1,323 & 90.3\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-4}{*}{\raggedright\arraybackslash ARIC} & \multirow{-4}{*}{\centering\arraybackslash 13,623} & \multirow{-4}{*}{\centering\arraybackslash 41} & Death & 6,662 & 51.1\\
+\bottomrule
+\end{longtable}
+\end{landscape}
+
+\end{knitrout}
 
@@
 
-<<>>=
-
-data_recoder <- data_key %>%
-  transmute(data,
-            label = paste0(label, "; ",
-                           outcome, ", n = ", .data$nrow,
-                           ", p = ", .data$ncol)) %>%
-  deframe()
-
-model_recoder <- model_key %>%
-  deframe()
-
-results_overall <- bm_pred_clean %>%
-  getElement('data') %>%
-  group_by(model) %>%
-  summarize(
-    across(
-      .cols = c(cstat, ibs_scaled, time_fit, time_pred),
-      .fns = list(mean = mean,
-                  median = median,
-                  sd = sd)
-    )
-  ) %>%
-  mutate(data = 'Overall')
-
-data_tbl <- bm_pred_clean %>%
-  getElement('data') %>%
-  group_by(model, data) %>%
-  summarize(
-    across(
-      .cols = c(cstat, ibs_scaled, time_fit, time_pred),
-      .fns = list(mean = mean,
-                  median = median,
-                  sd = sd)
-    )
-  ) %>%
-  bind_rows(results_overall) %>%
-  # mutate(
-  #   data = if_else(
-  #     is.na(n_z),
-  #     true = data,
-  #     false = as.character(
-  #       glue::glue("Simulation, N junk = {n_z}, N obs = {n_obs}, X corr less than or equal to {correlated_x}")
-  #     )
-  #   )
-  # ) %>%
-  arrange(data, desc(ibs_scaled_mean)) %>%
-  transmute(
-    data = recode(data, !!!data_recoder),
-    data = fct_relevel(factor(data), 'Overall'),
-    model = recode(model, !!!model_recoder),
-    ibs_scaled = table_glue(
-      "{ibs_scaled_mean} ({ibs_scaled_sd})"
-    ),
-    cstat = table_glue(
-      "{cstat_mean} ({cstat_sd})"
-    ),
-    time_fit_median = format(round(time_fit_median, 3), nsmall = 3),
-    time_pred_median = format(round(time_pred_median, 3), nsmall = 3)
-  ) %>%
-  arrange(data)
-
-indents <- table(data_tbl$data)
-
-data_tbl %>%
-  mutate(
-    ibs_scaled = if_else(
-      model == 'xgboost-aft',
-      '---',
-      ibs_scaled
-    )
-  ) %>%
-  select(-data) %>%
-  kable(booktabs=TRUE,
-        longtable=TRUE,
-        col.names = c(' ',
-                      'Scaled Brier',
-                      'C-Statistic',
-                      'Model fitting',
-                      'Risk prediction'),
-        align = 'lcccc',
-        caption = "Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.\\label{tab:bm_pred_all}") %>%
-  pack_rows(index = indents,
-            italic = TRUE,
-            hline_before = FALSE,
-            hline_after = TRUE) %>%
-  kable_styling(latex_options = c("repeat_header")) %>%
-  add_header_above(header = c(" " = 1,
-                              "Performance metric (SD)" = 2,
-                              "Computation time, seconds" = 2))
-
-@
-
-<<>>=
-
-bm_vi_smry <- bm_vi_viz$smry %>%
-  select(-x, -data) %>%
-  mutate(value = table_value(value*100)) %>%
-  pivot_wider(values_from = value, names_from = model) %>%
-  mutate(
-    variable = factor(
-      variable,
-      levels = c("Overall",
-                 "intr",
-                 "nlin",
-                 "cmbn",
-                 "main"),
-      labels = c("Overall",
-                 "Interaction effects",
-                 "Non-linear effects",
-                 "Combination effects",
-                 "Main effects")),
-    pred_corr_max = if_else(
-      is.na(pred_corr_max) | pred_corr_max == 1,
-      "Overall",
-      paste(as.integer(pred_corr_max * 100))
-    ),
-    n_obs = if_else(
-      is.na(n_obs) | n_obs == 0,
-      "Overall",
-      table_value(as.integer(n_obs))
-    )
-  ) %>%
-  select(
-    "variable",
-    "pred_corr_max",
-    "n_obs",
-    "aorsf-negate",
-    "aorsf-anova",
-    "aorsf-permute",
-    "xgboost-shap",
-    "xgboost-gain",
-    "randomForestSRC-permutation"
-  )
-
-indents <- table(bm_vi_smry$variable)
-
-bm_vi_smry %>%
-  ungroup() %>%
-  select(-variable) %>%
-  kable(booktabs=TRUE,
-        longtable=TRUE,
-        align = paste("llcccccc"),
-        col.names = c("Max correlation",
-                      "No. observations",
-                      "Negation",
-                      "ANOVA",
-                      "Permutation",
-                      "SHAP",
-                      "Gain",
-                      "Permutation"),
-        caption = "Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance. \\label{tab:bm_vi}") %>%
-  kable_styling(latex_options = c("repeat_header")) %>%
-  add_header_above(
-    header = c(" " = 2,
-               "accelerated oblique RSF" = 3,
-               "xgboost" = 2,
-               "RSF" = 1)
-  ) %>%
-  # collapse_rows(columns = 1) %>%
-  pack_rows(group_label = 'Interactions',
-            start_row = 2,
-            end_row = 11,
-            italic = TRUE,
-            hline_before = FALSE,
-            hline_after = TRUE) %>%
-  pack_rows(group_label = 'Non-linear effects',
-            start_row = 12,
-            end_row = 21,
-            italic = TRUE,
-            hline_before = FALSE,
-            hline_after = TRUE) %>%
-pack_rows(group_label = 'Combination effects',
-            start_row = 22,
-            end_row = 31,
-            italic = TRUE,
-            hline_before = FALSE,
-            hline_after = TRUE) %>%
-  pack_rows(group_label = 'Main effects',
-            start_row = 32,
-            end_row = 41,
-            italic = TRUE,
-            hline_before = FALSE,
-            hline_after = TRUE) %>%
-  landscape()
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\begin{longtable}[t]{lcccc}
+\caption{\label{tab:unnamed-chunk-11}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.\label{tab:bm_pred_all}}\\
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Performance metric (SD)} & \multicolumn{2}{c}{Computation time, seconds} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
+  & Scaled Brier & C-Statistic & Model fitting & Risk prediction\\
+\midrule
+\endfirsthead
+\caption[]{Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.\label{tab:bm_pred_all} \textit{(continued)}}\\
+\toprule
+  & Scaled Brier & C-Statistic & Model fitting & Risk prediction\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\endlastfoot
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Overall}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.132 (0.110) & 0.771 (0.073) & 0.458 & 0.107\\
+\hspace{1em}aorsf-cph & 0.131 (0.110) & 0.770 (0.072) & 1.145 & 0.087\\
+\hspace{1em}aorsf-net & 0.129 (0.113) & 0.769 (0.073) & 85.734 & 0.087\\
+\hspace{1em}obliqueRSF-net & 0.118 (0.085) & 0.769 (0.073) & 356.969 & 17.203\\
+\hspace{1em}cif-standard & 0.118 (0.098) & 0.763 (0.072) & 2.035 & 5.650\\
+\hspace{1em}rsf-standard & 0.118 (0.115) & 0.755 (0.077) & 2.157 & 0.194\\
+\hspace{1em}cif-rotate & 0.117 (0.126) & 0.754 (0.083) & 35.290 & 6.347\\
+\hspace{1em}glmnet-cox & 0.113 (0.121) & 0.755 (0.079) & 0.405 & 0.003\\
+\hspace{1em}ranger-extratrees & 0.103 (0.086) & 0.760 (0.069) & 0.716 & 0.848\\
+\hspace{1em}cif-extension & 0.099 (0.094) & 0.760 (0.074) & 15.496 & 6.211\\
+\hspace{1em}aorsf-random & 0.094 (0.081) & 0.740 (0.065) & 1.339 & 0.086\\
+\hspace{1em}xgboost-cox & 0.068 (0.102) & 0.747 (0.096) & 4.073 & 0.004\\
+\hspace{1em}nn-cox & 0.048 (0.111) & 0.649 (0.139) & 16.050 & 1.501\\
+\hspace{1em}xgboost-aft & --- & 0.761 (0.078) & 13.035 & 0.007\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{ACTG 320; AIDS diagnosis, n = 1151, p = 12}}}\\
+\hline
+\hspace{1em}aorsf-random & 0.028 (0.022) & 0.748 (0.038) & 0.539 & 0.040\\
+\hspace{1em}ranger-extratrees & 0.028 (0.017) & 0.740 (0.036) & 0.064 & 0.146\\
+\hspace{1em}obliqueRSF-net & 0.027 (0.022) & 0.746 (0.038) & 25.980 & 15.236\\
+\hspace{1em}aorsf-cph & 0.025 (0.029) & 0.751 (0.042) & 0.471 & 0.033\\
+\hspace{1em}cif-standard & 0.024 (0.031) & 0.744 (0.040) & 1.771 & 4.657\\
+\hspace{1em}aorsf-fast & 0.024 (0.028) & 0.745 (0.044) & 0.198 & 0.033\\
+\hspace{1em}cif-extension & 0.023 (0.015) & 0.722 (0.038) & 9.848 & 4.083\\
+\hspace{1em}aorsf-net & 0.019 (0.034) & 0.745 (0.042) & 18.451 & 0.035\\
+\hspace{1em}glmnet-cox & 0.016 (0.030) & 0.746 (0.037) & 0.179 & 0.003\\
+\hspace{1em}rsf-standard & 0.005 (0.041) & 0.730 (0.042) & 0.192 & 0.061\\
+\hspace{1em}cif-rotate & 0.004 (0.040) & 0.731 (0.038) & 16.095 & 3.888\\
+\hspace{1em}xgboost-cox & 0.000 (0.044) & 0.751 (0.033) & 3.704 & 0.003\\
+\hspace{1em}nn-cox & -0.001 (0.008) & 0.549 (0.125) & 11.075 & 0.668\\
+\hspace{1em}xgboost-aft & --- & 0.737 (0.035) & 10.015 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{ACTG 320; death, n = 1151, p = 12}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.010 (0.022) & 0.840 (0.054) & 0.086 & 0.020\\
+\hspace{1em}obliqueRSF-net & 0.007 (0.011) & 0.823 (0.052) & 8.869 & 11.004\\
+\hspace{1em}aorsf-cph & 0.007 (0.018) & 0.821 (0.060) & 0.414 & 0.020\\
+\hspace{1em}aorsf-random & 0.005 (0.014) & 0.788 (0.074) & 0.278 & 0.023\\
+\hspace{1em}cif-extension & 0.001 (0.020) & 0.765 (0.066) & 8.436 & 3.493\\
+\hspace{1em}ranger-extratrees & 0.001 (0.019) & 0.777 (0.069) & 0.044 & 0.138\\
+\hspace{1em}xgboost-cox & -0.004 (0.004) & 0.500 (0.000) & 0.119 & 0.002\\
+\hspace{1em}nn-cox & -0.004 (0.004) & 0.508 (0.119) & 10.867 & 0.518\\
+\hspace{1em}cif-standard & -0.005 (0.025) & 0.781 (0.062) & 1.726 & 4.648\\
+\hspace{1em}aorsf-net & -0.005 (0.032) & 0.806 (0.067) & 14.625 & 0.023\\
+\hspace{1em}rsf-standard & -0.031 (0.051) & 0.776 (0.073) & 0.090 & 0.035\\
+\hspace{1em}cif-rotate & -0.037 (0.049) & 0.707 (0.090) & 13.920 & 3.444\\
+\hspace{1em}glmnet-cox & -0.065 (0.095) & 0.746 (0.098) & 0.281 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.773 (0.071) & 9.190 & 0.005\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{ARIC; coronary heart disease, n = 13623, p = 41}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.157 (0.007) & 0.810 (0.007) & 4.640 & 1.320\\
+\hspace{1em}aorsf-cph & 0.153 (0.006) & 0.809 (0.007) & 14.503 & 1.347\\
+\hspace{1em}aorsf-net & 0.152 (0.006) & 0.809 (0.007) & 533.804 & 1.437\\
+\hspace{1em}rsf-standard & 0.150 (0.007) & 0.801 (0.007) & 9.407 & 0.991\\
+\hspace{1em}obliqueRSF-net & 0.143 (0.005) & 0.811 (0.008) & 2830.398 & 356.908\\
+\hspace{1em}cif-standard & 0.132 (0.005) & 0.809 (0.007) & 71.835 & 371.102\\
+\hspace{1em}glmnet-cox & 0.129 (0.011) & 0.795 (0.008) & 1.473 & 0.011\\
+\hspace{1em}nn-cox & 0.117 (0.029) & 0.786 (0.046) & 51.356 & 84.715\\
+\hspace{1em}ranger-extratrees & 0.112 (0.005) & 0.795 (0.009) & 293.864 & 61.837\\
+\hspace{1em}cif-rotate & 0.104 (0.004) & 0.783 (0.009) & 569.289 & 67.436\\
+\hspace{1em}aorsf-random & 0.098 (0.005) & 0.772 (0.008) & 11.694 & 1.330\\
+\hspace{1em}cif-extension & 0.069 (0.002) & 0.786 (0.009) & 169.206 & 56.091\\
+\hspace{1em}xgboost-cox & 0.064 (0.017) & 0.814 (0.006) & 8.544 & 0.015\\
+\hspace{1em}xgboost-aft & --- & 0.814 (0.006) & 23.781 & 0.013\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{ARIC; death, n = 13623, p = 41}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.217 (0.006) & 0.792 (0.004) & 932.212 & 2.377\\
+\hspace{1em}rsf-standard & 0.216 (0.006) & 0.789 (0.004) & 14.727 & 1.274\\
+\hspace{1em}aorsf-cph & 0.216 (0.006) & 0.792 (0.004) & 22.922 & 2.179\\
+\hspace{1em}aorsf-fast & 0.215 (0.007) & 0.792 (0.004) & 7.641 & 2.214\\
+\hspace{1em}obliqueRSF-net & 0.207 (0.005) & 0.791 (0.004) & 7329.229 & 331.164\\
+\hspace{1em}cif-standard & 0.201 (0.004) & 0.790 (0.004) & 72.253 & 384.744\\
+\hspace{1em}nn-cox & 0.193 (0.011) & 0.780 (0.005) & 103.296 & 92.992\\
+\hspace{1em}glmnet-cox & 0.191 (0.015) & 0.777 (0.007) & 2.256 & 0.011\\
+\hspace{1em}ranger-extratrees & 0.181 (0.004) & 0.780 (0.005) & 332.296 & 70.372\\
+\hspace{1em}cif-rotate & 0.151 (0.007) & 0.757 (0.006) & 589.958 & 66.749\\
+\hspace{1em}xgboost-cox & 0.131 (0.012) & 0.794 (0.004) & 11.220 & 0.015\\
+\hspace{1em}aorsf-random & 0.130 (0.005) & 0.734 (0.005) & 20.175 & 2.057\\
+\hspace{1em}cif-extension & 0.113 (0.002) & 0.775 (0.005) & 180.483 & 54.092\\
+\hspace{1em}xgboost-aft & --- & 0.794 (0.004) & 28.692 & 0.014\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{ARIC; heart failure, n = 13623, p = 41}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.234 (0.006) & 0.841 (0.005) & 5.268 & 2.193\\
+\hspace{1em}rsf-standard & 0.229 (0.006) & 0.835 (0.005) & 11.238 & 1.079\\
+\hspace{1em}aorsf-cph & 0.229 (0.006) & 0.841 (0.005) & 16.864 & 2.308\\
+\hspace{1em}aorsf-net & 0.228 (0.006) & 0.841 (0.005) & 623.727 & 1.685\\
+\hspace{1em}obliqueRSF-net & 0.212 (0.005) & 0.841 (0.005) & 3737.617 & 320.616\\
+\hspace{1em}cif-standard & 0.199 (0.005) & 0.839 (0.005) & 71.854 & 391.419\\
+\hspace{1em}nn-cox & 0.180 (0.017) & 0.826 (0.007) & 56.056 & 96.125\\
+\hspace{1em}cif-rotate & 0.172 (0.006) & 0.806 (0.007) & 589.494 & 69.448\\
+\hspace{1em}ranger-extratrees & 0.170 (0.004) & 0.824 (0.005) & 387.176 & 77.513\\
+\hspace{1em}glmnet-cox & 0.167 (0.044) & 0.817 (0.018) & 2.141 & 0.011\\
+\hspace{1em}aorsf-random & 0.139 (0.005) & 0.789 (0.006) & 14.001 & 1.519\\
+\hspace{1em}xgboost-cox & 0.122 (0.017) & 0.845 (0.005) & 10.926 & 0.015\\
+\hspace{1em}cif-extension & 0.109 (0.003) & 0.808 (0.006) & 176.907 & 57.216\\
+\hspace{1em}xgboost-aft & --- & 0.844 (0.005) & 24.549 & 0.013\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{ARIC; stroke, n = 13623, p = 41}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.093 (0.004) & 0.793 (0.007) & 4.179 & 1.122\\
+\hspace{1em}aorsf-net & 0.090 (0.004) & 0.792 (0.007) & 371.989 & 1.175\\
+\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.792 (0.007) & 13.462 & 1.149\\
+\hspace{1em}rsf-standard & 0.090 (0.006) & 0.784 (0.006) & 8.991 & 0.984\\
+\hspace{1em}obliqueRSF-net & 0.082 (0.003) & 0.791 (0.007) & 1869.359 & 387.014\\
+\hspace{1em}glmnet-cox & 0.078 (0.004) & 0.787 (0.007) & 1.673 & 0.011\\
+\hspace{1em}cif-standard & 0.073 (0.003) & 0.787 (0.007) & 73.989 & 364.863\\
+\hspace{1em}nn-cox & 0.070 (0.012) & 0.783 (0.010) & 32.099 & 82.720\\
+\hspace{1em}ranger-extratrees & 0.067 (0.003) & 0.779 (0.008) & 251.130 & 50.542\\
+\hspace{1em}aorsf-random & 0.059 (0.004) & 0.750 (0.008) & 9.712 & 1.132\\
+\hspace{1em}cif-rotate & 0.052 (0.003) & 0.768 (0.009) & 586.962 & 68.410\\
+\hspace{1em}xgboost-cox & 0.046 (0.014) & 0.794 (0.006) & 7.316 & 0.015\\
+\hspace{1em}cif-extension & 0.036 (0.002) & 0.769 (0.009) & 169.866 & 53.493\\
+\hspace{1em}xgboost-aft & --- & 0.793 (0.006) & 20.363 & 0.013\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Colon cancer; death, n = 929, p = 12}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.718 (0.012) & 0.239 & 0.053\\
+\hspace{1em}aorsf-cph & 0.099 (0.014) & 0.717 (0.011) & 0.638 & 0.052\\
+\hspace{1em}cif-standard & 0.097 (0.013) & 0.710 (0.012) & 0.745 & 3.685\\
+\hspace{1em}aorsf-net & 0.096 (0.014) & 0.717 (0.012) & 49.140 & 0.047\\
+\hspace{1em}aorsf-random & 0.096 (0.010) & 0.716 (0.011) & 0.919 & 0.044\\
+\hspace{1em}obliqueRSF-net & 0.089 (0.006) & 0.717 (0.012) & 252.190 & 16.726\\
+\hspace{1em}cif-rotate & 0.086 (0.017) & 0.705 (0.014) & 13.242 & 3.448\\
+\hspace{1em}rsf-standard & 0.086 (0.019) & 0.704 (0.011) & 1.901 & 0.150\\
+\hspace{1em}ranger-extratrees & 0.083 (0.007) & 0.710 (0.012) & 0.560 & 0.248\\
+\hspace{1em}cif-extension & 0.080 (0.006) & 0.709 (0.011) & 8.397 & 3.363\\
+\hspace{1em}glmnet-cox & 0.075 (0.016) & 0.711 (0.019) & 0.128 & 0.003\\
+\hspace{1em}xgboost-cox & 0.062 (0.013) & 0.701 (0.013) & 3.217 & 0.003\\
+\hspace{1em}nn-cox & -0.003 (0.003) & 0.508 (0.033) & 12.769 & 1.106\\
+\hspace{1em}xgboost-aft & --- & 0.706 (0.013) & 10.290 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Colon cancer; recurrence, n = 929, p = 12}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.099 (0.017) & 0.713 (0.016) & 0.225 & 0.050\\
+\hspace{1em}aorsf-cph & 0.098 (0.017) & 0.712 (0.015) & 0.629 & 0.050\\
+\hspace{1em}aorsf-net & 0.095 (0.018) & 0.713 (0.017) & 49.866 & 0.048\\
+\hspace{1em}aorsf-random & 0.091 (0.013) & 0.706 (0.013) & 0.926 & 0.043\\
+\hspace{1em}cif-standard & 0.091 (0.016) & 0.701 (0.017) & 0.717 & 3.703\\
+\hspace{1em}obliqueRSF-net & 0.087 (0.009) & 0.711 (0.015) & 249.790 & 16.701\\
+\hspace{1em}cif-rotate & 0.084 (0.020) & 0.694 (0.017) & 13.154 & 3.977\\
+\hspace{1em}cif-extension & 0.081 (0.009) & 0.706 (0.017) & 8.446 & 4.066\\
+\hspace{1em}rsf-standard & 0.081 (0.020) & 0.694 (0.015) & 1.831 & 0.153\\
+\hspace{1em}ranger-extratrees & 0.079 (0.011) & 0.700 (0.016) & 0.636 & 0.254\\
+\hspace{1em}glmnet-cox & 0.073 (0.018) & 0.706 (0.024) & 0.125 & 0.003\\
+\hspace{1em}xgboost-cox & 0.059 (0.011) & 0.695 (0.018) & 3.136 & 0.003\\
+\hspace{1em}nn-cox & -0.005 (0.006) & 0.531 (0.054) & 13.107 & 0.969\\
+\hspace{1em}xgboost-aft & --- & 0.701 (0.019) & 11.227 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Early breast cancer; recurrence or death, n = 614, p = 1692}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.072 (0.023) & 0.751 (0.029) & 1901.883 & 14.017\\
+\hspace{1em}cif-rotate & 0.070 (0.018) & 0.747 (0.027) & 6452.563 & 360.067\\
+\hspace{1em}cif-standard & 0.067 (0.019) & 0.747 (0.030) & 9.660 & 4.247\\
+\hspace{1em}aorsf-cph & 0.067 (0.029) & 0.747 (0.026) & 1.287 & 0.185\\
+\hspace{1em}aorsf-fast & 0.065 (0.028) & 0.746 (0.026) & 0.724 & 0.177\\
+\hspace{1em}cif-extension & 0.064 (0.016) & 0.746 (0.028) & 44.047 & 6.554\\
+\hspace{1em}ranger-extratrees & 0.061 (0.022) & 0.742 (0.031) & 0.228 & 0.169\\
+\hspace{1em}glmnet-cox & 0.041 (0.032) & 0.724 (0.036) & 5.780 & 0.006\\
+\hspace{1em}aorsf-random & 0.027 (0.015) & 0.696 (0.038) & 1.260 & 0.175\\
+\hspace{1em}xgboost-cox & 0.027 (0.034) & 0.741 (0.030) & 2.258 & 0.007\\
+\hspace{1em}rsf-standard & 0.024 (0.037) & 0.695 (0.033) & 0.366 & 0.743\\
+\hspace{1em}aorsf-net & 0.012 (0.062) & 0.740 (0.025) & 465.845 & 0.175\\
+\hspace{1em}nn-cox & -0.006 (0.043) & 0.669 (0.075) & 19.374 & 1.808\\
+\hspace{1em}xgboost-aft & --- & 0.744 (0.027) & 9.708 & 0.010\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{FCL; death, n = 541, p = 7}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.117 (0.028) & 0.787 (0.037) & 0.098 & 0.002\\
+\hspace{1em}aorsf-cph & 0.100 (0.039) & 0.769 (0.033) & 0.169 & 0.018\\
+\hspace{1em}aorsf-fast & 0.100 (0.038) & 0.768 (0.033) & 0.090 & 0.018\\
+\hspace{1em}aorsf-net & 0.097 (0.040) & 0.760 (0.034) & 12.619 & 0.018\\
+\hspace{1em}obliqueRSF-net & 0.089 (0.027) & 0.758 (0.036) & 97.158 & 5.447\\
+\hspace{1em}cif-rotate & 0.087 (0.048) & 0.755 (0.027) & 6.083 & 1.964\\
+\hspace{1em}cif-extension & 0.087 (0.036) & 0.730 (0.034) & 5.256 & 2.514\\
+\hspace{1em}aorsf-random & 0.087 (0.029) & 0.757 (0.032) & 0.256 & 0.018\\
+\hspace{1em}cif-standard & 0.084 (0.038) & 0.743 (0.036) & 0.347 & 1.132\\
+\hspace{1em}ranger-extratrees & 0.073 (0.016) & 0.741 (0.037) & 0.043 & 0.078\\
+\hspace{1em}rsf-standard & 0.072 (0.048) & 0.732 (0.034) & 0.156 & 0.040\\
+\hspace{1em}xgboost-cox & 0.029 (0.050) & 0.679 (0.121) & 0.266 & 0.002\\
+\hspace{1em}nn-cox & -0.004 (0.014) & 0.549 (0.110) & 11.152 & 0.406\\
+\hspace{1em}xgboost-aft & --- & 0.754 (0.038) & 6.738 & 0.005\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{FCL; relapse, n = 541, p = 7}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.029 (0.017) & 0.620 (0.024) & 0.100 & 0.002\\
+\hspace{1em}ranger-extratrees & 0.017 (0.016) & 0.596 (0.025) & 0.041 & 0.081\\
+\hspace{1em}obliqueRSF-net & 0.013 (0.016) & 0.593 (0.024) & 217.838 & 6.232\\
+\hspace{1em}aorsf-random & 0.013 (0.018) & 0.595 (0.024) & 0.394 & 0.021\\
+\hspace{1em}xgboost-cox & 0.010 (0.016) & 0.598 (0.031) & 1.331 & 0.002\\
+\hspace{1em}cif-standard & 0.008 (0.021) & 0.594 (0.023) & 0.315 & 1.056\\
+\hspace{1em}aorsf-cph & 0.007 (0.020) & 0.595 (0.026) & 0.262 & 0.021\\
+\hspace{1em}aorsf-fast & 0.007 (0.019) & 0.594 (0.025) & 0.122 & 0.021\\
+\hspace{1em}aorsf-net & 0.006 (0.020) & 0.592 (0.026) & 18.761 & 0.022\\
+\hspace{1em}cif-extension & -0.005 (0.023) & 0.580 (0.028) & 6.164 & 2.309\\
+\hspace{1em}nn-cox & -0.008 (0.023) & 0.526 (0.055) & 12.031 & 0.466\\
+\hspace{1em}cif-rotate & -0.012 (0.025) & 0.583 (0.030) & 7.411 & 2.486\\
+\hspace{1em}rsf-standard & -0.026 (0.032) & 0.577 (0.024) & 1.081 & 0.088\\
+\hspace{1em}xgboost-aft & --- & 0.582 (0.034) & 6.223 & 0.005\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{GBSG II; recurrence or death, n = 686, p = 10}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.124 (0.016) & 0.746 (0.017) & 286.149 & 6.874\\
+\hspace{1em}cif-standard & 0.123 (0.020) & 0.743 (0.020) & 0.507 & 2.289\\
+\hspace{1em}rsf-standard & 0.120 (0.023) & 0.738 (0.019) & 1.437 & 0.115\\
+\hspace{1em}aorsf-net & 0.120 (0.024) & 0.738 (0.020) & 36.113 & 0.038\\
+\hspace{1em}aorsf-cph & 0.120 (0.025) & 0.736 (0.018) & 0.411 & 0.038\\
+\hspace{1em}aorsf-fast & 0.115 (0.024) & 0.733 (0.017) & 0.168 & 0.037\\
+\hspace{1em}cif-extension & 0.114 (0.017) & 0.743 (0.019) & 7.560 & 2.919\\
+\hspace{1em}cif-rotate & 0.107 (0.023) & 0.729 (0.017) & 11.241 & 3.023\\
+\hspace{1em}aorsf-random & 0.104 (0.023) & 0.724 (0.025) & 0.754 & 0.036\\
+\hspace{1em}ranger-extratrees & 0.094 (0.018) & 0.736 (0.025) & 0.102 & 0.143\\
+\hspace{1em}glmnet-cox & 0.090 (0.019) & 0.728 (0.021) & 0.106 & 0.002\\
+\hspace{1em}xgboost-cox & 0.083 (0.017) & 0.730 (0.020) & 2.538 & 0.003\\
+\hspace{1em}nn-cox & -0.007 (0.012) & 0.509 (0.061) & 11.658 & 0.746\\
+\hspace{1em}xgboost-aft & --- & 0.729 (0.021) & 10.625 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{GUIDE-IT; CVD death, n = 894, p = 59}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.746 (0.027) & 0.152 & 0.036\\
+\hspace{1em}aorsf-net & 0.074 (0.019) & 0.743 (0.027) & 29.058 & 0.041\\
+\hspace{1em}aorsf-cph & 0.071 (0.018) & 0.741 (0.028) & 0.403 & 0.037\\
+\hspace{1em}glmnet-cox & 0.063 (0.041) & 0.715 (0.091) & 0.502 & 0.002\\
+\hspace{1em}obliqueRSF-net & 0.063 (0.013) & 0.741 (0.023) & 221.806 & 11.417\\
+\hspace{1em}cif-rotate & 0.059 (0.016) & 0.721 (0.025) & 35.190 & 4.947\\
+\hspace{1em}cif-standard & 0.058 (0.014) & 0.738 (0.022) & 1.564 & 3.334\\
+\hspace{1em}ranger-extratrees & 0.054 (0.013) & 0.737 (0.029) & 0.118 & 0.176\\
+\hspace{1em}cif-extension & 0.052 (0.011) & 0.730 (0.022) & 13.507 & 5.567\\
+\hspace{1em}rsf-standard & 0.046 (0.023) & 0.705 (0.025) & 0.195 & 0.064\\
+\hspace{1em}xgboost-cox & 0.039 (0.051) & 0.747 (0.020) & 3.831 & 0.003\\
+\hspace{1em}aorsf-random & 0.033 (0.012) & 0.695 (0.030) & 0.536 & 0.039\\
+\hspace{1em}nn-cox & 0.008 (0.018) & 0.630 (0.123) & 12.211 & 0.596\\
+\hspace{1em}xgboost-aft & --- & 0.734 (0.020) & 11.525 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{GUIDE-IT; HF hospitalization, n = 894, p = 59}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.082 (0.017) & 0.722 (0.023) & 53.095 & 0.058\\
+\hspace{1em}aorsf-cph & 0.081 (0.018) & 0.722 (0.023) & 0.659 & 0.052\\
+\hspace{1em}aorsf-fast & 0.081 (0.019) & 0.722 (0.025) & 0.232 & 0.052\\
+\hspace{1em}ranger-extratrees & 0.073 (0.010) & 0.722 (0.022) & 0.137 & 0.198\\
+\hspace{1em}obliqueRSF-net & 0.073 (0.010) & 0.721 (0.023) & 389.465 & 9.365\\
+\hspace{1em}cif-standard & 0.070 (0.010) & 0.716 (0.023) & 1.468 & 3.315\\
+\hspace{1em}cif-rotate & 0.067 (0.019) & 0.708 (0.029) & 41.655 & 5.185\\
+\hspace{1em}cif-extension & 0.064 (0.009) & 0.714 (0.022) & 15.396 & 6.113\\
+\hspace{1em}glmnet-cox & 0.058 (0.020) & 0.699 (0.025) & 0.416 & 0.003\\
+\hspace{1em}rsf-standard & 0.058 (0.022) & 0.694 (0.026) & 1.515 & 0.121\\
+\hspace{1em}nn-cox & 0.053 (0.028) & 0.706 (0.032) & 12.912 & 0.599\\
+\hspace{1em}aorsf-random & 0.049 (0.010) & 0.682 (0.023) & 0.914 & 0.054\\
+\hspace{1em}xgboost-cox & 0.038 (0.017) & 0.698 (0.027) & 2.955 & 0.003\\
+\hspace{1em}xgboost-aft & --- & 0.697 (0.025) & 11.409 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Lung cancer; death, n = 442, p = 24}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.063 (0.032) & 0.691 (0.019) & 0.316 & 0.030\\
+\hspace{1em}aorsf-net & 0.061 (0.030) & 0.685 (0.019) & 31.742 & 0.031\\
+\hspace{1em}aorsf-fast & 0.059 (0.033) & 0.690 (0.019) & 0.125 & 0.030\\
+\hspace{1em}obliqueRSF-net & 0.058 (0.020) & 0.678 (0.020) & 294.626 & 2.961\\
+\hspace{1em}cif-extension & 0.050 (0.018) & 0.667 (0.019) & 9.104 & 3.317\\
+\hspace{1em}rsf-standard & 0.050 (0.035) & 0.673 (0.023) & 0.941 & 0.073\\
+\hspace{1em}cif-standard & 0.050 (0.023) & 0.667 (0.022) & 0.315 & 0.846\\
+\hspace{1em}ranger-extratrees & 0.049 (0.016) & 0.675 (0.019) & 0.037 & 0.065\\
+\hspace{1em}cif-rotate & 0.047 (0.026) & 0.664 (0.021) & 17.129 & 3.089\\
+\hspace{1em}glmnet-cox & 0.041 (0.024) & 0.664 (0.034) & 0.123 & 0.002\\
+\hspace{1em}aorsf-random & 0.040 (0.022) & 0.651 (0.023) & 0.538 & 0.026\\
+\hspace{1em}nn-cox & 0.033 (0.025) & 0.647 (0.029) & 12.472 & 0.368\\
+\hspace{1em}xgboost-cox & 0.018 (0.019) & 0.647 (0.027) & 1.541 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.652 (0.026) & 8.410 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{MESA; coronary heart disease, n = 6785, p = 48}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.063 (0.010) & 0.807 (0.011) & 1.219 & 0.352\\
+\hspace{1em}aorsf-net & 0.062 (0.010) & 0.805 (0.012) & 176.990 & 0.387\\
+\hspace{1em}obliqueRSF-net & 0.062 (0.008) & 0.808 (0.012) & 488.662 & 265.171\\
+\hspace{1em}aorsf-cph & 0.060 (0.010) & 0.801 (0.012) & 5.393 & 0.382\\
+\hspace{1em}cif-standard & 0.059 (0.007) & 0.803 (0.013) & 24.446 & 98.767\\
+\hspace{1em}cif-rotate & 0.058 (0.009) & 0.802 (0.013) & 284.668 & 37.340\\
+\hspace{1em}rsf-standard & 0.057 (0.012) & 0.795 (0.013) & 3.426 & 1.202\\
+\hspace{1em}ranger-extratrees & 0.047 (0.004) & 0.794 (0.011) & 7.360 & 6.260\\
+\hspace{1em}cif-extension & 0.047 (0.003) & 0.805 (0.013) & 98.278 & 28.773\\
+\hspace{1em}glmnet-cox & 0.038 (0.017) & 0.775 (0.016) & 4.907 & 0.007\\
+\hspace{1em}nn-cox & 0.038 (0.017) & 0.767 (0.021) & 18.380 & 16.712\\
+\hspace{1em}aorsf-random & 0.031 (0.005) & 0.735 (0.015) & 2.927 & 0.397\\
+\hspace{1em}xgboost-cox & 0.015 (0.028) & 0.802 (0.013) & 4.763 & 0.009\\
+\hspace{1em}xgboost-aft & --- & 0.802 (0.012) & 18.127 & 0.009\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{MESA; death, n = 6793, p = 48}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.144 (0.008) & 0.792 (0.009) & 318.785 & 0.546\\
+\hspace{1em}aorsf-fast & 0.144 (0.009) & 0.792 (0.009) & 1.694 & 0.506\\
+\hspace{1em}aorsf-cph & 0.143 (0.008) & 0.791 (0.009) & 6.893 & 0.523\\
+\hspace{1em}rsf-standard & 0.140 (0.008) & 0.784 (0.009) & 4.818 & 0.502\\
+\hspace{1em}obliqueRSF-net & 0.139 (0.007) & 0.791 (0.009) & 1176.365 & 156.871\\
+\hspace{1em}cif-standard & 0.134 (0.007) & 0.788 (0.009) & 23.671 & 101.207\\
+\hspace{1em}glmnet-cox & 0.131 (0.026) & 0.789 (0.012) & 1.560 & 0.007\\
+\hspace{1em}nn-cox & 0.127 (0.020) & 0.784 (0.016) & 29.272 & 17.344\\
+\hspace{1em}cif-rotate & 0.126 (0.007) & 0.783 (0.010) & 319.953 & 37.290\\
+\hspace{1em}ranger-extratrees & 0.113 (0.004) & 0.784 (0.008) & 9.060 & 6.474\\
+\hspace{1em}cif-extension & 0.092 (0.003) & 0.781 (0.009) & 111.068 & 32.105\\
+\hspace{1em}aorsf-random & 0.068 (0.005) & 0.725 (0.008) & 5.608 & 0.565\\
+\hspace{1em}xgboost-cox & 0.056 (0.029) & 0.794 (0.009) & 8.021 & 0.009\\
+\hspace{1em}xgboost-aft & --- & 0.793 (0.009) & 20.287 & 0.010\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{MESA; heart failure, n = 6785, p = 48}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.115 (0.010) & 0.866 (0.013) & 1.094 & 0.311\\
+\hspace{1em}aorsf-net & 0.114 (0.011) & 0.863 (0.013) & 149.605 & 0.339\\
+\hspace{1em}aorsf-cph & 0.109 (0.011) & 0.858 (0.014) & 4.842 & 0.326\\
+\hspace{1em}rsf-standard & 0.108 (0.012) & 0.856 (0.012) & 3.125 & 1.151\\
+\hspace{1em}obliqueRSF-net & 0.108 (0.008) & 0.869 (0.011) & 393.285 & 338.322\\
+\hspace{1em}cif-rotate & 0.105 (0.010) & 0.869 (0.013) & 260.914 & 38.177\\
+\hspace{1em}cif-standard & 0.102 (0.009) & 0.864 (0.013) & 24.344 & 101.534\\
+\hspace{1em}cif-extension & 0.077 (0.005) & 0.864 (0.011) & 94.628 & 30.361\\
+\hspace{1em}ranger-extratrees & 0.075 (0.005) & 0.849 (0.015) & 7.492 & 6.923\\
+\hspace{1em}nn-cox & 0.071 (0.024) & 0.826 (0.016) & 15.797 & 17.312\\
+\hspace{1em}aorsf-random & 0.064 (0.006) & 0.795 (0.014) & 2.520 & 0.369\\
+\hspace{1em}glmnet-cox & 0.043 (0.044) & 0.767 (0.139) & 3.777 & 0.006\\
+\hspace{1em}xgboost-cox & -0.008 (0.019) & 0.869 (0.011) & 6.764 & 0.009\\
+\hspace{1em}xgboost-aft & --- & 0.870 (0.012) & 18.620 & 0.010\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{MESA; stroke, n = 6783, p = 48}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.025 (0.004) & 0.767 (0.016) & 357.039 & 299.786\\
+\hspace{1em}cif-rotate & 0.025 (0.004) & 0.764 (0.017) & 268.402 & 37.899\\
+\hspace{1em}cif-standard & 0.025 (0.004) & 0.762 (0.017) & 23.450 & 98.166\\
+\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.764 (0.016) & 1.072 & 0.307\\
+\hspace{1em}aorsf-net & 0.024 (0.006) & 0.759 (0.017) & 139.617 & 0.333\\
+\hspace{1em}aorsf-cph & 0.023 (0.005) & 0.758 (0.016) & 4.266 & 0.316\\
+\hspace{1em}ranger-extratrees & 0.022 (0.003) & 0.759 (0.016) & 7.610 & 6.738\\
+\hspace{1em}glmnet-cox & 0.021 (0.009) & 0.765 (0.017) & 3.876 & 0.007\\
+\hspace{1em}cif-extension & 0.021 (0.002) & 0.768 (0.017) & 94.913 & 29.730\\
+\hspace{1em}rsf-standard & 0.019 (0.009) & 0.745 (0.018) & 3.221 & 1.242\\
+\hspace{1em}nn-cox & 0.018 (0.007) & 0.746 (0.028) & 16.152 & 17.979\\
+\hspace{1em}aorsf-random & 0.013 (0.003) & 0.714 (0.022) & 2.420 & 0.343\\
+\hspace{1em}xgboost-cox & 0.000 (0.025) & 0.762 (0.018) & 4.347 & 0.008\\
+\hspace{1em}xgboost-aft & --- & 0.764 (0.015) & 16.257 & 0.009\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Monoclonal gammopathy; death, n = 1384, p = 8}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.159 (0.019) & 0.744 (0.014) & 15.123 & 4.858\\
+\hspace{1em}aorsf-cph & 0.158 (0.016) & 0.743 (0.011) & 1.154 & 0.084\\
+\hspace{1em}aorsf-fast & 0.157 (0.016) & 0.743 (0.011) & 0.408 & 0.088\\
+\hspace{1em}aorsf-net & 0.155 (0.016) & 0.741 (0.011) & 85.428 & 0.085\\
+\hspace{1em}obliqueRSF-net & 0.155 (0.013) & 0.743 (0.011) & 232.467 & 12.924\\
+\hspace{1em}cif-standard & 0.151 (0.015) & 0.738 (0.012) & 1.537 & 5.829\\
+\hspace{1em}rsf-standard & 0.151 (0.017) & 0.737 (0.011) & 2.281 & 0.194\\
+\hspace{1em}aorsf-random & 0.146 (0.013) & 0.735 (0.011) & 1.757 & 0.084\\
+\hspace{1em}cif-extension & 0.143 (0.009) & 0.747 (0.013) & 11.222 & 4.744\\
+\hspace{1em}glmnet-cox & 0.137 (0.021) & 0.726 (0.014) & 0.136 & 0.003\\
+\hspace{1em}xgboost-cox & 0.122 (0.012) & 0.733 (0.012) & 3.919 & 0.003\\
+\hspace{1em}ranger-extratrees & 0.115 (0.005) & 0.744 (0.012) & 0.064 & 0.181\\
+\hspace{1em}nn-cox & 0.034 (0.057) & 0.599 (0.112) & 16.529 & 0.689\\
+\hspace{1em}xgboost-aft & --- & 0.733 (0.013) & 12.094 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Monoclonal gammopathy; malignancy, n = 1384, p = 8}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.015 (0.011) & 0.651 (0.055) & 0.118 & 0.003\\
+\hspace{1em}aorsf-cph & 0.011 (0.013) & 0.644 (0.036) & 0.574 & 0.040\\
+\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.641 (0.036) & 0.201 & 0.041\\
+\hspace{1em}ranger-extratrees & 0.008 (0.006) & 0.642 (0.030) & 0.095 & 0.177\\
+\hspace{1em}cif-extension & 0.008 (0.010) & 0.625 (0.028) & 9.141 & 4.788\\
+\hspace{1em}obliqueRSF-net & 0.007 (0.010) & 0.628 (0.033) & 41.856 & 16.910\\
+\hspace{1em}aorsf-net & 0.007 (0.014) & 0.641 (0.034) & 22.366 & 0.041\\
+\hspace{1em}aorsf-random & 0.007 (0.013) & 0.633 (0.033) & 0.517 & 0.040\\
+\hspace{1em}xgboost-cox & 0.007 (0.017) & 0.639 (0.039) & 1.783 & 0.003\\
+\hspace{1em}cif-standard & 0.006 (0.011) & 0.628 (0.033) & 1.689 & 5.603\\
+\hspace{1em}nn-cox & -0.003 (0.005) & 0.510 (0.032) & 11.229 & 0.597\\
+\hspace{1em}rsf-standard & -0.009 (0.018) & 0.616 (0.036) & 0.824 & 0.073\\
+\hspace{1em}cif-rotate & -0.024 (0.023) & 0.553 (0.035) & 12.975 & 4.603\\
+\hspace{1em}xgboost-aft & --- & 0.629 (0.039) & 10.748 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Movies released in 2015-2018; gross 1M USD, n = 551, p = 46}}}\\
+\hline
+\hspace{1em}cif-rotate & 0.636 (0.024) & 0.943 (0.007) & 19.879 & 3.571\\
+\hspace{1em}glmnet-cox & 0.618 (0.034) & 0.940 (0.009) & 0.204 & 0.002\\
+\hspace{1em}nn-cox & 0.534 (0.072) & 0.910 (0.027) & 17.266 & 0.663\\
+\hspace{1em}aorsf-net & 0.530 (0.028) & 0.928 (0.010) & 50.720 & 0.043\\
+\hspace{1em}aorsf-cph & 0.522 (0.024) & 0.925 (0.011) & 0.788 & 0.041\\
+\hspace{1em}rsf-standard & 0.519 (0.022) & 0.922 (0.010) & 1.631 & 0.106\\
+\hspace{1em}aorsf-fast & 0.516 (0.027) & 0.923 (0.012) & 0.214 & 0.041\\
+\hspace{1em}xgboost-cox & 0.512 (0.029) & 0.932 (0.009) & 13.972 & 0.004\\
+\hspace{1em}cif-standard & 0.472 (0.029) & 0.902 (0.018) & 0.453 & 1.910\\
+\hspace{1em}cif-extension & 0.454 (0.025) & 0.920 (0.013) & 8.854 & 3.924\\
+\hspace{1em}ranger-extratrees & 0.430 (0.025) & 0.900 (0.019) & 0.049 & 0.103\\
+\hspace{1em}obliqueRSF-net & 0.319 (0.022) & 0.909 (0.017) & 155.421 & 8.847\\
+\hspace{1em}aorsf-random & 0.300 (0.032) & 0.849 (0.027) & 0.869 & 0.039\\
+\hspace{1em}xgboost-aft & --- & 0.927 (0.010) & 33.545 & 0.008\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{NCCTG Lung Cancer; death, n = 228, p = 9}}}\\
+\hline
+\hspace{1em}aorsf-random & 0.076 (0.030) & 0.686 (0.026) & 0.304 & 0.015\\
+\hspace{1em}ranger-extratrees & 0.062 (0.028) & 0.675 (0.033) & 0.023 & 0.031\\
+\hspace{1em}aorsf-fast & 0.060 (0.043) & 0.672 (0.026) & 0.067 & 0.016\\
+\hspace{1em}obliqueRSF-net & 0.058 (0.026) & 0.676 (0.029) & 106.084 & 1.468\\
+\hspace{1em}aorsf-cph & 0.058 (0.041) & 0.670 (0.024) & 0.150 & 0.016\\
+\hspace{1em}cif-standard & 0.055 (0.032) & 0.670 (0.030) & 0.130 & 0.252\\
+\hspace{1em}cif-extension & 0.051 (0.032) & 0.664 (0.029) & 3.799 & 1.502\\
+\hspace{1em}aorsf-net & 0.047 (0.040) & 0.668 (0.026) & 16.041 & 0.016\\
+\hspace{1em}glmnet-cox & 0.033 (0.031) & 0.638 (0.059) & 0.081 & 0.002\\
+\hspace{1em}rsf-standard & 0.023 (0.039) & 0.642 (0.025) & 0.087 & 0.037\\
+\hspace{1em}cif-rotate & 0.017 (0.041) & 0.632 (0.032) & 4.687 & 1.897\\
+\hspace{1em}xgboost-cox & 0.011 (0.023) & 0.648 (0.032) & 0.721 & 0.002\\
+\hspace{1em}nn-cox & -0.051 (0.163) & 0.512 (0.082) & 10.516 & 0.209\\
+\hspace{1em}xgboost-aft & --- & 0.637 (0.034) & 6.271 & 0.005\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{NKI 70 gene signature; death or metastasis, n = 144, p = 77}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.142 (0.056) & 0.804 (0.056) & 10.798 & 0.014\\
+\hspace{1em}aorsf-cph & 0.124 (0.049) & 0.802 (0.051) & 0.078 & 0.013\\
+\hspace{1em}aorsf-fast & 0.121 (0.052) & 0.802 (0.054) & 0.052 & 0.014\\
+\hspace{1em}cif-rotate & 0.118 (0.059) & 0.787 (0.049) & 27.382 & 3.379\\
+\hspace{1em}obliqueRSF-net & 0.106 (0.051) & 0.792 (0.061) & 79.059 & 0.558\\
+\hspace{1em}cif-extension & 0.098 (0.055) & 0.799 (0.061) & 8.595 & 3.554\\
+\hspace{1em}cif-standard & 0.088 (0.051) & 0.781 (0.065) & 0.145 & 0.149\\
+\hspace{1em}rsf-standard & 0.087 (0.048) & 0.755 (0.050) & 0.067 & 0.025\\
+\hspace{1em}ranger-extratrees & 0.064 (0.044) & 0.774 (0.054) & 0.024 & 0.030\\
+\hspace{1em}aorsf-random & 0.053 (0.045) & 0.741 (0.060) & 0.183 & 0.015\\
+\hspace{1em}nn-cox & 0.051 (0.102) & 0.715 (0.100) & 11.692 & 0.121\\
+\hspace{1em}glmnet-cox & 0.049 (0.064) & 0.726 (0.090) & 0.265 & 0.002\\
+\hspace{1em}xgboost-cox & -0.028 (0.029) & 0.566 (0.093) & 0.118 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.770 (0.056) & 4.896 & 0.005\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Non-alcohol fatty liver disease; death, n = 17549, p = 24}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.213 (0.008) & 0.868 (0.005) & 17.724 & 1.232\\
+\hspace{1em}aorsf-fast & 0.212 (0.009) & 0.869 (0.005) & 4.868 & 1.247\\
+\hspace{1em}aorsf-net & 0.210 (0.008) & 0.864 (0.006) & 471.404 & 1.283\\
+\hspace{1em}obliqueRSF-net & 0.209 (0.008) & 0.868 (0.006) & 1428.698 & 1042.701\\
+\hspace{1em}rsf-standard & 0.207 (0.009) & 0.860 (0.005) & 10.516 & 1.205\\
+\hspace{1em}glmnet-cox & 0.207 (0.011) & 0.860 (0.005) & 1.345 & 0.012\\
+\hspace{1em}cif-standard & 0.205 (0.007) & 0.863 (0.006) & 67.597 & 624.624\\
+\hspace{1em}cif-rotate & 0.190 (0.008) & 0.865 (0.005) & 263.660 & 62.919\\
+\hspace{1em}ranger-extratrees & 0.181 (0.007) & 0.860 (0.005) & 39.632 & 80.768\\
+\hspace{1em}cif-extension & 0.166 (0.003) & 0.866 (0.006) & 125.288 & 53.237\\
+\hspace{1em}aorsf-random & 0.140 (0.006) & 0.838 (0.007) & 8.915 & 1.339\\
+\hspace{1em}xgboost-cox & 0.020 (0.015) & 0.876 (0.005) & 8.907 & 0.017\\
+\hspace{1em}nn-cox & -0.002 (0.009) & 0.565 (0.092) & 20.937 & 106.131\\
+\hspace{1em}xgboost-aft & --- & 0.875 (0.005) & 27.908 & 0.015\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Primary biliary cholangitis; death, n = 276, p = 19}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.430 (0.032) & 0.908 (0.021) & 0.082 & 0.019\\
+\hspace{1em}aorsf-cph & 0.418 (0.034) & 0.906 (0.021) & 0.162 & 0.018\\
+\hspace{1em}aorsf-net & 0.413 (0.035) & 0.905 (0.021) & 14.047 & 0.019\\
+\hspace{1em}cif-rotate & 0.405 (0.040) & 0.899 (0.022) & 10.102 & 1.933\\
+\hspace{1em}rsf-standard & 0.392 (0.034) & 0.895 (0.023) & 0.113 & 0.038\\
+\hspace{1em}obliqueRSF-net & 0.369 (0.032) & 0.907 (0.022) & 111.656 & 1.787\\
+\hspace{1em}aorsf-random & 0.354 (0.031) & 0.893 (0.020) & 0.308 & 0.020\\
+\hspace{1em}cif-standard & 0.352 (0.034) & 0.904 (0.025) & 0.206 & 0.363\\
+\hspace{1em}cif-extension & 0.348 (0.033) & 0.901 (0.023) & 5.775 & 2.199\\
+\hspace{1em}glmnet-cox & 0.342 (0.044) & 0.886 (0.028) & 0.116 & 0.002\\
+\hspace{1em}ranger-extratrees & 0.277 (0.027) & 0.894 (0.027) & 0.029 & 0.038\\
+\hspace{1em}xgboost-cox & 0.256 (0.103) & 0.881 (0.027) & 4.960 & 0.003\\
+\hspace{1em}nn-cox & -0.017 (0.018) & 0.563 (0.124) & 11.751 & 0.247\\
+\hspace{1em}xgboost-aft & --- & 0.883 (0.024) & 9.644 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Rotterdam tumor bank; death, n = 2982, p = 11}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.166 (0.012) & 0.762 (0.009) & 147.998 & 0.185\\
+\hspace{1em}obliqueRSF-net & 0.163 (0.010) & 0.761 (0.009) & 439.210 & 37.683\\
+\hspace{1em}aorsf-cph & 0.163 (0.012) & 0.759 (0.009) & 2.520 & 0.201\\
+\hspace{1em}aorsf-fast & 0.161 (0.012) & 0.757 (0.009) & 0.845 & 0.198\\
+\hspace{1em}cif-standard & 0.159 (0.010) & 0.759 (0.009) & 4.629 & 22.523\\
+\hspace{1em}rsf-standard & 0.159 (0.014) & 0.756 (0.009) & 3.066 & 0.967\\
+\hspace{1em}aorsf-random & 0.153 (0.010) & 0.752 (0.010) & 2.840 & 0.180\\
+\hspace{1em}cif-rotate & 0.147 (0.011) & 0.751 (0.011) & 34.328 & 8.629\\
+\hspace{1em}ranger-extratrees & 0.139 (0.006) & 0.749 (0.009) & 3.498 & 2.152\\
+\hspace{1em}xgboost-cox & 0.130 (0.014) & 0.753 (0.010) & 4.068 & 0.004\\
+\hspace{1em}cif-extension & 0.129 (0.004) & 0.751 (0.008) & 22.740 & 8.982\\
+\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.731 (0.009) & 0.278 & 0.004\\
+\hspace{1em}nn-cox & -0.009 (0.042) & 0.531 (0.050) & 16.635 & 8.901\\
+\hspace{1em}xgboost-aft & --- & 0.761 (0.009) & 14.813 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Rotterdam tumor bank; recurrence, n = 2982, p = 11}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.148 (0.010) & 0.737 (0.009) & 520.813 & 39.774\\
+\hspace{1em}aorsf-net & 0.146 (0.011) & 0.735 (0.009) & 160.272 & 0.191\\
+\hspace{1em}aorsf-cph & 0.145 (0.012) & 0.734 (0.008) & 2.678 & 0.205\\
+\hspace{1em}cif-standard & 0.144 (0.011) & 0.734 (0.009) & 4.807 & 23.027\\
+\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 0.854 & 0.206\\
+\hspace{1em}aorsf-random & 0.141 (0.010) & 0.730 (0.008) & 3.192 & 0.185\\
+\hspace{1em}rsf-standard & 0.139 (0.012) & 0.731 (0.008) & 3.003 & 1.000\\
+\hspace{1em}ranger-extratrees & 0.135 (0.007) & 0.734 (0.009) & 3.564 & 2.555\\
+\hspace{1em}cif-rotate & 0.129 (0.010) & 0.725 (0.009) & 36.519 & 8.483\\
+\hspace{1em}cif-extension & 0.119 (0.006) & 0.731 (0.008) & 23.055 & 8.825\\
+\hspace{1em}glmnet-cox & 0.117 (0.008) & 0.727 (0.008) & 0.258 & 0.004\\
+\hspace{1em}xgboost-cox & 0.113 (0.008) & 0.729 (0.009) & 3.628 & 0.004\\
+\hspace{1em}nn-cox & -0.007 (0.027) & 0.511 (0.045) & 17.722 & 7.825\\
+\hspace{1em}xgboost-aft & --- & 0.735 (0.009) & 14.317 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Serum free light chain; death, n = 7874, p = 10}}}\\
+\hline
+\hspace{1em}aorsf-fast & 0.250 (0.014) & 0.825 (0.007) & 2.023 & 0.587\\
+\hspace{1em}aorsf-cph & 0.250 (0.013) & 0.825 (0.008) & 6.401 & 0.580\\
+\hspace{1em}aorsf-net & 0.250 (0.012) & 0.823 (0.008) & 278.411 & 0.563\\
+\hspace{1em}glmnet-cox & 0.248 (0.012) & 0.820 (0.007) & 0.539 & 0.006\\
+\hspace{1em}obliqueRSF-net & 0.247 (0.011) & 0.821 (0.008) & 1113.284 & 151.041\\
+\hspace{1em}ranger-extratrees & 0.243 (0.009) & 0.820 (0.007) & 12.743 & 12.085\\
+\hspace{1em}cif-standard & 0.243 (0.011) & 0.818 (0.008) & 19.565 & 120.023\\
+\hspace{1em}rsf-standard & 0.243 (0.013) & 0.815 (0.008) & 5.399 & 0.585\\
+\hspace{1em}aorsf-random & 0.231 (0.012) & 0.816 (0.008) & 6.681 & 0.568\\
+\hspace{1em}cif-rotate & 0.228 (0.009) & 0.819 (0.007) & 65.379 & 21.402\\
+\hspace{1em}cif-extension & 0.201 (0.005) & 0.820 (0.008) & 41.381 & 20.976\\
+\hspace{1em}xgboost-cox & 0.094 (0.038) & 0.824 (0.007) & 5.927 & 0.008\\
+\hspace{1em}nn-cox & 0.002 (0.005) & 0.616 (0.122) & 26.319 & 26.895\\
+\hspace{1em}xgboost-aft & --- & 0.823 (0.008) & 18.504 & 0.009\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{SPRINT; CVD death, n = 9361, p = 174}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.071 (0.011) & 0.795 (0.011) & 13.850 & 0.011\\
+\hspace{1em}aorsf-net & 0.070 (0.007) & 0.796 (0.011) & 337.860 & 0.660\\
+\hspace{1em}aorsf-fast & 0.069 (0.006) & 0.797 (0.011) & 2.581 & 0.638\\
+\hspace{1em}aorsf-cph & 0.069 (0.006) & 0.797 (0.011) & 9.028 & 0.596\\
+\hspace{1em}obliqueRSF-net & 0.068 (0.005) & 0.798 (0.012) & 1017.350 & 425.134\\
+\hspace{1em}rsf-standard & 0.065 (0.007) & 0.788 (0.014) & 3.894 & 1.314\\
+\hspace{1em}cif-standard & 0.061 (0.003) & 0.798 (0.011) & 50.694 & 181.616\\
+\hspace{1em}cif-rotate & 0.060 (0.005) & 0.791 (0.012) & 930.893 & 113.261\\
+\hspace{1em}ranger-extratrees & 0.054 (0.003) & 0.791 (0.012) & 7.314 & 7.943\\
+\hspace{1em}nn-cox & 0.039 (0.018) & 0.764 (0.027) & 20.414 & 24.555\\
+\hspace{1em}cif-extension & 0.034 (0.002) & 0.789 (0.011) & 122.779 & 33.342\\
+\hspace{1em}aorsf-random & 0.026 (0.002) & 0.747 (0.016) & 5.887 & 0.742\\
+\hspace{1em}xgboost-cox & 0.006 (0.017) & 0.799 (0.011) & 6.888 & 0.013\\
+\hspace{1em}xgboost-aft & --- & 0.796 (0.012) & 20.126 & 0.012\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{SPRINT; death, n = 9361, p = 174}}}\\
+\hline
+\hspace{1em}glmnet-cox & 0.123 (0.012) & 0.771 (0.009) & 5.422 & 0.010\\
+\hspace{1em}aorsf-cph & 0.117 (0.008) & 0.770 (0.008) & 12.876 & 1.527\\
+\hspace{1em}aorsf-fast & 0.116 (0.008) & 0.770 (0.008) & 3.583 & 1.514\\
+\hspace{1em}aorsf-net & 0.113 (0.009) & 0.769 (0.009) & 590.419 & 0.934\\
+\hspace{1em}obliqueRSF-net & 0.112 (0.007) & 0.767 (0.008) & 2630.588 & 231.667\\
+\hspace{1em}rsf-standard & 0.110 (0.008) & 0.763 (0.009) & 6.407 & 0.663\\
+\hspace{1em}cif-standard & 0.106 (0.006) & 0.764 (0.008) & 49.842 & 190.804\\
+\hspace{1em}nn-cox & 0.097 (0.010) & 0.757 (0.009) & 34.063 & 33.278\\
+\hspace{1em}ranger-extratrees & 0.096 (0.005) & 0.756 (0.009) & 11.323 & 9.400\\
+\hspace{1em}cif-rotate & 0.090 (0.007) & 0.745 (0.009) & 1109.925 & 112.893\\
+\hspace{1em}cif-extension & 0.055 (0.002) & 0.747 (0.009) & 137.470 & 34.230\\
+\hspace{1em}aorsf-random & 0.052 (0.003) & 0.720 (0.010) & 9.559 & 1.034\\
+\hspace{1em}xgboost-cox & 0.030 (0.023) & 0.772 (0.008) & 9.057 & 0.014\\
+\hspace{1em}xgboost-aft & --- & 0.772 (0.007) & 23.335 & 0.013\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Systolic Heart Failure; death, n = 2231, p = 41}}}\\
+\hline
+\hspace{1em}obliqueRSF-net & 0.114 (0.012) & 0.747 (0.012) & 381.891 & 25.692\\
+\hspace{1em}glmnet-cox & 0.113 (0.013) & 0.745 (0.012) & 0.276 & 0.004\\
+\hspace{1em}cif-rotate & 0.113 (0.013) & 0.741 (0.011) & 71.714 & 10.523\\
+\hspace{1em}aorsf-net & 0.112 (0.013) & 0.743 (0.012) & 118.505 & 0.158\\
+\hspace{1em}aorsf-cph & 0.112 (0.013) & 0.744 (0.012) & 1.895 & 0.147\\
+\hspace{1em}aorsf-fast & 0.110 (0.015) & 0.743 (0.011) & 0.586 & 0.146\\
+\hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 4.079 & 16.213\\
+\hspace{1em}rsf-standard & 0.105 (0.011) & 0.735 (0.011) & 2.510 & 0.252\\
+\hspace{1em}cif-extension & 0.094 (0.006) & 0.744 (0.012) & 29.918 & 10.109\\
+\hspace{1em}ranger-extratrees & 0.091 (0.008) & 0.738 (0.012) & 3.266 & 1.328\\
+\hspace{1em}xgboost-cox & 0.090 (0.009) & 0.744 (0.010) & 4.229 & 0.004\\
+\hspace{1em}aorsf-random & 0.080 (0.006) & 0.731 (0.013) & 2.448 & 0.151\\
+\hspace{1em}nn-cox & 0.074 (0.028) & 0.705 (0.036) & 18.945 & 5.181\\
+\hspace{1em}xgboost-aft & --- & 0.741 (0.009) & 13.087 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{VA lung cancer trial; death, n = 137, p = 8}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.201 (0.050) & 0.797 (0.035) & 9.602 & 0.011\\
+\hspace{1em}aorsf-fast & 0.200 (0.050) & 0.795 (0.034) & 0.082 & 0.014\\
+\hspace{1em}cif-rotate & 0.198 (0.065) & 0.789 (0.036) & 4.476 & 1.284\\
+\hspace{1em}aorsf-cph & 0.198 (0.052) & 0.794 (0.035) & 0.105 & 0.011\\
+\hspace{1em}rsf-standard & 0.176 (0.048) & 0.787 (0.037) & 0.078 & 0.025\\
+\hspace{1em}cif-extension & 0.174 (0.048) & 0.795 (0.034) & 3.676 & 1.195\\
+\hspace{1em}glmnet-cox & 0.160 (0.036) & 0.788 (0.037) & 0.087 & 0.002\\
+\hspace{1em}aorsf-random & 0.154 (0.044) & 0.780 (0.037) & 0.213 & 0.012\\
+\hspace{1em}cif-standard & 0.128 (0.040) & 0.770 (0.037) & 0.105 & 0.120\\
+\hspace{1em}obliqueRSF-net & 0.126 (0.034) & 0.796 (0.029) & 62.935 & 0.664\\
+\hspace{1em}ranger-extratrees & 0.092 (0.033) & 0.778 (0.038) & 0.020 & 0.026\\
+\hspace{1em}xgboost-cox & 0.067 (0.078) & 0.750 (0.046) & 1.408 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.754 (0.047) & 5.530 & 0.005\\
+\hspace{1em}nn-cox & -0.023 (0.033) & 0.517 (0.114) & 11.344 & 0.133\\*
+\end{longtable}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\begin{landscape}
+\begin{longtable}[t]{llcccccc}
+\caption{\label{tab:unnamed-chunk-12}Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance. \label{tab:bm_vi}}\\
+\toprule
+\multicolumn{2}{c}{ } & \multicolumn{3}{c}{accelerated oblique RSF} & \multicolumn{2}{c}{xgboost} & \multicolumn{1}{c}{RSF} \\
+\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-8}
+Max correlation & No. observations & Negation & ANOVA & Permutation & SHAP & Gain & Permutation\\
+\midrule
+\endfirsthead
+\caption[]{Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance. \label{tab:bm_vi} \textit{(continued)}}\\
+\toprule
+Max correlation & No. observations & Negation & ANOVA & Permutation & SHAP & Gain & Permutation\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\endlastfoot
+Overall & Overall & 76.0 & 74.0 & 73.2 & 69.7 & 64.7 & 67.8\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textit{\textbf{Interactions}}}\\
+\hline
+\hspace{1em}Overall & Overall & 57.9 & 57.8 & 58.1 & 54.7 & 49.4 & 57.1\\
+\hspace{1em}30 & 500 & 54.3 & 54.5 & 54.7 & 48.2 & 42.6 & 54.8\\
+\hspace{1em}30 & 1,000 & 57.0 & 56.6 & 57.9 & 53.5 & 48.7 & 56.5\\
+\hspace{1em}30 & 2,500 & 61.9 & 59.2 & 64.2 & 61.9 & 61.2 & 60.3\\
+\hspace{1em}15 & 500 & 53.4 & 53.6 & 53.1 & 47.0 & 40.9 & 54.5\\
+\hspace{1em}15 & 1,000 & 56.5 & 55.7 & 57.1 & 52.2 & 45.9 & 55.5\\
+\hspace{1em}15 & 2,500 & 61.3 & 59.0 & 62.6 & 61.1 & 59.0 & 60.8\\
+\hspace{1em}0 & 500 & 52.6 & 54.8 & 53.2 & 44.6 & 40.8 & 53.6\\
+\hspace{1em}0 & 1,000 & 56.9 & 58.7 & 55.5 & 53.0 & 43.1 & 55.6\\
+\hspace{1em}0 & 2,500 & 67.6 & 68.1 & 64.6 & 71.1 & 62.3 & 62.4\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textit{\textbf{Non-linear effects}}}\\
+\hline
+\hspace{1em}Overall & Overall & 71.8 & 69.4 & 67.9 & 65.9 & 60.1 & 61.7\\
+\hspace{1em}30 & 500 & 58.6 & 58.6 & 57.4 & 53.1 & 48.6 & 55.4\\
+\hspace{1em}30 & 1,000 & 61.2 & 59.6 & 58.6 & 57.4 & 52.0 & 55.9\\
+\hspace{1em}30 & 2,500 & 62.1 & 60.1 & 61.0 & 60.1 & 56.4 & 58.1\\
+\hspace{1em}15 & 500 & 63.6 & 61.5 & 60.8 & 54.6 & 49.0 & 57.7\\
+\hspace{1em}15 & 1,000 & 67.6 & 64.9 & 64.8 & 62.4 & 55.8 & 59.1\\
+\hspace{1em}15 & 2,500 & 70.7 & 67.3 & 68.8 & 66.7 & 62.1 & 62.6\\
+\hspace{1em}0 & 500 & 75.6 & 72.5 & 69.3 & 60.0 & 56.2 & 61.2\\
+\hspace{1em}0 & 1,000 & 88.4 & 84.0 & 78.3 & 81.7 & 69.1 & 67.2\\
+\hspace{1em}0 & 2,500 & 98.3 & 96.2 & 91.9 & 97.5 & 91.4 & 78.5\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textit{\textbf{Combination effects}}}\\
+\hline
+\hspace{1em}Overall & Overall & 78.4 & 76.0 & 74.9 & 70.8 & 65.3 & 68.3\\
+\hspace{1em}30 & 500 & 64.8 & 63.8 & 62.7 & 55.6 & 49.8 & 59.3\\
+\hspace{1em}30 & 1,000 & 67.5 & 65.7 & 65.0 & 61.4 & 55.7 & 61.5\\
+\hspace{1em}30 & 2,500 & 69.8 & 67.0 & 68.5 & 65.7 & 62.4 & 64.3\\
+\hspace{1em}15 & 500 & 70.4 & 68.0 & 66.6 & 59.2 & 53.0 & 62.3\\
+\hspace{1em}15 & 1,000 & 75.0 & 71.2 & 71.7 & 66.6 & 59.7 & 64.9\\
+\hspace{1em}15 & 2,500 & 78.9 & 74.8 & 77.1 & 72.9 & 69.0 & 69.9\\
+\hspace{1em}0 & 500 & 84.0 & 81.4 & 76.5 & 66.5 & 61.7 & 67.4\\
+\hspace{1em}0 & 1,000 & 95.4 & 92.4 & 87.8 & 89.4 & 78.6 & 76.3\\
+\hspace{1em}0 & 2,500 & 99.8 & 99.3 & 97.9 & 99.6 & 97.8 & 89.1\\
+\addlinespace[0.3em]
+\multicolumn{8}{l}{\textit{\textbf{Main effects}}}\\
+\hline
+\hspace{1em}Overall & Overall & 91.1 & 89.0 & 88.8 & 85.1 & 82.7 & 83.2\\
+\hspace{1em}30 & 500 & 79.3 & 77.5 & 75.3 & 70.2 & 66.5 & 71.2\\
+\hspace{1em}30 & 1,000 & 83.7 & 80.8 & 80.6 & 77.1 & 74.0 & 74.8\\
+\hspace{1em}30 & 2,500 & 86.7 & 83.7 & 85.2 & 81.8 & 80.5 & 79.3\\
+\hspace{1em}15 & 500 & 86.4 & 83.3 & 81.9 & 75.6 & 71.3 & 75.4\\
+\hspace{1em}15 & 1,000 & 91.3 & 88.2 & 88.7 & 84.9 & 81.6 & 81.0\\
+\hspace{1em}15 & 2,500 & 94.6 & 91.8 & 93.8 & 90.3 & 89.0 & 86.8\\
+\hspace{1em}0 & 500 & 97.7 & 96.2 & 94.1 & 86.2 & 83.6 & 85.7\\
+\hspace{1em}0 & 1,000 & 100.0 & 99.7 & 99.4 & 99.4 & 98.0 & 95.1\\
+\hspace{1em}0 & 2,500 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 99.8\\*
+\end{longtable}
+\end{landscape}
+
+\end{knitrout}
 

### 2022-07-27 R/bench_pred_real.R

@@ -76,7 +76,7 @@ bench_pred_real <- function(data_source,
     Score(
       object = set_names(list(predictions$pred), model_type),
       formula = Surv(time, status) ~ 1,
-      data = test,
+      data = select(test, time, status),
       summary = c('IPA', 'ibs'),
       times = pred_horizon
     ),

### 2022-07-27 R/bench_time.R

@@ -1,0 +1,91 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+
+bench_time <- function(n_obs=100, n_ftr=10, n_tree = 50) {
+
+  train <- sim_surv(n_obs = n_obs, n_pred_main = n_ftr) %>%
+    getElement("data") %>%
+    select(time, status, starts_with("main"))
+
+  pred_horizon <- median(train$time)
+
+  node_size <- 10
+  mtry <- ceiling(sqrt(n_ftr))
+
+
+  start_time <- Sys.time()
+
+  aorsf_fast <- orsf(
+    data = train,
+    n_tree = n_tree,
+    formula = Surv(time, status) ~ .,
+    mtry = mtry,
+    n_retry = 3,
+    split_min_obs = node_size,
+    control = orsf_control_cph(iter_max = 1,
+                               do_scale = FALSE),
+    importance = 'none',
+    oobag_pred = FALSE
+  )
+
+  end_time <- Sys.time()
+
+  time_fit_aorsf <- end_time - start_time
+
+  start_time <- Sys.time()
+
+  rsf_rfsrc <- rfsrc(Surv(time, status) ~ .,
+                        ntree = n_tree,
+                        samptype = 'swr',
+                        perf.type = 'none',
+                        data = train,
+                        mtry = mtry,
+                        nodesize = node_size)
+
+  end_time <- Sys.time()
+
+  time_fit_rfsrc <- end_time - start_time
+
+  start_time <- Sys.time()
+
+  rsf_ranger <- ranger(
+    Surv(time, status) ~ .,
+    num.trees = n_tree,
+    splitrule = 'extratrees',
+    data = train,
+    mtry = mtry,
+    oob.error = FALSE,
+    min.node.size = node_size
+  )
+
+  end_time <- Sys.time()
+
+  time_fit_ranger <- end_time - start_time
+
+
+  start_time <- Sys.time()
+
+  cif_party <- cforest(Surv(time, status) ~ .,
+                       controls = cforest_unbiased(mtry = mtry),
+                       data = train)
+
+  end_time <- Sys.time()
+
+  time_fit_party = end_time - start_time
+
+
+  list(
+    aorsf_fast = time_fit_aorsf,
+    rsf_rfsrc = time_fit_rfsrc,
+    rsf_ranger = time_fit_ranger,
[…]

### 2022-07-27 R/clean_bm_pred.R

@@ -19,8 +19,13 @@ clean_bm_pred <- function(bm_pred_real_comb,
   }
 
   to_omit <- bm_pred_comb |>
-    filter(is.na(cstat) | is.na(ibs_scaled)) |>
-    distinct(data, run) |>
+    filter(
+      is.na(cstat) |
+        is.na(ibs_scaled) |
+        is.infinite(ibs_scaled) |
+        is.infinite(cstat)
+    ) |>
+    distinct(model, data, run) |>
     group_by(data) |>
     group_split() |>
     map(as.list)
@@ -35,10 +40,17 @@ clean_bm_pred <- function(bm_pred_real_comb,
 
   # bm_pred_comb$IPA[bm_pred_comb$model == 'xgb_aft'] <- NA_real_
 
-  bm_pred_comb |>
+  data_omit <- map_dfr(to_omit, as_tibble)
+
+  data_out <- bm_pred_comb |>
     mutate(
       across(starts_with("time_"),
              as.numeric)
     )
+
+  list(data = data_out,
+       omit = data_omit)
+
+
 
 }

### 2022-07-27 R/coxph_err.R

@@ -1,0 +1,47 @@
+
+# Taken from the clinfun package
+
+coxph_err <- function (phfit, ngamma = NULL) {
+  if (class(phfit) != "coxph")
+    stop("phfit shoud be coxph class object")
+  if (is.null(phfit$x))
+    stop("coxph should have been called with x=TRUE option")
+  ss <- phfit$n
+  covec <- phfit$x - matrix(rep(apply(phfit$x, 2, mean), ss),
+                            nrow = ss, byrow = T)
+  if (is.null(ngamma))
+    ngamma <- 1:ncol(covec)
+  covec.gamma <- covec[, ngamma, drop = FALSE]
+  covec.beta <- covec[, -ngamma, drop = FALSE]
+  xf <- exp(covec %*% phfit$coef)
+  xf.gamma <- exp(covec.gamma %*% phfit$coef[ngamma])
+  ERR <- (log(mean(xf.gamma)))/(0.577215665 + (log(mean(xf))))
+  g <- log(mean(xf))
+  h <- log(mean(xf.gamma))
+  dgb <- (t(xf) %*% covec.beta)/sum(xf)
+  dga <- (t(xf) %*% covec.gamma)/sum(xf)
+  dha <- (t(xf.gamma) %*% covec.gamma)/sum(xf.gamma)
+  dxfb <- (-h * dgb)/((0.577215665 + g)^2)
+  dxfa <- (((0.577215665 + g) * dha) - (h * dga))/((0.577215665 +
+                                                      g)^2)
+  dxf <- cbind(dxfa, dxfb)
+  newcovmat11 <- phfit$var[ngamma, ngamma, drop = FALSE]
+  newcovmat12 <- phfit$var[ngamma, -ngamma, drop = FALSE]
+  newcovmat21 <- phfit$var[-ngamma, ngamma, drop = FALSE]
+  newcovmat22 <- phfit$var[-ngamma, -ngamma, drop = FALSE]
+  newcovmat <- cbind(rbind(newcovmat11, newcovmat21), rbind(newcovmat12,
+                                                            newcovmat22))
+  vr <- var(xf.gamma)/ss
+  vs <- var(xf)/ss
+  cvrs <- cov(xf.gamma, xf)/ss
+  dr <- 1/((mean(xf.gamma)) * (0.577215665 + log(mean(xf))))
+  ds <- (-log(mean(xf.gamma)))/(mean(xf) * ((0.577215665 +
[…]

### 2022-07-27 R/data_load.R

@@ -5,6 +5,36 @@
 #' @title
 #' @param data_source
 
+nki_load <- function(...){
+
+  data_in <- OpenML::getOMLDataSet(data.id = 1228)
+
+  data_in$data %>%
+    rename(status = event)
+
+}
+
+lung_load <- function(...){
+
+  data_in <- OpenML::getOMLDataSet(data.id = 1245)
+
+  data_in$data %>%
+    rename(status = OS_event,
+           time = OS_years) %>%
+    mutate(status = as.numeric(status)-1)
+
+}
+
+lung_ncctg_load <- function(...){
+
+  data(cancer, package="survival")
+
+  out <- cancer %>%
+    mutate(sex = sex - 1,
+           status = status - 1) %>%
+    select(-inst)
+
+}
 
 vdv_load <- function(...){
 

### 2022-07-27 R/sim_surv.R

@@ -149,21 +149,36 @@ sim_surv <- function(n_obs = 500,
                 x = data_covs,
                 maxt = pred_horiz * 2)
 
-  # head(data_covs)
-
   drop <- grep(pattern = '^hidden', x = names(data_covs))
 
+  data <- as_tibble(cbind(s1, data_covs[, -drop])) |>
+    rename(time = eventtime) |>
+    select(-id)
+
+  mdl_formula <- paste(
+    paste(main_names, "*", intr_main_names, collapse = ' + '),
+    paste0("splines::bs(", nlin_names,  ") * ", intr_nlin_names, collapse = ' + '),
+    paste(cmbn_names, "*", intr_cmbn_names, collapse = ' + '),
+    sep = ' + '
+  ) %>%
+    paste("Surv(time, status) ~ ", .) %>%
+    as.formula()
+
+  variation_explained <- mdl_formula %>%
+    coxph(data = data, x = TRUE) %>%
+    coxph_err() %>%
+    getElement('ERR')
+
   list(
-    data = as_tibble(cbind(s1, data_covs[, -drop])) |>
-      rename(time = eventtime) |>
-      select(-id),
+    data = data,
     cmbn_key = attr(data_covs, 'key'),
     effects = list(pred_main = eff_size_pred_main,
                    intr_main = eff_size_intr_main,
                    pred_nlin = eff_size_pred_nlin,
                    intr_nlin = eff_size_intr_nlin,
                    pred_cmbn = eff_size_pred_cmbn,
-                   intr_cmbn = eff_size_intr_cmbn)
+                   intr_cmbn = eff_size_intr_cmbn),
+    variation_explained = variation_explained
   )
 
 

### 2022-07-27 R/summarize_data_source.R

@@ -56,6 +56,9 @@ summarize_data_source <- function(analyses_real) {
         "rotterdam_recur" = "Rotterdam tumor bank",
         "sprint_acm" = "SPRINT",
         "sprint_cvd" = "SPRINT",
+        "nki" = "NKI 70 gene signature",
+        "lung" = "Lung cancer",
+        "lung_ncctg" = "NCCTG Lung Cancer",
         "time_to_million" = "Movies released in 2015-2018",
         "vdv" = "Gene expression",
         "veteran" = "VA lung cancer trial",
@@ -93,9 +96,20 @@ summarize_data_source <- function(analyses_real) {
         "rotterdam_recur" = "survival",
         "sprint_acm" = NA_character_,
         "sprint_cvd" = NA_character_,
+        "nki" = "OpenML",
+        "lung" = "OpenML",
+        "lung_ncctg" = "survival",
         "time_to_million" = "censored",
         "vdv" = "randomForestSRC",
-        "veteran" = "randomForestSRC"
+        "veteran" = "randomForestSRC",
+        "mesa_hf" = NA_character_,
+        "mesa_chd" = NA_character_,
+        "mesa_stroke" = NA_character_,
+        "mesa_death" = NA_character_,
+        "aric_hf" = NA_character_,
+        "aric_chd" = NA_character_,
+        "aric_stroke" = NA_character_,
+        "aric_death" = NA_character_
       ),
       cite = recode(
         data,
@@ -123,9 +137,20 @@ summarize_data_source <- function(analyses_real) {
         "rotterdam_recur" = "royston2013external",
         "sprint_acm" = "sprint2015randomized",
         "sprint_cvd" = "sprint2015randomized",
-        "time_to_million" = "rpack0.0.0.9000censored",
+        "nki" = "van2002gene",
+        "lung" = "director2008gene",
+        "lung_ncctg" = "loprinzi1994prospective",
+        "time_to_million" = "censored",
         "vdv" = "van2002gene",
-        "veteran" = "kalbfleisch2011statistical"
+        "veteran" = "kalbfleisch2011statistical",
+        "mesa_hf" = "bild2002multi",
+        "mesa_chd" = "bild2002multi",
+        "mesa_stroke" = "bild2002multi",
+        "mesa_death" = "bild2002multi",
+        "aric_hf" = "aric1989atherosclerosis",
+        "aric_chd" = "aric1989atherosclerosis",
+        "aric_stroke" = "aric1989atherosclerosis",
[…]

### 2022-08-01 README.Rmd
arxiv submission, readme add

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  echo = FALSE,
  comment = "#>"
)

library(table.glue)

targets::tar_load(
  names = c(bm_pred_time_viz,
            bm_pred_model_viz,
            bm_vi_viz)
)

```

# aorsf-bench

<!-- badges: start -->
<!-- badges: end -->

The goal of aorsf-bench is to introduce and evaluate

1. a method to increase the computational efficiency of (i.e., accelerate) the oblique random survival forest (RSF)
1. a method to estimate importance of individual predictor variables with the oblique RSF.

The entire project is summarized in a paper: `paper/arxix/main.pdf`.

## tl;dr

In case you want a much quicker summary of the paper:

- We made oblique RSFs faster and also developed a new method to estimate importance of individual predictors with them. These methods are available in the `aorsf` R package.

- We find that the accelerated oblique RSF (`aorsf-fast` in the paper) is very fast. In fact, in a benchmark with 35 different risk prediction tasks, `aorsf-fast` was faster than all of the learners we analyzed, except for penalized Cox regression models (`glmnet-cox` in the paper).

```{r, fig-bm-time, fig.cap="Distribution of time taken to fit a prediction model and compute predicted risk. The median time, in seconds, is printed and annotated for each learner by a vertical line.", fig.align='center', fig.width=8, fig.height=8}
bm_pred_time_viz$fig
```

- We find that `aorsf-fast` has the best index of prediction accuracy out of all the learners we evaluated:

```{r, fig-bm-ibs, fig.cap="Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms. A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.", fig.align='center', fig.width=8, fig.height=8}
bm_pred_model_viz$fig$ibs_scaled
```

- We find that negation variable importance improves the chances of ranking a relevant variable as more important than an irrelevant variable when using an oblique RSF to estimate variable importance:

```{r, fig-bm-vi, fig.cap="Concordance statistic for assigning higher importance to relevant versus irrelevant variables. Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.", fig.align='center', fig.width=8, fig.height=10}
bm_vi_viz$fig
```

## Reproducing this paper

We use `targets` to coordinate the general benchmark experiment and simulation study that are presented in this research, and hope that our use of `targets` also makes it easier for others to engage with our code.

Our work can be reproduced, mostly. The only thing that can't be reproduced are the results based on datasets that we can't share with you. To replicate our work using publicly available data, you need to edit the vector of datasets passed into our `targets` pipeline (see `_targets.R`) so that it only contains publicly available data. Below is a code chunk showing which datasets you need to comment out:

```{r data-to-omit, echo=TRUE}

data_source = c(
  "veteran",
  "colon_recur",
  "colon_acm",
  "pbc_orsf",
  "time_to_million",
  "gbsg2",
  "peakV02",
  "flchain",
  "nafld",
  "rotterdam_recur",
  "rotterdam_acm",
  "actg_aids",
  "actg_death",
  # "guide_it_cvd",    
  # "guide_it_hfhosp", 
  "breast",
  # "sprint_cvd",
  # "sprint_acm",
  "nki",
  "lung",
  "lung_ncctg",
  "follic_death",
  "follic_relapse",
  "mgus2_death",
  "mgus2_pcm"
  # "mesa_hf",
  # "mesa_chd",
  # "mesa_stroke",
  # "mesa_death",
  # "aric_hf",
  # "aric_chd",
  # "aric_stroke",
  # "aric_death",
  # "jhs_stroke",
  # "jhs_chd"
)

```

You'll still need to create the `nafld` data by running `nafld_build()`, which is an R function included in `R/nafld_build.R` that combines multiple datasets in the `survival` package into a dataset we analyzed in the current study.

Once you've completed these steps and installed the packages listed in `packages.R`, all you need to do is run `targets::tar_make()`. However, it will take a very long time to make the pipeline as-is and I recommend setting `run_seed` to be `1:3` (see `_targets.R` to modify this value) to request only 3 replications of Monte-Carlo cross validation be completed. Also, you are free to use only a subset of the learners by commenting out the ones you don't want to run. Here is what I'd recommend if you'd like to speed up the pipeline:

```{r models-to-omit, echo=TRUE}

# slower model fitters are commented out

model_fitters <- c(
  'aorsf_fast',
  'aorsf_cph',
  # 'aorsf_random',
  # 'aorsf_net',
  # 'rotsf',
  # 'rsfse',
  # 'cif',
  'cox_net',
  # 'coxtime',
  # 'obliqueRSF',
  'xgb_cox',
  # 'xgb_aft',
  'randomForestSRC',
  'ranger'
)

```

### 2022-08-01 paper/arxiv/main.Rnw
arxiv submission, readme add

@@
 \newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
-\newcommand{\ie}{that is}
-\newcommand{\eg}{for example}
+\newcommand{\ie}{\textit{i.e.}}
+\newcommand{\eg}{\textit{e.g.}}
 \newcommand{\cstat}{\widehat{\text{C}}(t)}
@@
 
-\date{\today}	% Here you can change the date presented in the paper title
+% \date{\today}	% Here you can change the date presented in the paper title
 
@@
                    bm_pred_time_viz,
+                   clincalc_r2,
                    data_key,
@@
 We estimate the importance of individual predictors for the oblique RSF by negating each coefficient used for the given predictor in linear combinations, and then computing the reduction in out-of-bag accuracy.
-In general benchmarking experiments, we find that our implementation of the oblique RSF is over 500 times faster with equivalent discrimination and superior Brier score compared to existing software for oblique RSFs.
-We find in simulation studies that `negation importance' discriminates between signal and noise predictors more reliably than permutation importance, Shapley additive explanations, and a previously introduced technique to measure variable importance with oblique RSFs based on analysis of variance.
+In general benchmarking experiments, we find that our implementation of the oblique RSF is approximately 450 times faster with equivalent discrimination and superior Brier score compared to existing software for oblique RSFs.
+We find in simulation studies that `negation importance' discriminates between relevant and irrelevant predictors more reliably than permutation importance, Shapley additive explanations, and a previously introduced technique to measure variable importance with oblique RSFs based on analysis of variance.
 All methods pertaining to oblique RSFs in the current study are available in the \texttt{aorsf} R package.
@@
 \end{equation}
-where $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (i.e., those still at risk at time $t_i$), and $j(i)$ is the index of the observation for which an event occurred at time $t_i$.
-Newton Raphson scoring is an exceptionally fast estimation procedure, and the \texttt{survival} package includes documentation that outlines how to efficiently program it \citep{therneau_survival_2022}.
+where $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (\ie, those still at risk at time $t_i$), and $j(i)$ is the index of the observation for which an event occurred at time $t_i$.
+Newton Raphson scoring is an exceptionally fast estimation procedure, and the \texttt{survival} package \citep{survival} includes documentation that outlines how to efficiently program it \citep{therneau_survival_2022}.
 Briefly, a vector of estimated regression coefficients, $\hat{\beta}$, is updated in each step of the procedure based on its first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
@@
 We used a collection of \Sexpr{n_data_sets} data sets containing a total of \Sexpr{n_risk_tasks} risk prediction tasks (tasks per data set ranged from one to four) to benchmark the accelerated oblique RSF versus other learners.
-Participant-level data from the GUIDE-IT and SPRINT clinical trials and the ARIC and MESA community cohort studies was obtained from the National Institute of Health Biologic Specimen and Data Repository Coordinating Center (BioLINCC).
-Designs and protocols for these studies have been made available \citep{aric1989atherosclerosis, bild2002multi, felker2017effect, sprint2015randomized}.
+Participant-level data from the GUIDE-IT and SPRINT clinical trials and the ARIC, MESA, and JHS community cohort studies was obtained from the National Institute of Health Biologic Specimen and Data Repository Coordinating Center (BioLINCC).
+Designs and protocols for these studies have been made available \citep{aric1989atherosclerosis, bild2002multi, felker2017effect, sprint2015randomized, taylor2005toward}.
 All other datasets were publicly available and obtained through R packages (see Appendix A.1).
@@
 More specifically, we concluded that two learners had practically equivalent IPA or time-dependent C-statistic if there was a 95\% or higher posterior probability that the absolute difference in the relevant metric was less than 1.
-We concluded that one learner was weakly superior when there was $\geq$ 95\% posterior probability that the difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 95\% posterior probability that the difference in the relevant metric was 1 or more.
+We concluded that one learner was weakly superior when there was $\geq$ 95\% posterior probability that the absolute difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 95\% posterior probability that the absolute difference in the relevant metric was 1 or more.
 
@@
 Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.
-As predicted survival probabilities are not a standard output from \\texttt{xgboost-aft}, it is not included in this figure.">>=
+As predicted survival probabilities are not a standard output from \\texttt{xgboost-aft}, it is not included in this figure.
+Also, since this figure is intended to compare \\texttt{aorsf-fast} to learners that are not oblique random survival forests, \\texttt{aorsf-cph}, \\texttt{aorsf-net}, \\texttt{aorsf-random}, and \\texttt{obliqueRSF-net} are not included.">>=
 bm_pred_viz$ibs_scaled$fig
@@
 <<bm_pred_viz_cstat, fig.height=10, fig.width=9, fig.cap="Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
-Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.">>=
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.
+Since this figure is intended to compare \\texttt{aorsf-fast} to learners that are not oblique random survival forests, \\texttt{aorsf-cph}, \\texttt{aorsf-net}, \\texttt{aorsf-random}, and \\texttt{obliqueRSF-net} are not included.">>=
 bm_pred_viz$cstat$fig
@@
 
-The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between variables that do or do not have a relationship with a simulated outcome.
+The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between relevant and irrelevant variables, where relevance is defined by having a relationship with the simulated outcome.
 We consider methods that are intrinsic to the oblique RF (\eg, ANOVA VI), those that are intrinsic to the RF (\eg, permutation VI), and those that are model-agnostic (\eg, SHAP VI).
@@
 For ANOVA VI, we applied a p-value threshold of 0.01, following the threshold recommended by \citet{menze2011oblique}.
-We compute SHAP VI for boosted tree models using the \texttt{xgboost} package, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
+We compute SHAP VI for boosted tree models using the \texttt{xgboost} package \citep{xgboost}, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
 
@@
 
+s <- mean_ci(clincalc_r2)*100
+
+clincalc_r2_sexpr <- table_glue(
+  "{s[['y']]} ({s[['ymin']]}, {s[['ymax']]})"
+)
+
 @
@@
 Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
-Using this design for simulated data, the proportion of relative risk explained by our covariates ranged from FILL IN to FILL IN, according to Heller's explained relative risk measure \citep{heller2012measure}.
+Using this design for simulated data, the Heller explained relative risk (95\% confidence interval) of our covariates was \Sexpr{clincalc_r2_sexpr} \citep{heller2012measure} with 2,500 observations.
 
@@
 Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
-In numeric experiments, we found that that \texttt{aorsf-fast} is over 500 times faster and just as accurate in risk prediction tasks compared to its predecessor, \texttt{obliqueRSF-net}.
+In numeric experiments, we found that that \texttt{aorsf-fast} is approximately \Sexpr{times$obliqueRSF_net$ratio} times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
 We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
@@
 Accurate risk prediction models have the potential to improve healthcare by directing timely interventions to patients who are most likely to benefit.
-However, prediction models that cannot scale adequately to large databases or cannot be interpreted and explained have no place in clinical practice.
+However, prediction models that cannot scale adequately to large databases or cannot be interpreted and explained will struggle to gain acceptance in clinical practice \citep{moss2022demystifying}.
 The current study advances the oblique RSF, an accurate risk prediction model, towards being accurate, scalable, and interpretable.
@@
 Thus, allowing the oblique RSF to account for competing risks is a high priority for future studies.
-In addition, missing data are not addressed in the accelerated oblique RSF, and users of the \texttt{aorsf} R package are expected to impute missing values prior to model training and testing.
-However, missing data are common and there are numerous techniques for ensemble tree methods to handle missing data during the tree growing procedure.
-Thus, a second item of high priority for future studies is to develop and evaluate strategies to handle missing data while growing an oblique RSF.
-Last, \citet{cui2017consistency} found that estimating an inverse-probability weighted hazard function at each non-leaf node of a survival tree allows the RSF to converge asymptotically to the true survival function when some variables contribute both to the risk of the event and the risk of censoring, a scenario that is very likely in the analysis of electronic medical records.
-The accelerated oblique RSF could incorporate this splitting technique by using Newton Raphson scoring to fit a model for the censoring distribution and then a weighted model could be fit to the failure distribution.
-This final item has the highest priority, as \citet{cui2017consistency} showed it is a requisite condition for consistency of axis based survival trees in fairly general settings.
+In addition, the current study only considered data without missing values, only evaluated oblique RSFs that applied the log-rank statistic for node splitting, and only considered negation VI estimates based on Harrell's C-statistic.
+Few studies have developed strategies to deal with missing data while growing oblique survival trees.
+Prior studies have found that log-rank tests can be mis-informative when survival curves cross \citep{li2015statistical}, and that Harrell's C-statistic is dependent on the censoring distribution of the outcome \citep{uno2011c}.
+Thus, a second item is to expand the range of options available to users of the \texttt{aorsf} package, enabling them to apply strategies for imputation of missing values and use a broad range of statistical criteria while growing oblique survival trees.
+Last, \citet{cui2017consistency} found that estimating an inverse-probability weighted hazard function at each non-leaf node of a survival tree allows the RSF to converge asymptotically to the true survival function when some variables contribute both to the risk of the event and the risk of censoring, a scenario that is very likely in the analysis of medical data.
+The accelerated oblique RSF could incorporate this splitting technique by using Newton Raphson scoring to fit a model for the censoring distribution after which a weighted model could be fit to the failure distribution.
+This final item has the highest priority, as \citet{cui2017consistency} showed it is a requisite condition for consistency of axis-based survival trees in fairly general settings.
 
 % Acknowledgements should go at the end, before appendices and references
+
+Oblique RSFs have exceptional prediction accuracy and this study has shown how they can be fit with computational efficiency that rivals their axis-based counterparts.
+We have also introduced a general and flexible method to estimate VI with oblique RFs, and demonstrated its effectiveness specifically for the oblique RSF.
+Code used for the current study is available at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}, and the \texttt{aorsf} package is available at \href{https://github.com/bcjaeger/aorsf}{https://github.com/bcjaeger/aorsf}.
 
@@
   ) %>%
-  glue_data(" \\item[] The ``{label}'' data \\citep{{{cite}}} were obtained from {source}") %>%
+  glue_data(" \\item The ``{label}'' data \\citep{{{cite}}} were obtained from {source}") %>%
   unique() %>%
@@
         align = 'lcccc',
-        caption = "Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.\\label{tab:bm_pred_all}") %>%
+        caption = paste("Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across", n_risk_tasks,  "risk prediction tasks.\\label{tab:bm_pred_all}")) %>%
   pack_rows(index = indents,

### 2022-08-01 paper/arxiv/main.tex
arxiv submission, readme add

@@
 
-We used a collection of 20 data sets containing a total of 33 risk prediction tasks (tasks per data set ranged from one to four) to benchmark the accelerated oblique RSF versus other learners.
-Participant-level data from the GUIDE-IT and SPRINT clinical trials and the ARIC and MESA community cohort studies was obtained from the National Institute of Health Biologic Specimen and Data Repository Coordinating Center (BioLINCC).
-Designs and protocols for these studies have been made available \citep{aric1989atherosclerosis, bild2002multi, felker2017effect, sprint2015randomized}.
+We used a collection of 21 data sets containing a total of 35 risk prediction tasks (tasks per data set ranged from one to four) to benchmark the accelerated oblique RSF versus other learners.
+Participant-level data from the GUIDE-IT and SPRINT clinical trials and the ARIC, MESA, and JHS community cohort studies was obtained from the National Institute of Health Biologic Specimen and Data Repository Coordinating Center (BioLINCC).
+Designs and protocols for these studies have been made available \citep{aric1989atherosclerosis, bild2002multi, felker2017effect, sprint2015randomized, taylor2005toward}.
 All other datasets were publicly available and obtained through R packages (see Appendix A.1).
-Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 1,384), the number of predictors ranged from 7 to 1,692 (median: 24), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 72.5) (\tabrefAppendix{tab:datasets}).
+Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 1,384), the number of predictors ranged from 7 to 1,692 (median: 41), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 78.1) (\tabrefAppendix{tab:datasets}).
 
@@
 
-After collecting data from 25 replications of Monte-Carlo cross validation for the 14 learners in all 33 risk prediction tasks, we analyzed the resulting 11,550 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
+After collecting data from 25 replications of Monte-Carlo cross validation for the 14 learners in all 35 risk prediction tasks, we analyzed the resulting 12,250 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
 Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using Bayesian models.
@@
 A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all}.
-In total, 821 out of 825 Monte-Carlo cross validation runs were completed.
+In total, 871 out of 875 Monte-Carlo cross validation runs were completed.
 On run 13, 18, 24 and 25 for the ACTG 320 data, the \texttt{nn-cox} learner encountered an error during its fitting procedure.
@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 18 out of 33 risk prediction tasks, with an overall mean IPA of 13.2 (Figure \ref{fig:bm_pred_viz_ibs}).
-Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.41 points higher, a relative increase of 12.0\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.87 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 20 out of 35 risk prediction tasks, with an overall mean IPA of 12.7 (Figure \ref{fig:bm_pred_viz_ibs}).
+Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.36 points higher, a relative increase of 12.0\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.79 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/bm_pred_viz_ibs-1} \caption[Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks]{Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
+\includegraphics[width=\maxwidth]{figure/bm_pred_viz_ibs-1} \caption{Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
 Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.
-As predicted survival probabilities are not a standard output from \texttt{xgboost-aft}, it is not included in this figure.}\label{fig:bm_pred_viz_ibs}
+As predicted survival probabilities are not a standard output from \texttt{xgboost-aft}, it is not included in this figure.
+Also, since this figure is intended to compare \texttt{aorsf-fast} to learners that are not oblique random survival forests, \texttt{aorsf-cph}, \texttt{aorsf-net}, \texttt{aorsf-random}, and \texttt{obliqueRSF-net} are not included.}\label{fig:bm_pred_viz_ibs}
 \end{figure}
@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 8 out of 33 risk prediction tasks, with an overall mean of 77.1 (Figure \ref{fig:bm_pred_viz_cstat}).
-Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.762 points higher, a relative increase of 0.998\%.
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 9 out of 35 risk prediction tasks, with an overall mean of 77.2 (Figure \ref{fig:bm_pred_viz_cstat}).
+Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.721 points higher, a relative increase of 0.943\%.
 The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.24 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
@@
 \includegraphics[width=\maxwidth]{figure/bm_pred_viz_cstat-1} \caption[Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks]{Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
-Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.}\label{fig:bm_pred_viz_cstat}
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.
+Since this figure is intended to compare \texttt{aorsf-fast} to learners that are not oblique random survival forests, \texttt{aorsf-cph}, \texttt{aorsf-net}, \texttt{aorsf-random}, and \texttt{obliqueRSF-net} are not included.}\label{fig:bm_pred_viz_cstat}
 \end{figure}
@@
 
-Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 158 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
-Comparing median computing times, \texttt{aorsf-fast} was 700.1 times faster than its predecessor, \texttt{obliqueRSF-net}.
-In addition, \texttt{aorsf-fast} was 13.6, 1.92, and 4.20 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
+Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 256 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+Comparing median computing times, \texttt{aorsf-fast} was 446.1 times faster than its predecessor, \texttt{obliqueRSF-net}.
+In addition, \texttt{aorsf-fast} was 18.9, 1.83, and 3.12 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
 
@@
 Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
-Using this design for simulated data, the proportion of relative risk explained by our covariates ranged from FILL IN to FILL IN, according to Heller's explained relative risk measure \citep{heller2012measure}.
+Using this design for simulated data, the Heller explained relative risk (95\% confidence interval) of our covariates was 88.4 (88.1, 88.7) \citep{heller2012measure} with 2,500 observations.
 
@@
 
-The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = 76.0$), second (\texttt{aorsf-anova}; $C = 74.0$), and third (\texttt{aorsf-permute}; $C = 73.2$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in 26 out of 36 VI tasks (Figure \ref{fig:bm_vi_viz}).
+The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = 75.9$), second (\texttt{aorsf-anova}; $C = 73.9$), and third (\texttt{aorsf-permute}; $C = 73.2$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in 26 out of 36 VI tasks (Figure \ref{fig:bm_vi_viz}).
 Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
 Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
-Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of 1.27 seconds versus 11.9 and 13.0 seconds, respectively.
+Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of 2.88 seconds versus 20.4 and 21.8 seconds, respectively.
 
@@
 Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
-In numeric experiments, we found that that \texttt{aorsf-fast} is over 500 times faster and just as accurate in risk prediction tasks compared to its predecessor, \texttt{obliqueRSF-net}.
+In numeric experiments, we found that that \texttt{aorsf-fast} is approximately 446.1 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
 We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
-Overall, we found that estimating VI using negation instead of ANOVA increased the C-statistic for ranking a relevant variable higher than an irrelevant variable by 1.97, a relative increase of 2.66\%.
+Overall, we found that estimating VI using negation instead of ANOVA increased the C-statistic for ranking a relevant variable higher than an irrelevant variable by 2.05, a relative increase of 2.78\%.
 
@@
 
- \item[] The ``VA lung cancer trial'' data \citep{kalbfleisch2011statistical} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
- \item[] The ``Colon cancer'' data \citep{moertel1995fluorouracil} were obtained from the \texttt{survival} R package \citep{survival}. 
- \item[] The ``Primary biliary cholangitis'' data \citep{therneau2000cox} were obtained from the \texttt{aorsf} R package \citep{aorsf}. 
- \item[] The ``Movies released in 2015-2018'' data  were obtained from the \texttt{censored} R package \citep{censored}. 
- \item[] The ``GBSG II'' data \citep{schumacher1994rauschecker} were obtained from the \texttt{TH.data} R package \citep{TH.data}. 
- \item[] The ``Systolic Heart Failure'' data \citep{hsich2011identifying} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
- \item[] The ``Serum free light chain'' data \citep{dispenzieri2012use, kyle2006prevalence} were obtained from the \texttt{survival} R package \citep{survival}. 
- \item[] The ``Non-alcohol fatty liver disease'' data \citep{allen2018nonalcoholic} were obtained from the \texttt{survival} R package \citep{survival}. 
- \item[] The ``Rotterdam tumor bank'' data \citep{royston2013external} were obtained from the \texttt{survival} R package \citep{survival}. 
- \item[] The ``ACTG 320'' data \citep{hosmer2002applied} were obtained from the \texttt{mlr3proba} R package \citep{mlr3proba}. 
- \item[] The ``GUIDE-IT'' data \citep{felker2017effect} were obtained from BioLINCC. 
- \item[] The ``Early breast cancer'' data \citep{desmedt2011multifactorial, hatzis2011genomic, ternes2017identification} were obtained from the \texttt{biospear} R package \citep{biospear}. 
- \item[] The ``SPRINT'' data \citep{sprint2015randomized} were obtained from BioLINCC. 
- \item[] The ``NKI 70 gene signature'' data \citep{van2002gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}. 
- \item[] The ``Lung cancer'' data \citep{director2008gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}. 
- \item[] The ``NCCTG Lung Cancer'' data \citep{loprinzi1994prospective} were obtained from the \texttt{survival} R package \citep{survival}. 
- \item[] The ``FCL'' data \citep{pintilie2006competing} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
- \item[] The ``Monoclonal gammopathy'' data \citep{kyle2002long} were obtained from the \texttt{survival} R package \citep{survival}. 
- \item[] The ``MESA'' data \citep{bild2002multi} were obtained from BioLINCC. 
- \item[] The ``ARIC'' data \citep{aric1989atherosclerosis} were obtained from BioLINCC.
+ \item The ``VA lung cancer trial'' data \citep{kalbfleisch2011statistical} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
+ \item The ``Colon cancer'' data \citep{moertel1995fluorouracil} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``Primary biliary cholangitis'' data \citep{therneau2000cox} were obtained from the \texttt{aorsf} R package \citep{aorsf}. 
+ \item The ``Movies released in 2015-2018'' data  were obtained from the \texttt{censored} R package \citep{censored}. 
+ \item The ``GBSG II'' data \citep{schumacher1994rauschecker} were obtained from the \texttt{TH.data} R package \citep{TH.data}. 
+ \item The ``Systolic Heart Failure'' data \citep{hsich2011identifying} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
+ \item The ``Serum free light chain'' data \citep{dispenzieri2012use, kyle2006prevalence} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``Non-alcohol fatty liver disease'' data \citep{allen2018nonalcoholic} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``Rotterdam tumor bank'' data \citep{royston2013external} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``ACTG 320'' data \citep{hosmer2002applied} were obtained from the \texttt{mlr3proba} R package \citep{mlr3proba}. 
+ \item The ``GUIDE-IT'' data \citep{felker2017effect} were obtained from BioLINCC. 
+ \item The ``Early breast cancer'' data \citep{desmedt2011multifactorial, hatzis2011genomic, ternes2017identification} were obtained from the \texttt{biospear} R package \citep{biospear}. 
+ \item The ``SPRINT'' data \citep{sprint2015randomized} were obtained from BioLINCC. 
+ \item The ``NKI 70 gene signature'' data \citep{van2002gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}. 
+ \item The ``Lung cancer'' data \citep{director2008gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}. 
+ \item The ``NCCTG Lung Cancer'' data \citep{loprinzi1994prospective} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``FCL'' data \citep{pintilie2006competing} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
+ \item The ``Monoclonal gammopathy'' data \citep{kyle2002long} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``MESA'' data \citep{bild2002multi} were obtained from BioLINCC. 
+ \item The ``ARIC'' data \citep{aric1989atherosclerosis} were obtained from BioLINCC. 
+ \item The ``JHS'' data \citep{taylor2005toward} were obtained from BioLINCC.
 
@@
 \multirow{-4}{*}{\raggedright\arraybackslash ARIC} & \multirow{-4}{*}{\centering\arraybackslash 13,623} & \multirow{-4}{*}{\centering\arraybackslash 41} & Death & 6,662 & 51.1\\
+\cmidrule{1-6}\pagebreak[0]
+ &  &  & Stroke & 152 & 95.8\\
+\cmidrule{4-6}\nopagebreak
+\multirow{-2}{*}{\raggedright\arraybackslash JHS} & \multirow{-2}{*}{\centering\arraybackslash 3,501} & \multirow{-2}{*}{\centering\arraybackslash 80} & Coronary Heart Disease & 190 & 94.6\\
 \bottomrule
@@
 \begin{longtable}[t]{lcccc}
-\caption{\label{tab:unnamed-chunk-11}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.\label{tab:bm_pred_all}}\\
+\caption{\label{tab:unnamed-chunk-11}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 35 risk prediction tasks.\label{tab:bm_pred_all}}\\
 \toprule
@@
 \endfirsthead
-\caption[]{Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.\label{tab:bm_pred_all} \textit{(continued)}}\\
+\caption[]{Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 35 risk prediction tasks.\label{tab:bm_pred_all} \textit{(continued)}}\\
 \toprule
@@
 \hline
-\hspace{1em}aorsf-fast & 0.132 (0.110) & 0.771 (0.073) & 0.458 & 0.107\\
-\hspace{1em}aorsf-cph & 0.131 (0.110) & 0.770 (0.072) & 1.145 & 0.087\\
-\hspace{1em}aorsf-net & 0.129 (0.113) & 0.769 (0.073) & 85.734 & 0.087\\
-\hspace{1em}obliqueRSF-net & 0.118 (0.085) & 0.769 (0.073) & 356.969 & 17.203\\
-\hspace{1em}cif-standard & 0.118 (0.098) & 0.763 (0.072) & 2.035 & 5.650\\
-\hspace{1em}rsf-standard & 0.118 (0.115) & 0.755 (0.077) & 2.157 & 0.194\\
-\hspace{1em}cif-rotate & 0.117 (0.126) & 0.754 (0.083) & 35.290 & 6.347\\
-\hspace{1em}glmnet-cox & 0.113 (0.121) & 0.755 (0.079) & 0.405 & 0.003\\
-\hspace{1em}ranger-extratrees & 0.103 (0.086) & 0.760 (0.069) & 0.716 & 0.848\\
-\hspace{1em}cif-extension & 0.099 (0.094) & 0.760 (0.074) & 15.496 & 6.211\\
-\hspace{1em}aorsf-random & 0.094 (0.081) & 0.740 (0.065) & 1.339 & 0.086\\
-\hspace{1em}xgboost-cox & 0.068 (0.102) & 0.747 (0.096) & 4.073 & 0.004\\
-\hspace{1em}nn-cox & 0.048 (0.111) & 0.649 (0.139) & 16.050 & 1.501\\
-\hspace{1em}xgboost-aft & --- & 0.761 (0.078) & 13.035 & 0.007\\
+\hspace{1em}aorsf-fast & 0.127 (0.109) & 0.772 (0.071) & 0.593 & 0.146\\
+\hspace{1em}aorsf-cph & 0.126 (0.109) & 0.771 (0.070) & 1.344 & 0.148\\
+\hspace{1em}aorsf-net & 0.124 (0.112) & 0.771 (0.071) & 79.741 & 0.158\\
+\hspace{1em}obliqueRSF-net & 0.113 (0.085) & 0.771 (0.071) & 300.393 & 18.803\\
+\hspace{1em}cif-standard & 0.113 (0.098) & 0.765 (0.071) & 4.293 & 6.044\\
+\hspace{1em}rsf-standard & 0.113 (0.114) & 0.755 (0.075) & 2.099 & 0.199\\
+\hspace{1em}cif-rotate & 0.112 (0.124) & 0.755 (0.081) & 37.695 & 8.348\\
+\hspace{1em}glmnet-cox & 0.108 (0.119) & 0.757 (0.077) & 0.473 & 0.003\\
+\hspace{1em}ranger-extratrees & 0.099 (0.085) & 0.762 (0.067) & 0.878 & 1.156\\
+\hspace{1em}cif-extension & 0.095 (0.092) & 0.761 (0.072) & 22.321 & 6.949\\
+\hspace{1em}aorsf-random & 0.090 (0.081) & 0.742 (0.063) & 1.855 & 0.152\\
+\hspace{1em}xgboost-cox & 0.064 (0.100) & 0.749 (0.094) & 3.973 & 0.004\\
+\hspace{1em}nn-cox & 0.047 (0.108) & 0.656 (0.138) & 15.352 & 2.060\\
+\hspace{1em}xgboost-aft & --- & 0.762 (0.076) & 13.060 & 0.007\\
 \addlinespace[0.3em]
@@
 \hspace{1em}xgboost-aft & --- & 0.697 (0.025) & 11.409 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{JHS; coronary heart disease, n = 3501, p = 80}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.040 (0.008) & 0.778 (0.015) & 6.783 & 0.588\\
+\hspace{1em}obliqueRSF-net & 0.039 (0.007) & 0.780 (0.015) & 185.659 & 130.539\\
+\hspace{1em}aorsf-fast & 0.039 (0.007) & 0.777 (0.015) & 2.260 & 0.566\\
+\hspace{1em}aorsf-net & 0.039 (0.009) & 0.777 (0.016) & 78.653 & 0.606\\
+\hspace{1em}cif-standard & 0.038 (0.006) & 0.779 (0.017) & 10.065 & 30.887\\
+\hspace{1em}cif-extension & 0.036 (0.004) & 0.781 (0.019) & 54.976 & 20.544\\
+\hspace{1em}ranger-extratrees & 0.035 (0.005) & 0.777 (0.017) & 3.892 & 1.677\\
+\hspace{1em}cif-rotate & 0.034 (0.010) & 0.769 (0.018) & 187.949 & 22.910\\
+\hspace{1em}glmnet-cox & 0.031 (0.010) & 0.774 (0.020) & 1.723 & 0.004\\
+\hspace{1em}rsf-standard & 0.031 (0.011) & 0.752 (0.016) & 2.099 & 0.226\\
+\hspace{1em}nn-cox & 0.030 (0.012) & 0.759 (0.021) & 10.787 & 5.787\\
+\hspace{1em}aorsf-random & 0.027 (0.004) & 0.763 (0.019) & 3.232 & 0.624\\
+\hspace{1em}xgboost-cox & 0.010 (0.023) & 0.785 (0.022) & 3.676 & 0.005\\
+\hspace{1em}xgboost-aft & --- & 0.782 (0.017) & 13.342 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{JHS; stroke, n = 3639, p = 80}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.036 (0.006) & 0.806 (0.016) & 6.729 & 0.588\\
+\hspace{1em}aorsf-net & 0.035 (0.008) & 0.807 (0.016) & 72.257 & 0.610\\
+\hspace{1em}aorsf-fast & 0.035 (0.007) & 0.807 (0.018) & 2.321 & 0.571\\
+\hspace{1em}obliqueRSF-net & 0.030 (0.006) & 0.807 (0.016) & 161.865 & 165.270\\
+\hspace{1em}glmnet-cox & 0.028 (0.008) & 0.798 (0.017) & 2.325 & 0.004\\
+\hspace{1em}cif-standard & 0.028 (0.005) & 0.803 (0.016) & 10.613 & 32.291\\
+\hspace{1em}rsf-standard & 0.027 (0.010) & 0.782 (0.018) & 1.210 & 0.190\\
+\hspace{1em}cif-extension & 0.025 (0.003) & 0.797 (0.018) & 55.652 & 21.758\\
+\hspace{1em}ranger-extratrees & 0.023 (0.005) & 0.791 (0.016) & 2.997 & 2.557\\
+\hspace{1em}cif-rotate & 0.023 (0.009) & 0.785 (0.017) & 188.792 & 24.524\\
+\hspace{1em}aorsf-random & 0.022 (0.004) & 0.775 (0.018) & 3.166 & 0.630\\
+\hspace{1em}nn-cox & 0.016 (0.027) & 0.772 (0.021) & 10.445 & 6.338\\
+\hspace{1em}xgboost-cox & 0.001 (0.030) & 0.776 (0.021) & 2.953 & 0.005\\
+\hspace{1em}xgboost-aft & --- & 0.784 (0.018) & 13.017 & 0.006\\
 \addlinespace[0.3em]
@@
 \endlastfoot
-Overall & Overall & 76.0 & 74.0 & 73.2 & 69.7 & 64.7 & 67.8\\
+Overall & Overall & 75.9 & 73.9 & 73.2 & 69.6 & 64.6 & 67.7\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 57.9 & 57.8 & 58.1 & 54.7 & 49.4 & 57.1\\
-\hspace{1em}30 & 500 & 54.3 & 54.5 & 54.7 & 48.2 & 42.6 & 54.8\\
-\hspace{1em}30 & 1,000 & 57.0 & 56.6 & 57.9 & 53.5 & 48.7 & 56.5\\
-\hspace{1em}30 & 2,500 & 61.9 & 59.2 & 64.2 & 61.9 & 61.2 & 60.3\\
-\hspace{1em}15 & 500 & 53.4 & 53.6 & 53.1 & 47.0 & 40.9 & 54.5\\
-\hspace{1em}15 & 1,000 & 56.5 & 55.7 & 57.1 & 52.2 & 45.9 & 55.5\\
-\hspace{1em}15 & 2,500 & 61.3 & 59.0 & 62.6 & 61.1 & 59.0 & 60.8\\
-\hspace{1em}0 & 500 & 52.6 & 54.8 & 53.2 & 44.6 & 40.8 & 53.6\\
-\hspace{1em}0 & 1,000 & 56.9 & 58.7 & 55.5 & 53.0 & 43.1 & 55.6\\
-\hspace{1em}0 & 2,500 & 67.6 & 68.1 & 64.6 & 71.1 & 62.3 & 62.4\\
+\hspace{1em}Overall & Overall & 57.8 & 57.4 & 58.0 & 54.6 & 49.2 & 56.9\\
+\hspace{1em}30 & 500 & 54.3 & 54.1 & 54.8 & 48.2 & 42.7 & 54.9\\
+\hspace{1em}30 & 1,000 & 56.9 & 55.7 & 58.1 & 53.1 & 48.0 & 56.3\\
+\hspace{1em}30 & 2,500 & 61.9 & 58.9 & 64.1 & 61.5 & 60.7 & 60.0\\
+\hspace{1em}15 & 500 & 53.1 & 53.5 & 52.8 & 47.1 & 41.1 & 54.1\\
+\hspace{1em}15 & 1,000 & 55.9 & 55.4 & 56.3 & 52.2 & 45.8 & 55.4\\
+\hspace{1em}15 & 2,500 & 61.0 & 58.6 & 63.0 & 61.0 & 58.9 & 59.9\\
+\hspace{1em}0 & 500 & 52.5 & 53.9 & 52.4 & 44.5 & 40.7 & 53.6\\
+\hspace{1em}0 & 1,000 & 57.2 & 58.6 & 55.8 & 53.1 & 42.8 & 56.1\\
+\hspace{1em}0 & 2,500 & 67.6 & 68.2 & 64.4 & 71.0 & 62.2 & 62.1\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 71.8 & 69.4 & 67.9 & 65.9 & 60.1 & 61.7\\
-\hspace{1em}30 & 500 & 58.6 & 58.6 & 57.4 & 53.1 & 48.6 & 55.4\\
-\hspace{1em}30 & 1,000 & 61.2 & 59.6 & 58.6 & 57.4 & 52.0 & 55.9\\
-\hspace{1em}30 & 2,500 & 62.1 & 60.1 & 61.0 & 60.1 & 56.4 & 58.1\\
-\hspace{1em}15 & 500 & 63.6 & 61.5 & 60.8 & 54.6 & 49.0 & 57.7\\
-\hspace{1em}15 & 1,000 & 67.6 & 64.9 & 64.8 & 62.4 & 55.8 & 59.1\\
-\hspace{1em}15 & 2,500 & 70.7 & 67.3 & 68.8 & 66.7 & 62.1 & 62.6\\
-\hspace{1em}0 & 500 & 75.6 & 72.5 & 69.3 & 60.0 & 56.2 & 61.2\\
-\hspace{1em}0 & 1,000 & 88.4 & 84.0 & 78.3 & 81.7 & 69.1 & 67.2\\
-\hspace{1em}0 & 2,500 & 98.3 & 96.2 & 91.9 & 97.5 & 91.4 & 78.5\\
+\hspace{1em}Overall & Overall & 71.7 & 69.3 & 67.9 & 66.1 & 60.1 & 61.8\\
+\hspace{1em}30 & 500 & 58.8 & 58.3 & 57.8 & 53.4 & 48.5 & 55.5\\
+\hspace{1em}30 & 1,000 & 61.1 & 59.4 & 59.0 & 57.1 & 52.0 & 56.3\\
+\hspace{1em}30 & 2,500 & 62.1 & 60.2 & 61.1 & 60.0 & 56.4 & 57.9\\
+\hspace{1em}15 & 500 & 63.8 & 61.5 & 60.7 & 55.3 & 49.4 & 57.7\\
+\hspace{1em}15 & 1,000 & 67.5 & 65.1 & 64.6 & 62.5 & 56.0 & 59.8\\
+\hspace{1em}15 & 2,500 & 70.2 & 67.2 & 69.1 & 66.8 & 62.3 & 62.3\\
+\hspace{1em}0 & 500 & 75.5 & 72.3 & 68.5 & 60.1 & 55.8 & 61.1\\
+\hspace{1em}0 & 1,000 & 88.3 & 83.9 & 78.0 & 81.5 & 68.6 & 67.6\\
+\hspace{1em}0 & 2,500 & 98.4 & 96.3 & 91.8 & 97.7 & 91.6 & 78.3\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 78.4 & 76.0 & 74.9 & 70.8 & 65.3 & 68.3\\
-\hspace{1em}30 & 500 & 64.8 & 63.8 & 62.7 & 55.6 & 49.8 & 59.3\\
-\hspace{1em}30 & 1,000 & 67.5 & 65.7 & 65.0 & 61.4 & 55.7 & 61.5\\
-\hspace{1em}30 & 2,500 & 69.8 & 67.0 & 68.5 & 65.7 & 62.4 & 64.3\\
-\hspace{1em}15 & 500 & 70.4 & 68.0 & 66.6 & 59.2 & 53.0 & 62.3\\
-\hspace{1em}15 & 1,000 & 75.0 & 71.2 & 71.7 & 66.6 & 59.7 & 64.9\\
-\hspace{1em}15 & 2,500 & 78.9 & 74.8 & 77.1 & 72.9 & 69.0 & 69.9\\
-\hspace{1em}0 & 500 & 84.0 & 81.4 & 76.5 & 66.5 & 61.7 & 67.4\\
-\hspace{1em}0 & 1,000 & 95.4 & 92.4 & 87.8 & 89.4 & 78.6 & 76.3\\
-\hspace{1em}0 & 2,500 & 99.8 & 99.3 & 97.9 & 99.6 & 97.8 & 89.1\\
+\hspace{1em}Overall & Overall & 78.3 & 75.8 & 74.8 & 70.7 & 65.2 & 68.2\\
+\hspace{1em}30 & 500 & 64.8 & 63.5 & 62.5 & 55.6 & 49.8 & 59.2\\
+\hspace{1em}30 & 1,000 & 67.4 & 65.3 & 65.3 & 61.0 & 55.3 & 61.5\\
+\hspace{1em}30 & 2,500 & 69.9 & 67.0 & 68.5 & 65.2 & 61.9 & 63.8\\
+\hspace{1em}15 & 500 & 70.2 & 68.0 & 66.3 & 59.2 & 52.8 & 61.8\\
+\hspace{1em}15 & 1,000 & 74.8 & 71.2 & 71.4 & 66.6 & 59.9 & 65.0\\
+\hspace{1em}15 & 2,500 & 78.6 & 74.6 & 77.1 & 72.6 & 68.6 & 69.1\\
+\hspace{1em}0 & 500 & 84.0 & 81.1 & 76.2 & 66.7 & 61.7 & 67.6\\
+\hspace{1em}0 & 1,000 & 95.4 & 92.4 & 87.8 & 89.4 & 78.7 & 76.3\\
+\hspace{1em}0 & 2,500 & 99.8 & 99.3 & 97.8 & 99.7 & 97.9 & 89.0\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 91.1 & 89.0 & 88.8 & 85.1 & 82.7 & 83.2\\
-\hspace{1em}30 & 500 & 79.3 & 77.5 & 75.3 & 70.2 & 66.5 & 71.2\\
-\hspace{1em}30 & 1,000 & 83.7 & 80.8 & 80.6 & 77.1 & 74.0 & 74.8\\
-\hspace{1em}30 & 2,500 & 86.7 & 83.7 & 85.2 & 81.8 & 80.5 & 79.3\\
-\hspace{1em}15 & 500 & 86.4 & 83.3 & 81.9 & 75.6 & 71.3 & 75.4\\
-\hspace{1em}15 & 1,000 & 91.3 & 88.2 & 88.7 & 84.9 & 81.6 & 81.0\\
-\hspace{1em}15 & 2,500 & 94.6 & 91.8 & 93.8 & 90.3 & 89.0 & 86.8\\
-\hspace{1em}0 & 500 & 97.7 & 96.2 & 94.1 & 86.2 & 83.6 & 85.7\\
-\hspace{1em}0 & 1,000 & 100.0 & 99.7 & 99.4 & 99.4 & 98.0 & 95.1\\
+\hspace{1em}Overall & Overall & 91.0 & 88.9 & 88.7 & 85.0 & 82.6 & 83.2\\
+\hspace{1em}30 & 500 & 79.3 & 77.3 & 75.5 & 70.3 & 66.5 & 71.2\\
+\hspace{1em}30 & 1,000 & 83.5 & 80.5 & 80.8 & 76.8 & 73.9 & 74.9\\
+\hspace{1em}30 & 2,500 & 86.5 & 83.5 & 85.1 & 81.7 & 80.4 & 79.3\\
+\hspace{1em}15 & 500 & 86.3 & 83.3 & 81.8 & 75.7 & 71.3 & 75.3\\
+\hspace{1em}15 & 1,000 & 91.3 & 88.1 & 88.5 & 84.6 & 81.3 & 81.1\\
+\hspace{1em}15 & 2,500 & 94.5 & 91.6 & 93.7 & 90.2 & 89.0 & 86.5\\
+\hspace{1em}0 & 500 & 97.8 & 96.3 & 94.0 & 86.5 & 83.4 & 85.9\\
+\hspace{1em}0 & 1,000 & 100.0 & 99.7 & 99.4 & 99.4 & 98.0 & 95.2\\
 \hspace{1em}0 & 2,500 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 99.8\\*

### 2022-08-01 R/bench_pred_model_visualize.R

@@ -176,3 +176,96 @@ bench_pred_model_visualize_worker <- function(.gg_data,
 
 }
 
+
+bench_pred_model_visualize_smol <- function(.gg_data,
+                                            equiv_bound){
+
+  xmax <- max(.gg_data$x)
+
+  y_col_0 = -equiv_bound * 10
+  y_col_1 = equiv_bound * 4
+
+  y_breaks <- seq(-5, 1) * 1/100
+
+  gg_header <- tibble(
+    x = c(xmax + 1,
+          xmax + 1),
+    median = c(y_col_0,
+               (min(y_breaks) + max(y_breaks)) / 2),
+    label = c("Learner",
+              as.character(.gg_data$metric[1])),
+    hjust = c(0, 1/2)
+  )
+
+  gg_rect <- tibble(
+    xmin = seq(xmax+1) - 1/2,
+    xmax = seq(xmax+1) + 1/2,
+    ymin = -Inf,
+    ymax = Inf
+  ) |>
+    filter(seq(n()) %% 2 == 0)
+
+  ggplot(.gg_data) +
+    aes(x = x, y = median, label = model) +
+    geom_segment(x = 0, y = -.01, xend = xmax+1/2, yend = -.01,
+                 color = 'purple', linetype = 2) +
+    geom_segment(x = 0, y = .01, xend = xmax+1/2, yend = .01,
+                 color = 'purple', linetype = 2) +
+    geom_segment(x = 0, y = 0, xend = xmax+1/2, yend = 0,
+                 color = 'darkorange', linetype = 2) +
+    geom_vline(xintercept = c(xmax + 1/2, xmax + 3/2)) +
+    geom_segment(
+      mapping = aes(x = x,
+                    y = ci_lwr,
+                    xend = x,
+                    yend = ci_upr),
+      size = 0.75,
+      color = 'grey80'
+    ) +
+    geom_segment(
+      mapping = aes(x = x,
+                    y = q25,
+                    xend = x,
+                    yend = q75),
+      size = 2,
+      color = 'grey60'
+    ) +
+    geom_rect(data = gg_rect,
+              inherit.aes = FALSE,
+              aes(xmin = xmin,
+                  xmax = xmax,
+                  ymin = ymin,
+                  ymax = ymax),
+              fill = 'grey',
+              alpha = 1/6) +
+    geom_segment(x = 0, xend = 0,
+                 y = min(y_breaks), yend = max(y_breaks)) +
+    geom_point(size = 3, color = 'darkorange') +
[…]

### 2022-08-01 R/bm_time_visualize.R

@@ -1,0 +1,55 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param bm_time
+bm_time_visualize <- function(bm_time) {
+
+  bm_time_smry <- bm_time %>%
+    group_by(n_ftr, n_obs) %>%
+    summarize(across(everything(), quantile, probs = c(0.025, .5, .975))) %>%
+    mutate(quant = c('lo', 'est', 'hi')) %>%
+    pivot_longer(cols = -c(n_ftr, n_obs, quant)) %>%
+    pivot_wider(names_from = quant, values_from = value) %>%
+    mutate(
+      name = factor(
+        name,
+        levels = c('cif_party',
+                   'rsf_rfsrc',
+                   'aorsf_fast',
+                   'rsf_ranger'),
+        labels = c('party',
+                   'randomForestSRC',
+                   'aorsf',
+                   'ranger')
+      ),
+      n_ftr = paste(n_ftr, "features")
+    )
+
+  fig <- ggplot(bm_time_smry, aes(x = n_obs,
+                                  y = est,
+                                  fill = name,
+                                  col = name)) +
+    geom_line() +
+    geom_point() +
+    geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.25) +
+    facet_wrap(~n_ftr) +
+    scale_y_log10() +
+    scale_x_log10() +
+    labs(y = 'Time to fit 1 tree, seconds',
+         x = 'Number of observations in training data',
+         color = 'R package',
+         fill = 'R package') +
+    theme_bw() +
+    theme(panel.grid.major.x = element_blank(),
+          panel.grid.minor.x = element_blank(),
+          panel.grid.minor.y = element_blank())
+
+  ggsave(plot = fig,
+         filename = 'temp.png', width = 10, height = 5, dpi = 300)
+
+  fig
+
+
+}

### 2022-08-01 R/jhs_make.R

@@ -1,0 +1,99 @@
+
+
+jhs_make <- function(){
+
+  library(magrittr)
+
+  fpath <- file.path("data", "JHS_2018a_cvd", "Data")
+
+  event_vars <- c('newid', 'CHD', 'stroke', 'years')
+
+  inc_events <-
+    list.files(
+      file.path(fpath, "Events"),
+      pattern = "incev",
+      include.dirs = FALSE,
+      full.names = TRUE
+    ) %>%
+    set_names(c('chd', 'hf', 'stroke')) %>%
+    map(haven::read_sas) %>%
+    map(~select(.x, any_of(event_vars)))
+
+  inc_events$stroke %<>% rename(time_stroke = years,
+                                status_stroke = stroke)
+
+  inc_events$chd %<>% rename(time_chd = years,
+                             status_chd = CHD)
+
+  events <- inc_events[c('chd', 'stroke')] %>%
+    reduce(.f = left_join, by = 'newid')
+
+  analysis <- haven::read_sas(
+    file.path(fpath, 'Analysis_Data', 'analysis1.sas7bdat')
+  ) %>%
+    mutate(creatinine = coalesce(CreatinineU24hr, CreatinineUSpot),
+           albumin = coalesce(AlbuminU24hr, AlbuminUSpot),
+           acr = albumin / creatinine) %>%
+    select(
+      newid,
+      age,
+      sex,
+      alc,
+      currentSmoker,
+      everSmoker,
+      weight,
+      height,
+      waist,
+      neck,
+      ends_with("Meds"),
+      sbp,
+      dbp,
+      abi,
+      BMI,
+      HbA1c,
+      FPG,
+      FastHours,
+      Diabetes,
+      creatinine,
+      albumin,
+      acr,
+      ldl,
+      hdl,
+      trigs,
+      totchol,
+      LEPTIN,
+      HSCRP,
+      QTcFram,
+      ENDOTHELIN,
+      ALDOSTERONE,
+      sCort,
+      SCrCC,
+      eGFRckdepi,
+      CHDHx,
+      strokeHx,
+      MedicaidIns,
+      MedicareIns,
+      perceivedStress,
+      starts_with('nb'),
+      activeIndex,
+      eggs,
+      fish,
+      darkgrnVeg,
+      ecgHR,
+      CV,
+      QRS,
+      hyIndex,
+      sportIndex,
+      FEV6,
+      LVMindex,
+      Insured,
[…]

### 2022-08-01 R/summarize_data_source.R

@@ -69,7 +69,9 @@ summarize_data_source <- function(analyses_real) {
         "aric_hf" = "ARIC",
         "aric_chd" = "ARIC",
         "aric_stroke" = "ARIC",
-        "aric_death" = "ARIC"
+        "aric_death" = "ARIC",
+        "jhs_stroke" = "JHS",
+        "jhs_chd" = "JHS"
       ),
       rpack = recode(
         data,
@@ -109,7 +111,9 @@ summarize_data_source <- function(analyses_real) {
         "aric_hf" = NA_character_,
         "aric_chd" = NA_character_,
         "aric_stroke" = NA_character_,
-        "aric_death" = NA_character_
+        "aric_death" = NA_character_,
+        "jhs_stroke" = NA_character_,
+        "jhs_chd" = NA_character_
       ),
       cite = recode(
         data,
@@ -150,7 +154,9 @@ summarize_data_source <- function(analyses_real) {
         "aric_hf" = "aric1989atherosclerosis",
         "aric_chd" = "aric1989atherosclerosis",
         "aric_stroke" = "aric1989atherosclerosis",
-        "aric_death" = "aric1989atherosclerosis"
+        "aric_death" = "aric1989atherosclerosis",
+        "jhs_stroke" = "taylor2005toward",
+        "jhs_chd" = "taylor2005toward"
       ),
       outcome = recode(
         data,
@@ -190,7 +196,9 @@ summarize_data_source <- function(analyses_real) {
         "aric_hf" = "heart failure",
         "aric_chd" = "coronary heart disease",
         "aric_stroke" = "stroke",
-        "aric_death" = "death"
+        "aric_death" = "death",
+        "jhs_stroke" = "stroke",
+        "jhs_chd" = "coronary heart disease"
       ),
       .before = 2
     )

### 2022-08-01 README.Rmd
fig caps visible now

@@
 In fact, in a benchmark with 35 different risk prediction tasks, `aorsf-fast` was faster than all of the learners we analyzed, except for penalized Cox regression models (`glmnet-cox` in the paper).
+__Figure__: Distribution of time taken to fit a prediction model and compute predicted risk.
+The median time, in seconds, is printed and annotated for each learner by a vertical line.
 
-```{r, fig-bm-time, fig.cap="Distribution of time taken to fit a prediction model and compute predicted risk.
-The median time, in seconds, is printed and annotated for each learner by a vertical line.", fig.align='center', fig.width=8, fig.height=8}
+```{r, fig-bm-time, fig.align='center', fig.width=8, fig.height=8}
 bm_pred_time_viz$fig
@@
 
-- We find that `aorsf-fast` has the best index of prediction accuracy out of all the learners we evaluated:
+- We find that `aorsf-fast` has the best index of prediction accuracy out of all the learners we evaluated: __Figure__: Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
+A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.
 
-```{r, fig-bm-ibs, fig.cap="Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
-A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.", fig.align='center', fig.width=8, fig.height=8}
+```{r, fig-bm-ibs, fig.align='center', fig.width=9, fig.height=8}
 bm_pred_model_viz$fig$ibs_scaled
@@
 
-- We find that negation variable importance improves the chances of ranking a relevant variable as more important than an irrelevant variable when using an oblique RSF to estimate variable importance:
+- We find that negation variable importance improves the chances of ranking a relevant variable as more important than an irrelevant variable when using an oblique RSF to estimate variable importance.
+__Figure__: Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
+Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.
 
-```{r, fig-bm-vi, fig.cap="Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
-Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.", fig.align='center', fig.width=8, fig.height=10}
+```{r, fig-bm-vi, fig.align='center', fig.width=8, fig.height=10}
 bm_vi_viz$fig

### 2022-08-11 paper/arxiv/main.Rnw
update paper; NP feedback

@@
 	 \And
-	 Matthew Segar \\
+	 Matthew W. Segar \\
    Department of Cardiology \\
@@
 Notable characteristics of the RSF include uniform convergence of its ensemble survival prediction function to the true survival function, first shown by \citet{ishwaran2010consistency} and later by \citet{cui2017consistency} under more general conditions.
-However, \citet{cui2017consistency} noted that the RSF is at a disadvantage when predictors are correlated and some are not relevant to the censored outcome, which is a strong possibility when large medical databases are leveraged for risk prediction.
+However, \citet{cui2017consistency} noted that the RSF is at a disadvantage when predictors are correlated and some are not relevant to the censored outcome, which is a strong possibility when large clinical and `omic' databases are leveraged for risk prediction.
 
@@
 The accelerated oblique RSF and multiple methods to compute VI for oblique RSFs are available in the \texttt{aorsf} R Package.
-
-% However, there remains considerable potential to improve the RSF in settings where training samples are not large enough to guarantee asymptotic properties or do not align with the conditions required for consistency of the RSF.
-
-% Random forests (RFs) are large sets of de-correlated, randomized decision trees \citep{breiman2001random}, which can be axis based or oblique.Although using oblique rather than axis-based trees to grow a RSF may improve its prediction accuracy,
 
@@
 
-We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome. Specifically, \begin{itemize}
+We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome on the log-hazard scale. Specifically, \begin{itemize}
 \item \textit{irrelevant} variables had no relationship with the outcome.
-\item \textit{main effect} variables had a linear relationship to the outcome.
+\item \textit{main effect} variables had a linear relationship to the outcome on the log-hazard scale.
 \item \textit{non-linear effect} variables had a non-linear relationship to the outcome.
+A normally distributed variable $x$ was generated with a linear relationship to the outcome on the log-hazard scale, then $\tilde{x} = \text{sin}(a \cdot \pi \cdot x)$ was retained for modeling.
+The constant $a$ varied uniformly from 0.125 to 0.25.
 \item \textit{combination effect} variables were formed by linear combinations of three other variables.
-While their combination was linearly related to the outcome, each of the three variables contributing to the combination had no relation to the outcome.
+While their combination was linearly related to the outcome on the log-hazard scale, each of the three variables contributing to the combination had no relation to the outcome.
 \item \textit{interaction effect} variables were related to the outcome by multiplicative interaction with one other variable, which could have been a main effect, non-linear effect, or combination effect variable.
@@
 Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
-A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package.
+A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package \citep{simsurv, simsurv_paper}.
 The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
@@
 The content is solely the responsibility of the authors and does not necessarily represent the official views of the NIH.
+Dr.
+Pajewski was supported by grant number P30AG021332 from the National Institutes of Health, while Dr.
+Speiser was supported by K25AG068253.
 

### 2022-08-11 R/bench_pred_model_visualize.R

@@ -50,6 +50,8 @@ bench_pred_model_visualize <- function(bm_pred_model,
                                  "Time-dependent C-statistic"))
     )
 
+  write_rds(gg_data, "../seminar-fastpack/eval_fig_data.rds")
+
   plts <- gg_data |>
     group_by(metric) |>
     group_split() |>

### 2022-08-11 R/bench_pred_time_visualize.R

@@ -39,6 +39,9 @@ bench_pred_time_visualize <- function(bm_pred_clean, model_key) {
       )
     )
 
+  write_rds(gg_data, '../seminar-fastpack/time_fig_data.rds')
+  write_rds(medians, '../seminar-fastpack/time_fig_medians.rds')
+
 
   model_subsets <- list(
     slide_one = c('ranger-extratrees',
@@ -61,17 +64,17 @@ bench_pred_time_visualize <- function(bm_pred_clean, model_key) {
       )
     )
 
-  ggsave(figs$slide_one,
-         filename = '../seminar-fastpack/img/aorsf-bench-time_1.png',
-         dpi = 300,
-         width = 5.5,
-         height = 4.5)
-
-  ggsave(figs$slide_two,
-         filename = '../seminar-fastpack/img/aorsf-bench-time_2.png',
-         dpi = 300,
-         width = 5.5,
-         height = 4.5)
+  # ggsave(figs$slide_one,
+  #        filename = '../seminar-fastpack/img/aorsf-bench-time_1.png',
+  #        dpi = 300,
+  #        width = 5.5,
+  #        height = 4.5)
+  #
+  # ggsave(figs$slide_two,
+  #        filename = '../seminar-fastpack/img/aorsf-bench-time_2.png',
+  #        dpi = 300,
+  #        width = 5.5,
+  #        height = 4.5)
 
   list(medians = medians,
        fig = figs$paper)

### 2022-08-12 paper/arxiv/main.tex
re-run with scale = true for aorsf-fast

@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 20 out of 35 risk prediction tasks, with an overall mean IPA of 12.7 (Figure \ref{fig:bm_pred_viz_ibs}).
-Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.36 points higher, a relative increase of 12.0\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.79 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 20 out of 35 risk prediction tasks, with an overall mean IPA of 12.6 (Figure \ref{fig:bm_pred_viz_ibs}).
+Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.35 points higher, a relative increase of 12.0\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.78 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
 
@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 9 out of 35 risk prediction tasks, with an overall mean of 77.2 (Figure \ref{fig:bm_pred_viz_cstat}).
-Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.721 points higher, a relative increase of 0.943\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.24 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 10 out of 35 risk prediction tasks, with an overall mean of 77.2 (Figure \ref{fig:bm_pred_viz_cstat}).
+Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.685 points higher, a relative increase of 0.896\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.21 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
 
@@
 
-Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 256 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
-Comparing median computing times, \texttt{aorsf-fast} was 446.1 times faster than its predecessor, \texttt{obliqueRSF-net}.
-In addition, \texttt{aorsf-fast} was 18.9, 1.83, and 3.12 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
+Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 287 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+Comparing median computing times, \texttt{aorsf-fast} was 428.0 times faster than its predecessor, \texttt{obliqueRSF-net}.
+In addition, \texttt{aorsf-fast} was 18.2, 1.75, and 2.99 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
 
@@
 Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
-In numeric experiments, we found that that \texttt{aorsf-fast} is approximately 446.1 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
+In numeric experiments, we found that that \texttt{aorsf-fast} is approximately 428.0 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
 We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
@@
 \hline
-\hspace{1em}aorsf-fast & 0.127 (0.109) & 0.772 (0.071) & 0.593 & 0.146\\
+\hspace{1em}aorsf-fast & 0.126 (0.110) & 0.772 (0.071) & 0.632 & 0.135\\
 \hspace{1em}aorsf-cph & 0.126 (0.109) & 0.771 (0.070) & 1.344 & 0.148\\
@@
 \hspace{1em}cif-standard & 0.024 (0.031) & 0.744 (0.040) & 1.771 & 4.657\\
-\hspace{1em}aorsf-fast & 0.024 (0.028) & 0.745 (0.044) & 0.198 & 0.033\\
+\hspace{1em}aorsf-fast & 0.024 (0.029) & 0.746 (0.043) & 1.057 & 0.032\\
 \hspace{1em}cif-extension & 0.023 (0.015) & 0.722 (0.038) & 9.848 & 4.083\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.010 (0.022) & 0.840 (0.054) & 0.086 & 0.020\\
 \hspace{1em}obliqueRSF-net & 0.007 (0.011) & 0.823 (0.052) & 8.869 & 11.004\\
 \hspace{1em}aorsf-cph & 0.007 (0.018) & 0.821 (0.060) & 0.414 & 0.020\\
+\hspace{1em}aorsf-fast & 0.005 (0.019) & 0.827 (0.056) & 0.993 & 0.019\\
 \hspace{1em}aorsf-random & 0.005 (0.014) & 0.788 (0.074) & 0.278 & 0.023\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.157 (0.007) & 0.810 (0.007) & 4.640 & 1.320\\
+\hspace{1em}aorsf-fast & 0.156 (0.007) & 0.810 (0.007) & 5.063 & 1.279\\
 \hspace{1em}aorsf-cph & 0.153 (0.006) & 0.809 (0.007) & 14.503 & 1.347\\
@@
 \hspace{1em}rsf-standard & 0.216 (0.006) & 0.789 (0.004) & 14.727 & 1.274\\
+\hspace{1em}aorsf-fast & 0.216 (0.007) & 0.792 (0.004) & 7.350 & 2.050\\
 \hspace{1em}aorsf-cph & 0.216 (0.006) & 0.792 (0.004) & 22.922 & 2.179\\
-\hspace{1em}aorsf-fast & 0.215 (0.007) & 0.792 (0.004) & 7.641 & 2.214\\
 \hspace{1em}obliqueRSF-net & 0.207 (0.005) & 0.791 (0.004) & 7329.229 & 331.164\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.234 (0.006) & 0.841 (0.005) & 5.268 & 2.193\\
+\hspace{1em}aorsf-fast & 0.233 (0.006) & 0.841 (0.005) & 5.741 & 1.473\\
 \hspace{1em}rsf-standard & 0.229 (0.006) & 0.835 (0.005) & 11.238 & 1.079\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.093 (0.004) & 0.793 (0.007) & 4.179 & 1.122\\
+\hspace{1em}aorsf-fast & 0.093 (0.004) & 0.794 (0.007) & 3.730 & 1.052\\
 \hspace{1em}aorsf-net & 0.090 (0.004) & 0.792 (0.007) & 371.989 & 1.175\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.718 (0.012) & 0.239 & 0.053\\
+\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.717 (0.012) & 0.234 & 0.047\\
 \hspace{1em}aorsf-cph & 0.099 (0.014) & 0.717 (0.011) & 0.638 & 0.052\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.099 (0.017) & 0.713 (0.016) & 0.225 & 0.050\\
+\hspace{1em}aorsf-fast & 0.100 (0.017) & 0.713 (0.016) & 0.238 & 0.049\\
 \hspace{1em}aorsf-cph & 0.098 (0.017) & 0.712 (0.015) & 0.629 & 0.050\\
@@
 \hspace{1em}aorsf-cph & 0.067 (0.029) & 0.747 (0.026) & 1.287 & 0.185\\
-\hspace{1em}aorsf-fast & 0.065 (0.028) & 0.746 (0.026) & 0.724 & 0.177\\
+\hspace{1em}aorsf-fast & 0.065 (0.028) & 0.747 (0.027) & 0.700 & 0.165\\
 \hspace{1em}cif-extension & 0.064 (0.016) & 0.746 (0.028) & 44.047 & 6.554\\
@@
 \hspace{1em}aorsf-cph & 0.100 (0.039) & 0.769 (0.033) & 0.169 & 0.018\\
-\hspace{1em}aorsf-fast & 0.100 (0.038) & 0.768 (0.033) & 0.090 & 0.018\\
+\hspace{1em}aorsf-fast & 0.100 (0.037) & 0.768 (0.032) & 0.078 & 0.017\\
 \hspace{1em}aorsf-net & 0.097 (0.040) & 0.760 (0.034) & 12.619 & 0.018\\
@@
 \hspace{1em}aorsf-cph & 0.007 (0.020) & 0.595 (0.026) & 0.262 & 0.021\\
-\hspace{1em}aorsf-fast & 0.007 (0.019) & 0.594 (0.025) & 0.122 & 0.021\\
+\hspace{1em}aorsf-fast & 0.007 (0.020) & 0.594 (0.026) & 0.113 & 0.020\\
 \hspace{1em}aorsf-net & 0.006 (0.020) & 0.592 (0.026) & 18.761 & 0.022\\
@@
 \hspace{1em}aorsf-cph & 0.120 (0.025) & 0.736 (0.018) & 0.411 & 0.038\\
-\hspace{1em}aorsf-fast & 0.115 (0.024) & 0.733 (0.017) & 0.168 & 0.037\\
+\hspace{1em}aorsf-fast & 0.115 (0.024) & 0.733 (0.017) & 0.163 & 0.036\\
 \hspace{1em}cif-extension & 0.114 (0.017) & 0.743 (0.019) & 7.560 & 2.919\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.746 (0.027) & 0.152 & 0.036\\
+\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.745 (0.027) & 0.165 & 0.035\\
 \hspace{1em}aorsf-net & 0.074 (0.019) & 0.743 (0.027) & 29.058 & 0.041\\
@@
 \hspace{1em}aorsf-cph & 0.081 (0.018) & 0.722 (0.023) & 0.659 & 0.052\\
-\hspace{1em}aorsf-fast & 0.081 (0.019) & 0.722 (0.025) & 0.232 & 0.052\\
+\hspace{1em}aorsf-fast & 0.080 (0.020) & 0.722 (0.025) & 0.253 & 0.051\\
 \hspace{1em}ranger-extratrees & 0.073 (0.010) & 0.722 (0.022) & 0.137 & 0.198\\
@@
 \hspace{1em}obliqueRSF-net & 0.039 (0.007) & 0.780 (0.015) & 185.659 & 130.539\\
-\hspace{1em}aorsf-fast & 0.039 (0.007) & 0.777 (0.015) & 2.260 & 0.566\\
+\hspace{1em}aorsf-fast & 0.039 (0.007) & 0.776 (0.014) & 0.581 & 0.138\\
 \hspace{1em}aorsf-net & 0.039 (0.009) & 0.777 (0.016) & 78.653 & 0.606\\
@@
 \hspace{1em}aorsf-net & 0.035 (0.008) & 0.807 (0.016) & 72.257 & 0.610\\
-\hspace{1em}aorsf-fast & 0.035 (0.007) & 0.807 (0.018) & 2.321 & 0.571\\
+\hspace{1em}aorsf-fast & 0.035 (0.007) & 0.806 (0.017) & 0.588 & 0.149\\
 \hspace{1em}obliqueRSF-net & 0.030 (0.006) & 0.807 (0.016) & 161.865 & 165.270\\
@@
 \hspace{1em}aorsf-net & 0.061 (0.030) & 0.685 (0.019) & 31.742 & 0.031\\
-\hspace{1em}aorsf-fast & 0.059 (0.033) & 0.690 (0.019) & 0.125 & 0.030\\
+\hspace{1em}aorsf-fast & 0.059 (0.033) & 0.690 (0.019) & 0.126 & 0.028\\
 \hspace{1em}obliqueRSF-net & 0.058 (0.020) & 0.678 (0.020) & 294.626 & 2.961\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.063 (0.010) & 0.807 (0.011) & 1.219 & 0.352\\
+\hspace{1em}aorsf-fast & 0.064 (0.009) & 0.807 (0.010) & 1.338 & 0.349\\
 \hspace{1em}aorsf-net & 0.062 (0.010) & 0.805 (0.012) & 176.990 & 0.387\\
@@
 \hline
+\hspace{1em}aorsf-fast & 0.145 (0.008) & 0.792 (0.008) & 1.863 & 0.497\\
 \hspace{1em}aorsf-net & 0.144 (0.008) & 0.792 (0.009) & 318.785 & 0.546\\
-\hspace{1em}aorsf-fast & 0.144 (0.009) & 0.792 (0.009) & 1.694 & 0.506\\
 \hspace{1em}aorsf-cph & 0.143 (0.008) & 0.791 (0.009) & 6.893 & 0.523\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.115 (0.010) & 0.866 (0.013) & 1.094 & 0.311\\
+\hspace{1em}aorsf-fast & 0.115 (0.011) & 0.865 (0.012) & 1.216 & 0.311\\
 \hspace{1em}aorsf-net & 0.114 (0.011) & 0.863 (0.013) & 149.605 & 0.339\\
@@
 \hspace{1em}cif-standard & 0.025 (0.004) & 0.762 (0.017) & 23.450 & 98.166\\
-\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.764 (0.016) & 1.072 & 0.307\\
+\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.764 (0.016) & 1.174 & 0.303\\
 \hspace{1em}aorsf-net & 0.024 (0.006) & 0.759 (0.017) & 139.617 & 0.333\\
@@
 \hspace{1em}aorsf-cph & 0.158 (0.016) & 0.743 (0.011) & 1.154 & 0.084\\
-\hspace{1em}aorsf-fast & 0.157 (0.016) & 0.743 (0.011) & 0.408 & 0.088\\
+\hspace{1em}aorsf-fast & 0.157 (0.016) & 0.743 (0.011) & 0.496 & 0.084\\
 \hspace{1em}aorsf-net & 0.155 (0.016) & 0.741 (0.011) & 85.428 & 0.085\\
@@
 \hspace{1em}aorsf-cph & 0.011 (0.013) & 0.644 (0.036) & 0.574 & 0.040\\
-\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.641 (0.036) & 0.201 & 0.041\\
+\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.642 (0.036) & 0.194 & 0.039\\
 \hspace{1em}ranger-extratrees & 0.008 (0.006) & 0.642 (0.030) & 0.095 & 0.177\\
@@
 \hspace{1em}rsf-standard & 0.519 (0.022) & 0.922 (0.010) & 1.631 & 0.106\\
-\hspace{1em}aorsf-fast & 0.516 (0.027) & 0.923 (0.012) & 0.214 & 0.041\\
+\hspace{1em}aorsf-fast & 0.517 (0.027) & 0.923 (0.012) & 0.314 & 0.039\\
 \hspace{1em}xgboost-cox & 0.512 (0.029) & 0.932 (0.009) & 13.972 & 0.004\\
@@
 \hspace{1em}ranger-extratrees & 0.062 (0.028) & 0.675 (0.033) & 0.023 & 0.031\\
-\hspace{1em}aorsf-fast & 0.060 (0.043) & 0.672 (0.026) & 0.067 & 0.016\\
+\hspace{1em}aorsf-fast & 0.061 (0.043) & 0.672 (0.025) & 0.068 & 0.015\\
 \hspace{1em}obliqueRSF-net & 0.058 (0.026) & 0.676 (0.029) & 106.084 & 1.468\\
@@
 \hspace{1em}aorsf-cph & 0.124 (0.049) & 0.802 (0.051) & 0.078 & 0.013\\
-\hspace{1em}aorsf-fast & 0.121 (0.052) & 0.802 (0.054) & 0.052 & 0.014\\
+\hspace{1em}aorsf-fast & 0.121 (0.052) & 0.802 (0.054) & 0.050 & 0.013\\
 \hspace{1em}cif-rotate & 0.118 (0.059) & 0.787 (0.049) & 27.382 & 3.379\\
@@
 \hspace{1em}aorsf-cph & 0.213 (0.008) & 0.868 (0.005) & 17.724 & 1.232\\
-\hspace{1em}aorsf-fast & 0.212 (0.009) & 0.869 (0.005) & 4.868 & 1.247\\
+\hspace{1em}aorsf-fast & 0.212 (0.008) & 0.868 (0.005) & 4.466 & 1.206\\
 \hspace{1em}aorsf-net & 0.210 (0.008) & 0.864 (0.006) & 471.404 & 1.283\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.430 (0.032) & 0.908 (0.021) & 0.082 & 0.019\\
+\hspace{1em}aorsf-fast & 0.430 (0.032) & 0.908 (0.021) & 0.068 & 0.017\\
 \hspace{1em}aorsf-cph & 0.418 (0.034) & 0.906 (0.021) & 0.162 & 0.018\\
@@
 \hspace{1em}aorsf-cph & 0.163 (0.012) & 0.759 (0.009) & 2.520 & 0.201\\
-\hspace{1em}aorsf-fast & 0.161 (0.012) & 0.757 (0.009) & 0.845 & 0.198\\
+\hspace{1em}aorsf-fast & 0.160 (0.013) & 0.757 (0.010) & 0.920 & 0.191\\
 \hspace{1em}cif-standard & 0.159 (0.010) & 0.759 (0.009) & 4.629 & 22.523\\
@@
 \hspace{1em}cif-standard & 0.144 (0.011) & 0.734 (0.009) & 4.807 & 23.027\\
-\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 0.854 & 0.206\\
+\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 0.990 & 0.201\\
 \hspace{1em}aorsf-random & 0.141 (0.010) & 0.730 (0.008) & 3.192 & 0.185\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.250 (0.014) & 0.825 (0.007) & 2.023 & 0.587\\
+\hspace{1em}aorsf-fast & 0.250 (0.014) & 0.825 (0.007) & 3.030 & 0.559\\
 \hspace{1em}aorsf-cph & 0.250 (0.013) & 0.825 (0.008) & 6.401 & 0.580\\
@@
 \hspace{1em}aorsf-net & 0.070 (0.007) & 0.796 (0.011) & 337.860 & 0.660\\
-\hspace{1em}aorsf-fast & 0.069 (0.006) & 0.797 (0.011) & 2.581 & 0.638\\
+\hspace{1em}aorsf-fast & 0.070 (0.006) & 0.797 (0.010) & 2.522 & 0.578\\
 \hspace{1em}aorsf-cph & 0.069 (0.006) & 0.797 (0.011) & 9.028 & 0.596\\
@@
 \hspace{1em}aorsf-cph & 0.117 (0.008) & 0.770 (0.008) & 12.876 & 1.527\\
-\hspace{1em}aorsf-fast & 0.116 (0.008) & 0.770 (0.008) & 3.583 & 1.514\\
+\hspace{1em}aorsf-fast & 0.115 (0.009) & 0.769 (0.008) & 3.749 & 1.716\\
 \hspace{1em}aorsf-net & 0.113 (0.009) & 0.769 (0.009) & 590.419 & 0.934\\
@@
 \hspace{1em}aorsf-cph & 0.112 (0.013) & 0.744 (0.012) & 1.895 & 0.147\\
-\hspace{1em}aorsf-fast & 0.110 (0.015) & 0.743 (0.011) & 0.586 & 0.146\\
 \hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 4.079 & 16.213\\
+\hspace{1em}aorsf-fast & 0.109 (0.015) & 0.743 (0.012) & 0.634 & 0.142\\
 \hspace{1em}rsf-standard & 0.105 (0.011) & 0.735 (0.011) & 2.510 & 0.252\\
@@
 \hspace{1em}aorsf-net & 0.201 (0.050) & 0.797 (0.035) & 9.602 & 0.011\\
-\hspace{1em}aorsf-fast & 0.200 (0.050) & 0.795 (0.034) & 0.082 & 0.014\\
+\hspace{1em}aorsf-fast & 0.200 (0.049) & 0.795 (0.034) & 0.047 & 0.010\\
 \hspace{1em}cif-rotate & 0.198 (0.065) & 0.789 (0.036) & 4.476 & 1.284\\

### 2022-08-12 R/model_fit.R

@@ -138,8 +138,7 @@ aorsf_fast_fit <- function(train, node_size = 10, ...){
     n_retry = 3,
     split_min_obs = node_size,
     split_min_events = split_min_events,
-    control = orsf_control_cph(iter_max = 1,
-                               do_scale = FALSE),
+    control = orsf_control_fast(),
     importance = 'none',
     oobag_pred = FALSE
   )

### 2022-08-30 paper/arxiv/main.Rnw
do 1 more revision before submit

@@
 In general benchmarking experiments, we find that our implementation of the oblique RSF is approximately 450 times faster with equivalent discrimination and superior Brier score compared to existing software for oblique RSFs.
-We find in simulation studies that `negation importance' discriminates between relevant and irrelevant predictors more reliably than permutation importance, Shapley additive explanations, and a previously introduced technique to measure variable importance with oblique RSFs based on analysis of variance.
+We find in simulation studies that `negation importance' discriminates between relevant and irrelevant predictors more accurately than permutation importance, Shapley additive explanations, and a previously introduced technique to measure variable importance with oblique RSFs based on analysis of variance.
 All methods pertaining to oblique RSFs in the current study are available in the \texttt{aorsf} R package.
@@
 % keywords can be removed
-\keywords{Random Forests \and Survival \and Efficiency \and Variable Importance}
+\keywords{Oblique \and Survival \and Random Forests \and Fast \and Variable Importance}
 
@@
 
-Oblique trees have at least two notable drawbacks compared to axis-based trees.
+Despite the potential for higher accuracy, oblique trees have at least two notable drawbacks compared to axis-based trees.
 First, finding a locally optimal oblique decision rule may require exponentially more computation than an axis-based rule.
@@
 
-The rest of this article is organized as follows.
+The aim of this paper is to introduce methodology that improves the computational efficiency and interpretation of oblique RSFs.
 \secref{sec:background} reviews prior studies that have developed methods related to those introduced in the current study.
@@
 In \secref{sec:discussion}, we summarize results from the current study and present ideas connecting the current work to existing frameworks and methods for RSFs that future studies may engage with.
-The accelerated oblique RSF and multiple methods to compute VI for oblique RSFs are available in the \texttt{aorsf} R Package.
 

### 2022-08-30 paper/arxiv/main.tex
do 1 more revision before submit

@@
 Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.35 points higher, a relative increase of 12.0\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.78 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.86 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
 
@@
 Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.685 points higher, a relative increase of 0.896\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.21 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was $>$ 0.999, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.18 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
 
@@
 
-Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 287 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
-Comparing median computing times, \texttt{aorsf-fast} was 428.0 times faster than its predecessor, \texttt{obliqueRSF-net}.
-In addition, \texttt{aorsf-fast} was 18.2, 1.75, and 2.99 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
+Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 385 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+Comparing median computing times, \texttt{aorsf-fast} was 379.8 times faster than its predecessor, \texttt{obliqueRSF-net}.
+In addition, \texttt{aorsf-fast} was 16.1, 1.55, and 2.66 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
 
@@
 Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
-In numeric experiments, we found that that \texttt{aorsf-fast} is approximately 428.0 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
+In numeric experiments, we found that that \texttt{aorsf-fast} is approximately 379.8 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
 We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
@@
 \hline
-\hspace{1em}aorsf-fast & 0.126 (0.110) & 0.772 (0.071) & 0.632 & 0.135\\
-\hspace{1em}aorsf-cph & 0.126 (0.109) & 0.771 (0.070) & 1.344 & 0.148\\
-\hspace{1em}aorsf-net & 0.124 (0.112) & 0.771 (0.071) & 79.741 & 0.158\\
+\hspace{1em}aorsf-fast & 0.126 (0.110) & 0.772 (0.071) & 0.620 & 0.145\\
+\hspace{1em}aorsf-cph & 0.126 (0.109) & 0.771 (0.070) & 1.912 & 0.148\\
+\hspace{1em}aorsf-net & 0.124 (0.112) & 0.771 (0.071) & 78.512 & 0.143\\
 \hspace{1em}obliqueRSF-net & 0.113 (0.085) & 0.771 (0.071) & 300.393 & 18.803\\
@@
 \hspace{1em}cif-extension & 0.095 (0.092) & 0.761 (0.072) & 22.321 & 6.949\\
-\hspace{1em}aorsf-random & 0.090 (0.081) & 0.742 (0.063) & 1.855 & 0.152\\
+\hspace{1em}aorsf-random & 0.090 (0.081) & 0.741 (0.063) & 1.790 & 0.141\\
 \hspace{1em}xgboost-cox & 0.064 (0.100) & 0.749 (0.094) & 3.973 & 0.004\\
@@
 \hline
-\hspace{1em}aorsf-random & 0.028 (0.022) & 0.748 (0.038) & 0.539 & 0.040\\
+\hspace{1em}aorsf-random & 0.028 (0.022) & 0.748 (0.038) & 0.382 & 0.034\\
 \hspace{1em}ranger-extratrees & 0.028 (0.017) & 0.740 (0.036) & 0.064 & 0.146\\
 \hspace{1em}obliqueRSF-net & 0.027 (0.022) & 0.746 (0.038) & 25.980 & 15.236\\
-\hspace{1em}aorsf-cph & 0.025 (0.029) & 0.751 (0.042) & 0.471 & 0.033\\
+\hspace{1em}aorsf-cph & 0.025 (0.029) & 0.751 (0.042) & 0.424 & 0.033\\
 \hspace{1em}cif-standard & 0.024 (0.031) & 0.744 (0.040) & 1.771 & 4.657\\
-\hspace{1em}aorsf-fast & 0.024 (0.029) & 0.746 (0.043) & 1.057 & 0.032\\
+\hspace{1em}aorsf-fast & 0.024 (0.029) & 0.746 (0.043) & 0.144 & 0.032\\
 \hspace{1em}cif-extension & 0.023 (0.015) & 0.722 (0.038) & 9.848 & 4.083\\
-\hspace{1em}aorsf-net & 0.019 (0.034) & 0.745 (0.042) & 18.451 & 0.035\\
+\hspace{1em}aorsf-net & 0.019 (0.034) & 0.745 (0.042) & 17.078 & 0.034\\
 \hspace{1em}glmnet-cox & 0.016 (0.030) & 0.746 (0.037) & 0.179 & 0.003\\
@@
 \hspace{1em}obliqueRSF-net & 0.007 (0.011) & 0.823 (0.052) & 8.869 & 11.004\\
-\hspace{1em}aorsf-cph & 0.007 (0.018) & 0.821 (0.060) & 0.414 & 0.020\\
-\hspace{1em}aorsf-fast & 0.005 (0.019) & 0.827 (0.056) & 0.993 & 0.019\\
-\hspace{1em}aorsf-random & 0.005 (0.014) & 0.788 (0.074) & 0.278 & 0.023\\
+\hspace{1em}aorsf-cph & 0.007 (0.018) & 0.821 (0.060) & 0.340 & 0.018\\
+\hspace{1em}aorsf-fast & 0.005 (0.019) & 0.827 (0.056) & 0.086 & 0.018\\
+\hspace{1em}aorsf-random & 0.005 (0.014) & 0.788 (0.074) & 0.221 & 0.022\\
 \hspace{1em}cif-extension & 0.001 (0.020) & 0.765 (0.066) & 8.436 & 3.493\\
@@
 \hspace{1em}cif-standard & -0.005 (0.025) & 0.781 (0.062) & 1.726 & 4.648\\
-\hspace{1em}aorsf-net & -0.005 (0.032) & 0.806 (0.067) & 14.625 & 0.023\\
+\hspace{1em}aorsf-net & -0.005 (0.032) & 0.806 (0.067) & 13.309 & 0.022\\
 \hspace{1em}rsf-standard & -0.031 (0.051) & 0.776 (0.073) & 0.090 & 0.035\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.156 (0.007) & 0.810 (0.007) & 5.063 & 1.279\\
-\hspace{1em}aorsf-cph & 0.153 (0.006) & 0.809 (0.007) & 14.503 & 1.347\\
-\hspace{1em}aorsf-net & 0.152 (0.006) & 0.809 (0.007) & 533.804 & 1.437\\
+\hspace{1em}aorsf-fast & 0.156 (0.007) & 0.810 (0.007) & 5.048 & 1.287\\
+\hspace{1em}aorsf-cph & 0.153 (0.006) & 0.809 (0.007) & 14.564 & 1.300\\
+\hspace{1em}aorsf-net & 0.152 (0.006) & 0.809 (0.007) & 480.098 & 1.437\\
 \hspace{1em}rsf-standard & 0.150 (0.007) & 0.801 (0.007) & 9.407 & 0.991\\
@@
 \hspace{1em}cif-rotate & 0.104 (0.004) & 0.783 (0.009) & 569.289 & 67.436\\
-\hspace{1em}aorsf-random & 0.098 (0.005) & 0.772 (0.008) & 11.694 & 1.330\\
+\hspace{1em}aorsf-random & 0.097 (0.005) & 0.772 (0.008) & 10.996 & 1.259\\
 \hspace{1em}cif-extension & 0.069 (0.002) & 0.786 (0.009) & 169.206 & 56.091\\
@@
 \hline
-\hspace{1em}aorsf-net & 0.217 (0.006) & 0.792 (0.004) & 932.212 & 2.377\\
+\hspace{1em}aorsf-net & 0.217 (0.006) & 0.792 (0.004) & 902.210 & 2.343\\
 \hspace{1em}rsf-standard & 0.216 (0.006) & 0.789 (0.004) & 14.727 & 1.274\\
-\hspace{1em}aorsf-fast & 0.216 (0.007) & 0.792 (0.004) & 7.350 & 2.050\\
-\hspace{1em}aorsf-cph & 0.216 (0.006) & 0.792 (0.004) & 22.922 & 2.179\\
+\hspace{1em}aorsf-fast & 0.216 (0.007) & 0.792 (0.004) & 7.268 & 2.936\\
+\hspace{1em}aorsf-cph & 0.215 (0.006) & 0.792 (0.004) & 22.420 & 3.070\\
 \hspace{1em}obliqueRSF-net & 0.207 (0.005) & 0.791 (0.004) & 7329.229 & 331.164\\
@@
 \hspace{1em}xgboost-cox & 0.131 (0.012) & 0.794 (0.004) & 11.220 & 0.015\\
-\hspace{1em}aorsf-random & 0.130 (0.005) & 0.734 (0.005) & 20.175 & 2.057\\
+\hspace{1em}aorsf-random & 0.130 (0.005) & 0.733 (0.005) & 19.416 & 2.051\\
 \hspace{1em}cif-extension & 0.113 (0.002) & 0.775 (0.005) & 180.483 & 54.092\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.233 (0.006) & 0.841 (0.005) & 5.741 & 1.473\\
+\hspace{1em}aorsf-fast & 0.233 (0.006) & 0.841 (0.005) & 5.731 & 1.497\\
 \hspace{1em}rsf-standard & 0.229 (0.006) & 0.835 (0.005) & 11.238 & 1.079\\
-\hspace{1em}aorsf-cph & 0.229 (0.006) & 0.841 (0.005) & 16.864 & 2.308\\
-\hspace{1em}aorsf-net & 0.228 (0.006) & 0.841 (0.005) & 623.727 & 1.685\\
+\hspace{1em}aorsf-cph & 0.229 (0.006) & 0.841 (0.005) & 16.768 & 1.549\\
+\hspace{1em}aorsf-net & 0.228 (0.006) & 0.841 (0.005) & 597.572 & 1.659\\
 \hspace{1em}obliqueRSF-net & 0.212 (0.005) & 0.841 (0.005) & 3737.617 & 320.616\\
@@
 \hspace{1em}glmnet-cox & 0.167 (0.044) & 0.817 (0.018) & 2.141 & 0.011\\
-\hspace{1em}aorsf-random & 0.139 (0.005) & 0.789 (0.006) & 14.001 & 1.519\\
+\hspace{1em}aorsf-random & 0.139 (0.005) & 0.789 (0.006) & 12.952 & 1.501\\
 \hspace{1em}xgboost-cox & 0.122 (0.017) & 0.845 (0.005) & 10.926 & 0.015\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.093 (0.004) & 0.794 (0.007) & 3.730 & 1.052\\
-\hspace{1em}aorsf-net & 0.090 (0.004) & 0.792 (0.007) & 371.989 & 1.175\\
-\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.792 (0.007) & 13.462 & 1.149\\
+\hspace{1em}aorsf-fast & 0.093 (0.004) & 0.794 (0.007) & 4.549 & 1.078\\
+\hspace{1em}aorsf-net & 0.090 (0.004) & 0.792 (0.007) & 349.547 & 1.189\\
 \hspace{1em}rsf-standard & 0.090 (0.006) & 0.784 (0.006) & 8.991 & 0.984\\
+\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.792 (0.007) & 12.609 & 1.077\\
 \hspace{1em}obliqueRSF-net & 0.082 (0.003) & 0.791 (0.007) & 1869.359 & 387.014\\
@@
 \hspace{1em}ranger-extratrees & 0.067 (0.003) & 0.779 (0.008) & 251.130 & 50.542\\
-\hspace{1em}aorsf-random & 0.059 (0.004) & 0.750 (0.008) & 9.712 & 1.132\\
+\hspace{1em}aorsf-random & 0.059 (0.004) & 0.750 (0.008) & 9.179 & 1.091\\
 \hspace{1em}cif-rotate & 0.052 (0.003) & 0.768 (0.009) & 586.962 & 68.410\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.717 (0.012) & 0.234 & 0.047\\
-\hspace{1em}aorsf-cph & 0.099 (0.014) & 0.717 (0.011) & 0.638 & 0.052\\
+\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.717 (0.012) & 0.237 & 0.049\\
+\hspace{1em}aorsf-cph & 0.099 (0.014) & 0.717 (0.011) & 0.636 & 0.049\\
 \hspace{1em}cif-standard & 0.097 (0.013) & 0.710 (0.012) & 0.745 & 3.685\\
-\hspace{1em}aorsf-net & 0.096 (0.014) & 0.717 (0.012) & 49.140 & 0.047\\
-\hspace{1em}aorsf-random & 0.096 (0.010) & 0.716 (0.011) & 0.919 & 0.044\\
+\hspace{1em}aorsf-net & 0.096 (0.014) & 0.717 (0.012) & 47.226 & 0.048\\
+\hspace{1em}aorsf-random & 0.096 (0.010) & 0.716 (0.011) & 1.717 & 0.044\\
 \hspace{1em}obliqueRSF-net & 0.089 (0.006) & 0.717 (0.012) & 252.190 & 16.726\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.100 (0.017) & 0.713 (0.016) & 0.238 & 0.049\\
-\hspace{1em}aorsf-cph & 0.098 (0.017) & 0.712 (0.015) & 0.629 & 0.050\\
-\hspace{1em}aorsf-net & 0.095 (0.018) & 0.713 (0.017) & 49.866 & 0.048\\
-\hspace{1em}aorsf-random & 0.091 (0.013) & 0.706 (0.013) & 0.926 & 0.043\\
+\hspace{1em}aorsf-fast & 0.100 (0.017) & 0.713 (0.016) & 0.237 & 0.054\\
+\hspace{1em}aorsf-cph & 0.098 (0.017) & 0.712 (0.015) & 0.659 & 0.852\\
+\hspace{1em}aorsf-net & 0.095 (0.018) & 0.713 (0.017) & 47.589 & 0.049\\
 \hspace{1em}cif-standard & 0.091 (0.016) & 0.701 (0.017) & 0.717 & 3.703\\
 \hspace{1em}obliqueRSF-net & 0.087 (0.009) & 0.711 (0.015) & 249.790 & 16.701\\
+\hspace{1em}aorsf-random & 0.087 (0.012) & 0.702 (0.015) & 1.815 & 0.046\\
 \hspace{1em}cif-rotate & 0.084 (0.020) & 0.694 (0.017) & 13.154 & 3.977\\
@@
 \hspace{1em}cif-standard & 0.067 (0.019) & 0.747 (0.030) & 9.660 & 4.247\\
-\hspace{1em}aorsf-cph & 0.067 (0.029) & 0.747 (0.026) & 1.287 & 0.185\\
-\hspace{1em}aorsf-fast & 0.065 (0.028) & 0.747 (0.027) & 0.700 & 0.165\\
+\hspace{1em}aorsf-cph & 0.067 (0.029) & 0.747 (0.026) & 1.107 & 0.175\\
+\hspace{1em}aorsf-fast & 0.065 (0.028) & 0.747 (0.027) & 0.712 & 0.178\\
 \hspace{1em}cif-extension & 0.064 (0.016) & 0.746 (0.028) & 44.047 & 6.554\\
@@
 \hspace{1em}glmnet-cox & 0.041 (0.032) & 0.724 (0.036) & 5.780 & 0.006\\
-\hspace{1em}aorsf-random & 0.027 (0.015) & 0.696 (0.038) & 1.260 & 0.175\\
+\hspace{1em}aorsf-random & 0.027 (0.015) & 0.696 (0.038) & 1.924 & 0.167\\
 \hspace{1em}xgboost-cox & 0.027 (0.034) & 0.741 (0.030) & 2.258 & 0.007\\
 \hspace{1em}rsf-standard & 0.024 (0.037) & 0.695 (0.033) & 0.366 & 0.743\\
-\hspace{1em}aorsf-net & 0.012 (0.062) & 0.740 (0.025) & 465.845 & 0.175\\
+\hspace{1em}aorsf-net & 0.012 (0.062) & 0.740 (0.025) & 448.941 & 0.168\\
 \hspace{1em}nn-cox & -0.006 (0.043) & 0.669 (0.075) & 19.374 & 1.808\\
@@
 \hspace{1em}glmnet-cox & 0.117 (0.028) & 0.787 (0.037) & 0.098 & 0.002\\
-\hspace{1em}aorsf-cph & 0.100 (0.039) & 0.769 (0.033) & 0.169 & 0.018\\
-\hspace{1em}aorsf-fast & 0.100 (0.037) & 0.768 (0.032) & 0.078 & 0.017\\
-\hspace{1em}aorsf-net & 0.097 (0.040) & 0.760 (0.034) & 12.619 & 0.018\\
+\hspace{1em}aorsf-cph & 0.100 (0.039) & 0.769 (0.033) & 0.159 & 0.018\\
+\hspace{1em}aorsf-fast & 0.100 (0.037) & 0.768 (0.032) & 0.078 & 0.018\\
+\hspace{1em}aorsf-net & 0.097 (0.040) & 0.760 (0.034) & 12.491 & 0.018\\
 \hspace{1em}obliqueRSF-net & 0.089 (0.027) & 0.758 (0.036) & 97.158 & 5.447\\
@@
 \hspace{1em}cif-extension & 0.087 (0.036) & 0.730 (0.034) & 5.256 & 2.514\\
-\hspace{1em}aorsf-random & 0.087 (0.029) & 0.757 (0.032) & 0.256 & 0.018\\
+\hspace{1em}aorsf-random & 0.087 (0.029) & 0.757 (0.032) & 1.061 & 0.018\\
 \hspace{1em}cif-standard & 0.084 (0.038) & 0.743 (0.036) & 0.347 & 1.132\\
@@
 \hspace{1em}obliqueRSF-net & 0.013 (0.016) & 0.593 (0.024) & 217.838 & 6.232\\
-\hspace{1em}aorsf-random & 0.013 (0.018) & 0.595 (0.024) & 0.394 & 0.021\\
+\hspace{1em}aorsf-random & 0.013 (0.018) & 0.595 (0.024) & 1.166 & 0.020\\
 \hspace{1em}xgboost-cox & 0.010 (0.016) & 0.598 (0.031) & 1.331 & 0.002\\
 \hspace{1em}cif-standard & 0.008 (0.021) & 0.594 (0.023) & 0.315 & 1.056\\
-\hspace{1em}aorsf-cph & 0.007 (0.020) & 0.595 (0.026) & 0.262 & 0.021\\
-\hspace{1em}aorsf-fast & 0.007 (0.020) & 0.594 (0.026) & 0.113 & 0.020\\
-\hspace{1em}aorsf-net & 0.006 (0.020) & 0.592 (0.026) & 18.761 & 0.022\\
+\hspace{1em}aorsf-cph & 0.007 (0.020) & 0.595 (0.026) & 0.256 & 0.022\\
+\hspace{1em}aorsf-fast & 0.007 (0.020) & 0.594 (0.026) & 0.114 & 0.021\\
+\hspace{1em}aorsf-net & 0.006 (0.020) & 0.592 (0.026) & 18.652 & 0.022\\
 \hspace{1em}cif-extension & -0.005 (0.023) & 0.580 (0.028) & 6.164 & 2.309\\
@@
 \hspace{1em}rsf-standard & 0.120 (0.023) & 0.738 (0.019) & 1.437 & 0.115\\
-\hspace{1em}aorsf-net & 0.120 (0.024) & 0.738 (0.020) & 36.113 & 0.038\\
-\hspace{1em}aorsf-cph & 0.120 (0.025) & 0.736 (0.018) & 0.411 & 0.038\\
-\hspace{1em}aorsf-fast & 0.115 (0.024) & 0.733 (0.017) & 0.163 & 0.036\\
+\hspace{1em}aorsf-net & 0.120 (0.024) & 0.738 (0.020) & 35.967 & 0.038\\
+\hspace{1em}aorsf-cph & 0.120 (0.025) & 0.736 (0.018) & 0.401 & 0.037\\
+\hspace{1em}aorsf-fast & 0.115 (0.024) & 0.733 (0.017) & 0.161 & 0.037\\
 \hspace{1em}cif-extension & 0.114 (0.017) & 0.743 (0.019) & 7.560 & 2.919\\
 \hspace{1em}cif-rotate & 0.107 (0.023) & 0.729 (0.017) & 11.241 & 3.023\\
-\hspace{1em}aorsf-random & 0.104 (0.023) & 0.724 (0.025) & 0.754 & 0.036\\
+\hspace{1em}aorsf-random & 0.104 (0.023) & 0.724 (0.025) & 1.496 & 0.035\\
 \hspace{1em}ranger-extratrees & 0.094 (0.018) & 0.736 (0.025) & 0.102 & 0.143\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.745 (0.027) & 0.165 & 0.035\\
-\hspace{1em}aorsf-net & 0.074 (0.019) & 0.743 (0.027) & 29.058 & 0.041\\
-\hspace{1em}aorsf-cph & 0.071 (0.018) & 0.741 (0.028) & 0.403 & 0.037\\
+\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.745 (0.027) & 0.161 & 0.035\\
+\hspace{1em}aorsf-net & 0.074 (0.019) & 0.743 (0.027) & 25.934 & 0.038\\
+\hspace{1em}aorsf-cph & 0.071 (0.018) & 0.741 (0.028) & 0.375 & 0.035\\
 \hspace{1em}glmnet-cox & 0.063 (0.041) & 0.715 (0.091) & 0.502 & 0.002\\
@@
 \hspace{1em}xgboost-cox & 0.039 (0.051) & 0.747 (0.020) & 3.831 & 0.003\\
-\hspace{1em}aorsf-random & 0.033 (0.012) & 0.695 (0.030) & 0.536 & 0.039\\
+\hspace{1em}aorsf-random & 0.033 (0.012) & 0.695 (0.030) & 0.427 & 0.037\\
 \hspace{1em}nn-cox & 0.008 (0.018) & 0.630 (0.123) & 12.211 & 0.596\\
@@
 \hline
-\hspace{1em}aorsf-net & 0.082 (0.017) & 0.722 (0.023) & 53.095 & 0.058\\
-\hspace{1em}aorsf-cph & 0.081 (0.018) & 0.722 (0.023) & 0.659 & 0.052\\
-\hspace{1em}aorsf-fast & 0.080 (0.020) & 0.722 (0.025) & 0.253 & 0.051\\
+\hspace{1em}aorsf-net & 0.082 (0.017) & 0.722 (0.023) & 50.238 & 0.056\\
+\hspace{1em}aorsf-cph & 0.081 (0.018) & 0.722 (0.023) & 0.668 & 0.051\\
+\hspace{1em}aorsf-fast & 0.080 (0.020) & 0.722 (0.025) & 0.248 & 0.051\\
 \hspace{1em}ranger-extratrees & 0.073 (0.010) & 0.722 (0.022) & 0.137 & 0.198\\
@@
 \hspace{1em}nn-cox & 0.053 (0.028) & 0.706 (0.032) & 12.912 & 0.599\\
-\hspace{1em}aorsf-random & 0.049 (0.010) & 0.682 (0.023) & 0.914 & 0.054\\
+\hspace{1em}aorsf-random & 0.049 (0.010) & 0.682 (0.023) & 0.803 & 0.051\\
 \hspace{1em}xgboost-cox & 0.038 (0.017) & 0.698 (0.027) & 2.955 & 0.003\\
@@
 \hline
-\hspace{1em}aorsf-cph & 0.040 (0.008) & 0.778 (0.015) & 6.783 & 0.588\\
+\hspace{1em}aorsf-cph & 0.040 (0.008) & 0.778 (0.015) & 2.036 & 0.153\\
 \hspace{1em}obliqueRSF-net & 0.039 (0.007) & 0.780 (0.015) & 185.659 & 130.539\\
-\hspace{1em}aorsf-fast & 0.039 (0.007) & 0.776 (0.014) & 0.581 & 0.138\\
-\hspace{1em}aorsf-net & 0.039 (0.009) & 0.777 (0.016) & 78.653 & 0.606\\
+\hspace{1em}aorsf-fast & 0.039 (0.007) & 0.776 (0.014) & 0.586 & 0.151\\
+\hspace{1em}aorsf-net & 0.039 (0.009) & 0.777 (0.016) & 76.845 & 0.149\\
 \hspace{1em}cif-standard & 0.038 (0.006) & 0.779 (0.017) & 10.065 & 30.887\\
@@
 \hspace{1em}nn-cox & 0.030 (0.012) & 0.759 (0.021) & 10.787 & 5.787\\
-\hspace{1em}aorsf-random & 0.027 (0.004) & 0.763 (0.019) & 3.232 & 0.624\\
+\hspace{1em}aorsf-random & 0.027 (0.004) & 0.763 (0.019) & 1.213 & 0.152\\
 \hspace{1em}xgboost-cox & 0.010 (0.023) & 0.785 (0.022) & 3.676 & 0.005\\
@@
 \hline
-\hspace{1em}aorsf-cph & 0.036 (0.006) & 0.806 (0.016) & 6.729 & 0.588\\
-\hspace{1em}aorsf-net & 0.035 (0.008) & 0.807 (0.016) & 72.257 & 0.610\\
-\hspace{1em}aorsf-fast & 0.035 (0.007) & 0.806 (0.017) & 0.588 & 0.149\\
+\hspace{1em}aorsf-cph & 0.036 (0.006) & 0.806 (0.016) & 2.012 & 0.149\\
+\hspace{1em}aorsf-net & 0.035 (0.008) & 0.807 (0.016) & 70.506 & 0.144\\
+\hspace{1em}aorsf-fast & 0.035 (0.007) & 0.806 (0.017) & 0.581 & 0.147\\
 \hspace{1em}obliqueRSF-net & 0.030 (0.006) & 0.807 (0.016) & 161.865 & 165.270\\
@@
 \hspace{1em}cif-rotate & 0.023 (0.009) & 0.785 (0.017) & 188.792 & 24.524\\
-\hspace{1em}aorsf-random & 0.022 (0.004) & 0.775 (0.018) & 3.166 & 0.630\\
+\hspace{1em}aorsf-random & 0.022 (0.004) & 0.775 (0.018) & 1.115 & 0.153\\
 \hspace{1em}nn-cox & 0.016 (0.027) & 0.772 (0.021) & 10.445 & 6.338\\
@@
 \hline
-\hspace{1em}aorsf-cph & 0.063 (0.032) & 0.691 (0.019) & 0.316 & 0.030\\
-\hspace{1em}aorsf-net & 0.061 (0.030) & 0.685 (0.019) & 31.742 & 0.031\\
-\hspace{1em}aorsf-fast & 0.059 (0.033) & 0.690 (0.019) & 0.126 & 0.028\\
+\hspace{1em}aorsf-cph & 0.063 (0.032) & 0.691 (0.019) & 0.312 & 0.030\\
+\hspace{1em}aorsf-net & 0.061 (0.030) & 0.685 (0.019) & 30.349 & 0.031\\
+\hspace{1em}aorsf-fast & 0.059 (0.033) & 0.690 (0.019) & 0.124 & 0.029\\
 \hspace{1em}obliqueRSF-net & 0.058 (0.020) & 0.678 (0.020) & 294.626 & 2.961\\
@@
 \hspace{1em}glmnet-cox & 0.041 (0.024) & 0.664 (0.034) & 0.123 & 0.002\\
-\hspace{1em}aorsf-random & 0.040 (0.022) & 0.651 (0.023) & 0.538 & 0.026\\
+\hspace{1em}aorsf-random & 0.040 (0.022) & 0.651 (0.023) & 0.507 & 0.026\\
 \hspace{1em}nn-cox & 0.033 (0.025) & 0.647 (0.029) & 12.472 & 0.368\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.064 (0.009) & 0.807 (0.010) & 1.338 & 0.349\\
-\hspace{1em}aorsf-net & 0.062 (0.010) & 0.805 (0.012) & 176.990 & 0.387\\
+\hspace{1em}aorsf-fast & 0.064 (0.009) & 0.807 (0.010) & 1.333 & 0.340\\
+\hspace{1em}aorsf-net & 0.062 (0.010) & 0.805 (0.012) & 169.694 & 0.379\\
 \hspace{1em}obliqueRSF-net & 0.062 (0.008) & 0.808 (0.012) & 488.662 & 265.171\\
-\hspace{1em}aorsf-cph & 0.060 (0.010) & 0.801 (0.012) & 5.393 & 0.382\\
+\hspace{1em}aorsf-cph & 0.060 (0.010) & 0.801 (0.012) & 4.935 & 0.352\\
 \hspace{1em}cif-standard & 0.059 (0.007) & 0.803 (0.013) & 24.446 & 98.767\\
@@
 \hspace{1em}nn-cox & 0.038 (0.017) & 0.767 (0.021) & 18.380 & 16.712\\
-\hspace{1em}aorsf-random & 0.031 (0.005) & 0.735 (0.015) & 2.927 & 0.397\\
+\hspace{1em}aorsf-random & 0.031 (0.005) & 0.735 (0.015) & 2.853 & 0.387\\
 \hspace{1em}xgboost-cox & 0.015 (0.028) & 0.802 (0.013) & 4.763 & 0.009\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.145 (0.008) & 0.792 (0.008) & 1.863 & 0.497\\
-\hspace{1em}aorsf-net & 0.144 (0.008) & 0.792 (0.009) & 318.785 & 0.546\\
-\hspace{1em}aorsf-cph & 0.143 (0.008) & 0.791 (0.009) & 6.893 & 0.523\\
+\hspace{1em}aorsf-fast & 0.145 (0.008) & 0.792 (0.008) & 1.868 & 0.487\\
+\hspace{1em}aorsf-net & 0.144 (0.008) & 0.792 (0.009) & 293.640 & 0.547\\
+\hspace{1em}aorsf-cph & 0.143 (0.008) & 0.791 (0.009) & 6.625 & 0.504\\
 \hspace{1em}rsf-standard & 0.140 (0.008) & 0.784 (0.009) & 4.818 & 0.502\\
@@
 \hspace{1em}cif-extension & 0.092 (0.003) & 0.781 (0.009) & 111.068 & 32.105\\
-\hspace{1em}aorsf-random & 0.068 (0.005) & 0.725 (0.008) & 5.608 & 0.565\\
+\hspace{1em}aorsf-random & 0.068 (0.005) & 0.725 (0.008) & 5.755 & 0.541\\
 \hspace{1em}xgboost-cox & 0.056 (0.029) & 0.794 (0.009) & 8.021 & 0.009\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.115 (0.011) & 0.865 (0.012) & 1.216 & 0.311\\
-\hspace{1em}aorsf-net & 0.114 (0.011) & 0.863 (0.013) & 149.605 & 0.339\\
-\hspace{1em}aorsf-cph & 0.109 (0.011) & 0.858 (0.014) & 4.842 & 0.326\\
+\hspace{1em}aorsf-fast & 0.115 (0.011) & 0.865 (0.012) & 1.218 & 0.301\\
+\hspace{1em}aorsf-net & 0.114 (0.011) & 0.863 (0.013) & 147.441 & 0.338\\
+\hspace{1em}aorsf-cph & 0.109 (0.011) & 0.858 (0.014) & 4.549 & 0.315\\
 \hspace{1em}rsf-standard & 0.108 (0.012) & 0.856 (0.012) & 3.125 & 1.151\\
@@
 \hspace{1em}nn-cox & 0.071 (0.024) & 0.826 (0.016) & 15.797 & 17.312\\
-\hspace{1em}aorsf-random & 0.064 (0.006) & 0.795 (0.014) & 2.520 & 0.369\\
+\hspace{1em}aorsf-random & 0.064 (0.006) & 0.795 (0.014) & 2.377 & 0.355\\
 \hspace{1em}glmnet-cox & 0.043 (0.044) & 0.767 (0.139) & 3.777 & 0.006\\
@@
 \hspace{1em}cif-standard & 0.025 (0.004) & 0.762 (0.017) & 23.450 & 98.166\\
-\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.764 (0.016) & 1.174 & 0.303\\
-\hspace{1em}aorsf-net & 0.024 (0.006) & 0.759 (0.017) & 139.617 & 0.333\\
-\hspace{1em}aorsf-cph & 0.023 (0.005) & 0.758 (0.016) & 4.266 & 0.316\\
+\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.764 (0.016) & 1.186 & 0.296\\
+\hspace{1em}aorsf-net & 0.024 (0.006) & 0.759 (0.017) & 134.136 & 0.330\\
+\hspace{1em}aorsf-cph & 0.023 (0.005) & 0.758 (0.016) & 4.128 & 0.305\\
 \hspace{1em}ranger-extratrees & 0.022 (0.003) & 0.759 (0.016) & 7.610 & 6.738\\
@@
 \hspace{1em}nn-cox & 0.018 (0.007) & 0.746 (0.028) & 16.152 & 17.979\\
-\hspace{1em}aorsf-random & 0.013 (0.003) & 0.714 (0.022) & 2.420 & 0.343\\
+\hspace{1em}aorsf-random & 0.013 (0.003) & 0.714 (0.022) & 2.275 & 0.330\\
 \hspace{1em}xgboost-cox & 0.000 (0.025) & 0.762 (0.018) & 4.347 & 0.008\\
@@
 \hspace{1em}cif-rotate & 0.159 (0.019) & 0.744 (0.014) & 15.123 & 4.858\\
-\hspace{1em}aorsf-cph & 0.158 (0.016) & 0.743 (0.011) & 1.154 & 0.084\\
-\hspace{1em}aorsf-fast & 0.157 (0.016) & 0.743 (0.011) & 0.496 & 0.084\\
-\hspace{1em}aorsf-net & 0.155 (0.016) & 0.741 (0.011) & 85.428 & 0.085\\
+\hspace{1em}aorsf-cph & 0.158 (0.016) & 0.743 (0.011) & 2.035 & 0.087\\
+\hspace{1em}aorsf-fast & 0.157 (0.016) & 0.743 (0.011) & 1.266 & 0.086\\
+\hspace{1em}aorsf-net & 0.155 (0.016) & 0.741 (0.011) & 84.984 & 0.088\\
 \hspace{1em}obliqueRSF-net & 0.155 (0.013) & 0.743 (0.011) & 232.467 & 12.924\\
@@
 \hspace{1em}rsf-standard & 0.151 (0.017) & 0.737 (0.011) & 2.281 & 0.194\\
-\hspace{1em}aorsf-random & 0.146 (0.013) & 0.735 (0.011) & 1.757 & 0.084\\
+\hspace{1em}aorsf-random & 0.146 (0.013) & 0.735 (0.011) & 2.457 & 0.082\\
 \hspace{1em}cif-extension & 0.143 (0.009) & 0.747 (0.013) & 11.222 & 4.744\\
@@
 \hspace{1em}glmnet-cox & 0.015 (0.011) & 0.651 (0.055) & 0.118 & 0.003\\
-\hspace{1em}aorsf-cph & 0.011 (0.013) & 0.644 (0.036) & 0.574 & 0.040\\
-\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.642 (0.036) & 0.194 & 0.039\\
+\hspace{1em}aorsf-cph & 0.011 (0.013) & 0.644 (0.036) & 0.568 & 0.040\\
+\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.642 (0.036) & 0.193 & 0.040\\
 \hspace{1em}ranger-extratrees & 0.008 (0.006) & 0.642 (0.030) & 0.095 & 0.177\\
@@
 \hspace{1em}obliqueRSF-net & 0.007 (0.010) & 0.628 (0.033) & 41.856 & 16.910\\
-\hspace{1em}aorsf-net & 0.007 (0.014) & 0.641 (0.034) & 22.366 & 0.041\\
-\hspace{1em}aorsf-random & 0.007 (0.013) & 0.633 (0.033) & 0.517 & 0.040\\
+\hspace{1em}aorsf-net & 0.007 (0.014) & 0.641 (0.034) & 22.236 & 0.041\\
+\hspace{1em}aorsf-random & 0.007 (0.013) & 0.633 (0.033) & 1.329 & 0.039\\
 \hspace{1em}xgboost-cox & 0.007 (0.017) & 0.639 (0.039) & 1.783 & 0.003\\
@@
 \hspace{1em}nn-cox & 0.534 (0.072) & 0.910 (0.027) & 17.266 & 0.663\\
-\hspace{1em}aorsf-net & 0.530 (0.028) & 0.928 (0.010) & 50.720 & 0.043\\
-\hspace{1em}aorsf-cph & 0.522 (0.024) & 0.925 (0.011) & 0.788 & 0.041\\
+\hspace{1em}aorsf-net & 0.530 (0.028) & 0.928 (0.010) & 50.081 & 0.045\\
+\hspace{1em}aorsf-cph & 0.522 (0.024) & 0.925 (0.011) & 1.645 & 0.043\\
 \hspace{1em}rsf-standard & 0.519 (0.022) & 0.922 (0.010) & 1.631 & 0.106\\
-\hspace{1em}aorsf-fast & 0.517 (0.027) & 0.923 (0.012) & 0.314 & 0.039\\
+\hspace{1em}aorsf-fast & 0.517 (0.027) & 0.923 (0.012) & 1.090 & 0.042\\
 \hspace{1em}xgboost-cox & 0.512 (0.029) & 0.932 (0.009) & 13.972 & 0.004\\
@@
 \hspace{1em}obliqueRSF-net & 0.319 (0.022) & 0.909 (0.017) & 155.421 & 8.847\\
-\hspace{1em}aorsf-random & 0.300 (0.032) & 0.849 (0.027) & 0.869 & 0.039\\
+\hspace{1em}aorsf-random & 0.300 (0.032) & 0.849 (0.027) & 1.681 & 0.039\\
 \hspace{1em}xgboost-aft & --- & 0.927 (0.010) & 33.545 & 0.008\\
@@
 \hline
-\hspace{1em}aorsf-random & 0.076 (0.030) & 0.686 (0.026) & 0.304 & 0.015\\
+\hspace{1em}aorsf-random & 0.076 (0.030) & 0.686 (0.026) & 1.162 & 0.016\\
 \hspace{1em}ranger-extratrees & 0.062 (0.028) & 0.675 (0.033) & 0.023 & 0.031\\
-\hspace{1em}aorsf-fast & 0.061 (0.043) & 0.672 (0.025) & 0.068 & 0.015\\
+\hspace{1em}aorsf-fast & 0.061 (0.043) & 0.672 (0.025) & 0.066 & 0.016\\
 \hspace{1em}obliqueRSF-net & 0.058 (0.026) & 0.676 (0.029) & 106.084 & 1.468\\
-\hspace{1em}aorsf-cph & 0.058 (0.041) & 0.670 (0.024) & 0.150 & 0.016\\
+\hspace{1em}aorsf-cph & 0.058 (0.041) & 0.670 (0.024) & 0.153 & 0.016\\
 \hspace{1em}cif-standard & 0.055 (0.032) & 0.670 (0.030) & 0.130 & 0.252\\
 \hspace{1em}cif-extension & 0.051 (0.032) & 0.664 (0.029) & 3.799 & 1.502\\
-\hspace{1em}aorsf-net & 0.047 (0.040) & 0.668 (0.026) & 16.041 & 0.016\\
+\hspace{1em}aorsf-net & 0.047 (0.040) & 0.668 (0.026) & 16.124 & 0.017\\
 \hspace{1em}glmnet-cox & 0.033 (0.031) & 0.638 (0.059) & 0.081 & 0.002\\
@@
 \hline
-\hspace{1em}aorsf-net & 0.142 (0.056) & 0.804 (0.056) & 10.798 & 0.014\\
-\hspace{1em}aorsf-cph & 0.124 (0.049) & 0.802 (0.051) & 0.078 & 0.013\\
-\hspace{1em}aorsf-fast & 0.121 (0.052) & 0.802 (0.054) & 0.050 & 0.013\\
+\hspace{1em}aorsf-net & 0.142 (0.056) & 0.804 (0.056) & 10.521 & 0.014\\
+\hspace{1em}aorsf-cph & 0.124 (0.049) & 0.802 (0.051) & 0.076 & 0.013\\
+\hspace{1em}aorsf-fast & 0.121 (0.052) & 0.802 (0.054) & 0.049 & 0.014\\
 \hspace{1em}cif-rotate & 0.118 (0.059) & 0.787 (0.049) & 27.382 & 3.379\\
@@
 \hspace{1em}ranger-extratrees & 0.064 (0.044) & 0.774 (0.054) & 0.024 & 0.030\\
-\hspace{1em}aorsf-random & 0.053 (0.045) & 0.741 (0.060) & 0.183 & 0.015\\
+\hspace{1em}aorsf-random & 0.053 (0.045) & 0.741 (0.060) & 0.136 & 0.014\\
 \hspace{1em}nn-cox & 0.051 (0.102) & 0.715 (0.100) & 11.692 & 0.121\\
@@
 \hline
-\hspace{1em}aorsf-cph & 0.213 (0.008) & 0.868 (0.005) & 17.724 & 1.232\\
-\hspace{1em}aorsf-fast & 0.212 (0.008) & 0.868 (0.005) & 4.466 & 1.206\\
-\hspace{1em}aorsf-net & 0.210 (0.008) & 0.864 (0.006) & 471.404 & 1.283\\
+\hspace{1em}aorsf-cph & 0.213 (0.008) & 0.868 (0.005) & 16.251 & 2.106\\
+\hspace{1em}aorsf-fast & 0.212 (0.008) & 0.868 (0.005) & 4.412 & 2.014\\
+\hspace{1em}aorsf-net & 0.210 (0.008) & 0.864 (0.006) & 433.878 & 1.276\\
 \hspace{1em}obliqueRSF-net & 0.209 (0.008) & 0.868 (0.006) & 1428.698 & 1042.701\\
@@
 \hspace{1em}cif-extension & 0.166 (0.003) & 0.866 (0.006) & 125.288 & 53.237\\
-\hspace{1em}aorsf-random & 0.140 (0.006) & 0.838 (0.007) & 8.915 & 1.339\\
+\hspace{1em}aorsf-random & 0.140 (0.006) & 0.838 (0.007) & 8.961 & 1.333\\
 \hspace{1em}xgboost-cox & 0.020 (0.015) & 0.876 (0.005) & 8.907 & 0.017\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.430 (0.032) & 0.908 (0.021) & 0.068 & 0.017\\
-\hspace{1em}aorsf-cph & 0.418 (0.034) & 0.906 (0.021) & 0.162 & 0.018\\
-\hspace{1em}aorsf-net & 0.413 (0.035) & 0.905 (0.021) & 14.047 & 0.019\\
+\hspace{1em}aorsf-fast & 0.430 (0.032) & 0.908 (0.021) & 0.067 & 0.018\\
+\hspace{1em}aorsf-cph & 0.418 (0.034) & 0.906 (0.021) & 0.149 & 0.018\\
+\hspace{1em}aorsf-net & 0.413 (0.035) & 0.905 (0.021) & 14.298 & 0.020\\
 \hspace{1em}cif-rotate & 0.405 (0.040) & 0.899 (0.022) & 10.102 & 1.933\\
@@
 \hspace{1em}obliqueRSF-net & 0.369 (0.032) & 0.907 (0.022) & 111.656 & 1.787\\
-\hspace{1em}aorsf-random & 0.354 (0.031) & 0.893 (0.020) & 0.308 & 0.020\\
+\hspace{1em}aorsf-random & 0.354 (0.031) & 0.893 (0.020) & 1.093 & 0.018\\
 \hspace{1em}cif-standard & 0.352 (0.034) & 0.904 (0.025) & 0.206 & 0.363\\
@@
 \hline
-\hspace{1em}aorsf-net & 0.166 (0.012) & 0.762 (0.009) & 147.998 & 0.185\\
+\hspace{1em}aorsf-net & 0.166 (0.012) & 0.762 (0.009) & 145.278 & 0.191\\
 \hspace{1em}obliqueRSF-net & 0.163 (0.010) & 0.761 (0.009) & 439.210 & 37.683\\
-\hspace{1em}aorsf-cph & 0.163 (0.012) & 0.759 (0.009) & 2.520 & 0.201\\
-\hspace{1em}aorsf-fast & 0.160 (0.013) & 0.757 (0.010) & 0.920 & 0.191\\
+\hspace{1em}aorsf-cph & 0.163 (0.012) & 0.759 (0.009) & 3.388 & 0.195\\
+\hspace{1em}aorsf-fast & 0.160 (0.013) & 0.757 (0.010) & 1.684 & 0.194\\
 \hspace{1em}cif-standard & 0.159 (0.010) & 0.759 (0.009) & 4.629 & 22.523\\
 \hspace{1em}rsf-standard & 0.159 (0.014) & 0.756 (0.009) & 3.066 & 0.967\\
-\hspace{1em}aorsf-random & 0.153 (0.010) & 0.752 (0.010) & 2.840 & 0.180\\
+\hspace{1em}aorsf-random & 0.153 (0.010) & 0.752 (0.010) & 3.554 & 0.181\\
 \hspace{1em}cif-rotate & 0.147 (0.011) & 0.751 (0.011) & 34.328 & 8.629\\
@@
 \hspace{1em}obliqueRSF-net & 0.148 (0.010) & 0.737 (0.009) & 520.813 & 39.774\\
-\hspace{1em}aorsf-net & 0.146 (0.011) & 0.735 (0.009) & 160.272 & 0.191\\
-\hspace{1em}aorsf-cph & 0.145 (0.012) & 0.734 (0.008) & 2.678 & 0.205\\
+\hspace{1em}aorsf-net & 0.146 (0.011) & 0.735 (0.009) & 155.933 & 0.198\\
+\hspace{1em}aorsf-cph & 0.145 (0.012) & 0.734 (0.008) & 3.589 & 0.206\\
 \hspace{1em}cif-standard & 0.144 (0.011) & 0.734 (0.009) & 4.807 & 23.027\\
-\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 0.990 & 0.201\\
-\hspace{1em}aorsf-random & 0.141 (0.010) & 0.730 (0.008) & 3.192 & 0.185\\
+\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 1.760 & 0.204\\
+\hspace{1em}aorsf-random & 0.140 (0.010) & 0.730 (0.008) & 3.803 & 0.185\\
 \hspace{1em}rsf-standard & 0.139 (0.012) & 0.731 (0.008) & 3.003 & 1.000\\
@@
 \hline
-\hspace{1em}aorsf-fast & 0.250 (0.014) & 0.825 (0.007) & 3.030 & 0.559\\
-\hspace{1em}aorsf-cph & 0.250 (0.013) & 0.825 (0.008) & 6.401 & 0.580\\
-\hspace{1em}aorsf-net & 0.250 (0.012) & 0.823 (0.008) & 278.411 & 0.563\\
+\hspace{1em}aorsf-fast & 0.250 (0.014) & 0.825 (0.007) & 2.956 & 0.566\\
+\hspace{1em}aorsf-cph & 0.250 (0.013) & 0.825 (0.008) & 7.220 & 0.575\\
+\hspace{1em}aorsf-net & 0.250 (0.012) & 0.823 (0.008) & 267.989 & 0.565\\
 \hspace{1em}glmnet-cox & 0.248 (0.012) & 0.820 (0.007) & 0.539 & 0.006\\
@@
 \hspace{1em}rsf-standard & 0.243 (0.013) & 0.815 (0.008) & 5.399 & 0.585\\
-\hspace{1em}aorsf-random & 0.231 (0.012) & 0.816 (0.008) & 6.681 & 0.568\\
+\hspace{1em}aorsf-random & 0.231 (0.012) & 0.816 (0.008) & 6.409 & 0.562\\
 \hspace{1em}cif-rotate & 0.228 (0.009) & 0.819 (0.007) & 65.379 & 21.402\\
@@
 \hspace{1em}glmnet-cox & 0.071 (0.011) & 0.795 (0.011) & 13.850 & 0.011\\
-\hspace{1em}aorsf-net & 0.070 (0.007) & 0.796 (0.011) & 337.860 & 0.660\\
-\hspace{1em}aorsf-fast & 0.070 (0.006) & 0.797 (0.010) & 2.522 & 0.578\\
-\hspace{1em}aorsf-cph & 0.069 (0.006) & 0.797 (0.011) & 9.028 & 0.596\\
+\hspace{1em}aorsf-net & 0.070 (0.007) & 0.796 (0.011) & 330.532 & 0.613\\
+\hspace{1em}aorsf-fast & 0.070 (0.006) & 0.797 (0.010) & 2.561 & 0.604\\
+\hspace{1em}aorsf-cph & 0.069 (0.006) & 0.797 (0.011) & 8.283 & 0.620\\
 \hspace{1em}obliqueRSF-net & 0.068 (0.005) & 0.798 (0.012) & 1017.350 & 425.134\\
@@
 \hspace{1em}cif-extension & 0.034 (0.002) & 0.789 (0.011) & 122.779 & 33.342\\
-\hspace{1em}aorsf-random & 0.026 (0.002) & 0.747 (0.016) & 5.887 & 0.742\\
+\hspace{1em}aorsf-random & 0.026 (0.002) & 0.747 (0.016) & 5.282 & 0.708\\
 \hspace{1em}xgboost-cox & 0.006 (0.017) & 0.799 (0.011) & 6.888 & 0.013\\
@@
 \hspace{1em}glmnet-cox & 0.123 (0.012) & 0.771 (0.009) & 5.422 & 0.010\\
-\hspace{1em}aorsf-cph & 0.117 (0.008) & 0.770 (0.008) & 12.876 & 1.527\\
-\hspace{1em}aorsf-fast & 0.115 (0.009) & 0.769 (0.008) & 3.749 & 1.716\\
-\hspace{1em}aorsf-net & 0.113 (0.009) & 0.769 (0.009) & 590.419 & 0.934\\
+\hspace{1em}aorsf-cph & 0.117 (0.008) & 0.770 (0.008) & 11.811 & 1.833\\
+\hspace{1em}aorsf-fast & 0.115 (0.009) & 0.769 (0.008) & 3.826 & 1.817\\
+\hspace{1em}aorsf-net & 0.113 (0.009) & 0.769 (0.009) & 587.892 & 0.933\\
 \hspace{1em}obliqueRSF-net & 0.112 (0.007) & 0.767 (0.008) & 2630.588 & 231.667\\
@@
 \hspace{1em}cif-extension & 0.055 (0.002) & 0.747 (0.009) & 137.470 & 34.230\\
-\hspace{1em}aorsf-random & 0.052 (0.003) & 0.720 (0.010) & 9.559 & 1.034\\
+\hspace{1em}aorsf-random & 0.052 (0.003) & 0.720 (0.010) & 8.360 & 0.992\\
 \hspace{1em}xgboost-cox & 0.030 (0.023) & 0.772 (0.008) & 9.057 & 0.014\\
@@
 \hspace{1em}cif-rotate & 0.113 (0.013) & 0.741 (0.011) & 71.714 & 10.523\\
-\hspace{1em}aorsf-net & 0.112 (0.013) & 0.743 (0.012) & 118.505 & 0.158\\
-\hspace{1em}aorsf-cph & 0.112 (0.013) & 0.744 (0.012) & 1.895 & 0.147\\
+\hspace{1em}aorsf-net & 0.112 (0.013) & 0.743 (0.012) & 114.909 & 0.160\\
+\hspace{1em}aorsf-cph & 0.112 (0.013) & 0.744 (0.012) & 1.931 & 0.145\\
 \hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 4.079 & 16.213\\
-\hspace{1em}aorsf-fast & 0.109 (0.015) & 0.743 (0.012) & 0.634 & 0.142\\
+\hspace{1em}aorsf-fast & 0.109 (0.015) & 0.743 (0.012) & 0.618 & 0.142\\
 \hspace{1em}rsf-standard & 0.105 (0.011) & 0.735 (0.011) & 2.510 & 0.252\\
@@
 \hspace{1em}xgboost-cox & 0.090 (0.009) & 0.744 (0.010) & 4.229 & 0.004\\
-\hspace{1em}aorsf-random & 0.080 (0.006) & 0.731 (0.013) & 2.448 & 0.151\\
+\hspace{1em}aorsf-random & 0.080 (0.006) & 0.731 (0.013) & 2.025 & 0.143\\
 \hspace{1em}nn-cox & 0.074 (0.028) & 0.705 (0.036) & 18.945 & 5.181\\
@@
 \hline
-\hspace{1em}aorsf-net & 0.201 (0.050) & 0.797 (0.035) & 9.602 & 0.011\\
-\hspace{1em}aorsf-fast & 0.200 (0.049) & 0.795 (0.034) & 0.047 & 0.010\\
+\hspace{1em}aorsf-net & 0.201 (0.050) & 0.797 (0.035) & 9.901 & 0.012\\
+\hspace{1em}aorsf-fast & 0.200 (0.049) & 0.795 (0.034) & 0.047 & 0.012\\
 \hspace{1em}cif-rotate & 0.198 (0.065) & 0.789 (0.036) & 4.476 & 1.284\\
-\hspace{1em}aorsf-cph & 0.198 (0.052) & 0.794 (0.035) & 0.105 & 0.011\\
+\hspace{1em}aorsf-cph & 0.198 (0.052) & 0.794 (0.035) & 0.094 & 0.012\\
 \hspace{1em}rsf-standard & 0.176 (0.048) & 0.787 (0.037) & 0.078 & 0.025\\
@@
 \hspace{1em}glmnet-cox & 0.160 (0.036) & 0.788 (0.037) & 0.087 & 0.002\\
-\hspace{1em}aorsf-random & 0.154 (0.044) & 0.780 (0.037) & 0.213 & 0.012\\
+\hspace{1em}aorsf-random & 0.154 (0.044) & 0.780 (0.037) & 1.060 & 0.011\\
 \hspace{1em}cif-standard & 0.128 (0.040) & 0.770 (0.037) & 0.105 & 0.120\\

### 2022-08-30 paper/jmlr/main.Rnw
do 1 more revision before submit

@@
 
+\newcommand{\nope}[1]{}
+
 % Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}
@@
 
-\ShortHeadings{Accelerated oblique random survival forests}{Jaeger et al}
+\ShortHeadings{Accelerated \& interpretable oblique RSFs}{Jaeger et al}
 \firstpageno{1}
@@
 
-\title{Accelerated oblique random survival forests}
+\title{Accelerated and interpretable oblique random survival forests}
 
@@
        \AND
-       \name Matthew Segar \email Matthew.Segar@UTSouthwestern.edu \\
-       \addr Division of Cardiology, Department of Internal Medicine, \\
-       University of Texas Southwestern Medical Center, Dallas
+       \name Matthew Segar \email Matthew.Segar@BCM.edu \\
+       \addr Department of Cardiology \\
+       Texas Heart Institute \\
+       Houston, TX 77030, USA
+       \AND
+       \name Ambarish Pandey \email Ambarish.Pandey@UTSouthwestern.edu \\
+       \addr Division of Cardiology, Department of Internal Medicine \\
+       University of Texas Southwestern Medical Center \\
+       Dallas, TX 75235, USA
        \AND
@@
                    bm_pred_time_viz,
+                   bm_time_viz,
+                   clincalc_r2,
                    data_key,
@@
 
-\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
+\begin{abstract}
 
 	The oblique random survival forest (RSF) is an ensemble supervised learning method for right-censored outcomes.
-Trees in the oblique RSF are grown using linear combinations of predictors to create branches, whereas in the standard RSF a single predictor is used.
-Oblique RSF ensembles often have higher prediction accuracy than standard RSF ensembles, but the additional computational overhead of assessing all possible linear combination of predictors is a severe limitation.
-In addition, few methods have been developed for interpretation of oblique RSF ensembles, and they remain something of a black box compared to their axis-based counterparts.
-In this article, we introduce and evaluate a method to increase computational efficiency of the oblique RSF and a method to estimate importance of individual predictor variables with the oblique RSF.
-Our strategy to reduce computational overhead makes use of Newton-Raphson scoring, a classical optimization technique that we apply to the Cox partial likelihood function within each non-leaf node of decision trees.
-We estimate importance of predictors for the oblique RSF by negating each coefficient used for the given predictor in linear combinations, and then computing the reduction in out-of-bag accuracy.
-In numeric experiments, we find that our implementation of the oblique RSF is over 500 times faster with equivalent discrimination and superior Brier score compared to existing software for oblique RSFs.
-We find in simulation studies that `negation importance' discriminates between signal and noise predictors more reliably than permutation importance, Shapley additive explanations, and a previously introduced technique to measure variable importance with oblique RSFs based on analysis of variance.
-All methods pertaining to oblique RSFs in the current study are available in the \texttt{aorsf} R package.
+Trees in the oblique RSF are grown using linear combinations of predictors, whereas in the standard RSF, a single predictor is used.
+Oblique RSF ensembles have high prediction accuracy, but assessing many linear combinations of predictors induces high computational overhead.
+In addition, few methods have been developed for estimation of variable importance (VI) with oblique RSFs.
+We introduce a method to increase computational efficiency of the oblique RSF and a method to estimate VI with the oblique RSF.
+Our computational approach uses Newton-Raphson scoring in each non-leaf node, We estimate VI by negating each coefficient used for a given predictor in linear combinations, and then computing the reduction in out-of-bag accuracy.
+In benchmarking experiments, we find our implementation of the oblique RSF is hundreds of times faster, with equivalent prediction accuracy, compared to existing software for oblique RSFs.
+We find in simulation studies that `negation VI' discriminates between relevant and irrelevant predictors more accurately than permutation VI, Shapley VI, and a technique to measure VI using analysis of variance.
+All  oblique RSF methods in the current study are available in the \texttt{aorsf} R package.
 
@@
 \begin{keywords}
-  Random Forests, Survival, Efficient, Variable Importance
+Oblique, Survival, Random Forests, Fast, Variable Importance
 \end{keywords}
@@
 
-Oblique trees have at least two notable drawbacks compared to axis-based trees.
+Despite the potential for higher accuracy, oblique trees have at least two notable drawbacks compared to axis-based trees.
 First, finding a locally optimal oblique decision rule may require exponentially more computation than an axis-based rule.
 If $p$ predictors are potentially used to split $n$ observations, up to $\mathcal{O}(n^p)$ oblique splits can be assessed versus $\mathcal{O}(n \cdot p)$ axis-based splits \citep{heath1993induction, murthy1994system}.
-Second, estimating variable importance (VI) using permutation (a standard method for RFs) may be less effective in ensembles of oblique trees, as permuting the values of one predictor may not destabilize decisions that are based on many predictors.
+Second, estimating variable importance (VI) using permutation (a standard method for RFs) may be less effective in ensembles of oblique trees, as permuting the values of one predictor may not destabilize decisions that are based on linear combinations of predictors.
 Although VI is one of the most widely used strategies to interpret random forests \citep{ishwaran2019standard}, few studies have investigated VI for oblique random forests \citep[see][Section~5]{menze2011oblique}, and fewer have investigated VI specifically for the oblique RSF.
 
-This study makes two contributions to oblique RSFs.
-First, we reduce their computational cost (\ie, accelerate them) with a scalable algorithm to identify linear combinations of coefficients.
-In a general benchmark experiment including \Sexpr{n_risk_tasks} risk prediction tasks, we show that accelerated oblique RSFs are roughly 500 times faster with equivalent or superior prediction accuracy compared to existing routines to fit oblique RSFs.
-Second, we improve the interpretability of oblique RSFs with `negation VI', a method to estimate VI that flips the sign of coefficients in linear combinations of predictors instead of permuting predictor values.
-In simulation studies where VI is estimated using permutation, analysis of variance (ANOVA; see \citet{menze2011oblique}), and approximations of Shapley values, we find that negation VI improves the oblique RSF's ability to discriminate between correlated signal and noise variables.
-The accelerated oblique RSF and multiple methods to compute VI for oblique RSFs (permutation, ANOVA, and negation) are available in the \texttt{aorsf} R Package.
-
-% However, there remains considerable potential to improve the RSF in settings where training samples are not large enough to guarantee asymptotic properties or do not align with the conditions required for consistency of the RSF.
-
-% Random forests (RFs) are large sets of de-correlated, randomized decision trees \citep{breiman2001random}, which can be axis based or oblique.Although using oblique rather than axis-based trees to grow a RSF may improve its prediction accuracy,
-
-\section{Related work}
+The aim of this paper is to introduce methodology that improves the computational efficiency and interpretation of oblique RSFs.
+\secref{sec:background} reviews prior studies that have developed methods related to those introduced in the current study.
+In \secref{sec:aorsf}, we reduce the computational cost of oblique RSFs (\ie, accelerate them) with a scalable algorithm to identify linear combinations of coefficients.
+In \secref{sec:negation_vi}, we improve the interpretability of oblique RSFs with `negation VI', a method to estimate VI that flips the sign of coefficients in linear combinations of predictors instead of permuting predictor values.
+We evaluate these methods with general benchmarking experiments and simulation studies in \secref{sec:numeric}.
+In \secref{sec:discussion}, we summarize results from the current study and present ideas connecting the current work to existing frameworks and methods for RSFs that future studies may engage with.
+
+\section{Related work} \label{sec:background}
 
@@
 \end{equation}
-where $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (i.e., those still at risk at time $t_i$), and $j(i)$ is the index of the observation for which an event occurred at time $t_i$.
-Newton Raphson scoring is an extremely fast estimation procedure, and the \texttt{survival} package includes documentation that outlines how to efficiently program it \citep{therneau_survival_2022}.
+where $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (\ie, those still at risk at time $t_i$), and $j(i)$ is the index of the observation for which an event occurred at time $t_i$.
+Newton Raphson scoring is an exceptionally fast estimation procedure, and the \texttt{survival} package \citep{survival} includes documentation that outlines how to efficiently program it \citep{therneau_survival_2022}.
 Briefly, a vector of estimated regression coefficients, $\hat{\beta}$, is updated in each step of the procedure based on its first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
@@
 The code used to run these experiments is available online at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}.
-All analyses were conducted using R version \Sexpr{r_version} with assistance from multiple R packages.
+All analyses were conducted using R version \Sexpr{r_version} and coordinated by the \texttt{targets} R package \citep{targets}.
 To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
 
-\subsection{Benchmark of prediction accuracy and computational efficiency} \label{sec:bm_pred}
-
-The aim of this numeric experiment is to evaluate and compare the accelerated oblique RSF with its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and with other machine learning algorithms for risk prediction.
+\subsection{Benchmark of prediction accuracy} \label{sec:bm_pred}
+
+The aim of this numeric experiment is to evaluate the prediction accuracy of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
 Inferences drawn from this experiment include equivalence and inferiority tests based on Bayesian linear mixed models.
@@
 
-We consider four classes of learners: RSFs (both axis based and oblique), boosting ensembles, regression models, and neural networks (\tabref{tab:learners}).
-For each class, we synchronized shared tuning parameters.
+We consider four classes of learners: RSFs (both axis-based and oblique), boosting ensembles, regression models, and neural networks.
+Specific learners from each class are summarized in \tabref{tab:learners}.
+To facilitate fair comparisons, tuning parameters were harmonized within each class.
 For example, for RSF learners, we set the minimum node size (a parameter shared by all RSF learners) as 10.
-Additionally, for RSF learners, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500.
-For boosting, regression, and neural network learners, nested 10-fold cross-validation was applied to tune relevant model parameters.
+Additionally, for RSF learners, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500 (a common default value for the number of trees).
+For boosting, regression, and neural network learners, nested cross-validation was applied to tune relevant model parameters.
 Specifically, tuning for boosting models included identifying the number of steps to complete.
@@
 
-We use a collection of \Sexpr{n_data_sets} data sets to benchmark the prediction accuracy and computational efficiency of the accelerated ORSF and each of the other learners described in \secref{sec:learners}.
-The number of right-censored outcomes per data set ranged from one to four, and the total number of risk prediction tasks we analyzed was \Sexpr{n_risk_tasks} (\tabrefAppendix{tab:datasets}).
-Across all prediction tasks, the number of observations ranged from \Sexpr{nrow_min} to \Sexpr{nrow_max} (median: \Sexpr{nrow_median}), the number of predictors ranged from \Sexpr{ncol_min} to \Sexpr{ncol_max} (median: \Sexpr{ncol_median}), and the percentage of censored observations ranged from \Sexpr{pcens_min} to \Sexpr{pcens_max} (median: \Sexpr{pcens_median}).
+We used a collection of \Sexpr{n_data_sets} data sets containing a total of \Sexpr{n_risk_tasks} risk prediction tasks (tasks per data set ranged from one to four) to benchmark the accelerated oblique RSF versus other learners.
+Participant-level data from the GUIDE-IT and SPRINT clinical trials and the ARIC, MESA, and JHS community cohort studies was obtained from the National Institute of Health Biologic Specimen and Data Repository Coordinating Center (BioLINCC).
+Designs and protocols for these studies have been made available \citep{aric1989atherosclerosis, bild2002multi, felker2017effect, sprint2015randomized, taylor2005toward}.
+All other datasets were publicly available and obtained through R packages (see Appendix A.1).
+Across all prediction tasks, the number of observations ranged from \Sexpr{nrow_min} to \Sexpr{nrow_max} (median: \Sexpr{nrow_median}), the number of predictors ranged from \Sexpr{ncol_min} to \Sexpr{ncol_max} (median: \Sexpr{ncol_median}), and the percentage of censored observations ranged from \Sexpr{pcens_min} to \Sexpr{pcens_max} (median: \Sexpr{pcens_median}) (\tabrefAppendix{tab:datasets}).
 
@@
 In each run, we used a random sample containing 50\% of the available data for training and the remaining 50\% for testing each of the learners described in \secref{sec:learners}.
-Then, for each learner, we computed the IPA, time-dependent C-statistic, and computational time required to fit a prediction model and compute risk predictions.
-If any learner failed to obtain predictions on any particular split of data\footnote{For example, when the prediction task was to predict risk of death in the ACTG 320 clinical trial (26 events total), some splits did not leave enough events in the training data to fit complex learners such as the neural network}, the results for that split were omitted from downstream analyses.
+Then, for each learner, we computed the IPA and time-dependent C-statistic.
+If any learner failed to obtain predictions on any particular split of data\footnote{For example, when the prediction task was to predict risk of death in the ACTG 320 clinical trial (26 events total), some splits did not leave enough events in the training data to fit complex learners such as neural networks}, the results for that split were omitted from downstream analyses for all learners.
 
@@
 More specifically, we concluded that two learners had practically equivalent IPA or time-dependent C-statistic if there was a 95\% or higher posterior probability that the absolute difference in the relevant metric was less than 1.
-We concluded that one learner was weakly superior when there was $\geq$ 95\% posterior probability that the difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 95\% posterior probability that the difference in the relevant metric was 1 or more.
+We concluded that one learner was weakly superior when there was $\geq$ 95\% posterior probability that the absolute difference in the relevant metric was non-zero, and concluded superiority when when there was $\geq$ 95\% posterior probability that the absolute difference in the relevant metric was 1 or more.
 
 <<>>=
+
+n_tasks_complete <- bm_pred_clean %>%
+  getElement("data") %>%
+  distinct(data, run) %>%
+  nrow()
+
+n_tasks_expected <- max(bm_pred_clean$data$run) *
+  length(unique(bm_pred_clean$data$data))
+
+bm_pred_failed_description <-
+  bm_pred_clean$omit %>%
+  mutate(
+    model = recode(model, !!!deframe(model_key)),
+    data = recode(data, !!!deframe(data_key[,c('data', 'label')]))
+  ) %>%
+  split(f = list(.$model, .$data)) %>%
+  map(
+    ~ glue(
+    "On run {glue_collapse(.x$run, sep = ', ', last = ' and ')} \\
+     for the {.x$data[1]} data, the \\texttt{{{.x$model[1]}}} \\
+     learner encountered an error during its fitting procedure"
+    )
+  ) %>%
+  reduce(paste, sep = '. ')
 
@@
 @
+
+\subsection{Benchmark of variable importance} \label{sec:bm_vi}
+
+The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between relevant and irrelevant variables, where relevance is defined by having a relationship with the simulated outcome.
+We consider methods that are intrinsic to the oblique RF (\eg, ANOVA VI), those that are intrinsic to the RF (\eg, permutation VI), and those that are model-agnostic (\eg, SHAP VI).
+VI methods with unavailable or still developing software were not included.\footnote{Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
+Therefore, it is not incorporated in the current simulation study.}
+
+\subsubsection{Variable importance techniques}
+
+We compute permutation VI for axis based RSFs using the \texttt{randomForestSRC} package.
+We compute ANOVA VI, negation VI, and permutation VI for oblique RSFs using the \texttt{aorsf} package.
+For ANOVA VI, we applied a p-value threshold of 0.01, following the threshold recommended by \citet{menze2011oblique}.
+We compute SHAP VI for boosted tree models using the \texttt{xgboost} package \citep{xgboost}, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
+
+% We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
+
+\subsubsection{Variable types}
+
+We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome on the log-hazard scale. Specifically, \begin{itemize}
+\item \textit{irrelevant} variables had no relationship with the outcome.
+\item \textit{main effect} variables had a linear relationship to the outcome on the log-hazard scale.
+\item \textit{non-linear effect} variables had a non-linear relationship to the outcome.
+A normally distributed variable $x$ was generated with a linear relationship to the outcome on the log-hazard scale, then $\tilde{x} = \text{sin}(a \cdot \pi \cdot x)$ was retained for modeling.
+The constant $a$ varied uniformly from 0.125 to 0.25.
+\item \textit{combination effect} variables were formed by linear combinations of three other variables.
+While their combination was linearly related to the outcome on the log-hazard scale, each of the three variables contributing to the combination had no relation to the outcome.
+\item \textit{interaction effect} variables were related to the outcome by multiplicative interaction with one other variable, which could have been a main effect, non-linear effect, or combination effect variable.
+\end{itemize}
+
+\subsubsection{Simulated data} \label{sec:data_sim}
+
+We initiated each set of simulated data with a random draw of size $n$ from a $p$-dimensional multivariate normal distribution, yielding $n$ observations of $p$ predictors.
+Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
+A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package \citep{simsurv, simsurv_paper}.
+The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
+Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be evaluated based on their ability to detect these effects.
+
+\subsubsection{Parameter specifications}
+
+<<>>=
+
+n_obs <- bm_vi_viz$smry %>%
+  ungroup() %>%
+  distinct(n_obs) %>%
+  drop_na() %>%
+  filter(n_obs > 0) %>%
+  pull(n_obs) %>%
+  glue_collapse(sep = ', ', last = ', and ')
+
+pred_corr <- bm_vi_viz$smry %>%
+  ungroup() %>%
+  distinct(pred_corr_max) %>%
+  drop_na() %>%
+  filter(pred_corr_max < 1) %>%
+  pull(pred_corr_max) %>%
+  glue_collapse(sep = ', ', last = ', and ')
+
+s <- mean_ci(clincalc_r2)*100
+
+clincalc_r2_sexpr <- table_glue(
+  "{s[['y']]} ({s[['ymin']]}, {s[['ymax']]})"
+)
+
+@
+
+Parameters that varied in the current simulation study included the number of observations (\Sexpr{n_obs}) and the absolute value of the maximum correlation between predictors (\Sexpr{pred_corr}).
+Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
+Using this design for simulated data, the Heller explained relative risk (95\% confidence interval) of our covariates was \Sexpr{clincalc_r2_sexpr} \citep{heller2012measure} with 2,500 observations.
+
+\subsubsection{Evaluation of variable importance}
+
+We compared VI techniques based on their discrimination (\ie, C-statistic) between relevant and irrelevant variables.
+Specifically, we generated a binary outcome for each predictor variable based on its relevance (\ie, the binary outcome is 1 if the variable is relevant, 0 otherwise).
+Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic which may be interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
+
+\subsubsection{Results} \label{sec:results_vi}
+
+<<>>=
+
+n_wins_aorsf <- bm_vi_viz %>%
+  getElement('rankings') %>%
+  filter(model == 'aorsf-negate') %>%
+  pull(n_wins)
+
+n_vi_tasks <- sum(bm_vi_viz$rankings$n_wins)
+
+cstat_mean_aorsf <- bm_vi_viz %>%
+  getElement('smry') %>%
+  filter(model == 'aorsf-negate',
+         data == 'Overall_NA_NA') %>%
+  mutate(value = table_value(value * 100)) %>%
+  pull(value)
+
+cstat_mean_anova <- bm_vi_viz %>%
+  getElement('smry') %>%
+  filter(model == 'aorsf-anova',
+         data == 'Overall_NA_NA') %>%
+  mutate(value = table_value(value * 100)) %>%
+  pull(value)
+
+cstat_mean_permute <- bm_vi_viz %>%
+  getElement('smry') %>%
+  filter(model == 'aorsf-permute',
+         data == 'Overall_NA_NA') %>%
+  mutate(value = table_value(value * 100)) %>%
+  pull(value)
+
+cstat_aorsf_won_by <- bm_vi_viz %>%
+  getElement('diffs') %>%
+  filter(data == 'Overall_NA_NA') %>%
+  transmute(percent = table_value(pdiff),
+            absolute = table_value(100*adiff)) %>%
+  as.list()
+
+cstat_vi_second_place <- bm_vi_viz %>%
+  getElement('smry') %>%
+  ungroup() %>%
+  filter(data == 'Overall_NA_NA') %>%
+  arrange(desc(value)) %>%
+  slice(2) %>%
+  transmute(model, value = table_value(100*value)) %>%
+  as.list()
+
+vi_times <- bm_vi_viz$times %>%
+  as_inline('model', 'time') %>%
+  map(as.numeric, unit = 'secs') %>%
+  map(table_value) %>%
+  set_names(str_replace(names(.), '-', '_'))
+
+@
+
+The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = \Sexpr{cstat_mean_aorsf}$), second (\texttt{aorsf-anova}; $C = \Sexpr{cstat_mean_anova}$), and third (\texttt{aorsf-permute}; $C = \Sexpr{cstat_mean_permute}$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in \Sexpr{n_wins_aorsf} out of \Sexpr{n_vi_tasks} VI tasks (Figure \ref{fig:bm_vi_viz}).
+Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
+Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
+Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of \Sexpr{vi_times$aorsf_anova} seconds versus \Sexpr{vi_times$aorsf_negate} and \Sexpr{vi_times$aorsf_permute} seconds, respectively.
+
+<<bm_vi_viz, fig.height=11, fig.width=9, fig.cap="Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
+Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.">>=
+bm_vi_viz$fig
+@
+
+\subsection{Benchmark of computational efficiency}
+
+The aim of this numeric experiment is to evaluate the computational efficiency of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
+
+\subsubsection{Evaluation of computational efficiency}
+
+For each learner discussed in \secref{sec:learners} and for each of the \Sexpr{n_risk_tasks} risk prediction tasks analyzed in \secref{sec:bm_pred}, we tracked the amount of time required to fit a prediction model (including time used to tune parameters) and compute predicted risk.
+
+We also performed more specific benchmarks on the time required to fit 50 trees\footnote{We decided to use 50 trees for this benchmark rather than 500, as using 500 trees caused excessive memory usage and job failure with larger datasets.} using the three fastest random forest R packages, \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger}.
+The learners that represented these R packages, respectively, are \texttt{aorsf-fast}, \texttt{rsf-standard}, and \texttt{rsf-extratrees}.
+We used the simulated data described in \secref{sec:data_sim} with number of observations in the training data ranging from 100 to 21544 and number of predictors ranging from 10 to 1000.
+
+\subsubsection{Results}
 
@@
 
-@
-
-\paragraph{Computational efficiency}
-
-Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 1/2 second longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+ms_diff <- round(abs(times$glmnet_cox$time - times$aorsf_fast$time)*1000)
+
+@
+
+In the analysis of \Sexpr{n_risk_tasks} risk prediction tasks, \texttt{aorsf-fast} was the second fastest learner overall, with an expected model development and risk prediction time about \Sexpr{ms_diff} milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
 Comparing median computing times, \texttt{aorsf-fast} was \Sexpr{times$obliqueRSF_net$ratio} times faster than its predecessor, \texttt{obliqueRSF-net}.
@@
 
-\subsection{Benchmark of variable importance} \label{sec:bm_vi}
-
-The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between variables that do or do not have a relationship with a simulated outcome.
-We consider methods that are intrinsic to the oblique RF (\eg, ANOVA VI), those that are intrinsic to the RF (\eg, permutation VI), and those that are model-agnostic (\eg, SHAP VI).
-VI methods with unavailable or still developing software were not included.\footnote{Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
-Therefore, it is not incorporated in the current simulation study.}
-
-\subsubsection{Variable importance techniques}
-
-We compute permutation VI for axis based RSFs using the \texttt{randomForestSRC} package.
-We compute ANOVA VI, negation VI, and permutation VI for oblique RSFs using the \texttt{aorsf} package.
-For ANOVA VI, we applied a p-value threshold of 0.01, following the threshold recommended by \citet{menze2011oblique}.
-We compute SHAP VI for boosted tree models using the \texttt{xgboost} package, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
-
-% We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
-
-\subsubsection{Variable types}
-
-We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome. Specifically, \begin{itemize}
-\item \textit{irrelevant} variables had no relationship with the outcome.
-\item \textit{main effect} variables had a linear relationship to the outcome.
-\item \textit{non-linear effect} variables had a non-linear relationship to the outcome.
-\item \textit{combination effect} variables were formed by linear combinations of three other variables.
-While their combination was linearly related to the outcome, each of the three variables contributing to the combination had no relation to the outcome.
-\item \textit{interaction effect} variables were related to the outcome by multiplicative interaction with one other variable, which could have been a main effect, non-linear effect, or combination effect variable.
-\end{itemize}
-
-\subsubsection{Simulated data}
-
-We initiated each set of simulated data with a random draw of size $n$ from a $p$-dimensional multivariate normal distribution, yielding $n$ observations of $p$ predictors.
-Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
-A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package.
-The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
-Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be evaluated based on their ability to detect these effects.
-
-\subsubsection{Parameter specifications}
-
-<<>>=
-
-n_obs <- bm_vi_viz$smry %>%
-  ungroup() %>%
-  distinct(n_obs) %>%
-  drop_na() %>%
-  filter(n_obs > 0) %>%
-  pull(n_obs) %>%
-  glue_collapse(sep = ', ', last = ', and ')
-
-pred_corr <- bm_vi_viz$smry %>%
-  ungroup() %>%
-  distinct(pred_corr_max) %>%
-  drop_na() %>%
-  filter(pred_corr_max < 1) %>%
-  pull(pred_corr_max) %>%
-  glue_collapse(sep = ', ', last = ', and ')
-
-@
-
-Parameters that varied in the current simulation study included the number of observations (\Sexpr{n_obs}) and the absolute value of the maximum correlation between predictors (\Sexpr{pred_corr}).
-Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
-
-\subsubsection{Evaluation of variable importance}
-
-We compared VI techniques based on their discrimination (\ie, C-statistic) between relevant and irrelevant variables.
-Specifically, we generated a binary outcome for each predictor variable based on its relevance (\ie, the binary outcome is 1 if the variable is relevant, 0 otherwise).
-Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic which may be interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
-
-\subsubsection{Results} \label{sec:results_vi}
-
-<<>>=
-
-n_wins_aorsf <- bm_vi_viz %>%
-  getElement('rankings') %>%
-  filter(model == 'aorsf-negate') %>%
-  pull(n_wins)
-
-n_vi_tasks <- sum(bm_vi_viz$rankings$n_wins)
-
-cstat_mean_aorsf <- bm_vi_viz %>%
-  getElement('smry') %>%
-  filter(model == 'aorsf-negate',
-         data == 'Overall_NA_NA') %>%
-  mutate(value = table_value(value * 100)) %>%
-  pull(value)
-
-cstat_mean_anova <- bm_vi_viz %>%
-  getElement('smry') %>%
-  filter(model == 'aorsf-anova',
-         data == 'Overall_NA_NA') %>%
-  mutate(value = table_value(value * 100)) %>%
-  pull(value)
-
-cstat_mean_permute <- bm_vi_viz %>%
-  getElement('smry') %>%
-  filter(model == 'aorsf-permute',
-         data == 'Overall_NA_NA') %>%
-  mutate(value = table_value(value * 100)) %>%
-  pull(value)
-
-cstat_aorsf_won_by <- bm_vi_viz %>%
-  getElement('diffs') %>%
-  filter(data == 'Overall_NA_NA') %>%
-  transmute(percent = table_value(pdiff),
-            absolute = table_value(100*adiff)) %>%
-  as.list()
-
-cstat_vi_second_place <- bm_vi_viz %>%
-  getElement('smry') %>%
-  ungroup() %>%
-  filter(data == 'Overall_NA_NA') %>%
-  arrange(desc(value)) %>%
-  slice(2) %>%
-  transmute(model, value = table_value(100*value)) %>%
-  as.list()
-
-vi_times <- bm_vi_viz$times %>%
-  as_inline('model', 'time') %>%
-  map(as.numeric, unit = 'secs') %>%
-  map(table_value) %>%
-  set_names(str_replace(names(.), '-', '_'))
-
-@
-
-The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = \Sexpr{cstat_mean_aorsf}$), second (\texttt{aorsf-anova}; $C = \Sexpr{cstat_mean_anova}$), and third (\texttt{aorsf-permute}; $C = \Sexpr{cstat_mean_permute}$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in \Sexpr{n_wins_aorsf} out of \Sexpr{n_vi_tasks} VI tasks (Figure \ref{fig:bm_vi_viz}).
-Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
-Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
-Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of \Sexpr{vi_times$aorsf_anova} seconds versus \Sexpr{vi_times$aorsf_negate} and \Sexpr{vi_times$aorsf_permute} seconds, respectively.
-
-<<bm_vi_viz, fig.height=11, fig.width=9, fig.cap="Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
-Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.">>=
-bm_vi_viz$fig
-@
-
-\section{Discussion}
+In the analysis of time to fit 50 trees using simulated data, the \texttt{ranger} package exhibited the fastest computation times for samples with 1000 or fewer observations while \texttt{aorsf} and \texttt{randomForestSRC} were more efficient in larger samples.
+In particular, \texttt{aorsf} was substantially faster than both \texttt{ranger} and \texttt{randomForestSRC} with 10 or 100 features and over 1000 observations in the training data (see Figure \ref{fig:bm_time_viz}).
+
+<<bm_time_viz, fig.height=4, fig.width=10, fig.cap="Time, in seconds, to fit an ensemble of 50 survival trees.
+The aorsf package appears to be more efficient in larger samples, particularly when 10 or 100 predictors are present in the training data.
+All three packages appear to scale linearly in computation time with the number of observations in the training data.">>=
+
+bm_time_viz
+
+@
+
+\section{Discussion} \label{sec:discussion}
 
@@
 Thus, allowing the oblique RSF to account for competing risks is a high priority for future studies.
-In addition, missing data are not addressed in the accelerated oblique RSF, and users of the \texttt{aorsf} R package are expected to impute missing values prior to model training and testing.
-However, missing data are common and there are numerous techniques for ensemble tree methods to handle missing data during the tree growing procedure.
-Thus, a second item of high priority for future studies is to develop and evaluate strategies to handle missing data while growing an oblique RSF.
-Last, \citet{cui2017consistency} found that estimating an inverse-probability weighted hazard function at each non-leaf node of a survival tree allows the RSF to converge asymptotically to the true survival function when some variables contribute both to the risk of the event and the risk of censoring, a scenario that is very likely in the analysis of electronic medical records.
-The accelerated oblique RSF could incorporate this splitting technique by using Newton Raphson scoring to fit a model for the censoring distribution and then a weighted model could be fit to the failure distribution.
-This final item has the highest priority, as \citet{cui2017consistency} showed it is a requisite condition for consistency of axis based survival trees in fairly general settings.
+In addition, the current study only considered data without missing values, only evaluated oblique RSFs that applied the log-rank statistic for node splitting, and only considered negation VI estimates based on Harrell's C-statistic.
+Few studies have developed strategies to deal with missing data while growing oblique survival trees.
+Prior studies have found that log-rank tests can be mis-informative when survival curves cross \citep{li2015statistical}, and that Harrell's C-statistic is dependent on the censoring distribution of the outcome \citep{uno2011c}.
+Thus, a second item is to expand the range of options available to users of the \texttt{aorsf} package, enabling them to apply strategies for imputation of missing values and use a broad range of statistical criteria while growing oblique survival trees.
+Last, \citet{cui2017consistency} found that estimating an inverse-probability weighted hazard function at each non-leaf node of a survival tree allows the RSF to converge asymptotically to the true survival function when some variables contribute both to the risk of the event and the risk of censoring, a scenario that is very likely in the analysis of medical data.
+The accelerated oblique RSF could incorporate this splitting technique by using Newton Raphson scoring to fit a model for the censoring distribution after which a weighted model could be fit to the failure distribution.
+This final item has the highest priority, as \citet{cui2017consistency} showed it is a requisite condition for consistency of axis-based survival trees in fairly general settings.
 
@@
 
-\acks{Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine.
+Oblique RSFs have exceptional prediction accuracy and this study has shown how they can be fit with computational efficiency that rivals their axis-based counterparts.
+We have also introduced a general and flexible method to estimate VI with oblique RFs, and demonstrated its effectiveness specifically for the oblique RSF.
+Code used for the current study is available at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}, and the \texttt{aorsf} package is available at \href{https://github.com/bcjaeger/aorsf}{https://github.com/bcjaeger/aorsf}.
+
+\subsection*{Acknowledgements}
+
+Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine.
 The project described was supported by the National Center for Advancing Translational Sciences (NCATS), National Institutes of Health, through Grant Award Number UL1TR001420.
-The content is solely the responsibility of the authors and does not necessarily represent the official views of the NIH.}
+The content is solely the responsibility of the authors and does not necessarily represent the official views of the NIH.
+Dr.
+Pajewski was supported by grant number P30AG021332 from the National Institutes of Health, while Dr.
+Speiser was supported by K25AG068253.
 
@@
   ungroup()
+@
+
+\begin{enumerate}
+
+<<results='asis'>>=
+
+data_key_tbl %>%
+  mutate(
+    source = if_else(
+      is.na(rpack),
+      'BioLINCC',
+      paste0('the \\texttt{', rpack, '} R package \\citep{', rpack, '}'))
+  ) %>%
+  glue_data(" \\item The ``{label}'' data \\citep{{{cite}}} were obtained from {source}") %>%
+  unique() %>%
+  paste(collapse = '. \n') %>%
+  # removes just the first occurrence, which is not needed.
+  str_remove(pattern = stringr::fixed('\\citep{censored}')) %>%
+  paste0(".") %>%
+  cat()
+
+@
+
+\end{enumerate}
+
+<<>>=
 

### 2022-08-30 paper/jmlr/main.tex
do 1 more revision before submit

@@
 
-Oblique trees have at least two notable drawbacks compared to axis-based trees.
+Despite the potential for higher accuracy, oblique trees have at least two notable drawbacks compared to axis-based trees.
 First, finding a locally optimal oblique decision rule may require exponentially more computation than an axis-based rule.
 If $p$ predictors are potentially used to split $n$ observations, up to $\mathcal{O}(n^p)$ oblique splits can be assessed versus $\mathcal{O}(n \cdot p)$ axis-based splits \citep{heath1993induction, murthy1994system}.
-Second, estimating variable importance (VI) using permutation (a standard method for RFs) may be less effective in ensembles of oblique trees, as permuting the values of one predictor may not destabilize decisions that are based on many predictors.
+Second, estimating variable importance (VI) using permutation (a standard method for RFs) may be less effective in ensembles of oblique trees, as permuting the values of one predictor may not destabilize decisions that are based on linear combinations of predictors.
 Although VI is one of the most widely used strategies to interpret random forests \citep{ishwaran2019standard}, few studies have investigated VI for oblique random forests \citep[see][Section~5]{menze2011oblique}, and fewer have investigated VI specifically for the oblique RSF.
 
-This study makes two contributions to oblique RSFs.
-First, we reduce their computational cost (\ie, accelerate them) with a scalable algorithm to identify linear combinations of coefficients.
-In a general benchmark experiment including 30 risk prediction tasks, we show that accelerated oblique RSFs are roughly 500 times faster with equivalent or superior prediction accuracy compared to existing routines to fit oblique RSFs.
-Second, we improve the interpretability of oblique RSFs with `negation VI', a method to estimate VI that flips the sign of coefficients in linear combinations of predictors instead of permuting predictor values.
-In simulation studies where VI is estimated using permutation, analysis of variance (ANOVA; see \citet{menze2011oblique}), and approximations of Shapley values, we find that negation VI improves the oblique RSF's ability to discriminate between correlated signal and noise variables.
-The accelerated oblique RSF and multiple methods to compute VI for oblique RSFs (permutation, ANOVA, and negation) are available in the \texttt{aorsf} R Package.
-
-% However, there remains considerable potential to improve the RSF in settings where training samples are not large enough to guarantee asymptotic properties or do not align with the conditions required for consistency of the RSF.
-
-% Random forests (RFs) are large sets of de-correlated, randomized decision trees \citep{breiman2001random}, which can be axis based or oblique.Although using oblique rather than axis-based trees to grow a RSF may improve its prediction accuracy,
-
-\section{Related work}
+The aim of this paper is to introduce methodology that improves the computational efficiency and interpretation of oblique RSFs.
+\secref{sec:background} reviews prior studies that have developed methods related to those introduced in the current study.
+In \secref{sec:aorsf}, we reduce the computational cost of oblique RSFs (\ie, accelerate them) with a scalable algorithm to identify linear combinations of coefficients.
+In \secref{sec:negation_vi}, we improve the interpretability of oblique RSFs with `negation VI', a method to estimate VI that flips the sign of coefficients in linear combinations of predictors instead of permuting predictor values.
+We evaluate these methods with general benchmarking experiments and simulation studies in \secref{sec:numeric}.
+In \secref{sec:discussion}, we summarize results from the current study and present ideas connecting the current work to existing frameworks and methods for RSFs that future studies may engage with.
+
+\section{Related work} \label{sec:background}
 
@@
 The code used to run these experiments is available online at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}.
-All analyses were conducted using R version 4.1.3 with assistance from multiple R packages.
+All analyses were conducted using R version 4.1.3 and coordinated by the \texttt{targets} R package \citep{targets}.
 To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
 
-\subsection{Benchmark of prediction accuracy and computational efficiency} \label{sec:bm_pred}
-
-The aim of this numeric experiment is to evaluate and compare the accelerated oblique RSF with its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and with other machine learning algorithms for risk prediction.
+\subsection{Benchmark of prediction accuracy} \label{sec:bm_pred}
+
+The aim of this numeric experiment is to evaluate the prediction accuracy of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
 Inferences drawn from this experiment include equivalence and inferiority tests based on Bayesian linear mixed models.
@@
 
-We use a collection of 17 data sets to benchmark the prediction accuracy and computational efficiency of the accelerated ORSF and each of the other learners described in \secref{sec:learners}.
-The number of right-censored outcomes per data set ranged from one to four, and the total number of risk prediction tasks we analyzed was 30 (\tabrefAppendix{tab:datasets}).
-Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 1,807.5), the number of predictors ranged from 7 to 1,692 (median: 32.5), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 78.1).
+We used a collection of 21 data sets containing a total of 35 risk prediction tasks (tasks per data set ranged from one to four) to benchmark the accelerated oblique RSF versus other learners.
+Participant-level data from the GUIDE-IT and SPRINT clinical trials and the ARIC, MESA, and JHS community cohort studies was obtained from the National Institute of Health Biologic Specimen and Data Repository Coordinating Center (BioLINCC).
+Designs and protocols for these studies have been made available \citep{aric1989atherosclerosis, bild2002multi, felker2017effect, sprint2015randomized, taylor2005toward}.
+All other datasets were publicly available and obtained through R packages (see Appendix A.1).
+Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 1,384), the number of predictors ranged from 7 to 1,692 (median: 41), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 78.1) (\tabrefAppendix{tab:datasets}).
 
@@
 
-For each risk prediction task, we completed 22 runs of Monte-Carlo cross validation.
+For each risk prediction task, we completed 25 runs of Monte-Carlo cross validation.
 In each run, we used a random sample containing 50\% of the available data for training and the remaining 50\% for testing each of the learners described in \secref{sec:learners}.
-Then, for each learner, we computed the IPA, time-dependent C-statistic, and computational time required to fit a prediction model and compute risk predictions.
-If any learner failed to obtain predictions on any particular split of data\footnote{For example, when the prediction task was to predict risk of death in the ACTG 320 clinical trial (26 events total), some splits did not leave enough events in the training data to fit complex learners such as the neural network}, the results for that split were omitted from downstream analyses.
+Then, for each learner, we computed the IPA and time-dependent C-statistic.
+If any learner failed to obtain predictions on any particular split of data\footnote{For example, when the prediction task was to predict risk of death in the ACTG 320 clinical trial (26 events total), some splits did not leave enough events in the training data to fit complex learners such as neural networks}, the results for that split were omitted from downstream analyses for all learners.
 
@@
 
-After collecting data from 22 replications of Monte-Carlo cross validation for the 14 learners in all 30 risk prediction tasks, we analyzed the resulting 9,240 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
+After collecting data from 25 replications of Monte-Carlo cross validation for the 14 learners in all 35 risk prediction tasks, we analyzed the resulting 12,250 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
 Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using Bayesian models.
@@
 A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all}.
+In total, 871 out of 875 Monte-Carlo cross validation runs were completed.
+On run 13, 18, 24 and 25 for the ACTG 320 data, the \texttt{nn-cox} learner encountered an error during its fitting procedure.
 
@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 16 out of 30 risk prediction tasks, with an overall mean IPA of 13.6 (Figure \ref{fig:bm_pred_viz_ibs}).
-Compared to the learner with the second highest mean IPA (\texttt{rsf-standard}), \texttt{aorsf-fast}'s mean was 1.32 points higher, a relative increase of 10.7\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.97, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.79 (versus \texttt{rsf-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 20 out of 35 risk prediction tasks, with an overall mean IPA of 12.6 (Figure \ref{fig:bm_pred_viz_ibs}).
+Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.35 points higher, a relative increase of 12.0\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.86 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
 
@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 10 out of 30 risk prediction tasks, with an overall mean of 77.6 (Figure \ref{fig:bm_pred_viz_cstat}).
-Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.664 points higher, a relative increase of 0.864\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was $>$ 0.999, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.19 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 10 out of 35 risk prediction tasks, with an overall mean of 77.2 (Figure \ref{fig:bm_pred_viz_cstat}).
+Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.685 points higher, a relative increase of 0.896\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was $>$ 0.999, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.18 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
 
@@
 
-\paragraph{Computational efficiency}
-
-Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 1/2 second longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
-Comparing median computing times, \texttt{aorsf-fast} was 525.2 times faster than its predecessor, \texttt{obliqueRSF-net}.
-In addition, \texttt{aorsf-fast} was 20.5, 4.27, and 2.79 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
+\subsection{Benchmark of variable importance} \label{sec:bm_vi}
+
+The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between relevant and irrelevant variables, where relevance is defined by having a relationship with the simulated outcome.
+We consider methods that are intrinsic to the oblique RF (\eg, ANOVA VI), those that are intrinsic to the RF (\eg, permutation VI), and those that are model-agnostic (\eg, SHAP VI).
+VI methods with unavailable or still developing software were not included.\footnote{Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
+Therefore, it is not incorporated in the current simulation study.}
+
+\subsubsection{Variable importance techniques}
+
+We compute permutation VI for axis based RSFs using the \texttt{randomForestSRC} package.
+We compute ANOVA VI, negation VI, and permutation VI for oblique RSFs using the \texttt{aorsf} package.
+For ANOVA VI, we applied a p-value threshold of 0.01, following the threshold recommended by \citet{menze2011oblique}.
+We compute SHAP VI for boosted tree models using the \texttt{xgboost} package \citep{xgboost}, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
+
+% We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
+
+\subsubsection{Variable types}
+
+We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome on the log-hazard scale. Specifically, \begin{itemize}
+\item \textit{irrelevant} variables had no relationship with the outcome.
+\item \textit{main effect} variables had a linear relationship to the outcome on the log-hazard scale.
+\item \textit{non-linear effect} variables had a non-linear relationship to the outcome.
+A normally distributed variable $x$ was generated with a linear relationship to the outcome on the log-hazard scale, then $\tilde{x} = \text{sin}(a \cdot \pi \cdot x)$ was retained for modeling.
+The constant $a$ varied uniformly from 0.125 to 0.25.
+\item \textit{combination effect} variables were formed by linear combinations of three other variables.
+While their combination was linearly related to the outcome on the log-hazard scale, each of the three variables contributing to the combination had no relation to the outcome.
+\item \textit{interaction effect} variables were related to the outcome by multiplicative interaction with one other variable, which could have been a main effect, non-linear effect, or combination effect variable.
+\end{itemize}
+
+\subsubsection{Simulated data} \label{sec:data_sim}
+
+We initiated each set of simulated data with a random draw of size $n$ from a $p$-dimensional multivariate normal distribution, yielding $n$ observations of $p$ predictors.
+Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
+A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package \citep{simsurv, simsurv_paper}.
+The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
+Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be evaluated based on their ability to detect these effects.
+
+\subsubsection{Parameter specifications}
+
+Parameters that varied in the current simulation study included the number of observations (500, 1000, and 2500) and the absolute value of the maximum correlation between predictors (0.3, 0.15, and 0).
+Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
+Using this design for simulated data, the Heller explained relative risk (95\% confidence interval) of our covariates was 88.4 (88.1, 88.7) \citep{heller2012measure} with 2,500 observations.
+
+\subsubsection{Evaluation of variable importance}
+
+We compared VI techniques based on their discrimination (\ie, C-statistic) between relevant and irrelevant variables.
+Specifically, we generated a binary outcome for each predictor variable based on its relevance (\ie, the binary outcome is 1 if the variable is relevant, 0 otherwise).
+Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic which may be interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
+
+\subsubsection{Results} \label{sec:results_vi}
+
+The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = 75.9$), second (\texttt{aorsf-anova}; $C = 73.9$), and third (\texttt{aorsf-permute}; $C = 73.2$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in 26 out of 36 VI tasks (Figure \ref{fig:bm_vi_viz}).
+Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
+Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
+Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of 2.88 seconds versus 20.4 and 21.8 seconds, respectively.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_vi_viz-1} \caption[Concordance statistic for assigning higher importance to relevant versus irrelevant variables]{Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
+Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.}\label{fig:bm_vi_viz}
+\end{figure}
+
+\end{knitrout}
+
+\subsection{Benchmark of computational efficiency}
+
+The aim of this numeric experiment is to evaluate the computational efficiency of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
+
+\subsubsection{Evaluation of computational efficiency}
+
+For each learner discussed in \secref{sec:learners} and for each of the 35 risk prediction tasks analyzed in \secref{sec:bm_pred}, we tracked the amount of time required to fit a prediction model (including time used to tune parameters) and compute predicted risk.
+
+We also performed more specific benchmarks on the time required to fit 50 trees\footnote{We decided to use 50 trees for this benchmark rather than 500, as using 500 trees caused excessive memory usage and job failure with larger datasets.} using the three fastest random forest R packages, \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger}.
+The learners that represented these R packages, respectively, are \texttt{aorsf-fast}, \texttt{rsf-standard}, and \texttt{rsf-extratrees}.
+We used the simulated data described in \secref{sec:data_sim} with number of observations in the training data ranging from 100 to 21544 and number of predictors ranging from 10 to 1000.
+
+\subsubsection{Results}
+
+In the analysis of 35 risk prediction tasks, \texttt{aorsf-fast} was the second fastest learner overall, with an expected model development and risk prediction time about 385 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+Comparing median computing times, \texttt{aorsf-fast} was 379.8 times faster than its predecessor, \texttt{obliqueRSF-net}.
+In addition, \texttt{aorsf-fast} was 16.1, 1.55, and 2.66 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
 
@@
 
-\subsection{Benchmark of variable importance} \label{sec:bm_vi}
-
-The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between variables that do or do not have a relationship with a simulated outcome.
-We consider methods that are intrinsic to the oblique RF (\eg, ANOVA VI), those that are intrinsic to the RF (\eg, permutation VI), and those that are model-agnostic (\eg, SHAP VI).
-VI methods with unavailable or still developing software were not included.\footnote{Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
-Therefore, it is not incorporated in the current simulation study.}
-
-\subsubsection{Variable importance techniques}
-
-We compute permutation VI for axis based RSFs using the \texttt{randomForestSRC} package.
-We compute ANOVA VI, negation VI, and permutation VI for oblique RSFs using the \texttt{aorsf} package.
-For ANOVA VI, we applied a p-value threshold of 0.01, following the threshold recommended by \citet{menze2011oblique}.
-We compute SHAP VI for boosted tree models using the \texttt{xgboost} package, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
-
-% We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
-
-\subsubsection{Variable types}
-
-We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome. Specifically, \begin{itemize}
-\item \textit{irrelevant} variables had no relationship with the outcome.
-\item \textit{main effect} variables had a linear relationship to the outcome.
-\item \textit{non-linear effect} variables had a non-linear relationship to the outcome.
-\item \textit{combination effect} variables were formed by linear combinations of three other variables.
-While their combination was linearly related to the outcome, each of the three variables contributing to the combination had no relation to the outcome.
-\item \textit{interaction effect} variables were related to the outcome by multiplicative interaction with one other variable, which could have been a main effect, non-linear effect, or combination effect variable.
-\end{itemize}
-
-\subsubsection{Simulated data}
-
-We initiated each set of simulated data with a random draw of size $n$ from a $p$-dimensional multivariate normal distribution, yielding $n$ observations of $p$ predictors.
-Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
-A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package.
-The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
-Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be evaluated based on their ability to detect these effects.
-
-\subsubsection{Parameter specifications}
-
-Parameters that varied in the current simulation study included the number of observations (500, 1000, and 2500) and the absolute value of the maximum correlation between predictors (0.3, 0.15, and 0).
-Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
-
-\subsubsection{Evaluation of variable importance}
-
-We compared VI techniques based on their discrimination (\ie, C-statistic) between relevant and irrelevant variables.
-Specifically, we generated a binary outcome for each predictor variable based on its relevance (\ie, the binary outcome is 1 if the variable is relevant, 0 otherwise).
-Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic which may be interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
-
-\subsubsection{Results} \label{sec:results_vi}
-
-The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = 76.0$), second (\texttt{aorsf-anova}; $C = 74.0$), and third (\texttt{aorsf-permute}; $C = 73.3$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in 27 out of 36 VI tasks (Figure \ref{fig:bm_vi_viz}).
-Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
-Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
-Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of 1.34 seconds versus 12.3 and 14.1 seconds, respectively.
+In the analysis of time to fit 50 trees using simulated data, the \texttt{ranger} package exhibited the fastest computation times for samples with 1000 or fewer observations while \texttt{aorsf} and \texttt{randomForestSRC} were more efficient in larger samples.
+In particular, \texttt{aorsf} was substantially faster than both \texttt{ranger} and \texttt{randomForestSRC} with 10 or 100 features and over 1000 observations in the training data (see Figure \ref{fig:bm_time_viz}).
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/bm_vi_viz-1} \caption[Concordance statistic for assigning higher importance to relevant versus irrelevant variables]{Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
-Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.}\label{fig:bm_vi_viz}
+\includegraphics[width=\maxwidth]{figure/bm_time_viz-1} \caption[Time, in seconds, to fit an ensemble of 50 survival trees]{Time, in seconds, to fit an ensemble of 50 survival trees.
+The aorsf package appears to be more efficient in larger samples, particularly when 10 or 100 predictors are present in the training data.
+All three packages appear to scale linearly in computation time with the number of observations in the training data.}\label{fig:bm_time_viz}
 \end{figure}
@@
 Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
-In numeric experiments, we found that that \texttt{aorsf-fast} is over 500 times faster and just as accurate in risk prediction tasks compared to its predecessor, \texttt{obliqueRSF-net}.
+In numeric experiments, we found that that \texttt{aorsf-fast} is approximately 379.8 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
 We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
-Overall, we found that estimating VI using negation instead of ANOVA increased the C-statistic for ranking a relevant variable higher than an irrelevant variable by 2.00, a relative increase of 2.70\%.
+Overall, we found that estimating VI using negation instead of ANOVA increased the C-statistic for ranking a relevant variable higher than an irrelevant variable by 2.05, a relative increase of 2.78\%.
 
@@
 \setcounter{table}{0}
+
+\subsection*{Data sources}
+
+\begin{enumerate}
+
+ \item The ``VA lung cancer trial'' data \citep{kalbfleisch2011statistical} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
+ \item The ``Colon cancer'' data \citep{moertel1995fluorouracil} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``Primary biliary cholangitis'' data \citep{therneau2000cox} were obtained from the \texttt{aorsf} R package \citep{aorsf}. 
+ \item The ``Movies released in 2015-2018'' data  were obtained from the \texttt{censored} R package \citep{censored}. 
+ \item The ``GBSG II'' data \citep{schumacher1994rauschecker} were obtained from the \texttt{TH.data} R package \citep{TH.data}. 
+ \item The ``Systolic Heart Failure'' data \citep{hsich2011identifying} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
+ \item The ``Serum free light chain'' data \citep{dispenzieri2012use, kyle2006prevalence} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``Non-alcohol fatty liver disease'' data \citep{allen2018nonalcoholic} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``Rotterdam tumor bank'' data \citep{royston2013external} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``ACTG 320'' data \citep{hosmer2002applied} were obtained from the \texttt{mlr3proba} R package \citep{mlr3proba}. 
+ \item The ``GUIDE-IT'' data \citep{felker2017effect} were obtained from BioLINCC. 
+ \item The ``Early breast cancer'' data \citep{desmedt2011multifactorial, hatzis2011genomic, ternes2017identification} were obtained from the \texttt{biospear} R package \citep{biospear}. 
+ \item The ``SPRINT'' data \citep{sprint2015randomized} were obtained from BioLINCC. 
+ \item The ``NKI 70 gene signature'' data \citep{van2002gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}. 
+ \item The ``Lung cancer'' data \citep{director2008gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}. 
+ \item The ``NCCTG Lung Cancer'' data \citep{loprinzi1994prospective} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``FCL'' data \citep{pintilie2006competing} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
+ \item The ``Monoclonal gammopathy'' data \citep{kyle2002long} were obtained from the \texttt{survival} R package \citep{survival}. 
+ \item The ``MESA'' data \citep{bild2002multi} were obtained from BioLINCC. 
+ \item The ``ARIC'' data \citep{aric1989atherosclerosis} were obtained from BioLINCC. 
+ \item The ``JHS'' data \citep{taylor2005toward} were obtained from BioLINCC.
+
+\end{enumerate}
 
@@
 \begin{longtable}[t]{lcclcc}
-\caption{\label{tab:unnamed-chunk-8}Data sets used for numeric experiments \label{tab:datasets}}\\
+\caption{\label{tab:unnamed-chunk-10}Data sets used for numeric experiments \label{tab:datasets}}\\
 \toprule
@@
 \multirow{-2}{*}{\raggedright\arraybackslash SPRINT} & \multirow{-2}{*}{\centering\arraybackslash 9,361} & \multirow{-2}{*}{\centering\arraybackslash 174} & Death & 1,644 & 82.4\\
+\cmidrule{1-6}\pagebreak[0]
+NKI 70 gene signature & 144 & 77 & Death Or Metastasis & 48 & 66.7\\
+\cmidrule{1-6}\pagebreak[0]
+Lung cancer & 442 & 24 & Death & 236 & 46.6\\
+\cmidrule{1-6}\pagebreak[0]
+NCCTG Lung Cancer & 228 & 9 & Death & 165 & 27.6\\
 \cmidrule{1-6}\pagebreak[0]
@@
 \begin{longtable}[t]{lcccc}
-\caption{\label{tab:unnamed-chunk-9}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 31 risk prediction tasks.\label{tab:bm_pred_all}}\\
+\caption{\label{tab:unnamed-chunk-11}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 35 risk prediction tasks.\label{tab:bm_pred_all}}\\
 \toprule
@@
 \hline
-\hspace{1em}aorsf-fast & 0.136 (0.113) & 0.776 (0.072) & 0.721 & 0.174\\
-\hspace{1em}aorsf-cph & 0.136 (0.113) & 0.775 (0.071) & 1.867 & 0.169\\
-\hspace{1em}aorsf-net & 0.129 (0.128) & 0.771 (0.075) & 131.131 & 0.167\\
-\hspace{1em}rsf-standard & 0.123 (0.118) & 0.761 (0.076) & 2.116 & 0.278\\
-\hspace{1em}cif-standard & 0.123 (0.101) & 0.769 (0.071) & 4.312 & 14.590\\
-\hspace{1em}obliqueRSF-net & 0.122 (0.087) & 0.775 (0.072) & 379.917 & 23.183\\
-\hspace{1em}cif-rotate & 0.121 (0.130) & 0.759 (0.082) & 39.895 & 8.598\\
-\hspace{1em}glmnet-cox & 0.119 (0.124) & 0.763 (0.075) & 0.433 & 0.004\\
-\hspace{1em}ranger-extratrees & 0.107 (0.088) & 0.765 (0.067) & 1.986 & 1.289\\
-\hspace{1em}cif-extension & 0.102 (0.096) & 0.764 (0.072) & 22.524 & 7.926\\
-\hspace{1em}aorsf-random & 0.097 (0.084) & 0.744 (0.064) & 2.201 & 0.169\\
-\hspace{1em}xgboost-cox & 0.074 (0.104) & 0.759 (0.089) & 4.384 & 0.004\\
-\hspace{1em}nn-cox & 0.050 (0.109) & 0.652 (0.138) & 16.298 & 3.578\\
-\hspace{1em}xgboost-aft & --- & 0.768 (0.075) & 14.513 & 0.007\\
+\hspace{1em}aorsf-fast & 0.126 (0.110) & 0.772 (0.071) & 0.620 & 0.145\\
+\hspace{1em}aorsf-cph & 0.126 (0.109) & 0.771 (0.070) & 1.912 & 0.148\\
+\hspace{1em}aorsf-net & 0.124 (0.112) & 0.771 (0.071) & 78.512 & 0.143\\
+\hspace{1em}obliqueRSF-net & 0.113 (0.085) & 0.771 (0.071) & 300.393 & 18.803\\
+\hspace{1em}cif-standard & 0.113 (0.098) & 0.765 (0.071) & 4.293 & 6.044\\
+\hspace{1em}rsf-standard & 0.113 (0.114) & 0.755 (0.075) & 2.099 & 0.199\\
+\hspace{1em}cif-rotate & 0.112 (0.124) & 0.755 (0.081) & 37.695 & 8.348\\
+\hspace{1em}glmnet-cox & 0.108 (0.119) & 0.757 (0.077) & 0.473 & 0.003\\
+\hspace{1em}ranger-extratrees & 0.099 (0.085) & 0.762 (0.067) & 0.878 & 1.156\\
+\hspace{1em}cif-extension & 0.095 (0.092) & 0.761 (0.072) & 22.321 & 6.949\\
+\hspace{1em}aorsf-random & 0.090 (0.081) & 0.741 (0.063) & 1.790 & 0.141\\
+\hspace{1em}xgboost-cox & 0.064 (0.100) & 0.749 (0.094) & 3.973 & 0.004\\
+\hspace{1em}nn-cox & 0.047 (0.108) & 0.656 (0.138) & 15.352 & 2.060\\
+\hspace{1em}xgboost-aft & --- & 0.762 (0.076) & 13.060 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}ranger-extratrees & 0.027 (0.017) & 0.736 (0.036) & 0.052 & 0.145\\
-\hspace{1em}aorsf-random & 0.027 (0.022) & 0.741 (0.035) & 0.408 & 0.035\\
-\hspace{1em}obliqueRSF-net & 0.026 (0.023) & 0.741 (0.038) & 26.825 & 15.427\\
-\hspace{1em}cif-standard & 0.023 (0.032) & 0.740 (0.041) & 1.062 & 4.542\\
-\hspace{1em}aorsf-cph & 0.023 (0.030) & 0.744 (0.039) & 0.436 & 0.035\\
-\hspace{1em}cif-extension & 0.023 (0.016) & 0.719 (0.040) & 9.253 & 4.180\\
-\hspace{1em}aorsf-fast & 0.022 (0.029) & 0.737 (0.041) & 0.142 & 0.034\\
-\hspace{1em}aorsf-net & 0.016 (0.035) & 0.738 (0.040) & 18.751 & 0.036\\
-\hspace{1em}glmnet-cox & 0.015 (0.029) & 0.742 (0.035) & 0.174 & 0.002\\
-\hspace{1em}rsf-standard & 0.005 (0.041) & 0.727 (0.044) & 0.149 & 0.059\\
-\hspace{1em}cif-rotate & 0.002 (0.042) & 0.729 (0.040) & 15.116 & 3.882\\
-\hspace{1em}nn-cox & -0.001 (0.017) & 0.636 (0.114) & 10.863 & 0.537\\
-\hspace{1em}xgboost-cox & -0.003 (0.046) & 0.747 (0.031) & 3.788 & 0.003\\
-\hspace{1em}xgboost-aft & --- & 0.734 (0.034) & 9.657 & 0.006\\
+\hspace{1em}aorsf-random & 0.028 (0.022) & 0.748 (0.038) & 0.382 & 0.034\\
+\hspace{1em}ranger-extratrees & 0.028 (0.017) & 0.740 (0.036) & 0.064 & 0.146\\
+\hspace{1em}obliqueRSF-net & 0.027 (0.022) & 0.746 (0.038) & 25.980 & 15.236\\
+\hspace{1em}aorsf-cph & 0.025 (0.029) & 0.751 (0.042) & 0.424 & 0.033\\
+\hspace{1em}cif-standard & 0.024 (0.031) & 0.744 (0.040) & 1.771 & 4.657\\
+\hspace{1em}aorsf-fast & 0.024 (0.029) & 0.746 (0.043) & 0.144 & 0.032\\
+\hspace{1em}cif-extension & 0.023 (0.015) & 0.722 (0.038) & 9.848 & 4.083\\
+\hspace{1em}aorsf-net & 0.019 (0.034) & 0.745 (0.042) & 17.078 & 0.034\\
+\hspace{1em}glmnet-cox & 0.016 (0.030) & 0.746 (0.037) & 0.179 & 0.003\\
+\hspace{1em}rsf-standard & 0.005 (0.041) & 0.730 (0.042) & 0.192 & 0.061\\
+\hspace{1em}cif-rotate & 0.004 (0.040) & 0.731 (0.038) & 16.095 & 3.888\\
+\hspace{1em}xgboost-cox & 0.000 (0.044) & 0.751 (0.033) & 3.704 & 0.003\\
+\hspace{1em}nn-cox & -0.001 (0.008) & 0.549 (0.125) & 11.075 & 0.668\\
+\hspace{1em}xgboost-aft & --- & 0.737 (0.035) & 10.015 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.007 (0.012) & 0.824 (0.053) & 8.814 & 10.613\\
-\hspace{1em}aorsf-cph & 0.006 (0.018) & 0.823 (0.061) & 0.351 & 0.020\\
-\hspace{1em}aorsf-fast & 0.006 (0.019) & 0.829 (0.057) & 0.086 & 0.020\\
-\hspace{1em}aorsf-random & 0.004 (0.015) & 0.791 (0.075) & 0.225 & 0.023\\
-\hspace{1em}cif-extension & 0.000 (0.020) & 0.764 (0.067) & 8.850 & 3.772\\
-\hspace{1em}ranger-extratrees & 0.000 (0.019) & 0.776 (0.070) & 0.041 & 0.124\\
-\hspace{1em}xgboost-cox & -0.004 (0.004) & 0.500 (0.000) & 0.111 & 0.002\\
-\hspace{1em}nn-cox & -0.005 (0.004) & 0.521 (0.095) & 10.159 & 0.520\\
-\hspace{1em}cif-standard & -0.006 (0.025) & 0.780 (0.063) & 1.117 & 4.526\\
-\hspace{1em}aorsf-net & -0.006 (0.033) & 0.808 (0.068) & 14.237 & 0.023\\
-\hspace{1em}rsf-standard & -0.033 (0.052) & 0.776 (0.075) & 0.094 & 0.036\\
-\hspace{1em}cif-rotate & -0.040 (0.048) & 0.702 (0.090) & 13.345 & 3.292\\
-\hspace{1em}glmnet-cox & -0.065 (0.098) & 0.747 (0.100) & 0.276 & 0.002\\
-\hspace{1em}xgboost-aft & --- & 0.773 (0.072) & 9.772 & 0.006\\
+\hspace{1em}obliqueRSF-net & 0.007 (0.011) & 0.823 (0.052) & 8.869 & 11.004\\
+\hspace{1em}aorsf-cph & 0.007 (0.018) & 0.821 (0.060) & 0.340 & 0.018\\
+\hspace{1em}aorsf-fast & 0.005 (0.019) & 0.827 (0.056) & 0.086 & 0.018\\
+\hspace{1em}aorsf-random & 0.005 (0.014) & 0.788 (0.074) & 0.221 & 0.022\\
+\hspace{1em}cif-extension & 0.001 (0.020) & 0.765 (0.066) & 8.436 & 3.493\\
+\hspace{1em}ranger-extratrees & 0.001 (0.019) & 0.777 (0.069) & 0.044 & 0.138\\
+\hspace{1em}xgboost-cox & -0.004 (0.004) & 0.500 (0.000) & 0.119 & 0.002\\
+\hspace{1em}nn-cox & -0.004 (0.004) & 0.508 (0.119) & 10.867 & 0.518\\
+\hspace{1em}cif-standard & -0.005 (0.025) & 0.781 (0.062) & 1.726 & 4.648\\
+\hspace{1em}aorsf-net & -0.005 (0.032) & 0.806 (0.067) & 13.309 & 0.022\\
+\hspace{1em}rsf-standard & -0.031 (0.051) & 0.776 (0.073) & 0.090 & 0.035\\
+\hspace{1em}cif-rotate & -0.037 (0.049) & 0.707 (0.090) & 13.920 & 3.444\\
+\hspace{1em}glmnet-cox & -0.065 (0.095) & 0.746 (0.098) & 0.281 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.773 (0.071) & 9.190 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.157 (0.007) & 0.810 (0.007) & 4.561 & 1.355\\
-\hspace{1em}aorsf-cph & 0.153 (0.007) & 0.809 (0.007) & 14.677 & 1.379\\
-\hspace{1em}aorsf-net & 0.153 (0.007) & 0.810 (0.007) & 511.536 & 1.484\\
-\hspace{1em}rsf-standard & 0.151 (0.007) & 0.801 (0.007) & 9.099 & 1.077\\
-\hspace{1em}obliqueRSF-net & 0.144 (0.005) & 0.812 (0.007) & 2814.937 & 353.143\\
-\hspace{1em}cif-standard & 0.132 (0.005) & 0.810 (0.007) & 70.476 & 358.500\\
-\hspace{1em}glmnet-cox & 0.129 (0.012) & 0.796 (0.008) & 1.547 & 0.011\\
-\hspace{1em}nn-cox & 0.122 (0.014) & 0.795 (0.007) & 52.898 & 105.741\\
-\hspace{1em}ranger-extratrees & 0.112 (0.005) & 0.796 (0.009) & 305.330 & 66.584\\
-\hspace{1em}cif-rotate & 0.104 (0.004) & 0.784 (0.007) & 571.763 & 70.690\\
-\hspace{1em}aorsf-random & 0.098 (0.005) & 0.772 (0.008) & 11.675 & 1.360\\
-\hspace{1em}cif-extension & 0.069 (0.002) & 0.787 (0.009) & 165.124 & 51.252\\
-\hspace{1em}xgboost-cox & 0.065 (0.017) & 0.814 (0.005) & 8.516 & 0.015\\
-\hspace{1em}xgboost-aft & --- & 0.815 (0.006) & 22.582 & 0.013\\
+\hspace{1em}aorsf-fast & 0.156 (0.007) & 0.810 (0.007) & 5.048 & 1.287\\
+\hspace{1em}aorsf-cph & 0.153 (0.006) & 0.809 (0.007) & 14.564 & 1.300\\
+\hspace{1em}aorsf-net & 0.152 (0.006) & 0.809 (0.007) & 480.098 & 1.437\\
+\hspace{1em}rsf-standard & 0.150 (0.007) & 0.801 (0.007) & 9.407 & 0.991\\
+\hspace{1em}obliqueRSF-net & 0.143 (0.005) & 0.811 (0.008) & 2830.398 & 356.908\\
+\hspace{1em}cif-standard & 0.132 (0.005) & 0.809 (0.007) & 71.835 & 371.102\\
+\hspace{1em}glmnet-cox & 0.129 (0.011) & 0.795 (0.008) & 1.473 & 0.011\\
+\hspace{1em}nn-cox & 0.117 (0.029) & 0.786 (0.046) & 51.356 & 84.715\\
+\hspace{1em}ranger-extratrees & 0.112 (0.005) & 0.795 (0.009) & 293.864 & 61.837\\
+\hspace{1em}cif-rotate & 0.104 (0.004) & 0.783 (0.009) & 569.289 & 67.436\\
+\hspace{1em}aorsf-random & 0.097 (0.005) & 0.772 (0.008) & 10.996 & 1.259\\
+\hspace{1em}cif-extension & 0.069 (0.002) & 0.786 (0.009) & 169.206 & 56.091\\
+\hspace{1em}xgboost-cox & 0.064 (0.017) & 0.814 (0.006) & 8.544 & 0.015\\
+\hspace{1em}xgboost-aft & --- & 0.814 (0.006) & 23.781 & 0.013\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.217 (0.006) & 0.792 (0.004) & 955.499 & 2.412\\
-\hspace{1em}rsf-standard & 0.216 (0.007) & 0.789 (0.004) & 13.881 & 1.320\\
-\hspace{1em}aorsf-cph & 0.215 (0.007) & 0.792 (0.004) & 23.030 & 2.291\\
-\hspace{1em}aorsf-fast & 0.215 (0.007) & 0.792 (0.004) & 7.760 & 2.281\\
-\hspace{1em}obliqueRSF-net & 0.207 (0.005) & 0.792 (0.004) & 7413.571 & 319.191\\
-\hspace{1em}cif-standard & 0.202 (0.004) & 0.790 (0.004) & 71.453 & 386.302\\
-\hspace{1em}nn-cox & 0.192 (0.012) & 0.780 (0.005) & 97.331 & 99.624\\
-\hspace{1em}glmnet-cox & 0.190 (0.015) & 0.777 (0.008) & 2.123 & 0.012\\
-\hspace{1em}ranger-extratrees & 0.181 (0.004) & 0.781 (0.005) & 406.320 & 66.433\\
-\hspace{1em}cif-rotate & 0.152 (0.007) & 0.757 (0.006) & 581.210 & 65.820\\
-\hspace{1em}xgboost-cox & 0.132 (0.011) & 0.795 (0.004) & 12.310 & 0.016\\
-\hspace{1em}aorsf-random & 0.130 (0.005) & 0.733 (0.005) & 21.733 & 2.051\\
-\hspace{1em}cif-extension & 0.113 (0.002) & 0.776 (0.005) & 183.959 & 53.651\\
-\hspace{1em}xgboost-aft & --- & 0.794 (0.004) & 27.733 & 0.014\\
+\hspace{1em}aorsf-net & 0.217 (0.006) & 0.792 (0.004) & 902.210 & 2.343\\
+\hspace{1em}rsf-standard & 0.216 (0.006) & 0.789 (0.004) & 14.727 & 1.274\\
+\hspace{1em}aorsf-fast & 0.216 (0.007) & 0.792 (0.004) & 7.268 & 2.936\\
+\hspace{1em}aorsf-cph & 0.215 (0.006) & 0.792 (0.004) & 22.420 & 3.070\\
+\hspace{1em}obliqueRSF-net & 0.207 (0.005) & 0.791 (0.004) & 7329.229 & 331.164\\
+\hspace{1em}cif-standard & 0.201 (0.004) & 0.790 (0.004) & 72.253 & 384.744\\
+\hspace{1em}nn-cox & 0.193 (0.011) & 0.780 (0.005) & 103.296 & 92.992\\
+\hspace{1em}glmnet-cox & 0.191 (0.015) & 0.777 (0.007) & 2.256 & 0.011\\
+\hspace{1em}ranger-extratrees & 0.181 (0.004) & 0.780 (0.005) & 332.296 & 70.372\\
+\hspace{1em}cif-rotate & 0.151 (0.007) & 0.757 (0.006) & 589.958 & 66.749\\
+\hspace{1em}xgboost-cox & 0.131 (0.012) & 0.794 (0.004) & 11.220 & 0.015\\
+\hspace{1em}aorsf-random & 0.130 (0.005) & 0.733 (0.005) & 19.416 & 2.051\\
+\hspace{1em}cif-extension & 0.113 (0.002) & 0.775 (0.005) & 180.483 & 54.092\\
+\hspace{1em}xgboost-aft & --- & 0.794 (0.004) & 28.692 & 0.014\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.234 (0.007) & 0.842 (0.005) & 5.445 & 1.619\\
-\hspace{1em}rsf-standard & 0.230 (0.007) & 0.835 (0.005) & 10.089 & 1.049\\
-\hspace{1em}aorsf-cph & 0.229 (0.007) & 0.841 (0.005) & 16.936 & 1.624\\
-\hspace{1em}aorsf-net & 0.217 (0.057) & 0.832 (0.043) & 631.093 & 1.707\\
-\hspace{1em}obliqueRSF-net & 0.213 (0.005) & 0.841 (0.005) & 3701.663 & 311.291\\
-\hspace{1em}cif-standard & 0.199 (0.005) & 0.839 (0.005) & 74.710 & 369.446\\
-\hspace{1em}nn-cox & 0.187 (0.020) & 0.826 (0.009) & 59.242 & 95.742\\
-\hspace{1em}cif-rotate & 0.172 (0.006) & 0.806 (0.007) & 581.038 & 67.850\\
-\hspace{1em}ranger-extratrees & 0.171 (0.004) & 0.824 (0.005) & 326.124 & 86.921\\
-\hspace{1em}glmnet-cox & 0.164 (0.046) & 0.816 (0.019) & 2.424 & 0.012\\
-\hspace{1em}aorsf-random & 0.139 (0.005) & 0.789 (0.006) & 15.571 & 1.574\\
-\hspace{1em}xgboost-cox & 0.121 (0.018) & 0.845 (0.005) & 11.223 & 0.015\\
-\hspace{1em}cif-extension & 0.109 (0.003) & 0.809 (0.006) & 170.011 & 49.372\\
-\hspace{1em}xgboost-aft & --- & 0.844 (0.005) & 26.160 & 0.014\\
+\hspace{1em}aorsf-fast & 0.233 (0.006) & 0.841 (0.005) & 5.731 & 1.497\\
+\hspace{1em}rsf-standard & 0.229 (0.006) & 0.835 (0.005) & 11.238 & 1.079\\
+\hspace{1em}aorsf-cph & 0.229 (0.006) & 0.841 (0.005) & 16.768 & 1.549\\
+\hspace{1em}aorsf-net & 0.228 (0.006) & 0.841 (0.005) & 597.572 & 1.659\\
+\hspace{1em}obliqueRSF-net & 0.212 (0.005) & 0.841 (0.005) & 3737.617 & 320.616\\
+\hspace{1em}cif-standard & 0.199 (0.005) & 0.839 (0.005) & 71.854 & 391.419\\
+\hspace{1em}nn-cox & 0.180 (0.017) & 0.826 (0.007) & 56.056 & 96.125\\
+\hspace{1em}cif-rotate & 0.172 (0.006) & 0.806 (0.007) & 589.494 & 69.448\\
+\hspace{1em}ranger-extratrees & 0.170 (0.004) & 0.824 (0.005) & 387.176 & 77.513\\
+\hspace{1em}glmnet-cox & 0.167 (0.044) & 0.817 (0.018) & 2.141 & 0.011\\
+\hspace{1em}aorsf-random & 0.139 (0.005) & 0.789 (0.006) & 12.952 & 1.501\\
+\hspace{1em}xgboost-cox & 0.122 (0.017) & 0.845 (0.005) & 10.926 & 0.015\\
+\hspace{1em}cif-extension & 0.109 (0.003) & 0.808 (0.006) & 176.907 & 57.216\\
+\hspace{1em}xgboost-aft & --- & 0.844 (0.005) & 24.549 & 0.013\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.093 (0.004) & 0.794 (0.007) & 4.101 & 1.127\\
-\hspace{1em}rsf-standard & 0.090 (0.006) & 0.785 (0.007) & 7.258 & 0.919\\
-\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.793 (0.007) & 13.277 & 1.119\\
-\hspace{1em}aorsf-net & 0.087 (0.017) & 0.786 (0.031) & 388.977 & 1.200\\
-\hspace{1em}obliqueRSF-net & 0.082 (0.003) & 0.792 (0.007) & 1768.748 & 384.697\\
-\hspace{1em}glmnet-cox & 0.078 (0.005) & 0.788 (0.007) & 1.662 & 0.010\\
-\hspace{1em}cif-standard & 0.073 (0.003) & 0.788 (0.007) & 72.160 & 363.855\\
-\hspace{1em}nn-cox & 0.071 (0.013) & 0.781 (0.009) & 31.997 & 88.257\\
-\hspace{1em}ranger-extratrees & 0.067 (0.003) & 0.780 (0.008) & 249.618 & 67.732\\
-\hspace{1em}aorsf-random & 0.059 (0.004) & 0.751 (0.009) & 9.374 & 1.121\\
-\hspace{1em}cif-rotate & 0.052 (0.003) & 0.769 (0.009) & 592.458 & 70.175\\
-\hspace{1em}xgboost-cox & 0.047 (0.013) & 0.794 (0.006) & 6.688 & 0.014\\
-\hspace{1em}cif-extension & 0.036 (0.002) & 0.771 (0.008) & 170.852 & 51.402\\
-\hspace{1em}xgboost-aft & --- & 0.793 (0.007) & 21.053 & 0.013\\
+\hspace{1em}aorsf-fast & 0.093 (0.004) & 0.794 (0.007) & 4.549 & 1.078\\
+\hspace{1em}aorsf-net & 0.090 (0.004) & 0.792 (0.007) & 349.547 & 1.189\\
+\hspace{1em}rsf-standard & 0.090 (0.006) & 0.784 (0.006) & 8.991 & 0.984\\
+\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.792 (0.007) & 12.609 & 1.077\\
+\hspace{1em}obliqueRSF-net & 0.082 (0.003) & 0.791 (0.007) & 1869.359 & 387.014\\
+\hspace{1em}glmnet-cox & 0.078 (0.004) & 0.787 (0.007) & 1.673 & 0.011\\
+\hspace{1em}cif-standard & 0.073 (0.003) & 0.787 (0.007) & 73.989 & 364.863\\
+\hspace{1em}nn-cox & 0.070 (0.012) & 0.783 (0.010) & 32.099 & 82.720\\
+\hspace{1em}ranger-extratrees & 0.067 (0.003) & 0.779 (0.008) & 251.130 & 50.542\\
+\hspace{1em}aorsf-random & 0.059 (0.004) & 0.750 (0.008) & 9.179 & 1.091\\
+\hspace{1em}cif-rotate & 0.052 (0.003) & 0.768 (0.009) & 586.962 & 68.410\\
+\hspace{1em}xgboost-cox & 0.046 (0.014) & 0.794 (0.006) & 7.316 & 0.015\\
+\hspace{1em}cif-extension & 0.036 (0.002) & 0.769 (0.009) & 169.866 & 53.493\\
+\hspace{1em}xgboost-aft & --- & 0.793 (0.006) & 20.363 & 0.013\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.098 (0.013) & 0.718 (0.012) & 0.228 & 0.050\\
-\hspace{1em}aorsf-cph & 0.097 (0.013) & 0.717 (0.012) & 0.630 & 0.051\\
-\hspace{1em}cif-standard & 0.096 (0.013) & 0.710 (0.012) & 0.670 & 3.620\\
-\hspace{1em}aorsf-random & 0.094 (0.009) & 0.715 (0.012) & 0.992 & 0.045\\
-\hspace{1em}aorsf-net & 0.090 (0.024) & 0.710 (0.036) & 49.564 & 0.046\\
-\hspace{1em}obliqueRSF-net & 0.088 (0.006) & 0.717 (0.012) & 250.492 & 16.952\\
-\hspace{1em}cif-rotate & 0.086 (0.018) & 0.705 (0.015) & 12.341 & 3.533\\
-\hspace{1em}rsf-standard & 0.085 (0.019) & 0.703 (0.011) & 1.557 & 0.151\\
-\hspace{1em}ranger-extratrees & 0.082 (0.007) & 0.710 (0.012) & 0.089 & 0.241\\
-\hspace{1em}cif-extension & 0.080 (0.006) & 0.709 (0.012) & 8.368 & 3.934\\
-\hspace{1em}glmnet-cox & 0.072 (0.013) & 0.709 (0.018) & 0.104 & 0.003\\
-\hspace{1em}xgboost-cox & 0.061 (0.012) & 0.700 (0.013) & 3.143 & 0.003\\
-\hspace{1em}nn-cox & -0.003 (0.003) & 0.515 (0.030) & 11.966 & 1.368\\
-\hspace{1em}xgboost-aft & --- & 0.706 (0.014) & 11.263 & 0.006\\
+\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.717 (0.012) & 0.237 & 0.049\\
+\hspace{1em}aorsf-cph & 0.099 (0.014) & 0.717 (0.011) & 0.636 & 0.049\\
+\hspace{1em}cif-standard & 0.097 (0.013) & 0.710 (0.012) & 0.745 & 3.685\\
+\hspace{1em}aorsf-net & 0.096 (0.014) & 0.717 (0.012) & 47.226 & 0.048\\
+\hspace{1em}aorsf-random & 0.096 (0.010) & 0.716 (0.011) & 1.717 & 0.044\\
+\hspace{1em}obliqueRSF-net & 0.089 (0.006) & 0.717 (0.012) & 252.190 & 16.726\\
+\hspace{1em}cif-rotate & 0.086 (0.017) & 0.705 (0.014) & 13.242 & 3.448\\
+\hspace{1em}rsf-standard & 0.086 (0.019) & 0.704 (0.011) & 1.901 & 0.150\\
+\hspace{1em}ranger-extratrees & 0.083 (0.007) & 0.710 (0.012) & 0.560 & 0.248\\
+\hspace{1em}cif-extension & 0.080 (0.006) & 0.709 (0.011) & 8.397 & 3.363\\
+\hspace{1em}glmnet-cox & 0.075 (0.016) & 0.711 (0.019) & 0.128 & 0.003\\
+\hspace{1em}xgboost-cox & 0.062 (0.013) & 0.701 (0.013) & 3.217 & 0.003\\
+\hspace{1em}nn-cox & -0.003 (0.003) & 0.508 (0.033) & 12.769 & 1.106\\
+\hspace{1em}xgboost-aft & --- & 0.706 (0.013) & 10.290 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.099 (0.017) & 0.713 (0.016) & 0.229 & 0.050\\
-\hspace{1em}aorsf-cph & 0.098 (0.016) & 0.712 (0.015) & 0.639 & 0.051\\
-\hspace{1em}cif-standard & 0.090 (0.016) & 0.701 (0.017) & 0.665 & 3.411\\
-\hspace{1em}aorsf-net & 0.087 (0.042) & 0.708 (0.026) & 50.808 & 0.048\\
-\hspace{1em}obliqueRSF-net & 0.087 (0.009) & 0.710 (0.016) & 258.163 & 16.507\\
-\hspace{1em}aorsf-random & 0.086 (0.013) & 0.702 (0.016) & 1.023 & 0.047\\
-\hspace{1em}cif-rotate & 0.084 (0.021) & 0.695 (0.018) & 12.248 & 3.554\\
-\hspace{1em}cif-extension & 0.081 (0.009) & 0.706 (0.017) & 8.129 & 3.936\\
-\hspace{1em}rsf-standard & 0.080 (0.021) & 0.694 (0.015) & 1.654 & 0.147\\
-\hspace{1em}ranger-extratrees & 0.079 (0.011) & 0.699 (0.016) & 0.090 & 0.242\\
-\hspace{1em}glmnet-cox & 0.071 (0.018) & 0.704 (0.024) & 0.116 & 0.003\\
-\hspace{1em}xgboost-cox & 0.059 (0.011) & 0.694 (0.018) & 3.002 & 0.003\\
-\hspace{1em}nn-cox & -0.014 (0.032) & 0.503 (0.034) & 13.121 & 1.248\\
-\hspace{1em}xgboost-aft & --- & 0.701 (0.019) & 12.035 & 0.006\\
+\hspace{1em}aorsf-fast & 0.100 (0.017) & 0.713 (0.016) & 0.237 & 0.054\\
+\hspace{1em}aorsf-cph & 0.098 (0.017) & 0.712 (0.015) & 0.659 & 0.852\\
+\hspace{1em}aorsf-net & 0.095 (0.018) & 0.713 (0.017) & 47.589 & 0.049\\
+\hspace{1em}cif-standard & 0.091 (0.016) & 0.701 (0.017) & 0.717 & 3.703\\
+\hspace{1em}obliqueRSF-net & 0.087 (0.009) & 0.711 (0.015) & 249.790 & 16.701\\
+\hspace{1em}aorsf-random & 0.087 (0.012) & 0.702 (0.015) & 1.815 & 0.046\\
+\hspace{1em}cif-rotate & 0.084 (0.020) & 0.694 (0.017) & 13.154 & 3.977\\
+\hspace{1em}cif-extension & 0.081 (0.009) & 0.706 (0.017) & 8.446 & 4.066\\
+\hspace{1em}rsf-standard & 0.081 (0.020) & 0.694 (0.015) & 1.831 & 0.153\\
+\hspace{1em}ranger-extratrees & 0.079 (0.011) & 0.700 (0.016) & 0.636 & 0.254\\
+\hspace{1em}glmnet-cox & 0.073 (0.018) & 0.706 (0.024) & 0.125 & 0.003\\
+\hspace{1em}xgboost-cox & 0.059 (0.011) & 0.695 (0.018) & 3.136 & 0.003\\
+\hspace{1em}nn-cox & -0.005 (0.006) & 0.531 (0.054) & 13.107 & 0.969\\
+\hspace{1em}xgboost-aft & --- & 0.701 (0.019) & 11.227 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.073 (0.023) & 0.750 (0.027) & 1867.035 & 13.505\\
-\hspace{1em}cif-rotate & 0.071 (0.017) & 0.746 (0.027) & 6498.327 & 347.595\\
-\hspace{1em}cif-standard & 0.068 (0.017) & 0.746 (0.028) & 8.392 & 4.008\\
-\hspace{1em}aorsf-cph & 0.066 (0.030) & 0.744 (0.022) & 1.313 & 0.182\\
-\hspace{1em}aorsf-fast & 0.065 (0.029) & 0.745 (0.023) & 0.740 & 0.180\\
-\hspace{1em}cif-extension & 0.065 (0.014) & 0.745 (0.025) & 43.993 & 6.218\\
-\hspace{1em}ranger-extratrees & 0.061 (0.022) & 0.741 (0.028) & 0.218 & 0.676\\
-\hspace{1em}glmnet-cox & 0.044 (0.032) & 0.724 (0.034) & 5.824 & 0.006\\
-\hspace{1em}aorsf-random & 0.027 (0.014) & 0.694 (0.038) & 1.692 & 0.172\\
-\hspace{1em}xgboost-cox & 0.027 (0.034) & 0.740 (0.027) & 2.297 & 0.007\\
-\hspace{1em}rsf-standard & 0.021 (0.039) & 0.692 (0.032) & 0.777 & 0.314\\
-\hspace{1em}nn-cox & -0.017 (0.073) & 0.681 (0.048) & 16.971 & 1.662\\
-\hspace{1em}aorsf-net & -0.039 (0.249) & 0.731 (0.052) & 455.331 & 0.176\\
-\hspace{1em}xgboost-aft & --- & 0.741 (0.023) & 9.590 & 0.010\\
+\hspace{1em}obliqueRSF-net & 0.072 (0.023) & 0.751 (0.029) & 1901.883 & 14.017\\
+\hspace{1em}cif-rotate & 0.070 (0.018) & 0.747 (0.027) & 6452.563 & 360.067\\
+\hspace{1em}cif-standard & 0.067 (0.019) & 0.747 (0.030) & 9.660 & 4.247\\
+\hspace{1em}aorsf-cph & 0.067 (0.029) & 0.747 (0.026) & 1.107 & 0.175\\
+\hspace{1em}aorsf-fast & 0.065 (0.028) & 0.747 (0.027) & 0.712 & 0.178\\
+\hspace{1em}cif-extension & 0.064 (0.016) & 0.746 (0.028) & 44.047 & 6.554\\
+\hspace{1em}ranger-extratrees & 0.061 (0.022) & 0.742 (0.031) & 0.228 & 0.169\\
+\hspace{1em}glmnet-cox & 0.041 (0.032) & 0.724 (0.036) & 5.780 & 0.006\\
+\hspace{1em}aorsf-random & 0.027 (0.015) & 0.696 (0.038) & 1.924 & 0.167\\
+\hspace{1em}xgboost-cox & 0.027 (0.034) & 0.741 (0.030) & 2.258 & 0.007\\
+\hspace{1em}rsf-standard & 0.024 (0.037) & 0.695 (0.033) & 0.366 & 0.743\\
+\hspace{1em}aorsf-net & 0.012 (0.062) & 0.740 (0.025) & 448.941 & 0.168\\
+\hspace{1em}nn-cox & -0.006 (0.043) & 0.669 (0.075) & 19.374 & 1.808\\
+\hspace{1em}xgboost-aft & --- & 0.744 (0.027) & 9.708 & 0.010\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.116 (0.029) & 0.787 (0.037) & 0.091 & 0.002\\
-\hspace{1em}aorsf-fast & 0.100 (0.040) & 0.768 (0.033) & 0.079 & 0.019\\
-\hspace{1em}aorsf-cph & 0.100 (0.041) & 0.769 (0.033) & 0.165 & 0.019\\
-\hspace{1em}aorsf-net & 0.093 (0.043) & 0.752 (0.049) & 13.137 & 0.019\\
-\hspace{1em}obliqueRSF-net & 0.090 (0.028) & 0.761 (0.037) & 96.051 & 5.285\\
-\hspace{1em}cif-extension & 0.086 (0.038) & 0.731 (0.036) & 5.213 & 2.395\\
-\hspace{1em}aorsf-random & 0.086 (0.031) & 0.757 (0.033) & 0.259 & 0.019\\
-\hspace{1em}cif-rotate & 0.085 (0.050) & 0.756 (0.028) & 6.045 & 2.042\\
-\hspace{1em}cif-standard & 0.085 (0.040) & 0.747 (0.035) & 0.289 & 1.106\\
-\hspace{1em}ranger-extratrees & 0.073 (0.017) & 0.742 (0.032) & 0.043 & 0.083\\
-\hspace{1em}rsf-standard & 0.071 (0.051) & 0.733 (0.036) & 0.111 & 0.038\\
-\hspace{1em}xgboost-cox & 0.033 (0.052) & 0.697 (0.109) & 0.374 & 0.002\\
-\hspace{1em}nn-cox & -0.003 (0.022) & 0.534 (0.114) & 11.145 & 0.437\\
-\hspace{1em}xgboost-aft & --- & 0.756 (0.039) & 7.831 & 0.006\\
+\hspace{1em}glmnet-cox & 0.117 (0.028) & 0.787 (0.037) & 0.098 & 0.002\\
+\hspace{1em}aorsf-cph & 0.100 (0.039) & 0.769 (0.033) & 0.159 & 0.018\\
+\hspace{1em}aorsf-fast & 0.100 (0.037) & 0.768 (0.032) & 0.078 & 0.018\\
+\hspace{1em}aorsf-net & 0.097 (0.040) & 0.760 (0.034) & 12.491 & 0.018\\
+\hspace{1em}obliqueRSF-net & 0.089 (0.027) & 0.758 (0.036) & 97.158 & 5.447\\
+\hspace{1em}cif-rotate & 0.087 (0.048) & 0.755 (0.027) & 6.083 & 1.964\\
+\hspace{1em}cif-extension & 0.087 (0.036) & 0.730 (0.034) & 5.256 & 2.514\\
+\hspace{1em}aorsf-random & 0.087 (0.029) & 0.757 (0.032) & 1.061 & 0.018\\
+\hspace{1em}cif-standard & 0.084 (0.038) & 0.743 (0.036) & 0.347 & 1.132\\
+\hspace{1em}ranger-extratrees & 0.073 (0.016) & 0.741 (0.037) & 0.043 & 0.078\\
+\hspace{1em}rsf-standard & 0.072 (0.048) & 0.732 (0.034) & 0.156 & 0.040\\
+\hspace{1em}xgboost-cox & 0.029 (0.050) & 0.679 (0.121) & 0.266 & 0.002\\
+\hspace{1em}nn-cox & -0.004 (0.014) & 0.549 (0.110) & 11.152 & 0.406\\
+\hspace{1em}xgboost-aft & --- & 0.754 (0.038) & 6.738 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.027 (0.018) & 0.619 (0.025) & 0.089 & 0.002\\
-\hspace{1em}ranger-extratrees & 0.016 (0.015) & 0.594 (0.025) & 0.032 & 0.080\\
-\hspace{1em}obliqueRSF-net & 0.011 (0.016) & 0.589 (0.023) & 217.918 & 6.187\\
-\hspace{1em}aorsf-random & 0.011 (0.018) & 0.594 (0.025) & 0.395 & 0.021\\
-\hspace{1em}xgboost-cox & 0.010 (0.016) & 0.596 (0.031) & 1.291 & 0.002\\
-\hspace{1em}aorsf-fast & 0.005 (0.020) & 0.592 (0.026) & 0.111 & 0.022\\
-\hspace{1em}aorsf-cph & 0.005 (0.021) & 0.593 (0.027) & 0.262 & 0.022\\
-\hspace{1em}cif-standard & 0.005 (0.020) & 0.591 (0.022) & 0.290 & 1.120\\
-\hspace{1em}aorsf-net & 0.005 (0.021) & 0.590 (0.027) & 19.255 & 0.022\\
-\hspace{1em}nn-cox & -0.003 (0.023) & 0.544 (0.064) & 11.514 & 0.442\\
-\hspace{1em}cif-extension & -0.007 (0.023) & 0.576 (0.028) & 6.044 & 2.303\\
-\hspace{1em}cif-rotate & -0.015 (0.025) & 0.580 (0.030) & 6.986 & 1.965\\
-\hspace{1em}rsf-standard & -0.030 (0.032) & 0.575 (0.025) & 0.843 & 0.086\\
-\hspace{1em}xgboost-aft & --- & 0.580 (0.035) & 6.226 & 0.006\\
+\hspace{1em}glmnet-cox & 0.029 (0.017) & 0.620 (0.024) & 0.100 & 0.002\\
+\hspace{1em}ranger-extratrees & 0.017 (0.016) & 0.596 (0.025) & 0.041 & 0.081\\
+\hspace{1em}obliqueRSF-net & 0.013 (0.016) & 0.593 (0.024) & 217.838 & 6.232\\
+\hspace{1em}aorsf-random & 0.013 (0.018) & 0.595 (0.024) & 1.166 & 0.020\\
+\hspace{1em}xgboost-cox & 0.010 (0.016) & 0.598 (0.031) & 1.331 & 0.002\\
+\hspace{1em}cif-standard & 0.008 (0.021) & 0.594 (0.023) & 0.315 & 1.056\\
+\hspace{1em}aorsf-cph & 0.007 (0.020) & 0.595 (0.026) & 0.256 & 0.022\\
+\hspace{1em}aorsf-fast & 0.007 (0.020) & 0.594 (0.026) & 0.114 & 0.021\\
+\hspace{1em}aorsf-net & 0.006 (0.020) & 0.592 (0.026) & 18.652 & 0.022\\
+\hspace{1em}cif-extension & -0.005 (0.023) & 0.580 (0.028) & 6.164 & 2.309\\
+\hspace{1em}nn-cox & -0.008 (0.023) & 0.526 (0.055) & 12.031 & 0.466\\
+\hspace{1em}cif-rotate & -0.012 (0.025) & 0.583 (0.030) & 7.411 & 2.486\\
+\hspace{1em}rsf-standard & -0.026 (0.032) & 0.577 (0.024) & 1.081 & 0.088\\
+\hspace{1em}xgboost-aft & --- & 0.582 (0.034) & 6.223 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.124 (0.016) & 0.746 (0.018) & 307.849 & 6.881\\
-\hspace{1em}cif-standard & 0.123 (0.020) & 0.743 (0.020) & 0.430 & 1.769\\
-\hspace{1em}rsf-standard & 0.120 (0.024) & 0.737 (0.020) & 1.508 & 0.116\\
-\hspace{1em}aorsf-cph & 0.120 (0.026) & 0.736 (0.018) & 0.406 & 0.038\\
-\hspace{1em}aorsf-fast & 0.117 (0.025) & 0.733 (0.017) & 0.168 & 0.039\\
-\hspace{1em}cif-extension & 0.115 (0.018) & 0.743 (0.020) & 7.990 & 3.331\\
-\hspace{1em}aorsf-net & 0.112 (0.056) & 0.734 (0.036) & 37.488 & 0.038\\
-\hspace{1em}cif-rotate & 0.107 (0.024) & 0.729 (0.018) & 10.801 & 2.745\\
-\hspace{1em}aorsf-random & 0.105 (0.025) & 0.724 (0.026) & 0.785 & 0.036\\
-\hspace{1em}ranger-extratrees & 0.095 (0.018) & 0.738 (0.025) & 0.052 & 0.136\\
-\hspace{1em}glmnet-cox & 0.090 (0.018) & 0.728 (0.021) & 0.098 & 0.002\\
-\hspace{1em}xgboost-cox & 0.082 (0.017) & 0.730 (0.019) & 2.465 & 0.003\\
-\hspace{1em}nn-cox & -0.003 (0.005) & 0.521 (0.051) & 11.570 & 0.838\\
-\hspace{1em}xgboost-aft & --- & 0.730 (0.022) & 10.495 & 0.006\\
+\hspace{1em}obliqueRSF-net & 0.124 (0.016) & 0.746 (0.017) & 286.149 & 6.874\\
+\hspace{1em}cif-standard & 0.123 (0.020) & 0.743 (0.020) & 0.507 & 2.289\\
+\hspace{1em}rsf-standard & 0.120 (0.023) & 0.738 (0.019) & 1.437 & 0.115\\
+\hspace{1em}aorsf-net & 0.120 (0.024) & 0.738 (0.020) & 35.967 & 0.038\\
+\hspace{1em}aorsf-cph & 0.120 (0.025) & 0.736 (0.018) & 0.401 & 0.037\\
+\hspace{1em}aorsf-fast & 0.115 (0.024) & 0.733 (0.017) & 0.161 & 0.037\\
+\hspace{1em}cif-extension & 0.114 (0.017) & 0.743 (0.019) & 7.560 & 2.919\\
+\hspace{1em}cif-rotate & 0.107 (0.023) & 0.729 (0.017) & 11.241 & 3.023\\
+\hspace{1em}aorsf-random & 0.104 (0.023) & 0.724 (0.025) & 1.496 & 0.035\\
+\hspace{1em}ranger-extratrees & 0.094 (0.018) & 0.736 (0.025) & 0.102 & 0.143\\
+\hspace{1em}glmnet-cox & 0.090 (0.019) & 0.728 (0.021) & 0.106 & 0.002\\
+\hspace{1em}xgboost-cox & 0.083 (0.017) & 0.730 (0.020) & 2.538 & 0.003\\
+\hspace{1em}nn-cox & -0.007 (0.012) & 0.509 (0.061) & 11.658 & 0.746\\
+\hspace{1em}xgboost-aft & --- & 0.729 (0.021) & 10.625 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.076 (0.017) & 0.748 (0.028) & 0.160 & 0.037\\
-\hspace{1em}aorsf-net & 0.075 (0.017) & 0.746 (0.028) & 27.437 & 0.039\\
-\hspace{1em}aorsf-cph & 0.072 (0.018) & 0.744 (0.029) & 0.379 & 0.037\\
-\hspace{1em}glmnet-cox & 0.068 (0.040) & 0.721 (0.084) & 0.510 & 0.003\\
-\hspace{1em}obliqueRSF-net & 0.063 (0.013) & 0.742 (0.024) & 222.174 & 11.114\\
-\hspace{1em}cif-rotate & 0.060 (0.013) & 0.721 (0.027) & 35.135 & 5.270\\
-\hspace{1em}cif-standard & 0.059 (0.013) & 0.739 (0.023) & 1.108 & 3.576\\
-\hspace{1em}ranger-extratrees & 0.054 (0.012) & 0.740 (0.029) & 0.091 & 0.183\\
-\hspace{1em}cif-extension & 0.052 (0.011) & 0.730 (0.023) & 13.427 & 5.518\\
-\hspace{1em}rsf-standard & 0.048 (0.021) & 0.707 (0.026) & 0.169 & 0.060\\
-\hspace{1em}xgboost-cox & 0.045 (0.045) & 0.746 (0.019) & 3.514 & 0.003\\
-\hspace{1em}aorsf-random & 0.033 (0.013) & 0.700 (0.029) & 0.511 & 0.039\\
-\hspace{1em}nn-cox & 0.009 (0.020) & 0.628 (0.086) & 10.335 & 0.565\\
-\hspace{1em}xgboost-aft & --- & 0.733 (0.021) & 10.963 & 0.006\\
+\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.745 (0.027) & 0.161 & 0.035\\
+\hspace{1em}aorsf-net & 0.074 (0.019) & 0.743 (0.027) & 25.934 & 0.038\\
+\hspace{1em}aorsf-cph & 0.071 (0.018) & 0.741 (0.028) & 0.375 & 0.035\\
+\hspace{1em}glmnet-cox & 0.063 (0.041) & 0.715 (0.091) & 0.502 & 0.002\\
+\hspace{1em}obliqueRSF-net & 0.063 (0.013) & 0.741 (0.023) & 221.806 & 11.417\\
+\hspace{1em}cif-rotate & 0.059 (0.016) & 0.721 (0.025) & 35.190 & 4.947\\
+\hspace{1em}cif-standard & 0.058 (0.014) & 0.738 (0.022) & 1.564 & 3.334\\
+\hspace{1em}ranger-extratrees & 0.054 (0.013) & 0.737 (0.029) & 0.118 & 0.176\\
+\hspace{1em}cif-extension & 0.052 (0.011) & 0.730 (0.022) & 13.507 & 5.567\\
+\hspace{1em}rsf-standard & 0.046 (0.023) & 0.705 (0.025) & 0.195 & 0.064\\
+\hspace{1em}xgboost-cox & 0.039 (0.051) & 0.747 (0.020) & 3.831 & 0.003\\
+\hspace{1em}aorsf-random & 0.033 (0.012) & 0.695 (0.030) & 0.427 & 0.037\\
+\hspace{1em}nn-cox & 0.008 (0.018) & 0.630 (0.123) & 12.211 & 0.596\\
+\hspace{1em}xgboost-aft & --- & 0.734 (0.020) & 11.525 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.080 (0.018) & 0.721 (0.024) & 0.683 & 0.054\\
-\hspace{1em}aorsf-fast & 0.079 (0.019) & 0.721 (0.026) & 0.241 & 0.053\\
-\hspace{1em}obliqueRSF-net & 0.072 (0.011) & 0.720 (0.024) & 385.158 & 9.315\\
-\hspace{1em}ranger-extratrees & 0.072 (0.010) & 0.721 (0.023) & 0.236 & 0.189\\
-\hspace{1em}aorsf-net & 0.072 (0.041) & 0.715 (0.036) & 53.536 & 0.057\\
-\hspace{1em}cif-standard & 0.069 (0.010) & 0.715 (0.024) & 0.931 & 3.280\\
-\hspace{1em}cif-rotate & 0.066 (0.019) & 0.706 (0.030) & 41.946 & 5.179\\
-\hspace{1em}cif-extension & 0.063 (0.009) & 0.713 (0.023) & 14.574 & 5.603\\
-\hspace{1em}glmnet-cox & 0.058 (0.020) & 0.699 (0.025) & 0.462 & 0.003\\
-\hspace{1em}rsf-standard & 0.055 (0.022) & 0.692 (0.026) & 1.528 & 0.119\\
-\hspace{1em}aorsf-random & 0.048 (0.010) & 0.682 (0.023) & 0.920 & 0.053\\
-\hspace{1em}nn-cox & 0.046 (0.027) & 0.695 (0.040) & 12.586 & 0.590\\
-\hspace{1em}xgboost-cox & 0.038 (0.017) & 0.697 (0.027) & 2.920 & 0.003\\
-\hspace{1em}xgboost-aft & --- & 0.695 (0.026) & 13.042 & 0.006\\
+\hspace{1em}aorsf-net & 0.082 (0.017) & 0.722 (0.023) & 50.238 & 0.056\\
+\hspace{1em}aorsf-cph & 0.081 (0.018) & 0.722 (0.023) & 0.668 & 0.051\\
+\hspace{1em}aorsf-fast & 0.080 (0.020) & 0.722 (0.025) & 0.248 & 0.051\\
+\hspace{1em}ranger-extratrees & 0.073 (0.010) & 0.722 (0.022) & 0.137 & 0.198\\
+\hspace{1em}obliqueRSF-net & 0.073 (0.010) & 0.721 (0.023) & 389.465 & 9.365\\
+\hspace{1em}cif-standard & 0.070 (0.010) & 0.716 (0.023) & 1.468 & 3.315\\
+\hspace{1em}cif-rotate & 0.067 (0.019) & 0.708 (0.029) & 41.655 & 5.185\\
+\hspace{1em}cif-extension & 0.064 (0.009) & 0.714 (0.022) & 15.396 & 6.113\\
+\hspace{1em}glmnet-cox & 0.058 (0.020) & 0.699 (0.025) & 0.416 & 0.003\\
+\hspace{1em}rsf-standard & 0.058 (0.022) & 0.694 (0.026) & 1.515 & 0.121\\
+\hspace{1em}nn-cox & 0.053 (0.028) & 0.706 (0.032) & 12.912 & 0.599\\
+\hspace{1em}aorsf-random & 0.049 (0.010) & 0.682 (0.023) & 0.803 & 0.051\\
+\hspace{1em}xgboost-cox & 0.038 (0.017) & 0.698 (0.027) & 2.955 & 0.003\\
+\hspace{1em}xgboost-aft & --- & 0.697 (0.025) & 11.409 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{JHS; coronary heart disease, n = 3501, p = 80}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.040 (0.008) & 0.778 (0.015) & 2.036 & 0.153\\
+\hspace{1em}obliqueRSF-net & 0.039 (0.007) & 0.780 (0.015) & 185.659 & 130.539\\
+\hspace{1em}aorsf-fast & 0.039 (0.007) & 0.776 (0.014) & 0.586 & 0.151\\
+\hspace{1em}aorsf-net & 0.039 (0.009) & 0.777 (0.016) & 76.845 & 0.149\\
+\hspace{1em}cif-standard & 0.038 (0.006) & 0.779 (0.017) & 10.065 & 30.887\\
+\hspace{1em}cif-extension & 0.036 (0.004) & 0.781 (0.019) & 54.976 & 20.544\\
+\hspace{1em}ranger-extratrees & 0.035 (0.005) & 0.777 (0.017) & 3.892 & 1.677\\
+\hspace{1em}cif-rotate & 0.034 (0.010) & 0.769 (0.018) & 187.949 & 22.910\\
+\hspace{1em}glmnet-cox & 0.031 (0.010) & 0.774 (0.020) & 1.723 & 0.004\\
+\hspace{1em}rsf-standard & 0.031 (0.011) & 0.752 (0.016) & 2.099 & 0.226\\
+\hspace{1em}nn-cox & 0.030 (0.012) & 0.759 (0.021) & 10.787 & 5.787\\
+\hspace{1em}aorsf-random & 0.027 (0.004) & 0.763 (0.019) & 1.213 & 0.152\\
+\hspace{1em}xgboost-cox & 0.010 (0.023) & 0.785 (0.022) & 3.676 & 0.005\\
+\hspace{1em}xgboost-aft & --- & 0.782 (0.017) & 13.342 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{JHS; stroke, n = 3639, p = 80}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.036 (0.006) & 0.806 (0.016) & 2.012 & 0.149\\
+\hspace{1em}aorsf-net & 0.035 (0.008) & 0.807 (0.016) & 70.506 & 0.144\\
+\hspace{1em}aorsf-fast & 0.035 (0.007) & 0.806 (0.017) & 0.581 & 0.147\\
+\hspace{1em}obliqueRSF-net & 0.030 (0.006) & 0.807 (0.016) & 161.865 & 165.270\\
+\hspace{1em}glmnet-cox & 0.028 (0.008) & 0.798 (0.017) & 2.325 & 0.004\\
+\hspace{1em}cif-standard & 0.028 (0.005) & 0.803 (0.016) & 10.613 & 32.291\\
+\hspace{1em}rsf-standard & 0.027 (0.010) & 0.782 (0.018) & 1.210 & 0.190\\
+\hspace{1em}cif-extension & 0.025 (0.003) & 0.797 (0.018) & 55.652 & 21.758\\
+\hspace{1em}ranger-extratrees & 0.023 (0.005) & 0.791 (0.016) & 2.997 & 2.557\\
+\hspace{1em}cif-rotate & 0.023 (0.009) & 0.785 (0.017) & 188.792 & 24.524\\
+\hspace{1em}aorsf-random & 0.022 (0.004) & 0.775 (0.018) & 1.115 & 0.153\\
+\hspace{1em}nn-cox & 0.016 (0.027) & 0.772 (0.021) & 10.445 & 6.338\\
+\hspace{1em}xgboost-cox & 0.001 (0.030) & 0.776 (0.021) & 2.953 & 0.005\\
+\hspace{1em}xgboost-aft & --- & 0.784 (0.018) & 13.017 & 0.006\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{Lung cancer; death, n = 442, p = 24}}}\\
+\hline
+\hspace{1em}aorsf-cph & 0.063 (0.032) & 0.691 (0.019) & 0.312 & 0.030\\
+\hspace{1em}aorsf-net & 0.061 (0.030) & 0.685 (0.019) & 30.349 & 0.031\\
+\hspace{1em}aorsf-fast & 0.059 (0.033) & 0.690 (0.019) & 0.124 & 0.029\\
+\hspace{1em}obliqueRSF-net & 0.058 (0.020) & 0.678 (0.020) & 294.626 & 2.961\\
+\hspace{1em}cif-extension & 0.050 (0.018) & 0.667 (0.019) & 9.104 & 3.317\\
+\hspace{1em}rsf-standard & 0.050 (0.035) & 0.673 (0.023) & 0.941 & 0.073\\
+\hspace{1em}cif-standard & 0.050 (0.023) & 0.667 (0.022) & 0.315 & 0.846\\
+\hspace{1em}ranger-extratrees & 0.049 (0.016) & 0.675 (0.019) & 0.037 & 0.065\\
+\hspace{1em}cif-rotate & 0.047 (0.026) & 0.664 (0.021) & 17.129 & 3.089\\
+\hspace{1em}glmnet-cox & 0.041 (0.024) & 0.664 (0.034) & 0.123 & 0.002\\
+\hspace{1em}aorsf-random & 0.040 (0.022) & 0.651 (0.023) & 0.507 & 0.026\\
+\hspace{1em}nn-cox & 0.033 (0.025) & 0.647 (0.029) & 12.472 & 0.368\\
+\hspace{1em}xgboost-cox & 0.018 (0.019) & 0.647 (0.027) & 1.541 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.652 (0.026) & 8.410 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.064 (0.009) & 0.807 (0.010) & 1.254 & 0.359\\
-\hspace{1em}aorsf-net & 0.063 (0.010) & 0.804 (0.010) & 175.507 & 0.380\\
-\hspace{1em}obliqueRSF-net & 0.063 (0.007) & 0.808 (0.009) & 495.036 & 263.736\\
-\hspace{1em}aorsf-cph & 0.061 (0.009) & 0.801 (0.011) & 5.065 & 0.365\\
-\hspace{1em}cif-standard & 0.059 (0.006) & 0.803 (0.010) & 23.165 & 98.928\\
-\hspace{1em}cif-rotate & 0.059 (0.007) & 0.802 (0.010) & 291.147 & 38.590\\
-\hspace{1em}rsf-standard & 0.058 (0.011) & 0.794 (0.011) & 3.497 & 1.115\\
-\hspace{1em}ranger-extratrees & 0.047 (0.004) & 0.794 (0.010) & 8.046 & 7.095\\
-\hspace{1em}cif-extension & 0.047 (0.003) & 0.805 (0.010) & 100.181 & 30.035\\
-\hspace{1em}glmnet-cox & 0.039 (0.016) & 0.775 (0.015) & 4.983 & 0.007\\
-\hspace{1em}nn-cox & 0.034 (0.014) & 0.771 (0.018) & 17.346 & 16.923\\
-\hspace{1em}aorsf-random & 0.031 (0.005) & 0.734 (0.015) & 3.611 & 0.409\\
-\hspace{1em}xgboost-cox & 0.016 (0.022) & 0.804 (0.010) & 4.416 & 0.008\\
-\hspace{1em}xgboost-aft & --- & 0.803 (0.010) & 18.681 & 0.009\\
+\hspace{1em}aorsf-fast & 0.064 (0.009) & 0.807 (0.010) & 1.333 & 0.340\\
+\hspace{1em}aorsf-net & 0.062 (0.010) & 0.805 (0.012) & 169.694 & 0.379\\
+\hspace{1em}obliqueRSF-net & 0.062 (0.008) & 0.808 (0.012) & 488.662 & 265.171\\
+\hspace{1em}aorsf-cph & 0.060 (0.010) & 0.801 (0.012) & 4.935 & 0.352\\
+\hspace{1em}cif-standard & 0.059 (0.007) & 0.803 (0.013) & 24.446 & 98.767\\
+\hspace{1em}cif-rotate & 0.058 (0.009) & 0.802 (0.013) & 284.668 & 37.340\\
+\hspace{1em}rsf-standard & 0.057 (0.012) & 0.795 (0.013) & 3.426 & 1.202\\
+\hspace{1em}ranger-extratrees & 0.047 (0.004) & 0.794 (0.011) & 7.360 & 6.260\\
+\hspace{1em}cif-extension & 0.047 (0.003) & 0.805 (0.013) & 98.278 & 28.773\\
+\hspace{1em}glmnet-cox & 0.038 (0.017) & 0.775 (0.016) & 4.907 & 0.007\\
+\hspace{1em}nn-cox & 0.038 (0.017) & 0.767 (0.021) & 18.380 & 16.712\\
+\hspace{1em}aorsf-random & 0.031 (0.005) & 0.735 (0.015) & 2.853 & 0.387\\
+\hspace{1em}xgboost-cox & 0.015 (0.028) & 0.802 (0.013) & 4.763 & 0.009\\
+\hspace{1em}xgboost-aft & --- & 0.802 (0.012) & 18.127 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.145 (0.008) & 0.792 (0.009) & 304.543 & 0.545\\
-\hspace{1em}aorsf-fast & 0.145 (0.009) & 0.792 (0.009) & 1.769 & 0.625\\
-\hspace{1em}aorsf-cph & 0.143 (0.008) & 0.791 (0.009) & 6.747 & 0.522\\
-\hspace{1em}rsf-standard & 0.141 (0.008) & 0.784 (0.009) & 4.694 & 0.475\\
-\hspace{1em}obliqueRSF-net & 0.140 (0.007) & 0.791 (0.009) & 1154.938 & 154.248\\
-\hspace{1em}nn-cox & 0.134 (0.012) & 0.790 (0.010) & 31.798 & 18.891\\
-\hspace{1em}cif-standard & 0.134 (0.007) & 0.788 (0.009) & 23.348 & 100.276\\
-\hspace{1em}glmnet-cox & 0.129 (0.027) & 0.789 (0.012) & 1.504 & 0.007\\
-\hspace{1em}cif-rotate & 0.126 (0.007) & 0.784 (0.010) & 319.140 & 36.836\\
-\hspace{1em}ranger-extratrees & 0.114 (0.004) & 0.784 (0.008) & 7.843 & 6.084\\
-\hspace{1em}cif-extension & 0.092 (0.003) & 0.781 (0.009) & 110.957 & 30.312\\
-\hspace{1em}aorsf-random & 0.069 (0.004) & 0.725 (0.008) & 5.765 & 0.551\\
-\hspace{1em}xgboost-cox & 0.056 (0.029) & 0.794 (0.009) & 8.347 & 0.009\\
-\hspace{1em}xgboost-aft & --- & 0.793 (0.009) & 21.600 & 0.009\\
+\hspace{1em}aorsf-fast & 0.145 (0.008) & 0.792 (0.008) & 1.868 & 0.487\\
+\hspace{1em}aorsf-net & 0.144 (0.008) & 0.792 (0.009) & 293.640 & 0.547\\
+\hspace{1em}aorsf-cph & 0.143 (0.008) & 0.791 (0.009) & 6.625 & 0.504\\
+\hspace{1em}rsf-standard & 0.140 (0.008) & 0.784 (0.009) & 4.818 & 0.502\\
+\hspace{1em}obliqueRSF-net & 0.139 (0.007) & 0.791 (0.009) & 1176.365 & 156.871\\
+\hspace{1em}cif-standard & 0.134 (0.007) & 0.788 (0.009) & 23.671 & 101.207\\
+\hspace{1em}glmnet-cox & 0.131 (0.026) & 0.789 (0.012) & 1.560 & 0.007\\
+\hspace{1em}nn-cox & 0.127 (0.020) & 0.784 (0.016) & 29.272 & 17.344\\
+\hspace{1em}cif-rotate & 0.126 (0.007) & 0.783 (0.010) & 319.953 & 37.290\\
+\hspace{1em}ranger-extratrees & 0.113 (0.004) & 0.784 (0.008) & 9.060 & 6.474\\
+\hspace{1em}cif-extension & 0.092 (0.003) & 0.781 (0.009) & 111.068 & 32.105\\
+\hspace{1em}aorsf-random & 0.068 (0.005) & 0.725 (0.008) & 5.755 & 0.541\\
+\hspace{1em}xgboost-cox & 0.056 (0.029) & 0.794 (0.009) & 8.021 & 0.009\\
+\hspace{1em}xgboost-aft & --- & 0.793 (0.009) & 20.287 & 0.010\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.114 (0.010) & 0.867 (0.012) & 1.145 & 0.317\\
-\hspace{1em}aorsf-cph & 0.109 (0.011) & 0.860 (0.014) & 4.847 & 0.330\\
-\hspace{1em}rsf-standard & 0.108 (0.011) & 0.857 (0.010) & 3.069 & 1.095\\
-\hspace{1em}obliqueRSF-net & 0.106 (0.008) & 0.870 (0.012) & 403.026 & 336.427\\
-\hspace{1em}cif-rotate & 0.104 (0.010) & 0.870 (0.012) & 262.282 & 37.519\\
-\hspace{1em}cif-standard & 0.102 (0.009) & 0.865 (0.012) & 24.266 & 98.770\\
-\hspace{1em}aorsf-net & 0.099 (0.067) & 0.851 (0.065) & 152.494 & 0.342\\
-\hspace{1em}cif-extension & 0.076 (0.005) & 0.865 (0.011) & 94.286 & 30.425\\
-\hspace{1em}ranger-extratrees & 0.075 (0.005) & 0.849 (0.015) & 7.052 & 6.710\\
-\hspace{1em}nn-cox & 0.071 (0.026) & 0.828 (0.022) & 15.582 & 14.999\\
-\hspace{1em}aorsf-random & 0.063 (0.006) & 0.795 (0.015) & 2.638 & 0.368\\
-\hspace{1em}glmnet-cox & 0.044 (0.044) & 0.761 (0.146) & 3.775 & 0.007\\
-\hspace{1em}xgboost-cox & -0.010 (0.020) & 0.871 (0.009) & 6.431 & 0.009\\
-\hspace{1em}xgboost-aft & --- & 0.872 (0.012) & 20.098 & 0.009\\
+\hspace{1em}aorsf-fast & 0.115 (0.011) & 0.865 (0.012) & 1.218 & 0.301\\
+\hspace{1em}aorsf-net & 0.114 (0.011) & 0.863 (0.013) & 147.441 & 0.338\\
+\hspace{1em}aorsf-cph & 0.109 (0.011) & 0.858 (0.014) & 4.549 & 0.315\\
+\hspace{1em}rsf-standard & 0.108 (0.012) & 0.856 (0.012) & 3.125 & 1.151\\
+\hspace{1em}obliqueRSF-net & 0.108 (0.008) & 0.869 (0.011) & 393.285 & 338.322\\
+\hspace{1em}cif-rotate & 0.105 (0.010) & 0.869 (0.013) & 260.914 & 38.177\\
+\hspace{1em}cif-standard & 0.102 (0.009) & 0.864 (0.013) & 24.344 & 101.534\\
+\hspace{1em}cif-extension & 0.077 (0.005) & 0.864 (0.011) & 94.628 & 30.361\\
+\hspace{1em}ranger-extratrees & 0.075 (0.005) & 0.849 (0.015) & 7.492 & 6.923\\
+\hspace{1em}nn-cox & 0.071 (0.024) & 0.826 (0.016) & 15.797 & 17.312\\
+\hspace{1em}aorsf-random & 0.064 (0.006) & 0.795 (0.014) & 2.377 & 0.355\\
+\hspace{1em}glmnet-cox & 0.043 (0.044) & 0.767 (0.139) & 3.777 & 0.006\\
+\hspace{1em}xgboost-cox & -0.008 (0.019) & 0.869 (0.011) & 6.764 & 0.009\\
+\hspace{1em}xgboost-aft & --- & 0.870 (0.012) & 18.620 & 0.010\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.025 (0.005) & 0.762 (0.017) & 271.158 & 37.410\\
-\hspace{1em}obliqueRSF-net & 0.025 (0.004) & 0.764 (0.016) & 354.662 & 286.074\\
-\hspace{1em}cif-standard & 0.025 (0.004) & 0.760 (0.017) & 23.751 & 98.574\\
-\hspace{1em}aorsf-fast & 0.024 (0.006) & 0.762 (0.015) & 1.095 & 0.311\\
-\hspace{1em}aorsf-cph & 0.023 (0.005) & 0.756 (0.016) & 4.436 & 0.320\\
-\hspace{1em}ranger-extratrees & 0.022 (0.003) & 0.757 (0.015) & 6.801 & 6.789\\
-\hspace{1em}glmnet-cox & 0.021 (0.010) & 0.764 (0.018) & 3.726 & 0.007\\
-\hspace{1em}cif-extension & 0.021 (0.002) & 0.767 (0.018) & 95.584 & 29.197\\
-\hspace{1em}rsf-standard & 0.019 (0.009) & 0.744 (0.018) & 3.147 & 1.066\\
-\hspace{1em}aorsf-net & 0.018 (0.026) & 0.749 (0.043) & 138.878 & 0.330\\
-\hspace{1em}nn-cox & 0.014 (0.010) & 0.725 (0.051) & 17.348 & 20.132\\
-\hspace{1em}aorsf-random & 0.013 (0.003) & 0.711 (0.023) & 2.519 & 0.338\\
-\hspace{1em}xgboost-cox & -0.001 (0.025) & 0.761 (0.018) & 4.044 & 0.008\\
-\hspace{1em}xgboost-aft & --- & 0.763 (0.016) & 17.880 & 0.010\\
+\hspace{1em}obliqueRSF-net & 0.025 (0.004) & 0.767 (0.016) & 357.039 & 299.786\\
+\hspace{1em}cif-rotate & 0.025 (0.004) & 0.764 (0.017) & 268.402 & 37.899\\
+\hspace{1em}cif-standard & 0.025 (0.004) & 0.762 (0.017) & 23.450 & 98.166\\
+\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.764 (0.016) & 1.186 & 0.296\\
+\hspace{1em}aorsf-net & 0.024 (0.006) & 0.759 (0.017) & 134.136 & 0.330\\
+\hspace{1em}aorsf-cph & 0.023 (0.005) & 0.758 (0.016) & 4.128 & 0.305\\
+\hspace{1em}ranger-extratrees & 0.022 (0.003) & 0.759 (0.016) & 7.610 & 6.738\\
+\hspace{1em}glmnet-cox & 0.021 (0.009) & 0.765 (0.017) & 3.876 & 0.007\\
+\hspace{1em}cif-extension & 0.021 (0.002) & 0.768 (0.017) & 94.913 & 29.730\\
+\hspace{1em}rsf-standard & 0.019 (0.009) & 0.745 (0.018) & 3.221 & 1.242\\
+\hspace{1em}nn-cox & 0.018 (0.007) & 0.746 (0.028) & 16.152 & 17.979\\
+\hspace{1em}aorsf-random & 0.013 (0.003) & 0.714 (0.022) & 2.275 & 0.330\\
+\hspace{1em}xgboost-cox & 0.000 (0.025) & 0.762 (0.018) & 4.347 & 0.008\\
+\hspace{1em}xgboost-aft & --- & 0.764 (0.015) & 16.257 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.159 (0.019) & 0.744 (0.015) & 15.254 & 4.543\\
-\hspace{1em}aorsf-cph & 0.157 (0.016) & 0.742 (0.011) & 1.155 & 0.087\\
-\hspace{1em}aorsf-fast & 0.156 (0.016) & 0.742 (0.011) & 0.393 & 0.088\\
-\hspace{1em}obliqueRSF-net & 0.155 (0.013) & 0.743 (0.011) & 229.681 & 12.810\\
-\hspace{1em}aorsf-net & 0.154 (0.015) & 0.741 (0.011) & 88.452 & 0.086\\
-\hspace{1em}cif-standard & 0.150 (0.015) & 0.738 (0.012) & 0.989 & 5.746\\
-\hspace{1em}rsf-standard & 0.150 (0.017) & 0.736 (0.011) & 2.022 & 0.201\\
-\hspace{1em}aorsf-random & 0.145 (0.014) & 0.734 (0.012) & 1.762 & 0.082\\
-\hspace{1em}cif-extension & 0.143 (0.010) & 0.747 (0.013) & 10.829 & 4.681\\
-\hspace{1em}glmnet-cox & 0.139 (0.021) & 0.728 (0.014) & 0.118 & 0.003\\
-\hspace{1em}xgboost-cox & 0.123 (0.012) & 0.733 (0.012) & 3.847 & 0.003\\
-\hspace{1em}ranger-extratrees & 0.115 (0.005) & 0.744 (0.012) & 0.060 & 0.184\\
-\hspace{1em}nn-cox & 0.028 (0.043) & 0.606 (0.100) & 15.492 & 0.691\\
-\hspace{1em}xgboost-aft & --- & 0.733 (0.013) & 12.513 & 0.006\\
+\hspace{1em}cif-rotate & 0.159 (0.019) & 0.744 (0.014) & 15.123 & 4.858\\
+\hspace{1em}aorsf-cph & 0.158 (0.016) & 0.743 (0.011) & 2.035 & 0.087\\
+\hspace{1em}aorsf-fast & 0.157 (0.016) & 0.743 (0.011) & 1.266 & 0.086\\
+\hspace{1em}aorsf-net & 0.155 (0.016) & 0.741 (0.011) & 84.984 & 0.088\\
+\hspace{1em}obliqueRSF-net & 0.155 (0.013) & 0.743 (0.011) & 232.467 & 12.924\\
+\hspace{1em}cif-standard & 0.151 (0.015) & 0.738 (0.012) & 1.537 & 5.829\\
+\hspace{1em}rsf-standard & 0.151 (0.017) & 0.737 (0.011) & 2.281 & 0.194\\
+\hspace{1em}aorsf-random & 0.146 (0.013) & 0.735 (0.011) & 2.457 & 0.082\\
+\hspace{1em}cif-extension & 0.143 (0.009) & 0.747 (0.013) & 11.222 & 4.744\\
+\hspace{1em}glmnet-cox & 0.137 (0.021) & 0.726 (0.014) & 0.136 & 0.003\\
+\hspace{1em}xgboost-cox & 0.122 (0.012) & 0.733 (0.012) & 3.919 & 0.003\\
+\hspace{1em}ranger-extratrees & 0.115 (0.005) & 0.744 (0.012) & 0.064 & 0.181\\
+\hspace{1em}nn-cox & 0.034 (0.057) & 0.599 (0.112) & 16.529 & 0.689\\
+\hspace{1em}xgboost-aft & --- & 0.733 (0.013) & 12.094 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.015 (0.012) & 0.648 (0.058) & 0.104 & 0.002\\
-\hspace{1em}aorsf-cph & 0.010 (0.011) & 0.644 (0.033) & 0.592 & 0.041\\
-\hspace{1em}aorsf-fast & 0.010 (0.012) & 0.640 (0.033) & 0.192 & 0.042\\
-\hspace{1em}ranger-extratrees & 0.008 (0.006) & 0.642 (0.031) & 0.050 & 0.175\\
-\hspace{1em}cif-extension & 0.008 (0.008) & 0.625 (0.025) & 8.953 & 4.503\\
-\hspace{1em}aorsf-net & 0.007 (0.012) & 0.641 (0.031) & 22.912 & 0.042\\
-\hspace{1em}aorsf-random & 0.007 (0.013) & 0.634 (0.032) & 0.510 & 0.041\\
-\hspace{1em}cif-standard & 0.006 (0.009) & 0.625 (0.028) & 1.137 & 6.173\\
-\hspace{1em}xgboost-cox & 0.005 (0.017) & 0.638 (0.038) & 1.774 & 0.003\\
-\hspace{1em}obliqueRSF-net & 0.003 (0.022) & 0.624 (0.038) & 41.561 & 16.686\\
-\hspace{1em}nn-cox & -0.003 (0.006) & 0.507 (0.055) & 10.592 & 0.704\\
-\hspace{1em}rsf-standard & -0.010 (0.015) & 0.614 (0.029) & 0.744 & 0.074\\
-\hspace{1em}cif-rotate & -0.024 (0.022) & 0.550 (0.032) & 12.665 & 4.579\\
-\hspace{1em}xgboost-aft & --- & 0.627 (0.039) & 11.031 & 0.006\\
+\hspace{1em}glmnet-cox & 0.015 (0.011) & 0.651 (0.055) & 0.118 & 0.003\\
+\hspace{1em}aorsf-cph & 0.011 (0.013) & 0.644 (0.036) & 0.568 & 0.040\\
+\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.642 (0.036) & 0.193 & 0.040\\
+\hspace{1em}ranger-extratrees & 0.008 (0.006) & 0.642 (0.030) & 0.095 & 0.177\\
+\hspace{1em}cif-extension & 0.008 (0.010) & 0.625 (0.028) & 9.141 & 4.788\\
+\hspace{1em}obliqueRSF-net & 0.007 (0.010) & 0.628 (0.033) & 41.856 & 16.910\\
+\hspace{1em}aorsf-net & 0.007 (0.014) & 0.641 (0.034) & 22.236 & 0.041\\
+\hspace{1em}aorsf-random & 0.007 (0.013) & 0.633 (0.033) & 1.329 & 0.039\\
+\hspace{1em}xgboost-cox & 0.007 (0.017) & 0.639 (0.039) & 1.783 & 0.003\\
+\hspace{1em}cif-standard & 0.006 (0.011) & 0.628 (0.033) & 1.689 & 5.603\\
+\hspace{1em}nn-cox & -0.003 (0.005) & 0.510 (0.032) & 11.229 & 0.597\\
+\hspace{1em}rsf-standard & -0.009 (0.018) & 0.616 (0.036) & 0.824 & 0.073\\
+\hspace{1em}cif-rotate & -0.024 (0.023) & 0.553 (0.035) & 12.975 & 4.603\\
+\hspace{1em}xgboost-aft & --- & 0.629 (0.039) & 10.748 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.635 (0.025) & 0.943 (0.007) & 19.464 & 3.497\\
-\hspace{1em}glmnet-cox & 0.616 (0.036) & 0.940 (0.009) & 0.179 & 0.002\\
-\hspace{1em}aorsf-net & 0.529 (0.029) & 0.928 (0.011) & 51.788 & 0.044\\
-\hspace{1em}aorsf-cph & 0.520 (0.024) & 0.925 (0.011) & 0.783 & 0.042\\
-\hspace{1em}rsf-standard & 0.518 (0.022) & 0.922 (0.011) & 1.324 & 0.103\\
-\hspace{1em}aorsf-fast & 0.514 (0.028) & 0.922 (0.013) & 0.216 & 0.043\\
-\hspace{1em}xgboost-cox & 0.514 (0.029) & 0.932 (0.009) & 13.877 & 0.004\\
-\hspace{1em}nn-cox & 0.512 (0.068) & 0.901 (0.027) & 17.133 & 0.681\\
-\hspace{1em}cif-standard & 0.469 (0.028) & 0.901 (0.018) & 0.375 & 1.238\\
-\hspace{1em}cif-extension & 0.452 (0.026) & 0.919 (0.013) & 9.070 & 3.976\\
-\hspace{1em}ranger-extratrees & 0.428 (0.026) & 0.898 (0.019) & 0.047 & 0.108\\
-\hspace{1em}obliqueRSF-net & 0.318 (0.023) & 0.908 (0.018) & 156.326 & 9.034\\
-\hspace{1em}aorsf-random & 0.299 (0.033) & 0.849 (0.029) & 0.901 & 0.039\\
-\hspace{1em}xgboost-aft & --- & 0.927 (0.010) & 35.252 & 0.007\\
+\hspace{1em}cif-rotate & 0.636 (0.024) & 0.943 (0.007) & 19.879 & 3.571\\
+\hspace{1em}glmnet-cox & 0.618 (0.034) & 0.940 (0.009) & 0.204 & 0.002\\
+\hspace{1em}nn-cox & 0.534 (0.072) & 0.910 (0.027) & 17.266 & 0.663\\
+\hspace{1em}aorsf-net & 0.530 (0.028) & 0.928 (0.010) & 50.081 & 0.045\\
+\hspace{1em}aorsf-cph & 0.522 (0.024) & 0.925 (0.011) & 1.645 & 0.043\\
+\hspace{1em}rsf-standard & 0.519 (0.022) & 0.922 (0.010) & 1.631 & 0.106\\
+\hspace{1em}aorsf-fast & 0.517 (0.027) & 0.923 (0.012) & 1.090 & 0.042\\
+\hspace{1em}xgboost-cox & 0.512 (0.029) & 0.932 (0.009) & 13.972 & 0.004\\
+\hspace{1em}cif-standard & 0.472 (0.029) & 0.902 (0.018) & 0.453 & 1.910\\
+\hspace{1em}cif-extension & 0.454 (0.025) & 0.920 (0.013) & 8.854 & 3.924\\
+\hspace{1em}ranger-extratrees & 0.430 (0.025) & 0.900 (0.019) & 0.049 & 0.103\\
+\hspace{1em}obliqueRSF-net & 0.319 (0.022) & 0.909 (0.017) & 155.421 & 8.847\\
+\hspace{1em}aorsf-random & 0.300 (0.032) & 0.849 (0.027) & 1.681 & 0.039\\
+\hspace{1em}xgboost-aft & --- & 0.927 (0.010) & 33.545 & 0.008\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{NCCTG Lung Cancer; death, n = 228, p = 9}}}\\
+\hline
+\hspace{1em}aorsf-random & 0.076 (0.030) & 0.686 (0.026) & 1.162 & 0.016\\
+\hspace{1em}ranger-extratrees & 0.062 (0.028) & 0.675 (0.033) & 0.023 & 0.031\\
+\hspace{1em}aorsf-fast & 0.061 (0.043) & 0.672 (0.025) & 0.066 & 0.016\\
+\hspace{1em}obliqueRSF-net & 0.058 (0.026) & 0.676 (0.029) & 106.084 & 1.468\\
+\hspace{1em}aorsf-cph & 0.058 (0.041) & 0.670 (0.024) & 0.153 & 0.016\\
+\hspace{1em}cif-standard & 0.055 (0.032) & 0.670 (0.030) & 0.130 & 0.252\\
+\hspace{1em}cif-extension & 0.051 (0.032) & 0.664 (0.029) & 3.799 & 1.502\\
+\hspace{1em}aorsf-net & 0.047 (0.040) & 0.668 (0.026) & 16.124 & 0.017\\
+\hspace{1em}glmnet-cox & 0.033 (0.031) & 0.638 (0.059) & 0.081 & 0.002\\
+\hspace{1em}rsf-standard & 0.023 (0.039) & 0.642 (0.025) & 0.087 & 0.037\\
+\hspace{1em}cif-rotate & 0.017 (0.041) & 0.632 (0.032) & 4.687 & 1.897\\
+\hspace{1em}xgboost-cox & 0.011 (0.023) & 0.648 (0.032) & 0.721 & 0.002\\
+\hspace{1em}nn-cox & -0.051 (0.163) & 0.512 (0.082) & 10.516 & 0.209\\
+\hspace{1em}xgboost-aft & --- & 0.637 (0.034) & 6.271 & 0.005\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textit{\textbf{NKI 70 gene signature; death or metastasis, n = 144, p = 77}}}\\
+\hline
+\hspace{1em}aorsf-net & 0.142 (0.056) & 0.804 (0.056) & 10.521 & 0.014\\
+\hspace{1em}aorsf-cph & 0.124 (0.049) & 0.802 (0.051) & 0.076 & 0.013\\
+\hspace{1em}aorsf-fast & 0.121 (0.052) & 0.802 (0.054) & 0.049 & 0.014\\
+\hspace{1em}cif-rotate & 0.118 (0.059) & 0.787 (0.049) & 27.382 & 3.379\\
+\hspace{1em}obliqueRSF-net & 0.106 (0.051) & 0.792 (0.061) & 79.059 & 0.558\\
+\hspace{1em}cif-extension & 0.098 (0.055) & 0.799 (0.061) & 8.595 & 3.554\\
+\hspace{1em}cif-standard & 0.088 (0.051) & 0.781 (0.065) & 0.145 & 0.149\\
+\hspace{1em}rsf-standard & 0.087 (0.048) & 0.755 (0.050) & 0.067 & 0.025\\
+\hspace{1em}ranger-extratrees & 0.064 (0.044) & 0.774 (0.054) & 0.024 & 0.030\\
+\hspace{1em}aorsf-random & 0.053 (0.045) & 0.741 (0.060) & 0.136 & 0.014\\
+\hspace{1em}nn-cox & 0.051 (0.102) & 0.715 (0.100) & 11.692 & 0.121\\
+\hspace{1em}glmnet-cox & 0.049 (0.064) & 0.726 (0.090) & 0.265 & 0.002\\
+\hspace{1em}xgboost-cox & -0.028 (0.029) & 0.566 (0.093) & 0.118 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.770 (0.056) & 4.896 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.214 (0.008) & 0.869 (0.005) & 17.839 & 1.266\\
-\hspace{1em}aorsf-fast & 0.213 (0.008) & 0.870 (0.005) & 4.838 & 1.314\\
-\hspace{1em}aorsf-net & 0.211 (0.007) & 0.865 (0.006) & 453.851 & 1.297\\
-\hspace{1em}obliqueRSF-net & 0.210 (0.008) & 0.869 (0.005) & 1414.334 & 1054.087\\
-\hspace{1em}rsf-standard & 0.208 (0.009) & 0.860 (0.005) & 9.897 & 1.177\\
-\hspace{1em}glmnet-cox & 0.207 (0.010) & 0.861 (0.005) & 1.745 & 0.012\\
-\hspace{1em}cif-standard & 0.206 (0.007) & 0.864 (0.006) & 67.606 & 629.975\\
-\hspace{1em}cif-rotate & 0.191 (0.007) & 0.866 (0.005) & 262.207 & 61.085\\
-\hspace{1em}ranger-extratrees & 0.181 (0.007) & 0.861 (0.005) & 37.518 & 96.239\\
-\hspace{1em}cif-extension & 0.167 (0.003) & 0.867 (0.006) & 125.152 & 53.538\\
-\hspace{1em}aorsf-random & 0.141 (0.007) & 0.840 (0.006) & 9.678 & 1.364\\
-\hspace{1em}xgboost-cox & 0.021 (0.015) & 0.877 (0.005) & 9.002 & 0.018\\
-\hspace{1em}nn-cox & 0.000 (0.000) & 0.555 (0.092) & 21.841 & 115.006\\
-\hspace{1em}xgboost-aft & --- & 0.875 (0.005) & 29.487 & 0.014\\
+\hspace{1em}aorsf-cph & 0.213 (0.008) & 0.868 (0.005) & 16.251 & 2.106\\
+\hspace{1em}aorsf-fast & 0.212 (0.008) & 0.868 (0.005) & 4.412 & 2.014\\
+\hspace{1em}aorsf-net & 0.210 (0.008) & 0.864 (0.006) & 433.878 & 1.276\\
+\hspace{1em}obliqueRSF-net & 0.209 (0.008) & 0.868 (0.006) & 1428.698 & 1042.701\\
+\hspace{1em}rsf-standard & 0.207 (0.009) & 0.860 (0.005) & 10.516 & 1.205\\
+\hspace{1em}glmnet-cox & 0.207 (0.011) & 0.860 (0.005) & 1.345 & 0.012\\
+\hspace{1em}cif-standard & 0.205 (0.007) & 0.863 (0.006) & 67.597 & 624.624\\
+\hspace{1em}cif-rotate & 0.190 (0.008) & 0.865 (0.005) & 263.660 & 62.919\\
+\hspace{1em}ranger-extratrees & 0.181 (0.007) & 0.860 (0.005) & 39.632 & 80.768\\
+\hspace{1em}cif-extension & 0.166 (0.003) & 0.866 (0.006) & 125.288 & 53.237\\
+\hspace{1em}aorsf-random & 0.140 (0.006) & 0.838 (0.007) & 8.961 & 1.333\\
+\hspace{1em}xgboost-cox & 0.020 (0.015) & 0.876 (0.005) & 8.907 & 0.017\\
+\hspace{1em}nn-cox & -0.002 (0.009) & 0.565 (0.092) & 20.937 & 106.131\\
+\hspace{1em}xgboost-aft & --- & 0.875 (0.005) & 27.908 & 0.015\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.431 (0.033) & 0.907 (0.022) & 0.069 & 0.018\\
-\hspace{1em}aorsf-cph & 0.419 (0.034) & 0.905 (0.022) & 0.152 & 0.018\\
-\hspace{1em}cif-rotate & 0.403 (0.042) & 0.897 (0.022) & 9.844 & 2.217\\
-\hspace{1em}aorsf-net & 0.396 (0.078) & 0.899 (0.031) & 14.684 & 0.019\\
-\hspace{1em}rsf-standard & 0.393 (0.036) & 0.894 (0.024) & 0.094 & 0.038\\
-\hspace{1em}obliqueRSF-net & 0.369 (0.034) & 0.905 (0.023) & 110.615 & 1.764\\
-\hspace{1em}aorsf-random & 0.356 (0.029) & 0.894 (0.021) & 0.286 & 0.019\\
-\hspace{1em}cif-standard & 0.351 (0.035) & 0.902 (0.026) & 0.186 & 0.363\\
-\hspace{1em}cif-extension & 0.348 (0.035) & 0.899 (0.024) & 5.248 & 2.252\\
-\hspace{1em}glmnet-cox & 0.340 (0.047) & 0.885 (0.029) & 0.115 & 0.002\\
-\hspace{1em}ranger-extratrees & 0.275 (0.028) & 0.893 (0.027) & 0.028 & 0.037\\
-\hspace{1em}xgboost-cox & 0.249 (0.106) & 0.878 (0.026) & 4.873 & 0.003\\
-\hspace{1em}nn-cox & -0.017 (0.017) & 0.551 (0.130) & 10.566 & 0.240\\
-\hspace{1em}xgboost-aft & --- & 0.882 (0.024) & 10.124 & 0.006\\
+\hspace{1em}aorsf-fast & 0.430 (0.032) & 0.908 (0.021) & 0.067 & 0.018\\
+\hspace{1em}aorsf-cph & 0.418 (0.034) & 0.906 (0.021) & 0.149 & 0.018\\
+\hspace{1em}aorsf-net & 0.413 (0.035) & 0.905 (0.021) & 14.298 & 0.020\\
+\hspace{1em}cif-rotate & 0.405 (0.040) & 0.899 (0.022) & 10.102 & 1.933\\
+\hspace{1em}rsf-standard & 0.392 (0.034) & 0.895 (0.023) & 0.113 & 0.038\\
+\hspace{1em}obliqueRSF-net & 0.369 (0.032) & 0.907 (0.022) & 111.656 & 1.787\\
+\hspace{1em}aorsf-random & 0.354 (0.031) & 0.893 (0.020) & 1.093 & 0.018\\
+\hspace{1em}cif-standard & 0.352 (0.034) & 0.904 (0.025) & 0.206 & 0.363\\
+\hspace{1em}cif-extension & 0.348 (0.033) & 0.901 (0.023) & 5.775 & 2.199\\
+\hspace{1em}glmnet-cox & 0.342 (0.044) & 0.886 (0.028) & 0.116 & 0.002\\
+\hspace{1em}ranger-extratrees & 0.277 (0.027) & 0.894 (0.027) & 0.029 & 0.038\\
+\hspace{1em}xgboost-cox & 0.256 (0.103) & 0.881 (0.027) & 4.960 & 0.003\\
+\hspace{1em}nn-cox & -0.017 (0.018) & 0.563 (0.124) & 11.751 & 0.247\\
+\hspace{1em}xgboost-aft & --- & 0.883 (0.024) & 9.644 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.165 (0.012) & 0.761 (0.009) & 156.780 & 0.189\\
-\hspace{1em}obliqueRSF-net & 0.162 (0.010) & 0.760 (0.009) & 449.043 & 37.754\\
-\hspace{1em}aorsf-cph & 0.162 (0.012) & 0.758 (0.009) & 2.515 & 0.198\\
-\hspace{1em}aorsf-fast & 0.159 (0.013) & 0.756 (0.009) & 0.796 & 0.198\\
-\hspace{1em}cif-standard & 0.159 (0.011) & 0.758 (0.009) & 4.650 & 22.504\\
-\hspace{1em}rsf-standard & 0.157 (0.014) & 0.755 (0.009) & 2.710 & 0.802\\
-\hspace{1em}aorsf-random & 0.153 (0.011) & 0.751 (0.010) & 2.990 & 0.184\\
-\hspace{1em}cif-rotate & 0.148 (0.012) & 0.751 (0.012) & 34.249 & 8.476\\
-\hspace{1em}ranger-extratrees & 0.138 (0.006) & 0.748 (0.009) & 2.921 & 2.599\\
-\hspace{1em}xgboost-cox & 0.131 (0.013) & 0.753 (0.010) & 3.742 & 0.004\\
-\hspace{1em}cif-extension & 0.130 (0.004) & 0.751 (0.009) & 22.114 & 8.625\\
-\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.732 (0.009) & 0.212 & 0.004\\
-\hspace{1em}nn-cox & -0.032 (0.092) & 0.513 (0.042) & 16.455 & 8.672\\
-\hspace{1em}xgboost-aft & --- & 0.760 (0.009) & 14.327 & 0.007\\
+\hspace{1em}aorsf-net & 0.166 (0.012) & 0.762 (0.009) & 145.278 & 0.191\\
+\hspace{1em}obliqueRSF-net & 0.163 (0.010) & 0.761 (0.009) & 439.210 & 37.683\\
+\hspace{1em}aorsf-cph & 0.163 (0.012) & 0.759 (0.009) & 3.388 & 0.195\\
+\hspace{1em}aorsf-fast & 0.160 (0.013) & 0.757 (0.010) & 1.684 & 0.194\\
+\hspace{1em}cif-standard & 0.159 (0.010) & 0.759 (0.009) & 4.629 & 22.523\\
+\hspace{1em}rsf-standard & 0.159 (0.014) & 0.756 (0.009) & 3.066 & 0.967\\
+\hspace{1em}aorsf-random & 0.153 (0.010) & 0.752 (0.010) & 3.554 & 0.181\\
+\hspace{1em}cif-rotate & 0.147 (0.011) & 0.751 (0.011) & 34.328 & 8.629\\
+\hspace{1em}ranger-extratrees & 0.139 (0.006) & 0.749 (0.009) & 3.498 & 2.152\\
+\hspace{1em}xgboost-cox & 0.130 (0.014) & 0.753 (0.010) & 4.068 & 0.004\\
+\hspace{1em}cif-extension & 0.129 (0.004) & 0.751 (0.008) & 22.740 & 8.982\\
+\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.731 (0.009) & 0.278 & 0.004\\
+\hspace{1em}nn-cox & -0.009 (0.042) & 0.531 (0.050) & 16.635 & 8.901\\
+\hspace{1em}xgboost-aft & --- & 0.761 (0.009) & 14.813 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.148 (0.011) & 0.737 (0.010) & 529.355 & 39.185\\
-\hspace{1em}aorsf-net & 0.146 (0.012) & 0.735 (0.009) & 166.455 & 0.193\\
-\hspace{1em}cif-standard & 0.144 (0.011) & 0.734 (0.009) & 4.545 & 22.929\\
-\hspace{1em}aorsf-cph & 0.144 (0.012) & 0.734 (0.009) & 2.760 & 0.211\\
-\hspace{1em}aorsf-fast & 0.143 (0.012) & 0.733 (0.009) & 0.872 & 0.210\\
-\hspace{1em}aorsf-random & 0.140 (0.011) & 0.730 (0.009) & 3.281 & 0.190\\
-\hspace{1em}rsf-standard & 0.138 (0.012) & 0.731 (0.009) & 2.861 & 0.846\\
-\hspace{1em}ranger-extratrees & 0.135 (0.007) & 0.734 (0.009) & 2.765 & 2.677\\
-\hspace{1em}cif-rotate & 0.129 (0.010) & 0.725 (0.009) & 36.702 & 8.632\\
-\hspace{1em}cif-extension & 0.119 (0.006) & 0.731 (0.009) & 22.734 & 8.788\\
-\hspace{1em}glmnet-cox & 0.117 (0.008) & 0.727 (0.009) & 0.227 & 0.004\\
-\hspace{1em}xgboost-cox & 0.114 (0.008) & 0.729 (0.009) & 3.255 & 0.004\\
-\hspace{1em}nn-cox & -0.011 (0.030) & 0.500 (0.055) & 17.957 & 9.371\\
-\hspace{1em}xgboost-aft & --- & 0.735 (0.009) & 14.774 & 0.007\\
+\hspace{1em}obliqueRSF-net & 0.148 (0.010) & 0.737 (0.009) & 520.813 & 39.774\\
+\hspace{1em}aorsf-net & 0.146 (0.011) & 0.735 (0.009) & 155.933 & 0.198\\
+\hspace{1em}aorsf-cph & 0.145 (0.012) & 0.734 (0.008) & 3.589 & 0.206\\
+\hspace{1em}cif-standard & 0.144 (0.011) & 0.734 (0.009) & 4.807 & 23.027\\
+\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 1.760 & 0.204\\
+\hspace{1em}aorsf-random & 0.140 (0.010) & 0.730 (0.008) & 3.803 & 0.185\\
+\hspace{1em}rsf-standard & 0.139 (0.012) & 0.731 (0.008) & 3.003 & 1.000\\
+\hspace{1em}ranger-extratrees & 0.135 (0.007) & 0.734 (0.009) & 3.564 & 2.555\\
+\hspace{1em}cif-rotate & 0.129 (0.010) & 0.725 (0.009) & 36.519 & 8.483\\
+\hspace{1em}cif-extension & 0.119 (0.006) & 0.731 (0.008) & 23.055 & 8.825\\
+\hspace{1em}glmnet-cox & 0.117 (0.008) & 0.727 (0.008) & 0.258 & 0.004\\
+\hspace{1em}xgboost-cox & 0.113 (0.008) & 0.729 (0.009) & 3.628 & 0.004\\
+\hspace{1em}nn-cox & -0.007 (0.027) & 0.511 (0.045) & 17.722 & 7.825\\
+\hspace{1em}xgboost-aft & --- & 0.735 (0.009) & 14.317 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.250 (0.014) & 0.826 (0.008) & 2.028 & 0.592\\
-\hspace{1em}aorsf-cph & 0.250 (0.014) & 0.825 (0.008) & 6.526 & 0.593\\
-\hspace{1em}glmnet-cox & 0.247 (0.012) & 0.820 (0.007) & 0.486 & 0.006\\
-\hspace{1em}obliqueRSF-net & 0.247 (0.012) & 0.821 (0.008) & 1094.380 & 148.463\\
-\hspace{1em}aorsf-net & 0.246 (0.024) & 0.821 (0.014) & 293.468 & 0.566\\
-\hspace{1em}ranger-extratrees & 0.243 (0.009) & 0.820 (0.007) & 9.981 & 11.444\\
-\hspace{1em}rsf-standard & 0.243 (0.014) & 0.815 (0.008) & 4.619 & 0.561\\
-\hspace{1em}cif-standard & 0.243 (0.011) & 0.818 (0.008) & 19.411 & 119.478\\
-\hspace{1em}aorsf-random & 0.232 (0.012) & 0.817 (0.008) & 6.725 & 0.570\\
-\hspace{1em}cif-rotate & 0.227 (0.008) & 0.819 (0.007) & 65.281 & 21.263\\
-\hspace{1em}cif-extension & 0.201 (0.005) & 0.820 (0.008) & 39.592 & 20.428\\
-\hspace{1em}xgboost-cox & 0.094 (0.040) & 0.823 (0.008) & 5.798 & 0.008\\
-\hspace{1em}nn-cox & 0.001 (0.006) & 0.591 (0.114) & 23.551 & 26.323\\
-\hspace{1em}xgboost-aft & --- & 0.823 (0.008) & 18.228 & 0.009\\
+\hspace{1em}aorsf-fast & 0.250 (0.014) & 0.825 (0.007) & 2.956 & 0.566\\
+\hspace{1em}aorsf-cph & 0.250 (0.013) & 0.825 (0.008) & 7.220 & 0.575\\
+\hspace{1em}aorsf-net & 0.250 (0.012) & 0.823 (0.008) & 267.989 & 0.565\\
+\hspace{1em}glmnet-cox & 0.248 (0.012) & 0.820 (0.007) & 0.539 & 0.006\\
+\hspace{1em}obliqueRSF-net & 0.247 (0.011) & 0.821 (0.008) & 1113.284 & 151.041\\
+\hspace{1em}ranger-extratrees & 0.243 (0.009) & 0.820 (0.007) & 12.743 & 12.085\\
+\hspace{1em}cif-standard & 0.243 (0.011) & 0.818 (0.008) & 19.565 & 120.023\\
+\hspace{1em}rsf-standard & 0.243 (0.013) & 0.815 (0.008) & 5.399 & 0.585\\
+\hspace{1em}aorsf-random & 0.231 (0.012) & 0.816 (0.008) & 6.409 & 0.562\\
+\hspace{1em}cif-rotate & 0.228 (0.009) & 0.819 (0.007) & 65.379 & 21.402\\
+\hspace{1em}cif-extension & 0.201 (0.005) & 0.820 (0.008) & 41.381 & 20.976\\
+\hspace{1em}xgboost-cox & 0.094 (0.038) & 0.824 (0.007) & 5.927 & 0.008\\
+\hspace{1em}nn-cox & 0.002 (0.005) & 0.616 (0.122) & 26.319 & 26.895\\
+\hspace{1em}xgboost-aft & --- & 0.823 (0.008) & 18.504 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.070 (0.011) & 0.794 (0.010) & 13.586 & 0.010\\
-\hspace{1em}aorsf-net & 0.070 (0.007) & 0.796 (0.011) & 348.986 & 0.675\\
-\hspace{1em}aorsf-fast & 0.069 (0.006) & 0.796 (0.011) & 2.415 & 0.604\\
-\hspace{1em}aorsf-cph & 0.069 (0.006) & 0.796 (0.011) & 9.014 & 0.612\\
-\hspace{1em}obliqueRSF-net & 0.067 (0.005) & 0.797 (0.012) & 1014.547 & 425.668\\
-\hspace{1em}rsf-standard & 0.064 (0.007) & 0.787 (0.014) & 4.574 & 1.245\\
-\hspace{1em}cif-standard & 0.061 (0.004) & 0.797 (0.011) & 51.137 & 182.954\\
-\hspace{1em}cif-rotate & 0.061 (0.005) & 0.789 (0.012) & 971.559 & 115.147\\
-\hspace{1em}ranger-extratrees & 0.054 (0.003) & 0.791 (0.012) & 7.589 & 8.207\\
-\hspace{1em}nn-cox & 0.036 (0.020) & 0.767 (0.019) & 21.632 & 28.604\\
-\hspace{1em}cif-extension & 0.034 (0.002) & 0.788 (0.011) & 124.094 & 32.778\\
-\hspace{1em}aorsf-random & 0.026 (0.003) & 0.746 (0.017) & 5.745 & 0.743\\
-\hspace{1em}xgboost-cox & 0.007 (0.018) & 0.798 (0.011) & 6.861 & 0.014\\
-\hspace{1em}xgboost-aft & --- & 0.794 (0.012) & 21.141 & 0.013\\
+\hspace{1em}glmnet-cox & 0.071 (0.011) & 0.795 (0.011) & 13.850 & 0.011\\
+\hspace{1em}aorsf-net & 0.070 (0.007) & 0.796 (0.011) & 330.532 & 0.613\\
+\hspace{1em}aorsf-fast & 0.070 (0.006) & 0.797 (0.010) & 2.561 & 0.604\\
+\hspace{1em}aorsf-cph & 0.069 (0.006) & 0.797 (0.011) & 8.283 & 0.620\\
+\hspace{1em}obliqueRSF-net & 0.068 (0.005) & 0.798 (0.012) & 1017.350 & 425.134\\
+\hspace{1em}rsf-standard & 0.065 (0.007) & 0.788 (0.014) & 3.894 & 1.314\\
+\hspace{1em}cif-standard & 0.061 (0.003) & 0.798 (0.011) & 50.694 & 181.616\\
+\hspace{1em}cif-rotate & 0.060 (0.005) & 0.791 (0.012) & 930.893 & 113.261\\
+\hspace{1em}ranger-extratrees & 0.054 (0.003) & 0.791 (0.012) & 7.314 & 7.943\\
+\hspace{1em}nn-cox & 0.039 (0.018) & 0.764 (0.027) & 20.414 & 24.555\\
+\hspace{1em}cif-extension & 0.034 (0.002) & 0.789 (0.011) & 122.779 & 33.342\\
+\hspace{1em}aorsf-random & 0.026 (0.002) & 0.747 (0.016) & 5.282 & 0.708\\
+\hspace{1em}xgboost-cox & 0.006 (0.017) & 0.799 (0.011) & 6.888 & 0.013\\
+\hspace{1em}xgboost-aft & --- & 0.796 (0.012) & 20.126 & 0.012\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.122 (0.011) & 0.770 (0.010) & 5.120 & 0.011\\
-\hspace{1em}aorsf-cph & 0.116 (0.008) & 0.770 (0.009) & 13.398 & 1.453\\
-\hspace{1em}aorsf-fast & 0.116 (0.008) & 0.770 (0.008) & 3.686 & 1.431\\
-\hspace{1em}aorsf-net & 0.113 (0.009) & 0.768 (0.009) & 609.415 & 0.984\\
-\hspace{1em}obliqueRSF-net & 0.112 (0.007) & 0.767 (0.008) & 2609.859 & 237.782\\
-\hspace{1em}rsf-standard & 0.110 (0.007) & 0.762 (0.009) & 6.441 & 0.687\\
-\hspace{1em}cif-standard & 0.106 (0.006) & 0.764 (0.008) & 49.213 & 190.044\\
-\hspace{1em}nn-cox & 0.098 (0.010) & 0.757 (0.010) & 36.524 & 31.856\\
-\hspace{1em}ranger-extratrees & 0.096 (0.005) & 0.756 (0.009) & 10.926 & 9.128\\
-\hspace{1em}cif-rotate & 0.090 (0.006) & 0.745 (0.009) & 1072.994 & 115.077\\
-\hspace{1em}cif-extension & 0.055 (0.002) & 0.746 (0.009) & 136.086 & 33.237\\
-\hspace{1em}aorsf-random & 0.052 (0.003) & 0.719 (0.009) & 9.318 & 1.018\\
-\hspace{1em}xgboost-cox & 0.030 (0.024) & 0.772 (0.008) & 9.349 & 0.013\\
-\hspace{1em}xgboost-aft & --- & 0.771 (0.008) & 26.417 & 0.014\\
+\hspace{1em}glmnet-cox & 0.123 (0.012) & 0.771 (0.009) & 5.422 & 0.010\\
+\hspace{1em}aorsf-cph & 0.117 (0.008) & 0.770 (0.008) & 11.811 & 1.833\\
+\hspace{1em}aorsf-fast & 0.115 (0.009) & 0.769 (0.008) & 3.826 & 1.817\\
+\hspace{1em}aorsf-net & 0.113 (0.009) & 0.769 (0.009) & 587.892 & 0.933\\
+\hspace{1em}obliqueRSF-net & 0.112 (0.007) & 0.767 (0.008) & 2630.588 & 231.667\\
+\hspace{1em}rsf-standard & 0.110 (0.008) & 0.763 (0.009) & 6.407 & 0.663\\
+\hspace{1em}cif-standard & 0.106 (0.006) & 0.764 (0.008) & 49.842 & 190.804\\
+\hspace{1em}nn-cox & 0.097 (0.010) & 0.757 (0.009) & 34.063 & 33.278\\
+\hspace{1em}ranger-extratrees & 0.096 (0.005) & 0.756 (0.009) & 11.323 & 9.400\\
+\hspace{1em}cif-rotate & 0.090 (0.007) & 0.745 (0.009) & 1109.925 & 112.893\\
+\hspace{1em}cif-extension & 0.055 (0.002) & 0.747 (0.009) & 137.470 & 34.230\\
+\hspace{1em}aorsf-random & 0.052 (0.003) & 0.720 (0.010) & 8.360 & 0.992\\
+\hspace{1em}xgboost-cox & 0.030 (0.023) & 0.772 (0.008) & 9.057 & 0.014\\
+\hspace{1em}xgboost-aft & --- & 0.772 (0.007) & 23.335 & 0.013\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.114 (0.012) & 0.748 (0.012) & 379.908 & 24.724\\
-\hspace{1em}glmnet-cox & 0.114 (0.013) & 0.747 (0.012) & 0.260 & 0.003\\
-\hspace{1em}cif-rotate & 0.114 (0.013) & 0.742 (0.011) & 70.063 & 10.518\\
-\hspace{1em}aorsf-net & 0.113 (0.013) & 0.745 (0.012) & 120.016 & 0.160\\
-\hspace{1em}aorsf-cph & 0.112 (0.014) & 0.746 (0.012) & 1.972 & 0.152\\
-\hspace{1em}cif-standard & 0.110 (0.011) & 0.745 (0.012) & 3.971 & 15.781\\
-\hspace{1em}aorsf-fast & 0.110 (0.016) & 0.745 (0.011) & 0.617 & 0.153\\
-\hspace{1em}rsf-standard & 0.106 (0.011) & 0.737 (0.010) & 2.067 & 0.278\\
-\hspace{1em}cif-extension & 0.095 (0.005) & 0.745 (0.012) & 28.919 & 9.534\\
-\hspace{1em}ranger-extratrees & 0.092 (0.008) & 0.739 (0.013) & 2.936 & 1.775\\
-\hspace{1em}xgboost-cox & 0.091 (0.009) & 0.746 (0.010) & 4.368 & 0.004\\
-\hspace{1em}aorsf-random & 0.082 (0.005) & 0.733 (0.012) & 2.553 & 0.149\\
-\hspace{1em}nn-cox & 0.078 (0.024) & 0.710 (0.031) & 18.849 & 4.563\\
-\hspace{1em}xgboost-aft & --- & 0.743 (0.009) & 13.559 & 0.007\\
+\hspace{1em}obliqueRSF-net & 0.114 (0.012) & 0.747 (0.012) & 381.891 & 25.692\\
+\hspace{1em}glmnet-cox & 0.113 (0.013) & 0.745 (0.012) & 0.276 & 0.004\\
+\hspace{1em}cif-rotate & 0.113 (0.013) & 0.741 (0.011) & 71.714 & 10.523\\
+\hspace{1em}aorsf-net & 0.112 (0.013) & 0.743 (0.012) & 114.909 & 0.160\\
+\hspace{1em}aorsf-cph & 0.112 (0.013) & 0.744 (0.012) & 1.931 & 0.145\\
+\hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 4.079 & 16.213\\
+\hspace{1em}aorsf-fast & 0.109 (0.015) & 0.743 (0.012) & 0.618 & 0.142\\
+\hspace{1em}rsf-standard & 0.105 (0.011) & 0.735 (0.011) & 2.510 & 0.252\\
+\hspace{1em}cif-extension & 0.094 (0.006) & 0.744 (0.012) & 29.918 & 10.109\\
+\hspace{1em}ranger-extratrees & 0.091 (0.008) & 0.738 (0.012) & 3.266 & 1.328\\
+\hspace{1em}xgboost-cox & 0.090 (0.009) & 0.744 (0.010) & 4.229 & 0.004\\
+\hspace{1em}aorsf-random & 0.080 (0.006) & 0.731 (0.013) & 2.025 & 0.143\\
+\hspace{1em}nn-cox & 0.074 (0.028) & 0.705 (0.036) & 18.945 & 5.181\\
+\hspace{1em}xgboost-aft & --- & 0.741 (0.009) & 13.087 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.197 (0.050) & 0.794 (0.033) & 0.047 & 0.011\\
-\hspace{1em}aorsf-net & 0.197 (0.050) & 0.796 (0.034) & 9.985 & 0.012\\
-\hspace{1em}aorsf-cph & 0.194 (0.053) & 0.793 (0.035) & 0.097 & 0.012\\
-\hspace{1em}cif-rotate & 0.192 (0.066) & 0.786 (0.037) & 4.248 & 1.059\\
-\hspace{1em}rsf-standard & 0.172 (0.049) & 0.786 (0.038) & 0.067 & 0.025\\
-\hspace{1em}cif-extension & 0.169 (0.048) & 0.793 (0.032) & 3.508 & 1.194\\
-\hspace{1em}glmnet-cox & 0.157 (0.032) & 0.786 (0.038) & 0.078 & 0.002\\
-\hspace{1em}aorsf-random & 0.151 (0.046) & 0.779 (0.037) & 0.205 & 0.011\\
-\hspace{1em}cif-standard & 0.124 (0.040) & 0.767 (0.035) & 0.098 & 0.119\\
-\hspace{1em}obliqueRSF-net & 0.123 (0.034) & 0.794 (0.028) & 59.944 & 0.669\\
-\hspace{1em}ranger-extratrees & 0.089 (0.033) & 0.777 (0.036) & 0.021 & 0.026\\
-\hspace{1em}xgboost-cox & 0.057 (0.076) & 0.748 (0.048) & 1.099 & 0.002\\
-\hspace{1em}xgboost-aft & --- & 0.755 (0.045) & 5.540 & 0.005\\
-\hspace{1em}nn-cox & -0.031 (0.036) & 0.523 (0.080) & 11.159 & 0.126\\*
+\hspace{1em}aorsf-net & 0.201 (0.050) & 0.797 (0.035) & 9.901 & 0.012\\
+\hspace{1em}aorsf-fast & 0.200 (0.049) & 0.795 (0.034) & 0.047 & 0.012\\
+\hspace{1em}cif-rotate & 0.198 (0.065) & 0.789 (0.036) & 4.476 & 1.284\\
+\hspace{1em}aorsf-cph & 0.198 (0.052) & 0.794 (0.035) & 0.094 & 0.012\\
+\hspace{1em}rsf-standard & 0.176 (0.048) & 0.787 (0.037) & 0.078 & 0.025\\
+\hspace{1em}cif-extension & 0.174 (0.048) & 0.795 (0.034) & 3.676 & 1.195\\
+\hspace{1em}glmnet-cox & 0.160 (0.036) & 0.788 (0.037) & 0.087 & 0.002\\
+\hspace{1em}aorsf-random & 0.154 (0.044) & 0.780 (0.037) & 1.060 & 0.011\\
+\hspace{1em}cif-standard & 0.128 (0.040) & 0.770 (0.037) & 0.105 & 0.120\\
+\hspace{1em}obliqueRSF-net & 0.126 (0.034) & 0.796 (0.029) & 62.935 & 0.664\\
+\hspace{1em}ranger-extratrees & 0.092 (0.033) & 0.778 (0.038) & 0.020 & 0.026\\
+\hspace{1em}xgboost-cox & 0.067 (0.078) & 0.750 (0.046) & 1.408 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.754 (0.047) & 5.530 & 0.005\\
+\hspace{1em}nn-cox & -0.023 (0.033) & 0.517 (0.114) & 11.344 & 0.133\\*
 \end{longtable}
@@
 \begin{longtable}[t]{llcccccc}
-\caption{\label{tab:unnamed-chunk-10}Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance. \label{tab:bm_vi}}\\
+\caption{\label{tab:unnamed-chunk-12}Discrimination of relevant versus irrelevant variables for several techniques to estimate variable importance. \label{tab:bm_vi}}\\
 \toprule
@@
 \endlastfoot
-Overall & Overall & 76.0 & 74.0 & 73.3 & 69.7 & 64.7 & 67.7\\
+Overall & Overall & 75.9 & 73.9 & 73.2 & 69.6 & 64.6 & 67.7\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 58.0 & 57.7 & 58.1 & 54.6 & 49.1 & 56.8\\
-\hspace{1em}30 & 500 & 55.0 & 54.5 & 55.7 & 48.1 & 42.4 & 54.4\\
-\hspace{1em}30 & 1,000 & 57.2 & 56.4 & 58.3 & 53.5 & 48.6 & 55.7\\
-\hspace{1em}30 & 2,500 & 62.2 & 59.6 & 64.3 & 62.2 & 61.4 & 60.8\\
-\hspace{1em}15 & 500 & 53.3 & 53.6 & 53.6 & 46.2 & 40.0 & 53.9\\
-\hspace{1em}15 & 1,000 & 56.5 & 55.2 & 56.5 & 51.6 & 45.2 & 54.5\\
-\hspace{1em}15 & 2,500 & 61.5 & 59.1 & 62.3 & 61.5 & 59.2 & 61.3\\
-\hspace{1em}0 & 500 & 51.7 & 53.6 & 53.5 & 44.6 & 40.3 & 53.5\\
-\hspace{1em}0 & 1,000 & 57.0 & 59.1 & 55.3 & 53.1 & 43.1 & 55.3\\
-\hspace{1em}0 & 2,500 & 67.6 & 68.4 & 63.7 & 70.8 & 61.5 & 61.8\\
+\hspace{1em}Overall & Overall & 57.8 & 57.4 & 58.0 & 54.6 & 49.2 & 56.9\\
+\hspace{1em}30 & 500 & 54.3 & 54.1 & 54.8 & 48.2 & 42.7 & 54.9\\
+\hspace{1em}30 & 1,000 & 56.9 & 55.7 & 58.1 & 53.1 & 48.0 & 56.3\\
+\hspace{1em}30 & 2,500 & 61.9 & 58.9 & 64.1 & 61.5 & 60.7 & 60.0\\
+\hspace{1em}15 & 500 & 53.1 & 53.5 & 52.8 & 47.1 & 41.1 & 54.1\\
+\hspace{1em}15 & 1,000 & 55.9 & 55.4 & 56.3 & 52.2 & 45.8 & 55.4\\
+\hspace{1em}15 & 2,500 & 61.0 & 58.6 & 63.0 & 61.0 & 58.9 & 59.9\\
+\hspace{1em}0 & 500 & 52.5 & 53.9 & 52.4 & 44.5 & 40.7 & 53.6\\
+\hspace{1em}0 & 1,000 & 57.2 & 58.6 & 55.8 & 53.1 & 42.8 & 56.1\\
+\hspace{1em}0 & 2,500 & 67.6 & 68.2 & 64.4 & 71.0 & 62.2 & 62.1\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 71.9 & 69.5 & 68.0 & 66.0 & 60.1 & 61.7\\
-\hspace{1em}30 & 500 & 59.0 & 58.7 & 57.7 & 53.0 & 48.4 & 55.2\\
-\hspace{1em}30 & 1,000 & 61.4 & 60.3 & 59.5 & 57.7 & 52.4 & 56.0\\
-\hspace{1em}30 & 2,500 & 62.0 & 60.2 & 60.9 & 60.0 & 56.5 & 58.0\\
-\hspace{1em}15 & 500 & 63.8 & 61.8 & 61.3 & 54.5 & 48.9 & 58.3\\
-\hspace{1em}15 & 1,000 & 68.0 & 65.1 & 65.2 & 63.1 & 56.4 & 59.2\\
-\hspace{1em}15 & 2,500 & 70.7 & 66.8 & 68.4 & 66.7 & 62.0 & 62.7\\
-\hspace{1em}0 & 500 & 75.1 & 71.8 & 68.9 & 59.5 & 56.1 & 61.2\\
-\hspace{1em}0 & 1,000 & 89.0 & 84.8 & 78.8 & 82.2 & 69.2 & 67.0\\
-\hspace{1em}0 & 2,500 & 98.4 & 96.2 & 91.7 & 97.6 & 91.3 & 78.0\\
+\hspace{1em}Overall & Overall & 71.7 & 69.3 & 67.9 & 66.1 & 60.1 & 61.8\\
+\hspace{1em}30 & 500 & 58.8 & 58.3 & 57.8 & 53.4 & 48.5 & 55.5\\
+\hspace{1em}30 & 1,000 & 61.1 & 59.4 & 59.0 & 57.1 & 52.0 & 56.3\\
+\hspace{1em}30 & 2,500 & 62.1 & 60.2 & 61.1 & 60.0 & 56.4 & 57.9\\
+\hspace{1em}15 & 500 & 63.8 & 61.5 & 60.7 & 55.3 & 49.4 & 57.7\\
+\hspace{1em}15 & 1,000 & 67.5 & 65.1 & 64.6 & 62.5 & 56.0 & 59.8\\
+\hspace{1em}15 & 2,500 & 70.2 & 67.2 & 69.1 & 66.8 & 62.3 & 62.3\\
+\hspace{1em}0 & 500 & 75.5 & 72.3 & 68.5 & 60.1 & 55.8 & 61.1\\
+\hspace{1em}0 & 1,000 & 88.3 & 83.9 & 78.0 & 81.5 & 68.6 & 67.6\\
+\hspace{1em}0 & 2,500 & 98.4 & 96.3 & 91.8 & 97.7 & 91.6 & 78.3\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 78.4 & 76.0 & 75.0 & 70.8 & 65.4 & 68.3\\
-\hspace{1em}30 & 500 & 65.1 & 64.0 & 63.4 & 55.6 & 50.0 & 59.5\\
-\hspace{1em}30 & 1,000 & 67.5 & 65.6 & 65.3 & 61.7 & 55.8 & 61.0\\
-\hspace{1em}30 & 2,500 & 70.1 & 67.5 & 68.6 & 66.0 & 62.7 & 64.7\\
-\hspace{1em}15 & 500 & 70.3 & 68.1 & 66.7 & 58.7 & 52.4 & 62.2\\
-\hspace{1em}15 & 1,000 & 74.8 & 71.1 & 71.5 & 66.5 & 59.8 & 64.4\\
-\hspace{1em}15 & 2,500 & 78.8 & 74.9 & 77.0 & 73.0 & 68.9 & 70.2\\
-\hspace{1em}0 & 500 & 83.8 & 81.1 & 76.5 & 66.8 & 62.1 & 67.5\\
-\hspace{1em}0 & 1,000 & 95.6 & 92.6 & 87.9 & 89.6 & 78.9 & 76.3\\
-\hspace{1em}0 & 2,500 & 99.8 & 99.3 & 97.8 & 99.6 & 97.8 & 88.9\\
+\hspace{1em}Overall & Overall & 78.3 & 75.8 & 74.8 & 70.7 & 65.2 & 68.2\\
+\hspace{1em}30 & 500 & 64.8 & 63.5 & 62.5 & 55.6 & 49.8 & 59.2\\
+\hspace{1em}30 & 1,000 & 67.4 & 65.3 & 65.3 & 61.0 & 55.3 & 61.5\\
+\hspace{1em}30 & 2,500 & 69.9 & 67.0 & 68.5 & 65.2 & 61.9 & 63.8\\
+\hspace{1em}15 & 500 & 70.2 & 68.0 & 66.3 & 59.2 & 52.8 & 61.8\\
+\hspace{1em}15 & 1,000 & 74.8 & 71.2 & 71.4 & 66.6 & 59.9 & 65.0\\
+\hspace{1em}15 & 2,500 & 78.6 & 74.6 & 77.1 & 72.6 & 68.6 & 69.1\\
+\hspace{1em}0 & 500 & 84.0 & 81.1 & 76.2 & 66.7 & 61.7 & 67.6\\
+\hspace{1em}0 & 1,000 & 95.4 & 92.4 & 87.8 & 89.4 & 78.7 & 76.3\\
+\hspace{1em}0 & 2,500 & 99.8 & 99.3 & 97.8 & 99.7 & 97.9 & 89.0\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}Overall & Overall & 91.0 & 88.9 & 88.7 & 85.0 & 82.7 & 83.0\\
-\hspace{1em}30 & 500 & 79.4 & 77.0 & 75.5 & 70.1 & 66.3 & 70.7\\
-\hspace{1em}30 & 1,000 & 83.6 & 80.6 & 80.6 & 77.0 & 73.9 & 74.6\\
-\hspace{1em}30 & 2,500 & 86.9 & 83.8 & 85.4 & 82.2 & 80.9 & 79.1\\
-\hspace{1em}15 & 500 & 86.3 & 83.3 & 81.7 & 74.6 & 70.4 & 74.4\\
-\hspace{1em}15 & 1,000 & 91.0 & 87.9 & 88.2 & 84.7 & 81.4 & 80.5\\
-\hspace{1em}15 & 2,500 & 94.6 & 91.7 & 93.7 & 90.2 & 88.7 & 86.7\\
-\hspace{1em}0 & 500 & 97.7 & 96.2 & 94.0 & 86.6 & 84.5 & 85.9\\
-\hspace{1em}0 & 1,000 & 99.9 & 99.8 & 99.3 & 99.5 & 97.9 & 95.0\\
+\hspace{1em}Overall & Overall & 91.0 & 88.9 & 88.7 & 85.0 & 82.6 & 83.2\\
+\hspace{1em}30 & 500 & 79.3 & 77.3 & 75.5 & 70.3 & 66.5 & 71.2\\
+\hspace{1em}30 & 1,000 & 83.5 & 80.5 & 80.8 & 76.8 & 73.9 & 74.9\\
+\hspace{1em}30 & 2,500 & 86.5 & 83.5 & 85.1 & 81.7 & 80.4 & 79.3\\
+\hspace{1em}15 & 500 & 86.3 & 83.3 & 81.8 & 75.7 & 71.3 & 75.3\\
+\hspace{1em}15 & 1,000 & 91.3 & 88.1 & 88.5 & 84.6 & 81.3 & 81.1\\
+\hspace{1em}15 & 2,500 & 94.5 & 91.6 & 93.7 & 90.2 & 89.0 & 86.5\\
+\hspace{1em}0 & 500 & 97.8 & 96.3 & 94.0 & 86.5 & 83.4 & 85.9\\
+\hspace{1em}0 & 1,000 & 100.0 & 99.7 & 99.4 & 99.4 & 98.0 & 95.2\\
 \hspace{1em}0 & 2,500 & 100.0 & 100.0 & 100.0 & 100.0 & 100.0 & 99.8\\*

### 2022-08-30 R/bm_time_visualize.R

@@ -8,40 +8,41 @@ bm_time_visualize <- function(bm_time) {
 
   bm_time_smry <- bm_time %>%
     group_by(n_ftr, n_obs) %>%
-    summarize(across(everything(), quantile, probs = c(0.025, .5, .975))) %>%
-    mutate(quant = c('lo', 'est', 'hi')) %>%
-    pivot_longer(cols = -c(n_ftr, n_obs, quant)) %>%
-    pivot_wider(names_from = quant, values_from = value) %>%
+    # summarize(across(everything(), quantile, probs = c(0.025, .5, .975))) %>%
+    # mutate(quant = c('lo', 'est', 'hi')) %>%
+    pivot_longer(cols = -c(n_ftr, n_obs)) %>%
+    # pivot_wider(names_from = quant, values_from = value) %>%
     mutate(
       name = factor(
         name,
-        levels = c('cif_party',
+        levels = c('rsf_ranger',
                    'rsf_rfsrc',
-                   'aorsf_fast',
-                   'rsf_ranger'),
-        labels = c('party',
+                   'aorsf_fast'),
+        labels = c('ranger',
                    'randomForestSRC',
-                   'aorsf',
-                   'ranger')
+                   'aorsf')
       ),
-      n_ftr = paste(n_ftr, "features")
+      n_ftr = paste(n_ftr, "predictors in training data")
     )
 
   fig <- ggplot(bm_time_smry, aes(x = n_obs,
-                                  y = est,
+                                  y = value,
                                   fill = name,
                                   col = name)) +
-    geom_line() +
-    geom_point() +
-    geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.25) +
+    # geom_line() +
+    # geom_point() +
+    # geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.25) +
+    geom_smooth(method = 'lm', formula = y~poly(x, 3)) +
     facet_wrap(~n_ftr) +
     scale_y_log10() +
     scale_x_log10() +
-    labs(y = 'Time to fit 1 tree, seconds',
+    labs(y = 'Time to fit 50 trees, seconds',
          x = 'Number of observations in training data',
          color = 'R package',
          fill = 'R package') +
     theme_bw() +
+    scale_color_manual(values = c('cyan4', 'orange', 'purple')) +
+    scale_fill_manual(values = c('cyan4', 'orange', 'purple')) +
     theme(panel.grid.major.x = element_blank(),
[…]

### 2022-08-30 R/model_fit.R

@@ -135,12 +135,11 @@ aorsf_fast_fit <- function(train, node_size = 10, ...){
     data = train,
     formula = Surv(time, status) ~ .,
     mtry = mtry,
-    n_retry = 3,
     split_min_obs = node_size,
     split_min_events = split_min_events,
     control = orsf_control_fast(),
     importance = 'none',
-    oobag_pred = FALSE
+    oobag_pred_type = 'none'
   )
 
   end_time <- Sys.time()
@@ -169,7 +168,7 @@ aorsf_random_fit <- function(train, node_size = 10, ...){
     split_min_obs = node_size,
     split_min_events = split_min_events,
     control = orsf_control_custom(beta_fun = beta_fun),
-    oobag_pred = FALSE,
+    oobag_pred_type = 'none',
     importance = 'none'
   )
 
@@ -191,12 +190,10 @@ aorsf_cph_fit <- function(train, node_size = 10, ...){
     data = train,
     formula = Surv(time, status) ~ .,
     mtry = mtry,
-    n_retry = 3,
     split_min_obs = node_size,
     split_min_events = split_min_events,
-    control = orsf_control_cph(iter_max = 20,
-                               do_scale = TRUE),
-    oobag_pred = FALSE,
+    control = orsf_control_cph(),
+    oobag_pred_type = 'none',
     importance = 'none'
   )
 
@@ -224,7 +221,8 @@ aorsf_net_fit <- function(train, node_size = 10, ...){
     split_min_obs = node_size,
     split_min_events = split_min_events,
     control = orsf_control_net(df_target = df_target),
-    oobag_pred = FALSE
+    oobag_pred_type = 'none',
+    importance = 'none'
   )
 
   end_time <- Sys.time()

### 2022-11-23 paper/arxiv/main.Rnw
working on jcgs submission

@@
                       dpi = 600,
-                      cache = FALSE)
+                      cache = FALSE,
+                      warning = FALSE)
 
@@
                    bm_pred_time_viz,
+                   bm_time_viz,
                    clincalc_r2,
@@
 	The oblique random survival forest (RSF) is an ensemble supervised learning method for right-censored outcomes.
-Trees in the oblique RSF are grown using linear combinations of predictors to create branches, whereas in the standard RSF, a single predictor is used.
-Oblique RSF ensembles often have higher prediction accuracy than standard RSF ensembles.
-However, assessing all possible linear combinations of predictors induces significant computational overhead that limits applications to large-scale data sets.
-In addition, few methods have been developed for interpretation of oblique RSF ensembles, and they remain more difficult to interpret compared to their axis-based counterparts.
-In this article, we introduce and evaluate a method to increase computational efficiency of the oblique RSF and a method to estimate importance of individual predictor variables with the oblique RSF.
-Our strategy to reduce computational overhead makes use of Newton-Raphson scoring, a classical optimization technique that we apply to the Cox partial likelihood function within each non-leaf node of decision trees.
-We estimate the importance of individual predictors for the oblique RSF by negating each coefficient used for the given predictor in linear combinations, and then computing the reduction in out-of-bag accuracy.
-In general benchmarking experiments, we find that our implementation of the oblique RSF is approximately 450 times faster with equivalent discrimination and superior Brier score compared to existing software for oblique RSFs.
-We find in simulation studies that `negation importance' discriminates between relevant and irrelevant predictors more accurately than permutation importance, Shapley additive explanations, and a previously introduced technique to measure variable importance with oblique RSFs based on analysis of variance.
-All methods pertaining to oblique RSFs in the current study are available in the \texttt{aorsf} R package.
+Trees in the oblique RSF are grown using linear combinations of predictors, whereas in the standard RSF, a single predictor is used.
+Oblique RSF ensembles have high prediction accuracy, but assessing many linear combinations of predictors induces high computational overhead.
+In addition, few methods have been developed for estimation of variable importance (VI) with oblique RSFs.
+We introduce a method to increase computational efficiency of the oblique RSF and a method to estimate VI with the oblique RSF.
+Our computational approach uses Newton-Raphson scoring in each non-leaf node, We estimate VI by negating each coefficient used for a given predictor in linear combinations, and then computing the reduction in out-of-bag accuracy.
+In benchmarking experiments, we find our implementation of the oblique RSF is hundreds of times faster, with equivalent prediction accuracy, compared to existing software for oblique RSFs.
+We find in simulation studies that `negation VI' discriminates between relevant and irrelevant numeric predictors more accurately than permutation VI, Shapley VI, and a technique to measure VI using analysis of variance.
+All  oblique RSF methods in the current study are available in the \texttt{aorsf} R package.
 
@@
 In \secref{sec:discussion}, we summarize results from the current study and present ideas connecting the current work to existing frameworks and methods for RSFs that future studies may engage with.
+All oblique RSF methods introduced are available in the \texttt{aorsf} R package \citep{jaeger2022aorsf}.
 
@@
 Newton Raphson scoring is an exceptionally fast estimation procedure, and the \texttt{survival} package \citep{survival} includes documentation that outlines how to efficiently program it \citep{therneau_survival_2022}.
-Briefly, a vector of estimated regression coefficients, $\hat{\beta}$, is updated in each step of the procedure based on its first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
+Briefly, a vector of length \texttt{mtry} (\ie, the number of randomly selected predictors) with estimated regression coefficients, $\hat{\beta}$, is updated in each step of the procedure based on its first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
 $$ \hat{\beta}^{k+1} =  \hat{\beta}^{k} + U(\hat{\beta} = \hat{\beta}^{k})\, H^{-1}(\hat{\beta} = \hat{\beta}^{k}) $$
@@
 Several steps are taken to reduce computational overhead.
-First, memory is conserved by conducting bootstrap resampling via randomly generated bootstrap weights rather than making a traditional bootstrap sample.
-Weights are integer valued, with a weight of $v$ indicating an observation was sampled $v$ times.
+First, memory is conserved by conducting bootstrap resampling via random integer-valued weights, rather than using a bootstrapped copy of the original data.
+Memory conservation also takes place in terminal nodes, where we restrict estimation of the survival and cumulative hazard function to event times that occur among observations in the node.
 Second, early stopping is applied to the tree-growing procedure if a statistical criterion is not met.
@@
 Specifically, negation VI measures the increase in an oblique RF's prediction error after flipping the sign of all coefficients linked to a variable (\ie, negating them).
-As the magnitude of a coefficient increases, so does the probability that negating it will change the oblique RF's predictions.
-For the current study, we use Harrell's concordance (C)-statistic \citep{harrell1982evaluating} to measure change in prediction error when computing negation VI.
+As negating a coefficient effectively flips decision boundaries around the corresponding predictor's axis, scaling numeric predictors to have a mean of zero and standard deviation of one is recommended.\footnote{The \texttt{aorsf} package automatically scales numeric inputs to a mean of zero and standard deviation of one.} For the current study, we use Harrell's concordance (C)-statistic \citep{harrell1982evaluating} to measure change in prediction error when computing negation VI.
+
+% A motivating problem for negation VI is that of correlated, numeric predictors.
+When two predictors are correlated and only one of them is relevant for prediction of an outcome, VI methods based on permutation are known to have upward bias in estimating the importance of the irrelevant predictor \citep{hooker2021unrestricted}.
+Permutation may distort the joint distribution of predictors, which may in turn increase a model's estimated prediction error due to extrapolation.
+On the other hand, negating coefficients modifies the decision rule rather than modifying the data.
+
+To demonstrate the negation VI, consider a classification task where the goal is prediction of penguin species based on bill length and bill depth.
+Scaling these predictors to be centered at 0, we find decision boundaries from an oblique tree correctly classify
 
 Negation VI has several helpful characteristics.
-First, negation VI generalizes to any oblique RF (\ie, not just RSFs) using any valid error function, making it both general and flexible.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic (see \texttt{?aorsf::orsf\_vi\_negate})} Second, since the coefficients in each non-leaf node of an oblique tree are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
-Third, unlike permutation, negation is non-random and hence reproducible without setting a random seed.
-Additionally, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% (a value indicative of type 2 diabetes) as a result of randomly permuting the values of Hemoglobin A1c.
+First, negation VI generalizes to any oblique RF (\ie, not just RSFs) using any valid error function, making it both general and flexible.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic.} Second, negation is non-random and hence reproducible without setting a random seed.
+Third, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% (a value indicative of type 2 diabetes) as a result of randomly permuting the values of Hemoglobin A1c.
 
@@
 The code used to run these experiments is available online at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}.
-All analyses were conducted using R version \Sexpr{r_version} and coordinated by the \texttt{targets} R package \citep{targets}.
+All analyses were conducted using R version \Sexpr{r_version} with version 0.0.4 of \texttt{aorsf} \citep{jaeger2022aorsf}, and coordinated by the \texttt{targets} R package \citep{targets}.
 To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
 
-\subsection{Benchmark of prediction accuracy and computational efficiency} \label{sec:bm_pred}
-
-The aim of this numeric experiment is to evaluate and compare the accelerated oblique RSF with its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and with other machine learning algorithms for risk prediction.
+\subsection{Benchmark of prediction accuracy} \label{sec:bm_pred}
+
+The aim of this numeric experiment is to evaluate the prediction accuracy of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
 Inferences drawn from this experiment include equivalence and inferiority tests based on Bayesian linear mixed models.
@@
 For example, for RSF learners, we set the minimum node size (a parameter shared by all RSF learners) as 10.
-Additionally, for RSF learners, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500.
-For boosting, regression, and neural network learners, nested 10-fold cross-validation was applied to tune relevant model parameters.
+Additionally, for RSF learners, the number of randomly selected predictors was the square root of the total number of predictors rounded to the nearest integer, and the number of trees in the ensemble was 500 (a common default value for the number of trees).
+For boosting, regression, and neural network learners, nested cross-validation was applied to tune relevant model parameters.
 Specifically, tuning for boosting models included identifying the number of steps to complete.
@@
  \texttt{rsf-standard} grows survival trees following Leo Breiman's original random forest algorithm with variables and cut-points selected to maximize a log-rank statistic.
-\texttt{rsf-extratrees} grows survival trees with randomly selected features and cut-points.
+\texttt{rsf-extratrees} grows survival trees with randomly selected predictors and cut-points.
 \texttt{cif-standard} uses the framework of conditional inference to grow survival trees.
@@
 
-We used a collection of \Sexpr{n_data_sets} data sets containing a total of \Sexpr{n_risk_tasks} risk prediction tasks (tasks per data set ranged from one to four) to benchmark the accelerated oblique RSF versus other learners.
+We used a collection of \Sexpr{n_data_sets} data sets containing a total of \Sexpr{n_risk_tasks} risk prediction tasks (tasks per data set ranged from one to four).
 Participant-level data from the GUIDE-IT and SPRINT clinical trials and the ARIC, MESA, and JHS community cohort studies was obtained from the National Institute of Health Biologic Specimen and Data Repository Coordinating Center (BioLINCC).
@@
   length(unique(bm_pred_clean$data$data))
+
+# bm_pred_failed_description <- "Nothing to say"
 
@@
 
+\subsection{Benchmark of variable importance} \label{sec:bm_vi}
+
+The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between relevant and irrelevant variables, where relevance is defined by having a relationship with the simulated outcome.
+We consider methods that are intrinsic to the oblique RF (\eg, ANOVA VI), those that are intrinsic to the RF (\eg, permutation VI), and those that are model-agnostic (\eg, SHAP VI).
+VI methods with unavailable or still developing software were not included.\footnote{Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
+Therefore, it is not incorporated in the current simulation study.}
+
+\subsubsection{Variable importance techniques}
+
+We compute permutation VI for axis based RSFs using the \texttt{randomForestSRC} package.
+We compute ANOVA VI, negation VI, and permutation VI for oblique RSFs using the \texttt{aorsf} package.
+For ANOVA VI, we applied a p-value threshold of 0.01, following the threshold recommended by \citet{menze2011oblique}.
+We compute SHAP VI for boosted tree models using the \texttt{xgboost} package \citep{xgboost}, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
+
+% We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
+
+\subsubsection{Variable types}
+
+We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome on the log-hazard scale. Specifically, \begin{itemize}
+\item \textit{irrelevant} variables had no relationship with the outcome.
+\item \textit{main effect} variables had a linear relationship to the outcome on the log-hazard scale.
+\item \textit{non-linear effect} variables had a non-linear relationship to the outcome.
+A normally distributed variable $x$ was generated with a linear relationship to the outcome on the log-hazard scale, then $\tilde{x} = \text{sin}(a \cdot \pi \cdot x)$ was retained for modeling.
+The constant $a$ varied uniformly from 0.125 to 0.25.
+\item \textit{combination effect} variables were formed by linear combinations of three other variables.
+While their combination was linearly related to the outcome on the log-hazard scale, each of the three variables contributing to the combination had no relation to the outcome.
+\item \textit{interaction effect} variables were related to the outcome by multiplicative interaction with one other variable, which could have been a main effect, non-linear effect, or combination effect variable.
+\end{itemize}
+
+\subsubsection{Simulated data} \label{sec:data_sim}
+
+We initiated each set of simulated data with a random draw of size $n$ from a $p$-dimensional multivariate normal distribution, yielding $n$ observations of $p$ predictors.
+Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
+A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package \citep{simsurv, simsurv_paper}.
+The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
+Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be evaluated based on their ability to detect these effects.
+
+\subsubsection{Parameter specifications}
+
+<<>>=
+
+n_obs <- bm_vi_viz$smry %>%
+  ungroup() %>%
+  distinct(n_obs) %>%
+  drop_na() %>%
+  filter(n_obs > 0) %>%
+  pull(n_obs) %>%
+  glue_collapse(sep = ', ', last = ', and ')
+
+pred_corr <- bm_vi_viz$smry %>%
+  ungroup() %>%
+  distinct(pred_corr_max) %>%
+  drop_na() %>%
+  filter(pred_corr_max < 1) %>%
+  pull(pred_corr_max) %>%
+  glue_collapse(sep = ', ', last = ', and ')
+
+s <- mean_ci(clincalc_r2)*100
+
+clincalc_r2_sexpr <- table_glue(
+  "{s[['y']]} ({s[['ymin']]}, {s[['ymax']]})"
+)
+
+@
+
+Parameters that varied in the current simulation study included the number of observations (\Sexpr{n_obs}) and the absolute value of the maximum correlation between predictors (\Sexpr{pred_corr}).
+Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
+Using this design for simulated data, the Heller explained relative risk (95\% confidence interval) of our covariates was \Sexpr{clincalc_r2_sexpr} \citep{heller2012measure} with 2,500 observations.
+
+\subsubsection{Evaluation of variable importance}
+
+We compared VI techniques based on their discrimination (\ie, C-statistic) between relevant and irrelevant variables.
+Specifically, we generated a binary outcome for each predictor variable based on its relevance (\ie, the binary outcome is 1 if the variable is relevant, 0 otherwise).
+Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic which may be interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
+
+\subsubsection{Results} \label{sec:results_vi}
+
+<<>>=
+
+n_wins_aorsf <- bm_vi_viz %>%
+  getElement('rankings') %>%
+  filter(model == 'aorsf-negate') %>%
+  pull(n_wins)
+
+n_vi_tasks <- sum(bm_vi_viz$rankings$n_wins)
+
+cstat_mean_aorsf <- bm_vi_viz %>%
+  getElement('smry') %>%
+  filter(model == 'aorsf-negate',
+         data == 'Overall_NA_NA') %>%
+  mutate(value = table_value(value * 100)) %>%
+  pull(value)
+
+cstat_mean_anova <- bm_vi_viz %>%
+  getElement('smry') %>%
+  filter(model == 'aorsf-anova',
+         data == 'Overall_NA_NA') %>%
+  mutate(value = table_value(value * 100)) %>%
+  pull(value)
+
+cstat_mean_permute <- bm_vi_viz %>%
+  getElement('smry') %>%
+  filter(model == 'aorsf-permute',
+         data == 'Overall_NA_NA') %>%
+  mutate(value = table_value(value * 100)) %>%
+  pull(value)
+
+cstat_aorsf_won_by <- bm_vi_viz %>%
+  getElement('diffs') %>%
+  filter(data == 'Overall_NA_NA') %>%
+  transmute(percent = table_value(pdiff),
+            absolute = table_value(100*adiff)) %>%
+  as.list()
+
+cstat_vi_second_place <- bm_vi_viz %>%
+  getElement('smry') %>%
+  ungroup() %>%
+  filter(data == 'Overall_NA_NA') %>%
+  arrange(desc(value)) %>%
+  slice(2) %>%
+  transmute(model, value = table_value(100*value)) %>%
+  as.list()
+
+vi_times <- bm_vi_viz$times %>%
+  as_inline('model', 'time') %>%
+  map(as.numeric, unit = 'secs') %>%
+  map(table_value) %>%
+  set_names(str_replace(names(.), '-', '_'))
+
+@
+
+The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = \Sexpr{cstat_mean_aorsf}$), second (\texttt{aorsf-anova}; $C = \Sexpr{cstat_mean_anova}$), and third (\texttt{aorsf-permute}; $C = \Sexpr{cstat_mean_permute}$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in \Sexpr{n_wins_aorsf} out of \Sexpr{n_vi_tasks} VI tasks (Figure \ref{fig:bm_vi_viz}).
+Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
+Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
+Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of \Sexpr{vi_times$aorsf_anova} seconds versus \Sexpr{vi_times$aorsf_negate} and \Sexpr{vi_times$aorsf_permute} seconds, respectively.
+
+<<bm_vi_viz, fig.height=11, fig.width=9, fig.cap="Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
+Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.">>=
+bm_vi_viz$fig
+@
+
+\subsection{Benchmark of computational efficiency} \label{sec:bm_compute}
+
+The aim of this numeric experiment is to evaluate the computational efficiency of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
+
+\subsubsection{Evaluation of computational efficiency}
+
+For each learner discussed in \secref{sec:learners} and for each of the \Sexpr{n_risk_tasks} risk prediction tasks analyzed in \secref{sec:bm_pred}, we tracked the amount of time required to fit a prediction model (including time used to tune parameters) and compute predicted risk.
+
+We performed additional benchmarks on the time required to fit 500 trees using \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger}.
+The learners that represented these R packages were \texttt{aorsf-fast}, \texttt{rsf-standard}, and \texttt{rsf-extratrees}, respectively.
+To allow for controlled comparisons of computational efficiency with varying dimensions of training data, we used the same process to simulate data as described in \secref{sec:data_sim}, varying the number of observations from 100 to 10000 and the number of predictors from 10 to 1000.
+The minimum node size of trees in this experiment was dynamically set as the nearest integer to the number of observations in the training set divided by 10.
+
+\subsubsection{Results}
+
 <<>>=
@@
 
-\paragraph{Computational efficiency}
-
-Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about \Sexpr{ms_diff} milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+In the analysis of \Sexpr{n_risk_tasks} risk prediction tasks, \texttt{aorsf-fast} was the second fastest learner overall, with a median time to develop a risk prediction model and compute predictions about \Sexpr{ms_diff} milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
 Comparing median computing times, \texttt{aorsf-fast} was \Sexpr{times$obliqueRSF_net$ratio} times faster than its predecessor, \texttt{obliqueRSF-net}.
@@
 
-\subsection{Benchmark of variable importance} \label{sec:bm_vi}
-
-The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between relevant and irrelevant variables, where relevance is defined by having a relationship with the simulated outcome.
-We consider methods that are intrinsic to the oblique RF (\eg, ANOVA VI), those that are intrinsic to the RF (\eg, permutation VI), and those that are model-agnostic (\eg, SHAP VI).
-VI methods with unavailable or still developing software were not included.\footnote{Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
-Therefore, it is not incorporated in the current simulation study.}
-
-\subsubsection{Variable importance techniques}
-
-We compute permutation VI for axis based RSFs using the \texttt{randomForestSRC} package.
-We compute ANOVA VI, negation VI, and permutation VI for oblique RSFs using the \texttt{aorsf} package.
-For ANOVA VI, we applied a p-value threshold of 0.01, following the threshold recommended by \citet{menze2011oblique}.
-We compute SHAP VI for boosted tree models using the \texttt{xgboost} package \citep{xgboost}, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
-
-% We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
-
-\subsubsection{Variable types}
-
-We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome on the log-hazard scale. Specifically, \begin{itemize}
-\item \textit{irrelevant} variables had no relationship with the outcome.
-\item \textit{main effect} variables had a linear relationship to the outcome on the log-hazard scale.
-\item \textit{non-linear effect} variables had a non-linear relationship to the outcome.
-A normally distributed variable $x$ was generated with a linear relationship to the outcome on the log-hazard scale, then $\tilde{x} = \text{sin}(a \cdot \pi \cdot x)$ was retained for modeling.
-The constant $a$ varied uniformly from 0.125 to 0.25.
-\item \textit{combination effect} variables were formed by linear combinations of three other variables.
-While their combination was linearly related to the outcome on the log-hazard scale, each of the three variables contributing to the combination had no relation to the outcome.
-\item \textit{interaction effect} variables were related to the outcome by multiplicative interaction with one other variable, which could have been a main effect, non-linear effect, or combination effect variable.
-\end{itemize}
-
-\subsubsection{Simulated data}
-
-We initiated each set of simulated data with a random draw of size $n$ from a $p$-dimensional multivariate normal distribution, yielding $n$ observations of $p$ predictors.
-Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
-A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package \citep{simsurv, simsurv_paper}.
-The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
-Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be evaluated based on their ability to detect these effects.
-
-\subsubsection{Parameter specifications}
-
-<<>>=
-
-n_obs <- bm_vi_viz$smry %>%
-  ungroup() %>%
-  distinct(n_obs) %>%
-  drop_na() %>%
-  filter(n_obs > 0) %>%
-  pull(n_obs) %>%
-  glue_collapse(sep = ', ', last = ', and ')
-
-pred_corr <- bm_vi_viz$smry %>%
-  ungroup() %>%
-  distinct(pred_corr_max) %>%
-  drop_na() %>%
-  filter(pred_corr_max < 1) %>%
-  pull(pred_corr_max) %>%
-  glue_collapse(sep = ', ', last = ', and ')
-
-s <- mean_ci(clincalc_r2)*100
-
-clincalc_r2_sexpr <- table_glue(
-  "{s[['y']]} ({s[['ymin']]}, {s[['ymax']]})"
-)
-
-@
-
-Parameters that varied in the current simulation study included the number of observations (\Sexpr{n_obs}) and the absolute value of the maximum correlation between predictors (\Sexpr{pred_corr}).
-Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
-Using this design for simulated data, the Heller explained relative risk (95\% confidence interval) of our covariates was \Sexpr{clincalc_r2_sexpr} \citep{heller2012measure} with 2,500 observations.
-
-\subsubsection{Evaluation of variable importance}
-
-We compared VI techniques based on their discrimination (\ie, C-statistic) between relevant and irrelevant variables.
-Specifically, we generated a binary outcome for each predictor variable based on its relevance (\ie, the binary outcome is 1 if the variable is relevant, 0 otherwise).
-Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic which may be interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
-
-\subsubsection{Results} \label{sec:results_vi}
-
-<<>>=
-
-n_wins_aorsf <- bm_vi_viz %>%
-  getElement('rankings') %>%
-  filter(model == 'aorsf-negate') %>%
-  pull(n_wins)
-
-n_vi_tasks <- sum(bm_vi_viz$rankings$n_wins)
-
-cstat_mean_aorsf <- bm_vi_viz %>%
-  getElement('smry') %>%
-  filter(model == 'aorsf-negate',
-         data == 'Overall_NA_NA') %>%
-  mutate(value = table_value(value * 100)) %>%
-  pull(value)
-
-cstat_mean_anova <- bm_vi_viz %>%
-  getElement('smry') %>%
-  filter(model == 'aorsf-anova',
-         data == 'Overall_NA_NA') %>%
-  mutate(value = table_value(value * 100)) %>%
-  pull(value)
-
-cstat_mean_permute <- bm_vi_viz %>%
-  getElement('smry') %>%
-  filter(model == 'aorsf-permute',
-         data == 'Overall_NA_NA') %>%
-  mutate(value = table_value(value * 100)) %>%
-  pull(value)
-
-cstat_aorsf_won_by <- bm_vi_viz %>%
-  getElement('diffs') %>%
-  filter(data == 'Overall_NA_NA') %>%
-  transmute(percent = table_value(pdiff),
-            absolute = table_value(100*adiff)) %>%
-  as.list()
-
-cstat_vi_second_place <- bm_vi_viz %>%
-  getElement('smry') %>%
-  ungroup() %>%
-  filter(data == 'Overall_NA_NA') %>%
-  arrange(desc(value)) %>%
-  slice(2) %>%
-  transmute(model, value = table_value(100*value)) %>%
-  as.list()
-
-vi_times <- bm_vi_viz$times %>%
-  as_inline('model', 'time') %>%
-  map(as.numeric, unit = 'secs') %>%
-  map(table_value) %>%
-  set_names(str_replace(names(.), '-', '_'))
-
-@
-
-The three techniques that used `aorsf' to estimate VI were ranked first (\texttt{aorsf-negate}; $C = \Sexpr{cstat_mean_aorsf}$), second (\texttt{aorsf-anova}; $C = \Sexpr{cstat_mean_anova}$), and third (\texttt{aorsf-permute}; $C = \Sexpr{cstat_mean_permute}$) in overall mean C-statistic across all of the simulation scenarios, with \texttt{aorsf-negate} obtaining the highest C-statistic in \Sexpr{n_wins_aorsf} out of \Sexpr{n_vi_tasks} VI tasks (Figure \ref{fig:bm_vi_viz}).
-Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
-Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
-Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of \Sexpr{vi_times$aorsf_anova} seconds versus \Sexpr{vi_times$aorsf_negate} and \Sexpr{vi_times$aorsf_permute} seconds, respectively.
-
-<<bm_vi_viz, fig.height=11, fig.width=9, fig.cap="Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
-Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.">>=
-bm_vi_viz$fig
+In the analysis of time to fit 500 trees using simulated data, the \texttt{ranger} package exhibited the fastest computation times overall (Figure \ref{fig:bm_time_viz}).
+\texttt{aorsf} was the second fastest when the number of predictors was 10 or 100,  and \texttt{randomForestSRC} had similar computation time versus \texttt{aorsf} when 1000 predictors were present.
+
+<<bm_time_viz, fig.height=4, fig.width=10, fig.cap="The expected time, in seconds, to fit an ensemble of 500 axis-based survival trees using the ranger or randomForestSRC package versus 500 oblique survival trees using the aorsf package.
+The ranger package is the most efficient overall, and aorsf appears to be relatively efficient in larger samples, particularly when 10 or 100 predictors are present in the training data.
+All three packages appear to scale linearly in computation time with the number of observations in the training data.">>=
+
+bm_time_viz
+
 @
@@
 Overall, we found that estimating VI using negation instead of ANOVA increased the C-statistic for ranking a relevant variable higher than an irrelevant variable by \Sexpr{cstat_aorsf_won_by$absolute}, a relative increase of \Sexpr{cstat_aorsf_won_by$percent}\%.
+
+To understand potential differences in computational efficiency, we reviewed code in the \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger} packages.
+We found differences in how survival outcome data are saved in leaf nodes.
+For each leaf node, \texttt{aorsf} stores data with one row per unique event time using training data that are stored in the leaf, whereas \texttt{randomForestSRC} and \texttt{ranger} store survival outcomes at a fixed grid of event times in each leaf.
+By default, \texttt{ranger} creates a grid that includes all event times in the training data.
+The grid strategy can cause higher computing time and memory usage when the grid of event times is large and a large number of leaf nodes are included in each tree, which can occur when minimum node size is small relative to the size of the training data.
+We kept minimum node size fixed in our benchmark of computational efficiency using real data, and dymanically increased minimum node size based on the size of the training set when we benchmarked computational efficiency using simulated data.
+Because of this decision, the \texttt{randomForestSRC} and \texttt{ranger} packages ran slower than \texttt{aorsf} in our benchmark of real data but not in the benchmark of simulated data.
 
@@
 
+\subsection{Conclusion}
+
 Oblique RSFs have exceptional prediction accuracy and this study has shown how they can be fit with computational efficiency that rivals their axis-based counterparts.
-We have also introduced a general and flexible method to estimate VI with oblique RFs, and demonstrated its effectiveness specifically for the oblique RSF.
+We have also introduced a general and flexible method to estimate VI with oblique RFs, and demonstrated its effectiveness for numeric, correlated predictors.
 Code used for the current study is available at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}, and the \texttt{aorsf} package is available at \href{https://github.com/bcjaeger/aorsf}{https://github.com/bcjaeger/aorsf}.

### 2022-11-23 paper/arxiv/main.tex
working on jcgs submission

@@
 Specifically, negation VI measures the increase in an oblique RF's prediction error after flipping the sign of all coefficients linked to a variable (\ie, negating them).
-As the magnitude of a coefficient increases, so does the probability that negating it will change the oblique RF's predictions.
-For the current study, we use Harrell's concordance (C)-statistic \citep{harrell1982evaluating} to measure change in prediction error when computing negation VI.
+As negating a coefficient effectively flips decision boundaries around the corresponding predictor's axis, scaling numeric predictors to have a mean of zero and standard deviation of one is recommended.\footnote{The \texttt{aorsf} package automatically scales numeric inputs to a mean of zero and standard deviation of one.} For the current study, we use Harrell's concordance (C)-statistic \citep{harrell1982evaluating} to measure change in prediction error when computing negation VI.
+
+A motivating problem for negation VI is that of correlated, numeric predictors.
+When two predictors are correlated and only one of them is relevant for prediction of an outcome, VI methods based on permutation are known to have upward bias in estimating the importance of the irrelevant predictor \citep{hooker2021unrestricted}.
+Permutation may distort the joint distribution of predictors, which may in turn increase a model's estimated prediction error due to extrapolation.
+On the other hand, negating coefficients modifies the decision rule rather than modifying the data.
+Thus, we hypothesize that negation VI can be more effective at identifying important predictors for correlated, numeric predictors.
 
 Negation VI has several helpful characteristics.
-First, negation VI generalizes to any oblique RF (\ie, not just RSFs) using any valid error function, making it both general and flexible.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic (see \texttt{?aorsf::orsf\_vi\_negate})} Second, since the coefficients in each non-leaf node of an oblique tree are adjusted for the accompanying predictors, negation VI may provide better estimation of VI in the presence of correlated variables compared to standard VI techniques.
-Third, unlike permutation, negation is non-random and hence reproducible without setting a random seed.
-Additionally, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% (a value indicative of type 2 diabetes) as a result of randomly permuting the values of Hemoglobin A1c.
+First, negation VI generalizes to any oblique RF (\ie, not just RSFs) using any valid error function, making it both general and flexible.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic.} Second, negation is non-random and hence reproducible without setting a random seed.
+Third, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% (a value indicative of type 2 diabetes) as a result of randomly permuting the values of Hemoglobin A1c.
 
@@
 The code used to run these experiments is available online at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}.
-All analyses were conducted using R version 4.1.3 and coordinated by the \texttt{targets} R package \citep{targets}.
+All analyses were conducted using R version 4.1.3 with version 0.0.4 of \texttt{aorsf} \citep{jaeger2022aorsf}, and coordinated by the \texttt{targets} R package \citep{targets}.
 To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
 
-\subsection{Benchmark of prediction accuracy and computational efficiency} \label{sec:bm_pred}
-
-The aim of this numeric experiment is to evaluate and compare the accelerated oblique RSF with its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and with other machine learning algorithms for risk prediction.
+\subsection{Benchmark of prediction accuracy} \label{sec:bm_pred}
+
+The aim of this numeric experiment is to evaluate the prediction accuracy of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
 Inferences drawn from this experiment include equivalence and inferiority tests based on Bayesian linear mixed models.
@@
 
-We used a collection of 21 data sets containing a total of 35 risk prediction tasks (tasks per data set ranged from one to four) to benchmark the accelerated oblique RSF versus other learners.
+We used a collection of 21 data sets containing a total of 35 risk prediction tasks (tasks per data set ranged from one to four).
 Participant-level data from the GUIDE-IT and SPRINT clinical trials and the ARIC, MESA, and JHS community cohort studies was obtained from the National Institute of Health Biologic Specimen and Data Repository Coordinating Center (BioLINCC).
@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 20 out of 35 risk prediction tasks, with an overall mean IPA of 12.6 (Figure \ref{fig:bm_pred_viz_ibs}).
-Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.35 points higher, a relative increase of 12.0\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.86 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 17 out of 35 risk prediction tasks, with an overall mean IPA of 12.6 (Figure \ref{fig:bm_pred_viz_ibs}).
+Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.33 points higher, a relative increase of 11.7\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.82 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
 
@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 10 out of 35 risk prediction tasks, with an overall mean of 77.2 (Figure \ref{fig:bm_pred_viz_cstat}).
-Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.685 points higher, a relative increase of 0.896\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was $>$ 0.999, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.18 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 9 out of 35 risk prediction tasks, with an overall mean of 77.2 (Figure \ref{fig:bm_pred_viz_cstat}).
+Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.668 points higher, a relative increase of 0.873\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was $>$ 0.999, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.14 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
 
@@
 A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.}\label{fig:bm_pred_model_viz_cstat}
-\end{figure}
-
-\end{knitrout}
-
-\paragraph{Computational efficiency}
-
-Overall, \texttt{aorsf-fast} was the second fastest learner, with an expected model development and risk prediction time about 385 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
-Comparing median computing times, \texttt{aorsf-fast} was 379.8 times faster than its predecessor, \texttt{obliqueRSF-net}.
-In addition, \texttt{aorsf-fast} was 16.1, 1.55, and 2.66 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/bm_pred_time-1} \caption[Distribution of time taken to fit a prediction model and compute predicted risk]{Distribution of time taken to fit a prediction model and compute predicted risk.
-The median time, in seconds, is printed and annotated for each learner by a vertical line.}\label{fig:bm_pred_time}
 \end{figure}
@@
 
-\subsubsection{Simulated data}
+\subsubsection{Simulated data} \label{sec:data_sim}
 
@@
 Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
-Using this design for simulated data, the Heller explained relative risk (95\% confidence interval) of our covariates was 88.4 (88.1, 88.7) \citep{heller2012measure} with 2,500 observations.
+Using this design for simulated data, the Heller explained relative risk (95\% confidence interval) of our covariates was 88.5 (88.2, 88.7) \citep{heller2012measure} with 2,500 observations.
 
@@
 
+\subsection{Benchmark of computational efficiency} \label{sec:bm_compute}
+
+The aim of this numeric experiment is to evaluate the computational efficiency of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
+
+\subsubsection{Evaluation of computational efficiency}
+
+For each learner discussed in \secref{sec:learners} and for each of the 35 risk prediction tasks analyzed in \secref{sec:bm_pred}, we tracked the amount of time required to fit a prediction model (including time used to tune parameters) and compute predicted risk.
+
+We performed additional benchmarks on the time required to fit 500 trees using \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger}.
+The learners that represented these R packages were \texttt{aorsf-fast}, \texttt{rsf-standard}, and \texttt{rsf-extratrees}, respectively.
+To allow for controlled comparisons of computational efficiency with varying dimensions of training data, we used the same process to simulate data as described in \secref{sec:data_sim}, varying the number of observations from 100 to 10000 and the number of predictors from 10 to 1000.
+The minimum node size of trees in this experiment was dynamically set as the nearest integer to the number of observations in the training set divided by 10.
+
+\subsubsection{Results}
+
+In the analysis of 35 risk prediction tasks, \texttt{aorsf-fast} was the second fastest learner overall, with a median time to develop a risk prediction model and compute predictions about 337 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+Comparing median computing times, \texttt{aorsf-fast} was 1,291.6 times faster than its predecessor, \texttt{obliqueRSF-net}.
+In addition, \texttt{aorsf-fast} was 19.8, 1.90, and 3.18 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_time-1} \caption[Distribution of time taken to fit a prediction model and compute predicted risk]{Distribution of time taken to fit a prediction model and compute predicted risk.
+The median time, in seconds, is printed and annotated for each learner by a vertical line.}\label{fig:bm_pred_time}
+\end{figure}
+
+\end{knitrout}
+
+In the analysis of time to fit 500 trees using simulated data, the \texttt{ranger} package exhibited the fastest computation times overall (Figure \ref{fig:bm_time_viz}).
+\texttt{aorsf} was the second fastest when the number of predictors was 10 or 100,  and \texttt{randomForestSRC} had similar computation time versus \texttt{aorsf} when 1000 predictors were present.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_time_viz-1} \caption[The expected time, in seconds, to fit an ensemble of 500 axis-based survival trees using the ranger or randomForestSRC package versus 500 oblique survival trees using the aorsf package]{The expected time, in seconds, to fit an ensemble of 500 axis-based survival trees using the ranger or randomForestSRC package versus 500 oblique survival trees using the aorsf package.
+The ranger package is the most efficient overall, and aorsf appears to be relatively efficient in larger samples, particularly when 10 or 100 predictors are present in the training data.
+All three packages appear to scale linearly in computation time with the number of observations in the training data.}\label{fig:bm_time_viz}
+\end{figure}
+
+\end{knitrout}
+
 \section{Discussion} \label{sec:discussion}
@@
 Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
-In numeric experiments, we found that that \texttt{aorsf-fast} is approximately 379.8 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
+In numeric experiments, we found that that \texttt{aorsf-fast} is approximately 1,291.6 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
 We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
 Overall, we found that estimating VI using negation instead of ANOVA increased the C-statistic for ranking a relevant variable higher than an irrelevant variable by 2.05, a relative increase of 2.78\%.
+
+To understand potential differences in computational efficiency, we reviewed code in the \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger} packages.
+We found differences in how survival outcome data are saved in leaf nodes.
+For each leaf node, \texttt{aorsf} stores data with one row per unique event time using training data that are stored in the leaf, whereas \texttt{randomForestSRC} and \texttt{ranger} store survival outcomes at a fixed grid of event times in each leaf.
+By default, \texttt{ranger} creates a grid that includes all event times in the training data.
+The grid strategy can cause higher computing time and memory usage when the grid of event times is large and a large number of leaf nodes are included in each tree, which can occur when minimum node size is small relative to the size of the training data.
+We kept minimum node size fixed in our benchmark of computational efficiency using real data, and dymanically increased minimum node size based on the size of the training set when we benchmarked computational efficiency using simulated data.
+Because of this decision, the \texttt{randomForestSRC} and \texttt{ranger} packages ran slower than \texttt{aorsf} in our benchmark of real data but not in the benchmark of simulated data.
 
@@
 \hline
-\hspace{1em}aorsf-fast & 0.126 (0.110) & 0.772 (0.071) & 0.620 & 0.145\\
-\hspace{1em}aorsf-cph & 0.126 (0.109) & 0.771 (0.070) & 1.912 & 0.148\\
-\hspace{1em}aorsf-net & 0.124 (0.112) & 0.771 (0.071) & 78.512 & 0.143\\
-\hspace{1em}obliqueRSF-net & 0.113 (0.085) & 0.771 (0.071) & 300.393 & 18.803\\
-\hspace{1em}cif-standard & 0.113 (0.098) & 0.765 (0.071) & 4.293 & 6.044\\
-\hspace{1em}rsf-standard & 0.113 (0.114) & 0.755 (0.075) & 2.099 & 0.199\\
-\hspace{1em}cif-rotate & 0.112 (0.124) & 0.755 (0.081) & 37.695 & 8.348\\
-\hspace{1em}glmnet-cox & 0.108 (0.119) & 0.757 (0.077) & 0.473 & 0.003\\
-\hspace{1em}ranger-extratrees & 0.099 (0.085) & 0.762 (0.067) & 0.878 & 1.156\\
-\hspace{1em}cif-extension & 0.095 (0.092) & 0.761 (0.072) & 22.321 & 6.949\\
-\hspace{1em}aorsf-random & 0.090 (0.081) & 0.741 (0.063) & 1.790 & 0.141\\
-\hspace{1em}xgboost-cox & 0.064 (0.100) & 0.749 (0.094) & 3.973 & 0.004\\
-\hspace{1em}nn-cox & 0.047 (0.108) & 0.656 (0.138) & 15.352 & 2.060\\
-\hspace{1em}xgboost-aft & --- & 0.762 (0.076) & 13.060 & 0.007\\
+\hspace{1em}aorsf-fast & 0.126 (0.109) & 0.772 (0.071) & 0.527 & 0.138\\
+\hspace{1em}aorsf-cph & 0.126 (0.109) & 0.771 (0.070) & 1.750 & 0.140\\
+\hspace{1em}cif-standard & 0.113 (0.098) & 0.765 (0.071) & 3.792 & 6.448\\
+\hspace{1em}rsf-standard & 0.113 (0.114) & 0.755 (0.075) & 1.945 & 0.196\\
+\hspace{1em}cif-rotate & 0.112 (0.124) & 0.755 (0.081) & 36.928 & 8.194\\
+\hspace{1em}obliqueRSF-net & 0.109 (0.081) & 0.773 (0.069) & 552.335 & 84.685\\
+\hspace{1em}glmnet-cox & 0.108 (0.119) & 0.757 (0.077) & 0.326 & 0.003\\
+\hspace{1em}ranger-extratrees & 0.099 (0.085) & 0.762 (0.067) & 0.790 & 1.109\\
+\hspace{1em}cif-extension & 0.095 (0.092) & 0.761 (0.072) & 21.977 & 6.922\\
+\hspace{1em}aorsf-random & 0.092 (0.079) & 0.744 (0.065) & 1.717 & 0.149\\
+\hspace{1em}xgboost-cox & 0.064 (0.100) & 0.749 (0.094) & 4.394 & 0.004\\
+\hspace{1em}nn-cox & 0.048 (0.106) & 0.657 (0.136) & 11.377 & 1.705\\
+\hspace{1em}xgboost-aft & --- & 0.762 (0.076) & 15.031 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-random & 0.028 (0.022) & 0.748 (0.038) & 0.382 & 0.034\\
-\hspace{1em}ranger-extratrees & 0.028 (0.017) & 0.740 (0.036) & 0.064 & 0.146\\
-\hspace{1em}obliqueRSF-net & 0.027 (0.022) & 0.746 (0.038) & 25.980 & 15.236\\
-\hspace{1em}aorsf-cph & 0.025 (0.029) & 0.751 (0.042) & 0.424 & 0.033\\
-\hspace{1em}cif-standard & 0.024 (0.031) & 0.744 (0.040) & 1.771 & 4.657\\
-\hspace{1em}aorsf-fast & 0.024 (0.029) & 0.746 (0.043) & 0.144 & 0.032\\
-\hspace{1em}cif-extension & 0.023 (0.015) & 0.722 (0.038) & 9.848 & 4.083\\
-\hspace{1em}aorsf-net & 0.019 (0.034) & 0.745 (0.042) & 17.078 & 0.034\\
-\hspace{1em}glmnet-cox & 0.016 (0.030) & 0.746 (0.037) & 0.179 & 0.003\\
-\hspace{1em}rsf-standard & 0.005 (0.041) & 0.730 (0.042) & 0.192 & 0.061\\
-\hspace{1em}cif-rotate & 0.004 (0.040) & 0.731 (0.038) & 16.095 & 3.888\\
-\hspace{1em}xgboost-cox & 0.000 (0.044) & 0.751 (0.033) & 3.704 & 0.003\\
-\hspace{1em}nn-cox & -0.001 (0.008) & 0.549 (0.125) & 11.075 & 0.668\\
-\hspace{1em}xgboost-aft & --- & 0.737 (0.035) & 10.015 & 0.006\\
+\hspace{1em}obliqueRSF-net & 0.029 (0.015) & 0.753 (0.037) & 115.320 & 18.196\\
+\hspace{1em}ranger-extratrees & 0.028 (0.017) & 0.740 (0.036) & 0.086 & 0.133\\
+\hspace{1em}aorsf-random & 0.027 (0.020) & 0.756 (0.036) & 0.465 & 0.035\\
+\hspace{1em}cif-standard & 0.024 (0.031) & 0.744 (0.040) & 1.657 & 4.377\\
+\hspace{1em}aorsf-cph & 0.024 (0.029) & 0.750 (0.042) & 0.436 & 0.036\\
+\hspace{1em}aorsf-fast & 0.024 (0.028) & 0.745 (0.045) & 0.141 & 0.036\\
+\hspace{1em}cif-extension & 0.023 (0.015) & 0.722 (0.038) & 9.010 & 4.189\\
+\hspace{1em}glmnet-cox & 0.016 (0.030) & 0.746 (0.037) & 0.197 & 0.002\\
+\hspace{1em}rsf-standard & 0.005 (0.041) & 0.730 (0.042) & 0.179 & 0.061\\
+\hspace{1em}cif-rotate & 0.004 (0.040) & 0.731 (0.038) & 14.549 & 3.604\\
+\hspace{1em}nn-cox & 0.000 (0.011) & 0.564 (0.101) & 7.755 & 0.811\\
+\hspace{1em}xgboost-cox & -0.001 (0.052) & 0.751 (0.033) & 3.729 & 0.003\\
+\hspace{1em}xgboost-aft & --- & 0.737 (0.035) & 11.383 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.007 (0.011) & 0.823 (0.052) & 8.869 & 11.004\\
-\hspace{1em}aorsf-cph & 0.007 (0.018) & 0.821 (0.060) & 0.340 & 0.018\\
-\hspace{1em}aorsf-fast & 0.005 (0.019) & 0.827 (0.056) & 0.086 & 0.018\\
-\hspace{1em}aorsf-random & 0.005 (0.014) & 0.788 (0.074) & 0.221 & 0.022\\
-\hspace{1em}cif-extension & 0.001 (0.020) & 0.765 (0.066) & 8.436 & 3.493\\
-\hspace{1em}ranger-extratrees & 0.001 (0.019) & 0.777 (0.069) & 0.044 & 0.138\\
-\hspace{1em}xgboost-cox & -0.004 (0.004) & 0.500 (0.000) & 0.119 & 0.002\\
-\hspace{1em}nn-cox & -0.004 (0.004) & 0.508 (0.119) & 10.867 & 0.518\\
-\hspace{1em}cif-standard & -0.005 (0.025) & 0.781 (0.062) & 1.726 & 4.648\\
-\hspace{1em}aorsf-net & -0.005 (0.032) & 0.806 (0.067) & 13.309 & 0.022\\
-\hspace{1em}rsf-standard & -0.031 (0.051) & 0.776 (0.073) & 0.090 & 0.035\\
-\hspace{1em}cif-rotate & -0.037 (0.049) & 0.707 (0.090) & 13.920 & 3.444\\
-\hspace{1em}glmnet-cox & -0.065 (0.095) & 0.746 (0.098) & 0.281 & 0.002\\
-\hspace{1em}xgboost-aft & --- & 0.773 (0.071) & 9.190 & 0.005\\
+\hspace{1em}aorsf-random & 0.008 (0.012) & 0.798 (0.073) & 0.285 & 0.024\\
+\hspace{1em}obliqueRSF-net & 0.006 (0.009) & 0.821 (0.049) & 49.070 & 11.201\\
+\hspace{1em}aorsf-fast & 0.006 (0.019) & 0.826 (0.057) & 0.088 & 0.020\\
+\hspace{1em}aorsf-cph & 0.006 (0.018) & 0.818 (0.062) & 0.357 & 0.020\\
+\hspace{1em}cif-extension & 0.001 (0.020) & 0.765 (0.066) & 8.283 & 3.478\\
+\hspace{1em}ranger-extratrees & 0.001 (0.019) & 0.777 (0.069) & 0.041 & 0.122\\
+\hspace{1em}xgboost-cox & -0.004 (0.004) & 0.500 (0.000) & 0.118 & 0.002\\
+\hspace{1em}nn-cox & -0.004 (0.004) & 0.547 (0.128) & 7.487 & 0.717\\
+\hspace{1em}cif-standard & -0.005 (0.025) & 0.781 (0.062) & 1.695 & 4.223\\
+\hspace{1em}rsf-standard & -0.031 (0.051) & 0.776 (0.073) & 0.098 & 0.037\\
+\hspace{1em}cif-rotate & -0.037 (0.049) & 0.707 (0.090) & 13.163 & 3.201\\
+\hspace{1em}glmnet-cox & -0.065 (0.095) & 0.746 (0.098) & 0.286 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.774 (0.070) & 10.124 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.156 (0.007) & 0.810 (0.007) & 5.048 & 1.287\\
-\hspace{1em}aorsf-cph & 0.153 (0.006) & 0.809 (0.007) & 14.564 & 1.300\\
-\hspace{1em}aorsf-net & 0.152 (0.006) & 0.809 (0.007) & 480.098 & 1.437\\
-\hspace{1em}rsf-standard & 0.150 (0.007) & 0.801 (0.007) & 9.407 & 0.991\\
-\hspace{1em}obliqueRSF-net & 0.143 (0.005) & 0.811 (0.008) & 2830.398 & 356.908\\
-\hspace{1em}cif-standard & 0.132 (0.005) & 0.809 (0.007) & 71.835 & 371.102\\
-\hspace{1em}glmnet-cox & 0.129 (0.011) & 0.795 (0.008) & 1.473 & 0.011\\
-\hspace{1em}nn-cox & 0.117 (0.029) & 0.786 (0.046) & 51.356 & 84.715\\
-\hspace{1em}ranger-extratrees & 0.112 (0.005) & 0.795 (0.009) & 293.864 & 61.837\\
-\hspace{1em}cif-rotate & 0.104 (0.004) & 0.783 (0.009) & 569.289 & 67.436\\
-\hspace{1em}aorsf-random & 0.097 (0.005) & 0.772 (0.008) & 10.996 & 1.259\\
-\hspace{1em}cif-extension & 0.069 (0.002) & 0.786 (0.009) & 169.206 & 56.091\\
-\hspace{1em}xgboost-cox & 0.064 (0.017) & 0.814 (0.006) & 8.544 & 0.015\\
-\hspace{1em}xgboost-aft & --- & 0.814 (0.006) & 23.781 & 0.013\\
+\hspace{1em}aorsf-fast & 0.156 (0.007) & 0.810 (0.007) & 4.590 & 1.434\\
+\hspace{1em}aorsf-cph & 0.153 (0.006) & 0.809 (0.007) & 14.582 & 1.450\\
+\hspace{1em}rsf-standard & 0.150 (0.007) & 0.801 (0.007) & 8.222 & 0.981\\
+\hspace{1em}obliqueRSF-net & 0.133 (0.005) & 0.811 (0.008) & 4468.696 & 1359.275\\
+\hspace{1em}cif-standard & 0.132 (0.005) & 0.809 (0.007) & 70.462 & 358.273\\
+\hspace{1em}glmnet-cox & 0.129 (0.011) & 0.795 (0.008) & 1.873 & 0.010\\
+\hspace{1em}nn-cox & 0.126 (0.012) & 0.795 (0.007) & 43.144 & 86.104\\
+\hspace{1em}ranger-extratrees & 0.112 (0.005) & 0.795 (0.009) & 283.364 & 69.939\\
+\hspace{1em}aorsf-random & 0.104 (0.005) & 0.771 (0.008) & 11.343 & 1.420\\
+\hspace{1em}cif-rotate & 0.104 (0.004) & 0.783 (0.009) & 558.249 & 68.510\\
+\hspace{1em}cif-extension & 0.069 (0.002) & 0.786 (0.009) & 164.161 & 50.420\\
+\hspace{1em}xgboost-cox & 0.064 (0.017) & 0.813 (0.006) & 9.660 & 0.015\\
+\hspace{1em}xgboost-aft & --- & 0.814 (0.006) & 29.321 & 0.013\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.217 (0.006) & 0.792 (0.004) & 902.210 & 2.343\\
-\hspace{1em}rsf-standard & 0.216 (0.006) & 0.789 (0.004) & 14.727 & 1.274\\
-\hspace{1em}aorsf-fast & 0.216 (0.007) & 0.792 (0.004) & 7.268 & 2.936\\
-\hspace{1em}aorsf-cph & 0.215 (0.006) & 0.792 (0.004) & 22.420 & 3.070\\
-\hspace{1em}obliqueRSF-net & 0.207 (0.005) & 0.791 (0.004) & 7329.229 & 331.164\\
-\hspace{1em}cif-standard & 0.201 (0.004) & 0.790 (0.004) & 72.253 & 384.744\\
-\hspace{1em}nn-cox & 0.193 (0.011) & 0.780 (0.005) & 103.296 & 92.992\\
-\hspace{1em}glmnet-cox & 0.191 (0.015) & 0.777 (0.007) & 2.256 & 0.011\\
-\hspace{1em}ranger-extratrees & 0.181 (0.004) & 0.780 (0.005) & 332.296 & 70.372\\
-\hspace{1em}cif-rotate & 0.151 (0.007) & 0.757 (0.006) & 589.958 & 66.749\\
-\hspace{1em}xgboost-cox & 0.131 (0.012) & 0.794 (0.004) & 11.220 & 0.015\\
-\hspace{1em}aorsf-random & 0.130 (0.005) & 0.733 (0.005) & 19.416 & 2.051\\
-\hspace{1em}cif-extension & 0.113 (0.002) & 0.775 (0.005) & 180.483 & 54.092\\
-\hspace{1em}xgboost-aft & --- & 0.794 (0.004) & 28.692 & 0.014\\
+\hspace{1em}rsf-standard & 0.216 (0.006) & 0.789 (0.004) & 12.352 & 1.162\\
+\hspace{1em}aorsf-fast & 0.216 (0.006) & 0.792 (0.004) & 7.463 & 2.519\\
+\hspace{1em}aorsf-cph & 0.215 (0.006) & 0.792 (0.004) & 22.389 & 2.569\\
+\hspace{1em}cif-standard & 0.201 (0.004) & 0.790 (0.004) & 68.083 & 373.333\\
+\hspace{1em}obliqueRSF-net & 0.195 (0.004) & 0.789 (0.004) & 7373.936 & 1276.463\\
+\hspace{1em}nn-cox & 0.191 (0.008) & 0.779 (0.005) & 83.418 & 84.770\\
+\hspace{1em}glmnet-cox & 0.191 (0.015) & 0.777 (0.007) & 2.282 & 0.011\\
+\hspace{1em}ranger-extratrees & 0.181 (0.004) & 0.780 (0.005) & 356.276 & 61.525\\
+\hspace{1em}cif-rotate & 0.151 (0.007) & 0.757 (0.006) & 563.575 & 64.849\\
+\hspace{1em}xgboost-cox & 0.131 (0.012) & 0.794 (0.004) & 12.568 & 0.015\\
+\hspace{1em}aorsf-random & 0.128 (0.006) & 0.725 (0.005) & 20.291 & 2.298\\
+\hspace{1em}cif-extension & 0.113 (0.002) & 0.775 (0.005) & 176.867 & 50.345\\
+\hspace{1em}xgboost-aft & --- & 0.794 (0.004) & 35.380 & 0.013\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.233 (0.006) & 0.841 (0.005) & 5.731 & 1.497\\
-\hspace{1em}rsf-standard & 0.229 (0.006) & 0.835 (0.005) & 11.238 & 1.079\\
-\hspace{1em}aorsf-cph & 0.229 (0.006) & 0.841 (0.005) & 16.768 & 1.549\\
-\hspace{1em}aorsf-net & 0.228 (0.006) & 0.841 (0.005) & 597.572 & 1.659\\
-\hspace{1em}obliqueRSF-net & 0.212 (0.005) & 0.841 (0.005) & 3737.617 & 320.616\\
-\hspace{1em}cif-standard & 0.199 (0.005) & 0.839 (0.005) & 71.854 & 391.419\\
-\hspace{1em}nn-cox & 0.180 (0.017) & 0.826 (0.007) & 56.056 & 96.125\\
-\hspace{1em}cif-rotate & 0.172 (0.006) & 0.806 (0.007) & 589.494 & 69.448\\
-\hspace{1em}ranger-extratrees & 0.170 (0.004) & 0.824 (0.005) & 387.176 & 77.513\\
-\hspace{1em}glmnet-cox & 0.167 (0.044) & 0.817 (0.018) & 2.141 & 0.011\\
-\hspace{1em}aorsf-random & 0.139 (0.005) & 0.789 (0.006) & 12.952 & 1.501\\
-\hspace{1em}xgboost-cox & 0.122 (0.017) & 0.845 (0.005) & 10.926 & 0.015\\
-\hspace{1em}cif-extension & 0.109 (0.003) & 0.808 (0.006) & 176.907 & 57.216\\
-\hspace{1em}xgboost-aft & --- & 0.844 (0.005) & 24.549 & 0.013\\
+\hspace{1em}aorsf-fast & 0.233 (0.006) & 0.841 (0.005) & 5.478 & 1.709\\
+\hspace{1em}rsf-standard & 0.229 (0.006) & 0.835 (0.005) & 10.326 & 1.039\\
+\hspace{1em}aorsf-cph & 0.229 (0.006) & 0.840 (0.005) & 17.063 & 1.730\\
+\hspace{1em}cif-standard & 0.199 (0.005) & 0.839 (0.005) & 68.929 & 364.202\\
+\hspace{1em}obliqueRSF-net & 0.198 (0.005) & 0.839 (0.005) & 5341.195 & 1624.560\\
+\hspace{1em}nn-cox & 0.188 (0.018) & 0.826 (0.006) & 58.351 & 89.012\\
+\hspace{1em}cif-rotate & 0.172 (0.006) & 0.806 (0.007) & 569.166 & 67.654\\
+\hspace{1em}ranger-extratrees & 0.170 (0.004) & 0.824 (0.005) & 411.253 & 73.737\\
+\hspace{1em}glmnet-cox & 0.167 (0.044) & 0.817 (0.018) & 2.257 & 0.010\\
+\hspace{1em}aorsf-random & 0.151 (0.006) & 0.792 (0.007) & 14.023 & 1.686\\
+\hspace{1em}xgboost-cox & 0.122 (0.017) & 0.845 (0.005) & 11.985 & 0.015\\
+\hspace{1em}cif-extension & 0.109 (0.003) & 0.808 (0.006) & 169.620 & 49.957\\
+\hspace{1em}xgboost-aft & --- & 0.844 (0.005) & 30.837 & 0.012\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.093 (0.004) & 0.794 (0.007) & 4.549 & 1.078\\
-\hspace{1em}aorsf-net & 0.090 (0.004) & 0.792 (0.007) & 349.547 & 1.189\\
-\hspace{1em}rsf-standard & 0.090 (0.006) & 0.784 (0.006) & 8.991 & 0.984\\
-\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.792 (0.007) & 12.609 & 1.077\\
-\hspace{1em}obliqueRSF-net & 0.082 (0.003) & 0.791 (0.007) & 1869.359 & 387.014\\
-\hspace{1em}glmnet-cox & 0.078 (0.004) & 0.787 (0.007) & 1.673 & 0.011\\
-\hspace{1em}cif-standard & 0.073 (0.003) & 0.787 (0.007) & 73.989 & 364.863\\
-\hspace{1em}nn-cox & 0.070 (0.012) & 0.783 (0.010) & 32.099 & 82.720\\
-\hspace{1em}ranger-extratrees & 0.067 (0.003) & 0.779 (0.008) & 251.130 & 50.542\\
-\hspace{1em}aorsf-random & 0.059 (0.004) & 0.750 (0.008) & 9.179 & 1.091\\
-\hspace{1em}cif-rotate & 0.052 (0.003) & 0.768 (0.009) & 586.962 & 68.410\\
-\hspace{1em}xgboost-cox & 0.046 (0.014) & 0.794 (0.006) & 7.316 & 0.015\\
-\hspace{1em}cif-extension & 0.036 (0.002) & 0.769 (0.009) & 169.866 & 53.493\\
-\hspace{1em}xgboost-aft & --- & 0.793 (0.006) & 20.363 & 0.013\\
+\hspace{1em}aorsf-fast & 0.093 (0.004) & 0.793 (0.007) & 3.625 & 1.205\\
+\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.792 (0.007) & 12.691 & 1.331\\
+\hspace{1em}rsf-standard & 0.090 (0.006) & 0.784 (0.006) & 8.134 & 0.916\\
+\hspace{1em}glmnet-cox & 0.078 (0.004) & 0.787 (0.007) & 1.781 & 0.010\\
+\hspace{1em}obliqueRSF-net & 0.073 (0.003) & 0.789 (0.008) & 3058.459 & 2338.694\\
+\hspace{1em}cif-standard & 0.073 (0.003) & 0.787 (0.007) & 69.723 & 355.372\\
+\hspace{1em}nn-cox & 0.068 (0.016) & 0.781 (0.012) & 29.662 & 78.191\\
+\hspace{1em}ranger-extratrees & 0.067 (0.003) & 0.779 (0.008) & 219.331 & 61.397\\
+\hspace{1em}aorsf-random & 0.061 (0.005) & 0.750 (0.009) & 9.153 & 1.186\\
+\hspace{1em}cif-rotate & 0.052 (0.003) & 0.768 (0.009) & 573.621 & 66.723\\
+\hspace{1em}xgboost-cox & 0.047 (0.014) & 0.794 (0.006) & 7.662 & 0.014\\
+\hspace{1em}cif-extension & 0.036 (0.002) & 0.769 (0.009) & 167.033 & 51.074\\
+\hspace{1em}xgboost-aft & --- & 0.793 (0.006) & 25.321 & 0.012\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.100 (0.014) & 0.717 (0.012) & 0.237 & 0.049\\
-\hspace{1em}aorsf-cph & 0.099 (0.014) & 0.717 (0.011) & 0.636 & 0.049\\
-\hspace{1em}cif-standard & 0.097 (0.013) & 0.710 (0.012) & 0.745 & 3.685\\
-\hspace{1em}aorsf-net & 0.096 (0.014) & 0.717 (0.012) & 47.226 & 0.048\\
-\hspace{1em}aorsf-random & 0.096 (0.010) & 0.716 (0.011) & 1.717 & 0.044\\
-\hspace{1em}obliqueRSF-net & 0.089 (0.006) & 0.717 (0.012) & 252.190 & 16.726\\
-\hspace{1em}cif-rotate & 0.086 (0.017) & 0.705 (0.014) & 13.242 & 3.448\\
-\hspace{1em}rsf-standard & 0.086 (0.019) & 0.704 (0.011) & 1.901 & 0.150\\
-\hspace{1em}ranger-extratrees & 0.083 (0.007) & 0.710 (0.012) & 0.560 & 0.248\\
-\hspace{1em}cif-extension & 0.080 (0.006) & 0.709 (0.011) & 8.397 & 3.363\\
-\hspace{1em}glmnet-cox & 0.075 (0.016) & 0.711 (0.019) & 0.128 & 0.003\\
-\hspace{1em}xgboost-cox & 0.062 (0.013) & 0.701 (0.013) & 3.217 & 0.003\\
-\hspace{1em}nn-cox & -0.003 (0.003) & 0.508 (0.033) & 12.769 & 1.106\\
-\hspace{1em}xgboost-aft & --- & 0.706 (0.013) & 10.290 & 0.006\\
+\hspace{1em}aorsf-random & 0.103 (0.011) & 0.724 (0.012) & 0.974 & 0.048\\
+\hspace{1em}aorsf-cph & 0.100 (0.015) & 0.717 (0.011) & 0.631 & 0.050\\
+\hspace{1em}aorsf-fast & 0.099 (0.014) & 0.718 (0.012) & 0.235 & 0.052\\
+\hspace{1em}cif-standard & 0.097 (0.013) & 0.710 (0.012) & 0.698 & 3.233\\
+\hspace{1em}obliqueRSF-net & 0.087 (0.006) & 0.717 (0.011) & 227.346 & 90.031\\
+\hspace{1em}cif-rotate & 0.086 (0.017) & 0.705 (0.014) & 12.581 & 3.222\\
+\hspace{1em}rsf-standard & 0.086 (0.019) & 0.704 (0.011) & 1.899 & 0.150\\
+\hspace{1em}ranger-extratrees & 0.083 (0.007) & 0.710 (0.012) & 0.079 & 0.231\\
+\hspace{1em}cif-extension & 0.080 (0.006) & 0.709 (0.011) & 7.680 & 3.708\\
+\hspace{1em}glmnet-cox & 0.075 (0.016) & 0.711 (0.019) & 0.133 & 0.002\\
+\hspace{1em}xgboost-cox & 0.063 (0.013) & 0.701 (0.013) & 3.694 & 0.003\\
+\hspace{1em}nn-cox & -0.003 (0.003) & 0.510 (0.045) & 9.217 & 1.188\\
+\hspace{1em}xgboost-aft & --- & 0.706 (0.013) & 12.025 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.100 (0.017) & 0.713 (0.016) & 0.237 & 0.054\\
-\hspace{1em}aorsf-cph & 0.098 (0.017) & 0.712 (0.015) & 0.659 & 0.852\\
-\hspace{1em}aorsf-net & 0.095 (0.018) & 0.713 (0.017) & 47.589 & 0.049\\
-\hspace{1em}cif-standard & 0.091 (0.016) & 0.701 (0.017) & 0.717 & 3.703\\
-\hspace{1em}obliqueRSF-net & 0.087 (0.009) & 0.711 (0.015) & 249.790 & 16.701\\
-\hspace{1em}aorsf-random & 0.087 (0.012) & 0.702 (0.015) & 1.815 & 0.046\\
-\hspace{1em}cif-rotate & 0.084 (0.020) & 0.694 (0.017) & 13.154 & 3.977\\
-\hspace{1em}cif-extension & 0.081 (0.009) & 0.706 (0.017) & 8.446 & 4.066\\
-\hspace{1em}rsf-standard & 0.081 (0.020) & 0.694 (0.015) & 1.831 & 0.153\\
-\hspace{1em}ranger-extratrees & 0.079 (0.011) & 0.700 (0.016) & 0.636 & 0.254\\
-\hspace{1em}glmnet-cox & 0.073 (0.018) & 0.706 (0.024) & 0.125 & 0.003\\
-\hspace{1em}xgboost-cox & 0.059 (0.011) & 0.695 (0.018) & 3.136 & 0.003\\
-\hspace{1em}nn-cox & -0.005 (0.006) & 0.531 (0.054) & 13.107 & 0.969\\
-\hspace{1em}xgboost-aft & --- & 0.701 (0.019) & 11.227 & 0.006\\
+\hspace{1em}aorsf-fast & 0.099 (0.017) & 0.713 (0.016) & 0.235 & 0.051\\
+\hspace{1em}aorsf-cph & 0.099 (0.016) & 0.712 (0.015) & 0.641 & 0.050\\
+\hspace{1em}aorsf-random & 0.094 (0.014) & 0.706 (0.015) & 0.989 & 0.047\\
+\hspace{1em}cif-standard & 0.091 (0.016) & 0.701 (0.017) & 0.685 & 3.216\\
+\hspace{1em}obliqueRSF-net & 0.086 (0.008) & 0.712 (0.015) & 220.136 & 52.240\\
+\hspace{1em}cif-rotate & 0.084 (0.020) & 0.694 (0.017) & 12.394 & 3.355\\
+\hspace{1em}cif-extension & 0.081 (0.009) & 0.706 (0.017) & 7.829 & 3.620\\
+\hspace{1em}rsf-standard & 0.081 (0.020) & 0.694 (0.015) & 1.839 & 0.152\\
+\hspace{1em}ranger-extratrees & 0.079 (0.011) & 0.700 (0.016) & 0.081 & 0.273\\
+\hspace{1em}glmnet-cox & 0.073 (0.018) & 0.706 (0.024) & 0.136 & 0.002\\
+\hspace{1em}xgboost-cox & 0.060 (0.010) & 0.695 (0.018) & 3.234 & 0.003\\
+\hspace{1em}nn-cox & -0.020 (0.074) & 0.533 (0.044) & 9.225 & 1.019\\
+\hspace{1em}xgboost-aft & --- & 0.701 (0.019) & 12.802 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.072 (0.023) & 0.751 (0.029) & 1901.883 & 14.017\\
-\hspace{1em}cif-rotate & 0.070 (0.018) & 0.747 (0.027) & 6452.563 & 360.067\\
-\hspace{1em}cif-standard & 0.067 (0.019) & 0.747 (0.030) & 9.660 & 4.247\\
-\hspace{1em}aorsf-cph & 0.067 (0.029) & 0.747 (0.026) & 1.107 & 0.175\\
-\hspace{1em}aorsf-fast & 0.065 (0.028) & 0.747 (0.027) & 0.712 & 0.178\\
-\hspace{1em}cif-extension & 0.064 (0.016) & 0.746 (0.028) & 44.047 & 6.554\\
-\hspace{1em}ranger-extratrees & 0.061 (0.022) & 0.742 (0.031) & 0.228 & 0.169\\
-\hspace{1em}glmnet-cox & 0.041 (0.032) & 0.724 (0.036) & 5.780 & 0.006\\
-\hspace{1em}aorsf-random & 0.027 (0.015) & 0.696 (0.038) & 1.924 & 0.167\\
-\hspace{1em}xgboost-cox & 0.027 (0.034) & 0.741 (0.030) & 2.258 & 0.007\\
-\hspace{1em}rsf-standard & 0.024 (0.037) & 0.695 (0.033) & 0.366 & 0.743\\
-\hspace{1em}aorsf-net & 0.012 (0.062) & 0.740 (0.025) & 448.941 & 0.168\\
-\hspace{1em}nn-cox & -0.006 (0.043) & 0.669 (0.075) & 19.374 & 1.808\\
-\hspace{1em}xgboost-aft & --- & 0.744 (0.027) & 9.708 & 0.010\\
+\hspace{1em}obliqueRSF-net & 0.072 (0.022) & 0.751 (0.027) & 1772.643 & 38.287\\
+\hspace{1em}cif-rotate & 0.070 (0.018) & 0.747 (0.027) & 6243.357 & 338.140\\
+\hspace{1em}cif-standard & 0.067 (0.019) & 0.747 (0.030) & 8.875 & 4.293\\
+\hspace{1em}aorsf-cph & 0.067 (0.029) & 0.747 (0.026) & 1.614 & 0.300\\
+\hspace{1em}aorsf-fast & 0.065 (0.028) & 0.746 (0.026) & 1.325 & 0.297\\
+\hspace{1em}cif-extension & 0.064 (0.016) & 0.746 (0.028) & 42.920 & 6.083\\
+\hspace{1em}ranger-extratrees & 0.061 (0.022) & 0.742 (0.031) & 0.219 & 0.311\\
+\hspace{1em}glmnet-cox & 0.041 (0.032) & 0.724 (0.036) & 5.782 & 0.005\\
+\hspace{1em}xgboost-cox & 0.028 (0.032) & 0.742 (0.032) & 2.472 & 0.006\\
+\hspace{1em}aorsf-random & 0.025 (0.016) & 0.691 (0.042) & 1.888 & 0.271\\
+\hspace{1em}rsf-standard & 0.024 (0.037) & 0.695 (0.033) & 0.883 & 0.169\\
+\hspace{1em}nn-cox & -0.010 (0.071) & 0.682 (0.067) & 14.875 & 1.621\\
+\hspace{1em}xgboost-aft & --- & 0.744 (0.027) & 10.373 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.117 (0.028) & 0.787 (0.037) & 0.098 & 0.002\\
-\hspace{1em}aorsf-cph & 0.100 (0.039) & 0.769 (0.033) & 0.159 & 0.018\\
-\hspace{1em}aorsf-fast & 0.100 (0.037) & 0.768 (0.032) & 0.078 & 0.018\\
-\hspace{1em}aorsf-net & 0.097 (0.040) & 0.760 (0.034) & 12.491 & 0.018\\
-\hspace{1em}obliqueRSF-net & 0.089 (0.027) & 0.758 (0.036) & 97.158 & 5.447\\
-\hspace{1em}cif-rotate & 0.087 (0.048) & 0.755 (0.027) & 6.083 & 1.964\\
-\hspace{1em}cif-extension & 0.087 (0.036) & 0.730 (0.034) & 5.256 & 2.514\\
-\hspace{1em}aorsf-random & 0.087 (0.029) & 0.757 (0.032) & 1.061 & 0.018\\
-\hspace{1em}cif-standard & 0.084 (0.038) & 0.743 (0.036) & 0.347 & 1.132\\
-\hspace{1em}ranger-extratrees & 0.073 (0.016) & 0.741 (0.037) & 0.043 & 0.078\\
-\hspace{1em}rsf-standard & 0.072 (0.048) & 0.732 (0.034) & 0.156 & 0.040\\
-\hspace{1em}xgboost-cox & 0.029 (0.050) & 0.679 (0.121) & 0.266 & 0.002\\
-\hspace{1em}nn-cox & -0.004 (0.014) & 0.549 (0.110) & 11.152 & 0.406\\
-\hspace{1em}xgboost-aft & --- & 0.754 (0.038) & 6.738 & 0.005\\
+\hspace{1em}glmnet-cox & 0.117 (0.028) & 0.787 (0.037) & 0.105 & 0.002\\
+\hspace{1em}aorsf-cph & 0.100 (0.039) & 0.769 (0.033) & 0.165 & 0.018\\
+\hspace{1em}aorsf-fast & 0.100 (0.037) & 0.768 (0.033) & 0.079 & 0.018\\
+\hspace{1em}obliqueRSF-net & 0.091 (0.023) & 0.769 (0.032) & 78.242 & 6.014\\
+\hspace{1em}cif-rotate & 0.087 (0.048) & 0.755 (0.027) & 5.839 & 1.758\\
+\hspace{1em}cif-extension & 0.087 (0.036) & 0.730 (0.034) & 5.195 & 2.616\\
+\hspace{1em}aorsf-random & 0.085 (0.029) & 0.754 (0.034) & 0.258 & 0.019\\
+\hspace{1em}cif-standard & 0.084 (0.038) & 0.743 (0.036) & 0.281 & 1.194\\
+\hspace{1em}ranger-extratrees & 0.073 (0.016) & 0.741 (0.037) & 0.031 & 0.081\\
+\hspace{1em}rsf-standard & 0.072 (0.048) & 0.732 (0.034) & 0.113 & 0.039\\
+\hspace{1em}xgboost-cox & 0.026 (0.053) & 0.679 (0.120) & 0.330 & 0.002\\
+\hspace{1em}nn-cox & 0.001 (0.028) & 0.553 (0.117) & 7.201 & 0.403\\
+\hspace{1em}xgboost-aft & --- & 0.754 (0.038) & 7.320 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.029 (0.017) & 0.620 (0.024) & 0.100 & 0.002\\
-\hspace{1em}ranger-extratrees & 0.017 (0.016) & 0.596 (0.025) & 0.041 & 0.081\\
-\hspace{1em}obliqueRSF-net & 0.013 (0.016) & 0.593 (0.024) & 217.838 & 6.232\\
-\hspace{1em}aorsf-random & 0.013 (0.018) & 0.595 (0.024) & 1.166 & 0.020\\
-\hspace{1em}xgboost-cox & 0.010 (0.016) & 0.598 (0.031) & 1.331 & 0.002\\
-\hspace{1em}cif-standard & 0.008 (0.021) & 0.594 (0.023) & 0.315 & 1.056\\
-\hspace{1em}aorsf-cph & 0.007 (0.020) & 0.595 (0.026) & 0.256 & 0.022\\
-\hspace{1em}aorsf-fast & 0.007 (0.020) & 0.594 (0.026) & 0.114 & 0.021\\
-\hspace{1em}aorsf-net & 0.006 (0.020) & 0.592 (0.026) & 18.652 & 0.022\\
-\hspace{1em}cif-extension & -0.005 (0.023) & 0.580 (0.028) & 6.164 & 2.309\\
-\hspace{1em}nn-cox & -0.008 (0.023) & 0.526 (0.055) & 12.031 & 0.466\\
-\hspace{1em}cif-rotate & -0.012 (0.025) & 0.583 (0.030) & 7.411 & 2.486\\
-\hspace{1em}rsf-standard & -0.026 (0.032) & 0.577 (0.024) & 1.081 & 0.088\\
-\hspace{1em}xgboost-aft & --- & 0.582 (0.034) & 6.223 & 0.005\\
+\hspace{1em}glmnet-cox & 0.029 (0.017) & 0.620 (0.024) & 0.107 & 0.002\\
+\hspace{1em}obliqueRSF-net & 0.018 (0.014) & 0.598 (0.024) & 165.938 & 8.270\\
+\hspace{1em}ranger-extratrees & 0.017 (0.016) & 0.596 (0.025) & 0.031 & 0.080\\
+\hspace{1em}aorsf-random & 0.012 (0.017) & 0.595 (0.023) & 0.401 & 0.021\\
+\hspace{1em}xgboost-cox & 0.011 (0.016) & 0.598 (0.032) & 1.548 & 0.002\\
+\hspace{1em}cif-standard & 0.008 (0.021) & 0.594 (0.023) & 0.277 & 1.221\\
+\hspace{1em}aorsf-cph & 0.007 (0.021) & 0.595 (0.026) & 0.260 & 0.023\\
+\hspace{1em}aorsf-fast & 0.007 (0.019) & 0.594 (0.025) & 0.116 & 0.022\\
+\hspace{1em}cif-extension & -0.005 (0.023) & 0.580 (0.028) & 5.912 & 2.183\\
+\hspace{1em}nn-cox & -0.006 (0.014) & 0.521 (0.059) & 8.447 & 0.457\\
+\hspace{1em}cif-rotate & -0.012 (0.025) & 0.583 (0.030) & 6.486 & 2.537\\
+\hspace{1em}rsf-standard & -0.026 (0.032) & 0.577 (0.024) & 0.891 & 0.083\\
+\hspace{1em}xgboost-aft & --- & 0.582 (0.034) & 6.799 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.124 (0.016) & 0.746 (0.017) & 286.149 & 6.874\\
-\hspace{1em}cif-standard & 0.123 (0.020) & 0.743 (0.020) & 0.507 & 2.289\\
-\hspace{1em}rsf-standard & 0.120 (0.023) & 0.738 (0.019) & 1.437 & 0.115\\
-\hspace{1em}aorsf-net & 0.120 (0.024) & 0.738 (0.020) & 35.967 & 0.038\\
-\hspace{1em}aorsf-cph & 0.120 (0.025) & 0.736 (0.018) & 0.401 & 0.037\\
-\hspace{1em}aorsf-fast & 0.115 (0.024) & 0.733 (0.017) & 0.161 & 0.037\\
-\hspace{1em}cif-extension & 0.114 (0.017) & 0.743 (0.019) & 7.560 & 2.919\\
-\hspace{1em}cif-rotate & 0.107 (0.023) & 0.729 (0.017) & 11.241 & 3.023\\
-\hspace{1em}aorsf-random & 0.104 (0.023) & 0.724 (0.025) & 1.496 & 0.035\\
-\hspace{1em}ranger-extratrees & 0.094 (0.018) & 0.736 (0.025) & 0.102 & 0.143\\
-\hspace{1em}glmnet-cox & 0.090 (0.019) & 0.728 (0.021) & 0.106 & 0.002\\
-\hspace{1em}xgboost-cox & 0.083 (0.017) & 0.730 (0.020) & 2.538 & 0.003\\
-\hspace{1em}nn-cox & -0.007 (0.012) & 0.509 (0.061) & 11.658 & 0.746\\
-\hspace{1em}xgboost-aft & --- & 0.729 (0.021) & 10.625 & 0.006\\
+\hspace{1em}cif-standard & 0.123 (0.020) & 0.743 (0.020) & 0.478 & 2.173\\
+\hspace{1em}obliqueRSF-net & 0.121 (0.014) & 0.747 (0.018) & 234.738 & 19.092\\
+\hspace{1em}rsf-standard & 0.120 (0.023) & 0.738 (0.019) & 1.362 & 0.114\\
+\hspace{1em}aorsf-cph & 0.117 (0.022) & 0.733 (0.017) & 0.404 & 0.038\\
+\hspace{1em}cif-extension & 0.114 (0.017) & 0.743 (0.019) & 7.544 & 3.429\\
+\hspace{1em}aorsf-fast & 0.112 (0.024) & 0.730 (0.018) & 0.180 & 0.040\\
+\hspace{1em}aorsf-random & 0.111 (0.017) & 0.727 (0.018) & 0.728 & 0.036\\
+\hspace{1em}cif-rotate & 0.107 (0.023) & 0.729 (0.017) & 10.139 & 2.954\\
+\hspace{1em}ranger-extratrees & 0.094 (0.018) & 0.736 (0.025) & 0.051 & 0.121\\
+\hspace{1em}glmnet-cox & 0.090 (0.019) & 0.728 (0.021) & 0.113 & 0.002\\
+\hspace{1em}xgboost-cox & 0.083 (0.015) & 0.730 (0.020) & 2.632 & 0.003\\
+\hspace{1em}nn-cox & -0.015 (0.048) & 0.504 (0.037) & 8.139 & 0.727\\
+\hspace{1em}xgboost-aft & --- & 0.729 (0.021) & 12.179 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.745 (0.027) & 0.161 & 0.035\\
-\hspace{1em}aorsf-net & 0.074 (0.019) & 0.743 (0.027) & 25.934 & 0.038\\
-\hspace{1em}aorsf-cph & 0.071 (0.018) & 0.741 (0.028) & 0.375 & 0.035\\
-\hspace{1em}glmnet-cox & 0.063 (0.041) & 0.715 (0.091) & 0.502 & 0.002\\
-\hspace{1em}obliqueRSF-net & 0.063 (0.013) & 0.741 (0.023) & 221.806 & 11.417\\
-\hspace{1em}cif-rotate & 0.059 (0.016) & 0.721 (0.025) & 35.190 & 4.947\\
-\hspace{1em}cif-standard & 0.058 (0.014) & 0.738 (0.022) & 1.564 & 3.334\\
-\hspace{1em}ranger-extratrees & 0.054 (0.013) & 0.737 (0.029) & 0.118 & 0.176\\
-\hspace{1em}cif-extension & 0.052 (0.011) & 0.730 (0.022) & 13.507 & 5.567\\
-\hspace{1em}rsf-standard & 0.046 (0.023) & 0.705 (0.025) & 0.195 & 0.064\\
-\hspace{1em}xgboost-cox & 0.039 (0.051) & 0.747 (0.020) & 3.831 & 0.003\\
-\hspace{1em}aorsf-random & 0.033 (0.012) & 0.695 (0.030) & 0.427 & 0.037\\
-\hspace{1em}nn-cox & 0.008 (0.018) & 0.630 (0.123) & 12.211 & 0.596\\
-\hspace{1em}xgboost-aft & --- & 0.734 (0.020) & 11.525 & 0.006\\
+\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.745 (0.028) & 0.154 & 0.036\\
+\hspace{1em}aorsf-cph & 0.071 (0.018) & 0.742 (0.027) & 0.386 & 0.037\\
+\hspace{1em}glmnet-cox & 0.063 (0.041) & 0.715 (0.091) & 0.489 & 0.003\\
+\hspace{1em}obliqueRSF-net & 0.060 (0.013) & 0.741 (0.027) & 209.529 & 11.066\\
+\hspace{1em}cif-rotate & 0.059 (0.016) & 0.721 (0.025) & 34.549 & 4.966\\
+\hspace{1em}cif-standard & 0.058 (0.014) & 0.738 (0.022) & 1.380 & 3.350\\
+\hspace{1em}ranger-extratrees & 0.054 (0.013) & 0.737 (0.029) & 0.082 & 0.196\\
+\hspace{1em}cif-extension & 0.052 (0.011) & 0.730 (0.022) & 13.080 & 5.523\\
+\hspace{1em}rsf-standard & 0.046 (0.023) & 0.705 (0.025) & 0.174 & 0.061\\
+\hspace{1em}xgboost-cox & 0.044 (0.041) & 0.747 (0.020) & 3.880 & 0.003\\
+\hspace{1em}aorsf-random & 0.030 (0.011) & 0.675 (0.035) & 0.510 & 0.038\\
+\hspace{1em}nn-cox & 0.022 (0.036) & 0.673 (0.089) & 8.663 & 0.566\\
+\hspace{1em}xgboost-aft & --- & 0.734 (0.020) & 11.747 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.082 (0.017) & 0.722 (0.023) & 50.238 & 0.056\\
-\hspace{1em}aorsf-cph & 0.081 (0.018) & 0.722 (0.023) & 0.668 & 0.051\\
-\hspace{1em}aorsf-fast & 0.080 (0.020) & 0.722 (0.025) & 0.248 & 0.051\\
-\hspace{1em}ranger-extratrees & 0.073 (0.010) & 0.722 (0.022) & 0.137 & 0.198\\
-\hspace{1em}obliqueRSF-net & 0.073 (0.010) & 0.721 (0.023) & 389.465 & 9.365\\
-\hspace{1em}cif-standard & 0.070 (0.010) & 0.716 (0.023) & 1.468 & 3.315\\
-\hspace{1em}cif-rotate & 0.067 (0.019) & 0.708 (0.029) & 41.655 & 5.185\\
-\hspace{1em}cif-extension & 0.064 (0.009) & 0.714 (0.022) & 15.396 & 6.113\\
-\hspace{1em}glmnet-cox & 0.058 (0.020) & 0.699 (0.025) & 0.416 & 0.003\\
-\hspace{1em}rsf-standard & 0.058 (0.022) & 0.694 (0.026) & 1.515 & 0.121\\
-\hspace{1em}nn-cox & 0.053 (0.028) & 0.706 (0.032) & 12.912 & 0.599\\
-\hspace{1em}aorsf-random & 0.049 (0.010) & 0.682 (0.023) & 0.803 & 0.051\\
-\hspace{1em}xgboost-cox & 0.038 (0.017) & 0.698 (0.027) & 2.955 & 0.003\\
-\hspace{1em}xgboost-aft & --- & 0.697 (0.025) & 11.409 & 0.006\\
+\hspace{1em}aorsf-fast & 0.081 (0.019) & 0.723 (0.024) & 0.239 & 0.054\\
+\hspace{1em}aorsf-cph & 0.080 (0.018) & 0.722 (0.024) & 0.682 & 0.055\\
+\hspace{1em}ranger-extratrees & 0.073 (0.010) & 0.722 (0.022) & 0.243 & 0.187\\
+\hspace{1em}obliqueRSF-net & 0.071 (0.009) & 0.721 (0.022) & 354.417 & 22.308\\
+\hspace{1em}cif-standard & 0.070 (0.010) & 0.716 (0.023) & 1.282 & 3.415\\
+\hspace{1em}cif-rotate & 0.067 (0.019) & 0.708 (0.029) & 40.978 & 4.799\\
+\hspace{1em}cif-extension & 0.064 (0.009) & 0.714 (0.022) & 14.406 & 5.796\\
+\hspace{1em}glmnet-cox & 0.058 (0.020) & 0.699 (0.025) & 0.391 & 0.002\\
+\hspace{1em}rsf-standard & 0.058 (0.022) & 0.694 (0.026) & 1.601 & 0.122\\
+\hspace{1em}nn-cox & 0.051 (0.026) & 0.701 (0.038) & 9.103 & 0.579\\
+\hspace{1em}xgboost-cox & 0.040 (0.016) & 0.699 (0.026) & 3.449 & 0.003\\
+\hspace{1em}aorsf-random & 0.039 (0.012) & 0.668 (0.028) & 0.889 & 0.053\\
+\hspace{1em}xgboost-aft & --- & 0.697 (0.025) & 13.258 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.040 (0.008) & 0.778 (0.015) & 2.036 & 0.153\\
-\hspace{1em}obliqueRSF-net & 0.039 (0.007) & 0.780 (0.015) & 185.659 & 130.539\\
-\hspace{1em}aorsf-fast & 0.039 (0.007) & 0.776 (0.014) & 0.586 & 0.151\\
-\hspace{1em}aorsf-net & 0.039 (0.009) & 0.777 (0.016) & 76.845 & 0.149\\
-\hspace{1em}cif-standard & 0.038 (0.006) & 0.779 (0.017) & 10.065 & 30.887\\
-\hspace{1em}cif-extension & 0.036 (0.004) & 0.781 (0.019) & 54.976 & 20.544\\
-\hspace{1em}ranger-extratrees & 0.035 (0.005) & 0.777 (0.017) & 3.892 & 1.677\\
-\hspace{1em}cif-rotate & 0.034 (0.010) & 0.769 (0.018) & 187.949 & 22.910\\
-\hspace{1em}glmnet-cox & 0.031 (0.010) & 0.774 (0.020) & 1.723 & 0.004\\
-\hspace{1em}rsf-standard & 0.031 (0.011) & 0.752 (0.016) & 2.099 & 0.226\\
-\hspace{1em}nn-cox & 0.030 (0.012) & 0.759 (0.021) & 10.787 & 5.787\\
-\hspace{1em}aorsf-random & 0.027 (0.004) & 0.763 (0.019) & 1.213 & 0.152\\
-\hspace{1em}xgboost-cox & 0.010 (0.023) & 0.785 (0.022) & 3.676 & 0.005\\
-\hspace{1em}xgboost-aft & --- & 0.782 (0.017) & 13.342 & 0.006\\
+\hspace{1em}aorsf-cph & 0.040 (0.007) & 0.778 (0.014) & 2.083 & 0.144\\
+\hspace{1em}aorsf-fast & 0.039 (0.007) & 0.777 (0.015) & 0.557 & 0.141\\
+\hspace{1em}obliqueRSF-net & 0.038 (0.005) & 0.784 (0.017) & 592.769 & 868.718\\
+\hspace{1em}cif-standard & 0.038 (0.006) & 0.779 (0.017) & 9.787 & 30.975\\
+\hspace{1em}cif-extension & 0.036 (0.004) & 0.781 (0.019) & 56.440 & 20.992\\
+\hspace{1em}ranger-extratrees & 0.035 (0.005) & 0.777 (0.017) & 3.678 & 2.536\\
+\hspace{1em}cif-rotate & 0.034 (0.010) & 0.769 (0.018) & 187.605 & 23.593\\
+\hspace{1em}glmnet-cox & 0.031 (0.010) & 0.774 (0.020) & 2.237 & 0.004\\
+\hspace{1em}rsf-standard & 0.031 (0.011) & 0.752 (0.016) & 2.011 & 0.215\\
+\hspace{1em}nn-cox & 0.025 (0.020) & 0.745 (0.029) & 10.189 & 6.685\\
+\hspace{1em}aorsf-random & 0.021 (0.004) & 0.746 (0.021) & 1.800 & 0.163\\
+\hspace{1em}xgboost-cox & 0.010 (0.023) & 0.785 (0.022) & 4.562 & 0.006\\
+\hspace{1em}xgboost-aft & --- & 0.782 (0.017) & 18.309 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.036 (0.006) & 0.806 (0.016) & 2.012 & 0.149\\
-\hspace{1em}aorsf-net & 0.035 (0.008) & 0.807 (0.016) & 70.506 & 0.144\\
-\hspace{1em}aorsf-fast & 0.035 (0.007) & 0.806 (0.017) & 0.581 & 0.147\\
-\hspace{1em}obliqueRSF-net & 0.030 (0.006) & 0.807 (0.016) & 161.865 & 165.270\\
-\hspace{1em}glmnet-cox & 0.028 (0.008) & 0.798 (0.017) & 2.325 & 0.004\\
-\hspace{1em}cif-standard & 0.028 (0.005) & 0.803 (0.016) & 10.613 & 32.291\\
-\hspace{1em}rsf-standard & 0.027 (0.010) & 0.782 (0.018) & 1.210 & 0.190\\
-\hspace{1em}cif-extension & 0.025 (0.003) & 0.797 (0.018) & 55.652 & 21.758\\
-\hspace{1em}ranger-extratrees & 0.023 (0.005) & 0.791 (0.016) & 2.997 & 2.557\\
-\hspace{1em}cif-rotate & 0.023 (0.009) & 0.785 (0.017) & 188.792 & 24.524\\
-\hspace{1em}aorsf-random & 0.022 (0.004) & 0.775 (0.018) & 1.115 & 0.153\\
-\hspace{1em}nn-cox & 0.016 (0.027) & 0.772 (0.021) & 10.445 & 6.338\\
-\hspace{1em}xgboost-cox & 0.001 (0.030) & 0.776 (0.021) & 2.953 & 0.005\\
-\hspace{1em}xgboost-aft & --- & 0.784 (0.018) & 13.017 & 0.006\\
+\hspace{1em}aorsf-cph & 0.035 (0.006) & 0.805 (0.017) & 2.137 & 0.141\\
+\hspace{1em}aorsf-fast & 0.035 (0.007) & 0.807 (0.018) & 0.527 & 0.139\\
+\hspace{1em}obliqueRSF-net & 0.028 (0.004) & 0.810 (0.016) & 528.781 & 577.511\\
+\hspace{1em}glmnet-cox & 0.028 (0.008) & 0.798 (0.017) & 2.915 & 0.004\\
+\hspace{1em}cif-standard & 0.028 (0.005) & 0.803 (0.016) & 10.497 & 32.921\\
+\hspace{1em}rsf-standard & 0.027 (0.010) & 0.782 (0.018) & 1.632 & 0.159\\
+\hspace{1em}cif-extension & 0.025 (0.003) & 0.797 (0.018) & 56.277 & 22.158\\
+\hspace{1em}aorsf-random & 0.024 (0.005) & 0.770 (0.023) & 1.726 & 0.158\\
+\hspace{1em}ranger-extratrees & 0.023 (0.005) & 0.791 (0.016) & 3.510 & 2.689\\
+\hspace{1em}cif-rotate & 0.023 (0.009) & 0.785 (0.017) & 186.661 & 24.918\\
+\hspace{1em}nn-cox & 0.014 (0.022) & 0.763 (0.045) & 9.541 & 6.840\\
+\hspace{1em}xgboost-cox & 0.002 (0.028) & 0.775 (0.023) & 3.500 & 0.005\\
+\hspace{1em}xgboost-aft & --- & 0.784 (0.018) & 16.110 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.063 (0.032) & 0.691 (0.019) & 0.312 & 0.030\\
-\hspace{1em}aorsf-net & 0.061 (0.030) & 0.685 (0.019) & 30.349 & 0.031\\
-\hspace{1em}aorsf-fast & 0.059 (0.033) & 0.690 (0.019) & 0.124 & 0.029\\
-\hspace{1em}obliqueRSF-net & 0.058 (0.020) & 0.678 (0.020) & 294.626 & 2.961\\
-\hspace{1em}cif-extension & 0.050 (0.018) & 0.667 (0.019) & 9.104 & 3.317\\
-\hspace{1em}rsf-standard & 0.050 (0.035) & 0.673 (0.023) & 0.941 & 0.073\\
-\hspace{1em}cif-standard & 0.050 (0.023) & 0.667 (0.022) & 0.315 & 0.846\\
-\hspace{1em}ranger-extratrees & 0.049 (0.016) & 0.675 (0.019) & 0.037 & 0.065\\
-\hspace{1em}cif-rotate & 0.047 (0.026) & 0.664 (0.021) & 17.129 & 3.089\\
-\hspace{1em}glmnet-cox & 0.041 (0.024) & 0.664 (0.034) & 0.123 & 0.002\\
-\hspace{1em}aorsf-random & 0.040 (0.022) & 0.651 (0.023) & 0.507 & 0.026\\
-\hspace{1em}nn-cox & 0.033 (0.025) & 0.647 (0.029) & 12.472 & 0.368\\
-\hspace{1em}xgboost-cox & 0.018 (0.019) & 0.647 (0.027) & 1.541 & 0.002\\
-\hspace{1em}xgboost-aft & --- & 0.652 (0.026) & 8.410 & 0.006\\
+\hspace{1em}aorsf-cph & 0.063 (0.031) & 0.691 (0.019) & 0.308 & 0.030\\
+\hspace{1em}aorsf-fast & 0.060 (0.033) & 0.690 (0.019) & 0.122 & 0.030\\
+\hspace{1em}obliqueRSF-net & 0.056 (0.018) & 0.679 (0.021) & 219.473 & 7.313\\
+\hspace{1em}cif-extension & 0.050 (0.018) & 0.667 (0.019) & 8.429 & 3.209\\
+\hspace{1em}rsf-standard & 0.050 (0.035) & 0.673 (0.023) & 1.081 & 0.072\\
+\hspace{1em}cif-standard & 0.050 (0.023) & 0.667 (0.022) & 0.318 & 0.924\\
+\hspace{1em}ranger-extratrees & 0.049 (0.016) & 0.675 (0.019) & 0.037 & 0.062\\
+\hspace{1em}cif-rotate & 0.047 (0.026) & 0.664 (0.021) & 16.753 & 2.820\\
+\hspace{1em}aorsf-random & 0.043 (0.021) & 0.653 (0.024) & 0.549 & 0.027\\
+\hspace{1em}glmnet-cox & 0.041 (0.024) & 0.664 (0.034) & 0.127 & 0.002\\
+\hspace{1em}nn-cox & 0.019 (0.038) & 0.625 (0.062) & 9.211 & 0.291\\
+\hspace{1em}xgboost-cox & 0.018 (0.019) & 0.644 (0.027) & 1.583 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.652 (0.026) & 8.520 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.064 (0.009) & 0.807 (0.010) & 1.333 & 0.340\\
-\hspace{1em}aorsf-net & 0.062 (0.010) & 0.805 (0.012) & 169.694 & 0.379\\
-\hspace{1em}obliqueRSF-net & 0.062 (0.008) & 0.808 (0.012) & 488.662 & 265.171\\
-\hspace{1em}aorsf-cph & 0.060 (0.010) & 0.801 (0.012) & 4.935 & 0.352\\
-\hspace{1em}cif-standard & 0.059 (0.007) & 0.803 (0.013) & 24.446 & 98.767\\
-\hspace{1em}cif-rotate & 0.058 (0.009) & 0.802 (0.013) & 284.668 & 37.340\\
-\hspace{1em}rsf-standard & 0.057 (0.012) & 0.795 (0.013) & 3.426 & 1.202\\
-\hspace{1em}ranger-extratrees & 0.047 (0.004) & 0.794 (0.011) & 7.360 & 6.260\\
-\hspace{1em}cif-extension & 0.047 (0.003) & 0.805 (0.013) & 98.278 & 28.773\\
-\hspace{1em}glmnet-cox & 0.038 (0.017) & 0.775 (0.016) & 4.907 & 0.007\\
-\hspace{1em}nn-cox & 0.038 (0.017) & 0.767 (0.021) & 18.380 & 16.712\\
-\hspace{1em}aorsf-random & 0.031 (0.005) & 0.735 (0.015) & 2.853 & 0.387\\
-\hspace{1em}xgboost-cox & 0.015 (0.028) & 0.802 (0.013) & 4.763 & 0.009\\
-\hspace{1em}xgboost-aft & --- & 0.802 (0.012) & 18.127 & 0.009\\
+\hspace{1em}aorsf-fast & 0.064 (0.010) & 0.807 (0.011) & 1.213 & 0.363\\
+\hspace{1em}aorsf-cph & 0.061 (0.010) & 0.802 (0.012) & 5.020 & 0.374\\
+\hspace{1em}cif-standard & 0.059 (0.007) & 0.803 (0.013) & 23.531 & 96.894\\
+\hspace{1em}obliqueRSF-net & 0.058 (0.006) & 0.809 (0.012) & 1296.402 & 747.185\\
+\hspace{1em}cif-rotate & 0.058 (0.009) & 0.802 (0.013) & 284.179 & 37.551\\
+\hspace{1em}rsf-standard & 0.057 (0.012) & 0.795 (0.013) & 3.455 & 1.337\\
+\hspace{1em}ranger-extratrees & 0.047 (0.004) & 0.794 (0.011) & 7.979 & 6.588\\
+\hspace{1em}cif-extension & 0.047 (0.003) & 0.805 (0.013) & 97.660 & 28.300\\
+\hspace{1em}aorsf-random & 0.041 (0.008) & 0.760 (0.015) & 2.930 & 0.404\\
+\hspace{1em}glmnet-cox & 0.038 (0.017) & 0.775 (0.016) & 4.514 & 0.006\\
+\hspace{1em}nn-cox & 0.035 (0.016) & 0.766 (0.019) & 13.123 & 15.303\\
+\hspace{1em}xgboost-cox & 0.014 (0.027) & 0.802 (0.013) & 5.344 & 0.008\\
+\hspace{1em}xgboost-aft & --- & 0.802 (0.012) & 20.582 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.145 (0.008) & 0.792 (0.008) & 1.868 & 0.487\\
-\hspace{1em}aorsf-net & 0.144 (0.008) & 0.792 (0.009) & 293.640 & 0.547\\
-\hspace{1em}aorsf-cph & 0.143 (0.008) & 0.791 (0.009) & 6.625 & 0.504\\
-\hspace{1em}rsf-standard & 0.140 (0.008) & 0.784 (0.009) & 4.818 & 0.502\\
-\hspace{1em}obliqueRSF-net & 0.139 (0.007) & 0.791 (0.009) & 1176.365 & 156.871\\
-\hspace{1em}cif-standard & 0.134 (0.007) & 0.788 (0.009) & 23.671 & 101.207\\
-\hspace{1em}glmnet-cox & 0.131 (0.026) & 0.789 (0.012) & 1.560 & 0.007\\
-\hspace{1em}nn-cox & 0.127 (0.020) & 0.784 (0.016) & 29.272 & 17.344\\
-\hspace{1em}cif-rotate & 0.126 (0.007) & 0.783 (0.010) & 319.953 & 37.290\\
-\hspace{1em}ranger-extratrees & 0.113 (0.004) & 0.784 (0.008) & 9.060 & 6.474\\
-\hspace{1em}cif-extension & 0.092 (0.003) & 0.781 (0.009) & 111.068 & 32.105\\
-\hspace{1em}aorsf-random & 0.068 (0.005) & 0.725 (0.008) & 5.755 & 0.541\\
-\hspace{1em}xgboost-cox & 0.056 (0.029) & 0.794 (0.009) & 8.021 & 0.009\\
-\hspace{1em}xgboost-aft & --- & 0.793 (0.009) & 20.287 & 0.010\\
+\hspace{1em}aorsf-fast & 0.144 (0.008) & 0.792 (0.008) & 1.725 & 0.541\\
+\hspace{1em}aorsf-cph & 0.143 (0.008) & 0.791 (0.008) & 6.596 & 0.543\\
+\hspace{1em}rsf-standard & 0.140 (0.008) & 0.784 (0.009) & 4.936 & 0.480\\
+\hspace{1em}cif-standard & 0.134 (0.007) & 0.788 (0.009) & 23.408 & 98.656\\
+\hspace{1em}obliqueRSF-net & 0.132 (0.006) & 0.790 (0.009) & 2468.159 & 526.499\\
+\hspace{1em}glmnet-cox & 0.131 (0.026) & 0.789 (0.012) & 1.373 & 0.006\\
+\hspace{1em}nn-cox & 0.129 (0.019) & 0.788 (0.010) & 24.110 & 17.345\\
+\hspace{1em}cif-rotate & 0.126 (0.007) & 0.783 (0.010) & 319.531 & 37.277\\
+\hspace{1em}ranger-extratrees & 0.113 (0.004) & 0.784 (0.008) & 9.502 & 6.313\\
+\hspace{1em}cif-extension & 0.092 (0.003) & 0.781 (0.009) & 108.674 & 28.132\\
+\hspace{1em}aorsf-random & 0.086 (0.006) & 0.741 (0.009) & 5.817 & 0.577\\
+\hspace{1em}xgboost-cox & 0.057 (0.029) & 0.794 (0.009) & 8.811 & 0.009\\
+\hspace{1em}xgboost-aft & --- & 0.793 (0.009) & 24.056 & 0.009\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.115 (0.011) & 0.865 (0.012) & 1.218 & 0.301\\
-\hspace{1em}aorsf-net & 0.114 (0.011) & 0.863 (0.013) & 147.441 & 0.338\\
-\hspace{1em}aorsf-cph & 0.109 (0.011) & 0.858 (0.014) & 4.549 & 0.315\\
-\hspace{1em}rsf-standard & 0.108 (0.012) & 0.856 (0.012) & 3.125 & 1.151\\
-\hspace{1em}obliqueRSF-net & 0.108 (0.008) & 0.869 (0.011) & 393.285 & 338.322\\
-\hspace{1em}cif-rotate & 0.105 (0.010) & 0.869 (0.013) & 260.914 & 38.177\\
-\hspace{1em}cif-standard & 0.102 (0.009) & 0.864 (0.013) & 24.344 & 101.534\\
-\hspace{1em}cif-extension & 0.077 (0.005) & 0.864 (0.011) & 94.628 & 30.361\\
-\hspace{1em}ranger-extratrees & 0.075 (0.005) & 0.849 (0.015) & 7.492 & 6.923\\
-\hspace{1em}nn-cox & 0.071 (0.024) & 0.826 (0.016) & 15.797 & 17.312\\
-\hspace{1em}aorsf-random & 0.064 (0.006) & 0.795 (0.014) & 2.377 & 0.355\\
-\hspace{1em}glmnet-cox & 0.043 (0.044) & 0.767 (0.139) & 3.777 & 0.006\\
-\hspace{1em}xgboost-cox & -0.008 (0.019) & 0.869 (0.011) & 6.764 & 0.009\\
-\hspace{1em}xgboost-aft & --- & 0.870 (0.012) & 18.620 & 0.010\\
+\hspace{1em}aorsf-fast & 0.115 (0.010) & 0.866 (0.012) & 1.118 & 0.321\\
+\hspace{1em}aorsf-cph & 0.109 (0.011) & 0.858 (0.013) & 4.817 & 0.334\\
+\hspace{1em}rsf-standard & 0.108 (0.012) & 0.856 (0.012) & 3.228 & 1.248\\
+\hspace{1em}cif-rotate & 0.105 (0.010) & 0.869 (0.013) & 254.592 & 36.536\\
+\hspace{1em}cif-standard & 0.102 (0.009) & 0.864 (0.013) & 23.983 & 97.903\\
+\hspace{1em}obliqueRSF-net & 0.099 (0.007) & 0.870 (0.012) & 1112.448 & 1225.449\\
+\hspace{1em}aorsf-random & 0.082 (0.009) & 0.819 (0.016) & 2.432 & 0.372\\
+\hspace{1em}cif-extension & 0.077 (0.005) & 0.864 (0.011) & 91.356 & 28.914\\
+\hspace{1em}nn-cox & 0.075 (0.021) & 0.832 (0.015) & 12.343 & 14.955\\
+\hspace{1em}ranger-extratrees & 0.075 (0.005) & 0.849 (0.015) & 7.105 & 6.412\\
+\hspace{1em}glmnet-cox & 0.043 (0.044) & 0.767 (0.139) & 3.485 & 0.006\\
+\hspace{1em}xgboost-cox & -0.011 (0.019) & 0.869 (0.011) & 7.135 & 0.009\\
+\hspace{1em}xgboost-aft & --- & 0.870 (0.012) & 22.191 & 0.008\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.025 (0.004) & 0.767 (0.016) & 357.039 & 299.786\\
-\hspace{1em}cif-rotate & 0.025 (0.004) & 0.764 (0.017) & 268.402 & 37.899\\
-\hspace{1em}cif-standard & 0.025 (0.004) & 0.762 (0.017) & 23.450 & 98.166\\
-\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.764 (0.016) & 1.186 & 0.296\\
-\hspace{1em}aorsf-net & 0.024 (0.006) & 0.759 (0.017) & 134.136 & 0.330\\
-\hspace{1em}aorsf-cph & 0.023 (0.005) & 0.758 (0.016) & 4.128 & 0.305\\
-\hspace{1em}ranger-extratrees & 0.022 (0.003) & 0.759 (0.016) & 7.610 & 6.738\\
-\hspace{1em}glmnet-cox & 0.021 (0.009) & 0.765 (0.017) & 3.876 & 0.007\\
-\hspace{1em}cif-extension & 0.021 (0.002) & 0.768 (0.017) & 94.913 & 29.730\\
-\hspace{1em}rsf-standard & 0.019 (0.009) & 0.745 (0.018) & 3.221 & 1.242\\
-\hspace{1em}nn-cox & 0.018 (0.007) & 0.746 (0.028) & 16.152 & 17.979\\
-\hspace{1em}aorsf-random & 0.013 (0.003) & 0.714 (0.022) & 2.275 & 0.330\\
-\hspace{1em}xgboost-cox & 0.000 (0.025) & 0.762 (0.018) & 4.347 & 0.008\\
-\hspace{1em}xgboost-aft & --- & 0.764 (0.015) & 16.257 & 0.009\\
+\hspace{1em}cif-rotate & 0.025 (0.004) & 0.764 (0.017) & 267.261 & 37.143\\
+\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.764 (0.016) & 1.087 & 0.318\\
+\hspace{1em}cif-standard & 0.025 (0.004) & 0.762 (0.017) & 23.820 & 97.317\\
+\hspace{1em}obliqueRSF-net & 0.024 (0.003) & 0.772 (0.017) & 975.645 & 1212.002\\
+\hspace{1em}aorsf-cph & 0.024 (0.006) & 0.760 (0.018) & 4.270 & 0.315\\
+\hspace{1em}ranger-extratrees & 0.022 (0.003) & 0.759 (0.016) & 7.125 & 6.067\\
+\hspace{1em}glmnet-cox & 0.021 (0.009) & 0.765 (0.017) & 3.417 & 0.006\\
+\hspace{1em}cif-extension & 0.021 (0.002) & 0.768 (0.017) & 93.628 & 27.983\\
+\hspace{1em}rsf-standard & 0.019 (0.009) & 0.745 (0.018) & 3.032 & 1.194\\
+\hspace{1em}aorsf-random & 0.016 (0.004) & 0.725 (0.023) & 2.309 & 0.342\\
+\hspace{1em}nn-cox & 0.016 (0.008) & 0.734 (0.040) & 11.686 & 18.015\\
+\hspace{1em}xgboost-cox & 0.000 (0.027) & 0.763 (0.016) & 4.469 & 0.008\\
+\hspace{1em}xgboost-aft & --- & 0.764 (0.015) & 20.407 & 0.008\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.159 (0.019) & 0.744 (0.014) & 15.123 & 4.858\\
-\hspace{1em}aorsf-cph & 0.158 (0.016) & 0.743 (0.011) & 2.035 & 0.087\\
-\hspace{1em}aorsf-fast & 0.157 (0.016) & 0.743 (0.011) & 1.266 & 0.086\\
-\hspace{1em}aorsf-net & 0.155 (0.016) & 0.741 (0.011) & 84.984 & 0.088\\
-\hspace{1em}obliqueRSF-net & 0.155 (0.013) & 0.743 (0.011) & 232.467 & 12.924\\
-\hspace{1em}cif-standard & 0.151 (0.015) & 0.738 (0.012) & 1.537 & 5.829\\
-\hspace{1em}rsf-standard & 0.151 (0.017) & 0.737 (0.011) & 2.281 & 0.194\\
-\hspace{1em}aorsf-random & 0.146 (0.013) & 0.735 (0.011) & 2.457 & 0.082\\
-\hspace{1em}cif-extension & 0.143 (0.009) & 0.747 (0.013) & 11.222 & 4.744\\
-\hspace{1em}glmnet-cox & 0.137 (0.021) & 0.726 (0.014) & 0.136 & 0.003\\
-\hspace{1em}xgboost-cox & 0.122 (0.012) & 0.733 (0.012) & 3.919 & 0.003\\
-\hspace{1em}ranger-extratrees & 0.115 (0.005) & 0.744 (0.012) & 0.064 & 0.181\\
-\hspace{1em}nn-cox & 0.034 (0.057) & 0.599 (0.112) & 16.529 & 0.689\\
-\hspace{1em}xgboost-aft & --- & 0.733 (0.013) & 12.094 & 0.006\\
+\hspace{1em}cif-rotate & 0.159 (0.019) & 0.744 (0.014) & 15.330 & 4.515\\
+\hspace{1em}aorsf-cph & 0.158 (0.016) & 0.743 (0.011) & 1.176 & 0.092\\
+\hspace{1em}aorsf-fast & 0.157 (0.016) & 0.743 (0.011) & 0.407 & 0.091\\
+\hspace{1em}cif-standard & 0.151 (0.015) & 0.738 (0.012) & 1.512 & 6.113\\
+\hspace{1em}rsf-standard & 0.151 (0.017) & 0.737 (0.011) & 2.305 & 0.203\\
+\hspace{1em}obliqueRSF-net & 0.148 (0.009) & 0.748 (0.011) & 543.632 & 42.863\\
+\hspace{1em}aorsf-random & 0.148 (0.013) & 0.738 (0.012) & 1.747 & 0.086\\
+\hspace{1em}cif-extension & 0.143 (0.009) & 0.747 (0.013) & 10.794 & 4.507\\
+\hspace{1em}glmnet-cox & 0.137 (0.021) & 0.726 (0.014) & 0.146 & 0.002\\
+\hspace{1em}xgboost-cox & 0.122 (0.012) & 0.733 (0.012) & 4.230 & 0.003\\
+\hspace{1em}ranger-extratrees & 0.115 (0.005) & 0.744 (0.012) & 0.052 & 0.169\\
+\hspace{1em}nn-cox & 0.026 (0.051) & 0.598 (0.100) & 11.948 & 0.652\\
+\hspace{1em}xgboost-aft & --- & 0.733 (0.013) & 13.595 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.015 (0.011) & 0.651 (0.055) & 0.118 & 0.003\\
-\hspace{1em}aorsf-cph & 0.011 (0.013) & 0.644 (0.036) & 0.568 & 0.040\\
-\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.642 (0.036) & 0.193 & 0.040\\
-\hspace{1em}ranger-extratrees & 0.008 (0.006) & 0.642 (0.030) & 0.095 & 0.177\\
-\hspace{1em}cif-extension & 0.008 (0.010) & 0.625 (0.028) & 9.141 & 4.788\\
-\hspace{1em}obliqueRSF-net & 0.007 (0.010) & 0.628 (0.033) & 41.856 & 16.910\\
-\hspace{1em}aorsf-net & 0.007 (0.014) & 0.641 (0.034) & 22.236 & 0.041\\
-\hspace{1em}aorsf-random & 0.007 (0.013) & 0.633 (0.033) & 1.329 & 0.039\\
-\hspace{1em}xgboost-cox & 0.007 (0.017) & 0.639 (0.039) & 1.783 & 0.003\\
-\hspace{1em}cif-standard & 0.006 (0.011) & 0.628 (0.033) & 1.689 & 5.603\\
-\hspace{1em}nn-cox & -0.003 (0.005) & 0.510 (0.032) & 11.229 & 0.597\\
-\hspace{1em}rsf-standard & -0.009 (0.018) & 0.616 (0.036) & 0.824 & 0.073\\
-\hspace{1em}cif-rotate & -0.024 (0.023) & 0.553 (0.035) & 12.975 & 4.603\\
-\hspace{1em}xgboost-aft & --- & 0.629 (0.039) & 10.748 & 0.006\\
+\hspace{1em}glmnet-cox & 0.015 (0.011) & 0.651 (0.055) & 0.129 & 0.002\\
+\hspace{1em}obliqueRSF-net & 0.012 (0.008) & 0.649 (0.032) & 143.443 & 22.157\\
+\hspace{1em}aorsf-cph & 0.010 (0.013) & 0.644 (0.036) & 0.594 & 0.041\\
+\hspace{1em}aorsf-fast & 0.010 (0.014) & 0.641 (0.036) & 0.190 & 0.041\\
+\hspace{1em}ranger-extratrees & 0.008 (0.006) & 0.642 (0.030) & 0.054 & 0.156\\
+\hspace{1em}cif-extension & 0.008 (0.010) & 0.625 (0.028) & 8.632 & 4.411\\
+\hspace{1em}aorsf-random & 0.007 (0.013) & 0.636 (0.032) & 0.532 & 0.040\\
+\hspace{1em}cif-standard & 0.006 (0.011) & 0.628 (0.033) & 1.490 & 5.778\\
+\hspace{1em}xgboost-cox & 0.005 (0.019) & 0.639 (0.040) & 1.686 & 0.003\\
+\hspace{1em}nn-cox & -0.003 (0.005) & 0.515 (0.056) & 7.746 & 0.606\\
+\hspace{1em}rsf-standard & -0.009 (0.018) & 0.616 (0.036) & 0.745 & 0.069\\
+\hspace{1em}cif-rotate & -0.024 (0.023) & 0.553 (0.035) & 12.670 & 4.047\\
+\hspace{1em}xgboost-aft & --- & 0.629 (0.039) & 11.326 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}cif-rotate & 0.636 (0.024) & 0.943 (0.007) & 19.879 & 3.571\\
-\hspace{1em}glmnet-cox & 0.618 (0.034) & 0.940 (0.009) & 0.204 & 0.002\\
-\hspace{1em}nn-cox & 0.534 (0.072) & 0.910 (0.027) & 17.266 & 0.663\\
-\hspace{1em}aorsf-net & 0.530 (0.028) & 0.928 (0.010) & 50.081 & 0.045\\
-\hspace{1em}aorsf-cph & 0.522 (0.024) & 0.925 (0.011) & 1.645 & 0.043\\
-\hspace{1em}rsf-standard & 0.519 (0.022) & 0.922 (0.010) & 1.631 & 0.106\\
-\hspace{1em}aorsf-fast & 0.517 (0.027) & 0.923 (0.012) & 1.090 & 0.042\\
-\hspace{1em}xgboost-cox & 0.512 (0.029) & 0.932 (0.009) & 13.972 & 0.004\\
-\hspace{1em}cif-standard & 0.472 (0.029) & 0.902 (0.018) & 0.453 & 1.910\\
-\hspace{1em}cif-extension & 0.454 (0.025) & 0.920 (0.013) & 8.854 & 3.924\\
-\hspace{1em}ranger-extratrees & 0.430 (0.025) & 0.900 (0.019) & 0.049 & 0.103\\
-\hspace{1em}obliqueRSF-net & 0.319 (0.022) & 0.909 (0.017) & 155.421 & 8.847\\
-\hspace{1em}aorsf-random & 0.300 (0.032) & 0.849 (0.027) & 1.681 & 0.039\\
-\hspace{1em}xgboost-aft & --- & 0.927 (0.010) & 33.545 & 0.008\\
+\hspace{1em}cif-rotate & 0.636 (0.024) & 0.943 (0.007) & 19.882 & 3.487\\
+\hspace{1em}glmnet-cox & 0.618 (0.034) & 0.940 (0.009) & 0.205 & 0.002\\
+\hspace{1em}nn-cox & 0.544 (0.055) & 0.909 (0.020) & 13.922 & 0.580\\
+\hspace{1em}aorsf-cph & 0.523 (0.024) & 0.926 (0.011) & 0.783 & 0.043\\
+\hspace{1em}rsf-standard & 0.519 (0.022) & 0.922 (0.010) & 1.503 & 0.103\\
+\hspace{1em}aorsf-fast & 0.516 (0.028) & 0.922 (0.012) & 0.227 & 0.043\\
+\hspace{1em}xgboost-cox & 0.512 (0.029) & 0.932 (0.009) & 13.524 & 0.004\\
+\hspace{1em}cif-standard & 0.472 (0.029) & 0.902 (0.018) & 0.354 & 1.715\\
+\hspace{1em}cif-extension & 0.454 (0.025) & 0.920 (0.013) & 9.152 & 3.724\\
+\hspace{1em}ranger-extratrees & 0.430 (0.025) & 0.900 (0.019) & 0.045 & 0.090\\
+\hspace{1em}obliqueRSF-net & 0.309 (0.020) & 0.912 (0.017) & 124.706 & 10.004\\
+\hspace{1em}aorsf-random & 0.303 (0.029) & 0.851 (0.026) & 0.950 & 0.042\\
+\hspace{1em}xgboost-aft & --- & 0.927 (0.010) & 35.466 & 0.007\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-random & 0.076 (0.030) & 0.686 (0.026) & 1.162 & 0.016\\
-\hspace{1em}ranger-extratrees & 0.062 (0.028) & 0.675 (0.033) & 0.023 & 0.031\\
-\hspace{1em}aorsf-fast & 0.061 (0.043) & 0.672 (0.025) & 0.066 & 0.016\\
-\hspace{1em}obliqueRSF-net & 0.058 (0.026) & 0.676 (0.029) & 106.084 & 1.468\\
-\hspace{1em}aorsf-cph & 0.058 (0.041) & 0.670 (0.024) & 0.153 & 0.016\\
-\hspace{1em}cif-standard & 0.055 (0.032) & 0.670 (0.030) & 0.130 & 0.252\\
-\hspace{1em}cif-extension & 0.051 (0.032) & 0.664 (0.029) & 3.799 & 1.502\\
-\hspace{1em}aorsf-net & 0.047 (0.040) & 0.668 (0.026) & 16.124 & 0.017\\
-\hspace{1em}glmnet-cox & 0.033 (0.031) & 0.638 (0.059) & 0.081 & 0.002\\
-\hspace{1em}rsf-standard & 0.023 (0.039) & 0.642 (0.025) & 0.087 & 0.037\\
-\hspace{1em}cif-rotate & 0.017 (0.041) & 0.632 (0.032) & 4.687 & 1.897\\
-\hspace{1em}xgboost-cox & 0.011 (0.023) & 0.648 (0.032) & 0.721 & 0.002\\
-\hspace{1em}nn-cox & -0.051 (0.163) & 0.512 (0.082) & 10.516 & 0.209\\
-\hspace{1em}xgboost-aft & --- & 0.637 (0.034) & 6.271 & 0.005\\
+\hspace{1em}ranger-extratrees & 0.062 (0.028) & 0.675 (0.033) & 0.022 & 0.030\\
+\hspace{1em}aorsf-random & 0.061 (0.029) & 0.676 (0.027) & 0.324 & 0.015\\
+\hspace{1em}aorsf-fast & 0.061 (0.042) & 0.672 (0.025) & 0.066 & 0.017\\
+\hspace{1em}aorsf-cph & 0.059 (0.040) & 0.671 (0.024) & 0.153 & 0.016\\
+\hspace{1em}obliqueRSF-net & 0.056 (0.025) & 0.678 (0.030) & 88.165 & 3.793\\
+\hspace{1em}cif-standard & 0.055 (0.032) & 0.670 (0.030) & 0.128 & 0.254\\
+\hspace{1em}cif-extension & 0.051 (0.032) & 0.664 (0.029) & 3.845 & 1.378\\
+\hspace{1em}glmnet-cox & 0.033 (0.031) & 0.638 (0.059) & 0.097 & 0.002\\
+\hspace{1em}rsf-standard & 0.023 (0.039) & 0.642 (0.025) & 0.099 & 0.038\\
+\hspace{1em}cif-rotate & 0.017 (0.041) & 0.632 (0.032) & 4.906 & 1.275\\
+\hspace{1em}xgboost-cox & 0.012 (0.022) & 0.648 (0.031) & 1.076 & 0.002\\
+\hspace{1em}nn-cox & -0.020 (0.019) & 0.517 (0.110) & 7.701 & 0.203\\
+\hspace{1em}xgboost-aft & --- & 0.637 (0.034) & 7.679 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.142 (0.056) & 0.804 (0.056) & 10.521 & 0.014\\
-\hspace{1em}aorsf-cph & 0.124 (0.049) & 0.802 (0.051) & 0.076 & 0.013\\
-\hspace{1em}aorsf-fast & 0.121 (0.052) & 0.802 (0.054) & 0.049 & 0.014\\
-\hspace{1em}cif-rotate & 0.118 (0.059) & 0.787 (0.049) & 27.382 & 3.379\\
-\hspace{1em}obliqueRSF-net & 0.106 (0.051) & 0.792 (0.061) & 79.059 & 0.558\\
-\hspace{1em}cif-extension & 0.098 (0.055) & 0.799 (0.061) & 8.595 & 3.554\\
-\hspace{1em}cif-standard & 0.088 (0.051) & 0.781 (0.065) & 0.145 & 0.149\\
-\hspace{1em}rsf-standard & 0.087 (0.048) & 0.755 (0.050) & 0.067 & 0.025\\
-\hspace{1em}ranger-extratrees & 0.064 (0.044) & 0.774 (0.054) & 0.024 & 0.030\\
-\hspace{1em}aorsf-random & 0.053 (0.045) & 0.741 (0.060) & 0.136 & 0.014\\
-\hspace{1em}nn-cox & 0.051 (0.102) & 0.715 (0.100) & 11.692 & 0.121\\
-\hspace{1em}glmnet-cox & 0.049 (0.064) & 0.726 (0.090) & 0.265 & 0.002\\
-\hspace{1em}xgboost-cox & -0.028 (0.029) & 0.566 (0.093) & 0.118 & 0.002\\
-\hspace{1em}xgboost-aft & --- & 0.770 (0.056) & 4.896 & 0.005\\
+\hspace{1em}aorsf-cph & 0.124 (0.049) & 0.802 (0.051) & 0.074 & 0.014\\
+\hspace{1em}aorsf-fast & 0.121 (0.052) & 0.802 (0.054) & 0.049 & 0.015\\
+\hspace{1em}cif-rotate & 0.118 (0.059) & 0.787 (0.049) & 26.703 & 2.970\\
+\hspace{1em}obliqueRSF-net & 0.098 (0.049) & 0.790 (0.062) & 77.169 & 0.555\\
+\hspace{1em}cif-extension & 0.098 (0.055) & 0.799 (0.061) & 8.367 & 3.531\\
+\hspace{1em}cif-standard & 0.088 (0.051) & 0.781 (0.065) & 0.141 & 0.130\\
+\hspace{1em}rsf-standard & 0.087 (0.048) & 0.755 (0.050) & 0.066 & 0.025\\
+\hspace{1em}ranger-extratrees & 0.064 (0.044) & 0.774 (0.054) & 0.023 & 0.030\\
+\hspace{1em}nn-cox & 0.060 (0.065) & 0.746 (0.059) & 7.922 & 0.115\\
+\hspace{1em}aorsf-random & 0.051 (0.047) & 0.733 (0.063) & 0.150 & 0.015\\
+\hspace{1em}glmnet-cox & 0.049 (0.064) & 0.726 (0.090) & 0.271 & 0.002\\
+\hspace{1em}xgboost-cox & -0.028 (0.029) & 0.569 (0.094) & 0.119 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.770 (0.056) & 4.807 & 0.005\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-cph & 0.213 (0.008) & 0.868 (0.005) & 16.251 & 2.106\\
-\hspace{1em}aorsf-fast & 0.212 (0.008) & 0.868 (0.005) & 4.412 & 2.014\\
-\hspace{1em}aorsf-net & 0.210 (0.008) & 0.864 (0.006) & 433.878 & 1.276\\
-\hspace{1em}obliqueRSF-net & 0.209 (0.008) & 0.868 (0.006) & 1428.698 & 1042.701\\
-\hspace{1em}rsf-standard & 0.207 (0.009) & 0.860 (0.005) & 10.516 & 1.205\\
-\hspace{1em}glmnet-cox & 0.207 (0.011) & 0.860 (0.005) & 1.345 & 0.012\\
-\hspace{1em}cif-standard & 0.205 (0.007) & 0.863 (0.006) & 67.597 & 624.624\\
-\hspace{1em}cif-rotate & 0.190 (0.008) & 0.865 (0.005) & 263.660 & 62.919\\
-\hspace{1em}ranger-extratrees & 0.181 (0.007) & 0.860 (0.005) & 39.632 & 80.768\\
-\hspace{1em}cif-extension & 0.166 (0.003) & 0.866 (0.006) & 125.288 & 53.237\\
-\hspace{1em}aorsf-random & 0.140 (0.006) & 0.838 (0.007) & 8.961 & 1.333\\
-\hspace{1em}xgboost-cox & 0.020 (0.015) & 0.876 (0.005) & 8.907 & 0.017\\
-\hspace{1em}nn-cox & -0.002 (0.009) & 0.565 (0.092) & 20.937 & 106.131\\
-\hspace{1em}xgboost-aft & --- & 0.875 (0.005) & 27.908 & 0.015\\
+\hspace{1em}aorsf-cph & 0.213 (0.009) & 0.869 (0.006) & 17.803 & 1.370\\
+\hspace{1em}aorsf-fast & 0.212 (0.009) & 0.869 (0.006) & 4.902 & 1.336\\
+\hspace{1em}rsf-standard & 0.207 (0.009) & 0.860 (0.005) & 10.179 & 1.126\\
+\hspace{1em}glmnet-cox & 0.207 (0.011) & 0.860 (0.005) & 1.330 & 0.012\\
+\hspace{1em}cif-standard & 0.205 (0.007) & 0.863 (0.006) & 64.986 & 621.600\\
+\hspace{1em}obliqueRSF-net & 0.204 (0.008) & 0.868 (0.006) & 2703.887 & 9972.393\\
+\hspace{1em}cif-rotate & 0.190 (0.008) & 0.865 (0.005) & 259.239 & 60.313\\
+\hspace{1em}ranger-extratrees & 0.181 (0.007) & 0.860 (0.005) & 40.520 & 81.674\\
+\hspace{1em}cif-extension & 0.166 (0.003) & 0.866 (0.006) & 124.635 & 54.345\\
+\hspace{1em}aorsf-random & 0.141 (0.006) & 0.839 (0.007) & 9.973 & 1.490\\
+\hspace{1em}xgboost-cox & 0.022 (0.014) & 0.876 (0.005) & 9.315 & 0.017\\
+\hspace{1em}nn-cox & 0.000 (0.002) & 0.557 (0.095) & 19.415 & 103.251\\
+\hspace{1em}xgboost-aft & --- & 0.875 (0.005) & 31.562 & 0.014\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.430 (0.032) & 0.908 (0.021) & 0.067 & 0.018\\
-\hspace{1em}aorsf-cph & 0.418 (0.034) & 0.906 (0.021) & 0.149 & 0.018\\
-\hspace{1em}aorsf-net & 0.413 (0.035) & 0.905 (0.021) & 14.298 & 0.020\\
-\hspace{1em}cif-rotate & 0.405 (0.040) & 0.899 (0.022) & 10.102 & 1.933\\
-\hspace{1em}rsf-standard & 0.392 (0.034) & 0.895 (0.023) & 0.113 & 0.038\\
-\hspace{1em}obliqueRSF-net & 0.369 (0.032) & 0.907 (0.022) & 111.656 & 1.787\\
-\hspace{1em}aorsf-random & 0.354 (0.031) & 0.893 (0.020) & 1.093 & 0.018\\
-\hspace{1em}cif-standard & 0.352 (0.034) & 0.904 (0.025) & 0.206 & 0.363\\
-\hspace{1em}cif-extension & 0.348 (0.033) & 0.901 (0.023) & 5.775 & 2.199\\
-\hspace{1em}glmnet-cox & 0.342 (0.044) & 0.886 (0.028) & 0.116 & 0.002\\
-\hspace{1em}ranger-extratrees & 0.277 (0.027) & 0.894 (0.027) & 0.029 & 0.038\\
-\hspace{1em}xgboost-cox & 0.256 (0.103) & 0.881 (0.027) & 4.960 & 0.003\\
-\hspace{1em}nn-cox & -0.017 (0.018) & 0.563 (0.124) & 11.751 & 0.247\\
-\hspace{1em}xgboost-aft & --- & 0.883 (0.024) & 9.644 & 0.006\\
+\hspace{1em}aorsf-fast & 0.423 (0.035) & 0.904 (0.021) & 0.069 & 0.018\\
+\hspace{1em}aorsf-cph & 0.413 (0.034) & 0.901 (0.022) & 0.151 & 0.018\\
+\hspace{1em}cif-rotate & 0.405 (0.040) & 0.899 (0.022) & 9.295 & 2.069\\
+\hspace{1em}rsf-standard & 0.392 (0.034) & 0.895 (0.023) & 0.094 & 0.038\\
+\hspace{1em}obliqueRSF-net & 0.359 (0.030) & 0.908 (0.022) & 101.477 & 1.862\\
+\hspace{1em}cif-standard & 0.352 (0.034) & 0.904 (0.025) & 0.188 & 0.331\\
+\hspace{1em}cif-extension & 0.348 (0.033) & 0.901 (0.023) & 5.399 & 2.040\\
+\hspace{1em}aorsf-random & 0.344 (0.031) & 0.891 (0.020) & 0.277 & 0.019\\
+\hspace{1em}glmnet-cox & 0.342 (0.044) & 0.886 (0.028) & 0.117 & 0.002\\
+\hspace{1em}ranger-extratrees & 0.277 (0.027) & 0.894 (0.027) & 0.026 & 0.036\\
+\hspace{1em}xgboost-cox & 0.256 (0.103) & 0.882 (0.026) & 5.057 & 0.002\\
+\hspace{1em}nn-cox & -0.024 (0.033) & 0.556 (0.123) & 8.423 & 0.195\\
+\hspace{1em}xgboost-aft & --- & 0.883 (0.024) & 9.373 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.166 (0.012) & 0.762 (0.009) & 145.278 & 0.191\\
-\hspace{1em}obliqueRSF-net & 0.163 (0.010) & 0.761 (0.009) & 439.210 & 37.683\\
-\hspace{1em}aorsf-cph & 0.163 (0.012) & 0.759 (0.009) & 3.388 & 0.195\\
-\hspace{1em}aorsf-fast & 0.160 (0.013) & 0.757 (0.010) & 1.684 & 0.194\\
-\hspace{1em}cif-standard & 0.159 (0.010) & 0.759 (0.009) & 4.629 & 22.523\\
-\hspace{1em}rsf-standard & 0.159 (0.014) & 0.756 (0.009) & 3.066 & 0.967\\
-\hspace{1em}aorsf-random & 0.153 (0.010) & 0.752 (0.010) & 3.554 & 0.181\\
-\hspace{1em}cif-rotate & 0.147 (0.011) & 0.751 (0.011) & 34.328 & 8.629\\
-\hspace{1em}ranger-extratrees & 0.139 (0.006) & 0.749 (0.009) & 3.498 & 2.152\\
-\hspace{1em}xgboost-cox & 0.130 (0.014) & 0.753 (0.010) & 4.068 & 0.004\\
-\hspace{1em}cif-extension & 0.129 (0.004) & 0.751 (0.008) & 22.740 & 8.982\\
-\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.731 (0.009) & 0.278 & 0.004\\
-\hspace{1em}nn-cox & -0.009 (0.042) & 0.531 (0.050) & 16.635 & 8.901\\
-\hspace{1em}xgboost-aft & --- & 0.761 (0.009) & 14.813 & 0.006\\
+\hspace{1em}aorsf-cph & 0.163 (0.012) & 0.759 (0.009) & 2.494 & 0.205\\
+\hspace{1em}aorsf-random & 0.161 (0.011) & 0.759 (0.010) & 3.004 & 0.189\\
+\hspace{1em}aorsf-fast & 0.160 (0.012) & 0.757 (0.009) & 0.806 & 0.205\\
+\hspace{1em}cif-standard & 0.159 (0.010) & 0.759 (0.009) & 4.694 & 22.024\\
+\hspace{1em}rsf-standard & 0.159 (0.014) & 0.756 (0.009) & 2.995 & 0.391\\
+\hspace{1em}obliqueRSF-net & 0.156 (0.007) & 0.759 (0.009) & 931.931 & 64.305\\
+\hspace{1em}cif-rotate & 0.147 (0.011) & 0.751 (0.011) & 34.565 & 8.675\\
+\hspace{1em}ranger-extratrees & 0.139 (0.006) & 0.749 (0.009) & 3.211 & 2.477\\
+\hspace{1em}xgboost-cox & 0.130 (0.014) & 0.753 (0.009) & 4.472 & 0.004\\
+\hspace{1em}cif-extension & 0.129 (0.004) & 0.751 (0.008) & 22.084 & 8.110\\
+\hspace{1em}glmnet-cox & 0.118 (0.008) & 0.731 (0.009) & 0.247 & 0.003\\
+\hspace{1em}nn-cox & -0.001 (0.001) & 0.507 (0.049) & 13.019 & 7.622\\
+\hspace{1em}xgboost-aft & --- & 0.761 (0.009) & 16.743 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.148 (0.010) & 0.737 (0.009) & 520.813 & 39.774\\
-\hspace{1em}aorsf-net & 0.146 (0.011) & 0.735 (0.009) & 155.933 & 0.198\\
-\hspace{1em}aorsf-cph & 0.145 (0.012) & 0.734 (0.008) & 3.589 & 0.206\\
-\hspace{1em}cif-standard & 0.144 (0.011) & 0.734 (0.009) & 4.807 & 23.027\\
-\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 1.760 & 0.204\\
-\hspace{1em}aorsf-random & 0.140 (0.010) & 0.730 (0.008) & 3.803 & 0.185\\
-\hspace{1em}rsf-standard & 0.139 (0.012) & 0.731 (0.008) & 3.003 & 1.000\\
-\hspace{1em}ranger-extratrees & 0.135 (0.007) & 0.734 (0.009) & 3.564 & 2.555\\
-\hspace{1em}cif-rotate & 0.129 (0.010) & 0.725 (0.009) & 36.519 & 8.483\\
-\hspace{1em}cif-extension & 0.119 (0.006) & 0.731 (0.008) & 23.055 & 8.825\\
-\hspace{1em}glmnet-cox & 0.117 (0.008) & 0.727 (0.008) & 0.258 & 0.004\\
-\hspace{1em}xgboost-cox & 0.113 (0.008) & 0.729 (0.009) & 3.628 & 0.004\\
-\hspace{1em}nn-cox & -0.007 (0.027) & 0.511 (0.045) & 17.722 & 7.825\\
-\hspace{1em}xgboost-aft & --- & 0.735 (0.009) & 14.317 & 0.006\\
+\hspace{1em}aorsf-random & 0.145 (0.011) & 0.734 (0.009) & 3.327 & 0.197\\
+\hspace{1em}aorsf-cph & 0.145 (0.012) & 0.734 (0.009) & 2.801 & 0.221\\
+\hspace{1em}cif-standard & 0.144 (0.011) & 0.734 (0.009) & 4.829 & 22.205\\
+\hspace{1em}aorsf-fast & 0.143 (0.011) & 0.733 (0.009) & 0.883 & 0.217\\
+\hspace{1em}obliqueRSF-net & 0.142 (0.008) & 0.737 (0.009) & 870.086 & 81.412\\
+\hspace{1em}rsf-standard & 0.139 (0.012) & 0.731 (0.008) & 3.113 & 0.947\\
+\hspace{1em}ranger-extratrees & 0.135 (0.007) & 0.734 (0.009) & 3.100 & 2.527\\
+\hspace{1em}cif-rotate & 0.129 (0.010) & 0.725 (0.009) & 36.405 & 8.349\\
+\hspace{1em}cif-extension & 0.119 (0.006) & 0.731 (0.008) & 22.537 & 8.390\\
+\hspace{1em}glmnet-cox & 0.117 (0.008) & 0.727 (0.008) & 0.227 & 0.004\\
+\hspace{1em}xgboost-cox & 0.113 (0.008) & 0.729 (0.009) & 4.123 & 0.004\\
+\hspace{1em}nn-cox & -0.002 (0.002) & 0.515 (0.029) & 13.602 & 8.901\\
+\hspace{1em}xgboost-aft & --- & 0.735 (0.009) & 16.138 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-fast & 0.250 (0.014) & 0.825 (0.007) & 2.956 & 0.566\\
-\hspace{1em}aorsf-cph & 0.250 (0.013) & 0.825 (0.008) & 7.220 & 0.575\\
-\hspace{1em}aorsf-net & 0.250 (0.012) & 0.823 (0.008) & 267.989 & 0.565\\
-\hspace{1em}glmnet-cox & 0.248 (0.012) & 0.820 (0.007) & 0.539 & 0.006\\
-\hspace{1em}obliqueRSF-net & 0.247 (0.011) & 0.821 (0.008) & 1113.284 & 151.041\\
-\hspace{1em}ranger-extratrees & 0.243 (0.009) & 0.820 (0.007) & 12.743 & 12.085\\
-\hspace{1em}cif-standard & 0.243 (0.011) & 0.818 (0.008) & 19.565 & 120.023\\
-\hspace{1em}rsf-standard & 0.243 (0.013) & 0.815 (0.008) & 5.399 & 0.585\\
-\hspace{1em}aorsf-random & 0.231 (0.012) & 0.816 (0.008) & 6.409 & 0.562\\
-\hspace{1em}cif-rotate & 0.228 (0.009) & 0.819 (0.007) & 65.379 & 21.402\\
-\hspace{1em}cif-extension & 0.201 (0.005) & 0.820 (0.008) & 41.381 & 20.976\\
-\hspace{1em}xgboost-cox & 0.094 (0.038) & 0.824 (0.007) & 5.927 & 0.008\\
-\hspace{1em}nn-cox & 0.002 (0.005) & 0.616 (0.122) & 26.319 & 26.895\\
-\hspace{1em}xgboost-aft & --- & 0.823 (0.008) & 18.504 & 0.009\\
+\hspace{1em}aorsf-fast & 0.250 (0.014) & 0.825 (0.008) & 2.063 & 0.635\\
+\hspace{1em}aorsf-cph & 0.250 (0.013) & 0.825 (0.008) & 6.461 & 0.629\\
+\hspace{1em}glmnet-cox & 0.248 (0.012) & 0.820 (0.007) & 0.503 & 0.006\\
+\hspace{1em}obliqueRSF-net & 0.247 (0.011) & 0.824 (0.007) & 2219.216 & 1284.916\\
+\hspace{1em}ranger-extratrees & 0.243 (0.009) & 0.820 (0.007) & 11.176 & 10.433\\
+\hspace{1em}cif-standard & 0.243 (0.011) & 0.818 (0.008) & 19.000 & 116.158\\
+\hspace{1em}rsf-standard & 0.243 (0.013) & 0.815 (0.008) & 5.643 & 0.562\\
+\hspace{1em}cif-rotate & 0.228 (0.009) & 0.819 (0.007) & 63.456 & 20.143\\
+\hspace{1em}aorsf-random & 0.209 (0.011) & 0.813 (0.008) & 6.607 & 0.610\\
+\hspace{1em}cif-extension & 0.201 (0.005) & 0.820 (0.008) & 40.190 & 19.948\\
+\hspace{1em}xgboost-cox & 0.095 (0.038) & 0.824 (0.007) & 6.464 & 0.008\\
+\hspace{1em}nn-cox & 0.001 (0.003) & 0.576 (0.111) & 19.271 & 22.093\\
+\hspace{1em}xgboost-aft & --- & 0.823 (0.008) & 21.594 & 0.008\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.071 (0.011) & 0.795 (0.011) & 13.850 & 0.011\\
-\hspace{1em}aorsf-net & 0.070 (0.007) & 0.796 (0.011) & 330.532 & 0.613\\
-\hspace{1em}aorsf-fast & 0.070 (0.006) & 0.797 (0.010) & 2.561 & 0.604\\
-\hspace{1em}aorsf-cph & 0.069 (0.006) & 0.797 (0.011) & 8.283 & 0.620\\
-\hspace{1em}obliqueRSF-net & 0.068 (0.005) & 0.798 (0.012) & 1017.350 & 425.134\\
-\hspace{1em}rsf-standard & 0.065 (0.007) & 0.788 (0.014) & 3.894 & 1.314\\
-\hspace{1em}cif-standard & 0.061 (0.003) & 0.798 (0.011) & 50.694 & 181.616\\
-\hspace{1em}cif-rotate & 0.060 (0.005) & 0.791 (0.012) & 930.893 & 113.261\\
-\hspace{1em}ranger-extratrees & 0.054 (0.003) & 0.791 (0.012) & 7.314 & 7.943\\
-\hspace{1em}nn-cox & 0.039 (0.018) & 0.764 (0.027) & 20.414 & 24.555\\
-\hspace{1em}cif-extension & 0.034 (0.002) & 0.789 (0.011) & 122.779 & 33.342\\
-\hspace{1em}aorsf-random & 0.026 (0.002) & 0.747 (0.016) & 5.282 & 0.708\\
-\hspace{1em}xgboost-cox & 0.006 (0.017) & 0.799 (0.011) & 6.888 & 0.013\\
-\hspace{1em}xgboost-aft & --- & 0.796 (0.012) & 20.126 & 0.012\\
+\hspace{1em}glmnet-cox & 0.071 (0.011) & 0.795 (0.011) & 13.048 & 0.010\\
+\hspace{1em}aorsf-cph & 0.070 (0.006) & 0.797 (0.011) & 8.638 & 0.627\\
+\hspace{1em}aorsf-fast & 0.069 (0.006) & 0.797 (0.011) & 2.365 & 0.643\\
+\hspace{1em}rsf-standard & 0.065 (0.007) & 0.788 (0.014) & 4.277 & 1.394\\
+\hspace{1em}obliqueRSF-net & 0.064 (0.004) & 0.799 (0.011) & 2639.976 & 3402.983\\
+\hspace{1em}cif-standard & 0.061 (0.003) & 0.798 (0.011) & 49.621 & 182.059\\
+\hspace{1em}cif-rotate & 0.060 (0.005) & 0.791 (0.012) & 924.836 & 113.844\\
+\hspace{1em}ranger-extratrees & 0.054 (0.003) & 0.791 (0.012) & 8.222 & 7.874\\
+\hspace{1em}nn-cox & 0.040 (0.015) & 0.763 (0.022) & 16.891 & 22.686\\
+\hspace{1em}aorsf-random & 0.038 (0.003) & 0.768 (0.013) & 5.475 & 0.742\\
+\hspace{1em}cif-extension & 0.034 (0.002) & 0.789 (0.011) & 120.288 & 32.189\\
+\hspace{1em}xgboost-cox & 0.004 (0.019) & 0.800 (0.011) & 7.700 & 0.013\\
+\hspace{1em}xgboost-aft & --- & 0.796 (0.012) & 25.017 & 0.012\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}glmnet-cox & 0.123 (0.012) & 0.771 (0.009) & 5.422 & 0.010\\
-\hspace{1em}aorsf-cph & 0.117 (0.008) & 0.770 (0.008) & 11.811 & 1.833\\
-\hspace{1em}aorsf-fast & 0.115 (0.009) & 0.769 (0.008) & 3.826 & 1.817\\
-\hspace{1em}aorsf-net & 0.113 (0.009) & 0.769 (0.009) & 587.892 & 0.933\\
-\hspace{1em}obliqueRSF-net & 0.112 (0.007) & 0.767 (0.008) & 2630.588 & 231.667\\
-\hspace{1em}rsf-standard & 0.110 (0.008) & 0.763 (0.009) & 6.407 & 0.663\\
-\hspace{1em}cif-standard & 0.106 (0.006) & 0.764 (0.008) & 49.842 & 190.804\\
-\hspace{1em}nn-cox & 0.097 (0.010) & 0.757 (0.009) & 34.063 & 33.278\\
-\hspace{1em}ranger-extratrees & 0.096 (0.005) & 0.756 (0.009) & 11.323 & 9.400\\
-\hspace{1em}cif-rotate & 0.090 (0.007) & 0.745 (0.009) & 1109.925 & 112.893\\
-\hspace{1em}cif-extension & 0.055 (0.002) & 0.747 (0.009) & 137.470 & 34.230\\
-\hspace{1em}aorsf-random & 0.052 (0.003) & 0.720 (0.010) & 8.360 & 0.992\\
-\hspace{1em}xgboost-cox & 0.030 (0.023) & 0.772 (0.008) & 9.057 & 0.014\\
-\hspace{1em}xgboost-aft & --- & 0.772 (0.007) & 23.335 & 0.013\\
+\hspace{1em}glmnet-cox & 0.123 (0.012) & 0.771 (0.009) & 5.430 & 0.010\\
+\hspace{1em}aorsf-cph & 0.117 (0.008) & 0.770 (0.008) & 12.921 & 0.996\\
+\hspace{1em}aorsf-fast & 0.115 (0.008) & 0.770 (0.008) & 4.217 & 0.977\\
+\hspace{1em}rsf-standard & 0.110 (0.008) & 0.763 (0.009) & 7.137 & 0.691\\
+\hspace{1em}obliqueRSF-net & 0.108 (0.006) & 0.766 (0.008) & 4500.673 & 664.611\\
+\hspace{1em}cif-standard & 0.106 (0.006) & 0.764 (0.008) & 49.263 & 185.385\\
+\hspace{1em}nn-cox & 0.097 (0.012) & 0.755 (0.011) & 28.348 & 28.860\\
+\hspace{1em}ranger-extratrees & 0.096 (0.005) & 0.756 (0.009) & 9.647 & 8.153\\
+\hspace{1em}cif-rotate & 0.090 (0.007) & 0.745 (0.009) & 1039.879 & 113.336\\
+\hspace{1em}aorsf-random & 0.072 (0.003) & 0.741 (0.009) & 8.907 & 1.067\\
+\hspace{1em}cif-extension & 0.055 (0.002) & 0.747 (0.009) & 135.763 & 32.580\\
+\hspace{1em}xgboost-cox & 0.030 (0.022) & 0.772 (0.008) & 10.871 & 0.013\\
+\hspace{1em}xgboost-aft & --- & 0.772 (0.007) & 27.708 & 0.012\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}obliqueRSF-net & 0.114 (0.012) & 0.747 (0.012) & 381.891 & 25.692\\
-\hspace{1em}glmnet-cox & 0.113 (0.013) & 0.745 (0.012) & 0.276 & 0.004\\
-\hspace{1em}cif-rotate & 0.113 (0.013) & 0.741 (0.011) & 71.714 & 10.523\\
-\hspace{1em}aorsf-net & 0.112 (0.013) & 0.743 (0.012) & 114.909 & 0.160\\
-\hspace{1em}aorsf-cph & 0.112 (0.013) & 0.744 (0.012) & 1.931 & 0.145\\
-\hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 4.079 & 16.213\\
-\hspace{1em}aorsf-fast & 0.109 (0.015) & 0.743 (0.012) & 0.618 & 0.142\\
-\hspace{1em}rsf-standard & 0.105 (0.011) & 0.735 (0.011) & 2.510 & 0.252\\
-\hspace{1em}cif-extension & 0.094 (0.006) & 0.744 (0.012) & 29.918 & 10.109\\
-\hspace{1em}ranger-extratrees & 0.091 (0.008) & 0.738 (0.012) & 3.266 & 1.328\\
-\hspace{1em}xgboost-cox & 0.090 (0.009) & 0.744 (0.010) & 4.229 & 0.004\\
-\hspace{1em}aorsf-random & 0.080 (0.006) & 0.731 (0.013) & 2.025 & 0.143\\
-\hspace{1em}nn-cox & 0.074 (0.028) & 0.705 (0.036) & 18.945 & 5.181\\
-\hspace{1em}xgboost-aft & --- & 0.741 (0.009) & 13.087 & 0.006\\
+\hspace{1em}glmnet-cox & 0.113 (0.013) & 0.745 (0.012) & 0.268 & 0.003\\
+\hspace{1em}cif-rotate & 0.113 (0.013) & 0.741 (0.011) & 69.724 & 10.269\\
+\hspace{1em}aorsf-cph & 0.111 (0.014) & 0.745 (0.012) & 1.939 & 0.156\\
+\hspace{1em}aorsf-fast & 0.110 (0.015) & 0.744 (0.012) & 0.611 & 0.150\\
+\hspace{1em}cif-standard & 0.110 (0.011) & 0.744 (0.011) & 3.777 & 14.994\\
+\hspace{1em}obliqueRSF-net & 0.108 (0.009) & 0.748 (0.012) & 774.433 & 96.195\\
+\hspace{1em}rsf-standard & 0.105 (0.011) & 0.735 (0.011) & 2.783 & 0.272\\
+\hspace{1em}aorsf-random & 0.095 (0.008) & 0.739 (0.012) & 2.375 & 0.149\\
+\hspace{1em}cif-extension & 0.094 (0.006) & 0.744 (0.012) & 27.865 & 9.373\\
+\hspace{1em}ranger-extratrees & 0.091 (0.008) & 0.738 (0.012) & 3.445 & 1.214\\
+\hspace{1em}xgboost-cox & 0.091 (0.010) & 0.744 (0.010) & 4.688 & 0.004\\
+\hspace{1em}nn-cox & 0.076 (0.021) & 0.710 (0.021) & 14.766 & 4.725\\
+\hspace{1em}xgboost-aft & --- & 0.741 (0.009) & 14.633 & 0.006\\
 \addlinespace[0.3em]
@@
 \hline
-\hspace{1em}aorsf-net & 0.201 (0.050) & 0.797 (0.035) & 9.901 & 0.012\\
-\hspace{1em}aorsf-fast & 0.200 (0.049) & 0.795 (0.034) & 0.047 & 0.012\\
-\hspace{1em}cif-rotate & 0.198 (0.065) & 0.789 (0.036) & 4.476 & 1.284\\
-\hspace{1em}aorsf-cph & 0.198 (0.052) & 0.794 (0.035) & 0.094 & 0.012\\
-\hspace{1em}rsf-standard & 0.176 (0.048) & 0.787 (0.037) & 0.078 & 0.025\\
-\hspace{1em}cif-extension & 0.174 (0.048) & 0.795 (0.034) & 3.676 & 1.195\\
-\hspace{1em}glmnet-cox & 0.160 (0.036) & 0.788 (0.037) & 0.087 & 0.002\\
-\hspace{1em}aorsf-random & 0.154 (0.044) & 0.780 (0.037) & 1.060 & 0.011\\
-\hspace{1em}cif-standard & 0.128 (0.040) & 0.770 (0.037) & 0.105 & 0.120\\
-\hspace{1em}obliqueRSF-net & 0.126 (0.034) & 0.796 (0.029) & 62.935 & 0.664\\
+\hspace{1em}aorsf-cph & 0.201 (0.052) & 0.795 (0.034) & 0.093 & 0.011\\
+\hspace{1em}aorsf-fast & 0.200 (0.050) & 0.795 (0.034) & 0.047 & 0.011\\
+\hspace{1em}cif-rotate & 0.198 (0.065) & 0.789 (0.036) & 4.005 & 1.004\\
+\hspace{1em}rsf-standard & 0.176 (0.048) & 0.787 (0.037) & 0.065 & 0.026\\
+\hspace{1em}cif-extension & 0.174 (0.048) & 0.795 (0.034) & 3.264 & 1.159\\
+\hspace{1em}glmnet-cox & 0.160 (0.036) & 0.788 (0.037) & 0.083 & 0.002\\
+\hspace{1em}aorsf-random & 0.151 (0.044) & 0.777 (0.035) & 0.205 & 0.012\\
+\hspace{1em}cif-standard & 0.128 (0.040) & 0.770 (0.037) & 0.093 & 0.119\\
+\hspace{1em}obliqueRSF-net & 0.114 (0.033) & 0.799 (0.029) & 53.069 & 0.734\\
 \hspace{1em}ranger-extratrees & 0.092 (0.033) & 0.778 (0.038) & 0.020 & 0.026\\
-\hspace{1em}xgboost-cox & 0.067 (0.078) & 0.750 (0.046) & 1.408 & 0.002\\
-\hspace{1em}xgboost-aft & --- & 0.754 (0.047) & 5.530 & 0.005\\
-\hspace{1em}nn-cox & -0.023 (0.033) & 0.517 (0.114) & 11.344 & 0.133\\*
+\hspace{1em}xgboost-cox & 0.067 (0.076) & 0.753 (0.045) & 1.515 & 0.002\\
+\hspace{1em}xgboost-aft & --- & 0.754 (0.047) & 5.770 & 0.005\\
+\hspace{1em}nn-cox & -0.030 (0.028) & 0.521 (0.093) & 7.791 & 0.118\\*
 \end{longtable}

### 2022-11-23 paper/jbi/cover-letter/coverletter_main.tex
working on jcgs submission

% !TEX program = pdflatex
\input{coverletter_preamble.tex}

\begin{document}
\hfill{\today}

Journal of Biomedical Informatics

\bigskip

Dear Editors:

We are writing to submit our manuscript ``\red{Accelerated and interpretable oblique random survival forests}'' to the \emph{Journal of Biomedical Informatics}.

Our manuscript studies the \red{computational efficiency and interpretability of oblique random survival forests}, which is important because \red{oblique random survival forests have high prediction accuracy but high computational overhead and few methods have been developed to interpret them}. This paper extends our previous work in \emph{Annals of Applied Statistics}, \red{Oblique Random Survival Forests} (DOI: 10.1214/19-AOAS1261), by addressing \red{the computational inefficiency and difficulty of interpreting oblique random survival forests}.

We suggest the following reviewers:
\begin{itemize}
    \item \red{Terry M. Therneau, Mayo Clinic (therneau@mayo.edu)}
    \item \red{Jack Dunn, Massachusetts Institute of Technology (jack.dunn.nz@gmail.com)}
    \item \red{Marvin N. Wright, University of Bremen (wright@leibniz-bips.de)}
\end{itemize}

Our submission has the following keywords: \red{Oblique}, \red{Survival}, \red{Random Forests}, \red{Fast}, \red{Variable Importance}

As the corresponding author, I confirm that none of the co-authors listed below have a conflict of interest with the action editors and referees I suggest above. Further, I confirm that all co-authors below consent to my submission of this manuscript to the \emph{Journal of Biomedical Informatics}.

\bigskip

Sincerely,

\medskip

\red{Byron C. Jaeger (Wake Forest University School of Medicine)}\\
\red{Sawyer Welden (Wake Forest University School of Medicine)}\\
\red{Kristin Lenoir (Wake Forest University School of Medicine)}\\
\red{Jaime L. Speiser (Wake Forest University School of Medicine)}\\
\red{Matthew W. Segar (Texas Heart Institute)}\\
\red{Ambarish Pandey (University of Texas Southwestern Medical Center)}\\
\red{Nicholas M. Pajewski (Wake Forest University School of Medicine)}

\end{document}

### 2022-11-23 paper/jcgs/jcgs-template.tex
working on jcgs submission

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

\begin{document}

%\bibliographystyle{natbib}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf Title}
  \author{Author 1\thanks{
    The authors gratefully acknowledge \textit{please remember to list all relevant funding sources in the unblinded version}}\hspace{.2cm}\\
    Department of YYY, University of XXX\\
    and \\
    Author 2 \\
    Department of ZZZ, University of WWW}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Title}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
The text of your abstract.  200 or fewer words.
\end{abstract}

\noindent%
{\it Keywords:}  3 to 6 keywords, that do not appear in the title
\vfill

\newpage
\spacingset{1.5} % DON'T change the spacing!
\section{Introduction}
\label{sec:intro}

Body of paper.  Margins in this document are roughly 0.75 inches all
around, letter size paper.

\begin{figure}
\begin{center}
\includegraphics[width=3in]{fig1.pdf}
\end{center}
\caption{Consistency comparison in fitting surrogate model in the tidal
power example. \label{fig:first}}
\end{figure}

\begin{table}
\caption{D-optimality values for design $X$ under five different scenarios.  \label{tab:tabone}}
\begin{center}
\begin{tabular}{rrrrr}
one & two & three & four & five\\\hline
1.23 & 3.45 & 5.00 & 1.21 & 3.41 \\
1.23 & 3.45 & 5.00 & 1.21 & 3.42 \\
1.23 & 3.45 & 5.00 & 1.21 & 3.43 \\
\end{tabular}
\end{center}
\end{table}

\begin{itemize}
\item Note that figures and tables (such as Figure~\ref{fig:first} and
Table~\ref{tab:tabone}) should appear in the paper, not at the end or
in separate files.
\item In the latex source, near the top of the file the command
\verb+\newcommand{\blind}{1}+ can be used to hide the authors and
acknowledgements, producing the required blinded version.
\item Remember that in the blind version, you should not identify authors
indirectly in the text.  That is, don't say ``In Smith et. al.  (2009) we
showed that ...''.  Instead, say ``Smith et. al. (2009) showed that ...''.
\item These points are only intended to remind you of some requirements.
Please refer to the instructions for authors
at \url{http://amstat.tandfonline.com/action/authorSubmission?journalCode=ubes20&page=instructions#}
\item For more about ASA\ style, please see \url{http://journals.taylorandfrancis.com/amstat/asa-style-guide/}
\item If you have supplementary material (e.g., software, data, technical
proofs), identify them in the section below.  In early stages of the
submission process, you may be unsure what to include as supplementary
material.  Don't worry---this is something that can be worked out at later stages.
\end{itemize}

\section{Methods}
\label{sec:meth}
Don't take any of these section titles seriously.  They're just for
illustration.

\section{Verifications}
\label{sec:verify}
This section will be just long enough to illustrate what a full page of
text looks like, for margins and spacing.

\cite{Campbell02}, \cite{Schubert13}, \cite{Chi81}

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
{\bf With this spacing we have 30 lines per page.}
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

\section{Conclusion}
\label{sec:conc}

\bigskip
\begin{center}
{\large\bf SUPPLEMENTARY MATERIAL}
\end{center}

\begin{description}

\item[Title:] Brief description. (file type)

\item[R-package for  MYNEW routine:] R-package ?MYNEW? containing code to perform the diagnostic methods described in the article. The package also contains all datasets used as examples in the article. (GNU zipped tar file)

\item[HIV data set:] Data set used in the illustration of MYNEW method in Section~ 3.2. (.txt file)

\end{description}

\section{BibTeX}

We hope you've chosen to use BibTeX!\ If you have, please feel free to use the package natbib with any bibliography style you're comfortable with. The .bst file Chicago was used here, and agsm.bst has been included here for your convenience.

\bibliographystyle{Chicago}

\bibliography{Bibliography-MM-MC}
\end{document}

### 2022-11-23 paper/jcgs/main.Rnw
working on jcgs submission

--- 2022-11-23 paper/arxiv/main.Rnw
@@
-\documentclass{article}
-
-\usepackage{arxiv}
+\documentclass[12pt]{article}
+\usepackage{amsmath}
+\usepackage{graphicx}
+%\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{url} % not crucial - just used below for the URL
 
 \usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+% \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
 \usepackage{hyperref}       % hyperlinks
@@
 \usepackage{doi}
-
-\usepackage{lipsum}
 
@@
 
-\title{Accelerated and interpretable oblique random survival forests}
-
-% \date{\today}	% Here you can change the date presented in the paper title
-
-\author{ \href{https://orcid.org/0000-0001-7399-2299}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Byron C. Jaeger} \\
-	Department of Biostatistics and Data Science\\
-	Wake Forest University School of Medicine\\
-	Winston-Salem, NC 27157, USA \\
-	\texttt{bjaeger@wakehealth.edu}
-	\AND
-   Sawyer Welden \\
-   Department of Biostatistics and Data Science\\
-   Wake Forest University School of Medicine\\
-   Winston-Salem, NC 27157, USA \\
-   \texttt{swelden@wakehealth.edu}
-   \And
-   Kristin Lenoir \\
-   Department of Biostatistics and Data Science\\
-   Wake Forest University School of Medicine\\
-   Winston-Salem, NC 27157, USA \\
-   \texttt{klenoir@wakehealth.edu}
-	 \And
-	 Jaime L.~Speiser \\
-	 Department of Biostatistics and Data Science\\
-	 Wake Forest University School of Medicine\\
-	 Winston-Salem, NC 27157, USA \\
-	 \texttt{jspeiser@wakehealth.edu}
-	 \And
-	 Matthew W. Segar \\
-   Department of Cardiology \\
-   Texas Heart Institute \\
-   Houston, TX 77030, USA \\
-	 \texttt{Matthew.Segar@BCM.edu}
-   \And
-	 Ambarish Pandey \\
-   Division of Cardiology, Department of Internal Medicine \\
-   University of Texas Southwestern Medical Center \\
-   Dallas, TX 75235, USA \\
-	 \texttt{Ambarish.Pandey@UTSouthwestern.edu}
-	 \And
-	 Nicholas M.~Pajewski \\
-	 Department of Biostatistics and Data Science\\
-	 Wake Forest University School of Medicine\\
-	 Winston-Salem, NC 27157, USA \\
-	 \texttt{npajewsk@wakehealth.edu}
-	%% \AND
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-	%% \And
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-	%% \And
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-}
-
-% Uncomment to remove the date
-%\date{}
-
-% Uncomment to override  the `A preprint' in the header
-%\renewcommand{\headeright}{Technical Report}
-%\renewcommand{\undertitle}{Technical Report}
-\renewcommand{\shorttitle}{\textit{arXiv} Accelerated \& interpretable oblique RSFs}
-
-%%% Add PDF metadata to help others organize their library
-%%% Once the PDF is generated, you can check the metadata with
-%%% $ pdfinfo template.pdf
-\hypersetup{
-pdftitle={Accelerated and interpretable oblique random survival forests},
-pdfsubject={q-bio.NC, q-bio.QM},
-pdfauthor={Byron C.~Jaeger},
-pdfkeywords={Random Forest, Survival, Efficiency, Variable Importance},
-}
-
-\begin{document}
-
-\maketitle
+%\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{0}
+
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
 
@@
 
+\begin{document}
+
+%\bibliographystyle{natbib}
+
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\if0\blind
+{
+  \title{\bf Accelerated and interpretable oblique random survival forests}
+  \author{Byron C.~Jaeger\thanks{
+    The authors gratefully acknowledge \textit{the Center for Biomedical Informatics, Wake Forest University School of Medicine for supporting this research.
+The project was also supported by the National Center for Advancing Translational Sciences (NCATS), National Institutes of Health through Grant Award Number UL1TR001420.
+The content is solely the responsibility of the authors and does not necessarily represent the official views of the NIH.
+Dr.
+Pajewski was supported by grant number P30AG021332 from the National Institutes of Health, while Dr.
+Speiser was supported by K25AG068253.}}\hspace{.2cm}\\
+   Dept. of Biostatistics and Data Science,
+	 Wake Forest Univ. School of Medicine\\
+  and \\
+   Sawyer Welden \\
+   Dept. of Biostatistics and Data Science,
+   Wake Forest Univ. School of Medicine \\
+  and \\
+   Kristin Lenoir \\
+   Dept. of Biostatistics and Data Science,
+   Wake Forest Univ. School of Medicine\\
+  and \\
+   Jaime L.~Speiser \\
+	 Dept. of Biostatistics and Data Science,
+	 Wake Forest Univ. School of Medicine\\
+	and \\
+	 Matthew W. Segar \\
+   Dept. of Cardiology,
+   Texas Heart Institute \\
+  and \\
+   Ambarish Pandey \\
+   Division of Cardiology, Dept. of Internal Medicine, \\
+   University of Texas Southwestern Medical Center \\
+  and \\
+   Nicholas M.~Pajewski \\
+	 Dept. of Biostatistics and Data Science,
+	 Wake Forest Univ. School of Medicine
+  }
+  \maketitle
+} \fi
+
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf Title}
+\end{center}
+  \medskip
+} \fi
+
+\newpage
 \begin{abstract}
-
 	The oblique random survival forest (RSF) is an ensemble supervised learning method for right-censored outcomes.
@@
 All  oblique RSF methods in the current study are available in the \texttt{aorsf} R package.
-
 \end{abstract}
 
-% keywords can be removed
-\keywords{Oblique \and Survival \and Random Forests \and Fast \and Variable Importance}
+\noindent%
+{\it Keywords:}  Supervised learning, Computational efficiency, Variable importance
+\vfill
+
+\newpage
+\spacingset{1.5} % DON'T change the spacing!
 
@@
 
-Risk prediction may reduce the burden of disease by guiding strategies for prevention and treatment in a wide range of domains \citep{moons2012riskII, moons2012riskI}.
+Risk prediction may reduce the burden of disease by guiding strategies for prevention and treatment in a wide range of domains \citep{moons2012riskI}.
 The random survival forest (RSF; \citet{ishwaran2008random, hothorn2006unbiased}) is a supervised learning algorithm that has been used frequently for risk prediction \citep{wang2017selective}.
@@
 \citet{menze2011oblique} examined prediction accuracy of RFs in the presence of correlated predictors and found that oblique RFs had substantially higher prediction accuracy compared to axis-based RFs.
-Similarly, \citet{jaeger2019oblique} found that growing RSFs with oblique rather than axis-based survival trees reduced the RSF's concordance error, with improvements ranging from 2.5\% to 24.9\% depending on the data analyzed.
+Similarly, \citet{jaeger2019oblique} found that growing RSFs with oblique rather than axis-based trees reduced the RSF's concordance error, with improvements ranging from 2.5\% to 24.9\% depending on the data analyzed.
 
@@
 If $p$ predictors are potentially used to split $n$ observations, up to $\mathcal{O}(n^p)$ oblique splits can be assessed versus $\mathcal{O}(n \cdot p)$ axis-based splits \citep{heath1993induction, murthy1994system}.
-Second, estimating variable importance (VI) using permutation (a standard method for RFs) may be less effective in ensembles of oblique trees, as permuting the values of one predictor may not destabilize decisions that are based on linear combinations of predictors.
-Although VI is one of the most widely used strategies to interpret random forests \citep{ishwaran2019standard}, few studies have investigated VI for oblique random forests \citep[see][Section~5]{menze2011oblique}, and fewer have investigated VI specifically for the oblique RSF.
+Second, although variable importance (VI) is one of the most widely used strategies to interpret RFs \citep{ishwaran2019standard}, few studies have investigated VI for oblique RFs \citep[see][Section~5]{menze2011oblique}, and fewer have investigated VI specifically for the oblique RSF.
+Without general methodology to estimate VI, interpretation of oblique RFs is challenging.
 
 The aim of this paper is to introduce methodology that improves the computational efficiency and interpretation of oblique RSFs.
-\secref{sec:background} reviews prior studies that have developed methods related to those introduced in the current study.
-In \secref{sec:aorsf}, we reduce the computational cost of oblique RSFs (\ie, accelerate them) with a scalable algorithm to identify linear combinations of coefficients.
-In \secref{sec:negation_vi}, we improve the interpretability of oblique RSFs with `negation VI', a method to estimate VI that flips the sign of coefficients in linear combinations of predictors instead of permuting predictor values.
-We evaluate these methods with general benchmarking experiments and simulation studies in \secref{sec:numeric}.
-In \secref{sec:discussion}, we summarize results from the current study and present ideas connecting the current work to existing frameworks and methods for RSFs that future studies may engage with.
-All oblique RSF methods introduced are available in the \texttt{aorsf} R package \citep{jaeger2022aorsf}.
-
-\section{Related work} \label{sec:background}
+\secref{sec:methods} reviews prior work, introduces our method to reduce the computational cost of oblique RSFs (\ie, accelerate them), and introduces `negation VI', a method to estimate VI with oblique RSFs that does not require permutation of data.
+We describe benchmarking experiments and simulation studies to evaluate these methods in \secref{sec:numeric}, and present results in \secref{sec:results}.
+In \secref{sec:discussion}, we summarize results from the current study, connecting our findings to prior work and outlining potential future research topics.
+All oblique RSF methods introduced in the current study are available in the \texttt{aorsf} R package \citep{jaeger2022aorsf}.
+
+\section{Methods and materials} \label{sec:methods}
 
 Sections \ref{sec:rw_forests} and \ref{sec:rw_vi} briefly summarize prior studies that have developed methods related to the oblique RSF and VI, respectively.
+\secref{sec:aorsf} describes our approach to reduce computational overhead of the oblique RSF and \secref{sec:negation_vi} introduces negation VI, a novel technique to estimate VI in oblique RFs.
 
@@
 
-\section{The accelerated oblique random survival forest} \label{sec:aorsf}
-
-This section describes our approach to reduce computational overhead of the oblique RSF.
+\subsection{The accelerated oblique random survival forest} \label{sec:aorsf}
+
 Consider the usual framework for right-censored time-to-event outcomes with training data $$\dataset_{\text{train}} = \left\{ (T_i, \delta_i, \bm{x}_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$ Here, $T_i$ is the event time if $\delta_i=1$ or the censoring time if $\delta_i=0$, and $\bm{x}_i$ is a vector of predictors values.
@@
 
+\spacingset{1}
 \begin{algorithm}
@@
 \end{algorithm}
-
-\section{Negation variable importance} \label{sec:negation_vi}
+\spacingset{1.5}
+
+\subsection{Negation variable importance} \label{sec:negation_vi}
 
@@
 On the other hand, negating coefficients modifies the decision rule rather than modifying the data.
-
-To demonstrate the negation VI, consider a classification task where the goal is prediction of penguin species based on bill length and bill depth.
-Scaling these predictors to be centered at 0, we find decision boundaries from an oblique tree correctly classify
-
-Negation VI has several helpful characteristics.
-First, negation VI generalizes to any oblique RF (\ie, not just RSFs) using any valid error function, making it both general and flexible.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic.} Second, negation is non-random and hence reproducible without setting a random seed.
-Third, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% (a value indicative of type 2 diabetes) as a result of randomly permuting the values of Hemoglobin A1c.
+Thus, we hypothesize that negation VI can be more effective at identifying important predictors for correlated, numeric predictors.
+
+To demonstrate negation VI, consider a classification task where the goal is prediction of penguin species based on bill length and bill depth.
+Scaling these predictors to be centered at 0, we find oblique decision boundaries defined by linear combinations of bill length and bill depth correctly classify most of the data (Figure \ref{fig:negation_vs_permutation_viz}, Panel A).
+Permuting the values of bill length leads to several mis-classified observations, suggesting that bill length is an important predictor (Figure \ref{fig:negation_vs_permutation_viz}, Panel B).
+However, inspecting the permuted data shows that a number of observations moved to a region in the predictor space where there were previously no observations.
+Moving data to unobserved or perhaps unobservable regions of the predictor space may cause extrapolation error, which \citet{hooker2021unrestricted} identified as a cause of bias in permutation importance.
+Negating the coefficients for bill length in the linear combinations that define our decision boundaries causes the boundaries to flip across bill length's axis (Figure \ref{fig:negation_vs_permutation_viz}, Panel C).
+This leads to several mis-classified observations, suggesting that bill length is an important predictor without distorting the joint distribution of bill length and bill depth.
+
+Negation VI is an extension of ``anti VI", a VI technique for axis-based trees which became the default VI method for \texttt{randomForestSRC} in version 2.14.0.
+Anti VI reverses the direction of all decision nodes that use a specific variable, and then reassesses the ensemble prediction error.
+So, if an axis-based decision rule were defined as $x > 5 \Rightarrow$ send data to right node, the decision rule would become $x > 5 \Rightarrow$ send data to left node when computing the importance of a predictor $x$.
+Put in a way that makes the connection to negation VI more explicit, the `noised up' decision rule can be written as $-x > 5 \Rightarrow$ send data to right node.
+
+<<negation_vs_permutation_viz, fig.height=4, fig.width=12, fig.cap="Demonstration of negation and permutation importance for a single oblique tree.
+Panel A shows the original data and decision boundaries.
+Panel B shows the data with permuted bill length values.
+Panel C shows the decision boundaries after negating coefficients for bill length.
+Permutation and negation both show that bill length is an important predictor, but permuting bill length distorts its joint distribution with bill depth.">>=
+
+cols <- c("darkorange", "purple", "cyan4")
+
+penguins <- drop_na(palmerpenguins::penguins)
+
+simple_scale <- function(x) (x - mean(x))/sd(x)
+
+penguins_scaled <- penguins %>%
+  mutate(x = simple_scale(bill_length_mm),
+         y = simple_scale(bill_depth_mm)) %>%
+  filter(x > -3, x < 3, y > -2, y < 2)
+
+poly1 <- data.frame(
+  x = c(-3, -1.8, .8, -3, -3),
+  y = c(-2, -2,   2, 2, -2)
+)
+
+poly2 <- data.frame(
+  x = c(-1.35, .8,  3,  3, -1.35),
+  y = c(-1.3,   2,  2, .9, -1.3)
+)
+
+poly3 <- data.frame(
+  x = c(-1.8, -1.35, 3, 3, -1.8),
+  y = c(-2,    -1.3, .9, -2, -2)
+)
+
+p1 <- ggplot(data = penguins_scaled) +
+  aes(x = x, y = y) +
+  geom_point(aes(color = species, shape = species),
+             size = 3,
+             alpha = 0.8) +
+  geom_polygon(data=poly1, fill=cols[1], color='black', alpha=0.2) +
+  geom_polygon(data=poly2, fill=cols[2], color='black', alpha=0.2) +
+  geom_polygon(data=poly3, fill=cols[3], color='black', alpha=0.2) +
+  theme_minimal() +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(expand = c(0,0)) +
+  scale_color_manual(values = cols) +
+  scale_fill_manual(values = cols) +
+  labs(y = "Bill depth, scaled",
+       x = "") +
+  coord_cartesian(ylim = c(-2.1, 2.1),
+                  xlim = c(-3.1, 3.1)) +
+  theme(panel.grid = element_blank(),
+        legend.position = '',
+        text = element_text(size = 12))
+
+poly1_flip <- mutate(poly1, x = -x)
+poly2_flip <- mutate(poly2, x = -x)
+poly3_flip <- mutate(poly3, x = -x)
+
+p2 <- ggplot(data = penguins_scaled) +
+  aes(x = x, y = y) +
+  geom_point(aes(color = species, shape = species),
+             size = 3,
+             alpha = 0.8) +
+  geom_polygon(data=poly1_flip, fill=cols[1], color='black', alpha=0.2) +
+  geom_polygon(data=poly2_flip, fill=cols[2], color='black', alpha=0.2) +
+  geom_polygon(data=poly3_flip, fill=cols[3], color='black', alpha=0.2) +
+  theme_minimal() +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(expand = c(0,0)) +
+  scale_color_manual(values = cols) +
+  scale_fill_manual(values = cols) +
+  labs(x = "", y = "") +
+  coord_cartesian(ylim = c(-2.1, 2.1),
+                  xlim = c(-3.1, 3.1)) +
+  theme(panel.grid = element_blank(),
+        legend.position = '',
+        text = element_text(size = 12),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        axis.title.y = element_blank())
+
+penguins_permuted <- penguins_scaled %>%
+  mutate(x = sample(x, n(), replace = FALSE))
+
+p3 <- ggplot(data = penguins_permuted) +
+  aes(x = x, y = y) +
+  geom_point(aes(color = species, shape = species),
+             size = 3,
+             alpha = 0.8) +
+  geom_polygon(data = poly1, fill = cols[1], color = 'black', alpha = 0.2) +
+  geom_polygon(data = poly2, fill = cols[2], color = 'black', alpha = 0.2) +
+  geom_polygon(data = poly3, fill = cols[3], color = 'black', alpha = 0.2) +
+  geom_text(aes(x = -1.5, y = -1.5, label = "Impossible?"),
+            size = 4, check_overlap = TRUE) +
+  theme_minimal() +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(expand = c(0,0)) +
+  scale_color_manual(values = cols) +
+  scale_fill_manual(values = cols) +
+  labs(x = "Bill length, scaled") +
+  coord_cartesian(ylim = c(-2.1, 2.1),
+                  xlim = c(-3.1, 3.1)) +
+  theme(panel.grid = element_blank(),
+        legend.position = '',
+        text = element_text(size = 12),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        axis.title.y = element_blank())
+
+ggarrange(tag_facet(p1, tag_pool = "A", vjust = 2),
+          tag_facet(p3, tag_pool = "B", vjust = 2),
+          tag_facet(p2, tag_pool = "C", vjust = 2),
+          nrow = 1)
+
+@
+
+Negation VI has several strengths.
+First, it generalizes to any oblique RF (\ie, not just RSFs) using any valid error function, making it both general and flexible.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic.} Second, negation is non-random, making it reproducible without setting a random seed and making it slightly faster than permutation importance.
+Fourth, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% (a value indicative of type 2 diabetes) as a result of randomly permuting the values of Hemoglobin A1c.
+However, in scenarios where decision boundaries have symmetry around the origin of the predictor space (\eg, all positive cases lie in a circle centered at the origin, with negative cases sitting outside the circle), negation importance will be less effective than permutation.
 
@@
 
-Sections \ref{sec:bm_pred} and \ref{sec:bm_vi} present numerical experiments examining the accelerated oblique RSF and negation VI, respectively.
-The code used to run these experiments is available online at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}.
-All analyses were conducted using R version \Sexpr{r_version} with version 0.0.4 of \texttt{aorsf} \citep{jaeger2022aorsf}, and coordinated by the \texttt{targets} R package \citep{targets}.
-To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
+Sections \ref{sec:bm_pred} and \ref{sec:bm_vi} present the design of numerical experiments examining the accelerated oblique RSF and negation VI, respectively.
+\secref{sec:bm_compute} summarizes our approach to evaluating computational efficiency of learning algorithms, with a focus on the accelerated oblique RSF and other RSF implementations.
+\secref{sec:computing} provides details on computation and code.
 
@@
 \begin{landscape}
-
+\spacingset{1}
 \begin{table}[h!]
@@
 
- \texttt{rsf-standard} grows survival trees following Leo Breiman's original random forest algorithm with variables and cut-points selected to maximize a log-rank statistic.
+ \texttt{rsf-standard} grows survival trees following Leo Breiman's random forest algorithm with cut-points selected to maximize a log-rank statistic.
 \texttt{rsf-extratrees} grows survival trees with randomly selected predictors and cut-points.
-\texttt{cif-standard} uses the framework of conditional inference to grow survival trees.
+\texttt{cif-standard} uses conditional inference.
 \texttt{cif-rotate} extends \texttt{cif-standard} by applying principal component analysis to random subsets of data prior to growing each survival tree.
@@
  \texttt{obliqueRSF-net} \newline
- \texttt{aorsf-net} \newline
+ % \texttt{aorsf-net} \newline
  \textcolor{purple}{\texttt{aorsf-fast}} \newline
@@
  Oblique survival trees following Leo Breiman's random forest algorithm.
-Linear combinations of inputs are derived using \texttt{glmnet} in \texttt{obliqueRSF-net} and \texttt{aorsf-net}, using Newton Raphson scoring for the Cox partial likelihood function in \texttt{aorsf-fast} (1 iteration of scoring) and \texttt{aorsf-cph} (up to 20 iterations), and chosen randomly from a uniform distribution in \texttt{aorsf-extratrees}.
-Cut-points are selected from 5 randomly selected candidates to maximize a log-rank statistic.
+Linear combinations of inputs are derived using \texttt{glmnet} in \texttt{obliqueRSF-net}, using Newton Raphson scoring for the Cox partial likelihood function in \texttt{aorsf-fast} (1 iteration of scoring) and \texttt{aorsf-cph} (up to 20 iterations), and chosen randomly from a uniform distribution in \texttt{aorsf-extratrees}.
+Cut-points are selected to maximize a log-rank statistic.
 \\
@@
  \texttt{xgboost-cox} maximizes the Cox partial likelihood function, whereas \texttt{xgboost-aft} maximizes the accelerated failure time likelihood function.
-Nested cross validation (5 folds) is applied to tune the number of trees grown, the minimum number of observations in a leaf node was 10, the maximum depth of trees was 6, and $\sqrt{p}$ variables were considered randomly for each tree split, where $p$ is the total number of predictors.
+Nested cross validation (5 folds) is applied to tune the number of trees.
+The minimum number of observations in a leaf node was 10, the maximum depth of trees was 6, and $\sqrt{p}$ variables were considered randomly for each split, where $p$ is the number of predictors.
 \\
@@
 \restoregeometry
+\spacingset{1.5}
 
@@
 
-\subsubsection{Results} \label{sec:results_pred}
+\subsection{Benchmark of variable importance} \label{sec:bm_vi}
+
+The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between relevant and irrelevant variables, where relevance is defined by having a relationship with the simulated outcome.
+We consider methods that are intrinsic to the oblique RF (\eg, ANOVA VI), those that are intrinsic to the RF (\eg, permutation VI), and those that are model-agnostic (\eg, SHAP VI).
+VI methods with unavailable or still developing software were not included.\footnote{Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
+Therefore, it is not incorporated in the current simulation study.}
+
+\subsubsection{Variable importance techniques}
+
+We compute permutation VI for axis based RSFs using the \texttt{randomForestSRC} package.
+We compute ANOVA VI, negation VI, and permutation VI for oblique RSFs using the \texttt{aorsf} package.
+For ANOVA VI, we applied a p-value threshold of 0.01, following the threshold recommended by \citet{menze2011oblique}.
+We compute SHAP VI for boosted tree models using the \texttt{xgboost} package \citep{xgboost}, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
+
+% We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
+
+\subsubsection{Variable types}
+
+We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome on the log-hazard scale. Specifically, \begin{itemize}
+\item \textit{irrelevant} variables had no relationship with the outcome.
+\item \textit{main effect} variables had a linear relationship to the outcome on the log-hazard scale.
+\item \textit{non-linear effect} variables had a non-linear relationship to the outcome.
+A normally distributed variable $x$ was generated with a linear relationship to the outcome on the log-hazard scale, then $\tilde{x} = \text{sin}(a \cdot \pi \cdot x)$ was retained for modeling.
+The constant $a$ varied uniformly from 0.125 to 0.25.
+\item \textit{combination effect} variables were formed by linear combinations of three other variables.
+While their combination was linearly related to the outcome on the log-hazard scale, each of the three variables contributing to the combination had no relation to the outcome.
+\item \textit{interaction effect} variables were related to the outcome by multiplicative interaction with one other variable, which could have been a main effect, non-linear effect, or combination effect variable.
+\end{itemize}
+
+\subsubsection{Simulated data} \label{sec:data_sim}
+
+We initiated each set of simulated data with a random draw of size $n$ from a $p$-dimensional multivariate normal distribution, yielding $n$ observations of $p$ predictors.
+Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
+A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package \citep{simsurv, simsurv_paper}.
+The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
+Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be evaluated based on their ability to detect these effects.
+
+\subsubsection{Parameter specifications}
+
+<<>>=
+
+n_obs <- bm_vi_viz$smry %>%
+  ungroup() %>%
+  distinct(n_obs) %>%
+  drop_na() %>%
+  filter(n_obs > 0) %>%
+  pull(n_obs) %>%
+  glue_collapse(sep = ', ', last = ', and ')
+
+pred_corr <- bm_vi_viz$smry %>%
+  ungroup() %>%
+  distinct(pred_corr_max) %>%
+  drop_na() %>%
+  filter(pred_corr_max < 1) %>%
+  pull(pred_corr_max) %>%
+  glue_collapse(sep = ', ', last = ', and ')
+
+s <- mean_ci(clincalc_r2)*100
+
+clincalc_r2_sexpr <- table_glue(
+  "{s[['y']]} ({s[['ymin']]}, {s[['ymax']]})"
+)
+
+@
+
+Parameters that varied in the current simulation study included the number of observations (\Sexpr{n_obs}) and the absolute value of the maximum correlation between predictors (\Sexpr{pred_corr}).
+Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
+Using this design for simulated data, the Heller explained relative risk (95\% confidence interval) of our covariates was \Sexpr{clincalc_r2_sexpr} \citep{heller2012measure} with 2,500 observations.
+
+\subsubsection{Evaluation of variable importance}
+
+We compared VI techniques based on their discrimination (\ie, C-statistic) between relevant and irrelevant variables.
+Specifically, we generated a binary outcome for each predictor variable based on its relevance (\ie, the binary outcome is 1 if the variable is relevant, 0 otherwise).
+Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic which may be interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
+
+\subsection{Benchmark of computational efficiency} \label{sec:bm_compute}
+
+The aim of this numeric experiment is to evaluate the computational efficiency of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
+
+\subsubsection{Evaluation of computational efficiency}
+
+For each learner discussed in \secref{sec:learners} and for each of the \Sexpr{n_risk_tasks} risk prediction tasks analyzed in \secref{sec:bm_pred}, we tracked the amount of time required to fit a prediction model (including time used to tune parameters) and compute predicted risk.
+
+We performed additional benchmarks on the time required to fit 500 trees using \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger}.
+The learners that represented these R packages were \texttt{aorsf-fast}, \texttt{rsf-standard}, and \texttt{rsf-extratrees}, respectively.
+To allow for controlled comparisons of computational efficiency with varying dimensions of training data, we used the same process to simulate data as described in \secref{sec:data_sim}, varying the number of observations from 100 to 10000 and the number of predictors from 10 to 1000.
+The minimum node size of trees in this experiment was dynamically set as the nearest integer to the number of observations in the training set divided by 10.
+
+\subsection{Computational details} \label{sec:computing}
+
+All analyses were conducted using R version \Sexpr{r_version} with version 0.0.4 of the \texttt{aorsf} \citep{jaeger2022aorsf} package.
+Analyses were coordinated with assistance from the \texttt{targets} package \citep{targets}.
+To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
+All code used in the current study is available at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench},
+
+\section{Results} \label{sec:results}
+
+In \secref{sec:results_pred}, \secref{sec:results_vi}, and \secref{sec:results_computing}, we present results from the benchmark or prediction accuracy, the simulation study of VI, and the benchmark of computational efficiency, respectively.
+
+\subsection{Prediction accuracy} \label{sec:results_pred}
 
@@
 
-\subsection{Benchmark of variable importance} \label{sec:bm_vi}
-
-The aim of this experiment is to evaluate negation VI and similar VI methods based on how well they can discriminate between relevant and irrelevant variables, where relevance is defined by having a relationship with the simulated outcome.
-We consider methods that are intrinsic to the oblique RF (\eg, ANOVA VI), those that are intrinsic to the RF (\eg, permutation VI), and those that are model-agnostic (\eg, SHAP VI).
-VI methods with unavailable or still developing software were not included.\footnote{Although the \texttt{party} package implements the approach to VI developed by \citet{strobl2007bias}, the developers of the \texttt{party} package note that the implementation of this approach for survival outcomes is ``extremely slow and experimental'' as of version 1.3.10.
-Therefore, it is not incorporated in the current simulation study.}
-
-\subsubsection{Variable importance techniques}
-
-We compute permutation VI for axis based RSFs using the \texttt{randomForestSRC} package.
-We compute ANOVA VI, negation VI, and permutation VI for oblique RSFs using the \texttt{aorsf} package.
-For ANOVA VI, we applied a p-value threshold of 0.01, following the threshold recommended by \citet{menze2011oblique}.
-We compute SHAP VI for boosted tree models using the \texttt{xgboost} package \citep{xgboost}, which incorporates the tree SHAP approach proposed by \citet{lundberg2018consistent}.
-
-% We also compute SHAP VI for accelerated oblique RSFs using the \texttt{fastshap} package.
-
-\subsubsection{Variable types}
-
-We considered five classes of predictor variables, with each class characterized by its variables' relationship to a right-censored outcome on the log-hazard scale. Specifically, \begin{itemize}
-\item \textit{irrelevant} variables had no relationship with the outcome.
-\item \textit{main effect} variables had a linear relationship to the outcome on the log-hazard scale.
-\item \textit{non-linear effect} variables had a non-linear relationship to the outcome.
-A normally distributed variable $x$ was generated with a linear relationship to the outcome on the log-hazard scale, then $\tilde{x} = \text{sin}(a \cdot \pi \cdot x)$ was retained for modeling.
-The constant $a$ varied uniformly from 0.125 to 0.25.
-\item \textit{combination effect} variables were formed by linear combinations of three other variables.
-While their combination was linearly related to the outcome on the log-hazard scale, each of the three variables contributing to the combination had no relation to the outcome.
-\item \textit{interaction effect} variables were related to the outcome by multiplicative interaction with one other variable, which could have been a main effect, non-linear effect, or combination effect variable.
-\end{itemize}
-
-\subsubsection{Simulated data} \label{sec:data_sim}
-
-We initiated each set of simulated data with a random draw of size $n$ from a $p$-dimensional multivariate normal distribution, yielding $n$ observations of $p$ predictors.
-Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
-A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package \citep{simsurv, simsurv_paper}.
-The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
-Interactions, non-linear mappings, and combinations were dropped from the predictor matrix after the outcome was generated so that VI techniques could be evaluated based on their ability to detect these effects.
-
-\subsubsection{Parameter specifications}
-
-<<>>=
-
-n_obs <- bm_vi_viz$smry %>%
-  ungroup() %>%
-  distinct(n_obs) %>%
-  drop_na() %>%
-  filter(n_obs > 0) %>%
-  pull(n_obs) %>%
-  glue_collapse(sep = ', ', last = ', and ')
-
-pred_corr <- bm_vi_viz$smry %>%
-  ungroup() %>%
-  distinct(pred_corr_max) %>%
-  drop_na() %>%
-  filter(pred_corr_max < 1) %>%
-  pull(pred_corr_max) %>%
-  glue_collapse(sep = ', ', last = ', and ')
-
-s <- mean_ci(clincalc_r2)*100
-
-clincalc_r2_sexpr <- table_glue(
-  "{s[['y']]} ({s[['ymin']]}, {s[['ymax']]})"
-)
-
-@
-
-Parameters that varied in the current simulation study included the number of observations (\Sexpr{n_obs}) and the absolute value of the maximum correlation between predictors (\Sexpr{pred_corr}).
-Parameters that remain fixed throughout the study included the number of predictors in each class (15) and the effect size of each predictor (one standard deviation increase associated with a 64\% increase in relative risk).
-Using this design for simulated data, the Heller explained relative risk (95\% confidence interval) of our covariates was \Sexpr{clincalc_r2_sexpr} \citep{heller2012measure} with 2,500 observations.
-
-\subsubsection{Evaluation of variable importance}
-
-We compared VI techniques based on their discrimination (\ie, C-statistic) between relevant and irrelevant variables.
-Specifically, we generated a binary outcome for each predictor variable based on its relevance (\ie, the binary outcome is 1 if the variable is relevant, 0 otherwise).
-Treating VI as if it were a ‘prediction’ for these binary outcomes yields a C-statistic which may be interpreted as the probability that the VI technique will rank a relevant variable higher than an irrelevant variable \citep{harrell1982evaluating}.
-
-\subsubsection{Results} \label{sec:results_vi}
+\subsection{Variable importance} \label{sec:results_vi}
 
@@
 
-\subsection{Benchmark of computational efficiency} \label{sec:bm_compute}
-
-The aim of this numeric experiment is to evaluate the computational efficiency of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
-
-\subsubsection{Evaluation of computational efficiency}
-
-For each learner discussed in \secref{sec:learners} and for each of the \Sexpr{n_risk_tasks} risk prediction tasks analyzed in \secref{sec:bm_pred}, we tracked the amount of time required to fit a prediction model (including time used to tune parameters) and compute predicted risk.
-
-We performed additional benchmarks on the time required to fit 500 trees using \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger}.
-The learners that represented these R packages were \texttt{aorsf-fast}, \texttt{rsf-standard}, and \texttt{rsf-extratrees}, respectively.
-To allow for controlled comparisons of computational efficiency with varying dimensions of training data, we used the same process to simulate data as described in \secref{sec:data_sim}, varying the number of observations from 100 to 10000 and the number of predictors from 10 to 1000.
-The minimum node size of trees in this experiment was dynamically set as the nearest integer to the number of observations in the training set divided by 10.
-
-\subsubsection{Results}
+\subsection{Computational efficiency} \label{sec:results_computing}
 
@@
 We have also introduced a general and flexible method to estimate VI with oblique RFs, and demonstrated its effectiveness for numeric, correlated predictors.
-Code used for the current study is available at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}, and the \texttt{aorsf} package is available at \href{https://github.com/bcjaeger/aorsf}{https://github.com/bcjaeger/aorsf}.
-
-\subsection*{Acknowledgements}
-
-Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine.
-The project described was supported by the National Center for Advancing Translational Sciences (NCATS), National Institutes of Health, through Grant Award Number UL1TR001420.
-The content is solely the responsibility of the authors and does not necessarily represent the official views of the NIH.
-Dr.
-Pajewski was supported by grant number P30AG021332 from the National Institutes of Health, while Dr.
-Speiser was supported by K25AG068253.
-
-% Manual newpage inserted to improve layout of sample file - not
-% needed in general before appendices/bibliography.
-
-\newpage
 
@@
 
-\vskip 0.2in
-\bibliographystyle{unsrtnat}
+\bibliographystyle{Chicago}
+
 \bibliography{main}
-
 \end{document}

### 2022-11-23 paper/jcgs/main.tex
working on jcgs submission

--- 2022-11-23 paper/arxiv/main.tex
@@
-\documentclass{article}\usepackage[]{graphicx}\usepackage[]{xcolor}
+\documentclass[12pt]{article}\usepackage[]{graphicx}\usepackage[]{xcolor}
 % maxwidth is the original width if it is less than linewidth
@@
 \usepackage{alltt}
-
-\usepackage{arxiv}
+\usepackage{amsmath}
+\usepackage{graphicx}
+%\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{url} % not crucial - just used below for the URL
 
 \usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+% \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
 \usepackage{hyperref}       % hyperlinks
@@
 
-\title{Accelerated and interpretable oblique random survival forests}
-
-% \date{\today}	% Here you can change the date presented in the paper title
-
-\author{ \href{https://orcid.org/0000-0001-7399-2299}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Byron C. Jaeger} \\
-	Department of Biostatistics and Data Science\\
-	Wake Forest University School of Medicine\\
-	Winston-Salem, NC 27157, USA \\
-	\texttt{bjaeger@wakehealth.edu}
-	\AND
-   Sawyer Welden \\
-   Department of Biostatistics and Data Science\\
-   Wake Forest University School of Medicine\\
-   Winston-Salem, NC 27157, USA \\
-   \texttt{swelden@wakehealth.edu}
-   \And
-   Kristin Lenoir \\
-   Department of Biostatistics and Data Science\\
-   Wake Forest University School of Medicine\\
-   Winston-Salem, NC 27157, USA \\
-   \texttt{klenoir@wakehealth.edu}
-	 \And
-	 Jaime L.~Speiser \\
-	 Department of Biostatistics and Data Science\\
-	 Wake Forest University School of Medicine\\
-	 Winston-Salem, NC 27157, USA \\
-	 \texttt{jspeiser@wakehealth.edu}
-	 \And
-	 Matthew W. Segar \\
-   Department of Cardiology \\
-   Texas Heart Institute \\
-   Houston, TX 77030, USA \\
-	 \texttt{Matthew.Segar@BCM.edu}
-   \And
-	 Ambarish Pandey \\
-   Division of Cardiology, Department of Internal Medicine \\
-   University of Texas Southwestern Medical Center \\
-   Dallas, TX 75235, USA \\
-	 \texttt{Ambarish.Pandey@UTSouthwestern.edu}
-	 \And
-	 Nicholas M.~Pajewski \\
-	 Department of Biostatistics and Data Science\\
-	 Wake Forest University School of Medicine\\
-	 Winston-Salem, NC 27157, USA \\
-	 \texttt{npajewsk@wakehealth.edu}
-	%% \AND
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-	%% \And
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-	%% \And
-	%% Coauthor \\
-	%% Affiliation \\
-	%% Address \\
-	%% \texttt{email} \\
-}
-
-% Uncomment to remove the date
-%\date{}
-
-% Uncomment to override  the `A preprint' in the header
-%\renewcommand{\headeright}{Technical Report}
-%\renewcommand{\undertitle}{Technical Report}
-\renewcommand{\shorttitle}{\textit{arXiv} Accelerated \& interpretable oblique RSFs}
-
-%%% Add PDF metadata to help others organize their library
-%%% Once the PDF is generated, you can check the metadata with
-%%% $ pdfinfo template.pdf
-\hypersetup{
-pdftitle={Accelerated and interpretable oblique random survival forests},
-pdfsubject={q-bio.NC, q-bio.QM},
-pdfauthor={Byron C.~Jaeger},
-pdfkeywords={Random Forest, Survival, Efficiency, Variable Importance},
-}
+%\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{0}
+
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
+
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
@@
 
+%\bibliographystyle{natbib}
+
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\if0\blind
+{
+  \title{\bf Accelerated and interpretable oblique random survival forests}
+  \author{Byron C.~Jaeger\thanks{
+    The authors gratefully acknowledge \textit{the Center for Biomedical Informatics, Wake Forest University School of Medicine for supporting this research.
+The project was also supported by the National Center for Advancing Translational Sciences (NCATS), National Institutes of Health through Grant Award Number UL1TR001420.
+The content is solely the responsibility of the authors and does not necessarily represent the official views of the NIH.
+Dr.
+Pajewski was supported by grant number P30AG021332 from the National Institutes of Health, while Dr.
+Speiser was supported by K25AG068253.}}\hspace{.2cm}\\
+   Dept. of Biostatistics and Data Science,
+	 Wake Forest Univ. School of Medicine\\
+  and \\
+   Sawyer Welden \\
+   Dept. of Biostatistics and Data Science,
+   Wake Forest Univ. School of Medicine \\
+  and \\
+   Kristin Lenoir \\
+   Dept. of Biostatistics and Data Science,
+   Wake Forest Univ. School of Medicine\\
+  and \\
+   Jaime L.~Speiser \\
+	 Dept. of Biostatistics and Data Science,
+	 Wake Forest Univ. School of Medicine\\
+	and \\
+	 Matthew W. Segar \\
+   Dept. of Cardiology,
+   Texas Heart Institute \\
+  and \\
+   Ambarish Pandey \\
+   Division of Cardiology, Dept. of Internal Medicine, \\
+   University of Texas Southwestern Medical Center \\
+  and \\
+   Nicholas M.~Pajewski \\
+	 Dept. of Biostatistics and Data Science,
+	 Wake Forest Univ. School of Medicine
+  }
   \maketitle
-
+} \fi
+
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf Title}
+\end{center}
+  \medskip
+} \fi
+
+\newpage
 \begin{abstract}
-
 	The oblique random survival forest (RSF) is an ensemble supervised learning method for right-censored outcomes.
@@
 
-A motivating problem for negation VI is that of correlated, numeric predictors.
+% A motivating problem for negation VI is that of correlated, numeric predictors.
 When two predictors are correlated and only one of them is relevant for prediction of an outcome, VI methods based on permutation are known to have upward bias in estimating the importance of the irrelevant predictor \citep{hooker2021unrestricted}.
@@
 
-Negation VI has several helpful characteristics.
-First, negation VI generalizes to any oblique RF (\ie, not just RSFs) using any valid error function, making it both general and flexible.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic.} Second, negation is non-random and hence reproducible without setting a random seed.
-Third, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% (a value indicative of type 2 diabetes) as a result of randomly permuting the values of Hemoglobin A1c.
+To demonstrate negation VI, consider a classification task where the goal is prediction of penguin species based on bill length and bill depth.
+Scaling these predictors to be centered at 0, we find oblique decision boundaries defined by linear combinations of bill length and bill depth correctly classify most of the data (Figure \ref{fig:negation_vs_permutation_viz}, Panel A).
+Permuting the values of bill length leads to several mis-classified observations, suggesting that bill length is an important predictor (Figure \ref{fig:negation_vs_permutation_viz}, Panel B).
+However, inspecting the permuted data shows that a number of observations moved to a region in the predictor space where there were previously no observations.
+Moving data to unobserved or perhaps unobservable regions of the predictor space may cause extrapolation error, which \citet{hooker2021unrestricted} identified as a cause of bias in permutation importance.
+Negating the coefficients for bill length in the linear combinations that define our decision boundaries causes the boundaries to flip across bill length's axis (Figure \ref{fig:negation_vs_permutation_viz}, Panel C).
+This leads to several mis-classified observations, suggesting that bill length is an important predictor without distorting the joint distribution of bill length and bill depth.
+
+Negation VI is an extension of ``anti VI", a VI technique for axis-based trees which became the default VI method for \texttt{randomForestSRC} in version 2.14.0.
+Anti VI reverses the direction of all decision nodes that use a specific variable, and then reassesses the ensemble prediction error.
+So, if an axis-based decision rule were defined as $x > 5 \Rightarrow$ send data to right node, the decision rule would become $x > 5 \Rightarrow$ send data to left node when computing the importance of a predictor $x$.
+Put in a way that makes the connection to negation VI more explicit, the `noised up' decision rule can be written as $-x > 5 \Rightarrow$ send data to right node.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/negation_vs_permutation_viz-1} \caption[Demonstration of negation and permutation importance for a single oblique tree]{Demonstration of negation and permutation importance for a single oblique tree.
+Panel A shows the original data and decision boundaries.
+Panel B shows the data with permuted bill length values.
+Panel C shows the decision boundaries after negating coefficients for bill length.
+Permutation and negation both show that bill length is an important predictor, but permuting bill length distorts its joint distribution with bill depth.}\label{fig:negation_vs_permutation_viz}
+\end{figure}
+
+\end{knitrout}
+
+Negation VI has several strengths.
+First, it generalizes to any oblique RF (\ie, not just RSFs) using any valid error function, making it both general and flexible.\footnote{The \texttt{aorsf} package enables customized functions to be applied in lieu of the default C-statistic.} Second, negation is non-random, making it reproducible without setting a random seed and making it slightly faster than permutation importance.
+Fourth, since negation VI does not permute variables, the analyst need not worry about impossible combinations of predictors that may occur when one predictor is randomly permuted, such as having a negative status for type 2 diabetes and having Hemoglobin A1c level $\geq$ 6.5\% (a value indicative of type 2 diabetes) as a result of randomly permuting the values of Hemoglobin A1c.
+However, in scenarios where decision boundaries have symmetry around the origin of the predictor space (\eg, all positive cases lie in a circle centered at the origin, with negative cases sitting outside the circle), negation importance will be less effective than permutation.
 
@@
 
-Sections \ref{sec:bm_pred} and \ref{sec:bm_vi} present numerical experiments examining the accelerated oblique RSF and negation VI, respectively.
-The code used to run these experiments is available online at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench}.
-All analyses were conducted using R version 4.1.3 with version 0.0.4 of \texttt{aorsf} \citep{jaeger2022aorsf}, and coordinated by the \texttt{targets} R package \citep{targets}.
-To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
+Sections \ref{sec:bm_pred} and \ref{sec:bm_vi} present the design of numerical experiments examining the accelerated oblique RSF and negation VI, respectively.
+\secref{sec:bm_compute} summarizes our approach to evaluating computational efficiency of learning algorithms, with a focus on the accelerated oblique RSF and other RSF implementations.
+\secref{sec:computing} provides details on computation and code.
 
@@
 
-\subsubsection{Results} \label{sec:results_pred}
-
-A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all}.
-In total, 871 out of 875 Monte-Carlo cross validation runs were completed.
-On run 13, 18, 24 and 25 for the ACTG 320 data, the \texttt{nn-cox} learner encountered an error during its fitting procedure.
-
-\paragraph{Index of prediction accuracy}
-
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 17 out of 35 risk prediction tasks, with an overall mean IPA of 12.6 (Figure \ref{fig:bm_pred_viz_ibs}).
-Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.33 points higher, a relative increase of 11.7\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.82 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/bm_pred_viz_ibs-1} \caption{Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
-Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.
-As predicted survival probabilities are not a standard output from \texttt{xgboost-aft}, it is not included in this figure.
-Also, since this figure is intended to compare \texttt{aorsf-fast} to learners that are not oblique random survival forests, \texttt{aorsf-cph}, \texttt{aorsf-net}, \texttt{aorsf-random}, and \texttt{obliqueRSF-net} are not included.}\label{fig:bm_pred_viz_ibs}
-\end{figure}
-
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/bm_pred_model_viz_ibs-1} \caption[Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms]{Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
-A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.}\label{fig:bm_pred_model_viz_ibs}
-\end{figure}
-
-\end{knitrout}
-
-\paragraph{Time-dependent concordance statistic}
-
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 9 out of 35 risk prediction tasks, with an overall mean of 77.2 (Figure \ref{fig:bm_pred_viz_cstat}).
-Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.668 points higher, a relative increase of 0.873\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was $>$ 0.999, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.14 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/bm_pred_viz_cstat-1} \caption[Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks]{Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
-Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.
-Since this figure is intended to compare \texttt{aorsf-fast} to learners that are not oblique random survival forests, \texttt{aorsf-cph}, \texttt{aorsf-net}, \texttt{aorsf-random}, and \texttt{obliqueRSF-net} are not included.}\label{fig:bm_pred_viz_cstat}
-\end{figure}
-
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/bm_pred_model_viz_cstat-1} \caption[Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms]{Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms.
-A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.}\label{fig:bm_pred_model_viz_cstat}
-\end{figure}
-
-\end{knitrout}
-
 \subsection{Benchmark of variable importance} \label{sec:bm_vi}
@@
 
-\subsubsection{Results} \label{sec:results_vi}
+\subsection{Benchmark of computational efficiency} \label{sec:bm_compute}
+
+The aim of this numeric experiment is to evaluate the computational efficiency of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
+
+\subsubsection{Evaluation of computational efficiency}
+
+For each learner discussed in \secref{sec:learners} and for each of the 35 risk prediction tasks analyzed in \secref{sec:bm_pred}, we tracked the amount of time required to fit a prediction model (including time used to tune parameters) and compute predicted risk.
+
+We performed additional benchmarks on the time required to fit 500 trees using \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger}.
+The learners that represented these R packages were \texttt{aorsf-fast}, \texttt{rsf-standard}, and \texttt{rsf-extratrees}, respectively.
+To allow for controlled comparisons of computational efficiency with varying dimensions of training data, we used the same process to simulate data as described in \secref{sec:data_sim}, varying the number of observations from 100 to 10000 and the number of predictors from 10 to 1000.
+The minimum node size of trees in this experiment was dynamically set as the nearest integer to the number of observations in the training set divided by 10.
+
+\subsection{Computational details} \label{sec:computing}
+
+All analyses were conducted using R version 4.1.3 with version 0.0.4 of the \texttt{aorsf} \citep{jaeger2022aorsf} package.
+Analyses were coordinated with assistance from the \texttt{targets} package \citep{targets}.
+To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
+All code used in the current study is available at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench},
+
+\section{Results} \label{sec:results}
+
+In \secref{sec:results_pred}, \secref{sec:results_vi}, and \secref{sec:results_computing}, we present results from the benchmark or prediction accuracy, the simulation study of VI, and the benchmark of computational efficiency, respectively.
+
+\subsection{Prediction accuracy} \label{sec:results_pred}
+
+A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all}.
+In total, 871 out of 875 Monte-Carlo cross validation runs were completed.
+On run 13, 18, 24 and 25 for the ACTG 320 data, the \texttt{nn-cox} learner encountered an error during its fitting procedure.
+
+\paragraph{Index of prediction accuracy}
+
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 17 out of 35 risk prediction tasks, with an overall mean IPA of 12.6 (Figure \ref{fig:bm_pred_viz_ibs}).
+Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.33 points higher, a relative increase of 11.7\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.80 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_viz_ibs-1} \caption{Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.
+As predicted survival probabilities are not a standard output from \texttt{xgboost-aft}, it is not included in this figure.
+Also, since this figure is intended to compare \texttt{aorsf-fast} to learners that are not oblique random survival forests, \texttt{aorsf-cph}, \texttt{aorsf-net}, \texttt{aorsf-random}, and \texttt{obliqueRSF-net} are not included.}\label{fig:bm_pred_viz_ibs}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_model_viz_ibs-1} \caption[Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms]{Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
+A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.}\label{fig:bm_pred_model_viz_ibs}
+\end{figure}
+
+\end{knitrout}
+
+\paragraph{Time-dependent concordance statistic}
+
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 9 out of 35 risk prediction tasks, with an overall mean of 77.2 (Figure \ref{fig:bm_pred_viz_cstat}).
+Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.668 points higher, a relative increase of 0.873\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was $>$ 0.999, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.15 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_viz_cstat-1} \caption[Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks]{Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.
+Since this figure is intended to compare \texttt{aorsf-fast} to learners that are not oblique random survival forests, \texttt{aorsf-cph}, \texttt{aorsf-net}, \texttt{aorsf-random}, and \texttt{obliqueRSF-net} are not included.}\label{fig:bm_pred_viz_cstat}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/bm_pred_model_viz_cstat-1} \caption[Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms]{Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms.
+A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.}\label{fig:bm_pred_model_viz_cstat}
+\end{figure}
+
+\end{knitrout}
+
+\subsection{Variable importance} \label{sec:results_vi}
 
@@
 
-\subsection{Benchmark of computational efficiency} \label{sec:bm_compute}
-
-The aim of this numeric experiment is to evaluate the computational efficiency of the accelerated oblique RSF compared to its predecessor (the oblique RSF from the \texttt{obliqueRSF} R package) and to several other machine learning algorithms.
-
-\subsubsection{Evaluation of computational efficiency}
-
-For each learner discussed in \secref{sec:learners} and for each of the 35 risk prediction tasks analyzed in \secref{sec:bm_pred}, we tracked the amount of time required to fit a prediction model (including time used to tune parameters) and compute predicted risk.
-
-We performed additional benchmarks on the time required to fit 500 trees using \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger}.
-The learners that represented these R packages were \texttt{aorsf-fast}, \texttt{rsf-standard}, and \texttt{rsf-extratrees}, respectively.
-To allow for controlled comparisons of computational efficiency with varying dimensions of training data, we used the same process to simulate data as described in \secref{sec:data_sim}, varying the number of observations from 100 to 10000 and the number of predictors from 10 to 1000.
-The minimum node size of trees in this experiment was dynamically set as the nearest integer to the number of observations in the training set divided by 10.
-
-\subsubsection{Results}
+\subsection{Computational efficiency} \label{sec:results_computing}
 

### 2022-11-23 paper/jmlr/cover-letter/jmlr_coverletter.tex
working on jcgs submission

--- 2022-11-23 paper/jbi/cover-letter/coverletter_main.tex
@@
 % !TEX program = pdflatex
-\input{coverletter_preamble.tex}
+\input{jmlr_coverletter_preamble.tex}
 
@@
 
-Journal of Biomedical Informatics
+Journal of Machine Learning Research
 
@@
 
-We are writing to submit our manuscript ``\red{Accelerated and interpretable oblique random survival forests}'' to the \emph{Journal of Biomedical Informatics}.
+We are writing to submit our manuscript ``\red{Accelerated and interpretable oblique random survival forests}'' to the \emph{Journal of Machine Learning Research}.
 
@@
 This paper extends our previous work in \emph{Annals of Applied Statistics}, \red{Oblique Random Survival Forests} (DOI: 10.1214/19-AOAS1261), by addressing \red{the computational inefficiency and difficulty of interpreting oblique random survival forests}.
+We understand the number of pages in our submission is high.
+This is due to a large table included in our appendix that summarizes results from a general benchmark that includes 35 prediction tasks.
+We have included this table and other specific details in the appendix for completeness, but we acknowledge they are not critical to the paper and would be happy to reduce the total page count by removing select content in our appendices.
 
-We suggest the following reviewers:
+We suggest the following action editors and referees for our submission.
+
+Action Editors:
+\begin{itemize}
+    \item \red{Miguel Carreira-Perpinan, University of California (mcarreira-perpinan@ucmerced.edu)}
+    \item \red{Jason Klusowski, Princeton University (jason.klusowski@princeton.edu)}
+    \item \red{Amichai Painsky, Tel Aviv University (amichaip@tauex.tau.ac.il)}
+\end{itemize}
+
+Reviewers:
 \begin{itemize}
@@
 As the corresponding author, I confirm that none of the co-authors listed below have a conflict of interest with the action editors and referees I suggest above.
-Further, I confirm that all co-authors below consent to my submission of this manuscript to the \emph{Journal of Biomedical Informatics}.
+Further, I confirm that all co-authors below consent to my submission of this manuscript to the \emph{Journal of Machine Learning Research}.
 

### 2022-11-23 paper/jmlr/main.Rnw
working on jcgs submission

@@
        \AND
-       \name Jaime L Speiser \email jspeiser@wakehealth.edu \\
+       \name Jaime L. Speiser \email jspeiser@wakehealth.edu \\
        \addr Department of Biostatistics and Data Science\\
@@
        \AND
-       \name Matthew Segar \email Matthew.Segar@BCM.edu \\
+       \name Matthew W. Segar \email Matthew.Segar@BCM.edu \\
        \addr Department of Cardiology \\
@@
 
-\subsection{Benchmark of computational efficiency}
+\subsection{Benchmark of computational efficiency} \label{sec:bm_compute}
 
@@
 
-We also performed more specific benchmarks on the time required to fit 50 trees\footnote{We decided to use 50 trees for this benchmark rather than 500, as using 500 trees caused excessive memory usage and job failure with larger datasets.} using the three fastest random forest R packages, \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger}.
-The learners that represented these R packages, respectively, are \texttt{aorsf-fast}, \texttt{rsf-standard}, and \texttt{rsf-extratrees}.
-We used the simulated data described in \secref{sec:data_sim} with number of observations in the training data ranging from 100 to 21544 and number of predictors ranging from 10 to 1000.
+We performed additional benchmarks on the time required to fit 500 trees using \texttt{aorsf}, \texttt{randomForestSRC}, and \texttt{ranger}.
+The learners that represented these R packages were \texttt{aorsf-fast}, \texttt{rsf-standard}, and \texttt{rsf-extratrees}, respectively.
+To allow for controlled comparisons of computational efficiency with varying dimensions of training data, we used the same process to simulate data as described in \secref{sec:data_sim}, varying the number of observations from 100 to 10000 and the number of predictors from 10 to 1000.
+The minimum node size of trees in this experiment was dynamically set as the nearest integer to the number of observations in the training set divided by 10.
 
@@
 
-In the analysis of \Sexpr{n_risk_tasks} risk prediction tasks, \texttt{aorsf-fast} was the second fastest learner overall, with an expected model development and risk prediction time about \Sexpr{ms_diff} milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+In the analysis of \Sexpr{n_risk_tasks} risk prediction tasks, \texttt{aorsf-fast} was the second fastest learner overall, with a median time to develop a risk prediction model and compute predictions about \Sexpr{ms_diff} milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
 Comparing median computing times, \texttt{aorsf-fast} was \Sexpr{times$obliqueRSF_net$ratio} times faster than its predecessor, \texttt{obliqueRSF-net}.
@@
 
-In the analysis of time to fit 50 trees using simulated data, the \texttt{ranger} package exhibited the fastest computation times for samples with 1000 or fewer observations while \texttt{aorsf} and \texttt{randomForestSRC} were more efficient in larger samples.
-In particular, \texttt{aorsf} was substantially faster than both \texttt{ranger} and \texttt{randomForestSRC} with 10 or 100 features and over 1000 observations in the training data (see Figure \ref{fig:bm_time_viz}).
-
-<<bm_time_viz, fig.height=4, fig.width=10, fig.cap="Time, in seconds, to fit an ensemble of 50 survival trees.
-The aorsf package appears to be more efficient in larger samples, particularly when 10 or 100 predictors are present in the training data.
+In the analysis of time to fit 500 trees using simulated data, the \texttt{ranger} package exhibited the fastest computation times overall (Figure \ref{fig:bm_time_viz}).
+\texttt{aorsf} was the second fastest when the number of predictors was 10 or 100,  and \texttt{randomForestSRC} had similar computation time versus \texttt{aorsf} when 1000 predictors were present.
+
+<<bm_time_viz, fig.height=4, fig.width=10, fig.cap="The expected time, in seconds, to fit an ensemble of 500 axis-based survival trees using the ranger or randomForestSRC package versus 500 oblique survival trees using the aorsf package.
+The ranger package is the most efficient overall, and aorsf appears to be relatively efficient in larger samples, particularly when 10 or 100 predictors are present in the training data.
 All three packages appear to scale linearly in computation time with the number of observations in the training data.">>=

### 2022-11-23 paper/jmlr/main.tex
working on jcgs submission

@@
 
-In the analysis of 35 risk prediction tasks, \texttt{aorsf-fast} was the second fastest learner overall, with an expected model development and risk prediction time about 385 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+In the analysis of 35 risk prediction tasks, \texttt{aorsf-fast} was the second fastest learner overall, with a median time to develop a risk prediction model and compute predictions about 385 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
 Comparing median computing times, \texttt{aorsf-fast} was 379.8 times faster than its predecessor, \texttt{obliqueRSF-net}.
@@
 
-In the analysis of time to fit 50 trees using simulated data, the \texttt{ranger} package exhibited the fastest computation times for samples with 1000 or fewer observations while \texttt{aorsf} and \texttt{randomForestSRC} were more efficient in larger samples.
-In particular, \texttt{aorsf} was substantially faster than both \texttt{ranger} and \texttt{randomForestSRC} with 10 or 100 features and over 1000 observations in the training data (see Figure \ref{fig:bm_time_viz}).
+In the analysis of time to fit 500 trees using simulated data, the \texttt{ranger} package exhibited the fastest computation times overall (Figure \ref{fig:bm_time_viz}).
+\texttt{aorsf} was the second fastest when the number of predictors was 10 or 100,  and \texttt{randomForestSRC} had similar computation time versus \texttt{aorsf} when 1000 predictors were present.
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/bm_time_viz-1} \caption[Time, in seconds, to fit an ensemble of 50 survival trees]{Time, in seconds, to fit an ensemble of 50 survival trees.
-The aorsf package appears to be more efficient in larger samples, particularly when 10 or 100 predictors are present in the training data.
+\includegraphics[width=\maxwidth]{figure/bm_time_viz-1} \caption[The expected time, in seconds, to fit an ensemble of 500 axis-based survival trees using the ranger or randomForestSRC package versus 500 oblique survival trees using the aorsf package]{The expected time, in seconds, to fit an ensemble of 500 axis-based survival trees using the ranger or randomForestSRC package versus 500 oblique survival trees using the aorsf package.
+The ranger package is the most efficient overall, and aorsf appears to be relatively efficient in larger samples, particularly when 10 or 100 predictors are present in the training data.
 All three packages appear to scale linearly in computation time with the number of observations in the training data.}\label{fig:bm_time_viz}

### 2022-11-23 poster/poster.Rnw
working on jcgs submission

%==============================================================================
%== template for LATEX poster =================================================
%==============================================================================
%
%--A0 beamer slide-------------------------------------------------------------
\documentclass[final]{beamer}
\usepackage[orientation=portrait,
            size=custom,
            width=91.44,
            height=152.4,
            scale=1.5         % font scale factor
           ]{beamerposter}

\geometry{
  hmargin=2.5cm, % little modification of margins
}

%
\usepackage[utf8]{inputenc}

\newcommand{\dataset}{{\cal D}}

\linespread{1.05}
%
%==The poster style============================================================
\usetheme{sharelatex}

%==Title, date and authors of the poster=======================================
\title
[Wake Forest Biomedical Informatics Colloquium 2022] % Conference
{ % Poster title
Accelerated and interpretable oblique random survival forests
}

\author{ % Authors
Byron C. Jaeger\inst{1}, Sawyer Welden\inst{1}, Kristin Lenoir\inst{1}, Jaime L. Speiser\inst{1}, Matthew W. Segar\inst{2}, Ambarish Pandey\inst{3}, and Nicholas M. Pajewski\inst{1}
}
\institute
[Wake Forest University School of Medicine] % General University
{
\inst{1} Wake Forest University School of Medicine, Winston-Salem NC\\[0.3ex]
\inst{2} Texas Heart Institute, Houston TX\\[0.3ex]
\inst{3} University of Texas Southwestern Medical Center, Dallas TX
}
\date{September 23, 2022}

\begin{document}
\begin{frame}[t]
%==============================================================================
\begin{multicols}{3}
%==============================================================================
%==The poster content==========================================================
%==============================================================================

\section{Introduction}

\begin{itemize}

\item Risk prediction may reduce disease burden by guiding strategies for prevention and treatment.

\item Oblique random survival forests (RSFs) have high prediction accuracy, but also have high computational overhead and few methods for interpretation.\cite{ref1}

\item We developed methods to make oblique RSFs faster and more interpretable.

\end{itemize}

% In Ref.~\cite{ref1}...
% In Refs.~\cite{ref1,ref2}...
% On webpage~\cite{web}...

\section{Background}

\subsection{Axis-based and oblique trees}

Decision trees grow by splitting a set of training data into two subsets with maximally different expected outcomes. When the new subsets are formed based on \emph{a single predictor}, the tree is \textbf{axis-based} because the splits of the data are perpendicular to the axis of the predictor. When subsets are formed based on \textbf{a linear combination of predictors}, the tree is \textbf{oblique} because the splits are neither parallel nor perpendicular to the axis.

\vskip1ex
\begin{figure}
\centering
\includegraphics[width=0.99\columnwidth]{tree_axis_v_oblique.png}
\caption{Decision trees with axis-based splitting (left) and oblique splitting (right). The oblique trees do a better job of separating the two classes.}
\end{figure}
\vskip2ex

\textbf{Problems}: \begin{itemize}

\item Oblique RSFs have high computational overhead due to the large number of possible oblique splits to search through.

\item Oblique RSFs are difficult to interpret as there are few methods to estimate predictor importance using an oblique RSF.

\end{itemize}

\subsection{Standard technique for predictor importance: permutation}

\textbf{Definition}: For predictor $X$, the increase in prediction error after $X$ is randomly permuted.

\textbf{Problem}: Permuting a predictor does not account for the size of coefficients attached to it in linear combinations. In oblique random forests, important predictors are likely to have larger coefficients, and ignoring this leads to unreliable importance estimates.

\section{Accelerating the oblique random survival forest}

\subsection{Partial Newton Raphson scoring}

% Consider the usual framework for right-censored time-to-event outcomes. Let $\dataset_{\text{train}} = \left\{ (T_i, \delta_i, x_{i}) \right\}_{i=1}^{N_{\text{train}}}.$ Here, $T_i$ is the event time if $\delta_i=1$ or the censoring time if $\delta_i=0$, and $x_i$ is a vector of predictors values.

We propose to identify linear combinations of predictors in non-leaf nodes by applying Newton Raphson scoring to the partial Cox likelihood.

% \begin{equation}\label{eqn:cox-partial-likelihood}
% L(\beta) = \prod_{i=1}^m \frac{e^{x_{j(i)}^T \beta}}{\sum_{j \in R_i} e^{x_j^T \beta}},
% \end{equation}
% where $R_i$ is the set of indices, $j$, with $T_j \geq t_i$ (those still at risk at time $t_i$), and $j(i)$ is the index of the observation for which an event occurred at time $t_i$.

\textbf{Hypothesis}: Using one Newton Raphson iteration to identify linear combinations of predictors will yield an efficient oblique RSF with no loss of prediction accuracy compared to other learners: \begin{itemize}

\item \texttt{aorsf-fast}: One Newton Raphson iteration

\item \texttt{aorsf-cph}: Newton Raphson until convergence (\emph{i.e.}, fits a Cox proportional hazards model)

\item \texttt{obliqueRSF}: Penalized regression (\emph{i.e.}, the original method used for oblique RSFs)

\item Many other learners (see ArXiv paper for full description - QR code is in the references)

\end{itemize}

\vskip3ex

\section{Introducing negation importance}

\textbf{Definition}: For predictor $X$, the increase in an oblique random forest's prediction error after coefficients attached to $X$ are multiplied by -1.

\textbf{Hypothesis}: negation importance will improve detection of signal versus noise predictors.

\section{Benchmarks}

\subsection{Prediction accuracy}

We evaluated \texttt{aorsf-fast}'s Discrimination (C-statistic) compared to several machine learning algorithms in 35 distinct risk prediction tasks drawn from 21 distinct datasets. Using Bayesian mixed models, inferences on equivalence and inferiority of \texttt{aorsf-fast} versus other learners were made.

\vskip1ex
\begin{figure}
\centering
\includegraphics[width=0.99\columnwidth]{bm_pred_model_viz_cstat-1.pdf}
\caption{Expected differences in C-statistic between \texttt{aorsf-fast} and other learners. A region of practical equivalence is shown by purple lines, and a boundary of non-zero difference is shown by an orange line.}
\end{figure}
\vskip2ex

\subsection{Predictor importance}

We evaluated negation importance and several other methods based on how well they discriminated between relevant and irrelevant predictors in a simulation study. In addition to negation, we considered \begin{itemize}

\item ANOVA importance: the proportion of times a given predictor's p-value is <0.001 in linear combinations

\item Permutation importance: increase in prediction error after a given predictor is randomly permuted.

\item Shapley importance: the expected absolute contribution of a predictor to a model's predictions.

\end{itemize}

\vskip1ex
\begin{figure}
\centering
\includegraphics[width=0.99\columnwidth]{fig_vi_smry.pdf}
\caption{C-statistic for variable selection using different techniques to estimate predictor importance.}
\end{figure}
\vskip2ex

\subsection{Computational efficiency}

We evaluated the computational efficiency of the \texttt{aorsf-fast} compared to other machine learning algorithms.

\vskip1ex
\begin{figure}
\centering
\includegraphics[width=0.99\columnwidth]{fig_pred_time.pdf}
\caption{Distribution of time taken to fit a prediction model and compute predicted risk. The median time, in seconds, is printed for each learner}
\end{figure}
\vskip2ex

\section{Summary and conclusions}

\begin{itemize}

\item Oblique RSFs have exceptional prediction accuracy.

\item We have developed a method to fit oblique RSFs efficiently, with no loss of prediction accuracy.

\item We have also introduced a general method to estimate predictor importance with oblique random forests (not just RSFs), and demonstrated its effectiveness specifically for the oblique RSF.

\end{itemize}

\subsection{Acknowledgments}

Research reported in this publication was supported by the Center for Biomedical Informatics, Wake Forest University School of Medicine. The project described was supported by the National Center for Advancing Translational Sciences (NCATS), National Institutes of Health, through Grant Award Number UL1TR001420. The content is solely the responsibility of the authors and does not necessarily represent the official views of the NIH.

%==============================================================================
%==End of content==============================================================
%==============================================================================

%--References------------------------------------------------------------------

\subsection{References}

\vskip1ex
\begin{center}
\includegraphics[width=0.4\columnwidth]{aorsf-package.png}
\hspace{1cm}
\includegraphics[width=0.4\columnwidth]{aorsf-arxiv.png}
\end{center}

\begin{thebibliography}{99}

\bibitem{ref1} Jaeger, Byron C., et al. ``Oblique random survival forests." \emph{The Annals of Applied Statistics} 13.3 (2019): 1847-1883.

\end{thebibliography}
%--End of references-----------------------------------------------------------

\end{multicols}

%==============================================================================
\end{frame}
\end{document}

### 2022-11-23 R/bench_pred_real.R

@@ -117,13 +117,17 @@ bench_pred_real <- function(data_source,
 
   if( !inherits(model, 'try-error') ) {
     out$time_fit <- model$time_fit
+  } else {
+    print(model)
   }
 
   if( !inherits(predictions, 'try-error') ) {
     out$time_pred <- predictions$time
+  } else {
+    print(predictions)
   }
 
-  print(out)
+  # print(out)
 
   out
 

### 2022-11-23 R/bench_time.R

@@ -4,14 +4,28 @@
 #'
 #' @title
 
-bench_time <- function(data, n_obs=100, n_ftr=10, n_tree = 50) {
+bench_time <- function(n_obs = 100,
+                       n_ftr = 10,
+                       n_tree = 500,
+                       n_times = NULL) {
 
-  train <- data[seq(n_obs), seq(n_ftr)]
+  data <- read_rds("data/bench_time.rds")[seq(n_obs), ]
 
-  pred_horizon <- median(train$time)
+  if(n_ftr == 10000){
+    for(i in seq(9000)){
+      data[[paste("junk", i, sep="_")]] <- rnorm(n = nrow(data))
+    }
+  }
 
-  node_size <- 10
+  train <- data[, seq(n_ftr + 2)]
+
+  node_size <- round(n_obs / 10)
+
   mtry <- ceiling(sqrt(n_ftr))
+
+  if(!is.null(n_times) && length(unique(train$time)) > n_times){
+    train$time <- 5 * as.numeric(cut(train$time, breaks = n_times)) / n_times
+  }
 
   start_time <- Sys.time()
 
@@ -20,7 +34,8 @@ bench_time <- function(data, n_obs=100, n_ftr=10, n_tree = 50) {
     n_tree = n_tree,
     formula = Surv(time, status) ~ .,
     mtry = mtry,
-    n_retry = 3,
+    n_retry = 1,
+    n_split = 5,
     split_min_obs = node_size,
     control = orsf_control_fast(),
     importance = 'none',
@@ -34,12 +49,14 @@ bench_time <- function(data, n_obs=100, n_ftr=10, n_tree = 50) {
   start_time <- Sys.time()
 
   rsf_rfsrc <- rfsrc(Surv(time, status) ~ .,
-                        ntree = n_tree,
-                        samptype = 'swr',
-                        perf.type = 'none',
-                        data = train,
-                        mtry = mtry,
-                        nodesize = node_size)
+                     ntree = n_tree,
+                     samptype = 'swr',
+                     perf.type = 'none',
+                     data = train,
+                     mtry = mtry,
+                     nsplit = 5,
+                     ntime = 0,
+                     nodesize = node_size)
 
   end_time <- Sys.time()
 
@@ -53,6 +70,7 @@ bench_time <- function(data, n_obs=100, n_ftr=10, n_tree = 50) {
[…]

### 2022-11-23 R/bench_vi_real.R

@@ -1,0 +1,202 @@
+
+
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param data_source
+#' @param run_seed
+bench_vi_real <- function(data_source,
+                          data_load_fun,
+                          run_seed,
+                          test_prop = 1/2) {
+
+  set.seed(run_seed)
+
+  data_all <- data_load_fun()
+
+  # Some R packages (not aorsf) have trouble
+  # with factors that have special characters
+  data_all <-  data_all |>
+    mutate(across(where(is.character), as.factor),
+           across(where(is.factor), simplify_levels))
+
+  test_index <- sample(x = seq(nrow(data_all)),
+                       size = round(nrow(data_all) * test_prop),
+                       replace = FALSE)
+
+  train <- data_all[-test_index, ]
+  test <- data_all[test_index, ]
+
+  imputer <- recipe(x = train, time + status ~ .) %>%
+    step_nzv(all_predictors()) %>%
+    step_impute_mean(all_numeric_predictors()) %>%
+    step_normalize(all_numeric_predictors()) %>%
+    step_impute_mode(all_nominal_predictors()) %>%
+    step_dummy(all_nominal_predictors()) %>%
+    prep()
+
+  .train <- as.data.frame(juice(imputer))
+  .test <- as.data.frame(bake(imputer, new_data = test))
+
+  event_time_bounds <- quantile(
+    x = data_all$time[data_all$status==1],
+    probs = c(.25, .75)
+  )
+
+  pred_horizon <- sort(unique(.test$time[.test$status == 1]))
+  pred_horizon <- pred_horizon[pred_horizon <= event_time_bounds['75%']]
+  pred_horizon <- pred_horizon[pred_horizon >= event_time_bounds['25%']]
+
+  if(is_empty(pred_horizon)) return(NULL)
+
+  if(length(pred_horizon) > 30){
+    pred_horizon <-
+      pred_horizon[floor(seq(1, length(pred_horizon), length.out=30))]
+  }
+
+  fit_orsf <- orsf(.train, time + status ~ ., control = orsf_control_cph())
+  fit_xgb <- xgb_cox_fit(.train, pred_horizon = pred_horizon)
[…]

### 2022-11-23 R/bm_time_visualize.R

@@ -15,14 +15,15 @@ bm_time_visualize <- function(bm_time) {
     mutate(
       name = factor(
         name,
-        levels = c('rsf_ranger',
-                   'rsf_rfsrc',
-                   'aorsf_fast'),
-        labels = c('ranger',
-                   'randomForestSRC',
-                   'aorsf')
+        levels = c('rsf_rfsrc',
+                   'aorsf_fast',
+                   'rsf_ranger'),
+        labels = c('randomForestSRC',
+                   'aorsf',
+                   'ranger')
       ),
-      n_ftr = paste(n_ftr, "predictors in training data")
+      n_ftr = paste(n_ftr, "predictors")
+      # n_times = paste(n_times, "unique event times")
     )
 
   fig <- ggplot(bm_time_smry, aes(x = n_obs,
@@ -33,22 +34,22 @@ bm_time_visualize <- function(bm_time) {
     # geom_point() +
     # geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.25) +
     geom_smooth(method = 'lm', formula = y~poly(x, 3)) +
-    facet_wrap(~n_ftr) +
+    facet_grid(~n_ftr) +
     scale_y_log10() +
     scale_x_log10() +
-    labs(y = 'Time to fit 50 trees, seconds',
+    labs(y = 'Time to fit 500 trees, seconds',
          x = 'Number of observations in training data',
          color = 'R package',
          fill = 'R package') +
     theme_bw() +
-    scale_color_manual(values = c('cyan4', 'orange', 'purple')) +
-    scale_fill_manual(values = c('cyan4', 'orange', 'purple')) +
+    scale_color_manual(values = c('cyan4', 'purple', 'orange')) +
+    scale_fill_manual(values = c('cyan4', 'purple', 'orange')) +
     theme(panel.grid.major.x = element_blank(),
           panel.grid.minor.x = element_blank(),
           panel.grid.minor.y = element_blank())
 
   ggsave(plot = fig,
-         filename = 'temp.png', width = 10, height = 5, dpi = 300)
+         filename = 'temp2.png', width = 10, height = 6, dpi = 300)
 
   fig
 

### 2022-11-23 R/model_fit.R

@@ -207,7 +207,7 @@ aorsf_net_fit <- function(train, node_size = 10, ...){
 
   mtry <- round(sqrt(ncol(train)-2))
 
-  df_target <- max(mtry - 2, round(mtry/2), 2)
+  df_target <- max(mtry - 2, round(mtry/2), 1+1)
 
   split_min_events <- min( round(sum(train$status) / 5), 5)
 
@@ -356,11 +356,16 @@ obliqueRSF_fit <- function(train, node_size = 10, ...){
 
   start_time <- Sys.time()
 
+
   fit <- ORSF(train,
               ntree = 500,
               mtry = mtry,
               verbose = FALSE,
-              use.cv = nrow(train) < 500,
+              use.cv = TRUE,
+              min_events_in_leaf_node = 1,
+              min_obs_in_leaf_node = 5,
+              min_events_to_split_node = 5,
+              nsplit = 5,
               min_obs_to_split_node = node_size)
 
   end_time <- Sys.time()

### 2022-11-23 conflicts.R

@@ -4,3 +4,4 @@ conflict_prefer("filter", "dplyr", quiet = TRUE)
 conflict_prefer("slice", "dplyr", quiet = TRUE)
 conflict_prefer("summarize", "dplyr", quiet = TRUE)
 conflict_prefer("Predict", "modeltools", quiet = TRUE)
+conflict_prefer("ggarrange", "egg", quiet = TRUE)

### 2022-11-23 paper/plotly_demo_negate.R

@@ -1,0 +1,242 @@
+set.seed(329)
+
+poly_1 <- tibble(
+  x = c(0, 0, 1, 0, 0, 0, 1, 0, 0, 1, 1, 0),
+  y = c(0, 1, 1, 0, 0, 1, 0, 0, 1, 0, 1, 1),
+  f = c(1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3),
+  ff = factor(f, labels = c(': Original',
+                            ': Negate y coefficient',
+                            ': Negate x coefficient'))
+)
+
+poly_2 = poly_1 %>%
+  mutate(x = -(x-1), y = -(y-1))
+
+points <- tibble(
+  x = runif(100),
+  y = runif(100)
+)
+
+points_1 <- points %>%
+  filter(x < y)
+
+points_2 <- points %>%
+  filter(x > y)
+
+plot_ly(x = ~x, y = ~y) %>%
+  add_polygons(data = poly_1,
+               frame = ~paste0(f, ff),
+               color = I('purple'),
+               alpha = I(1/5)) %>%
+  add_polygons(data = poly_2,
+               frame = ~paste0(f, ff),
+               color = I('orange'),
+               alpha = I(1/5)) %>%
+  add_markers(data = points_1,
+              color = I("purple")) %>%
+  add_markers(data = points_2,
+              color = I("orange")) %>%
+  animation_opts(frame = 1000,
+                 transition = 1000,
+                 easing = 'elastic',
+                 redraw = FALSE) %>%
+  animation_slider(currentvalue = list(prefix = "")) %>%
+  hide_legend()
+
+
+
+
+poly_2 <- tibble(
+  x = c(-2, -2, 2, -2, -2, -2, 2, -2, -2, 2, 2, -2),
+  y = c(-2, 2, 2, -2, -2, 2, -2, -2, 2, -2, 2, 2),
+  f = c(1, 1, 1, 1, 2, 2, 2, 2, 3, 3, 3, 3),
+  ff = factor(f, labels = c(': Original',
+                            ': Negate y coefficient',
+                            ': Negate x coefficient'))
+)
+
+poly_2 = poly_1 %>%
+  mutate(x = -x, y = -y)
+
+points <- tibble(
+  x = rnorm(100),
+  y = x + rnorm(100, sd=1/2)
+) %>%
+  filter(x > -2, x < 2,
+         y > -2, y < 2)
+
[…]

### 2023-04-28 paper/jcgs/cover-letter/coverletter_main.tex
paper can be made using only public data

--- 2022-11-23 paper/jbi/cover-letter/coverletter_main.tex
@@
 
-Journal of Biomedical Informatics
+Journal of Computational and Graphical Statistics
 
@@
 
-We are writing to submit our manuscript ``\red{Accelerated and interpretable oblique random survival forests}'' to the \emph{Journal of Biomedical Informatics}.
+We are writing to submit our manuscript ``\red{Accelerated and interpretable oblique random survival forests}'' to the \emph{Journal of Computational and Graphical Statistics}.
 
@@
     \item \red{Terry M. Therneau, Mayo Clinic (therneau@mayo.edu)}
-    \item \red{Jack Dunn, Massachusetts Institute of Technology (jack.dunn.nz@gmail.com)}
     \item \red{Marvin N. Wright, University of Bremen (wright@leibniz-bips.de)}
@@
 As the corresponding author, I confirm that none of the co-authors listed below have a conflict of interest with the action editors and referees I suggest above.
-Further, I confirm that all co-authors below consent to my submission of this manuscript to the \emph{Journal of Biomedical Informatics}.
 

### 2023-04-28 paper/jcgs/main.Rnw
paper can be made using only public data

@@
 % NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{0}
+\newcommand{\blind}{1}
 
@@
   \begin{center}
-    {\LARGE\bf Title}
+    {\LARGE\bf Accelerated and interpretable oblique random survival forests}
 \end{center}
@@
 Oblique trees split data using a linear combination of predictors, creating decision boundaries that are neither parallel nor perpendicular to axes of their contributing predictors \citep[see][Chapter~5]{breiman2017classification}.
+Oblique trees may create more adequate partitions of a predictor space compared to axis-based trees, as demonstrated in Figure \ref{fig:axis_v_oblique}.
 \citet{menze2011oblique} examined prediction accuracy of RFs in the presence of correlated predictors and found that oblique RFs had substantially higher prediction accuracy compared to axis-based RFs.
 Similarly, \citet{jaeger2019oblique} found that growing RSFs with oblique rather than axis-based trees reduced the RSF's concordance error, with improvements ranging from 2.5\% to 24.9\% depending on the data analyzed.
+
+<<axis_v_oblique, fig.height=5, fig.width=12, fig.cap="Decision boundaries from an axis based (panel A) and oblique (panel B) decision tree used to classify penguin species based on bill depth and bill length.
+The decision boundary from the oblique tree is better able to capture the geometry of this data, leading to fewer mis-classified penguins.">>=
+
+cols <- c("darkorange", "purple", "cyan4")
+
+penguins <- drop_na(palmerpenguins::penguins)
+
+simple_scale <- function(x) (x - mean(x))/sd(x)
+
+penguins_scaled <- penguins %>%
+  mutate(x = simple_scale(bill_length_mm),
+         y = simple_scale(bill_depth_mm)) %>%
+  filter(x > -3, x < 3, y > -2, y < 2)
+
+poly1_axis <- data.frame(
+ x = c(-3, 0.2116068, 0.2116068, -3, -3),
+ y = c(-2, -2,   2, 2, -2)
+)
+
+poly2_axis <- data.frame(
+ x = c(0.2116068, 3, 3, 0.2116068, 0.2116068),
+ y = c(-0.4137976, -0.4137976, -2, -2, -0.4137976)
+)
+
+poly3_axis <- data.frame(
+ x = c(0.2116068, 3, 3, 0.2116068, 0.2116068),
+ y = c(2, 2, -0.4137976, -0.4137976, 2)
+)
+
+poly1 <- data.frame(
+  x = c(-3, -1.8, .8, -3, -3),
+  y = c(-2, -2,   2, 2, -2)
+)
+
+poly2 <- data.frame(
+  x = c(-1.35, .8,  3,  3, -1.35),
+  y = c(-1.3,   2,  2, .9, -1.3)
+)
+
+poly3 <- data.frame(
+  x = c(-1.8, -1.35, 3, 3, -1.8),
+  y = c(-2,    -1.3, .9, -2, -2)
+)
+
+p1 <- ggplot(data = penguins_scaled) +
+  aes(x = x, y = y) +
+  geom_point(aes(color = species, shape = species),
+             size = 3,
+             alpha = 0.8) +
+  geom_polygon(data=poly1_axis, fill=cols[1], color='black', alpha=0.2) +
+  geom_polygon(data=poly2_axis, fill=cols[2], color='black', alpha=0.2) +
+  geom_polygon(data=poly3_axis, fill=cols[3], color='black', alpha=0.2) +
+  theme_minimal() +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(expand = c(0,0)) +
+  scale_color_manual(values = cols) +
+  scale_fill_manual(values = cols) +
+  labs(y = "Bill depth, scaled",
+       x = "Bill length, scaled") +
+  coord_cartesian(ylim = c(-2.1, 2.1),
+                  xlim = c(-3.1, 3.1)) +
+  theme(panel.grid = element_blank(),
+        legend.position = '',
+        text = element_text(size = 12))
+
+p2 <- ggplot(data = penguins_scaled) +
+  aes(x = x, y = y) +
+  geom_point(aes(color = species, shape = species),
+             size = 3,
+             alpha = 0.8) +
+  geom_polygon(data=poly1, fill=cols[1], color='black', alpha=0.2) +
+  geom_polygon(data=poly2, fill=cols[2], color='black', alpha=0.2) +
+  geom_polygon(data=poly3, fill=cols[3], color='black', alpha=0.2) +
+  theme_minimal() +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(expand = c(0,0)) +
+  scale_color_manual(values = cols) +
+  scale_fill_manual(values = cols) +
+  labs(y = "",
+       x = "Bill length, scaled") +
+  coord_cartesian(ylim = c(-2.1, 2.1),
+                  xlim = c(-3.1, 3.1)) +
+  theme(panel.grid = element_blank(),
+        legend.position = '',
+        text = element_text(size = 12))
+
+p3 <- ggarrange(tag_facet(p1, tag_pool = "A", vjust = 2.5),
+                tag_facet(p2, tag_pool = "B", vjust = 2.5),
+                nrow = 1)
+
+p3
+
+@
 
@@
 
-Building on prior research for bagging survival trees \citep{hothorn2004bagging}, \citet{hothorn2006unbiased} developed an axis-based RSF in their framework for unbiased recursive partitioning, more commonly referred to as the conditional inference forest (CIF).
+\citet{hothorn2006unbiased} developed an axis-based RSF in their framework for unbiased recursive partitioning, more commonly referred to as the conditional inference forest (CIF).
 \citet{zhou2016random} developed a rotation forest based on the CIF and \citet{wang2017random} developed a method for extending the predictor space of the CIF.
@@
 Several techniques to estimate VI have been developed since \citet{breiman2001random} introduced permutation VI, which is defined for each predictor as the difference in a RF's estimated prediction error before versus after the predictor's values are randomly permuted.
-\citet{strobl2007bias} identified bias in permutation VI driven by variable selection bias and effects induced by bootstrap sampling, and proposed an unbiased permutation VI measure based on unbiased recursive partitioning \citep{hothorn2006unbiased}.
+\citet{strobl2007bias} identified bias in permutation VI driven by categorical predictors and bootstrap sampling, and proposed a permutation VI measure based on unbiased recursive partitioning \citep{hothorn2006unbiased}.
 \citet{menze2011oblique} introduced an approach to estimate VI for oblique RFs that computes an analysis of variance (ANOVA) table in non-leaf nodes to obtain p-values for each predictor contributing to the node.
 The ANOVA VI\footnote{\citet{menze2011oblique} name their method `oblique RF VI', but we use the name `ANOVA VI' in this article to avoid confusing Menze's approach with other approaches to estimate VI for oblique RFs.} is then defined for each predictor as the number of times a p-value associated with the predictor is $\leq 0.01$ while growing a forest.
-\citet{lundberg2017unified} introduced a method to estimate VI using SHapley Additive exPlanation (SHAP) values, which estimate the contribution of a predictor to a model's prediction for a given observation.
+\citet{lundberg2017unified} introduced a method to estimate VI using SHapley Additive exPlanation (SHAP) values, which estimates the contribution of a predictor to a model's prediction for a given observation.
 SHAP VI is computed for each predictor by taking the mean absolute value of SHAP values for that predictor across all observations in a given set.
@@
 
-To demonstrate negation VI, consider a classification task where the goal is prediction of penguin species based on bill length and bill depth.
-Scaling these predictors to be centered at 0, we find oblique decision boundaries defined by linear combinations of bill length and bill depth correctly classify most of the data (Figure \ref{fig:negation_vs_permutation_viz}, Panel A).
-Permuting the values of bill length leads to several mis-classified observations, suggesting that bill length is an important predictor (Figure \ref{fig:negation_vs_permutation_viz}, Panel B).
+To demonstrate negation VI, consider a classification task where the goal is prediction of penguin species (chinstrap, gentoo, or adelie) based on bill length and bill depth \citep{palmerpenguins_rpack}.
+Scaling these predictors to be centered at 0, we find oblique decision boundaries defined by linear combinations of bill length and bill depth correctly classify most of the data (Figure \ref{fig:negation}, Panel A).
+Permuting the values of bill length leads to several mis-classified observations, suggesting that bill length is an important predictor (Figure \ref{fig:negation}, Panel B).
 However, inspecting the permuted data shows that a number of observations moved to a region in the predictor space where there were previously no observations.
 Moving data to unobserved or perhaps unobservable regions of the predictor space may cause extrapolation error, which \citet{hooker2021unrestricted} identified as a cause of bias in permutation importance.
-Negating the coefficients for bill length in the linear combinations that define our decision boundaries causes the boundaries to flip across bill length's axis (Figure \ref{fig:negation_vs_permutation_viz}, Panel C).
+Negating the coefficients for bill length in the linear combinations that define our decision boundaries causes the boundaries to flip across bill length's axis (Figure \ref{fig:negation}, Panel C).
 This leads to several mis-classified observations, suggesting that bill length is an important predictor without distorting the joint distribution of bill length and bill depth.
@@
 
-<<negation_vs_permutation_viz, fig.height=4, fig.width=12, fig.cap="Demonstration of negation and permutation importance for a single oblique tree.
+<<negation, fig.height=4, fig.width=12, fig.cap="Demonstration of negation and permutation importance for a single oblique tree.
 Panel A shows the original data and decision boundaries.
@@
 Permutation and negation both show that bill length is an important predictor, but permuting bill length distorts its joint distribution with bill depth.">>=
-
-cols <- c("darkorange", "purple", "cyan4")
-
-penguins <- drop_na(palmerpenguins::penguins)
-
-simple_scale <- function(x) (x - mean(x))/sd(x)
-
-penguins_scaled <- penguins %>%
-  mutate(x = simple_scale(bill_length_mm),
-         y = simple_scale(bill_depth_mm)) %>%
-  filter(x > -3, x < 3, y > -2, y < 2)
-
-poly1 <- data.frame(
-  x = c(-3, -1.8, .8, -3, -3),
-  y = c(-2, -2,   2, 2, -2)
-)
-
-poly2 <- data.frame(
-  x = c(-1.35, .8,  3,  3, -1.35),
-  y = c(-1.3,   2,  2, .9, -1.3)
-)
-
-poly3 <- data.frame(
-  x = c(-1.8, -1.35, 3, 3, -1.8),
-  y = c(-2,    -1.3, .9, -2, -2)
-)
 
@@
   geom_polygon(data = poly3, fill = cols[3], color = 'black', alpha = 0.2) +
-  geom_text(aes(x = -1.5, y = -1.5, label = "Impossible?"),
-            size = 4, check_overlap = TRUE) +
+  # geom_text(aes(x = -2, y = -1.5, label = "Impossible?"),
+            # size = 4, check_overlap = TRUE) +
   theme_minimal() +
@@
 To standardize comparisons of computational efficiency, all learners and VI techniques used up to 4 processing units.
-All code used in the current study is available at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench},
+
+% All code used in the current study is available at \href{https://github.com/bcjaeger/aorsf-bench}{https://github.com/bcjaeger/aorsf-bench},
 
@@
 
-<<bm_pred_viz_ibs, fig.height=10, fig.width=9, fig.cap="Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
-Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.
-As predicted survival probabilities are not a standard output from \\texttt{xgboost-aft}, it is not included in this figure.
-Also, since this figure is intended to compare \\texttt{aorsf-fast} to learners that are not oblique random survival forests, \\texttt{aorsf-cph}, \\texttt{aorsf-net}, \\texttt{aorsf-random}, and \\texttt{obliqueRSF-net} are not included.">>=
+<<bm_pred_viz_ibs, fig.height=9, fig.width=9, fig.cap="Index of prediction accuracy in multiple risk prediction tasks.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest score, showing absolute and relative improvement over the second best learner.
+Since this figure is intended to compare \\texttt{aorsf-fast} to learners that are not oblique random survival forests, \\texttt{aorsf-cph}, \\texttt{aorsf-random}, and \\texttt{obliqueRSF-net} are not included.">>=
 bm_pred_viz$ibs_scaled$fig
@@
 
-<<bm_pred_model_viz_ibs, fig.height=10, fig.width=9, fig.cap="Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
+<<bm_pred_model_viz_ibs, fig.height=9, fig.width=9, fig.cap="Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
 A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.">>=
@@
 
-<<bm_pred_viz_cstat, fig.height=10, fig.width=9, fig.cap="Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
+<<bm_pred_viz_cstat, fig.height=9, fig.width=9, fig.cap="Time-dependent concordance statistic for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
 Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.
-Since this figure is intended to compare \\texttt{aorsf-fast} to learners that are not oblique random survival forests, \\texttt{aorsf-cph}, \\texttt{aorsf-net}, \\texttt{aorsf-random}, and \\texttt{obliqueRSF-net} are not included.">>=
+Since this figure is intended to compare \\texttt{aorsf-fast} to learners that are not oblique random survival forests, \\texttt{aorsf-cph}, \\texttt{aorsf-random}, and \\texttt{obliqueRSF-net} are not included.">>=
 bm_pred_viz$cstat$fig
@@
 
-<<bm_pred_model_viz_cstat, fig.height=10, fig.width=9, fig.cap="Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms.
+<<bm_pred_model_viz_cstat, fig.height=9, fig.width=9, fig.cap="Expected differences in time-dependent concordance statistic between the accelerated oblique random survival forest and other learning algorithms.
 A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.">>=
@@
 
-<<bm_vi_viz, fig.height=11, fig.width=9, fig.cap="Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
+<<bm_vi_viz, fig.height=10, fig.width=9, fig.cap="Concordance statistic for assigning higher importance to relevant versus irrelevant variables.
 Text appears in rows where negation importance obtained the highest concordance, showing absolute and percent improvement over the second best technique.">>=
@@
 Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
-In numeric experiments, we found that that \texttt{aorsf-fast} is approximately \Sexpr{times$obliqueRSF_net$ratio} times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
+In numeric experiments, we found that \texttt{aorsf-fast} is approximately \Sexpr{times$obliqueRSF_net$ratio} times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
 We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.

### 2023-04-28 paper/jcgs/main.tex
paper can be made using only public data

@@
 Oblique trees split data using a linear combination of predictors, creating decision boundaries that are neither parallel nor perpendicular to axes of their contributing predictors \citep[see][Chapter~5]{breiman2017classification}.
+Oblique trees may create more adequate partitions of a predictor space compared to axis-based trees, as demonstrated in Figure \ref{fig:axis_v_oblique}.
 \citet{menze2011oblique} examined prediction accuracy of RFs in the presence of correlated predictors and found that oblique RFs had substantially higher prediction accuracy compared to axis-based RFs.
 Similarly, \citet{jaeger2019oblique} found that growing RSFs with oblique rather than axis-based trees reduced the RSF's concordance error, with improvements ranging from 2.5\% to 24.9\% depending on the data analyzed.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/axis_v_oblique-1} \caption[Decision boundaries from an axis based (panel A) and oblique (panel B) decision tree used to classify penguin species based on bill depth and bill length]{Decision boundaries from an axis based (panel A) and oblique (panel B) decision tree used to classify penguin species based on bill depth and bill length.
+The decision boundary from the oblique tree is better able to capture the geometry of this data, leading to fewer mis-classified penguins.}\label{fig:axis_v_oblique-1}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\maxwidth]{figure/axis_v_oblique-2} \caption[Decision boundaries from an axis based (panel A) and oblique (panel B) decision tree used to classify penguin species based on bill depth and bill length]{Decision boundaries from an axis based (panel A) and oblique (panel B) decision tree used to classify penguin species based on bill depth and bill length.
+The decision boundary from the oblique tree is better able to capture the geometry of this data, leading to fewer mis-classified penguins.}\label{fig:axis_v_oblique-2}
+\end{figure}
+
+\end{knitrout}
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/negation_vs_permutation_viz-1} \caption[Demonstration of negation and permutation importance for a single oblique tree]{Demonstration of negation and permutation importance for a single oblique tree.
+\includegraphics[width=\maxwidth]{figure/negation-1} \caption[Demonstration of negation and permutation importance for a single oblique tree]{Demonstration of negation and permutation importance for a single oblique tree.
 Panel A shows the original data and decision boundaries.
@@
 Panel C shows the decision boundaries after negating coefficients for bill length.
-Permutation and negation both show that bill length is an important predictor, but permuting bill length distorts its joint distribution with bill depth.}\label{fig:negation_vs_permutation_viz}
+Permutation and negation both show that bill length is an important predictor, but permuting bill length distorts its joint distribution with bill depth.}\label{fig:negation}
 \end{figure}
@@
 
-We used a collection of 21 data sets containing a total of 35 risk prediction tasks (tasks per data set ranged from one to four).
+We used a collection of 16 data sets containing a total of 21 risk prediction tasks (tasks per data set ranged from one to four).
 Participant-level data from the GUIDE-IT and SPRINT clinical trials and the ARIC, MESA, and JHS community cohort studies was obtained from the National Institute of Health Biologic Specimen and Data Repository Coordinating Center (BioLINCC).
@@
 All other datasets were publicly available and obtained through R packages (see Appendix A.1).
-Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 1,384), the number of predictors ranged from 7 to 1,692 (median: 41), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 78.1) (\tabrefAppendix{tab:datasets}).
+Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 929), the number of predictors ranged from 7 to 1,692 (median: 12), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 57.3) (\tabrefAppendix{tab:datasets}).
 
@@
 
-After collecting data from 25 replications of Monte-Carlo cross validation for the 14 learners in all 35 risk prediction tasks, we analyzed the resulting 12,250 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
+After collecting data from 25 replications of Monte-Carlo cross validation for the 14 learners in all 21 risk prediction tasks, we analyzed the resulting 7,350 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model.
 Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using Bayesian models.
@@
 
-For each learner discussed in \secref{sec:learners} and for each of the 35 risk prediction tasks analyzed in \secref{sec:bm_pred}, we tracked the amount of time required to fit a prediction model (including time used to tune parameters) and compute predicted risk.
+For each learner discussed in \secref{sec:learners} and for each of the 21 risk prediction tasks analyzed in \secref{sec:bm_pred}, we tracked the amount of time required to fit a prediction model (including time used to tune parameters) and compute predicted risk.
 
@@
 A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all}.
-In total, 871 out of 875 Monte-Carlo cross validation runs were completed.
+In total, 521 out of 525 Monte-Carlo cross validation runs were completed.
 On run 13, 18, 24 and 25 for the ACTG 320 data, the \texttt{nn-cox} learner encountered an error during its fitting procedure.
@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 17 out of 35 risk prediction tasks, with an overall mean IPA of 12.6 (Figure \ref{fig:bm_pred_viz_ibs}).
-Compared to the learner with the second highest mean IPA (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 1.33 points higher, a relative increase of 11.7\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.80 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in 7 out of 21 risk prediction tasks, with an overall mean IPA of 14.1 (Figure \ref{fig:bm_pred_viz_ibs}).
+Compared to the learner with the second highest mean IPA (\texttt{cif-rotate}), \texttt{aorsf-fast}'s mean was 0.851 points higher, a relative increase of 6.43\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.89, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.37 (versus \texttt{cif-rotate}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
-\includegraphics[width=\maxwidth]{figure/bm_pred_viz_ibs-1} \caption{Index of prediction accuracy for the accelerated oblique random survival forest and other learning algorithms across multiple risk prediction tasks.
-Text appears in tasks where the accelerated oblique random survival forest obtained the highest index of prediction accuracy, showing the absolute and percent improvement over the second best learner.
-As predicted survival probabilities are not a standard output from \texttt{xgboost-aft}, it is not included in this figure.
-Also, since this figure is intended to compare \texttt{aorsf-fast} to learners that are not oblique random survival forests, \texttt{aorsf-cph}, \texttt{aorsf-net}, \texttt{aorsf-random}, and \texttt{obliqueRSF-net} are not included.}\label{fig:bm_pred_viz_ibs}
+\includegraphics[width=\maxwidth]{figure/bm_pred_viz_ibs-1} \caption[Index of prediction accuracy in multiple risk prediction tasks]{Index of prediction accuracy in multiple risk prediction tasks.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest score, showing absolute and relative improvement over the second best learner.
+Since this figure is intended to compare \texttt{aorsf-fast} to learners that are not oblique random survival forests, \texttt{aorsf-cph}, \texttt{aorsf-random}, and \texttt{obliqueRSF-net} are not included.}\label{fig:bm_pred_viz_ibs}
 \end{figure}
@@
 
-Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 9 out of 35 risk prediction tasks, with an overall mean of 77.2 (Figure \ref{fig:bm_pred_viz_cstat}).
-Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.668 points higher, a relative increase of 0.873\%.
-The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was $>$ 0.999, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.15 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
+Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in 6 out of 21 risk prediction tasks, with an overall mean of 75.8 (Figure \ref{fig:bm_pred_viz_cstat}).
+Compared to the learner with the second highest mean C-statistic (\texttt{cif-standard}), \texttt{aorsf-fast}'s mean was 0.903 points higher, a relative increase of 1.20\%.
+The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.96, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.44 (versus \texttt{cif-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})
 
@@
 Text appears in tasks where the accelerated oblique random survival forest obtained the highest concordance, showing the absolute and percent improvement over the second best learner.
-Since this figure is intended to compare \texttt{aorsf-fast} to learners that are not oblique random survival forests, \texttt{aorsf-cph}, \texttt{aorsf-net}, \texttt{aorsf-random}, and \texttt{obliqueRSF-net} are not included.}\label{fig:bm_pred_viz_cstat}
+Since this figure is intended to compare \texttt{aorsf-fast} to learners that are not oblique random survival forests, \texttt{aorsf-cph}, \texttt{aorsf-random}, and \texttt{obliqueRSF-net} are not included.}\label{fig:bm_pred_viz_cstat}
 \end{figure}
@@
 
-In the analysis of 35 risk prediction tasks, \texttt{aorsf-fast} was the second fastest learner overall, with a median time to develop a risk prediction model and compute predictions about 337 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
-Comparing median computing times, \texttt{aorsf-fast} was 1,291.6 times faster than its predecessor, \texttt{obliqueRSF-net}.
-In addition, \texttt{aorsf-fast} was 19.8, 1.90, and 3.18 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
+In the analysis of 21 risk prediction tasks, \texttt{aorsf-fast} was the second fastest learner overall, with a median time to develop a risk prediction model and compute predictions about 76 milliseconds longer than \texttt{glmnet-cox} (Figure \ref{fig:bm_pred_time}).
+Comparing median computing times, \texttt{aorsf-fast} was 917.1 times faster than its predecessor, \texttt{obliqueRSF-net}.
+In addition, \texttt{aorsf-fast} was 16.0, 0.820, and 4.70 faster than axis based forests grown using the \texttt{party}, \texttt{ranger}, and \texttt{randomForestSRC} packages, respectively.
 
@@
 Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
-In numeric experiments, we found that that \texttt{aorsf-fast} is approximately 1,291.6 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
+In numeric experiments, we found that \texttt{aorsf-fast} is approximately 917.1 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
 We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.
@@
  \item The ``ACTG 320'' data \citep{hosmer2002applied} were obtained from the \texttt{mlr3proba} R package \citep{mlr3proba}. 
- \item The ``GUIDE-IT'' data \citep{felker2017effect} were obtained from BioLINCC. 
  \item The ``Early breast cancer'' data \citep{desmedt2011multifactorial, hatzis2011genomic, ternes2017identification} were obtained from the \texttt{biospear} R package \citep{biospear}. 
- \item The ``SPRINT'' data \citep{sprint2015randomized} were obtained from BioLINCC. 
  \item The ``NKI 70 gene signature'' data \citep{van2002gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}. 
@@
  \item The ``Monoclonal gammopathy'' data \citep{kyle2002long} were obtained from the \texttt{survival} R package \citep{survival}.
- \item The ``MESA'' data \citep{bild2002multi} were obtained from BioLINCC. 
- \item The ``ARIC'' data \citep{aric1989atherosclerosis} were obtained from BioLINCC. 
- \item The ``JHS'' data \citep{taylor2005toward} were obtained from BioLINCC.
 
@@
 \cmidrule{1-6}\pagebreak[0]
- &  &  & Cardiovascular Death & 110 & 87.7\\
-\cmidrule{4-6}\nopagebreak
-\multirow{-2}{*}{\raggedright\arraybackslash GUIDE-IT} & \multirow{-2}{*}{\centering\arraybackslash 894} & \multirow{-2}{*}{\centering\arraybackslash 59} & Hf Hospitalization & 288 & 67.8\\
-\cmidrule{1-6}\pagebreak[0]
 Early breast cancer & 614 & 1,692 & Recurrence Or Death & 134 & 78.2\\
-\cmidrule{1-6}\pagebreak[0]
- &  &  & Cardiovascular Death & 521 & 94.4\\
-\cmidrule{4-6}\nopagebreak
-\multirow{-2}{*}{\raggedright\arraybackslash SPRINT} & \multirow{-2}{*}{\centering\arraybackslash 9,361} & \multirow{-2}{*}{\centering\arraybackslash 174} & Death & 1,644 & 82.4\\
 \cmidrule{1-6}\pagebreak[0]
@@
 \multirow{-2}{*}{\raggedright\arraybackslash Monoclonal gammopathy} & \multirow{-2}{*}{\centering\arraybackslash 1,384} & \multirow{-2}{*}{\centering\arraybackslash 8} & Malignancy & 115 & 91.7\\
-\cmidrule{1-6}\pagebreak[0]
- &  &  & Heart Failure & 339 & 95.0\\
-\cmidrule{4-6}\nopagebreak
- &  &  & Coronary Heart Disease & 439 & 93.5\\
-\cmidrule{4-6}\nopagebreak
- &  &  & Stroke & 292 & 95.7\\
-\cmidrule{4-6}\nopagebreak
-\multirow{-4}{*}{\raggedright\arraybackslash MESA} & \multirow{-4}{*}{\centering\arraybackslash 6,783} & \multirow{-4}{*}{\centering\arraybackslash 48} & Death & 1,297 & 80.9\\
-\cmidrule{1-6}\pagebreak[0]
- &  &  & Heart Failure & 2,981 & 78.1\\
-\cmidrule{4-6}\nopagebreak
- &  &  & Coronary Heart Disease & 2,282 & 83.2\\
-\cmidrule{4-6}\nopagebreak
- &  &  & Stroke & 1,323 & 90.3\\
-\cmidrule{4-6}\nopagebreak
-\multirow{-4}{*}{\raggedright\arraybackslash ARIC} & \multirow{-4}{*}{\centering\arraybackslash 13,623} & \multirow{-4}{*}{\centering\arraybackslash 41} & Death & 6,662 & 51.1\\
-\cmidrule{1-6}\pagebreak[0]
- &  &  & Stroke & 152 & 95.8\\
-\cmidrule{4-6}\nopagebreak
-\multirow{-2}{*}{\raggedright\arraybackslash JHS} & \multirow{-2}{*}{\centering\arraybackslash 3,501} & \multirow{-2}{*}{\centering\arraybackslash 80} & Coronary Heart Disease & 190 & 94.6\\
 \bottomrule
@@
 \begin{longtable}[t]{lcccc}
-\caption{\label{tab:unnamed-chunk-11}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 35 risk prediction tasks.\label{tab:bm_pred_all}}\\
+\caption{\label{tab:unnamed-chunk-11}Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 21 risk prediction tasks.\label{tab:bm_pred_all}}\\
 \toprule
@@
 \endfirsthead
-\caption[]{Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 35 risk prediction tasks.\label{tab:bm_pred_all} \textit{(continued)}}\\
+\caption[]{Index of prediction accuracy, time-dependent concordance statistic, and computational time required to fit and compute predictions for several learning algorithms across 21 risk prediction tasks.\label{tab:bm_pred_all} \textit{(continued)}}\\
 \toprule
@@
 \hline
-\hspace{1em}aorsf-fast & 0.126 (0.109) & 0.772 (0.071) & 0.527 & 0.138\\
-\hspace{1em}aorsf-cph & 0.126 (0.109) & 0.771 (0.070) & 1.750 & 0.140\\
-\hspace{1em}cif-standard & 0.113 (0.098) & 0.765 (0.071) & 3.792 & 6.448\\
-\hspace{1em}rsf-standard & 0.113 (0.114) & 0.755 (0.075) & 1.945 & 0.196\\
-\hspace{1em}cif-rotate & 0.112 (0.124) & 0.755 (0.081) & 36.928 & 8.194\\
-\hspace{1em}obliqueRSF-net & 0.109 (0.081) & 0.773 (0.069) & 552.335 & 84.685\\
-\hspace{1em}glmnet-cox & 0.108 (0.119) & 0.757 (0.077) & 0.326 & 0.003\\
-\hspace{1em}ranger-extratrees & 0.099 (0.085) & 0.762 (0.067) & 0.790 & 1.109\\
-\hspace{1em}cif-extension & 0.095 (0.092) & 0.761 (0.072) & 21.977 & 6.922\\
-\hspace{1em}aorsf-random & 0.092 (0.079) & 0.744 (0.065) & 1.717 & 0.149\\
-\hspace{1em}xgboost-cox & 0.064 (0.100) & 0.749 (0.094) & 4.394 & 0.004\\
-\hspace{1em}nn-cox & 0.048 (0.106) & 0.657 (0.136) & 11.377 & 1.705\\
-\hspace{1em}xgboost-aft & --- & 0.762 (0.076) & 15.031 & 0.007\\
+\hspace{1em}aorsf-cph & 0.142 (0.129) & 0.759 (0.083) & 0.598 & 0.042\\
+\hspace{1em}aorsf-fast & 0.141 (0.129) & 0.758 (0.084) & 0.200 & 0.043\\
+\hspace{1em}cif-rotate & 0.132 (0.153) & 0.741 (0.096) & 14.486 & 3.435\\
+\hspace{1em}cif-standard & 0.127 (0.116) & 0.749 (0.082) & 0.939 & 3.370\\
+\hspace{1em}glmnet-cox & 0.124 (0.144) & 0.746 (0.087) & 0.183 & 0.002\\
+\hspace{1em}rsf-standard & 0.124 (0.135) & 0.741 (0.088) & 1.103 & 0.105\\
+\hspace{1em}obliqueRSF-net & 0.121 (0.094) & 0.760 (0.081) & 211.788 & 20.351\\
+\hspace{1em}cif-extension & 0.119 (0.111) & 0.749 (0.086) & 8.578 & 3.809\\
+\hspace{1em}aorsf-random & 0.111 (0.092) & 0.742 (0.076) & 0.915 & 0.040\\
+\hspace{1em}ranger-extratrees & 0.111 (0.101) & 0.749 (0.079) & 0.057 & 0.143\\
+\hspace{1em}xgboost-cox & 0.081 (0.121) & 0.722 (0.108) & 3.406 & 0.003\\
+\hspace{1em}nn-cox & 0.028 (0.124) & 0.584 (0.126) & 9.229 & 0.680\\
+\hspace{1em}xgboost-aft & --- & 0.745 (0.088) & 11.525 & 0.006\\
 \addlinespace[0.3em]
@@
 \addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{ARIC; coronary heart disease, n = 13623, p = 41}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.156 (0.007) & 0.810 (0.007) & 4.590 & 1.434\\
-\hspace{1em}aorsf-cph & 0.153 (0.006) & 0.809 (0.007) & 14.582 & 1.450\\
-\hspace{1em}rsf-standard & 0.150 (0.007) & 0.801 (0.007) & 8.222 & 0.981\\
-\hspace{1em}obliqueRSF-net & 0.133 (0.005) & 0.811 (0.008) & 4468.696 & 1359.275\\
-\hspace{1em}cif-standard & 0.132 (0.005) & 0.809 (0.007) & 70.462 & 358.273\\
-\hspace{1em}glmnet-cox & 0.129 (0.011) & 0.795 (0.008) & 1.873 & 0.010\\
-\hspace{1em}nn-cox & 0.126 (0.012) & 0.795 (0.007) & 43.144 & 86.104\\
-\hspace{1em}ranger-extratrees & 0.112 (0.005) & 0.795 (0.009) & 283.364 & 69.939\\
-\hspace{1em}aorsf-random & 0.104 (0.005) & 0.771 (0.008) & 11.343 & 1.420\\
-\hspace{1em}cif-rotate & 0.104 (0.004) & 0.783 (0.009) & 558.249 & 68.510\\
-\hspace{1em}cif-extension & 0.069 (0.002) & 0.786 (0.009) & 164.161 & 50.420\\
-\hspace{1em}xgboost-cox & 0.064 (0.017) & 0.813 (0.006) & 9.660 & 0.015\\
-\hspace{1em}xgboost-aft & --- & 0.814 (0.006) & 29.321 & 0.013\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{ARIC; death, n = 13623, p = 41}}}\\
-\hline
-\hspace{1em}rsf-standard & 0.216 (0.006) & 0.789 (0.004) & 12.352 & 1.162\\
-\hspace{1em}aorsf-fast & 0.216 (0.006) & 0.792 (0.004) & 7.463 & 2.519\\
-\hspace{1em}aorsf-cph & 0.215 (0.006) & 0.792 (0.004) & 22.389 & 2.569\\
-\hspace{1em}cif-standard & 0.201 (0.004) & 0.790 (0.004) & 68.083 & 373.333\\
-\hspace{1em}obliqueRSF-net & 0.195 (0.004) & 0.789 (0.004) & 7373.936 & 1276.463\\
-\hspace{1em}nn-cox & 0.191 (0.008) & 0.779 (0.005) & 83.418 & 84.770\\
-\hspace{1em}glmnet-cox & 0.191 (0.015) & 0.777 (0.007) & 2.282 & 0.011\\
-\hspace{1em}ranger-extratrees & 0.181 (0.004) & 0.780 (0.005) & 356.276 & 61.525\\
-\hspace{1em}cif-rotate & 0.151 (0.007) & 0.757 (0.006) & 563.575 & 64.849\\
-\hspace{1em}xgboost-cox & 0.131 (0.012) & 0.794 (0.004) & 12.568 & 0.015\\
-\hspace{1em}aorsf-random & 0.128 (0.006) & 0.725 (0.005) & 20.291 & 2.298\\
-\hspace{1em}cif-extension & 0.113 (0.002) & 0.775 (0.005) & 176.867 & 50.345\\
-\hspace{1em}xgboost-aft & --- & 0.794 (0.004) & 35.380 & 0.013\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{ARIC; heart failure, n = 13623, p = 41}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.233 (0.006) & 0.841 (0.005) & 5.478 & 1.709\\
-\hspace{1em}rsf-standard & 0.229 (0.006) & 0.835 (0.005) & 10.326 & 1.039\\
-\hspace{1em}aorsf-cph & 0.229 (0.006) & 0.840 (0.005) & 17.063 & 1.730\\
-\hspace{1em}cif-standard & 0.199 (0.005) & 0.839 (0.005) & 68.929 & 364.202\\
-\hspace{1em}obliqueRSF-net & 0.198 (0.005) & 0.839 (0.005) & 5341.195 & 1624.560\\
-\hspace{1em}nn-cox & 0.188 (0.018) & 0.826 (0.006) & 58.351 & 89.012\\
-\hspace{1em}cif-rotate & 0.172 (0.006) & 0.806 (0.007) & 569.166 & 67.654\\
-\hspace{1em}ranger-extratrees & 0.170 (0.004) & 0.824 (0.005) & 411.253 & 73.737\\
-\hspace{1em}glmnet-cox & 0.167 (0.044) & 0.817 (0.018) & 2.257 & 0.010\\
-\hspace{1em}aorsf-random & 0.151 (0.006) & 0.792 (0.007) & 14.023 & 1.686\\
-\hspace{1em}xgboost-cox & 0.122 (0.017) & 0.845 (0.005) & 11.985 & 0.015\\
-\hspace{1em}cif-extension & 0.109 (0.003) & 0.808 (0.006) & 169.620 & 49.957\\
-\hspace{1em}xgboost-aft & --- & 0.844 (0.005) & 30.837 & 0.012\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{ARIC; stroke, n = 13623, p = 41}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.093 (0.004) & 0.793 (0.007) & 3.625 & 1.205\\
-\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.792 (0.007) & 12.691 & 1.331\\
-\hspace{1em}rsf-standard & 0.090 (0.006) & 0.784 (0.006) & 8.134 & 0.916\\
-\hspace{1em}glmnet-cox & 0.078 (0.004) & 0.787 (0.007) & 1.781 & 0.010\\
-\hspace{1em}obliqueRSF-net & 0.073 (0.003) & 0.789 (0.008) & 3058.459 & 2338.694\\
-\hspace{1em}cif-standard & 0.073 (0.003) & 0.787 (0.007) & 69.723 & 355.372\\
-\hspace{1em}nn-cox & 0.068 (0.016) & 0.781 (0.012) & 29.662 & 78.191\\
-\hspace{1em}ranger-extratrees & 0.067 (0.003) & 0.779 (0.008) & 219.331 & 61.397\\
-\hspace{1em}aorsf-random & 0.061 (0.005) & 0.750 (0.009) & 9.153 & 1.186\\
-\hspace{1em}cif-rotate & 0.052 (0.003) & 0.768 (0.009) & 573.621 & 66.723\\
-\hspace{1em}xgboost-cox & 0.047 (0.014) & 0.794 (0.006) & 7.662 & 0.014\\
-\hspace{1em}cif-extension & 0.036 (0.002) & 0.769 (0.009) & 167.033 & 51.074\\
-\hspace{1em}xgboost-aft & --- & 0.793 (0.006) & 25.321 & 0.012\\
-\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Colon cancer; death, n = 929, p = 12}}}\\
@@
 \addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{GUIDE-IT; CVD death, n = 894, p = 59}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.075 (0.018) & 0.745 (0.028) & 0.154 & 0.036\\
-\hspace{1em}aorsf-cph & 0.071 (0.018) & 0.742 (0.027) & 0.386 & 0.037\\
-\hspace{1em}glmnet-cox & 0.063 (0.041) & 0.715 (0.091) & 0.489 & 0.003\\
-\hspace{1em}obliqueRSF-net & 0.060 (0.013) & 0.741 (0.027) & 209.529 & 11.066\\
-\hspace{1em}cif-rotate & 0.059 (0.016) & 0.721 (0.025) & 34.549 & 4.966\\
-\hspace{1em}cif-standard & 0.058 (0.014) & 0.738 (0.022) & 1.380 & 3.350\\
-\hspace{1em}ranger-extratrees & 0.054 (0.013) & 0.737 (0.029) & 0.082 & 0.196\\
-\hspace{1em}cif-extension & 0.052 (0.011) & 0.730 (0.022) & 13.080 & 5.523\\
-\hspace{1em}rsf-standard & 0.046 (0.023) & 0.705 (0.025) & 0.174 & 0.061\\
-\hspace{1em}xgboost-cox & 0.044 (0.041) & 0.747 (0.020) & 3.880 & 0.003\\
-\hspace{1em}aorsf-random & 0.030 (0.011) & 0.675 (0.035) & 0.510 & 0.038\\
-\hspace{1em}nn-cox & 0.022 (0.036) & 0.673 (0.089) & 8.663 & 0.566\\
-\hspace{1em}xgboost-aft & --- & 0.734 (0.020) & 11.747 & 0.006\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{GUIDE-IT; HF hospitalization, n = 894, p = 59}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.081 (0.019) & 0.723 (0.024) & 0.239 & 0.054\\
-\hspace{1em}aorsf-cph & 0.080 (0.018) & 0.722 (0.024) & 0.682 & 0.055\\
-\hspace{1em}ranger-extratrees & 0.073 (0.010) & 0.722 (0.022) & 0.243 & 0.187\\
-\hspace{1em}obliqueRSF-net & 0.071 (0.009) & 0.721 (0.022) & 354.417 & 22.308\\
-\hspace{1em}cif-standard & 0.070 (0.010) & 0.716 (0.023) & 1.282 & 3.415\\
-\hspace{1em}cif-rotate & 0.067 (0.019) & 0.708 (0.029) & 40.978 & 4.799\\
-\hspace{1em}cif-extension & 0.064 (0.009) & 0.714 (0.022) & 14.406 & 5.796\\
-\hspace{1em}glmnet-cox & 0.058 (0.020) & 0.699 (0.025) & 0.391 & 0.002\\
-\hspace{1em}rsf-standard & 0.058 (0.022) & 0.694 (0.026) & 1.601 & 0.122\\
-\hspace{1em}nn-cox & 0.051 (0.026) & 0.701 (0.038) & 9.103 & 0.579\\
-\hspace{1em}xgboost-cox & 0.040 (0.016) & 0.699 (0.026) & 3.449 & 0.003\\
-\hspace{1em}aorsf-random & 0.039 (0.012) & 0.668 (0.028) & 0.889 & 0.053\\
-\hspace{1em}xgboost-aft & --- & 0.697 (0.025) & 13.258 & 0.006\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{JHS; coronary heart disease, n = 3501, p = 80}}}\\
-\hline
-\hspace{1em}aorsf-cph & 0.040 (0.007) & 0.778 (0.014) & 2.083 & 0.144\\
-\hspace{1em}aorsf-fast & 0.039 (0.007) & 0.777 (0.015) & 0.557 & 0.141\\
-\hspace{1em}obliqueRSF-net & 0.038 (0.005) & 0.784 (0.017) & 592.769 & 868.718\\
-\hspace{1em}cif-standard & 0.038 (0.006) & 0.779 (0.017) & 9.787 & 30.975\\
-\hspace{1em}cif-extension & 0.036 (0.004) & 0.781 (0.019) & 56.440 & 20.992\\
-\hspace{1em}ranger-extratrees & 0.035 (0.005) & 0.777 (0.017) & 3.678 & 2.536\\
-\hspace{1em}cif-rotate & 0.034 (0.010) & 0.769 (0.018) & 187.605 & 23.593\\
-\hspace{1em}glmnet-cox & 0.031 (0.010) & 0.774 (0.020) & 2.237 & 0.004\\
-\hspace{1em}rsf-standard & 0.031 (0.011) & 0.752 (0.016) & 2.011 & 0.215\\
-\hspace{1em}nn-cox & 0.025 (0.020) & 0.745 (0.029) & 10.189 & 6.685\\
-\hspace{1em}aorsf-random & 0.021 (0.004) & 0.746 (0.021) & 1.800 & 0.163\\
-\hspace{1em}xgboost-cox & 0.010 (0.023) & 0.785 (0.022) & 4.562 & 0.006\\
-\hspace{1em}xgboost-aft & --- & 0.782 (0.017) & 18.309 & 0.007\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{JHS; stroke, n = 3639, p = 80}}}\\
-\hline
-\hspace{1em}aorsf-cph & 0.035 (0.006) & 0.805 (0.017) & 2.137 & 0.141\\
-\hspace{1em}aorsf-fast & 0.035 (0.007) & 0.807 (0.018) & 0.527 & 0.139\\
-\hspace{1em}obliqueRSF-net & 0.028 (0.004) & 0.810 (0.016) & 528.781 & 577.511\\
-\hspace{1em}glmnet-cox & 0.028 (0.008) & 0.798 (0.017) & 2.915 & 0.004\\
-\hspace{1em}cif-standard & 0.028 (0.005) & 0.803 (0.016) & 10.497 & 32.921\\
-\hspace{1em}rsf-standard & 0.027 (0.010) & 0.782 (0.018) & 1.632 & 0.159\\
-\hspace{1em}cif-extension & 0.025 (0.003) & 0.797 (0.018) & 56.277 & 22.158\\
-\hspace{1em}aorsf-random & 0.024 (0.005) & 0.770 (0.023) & 1.726 & 0.158\\
-\hspace{1em}ranger-extratrees & 0.023 (0.005) & 0.791 (0.016) & 3.510 & 2.689\\
-\hspace{1em}cif-rotate & 0.023 (0.009) & 0.785 (0.017) & 186.661 & 24.918\\
-\hspace{1em}nn-cox & 0.014 (0.022) & 0.763 (0.045) & 9.541 & 6.840\\
-\hspace{1em}xgboost-cox & 0.002 (0.028) & 0.775 (0.023) & 3.500 & 0.005\\
-\hspace{1em}xgboost-aft & --- & 0.784 (0.018) & 16.110 & 0.007\\
-\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Lung cancer; death, n = 442, p = 24}}}\\
@@
 \addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{MESA; coronary heart disease, n = 6785, p = 48}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.064 (0.010) & 0.807 (0.011) & 1.213 & 0.363\\
-\hspace{1em}aorsf-cph & 0.061 (0.010) & 0.802 (0.012) & 5.020 & 0.374\\
-\hspace{1em}cif-standard & 0.059 (0.007) & 0.803 (0.013) & 23.531 & 96.894\\
-\hspace{1em}obliqueRSF-net & 0.058 (0.006) & 0.809 (0.012) & 1296.402 & 747.185\\
-\hspace{1em}cif-rotate & 0.058 (0.009) & 0.802 (0.013) & 284.179 & 37.551\\
-\hspace{1em}rsf-standard & 0.057 (0.012) & 0.795 (0.013) & 3.455 & 1.337\\
-\hspace{1em}ranger-extratrees & 0.047 (0.004) & 0.794 (0.011) & 7.979 & 6.588\\
-\hspace{1em}cif-extension & 0.047 (0.003) & 0.805 (0.013) & 97.660 & 28.300\\
-\hspace{1em}aorsf-random & 0.041 (0.008) & 0.760 (0.015) & 2.930 & 0.404\\
-\hspace{1em}glmnet-cox & 0.038 (0.017) & 0.775 (0.016) & 4.514 & 0.006\\
-\hspace{1em}nn-cox & 0.035 (0.016) & 0.766 (0.019) & 13.123 & 15.303\\
-\hspace{1em}xgboost-cox & 0.014 (0.027) & 0.802 (0.013) & 5.344 & 0.008\\
-\hspace{1em}xgboost-aft & --- & 0.802 (0.012) & 20.582 & 0.009\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{MESA; death, n = 6793, p = 48}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.144 (0.008) & 0.792 (0.008) & 1.725 & 0.541\\
-\hspace{1em}aorsf-cph & 0.143 (0.008) & 0.791 (0.008) & 6.596 & 0.543\\
-\hspace{1em}rsf-standard & 0.140 (0.008) & 0.784 (0.009) & 4.936 & 0.480\\
-\hspace{1em}cif-standard & 0.134 (0.007) & 0.788 (0.009) & 23.408 & 98.656\\
-\hspace{1em}obliqueRSF-net & 0.132 (0.006) & 0.790 (0.009) & 2468.159 & 526.499\\
-\hspace{1em}glmnet-cox & 0.131 (0.026) & 0.789 (0.012) & 1.373 & 0.006\\
-\hspace{1em}nn-cox & 0.129 (0.019) & 0.788 (0.010) & 24.110 & 17.345\\
-\hspace{1em}cif-rotate & 0.126 (0.007) & 0.783 (0.010) & 319.531 & 37.277\\
-\hspace{1em}ranger-extratrees & 0.113 (0.004) & 0.784 (0.008) & 9.502 & 6.313\\
-\hspace{1em}cif-extension & 0.092 (0.003) & 0.781 (0.009) & 108.674 & 28.132\\
-\hspace{1em}aorsf-random & 0.086 (0.006) & 0.741 (0.009) & 5.817 & 0.577\\
-\hspace{1em}xgboost-cox & 0.057 (0.029) & 0.794 (0.009) & 8.811 & 0.009\\
-\hspace{1em}xgboost-aft & --- & 0.793 (0.009) & 24.056 & 0.009\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{MESA; heart failure, n = 6785, p = 48}}}\\
-\hline
-\hspace{1em}aorsf-fast & 0.115 (0.010) & 0.866 (0.012) & 1.118 & 0.321\\
-\hspace{1em}aorsf-cph & 0.109 (0.011) & 0.858 (0.013) & 4.817 & 0.334\\
-\hspace{1em}rsf-standard & 0.108 (0.012) & 0.856 (0.012) & 3.228 & 1.248\\
-\hspace{1em}cif-rotate & 0.105 (0.010) & 0.869 (0.013) & 254.592 & 36.536\\
-\hspace{1em}cif-standard & 0.102 (0.009) & 0.864 (0.013) & 23.983 & 97.903\\
-\hspace{1em}obliqueRSF-net & 0.099 (0.007) & 0.870 (0.012) & 1112.448 & 1225.449\\
-\hspace{1em}aorsf-random & 0.082 (0.009) & 0.819 (0.016) & 2.432 & 0.372\\
-\hspace{1em}cif-extension & 0.077 (0.005) & 0.864 (0.011) & 91.356 & 28.914\\
-\hspace{1em}nn-cox & 0.075 (0.021) & 0.832 (0.015) & 12.343 & 14.955\\
-\hspace{1em}ranger-extratrees & 0.075 (0.005) & 0.849 (0.015) & 7.105 & 6.412\\
-\hspace{1em}glmnet-cox & 0.043 (0.044) & 0.767 (0.139) & 3.485 & 0.006\\
-\hspace{1em}xgboost-cox & -0.011 (0.019) & 0.869 (0.011) & 7.135 & 0.009\\
-\hspace{1em}xgboost-aft & --- & 0.870 (0.012) & 22.191 & 0.008\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{MESA; stroke, n = 6783, p = 48}}}\\
-\hline
-\hspace{1em}cif-rotate & 0.025 (0.004) & 0.764 (0.017) & 267.261 & 37.143\\
-\hspace{1em}aorsf-fast & 0.025 (0.006) & 0.764 (0.016) & 1.087 & 0.318\\
-\hspace{1em}cif-standard & 0.025 (0.004) & 0.762 (0.017) & 23.820 & 97.317\\
-\hspace{1em}obliqueRSF-net & 0.024 (0.003) & 0.772 (0.017) & 975.645 & 1212.002\\
-\hspace{1em}aorsf-cph & 0.024 (0.006) & 0.760 (0.018) & 4.270 & 0.315\\
-\hspace{1em}ranger-extratrees & 0.022 (0.003) & 0.759 (0.016) & 7.125 & 6.067\\
-\hspace{1em}glmnet-cox & 0.021 (0.009) & 0.765 (0.017) & 3.417 & 0.006\\
-\hspace{1em}cif-extension & 0.021 (0.002) & 0.768 (0.017) & 93.628 & 27.983\\
-\hspace{1em}rsf-standard & 0.019 (0.009) & 0.745 (0.018) & 3.032 & 1.194\\
-\hspace{1em}aorsf-random & 0.016 (0.004) & 0.725 (0.023) & 2.309 & 0.342\\
-\hspace{1em}nn-cox & 0.016 (0.008) & 0.734 (0.040) & 11.686 & 18.015\\
-\hspace{1em}xgboost-cox & 0.000 (0.027) & 0.763 (0.016) & 4.469 & 0.008\\
-\hspace{1em}xgboost-aft & --- & 0.764 (0.015) & 20.407 & 0.008\\
-\addlinespace[0.3em]
 \multicolumn{5}{l}{\textit{\textbf{Monoclonal gammopathy; death, n = 1384, p = 8}}}\\
@@
 \hspace{1em}xgboost-aft & --- & 0.823 (0.008) & 21.594 & 0.008\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{SPRINT; CVD death, n = 9361, p = 174}}}\\
-\hline
-\hspace{1em}glmnet-cox & 0.071 (0.011) & 0.795 (0.011) & 13.048 & 0.010\\
-\hspace{1em}aorsf-cph & 0.070 (0.006) & 0.797 (0.011) & 8.638 & 0.627\\
-\hspace{1em}aorsf-fast & 0.069 (0.006) & 0.797 (0.011) & 2.365 & 0.643\\
-\hspace{1em}rsf-standard & 0.065 (0.007) & 0.788 (0.014) & 4.277 & 1.394\\
-\hspace{1em}obliqueRSF-net & 0.064 (0.004) & 0.799 (0.011) & 2639.976 & 3402.983\\
-\hspace{1em}cif-standard & 0.061 (0.003) & 0.798 (0.011) & 49.621 & 182.059\\
-\hspace{1em}cif-rotate & 0.060 (0.005) & 0.791 (0.012) & 924.836 & 113.844\\
-\hspace{1em}ranger-extratrees & 0.054 (0.003) & 0.791 (0.012) & 8.222 & 7.874\\
-\hspace{1em}nn-cox & 0.040 (0.015) & 0.763 (0.022) & 16.891 & 22.686\\
-\hspace{1em}aorsf-random & 0.038 (0.003) & 0.768 (0.013) & 5.475 & 0.742\\
-\hspace{1em}cif-extension & 0.034 (0.002) & 0.789 (0.011) & 120.288 & 32.189\\
-\hspace{1em}xgboost-cox & 0.004 (0.019) & 0.800 (0.011) & 7.700 & 0.013\\
-\hspace{1em}xgboost-aft & --- & 0.796 (0.012) & 25.017 & 0.012\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textit{\textbf{SPRINT; death, n = 9361, p = 174}}}\\
-\hline
-\hspace{1em}glmnet-cox & 0.123 (0.012) & 0.771 (0.009) & 5.430 & 0.010\\
-\hspace{1em}aorsf-cph & 0.117 (0.008) & 0.770 (0.008) & 12.921 & 0.996\\
-\hspace{1em}aorsf-fast & 0.115 (0.008) & 0.770 (0.008) & 4.217 & 0.977\\
-\hspace{1em}rsf-standard & 0.110 (0.008) & 0.763 (0.009) & 7.137 & 0.691\\
-\hspace{1em}obliqueRSF-net & 0.108 (0.006) & 0.766 (0.008) & 4500.673 & 664.611\\
-\hspace{1em}cif-standard & 0.106 (0.006) & 0.764 (0.008) & 49.263 & 185.385\\
-\hspace{1em}nn-cox & 0.097 (0.012) & 0.755 (0.011) & 28.348 & 28.860\\
-\hspace{1em}ranger-extratrees & 0.096 (0.005) & 0.756 (0.009) & 9.647 & 8.153\\
-\hspace{1em}cif-rotate & 0.090 (0.007) & 0.745 (0.009) & 1039.879 & 113.336\\
-\hspace{1em}aorsf-random & 0.072 (0.003) & 0.741 (0.009) & 8.907 & 1.067\\
-\hspace{1em}cif-extension & 0.055 (0.002) & 0.747 (0.009) & 135.763 & 32.580\\
-\hspace{1em}xgboost-cox & 0.030 (0.022) & 0.772 (0.008) & 10.871 & 0.013\\
-\hspace{1em}xgboost-aft & --- & 0.772 (0.007) & 27.708 & 0.012\\
 \addlinespace[0.3em]

### 2023-04-28 R/data_load.R

@@ -1809,3 +1809,7 @@ jhs_stroke_load <- function(){
 jhs_chd_load <- function(){
   jhs_load("chd")
 }
+
+ehr_hfhosp_load <- function(){
+  fread("D:/aorsf-HF-hospitalization/data/temp.csv")
+}

### 2023-05-16 paper/jcgs/reviewer-response/reviewer-response.Rmd
R1 updates

---
title: "Hypertension statistics for US adults: an open-source web application for analysis and visualization of US NHANES data"
always_allow_html: true
bibliography: refs.bib
csl: jama.csl
output: 
  officedown::rdocx_document:
    reference_docx: style_manuscript_times_new_roman.docx
    keep_md: true
---

Reviewer: 1

Comments to the Author

This manuscript adds two contributions to the literature of random forests. 1) The development of a computational efficient oblique random forest algorithm for right censored/survival data and 2) An alternative approach to estimate variable important using what is called “negation variable importance”. The authors apply their approach on both simulated and real data sets. Overall, the manuscript is well written, and the manuscript is in line with JCGS’s scopes and aims. The authors do an excellent job outlining their approach and planned future directions.

Below are a few minor comments that I would like to have addressed.

1.	The validity of the Cox partial likelihood function requires the non-informative censoring assumption (true survival time and censoring time are independent given the features X). I did not see this explicitly stated as an assumption in Section 2.3.

**Response**: We agree with the reviewer and have modified the manuscript to include this information. Specifically, because non-informative censoring presents a possible limitation for our approach, we have added the following text to Section 5.2:

"The validity of the Cox partial likelihood function depends on an assumption of non-informative censoring (*i.e.*, true survival time and censoring time are independent given the predictors). Thus, the oblique RSF may be improved by incorporating methods to account for informative censoring prior to identifying a linear combination of variables."

2.	For the simulations proposed in Section 3.2.3, the authors use the simsurv package. The underlying data generating model was not included so it is unclear how exactly the data were simulated. More clarity on the data generation procedure would be appreciated. I am guessing that the authors generated data under a PH model. However, it would be advantageous to see the performance of aosrf under data generated under a non-PH model.

**Response**: Thank you for noticing this. We have clarified the sentence in Section 3.2.3 so that the underlying model is clear. In the updated paper, we write:

"A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package from a Weibull distribution"

We agree that a scenario where the PH assumption does not hold is interesting. In our prior paper introducing the original oblique RSF (PMC9875945), scenario C in our simulation was designed to investigate the prediction accuracy of oblique RSFs when the PH assumption was not valid. We found that the oblique RSF did well in this scenario (see Table 1 of PMC9875945), and thus we did not replicate the non-PH scenario in our current paper.

3.	It would be good to see how the various methods perform under high censoring, especially since several of the datasets that are included have censoring > 80%.

**Response**: We agree that this is an important consideration.

```{r, eval=FALSE}

R.utils::sourceDirectory("R")

tar_load(bm_pred_clean)
tar_load(data_key)
tar_load(model_key)

data <- bm_pred_clean$data %>% 
  left_join(data_key) %>% 
  filter(pcens >= 0.80)

figs <- bench_pred_visualize(data,
                             data_key,
                             model_key)

figs$ibs_scaled

figs$cstat

```

Reviewer: 2

Comments to the Author

1. Lines 42-49 on page 6: I would like to request further clarification on the process for obtaining linear combinations of predictor variables through the use of Newton-Raphson scoring.

**Response**:

2. Equation in line 13 on page 7,  I have some doubts as to whether the sign on the right-hand side should be negative (positive in Fisher scoring with the information matrix). Furthermore, it may be better to bold the beta symbol in the equation to be consistent with the previous formula.

**Response**:

Associate Editor's Comments to the Author:

This paper improves the computational efficiency and interpretation of oblique random survival forests (RSFs). The paper is clearly written. The numerical experiments are exceptionally well-planned, executed, and presented. Two reviewers' and below comments (mostly minor) need to be addressed.

1. The package associated with this manuscript, aorsf, is one of the supported engines by tidymodels (https://urldefense.com/v3/__https://parsnip.tidymodels.org/reference/details_rand_forest_aorsf.html__;!!GA8Xfdg!yI2a4uGp0KH2vYEOZyxWCuA5MK9PUwHaWFlkvdEAr73zIbT1eicot7N-Mj6CaKHRP3OUkh030vi3ORph5zQfVgCSRYXfHA$ ) and is widely used. This paper has potentially high impact.

**Response**:

2. The numerical experiments are extensive and well-planned. They set a high standard for JCGS articles. It boasts 21 data sets with a total of 35 learning tasks. Performances of learners are compared using the Bayesian linear mixed model.

**Response**:

3. Conceptually, how does oblique RSF compare to first creating linear (PCA, PLS) and nonlinear features (UMP) and then applying standard axis RSF? Authors don't need to make extra comparisons. A brief explanation suffices.

**Response**:

4. page 7, line 13: What are the $U$ and $H$ functions? Score and Hessian? Please define.

**Response**:

5. page 7, line 23 and footnote: $x \hat \beta$ should be $x^T \beta$.

**Response**:

6. Page 12, line 2: `number and density of layers` means `number and width of layers` or `number and dropout rates of layers`?

**Response**:

7. For boosting, is the learning rate tuned? How are the neural networks tuned (depth and width of layers, drop out rate, etc)?

**Response**:

8. In general, the paper lacks details on how several competing learning methods are tuned. For reproducibility, (1) how the data sets are retrieved and pre-processed and (2) the code and script for numerical experiments need to be made public.

**Response**:

9. Please briefly explain what nested cross-validation is.

**Response**:

### 2023-05-16 paper/jcgs/reviewer-response/reviewer-response.md
R1 updates

--- 2023-05-16 paper/jcgs/reviewer-response/reviewer-response.Rmd
@@
 
-"The validity of the Cox partial likelihood function depends on an assumption of non-informative censoring (*i.e.*, true survival time and censoring time are independent given the predictors).
+> "The validity of the Cox partial likelihood function depends on an assumption of non-informative censoring (*i.e.*, true survival time and censoring time are independent given the predictors).
 Thus, the oblique RSF may be improved by incorporating methods to account for informative censoring prior to identifying a linear combination of variables."
@@
 
-**Response**: Thank you for noticing this. We have clarified the sentence in Section 3.2.3 so that the underlying model is clear. In the updated paper, we write:
-
-"A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package from a Weibull distribution"
-
-We agree that a scenario where the PH assumption does not hold is interesting.
-In our prior paper introducing the original oblique RSF (PMC9875945), scenario C in our simulation was designed to investigate the prediction accuracy of oblique RSFs when the PH assumption was not valid.
-We found that the oblique RSF did well in this scenario (see Table 1 of PMC9875945), and thus we did not replicate the non-PH scenario in our current paper.
+**Response**:
 
@@
 
-**Response**: We agree that this is an important consideration.
-
-```{r, eval=FALSE}
-
-R.utils::sourceDirectory("R")
-
-tar_load(bm_pred_clean)
-tar_load(data_key)
-tar_load(model_key)
-
-data <- bm_pred_clean$data %>% 
-  left_join(data_key) %>% 
-  filter(pcens >= 0.80)
-
-figs <- bench_pred_visualize(data,
-                             data_key,
-                             model_key)
-
-figs$ibs_scaled
-
-figs$cstat
-
-```
+**Response**:
 

### 2023-05-16 paper/jcgs/main.Rnw
R1 updates

@@
 Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
-A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package \citep{simsurv, simsurv_paper}.
+A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package \citep{simsurv, simsurv_paper} from a Weibull distribution.
 The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
@@
 While the current study advances the oblique RSF towards being scalable and interpretable, there remain several limitations that can be targeted in future studies.
+The validity of the Cox partial likelihood function depends on an assumption of non-informative censoring (\ie, true survival time and censoring time are independent given the predictors).
+Thus, the oblique RSF may be improved by incorporating methods to account for informative censoring prior to identifying a linear combination of variables \citet{cui2017consistency}.
 The accelerated oblique RSF does not account for competing risks, and biased estimation of incidence may occur when competing risks are ignored.

### 2023-05-16 paper/jcgs/main.tex
R1 updates

--- 2022-11-23 paper/jcgs/main.tex
@@
 Our technique to accelerate the oblique RSF reduces the number of operations required to find linear combinations of inputs using a single iteration of Newton Raphson scoring, while our VI technique directly engages with coefficients in linear combinations of inputs to measure importance of individual variables.
-In numeric experiments, we found that that \texttt{aorsf-fast} is approximately 1,291.6 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
+In numeric experiments, we found that \texttt{aorsf-fast} is approximately 1,291.6 times faster than its predecessor, \texttt{obliqueRSF-net}, with a practically equivalent C-statistic.
 We also found that negation VI, a technique to estimate VI using the oblique RSF, detected non-linear, combination, and main effects more effectively than three standard methods to estimate VI: permutation, ANOVA, and SHAP VI.

### 2023-05-25 paper/jcgs/reviewer-response/reviewer-response.Rmd
R2 and AE updates

@@
 ---
-title: "Hypertension statistics for US adults: an open-source web application for analysis and visualization of US NHANES data"
+title: "Accelerated and interpretable oblique random survival forests:"
+subtitle: "Response to reviewers"
 always_allow_html: true
@@
 
-Reviewer: 1
+```{r, echo=FALSE, include=FALSE}
+knitr::opts_chunk$set(echo=FALSE,
+                      fig.width = 6,
+                      fig.height = 8)
+```
 
-Comments to the Author
+<br/>
+<br/>
+
+We thank the reviewers and associate editor for their thoughtful and helpful comments. Below we provide a point-by-point response to each of their comments.
+
+<br/>
+
+## Reviewer 1 Comments to the Author
 
@@
 
-"A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package from a Weibull distribution"
+"A time-to-event outcome with roughly 45\% of observations censored was generated using the `simsurv` package from a Weibull distribution"
 
@@
 **Response**: We agree that this is an important consideration.
+Figures 1 and 2 examine our learning algorithms only in the datasets with at least 80% censoring, and the results are similar to our main analysis.
+Due to space constraints, we have not included these results in our revision.
 
@@
                              data_key,
-                             model_key)
+                             model_key,
+                             ymax_scale_ibs = 3)
 
-figs$ibs_scaled
+ggsave(filename = 'reviewer_1_item_3a.png',
+       plot = figs$ibs_scaled$fig, 
+       device = 'png', 
+       width = 6, 
+       height = 8, 
+       dpi = 300,
+       path = file.path(here::here(), 
+                        'paper',
+                        'jcgs', 
+                        'reviewer-response'))
 
-figs$cstat
+ggsave(filename = 'reviewer_1_item_3b.png',
+       plot = figs$cstat$fig, 
+       device = 'png', 
+       width = 6, 
+       height = 8, 
+       dpi = 300,
+       path = file.path(here::here(), 
+                        'paper',
+                        'jcgs', 
+                        'reviewer-response'))
 
@@
 
-Reviewer: 2
+**Figure 1**: Index of prediction accuracy in risk prediction tasks with censoring of 80% or higher.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest score, showing absolute and relative improvement over the second best learner.
 
-Comments to the Author
+```{r}
+knitr::include_graphics("reviewer_1_item_3a.png")
+```
+
+**Figure 2**: Time-dependent concordance statistic in risk prediction tasks with censoring of 80% or higher.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest score, showing absolute and relative improvement over the second best learner.
+
+```{r}
+knitr::include_graphics("reviewer_1_item_3b.png")
+```
+
+## Reviewer 2 Comments to the Author
 
@@
 
-**Response**:
+**Response**: In each non-leaf node, the process for obtaining a linear combination of predictors is as follows:
+
+*Step 1*. Identify a random subset of `mtry` predictors.
+
+*Step 2*. Apply Newton-Raphson scoring to estimate ${\mathbf{\beta}}$ as in Equation (1), using all predictors from Step 1.
+
+*Step 3*.
+Create the linear combination of variables using the $\mathbf{\beta}$ estimate from Step 2., i.e., $$\mathbf{\eta} = \hat{\beta}_1 \cdot \mathbf{x}_1 + \ldots + \hat{\beta}_{\text{mtry}} \cdot \mathbf{x}_{\text{mtry}}.$$
+
+*Step 4*. Identify a cut-point for $\mathbf{\eta}$ that maximizes a splitting criterion.
+
+We have added the following text to the first paragraph of page 7 in the revised manuscript to clarify Step 3:
+
+"After obtaining $\hat{\mathbf{\beta}}$, a linear combination of variables, $\eta$, can be obtained by computing $\eta = \mathbf{x}^T \hat{\mathbf{\beta}}$"
+
+This clarification is also included in line 14 of Algorithm 1 of the revised manuscript.
 
@@
 
-**Response**:
+**Response**: Thank you for noticing these details.
+We have updated this equation to match the terms given in Equation 3.8 in "Modeling Survival Data: Extending the Cox Model" By Terry M.
+Therneau and  Patricia M.
+Grambsch.
+Specifically, in the revised manuscript, we write:
 
-Associate Editor's Comments to the Author:
+"As described in Therneau and Grambsch (2000), a vector of estimated regression coefficients, $\hat{\mathbf{\beta}}$, is updated in each step of the procedure: $$\hat{\mathbf{\beta}}^{k+1} =  \hat{\mathbf{\beta}}^{k} + U(\hat{\mathbf{\beta}} = \hat{\mathbf{\beta}}^{k})\, \mathcal{I}^{-1}(\hat{\mathbf{\beta}} = \hat{\mathbf{\beta}}^{k}),$$ where $U(\hat{\mathbf{\beta}})$ is the score vector and $\mathcal{I}^{-1}(\hat{\mathbf{\beta}})$ is the inverse of the observed information matrix."
+
+We have also written $\mathbf{\beta}$ in bold throughout the revised manuscript.
+
+## Associate Editor's Comments to the Author:
 
@@
 This paper has potentially high impact.
-
-**Response**:
-
-2.
 The numerical experiments are extensive and well-planned.
@@
 
-**Response**:
+**Response**: Thank you!
 
-3.
+2.
 Conceptually, how does oblique RSF compare to first creating linear (PCA, PLS) and nonlinear features (UMP) and then applying standard axis RSF?
@@
 
-**Response**:
+**Response**: This is an important distinction and we have incorporated it into the Introduction of the revised manuscript:
 
-4. page 7, line 13: What are the $U$ and $H$ functions? Score and Hessian? Please define.
+"Conceptually, oblique trees are similar to methods that use covariate rotation or extension to generate linear combinations of predictors prior to growing axis-based trees (Zhou et al., 2016; Wang and Zhou, 2017).
+The difference is that oblique trees generate linear combinations of predictors within each non-leaf node, using only the data and predictors associated with that node, instead of generating the linear combinations prior to growing the tree.
+This ``node-specific'' approach to creating linear combinations of predictors leads to greater diversity in oblique tree ensembles, which may lead to greater prediction accuracy Breiman (2001)."
 
-**Response**:
+3. page 7, line 13: What are the $U$ and $H$ functions? Score and Hessian? Please define.
 
-5. page 7, line 23 and footnote: $x \hat \beta$ should be $x^T \beta$.
+**Response**: We have clarified $U$ and $H$ (see response to comment \#2 from Reviewer \#2)
 
-**Response**:
+4. page 7, line 23 and footnote: $x \hat \beta$ should be $x^T \beta$.
 
-6. Page 12, line 2: `number and density of layers` means `number and width of layers` or `number and dropout rates of layers`?
+**Response**: We have updated the text and footnote to correctly reflect that $x$ is transposed.
+We retained the hat over $\beta$ for consistency with our definition of $U(\hat{\beta})$ and $H(\hat{\beta})$ defined above.
 
-**Response**:
+5. Page 12, line 2: `number and density of layers` means `number and width of layers` or `number and dropout rates of layers`?
 
-7. For boosting, is the learning rate tuned? How are the neural networks tuned (depth and width of layers, drop out rate, etc)?
+**Response**: We have updated this sentence to provide more clarity and detail on how we tuned neural networks: "For neural networks, the number of layers (*i.e.*, length) and number of nodes in the layers (*i.e.*, width) was tuned, while dropout rate was fixed at 10\%, batch size was fixed at 32 observations, and the rectified linear unit activation function was applied.
+In addition, neural networks completed a maximum of 500 epochs, with possible early stopping based on prediction accuracy in a validation set comprising 25\% of its training data."
 
-**Response**:
+6. For boosting, is the learning rate tuned? How are the neural networks tuned (depth and width of layers, drop out rate, etc)?
 
-8.
+**Response**: We have updated our description of tuning for neural networks (see previous response) and boosting.
+Our updated text for boosting is as follows: "Specifically, tuning for boosting models included identifying the number of steps to complete.
+The maximum number of steps was 5000, the learning rate was fixed at 0.01, and early stopping was applied if there was no improvement in cross-validated negative log-likelihood for 25 steps."
+
+7.
 In general, the paper lacks details on how several competing learning methods are tuned.
@@
 
-**Response**:
+**Response**: We have included more detail in the text regarding tuning of the competing learners (see response to comment 5 and 6), and have included details regarding tuning of competing learners in the 'Description' column of Table 1.
+We have included details on how each data set was retrieved and pre-processed in the 'Data Sources' section of the Appendix.
+We have made the code and script for numerical experiments publicly available at https://github.com/bcjaeger/aorsf-bench.
+In particular,
 
-9. Please briefly explain what nested cross-validation is.
+- data pre-processing code can be found here: https://github.com/bcjaeger/aorsf-bench/blob/main/R/data_load.R
 
-**Response**:
+- code for tuning of competing learners can be found here: https://github.com/bcjaeger/aorsf-bench/blob/main/R/model_fit.R
+
+8. Please briefly explain what nested cross-validation is.
+
+**Response**: We have included a brief explanation in the update: "Nested cross-validation includes an 'inner' cross-validation loop to evaluate different specifications of tuning parameters and an 'outer' loop that evaluates the tuned model, providing an unbiased estimate of the underlying model and its tuning procedure"

### 2023-05-25 paper/jcgs/reviewer-response/reviewer-response.md
R2 and AE updates

--- 2023-05-16 paper/jcgs/reviewer-response/reviewer-response.Rmd
@@
 
-Reviewer: 1
+<br/>
+<br/>
 
-Comments to the Author
+We thank the reviewers and associate editor for their thoughtful and helpful comments. Below we provide a point-by-point response to each of their comments.
+
+<br/>
+
+## Reviewer 1 Comments to the Author
 
@@
 **Response**: We agree that this is an important consideration.
+Figures 1 and 2 examine our learning algorithms only in the datasets with at least 80% censoring, and the results are similar to our main analysis.
+Due to space constraints, we have not included these results in our revision.
 
-```{r, eval=FALSE}
+**Figure 1**: Index of prediction accuracy in risk prediction tasks with censoring of 80% or higher.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest score, showing absolute and relative improvement over the second best learner.
 
-R.utils::sourceDirectory("R")
-
-tar_load(bm_pred_clean)
-tar_load(data_key)
-tar_load(model_key)
-
-data <- bm_pred_clean$data %>% 
-  left_join(data_key) %>% 
-  filter(pcens >= 0.80)
-
-figs <- bench_pred_visualize(data,
-                             data_key,
-                             model_key)
-
-figs$ibs_scaled
-
-figs$cstat
-
+```{=openxml}
+<w:p><w:pPr><w:jc w:val="center"/><w:pStyle w:val="Figure"/></w:pPr><w:r><w:rPr/><w:drawing xmlns:r="http://schemas.openxmlformats.org/officeDocument/2006/relationships"><wp:inline distT="0" distB="0" distL="0" distR="0"><wp:extent cx="5486400" cy="7315200"/><wp:docPr id="" name="" descr=""/><wp:cNvGraphicFramePr><a:graphicFrameLocks xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main" noChangeAspect="1"/></wp:cNvGraphicFramePr><a:graphic xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main"><a:graphicData uri="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:pic xmlns:pic="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:nvPicPr><pic:cNvPr id="" name=""/><pic:cNvPicPr><a:picLocks noChangeAspect="1" noChangeArrowheads="1"/></pic:cNvPicPr></pic:nvPicPr><pic:blipFill><a:blip cstate="print" r:embed="C:\Users\bjaeger\AppData\Local\Temp\RtmpKusyHF\file7834640464bb.png"/><a:stretch><a:fillRect/></a:stretch></pic:blipFill><pic:spPr bwMode="auto"><a:xfrm><a:off x="0" y="0"/><a:ext cx="76200" cy="101600"/></a:xfrm><a:prstGeom prst="rect"><a:avLst/></a:prstGeom><a:noFill/></pic:spPr></pic:pic></a:graphicData></a:graphic></wp:inline></w:drawing></w:r></w:p>
 ```
 
-Reviewer: 2
+**Figure 2**: Time-dependent concordance statistic in risk prediction tasks with censoring of 80% or higher.
+Text appears in tasks where the accelerated oblique random survival forest obtained the highest score, showing absolute and relative improvement over the second best learner.
 
-Comments to the Author
+```{=openxml}
+<w:p><w:pPr><w:jc w:val="center"/><w:pStyle w:val="Figure"/></w:pPr><w:r><w:rPr/><w:drawing xmlns:r="http://schemas.openxmlformats.org/officeDocument/2006/relationships"><wp:inline distT="0" distB="0" distL="0" distR="0"><wp:extent cx="5486400" cy="7315200"/><wp:docPr id="" name="" descr=""/><wp:cNvGraphicFramePr><a:graphicFrameLocks xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main" noChangeAspect="1"/></wp:cNvGraphicFramePr><a:graphic xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main"><a:graphicData uri="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:pic xmlns:pic="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:nvPicPr><pic:cNvPr id="" name=""/><pic:cNvPicPr><a:picLocks noChangeAspect="1" noChangeArrowheads="1"/></pic:cNvPicPr></pic:nvPicPr><pic:blipFill><a:blip cstate="print" r:embed="C:\Users\bjaeger\AppData\Local\Temp\RtmpKusyHF\file78341ecb6257.png"/><a:stretch><a:fillRect/></a:stretch></pic:blipFill><pic:spPr bwMode="auto"><a:xfrm><a:off x="0" y="0"/><a:ext cx="76200" cy="101600"/></a:xfrm><a:prstGeom prst="rect"><a:avLst/></a:prstGeom><a:noFill/></pic:spPr></pic:pic></a:graphicData></a:graphic></wp:inline></w:drawing></w:r></w:p>
+```
+
+## Reviewer 2 Comments to the Author
 

### 2023-05-25 paper/jcgs/main.Rnw
R2 and AE updates

@@
 
-p3 <- ggarrange(tag_facet(p1, tag_pool = "A", vjust = 2.5),
+ggarrange(tag_facet(p1, tag_pool = "A", vjust = 2.5),
           tag_facet(p2, tag_pool = "B", vjust = 2.5),
@@
 
-p3
-
-@
+@
+
+Conceptually, oblique trees are similar to methods that use covariate rotation or extension to generate linear combinations of predictors prior to growing axis-based trees \citep{zhou2016random, wang2017random}.
+The difference is that oblique trees generate linear combinations of predictors within each non-leaf node, using only the data and predictors associated with that node, instead of generating the linear combinations prior to growing the tree.
+This ``node-specific'' approach to creating linear combinations of predictors leads to greater diversity in oblique tree ensembles, which may lead to greater prediction accuracy \citep{breiman2001random}.
 
@@
 Newton Raphson scoring is an exceptionally fast estimation procedure, and the \texttt{survival} package \citep{survival} includes documentation that outlines how to efficiently program it \citep{therneau_survival_2022}.
-Briefly, a vector of length \texttt{mtry} (\ie, the number of randomly selected predictors) with estimated regression coefficients, $\hat{\beta}$, is updated in each step of the procedure based on its first derivative, $U(\hat{\beta})$, and second derivative, $H(\hat{\beta})$:
-$$ \hat{\beta}^{k+1} =  \hat{\beta}^{k} + U(\hat{\beta} = \hat{\beta}^{k})\, H^{-1}(\hat{\beta} = \hat{\beta}^{k}) $$
-
-For statistical inference, it is recommended to continue updating $\hat{\beta}$ by completing additional iterations of Newton Raphson scoring until a convergence threshold is met.
-However, since an estimate of $\hat{\beta}$ is created by the first iteration of Newton Raphson scoring, only one iteration of Newton Raphson scoring is needed to identify a valid linear combination of predictors.
-Moreover, computing $U$ and $H$ requires computation and exponentiation of the vector $\bm{x}\hat{\beta}$, but these steps can be skipped on the first iteration of Newton Raphson scoring if an initial value of $\hat{\beta} = 0$ is chosen, allowing for a reduction in computing operations and removing the need to scale predictor values prior to initiating the Newton Raphson algorithm.\footnote{Predictors are scaled prior to initiating the Newton Raphson algorithm to avoid exponentiation of large numbers.
-However, if only one iteration is completed with an initial value of 0 for $\hat{\beta}$, then $\exp(\bm{x}\hat{\beta}) = 1$.} In \secref{sec:results_pred}, we formally test whether growing oblique survival trees using one iteration of Newton Raphson scoring provides equivalent prediction accuracy compared to trees where iterations are completed until a convergence threshold is met.
+As described in \cite{therneau2000cox}, a vector of estimated regression coefficients, $\hat{\bm{\beta}}$, is updated in each step of the procedure: $$\hat{\bm{\beta}}^{k+1} =  \hat{\bm{\beta}}^{k} + U(\hat{\bm{\beta}} = \hat{\bm{\beta}}^{k})\, \mathcal{I}^{-1}(\hat{\bm{\beta}} = \hat{\bm{\beta}}^{k}),$$ where $U(\hat{\bm{\beta}})$ is the score vector and $\mathcal{I}^{-1}(\hat{\bm{\beta}})$ is the inverse of the observed information matrix.
+After obtaining $\hat{\bm\beta}$, a linear combination of variables, $\eta$, is obtained by computing $\eta = \bm{x}^T \hat{\bm{\beta}}$.
+
+For statistical inference, it is recommended to continue updating $\hat{\bm{\beta}}$ by completing additional iterations of Newton Raphson scoring until a convergence threshold is met.
+However, since an estimate of $\hat{\bm{\beta}}$ is created by the first iteration of Newton Raphson scoring, only one iteration of Newton Raphson scoring is needed to identify a valid linear combination of predictors.
+In \secref{sec:results_pred}, we formally test whether growing oblique survival trees using one iteration of Newton Raphson scoring provides equivalent prediction accuracy compared to trees where iterations are completed until a convergence threshold is met.
 
@@
        \State $\beta \gets \text{newt\_raph}(\dataset_{\text{node}},\, \text{weights} = \text{subset}(w, \text{node\_rows}),\, \text{max\_iter} = 1)$
-       \State $\eta \gets \bm{x}_{\text{node}} \times \beta$
+       \State $\eta \gets \bm{x}^T_{\text{node}} \times \beta$
        \State $\mathcal{C} \gets \text{sample}(\text{from} = \text{unique}(\eta),\, \text{size} = \text{n\_split},\,\text{replace} = \text{F})$
@@
 For boosting, regression, and neural network learners, nested cross-validation was applied to tune relevant model parameters.
+Nested cross-validation includes an `inner' cross-validation loop to evaluate different specifications of tuning parameters and an `outer' loop that evaluates the tuned model, providing an unbiased estimate of the underlying model and its tuning procedure.
 Specifically, tuning for boosting models included identifying the number of steps to complete.
+The maximum number of steps was 5000, the learning rate was fixed at 0.01, and early stopping was applied if there was no improvement in cross-validated negative log-likelihood for 25 steps.
 For regression models, tuning was used to identify the magnitude of penalization.
-For neural networks, the number and density of layers was tuned.
+For neural networks, the number of layers (\ie, length) and number of nodes in the layers (\ie, width) was tuned, while dropout rate was fixed at 10\%, batch size was fixed at 32 observations, and the rectified linear unit activation function was applied.
+In addition, neural networks completed a maximum of 500 epochs, with possible early stopping based on prediction accuracy in a validation set comprising 25\% of its training data..
 
@@
       'BioLINCC',
-      paste0('the \\texttt{', rpack, '} R package \\citep{', rpack, '}'))
+      paste0('the \\texttt{', rpack, '} R package \\citep{', rpack, '}')),
+    preproc = if_else(
+      preproc == 'none',
+      "No relevant pre-processing steps were taken",
+      paste0("In pre-processing steps, ", preproc)
+    )
   ) %>%
-  glue_data(" \\item The ``{label}'' data \\citep{{{cite}}} were obtained from {source}") %>%
+  glue_data(" \\item The ``{label}'' data \\citep{{{cite}}} were obtained from {source}. {preproc}") %>%
   unique() %>%

### 2023-05-25 paper/jcgs/main.tex
R2 and AE updates

@@
 \includegraphics[width=\maxwidth]{figure/axis_v_oblique-1} \caption[Decision boundaries from an axis based (panel A) and oblique (panel B) decision tree used to classify penguin species based on bill depth and bill length]{Decision boundaries from an axis based (panel A) and oblique (panel B) decision tree used to classify penguin species based on bill depth and bill length.
-The decision boundary from the oblique tree is better able to capture the geometry of this data, leading to fewer mis-classified penguins.}\label{fig:axis_v_oblique-1}
+The decision boundary from the oblique tree is better able to capture the geometry of this data, leading to fewer mis-classified penguins.}\label{fig:axis_v_oblique}
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=\maxwidth]{figure/axis_v_oblique-2} \caption[Decision boundaries from an axis based (panel A) and oblique (panel B) decision tree used to classify penguin species based on bill depth and bill length]{Decision boundaries from an axis based (panel A) and oblique (panel B) decision tree used to classify penguin species based on bill depth and bill length.
-The decision boundary from the oblique tree is better able to capture the geometry of this data, leading to fewer mis-classified penguins.}\label{fig:axis_v_oblique-2}
-\end{figure}
-
 \end{knitrout}
+
+Conceptually, oblique trees are similar to methods that use covariate rotation or extension to generate linear combinations of predictors prior to growing axis-based trees \citep{zhou2016random, wang2017random}.
+The difference is that oblique trees generate linear combinations of predictors within each non-leaf node, using only the data and predictors associated with that node, instead of generating the linear combinations prior to growing the tree.
+This ``node-specific'' approach to creating linear combinations of predictors leads to greater diversity in oblique tree ensembles, which may lead to greater prediction accuracy \citep{breiman2001random}.
 
@@
  \item The ``VA lung cancer trial'' data \citep{kalbfleisch2011statistical} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}.
+No relevant pre-processing steps were taken.
  \item The ``Colon cancer'' data \citep{moertel1995fluorouracil} were obtained from the \texttt{survival} R package \citep{survival}.
- \item The ``Primary biliary cholangitis'' data \citep{therneau2000cox} were obtained from the \texttt{aorsf} R package \citep{aorsf}. 
+In pre-processing steps, the predictor, node4, which is an indicator for having more than 4 positive lymph nodes, was dropped, while the nodes predictor, which indicates the number of positive lymph nodes, was retained.
+ \item The ``Primary biliary cholangitis'' data \citep{therneau2000cox} were obtained from the \texttt{aorsf} R package \citep{aorsf}. No relevant pre-processing steps were taken. 
  \item The ``Movies released in 2015-2018'' data  were obtained from the \texttt{censored} R package \citep{censored}.
- \item The ``GBSG II'' data \citep{schumacher1994rauschecker} were obtained from the \texttt{TH.data} R package \citep{TH.data}. 
- \item The ``Systolic Heart Failure'' data \citep{hsich2011identifying} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
+In pre-processing steps, text and date variables (movie title, release date, and distributor) were dropped..
+ \item The ``GBSG II'' data \citep{schumacher1994rauschecker} were obtained from the \texttt{TH.data} R package \citep{TH.data}. No relevant pre-processing steps were taken. 
+ \item The ``Systolic Heart Failure'' data \citep{hsich2011identifying} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. No relevant pre-processing steps were taken. 
  \item The ``Serum free light chain'' data \citep{dispenzieri2012use, kyle2006prevalence} were obtained from the \texttt{survival} R package \citep{survival}.
+In pre-processing steps, the chapter variable, which indicates death status, was removed, since death was the outcome.
+Outcomes occurring on day 0 were assumed to have a time of 1/2 day rather than 0 days.
  \item The ``Non-alcohol fatty liver disease'' data \citep{allen2018nonalcoholic} were obtained from the \texttt{survival} R package \citep{survival}.
- \item The ``Rotterdam tumor bank'' data \citep{royston2013external} were obtained from the \texttt{survival} R package \citep{survival}. 
- \item The ``ACTG 320'' data \citep{hosmer2002applied} were obtained from the \texttt{mlr3proba} R package \citep{mlr3proba}. 
+In pre-processing steps, data from before or on the index data were used as predictors.
+The mean value prior to the index date for lab values in nafld2 was used as a predictor, and the number of days between the most recent lab test and the index date was also used as a predictor.
+ \item The ``Rotterdam tumor bank'' data \citep{royston2013external} were obtained from the \texttt{survival} R package \citep{survival}. No relevant pre-processing steps were taken. 
+ \item The ``ACTG 320'' data \citep{hosmer2002applied} were obtained from the \texttt{mlr3proba} R package \citep{mlr3proba}. In pre-processing steps, redundant predictors were dropped. 
  \item The ``GUIDE-IT'' data \citep{felker2017effect} were obtained from BioLINCC.
+In pre-processing steps, baseline data including biomarkers, questionnaires, and randomized group were included as predictors.
  \item The ``Early breast cancer'' data \citep{desmedt2011multifactorial, hatzis2011genomic, ternes2017identification} were obtained from the \texttt{biospear} R package \citep{biospear}.
+No relevant pre-processing steps were taken.
  \item The ``SPRINT'' data \citep{sprint2015randomized} were obtained from BioLINCC.
- \item The ``NKI 70 gene signature'' data \citep{van2002gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}. 
+In pre-processing steps, baseline data including biomarkers, cognitive questionnaires, medications, and randomization group were included as predictors.
+Predictors with over 40 percent missing data were dropped.
+Zero variance predictors were also dropped.
+ \item The ``NKI 70 gene signature'' data \citep{van2002gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}. No relevant pre-processing steps were taken. 
  \item The ``Lung cancer'' data \citep{director2008gene} were obtained from the \texttt{OpenML} R package \citep{OpenML}.
+In pre-processing steps, status was transformed to have values of 0 and 1 instead of 1 and 2.
  \item The ``NCCTG Lung Cancer'' data \citep{loprinzi1994prospective} were obtained from the \texttt{survival} R package \citep{survival}.
- \item The ``FCL'' data \citep{pintilie2006competing} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. 
- \item The ``Monoclonal gammopathy'' data \citep{kyle2002long} were obtained from the \texttt{survival} R package \citep{survival}. 
+In pre-processing steps, institution code was not used as a predictor, and values of both sex and event status were transformed to be 0 and 1 instead of 1 and 2.
+ \item The ``FCL'' data \citep{pintilie2006competing} were obtained from the \texttt{randomForestSRC} R package \citep{randomForestSRC}. No relevant pre-processing steps were taken. 
+ \item The ``Monoclonal gammopathy'' data \citep{kyle2002long} were obtained from the \texttt{survival} R package \citep{survival}. No relevant pre-processing steps were taken. 
  \item The ``MESA'' data \citep{bild2002multi} were obtained from BioLINCC.
+In pre-processing steps, visit 1 data including biomarkers, health behaviors, and comorbidities were included as predictors.
  \item The ``ARIC'' data \citep{aric1989atherosclerosis} were obtained from BioLINCC.
+In pre-processing steps, visit 1 data including biomarkers, health behaviors, and comorbidities were included as predictors.
  \item The ``JHS'' data \citep{taylor2005toward} were obtained from BioLINCC.
+In pre-processing steps, visit 1 data including biomarkers, health behaviors, neighborhood characteristics, and comorbidities were included as predictors.
 

### 2023-05-25 R/bench_pred_visualize.R

@@ -4,7 +4,9 @@ perc_diff <- function(a,b){
 
 bench_pred_visualize <- function(bm_pred_clean,
                                  data_key,
-                                 model_key){
+                                 model_key,
+                                 ymax_scale_ibs = 1.15,
+                                 ymax_scale_cstat = 1.15){
 
 
   data_recoder <- data_key |>
@@ -23,7 +25,8 @@ bench_pred_visualize <- function(bm_pred_clean,
       y_col_1 = -0.4,
       y_min = 0,
       y_breaks = seq(0, .6, by = .1),
-      eval_label = 'Index of Prediction Accuracy'
+      eval_label = 'Index of Prediction Accuracy',
+      ymax_scale = ymax_scale_ibs
     ),
     cstat = bench_pred_visualize_(
       filter(bm_pred_clean, data != 'sim'),
@@ -34,7 +37,8 @@ bench_pred_visualize <- function(bm_pred_clean,
       y_col_1 = 0.35,
       y_min = .55,
       y_breaks = seq(.7, 1, by = .1),
-      eval_label = 'C-statistic'
+      eval_label = 'C-statistic',
+      ymax_scale = ymax_scale_cstat
     )
   )
 
@@ -50,7 +54,8 @@ bench_pred_visualize_ <- function(
     y_col_1 = -0.4,
     y_min = 0,
     y_breaks = seq(0, .6, by = .1),
-    eval_label = 'Index of Prediction Accuracy'
+    eval_label = 'Index of Prediction Accuracy',
+    ymax_scale = 1.15
 ){
 
   bm_pred_inner <- bm_pred_clean |>
@@ -229,7 +234,7 @@ bench_pred_visualize_ <- function(
           axis.text.y = element_blank(),
           legend.position = '') +
     scale_fill_manual(values = oranges) +
-    scale_y_continuous(limits = c(y_col_1, max(data_fig$eval)*1.15),
+    scale_y_continuous(limits = c(y_col_1, max(data_fig$eval)*ymax_scale),
                        expand = c(0, 0),
                        breaks = y_breaks,
                        labels = function(x) x * 100) +

### 2023-05-25 R/nafld_build.R

@@ -1,4 +1,7 @@
 
+# this function creates the nafld data. It takes awhile to run, so I
+# found it more convenient to save the output in a flat file and then
+# read that file into R whenever the nafld data were needed.
 
 nafld_build <- function(){
 

### 2023-05-25 R/summarize_data_source.R

@@ -115,6 +115,48 @@ summarize_data_source <- function(analyses_real) {
         "jhs_stroke" = NA_character_,
         "jhs_chd" = NA_character_
       ),
+      preproc = recode(
+        data,
+        "accord_acm" = "baseline data including biomarkers, questionnaires, and medications were included as predictors. Outcomes occuring the same day as the baseline examination were given a time value of 1/2 day rather than 0 days",
+        "accord_cvd" = "baseline data including biomarkers, questionnaires, and medications were included as predictors. Outcomes occuring the same day as the baseline examination were given a time value of 1/2 day rather than 0 days",
+        "actg_death" = "redundant predictors were dropped",
+        "actg_aids"  = "redundant predictors were dropped",
+        "breast" = "none",
+        "colon_acm" = "the predictor, node4, which is an indicator for having more than 4 positive lymph nodes, was dropped, while the nodes predictor, which indicates the number of positive lymph nodes, was retained",
+        "colon_recur" = "the predictor, node4, which is an indicator for having more than 4 positive lymph nodes, was dropped, while the nodes predictor, which indicates the number of positive lymph nodes, was retained",
+        "flchain" = "the chapter variable, which indicates death status, was removed, since death was the outcome. Outcomes occurring on day 0 were assumed to have a time of 1/2 day rather than 0 days",
+        "follic_death" = "none",
+        "follic_relapse" = "none",
+        "gbsg2" = "none",
+        "guide_it_hfhosp" = "baseline data including biomarkers, questionnaires, and randomized group were included as predictors",
+        "guide_it_cvd" = "baseline data including biomarkers, questionnaires, and randomized group were included as predictors",
+        "mgus2_death" = "none",
+        "mgus2_pcm"   = "none",
+        "nafld" = "data from before or on the index data were used as predictors. The mean value prior to the index date for lab values in nafld2 was used as a predictor, and the number of days between the most recent lab test and the index date was also used as a predictor",
+        "pbc_orsf" = "none",
+        "peakV02" = "none",
+        "phts" = "none",
+        "rotterdam_acm" = "none",
+        "rotterdam_recur" = "none",
+        "sprint_acm" = "baseline data including biomarkers, cognitive questionnaires, medications, and randomization group were included as predictors. Predictors with over 40 percent missing data were dropped. Zero variance predictors were also dropped",
[…]

### 2023-06-05 paper/jcgs/reviewer-response/reviewer-response.Rmd
NMP review incorporated

@@
 
-1.	The validity of the Cox partial likelihood function requires the non-informative censoring assumption (true survival time and censoring time are independent given the features X).
+**Comment 1**:	The validity of the Cox partial likelihood function requires the non-informative censoring assumption (true survival time and censoring time are independent given the features X).
 I did not see this explicitly stated as an assumption in Section 2.3.
@@
 
-2.	For the simulations proposed in Section 3.2.3, the authors use the simsurv package.
+**Comment 2**:	For the simulations proposed in Section 3.2.3, the authors use the simsurv package.
 The underlying data generating model was not included so it is unclear how exactly the data were simulated.
@@
 
-3.	It would be good to see how the various methods perform under high censoring, especially since several of the datasets that are included have censoring > 80%.
+**Comment 3**: It would be good to see how the various methods perform under high censoring, especially since several of the datasets that are included have censoring > 80%.
 
@@
 
-1. Lines 42-49 on page 6: I would like to request further clarification on the process for obtaining linear combinations of predictor variables through the use of Newton-Raphson scoring.
+**Comment 1**: Lines 42-49 on page 6: I would like to request further clarification on the process for obtaining linear combinations of predictor variables through the use of Newton-Raphson scoring.
 
@@
 
-We have added the following text to the first paragraph of page 7 in the revised manuscript to clarify Step 3:
+We have added the following text to page 7 of the revised manuscript clarifying Step 3:
 
@@
 
-2.
-Equation in line 13 on page 7,  I have some doubts as to whether the sign on the right-hand side should be negative (positive in Fisher scoring with the information matrix).
+**Comment 2**: Equation in line 13 on page 7,  I have some doubts as to whether the sign on the right-hand side should be negative (positive in Fisher scoring with the information matrix).
 Furthermore, it may be better to bold the beta symbol in the equation to be consistent with the previous formula.
 
-**Response**: Thank you for noticing these details.
+**Response**: Thank you for noticing this.
 We have updated this equation to match the terms given in Equation 3.8 in "Modeling Survival Data: Extending the Cox Model" By Terry M.
@@
 Grambsch.
-Specifically, in the revised manuscript, we write:
+Specifically, on page 7 of the revised manuscript, we write:
 
@@
 
-This paper improves the computational efficiency and interpretation of oblique random survival forests (RSFs).
+**Comment 1**: This paper improves the computational efficiency and interpretation of oblique random survival forests (RSFs).
 The paper is clearly written.
@@
 Two reviewers' and below comments (mostly minor) need to be addressed.
-
-1.
 The package associated with this manuscript, aorsf, is one of the supported engines by tidymodels (https://urldefense.com/v3/__https://parsnip.tidymodels.org/reference/details_rand_forest_aorsf.html__;!!GA8Xfdg!yI2a4uGp0KH2vYEOZyxWCuA5MK9PUwHaWFlkvdEAr73zIbT1eicot7N-Mj6CaKHRP3OUkh030vi3ORph5zQfVgCSRYXfHA$ ) and is widely used.
@@
 
-**Response**: Thank you!
+**Response**: Thank you! We appreciate your summary and review of our work.
 
-2.
-Conceptually, how does oblique RSF compare to first creating linear (PCA, PLS) and nonlinear features (UMP) and then applying standard axis RSF?
+**Comment 2**: Conceptually, how does oblique RSF compare to first creating linear (PCA, PLS) and nonlinear features (UMP) and then applying standard axis RSF?
 Authors don't need to make extra comparisons.
@@
 
-**Response**: This is an important distinction and we have incorporated it into the Introduction of the revised manuscript:
+**Response**: This is an important distinction and we have incorporated it into the Introduction (pages 3-4) of the revised manuscript:
 
@@
 The difference is that oblique trees generate linear combinations of predictors within each non-leaf node, using only the data and predictors associated with that node, instead of generating the linear combinations prior to growing the tree.
-This ``node-specific'' approach to creating linear combinations of predictors leads to greater diversity in oblique tree ensembles, which may lead to greater prediction accuracy Breiman (2001)."
+This "node-specific" approach to creating linear combinations of predictors leads to greater diversity in oblique tree ensembles, which may lead to greater prediction accuracy Breiman (2001)."
 
-3. page 7, line 13: What are the $U$ and $H$ functions? Score and Hessian? Please define.
+**Comment 3**: page 7, line 13: What are the $U$ and $H$ functions? Score and Hessian? Please define.
 
-**Response**: We have clarified $U$ and $H$ (see response to comment \#2 from Reviewer \#2)
+**Response**: We have clarified $U$ and $H$ (see response to comment \#2 from Reviewer \#2, with changes incorporated into Section 2.3)
 
-4. page 7, line 23 and footnote: $x \hat \beta$ should be $x^T \beta$.
+**Comment 4**: page 7, line 23 and footnote: $x \hat \beta$ should be $x^T \beta$.
 
-**Response**: We have updated the text and footnote to correctly reflect that $x$ is transposed.
-We retained the hat over $\beta$ for consistency with our definition of $U(\hat{\beta})$ and $H(\hat{\beta})$ defined above.
+**Response**: We have updated the text on page 7 to correctly reflect that $x$ is transposed.
+We retained the hat over $\beta$ for consistency with our definition of $U(\hat{\beta})$ and $\mathcal{I}^{-1}(\hat{\beta})$.
+We deleted the footnote and its associated text in the paper because we felt the level of detail was unnecessary and we wanted to make room for text we added in response to other comments so that the length of the manuscript would stay approximately unchanged.
 
-5. Page 12, line 2: `number and density of layers` means `number and width of layers` or `number and dropout rates of layers`?
+**Comment 5**: Page 12, line 2: `number and density of layers` means `number and width of layers` or `number and dropout rates of layers`?
 
-**Response**: We have updated this sentence to provide more clarity and detail on how we tuned neural networks: "For neural networks, the number of layers (*i.e.*, length) and number of nodes in the layers (*i.e.*, width) was tuned, while dropout rate was fixed at 10\%, batch size was fixed at 32 observations, and the rectified linear unit activation function was applied.
+**Response**: We have updated this sentence to provide more clarity and detail on how we tuned neural networks. In Section 3.1.1, we now write
+
+"For neural networks, the number of layers (*i.e.*, length) and number of nodes in the layers (*i.e.*, width) was tuned, while dropout rate was fixed at 10\%, batch size was fixed at 32 observations, and the rectified linear unit activation function was applied.
 In addition, neural networks completed a maximum of 500 epochs, with possible early stopping based on prediction accuracy in a validation set comprising 25\% of its training data."
 
-6. For boosting, is the learning rate tuned? How are the neural networks tuned (depth and width of layers, drop out rate, etc)?
+**Comment 6**: For boosting, is the learning rate tuned? How are the neural networks tuned (depth and width of layers, drop out rate, etc)?
 
-**Response**: We have updated our description of tuning for neural networks (see previous response) and boosting.
-Our updated text for boosting is as follows: "Specifically, tuning for boosting models included identifying the number of steps to complete.
+**Response**: We have updated our description of tuning for neural networks (see previous response).
+We also included addition text to clarify the tuning procedure for boosting models.
+In Section 3.1.1, we write:
+
+"Tuning for boosting models included identifying the number of steps to complete.
 The maximum number of steps was 5000, the learning rate was fixed at 0.01, and early stopping was applied if there was no improvement in cross-validated negative log-likelihood for 25 steps."
 
-7.
-In general, the paper lacks details on how several competing learning methods are tuned.
+**Comment 7**: In general, the paper lacks details on how several competing learning methods are tuned.
 For reproducibility, (1) how the data sets are retrieved and pre-processed and (2) the code and script for numerical experiments need to be made public.
 
-**Response**: We have included more detail in the text regarding tuning of the competing learners (see response to comment 5 and 6), and have included details regarding tuning of competing learners in the 'Description' column of Table 1.
+**Response**: We have included more detail in the text regarding tuning of the competing learners (see responses to comments 5 and 6).
+Details regarding tuning of competing learners are also presented in the 'Description' column of Table 1.
 We have included details on how each data set was retrieved and pre-processed in the 'Data Sources' section of the Appendix.
@@
 
-8. Please briefly explain what nested cross-validation is.
+- instructions for reproducing the numeric experiments using only publicly available data are included in the repo's readMe file.
 
-**Response**: We have included a brief explanation in the update: "Nested cross-validation includes an 'inner' cross-validation loop to evaluate different specifications of tuning parameters and an 'outer' loop that evaluates the tuned model, providing an unbiased estimate of the underlying model and its tuning procedure"
+**Comment 8**: Please briefly explain what nested cross-validation is.
+
+**Response**: We have included a brief explanation in the update in Section 3.1.1: "Nested cross-validation includes an 'inner' cross-validation loop to evaluate different specifications of tuning parameters and an 'outer' loop that evaluates the tuned model, providing an unbiased estimate of the underlying model and its tuning procedure"

### 2023-06-05 paper/jcgs/reviewer-response/reviewer-response.md
NMP review incorporated

@@
 ```{=openxml}
-<w:p><w:pPr><w:jc w:val="center"/><w:pStyle w:val="Figure"/></w:pPr><w:r><w:rPr/><w:drawing xmlns:r="http://schemas.openxmlformats.org/officeDocument/2006/relationships"><wp:inline distT="0" distB="0" distL="0" distR="0"><wp:extent cx="5486400" cy="7315200"/><wp:docPr id="" name="" descr=""/><wp:cNvGraphicFramePr><a:graphicFrameLocks xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main" noChangeAspect="1"/></wp:cNvGraphicFramePr><a:graphic xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main"><a:graphicData uri="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:pic xmlns:pic="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:nvPicPr><pic:cNvPr id="" name=""/><pic:cNvPicPr><a:picLocks noChangeAspect="1" noChangeArrowheads="1"/></pic:cNvPicPr></pic:nvPicPr><pic:blipFill><a:blip cstate="print" r:embed="C:\Users\bjaeger\AppData\Local\Temp\RtmpKusyHF\file7834640464bb.png"/><a:stretch><a:fillRect/></a:stretch></pic:blipFill><pic:spPr bwMode="auto"><a:xfrm><a:off x="0" y="0"/><a:ext cx="76200" cy="101600"/></a:xfrm><a:prstGeom prst="rect"><a:avLst/></a:prstGeom><a:noFill/></pic:spPr></pic:pic></a:graphicData></a:graphic></wp:inline></w:drawing></w:r></w:p>
+<w:p><w:pPr><w:jc w:val="center"/><w:pStyle w:val="Figure"/></w:pPr><w:r><w:rPr/><w:drawing xmlns:r="http://schemas.openxmlformats.org/officeDocument/2006/relationships"><wp:inline distT="0" distB="0" distL="0" distR="0"><wp:extent cx="5486400" cy="7315200"/><wp:docPr id="" name="" descr=""/><wp:cNvGraphicFramePr><a:graphicFrameLocks xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main" noChangeAspect="1"/></wp:cNvGraphicFramePr><a:graphic xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main"><a:graphicData uri="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:pic xmlns:pic="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:nvPicPr><pic:cNvPr id="" name=""/><pic:cNvPicPr><a:picLocks noChangeAspect="1" noChangeArrowheads="1"/></pic:cNvPicPr></pic:nvPicPr><pic:blipFill><a:blip cstate="print" r:embed="C:\Users\bjaeger\AppData\Local\Temp\Rtmpu2OISd\file855872787561.png"/><a:stretch><a:fillRect/></a:stretch></pic:blipFill><pic:spPr bwMode="auto"><a:xfrm><a:off x="0" y="0"/><a:ext cx="76200" cy="101600"/></a:xfrm><a:prstGeom prst="rect"><a:avLst/></a:prstGeom><a:noFill/></pic:spPr></pic:pic></a:graphicData></a:graphic></wp:inline></w:drawing></w:r></w:p>
 ```
@@
 ```{=openxml}
-<w:p><w:pPr><w:jc w:val="center"/><w:pStyle w:val="Figure"/></w:pPr><w:r><w:rPr/><w:drawing xmlns:r="http://schemas.openxmlformats.org/officeDocument/2006/relationships"><wp:inline distT="0" distB="0" distL="0" distR="0"><wp:extent cx="5486400" cy="7315200"/><wp:docPr id="" name="" descr=""/><wp:cNvGraphicFramePr><a:graphicFrameLocks xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main" noChangeAspect="1"/></wp:cNvGraphicFramePr><a:graphic xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main"><a:graphicData uri="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:pic xmlns:pic="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:nvPicPr><pic:cNvPr id="" name=""/><pic:cNvPicPr><a:picLocks noChangeAspect="1" noChangeArrowheads="1"/></pic:cNvPicPr></pic:nvPicPr><pic:blipFill><a:blip cstate="print" r:embed="C:\Users\bjaeger\AppData\Local\Temp\RtmpKusyHF\file78341ecb6257.png"/><a:stretch><a:fillRect/></a:stretch></pic:blipFill><pic:spPr bwMode="auto"><a:xfrm><a:off x="0" y="0"/><a:ext cx="76200" cy="101600"/></a:xfrm><a:prstGeom prst="rect"><a:avLst/></a:prstGeom><a:noFill/></pic:spPr></pic:pic></a:graphicData></a:graphic></wp:inline></w:drawing></w:r></w:p>
+<w:p><w:pPr><w:jc w:val="center"/><w:pStyle w:val="Figure"/></w:pPr><w:r><w:rPr/><w:drawing xmlns:r="http://schemas.openxmlformats.org/officeDocument/2006/relationships"><wp:inline distT="0" distB="0" distL="0" distR="0"><wp:extent cx="5486400" cy="7315200"/><wp:docPr id="" name="" descr=""/><wp:cNvGraphicFramePr><a:graphicFrameLocks xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main" noChangeAspect="1"/></wp:cNvGraphicFramePr><a:graphic xmlns:a="http://schemas.openxmlformats.org/drawingml/2006/main"><a:graphicData uri="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:pic xmlns:pic="http://schemas.openxmlformats.org/drawingml/2006/picture"><pic:nvPicPr><pic:cNvPr id="" name=""/><pic:cNvPicPr><a:picLocks noChangeAspect="1" noChangeArrowheads="1"/></pic:cNvPicPr></pic:nvPicPr><pic:blipFill><a:blip cstate="print" r:embed="C:\Users\bjaeger\AppData\Local\Temp\Rtmpu2OISd\file855814fc1ad.png"/><a:stretch><a:fillRect/></a:stretch></pic:blipFill><pic:spPr bwMode="auto"><a:xfrm><a:off x="0" y="0"/><a:ext cx="76200" cy="101600"/></a:xfrm><a:prstGeom prst="rect"><a:avLst/></a:prstGeom><a:noFill/></pic:spPr></pic:pic></a:graphicData></a:graphic></wp:inline></w:drawing></w:r></w:p>
 ```

### 2023-06-05 paper/jcgs/main.Rnw
NMP review incorporated

@@
 Nested cross-validation includes an `inner' cross-validation loop to evaluate different specifications of tuning parameters and an `outer' loop that evaluates the tuned model, providing an unbiased estimate of the underlying model and its tuning procedure.
-Specifically, tuning for boosting models included identifying the number of steps to complete.
+Tuning for boosting models included identifying the number of steps to complete.
 The maximum number of steps was 5000, the learning rate was fixed at 0.01, and early stopping was applied if there was no improvement in cross-validated negative log-likelihood for 25 steps.
@@
 Each of $p$ predictor variables had a mean of zero, standard deviation of 1, and correlation with other predictor variables drawn at random between a lower and upper boundary.
-A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package \citep{simsurv, simsurv_paper} from a Weibull distribution.
+A time-to-event outcome with roughly 45\% of observations censored was generated using the \texttt{simsurv} package \citep{simsurv, simsurv_paper} from a Weibull distribution with scale parameter (\ie, \texttt{lambdas}) equal to 0.1 and shape parameter (\ie, \texttt{gammas}) equal to 1.5.
 The full predictor matrix (\ie, including interactions, non-linear mappings, and combinations) was used to generate the outcome.
@@
 While the current study advances the oblique RSF towards being scalable and interpretable, there remain several limitations that can be targeted in future studies.
-The validity of the Cox partial likelihood function depends on an assumption of non-informative censoring (\ie, true survival time and censoring time are independent given the predictors).
-Thus, the oblique RSF may be improved by incorporating methods to account for informative censoring prior to identifying a linear combination of variables \citet{cui2017consistency}.
+The validity of the Cox partial likelihood function depends on an assumption of non-informative censoring, therefore the oblique RSF could be improved by incorporating methods to account for informative censoring prior to identifying a linear combination of variables \citep{he2016proportional, cui2017consistency}.
 The accelerated oblique RSF does not account for competing risks, and biased estimation of incidence may occur when competing risks are ignored.

### 2023-06-05 README.Rmd
skip the ggplot2 warnings
editing for clarity

@@
   dpi = 300,
+  warning = FALSE,
   echo = FALSE,
@@
 
-In case you want a much quicker summary of the paper:
-
 - We made oblique RSFs faster and also developed a new method to estimate importance of individual predictors with them. These methods are available in the `aorsf` R package.
 
-- We find that the accelerated oblique RSF (`aorsf-fast` in the paper) is very fast.
-In fact, in a benchmark with 35 different risk prediction tasks, `aorsf-fast` was faster than all of the learners we analyzed, except for penalized Cox regression models (`glmnet-cox` in the paper).
+- We find that the accelerated oblique RSF (`aorsf-fast` in the paper) is fast and accurate.
+In a benchmark with 35 different risk prediction tasks, `aorsf-fast` was faster than all of the learners we analyzed except for penalized Cox regression models (`glmnet-cox` in the paper).
 __Figure__: Distribution of time taken to fit a prediction model and compute predicted risk.
@@
 
-- We find that `aorsf-fast` has the best index of prediction accuracy out of all the learners we evaluated: __Figure__: Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
+- We find that `aorsf-fast` has the best index of prediction accuracy out of all the learners we evaluated.
+__Figure__: Expected differences in index of prediction accuracy between the accelerated oblique random survival forest and other learning algorithms.
 A region of practical equivalence is shown by purple dotted lines, and a boundary of non-zero difference is shown by an orange dotted line at the origin.
@@
 
-We use `targets` to coordinate the general benchmark experiment and simulation study that are presented in this research, and hope that our use of `targets` also makes it easier for others to engage with our code.
+We use `targets` to coordinate our numerical experiments.
+Thus, our results on publicly available data can be reproduced by cloning our repo and running `tar_make()` with only publicly available data requested in the `targets` pipeline.
+Below are the steps involved:
 
-Our work can be reproduced, mostly.
-The only thing that can't be reproduced are the results based on datasets that we can't share with you.
-To replicate our work using publicly available data, you need to edit the vector of datasets passed into our `targets` pipeline (see `_targets.R`) so that it only contains publicly available data.
-Below is a code chunk showing which datasets you need to comment out:
+1. Clone our repo and open the associated Rstudio project.
+
+2. Open `packages.R` and ensure you have installed the R packages listed in this file.
+
+3.
+In `_targets.R`, edit the vector of datasets passed into our `targets` pipeline so that it only contains publicly available data.
+Below is a code chunk showing which datasets you need to comment out to request only the publicly available ones:
 
@@
 
-You'll still need to create the `nafld` data by running `nafld_build()`, which is an R function included in `R/nafld_build.R` that combines multiple datasets in the `survival` package into a dataset we analyzed in the current study.
+4.
+Create the `nafld` data by running `nafld_build()`, which is an R function included in `R/nafld_build.R` that combines multiple datasets in the `survival` package into a dataset we analyzed in the current study.
+An example of how this can be done is below:
 
-Once you've completed these steps and installed the packages listed in `packages.R`, all you need to do is run `targets::tar_make()`.
-However, it will take a very long time to make the pipeline as-is and I recommend setting `run_seed` to be `1:3` (see `_targets.R` to modify this value) to request only 3 replications of Monte-Carlo cross validation be completed.
-Also, you are free to use only a subset of the learners by commenting out the ones you don't want to run.
-Here is what I'd recommend if you'd like to speed up the pipeline:
+```{r, eval=FALSE}
+# load all R functions in the R directory
+R.utils::sourceDirectory("R")
+# load all relevant packages for this project
+source("packages.R")
+# run nafld_build() (takes several minutes)
+nafld_build()
+```
+
+5. Run `targets::tar_make()` to make the targets pipeline, but be aware that it will take a very long time to make the pipeline as-is.
+
+To make the process run quickly, I recommend setting `run_seed` to be `1:3` in `_targets.R` to request only 3 replications of Monte-Carlo cross validation be completed.
+Also in `_targets.R`, use a subset of the faster learners by commenting out the slower ones:
 

### 2023-06-08 paper/jcgs/main.Rnw
appendix kept separate as jcgs requests

@@
 We find in simulation studies that `negation VI' discriminates between relevant and irrelevant numeric predictors more accurately than permutation VI, Shapley VI, and a technique to measure VI using analysis of variance.
-All  oblique RSF methods in the current study are available in the \texttt{aorsf} R package.
+All  oblique RSF methods in the current study are available in the \texttt{aorsf} R package, and additional supplemental materials are available online.
 \end{abstract}
@@
 Designs and protocols for these studies have been made available \citep{aric1989atherosclerosis, bild2002multi, felker2017effect, sprint2015randomized, taylor2005toward}.
-All other datasets were publicly available and obtained through R packages (see Appendix A.1).
-Across all prediction tasks, the number of observations ranged from \Sexpr{nrow_min} to \Sexpr{nrow_max} (median: \Sexpr{nrow_median}), the number of predictors ranged from \Sexpr{ncol_min} to \Sexpr{ncol_max} (median: \Sexpr{ncol_median}), and the percentage of censored observations ranged from \Sexpr{pcens_min} to \Sexpr{pcens_max} (median: \Sexpr{pcens_median}) (\tabrefAppendix{tab:datasets}).
+All other datasets were publicly available and obtained through R packages (see Appendix A.1 in Supplementary Materials).
+Across all prediction tasks, the number of observations ranged from \Sexpr{nrow_min} to \Sexpr{nrow_max} (median: \Sexpr{nrow_median}), the number of predictors ranged from \Sexpr{ncol_min} to \Sexpr{ncol_max} (median: \Sexpr{ncol_median}), and the percentage of censored observations ranged from \Sexpr{pcens_min} to \Sexpr{pcens_max} (median: \Sexpr{pcens_median}) (\tabrefAppendix{tab:datasets} in Supplementary Materials).
 
@@
 
-A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all}.
+A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all} in Supplementary Materials.
 In total, \Sexpr{n_tasks_complete} out of \Sexpr{n_tasks_expected} Monte-Carlo cross validation runs were completed.
@@
 Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
-Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
+Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi} in Supplementary Materials.
 Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of \Sexpr{vi_times$aorsf_anova} seconds versus \Sexpr{vi_times$aorsf_negate} and \Sexpr{vi_times$aorsf_permute} seconds, respectively.
@@
 We have also introduced a general and flexible method to estimate VI with oblique RFs, and demonstrated its effectiveness for numeric, correlated predictors.
+
+\section{Supplementary Materials}
+
+Supplemental materials for the current analysis are available online.
+
+\begin{description}
+
+\item[Code] The code used to generate results in the current analysis are available online at \newline https://github.com/bcjaeger/aorsf-bench and provided as supplemental material (aorsf\_bench.zip).
+
+\item[aorsf] The R package used to fit oblique RSFs in the current analysis is available online at \newline https://github.com/ropensci/aorsf and version 0.0.7.9000 is provided as supplemental material (aorsf\_package.zip).
+
+\item[Appendix] Additional details on data used in the current analysis as well as additional details for numeric experiments (aorsf\_appendix.pdf).
+
+\end{description}
+
+\bibliographystyle{Chicago}
+
+\bibliography{main}
+
+\newpage
 
@@
 
-\bibliographystyle{Chicago}
-
-\bibliography{main}
 \end{document}

### 2023-06-08 paper/jcgs/main.tex
appendix kept separate as jcgs requests

@@
 Designs and protocols for these studies have been made available \citep{aric1989atherosclerosis, bild2002multi, felker2017effect, sprint2015randomized, taylor2005toward}.
-All other datasets were publicly available and obtained through R packages (see Appendix A.1).
-Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 1,384), the number of predictors ranged from 7 to 1,692 (median: 41), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 78.1) (\tabrefAppendix{tab:datasets}).
+All other datasets were publicly available and obtained through R packages (see Appendix A.1 in Supplementary Materials).
+Across all prediction tasks, the number of observations ranged from 137 to 17,549 (median: 1,384), the number of predictors ranged from 7 to 1,692 (median: 41), and the percentage of censored observations ranged from 5.26 to 97.7 (median: 78.1) (\tabrefAppendix{tab:datasets} in Supplementary Materials).
 
@@
 
-A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all}.
+A full summary of all results presented in this Section is provided in \tabrefAppendix{tab:bm_pred_all} in Supplementary Materials.
 In total, 871 out of 875 Monte-Carlo cross validation runs were completed.
@@
 Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.
-Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi}.
+Full results from the experiment are provided in \tabrefAppendix{tab:bm_vi} in Supplementary Materials.
 Computationally, ANOVA VI was faster than negation and permutation VI, with a median time of 2.88 seconds versus 20.4 and 21.8 seconds, respectively.
